### 2017-12-12 genus-one-relative-maps.tex
Started pdf

\documentclass[11pt]{amsart}
%\usepackage[english]{babel}
\usepackage{appendix}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
%\usepackage{showlabels}
\usepackage{hyperref}
\usepackage{amsthm}
\usepackage{marginnote}
\usepackage{stmaryrd}
\usepackage{enumitem}
\usepackage[english]{babel}
\usepackage{yfonts}
\usepackage[T1]{fontenc}
\usepackage[utf8x]{inputenc}
%\usepackage{enumerate}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{faktor}
\usepackage{xcolor}
\usepackage{xfrac}
\usepackage{tikz,tikz-cd}
\usetikzlibrary{decorations.pathmorphing,decorations.pathreplacing,patterns}
\usepackage[all]{xy}
\usepackage{bbm}
\usepackage{tabularx}
\usepackage{longtable}
\usepackage{tabu}
\usepackage{booktabs}
\usepackage{mathtools}

\newcommand{\TT}{\operatorname{T}}
\newcommand{\M}[4]{\overline{\mathcal{M}}_{#1,#2}(#3,#4)}
\newcommand{\Q}[4]{\mathcal{Q}_{#1,#2}(#3,#4)}
\newcommand{\Qe}[4]{\mathcal{Q}^{\epsilon}_{#1,#2}(#3,#4)}
\newcommand{\Qt}[4]{\widetilde{\mathcal Q}_{#1,#2}(#3,#4)}
\newcommand{\QG}[4]{\mathcal{Q}G_{#1,#2}(#3,#4)}
\newcommand{\QGe}[4]{\mathcal{Q}G^{\epsilon}_{#1,#2}(#3,#4)}
\newcommand{\D}[3]{\mathcal{D^Q}(#1,#2,#3)}
\newcommand{\E}[3]{\mathcal{E^Q}(#1,#2,#3)}
\newcommand{\PP}{\mathbb P}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\OO}{\mathcal{O}}
\renewcommand{\to}{\rightarrow}
\newcommand{\A}{\mathcal A}
\newcommand{\B}{\mathcal B}
\newcommand{\C}{\mathfrak C}
\newcommand{\EE}{\mathbf{E}}
\renewcommand{\L}{\mathcal L}
\newcommand{\LL}{\mathbf{L}}
\newcommand{\MM}{\mathfrak M}
\newcommand{\Aaff}{\mathbb{A}}
\newcommand{\kfield}{\Bbbk}
\newcommand{\comp}{\chi}
\newcommand{\sst}{\sigma^{\operatorname{ss}}}
\newcommand{\Pic}{\operatorname{Pic}}
\newcommand{\Def}{\operatorname{Def}}
\newcommand{\Spec}{\operatorname{Spec}}
\newcommand{\Proj}{\operatorname{Proj}}
\newcommand{\Hom}{\operatorname{Hom}}
\newcommand{\Ext}{\operatorname{Ext}}
\newcommand{\Gm}{\mathbb{G}_{\text{m}}}
\newcommand{\virt}[1]{[#1]^{\operatorname{virt}}}
\newcommand{\vip}[1]{[#1]^{\operatorname{prod}}}
\newcommand{\Id}{\operatorname{Id}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\QQ}{\mathbb{Q}}
\newcommand{\HH}{\operatorname{H}}
\newcommand{\Achow}{\operatorname{A}}
\newcommand{\pt}{\operatorname{pt}}
\newcommand{\bq}{\begin{equation}}
\newcommand{\eq}{\end{equation}}
\newcommand{\ba}{\begin{aligned}}
\newcommand{\ea}{\end{aligned}}
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}
\newcommand{\bsm}{\left(\begin{smallmatrix}}
\newcommand{\esm}{\end{smallmatrix}\right)}                   
\newcommand{\bpm}{\begin{pmatrix}}
\newcommand{\epm}{\end{pmatrix}}
\newcommand{\barr}{\begin{displaymath}\begin{array}{cccc}}
\newcommand{\earr}{\end{array}\end{displaymath}}
\newcommand{\barrl}{\begin{displaymath}\begin{array}{lcl}}
\newcommand{\earrl}{\end{array}\end{displaymath}}
\newcommand{\barl}{\begin{displaymath}\begin{array}{l}}
\newcommand{\earl}{\end{array}\end{displaymath}}
\newcommand{\bxym}{ \begin{displaymath}\xymatrix }
\newcommand{\exym}{\end{displaymath}}
\newcommand{\bcd}{\begin{center}\begin{tikzcd}}
\newcommand{\ecd}{\end{tikzcd}\end{center}}
\newcommand{\R}{\operatorname{R}^{\bullet}}
%\newcommand{\sslash}{\mathbin{/\mkern-6mu/}}
\newcommand{\tr}{{\rm tr}}
\newcommand{\Isom}{\text{Isom}}
\newcommand{\pr}{\operatorname{pr}}
\newcommand{\ev}{\operatorname{ev}}
\newcommand{\codim}{\operatorname{codim}}
\newcommand{\vdim}{\operatorname{vdim}}
\newcommand{\ildef}[1]{\emph{#1}}
\newcommand{\om}[1]{\mathcal{#1}}
\newcommand{\h}{\operatorname{h}}
\newcommand{\Aut}{\operatorname{Aut}}
\newcommand{\RR}{\textbf{R}}
\newcommand{\NN}{\operatorname{N}}

\theoremstyle{definition}
\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{lemma}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary}
\newtheorem*{teo*}{Theorem}
\newtheorem{ipotesi}{ipotesi}
\newtheorem*{nota}{Nota}
\newtheorem{claim}{Claim}
\newtheorem{question}[thm]{Question}
\newtheorem{conj}[thm]{Conjecture}

\newtheorem{innercustomthm}{Theorem}
\newenvironment{customthm}[1]
  {\renewcommand\theinnercustomthm{#1}\innercustomthm}
  {\endinnercustomthm}

\theoremstyle{definition}
\newtheorem{example}[thm]{Example}
\newtheorem{ex}[thm]{Example}
\newtheorem{dfn}[thm]{Definition}
\newtheorem{definition}[thm]{Definition}
\newtheorem{aside}[thm]{Aside}
\newtheorem{remark}[thm]{Remark}
\newtheorem{com}[thm]{Comment}
\newtheorem{num}{Number}
\newtheorem*{sketch}{Sketch}
\newtheorem*{rem}{Remark}
\newtheorem*{aside*}{Aside}
\newtheorem*{acknowledgements}{Acknowledgements}

\newcommand{\ilemph}[1]{\emph{#1}}

\setcounter{tocdepth}{1}

\newcommand{\todo}[1]{\vspace{5mm}\par \noindent
\framebox{\begin{minipage}[c]{0.95 \textwidth} \tt #1\end{minipage}} \vspace{5mm} \par}

\def\ti{-\allowhyphens}
\newcommand{\thismonth}{\ifcase\month % case 0 --- impossible!
  \or January\or February\or March\or April\or May\or June%
  \or July\or August\or September\or October\or November%
  \or December\fi}
\newcommand{\thismonthyear}{{\thismonth} {\number\year}}
\newcommand{\thisdaymonthyear}{{\number\day} {\thismonth} {\number\year}}

\usepackage[T1]{fontenc}
\usepackage{newpxtext,newpxmath}

\title[Genus One Radial Maps]{Relative Stable Maps in Genus One via Radial Alignments}
\author{Luca Battistella and Navid Nabijou}
\begin{document}

%\begin{abstract} \end{abstract}

\maketitle
%\appendixtitletocoff
%\tableofcontents

\section{Relative space equals closure of the nice locus}
Have to show that given a relative map, we can smooth it to one in the nice locus.

\newpage
\bibliographystyle{alpha}
\bibliography{relqm}

\bigskip\bigskip

\noindent Luca Battistella\\
Department of Mathematics, Imperial College London \\
\texttt{l.battistella14@imperial.ac.uk}\\

\noindent Navid Nabijou \\
Department of Mathematics, Imperial College London \\
\texttt{navid.nabijou09@imperial.ac.uk}

\end{document}

### 2017-12-12 genus-one-relative-maps.tex
Started writing smoothing of non-contracted genus one internal component

@@
 \section{Relative space equals closure of the nice locus}
-Have to show that given a relative map, we can smooth it to one in the nice locus.
+Have to show that given a relative map, we can smooth it to one in the nice locus. This is done by considering different cases locally, then glueing.
+
+\subsection*{Case 1: non-contracted genus one internal component} Assume that the curve takes the form
+\begin{equation*} C = C_0 \cup C_1 \cup \ldots \cup C_k \end{equation*}
+where all the $C_i$ are smooth, $C_0$ has genus one, all the other $C_i$ have genus zero, and for $i = 1,\ldots,k$, $C_i$ intersects $C_0$ at a single node (denoted $q_i$) and does not intersect any other components.
+
+Suppose furthermore that $C_0$ is an \emph{internal component}, meaning that it is mapped into $H$ via $f$, and that $C_1$,\ldots,$C_k$ are \emph{external components}, meaning that they are not mapped into $H$ via $f$.
+The picture is:
+
+[FIGURE]
+
+Suppose that this is a relative stable map.
+This means that [BLAH].
+We claim that it can be smoothed to a relative stable map in the nice locus.
+The construction depends on choosing an appropriate smoothing of the curve $C$, so that the map also smooths.
+
+We start with $W = C_0 \times \Aaff^1_t$ (where $t$ denotes a fixed co-ordinate on the affine line).
+This is a smooth surface, fibred over $\Aaff^1_t$, with fibre equal to the elliptic curve $C_0$.
+Consider the points $q_1, \ldots, q_k$ on $C_0$.
+We will perform a series of weighted blow-ups at the points $(q_i,0) \in W$, in order to obtain a surface whose general fibre is smooth (in fact, isomorphic to $C_0$) and whose central fibre is isomorphic to $C$.
 

### 2017-12-16 genus-one-relative-maps.tex
More on setting up notation for blowup

@@
 \section{Relative space equals closure of the nice locus}
-Have to show that given a relative map, we can smooth it to one in the nice locus. This is done by considering different cases locally, then glueing.
+Since the log structures only come into play when the source curve is reducible, it follows that the nice locus in the radially aligned setting is the same as the nice locus in the ordinary setting.
+In particular, it is irreducible.
+
+We now want to show that the relative space in the radially aligned setting is equal to the closure of the nice locus; irreducibility follows immediately. One direction is clear: [WHY?]
+
+It thus remains to show that, given a relative radially aligned map, we can smooth it to one in the nice locus. This is done by considering different cases locally, then glueing.
 
@@
 Suppose furthermore that $C_0$ is an \emph{internal component}, meaning that it is mapped into $H$ via $f$, and that $C_1$,\ldots,$C_k$ are \emph{external components}, meaning that they are not mapped into $H$ via $f$.
+Finally, suppose that $f$ is not constant on $C_0$.
 The picture is:
@@
 We will perform a series of weighted blow-ups at the points $(q_i,0) \in W$, in order to obtain a surface whose general fibre is smooth (in fact, isomorphic to $C_0$) and whose central fibre is isomorphic to $C$.
+
+Fix $i =1,\ldots,k$ and let $m_i$ be the multiplicity of $f$ with $H$ at $q_i \in C_i$. We define:
+\begin{equation*} \beta = \prod_{i=1}^k m_i \qquad r_i = \beta/m_i \end{equation*}
 

### 2017-12-17 genus-one-relative-maps.tex
More thing on line bundle

@@
 
-It thus remains to show that, given a relative radially aligned map, we can smooth it to one in the nice locus. This is done by considering different cases locally, then glueing.
+It thus remains to show that, given a relative radially aligned map, we can smooth it to one in the nice locus. This is done by considering different cases locally, then gluing.
 
@@
 
-Suppose furthermore that $C_0$ is an \emph{internal component}, meaning that it is mapped into $H$ via $f$, and that $C_1$,\ldots,$C_k$ are \emph{external components}, meaning that they are not mapped into $H$ via $f$.
-Finally, suppose that $f$ is not constant on $C_0$.
+Suppose furthermore that $C_0$ is a non-contracted \emph{internal component}, meaning that it is mapped into $H$ via $f$, and that $C_1$,\ldots,$C_k$ are \emph{external components}, meaning that they are not mapped into $H$ via $f$.
 The picture is:
@@
 \begin{equation*} \beta = \prod_{i=1}^k m_i \qquad r_i = \beta/m_i \end{equation*}
+We now blow-up the surface $W$ at the points $(q_i,0)$ with weight $r_i$ in the horizontal direction and weight $1$ in the vertical direction: if $x_i$ is a local co-ordinate for the fibre around $q_i$, this means that we blow-up in the ideal $(x_i,t^{r_i})$.
+
+The result is a fibred surface $W^\prime \to \Aaff^1_t$ with general fibre isomorphic to $C_0$ and central fibre isomorphic to $C$.
+The total space of $W^\prime$ is no longer smooth, but this is fine; the projection to $\Aaff^1_t$ is still flat.
+The central fibre is a linearly trivial Cartier divisor:
+\begin{equation*} W^\prime_0 = C_0 + C_1 + \ldots + C_k = 0 \in \Pic W^\prime \end{equation*}
+The $C_i$ are not themselves Cartier, but $r_i  C_i$ is Cartier for $i=1,\ldots,k$. We have:
+\begin{equation*} r_i C_i \cdot C_0 = 1 \end{equation*}
+Now, let $x_1,\ldots,x_n$ denote the marked points of $C$.
+These are divisors on the central fibre $W^\prime_0$, and hence can be extended to divisors $\tilde{x}_1,\ldots,\tilde{x}_n$ on $W^\prime$.
+Consider the line bundle:
+\begin{equation*} \tilde{L} = \OO_{W^\prime}(\beta C_0 + \Sigma_{i=1}^n \alpha_i \tilde{x}_i) \end{equation*}
+Note that $\beta C_0$ is indeed a Cartier divisor, since
+\begin{equation*} \beta C_0 = - \sum_{i=1}^k \beta C_i = - \sum_{i=1}^k m_i (r_i C_i) \end{equation*}
+and the $r_i C_i$ are Cartier. We claim that when we restrict $\tilde{L}$ to the central fibre we recover the line bundle $L = f^* \OO(1)$ that we started with.
+
+For $i=1,\ldots,k$, we have:
+\begin{align*} \tilde{L}|_{C_i} & = \OO_{C_i} \left( \beta (C_0 \cdot C_i) q_i + \Sigma_{x_j \in C_i} \alpha_j x_j \right) \\
+& = \OO_{C_i} \left( (\beta/r_i) q_i + \Sigma_{x_j \in C_i} \alpha_j x_j \right)\\
+& = \OO_{C_i} \left( m_i q_i + \Sigma_{x_j \in C_i} \alpha_j x_j \right) \\
+& = L|_{C_i} \end{align*}
+On the other hand
+\begin{align*} \tilde{L}|_{C_0} & = \OO_{C_0} \left( - \sum_{i=1}^k \beta (C_i \cdot C_0) q_i + \sum_{x_j \in C_0} \alpha_j x_j \right) \\
+& = \OO_{C_0} \left( - \sum_{i=1}^k m_i q_i + \sum_{x_j \in C_0} \alpha_j x_j \right) \\
+& = L|_{C_0} \end{align*}
+and the fact that $\tilde{L}|_{W^\prime_0} = L$ follows from the fact that the dual intersection graph of $C$ has genus zero.
+
+Now, $\tilde{L}$ comes with a unique section whose restriction to $W^\prime_0 \cong C$ is $s_0$.
+After we extend the sections $s_1,\ldots,s_N$, it is clear that the resulting stable map is in the nice locus (i.e.
+that it is not mapped into $H$).
+
+Now, to extend the sections $s_1,\ldots,s_N$, we simply check that they are unobstructed. The space containing the obstructions is:
+\begin{equation*} \HH^1(C,L) \end{equation*} \marginpar{Is this true even when $C$ is reducible}
+By taking the normalisation exact sequence for $C$, tensoring with $L$ and passing to cohomology, we obtain:
 

### 2017-12-17 genus-one-relative-maps.tex
Expository changes

--- 2017-12-16 genus-one-relative-maps.tex
@@
 \begin{equation*} C = C_0 \cup C_1 \cup \ldots \cup C_k \end{equation*}
-where all the $C_i$ are smooth, $C_0$ has genus one, all the other $C_i$ have genus zero, and for $i = 1,\ldots,k$, $C_i$ intersects $C_0$ at a single node (denoted $q_i$) and does not intersect any other components.
+where all the $C_i$ are smooth, $C_0$ has genus one, all the other $C_i$ have genus zero, and for $i \in \{1,\ldots,k\}$, $C_i$ intersects $C_0$ at a single node (denoted $q_i$) and does not intersect any other components.
 
-Suppose furthermore that $C_0$ is an \emph{internal component}, meaning that it is mapped into $H$ via $f$, and that $C_1$,\ldots,$C_k$ are \emph{external components}, meaning that they are not mapped into $H$ via $f$.
-Finally, suppose that $f$ is not constant on $C_0$.
+Suppose furthermore that $C_0$ is a non-contracted \emph{internal component}, meaning that it is mapped into $H$ via $f$, and that $C_1$,\ldots,$C_k$ are \emph{external components}, meaning that they are not mapped into $H$ via $f$.
 The picture is:
@@
 
-Fix $i =1,\ldots,k$ and let $m_i$ be the multiplicity of $f$ with $H$ at $q_i \in C_i$. We define:
-\begin{equation*} \beta = \prod_{i=1}^k m_i \qquad r_i = \beta/m_i \end{equation*}
+Fix $i \in \{1,\ldots,k\}$ and let $m_i$ be the multiplicity of $f$ with $H$ at $q_i \in C_i$. We define:
+\begin{equation*} l = \operatorname{lcm}(m_1,\ldots,m_k) \qquad r_i = l/m_i \end{equation*}
+We now blow-up the surface $W$ at the points $(q_i,0)$ with weight $r_i$ in the horizontal direction and weight $1$ in the vertical direction: if $x_i$ is a local co-ordinate for the fibre around $q_i$, this means that we blow-up in the ideal $(x_i,t^{r_i})$.
+
+The result is a fibred surface $W^\prime \to \Aaff^1_t$ with general fibre isomorphic to $C_0$ and central fibre isomorphic to $C$.
+The total space of $W^\prime$ is no longer smooth, but this is fine; the projection to $\Aaff^1_t$ is still flat.
+The central fibre is a linearly trivial Cartier divisor:
+\begin{equation*} W^\prime_0 = C_0 + C_1 + \ldots + C_k = 0 \in \Pic W^\prime \end{equation*}
+Fix $i \in \{1,\ldots,k\}$; then $r_i C_i$ is Cartier, although $C_i$ may not necessarily be. Furthermore, since
+\begin{equation*} l C_0 = - \sum_{i=1}^k l C_i = - \sum_{i=1}^k m_i (r_i C_i) \end{equation*}
+in $A_1(W^\prime)$, it follows that $lC_0$ is Cartier. Finally, a local computation shows that
+\begin{equation*} r_i C_i \cdot C_0 = 1 \end{equation*}
+for $i \in \{1,\ldots,k\}$.
+Now, let $x_1,\ldots,x_n$ denote the marked points of $C$.
+These are smooth points of the central fibre $W^\prime_0$, and hence can be extended to Cartier divisors $\tilde{x}_1,\ldots,\tilde{x}_n$ on $W^\prime$.
+Consider the line bundle:
+\begin{equation*} \tilde{L} = \OO_{W^\prime}(l C_0 + \Sigma_{j=1}^n \alpha_j \tilde{x}_j) \end{equation*}
+on $W^\prime$.
+We claim that this gives a smoothing of the line bundle $L=f^*\OO(1)$ on $C$, i.e.
+that $\tilde{L}|_{W^\prime_0} = L$.
+We show this by first restricting $\tilde{L}$ to each of the components $C_i$ of $W^\prime_0 \cong C$.
+For $i \in \{1,\ldots,k\}$, we have
+\begin{align*} \tilde{L}|_{C_i} & = \OO_{C_i} \left( (l C_0 \cdot C_i) q_i + \sum_{x_j \in C_i} \alpha_j x_j \right) = \OO_{C_i} \left( (l/r_i) q_i + \sum_{x_j \in C_i} \alpha_j x_j \right)\\
+& = \OO_{C_i} \left( m_i q_i + \sum_{x_j \in C_i} \alpha_j x_j \right) = L|_{C_i} \end{align*}
+while for $i=0$ we have:
+\begin{align*} \tilde{L}|_{C_0} & = \OO_{C_0} \left( - \sum_{i=1}^k (l C_i \cdot C_0) q_i + \sum_{x_j \in C_0} \alpha_j x_j \right) = \OO_{C_0} \left( - \sum_{i=1}^k m_i q_i + \sum_{x_j \in C_0} \alpha_j x_j \right)  = L|_{C_0} \end{align*}
+Finally the fact that $\tilde{L}|_{W^\prime_0} = L$ follows from the fact that the dual intersection graph of $C$ has genus zero.
+
+Now, $\tilde{L}$ comes with a unique section whose restriction to $W^\prime_0 \cong C$ is $s_0$.
+After we extend the sections $s_1,\ldots,s_N$, it is clear that the resulting stable map is in the nice locus (i.e.
+that it is not mapped into $H$).
+
+Now, to extend the sections $s_1,\ldots,s_N$, we simply check that they are unobstructed. The space containing the obstructions is:
+\begin{equation*} \HH^1(C,L) \end{equation*} \marginpar{Is this true even when $C$ is reducible}
+By taking the normalisation exact sequence for $C$, tensoring with $L$ and passing to cohomology, we obtain:
 

### 2017-12-18 genus-one-relative-maps.tex
Finished smoothing of comb component, without log structures

@@
 
-The result is a fibred surface $W^\prime \to \Aaff^1_t$ with general fibre isomorphic to $C_0$ and central fibre isomorphic to $C$.
-The total space of $W^\prime$ is no longer smooth, but this is fine; the projection to $\Aaff^1_t$ is still flat.
+The result is a fibred surface $W^\prime \to \Aaff^1_t$ with general fibre equal to $C_0$ and central fibre $W^\prime_0 \cong C$.
+The total space of $W^\prime$ is no longer smooth (its singular points are [BLAH]), but this is not a problem since the projection to $\Aaff^1_t$ is still flat.
 The central fibre is a linearly trivial Cartier divisor:
 \begin{equation*} W^\prime_0 = C_0 + C_1 + \ldots + C_k = 0 \in \Pic W^\prime \end{equation*}
-Fix $i \in \{1,\ldots,k\}$; then $r_i C_i$ is Cartier, although $C_i$ may not necessarily be. Furthermore, since
+For $i \in \{1,\ldots,k\}$ we have that $r_i C_i$ is Cartier, although the same is not necessarily true of $C_i$. Furthermore, since
 \begin{equation*} l C_0 = - \sum_{i=1}^k l C_i = - \sum_{i=1}^k m_i (r_i C_i) \end{equation*}
@@
 
-Now, to extend the sections $s_1,\ldots,s_N$, we simply check that they are unobstructed. The space containing the obstructions is:
-\begin{equation*} \HH^1(C,L) \end{equation*} \marginpar{Is this true even when $C$ is reducible}
-By taking the normalisation exact sequence for $C$, tensoring with $L$ and passing to cohomology, we obtain:
+In order to extend the sections $s_1,\ldots,s_N$, we simply check that they are unobstructed. The space containing the obstructions to extending the sections is:
+\begin{equation*} \HH^1(C,L) \end{equation*}
+\marginpar{Is this true even when $C$ is reducible}By taking the normalisation exact sequence for $C$, tensoring with $L$ and passing to cohomology, we obtain an exact sequence:
+\begin{align*} 0 \to & \HH^0(C,L) \to \bigoplus_{i=0}^k \HH^0(C_i,L) \xrightarrow{\theta} \bigoplus_{i=1}^k L_{q_i} \to \\
+\to & \HH^1(C,L) \to \bigoplus_{i=0}^k \HH^1(C_i,L) \to 0 \end{align*}
+Now, each of $C_1,\ldots,C_k$ is isomorphic to $\PP^1$ and $L|_{C_i}$ has non-negative degree. Hence the map $\theta$ is surjective. Thus the map
+\begin{equation*} \HH^1(C,L) \to \bigoplus_{i=0}^k \HH^1(C_i,L) \end{equation*}
+is an isomorphism. But $\HH^1(C_i,L)=0$ for $i \in \{1,\ldots,k\}$ since $C_i \cong \PP^1$ and $L|_{C_i}$ has non-negative degree, and by Serre duality
+\begin{equation*} \HH^1(C_0,L) \cong \HH^0(C_0, L^\vee \otimes \omega_{C_0}) = \HH^0(C_0,L^\vee) = 0 \end{equation*}
+where the penultimate equality holds because $\operatorname{g}(C_0)=1$ and the last equality holds because $L|_{C_0}$ has \emph{strictly} positive degree (here we are using the fact that $f|_{C_0}$ is non-constant).
+
+To conclude, we have a family $\tilde{C} = W^\prime$ of nodal curves and a map from this family to $\PP^N$
+\bcd
+\tilde{C} \ar[r,"\tilde{f}"] \ar[d,"\pi"] & \PP^N \\
+\Aaff^1_t & \,
+\ecd
+such that when we restrict to $0 \in \Aaff^1_t$ we get $C \to \PP^N$ and such that the general fibre is an element of the nice locus.
 

### 2017-12-18 genus-one-relative-maps.tex
More additions to smoothing of comb component

@@
 \to & \HH^1(C,L) \to \bigoplus_{i=0}^k \HH^1(C_i,L) \to 0 \end{align*}
-Now, each of $C_1,\ldots,C_k$ is isomorphic to $\PP^1$ and $L|_{C_i}$ has non-negative degree. Hence the map $\theta$ is surjective. Thus the map
+Now, each of $C_1,\ldots,C_k$ is isomorphic to $\PP^1$ and $L|_{C_i}$ has non-negative degree; hence the map $\theta$ is surjective. Thus the map
 \begin{equation*} \HH^1(C,L) \to \bigoplus_{i=0}^k \HH^1(C_i,L) \end{equation*}
-is an isomorphism. But $\HH^1(C_i,L)=0$ for $i \in \{1,\ldots,k\}$ since $C_i \cong \PP^1$ and $L|_{C_i}$ has non-negative degree, and by Serre duality
+is an isomorphism. But $\HH^1(C_i,L)=0$ for $i \in \{1,\ldots,k\}$ since $C_i \cong \PP^1$ and $L|_{C_i}$ has non-negative degree; also we have by Serre duality
 \begin{equation*} \HH^1(C_0,L) \cong \HH^0(C_0, L^\vee \otimes \omega_{C_0}) = \HH^0(C_0,L^\vee) = 0 \end{equation*}
@@
 \ecd
-such that when we restrict to $0 \in \Aaff^1_t$ we get $C \to \PP^N$ and such that the general fibre is an element of the nice locus.
+such that when we restrict to $0 \in \Aaff^1_t$ we recover the map $f\colon C \to \PP^N$ and such that the general fibre is an element of the nice locus.
 

### 2017-12-20 genus-one-relative-maps.tex
added definition of central alignment and the relative space

@@
 
+\newcommand{\plC}{\scalebox{0.8}[1.3]{$\sqsubset$}}
+
 \newcommand{\TT}{\operatorname{T}}
+\newcommand{\oM}{\overline{\mathcal{M}}}
 \newcommand{\M}[4]{\overline{\mathcal{M}}_{#1,#2}(#3,#4)}
@@
 \newcommand{\Z}{\mathbb{Z}}
+\newcommand{\tVZc}{\widetilde{\mathcal{V\!Z}}^{\rm{ctr}}_{1,n}}
 \newcommand{\N}{\mathbb{N}}
@@
 
+Recall \cite[Proposition 4.6.2.2]{RSPW}:
+\begin{prop}
+The morphism $\MM^{\rm{ctr}}_{1,n}\to\MM^{\dagger}_{1,n}$ is a log-modification.
+\end{prop}
+
+Explanation: this is a local statement so I can probably reduce to an atomic neighbourhood $S$ of a point $p$.
+$S$ and the curve over it are endowed with the minimal log structure; let $P=\oM_p$ determine a chart for this log structure.
+Observe that the subcurve $\plC_0$ of the tropicalisation $\plC$ of $C_p$ determines a subset $\rm{MinPos}$ of the set of vertices, namely those adjacent to $\plC_0$.
+Perform the following log-blowups: consider the set of primitive values of the function $\lambda\colon \plC\to P$, and blow up the ideal that they generate; now locally the set of values of $\lambda$ is principal with generator $p$: blow up the ideal generated by $\{\lambda(v)-p\}\setminus\{-p\}$.
+Keep going until $\lambda(v_i)$ is reached for some $v_i\in\rm{MinPos}$; at this point stop and declare the contraction radius $\delta:=\lambda(v_i)$.
+Finish by adjoining $\lambda(v)-\delta$ for all the vertices untouched to this stage.
+This shows that the choice of $\delta$ is not an extra degree of freedom.\marginpar{do I sound like a physicist?}
+
 \section{Relative space equals closure of the nice locus}
+Recall the definition of maps from centrally aligned curves via the cartesian diagram:
+\bcd
+\tVZc(X,\beta)\ar[d]\ar[r]\ar[dr,phantom,"\Box"] & \M{1}{n}{X}{\beta}\ar[d] \\
+\MM_{1,n}^{\rm{ctr}}\ar[r] & \MM_{1,n}^{\dagger}
+\ecd
+
+\begin{dfn}
+The centrally aligned relative space is defined within $\tVZc(Y,\beta)$ by the following:
+\begin{itemize}
+\item \emph{factorisation condition}: the map $f\colon C\to X$ factors through the associated contraction to a Smyth's singularity:
+\bcd
+\widetilde C\ar[r]\ar[d] & \overline C\ar[d,"\bar f"] \\
+C\ar[r,"f"] & X
+\ecd
+
+\item \emph{Gathmann's relative condition}: for every connected component $Z$ of $f^{-1}(Y)$, either $Z$ is a point and, if it is marked $Z=x_i$, the multiplicity of $f$ at $x_i$ along $Y$ is at least $\alpha_i$; or $Z$ is a curve and $f^*\OO_X(Y)-\sum_{x_i\in Z}\alpha_ix_i$ is effective.
+Notice that $Z$ is at most genus $1$ and every line bundle of positive degree on a Gorenstein irreducible genus $1$ curve is effective, hence this condition can be rephrased as: the numerical condition
+\[f_*[Z]\cdot Y+\sum_{j=1}^r m^{(j)}\geq \sum_{x_i\in Z}\alpha_i,\]
+and, in case the numerical equality holds, the following equality of line bundles:
+\[f_{\lvert Z}^*\OO_X(Y)=\OO_Z\left(\sum_{x_i\in Z}\alpha_ix_i - \sum_{j=1}^r m^{(j)}y_j\right)\in\Pic(Z).\]
+
+\item \emph{novel condition}: there are no two vertices of $\rm{MinPos}$ closest to the circuit (i.e.
+$v_1\neq v_2\in \rm{MinPos}$ with $\delta=\lambda(v_1)=\lambda(v_2)$) unless the corresponding $m^{(j_1)}$ and $m^{(j_2)}$ are equal.
+\end{itemize}
+\end{dfn}
+
 Since the log structures only come into play when the source curve is reducible, it follows that the nice locus in the radially aligned setting is the same as the nice locus in the ordinary setting.

### 2017-12-20 genus-one-relative-maps.tex
Added reference for deformation theory of line bundle and sections on arbitrary scheme: Jie Wang

@@
 
-In order to extend the sections $s_1,\ldots,s_N$, we simply check that they are unobstructed. The space containing the obstructions to extending the sections is:
+In order to extend the sections $s_1,\ldots,s_N$, we simply check that they are unobstructed. The space containing the obstructions to extending the sections is \cite[Theorem 3.1]{WangDeformations}:
 \begin{equation*} \HH^1(C,L) \end{equation*}
-\marginpar{Is this true even when $C$ is reducible}By taking the normalisation exact sequence for $C$, tensoring with $L$ and passing to cohomology, we obtain an exact sequence:
+By taking the normalisation exact sequence for $C$, tensoring with $L$ and passing to cohomology, we obtain an exact sequence:
 \begin{align*} 0 \to & \HH^0(C,L) \to \bigoplus_{i=0}^k \HH^0(C_i,L) \xrightarrow{\theta} \bigoplus_{i=1}^k L_{q_i} \to \\

### 2017-12-20 genus-one-relative-maps.tex
dimension computation to see the novel condition is necessary

--- 2017-12-20 genus-one-relative-maps.tex
@@
 
-Since the log structures only come into play when the source curve is reducible, it follows that the nice locus in the radially aligned setting is the same as the nice locus in the ordinary setting.
+Here is one example where we show by a dimensional computation that the novel condition must be included if we hope to determine the closure of the nice locus.
+\begin{example}
+Consider $\M{1}{(3)}{\PP^1|H}{3}$.
+The virtual dimension is $7-3=4$.
+Here is a parametrisation of the nice locus: choose an element $(E,p)$ of $\oM_{1,1}\setminus\partial\oM_{1,1}$ (which has dimension $1$), let then $s_0\colon\OO_E\hookrightarrow\OO_E(3p)$ and $s_1$ be any section of $\OO_E(3p)$ not vanishing at $p$ (notice that $h^0(E,\OO_E(3p))=3$).
+Consider now the following weighted graph for a map in the boundary:
+\begin{center}
+\begin{tikzpicture}
+\draw[color=brown] (0,0) node[left]{$E$} -- (4,0);
+\draw[fill=black] (1,0) circle[radius=2pt] node[above]{$x_1$};
+\draw[fill=black] (2,0) circle[radius=2pt] node[below right]{$y_1$};
+\draw[fill=black] (3,0) circle[radius=2pt] node[below right]{$y_2$};
+\draw (2,1.5) node[left]{$R_1$} (3,1.5) node[left]{$R_2$};
+\draw (2,-1) -- (2,2) node[above]{$2$} (3,-1) -- (3,2) node[above]{$1$};
+\draw[->] (5,0.5) -- (8,0.5);
+\draw (9,-1) -- (9,2) node[above]{$\PP^1$};
+\draw[fill=black] (9,0) circle[radius=2pt] node[right]{$H$};
+\end{tikzpicture}
+\end{center}
+where the brown line represents a contracted genus $1$ curve.
+Now $(E,x_1,y_1,y_2)$ is a point of $\oM_{1,3}$ subject to the divisorial condition $3x_1-2y_1-y_2=0\in A_0(E)$; furthermore we have to choose the second ramification value of the $2\colon 1$ map from $R_1$ to $\PP^1$.
+This already makes up for a $3$-dimensional moduli space of degenerate relative maps corresponding to such a graph.
+The minimal log structure for this curve has a chart from $\-mathbb N^2$, with generators $e_1$ and $e_2$ corresponding to the smoothing parameters of the two nodes.
+If we allowed $e_1$ and $e_2$ to be identified in the characteristic sheaf, then we would get an extra $\Gm$ of choices for the log structure, so in total a $4$-dimensional moduli space.
+There is no chance this could live in the closure of the nice locus.
+\end{example}
+
+Thanks to the compatibility of $\delta$ (the contraction radius) with the stable map, namely the subcurve $C_0$ where $\lambda<\delta$ is the maximal connected subcurve of genus $1$ contracted by $f$, when the source curve is irreducible we have $\delta=0$, which is already ordered in every path to infinity.
+Hence the log structures only come into play when the source curve is reducible.
+We see then the nice locus in the radially aligned setting is the same as the nice locus in the ordinary setting.
 In particular, it is irreducible.
+
+\begin{lem}
+The nice locus is irreducible.
+\end{lem}
+\begin{proof}
+A parametrisation is given by
+\end{proof}
 

### 2017-12-21 genus-one-relative-maps.tex
heuristics for the novel condition is satisfied on the closure of the nice locus

@@
 \newcommand{\C}{\mathfrak C}
+\newcommand{\cC}{\mathcal C}
 \newcommand{\EE}{\mathbf{E}}
@@
 \begin{proof}
-A parametrisation is given by
+A parametrisation can be given from the vector bundle:
+\[ \operatorname{Vb}\left(\pi_*\OO_{\mathcal E}(\sum_{j=n+1}^{n+\delta}\sigma_j)\oplus\pi_*\OO_{\mathcal E}(\sum_{j=1}^{n+\delta}\sigma_j)^{\oplus r}\right) \quad \text{on} \quad \mathcal{M}_{1,n+\delta}\]
+where $\pi\colon\mathcal E\to\mathcal M$ is the universal curve and $\delta=d-\sum\alpha_i$.
 \end{proof}
 
-We now want to show that the relative space in the radially aligned setting is equal to the closure of the nice locus; irreducibility follows immediately. One direction is clear: [WHY?]
+We now want to show that the relative space in the radially aligned setting is equal to the closure of the nice locus; irreducibility follows immediately.
 
-It thus remains to show that, given a relative radially aligned map, we can smooth it to one in the nice locus. This is done by considering different cases locally, then gluing.
+\begin{lem}
+The closure of the nice locus is contained in the relative space.
+\end{lem}
+\begin{proof}
+We address the relative conditions one at a time. Notice that they are all obviuously satisfied on the nice locus.
+\begin{itemize}
+\item The factorisation property is closed: see \cite[Theorem 4.3]{RSPW}.
+\item Gathmann's relative condition is closed: see \cite[Proposition 4.9]{Vre}.
+\item The novel condition is satisfied on the closure of the nice locus. Here is no proof but some heuristics. Consider for example a map similar to the one above:
+\begin{center}
+\begin{tikzpicture}
+\draw[color=brown] (0,0) node[left]{$E$} -- (4,0);
+\draw[fill=black] (1,0) circle[radius=2pt] node[above]{$x_1$};
+\draw[fill=black] (2,0) circle[radius=2pt] node[below right]{$y_1$};
+\draw[fill=black] (3,0) circle[radius=2pt] node[below right]{$y_2$};
+\draw (2,1.5) node[left]{$R_1$} (3,1.5) node[left]{$R_2$};
+\draw (2,-1) -- (2,2) node[above]{$3$} (3,-1) -- (3,2) node[above]{$2$};
+\draw[->] (5,0.5) -- (8,0.5);
+\draw (9,-1) -- (9,2) node[above]{$\PP^1$};
+\draw[fill=black] (9,0) circle[radius=2pt] node[right]{$H$};
+\draw[fill=black] (9,1.5) circle[radius=2pt] node[right]{$H'$};
+\end{tikzpicture}
+\end{center}
+and assume that it is in the closure of the nice locus; I want to argue that the two smoothing parameters cannot be identified.
+By the previous points I may assume that the factorisation property and Gathmann's relative conditions hold.
+I have a diagram:
+\bcd
+\cC^{\rm{ss}}\ar[r]\ar[dr] & \widetilde \cC\ar[r]\ar[d] & \overline \cC\ar[d,"\bar f"] \\
+& \cC\ar[r,"f"] & X
+\ecd
+where I have included the semistable model of $\cC$ (and $\widetilde \cC$), thought of as a curve marked with $f^{-1}(H')$ as well, where $H\neq H'\in\PP^1$.
+
+Notice that $\cC$ is a normal surface with at worst singular points at the nodes of $C=\cC_0$ (a variety is smooth at any smooth point of a Cartier divisor) and the singularities are of type $A_{n_i},\ i=1,2$ (from the deformation theory of nodal curves).
+
+I assume maximal multiplicity $\sum\alpha=d$, i.e.
+I am looking at the moduli space $\M{1}{(5)}{\PP^1|H}{5}$.
+Hence the line bundle and $s_0$ are determined as $f^*\OO_{\PP^1}(1)=\OO_{\cC}(5x_1)\otimes\OO_{\cC}(\beta E)$ for some (positive rational) $\beta$ and $s_0$ is the natural inclusion of $\OO_{\cC}$ (up to $\Gm$).
+
+The map is totally ramified at $y_i$ by Gathmann's condition. We conclude:
+\[ \frac{\beta}{n_i+1}=(\beta E)\cdot R_i=m^{(i)}\]
+Hence, having fixed the multiplicities, the two possible singularities of $\cC$ determine each other.
+In our example we may pick $n_1=1,\ n_2=2,\ \beta=6$.
+But knowing the singularity determines the semistable model: in our case $y_1$ is replaced by a $(-2)$-curve and $y_2$ by a chain of two $(-2)$-curves.
+Now we know from the work of Smyth \cite[Proposition 2.12]{SMY1} that the exceptional locus of $\cC^{\rm{ss}}\to\overline\cC$ is balanced, therefore we may deduce that $\bar f$ is constant on the branch of the genus $1$ singularity to which $R_2$ is joined, so $\overline C$ looks like this:
+
+\begin{center}
+\begin{tikzpicture}
+\draw (-1,0) -- (1,0) node[right]{$\overline R_1$};
+\draw[color=gray!50] (-1,-1) -- (1,1);
+\draw[fill=black] (-.75,-.75) circle[radius=2pt] node[left]{$x_1$};
+\draw[color=gray!50] (0,-1) -- (0,1);
+\draw (-1,1.5) node[above left]{$\overline R_2$} -- (.25,.5);
+\end{tikzpicture}
+\end{center}
+where a gray line is contracted by the map.
+On the other hand if $\delta=\lambda(v_1)=\lambda(v_2)$ then the prescription of \cite[Proposition 3.6.1]{RSPW} implies that $\tilde C\to \overline C$ looks like:
+\begin{center}
+\begin{tikzpicture}
+\draw[color=brown] (0,0) node[left]{$E$} -- (4,0);
+\draw[color=gray!50] (1,-1) -- (1,2);
+\draw[fill=black] (1,1) circle[radius=2pt] node[left]{$x_1$};
+\draw (2,1.5) node[left]{$R_1$} (3,1.5) node[left]{$R_2$};
+\draw (2,-1) -- (2,2) node[above]{$3$} (3,-1) -- (3,2) node[above]{$2$};
+\draw[->] (5,0.5) -- (7,0.5);
+\draw (8,0.5) -- (10,0.5) node[right]{$\overline R_1$};
+\draw[color=gray!50] (8,-.5) -- (10,1.5);
+\draw[fill=black] (8.25,-.25) circle[radius=2pt] node[left]{$x_1$};
+\draw (9,-.5) -- (9,1.5) node[above left]{$\overline R_2$};
+\end{tikzpicture}
+\end{center}
+Contradiction!
+\end{itemize}
+\end{proof}
+
+It thus remains to show that, given a relative radially aligned map, we can smooth it to one in the nice locus.
+\textcolor{red}{This is done by considering different cases locally, then gluing.
+\marginpar{what do we mean?}}
 

### 2017-12-21 genus-one-relative-maps.tex
more comments on smoothability

@@
 
+\textcolor{red}{Address the case that $C_0$ is not irreducible, and that $C_i,\ i\neq 0$ are chains of $\PP^1$'s.}
+
+\subsection*{Case 2: contracted genus one internal component} This is similar to the previous one but slightly more delicate.
+
+Pick the smoothing $W'$, the line bundle $\tilde L$ and the section $s_0$ as before. Now $H^1(C,L)\neq 0$, so we need to argue that we can extend the other sections.
+
+Let us first extend the centrally aligned log structure: this is done by sending $e_i\mapsto t^{r_i}$; by the novel condition, if $e_i=e_j$ in the minimal centrally aligned structure that we start with on $C$, then $r_i=r_j$, so the chart that we have just defined factors indeed through the sharpening of $\mathbb N^r$.
+We declare the contraction radius $\delta$ to be $e_i$ for those $i$'s corresponding to branches of the genus $1$ singularity on which $\bar f$ is non-constant.
+\marginpar{actually this sounds like bs and I probably have $\delta$ already?}
+
+The central alignment provides us with a diagram:
+\bcd
+\widetilde \cC\ar[r]\ar[d] & \overline \cC \\
+\cC & 
+\ecd
+We can now extend the sections $\bar s_1,\ldots,\bar s_N$ onto $\overline \cC$ because $H^1(\overline C,\bar L)=0$, so we get a map $\bar F\colon\overline\cC\to\PP^N$ deforming $\bar f$.
+Finally we claim that $F\colon\cC\to\PP^N$ is the stable model of $\bar F$.
 \newpage

### 2017-12-21 genus-one-relative-maps.tex
Some changes, made on master because I forgot. Sorry. Minor cosmetic changes anyway.

@@
 
-\title[Genus One Radial Maps]{Relative Stable Maps in Genus One via Radial Alignments}
+\title[Genus One Radial Maps]{Relative Stable Maps in Genus One via Central Alignments}
 \author{Luca Battistella and Navid Nabijou}
@@
 \section{Relative space equals closure of the nice locus}
-Recall the definition of maps from centrally aligned curves via the cartesian diagram:
+Recall that the moduli space of maps from centrally aligned curves is defined via the following Cartesian diagram:
 \bcd
@@
 \begin{dfn}
-The centrally aligned relative space is defined within $\tVZc(Y,\beta)$ by the following:
-\begin{itemize}
-\item \emph{factorisation condition}: the map $f\colon C\to X$ factors through the associated contraction to a Smyth's singularity:
+The \emph{centrally aligned relative space} is defined to be the substack of $\tVZc(Y,\beta)$ satisfying the following conditions:
+\begin{enumerate}
+\item \emph{Factorisation condition.} The map $f\colon C\to X$ factors through the associated contraction to a Smyth singularity:
 \bcd
@@
 
-\item \emph{Gathmann's relative condition}: for every connected component $Z$ of $f^{-1}(Y)$, either $Z$ is a point and, if it is marked $Z=x_i$, the multiplicity of $f$ at $x_i$ along $Y$ is at least $\alpha_i$; or $Z$ is a curve and $f^*\OO_X(Y)-\sum_{x_i\in Z}\alpha_ix_i$ is effective.
-Notice that $Z$ is at most genus $1$ and every line bundle of positive degree on a Gorenstein irreducible genus $1$ curve is effective, hence this condition can be rephrased as: the numerical condition
-\[f_*[Z]\cdot Y+\sum_{j=1}^r m^{(j)}\geq \sum_{x_i\in Z}\alpha_i,\]
-and, in case the numerical equality holds, the following equality of line bundles:
-\[f_{\lvert Z}^*\OO_X(Y)=\OO_Z\left(\sum_{x_i\in Z}\alpha_ix_i - \sum_{j=1}^r m^{(j)}y_j\right)\in\Pic(Z).\]
+\item \emph{Gathmann's relative condition.} Let $Z$ be a connected component of $f^{-1}(Y)$.
+If $Z$ is a marked point $x_i$ then the multiplicity of $f$ at $x_i$ along $Y$ is at least $\alpha_i$.
+On the other hand if $Z\subseteq C$ is a curve then
+\begin{equation*} f^*\OO_X(Y)|_Z -\sum_{x_i\in Z}\alpha_ix_i\end{equation*}
+is an effective class on $Z$.
+Notice that since $Z$ is at most genus $1$ and every line bundle of positive degree on a Gorenstein irreducible genus $1$ curve is effective, this condition can be rephrased as a numerical condition
+\begin{equation*} f_*[Z]\cdot Y+\sum_{j=1}^r m^{(j)}\geq \sum_{x_i\in Z}\alpha_i \end{equation*}
+together with the following equality of line bundles in $\Pic(Z)$:
+\begin{equation*} (f|_{Z})^*\OO_X(Y)=\OO_Z\left(\sum_{x_i\in Z}\alpha_ix_i - \sum_{j=1}^r m^{(j)}y_j\right)\end{equation*}
 
-\item \emph{novel condition}: there are no two vertices of $\rm{MinPos}$ closest to the circuit (i.e.
-$v_1\neq v_2\in \rm{MinPos}$ with $\delta=\lambda(v_1)=\lambda(v_2)$) unless the corresponding $m^{(j_1)}$ and $m^{(j_2)}$ are equal.
-\end{itemize}
+\item \emph{Novel condition.} There are no two vertices of $\rm{MinPos}$ closest to the circuit (i.e.
+$v_1, v_2\in \rm{MinPos}$  with $\delta=\lambda(v_1)=\lambda(v_2)$) unless the corresponding $m^{(j_1)}$ and $m^{(j_2)}$ are equal.
+\end{enumerate}
 \end{dfn}
 
+Remember that we are trying to impose conditions which determine the closure of the nice locus inside the moduli space of centrally aligned maps.
 Here is one example where we show by a dimensional computation that the novel condition must be included if we hope to determine the closure of the nice locus.

### 2017-12-21 genus-one-relative-maps.tex
Some minor changes

@@
 The virtual dimension is $7-3=4$.
-Here is a parametrisation of the nice locus: choose an element $(E,p)$ of $\oM_{1,1}\setminus\partial\oM_{1,1}$ (which has dimension $1$), let then $s_0\colon\OO_E\hookrightarrow\OO_E(3p)$ and $s_1$ be any section of $\OO_E(3p)$ not vanishing at $p$ (notice that $h^0(E,\OO_E(3p))=3$).
-Consider now the following weighted graph for a map in the boundary:
+Here is a parametrisation of the nice locus: choose an element $(E,p)$ of $\oM_{1,1}\setminus\partial\oM_{1,1}$ (which has dimension $1$), and let $s_0$ be the natural section $s_0 \colon\OO_E\hookrightarrow\OO_E(3p)$ and $s_1$ any other section of $\OO_E(3p)$ not vanishing at $p$ (notice that $\h^0(E,\OO_E(3p))=3$).
+Then $(E,p,[\lambda s_0,s_1])$ gives a well-defined element of the nice locus for $\lambda \neq 0$.
+
+Consider now the following weighted graph for a map in the boundary
 \begin{center}
@@
 where the brown line represents a contracted genus $1$ curve.
-Now $(E,x_1,y_1,y_2)$ is a point of $\oM_{1,3}$ subject to the divisorial condition $3x_1-2y_1-y_2=0\in A_0(E)$; furthermore we have to choose the second ramification value of the $2\colon 1$ map from $R_1$ to $\PP^1$.
+Now $(E,x_1,y_1,y_2)$ is a point of $\oM_{1,3}$ subject to the divisorial condition $3x_1-2y_1-y_2=0\in \Achow_0(E)$; furthermore we have to choose the second branch point of the $2\colon 1$ map from $R_1$ to $\PP^1$.
 This already makes up for a $3$-dimensional moduli space of degenerate relative maps corresponding to such a graph.
-The minimal log structure for this curve has a chart from $\-mathbb N^2$, with generators $e_1$ and $e_2$ corresponding to the smoothing parameters of the two nodes.
+The minimal log structure for this curve has a chart from $\mathbb N^2$, with generators $e_1$ and $e_2$ corresponding to the smoothing parameters of the two nodes.
 If we allowed $e_1$ and $e_2$ to be identified in the characteristic sheaf, then we would get an extra $\Gm$ of choices for the log structure, so in total a $4$-dimensional moduli space.
-There is no chance this could live in the closure of the nice locus.
+Thus if we don't impose the novel condition then we get a whole other component of the relative space, which of course for dimensional reasons cannot be contained in the closure of the nice locus.
 \end{example}
 
-Thanks to the compatibility of $\delta$ (the contraction radius) with the stable map, namely the subcurve $C_0$ where $\lambda<\delta$ is the maximal connected subcurve of genus $1$ contracted by $f$, when the source curve is irreducible we have $\delta=0$, which is already ordered in every path to infinity.
+Thanks to the compatibility of $\delta$ (the contraction radius) with the stable map, namely the fact that the subcurve $C_0$ where $\lambda<\delta$ is the maximal connected subcurve of genus $1$ contracted by $f$, when the source curve is irreducible we have $\delta=0$, which is already ordered in every path to infinity.
 Hence the log structures only come into play when the source curve is reducible.
@@
 
-We now want to show that the relative space in the radially aligned setting is equal to the closure of the nice locus; irreducibility follows immediately.
+We now want to show that the relative space in the centrally aligned setting is equal to the closure of the nice locus; irreducibility then follows immediately. We start with one direction.
 
@@
 \begin{proof}
-We address the relative conditions one at a time. Notice that they are all obviuously satisfied on the nice locus.
-\begin{itemize}
-\item The factorisation property is closed: see \cite[Theorem 4.3]{RSPW}.
-\item Gathmann's relative condition is closed: see \cite[Proposition 4.9]{Vre}.
-\item The novel condition is satisfied on the closure of the nice locus. Here is no proof but some heuristics. Consider for example a map similar to the one above:
+We address the relative conditions one at a time. Notice that they are all obviously satisfied on the nice locus.
+
+The factorisation property is closed: see \cite[Theorem 4.3]{RSPW}.
+
+Gathmann's relative condition is closed: see \cite[Proposition 4.9]{Vre}.
+
+It remains to show that the novel condition is satisfied on the closure of the nice locus. Here is no proof but rather some heuristics. Consider for example a map similar to the one above
 \begin{center}
@@
 Contradiction!
-\end{itemize}
 \end{proof}

### 2017-12-21 genus-one-relative-maps.tex
Minor changes; some more explanations/modifications

@@
 
-Notice that $\cC$ is a normal surface with at worst singular points at the nodes of $C=\cC_0$ (a variety is smooth at any smooth point of a Cartier divisor) and the singularities are of type $A_{n_i},\ i=1,2$ (from the deformation theory of nodal curves).
+Notice that $\cC$ is a normal surface with at worst singular points at the nodes of $C=\cC_0$ (the central fibre $C=E+R_1+R_2$ is Cartier and a variety is smooth at any smooth point of a Cartier divisor) and the singularities are of type $A_{n_i},\ i=1,2$ (from the deformation theory of nodal curves).
 
@@
 \end{center}
-Contradiction!
+which is a contradiction.
 \end{proof}
@@
 \textcolor{red}{This is done by considering different cases locally, then gluing.
-\marginpar{what do we mean?}}
+\marginpar{What do we exactly mean by this?
+How does gluing work in the centrally aligned setting?}}
 
@@
 
-\textcolor{red}{Address the case that $C_0$ is not irreducible, and that $C_i,\ i\neq 0$ are chains of $\PP^1$'s.}
+\textcolor{red}{Address the case that $C_0$ is not irreducible, and that $C_i,\ i\neq 0$ are chains of $\PP^1$'s.}\marginpar{This should follow from gluing, whatever that means.}
 
-\subsection*{Case 2: contracted genus one internal component} This is similar to the previous one but slightly more delicate.
+\subsection*{Case 2: contracted genus one internal component} This is similar to the previous case, but slightly more delicate.
+The smoothing $W'$, the line bundle $\tilde L$ and the section $s_0$ are constructed as before.
+Now, however, $\HH^1(C,L)\neq 0$, so we need to work harder to show that we can extend the other sections.
 
-Pick the smoothing $W'$, the line bundle $\tilde L$ and the section $s_0$ as before. Now $H^1(C,L)\neq 0$, so we need to argue that we can extend the other sections.
-
-Let us first extend the centrally aligned log structure: this is done by sending $e_i\mapsto t^{r_i}$; by the novel condition, if $e_i=e_j$ in the minimal centrally aligned structure that we start with on $C$, then $r_i=r_j$, so the chart that we have just defined factors indeed through the sharpening of $\mathbb N^r$.
+Before extending the sections let us first extend the centrally aligned log structure.
+On the base $\Aaff^1_t$ the chart sends $e_i \in \N^r$ to $t^{r_i}$.
+By the novel condition, if $e_i=e_j$ in the minimal centrally aligned structure that we start with on $C$, then $r_i=r_j$, so the chart that we have just defined factors indeed through the sharpening of the submonoid of $\mathbb Z^r$ generated by $\N^r$ and the differences $\lambda(v) - \lambda(w)$.
 We declare the contraction radius $\delta$ to be $e_i$ for those $i$'s corresponding to branches of the genus $1$ singularity on which $\bar f$ is non-constant.
@@
 \ecd
-We can now extend the sections $\bar s_1,\ldots,\bar s_N$ onto $\overline \cC$ because $H^1(\overline C,\bar L)=0$, so we get a map $\bar F\colon\overline\cC\to\PP^N$ deforming $\bar f$.
+We can now extend the sections $\bar s_1,\ldots,\bar s_N$ onto $\overline \cC$ because $\HH^1(\overline C,\bar L)=0$, so we get a map $\bar F\colon\overline\cC\to\PP^N$ deforming $\bar f$.
 Finally we claim that $F\colon\cC\to\PP^N$ is the stable model of $\bar F$.

### 2018-02-01 genus-one-relative-maps.tex
Minor changes - not sure what
Restructured beginning a bit, changed font and did some minor cosmetic fixes

@@
 \documentclass[11pt]{amsart}
-%\usepackage[english]{babel}
+
+\usepackage[english]{babel}
 \usepackage{appendix}
@@
 \usepackage{amssymb}
-%\usepackage{showlabels}
+\usepackage{showlabels}
 \usepackage{hyperref}
@@
 \usepackage[utf8x]{inputenc}
-%\usepackage{enumerate}
 \usepackage{verbatim}
@@
 \usetikzlibrary{decorations.pathmorphing,decorations.pathreplacing,patterns}
+
 \usepackage[all]{xy}
@@
 \usepackage{mathtools}
+
+\usepackage[]{textcomp}
+\usepackage[sups]{Baskervaldx}
+\usepackage{cabin}
+\usepackage[varqu,varl]{inconsolata}
+\usepackage[baskervaldx,bigdelims,vvarbb]{newtxmath}
+\usepackage[cal=cm]{mathalfa}
 
@@
 \newcommand{\tVZc}{\widetilde{\mathcal{V\!Z}}^{\rm{ctr}}_{1,n}}
+\newcommand{\VZc}{{\mathcal{V\!Z}}^{\rm{ctr}}_{1,n}}
+\newcommand{\VZcrel}{{\mathcal{V\!Z}}^{\rm{ctr}}_{1,\alpha}}
 \newcommand{\N}{\mathbb{N}}
@@
 
-\usepackage[T1]{fontenc}
-\usepackage{newpxtext,newpxmath}
+\title[Genus One Reduced Relative Invariants]{Relative Stable Maps in Genus One via Central Alignments}
+\author{Luca Battistella, Navid Nabijou and Dhruv Ranganathan}
+\date{\thismonthyear}
 
-\title[Genus One Radial Maps]{Relative Stable Maps in Genus One via Central Alignments}
-\author{Luca Battistella and Navid Nabijou}
 \begin{document}
+\maketitle
 
-%\begin{abstract} \end{abstract}
+\begin{abstract} For a smooth projective variety $X$ and a smooth very ample hypersurface $Y \subseteq X$, we define moduli spaces of relative stable maps to $(X,Y)$ in genus one, as closed substacks of the moduli space of maps from centrally aligned curves, constructed in \cite{RSPW}.
+We construct virtual classes for these moduli spaces, which we use to define \emph{reduced relative Gromov--Witten invariants} in genus one.
 
-\maketitle
-%\appendixtitletocoff
-%\tableofcontents
+[GOALS: We prove a recursion formula which allows us to completely determine these invariants in terms of the reduced Gromov--Witten invariants, as defined in [REF].
+We also prove a relative version of the Li--Zinger formula, relating our invariants to the usual relative Gromov--Witten invariants.
+Also say something about quasimaps.]
+\end{abstract}
 
-Recall \cite[Proposition 4.6.2.2]{RSPW}:
-\begin{prop}
-The morphism $\MM^{\rm{ctr}}_{1,n}\to\MM^{\dagger}_{1,n}$ is a log-modification.
-\end{prop}
+\appendixtitletocoff
+\tableofcontents
 
-Explanation: this is a local statement so I can probably reduce to an atomic neighbourhood $S$ of a point $p$.
-$S$ and the curve over it are endowed with the minimal log structure; let $P=\oM_p$ determine a chart for this log structure.
-Observe that the subcurve $\plC_0$ of the tropicalisation $\plC$ of $C_p$ determines a subset $\rm{MinPos}$ of the set of vertices, namely those adjacent to $\plC_0$.
-Perform the following log-blowups: consider the set of primitive values of the function $\lambda\colon \plC\to P$, and blow up the ideal that they generate; now locally the set of values of $\lambda$ is principal with generator $p$: blow up the ideal generated by $\{\lambda(v)-p\}\setminus\{-p\}$.
-Keep going until $\lambda(v_i)$ is reached for some $v_i\in\rm{MinPos}$; at this point stop and declare the contraction radius $\delta:=\lambda(v_i)$.
-Finish by adjoining $\lambda(v)-\delta$ for all the vertices untouched to this stage.
-This shows that the choice of $\delta$ is not an extra degree of freedom.\marginpar{do I sound like a physicist?}
-
-\section{Relative space equals closure of the nice locus}
-Recall that the moduli space of maps from centrally aligned curves is defined via the following Cartesian diagram:
+\section{Identifying the closure of the nice locus for $(\PP^N,H)$}
+Recall \cite{RSPW} that the moduli space of maps from centrally aligned curves is obtained by first considering the Cartesian diagram
 \bcd
@@
 \ecd
-
-\begin{dfn}
-The \emph{centrally aligned relative space} is defined to be the substack of $\tVZc(Y,\beta)$ satisfying the following conditions:
-\begin{enumerate}
-\item \emph{Factorisation condition.} The map $f\colon C\to X$ factors through the associated contraction to a Smyth singularity:
+and then defining
+\begin{equation*} \VZc(X,\beta) \subseteq \tVZc(X,\beta) \end{equation*}
+to be the closed substack consisting of maps satisfying the \emph{factorisation condition}, namely that the map $f\colon C\to X$ factors through the associated contraction to a Smyth curve, i.e.
+there exists a map $\bar{f}$ making the following square commute:
 \bcd
-\widetilde C\ar[r]\ar[d] & \overline C\ar[d,"\bar f"] \\
+\widetilde C\ar[r]\ar[d] & \overline C\ar[d,"\bar f" left,dotted] \\
 C\ar[r,"f"] & X
@@
 
-\item \emph{Gathmann's relative condition.} Let $Z$ be a connected component of $f^{-1}(Y)$.
-If $Z$ is a marked point $x_i$ then the multiplicity of $f$ at $x_i$ along $Y$ is at least $\alpha_i$.
-On the other hand if $Z\subseteq C$ is a curve then
-\begin{equation*} f^*\OO_X(Y)|_Z -\sum_{x_i\in Z}\alpha_ix_i\end{equation*}
-is an effective class on $Z$.
-Notice that since $Z$ is at most genus $1$ and every line bundle of positive degree on a Gorenstein irreducible genus $1$ curve is effective, this condition can be rephrased as a numerical condition
-\begin{equation*} f_*[Z]\cdot Y+\sum_{j=1}^r m^{(j)}\geq \sum_{x_i\in Z}\alpha_i \end{equation*}
-together with the following equality of line bundles in $\Pic(Z)$:
-\begin{equation*} (f|_{Z})^*\OO_X(Y)=\OO_Z\left(\sum_{x_i\in Z}\alpha_ix_i - \sum_{j=1}^r m^{(j)}y_j\right)\end{equation*}
+\subsection{Definition of the relative space} We now give the central definition of this article.
+\begin{dfn}
+Fix a vector of tangency conditions $\alpha=(\alpha_1,\ldots,\alpha_n)$ with $\Sigma_i \alpha_i \leq Y \cdot \beta$. Then the \emph{centrally aligned relative space} 
+\begin{equation*}\VZcrel(X|Y,\beta) \end{equation*}
+is defined to be the closed substack of $\VZc(X,\beta)$ satisfying the following conditions:
+\begin{enumerate}
+\item \emph{Gathmann's relative condition:} for each connected component $Z$ of $f^{-1}(Y)$, either:
+\begin{enumerate}
+\item $Z$ is a single point of $C$, in which case if $Z=x_i$ is a marking then we require that the multiplicity of $f$ at $x_i$ along $Y$ is at least $\alpha_i$ (if $Z$ is not a marking then there is no condition);
+\item $Z$ is a subcurve $Z \subseteq C$, in which case we require that
+\begin{equation*} f^*[Y]|_Z -\sum_{x_i\in Z}\alpha_ix_i\end{equation*}
+is an effective class in $\Achow_1(Z)$.
+Since $Z$ is at most genus one and any line bundle of strictly positive degree on a Gorenstein genus one curve is effective, this condition can be rephrased as the following numerical criterion
+\begin{equation*} f_*[Z]\cdot [Y]+\sum_{j=1}^r m^{(j)}\geq \sum_{x_i\in Z}\alpha_i \end{equation*}
+together with the additional requirement that, when the above is an equality, there is an isomorphism of line bundles:
+\begin{equation*} (f|_{Z})^*\OO_X(Y) \otimes \OO_Z\left(\sum_{j=1}^r m^{(j)}y_j\right)=\OO_Z\left(\sum_{x_i\in Z}\alpha_ix_i\right)\end{equation*}
+\end{enumerate}
 
-\item \emph{Novel condition.} There are no two vertices of $\rm{MinPos}$ closest to the circuit (i.e.
-$v_1, v_2\in \rm{MinPos}$  with $\delta=\lambda(v_1)=\lambda(v_2)$) unless the corresponding $m^{(j_1)}$ and $m^{(j_2)}$ are equal.
+\item \emph{Novel condition:} if $v_1,v_2$ are two vertices belonging to $R_\delta$, then the corresponding tangencies to the divisor $m^{(j_1)}$ and $m^{(j_2)}$ must be equal.
+Here $R_\delta$ is the set of vertices $v \in \plC$ with $\lambda(v)=\delta$.
 \end{enumerate}
@@
 
+\subsection{Justifying the novel condition}
 Remember that we are trying to impose conditions which determine the closure of the nice locus inside the moduli space of centrally aligned maps.
@@
 
+\subsection{Proof}
 Thanks to the compatibility of $\delta$ (the contraction radius) with the stable map, namely the fact that the subcurve $C_0$ where $\lambda<\delta$ is the maximal connected subcurve of genus $1$ contracted by $f$, when the source curve is irreducible we have $\delta=0$, which is already ordered in every path to infinity.
@@
 Finally we claim that $F\colon\cC\to\PP^N$ is the stable model of $\bar F$.
-\newpage
+
+\appendix
+
+\section{Basic facts about centrally aligned curves}
+\begin{prop}[{\cite[Proposition 4.6.2.2]{RSPW}}]
+The morphism $\MM^{\rm{ctr}}_{1,n}\to\MM^{\dagger}_{1,n}$ is a log-modification.
+\end{prop}
+
+Explanation: this is a local statement so I can probably reduce to an atomic neighbourhood $S$ of a point $p$.
+$S$ and the curve over it are endowed with the minimal log structure; let $P=\oM_p$ determine a chart for this log structure.
+Observe that the subcurve $\plC_0$ of the tropicalisation $\plC$ of $C_p$ determines a subset $\rm{MinPos}$ of the set of vertices, namely those adjacent to $\plC_0$.
+Perform the following log-blowups: consider the set of primitive values of the function $\lambda\colon \plC\to P$, and blow up the ideal that they generate; now locally the set of values of $\lambda$ is principal with generator $p$: blow up the ideal generated by $\{\lambda(v)-p\}\setminus\{-p\}$.
+Keep going until $\lambda(v_i)$ is reached for some $v_i\in\rm{MinPos}$; at this point stop and declare the contraction radius $\delta:=\lambda(v_i)$.
+Finish by adjoining $\lambda(v)-\delta$ for all the vertices untouched to this stage.
+This shows that the choice of $\delta$ is not an extra degree of freedom.\marginpar{do I sound like a physicist?}
+
 \bibliographystyle{alpha}
@@
 Department of Mathematics, Imperial College London \\
-\texttt{navid.nabijou09@imperial.ac.uk}
+\texttt{navid.nabijou09@imperial.ac.uk}\\
+
+\noindent Dhruv Ranganathan \\
+Department of Mathematics, Massachusetts Institute of Technology \\
+\texttt{dhruvr@mit.edu}
 

### 2018-02-01 genus-one-relative-maps.tex
More restructuring and clarifying

@@
 
-\setcounter{tocdepth}{1}
+\setcounter{tocdepth}{2}
 
@@
 
-\section{Identifying the closure of the nice locus for $(\PP^N,H)$}
-Recall \cite{RSPW} that the moduli space of maps from centrally aligned curves is obtained by first considering the Cartesian diagram
+\section{The space of relative centrally aligned maps}
+\noindent Recall \cite{RSPW} that the moduli space of maps from centrally aligned curves is obtained by first considering the Cartesian diagram
 \bcd
@@
 
+\section{The relative space is equal to the closure of the nice locus for $(\PP^N,H)$}
+\noindent In general we do not know very much about the space we have just defined.
+The aim of this section is to show that, in the case where $X=\PP^N$ and $Y=H$ is a hyperplane, the space is proper and irreducible of the expected dimension.
+As such it has a fundamental class, which we can use to define reduced relative Gromov--Witten invariants in genus one.
+
+\begin{remark} In the case of a general pair $(X,Y)$ we will see that the moduli space is still proper, but is not in general irreducible or even equidimensional.
+Nevertheless, we can equip it with a virtual class by `pulling back'' from the case of $(\PP^N,H)$; for details, see \S [REF].
+\end{remark}
+
+The strategy is as follows. We define (Definition \ref{Definition of nice locus})an open subspace
+\begin{equation*}\VZcrel(\PP^N|H,d)^{\circ} \subseteq \VZcrel(\PP^N|H,d)\end{equation*}
+called the \emph{nice locus}, on which the source curve and the map take a particularly simple form.
+Because of this simplicity, it is easy to show that the nice locus is irreducible (Lemma \ref{Nice locus is irreducible}).
+We then prove that $\VZcrel(\PP^N|H,d)$ is equal to the closure of the nice locus inside $\VZc(\PP^N,d)$.
+Thus it is proper, since it is a closed space of a proper space, and it is irreducible, since it is the closure of an irreducible space inside an irreducible space.
+
+\begin{definition} \label{Definition of nice locus} The \emph{nice locus} is defined as the open substack
+\begin{equation*}\VZcrel(\PP^N|H,d)^{\circ} \subseteq \VZcrel(\PP^N|H,d)\end{equation*}
+of centrally aligned maps satisfying the following two conditions:
+\begin{enumerate}
+\item the source curve $C$ is irreducible;
+\item $f$ does not map $C$ inside $H$.
+\end{enumerate}
+\end{definition}
+
+\begin{lem}\label{Nice locus is irreducible}
+The nice locus $\VZcrel(\PP^N|H,d)^{\circ}$ is irreducible.
+\end{lem}
+\begin{proof}
+By definition the contraction radius $\delta$ is compatible with the map, i.e.
+the subcurve $C_0\subseteq C$ where $\lambda<\delta$ is equal to the maximal connected genus one subcurve contracted by $f$.
+Hence when the source curve is irreducible we must have $\delta=0$, and we see that the central alignment on $C$ is uniquely and trivially determined.
+Thus to specify a point in the nice locus we only need to specify the source curve $C$ (as a scheme) and the map $f$.
+A parametrisation can be given from the vector bundle:\marginnote{I'm sure there's a simpler way to say this - Navid}
+\[ \operatorname{Vb}\left(\pi_*\OO_{\mathcal E}(\sum_{j=n+1}^{n+\delta}\sigma_j)\oplus\pi_*\OO_{\mathcal E}(\sum_{j=1}^{n+\delta}\sigma_j)^{\oplus r}\right) \quad \text{on} \quad \mathcal{M}_{1,n+\delta}\]
+where $\pi\colon\mathcal E\to\mathcal M$ is the universal curve and $\delta=d-\sum\alpha_i$.
+\end{proof}
+
 \subsection{Justifying the novel condition}
@@
 
+\begin{example} In this example we will give further justification for the novel condition, using as motivation the expanded degeneration approach to relative stable maps.
+
+\end{example}
+
 \subsection{Proof}
-Thanks to the compatibility of $\delta$ (the contraction radius) with the stable map, namely the fact that the subcurve $C_0$ where $\lambda<\delta$ is the maximal connected subcurve of genus $1$ contracted by $f$, when the source curve is irreducible we have $\delta=0$, which is already ordered in every path to infinity.
-Hence the log structures only come into play when the source curve is reducible.
-We see then the nice locus in the radially aligned setting is the same as the nice locus in the ordinary setting.
-In particular, it is irreducible.
-
-\begin{lem}
-The nice locus is irreducible.
-\end{lem}
-\begin{proof}
-A parametrisation can be given from the vector bundle:
-\[ \operatorname{Vb}\left(\pi_*\OO_{\mathcal E}(\sum_{j=n+1}^{n+\delta}\sigma_j)\oplus\pi_*\OO_{\mathcal E}(\sum_{j=1}^{n+\delta}\sigma_j)^{\oplus r}\right) \quad \text{on} \quad \mathcal{M}_{1,n+\delta}\]
-where $\pi\colon\mathcal E\to\mathcal M$ is the universal curve and $\delta=d-\sum\alpha_i$.
-\end{proof}
-
 We now want to show that the relative space in the centrally aligned setting is equal to the closure of the nice locus; irreducibility then follows immediately. We start with one direction.

### 2018-02-02 genus-one-relative-maps.tex
Expanded the recap section at the start

@@
 \ecd
-and then defining
+so that objects of $\tVZc(X,\beta)$ consist of
+\begin{enumerate}
+\item a centrally aligned curve $(C,M_C,\delta)$;
+\item a stable map $f\colon C \to X$;
+\end{enumerate}
+subject to the condition that the contraction radius $\delta$ of the central alignment is equal to $\delta_f$, the contraction radius of the stable map $f$. We then define
 \begin{equation*} \VZc(X,\beta) \subseteq \tVZc(X,\beta) \end{equation*}
@@
 \ecd
+One should think of the factorisation condition as identifying the main component of the moduli space.
 
@@
 \begin{dfn}
-Fix a vector of tangency conditions $\alpha=(\alpha_1,\ldots,\alpha_n)$ with $\Sigma_i \alpha_i \leq Y \cdot \beta$. Then the \emph{centrally aligned relative space} 
+Fix a vector of tangency conditions $\alpha=(\alpha_1,\ldots,\alpha_n)$ with $\Sigma_{i=1}^n \alpha_i \leq Y \cdot \beta$. Then the \emph{centrally aligned relative space} 
 \begin{equation*}\VZcrel(X|Y,\beta) \end{equation*}

### 2018-02-02 genus-one-relative-maps.tex
Started writing up example of novel condition justification using expanded degenerations

@@
 \newcommand{\Z}{\mathbb{Z}}
-\newcommand{\tVZc}{\widetilde{\mathcal{V\!Z}}^{\rm{ctr}}_{1,n}}
-\newcommand{\VZc}{{\mathcal{V\!Z}}^{\rm{ctr}}_{1,n}}
-\newcommand{\VZcrel}{{\mathcal{V\!Z}}^{\rm{ctr}}_{1,\alpha}}
+\newcommand{\tVZc}[4]{\widetilde{\mathcal{V\!Z}}^{\rm{ctr}}_{#1,#2}(#3,#4)}
+\newcommand{\VZc}[4]{\mathcal{V\!Z}^{\rm{ctr}}_{#1,#2}(#3,#4)}
+\newcommand{\VZcLi}[4]{\mathcal{V\!Z}^{\rm{ctr, Li}}_{#1,#2}(#3,#4)}
 \newcommand{\N}{\mathbb{N}}
@@
 \bcd
-\tVZc(X,\beta)\ar[d]\ar[r]\ar[dr,phantom,"\Box"] & \M{1}{n}{X}{\beta}\ar[d] \\
+\tVZc{1}{n}{X}{\beta}\ar[d]\ar[r]\ar[dr,phantom,"\Box"] & \M{1}{n}{X}{\beta}\ar[d] \\
 \MM_{1,n}^{\rm{ctr}}\ar[r] & \MM_{1,n}^{\dagger}
 \ecd
-so that objects of $\tVZc(X,\beta)$ consist of
+so that objects of $\tVZc{1}{n}{X}{\beta}$ consist of
 \begin{enumerate}
@@
 subject to the condition that the contraction radius $\delta$ of the central alignment is equal to $\delta_f$, the contraction radius of the stable map $f$. We then define
-\begin{equation*} \VZc(X,\beta) \subseteq \tVZc(X,\beta) \end{equation*}
+\begin{equation*} \VZc{1}{n}{X}{\beta} \subseteq \tVZc{1}{n}{X}{\beta} \end{equation*}
 to be the closed substack consisting of maps satisfying the \emph{factorisation condition}, namely that the map $f\colon C\to X$ factors through the associated contraction to a Smyth curve, i.e.
@@
 Fix a vector of tangency conditions $\alpha=(\alpha_1,\ldots,\alpha_n)$ with $\Sigma_{i=1}^n \alpha_i \leq Y \cdot \beta$. Then the \emph{centrally aligned relative space} 
-\begin{equation*}\VZcrel(X|Y,\beta) \end{equation*}
-is defined to be the closed substack of $\VZc(X,\beta)$ satisfying the following conditions:
+\begin{equation*}\VZc{1}{\alpha}{X|Y}{\beta} \end{equation*}
+is defined to be the closed substack of $\VZc{1}{n}{X}{\beta}$ satisfying the following conditions:
 \begin{enumerate}
@@
 Since $Z$ is at most genus one and any line bundle of strictly positive degree on a Gorenstein genus one curve is effective, this condition can be rephrased as the following numerical criterion
-\begin{equation*} f_*[Z]\cdot [Y]+\sum_{j=1}^r m^{(j)}\geq \sum_{x_i\in Z}\alpha_i \end{equation*}
-together with the additional requirement that, when the above is an equality, there is an isomorphism of line bundles:
-\begin{equation*} (f|_{Z})^*\OO_X(Y) \otimes \OO_Z\left(\sum_{j=1}^r m^{(j)}y_j\right)=\OO_Z\left(\sum_{x_i\in Z}\alpha_ix_i\right)\end{equation*}
+\begin{equation*} f_*[Z]\cdot [Y]+\sum_{j=1}^r m_j\geq \sum_{x_i\in Z}\alpha_i \end{equation*}
+where the $m_j$ denote the multiplicities of $f$ along $Y$ at the points $y_j \in Z \cap \overline{C \setminus Z}$ (necessarily a finite number of nodes), together with the requirement that, when we have equality in the above, there is an isomorphism of line bundles:
+\begin{equation*} (f|_{Z})^*\OO_X(Y) \otimes \OO_Z\left(\sum_{j=1}^r m_j y_j\right)=\OO_Z\left(\sum_{x_i\in Z}\alpha_ix_i\right)\end{equation*}
 \end{enumerate}
 
-\item \emph{Novel condition:} if $v_1,v_2$ are two vertices belonging to $R_\delta$, then the corresponding tangencies to the divisor $m^{(j_1)}$ and $m^{(j_2)}$ must be equal.
-Here $R_\delta$ is the set of vertices $v \in \plC$ with $\lambda(v)=\delta$.
+\item \emph{Novel condition:} if $v_1,v_2$ are two vertices belonging to $R_\delta$, then the corresponding tangencies to the divisor $m_{j_1}$ and $m_{j_2}$ must be equal.
+Here $R_\delta$ is the set of vertices $v \in \plC$ with $\lambda(v)=\delta$ equal to the contraction radius.
 \end{enumerate}
@@
 The strategy is as follows. We define (Definition \ref{Definition of nice locus})an open subspace
-\begin{equation*}\VZcrel(\PP^N|H,d)^{\circ} \subseteq \VZcrel(\PP^N|H,d)\end{equation*}
+\begin{equation*}\VZc{1}{\alpha}{\PP^N|H}{d}^{\circ} \subseteq \VZc{1}{\alpha}{\PP^N|H}{d}\end{equation*}
 called the \emph{nice locus}, on which the source curve and the map take a particularly simple form.
 Because of this simplicity, it is easy to show that the nice locus is irreducible (Lemma \ref{Nice locus is irreducible}).
-We then prove that $\VZcrel(\PP^N|H,d)$ is equal to the closure of the nice locus inside $\VZc(\PP^N,d)$.
+We then prove that $\VZc{1}{\alpha}{\PP^N|H}{d}$ is equal to the closure of the nice locus inside $\VZc{1}{n}{\PP^N}{d}$.
 Thus it is proper, since it is a closed space of a proper space, and it is irreducible, since it is the closure of an irreducible space inside an irreducible space.
@@
 \begin{definition} \label{Definition of nice locus} The \emph{nice locus} is defined as the open substack
-\begin{equation*}\VZcrel(\PP^N|H,d)^{\circ} \subseteq \VZcrel(\PP^N|H,d)\end{equation*}
+\begin{equation*}\VZc{1}{\alpha}{\PP^N|H}{d}^{\circ} \subseteq \VZc{1}{\alpha}{\PP^N|H}{d}\end{equation*}
 of centrally aligned maps satisfying the following two conditions:
@@
 \begin{lem}\label{Nice locus is irreducible}
-The nice locus $\VZcrel(\PP^N|H,d)^{\circ}$ is irreducible.
+The nice locus $\VZc{1}{\alpha}{\PP^N|H}{d}^{\circ}$ is irreducible.
 \end{lem}
@@
 
-\begin{example} In this example we will give further justification for the novel condition, using as motivation the expanded degeneration approach to relative stable maps.
+\begin{example} In this example we will give further moral justification for the novel condition, using as motivation the expanded degenerations approach to relative stable maps.
+This is not strictly necessary for what we want to do (since our spaces don't involve expanded degenerations), but it helps to explain where this condition comes from.
+
+So, let us pretend that we have a good definition of the ``centrally aligned Li space'' of maps from centrally aligned curves to expanded degenerations:
+\begin{equation*} \VZcLi{1}{\alpha}{X|D}{\beta} \end{equation*}
+Objects of this moduli space should consist of maps $C \to \mathfrak{X}$ where $\mathfrak{X} \to X$ is an expansion of the pair $(X,D)$, together with a central alignment on $C$ which is compatible with this map.
+The factorisation property should say that the following diagram commutes:
+\bcd
+& \tilde{C} \ar[ld,"\nu" left] \ar[rd,"\tau"] & \\
+C \ar[d,"f" left] & & \overline{C} \ar[d,"\overline{f}", dotted] \\
+\mathfrak{X} \ar[rd,"\pi"] & & \mathfrak{X} \ar[ld,"\pi"] \\
+& X & 
+\ecd
+Morally speaking, the projection map
+\begin{equation*} \pi_* \colon \VZcLi{1}{\alpha}{X|D}{\beta} \to \VZc{1}{n}{X}{\beta} \end{equation*}
+should have as its image our space $\VZc{1}{\alpha}{X|D}{\beta}$.
+We will see that everything in the image of this space must satisfy the novel condition, thus providing further justification for us imposing it.
+
+Consider therefore the following ``object'' of $\VZc{1}{(5)}{\PP^2|\PP^1}{5}$, which \emph{does not} satisfy the novel condition:
 

### 2018-02-02 genus-one-relative-maps.tex
Drew some of the pictures for the Li space example

@@
 
-Consider therefore the following ``object'' of $\VZc{1}{(5)}{\PP^2|\PP^1}{5}$, which \emph{does not} satisfy the novel condition:
+We proceed by contradiction. Consider a genus one map $C \to \PP^1$ of the following form
+\begin{center}
+\begin{tikzpicture}
+\draw[fill=black] (0,0) node[left]{$E$} -- (4,0);
+\draw[fill=black] (0.7,0) circle[radius=2pt] node[below]{$5$};
+\draw[fill=black] (2,0) circle[radius=2pt] node[above right]{$2$};
+\draw[fill=black] (3,0) circle[radius=2pt] node[above right]{$3$};
+\draw (2,1.5) node[right]{$C_1$};
+\draw (3,1.5) node[right]{$C_2$};
+\draw (2,-1) -- (2,2) node[above]{$2$};
+\draw (3,-1) -- (3,2) node[above]{$3$};
+
+\draw[->] (4.5,0) -- (6.5,0);
+\draw (5.5,0) node[above]{$f$};
+\draw (7,-1) -- (7,2) node[above]{$\PP^1$};
+\draw[fill=black] (7,0) circle[radius=2pt] node[right]{$\infty$};
+\end{tikzpicture}
+\end{center}
+and equip the source curve $C$ with a central alignment which identifies the lengths of the components $C_1$ and $C_2$:
+\begin{center}
+\begin{tikzpicture}
+\draw[red,thick,dashed] (0,0) circle[radius=51pt];
+\draw[red] (-1.75,0) node[left]{$R_\delta$};
+\draw[fill=white] (0,0) circle[radius=4pt];
+\draw (0,0.1) node[above]{$E$};
+\draw[fill=black] (-1,-1.5) circle[radius=4pt];
+\draw (-1.1,-1.5) node[left]{$C_1$};
+\draw[fill=black] (-0.1,-0.1) -- (-1,-1.5);
+\draw[fill=black] (1,-1.5) circle[radius=4pt];
+\draw (1.1,-1.5) node[right]{$C_2$};
+\draw[fill=black] (0.1,-0.1) -- (1,-1.5);
+\end{tikzpicture}
+\end{center}
+This defines an ``object'' of $\VZc{1}{(5)}{\PP^1|\infty}{5}$, satisfying all the necessary conditions \emph{except for the novel condition}.
+We will show that this cannot belong to the image of $\pi_*$.
+
+First we have to identify what the possible lifts of this object to the centrally aligned Li space are.
 

### 2018-02-05 genus-one-relative-maps.tex
Minor notation change

@@
 Since $Z$ is at most genus one and any line bundle of strictly positive degree on a Gorenstein genus one curve is effective, this condition can be rephrased as the following numerical criterion
-\begin{equation*} f_*[Z]\cdot [Y]+\sum_{j=1}^r m_j\geq \sum_{x_i\in Z}\alpha_i \end{equation*}
+\begin{equation*} Y \cdot f_*[Z]+\sum_{j=1}^r m_j\geq \sum_{x_i\in Z}\alpha_i \end{equation*}
 where the $m_j$ denote the multiplicities of $f$ along $Y$ at the points $y_j \in Z \cap \overline{C \setminus Z}$ (necessarily a finite number of nodes), together with the requirement that, when we have equality in the above, there is an isomorphism of line bundles:

### 2018-02-08 genus-one-relative-maps.tex
some remarks on the last version

--- 2018-02-02 genus-one-relative-maps.tex
@@
 \newcommand{\Z}{\mathbb{Z}}
-\newcommand{\tVZc}[4]{\widetilde{\mathcal{V\!Z}}^{\rm{ctr}}_{#1,#2}(#3,#4)}
-\newcommand{\VZc}[4]{\mathcal{V\!Z}^{\rm{ctr}}_{#1,#2}(#3,#4)}
-\newcommand{\VZcLi}[4]{\mathcal{V\!Z}^{\rm{ctr, Li}}_{#1,#2}(#3,#4)}
+\newcommand{\tVZc}{\widetilde{\mathcal{V\!Z}}^{\rm{ctr}}_{1,n}}
+\newcommand{\VZc}{{\mathcal{V\!Z}}^{\rm{ctr}}_{1,n}}
+\newcommand{\VZcrel}{{\mathcal{V\!Z}}^{\rm{ctr}}_{1,\alpha}}
 \newcommand{\N}{\mathbb{N}}
@@
 \bcd
-\tVZc{1}{n}{X}{\beta}\ar[d]\ar[r]\ar[dr,phantom,"\Box"] & \M{1}{n}{X}{\beta}\ar[d] \\
+\tVZc(X,\beta)\ar[d]\ar[r]\ar[dr,phantom,"\Box"] & \M{1}{n}{X}{\beta}\ar[d] \\
 \MM_{1,n}^{\rm{ctr}}\ar[r] & \MM_{1,n}^{\dagger}
 \ecd
-so that objects of $\tVZc{1}{n}{X}{\beta}$ consist of
+so that objects of $\tVZc(X,\beta)$ consist of
 \begin{enumerate}
@@
 \end{enumerate}
-subject to the condition that the contraction radius $\delta$ of the central alignment is equal to $\delta_f$, the contraction radius of the stable map $f$. We then define
-\begin{equation*} \VZc{1}{n}{X}{\beta} \subseteq \tVZc{1}{n}{X}{\beta} \end{equation*}
+subject to the condition that the contraction radius $\delta$ of the central alignment is equal to $\delta_f$, the contraction radius of the stable map $f$.
+\marginpar{what is the contraction radius of $f$?
+I think to be precise we need to say $\delta=\lambda(v)$ for $v$ such that $f$ contracts any component of $C$ closer to the circuit than $C_v$, while it has positive degree on $C_v$...} We then define
+\begin{equation*} \VZc(X,\beta) \subseteq \tVZc(X,\beta) \end{equation*}
 to be the closed substack consisting of maps satisfying the \emph{factorisation condition}, namely that the map $f\colon C\to X$ factors through the associated contraction to a Smyth curve, i.e.
@@
 Fix a vector of tangency conditions $\alpha=(\alpha_1,\ldots,\alpha_n)$ with $\Sigma_{i=1}^n \alpha_i \leq Y \cdot \beta$. Then the \emph{centrally aligned relative space} 
-\begin{equation*}\VZc{1}{\alpha}{X|Y}{\beta} \end{equation*}
-is defined to be the closed substack of $\VZc{1}{n}{X}{\beta}$ satisfying the following conditions:
+\begin{equation*}\VZcrel(X|Y,\beta) \end{equation*}
+is defined to be the closed substack of $\VZc(X,\beta)$ satisfying the following conditions:
 \begin{enumerate}
@@
 is an effective class in $\Achow_1(Z)$.
-Since $Z$ is at most genus one and any line bundle of strictly positive degree on a Gorenstein genus one curve is effective, this condition can be rephrased as the following numerical criterion
-\begin{equation*} f_*[Z]\cdot [Y]+\sum_{j=1}^r m_j\geq \sum_{x_i\in Z}\alpha_i \end{equation*}
-where the $m_j$ denote the multiplicities of $f$ along $Y$ at the points $y_j \in Z \cap \overline{C \setminus Z}$ (necessarily a finite number of nodes), together with the requirement that, when we have equality in the above, there is an isomorphism of line bundles:
-\begin{equation*} (f|_{Z})^*\OO_X(Y) \otimes \OO_Z\left(\sum_{j=1}^r m_j y_j\right)=\OO_Z\left(\sum_{x_i\in Z}\alpha_ix_i\right)\end{equation*}
+Since $Z$ is at most genus one and any line bundle of strictly positive degree on a Gorenstein genus one curve is effective, \marginpar{need to look at each irreducible component of $Z$ separately} this condition can be rephrased as the following numerical criterion
+\begin{equation*} f_*[Z]\cdot [Y]+\sum_{j=1}^r m^{(j)}\geq \sum_{x_i\in Z}\alpha_i \end{equation*}
+together with the additional requirement that, when the above is an equality, there is an isomorphism of line bundles:
+\begin{equation*} (f|_{Z})^*\OO_X(Y) \otimes \OO_Z\left(\sum_{j=1}^r m^{(j)}y_j\right)=\OO_Z\left(\sum_{x_i\in Z}\alpha_ix_i\right)\end{equation*}
 \end{enumerate}
 
-\item \emph{Novel condition:} if $v_1,v_2$ are two vertices belonging to $R_\delta$, then the corresponding tangencies to the divisor $m_{j_1}$ and $m_{j_2}$ must be equal.
-Here $R_\delta$ is the set of vertices $v \in \plC$ with $\lambda(v)=\delta$ equal to the contraction radius.
+\item \emph{Novel condition:} if $v_1,v_2$ are two vertices belonging to $R_\delta$, then the corresponding tangencies to the divisor $m^{(j_1)}$ and $m^{(j_2)}$ must be equal.
+Here $R_\delta$ is the set of vertices $v \in \plC$ with $\lambda(v)=\delta$.
 \end{enumerate}
@@
 The strategy is as follows. We define (Definition \ref{Definition of nice locus})an open subspace
-\begin{equation*}\VZc{1}{\alpha}{\PP^N|H}{d}^{\circ} \subseteq \VZc{1}{\alpha}{\PP^N|H}{d}\end{equation*}
+\begin{equation*}\VZcrel(\PP^N|H,d)^{\circ} \subseteq \VZcrel(\PP^N|H,d)\end{equation*}
 called the \emph{nice locus}, on which the source curve and the map take a particularly simple form.
 Because of this simplicity, it is easy to show that the nice locus is irreducible (Lemma \ref{Nice locus is irreducible}).
-We then prove that $\VZc{1}{\alpha}{\PP^N|H}{d}$ is equal to the closure of the nice locus inside $\VZc{1}{n}{\PP^N}{d}$.
+We then prove that $\VZcrel(\PP^N|H,d)$ is equal to the closure of the nice locus inside $\VZc(\PP^N,d)$.
 Thus it is proper, since it is a closed space of a proper space, and it is irreducible, since it is the closure of an irreducible space inside an irreducible space.
@@
 \begin{definition} \label{Definition of nice locus} The \emph{nice locus} is defined as the open substack
-\begin{equation*}\VZc{1}{\alpha}{\PP^N|H}{d}^{\circ} \subseteq \VZc{1}{\alpha}{\PP^N|H}{d}\end{equation*}
+\begin{equation*}\VZcrel(\PP^N|H,d)^{\circ} \subseteq \VZcrel(\PP^N|H,d)\end{equation*}
 of centrally aligned maps satisfying the following two conditions:
@@
 \begin{lem}\label{Nice locus is irreducible}
-The nice locus $\VZc{1}{\alpha}{\PP^N|H}{d}^{\circ}$ is irreducible.
+The nice locus $\VZcrel(\PP^N|H,d)^{\circ}$ is irreducible.
 \end{lem}
@@
 By definition the contraction radius $\delta$ is compatible with the map, i.e.
-the subcurve $C_0\subseteq C$ where $\lambda<\delta$ is equal to the maximal connected genus one subcurve contracted by $f$.
-Hence when the source curve is irreducible we must have $\delta=0$, and we see that the central alignment on $C$ is uniquely and trivially determined.
+the subcurve $C_0\subseteq C$ where $\lambda<\delta$ is equal to the maximal connected genus one subcurve contracted by $f$.\marginpar{this is FALSE!
+I guess we may say $\delta=\lambda(v)$ for some $v$ and there is only one $v$ in this case} Hence when the source curve is irreducible we must have $\delta=0$, and we see that the central alignment on $C$ is uniquely and trivially determined.
 Thus to specify a point in the nice locus we only need to specify the source curve $C$ (as a scheme) and the map $f$.
@@
 If we allowed $e_1$ and $e_2$ to be identified in the characteristic sheaf, then we would get an extra $\Gm$ of choices for the log structure, so in total a $4$-dimensional moduli space.
-Thus if we don't impose the novel condition then we get a whole other component of the relative space, which of course for dimensional reasons cannot be contained in the closure of the nice locus.
+Thus if we don't impose the novel condition then we get a whole other component of the relative space, which of course for dimensional reasons cannot be contained in the closure of the nice locus.\marginpar{maybe the Vakil-Zinger interpretation as iterated blowups make it clearer that sometimes we cannot take all the exceptional divisors inside the relative locus if we want it to be the closure of the nice locus}
 \end{example}
 
-\begin{example} In this example we will give further moral justification for the novel condition, using as motivation the expanded degenerations approach to relative stable maps.
-This is not strictly necessary for what we want to do (since our spaces don't involve expanded degenerations), but it helps to explain where this condition comes from.
-
-So, let us pretend that we have a good definition of the ``centrally aligned Li space'' of maps from centrally aligned curves to expanded degenerations:
-\begin{equation*} \VZcLi{1}{\alpha}{X|D}{\beta} \end{equation*}
-Objects of this moduli space should consist of maps $C \to \mathfrak{X}$ where $\mathfrak{X} \to X$ is an expansion of the pair $(X,D)$, together with a central alignment on $C$ which is compatible with this map.
-The factorisation property should say that the following diagram commutes:
-\bcd
-& \tilde{C} \ar[ld,"\nu" left] \ar[rd,"\tau"] & \\
-C \ar[d,"f" left] & & \overline{C} \ar[d,"\overline{f}", dotted] \\
-\mathfrak{X} \ar[rd,"\pi"] & & \mathfrak{X} \ar[ld,"\pi"] \\
-& X & 
-\ecd
-Morally speaking, the projection map
-\begin{equation*} \pi_* \colon \VZcLi{1}{\alpha}{X|D}{\beta} \to \VZc{1}{n}{X}{\beta} \end{equation*}
-should have as its image our space $\VZc{1}{\alpha}{X|D}{\beta}$.
-We will see that everything in the image of this space must satisfy the novel condition, thus providing further justification for us imposing it.
-
-Consider therefore the following ``object'' of $\VZc{1}{(5)}{\PP^2|\PP^1}{5}$, which \emph{does not} satisfy the novel condition:
+\begin{example} In this example we will give further justification for the novel condition, using as motivation the expanded degeneration approach to relative stable maps.
 

### 2018-02-08 genus-one-relative-maps.tex
Changed code

@@
 \end{enumerate}
-subject to the condition that the contraction radius $\delta$ of the central alignment is equal to $\delta_f$, the contraction radius of the stable map $f$.
-\marginpar{what is the contraction radius of $f$?
-I think to be precise we need to say $\delta=\lambda(v)$ for $v$ such that $f$ contracts any component of $C$ closer to the circuit than $C_v$, while it has positive degree on $C_v$...} We then define
+subject to the condition that the contraction radius $\delta$ of the central alignment is equal to $\delta_f$, the contraction radius of the stable map $f$. We then define
 \begin{equation*} \VZc(X,\beta) \subseteq \tVZc(X,\beta) \end{equation*}
@@
 By definition the contraction radius $\delta$ is compatible with the map, i.e.
-the subcurve $C_0\subseteq C$ where $\lambda<\delta$ is equal to the maximal connected genus one subcurve contracted by $f$.\marginpar{this is FALSE!
-I guess we may say $\delta=\lambda(v)$ for some $v$ and there is only one $v$ in this case} Hence when the source curve is irreducible we must have $\delta=0$, and we see that the central alignment on $C$ is uniquely and trivially determined.
+the subcurve $C_0\subseteq C$ where $\lambda<\delta$ is equal to the maximal connected genus one subcurve contracted by $f$.
+Hence when the source curve is irreducible we must have $\delta=0$, and we see that the central alignment on $C$ is uniquely and trivially determined.
 Thus to specify a point in the nice locus we only need to specify the source curve $C$ (as a scheme) and the map $f$.

### 2018-02-08 genus-one-relative-maps.tex

@@
 \begin{document}
-\maketitle
 
@@
 \end{abstract}
+
+\maketitle
 
@@
 \begin{equation*} f^*[Y]|_Z -\sum_{x_i\in Z}\alpha_ix_i\end{equation*}
-is an effective class in $\Achow_1(Z)$.
-Since $Z$ is at most genus one and any line bundle of strictly positive degree on a Gorenstein genus one curve is effective, \marginpar{need to look at each irreducible component of $Z$ separately} this condition can be rephrased as the following numerical criterion
-\begin{equation*} f_*[Z]\cdot [Y]+\sum_{j=1}^r m^{(j)}\geq \sum_{x_i\in Z}\alpha_i \end{equation*}
-together with the additional requirement that, when the above is an equality, there is an isomorphism of line bundles:
-\begin{equation*} (f|_{Z})^*\OO_X(Y) \otimes \OO_Z\left(\sum_{j=1}^r m^{(j)}y_j\right)=\OO_Z\left(\sum_{x_i\in Z}\alpha_ix_i\right)\end{equation*}
+is an effective class in $\Achow_0(Z)$.
 \end{enumerate}
@@
 \end{dfn}
+
+\begin{remark}
+Trying to straighten out Gathmann's condition for a curve component of $f^{-1}(Y)$ into an easily verifiable criterion: if $Z$ is a smooth elliptic curve, recall that every line bundle of positive degree on it is effective, hence the relative condition can be rephrased as the following numerical criterion:
+\begin{equation*} f_*[Z]\cdot [Y]+\sum_{j=1}^r m^{(j)}\geq \sum_{x_i\in Z}\alpha_i \end{equation*}
+together with the additional requirement that, when the above is an equality, there is an isomorphism of line bundles:
+\begin{equation} \label{eqn:eq_in_Pic}
+(f|_{Z})^*\OO_X(Y) \otimes \OO_Z\left(\sum_{j=1}^r m^{(j)}y_j\right)=\OO_Z\left(\sum_{x_i\in Z}\alpha_ix_i\right) 
+\end{equation}
+
+ If $Z$ is reducible, the correct extension is not to impose the same condition componentwise; rather, we should ask the numerical condition for the total degree, and, if $Z$ is obtained by gluing a smooth elliptic curve $E$ with a forest of rational trees $R_i$ at roots $q^E_i$, then the line bundle equality \eqref{eqn:eq_in_Pic} should be required in $\Pic(E)$ after counting each $q^E_i$ towards the left hand side with multiplicity
+ \[f_*[R_i]\cdot [Y]+\sum_{\text{external components attached to $R_i$}} m^{(j)}- \sum_{x_j\in R_i}\alpha_j.\]
+
+ That this is the right thing to do follows from the proof that Gathmann's relative space is the projection of Jun Li's moduli space of maps to the expanded pair after contracting the higher levels of the accordion.
+\end{remark}
 
@@
 If we allowed $e_1$ and $e_2$ to be identified in the characteristic sheaf, then we would get an extra $\Gm$ of choices for the log structure, so in total a $4$-dimensional moduli space.
-Thus if we don't impose the novel condition then we get a whole other component of the relative space, which of course for dimensional reasons cannot be contained in the closure of the nice locus.\marginpar{maybe the Vakil-Zinger interpretation as iterated blowups make it clearer that sometimes we cannot take all the exceptional divisors inside the relative locus if we want it to be the closure of the nice locus}
+Thus if we don't impose the novel condition then we get a whole other component of the relative space, which of course for dimensional reasons cannot be contained in the closure of the nice locus.
 \end{example}
+
+\begin{remark}
+ For the non-expert reader, it might be convenient to recall that the extra data of a centrally aligned log structure on the curves gives a modular interpretation to the iterated blow-up procedure of Vakil and Zinger.
+In particular the novel condition on the log structure can be translated into a closed condition on the exceptional loci of these blow-ups.
+\end{remark}
 

### 2018-02-09 genus-one-relative-maps.tex

@@
 
+\section{Novel Condition 2.0}
+
+This is done with $(\PP^1,H)$ in mind; in general it will need to be modified to account for internal components of positive degree.
+
+\textbf{Novel condition 2.0:} if $v_1,v_2$ are two vertices belonging to $R_\delta$, then the corresponding tangencies $m^{(j_1)}$ and $m^{(j_2)}$ to $H$ must be equal \emph{if the corresponding rational tails are attached to the same irreducible component of $\plC_0$}.
+Here $R_\delta$ is the set of vertices $v \in \plC$ with $\lambda(v)=\delta$ and $\plC_0$ is the set of vertices with $\lambda(v)<\delta$.
+
+\textbf{Sketch of ``sufficient'' direction}: Denote by $S_0=E,S_1,\ldots,S_k$ the irreducible components of $Z$ and assume $E$ is smooth elliptic (or the core).
+Every $S_i$ for $i\geq 0$ comes with a bunch of special points: divide them into $B^-(i)=$ the singleton representing the only node separating $S_i$ from $S_0$ (this is not defined for $i=0$); $B^+(i)=$ the set of remaining nodes; and $A(i)=$ the set of markings on $S_i$.
+Start with the trivial family $E\times\Aaff^1$, where $E$ is marked with the points of $B(0)=B^+(0)$ and $A(0)$.
+Now perform a weighted blow-up at the points $\{q\in B(0)\}\times\{0\in\Aaff^1\}$ of weight $r_q$; call each resulting rational tail $S_i$ correspondingly to the original picture.
+On $S_i$ we may mark points $B^+(i)$ and $A(i)$ in such a way that the resulting point of $\oM_{0,1+|B^+(i)|+|A(i)|}$ corresponds to the one we started with.
+Now blow up this family in all the $B^+(i)\times\{0\}$ with a weight.
+Keep going until you have recreated $C$.
+Call $R_j$ the first external components, namely those corresponding to the vertices with $\lambda(v)\geq\delta$, $\nexists v'$ with $\lambda(v)>\lambda(v')\geq\delta$.
+
+We define the line bundle $\mathcal L=\OO_{\cC}(\sum \beta_iS_i)(\sum \alpha_ix_i)$; let's look at the equations that it gives us, starting from the outside.
+\begin{enumerate}
+ \item $m^{(j)}=\mathcal L_{|R_j}=\frac{\beta^-(j)}{r_{q^-(j)}}$;
+ \item on every $S_i, i\geq1$ we can prove inductively that:
+ \[0=\mathcal L_{|S_i}=\frac{\beta^-(i)-\beta_i}{r_{q^-(i)}}+\sum_{x_h\in A(i)}\alpha_i+\sum_{y_h\in B^+(i)}M^{(h)},\]
+ where I have denoted by $M^{(h)}$ the sum of all the contributions (both $\alpha_l$ and $m^{(l)}$) coming from the rational tree attached to the corresponding point of $B^+(i)$;
+ \item it turns out that $\OO_{S_0}\simeq\mathcal L_{|S_0}$ is precisely Gathmann's condition (in the numeric form if $S_0$ is a circle of rational curves). 
+\end{enumerate}
+Now notice that $\lambda(v_j)=\lambda(v_j')$ may happen only at the first external components; \marginpar{is this true?
+if not, probably there are contributions $M^{(h)}$ and $M^{(h')}$ to equate} in this case $r_{q^-(j)}=r_{q^-(j')}$, and from the first equation we see that $m^{(j)}=m^{(j')}$ if they are attached to the same component ($\beta^-(j)=\beta^-(j')$).
+The second equation can be made to hold for every $S_i$ by appropriately choosing $\beta^-(i), r_{q^-(i)}$. The last equation is automatically satisfied.
+
+Extending sections is the usual business of exploiting the fatorisation through the elliptic $m$-fold.
+
+\textbf{Sketch of ``necessary'' direction}: pick a smoothing $\cC$ of $(C,f)$.
+Suppose that $\lambda(v)=\lambda(v')$ and the corresponding $R$, $R'$ are attached to the same $S_i$, i.e.
+they share the same the tree separating them from $C_0$.
+Notice that $R$ and $R'$ map to two branches of the Smyth singularity.
+Looking at the semistable model of $\cC$, it follows that (the strict transforms of) $R$ and $R'$ still share the same tree there.
+Then by writing $(f^{\rm{ss}})^*\OO_{\PP}(1)=\OO_{\cC^{\rm{ss}}}(\sum \beta_iS_i)(\sum \alpha_ix_i)$ and intersecting with $R$, $R'$, we see that they must have the same contact order to $H$.
+
 \appendix

### 2018-02-09 the_intersection_of_two_branches_of_a_Smyth_singularity_inside_a_smoothing_is_independent_of_which_branches.sage.py
Changed code files because they were all terrible anyway

@@ -1,0 +1,26 @@
+
+# This file was *autogenerated* from the file the_intersection_of_two_branches_of_a_Smyth_singularity_inside_a_smoothing_is_independent_of_which_branches.sage
+from sage.all_cmdline import *   # import sage library
+
+_sage_const_3 = Integer(3); _sage_const_2 = Integer(2); _sage_const_1 = Integer(1); _sage_const_0 = Integer(0); _sage_const_7 = Integer(7)
+A = PolynomialRing(QQ, names=('E', 'S0', 'S1', 'R0', 'R1', 'R2', 'a0', 'a1', 'a2', 'b00', 'b01', 'b10', 'b11', 'b20', 'b21', 'T0', 'T1', 'T2',)); (E, S0, S1, R0, R1, R2, a0, a1, a2, b00, b01, b10, b11, b20, b21, T0, T1, T2,) = A._first_ngens(18);
+
+I = ideal(T0-R0-a0*E-b00*S0-b01*S1,T1-R1-a1*E-b10*S0-b11*S1,T2-R2-a2*E-b20*S0-b21*S1,E*T0,S0*T0,S1*T0,E*T1,S0*T1,S1*T1,E*T2,S0*T2,S1*T2,T0+T1+T2,R0+R1+R2+S0+S1+E,R0**_sage_const_2 +_sage_const_1 ,R1**_sage_const_2 +_sage_const_1 ,R2**_sage_const_2 +_sage_const_1 ,S0**_sage_const_2 +_sage_const_3 ,S1**_sage_const_2 +_sage_const_2 ,E**_sage_const_2 +_sage_const_2 ,R0*S0-_sage_const_1 ,R0*R1,R0*E,R0*S1,R0*R2,R1*S0-_sage_const_1 ,R1*R0,R1*E,R1*S1,R1*R2,S0*R0-_sage_const_1 ,S0*R1-_sage_const_1 ,S0*E-_sage_const_1 ,S0*S1,S0*R2,E*S1-_sage_const_1 ,E*R2,S1*R2-_sage_const_1 )
+
+B=A.quotient(I);
+
+K=ideal(T1*T2-T0*T2)
+
+#isSubset(K,I)
+
+e=B(S0-_sage_const_2 );
+x=B(T0*(T1-T2)-(_sage_const_3 /_sage_const_7 ));
+z=B(T0*(T1-T2)-R0*(T1-T2));
[…]

### 2018-02-09 genus-one-relative-maps.tex

@@
 is an effective class in $\Achow_0(Z)$.
+Since $Z$ is at most genus one and any line bundle of strictly positive degree on a Gorenstein genus one curve is effective, this condition can be rephrased as the following numerical criterion
+\begin{equation*} Y \cdot f_*[Z]+\sum_{j=1}^r m_j\geq \sum_{x_i\in Z}\alpha_i \end{equation*}
+where the $m_j$ denote the multiplicities of $f$ along $Y$ at the points $y_j \in Z \cap \overline{C \setminus Z}$ (necessarily a finite number of nodes), together with the requirement that, when we have equality in the above, there is an isomorphism of line bundles:
+\begin{equation*} (f|_{Z})^*\OO_X(Y) \otimes \OO_Z\left(\sum_{j=1}^r m_j y_j\right)=\OO_Z\left(\sum_{x_i\in Z}\alpha_ix_i\right)\end{equation*}
 \end{enumerate}
 
-\item \emph{Novel condition:} if $v_1,v_2$ are two vertices belonging to $R_\delta$, then the corresponding tangencies to the divisor $m^{(j_1)}$ and $m^{(j_2)}$ must be equal.
-Here $R_\delta$ is the set of vertices $v \in \plC$ with $\lambda(v)=\delta$.
+\item \emph{Novel condition:} if $v_1,v_2$ are two vertices belonging to $R_\delta$, then the corresponding tangencies to the divisor $m_{j_1}$ and $m_{j_2}$ must be equal.
+Here $R_\delta$ is the set of vertices $v \in \plC$ with $\lambda(v)=\delta$ equal to the contraction radius.
 \end{enumerate}
@@
 
-\begin{example} In this example we will give further justification for the novel condition, using as motivation the expanded degeneration approach to relative stable maps.
+\begin{example} In this example we will give further moral justification for the novel condition, using as motivation the expanded degenerations approach to relative stable maps.
+This is not strictly necessary for what we want to do (since our spaces don't involve expanded degenerations), but it helps to explain where this condition comes from.
+
+So, let us pretend that we have a good definition of the ``centrally aligned Li space'' of maps from centrally aligned curves to expanded degenerations:
+\begin{equation*} \VZcLi{1}{\alpha}{X|D}{\beta} \end{equation*}
+Objects of this moduli space should consist of maps $C \to \mathfrak{X}$ where $\mathfrak{X} \to X$ is an expansion of the pair $(X,D)$, together with a central alignment on $C$ which is compatible with this map.
+The factorisation property should say that the following diagram commutes:
+\bcd
+& \tilde{C} \ar[ld,"\nu" left] \ar[rd,"\tau"] & \\
+C \ar[d,"f" left] & & \overline{C} \ar[d,"\overline{f}", dotted] \\
+\mathfrak{X} \ar[rd,"\pi"] & & \mathfrak{X} \ar[ld,"\pi"] \\
+& X & 
+\ecd
+Morally speaking, the projection map
+\begin{equation*} \pi_* \colon \VZcLi{1}{\alpha}{X|D}{\beta} \to \VZc{1}{n}{X}{\beta} \end{equation*}
+should have as its image our space $\VZc{1}{\alpha}{X|D}{\beta}$.
+We will see that everything in the image of this space must satisfy the novel condition, thus providing further justification for us imposing it.
+
+We proceed by contradiction. Consider a genus one map $C \to \PP^1$ of the following form
+\begin{center}
+\begin{tikzpicture}
+\draw[fill=black] (0,0) node[left]{$E$} -- (4,0);
+\draw[fill=black] (0.7,0) circle[radius=2pt] node[below]{$5$};
+\draw[fill=black] (2,0) circle[radius=2pt] node[above right]{$2$};
+\draw[fill=black] (3,0) circle[radius=2pt] node[above right]{$3$};
+\draw (2,1.5) node[right]{$C_1$};
+\draw (3,1.5) node[right]{$C_2$};
+\draw (2,-1) -- (2,2) node[above]{$2$};
+\draw (3,-1) -- (3,2) node[above]{$3$};
+
+\draw[->] (4.5,0) -- (6.5,0);
+\draw (5.5,0) node[above]{$f$};
+\draw (7,-1) -- (7,2) node[above]{$\PP^1$};
+\draw[fill=black] (7,0) circle[radius=2pt] node[right]{$\infty$};
+\end{tikzpicture}
+\end{center}
+and equip the source curve $C$ with a central alignment which identifies the lengths of the components $C_1$ and $C_2$:
+\begin{center}
+\begin{tikzpicture}
+\draw[red,thick,dashed] (0,0) circle[radius=51pt];
+\draw[red] (-1.75,0) node[left]{$R_\delta$};
+\draw[fill=white] (0,0) circle[radius=4pt];
+\draw (0,0.1) node[above]{$E$};
+\draw[fill=black] (-1,-1.5) circle[radius=4pt];
+\draw (-1.1,-1.5) node[left]{$C_1$};
+\draw[fill=black] (-0.1,-0.1) -- (-1,-1.5);
+\draw[fill=black] (1,-1.5) circle[radius=4pt];
+\draw (1.1,-1.5) node[right]{$C_2$};
+\draw[fill=black] (0.1,-0.1) -- (1,-1.5);
+\end{tikzpicture}
+\end{center}
+This defines an ``object'' of $\VZc{1}{(5)}{\PP^1|\infty}{5}$, satisfying all the necessary conditions \emph{except for the novel condition}.
+We will show that this cannot belong to the image of $\pi_*$.
+
+First we have to identify what the possible lifts of this object to the centrally aligned Li space are.
+
+>>>>>>> navid
 

### 2018-02-09 genus-one-relative-maps.tex
Added some pictures to example

@@
 together with the additional requirement that, when the above is an equality, there is an isomorphism of line bundles:
-\begin{equation} \label{eqn:eq_in_Pic}
+\begin{equation}\label{eqn:eq_in_Pic}
 (f|_{Z})^*\OO_X(Y) \otimes \OO_Z\left(\sum_{j=1}^r m^{(j)}y_j\right)=\OO_Z\left(\sum_{x_i\in Z}\alpha_ix_i\right) 
@@
 
-First we have to identify what the possible lifts of this object to the centrally aligned Li space are.
+First we have to identify what the possible lifts of this object to the centrally aligned Li space are. The map $C \to \mathfrak{X}$ takes the following form:
 
->>>>>>> navid
+\begin{center}
+\begin{tikzpicture}
+\draw (-1,-1) -- (1,-1);
+\draw (-1,-1) -- (-1,1);
+\draw (1,-1) -- (1,1);
+\draw (-1,1) -- (1,1);
+\draw (-1,-1) -- (-2,-2.5);
+\draw (-2,-2.5) -- (0,-2.5);
+\draw (0,-2.5) -- (1,-1);
+\draw[red,very thick] (-2,-2.5) -- (-0.5,-1);
+\draw[red] (-1,-1.5) node[right]{$C_1$};
+\draw[red,fill=red] (-0.5,-1) circle[radius=2pt];
+\draw[red] (-0.6,-1) node[above]{$2$};
+
+\draw[red,very thick] (0,-2.5) -- (0,-1);
+\draw[red] (-0.1,-1.5) node[right]{$C_2$};
+\draw[red,fill=red] (0,-1) circle[radius=2pt];
+\draw[red] (0.1,-1) node[above]{$3$};
+
+\draw[red,very thick] (-0.5,-1) to [out=90,in=180] (-0.25,-0.8) to [out=0,in=90] (0,-1);
+\draw[red,very thick] (-0.25,-0.8) -- (0,1);
+\draw[red] (0.1,0) node{$E$};
+\draw[red,fill=red] (0,1) circle[radius=2pt] node[above]{$5$};
+\end{tikzpicture}
+\end{center}
+(Here the box at level $1$ represents a single fibre of the expanded degeneration; $E$ is mapped into a fibre and has zero horizontal degree.) In this case $\tilde{C}$ is obtained from $C$ by bubbling a rational component at the marking, and so the map $\tilde{C} \to \mathfrak{X}$ is given by:
+
+\begin{center}
+\begin{tikzpicture}
+\draw (-1,-1) -- (1,-1);
+\draw (-1,-1) -- (-1,1);
+\draw (1,-1) -- (1,1);
+\draw (-1,1) -- (1,1);
+\draw (-1,-1) -- (-2,-2.5);
+\draw (-2,-2.5) -- (0,-2.5);
+\draw (0,-2.5) -- (1,-1);
+\draw (-1,1) -- (-1,3);
+\draw (-1,3) -- (1,3);
+\draw (1,3) -- (1,1);
+\draw[red,very thick] (-2,-2.5) -- (-0.5,-1);
+\draw[red] (-1,-1.5) node[right]{$C_1$};
+\draw[red,fill=red] (-0.5,-1) circle[radius=2pt];
+\draw[red] (-0.6,-1) node[above]{$2$};
+
+\draw[red,very thick] (0,-2.5) -- (0,-1);
+\draw[red] (-0.1,-1.5) node[right]{$C_2$};
+\draw[red,fill=red] (0,-1) circle[radius=2pt];
+\draw[red] (0.1,-1) node[above]{$3$};
+
+\draw[red,very thick] (-0.5,-1) to [out=90,in=180] (-0.25,-0.8) to [out=0,in=90] (0,-1);
+\draw[red,very thick] (-0.25,-0.8) -- (0,1);
+\draw[red] (0.1,0) node{$E$};
+\draw[red,fill=red] (0,1) circle[radius=2pt];
+\draw[red] (-0.2,1) node[above]{$5$};
+
+\draw[red, very thick] (0,1) -- (0,3);
+\draw[red] (0,2) node[right]{$C_3$};
+\draw[red,fill=red] (0,3) circle[radius=2pt] node[above]{$5$};
+\end{tikzpicture}
+\end{center}
 

### 2018-02-10 genus-one-relative-maps.tex
Finished example of expanded degeneration justifying novel condition (it ended up quite long)

@@
 \newcommand{\NN}{\operatorname{N}}
+\newcommand{\ovm}[1]{\overline{\mathcal{#1}}}
+\newcommand{\ovt}[1]{\widetilde{\mathcal{#1}}}
+\newcommand{\ov}[1]{\overline{#1}}
 
@@
 If we allowed $e_1$ and $e_2$ to be identified in the characteristic sheaf, then we would get an extra $\Gm$ of choices for the log structure, so in total a $4$-dimensional moduli space.
-Thus if we don't impose the novel condition then we get a whole other component of the relative space, which of course for dimensional reasons cannot be contained in the closure of the nice locus.
+Thus if we don't impose the novel condition then we get a whole other component of the relative space, which of course for dimensional reasons cannot be contained in the closure of the nice locus.\qed
 \end{example}
@@
 \begin{equation*} \VZcLi{1}{\alpha}{X|D}{\beta} \end{equation*}
-Objects of this moduli space should consist of maps $C \to \mathfrak{X}$ where $\mathfrak{X} \to X$ is an expansion of the pair $(X,D)$, together with a central alignment on $C$ which is compatible with this map.
+Objects of this moduli space should consist of maps $C \to X_l$ where $X_l \to X$ is an expansion (of some length $l$) of the pair $(X,D)$, together with a central alignment on $C$ which is compatible with this map.
 The factorisation property should say that the following diagram commutes:
@@
 C \ar[d,"f" left] & & \overline{C} \ar[d,"\overline{f}", dotted] \\
-\mathfrak{X} \ar[rd,"\pi"] & & \mathfrak{X} \ar[ld,"\pi"] \\
+X_l \ar[rd,"\pi"] & & X_l \ar[ld,"\pi"] \\
 & X & 
@@
 
-First we have to identify what the possible lifts of this object to the centrally aligned Li space are. The map $C \to \mathfrak{X}$ takes the following form:
+First we have to identify what the possible lifts of this object to the centrally aligned Li space are. The map $C \to X_1$ takes the following form:
 
@@
 \end{center}
-(Here the box at level $1$ represents a single fibre of the expanded degeneration; $E$ is mapped into a fibre and has zero horizontal degree.) In this case $\tilde{C}$ is obtained from $C$ by bubbling a rational component at the marking, and so the map $\tilde{C} \to \mathfrak{X}$ is given by:
-
+(Here we use Navid's convention for drawing maps to expanded degenerations, so that the box at level $1$ represents a \emph{single fibre} of the expanded degeneration, i.e.
+$E$ is mapped into a fibre and has zero horizontal degree.) Now, $\widetilde{C}$ is obtained from $C$ by bubbling a rational component $C_3$ at the single marking, and so the map $\widetilde{C} \to X_2$ is given by:
 \begin{center}
@@
 \end{center}
+The map $\widetilde{C} \to \overline{C}$ contracts the elliptic component $E$, and so the map $\overline{C} \to X_1$ \emph{should} take the form:
+\begin{center}
+\begin{tikzpicture}
+\draw (-1,-1) -- (1,-1);
+\draw (-1,-1) -- (-1,1);
+\draw (1,-1) -- (1,1);
+\draw (-1,1) -- (1,1);
+\draw (-1,-1) -- (-2,-2.5);
+\draw (-2,-2.5) -- (0,-2.5);
+\draw (0,-2.5) -- (1,-1);
+\draw[red,very thick] (-2,-2.5) -- (0,-1);
+\draw[red] (-0.8,-1.7) node[below]{$\overline{C}_1$};
+\draw[red,fill=red] (0,-1) circle[radius=2pt];
 
+\draw[red,very thick] (0,-2.5) -- (0,-1);
+\draw[red] (-0.05,-1.5) node[right]{$\overline{C}_2$};
+\draw[red,fill=red] (0,-1) circle[radius=2pt];
+
+\draw[red,very thick] (0,-1) -- (0,1);
+\draw[red] (0.35,0) node{$\overline{C}_3$};
+\draw[red,fill=red] (0,1) circle[radius=2pt] node[above]{$5$};
+\end{tikzpicture}
+\end{center}
+We will now see that, in this example, the map drawn above cannot actually exist, and that this occurs precisely because we have violated the novel condition.
+
+We start by choosing a one-parameter smoothing $\mathcal{C} \to \Aaff^1$ of the centrally aligned curve $C$.
+This induces one-parameter smoothings $\widetilde{\mathcal{C}}$ of $\widetilde{C}$ and $\overline{\mathcal{C}}$ of $\overline{C}$.
+Since the factorisation condition must also hold in families, we must have a map $\overline{\mathcal{C}} \to \mathfrak{X}$, whose general fibre maps to the space $X_0=X$ (with no expansion) and whose general fibre maps to $X_1=X \sqcup_D Y$.
+
+We thus have a map $\ovm{C} \to \mathfrak{X}$, where $\mathfrak{X}$ is the total space of the expanded degeneration.
+This is obtained as the toric blow-up of $\PP^1 \times \Aaff^1$ at the point $(\infty,0)$.
+Thus it is also a smooth toric variety, with fan given by:
+\begin{center}
+\begin{tikzpicture}
+\draw[fill=black] (0,0) circle[radius=2pt];
+\draw[thick] (0,0) -- (2,0) node[above]{$\rho_1$};
+\draw[thick] (0,0) -- (1.75,1.75) node[right]{$\rho_2$};
+\draw[thick] (0,0) -- (0,2) node[left]{$\rho_3$};
+\draw[thick] (0,0) -- (0,-1.75) node[left]{$\rho_4$};
+\end{tikzpicture}
+\end{center}
+There is a map $\mathfrak{X} \to \Aaff^1$ whose general fibre is isomorphic to $X$ and whose central fibre is isomorphic to $X_1$.
+We see from the fan above that $\Pic(\mathfrak{X})$ is generated by $\OO_{\mathfrak{X}}(D_{\rho_i})$ for $i=1,\ldots,4$, subject to the relations:
+\begin{align*}
+\OO_{\mathfrak{X}}(D_{\rho_1}) \otimes \OO_{\mathfrak{X}}(D_{\rho_2}) & \cong \OO_{\mathfrak{X}} \\
+\OO_{\mathfrak{X}}(D_{\rho_2}) \otimes \OO_{\mathfrak{X}}(D_{\rho_3}) & \cong \OO_{\mathfrak{X}}(D_{\rho_4})
+\end{align*}
+Choosing as $\{\OO_{\mathfrak{X}}(D_{\rho_1}), \OO_{\mathfrak{X}}(D_{\rho_3})\}$ our minimal set of generators, we see that a map $\overline{\mathcal{C}} \to \mathfrak{X}$ is given by the data of line bundes $L_1$ and $L_3$ on $\overline{\mathcal{C}}$ together with sections:
+\begin{align*}
+s_1 & \in \HH^0(\overline{\mathcal{C}},L_1) \\
+s_2 & \in \HH^0(\overline{\mathcal{C}},L_1^{-1}) \\
+s_3 & \in \HH^0(\overline{\mathcal{C}},L_3) \\
+s_4 & \in \HH^0(\overline{\mathcal{C}},L_1^{-1}\otimes L_3)
+\end{align*}
+The divisors $D_{\rho_1}$ and $D_{\rho_2}$ are, respectively, the level-$0$ and level-$1$ pieces of the central fibre of $\mathfrak{X}$. Therefore we must have
+\begin{align*} & L_1 \cong \OO_{\overline{\mathcal{C}}}(a_1 \ov{C}_1 + a_2 \ov{C}_2) \\
+& L_1^{-1} \cong \OO_{\ov{C}}(a_3 \ov{C}_3)
+\end{align*}
+for some positive integers $a_1,a_2$ and $a_3$.
+Here we are using the fact that each $\ov{C}_i$ is a $\QQ$-Cartier divisor on $\ovm{C}$, so that (after possibly multipltying by some positive integer) the corresponding line bundle makes sense.
+Furthermore, the intersection multiplicites of $\ov{C}_1$ and $\ov{C}_2$ with the level-$1$ piece mean that we must have:
+\begin{align*} \deg(L_1^{-1}|_{\ov{C}_1}) & = 2\\
+\deg(L_1^{-1}|_{\ov{C}_2}) & = 3 \end{align*}
+We thus obtain:
+\begin{align*} a_3 (\ov{C}_1 \cdot \ov{C}_3)&  = 2 \\
+a_3 (\ov{C}_2 \cdot \ov{C}_3)& = 3 \end{align*}
+However, we claim that in fact $\ov{C}_1 \cdot \ov{C}_3 = \ov{C}_2 \cdot \ov{C}_3$, so that the above equations cannot hold.
+To calculate these intersection numbers, we pass to the semistable model of $\ovm{C}$.
+This is obtained by performing further blow-ups to $\ovt{C}$, resulting in a semistable model $\ovt{C}^{\operatorname{ss}}$of the following form:
+\begin{center}
+\begin{tikzpicture}
+\draw (-3,-3) -- (-3,2);
+\draw (-3,-2.5) node[left]{$E$};
+
+\draw (-3.5,1.5) -- (-0.5,1.5);
+\draw (-1.3,1.725) -- (0.5,0.5);
+\draw[fill=black] (0.8,0.5) circle[radius=0.5pt];
+\draw[fill=black] (0.9,0.5) circle[radius=0.5pt];
+\draw[fill=black] (1,0.5) circle[radius=0.5pt];
+\draw (3,1.725) -- (1.2,0.5);
+\draw (1.9,0.9) node[right]{$R_1^1$};
+\draw (2.5,1.5) -- (5,1.5);
+\draw (4,1.5) node[below]{$R_1$};
+
+\draw (-3.5,0) -- (-0.5,0);
+\draw (-1.3,0.225) -- (0.5,-1);
+\draw[fill=black] (0.8,-1) circle[radius=0.5pt];
+\draw[fill=black] (0.9,-1) circle[radius=0.5pt];
+\draw[fill=black] (1,-1) circle[radius=0.5pt];
+\draw (3,0.225) -- (1.2,-1);
+\draw (1.9,-0.6) node[right]{$R_2^1$};
+\draw (2.5,0) -- (5,0);
+\draw (4,0) node[below]{$R_2$};
+
+\draw (-3.5,-1.5) -- (-0.5,-1.5);
+\draw (-1.3,-1.275) -- (0.5,-2.5);
+\draw[fill=black] (0.8,-2.5) circle[radius=0.5pt];
+\draw[fill=black] (0.9,-2.5) circle[radius=0.5pt];
+\draw[fill=black] (1,-2.5) circle[radius=0.5pt];
+\draw (3,-1.275) -- (1.2,-2.5);
+\draw (2.5,-1.5) -- (5,-1.5);
+\draw (4,-1.5) node[below]{$R_3$};
+\end{tikzpicture}
+\end{center}
+Here the component labeled $E$ is smooth elliptic and all the other components are smooth rational.
+The projection $\pi: \ovt{C}^{\operatorname{ss}} \to \ovm{C}$ sends each $R_i$ to $\ov{C}_i$ and contracts all the other components.
+The semistable model has the advantage that the total space is regular, so the intersections are precisely those that you ``see'' in the picture.
+In particular, any two adjacent components have intersection $1$, and the self-intersection of any component is equal to minus the number of adjacent components.
+
+Now, $\ov{C}_i \cdot \ov{C}_j = (\pi^* \ov{C}_i)\cdot(\pi^* \ov{C}_j)$, so we want to show that:
+\begin{equation*} (\pi^* \ov{C}_1)\cdot(\pi^*\ov{C}_3) = (\pi^* \ov{C}_2)\cdot(\pi^*\ov{C}_3) \end{equation*}
+For each $i$, $\pi^*\ov{C}_i$ is equal to $R_i$ plus a non-negative linear combination of the components in $\ovt{C}^{\operatorname{ss}}$ contracted by $\pi$.
+By the projection formula, any component contracted by $\pi$ will multiply to zero with a class pulled back along $\pi$.
+Thus
+\begin{equation*} (\pi^* \ov{C}_1)\cdot(\pi^*\ov{C}_3) = R_1 \cdot (\pi^*\ov{C}_3) = a_3(R_1^1) \end{equation*}
+the coefficient of $R_1^1$ in $\pi^* \ov{C}_3$. Similarly
+\begin{equation*} (\pi^* \ov{C}_2) \cdot (\pi^* \ov{C}_3) = a_3(R_2^1) \end{equation*}
+the coefficient of $R_2^1$ in $\pi^* \ov{C}_3$. So we need to show that:
+\begin{equation*} a_3(R_1^1) = a_3(R_1^2) \end{equation*}
+Now, we have
+\begin{equation*} 0 = R_1^1 \cdot (\pi^* \ov{C}_3) = a_3(R_1^2) - 2a_3(R_1^1) \end{equation*}
+because $(R_1^1)^2=-2$. So $a_3(R_1^1) = a_3(R_1^2)/2$. Similarly:
+\begin{equation*} 0 = R_1^2 \cdot (\pi^*\ov{C}_3) = a_3(R_1^1) - 2a_3(R_1^2) + a_3(R_1^3) = -3a_3(R_1^1) + a_3(R_1^3) \end{equation*}
+So $a_3(R_1^1) = a_3(R_1^3)/3$. Continuing in this way, we find that
+\begin{equation*} a_3(R_1^1) = a_3(E)/l_1 \end{equation*}
+where $l_1$ is the length of the rational tail connecting $E$ to $R_1$.
+Similarly $a_3(R_1^2) = a_3(E)/l_2$.
+But by Smyth's balancing condition for the semistable model \cite[Proposition 2.11]{SMY1}, we must have $l_1=l_2$.
+This concludes the proof that $\ov{C}_1 \cdot \ov{C}_3 = \ov{C}_2 \cdot \ov{C}_3$, which shows the necessity of the novel condition in this example.
+
+Notice that here we used the fact that the rational tails $\ov{C}_1$ and $\ov{C}_2$ are adjacent to the same irreducible component (namely $E$) of the core.\qed
 \end{example}
 
-\subsection{Proof}
-We now want to show that the relative space in the centrally aligned setting is equal to the closure of the nice locus; irreducibility then follows immediately. We start with one direction.
+\subsection{Proof that the relative space equals the closure of the nice locus.}
+We now want to show that the relative space in the centrally aligned setting is equal to the closure of the nice locus; irreducibility then follows immediately. We start with one direction:
 
@@
 \begin{proof}
-We address the relative conditions one at a time. Notice that they are all obviously satisfied on the nice locus.
-
-The factorisation property is closed: see \cite[Theorem 4.3]{RSPW}.
-
-Gathmann's relative condition is closed: see \cite[Proposition 4.9]{Vre}.
+We address the relative conditions one at a time.
+Notice that they are all obviously satisfied on the nice locus.
+Also, Gathmann's relative condition is obviously closed; see \cite[Proposition 4.9]{Vre}.
 

### 2018-02-16 genus-one-relative-maps.tex

@@
 \end{enumerate}
-subject to the condition that the contraction radius $\delta$ of the central alignment is equal to $\delta_f$, the contraction radius of the stable map $f$. We then define
+subject to the condition that the subcurve $C_0 \subseteq C$, consisting of those components $C_v$ for which $\lambda(v) < \delta$, coincides with the maximal connected genus one subcurve contracted by $f$.
+We then define
 \begin{equation*} \VZc{1}{n}{X}{\beta} \subseteq \tVZc{1}{n}{X}{\beta} \end{equation*}
@@
 \begin{remark} In the case of a general pair $(X,Y)$ we will see that the moduli space is still proper, but is not in general irreducible or even equidimensional.
-Nevertheless, we can equip it with a virtual class by `pulling back'' from the case of $(\PP^N,H)$; for details, see \S [REF].
+Nevertheless, we can equip it with a virtual class by ``pulling back'' from the case of $(\PP^N,H)$; for details, see \S [REF].
 \end{remark}
 
-The strategy is as follows. We define (Definition \ref{Definition of nice locus})an open subspace
+The strategy is as follows. We define (Definition \ref{Definition of nice locus}) an open subspace
 \begin{equation*}\VZc{1}{\alpha}{\PP^N|H}{d}^{\circ} \subseteq \VZc{1}{\alpha}{\PP^N|H}{d}\end{equation*}
@@
 We then prove that $\VZc{1}{\alpha}{\PP^N|H}{d}$ is equal to the closure of the nice locus inside $\VZc{1}{n}{\PP^N}{d}$.
-Thus it is proper, since it is a closed space of a proper space, and it is irreducible, since it is the closure of an irreducible space inside an irreducible space.
+Thus it is proper, since it is a closed subspace of a proper space, and it is irreducible, since it is the closure of an irreducible space.
 
@@
 Consider $\M{1}{(3)}{\PP^1|H}{3}$.
-The virtual dimension is $7-3=4$.
-Here is a parametrisation of the nice locus: choose an element $(E,p)$ of $\oM_{1,1}\setminus\partial\oM_{1,1}$ (which has dimension $1$), and let $s_0$ be the natural section $s_0 \colon\OO_E\hookrightarrow\OO_E(3p)$ and $s_1$ any other section of $\OO_E(3p)$ not vanishing at $p$ (notice that $\h^0(E,\OO_E(3p))=3$).
+This moduli space has virtual dimension $6+1-3=4$.
+Here is a parametrisation of the nice locus: choose an object $(E,p) \in \mathcal{M}_{1,1}$, and let $s_0$ be the natural section $s_0 \colon\OO_E\hookrightarrow\OO_E(3p)$ and $s_1$ any other section of $\OO_E(3p)$ not vanishing at $p$ (notice that $\h^0(E,\OO_E(3p))=3$).
 Then $(E,p,[\lambda s_0,s_1])$ gives a well-defined element of the nice locus for $\lambda \neq 0$.
@@
 where the brown line represents a contracted genus $1$ curve.
-Now $(E,x_1,y_1,y_2)$ is a point of $\oM_{1,3}$ subject to the divisorial condition $3x_1-2y_1-y_2=0\in \Achow_0(E)$; furthermore we have to choose the second branch point of the $2\colon 1$ map from $R_1$ to $\PP^1$.
+Now $(E,x_1,y_1,y_2)$ is a point of $\mathcal{M}_{1,3}$ subject to the divisorial condition $3x_1-2y_1-y_2=0\in \Achow_0(E)$; furthermore we have to choose the second branch point of the $2:1$ map from $R_1$ to $\PP^1$.
 This already makes up for a $3$-dimensional moduli space of degenerate relative maps corresponding to such a graph.

### 2018-02-17 genus-one-relative-maps.tex
changed compatibility into monoid factorisation

@@
 \usepackage{amssymb}
-\usepackage{showlabels}
+%\usepackage{showlabels}
 \usepackage{hyperref}
@@
 \section{The space of relative centrally aligned maps}
-\noindent Recall \cite{RSPW} that the moduli space of maps from centrally aligned curves is obtained by first considering the  Cartesian diagram
+\noindent Recall \cite{RSPW} that the moduli space of maps from centrally aligned curves is obtained by considering the  Cartesian diagram
 \bcd
@@
 subject to the condition that the subcurve $C_0 \subseteq C$, consisting of those components $C_v$ for which $\lambda(v) < \delta$, coincides with the maximal connected genus one subcurve contracted by $f$.
-We then define
+They then define
 \begin{equation*} \VZc{1}{n}{X}{\beta} \subseteq \tVZc{1}{n}{X}{\beta} \end{equation*}
@@
 
-\subsection{Definition of the relative space} We now give the central definition of this article.
+\subsection{Definition of the relative space} We now give a definition of the relative space inside the moduli space of centrally aligned stable maps.
 \begin{dfn}
-Fix a vector of tangency conditions $\alpha=(\alpha_1,\ldots,\alpha_n)$ with $\Sigma_{i=1}^n \alpha_i \leq Y \cdot \beta$. Then the \emph{centrally aligned relative space} 
+Let $X$ be a smooth projective variety with a smooth divisor $Y$.
+Fix a vector of tangency conditions $\alpha=(\alpha_1,\ldots,\alpha_n)$ with $\Sigma_{i=1}^n \alpha_i = Y \cdot \beta$.
+Then the \emph{centrally aligned relative space}
 \begin{equation*}\VZc{1}{\alpha}{X|Y}{\beta} \end{equation*}
@@
 is an effective class in $\Achow_0(Z)$.
-Since $Z$ is at most genus one and any line bundle of strictly positive degree on a Gorenstein genus one curve is effective, this condition can be rephrased as the following numerical criterion
-\begin{equation*} Y \cdot f_*[Z]+\sum_{j=1}^r m_j\geq \sum_{x_i\in Z}\alpha_i \end{equation*}
-where the $m_j$ denote the multiplicities of $f$ along $Y$ at the points $y_j \in Z \cap \overline{C \setminus Z}$ (necessarily a finite number of nodes), together with the requirement that, when we have equality in the above, there is an isomorphism of line bundles:
-\begin{equation*} (f|_{Z})^*\OO_X(Y) \otimes \OO_Z\left(\sum_{j=1}^r m_j y_j\right)=\OO_Z\left(\sum_{x_i\in Z}\alpha_ix_i\right)\end{equation*}
 \end{enumerate}
 
-\item \emph{Novel condition:} if $v_1,v_2$ are two vertices belonging to $R_\delta$, then the corresponding tangencies to the divisor $m_{j_1}$ and $m_{j_2}$ must be equal.
-Here $R_\delta$ is the set of vertices $v \in \plC$ with $\lambda(v)=\delta$ equal to the contraction radius.
+\item \emph{Compatibility condition:} this applies when the minimal subcurve of genus one (the \emph{circuit} or \emph{core}) is contracted to a point in $Y$.
+In this case we require that the following diagram of solid arrows may be completed to a commutative diagram:
+\bcd
+Q_{\rm{min}}^{\rm{prestable}}\ar[r]\ar[d] & Q_{\rm{min}}^{\rm{log.map}} \\
+Q_{\rm{min}}^{\rm{cen.align}}\ar[dashed,ur]
+\ecd
 \end{enumerate}
@@
 
-\begin{remark}
-Trying to straighten out Gathmann's condition for a curve component of $f^{-1}(Y)$ into an easily verifiable criterion: if $Z$ is a smooth elliptic curve, recall that every line bundle of positive degree on it is effective, hence the relative condition can be rephrased as the following numerical criterion:
+\begin{remark}[Explaining Gathmann]
+Gathmann's condition is promptly extended to the case that $\Sigma_{i=1}^n \alpha_i \leq Y \cdot \beta$.
+\textcolor{red}{Question: what is the correct generalisation of the compatibility condition?} Here we try to make the condition for a curve component of $f^{-1}(Y)$ into an easily verifiable criterion: if $Z$ is a smooth elliptic curve, recall that every line bundle of positive degree on it is effective, hence the relative condition can be rephrased as the following numerical criterion:
 \begin{equation*} f_*[Z]\cdot [Y]+\sum_{j=1}^r m^{(j)}\geq \sum_{x_i\in Z}\alpha_i \end{equation*}
@@
 
- If $Z$ is reducible, the correct extension is not to impose the same condition componentwise; rather, we should ask the numerical condition for the total degree, and, if $Z$ is obtained by gluing a smooth elliptic curve $E$ with a forest of rational trees $R_i$ at roots $q^E_i$, then the line bundle equality \eqref{eqn:eq_in_Pic} should be required in $\Pic(E)$ after counting each $q^E_i$ towards the left hand side with multiplicity
- \[f_*[R_i]\cdot [Y]+\sum_{\text{external components attached to $R_i$}} m^{(j)}- \sum_{x_j\in R_i}\alpha_j.\]
+ If $Z$ is reducible, the correct extension is not to impose the same condition componentwise; rather, we should ask the numerical condition for the total degree, and, if $Z$ is obtained by gluing a smooth elliptic curve $E$ with a forest of rational trees $T_i$ at roots $q^E_i$, then the line bundle equality \eqref{eqn:eq_in_Pic} should be required in $\Pic(E)$ after counting each $q^E_i$ towards the left hand side with multiplicity
+ \[f_*[T_i]\cdot [Y]+\sum_{\text{external components attached to $T_i$}} m^{(j)}- \sum_{x_j\in T_i}\alpha_j.\]
 
- That this is the right thing to do follows from the proof that Gathmann's relative space is the projection of Jun Li's moduli space of maps to the expanded pair after contracting the higher levels of the accordion.
+ %That this is the right thing to do follows from the proof that Gathmann's relative space is the projection of Jun Li's moduli space of maps to the expanded pair after contracting the higher levels of the accordion.
+\end{remark}
+
+\begin{remark}[Explaining compatibility]
+First I wish to define the first line $Q_{\rm{min}}^{\rm{prestable}}\to Q_{\rm{min}}^{\rm{log.map}}$; when looking at a geometric point $\Spec(k=\bar k)$ it is well-known that \[ Q_{\rm{min}}^{\rm{prestable}}=\prod_{q\ \text{node}}\mathbb N_q.\]
+Let me assume that all the nodes are internal, i.e.
+map to $Y$, for all the action happens there, and also that there is only one internal connected component $Z$, which has arithmetic genus one.
+Then I define $Q_{\rm{min}}^{\rm{log.map}}$ as the saturation of the quotient of
+\begin{equation}\label{eq:logminmod} \prod_{q\ \text{node}}\mathbb N_q \times \prod_{S\ \text{internal irr. compo.}}\mathbb N_S\end{equation}
+by the relation generated in the groupification of the latter by
+\[\langle \rm{Rel}_q=(u_q,\ldots,1,\ldots,-1,\ldots),\ q\ \text{internal node} \rangle\]
+where $1$ is in position $S_q^+$ (adjacent to $q$ and further from the circuit), $-1$ in position $S_q^-$ (adjacent to $q$ and closer to the circuit), and $u_q$ in position $q$ is defined as to include the tropical balancing condition (I don't know whether this is standard):
+\[u_q=f_*[T_q]\cdot [Y]+\sum_{R_i \text{external compo. attached to }T_q} m^{(i)}- \sum_{x_j\in T_q}\alpha_j,\]
+where $T_q$ is the tree of internal components that $q$ separates from the circuit.
+Notice that the nodes separating $Z$ from the external components have no $1$, so the corresponding relations look like \[(u_q,\ldots,-1,\ldots).\]
+The map $Q_{\rm{min}}^{\rm{prestable}}\to Q_{\rm{min}}^{\rm{log.map}}$ is induced by the inclusion of the node factors in \eqref{eq:logminmod}.
+If we call $e_q$ the image in $Q_{\rm{min}}^{\rm{log.map}}$ of the $q$-th basis vector, then we can verify that the following equations hold: chosen any internal component $S_i$ and any two external component $R_i^1, R_i^2$
+such that their path to the circuit goes through $S_i$, then
+\begin{equation}
+ \sum_{q\in[R_i^1,S_i]}u_qe_q=\sum_{q\in[R_i^2,S_i]}u_qe_q.
+\end{equation}
+\textcolor{red}{Question: is this monoid factorisation condition a closed one?}
+\end{remark}
+
+\begin{remark}
+ Here is a tidy example: start with an elliptic curve $E$ contracted to $Y$, with two external components $R_1, R_2$ attached to it and a single marking $x\in E$. The tropical picture would be:
+ \begin{figure}
+ \begin{tikzpicture}[radius=2pt,scale=0.5]
+ \draw[fill=black] (0,0) circle;
+ \draw (0,0) -- (4,0);
+ \draw[fill=black] (0,2) circle;
+ \draw[fill=black] (0,4) circle;
+ \draw (0,2) -- (2,3);
+ \draw (0,4) -- (2,3);
+ \draw (2,3) -- (4,3);
+ \draw[fill=white] (2,3) circle;
+ \draw[->] (2,1.5) -- (2,.5);
+ \end{tikzpicture}
+ \end{figure}
+The dual picture of the compatibility condition would be:
+\begin{tikzpicture}[scale=0.8]
+ \draw (0,0) -- (0,2)  (0,0)--(2,0);
+ \draw[->] (1,-1.5) -- (1,-.5);
+ \draw (0,-4) -- (0,-2) (0,-4) -- (2,-4) (0,-4) -- (2,-2) node[above right]{$e_1=e_2$};
+ \draw (1,-2) node[left]{$e_2>e_1$} (2,-3) node[right]{$e_1>e_2$};
+ \draw[->] (2.5,1)--(3.5,1);
+ \draw[gray!=30] (4,0) -- (4,2)  (4,0)--(6,0);
+ \draw (4,0) -- (4.6,2) node[above right]{$m_1/m_2$};
+\end{tikzpicture}
+which is compatible with the fact that $Q_{\rm{min}}^{\rm{prestable}}\to Q_{\rm{min}}^{\rm{log.map}}$ is given by:
+$e_1\mapsto m_2, e_2\mapsto m_1$.
 \end{remark}

### 2018-03-21 genus-one-relative-maps.tex

@@
 \newcommand{\R}{\operatorname{R}^{\bullet}}
+\newcommand{\dvr}{\Delta}
 %\newcommand{\sslash}{\mathbin{/\mkern-6mu/}}
@@
 
-\setcounter{tocdepth}{2}
+\setcounter{tocdepth}{1}
 
@@
 \begin{remark}[Explaining compatibility]
-First I wish to define the first line $Q_{\rm{min}}^{\rm{prestable}}\to Q_{\rm{min}}^{\rm{log.map}}$; when looking at a geometric point $\Spec(k=\bar k)$ it is well-known that \[ Q_{\rm{min}}^{\rm{prestable}}=\prod_{q\ \text{node}}\mathbb N_q.\]
-Let me assume that all the nodes are internal, i.e.
-map to $Y$, for all the action happens there, and also that there is only one internal connected component $Z$, which has arithmetic genus one.
-Then I define $Q_{\rm{min}}^{\rm{log.map}}$ as the saturation of the quotient of
+First we need to define the monoids and maps involved.
+We start with $Q_{\rm{min}}^{\rm{prestable}}\to Q_{\rm{min}}^{\rm{log.map}}$; when looking at a geometric point $\Spec(k=\bar k)$ it is well-known that \[ Q_{\rm{min}}^{\rm{prestable}}=\prod_{q\ \text{node}}\mathbb N_q.\]
+Let us assume that all the nodes are internal, i.e.
+map to $Y$, for all the action happens there, and also that there is only one internal connected component $Z$, which is a curve of arithmetic genus one.
+Then we define $Q_{\rm{min}}^{\rm{log.map}}$ as the saturation of the quotient of
 \begin{equation}\label{eq:logminmod} \prod_{q\ \text{node}}\mathbb N_q \times \prod_{S\ \text{internal irr. compo.}}\mathbb N_S\end{equation}
@@
 where $T_q$ is the tree of internal components that $q$ separates from the circuit.
-Notice that the nodes separating $Z$ from the external components have no $1$, so the corresponding relations look like \[(u_q,\ldots,-1,\ldots).\]
+Notice that the nodes between $Z$ and an external component $R_i$ have no $1$, so the corresponding relations look like \[(u_q,\ldots,-1,\ldots).\]
 The map $Q_{\rm{min}}^{\rm{prestable}}\to Q_{\rm{min}}^{\rm{log.map}}$ is induced by the inclusion of the node factors in \eqref{eq:logminmod}.
@@
  Here is a tidy example: start with an elliptic curve $E$ contracted to $Y$, with two external components $R_1, R_2$ attached to it and a single marking $x\in E$. The tropical picture would be:
- \begin{figure}
+\begin{center}
  \begin{tikzpicture}[radius=2pt,scale=0.5]
@@
  \end{tikzpicture}
- \end{figure}
-The dual picture of the compatibility condition would be:
+\end{center}
+The dual monoids in the compatibility condition give us the following nice picture:
+\begin{center}
 \begin{tikzpicture}[scale=0.8]
  \draw (0,0) -- (0,2)  (0,0)--(2,0);
- \draw[->] (1,-1.5) -- (1,-.5);
+ \draw[->] (1,-1.3) -- (1,-.5);
+ \fill[gray!30] (0,-4) -- (0,-2) -- (2,-2) -- (0,-4);
+ \fill[gray!50] (0,-4) -- (2,-4) -- (2,-2) -- (0,-4);
  \draw (0,-4) -- (0,-2) (0,-4) -- (2,-4) (0,-4) -- (2,-2) node[above right]{$e_1=e_2$};
- \draw (1,-2) node[left]{$e_2>e_1$} (2,-3) node[right]{$e_1>e_2$};
- \draw[->] (2.5,1)--(3.5,1);
+ \draw (1,-2) node[above]{$e_2>e_1$} (2,-3) node[right]{$e_1>e_2$};
+ \draw[<-] (2.5,1)--(3.5,1);
  \draw[gray!=30] (4,0) -- (4,2)  (4,0)--(6,0);
  \draw (4,0) -- (4.6,2) node[above right]{$m_1/m_2$};
+ \draw[<-,dashed] (2.7,-1.3)--(3.5,-.5);
 \end{tikzpicture}
-which is compatible with the fact that $Q_{\rm{min}}^{\rm{prestable}}\to Q_{\rm{min}}^{\rm{log.map}}$ is given by:
+\end{center}
+So, for example, the factorisation exists for the subcone $e_2>e_1$ only when $m_1>m_2$, which is compatible with the fact that $\mathbb N^2=Q_{\rm{min}}^{\rm{prestable}}\to Q_{\rm{min}}^{\rm{log.map}}=\mathbb N$ is given by
 $e_1\mapsto m_2, e_2\mapsto m_1$.
@@
 
-\section{The relative space is equal to the closure of the nice locus for $(\PP^N,H)$}
+\section{The relative space is the closure of the nice locus for $(\PP^N,H)$}
 \noindent In general we do not know very much about the space we have just defined.
@@
 Thus to specify a point in the nice locus we only need to specify the source curve $C$ (as a scheme) and the map $f$.
-A parametrisation can be given from the vector bundle:\marginnote{I'm sure there's a simpler way to say this - Navid}
+A parametrisation can be given from the vector bundle:
 \[ \operatorname{Vb}\left(\pi_*\OO_{\mathcal E}(\sum_{j=n+1}^{n+\delta}\sigma_j)\oplus\pi_*\OO_{\mathcal E}(\sum_{j=1}^{n+\delta}\sigma_j)^{\oplus r}\right) \quad \text{on} \quad \mathcal{M}_{1,n+\delta}\]
@@
 
-\subsection{Justifying the novel condition}
-Remember that we are trying to impose conditions which determine the closure of the nice locus inside the moduli space of centrally aligned maps.
-Here is one example where we show by a dimensional computation that the novel condition must be included if we hope to determine the closure of the nice locus.
+\subsection{Justifying the novel condition by dimensional reasons}
+Here is a dimensional computation in an explicit example which shows that being in the closure of the nice locus must impose some condition on the log structure.
 \begin{example}
@@
 \begin{remark}
- For the non-expert reader, it might be convenient to recall that the extra data of a centrally aligned log structure on the curves gives a modular interpretation to the iterated blow-up procedure of Vakil and Zinger.
-In particular the novel condition on the log structure can be translated into a closed condition on the exceptional loci of these blow-ups.
+ For the reader who is unfamiliar with centrally aligned log curves, it might be convenient to recall that they provide a modular interpretation of the iterated blow-up procedure of Vakil and Zinger.
+In particular it is natural that not all of the exceptional divisors be contained in the closure of the nice locus for every $\alpha$; this geometric information is contained in the compatibility condition.
 \end{remark}
+
+\subsection{Proof sketch} \textcolor{red}{The compatibility condition should imply that the map admits a log-enhancement;} if we can prove that there is a smooth, connected and proper moduli space above, then we automatically get that the Gathmann-like relative space is closed and irreducible, and it obviously contains the nice locus; hence, if we can prove that the latter is dense, we win.
+
+It thus remains to show that, given a relative centrally aligned map, we can smooth it to one in the nice locus.
+The only interesting case \textcolor{red}{should be} that the core is contracted to a point of $Y$.
+Here is how we prove it:
+\begin{enumerate}
+ \item we consider the core (say it's a smooth elliptic curve) marked with all the special points (markings and nodes); consider $E\times\dvr$ and blow it up in all the points of the central fiber that originally corresponded to nodes; we carefully and iteratively blow up smooth points of the central fiber in order to reconstruct the curve $C$ that we started with.
+In fact we may perform weighted instead of ordinary blow-ups, picking the ideal $(z,t^r)$ where $z$ is a vertical coordinate; this has the effect of introducing an $A_{r-1}$ surface singularity at the corresponding node of the central fiber.
+We do so by choosing a homomorphism $Q_{\rm{min}}^{\rm{log.map}}\to\mathbb N$ and composing it with $Q_{\rm{min}}^{\rm{prestable}}\to Q_{\rm{min}}^{\rm{log.map}}$ to determine the relevant $r$ for every node.
+ \item Let $E,S_1,\ldots,S_k$ be the irreducible components of $f^{-1}(Y)$; we define a line bundle on the smoothing by
+ \[\mathcal L=\OO_{\cC}\left(\sum \gamma_iS_i\right)\left(\sum \alpha_ix_i\right).\]
+ Using intersection theory on the surface (recall that the local multiplicity of intersection of the two branches of the node underlying an $A_{r-1}$ singularity is $\frac{1}{r}$) we check that the compatibility condition is precisely what we need in order to be able to choose $\gamma_i$ adequately so that the following equations hold:
+ \begin{align*}
+  0&=\deg(\mathcal L_{|S_i}) \\
+  m^{(i)}&=\deg(\mathcal L_{|R_i}) \\
+  \mathcal O_E&\cong\mathcal L_{|E}
+ \end{align*}
+ the last from Gathmann's condition.
+ \item It is not clear that sections of $\mathcal L$ are unobstructed. In order to extend them we pass to $\overline{\mathcal C}$.
+\end{enumerate}
+
+\appendix
+
+\section{Old}
+
+\subsection{Basic facts about centrally aligned curves}
+\begin{prop}[{\cite[Proposition 4.6.2.2]{RSPW}}]
+The morphism $\MM^{\rm{ctr}}_{1,n}\to\MM^{\dagger}_{1,n}$ is a log-modification.
+\end{prop}
+
+Explanation: this is a local statement so I can probably reduce to an atomic neighbourhood $S$ of a point $p$.
+$S$ and the curve over it are endowed with the minimal log structure; let $P=\oM_p$ determine a chart for this log structure.
+Observe that the subcurve $\plC_0$ of the tropicalisation $\plC$ of $C_p$ determines a subset $\rm{MinPos}$ of the set of vertices, namely those adjacent to $\plC_0$.
+Perform the following log-blowups: consider the set of primitive values of the function $\lambda\colon \plC\to P$, and blow up the ideal that they generate; now locally the set of values of $\lambda$ is principal with generator $p$: blow up the ideal generated by $\{\lambda(v)-p\}\setminus\{-p\}$.
+Keep going until $\lambda(v_i)$ is reached for some $v_i\in\rm{MinPos}$; at this point stop and declare the contraction radius $\delta:=\lambda(v_i)$.
+Finish by adjoining $\lambda(v)-\delta$ for all the vertices untouched to this stage.
+This shows that the choice of $\delta$ is not an extra degree of freedom.\marginpar{do I sound like a physicist?}
+
+\subsection{Moral justification of the novel condition}
 
@@
 
-It thus remains to show that, given a relative radially aligned map, we can smooth it to one in the nice locus.
-\textcolor{red}{This is done by considering different cases locally, then gluing.
-\marginpar{What do we exactly mean by this?
-How does gluing work in the centrally aligned setting?}}
+\subsection{Novel Condition 2.0}
+
+This is done with $(\PP^1,H)$ in mind; in general it will need to be modified to account for internal components of positive degree.
+
+\textbf{Novel condition 2.0:} if $v_1,v_2$ are two vertices belonging to $R_\delta$, then the corresponding tangencies $m^{(j_1)}$ and $m^{(j_2)}$ to $H$ must be equal \emph{if the corresponding rational tails are attached to the same irreducible component of $\plC_0$}.
+Here $R_\delta$ is the set of vertices $v \in \plC$ with $\lambda(v)=\delta$ and $\plC_0$ is the set of vertices with $\lambda(v)<\delta$.
+
+\textbf{Sketch of ``sufficient'' direction}: Denote by $S_0=E,S_1,\ldots,S_k$ the irreducible components of $Z$ and assume $E$ is smooth elliptic (or the core).
+Every $S_i$ for $i\geq 0$ comes with a bunch of special points: divide them into $B^-(i)=$ the singleton representing the only node separating $S_i$ from $S_0$ (this is not defined for $i=0$); $B^+(i)=$ the set of remaining nodes; and $A(i)=$ the set of markings on $S_i$.
+Start with the trivial family $E\times\Aaff^1$, where $E$ is marked with the points of $B(0)=B^+(0)$ and $A(0)$.
+Now perform a weighted blow-up at the points $\{q\in B(0)\}\times\{0\in\Aaff^1\}$ of weight $r_q$; call each resulting rational tail $S_i$ correspondingly to the original picture.
+On $S_i$ we may mark points $B^+(i)$ and $A(i)$ in such a way that the resulting point of $\oM_{0,1+|B^+(i)|+|A(i)|}$ corresponds to the one we started with.
+Now blow up this family in all the $B^+(i)\times\{0\}$ with a weight.
+Keep going until you have recreated $C$.
+Call $R_j$ the first external components, namely those corresponding to the vertices with $\lambda(v)\geq\delta$, $\nexists v'$ with $\lambda(v)>\lambda(v')\geq\delta$.
+
+We define the line bundle $\mathcal L=\OO_{\cC}(\sum \beta_iS_i)(\sum \alpha_ix_i)$; let's look at the equations that it gives us, starting from the outside.
+\begin{enumerate}
+ \item $m^{(j)}=\mathcal L_{|R_j}=\frac{\beta^-(j)}{r_{q^-(j)}}$;
+ \item on every $S_i, i\geq1$ we can prove inductively that:
+ \[0=\mathcal L_{|S_i}=\frac{\beta^-(i)-\beta_i}{r_{q^-(i)}}+\sum_{x_h\in A(i)}\alpha_i+\sum_{y_h\in B^+(i)}M^{(h)},\]
+ where I have denoted by $M^{(h)}$ the sum of all the contributions (both $\alpha_l$ and $m^{(l)}$) coming from the rational tree attached to the corresponding point of $B^+(i)$;
+ \item it turns out that $\OO_{S_0}\simeq\mathcal L_{|S_0}$ is precisely Gathmann's condition (in the numeric form if $S_0$ is a circle of rational curves). 
+\end{enumerate}
+Now notice that $\lambda(v_j)=\lambda(v_j')$ may happen only at the first external components; \marginpar{is this true?
+if not, probably there are contributions $M^{(h)}$ and $M^{(h')}$ to equate} in this case $r_{q^-(j)}=r_{q^-(j')}$, and from the first equation we see that $m^{(j)}=m^{(j')}$ if they are attached to the same component ($\beta^-(j)=\beta^-(j')$).
+The second equation can be made to hold for every $S_i$ by appropriately choosing $\beta^-(i), r_{q^-(i)}$. The last equation is automatically satisfied.
+
+Extending sections is the usual business of exploiting the fatorisation through the elliptic $m$-fold.
+
+\textbf{Sketch of ``necessary'' direction}: pick a smoothing $\cC$ of $(C,f)$.
+Suppose that $\lambda(v)=\lambda(v')$ and the corresponding $R$, $R'$ are attached to the same $S_i$, i.e.
+they share the same the tree separating them from $C_0$.
+Notice that $R$ and $R'$ map to two branches of the Smyth singularity.
+Looking at the semistable model of $\cC$, it follows that (the strict transforms of) $R$ and $R'$ still share the same tree there.
+Then by writing $(f^{\rm{ss}})^*\OO_{\PP}(1)=\OO_{\cC^{\rm{ss}}}(\sum \beta_iS_i)(\sum \alpha_ix_i)$ and intersecting with $R$, $R'$, we see that they must have the same contact order to $H$.
+
+\subsection{Details of the proof}
 
@@
 
-\section{Novel Condition 2.0}
-
-This is done with $(\PP^1,H)$ in mind; in general it will need to be modified to account for internal components of positive degree.
-
-\textbf{Novel condition 2.0:} if $v_1,v_2$ are two vertices belonging to $R_\delta$, then the corresponding tangencies $m^{(j_1)}$ and $m^{(j_2)}$ to $H$ must be equal \emph{if the corresponding rational tails are attached to the same irreducible component of $\plC_0$}.
-Here $R_\delta$ is the set of vertices $v \in \plC$ with $\lambda(v)=\delta$ and $\plC_0$ is the set of vertices with $\lambda(v)<\delta$.
-
-\textbf{Sketch of ``sufficient'' direction}: Denote by $S_0=E,S_1,\ldots,S_k$ the irreducible components of $Z$ and assume $E$ is smooth elliptic (or the core).
-Every $S_i$ for $i\geq 0$ comes with a bunch of special points: divide them into $B^-(i)=$ the singleton representing the only node separating $S_i$ from $S_0$ (this is not defined for $i=0$); $B^+(i)=$ the set of remaining nodes; and $A(i)=$ the set of markings on $S_i$.
-Start with the trivial family $E\times\Aaff^1$, where $E$ is marked with the points of $B(0)=B^+(0)$ and $A(0)$.
-Now perform a weighted blow-up at the points $\{q\in B(0)\}\times\{0\in\Aaff^1\}$ of weight $r_q$; call each resulting rational tail $S_i$ correspondingly to the original picture.
-On $S_i$ we may mark points $B^+(i)$ and $A(i)$ in such a way that the resulting point of $\oM_{0,1+|B^+(i)|+|A(i)|}$ corresponds to the one we started with.
-Now blow up this family in all the $B^+(i)\times\{0\}$ with a weight.
-Keep going until you have recreated $C$.
-Call $R_j$ the first external components, namely those corresponding to the vertices with $\lambda(v)\geq\delta$, $\nexists v'$ with $\lambda(v)>\lambda(v')\geq\delta$.
-
-We define the line bundle $\mathcal L=\OO_{\cC}(\sum \beta_iS_i)(\sum \alpha_ix_i)$; let's look at the equations that it gives us, starting from the outside.
-\begin{enumerate}
- \item $m^{(j)}=\mathcal L_{|R_j}=\frac{\beta^-(j)}{r_{q^-(j)}}$;
- \item on every $S_i, i\geq1$ we can prove inductively that:
- \[0=\mathcal L_{|S_i}=\frac{\beta^-(i)-\beta_i}{r_{q^-(i)}}+\sum_{x_h\in A(i)}\alpha_i+\sum_{y_h\in B^+(i)}M^{(h)},\]
- where I have denoted by $M^{(h)}$ the sum of all the contributions (both $\alpha_l$ and $m^{(l)}$) coming from the rational tree attached to the corresponding point of $B^+(i)$;
- \item it turns out that $\OO_{S_0}\simeq\mathcal L_{|S_0}$ is precisely Gathmann's condition (in the numeric form if $S_0$ is a circle of rational curves). 
-\end{enumerate}
-Now notice that $\lambda(v_j)=\lambda(v_j')$ may happen only at the first external components; \marginpar{is this true?
-if not, probably there are contributions $M^{(h)}$ and $M^{(h')}$ to equate} in this case $r_{q^-(j)}=r_{q^-(j')}$, and from the first equation we see that $m^{(j)}=m^{(j')}$ if they are attached to the same component ($\beta^-(j)=\beta^-(j')$).
-The second equation can be made to hold for every $S_i$ by appropriately choosing $\beta^-(i), r_{q^-(i)}$. The last equation is automatically satisfied.
-
-Extending sections is the usual business of exploiting the fatorisation through the elliptic $m$-fold.
-
-\textbf{Sketch of ``necessary'' direction}: pick a smoothing $\cC$ of $(C,f)$.
-Suppose that $\lambda(v)=\lambda(v')$ and the corresponding $R$, $R'$ are attached to the same $S_i$, i.e.
-they share the same the tree separating them from $C_0$.
-Notice that $R$ and $R'$ map to two branches of the Smyth singularity.
-Looking at the semistable model of $\cC$, it follows that (the strict transforms of) $R$ and $R'$ still share the same tree there.
-Then by writing $(f^{\rm{ss}})^*\OO_{\PP}(1)=\OO_{\cC^{\rm{ss}}}(\sum \beta_iS_i)(\sum \alpha_ix_i)$ and intersecting with $R$, $R'$, we see that they must have the same contact order to $H$.
-
-\appendix
-
-\section{Basic facts about centrally aligned curves}
-\begin{prop}[{\cite[Proposition 4.6.2.2]{RSPW}}]
-The morphism $\MM^{\rm{ctr}}_{1,n}\to\MM^{\dagger}_{1,n}$ is a log-modification.
-\end{prop}
-
-Explanation: this is a local statement so I can probably reduce to an atomic neighbourhood $S$ of a point $p$.
-$S$ and the curve over it are endowed with the minimal log structure; let $P=\oM_p$ determine a chart for this log structure.
-Observe that the subcurve $\plC_0$ of the tropicalisation $\plC$ of $C_p$ determines a subset $\rm{MinPos}$ of the set of vertices, namely those adjacent to $\plC_0$.
-Perform the following log-blowups: consider the set of primitive values of the function $\lambda\colon \plC\to P$, and blow up the ideal that they generate; now locally the set of values of $\lambda$ is principal with generator $p$: blow up the ideal generated by $\{\lambda(v)-p\}\setminus\{-p\}$.
-Keep going until $\lambda(v_i)$ is reached for some $v_i\in\rm{MinPos}$; at this point stop and declare the contraction radius $\delta:=\lambda(v_i)$.
-Finish by adjoining $\lambda(v)-\delta$ for all the vertices untouched to this stage.
-This shows that the choice of $\delta$ is not an extra degree of freedom.\marginpar{do I sound like a physicist?}
-
 \bibliographystyle{alpha}

### 2018-03-22 genus-one-relative-maps.tex
Restructured
started recursion

@@
 \newcommand{\plC}{\scalebox{0.8}[1.3]{$\sqsubset$}}
+\newcommand{\sidenote}[1]{\marginpar{\textbf{\color{red}#1}}}
 
@@
 One should think of the factorisation condition as identifying the main component of the moduli space.
+
+\section{Definition of centrally aligned relative space}
+\section{Characterisation of the closed points of the relative space}
+\section{Recursion formula}
+
+\subsection{The case $\sum\alpha=d$}
+
+\subsection{Definition of the boundary components} According to Vakil's article there should be three sorts of boundary components.
+\begin{enumerate}[label=(\alph*)]
+ \item \[\mathcal Y^a=\M{0}{\lvert\alpha^{(0)}\rvert+r}{H}{d_0}\times_{H^r}\left(\VZc{1}{\alpha^{(1)}\cup\{m^{(1)}\}}{\PP^N|H}{d_1}\times\prod_{i=2}^r\M{0}{\alpha^{(i)}\cup\{m^{(i)}\}}{\PP^N|H}{d_i}\right)\]
+ \item \[\mathcal Y^b=\M{0}{\lvert\alpha^{(0)}\rvert+r}{H}{d_0}\times_{H^r}\left(\M{0}{\alpha^{(1)}\cup\{m^{(1)},m^{(2)}\}}{\PP^N|H}{d_1}\times\prod_{i=3}^r\M{0}{\alpha^{(i)}\cup\{m^{(i)}\}}{\PP^N|H}{d_i}\right)\]
+ \item \[\mathcal Y^c\subseteq \VZc{1}{\lvert\alpha^{(0)}\rvert+r}{H}{d_0}\times_{H^r}\prod_{i=1}^r\M{0}{\alpha^{(i)}\cup\{m^{(i)}\}}{\PP^N|H}{d_i}\]
+ $\mathcal Y^c$ is cut within the latter by Gathmann's condition on line bundles:
+ \[f_{|E}^*\mathcal O_H(1)\cong\mathcal O_E\left(\sum_{x_j\in E}\alpha_jx_j-\sum_{i=1}^r m^{(i)}y_i\right)\]\sidenote{Express the line bundle condition in terms of tautological classes?}
+ Notice that such condition depends on the choice of $m^{(i)}$ but is really just a condition on the first factor of the product, so $\mathcal Y^c$ itself can be expressed as a product.
+\end{enumerate}
+
+\begin{remark}
+ Notice that gluing does not present the subtleties to which log geometry has made us used, since we endow the curves with the minimal centrally aligned structure, possibly after prescribing that the smoothing parameters for the newly created nodes are \emph{bigger} than the contraction radius $\delta$.
+\end{remark}
+
+\begin{remark}
+ A dimensional computation shows that $\mathcal Y^b$ is never relevant to the purpose of the recursion formula.
+On the other hand the classes of $\mathcal Y^a$ and $\mathcal Y^c$ should be weighted with the coefficient $\frac{\prod m^{(i)}}{r!}$.
+Let $D_{1,\alpha,k}(\PP^N|H)$ be the union of all the $\mathcal Y^a$ and $\mathcal Y^c$ as above, for any choice of number of external components $r$, distribution of the markings $A$, and of the degree $D$, provided the marked point $x_k$ lies on the internal component $C^{(0)}$.
+Let each component be endowed with its fundamental class weighted as above and let $\virt{D_{1,\alpha,k}(\PP^N|H)}$ be the sum of all these classes.
+\end{remark}
+
+\begin{thm}
+ Assume $\sum\alpha=d$. Then \[(\alpha_k\psi_k+\ev_k^*H)[\VZc{1}{\alpha}{\PP^N|H}{d}]=\virt{D_{1,\alpha,k}(\PP^N|H)}.\]
+\end{thm}
+\begin{proof}
+We perform a number of reductions.
+ \begin{itemize}%[leftmargin=1cm]
+  \item \textbf{Reduction to the case of $\PP^1|\{\infty\}$:} by choosing a general $N-2$-plane $A\subseteq H$ and projecting away from it.
+Must show that the rational map $\rho_A\colon \VZc{1}{n}{\PP^N|H}{d}\dashrightarrow \VZc{1}{n}{\PP^1|\{\infty\}}{d}$ is defined and smooth at a general point of $D_{1,\alpha,k}(\PP^N|H)$.
+
+  \item \textbf{Reduction to an \'etale neighbourhood of $C^{(0)}$:} the plan is to understand the global perfect obstruction theory of $\VZc{1}{n}{\PP^1}{d}$ and see that the tangent to the latter is a sum of contributions from the \emph{special loci}, namely contracted components, ramification points, markings and nodes.
+
+  \begin{remark}
+   When we are studying the infinitesimal deformation theory of centrally aligned curves, notice that being centrally aligned must be checked on geometric points, and minimality is open, hence any deformation as a log smooth curve will automatically be minimal centrally aligned.
+The tangent space is then $H^1(C,T_C^{\rm{log}})$; notice that this is independent from the log structure on the base.
+  \end{remark}
+
+  \begin{example}
+   There are non-trivial deformations that are trivial on the underlying marked prestable curve.
+If $(C,\mathcal M_C)\to (\Spec(k),Q^{\rm{cen}})$ is a centrally aligned curve, then in order to define a deformation over $\Spec(k[\epsilon])$ we need to extend the log structure on the base by choosing a map $Q^{\rm{cen}}\to k[\epsilon]$.
+Notice that if we want the underlying curve to be a trivial deformation we better send all the smoothing parameters to $0$ in $k[\epsilon]$; on the other hand, if $Q^{\rm{cen}}$ contains an element such as $e_i-e_j$ (making $R_i$ further from the circuit than $R_j$), then we are free to map it to an invertible element in $k[\epsilon]$, which will kill it in the associated log structure;\sidenote{Invertible elements of $k[\epsilon]$ remain invertible when setting $\epsilon=0$, which seems to kill $e_i-e_j$ on the central fiber too.} this will make $R_i$ and $R_j$ be \emph{at the same distance} from the circuit in the deformation.
+Importantly, $Q^{\rm{log}}\to Q^{\rm{cen}}$ is an epimorphism only in the category of integral monoid (of which the multiplicative monoid of a ring is never an object, because it has a sink).
+  \end{example}
+
+ \end{itemize}
+
+\end{proof}
+
+\appendix
+\section{Old}
 
@@
 \end{enumerate}
-
-\appendix
-
-\section{Old}
 

### 2018-03-22 genus-one-relative-maps.tex
Started writing characterisation

--- 2018-03-21 genus-one-relative-maps.tex
@@
 %\usepackage{showlabels}
-\usepackage{hyperref}
+\usepackage[hidelinks]{hyperref}
 \usepackage{amsthm}
@@
 
+\newcommand{\sidenote}[1]{\marginpar{\textbf{\color{red}#1}}}
+\newcommand{\basenote}[1]{\footnote{\color{red}#1}}
+
 \newcommand{\plC}{\scalebox{0.8}[1.3]{$\sqsubset$}}
 
+\newcommand{\spec}{\operatorname{Spec}}
 \newcommand{\TT}{\operatorname{T}}
@@
 \newcommand{\VZc}[4]{\mathcal{V\!Z}^{\rm{ctr}}_{#1,#2}(#3,#4)}
+\newcommand{\VZco}[4]{\mathcal{V\!Z}^{\rm{ctr},\circ}_{#1,#2}(#3,#4)}
 \newcommand{\VZcLi}[4]{\mathcal{V\!Z}^{\rm{ctr, Li}}_{#1,#2}(#3,#4)}
@@
 
+\newcommand{\Ccal}{\mathcal{C}}
+\newcommand{\Mcal}{\mathcal{M}}
+\newcommand{\Lcal}{\mathcal{L}}
+\newcommand{\Mfrak}{\mathfrak{M}}
+
 \theoremstyle{definition}
@@
 
-\begin{abstract} For a smooth projective variety $X$ and a smooth very ample hypersurface $Y \subseteq X$, we define moduli spaces of relative stable maps to $(X,Y)$ in genus one, as closed substacks of the moduli space of maps from centrally aligned curves, constructed in \cite{RSPW}.
+\begin{abstract} For a smooth projective variety $X$ and a smooth very ample hypersurface $Y \subseteq X$, we define moduli spaces of relative stable maps to $(X,Y)$ in genus one, as closed substacks of the moduli space of maps from centrally aligned curves, as constructed in \cite{RSPW}.
 We construct virtual classes for these moduli spaces, which we use to define \emph{reduced relative Gromov--Witten invariants} in genus one.
@@
 \section{The space of relative centrally aligned maps}
-\noindent Recall \cite{RSPW} that the moduli space of maps from centrally aligned curves is obtained by considering the  Cartesian diagram
+\noindent Recall \cite{RSPW} that the moduli space of maps from centrally aligned curves is obtained by first considering the Cartesian diagram
 \bcd
@@
 \begin{enumerate}
-\item a centrally aligned curve $(C,M_C,\delta)$;
+\item a centrally aligned curve $(C,\Mcal_C,\delta)$;
 \item a stable map $f\colon C \to X$;
@@
 One should think of the factorisation condition as identifying the main component of the moduli space.
+
+\section{Definition of centrally aligned relative space}
+Fix a vector $\alpha=(\alpha_1,\ldots,\alpha_n)$ of tangency conditions, and suppose for the moment that $\Sigma \alpha = d$.
+We consider the so-called \emph{nice locus} of relative centrally aligned maps.
+This is the locally closed substack of $\VZc{1}{n}{\PP^N}{d}$ consisting of centrally aligned maps $(C,x_1,\ldots,x_n,\Mcal_C,\delta,f)$ such that:
+\begin{enumerate}
+\item the source curve $C$ is smooth;
+\item $C$ is not mapped entirely into $H$ by $f$;
+\item the points of $C$ which are mapped into $H$ (necessarily a finite number by the previous condition) are all marked, with the map having tangency $\alpha_i$ to $H$ at the marking $x_i$.
+\end{enumerate}
+These conditions mean that $\delta=0$ and that the log structure $\Mcal_C$ (which is a minimal centrally aligned log structure) is equal to the minimal structure for a log smooth curve, which in this case (since there are no nodes) is just the divisorial log structure with respect to the markings $x_1,\ldots,x_n$.
+
+This is a locally closed substack of expected codimension $\Sigma \alpha=d$, and is denoted:
+\begin{equation*} \VZco{1}{\alpha}{\PP^N|H}{d} \end{equation*}
+It has a well-defined stack structure since it is a moduli space. Note that it is irreducible, since we can find a parametrisation for it over $\Mfrak_{1,n}$.
+
+We now define the \emph{centrally alined relative space} to be the closure of the nice locus:
+\begin{equation*} \VZc{1}{\alpha}{\PP^N|H}{d} := \overline{\VZco{1}{\alpha}{\PP^N|H}{d}} \subseteq \VZc{1}{n}{\PP^N}{d} \end{equation*}
+This inherits the natural structure of a stack from the stack structure of the nice locus.
+It is proper since it is a closed substack of a proper stack, and it is irreducible because it is the closure of an irreducible stack.
+Hence it admits a fundamental class, which we can use to define \emph{reduced relative Gromov--Witten invariants}:
+\begin{equation*} \langle \tau_{k_1}(\gamma_1), \ldots, \tau_{k_n}(\gamma_n) \rangle^{\PP^N|H, \operatorname{red}}_{0,\alpha,d} := \int_{[\VZc{1}{\alpha}{\PP^N|H}{d}]} \prod_{i=1}^n \ev_i^*(\gamma_i) \psi_i^{k_i} \end{equation*}
+
+\section{Characterisation of the closed points of the relative space}
+It will be important for our purposes to have an understanding of the boundary of the relative space, i.e.
+what we add in when we take the closure of the nice locus.
+In this section we will describe this boundary on the level of closed points.
+
+\begin{prop} \label{closed pts of relative space} A centrally aligned map over a closed point $\spec \mathbbm{k}$ is in the relative space if and only if the following two conditions are satisfied:
+\begin{enumerate}
+\item \emph{Gathmann's relative condition:} for each connected component $Z$ of $f^{-1}(Y)$, either:
+\begin{enumerate}
+\item $Z$ is a single point of $C$, in which case if $Z=x_i$ is a marking then we require that the multiplicity of $f$ at $x_i$ along $Y$ is at least $\alpha_i$ (if $Z$ is not a marking then there is no condition);
+\item $Z$ is a subcurve $Z \subseteq C$, in which case we require that
+\begin{equation*} f^*[Y]|_Z -\sum_{x_i\in Z}\alpha_ix_i\end{equation*}
+is an effective class in $\Achow_0(Z)$.
+\end{enumerate}
+
+\item \emph{Compatibility condition:} this applies when the minimal subcurve of genus one (the \emph{circuit}) is contracted to a point in $Y$.
+In this case we require that there is a local morphism of monoids:
+\begin{equation*} Q^{\operatorname{GS}} \to \N\end{equation*}
+such that the dashed arrow can be filled in to make the following square commutative:
+\bcd
+Q^{\operatorname{log}} \ar[r]\ar[d] & Q^{\operatorname{GS}} \ar[d] \\
+Q^{\operatorname{ctr}}\ar[r,dashed] & \N
+\ecd
+It is obvious from the construction that the map $Q^{\operatorname{ctr}} \to \N$ is unique if it exists
+\end{enumerate}
+\end{prop}
+
+\begin{remark} Gathmann's condition obviously extends to the case $\Sigma \alpha \leq d$.
+\basenote{What is the correct generalisation of the compatibility condition?} Here we try to make the condition for a curve component of $f^{-1}(Y)$ into an easily verifiable criterion: if $Z$ is a smooth elliptic curve, recall that every line bundle of positive degree on it is effective, hence the relative condition can be rephrased as the following numerical criterion:
+\begin{equation*} f_*[Z]\cdot [Y]+\sum_{j=1}^r m^{(j)}\geq \sum_{x_i\in Z}\alpha_i \end{equation*}
+together with the additional requirement that, when the above is an equality, there is an isomorphism of line bundles:
+\begin{equation}\label{eqn:eq_in_Pic}
+(f|_{Z})^*\OO_X(Y) \otimes \OO_Z\left(\sum_{j=1}^r m^{(j)}y_j\right)=\OO_Z\left(\sum_{x_i\in Z}\alpha_ix_i\right) 
+\end{equation}
+
+If $Z$ is reducible, the correct extension is not to impose the same condition componentwise; rather, we should ask the numerical condition for the total degree, and, if $Z$ is obtained by gluing a smooth elliptic curve $E$ with a forest of rational trees $T_i$ at roots $q^E_i$, then the line bundle equality \eqref{eqn:eq_in_Pic} should be required in $\Pic(E)$ after counting each $q^E_i$ towards the left hand side with multiplicity:
+\[f_*[T_i]\cdot [Y]+\sum_{\text{external components attached to $T_i$}} m^{(j)} \geq \sum_{x_j\in T_i}\alpha_j\]
+%That this is the right thing to do follows from the proof that Gathmann's relative space is the projection of Jun Li's moduli space of maps to the expanded pair after contracting the higher levels of the accordion.
+\end{remark}
+
+\begin{remark} The monoid $Q^{\operatorname{GS}}$ above is the minimal monoid for the moduli space of log stable maps, as constructed by Gross--Siebert.
+Its definition relies on a choice of \emph{type}, which in our setting is uniquely determined except when the source curve $C$ contains a wheel of $\PP^1$s.
+\end{remark}
+
+\begin{proof}[Proof of Proposition \ref{closed pts of relative space}]
+First suppose that Gathmann's condition is satisfied and that we have a factorisation:
+\bcd
+Q^{\operatorname{log}} \ar[r]\ar[d] & Q^{\operatorname{GS}} \ar[d] \\
+Q^{\operatorname{ctr}}\ar[r] & \N
+\ecd
+We will construct a smoothing of the centrally aligned map, i.e. a $1$-parameter family whose central fibre is the map we started with and whose general fibre is in the nice locus.
+
+The construction of the source curve $\Ccal \to \spec \mathbbm{k} \llbracket t \rrbracket$ is given in the usual way by starting with the circuit $E$ and performing a weighted blow-up to reconstruct the rest of the curve.\basenote{What do we do if $E$ is not smooth?
+We need to smooth $E$ itself, and we also need some node multiplicities at the nodes internal to $E$.} The weights are determined by the map $Q^{\operatorname{log}} \to \N$; this map is local since the map $Q^{\operatorname{log}} \to Q^{\operatorname{GS}}$ is local\basenote{Is this always true?
+Isn't this only true if there exists a log lifting?
+But maybe it's always true for Deligne--Faltings pairs.} and the map $Q^{\operatorname{GS}} \to \N$ is local by assumption.
+Thus each generator $e_q \in Q^{\operatorname{log}}$ maps to a positive integer $r_q$, and this is the weight we choose.
+This means that if $C_1$ and $C_2$ are the two branches of $C$ around $q$, then these are $\QQ$-Cartier divisors in the total space $\Ccal$, with:
+\begin{equation*} C_1 \cdot C_2 = 1/r_q \end{equation*}
+We now define the map $f \colon \Ccal \to \PP^N$ extending the map $f \colon C \to \PP^N$.
+We assume that $H=\{ z_0=0\}$ is a co-ordinate hyperplane.
+We have sections $u_0,\ldots,u_N$ of a line bundle $L$ on $C$ and we need to extend these to sections $\tilde{u}_0,\ldots,\tilde{u}_N$ of a line bundle $\Lcal$ on $\Ccal$.
+
+Let us write $C = C_1 \cup \ldots \cup C_m$ with $C_1,\ldots,C_r$ internal and the rest external. We define the line bundle $\Lcal$ as
+\begin{equation*} \Lcal = \OO_{\Ccal}\left(\sum_{i=1}^r \gamma_i C_i + \sum_{i=1}^n \alpha_i \tilde{x}_i \right) \end{equation*}
+where each $\gamma_i$ is a positive integer obtained as the image under $Q^{\operatorname{GS}} \to \N$ of the generator corresponding to $C_i$.
+
+This comes with a natural section (or rather, a $\CC^*$-equivalence class of sections) $\tilde{u}_0$ given by the divisor in brackets, and this can be chosen in a unique way so that it restricts to $u_0$ on the central fibre of $\Ccal$.
+
+For each external component $C_j$, we have
+\begin{equation*} \Lcal|_{C_j} = \OO_{C_j} \left( \sum_{x_i \in C_j} \alpha_i x_i + \sum_{q_i \in C_j} (\gamma_i/r_i) q_j \right) \end{equation*}
+where the latter sum is over nodes of $C_j$ which connect $C_j$ to an internal component $C_i$. We thus need:
+\begin{equation*} m_i = \gamma_i / r_i \end{equation*}
+But this is true, because in $Q^{\operatorname{GS}}$ the generator corresponding to the internal component $C_i$ is identified with $m_i$ times the generator corresponding to $q_i$; pushing forward this relation to $\N$ gives the equation above.
+
+\begin{comment} 
+Now let us consider an internal component $C_j$. We have
+\begin{align*} \Lcal|_{C_j} & = \OO_{C_j} \left( \sum_{x_i \in C_j} \alpha_i x_i + \sum_{q_i \in C_j} (\gamma_i/r_i) q_i \right) \otimes \OO_{\mathcal{C}}\left(- \gamma_j \sum_{i \neq j} C_i \right) \\
+& = \OO_{C_j}\left( \sum_{x_i \in C_j} \alpha_i x_i + \sum_{q_i \in C_j} \left(\frac{\gamma_i - \gamma_j}{r_i}\right) q_i - \sum_{\tilde{q}_i \in C_j} (\gamma_j/r_i) \tilde{q}_i \right)\end{align*}
+where the middle sum is over adjacent internal components and the final sum is over adjacent external components. The fact that $\gamma_j/r_i = m_i$ follows as in the previous case.
+
+It remains to verify the Gathmann-like condition for internal components.
+Let $Z \subseteq C$ be a connected component of $f^{-1}(H)$, and suppose wlog that $Z = C_1 \cup \ldots \cup C_k$ for some of the internal components $C_1,\ldots,C_k$.
+If $Z$ has genus zero then the condition is purely numerical, and we find from the above description that
+\begin{equation*} \deg \Lcal|_Z = \sum_{x_i \in Z} \alpha_i x_i - \sum_{\tilde{q}_i \in Z} m_i \end{equation*}
+where the sum is over external nodes $\tilde{q}_i$, i.e. those connecting to the rest of the curve. By the Gathmann condition, this is exactly $\deg f|_Z^* \OO_{\PP^N}(H)$, which is what we wanted.
+
+On the other hand suppose that $Z$ is genus one. Suppose first off that it has a smooth genus one component, say $C_1$.
+\end{comment}
+
+Let $Z$ be a connected component of $f^{-1}(H)$. Suppose wlog that $Z= C_1 \cup \ldots \cup C_k$. Then because $Z$ does not intersect $C_{k+1},\ldots,C_r$ we have
+\begin{align*} \Lcal|_Z & = \OO_Z \left( \sum_{x_i \in Z} \alpha_i x_i + \sum_{i=1}^k \gamma_i C_i \right) \\
+& = \OO_Z \left( \sum_{x_i \in Z} \alpha_i x_i - \sum_{q_i \in Z} (\gamma_i/r_i) q_i \right) \\
+& = \OO_Z \left( \sum_{x_i \in Z} \alpha_i x_i - \sum_{q_i \in Z} m_i q_i \right) \end{align*}
+where the sum is over external components of $C$ which are adjacent to $Z$ via $q_i$. By the Gathmann-like condition, this is exactly $f^* \OO(Y)|_Z$.
+
+We have thus shown that when we restrict $\Lcal$ to either an external component or an internal component (where here we mean a connected component of $f^{-1}(Y)$) we get the correct line bundle.
+Assuming that there is no wheel of $\PP^1$s, or more generally that any wheel of $\PP^1$s which does appear appears inside a connected component, this shows that $\Lcal_{\Ccal_0} = L$, as claimed.
+
+\end{proof}
+
+\newpage
+
+\section{Recursion formula for $\PP^1|\infty, \Sigma \alpha = d$}
+
+\newpage
+\appendix
+\section{Old}
 
@@
 
-\section{The relative space is the closure of the nice locus for $(\PP^N,H)$}
+\subsection{The relative space is the closure of the nice locus for $(\PP^N,H)$}
 \noindent In general we do not know very much about the space we have just defined.

### 2018-03-22 genus-one-relative-maps.tex
didn't change anything

@@
 We have thus shown that when we restrict $\Lcal$ to either an external component or an internal component (where here we mean a connected component of $f^{-1}(Y)$) we get the correct line bundle.
-Assuming that there is no wheel of $\PP^1$s, or more generally that any wheel of $\PP^1$s which does appear appears inside a connected component, this shows that $\Lcal_{\Ccal_0} = L$, as claimed.
+Assuming that there is no wheel of $\PP^1$s, or more generally that any wheel of $\PP^1$s which does appear appears inside a connected component, this shows that $\Lcal_{\Ccal_0} = L$, as claimed.\basenote{What about in general?}
 

### 2018-03-22 genus-one-relative-maps.tex
Minor changes

--- 2018-03-22 genus-one-relative-maps.tex
@@
   \begin{remark}
-   When we are studying the infinitesimal deformation theory of centrally aligned curves, notice that being centrally aligned must be checked on geometric points, and minimality is open, hence any deformation as a log smooth curve will automatically be minimal centrally aligned.
+   When we are studying the infinitesimal deformation theory of centrally aligned curves, notice that being centrally aligned must be checked on geometric points, and minimality is open, hence any first-order deformation as a log smooth curve will automatically be minimal centrally aligned.
 The tangent space is then $H^1(C,T_C^{\rm{log}})$; notice that this is independent from the log structure on the base.

### 2018-03-22 genus-one-relative-maps.tex
WRote up most of proof of existence of smoothing

--- 2018-03-22 genus-one-relative-maps.tex
@@
 \newcommand{\plC}{\scalebox{0.8}[1.3]{$\sqsubset$}}
+
+\newcommand{\formLine}{\spec \mathbbm{k}\llbracket t \rrbracket}
 
@@
 
+\begin{remark} The monoid $Q^{\operatorname{GS}}$ depends on a choice of \emph{type}, in this case a choice of the $u_q$ (the $u_p$ are already determined by the choice of $\alpha$).
+Here we are not allowed to choose a random type, but have to choose one which is compatible with the underlying stable map, in the sense that the modified tropical balancing condition is satisfied.
+Remember that we get one balancing condition for each generator of $\Gamma(C, f^* \overline{\Mcal}_H)$, so as well as there being a balancing condition for each internal component there is also one wherever the curve intersects the divisor in an isolate point (where for instance we get that $u_q = m_q$ at nodes connecting an external to an internal component).
+Also we require this condition to take place in $\Pic(C)$, but we are entitled at any point to restrict to components of $C$ or take degrees to get (in general weaker) conditions.
+\end{remark}
+
 \begin{remark} Gathmann's condition obviously extends to the case $\Sigma \alpha \leq d$.
@@
 
-\begin{remark} The monoid $Q^{\operatorname{GS}}$ above is the minimal monoid for the moduli space of log stable maps, as constructed by Gross--Siebert.
-Its definition relies on a choice of \emph{type}, which in our setting is uniquely determined except when the source curve $C$ contains a wheel of $\PP^1$s.
-\end{remark}
-
 \begin{proof}[Proof of Proposition \ref{closed pts of relative space}]
-First suppose that Gathmann's condition is satisfied and that we have a factorisation:
+First suppose that the conditions (1) and (2) of the Proposition are satisfied; so we have Gathmann's condition on the level of line bundles and a factorisation:
 \bcd
@@
 \ecd
-We will construct a smoothing of the centrally aligned map, i.e. a $1$-parameter family whose central fibre is the map we started with and whose general fibre is in the nice locus.
-
-The construction of the source curve $\Ccal \to \spec \mathbbm{k} \llbracket t \rrbracket$ is given in the usual way by starting with the circuit $E$ and performing a weighted blow-up to reconstruct the rest of the curve.\basenote{What do we do if $E$ is not smooth?
-We need to smooth $E$ itself, and we also need some node multiplicities at the nodes internal to $E$.} The weights are determined by the map $Q^{\operatorname{log}} \to \N$; this map is local since the map $Q^{\operatorname{log}} \to Q^{\operatorname{GS}}$ is local\basenote{Is this always true?
+We will construct a smoothing of the centrally aligned map, i.e.
+a $1$-parameter family whose central fibre is the map we started with and whose general fibre is in the nice locus.
+The construction proceeds in the following order:
+\begin{enumerate}
+\item construct the smoothing $\Ccal$ of the source curve $C$, as a scheme;
+\item construct the extension $(\Mcal_{\Ccal},\delta)$ of the central alignment on $C$;
+\item construct the extension $\Lcal$ of the line bundle $L=f^*\OO_{\PP^N}(H)$ from $C$ to $\Ccal$;
+\item construct the extension of the section $u_0 \in \HH^0(C,L)$;
+\item construct the extensions of the sections $u_1,\ldots,u_N$.
+\end{enumerate}
+
+We start with (1), i.e.
+the construction of the source curve $\Ccal$ as a family over $\spec \mathbbm{k}\llbracket t \rrbracket$.
+Let $E \subseteq C$ be the circuit, i.e.
+the minimal genus one subcurve.
+This is either a smooth elliptic curve or a wheel of rational curves.
+Look at the corresponding moduli point $[E] \in \Mfrak_{1,n}$.
+Since this is a smooth stack, we may choose an \'etale chart which locally looks like the tangent space of the stack, which in this case is the deformation space of the elliptic curve.
+This contains a factor $\Aaff^p$ where $p$ is the number of nodes of $C$; the $i$th co-ordinate axis corresponds to a smoothing of the $i$th node, keeping the others fixed, while the generic point of the corresponding orthogonal hyperplane corresponds to a deformation which smooths all the nodes except the $i$th one.
+
+We need to choose a map $\formLine \to \Mfrak_{1,n}$ which sends the closed point to $[E]$ and the generic point to the locus of smooth curves.
+By the discussion of the previous paragraph, we can do this by choosing a map $\formLine \to \Aaff^p$ which sends the closed point to the origin and the generic point to the complmenet $\Gm^p \subseteq \Aaff^p$ of the co-ordinate axes.
+We can certainly choose such a map; furthermore, if for each node $q$ we choose a positive integer $r_q$, then we can choose the map so that it has tangency order $r_q$ to the hyperplane of $\Aaff^p$ corresponding to $q$.
+In terms of the resulting curve $\Ccal$ over $\formLine$, this means that if $C_1, C_2 \subseteq \Ccal$ are the two branches of $C$ around $q$, then these are $\QQ$-Cartier divisors in $\Ccal$, with:
+\begin{equation*} C_1 \cdot C_2 = 1/r_q \end{equation*}
+The weights $r_q$ are chosen by looking at the map $Q^{\operatorname{log}} \to \N$; this map is local since the map $Q^{\operatorname{log}} \to Q^{\operatorname{GS}}$ is local\basenote{Is this always true?
 Isn't this only true if there exists a log lifting?
@@
 Thus each generator $e_q \in Q^{\operatorname{log}}$ maps to a positive integer $r_q$, and this is the weight we choose.
-This means that if $C_1$ and $C_2$ are the two branches of $C$ around $q$, then these are $\QQ$-Cartier divisors in the total space $\Ccal$, with:
-\begin{equation*} C_1 \cdot C_2 = 1/r_q \end{equation*}
-We now define the map $f \colon \Ccal \to \PP^N$ extending the map $f \colon C \to \PP^N$.
-We assume that $H=\{ z_0=0\}$ is a co-ordinate hyperplane.
-We have sections $u_0,\ldots,u_N$ of a line bundle $L$ on $C$ and we need to extend these to sections $\tilde{u}_0,\ldots,\tilde{u}_N$ of a line bundle $\Lcal$ on $\Ccal$.
-
-Let us write $C = C_1 \cup \ldots \cup C_m$ with $C_1,\ldots,C_r$ internal and the rest external. We define the line bundle $\Lcal$ as
+We have thus constructed the smoothing $\Ccal$ of $C$.
+
+We now move on to step (2), which involves extending the central alignment from $C$ to $\Ccal$.
+This is a relative trivial step: since the general fibre of $\Ccal$ is smooth, there is no choice of ordering of the markings or of contraction radius, and its minimal centrally aligned monoid is trivial.
+We can thus take the log structures on the central fibre as charts for the log structures on the deformation.
+To be more precise, in the base we have a chart:
+\begin{align*} Q^{\operatorname{ctr}} & \to \mathbbm{k} \llbracket t \rrbracket \\
+e_q & \mapsto t^{r_q} \end{align*}
+Note that this is well-defined by the fact that we have the factorisation $Q^{\operatorname{ctr}} \to \N$.
+The log structure on $\Ccal$ is obtained by pushing forward the log structure on the central fibre $C$.
+This completes step (2).
+
+We now begin step (3), that of extending the line bundle $L=f^*\OO_{\PP^N}(H)$ on $C$ to a line bundle $\Lcal$ on $\Ccal$.
+In case it hasn't been mentioned already, we assume that $H=\{ z_0=0\}$ is a co-ordinate hyperplane.
+
+Let us write $C$ in terms of its irreducible components as $C = C_1 \cup \ldots \cup C_m$ with $C_1,\ldots,C_r$ internal and the rest external. We define the line bundle $\Lcal$ as
 \begin{equation*} \Lcal = \OO_{\Ccal}\left(\sum_{i=1}^r \gamma_i C_i + \sum_{i=1}^n \alpha_i \tilde{x}_i \right) \end{equation*}
-where each $\gamma_i$ is a positive integer obtained as the image under $Q^{\operatorname{GS}} \to \N$ of the generator corresponding to $C_i$.
-
-This comes with a natural section (or rather, a $\CC^*$-equivalence class of sections) $\tilde{u}_0$ given by the divisor in brackets, and this can be chosen in a unique way so that it restricts to $u_0$ on the central fibre of $\Ccal$.
-
-For each external component $C_j$, we have
+where each $\gamma_i$ is a positive integer obtained as the image under $Q^{\operatorname{GS}} \to \N$ of the generator corresponding to $C_i$, and the $\tilde{x}_i$ are extensions of the Cartier divisors $x_i$ to all of $\Ccal$.
+
+This comes with a natural section (or rather, a $\CC^*$-equivalence class of sections) $\tilde{u}_0$ given by the divisor in brackets above, and this can be chosen in a unique way so that it restricts to $u_0$ on the central fibre of $\Ccal$.
+This completes step (4).
+
+Now we must verify that $\Lcal|_C=L$. For each external component $C_j$, we have
 \begin{equation*} \Lcal|_{C_j} = \OO_{C_j} \left( \sum_{x_i \in C_j} \alpha_i x_i + \sum_{q_i \in C_j} (\gamma_i/r_i) q_j \right) \end{equation*}
-where the latter sum is over nodes of $C_j$ which connect $C_j$ to an internal component $C_i$. We thus need:
+where the latter sum is over nodes of $C_j$ which connect $C_j$ to an internal component $C_i$. We thus need
 \begin{equation*} m_i = \gamma_i / r_i \end{equation*}
-But this is true, because in $Q^{\operatorname{GS}}$ the generator corresponding to the internal component $C_i$ is identified with $m_i$ times the generator corresponding to $q_i$; pushing forward this relation to $\N$ gives the equation above.
-
-\begin{comment} 
+in order to conclude that $\Lcal|_{C_j} = L|_{C_j}$.
+But this is true, because in $Q^{\operatorname{GS}}$ the generator corresponding to the internal component $C_i$ is identified with $u_{q_i}$ times the generator corresponding to $q_i$, and $u_{q_i}=m_i$ by the fact that the type we chose to define $Q^{\operatorname{GS}}$ must satisfy the tropical balancing condition.
+Pushing forward this relation from $Q^{\operatorname{GS}}$ to $\N$ gives the equation above.
+This argument also applies when we have an external subcurve $Z \subseteq C$ which is a wheel of rational components.
+
 Now let us consider an internal component $C_j$. We have
-\begin{align*} \Lcal|_{C_j} & = \OO_{C_j} \left( \sum_{x_i \in C_j} \alpha_i x_i + \sum_{q_i \in C_j} (\gamma_i/r_i) q_i \right) \otimes \OO_{\mathcal{C}}\left(- \gamma_j \sum_{i \neq j} C_i \right) \\
-& = \OO_{C_j}\left( \sum_{x_i \in C_j} \alpha_i x_i + \sum_{q_i \in C_j} \left(\frac{\gamma_i - \gamma_j}{r_i}\right) q_i - \sum_{\tilde{q}_i \in C_j} (\gamma_j/r_i) \tilde{q}_i \right)\end{align*}
+\begin{align*} \Lcal|_{C_j} & = \OO_{C_j} \left( \sum_{x_i \in C_j} \alpha_i x_i + \sum_{\tilde{q}_i \in C_j} (\gamma_i/r_i) \tilde{q}_i \right) \otimes \OO_{\mathcal{C}}\left(- \gamma_j \sum_{i \neq j} C_i \right) \\
+& = \OO_{C_j}\left( \sum_{x_i \in C_j} \alpha_i x_i + \sum_{q_i \in C_j} \left(\frac{\gamma_i - \gamma_j}{r_i}\right) q_i - \sum_{\tilde{q}_i \in C_j} m_i \tilde{q}_i \right)\end{align*}
 where the middle sum is over adjacent internal components and the final sum is over adjacent external components. The fact that $\gamma_j/r_i = m_i$ follows as in the previous case.
 
-It remains to verify the Gathmann-like condition for internal components.
-Let $Z \subseteq C$ be a connected component of $f^{-1}(H)$, and suppose wlog that $Z = C_1 \cup \ldots \cup C_k$ for some of the internal components $C_1,\ldots,C_k$.
-If $Z$ has genus zero then the condition is purely numerical, and we find from the above description that
-\begin{equation*} \deg \Lcal|_Z = \sum_{x_i \in Z} \alpha_i x_i - \sum_{\tilde{q}_i \in Z} m_i \end{equation*}
-where the sum is over external nodes $\tilde{q}_i$, i.e. those connecting to the rest of the curve. By the Gathmann condition, this is exactly $\deg f|_Z^* \OO_{\PP^N}(H)$, which is what we wanted.
-
-On the other hand suppose that $Z$ is genus one. Suppose first off that it has a smooth genus one component, say $C_1$.
-\end{comment}
-
-Let $Z$ be a connected component of $f^{-1}(H)$. Suppose wlog that $Z= C_1 \cup \ldots \cup C_k$. Then because $Z$ does not intersect $C_{k+1},\ldots,C_r$ we have
-\begin{align*} \Lcal|_Z & = \OO_Z \left( \sum_{x_i \in Z} \alpha_i x_i + \sum_{i=1}^k \gamma_i C_i \right) \\
-& = \OO_Z \left( \sum_{x_i \in Z} \alpha_i x_i - \sum_{q_i \in Z} (\gamma_i/r_i) q_i \right) \\
-& = \OO_Z \left( \sum_{x_i \in Z} \alpha_i x_i - \sum_{q_i \in Z} m_i q_i \right) \end{align*}
-where the sum is over external components of $C$ which are adjacent to $Z$ via $q_i$. By the Gathmann-like condition, this is exactly $f^* \OO(Y)|_Z$.
-
-We have thus shown that when we restrict $\Lcal$ to either an external component or an internal component (where here we mean a connected component of $f^{-1}(Y)$) we get the correct line bundle.
-Assuming that there is no wheel of $\PP^1$s, or more generally that any wheel of $\PP^1$s which does appear appears inside a connected component, this shows that $\Lcal_{\Ccal_0} = L$, as claimed.
+We must argue that $\Lcal|_{C_j} = L|_{C_j}$. Suppose for the moment that $C_j$ is genus zero, so that we only need to check the degrees. We must show:
+\begin{equation*} \deg L|_{C_j} = \sum_{x_i \in C_j} \alpha_i - \sum_{q_i \in C_j} \left( \dfrac{\gamma_j - \gamma_i}{r_i}\right) - \sum_{\tilde{q}_i \in C_j} u_{\tilde{q}_i}\end{equation*}
+But by the definition of $Q^{\operatorname{GS}}$ we have:
+\begin{equation*} (\gamma_j - \gamma_i)/r_i = u_{q_i} \end{equation*}
+From which the above formula holds because of the tropical balancing condition we imposed when choosing the type.
+
+Similarly if $C_j$ is smooth of genus one we must show:
+\begin{equation*} L|_{C_j} = \OO_{C_j} \left( \sum_{x_i \in C_j} \alpha_i x_i - \sum_{q_i \in C_j} u_{q_i} q_i - \sum_{\tilde{q}_i \in C_j} u_{\tilde{q}_i} \tilde{q}_i \right) \end{equation*}
+But this is just the balancing condition on the level of $\Pic(C_j)$.
+
+What about if $C_j$ is a wheel of rational components?
+Then it isn't irreducible, so let's write it as $Z= C_1 \cup \ldots \cup C_k$.
+So there are other internal components $C_{k+1},\ldots,C_r$ and external components $C_{r+1},\ldots,C_m$.
+We assume that $C_1,\ldots,C_k$ are ordered so that $C_i$ intersects $C_{i-1}$, $C_{i+1}$ and none others.
+Notice that this means that:
+\begin{equation*} C_i^2 = -1/r_{i-1} - 1/r_{i+1} - \sum_{q_j \in C_i} 1/r_j \end{equation*}
+for all $i \in \{1,\ldots,k\}$, where the sum is over all nodes $q_j$ which connect $Z$ to the rest of the curve. Thus we obtain:
+\begin{align*} \Lcal|_Z & = \OO_Z \left( \sum_{x_i \in Z} \alpha_i x_i\right) \otimes \OO_{\Ccal} \left( \sum_{i=1}^r \gamma_i C_i \right)\bigg|_Z \\
+& = \OO_Z \left( \sum_{x_i \in Z} \alpha_i x_i + \sum_{\substack{q_i \in Z \\ \text{$q_i$ joins $Z$} \\ \text{to int.
+cpt.}}} (\gamma_i/r_i) q_i \right) \otimes \OO_{\Ccal} \left( \sum_{i=1}^k \gamma_i C_i \right) \bigg|_Z \\
+& = \OO_Z \left( \sum_{x_i \in Z} \alpha_i x_i + \sum_{\substack{q_i \in Z \\ \text{$q_i$ joins $Z$} \\ \text{to int.
+cpt.}}} (\gamma_i/r_i) q_i + \sum_{i=1}^k \gamma_i \left( \frac{1}{r_{i,i-1}} q_{i-1} + \frac{1}{r_{i,i+1}} q_{i+1} + (C_i^2) s_i \right)\right)
+\end{align*}
+where $q_{i-1}$ is the node connecting $C_{i-1}$ and $C_i$ (and similarly for $q_{i+1}$) and $s_i$ is some point of $C_i$ (doesn't really matter which, since $C_i$ is rational).
+
+Using the description of $C_i^2$ given above, we see that the terms $q_{i-1}/r_{i,i-1}$ and $q_{i+1}/r_{i,i+1}$ cancel, and we are left with
+\begin{align*} \Lcal|_Z & = \OO_Z \left( \sum_{x_i \in Z} \alpha_i x_i + \sum_{\substack{q_i \in Z \\ \text{$q_i$ joins $Z$} \\ \text{to int.
+cpt.}}} (\gamma_i/r_i) q_i + \sum_{\substack{q_i \in Z \\ \text{$q_i$ joins $Z$} \\ \text{to rest of curve}}} (\gamma_i/r_i) q_i \right) \\
+& = \OO_Z \left( \sum_{x_i \in Z} \alpha_i x_i + \sum_{\substack{q_i \in Z \\ \text{$q_i$ joins $Z$} \\ \text{to int.
+cpt.}}} \left( \dfrac{\gamma_i-\gamma_j}{r_i} \right) q_i - \sum_{\substack{q_i \in Z \\ \text{$q_i$ joins $Z$} \\ \text{to ext.
+cpt}}} (\gamma_i/r_i) q_i \right)
+\end{align*}
+and this is precisely the balancing condition on the level of $\Pic(Z)$.
+This proves that $\Lcal|_C = L$, except for one case which we haven't yet considered, namely when there is a wheel of rational curves which is partially internal and partially external.
+In this case essentially the same argument as given above applies.
+
+We have thus shown that we can break $C$ up into pieces (mostly into its irreducible components, unless there is a rational wheel in which case we treat this as a single piece) such that the corresponding intersection graph has genus zero and such that $\Lcal$ restricts to $L$ on each of the pieces.
+The fact that $\Lcal|_C = L$ then immediately follows (since the intersection graph has genus zero, so the Picard group of $C$ is equal to the direct sum of the Picard groups of the pieces).
+This completes the proof of step (3).
+
+As mentioned above, step (4) is immediate by the construction of $\Lcal$.
+It remains to carry out step (5), i.e.
+to extend the sections $u_1,\ldots,u_N$.
+By standard results in deformation theory, obstructions to extending sections of a deformation of $L$ are contained in $\HH^1(C,L)$.
+If $L$ is non-trivial on the circuit, then this space vanishes and so the sections extend immediately.
+
+Thus the only case we need to check is when $L$ is trivial on the circuit, which means that the circuit $E$ (again, either a smooth elliptic curve or a wheel of rational components) is contracted by the map $f$.
+In this case we want to extend the sections by referring to the corresponding Smyth curve.
+From the centrally aligned curve $\Ccal$ we obtain a diagram:
+\bcd
+& \tilde{\Ccal} \ar[ld] \ar[rd] & \\
+\Ccal & & \overline{\Ccal}
+\ecd
 
 \end{proof}
-
 \newpage

### 2018-03-23 genus-one-relative-maps.tex
Almost finished proof of condition for closed

@@
 Here we are not allowed to choose a random type, but have to choose one which is compatible with the underlying stable map, in the sense that the modified tropical balancing condition is satisfied.
+The Gathmann-style condition (1) is a necessary condition for the existence of a compatible type (on the level of $\Pic C$).
+
 Remember that we get one balancing condition for each generator of $\Gamma(C, f^* \overline{\Mcal}_H)$, so as well as there being a balancing condition for each internal component there is also one wherever the curve intersects the divisor in an isolate point (where for instance we get that $u_q = m_q$ at nodes connecting an external to an internal component).
@@
 \ecd
+\basenote{Finish this}
+
+We have thus constructed the smoothing, which shows that conditions (1) and (2) above are sufficient to characterise points in the closure of the nice locus.
+
+We will now show that these conditions are necessary.
+Suppose therefore that there is a family $\Ccal \to \formLine$ and consider the central fibre $\Ccal_0 = C$.
+Condition (1) for $C$ follows immediately from continuity of intersection products.
+
+To show condition (2), let $u_0 = f^*(z_0) \in \HH^0(\Ccal,f^* \OO_{\PP^N}(H))$.
+For each component $C_i$ of the central fibre $C$, let $\gamma_i$ be the vanishing order of $u_0$ along the Weil divisor $C_i$.
+For each internal component of $C$ this defines a non-zero map $\gamma_i \colon \N \to \N$.
+On the other hand, for each node $q$ consider the corresponding generator $e_q \in Q^{\operatorname{ctr}}$.
+A chart for the log structure on the base is given by a map
+\begin{equation*} Q^{\operatorname{ctr}} \to \mathbbm{k} \llbracket t \rrbracket \end{equation*}
+which we can compose with the valuation on $\mathbbm{k} \llbracket t \rrbracket$ to get a map:
+\begin{equation*} Q^{\operatorname{ctr}} \to \N \end{equation*}
+Let $r_q$ be the image of $e_q$ along this map.
+This is always non-zero because every node is smoothed in the family $\Ccal$; thus we have a non-zero map $r_q \colon \N \to \N$.
+These, together with the $\gamma_i$ defined above, give a local morphism
+\begin{equation*} \prod_{q \in C} \N_q \times \prod_{C_i} \N_{\eta_i} \to \N \end{equation*}
+where the second product is over the internal components of $C$.
+We claim that this descends to the quotient $Q^{\operatorname{GS}}$ (recall again that this quotient depends on a choice of type).
+We have to check that for every node $q$ we have
+\begin{equation*} u_q r_q = \gamma_i - \gamma_j \end{equation*}
+where $C_i$ and $C_j$ are the adjacent components (this makes for all nodes, since $\gamma_i=0$ for any external component).
+Remember that the $u_q$ are not fixed a priori; thus we can think of the above formula as determining the $u_q$.
+What we then need to check is that the $u_q$ thus defined are all integers, and that they satisfy the tropical balancing condition on the level of $\Pic (C)$.
+
+Consider the dual graph of $C$, treating the circuit $E$ as a single node of this graph, so that the graph has genus zero.
+Start from a leaf $C_i$ of this graph, so that there is only one node $q$ of the corresponding component.
+Let $C_j$ be the unique component of $C$ which is adjacent to $C_i$ (via $q$).
+Then we have:
+\begin{equation*} \deg f|_{C_i} = \deg \Lcal|_{C_i} = (\gamma_i - \gamma_j)/r_q + \sum_{x_k \in C_i} \alpha_k \end{equation*}
+Rearranging, we see that $(\gamma_i - \gamma_i)/r_q$ is an integer.
+Substiting in $u_q$ for this value, we obtain precisely the balancing condition, which we can view as happening on the level of $\Pic (C_j)$ (if we refrain from taking the degree first).
+
+We now proceed by induction.
+The process is as follows: having determined $q$, we pass to the next component $C_j$.
+If this has only one other node $r$ besides $q$, we apply the same argument as before to show that $u_r$ is an integer and satisfies the balancing condition.
+If it contains more than one other node, we pick one of them and follow the resulting path through the dual graph until we arrive at a leaf with a single undetermined node (which must exist, since otherwise the node we started with would have been determined).
+We then start the process again from there.
+
+This procedure proves that all the $u_q$ are integers and that the balancing condition is satisfied on every component, except for those nodes and those components belonging to the circuit $E$.
+If the circuit is smooth there is nothing additional to prove, except to note that the Gathmann-like condition (1) ensures that the balancing condition will be satisfied on the level of $\Pic(E)$ (rather than just on the level of degree), so that it is satisfied for $\Pic(C)$.
+
+It remains to consider the case when $E$ is a wheel of rational components.
+Again the Gathmann-like condition (1) ensures we have balancing on the level of $\Pic(E)$, once we show that all the $u_q$ for the nodes internal to $E$ are integers.
 

### 2018-03-23 genus-one-relative-maps.tex
Redid construction of log structure on C

@@
 Note that this is well-defined by the fact that we have the factorisation $Q^{\operatorname{ctr}} \to \N$.
-The log structure on $\Ccal$ is obtained by pushing forward the log structure on the central fibre $C$.
+This defines a log structure $\Mcal_S^{\operatorname{ctr}}$ on $S$.
+On the other hand the morphism $S \to \Mfrak_{1,n}$ defines another log structure $\Mcal_S^{\operatorname{log}}$ on $S$ corresponding to the minimal structure of a log smooth curve on $\Ccal$.
+There is a map $\Mcal_S^{\operatorname{log}} \to \Mcal_S^{\operatorname{ctr}}$ induced by the map of charts $Q^{\operatorname{log}} \to Q^{\operatorname{ctr}}$, and this gives a diagram:
+\bcd
+& (C,\Mcal_C^{\operatorname{log}}) \ar[d] \\
+(S,\Mcal_S^{\operatorname{ctr}}) \ar[r] & (S,\Mcal_S^{\operatorname{log}})
+\ecd
+We define $(\Ccal,\Mcal_{\Ccal}^{\operatorname{ctr}})$ to be the fibre product.
+This is clearly a log smooth centrally aligned curve over $(S,\Mcal_S^{\operatorname{ctr}})$, with radius $\delta$ given by the radius on the central fibre (note that $\overline{\Mcal_S}^{\operatorname{ctr}}$ is supported on the closed point).
 This completes step (2).

### 2018-03-24 genus-one-relative-maps.tex
Almost finished proof

@@
 Again the Gathmann-like condition (1) ensures we have balancing on the level of $\Pic(E)$, once we show that all the $u_q$ for the nodes internal to $E$ are integers.
+Labelling the components of $E$ as $C_1,\ldots,C_k$ with $C_i$ intersecting $C_{i-1}$ and $C_{i+1}$, we obtain relations:
+\begin{equation*} u_{q_i} r_{q_i} = \gamma_{i+1} - \gamma_{i-1} \end{equation*}
+Thus $u_{q_i} \in r_{q_i}^{-1} \cdot \Z$.
+But if we restrict $\Lcal$ to each component and look at the resulting equation, we see that in fact $u_{q_i} \in (1/r_{q_j}) \Z$ for all $j$.
+Thus $u_{q_i} \in (1/g) \Z$ where $g = \operatorname{gcd}(r_{q_1},\ldots,r_{q_k})$.
+\basenote{Maybe we can fix this using saturation: note that we only need a map from the saturation of the quotient to $\N$, not from the quotient itself.}
 

### 2018-03-24 genus-one-relative-maps.tex

@@
 
+\newcommand{\basenote}[1]{\footnote{\color{red}#1}}
+
+\newcommand{\plC}{\scalebox{0.8}[1.3]{$\sqsubset$}}
 \newcommand{\sidenote}[1]{\marginpar{\textbf{\color{red}#1}}}
-\newcommand{\basenote}[1]{\footnote{\color{red}#1}}
-
-\newcommand{\plC}{\scalebox{0.8}[1.3]{$\sqsubset$}}
 
@@
 \section{Recursion formula for $\PP^1|\infty, \Sigma \alpha = d$}
+=======
+\section{Recursion formula}
+
+\subsection{The case $\sum\alpha=d$}
+
+\subsection{Definition of the boundary components} According to Vakil's article there should be three sorts of boundary components.
+\begin{enumerate}[label=(\alph*)]
+ \item \[\mathcal Y^a=\M{0}{\lvert\alpha^{(0)}\rvert+r}{H}{d_0}\times_{H^r}\left(\VZc{1}{\alpha^{(1)}\cup\{m^{(1)}\}}{\PP^N|H}{d_1}\times\prod_{i=2}^r\M{0}{\alpha^{(i)}\cup\{m^{(i)}\}}{\PP^N|H}{d_i}\right)\]
+ \item \[\mathcal Y^b=\M{0}{\lvert\alpha^{(0)}\rvert+r}{H}{d_0}\times_{H^r}\left(\M{0}{\alpha^{(1)}\cup\{m^{(1)},m^{(2)}\}}{\PP^N|H}{d_1}\times\prod_{i=3}^r\M{0}{\alpha^{(i)}\cup\{m^{(i)}\}}{\PP^N|H}{d_i}\right)\]
+ \item \[\mathcal Y^c\subseteq \VZc{1}{\lvert\alpha^{(0)}\rvert+r}{H}{d_0}\times_{H^r}\prod_{i=1}^r\M{0}{\alpha^{(i)}\cup\{m^{(i)}\}}{\PP^N|H}{d_i}\]
+ $\mathcal Y^c$ is cut within the latter by Gathmann's condition on line bundles:
+ \[f_{|E}^*\mathcal O_H(1)\cong\mathcal O_E\left(\sum_{x_j\in E}\alpha_jx_j-\sum_{i=1}^r m^{(i)}y_i\right)\]\sidenote{Express the line bundle condition in terms of tautological classes?}
+ Notice that such condition depends on the choice of $m^{(i)}$ but is really just a condition on the first factor of the product, so $\mathcal Y^c$ itself can be expressed as a product.
+\end{enumerate}
+
+\begin{remark}
+ Notice that gluing does not present the subtleties to which log geometry has made us used, since we endow the curves with the minimal centrally aligned structure, possibly after prescribing that the smoothing parameters for the newly created nodes are \emph{bigger} than the contraction radius $\delta$.
+\end{remark}
+
+\begin{remark}
+ A dimensional computation shows that $\mathcal Y^b$ is never relevant to the purpose of the recursion formula.
+On the other hand the classes of $\mathcal Y^a$ and $\mathcal Y^c$ should be weighted with the coefficient $\frac{\prod m^{(i)}}{r!}$.
+Let $D_{1,\alpha,k}(\PP^N|H)$ be the union of all the $\mathcal Y^a$ and $\mathcal Y^c$ as above, for any choice of number of external components $r$, distribution of the markings $A$, and of the degree $D$, provided the marked point $x_k$ lies on the internal component $C^{(0)}$.
+Let each component be endowed with its fundamental class weighted as above and let $\virt{D_{1,\alpha,k}(\PP^N|H)}$ be the sum of all these classes.
+\end{remark}
+
+\begin{thm}
+ Assume $\sum\alpha=d$. Then \[(\alpha_k\psi_k+\ev_k^*H)[\VZc{1}{\alpha}{\PP^N|H}{d}]=\virt{D_{1,\alpha,k}(\PP^N|H)}.\]
+\end{thm}
+\begin{proof}
+We perform a number of reductions.
+ \begin{itemize}%[leftmargin=1cm]
+  \item \textbf{Reduction to the case of $\PP^1|\{\infty\}$:} by choosing a general $N-2$-plane $A\subseteq H$ and projecting away from it.
+Must show that the rational map $\rho_A\colon \VZc{1}{n}{\PP^N|H}{d}\dashrightarrow \VZc{1}{n}{\PP^1|\{\infty\}}{d}$ is defined and smooth at a general point of $D_{1,\alpha,k}(\PP^N|H)$.
+
+  \item \textbf{Reduction to an \'etale neighbourhood of $C^{(0)}$:} the plan is to understand the global perfect obstruction theory of $\VZc{1}{n}{\PP^1}{d}$ and see that the tangent to the latter is a sum of contributions from the \emph{special loci}, namely contracted components, ramification points, markings and nodes.
+
+  \begin{remark}
+   When we are studying the infinitesimal deformation theory of centrally aligned curves, notice that being centrally aligned must be checked on geometric points, and minimality is open, hence any first-order deformation as a log smooth curve will automatically be minimal centrally aligned.
+The tangent space is then $H^1(C,T_C^{\rm{log}})$; notice that this is independent from the log structure on the base.
+  \end{remark}
+
+  \begin{example}
+   There are non-trivial deformations that are trivial on the underlying marked prestable curve.
+If $(C,\mathcal M_C)\to (\Spec(k),Q^{\rm{cen}})$ is a centrally aligned curve, then in order to define a deformation over $\Spec(k[\epsilon])$ we need to extend the log structure on the base by choosing a map $Q^{\rm{cen}}\to k[\epsilon]$.
+Notice that if we want the underlying curve to be a trivial deformation we better send all the smoothing parameters to $0$ in $k[\epsilon]$; on the other hand, if $Q^{\rm{cen}}$ contains an element such as $e_i-e_j$ (making $R_i$ further from the circuit than $R_j$), then we are free to map it to an invertible element in $k[\epsilon]$, which will kill it in the associated log structure;\sidenote{Invertible elements of $k[\epsilon]$ remain invertible when setting $\epsilon=0$, which seems to kill $e_i-e_j$ on the central fiber too.} this will make $R_i$ and $R_j$ be \emph{at the same distance} from the circuit in the deformation.
+Importantly, $Q^{\rm{log}}\to Q^{\rm{cen}}$ is an epimorphism only in the category of integral monoid (of which the multiplicative monoid of a ring is never an object, because it has a sink).
+  \end{example}
+
+\end{itemize}
+\end{proof}
 

### 2018-04-29 genus-one-relative-maps.tex
no real changes

@@
 %\usepackage{showlabels}
-\usepackage[hidelinks]{hyperref}
+\usepackage{hyperref}
 \usepackage{amsthm}
@@
 
-\newcommand{\basenote}[1]{\footnote{\color{red}#1}}
-
 \newcommand{\plC}{\scalebox{0.8}[1.3]{$\sqsubset$}}
@@
 
-\newcommand{\formLine}{\spec \mathbbm{k}\llbracket t \rrbracket}
-
-\newcommand{\spec}{\operatorname{Spec}}
 \newcommand{\TT}{\operatorname{T}}
@@
 \newcommand{\VZc}[4]{\mathcal{V\!Z}^{\rm{ctr}}_{#1,#2}(#3,#4)}
-\newcommand{\VZco}[4]{\mathcal{V\!Z}^{\rm{ctr},\circ}_{#1,#2}(#3,#4)}
 \newcommand{\VZcLi}[4]{\mathcal{V\!Z}^{\rm{ctr, Li}}_{#1,#2}(#3,#4)}
@@
 
-\newcommand{\Ccal}{\mathcal{C}}
-\newcommand{\Mcal}{\mathcal{M}}
-\newcommand{\Lcal}{\mathcal{L}}
-\newcommand{\Mfrak}{\mathfrak{M}}
-
 \theoremstyle{definition}
@@
 
-\begin{abstract} For a smooth projective variety $X$ and a smooth very ample hypersurface $Y \subseteq X$, we define moduli spaces of relative stable maps to $(X,Y)$ in genus one, as closed substacks of the moduli space of maps from centrally aligned curves, as constructed in \cite{RSPW}.
+\begin{abstract} For a smooth projective variety $X$ and a smooth very ample hypersurface $Y \subseteq X$, we define moduli spaces of relative stable maps to $(X,Y)$ in genus one, as closed substacks of the moduli space of maps from centrally aligned curves, constructed in \cite{RSPW}.
 We construct virtual classes for these moduli spaces, which we use to define \emph{reduced relative Gromov--Witten invariants} in genus one.
@@
 \section{The space of relative centrally aligned maps}
-\noindent Recall \cite{RSPW} that the moduli space of maps from centrally aligned curves is obtained by first considering the Cartesian diagram
+\noindent Recall \cite{RSPW} that the moduli space of maps from centrally aligned curves is obtained by considering the  Cartesian diagram
 \bcd
@@
 \begin{enumerate}
-\item a centrally aligned curve $(C,\Mcal_C,\delta)$;
+\item a centrally aligned curve $(C,M_C,\delta)$;
 \item a stable map $f\colon C \to X$;
@@
 \section{Definition of centrally aligned relative space}
-Fix a vector $\alpha=(\alpha_1,\ldots,\alpha_n)$ of tangency conditions, and suppose for the moment that $\Sigma \alpha = d$.
-We consider the so-called \emph{nice locus} of relative centrally aligned maps.
-This is the locally closed substack of $\VZc{1}{n}{\PP^N}{d}$ consisting of centrally aligned maps $(C,x_1,\ldots,x_n,\Mcal_C,\delta,f)$ such that:
-\begin{enumerate}
-\item the source curve $C$ is smooth;
-\item $C$ is not mapped entirely into $H$ by $f$;
-\item the points of $C$ which are mapped into $H$ (necessarily a finite number by the previous condition) are all marked, with the map having tangency $\alpha_i$ to $H$ at the marking $x_i$.
-\end{enumerate}
-These conditions mean that $\delta=0$ and that the log structure $\Mcal_C$ (which is a minimal centrally aligned log structure) is equal to the minimal structure for a log smooth curve, which in this case (since there are no nodes) is just the divisorial log structure with respect to the markings $x_1,\ldots,x_n$.
-
-This is a locally closed substack of expected codimension $\Sigma \alpha=d$, and is denoted:
-\begin{equation*} \VZco{1}{\alpha}{\PP^N|H}{d} \end{equation*}
-It has a well-defined stack structure since it is a moduli space. Note that it is irreducible, since we can find a parametrisation for it over $\Mfrak_{1,n}$.
-
-We now define the \emph{centrally alined relative space} to be the closure of the nice locus:
-\begin{equation*} \VZc{1}{\alpha}{\PP^N|H}{d} := \overline{\VZco{1}{\alpha}{\PP^N|H}{d}} \subseteq \VZc{1}{n}{\PP^N}{d} \end{equation*}
-This inherits the natural structure of a stack from the stack structure of the nice locus.
-It is proper since it is a closed substack of a proper stack, and it is irreducible because it is the closure of an irreducible stack.
-Hence it admits a fundamental class, which we can use to define \emph{reduced relative Gromov--Witten invariants}:
-\begin{equation*} \langle \tau_{k_1}(\gamma_1), \ldots, \tau_{k_n}(\gamma_n) \rangle^{\PP^N|H, \operatorname{red}}_{0,\alpha,d} := \int_{[\VZc{1}{\alpha}{\PP^N|H}{d}]} \prod_{i=1}^n \ev_i^*(\gamma_i) \psi_i^{k_i} \end{equation*}
-
 \section{Characterisation of the closed points of the relative space}
-It will be important for our purposes to have an understanding of the boundary of the relative space, i.e.
-what we add in when we take the closure of the nice locus.
-In this section we will describe this boundary on the level of closed points.
-
-\begin{prop} \label{closed pts of relative space} A centrally aligned map over a closed point $\spec \mathbbm{k}$ is in the relative space if and only if the following two conditions are satisfied:
-\begin{enumerate}
-\item \emph{Gathmann's relative condition:} for each connected component $Z$ of $f^{-1}(Y)$, either:
-\begin{enumerate}
-\item $Z$ is a single point of $C$, in which case if $Z=x_i$ is a marking then we require that the multiplicity of $f$ at $x_i$ along $Y$ is at least $\alpha_i$ (if $Z$ is not a marking then there is no condition);
-\item $Z$ is a subcurve $Z \subseteq C$, in which case we require that
-\begin{equation*} f^*[Y]|_Z -\sum_{x_i\in Z}\alpha_ix_i\end{equation*}
-is an effective class in $\Achow_0(Z)$.
-\end{enumerate}
-
-\item \emph{Compatibility condition:} this applies when the minimal subcurve of genus one (the \emph{circuit}) is contracted to a point in $Y$.
-In this case we require that there is a local morphism of monoids:
-\begin{equation*} Q^{\operatorname{GS}} \to \N\end{equation*}
-such that the dashed arrow can be filled in to make the following square commutative:
-\bcd
-Q^{\operatorname{log}} \ar[r]\ar[d] & Q^{\operatorname{GS}} \ar[d] \\
-Q^{\operatorname{ctr}}\ar[r,dashed] & \N
-\ecd
-It is obvious from the construction that the map $Q^{\operatorname{ctr}} \to \N$ is unique if it exists
-\end{enumerate}
-\end{prop}
-
-\begin{remark} The monoid $Q^{\operatorname{GS}}$ depends on a choice of \emph{type}, in this case a choice of the $u_q$ (the $u_p$ are already determined by the choice of $\alpha$).
-Here we are not allowed to choose a random type, but have to choose one which is compatible with the underlying stable map, in the sense that the modified tropical balancing condition is satisfied.
-The Gathmann-style condition (1) is a necessary condition for the existence of a compatible type (on the level of $\Pic C$).
-
-Remember that we get one balancing condition for each generator of $\Gamma(C, f^* \overline{\Mcal}_H)$, so as well as there being a balancing condition for each internal component there is also one wherever the curve intersects the divisor in an isolate point (where for instance we get that $u_q = m_q$ at nodes connecting an external to an internal component).
-Also we require this condition to take place in $\Pic(C)$, but we are entitled at any point to restrict to components of $C$ or take degrees to get (in general weaker) conditions.
-\end{remark}
-
-\begin{remark} Gathmann's condition obviously extends to the case $\Sigma \alpha \leq d$.
-\basenote{What is the correct generalisation of the compatibility condition?} Here we try to make the condition for a curve component of $f^{-1}(Y)$ into an easily verifiable criterion: if $Z$ is a smooth elliptic curve, recall that every line bundle of positive degree on it is effective, hence the relative condition can be rephrased as the following numerical criterion:
-\begin{equation*} f_*[Z]\cdot [Y]+\sum_{j=1}^r m^{(j)}\geq \sum_{x_i\in Z}\alpha_i \end{equation*}
-together with the additional requirement that, when the above is an equality, there is an isomorphism of line bundles:
-\begin{equation}\label{eqn:eq_in_Pic}
-(f|_{Z})^*\OO_X(Y) \otimes \OO_Z\left(\sum_{j=1}^r m^{(j)}y_j\right)=\OO_Z\left(\sum_{x_i\in Z}\alpha_ix_i\right) 
-\end{equation}
-
-If $Z$ is reducible, the correct extension is not to impose the same condition componentwise; rather, we should ask the numerical condition for the total degree, and, if $Z$ is obtained by gluing a smooth elliptic curve $E$ with a forest of rational trees $T_i$ at roots $q^E_i$, then the line bundle equality \eqref{eqn:eq_in_Pic} should be required in $\Pic(E)$ after counting each $q^E_i$ towards the left hand side with multiplicity:
-\[f_*[T_i]\cdot [Y]+\sum_{\text{external components attached to $T_i$}} m^{(j)} \geq \sum_{x_j\in T_i}\alpha_j\]
-%That this is the right thing to do follows from the proof that Gathmann's relative space is the projection of Jun Li's moduli space of maps to the expanded pair after contracting the higher levels of the accordion.
-\end{remark}
-
-\begin{proof}[Proof of Proposition \ref{closed pts of relative space}]
-First suppose that the conditions (1) and (2) of the Proposition are satisfied; so we have Gathmann's condition on the level of line bundles and a factorisation:
-\bcd
-Q^{\operatorname{log}} \ar[r]\ar[d] & Q^{\operatorname{GS}} \ar[d] \\
-Q^{\operatorname{ctr}}\ar[r] & \N
-\ecd
-We will construct a smoothing of the centrally aligned map, i.e.
-a $1$-parameter family whose central fibre is the map we started with and whose general fibre is in the nice locus.
-The construction proceeds in the following order:
-\begin{enumerate}
-\item construct the smoothing $\Ccal$ of the source curve $C$, as a scheme;
-\item construct the extension $(\Mcal_{\Ccal},\delta)$ of the central alignment on $C$;
-\item construct the extension $\Lcal$ of the line bundle $L=f^*\OO_{\PP^N}(H)$ from $C$ to $\Ccal$;
-\item construct the extension of the section $u_0 \in \HH^0(C,L)$;
-\item construct the extensions of the sections $u_1,\ldots,u_N$.
-\end{enumerate}
-
-We start with (1), i.e.
-the construction of the source curve $\Ccal$ as a family over $\spec \mathbbm{k}\llbracket t \rrbracket$.
-Let $E \subseteq C$ be the circuit, i.e.
-the minimal genus one subcurve.
-This is either a smooth elliptic curve or a wheel of rational curves.
-Look at the corresponding moduli point $[E] \in \Mfrak_{1,n}$.
-Since this is a smooth stack, we may choose an \'etale chart which locally looks like the tangent space of the stack, which in this case is the deformation space of the elliptic curve.
-This contains a factor $\Aaff^p$ where $p$ is the number of nodes of $C$; the $i$th co-ordinate axis corresponds to a smoothing of the $i$th node, keeping the others fixed, while the generic point of the corresponding orthogonal hyperplane corresponds to a deformation which smooths all the nodes except the $i$th one.
-
-We need to choose a map $\formLine \to \Mfrak_{1,n}$ which sends the closed point to $[E]$ and the generic point to the locus of smooth curves.
-By the discussion of the previous paragraph, we can do this by choosing a map $\formLine \to \Aaff^p$ which sends the closed point to the origin and the generic point to the complmenet $\Gm^p \subseteq \Aaff^p$ of the co-ordinate axes.
-We can certainly choose such a map; furthermore, if for each node $q$ we choose a positive integer $r_q$, then we can choose the map so that it has tangency order $r_q$ to the hyperplane of $\Aaff^p$ corresponding to $q$.
-In terms of the resulting curve $\Ccal$ over $\formLine$, this means that if $C_1, C_2 \subseteq \Ccal$ are the two branches of $C$ around $q$, then these are $\QQ$-Cartier divisors in $\Ccal$, with:
-\begin{equation*} C_1 \cdot C_2 = 1/r_q \end{equation*}
-The weights $r_q$ are chosen by looking at the map $Q^{\operatorname{log}} \to \N$; this map is local since the map $Q^{\operatorname{log}} \to Q^{\operatorname{GS}}$ is local\basenote{Is this always true?
-Isn't this only true if there exists a log lifting?
-But maybe it's always true for Deligne--Faltings pairs.} and the map $Q^{\operatorname{GS}} \to \N$ is local by assumption.
-Thus each generator $e_q \in Q^{\operatorname{log}}$ maps to a positive integer $r_q$, and this is the weight we choose.
-We have thus constructed the smoothing $\Ccal$ of $C$.
-
-We now move on to step (2), which involves extending the central alignment from $C$ to $\Ccal$.
-This is a relative trivial step: since the general fibre of $\Ccal$ is smooth, there is no choice of ordering of the markings or of contraction radius, and its minimal centrally aligned monoid is trivial.
-We can thus take the log structures on the central fibre as charts for the log structures on the deformation.
-To be more precise, in the base we have a chart:
-\begin{align*} Q^{\operatorname{ctr}} & \to \mathbbm{k} \llbracket t \rrbracket \\
-e_q & \mapsto t^{r_q} \end{align*}
-Note that this is well-defined by the fact that we have the factorisation $Q^{\operatorname{ctr}} \to \N$.
-This defines a log structure $\Mcal_S^{\operatorname{ctr}}$ on $S$.
-On the other hand the morphism $S \to \Mfrak_{1,n}$ defines another log structure $\Mcal_S^{\operatorname{log}}$ on $S$ corresponding to the minimal structure of a log smooth curve on $\Ccal$.
-There is a map $\Mcal_S^{\operatorname{log}} \to \Mcal_S^{\operatorname{ctr}}$ induced by the map of charts $Q^{\operatorname{log}} \to Q^{\operatorname{ctr}}$, and this gives a diagram:
-\bcd
-& (C,\Mcal_C^{\operatorname{log}}) \ar[d] \\
-(S,\Mcal_S^{\operatorname{ctr}}) \ar[r] & (S,\Mcal_S^{\operatorname{log}})
-\ecd
-We define $(\Ccal,\Mcal_{\Ccal}^{\operatorname{ctr}})$ to be the fibre product.
-This is clearly a log smooth centrally aligned curve over $(S,\Mcal_S^{\operatorname{ctr}})$, with radius $\delta$ given by the radius on the central fibre (note that $\overline{\Mcal_S}^{\operatorname{ctr}}$ is supported on the closed point).
-This completes step (2).
-
-We now begin step (3), that of extending the line bundle $L=f^*\OO_{\PP^N}(H)$ on $C$ to a line bundle $\Lcal$ on $\Ccal$.
-In case it hasn't been mentioned already, we assume that $H=\{ z_0=0\}$ is a co-ordinate hyperplane.
-
-Let us write $C$ in terms of its irreducible components as $C = C_1 \cup \ldots \cup C_m$ with $C_1,\ldots,C_r$ internal and the rest external. We define the line bundle $\Lcal$ as
-\begin{equation*} \Lcal = \OO_{\Ccal}\left(\sum_{i=1}^r \gamma_i C_i + \sum_{i=1}^n \alpha_i \tilde{x}_i \right) \end{equation*}
-where each $\gamma_i$ is a positive integer obtained as the image under $Q^{\operatorname{GS}} \to \N$ of the generator corresponding to $C_i$, and the $\tilde{x}_i$ are extensions of the Cartier divisors $x_i$ to all of $\Ccal$.
-
-This comes with a natural section (or rather, a $\CC^*$-equivalence class of sections) $\tilde{u}_0$ given by the divisor in brackets above, and this can be chosen in a unique way so that it restricts to $u_0$ on the central fibre of $\Ccal$.
-This completes step (4).
-
-Now we must verify that $\Lcal|_C=L$. For each external component $C_j$, we have
-\begin{equation*} \Lcal|_{C_j} = \OO_{C_j} \left( \sum_{x_i \in C_j} \alpha_i x_i + \sum_{q_i \in C_j} (\gamma_i/r_i) q_j \right) \end{equation*}
-where the latter sum is over nodes of $C_j$ which connect $C_j$ to an internal component $C_i$. We thus need
-\begin{equation*} m_i = \gamma_i / r_i \end{equation*}
-in order to conclude that $\Lcal|_{C_j} = L|_{C_j}$.
-But this is true, because in $Q^{\operatorname{GS}}$ the generator corresponding to the internal component $C_i$ is identified with $u_{q_i}$ times the generator corresponding to $q_i$, and $u_{q_i}=m_i$ by the fact that the type we chose to define $Q^{\operatorname{GS}}$ must satisfy the tropical balancing condition.
-Pushing forward this relation from $Q^{\operatorname{GS}}$ to $\N$ gives the equation above.
-This argument also applies when we have an external subcurve $Z \subseteq C$ which is a wheel of rational components.
-
-Now let us consider an internal component $C_j$. We have
-\begin{align*} \Lcal|_{C_j} & = \OO_{C_j} \left( \sum_{x_i \in C_j} \alpha_i x_i + \sum_{\tilde{q}_i \in C_j} (\gamma_i/r_i) \tilde{q}_i \right) \otimes \OO_{\mathcal{C}}\left(- \gamma_j \sum_{i \neq j} C_i \right) \\
-& = \OO_{C_j}\left( \sum_{x_i \in C_j} \alpha_i x_i + \sum_{q_i \in C_j} \left(\frac{\gamma_i - \gamma_j}{r_i}\right) q_i - \sum_{\tilde{q}_i \in C_j} m_i \tilde{q}_i \right)\end{align*}
-where the middle sum is over adjacent internal components and the final sum is over adjacent external components. The fact that $\gamma_j/r_i = m_i$ follows as in the previous case.
-
-We must argue that $\Lcal|_{C_j} = L|_{C_j}$. Suppose for the moment that $C_j$ is genus zero, so that we only need to check the degrees. We must show:
-\begin{equation*} \deg L|_{C_j} = \sum_{x_i \in C_j} \alpha_i - \sum_{q_i \in C_j} \left( \dfrac{\gamma_j - \gamma_i}{r_i}\right) - \sum_{\tilde{q}_i \in C_j} u_{\tilde{q}_i}\end{equation*}
-But by the definition of $Q^{\operatorname{GS}}$ we have:
-\begin{equation*} (\gamma_j - \gamma_i)/r_i = u_{q_i} \end{equation*}
-From which the above formula holds because of the tropical balancing condition we imposed when choosing the type.
-
-Similarly if $C_j$ is smooth of genus one we must show:
-\begin{equation*} L|_{C_j} = \OO_{C_j} \left( \sum_{x_i \in C_j} \alpha_i x_i - \sum_{q_i \in C_j} u_{q_i} q_i - \sum_{\tilde{q}_i \in C_j} u_{\tilde{q}_i} \tilde{q}_i \right) \end{equation*}
-But this is just the balancing condition on the level of $\Pic(C_j)$.
-
-What about if $C_j$ is a wheel of rational components?
-Then it isn't irreducible, so let's write it as $Z= C_1 \cup \ldots \cup C_k$.
-So there are other internal components $C_{k+1},\ldots,C_r$ and external components $C_{r+1},\ldots,C_m$.
-We assume that $C_1,\ldots,C_k$ are ordered so that $C_i$ intersects $C_{i-1}$, $C_{i+1}$ and none others.
-Notice that this means that:
-\begin{equation*} C_i^2 = -1/r_{i-1} - 1/r_{i+1} - \sum_{q_j \in C_i} 1/r_j \end{equation*}
-for all $i \in \{1,\ldots,k\}$, where the sum is over all nodes $q_j$ which connect $Z$ to the rest of the curve. Thus we obtain:
-\begin{align*} \Lcal|_Z & = \OO_Z \left( \sum_{x_i \in Z} \alpha_i x_i\right) \otimes \OO_{\Ccal} \left( \sum_{i=1}^r \gamma_i C_i \right)\bigg|_Z \\
-& = \OO_Z \left( \sum_{x_i \in Z} \alpha_i x_i + \sum_{\substack{q_i \in Z \\ \text{$q_i$ joins $Z$} \\ \text{to int.
-cpt.}}} (\gamma_i/r_i) q_i \right) \otimes \OO_{\Ccal} \left( \sum_{i=1}^k \gamma_i C_i \right) \bigg|_Z \\
-& = \OO_Z \left( \sum_{x_i \in Z} \alpha_i x_i + \sum_{\substack{q_i \in Z \\ \text{$q_i$ joins $Z$} \\ \text{to int.
-cpt.}}} (\gamma_i/r_i) q_i + \sum_{i=1}^k \gamma_i \left( \frac{1}{r_{i,i-1}} q_{i-1} + \frac{1}{r_{i,i+1}} q_{i+1} + (C_i^2) s_i \right)\right)
-\end{align*}
-where $q_{i-1}$ is the node connecting $C_{i-1}$ and $C_i$ (and similarly for $q_{i+1}$) and $s_i$ is some point of $C_i$ (doesn't really matter which, since $C_i$ is rational).
-
-Using the description of $C_i^2$ given above, we see that the terms $q_{i-1}/r_{i,i-1}$ and $q_{i+1}/r_{i,i+1}$ cancel, and we are left with
-\begin{align*} \Lcal|_Z & = \OO_Z \left( \sum_{x_i \in Z} \alpha_i x_i + \sum_{\substack{q_i \in Z \\ \text{$q_i$ joins $Z$} \\ \text{to int.
-cpt.}}} (\gamma_i/r_i) q_i + \sum_{\substack{q_i \in Z \\ \text{$q_i$ joins $Z$} \\ \text{to rest of curve}}} (\gamma_i/r_i) q_i \right) \\
-& = \OO_Z \left( \sum_{x_i \in Z} \alpha_i x_i + \sum_{\substack{q_i \in Z \\ \text{$q_i$ joins $Z$} \\ \text{to int.
-cpt.}}} \left( \dfrac{\gamma_i-\gamma_j}{r_i} \right) q_i - \sum_{\substack{q_i \in Z \\ \text{$q_i$ joins $Z$} \\ \text{to ext.
-cpt}}} (\gamma_i/r_i) q_i \right)
-\end{align*}
-and this is precisely the balancing condition on the level of $\Pic(Z)$.
-This proves that $\Lcal|_C = L$, except for one case which we haven't yet considered, namely when there is a wheel of rational curves which is partially internal and partially external.
-In this case essentially the same argument as given above applies.
-
-We have thus shown that we can break $C$ up into pieces (mostly into its irreducible components, unless there is a rational wheel in which case we treat this as a single piece) such that the corresponding intersection graph has genus zero and such that $\Lcal$ restricts to $L$ on each of the pieces.
-The fact that $\Lcal|_C = L$ then immediately follows (since the intersection graph has genus zero, so the Picard group of $C$ is equal to the direct sum of the Picard groups of the pieces).
-This completes the proof of step (3).
-
-As mentioned above, step (4) is immediate by the construction of $\Lcal$.
-It remains to carry out step (5), i.e.
-to extend the sections $u_1,\ldots,u_N$.
-By standard results in deformation theory, obstructions to extending sections of a deformation of $L$ are contained in $\HH^1(C,L)$.
-If $L$ is non-trivial on the circuit, then this space vanishes and so the sections extend immediately.
-
-Thus the only case we need to check is when $L$ is trivial on the circuit, which means that the circuit $E$ (again, either a smooth elliptic curve or a wheel of rational components) is contracted by the map $f$.
-In this case we want to extend the sections by referring to the corresponding Smyth curve.
-From the centrally aligned curve $\Ccal$ we obtain a diagram:
-\bcd
-& \tilde{\Ccal} \ar[ld] \ar[rd] & \\
-\Ccal & & \overline{\Ccal}
-\ecd
-\basenote{Finish this}
-
-We have thus constructed the smoothing, which shows that conditions (1) and (2) above are sufficient to characterise points in the closure of the nice locus.
-
-We will now show that these conditions are necessary.
-Suppose therefore that there is a family $\Ccal \to \formLine$ and consider the central fibre $\Ccal_0 = C$.
-Condition (1) for $C$ follows immediately from continuity of intersection products.
-
-To show condition (2), let $u_0 = f^*(z_0) \in \HH^0(\Ccal,f^* \OO_{\PP^N}(H))$.
-For each component $C_i$ of the central fibre $C$, let $\gamma_i$ be the vanishing order of $u_0$ along the Weil divisor $C_i$.
-For each internal component of $C$ this defines a non-zero map $\gamma_i \colon \N \to \N$.
-On the other hand, for each node $q$ consider the corresponding generator $e_q \in Q^{\operatorname{ctr}}$.
-A chart for the log structure on the base is given by a map
-\begin{equation*} Q^{\operatorname{ctr}} \to \mathbbm{k} \llbracket t \rrbracket \end{equation*}
-which we can compose with the valuation on $\mathbbm{k} \llbracket t \rrbracket$ to get a map:
-\begin{equation*} Q^{\operatorname{ctr}} \to \N \end{equation*}
-Let $r_q$ be the image of $e_q$ along this map.
-This is always non-zero because every node is smoothed in the family $\Ccal$; thus we have a non-zero map $r_q \colon \N \to \N$.
-These, together with the $\gamma_i$ defined above, give a local morphism
-\begin{equation*} \prod_{q \in C} \N_q \times \prod_{C_i} \N_{\eta_i} \to \N \end{equation*}
-where the second product is over the internal components of $C$.
-We claim that this descends to the quotient $Q^{\operatorname{GS}}$ (recall again that this quotient depends on a choice of type).
-We have to check that for every node $q$ we have
-\begin{equation*} u_q r_q = \gamma_i - \gamma_j \end{equation*}
-where $C_i$ and $C_j$ are the adjacent components (this makes for all nodes, since $\gamma_i=0$ for any external component).
-Remember that the $u_q$ are not fixed a priori; thus we can think of the above formula as determining the $u_q$.
-What we then need to check is that the $u_q$ thus defined are all integers, and that they satisfy the tropical balancing condition on the level of $\Pic (C)$.
-
-Consider the dual graph of $C$, treating the circuit $E$ as a single node of this graph, so that the graph has genus zero.
-Start from a leaf $C_i$ of this graph, so that there is only one node $q$ of the corresponding component.
-Let $C_j$ be the unique component of $C$ which is adjacent to $C_i$ (via $q$).
-Then we have:
-\begin{equation*} \deg f|_{C_i} = \deg \Lcal|_{C_i} = (\gamma_i - \gamma_j)/r_q + \sum_{x_k \in C_i} \alpha_k \end{equation*}
-Rearranging, we see that $(\gamma_i - \gamma_i)/r_q$ is an integer.
-Substiting in $u_q$ for this value, we obtain precisely the balancing condition, which we can view as happening on the level of $\Pic (C_j)$ (if we refrain from taking the degree first).
-
-We now proceed by induction.
-The process is as follows: having determined $q$, we pass to the next component $C_j$.
-If this has only one other node $r$ besides $q$, we apply the same argument as before to show that $u_r$ is an integer and satisfies the balancing condition.
-If it contains more than one other node, we pick one of them and follow the resulting path through the dual graph until we arrive at a leaf with a single undetermined node (which must exist, since otherwise the node we started with would have been determined).
-We then start the process again from there.
-
-This procedure proves that all the $u_q$ are integers and that the balancing condition is satisfied on every component, except for those nodes and those components belonging to the circuit $E$.
-If the circuit is smooth there is nothing additional to prove, except to note that the Gathmann-like condition (1) ensures that the balancing condition will be satisfied on the level of $\Pic(E)$ (rather than just on the level of degree), so that it is satisfied for $\Pic(C)$.
-
-It remains to consider the case when $E$ is a wheel of rational components.
-Again the Gathmann-like condition (1) ensures we have balancing on the level of $\Pic(E)$, once we show that all the $u_q$ for the nodes internal to $E$ are integers.
-Labelling the components of $E$ as $C_1,\ldots,C_k$ with $C_i$ intersecting $C_{i-1}$ and $C_{i+1}$, we obtain relations:
-\begin{equation*} u_{q_i} r_{q_i} = \gamma_{i+1} - \gamma_{i-1} \end{equation*}
-Thus $u_{q_i} \in r_{q_i}^{-1} \cdot \Z$.
-But if we restrict $\Lcal$ to each component and look at the resulting equation, we see that in fact $u_{q_i} \in (1/r_{q_j}) \Z$ for all $j$.
-Thus $u_{q_i} \in (1/g) \Z$ where $g = \operatorname{gcd}(r_{q_1},\ldots,r_{q_k})$.
-\basenote{Maybe we can fix this using saturation: note that we only need a map from the saturation of the quotient to $\N$, not from the quotient itself.}
-
-\end{proof}
-\newpage
-
-\section{Recursion formula for $\PP^1|\infty, \Sigma \alpha = d$}
-=======
 \section{Recursion formula}
@@
  \end{itemize}
+
 \end{proof}
 
-\newpage
 \appendix
@@
 
-\subsection{The relative space is the closure of the nice locus for $(\PP^N,H)$}
+\section{The relative space is the closure of the nice locus for $(\PP^N,H)$}
 \noindent In general we do not know very much about the space we have just defined.

### 2018-04-29 genus-one-relative-maps.tex

--- 2018-03-24 genus-one-relative-maps.tex
@@
 \newcommand{\VZc}[4]{\mathcal{V\!Z}^{\rm{ctr}}_{#1,#2}(#3,#4)}
+\newcommand{\VZclb}[4]{\mathcal{V\!Z}^{\rm{ctr,lb}}_{#1,#2}(#3,#4)}
 \newcommand{\VZco}[4]{\mathcal{V\!Z}^{\rm{ctr},\circ}_{#1,#2}(#3,#4)}
@@
 
-We now define the \emph{centrally alined relative space} to be the closure of the nice locus:
+We now define the \emph{centrally aligned relative space} to be the closure of the nice locus:
 \begin{equation*} \VZc{1}{\alpha}{\PP^N|H}{d} := \overline{\VZco{1}{\alpha}{\PP^N|H}{d}} \subseteq \VZc{1}{n}{\PP^N}{d} \end{equation*}
@@
 Hence it admits a fundamental class, which we can use to define \emph{reduced relative Gromov--Witten invariants}:
-\begin{equation*} \langle \tau_{k_1}(\gamma_1), \ldots, \tau_{k_n}(\gamma_n) \rangle^{\PP^N|H, \operatorname{red}}_{0,\alpha,d} := \int_{[\VZc{1}{\alpha}{\PP^N|H}{d}]} \prod_{i=1}^n \ev_i^*(\gamma_i) \psi_i^{k_i} \end{equation*}
+\begin{equation*} \langle \tau_{k_1}(\gamma_1), \ldots, \tau_{k_n}(\gamma_n) \rangle^{\PP^N|H, \operatorname{red}}_{0,\alpha,d} := \int_{[\VZc{1}{\alpha}{\PP^N|H}{d}]} \prod_{i=1}^n \ev_i^*(\gamma_i) \cdot \psi_i^{k_i} \end{equation*}
 
@@
 
-\section{Recursion formula for $\PP^1|\infty, \Sigma \alpha = d$}
-=======
+\section{Recursion formula for $\PP^1|\infty$, $\Sigma \alpha = d$.}
+As in the genus zero case, we construct a line bundle (a quotient of jet bundles) and a section of that line bundle whose vanishing locus equals a union of boundary components (comb loci).
+(The moduli space for $\alpha+e_k$ does not appear because we are assuming maximal tangency.) These fit into the following families:
+\subsection{$\mathcal{Y}^a$}
+The first family is where the circuit is external:
+\begin{equation*} \mathcal{Y}^a=\oM_{0,\lvert\alpha^{(0)}\rvert+r} \times\left(\VZc{1}{\alpha^{(1)}\cup\{m^{(1)}\}}{\PP^1|\infty}{d_1}\times_H {\prod_{i=2}^r} {}_H \M{0}{\alpha^{(i)}\cup\{m^{(i)}\}}{\PP^1|\infty}{d_i}\right) \end{equation*}
+
+\subsection{$\mathcal{Y}^b$}
+The second family is where the circuit is partly internal, partly external (and hence is a wheel of rational curves).
+\begin{equation*} \mathcal Y^b=\oM_{0,\lvert\alpha^{(0)}\rvert+r}\times \left(\M{0}{\alpha^{(1)}\cup\{m^{(1)},m^{(2)}\}}{\PP^1|\infty}{d_1}\times_H \prod_{i=3}^r {}_H \M{0}{\alpha^{(i)}\cup\{m^{(i)}\}}{\PP^1|\infty}{d_i}\right)\end{equation*}
+
+\subsection{$\mathcal{Y}^c$}
+The third family is where the circuit is internal (and thus has zero degree, since we are working with $\PP^1$ relative $\infty$).
+\begin{equation*} \mathcal Y^c = \oM^{\operatorname{ctr,lb}}_{1,\lvert\alpha^{(0)}\rvert+r} \times \prod_{i=1}^r {}_H \M{0}{\alpha^{(i)}\cup\{m^{(i)}\}}{\PP^1|\infty}{d_i} \end{equation*}
+In the above, the first factor
+\begin{equation*} \oM^{\operatorname{ctr,lb}}_{1,\lvert\alpha^{(0)}\rvert+r} \subseteq \oM^{\operatorname{ctr}}_{1,\lvert\alpha^{(0)}\rvert+r}  \end{equation*}
+consists of those centrally aligned curves satisfying Gathmann's condition in $\Achow_0(C)$:
+\begin{equation*} \sum_{x_j\in C}\alpha_jx_j-\sum_{i=1}^r m^{(i)}y_i= 0 \in \Achow_0(C)\end{equation*}
+We saw before how to express this as a condition in $\Pic(E)$ where $E \subseteq C$ is the circuit.
+Notice that the condition above epends on the choice of $m^{(i)}$ but is really just a condition on the first factor of the product, so $\mathcal Y^c$ itself can be expressed as a product.
+\sidenote{Express the line bundle condition in terms of tautological classes?}
+
+In this third case there is also a degeneracy condition that must be imposed on the second factor, which ensures that the map factors through the Smyth curve.
+To be more precise, the condition is that the derivatives
+\begin{equation*} (\operatorname{d}\!f)|_{q_i} \in \operatorname{T}|_{\PP^1} \qquad i=1,\ldots,r \end{equation*}
+are linearly dependent. Note that if $m_i > 1$ for any $i$, or if $r \geq 2$, then this is automatically satisfied. Thus the only case in which we have to impose this is for
+\begin{equation*} \mathcal{Y}^c = \oM^{\operatorname{ctr,lb}}_{1,|\alpha^{(0)}|+r} \times {\M{0}{\alpha^{(i)}\cup (1}{\PP^1|\infty}{d}}^{\operatorname{degen}} \end{equation*}
+where ``degen'' indicates that we impose degeneracy.
+
+These spaces are all irreducible of the expected dimension, and it can be checked that they define divisors inside:
+\begin{equation*} \VZc{1}{\alpha}{\PP^1|\infty}{d} \end{equation*}
+In fact, this applies to all of the above spaces \emph{except} for the special case mentioned above (where we impose degeneracy).
+This has too small dimension, and hence will not appear in the recursion formula.
+
 \section{Recursion formula}
@@
  \end{itemize}
+
 \end{proof}
@@
 \[ \operatorname{Vb}\left(\pi_*\OO_{\mathcal E}(\sum_{j=n+1}^{n+\delta}\sigma_j)\oplus\pi_*\OO_{\mathcal E}(\sum_{j=1}^{n+\delta}\sigma_j)^{\oplus r}\right) \quad \text{on} \quad \mathcal{M}_{1,n+\delta}\]
-where $\pi\colon\mathcal E\to\mathcal M$ is the universal curve and $\delta=d-\sum\alpha_i$.
+where $\pi\colon\mathcal E\to\mathcal M$ is the universal curve and $\delta=d-\sum\alpha_i$. Notice that this is a vector bundle because the source curve is smooth of genus one.
 \end{proof}

### 2018-05-09 genus-one-relative-maps.tex
chen-kim

--- 2018-04-29 genus-one-relative-maps.tex
@@
 \usepackage[utf8x]{inputenc}
+
+\usepackage{calrsfs}
+\DeclareMathAlphabet{\pazocal}{OMS}{zplm}{m}{n}
+
 \usepackage{verbatim}
@@
 
+\newcommand{\pM}{\pazocal{M}}
 \newcommand{\TT}{\operatorname{T}}
@@
 \newcommand{\RR}{\textbf{R}}
-\newcommand{\NN}{\operatorname{N}}
+\newcommand{\NN}{\mathbb{N}}
 \newcommand{\ovm}[1]{\overline{\mathcal{#1}}}
@@
 
+\section{A desingularisation of Chen-Kim's moduli space of genus one logarithmic maps to expanded pairs, for $(\PP^N|H)$}
+
+We recall a number of definitions from \cite{ChenDegeneration}; see also \cite{KimLog}.
+
+Fix a smooth pair $(X,Y)$, i.e. a smooth projective variety $X$ with a smooth divisor $Y$.
+
+\begin{definition}
+ An \emph{extended log twisted expansion} of $(X,Y)$ is a quadruple $(\pi_S\colon W\to S, \pi_X\colon W\to X, D\subseteq W, \pM_S^{W/S}\to\pM_S)$ such that:
+ \begin{enumerate}
+  \item $W$ is an $S$-algebraic space, $\pi_S$ is a proper and flat morphism, with fibers at worst nodal in codimension 1, admitting a lifting to a special log morphism $\pi\colon (W,\pM_W^{W/S})\to(S,\pM_S^{W/S})$, such that:
+  \begin{enumerate}
+   \item $\pM_W^{W/S}$ and $\pM_S^{W/S}$ are locally free log structures;
+   \item for every geometric point $\bar{w}\to W$, either $\bar{w}$ is in the smooth locus of $\pi_S$ and $\pi^\flat\colon \pi^*\overline{\pM}_{S,\bar{w}}^{W/S}\to \overline{\pM}_{W,\bar{w}}^{W/S}$ is an isomorphism, or $\bar{w}$ is in the nodal locus and the following diagram is cocartesian:
+   \bcd
+   \NN\ar[r,"{(1,1)}"]\ar[d,"h"] & \NN^2\ar[d] \\
+   \pi^*\overline{\pM}_{S,\bar{w}}^{W/S}\ar[r] & \overline{\pM}_{W,\bar{w}}^{W/S}
+   \ecd
+   with $h(e)$ irreducible;
+   \item for every geometric point $\bar{s}\to S$ there is a bijection between the irreducible elements of $\overline{\pM}_{S,\bar{s}}^{W/S}$ and the irreducible components of $W_{\bar{s}}^{\text{sing}}$.
+  \end{enumerate}
+  \item $D\subseteq W$ is a Cartier divisor, smooth over $S$, and such that $\pi_X(D)=Y$;
+ \item $\pM_S$ is twisted by integers $(r_1,\ldots,r_l)$ and expanded with respect to $\pM_S^{W/S}$, namely \'{e}tale locally at every point $s\in S$ the morphism of log structures $\pM_S^{W/S}\to\pM_S$ admits a chart:
+ \bcd
+ \NN^l\ar[d]\ar[r,"{(r_1,\cdots,r_l)}"] &\NN^l\ar[r,"{(id,0)}"]&\NN^l\oplus\NN^k\ar[d] \\
+ \pM_S^{W/S}\ar[rr] & & \pM_S
+ \ecd
+
+ \end{enumerate}
+
+ The log structure on $W$ is given by
+\end{definition}
+
+\section{Gathmann's recursive structure on the boundary of maps to expanded pairs}
+
 \section{The space of relative centrally aligned maps}
@@
   \begin{remark}
-   When we are studying the infinitesimal deformation theory of centrally aligned curves, notice that being centrally aligned must be checked on geometric points, and minimality is open, hence any first-order deformation as a log smooth curve will automatically be minimal centrally aligned.
+   When we are studying the infinitesimal deformation theory of centrally aligned curves, notice that being centrally aligned must be checked on geometric points, and minimality is open, hence any deformation as a log smooth curve will automatically be minimal centrally aligned.
 The tangent space is then $H^1(C,T_C^{\rm{log}})$; notice that this is independent from the log structure on the base.

### 2018-05-10 genus-one-relative-maps.tex
stable log map def

@@
 \begin{definition}
- An \emph{extended log twisted expansion} of $(X,Y)$ is a quadruple $(\pi_S\colon W\to S, \pi_X\colon W\to X, D\subseteq W, \pM_S^{W/S}\to\pM_S)$ such that:
+ An \emph{extended log twisted expansion} of $(X,Y)$ is a quadruple $(\pi\colon W\to S, \pi_X\colon W\to X, D\subseteq W, \pM_S^{W/S}\to\pM_S)$ such that:
  \begin{enumerate}
-  \item $W$ is an $S$-algebraic space, $\pi_S$ is a proper and flat morphism, with fibers at worst nodal in codimension 1, admitting a lifting to a special log morphism $\pi\colon (W,\pM_W^{W/S})\to(S,\pM_S^{W/S})$, such that:
+  \item $\pi$ makes $W$ into a flat, proper algebraic space over $S$, with fibers at worst nodal in codimension 1, admitting a lifting to a special log morphism $\pi\colon (W,\pM_W^{W/S})\to(S,\pM_S^{W/S})$, such that:
   \begin{enumerate}
@@
  \end{enumerate}
-
- The log structure on $W$ is given by
+\end{definition}
+ The log structure on $W$ is then given by
+ \[ \pM_W=\pi^*\pM_S\oplus_{\pi^*\pM_S^{W/S}}\pM_W^{W/S}\oplus_{\OO^*_W}\pM^D\]
+ where $\pM_D$ is the divisorial log structure associated to $D$. 
+Notice that with this definition $(W,\pM_W)\to(S,\pM_S)$ is log smooth.
+
+Similarly a \emph{log twisted curve} is $((C,p_1,\ldots,p_n)\to S, \pM_S^{C/S}\to\pM_S)$ with
+\[\pM_C=\pi^*\pM_S\oplus_{\pi^*\pM_S^{C/S}}\pM_C^{C/S}\oplus_{\OO^*_C}\bigoplus_{i=1}^n\pM^{p_i}\]
+A log twisted curve is \emph{minimal} if the log structure $\pM_S$ is locally free, and for every geometric point $\bar{s}\to S$ and irreducible element $b\in\overline{\pM}_S$, we can find an irreducible $a\in\overline{\pM}^{C/S}_S$ and a positive integer $l$ such that $a\mapsto lb$ (by definition this means that the morphism of log structures $\pM_S^{C/S}\to\pM_S$ is \emph{simple}).
+So essentially we are allowed to take roots of the smoothing parameters of the nodes of $C_{\bar{s}}$.
+
+Finally, fix an $n$-tuple of non-negative contact orders $(c_1,\ldots,c_n)$.
+\begin{definition}
+ A \emph{relative log prestable map} with tangency condition $\mathbf{c}$ is given by a diagram of log morphisms:
+ \bcd
+ ((C,\mathbf p),\pM_C)\ar[rr,"f"]\ar[dr] & & ((W,D),\pM_W)\ar[rr,"\pi_X"]\ar[dl] & & (X,Y)\times S \\
+  & (S,\pM_S) & & &
+ \ecd
+ \begin{enumerate}
+  \item $(C,\mathbf p),\pM_C)\to (S,\pM_S)$ is a minimal log twisted curve;
+  \item $((W,\pM_W)\to (S,\pM_S),(W,D)\to(X,Y))$ is an extended twisted log expansion of $(X,Y)$;
+  \item (\emph{corank condition}) \sidenote{split the definition into a more general one over LogSch and minimality?} for every geometric point $\bar{s}\in S$, the rank of \[\operatorname{Coker}(\pM^{W/S}_{S,\bar{s}}\to \pM_{S,\bar{s}})\] is equal to the number of non-distinguished nodes of $C_{\bar{s}}$; recall that a node of $C_{\bar{s}}$ is \emph{distinguished} if it is mapped under $f$ to the singular locus of $W_{\bar{s}}$.
+  \item (\emph{log admissibility}) the morphism of log structures $f^\flat\colon f^*\pM_W\to\pM_C$ is simple at every distinguished node;
+  \item (\emph{tangency condition}) the underlying map $\underline{f}\colon C\to (W,D)$ is non-degenerate, namely no component of $C$ is mapped entirely into $D$, and locally around every marking $p_i$ we can find a chart
+  \bcd
+  \NN\ar[r,"\cdot c_i"]\ar[d] & \NN\ar[d] \\
+  f^*\pM^D\ar[r] & \pM^{p_i}
+  \ecd
+  for the restriction of $f^\flat$ to the $f^*\pM^D$ factor.
+  \end{enumerate}
+\end{definition}
+\begin{definition}
+ A relative log prestable map as above is \emph{stable} if for every geometric point $\bar{s}\in S$ the group of automorphisms $(\sigma,\tau)$ is finite, where:
+ \begin{enumerate}
+  \item $\sigma$ is an automorphism of $((C,\pM_C)\to (S,\pM_S))_{\bar{s}}$ preserving the markings $\mathbf p$;
+  \item $\tau$ is an automorphism of $((W,\pM_W)\to (S,\pM_S))_{\bar{s}}$ preserving $D$ and $\pi_X\colon W_{\bar{s}}\to X$;
+  \item $\tau\circ f_{\bar{s}}=f_{\bar{s}}\circ \sigma$.
+ \end{enumerate}
+\begin{remark}
+ The corank and simplicity condition imply the following: the rank of the locally free log structure $\pM_S$ at $\bar{s}$ amounts to the number of irreducible components of $W_{\bar{s}}^{\text{sing}}$ plus the number of non-distinguished nodes of $C_{\bar{s}}$; all the smoothing parameters of the distinguished nodes mapping to the same component of $W_{\bar{s}}^{\text{sing}}$ have been identified \emph{up to twisting}.
+In facts, at a distinguished node $q$ of $C$, letting $R$ be the local ring of $S$ at $\pi(q)$, we can find \'{e}tale local charts
+ \bcd
+ \NN^2\oplus_{\NN} \pM_{S}\ar[r,"{(id,\cdot m_q)}"]\ar[d] & \NN^2\oplus_{\NN} \pM_{S}\ar[d] \\
+ f^*\pM_W \ar[r,"f^\flat"]\ar[d] & \pM_C\ar[d] \\
+ R[z_1,\ldots,z_{\dim(X)-1},x,y]/xy-t\ar[r,"\left(\substack{x\mapsto a^{m_q}\\ y\mapsto b^{m_q}\\ t\mapsto s^{m_q}}\right)" below=.2cm] & R[a,b]/ab-s
+ \ecd
+ where the twist at $f(q)$ is given by $l$, that at $q$ is given by $r_q$, and the equality $l=r_qm_q$ has to hold.
+\end{remark}
+
 \end{definition}

### 2018-05-10 genus-one-relative-maps.tex
finished chen-kim review

@@
 
-We recall a number of definitions from \cite{ChenDegeneration}; see also \cite{KimLog}.
+\subsection{Relative logarithmic maps to expanded pairs} We recall a number of definitions from \cite{ChenDegeneration}; see also \cite{KimLog}.
 
@@
  \end{enumerate}
+\end{definition}
 \begin{remark}
@@
  \bcd
- \NN^2\oplus_{\NN} \pM_{S}\ar[r,"{(id,\cdot m_q)}"]\ar[d] & \NN^2\oplus_{\NN} \pM_{S}\ar[d] \\
- f^*\pM_W \ar[r,"f^\flat"]\ar[d] & \pM_C\ar[d] \\
- R[z_1,\ldots,z_{\dim(X)-1},x,y]/xy-t\ar[r,"\left(\substack{x\mapsto a^{m_q}\\ y\mapsto b^{m_q}\\ t\mapsto s^{m_q}}\right)" below=.2cm] & R[a,b]/ab-s
- \ecd
- where the twist at $f(q)$ is given by $l$, that at $q$ is given by $r_q$, and the equality $l=r_qm_q$ has to hold.
+ \NN^2\oplus_{\NN} \pM_{S}\ar[r,"{(id,\cdot m_q)}" below]\ar[d] & \NN^2\oplus_{\NN} \pM_{S}\ar[d] \\
+ f^*\pM_W \ar[r,"f^\flat" below]\ar[d] & \pM_C\ar[d] \\
+ R[z_1,\ldots,z_{\dim(X)-1},x,y]/(xy-t)\ar[r,"\left(\substack{x\mapsto a^{m_q}\\ y\mapsto b^{m_q}\\ t\mapsto s^{m_q}}\right)" below=.2cm] & R[a,b]/(ab-s)
+ \ecd
+ where the twist at $f(q)$ is given by $l$, the one at $q$ is given by $r_q$, and the equality $l=r_qm_q$ has to hold.
 \end{remark}
 
-\end{definition}
+\subsection{The desingularisation via central alignments} The following is a variation on \cite[\S 3.3]{RSPW2}.
 

### 2018-11-13 genus-one-relative-maps.tex
a new plan of conquest

@@
 \newcommand{\VZcLi}[4]{\mathcal{V\!Z}^{\rm{ctr, Li}}_{#1,#2}(#3,#4)}
+\newcommand{\VZrel}[4]{\mathcal{V\!Z}^{\rm{rel}}_{#1,#2}(#3,#4)}
+\newcommand{\stab}{\rm{stab}}
+\newcommand{\stC}{C'}
+\newcommand{\stf}{f'}
+\newcommand{\stpi}{\pi'}
+\newcommand{\sts}{s'}
 \newcommand{\N}{\mathbb{N}}
@@
 
+We find a natural line bundle with a section whose vanishing locus consists of those maps where the target splits and the marking $p_k$ is mapped to a higher level of the accordion.
+We express these boundary strata recursively as fibered products of desingularised relative and rubber spaces with lower numerical invariants; the multiplicity calcultion is performed for $\PP^1|\{\infty\}$ and rests on work of Vakil \cite{Vre}.
+Putting everything together we reobtain Gathmann's algorithm for computing relative invariants, or the invariants of a smooth hyperplane section.
+
+\subsection{The line bundle and section}
+On $\VZrel{1}{\alpha}{X}{\beta}$, as on any space of maps to an expansion really, there is not only a universal curve $C$ with universal map $f$ to the expansion $W$, but also the stabilisation of the collapsed map obtained by composing $f$ with $\pi_X\colon W\to X$:
+\bcd
+C\ar[r,"f"]\ar[d,"\stab"] & W \ar[d,"\pi_X"] \\
+\stC\ar[r,"\stf"] & X
+\ecd
+Notice that the image of the marking $p_k$ on $\stC$ has either contact order $\alpha_k$ to $Y$, or it lies on an internal component.
+The section $s\in\Gamma(X,\OO_X(Y))$ whose vanishing locus defines $Y$, induces a section $\sts$ of $\stpi_*\stf^*\OO_X(Y)$.
+By the previous discussion, the image of $\sts$ in $\ev_k^*\mathcal P^{\alpha_k}\OO_X(Y)$ vanishes, hence by the principal parts exact sequence
+\[ 0\to p_k^*\Omega_{\stC}^{\otimes\alpha_k+1}\otimes\ev_k^*\OO_X(Y)\to \ev_k^*\mathcal P^{\alpha_k+1}\OO_X(Y)\to \ev_k^*\mathcal P^{\alpha_k}\OO_X(Y)\to 0\]
+we obtain a section $\sts_k$ of the line bundle $p_k^*\Omega_{\stC}^{\otimes\alpha_k+1}\otimes\ev_k^*\OO_X(Y)$.
+
+It is apparent that, set-theoretically at least, the vanishing locus of $\sts_k$ consists of those maps such that $p_k$ lies on an internal component of $\stC$, or, equivalently, it is mapped to higher level in the expansion and lies not on a ``trivial bubble'' in $C$.
+
+\subsection{Boundary loci}
+We follow in Vakil's footsteps in setting the following notation:
+\begin{enumerate}[label=(\alph*)]
+ \item \[\mathcal Y^a=\M{0}{\lvert\alpha^{(0)}\rvert+r}{H}{d_0}\times_{H^r}\left(\VZc{1}{\alpha^{(1)}\cup\{m^{(1)}\}}{\PP^N|H}{d_1}\times\prod_{i=2}^r\M{0}{\alpha^{(i)}\cup\{m^{(i)}\}}{\PP^N|H}{d_i}\right)\]
+ \item \[\mathcal Y^b=\M{0}{\lvert\alpha^{(0)}\rvert+r}{H}{d_0}\times_{H^r}\left(\M{0}{\alpha^{(1)}\cup\{m^{(1)},m^{(2)}\}}{\PP^N|H}{d_1}\times\prod_{i=3}^r\M{0}{\alpha^{(i)}\cup\{m^{(i)}\}}{\PP^N|H}{d_i}\right)\]
+ \item \[\mathcal Y^c\subseteq \VZc{1}{\lvert\alpha^{(0)}\rvert+r}{H}{d_0}\times_{H^r}\prod_{i=1}^r\M{0}{\alpha^{(i)}\cup\{m^{(i)}\}}{\PP^N|H}{d_i}\]
+ $\mathcal Y^c$ is cut within the latter by Gathmann's condition on line bundles:
+ \[f_{|E}^*\mathcal O_H(1)\cong\mathcal O_E\left(\sum_{x_j\in E}\alpha_jx_j-\sum_{i=1}^r m^{(i)}y_i\right)\]\sidenote{Express the line bundle condition in terms of tautological classes?}
+ Notice that such condition depends on the choice of $m^{(i)}$ but is really just a condition on the first factor of the product, so $\mathcal Y^c$ itself can be expressed as a product.
+\end{enumerate}
+
 \section{The space of relative centrally aligned maps}

### 2018-11-13 new.tex
a new plan of conquest

--- 2018-11-13 genus-one-relative-maps.tex
@@
 \newcommand{\Z}{\mathbb{Z}}
+\newcommand{\VZ}{\pazocal{V\!Z}}
 \newcommand{\tVZc}[4]{\widetilde{\mathcal{V\!Z}}^{\rm{ctr}}_{#1,#2}(#3,#4)}
@@
 
-\section{A desingularisation of Chen-Kim's moduli space of genus one logarithmic maps to expanded pairs, for $(\PP^N|H)$}
+\section{Introduction}
 
-\subsection{Relative logarithmic maps to expanded pairs} We recall a number of definitions from \cite{ChenDegeneration}; see also \cite{KimLog}.
+\textbf{Statement of the problem.} Contrary to the genus zero case, the moduli space of genus one maps to projective space - with or without markings - is far from smooth; indeed it has various boundary components of different dimensions, representing maps that contract a genus one curve and have all the degree supported on a number of rational tails.
+The many incarnations of relative moduli spaces also suffer of the same undesirable feature.
 
-Fix a smooth pair $(X,Y)$, i.e. a smooth projective variety $X$ with a smooth divisor $Y$.
+Since the work of Vakil--Zinger and Ranganathan--Santos-Parker--Wise, it has been clear that it is possible to identify a desingularisation of the main component by adding the extra data of a contraction of the source curve $\nu\colon C\to \bar{C}$ - where the latter is allowed to acquire a Smyth singularity - and requiring the stable map $f\colon C\to \PP^N$ to factor through $\nu$.
 
-\begin{definition}
- An \emph{extended log twisted expansion} of $(X,Y)$ is a quadruple $(\pi\colon W\to S, \pi_X\colon W\to X, D\subseteq W, \pM_S^{W/S}\to\pM_S)$ such that:
+\textbf{Choice of relative space and desingularisation.} We focus on the space of logarithmic stable maps to $(\PP^N|H)$, following ACGS.
+We perform a log modification of this space as detailed below.
+For a log curve $C\to S=\Spec(k=\bar k)$, modify the dual graph of $C$ by replacing the minimal genus one subcurve (in case it is a circle of $\PP^1$) by a single vertex of genus one, called the \emph{core} and denoted by $\circ$, and define a piecewise linear function with values in $\overline{\pazocal M}_S$ on such a graph by setting \[\lambda(v)=\sum_{q\in[\circ,v]}\rho_q,\]
+where the $\rho_q$ are the smoothing parameters of the nodes $q$ separating $v$ from the core.
+Such a function is related to the log canonical bundle of $C\to S$.
+When the map contracts a subcurve of genus one, we endow it with the extra data of a radius $\delta\in\overline{\pazocal M}_S$ subject to the following compatibility condition:
+
+(*) \emph{the circle of radius $\delta$ around $\circ$ passes through $\geq1$ vertex of positive $f$-degree}.
+
+\noindent Furthermore, we require all the values of $\lambda$ to be comparable with $\delta$, and among themselves whenever they are $\leq \delta$.
+This is called a \emph{centrally aligned} log structure and carries enough information to define a contraction $\nu\colon C\to \bar{C}$, possibly after a semistabilisation of $(C,f)$ - in fact even more.
+The space thus obtained, $\widetilde \VZ_{1,\alpha}(\PP^N|H,d)$, is a log modification of $\M{1}{\alpha}{\PP^N|H}{d}$.
+
+The main component $\VZ_{1,\alpha}(\PP^N|H,d)$ is then identified by a double factorisation condition:
 \begin{enumerate}
-  \item $\pi$ makes $W$ into a flat, proper algebraic space over $S$, with fibers at worst nodal in codimension 1, admitting a lifting to a special log morphism $\pi\colon (W,\pM_W^{W/S})\to(S,\pM_S^{W/S})$, such that:
-  \begin{enumerate}
-   \item $\pM_W^{W/S}$ and $\pM_S^{W/S}$ are locally free log structures;
-   \item for every geometric point $\bar{w}\to W$, either $\bar{w}$ is in the smooth locus of $\pi_S$ and $\pi^\flat\colon \pi^*\overline{\pM}_{S,\bar{w}}^{W/S}\to \overline{\pM}_{W,\bar{w}}^{W/S}$ is an isomorphism, or $\bar{w}$ is in the nodal locus and the following diagram is cocartesian:
-   \bcd
-   \NN\ar[r,"{(1,1)}"]\ar[d,"h"] & \NN^2\ar[d] \\
-   \pi^*\overline{\pM}_{S,\bar{w}}^{W/S}\ar[r] & \overline{\pM}_{W,\bar{w}}^{W/S}
-   \ecd
-   with $h(e)$ irreducible;
-   \item for every geometric point $\bar{s}\to S$ there is a bijection between the irreducible elements of $\overline{\pM}_{S,\bar{s}}^{W/S}$ and the irreducible components of $W_{\bar{s}}^{\text{sing}}$.
+ \item If $f$ contracts a genus one subcurve, then $f$ is required to factor through the Smyth singularity $\nu\colon C\to \bar C$ determined by the contraction radius $\delta$ as above.
+ \item If furthermore the core is contracted by the associated tropical map $\phi$, let $\delta_2$ be the minimal distance from $\circ$ to a vertex supporting a flag that escapes $\phi^{-1}(\phi(\circ))$; we require $f$ to factor through $\nu_2\colon C\to\bar C_2$.
 \end{enumerate}
-  \item $D\subseteq W$ is a Cartier divisor, smooth over $S$, and such that $\pi_X(D)=Y$;
- \item $\pM_S$ is twisted by integers $(r_1,\ldots,r_l)$ and expanded with respect to $\pM_S^{W/S}$, namely \'{e}tale locally at every point $s\in S$ the morphism of log structures $\pM_S^{W/S}\to\pM_S$ admits a chart:
- \bcd
- \NN^l\ar[d]\ar[r,"{(r_1,\cdots,r_l)}"] &\NN^l\ar[r,"{(id,0)}"]&\NN^l\oplus\NN^k\ar[d] \\
- \pM_S^{W/S}\ar[rr] & & \pM_S
- \ecd
+The main result is that
+\begin{thm}
+ $\VZ_{1,\alpha}(\PP^N|H,d)$ is (log) smooth.
+\end{thm}
 
- \end{enumerate}
-\end{definition}
- The log structure on $W$ is then given by
- \[ \pM_W=\pi^*\pM_S\oplus_{\pi^*\pM_S^{W/S}}\pM_W^{W/S}\oplus_{\OO^*_W}\pM^D\]
- where $\pM_D$ is the divisorial log structure associated to $D$. 
-Notice that with this definition $(W,\pM_W)\to(S,\pM_S)$ is log smooth.
-
-Similarly a \emph{log twisted curve} is $((C,p_1,\ldots,p_n)\to S, \pM_S^{C/S}\to\pM_S)$ with
-\[\pM_C=\pi^*\pM_S\oplus_{\pi^*\pM_S^{C/S}}\pM_C^{C/S}\oplus_{\OO^*_C}\bigoplus_{i=1}^n\pM^{p_i}\]
-A log twisted curve is \emph{minimal} if the log structure $\pM_S$ is locally free, and for every geometric point $\bar{s}\to S$ and irreducible element $b\in\overline{\pM}_S$, we can find an irreducible $a\in\overline{\pM}^{C/S}_S$ and a positive integer $l$ such that $a\mapsto lb$ (by definition this means that the morphism of log structures $\pM_S^{C/S}\to\pM_S$ is \emph{simple}).
-So essentially we are allowed to take roots of the smoothing parameters of the nodes of $C_{\bar{s}}$.
-
-Finally, fix an $n$-tuple of non-negative contact orders $(c_1,\ldots,c_n)$.
-\begin{definition}
- A \emph{relative log prestable map} with tangency condition $\mathbf{c}$ is given by a diagram of log morphisms:
- \bcd
- ((C,\mathbf p),\pM_C)\ar[rr,"f"]\ar[dr] & & ((W,D),\pM_W)\ar[rr,"\pi_X"]\ar[dl] & & (X,Y)\times S \\
-  & (S,\pM_S) & & &
- \ecd
- \begin{enumerate}
-  \item $(C,\mathbf p),\pM_C)\to (S,\pM_S)$ is a minimal log twisted curve;
-  \item $((W,\pM_W)\to (S,\pM_S),(W,D)\to(X,Y))$ is an extended twisted log expansion of $(X,Y)$;
-  \item (\emph{corank condition}) \sidenote{split the definition into a more general one over LogSch and minimality?} for every geometric point $\bar{s}\in S$, the rank of \[\operatorname{Coker}(\pM^{W/S}_{S,\bar{s}}\to \pM_{S,\bar{s}})\] is equal to the number of non-distinguished nodes of $C_{\bar{s}}$; recall that a node of $C_{\bar{s}}$ is \emph{distinguished} if it is mapped under $f$ to the singular locus of $W_{\bar{s}}$.
-  \item (\emph{log admissibility}) the morphism of log structures $f^\flat\colon f^*\pM_W\to\pM_C$ is simple at every distinguished node;
-  \item (\emph{tangency condition}) the underlying map $\underline{f}\colon C\to (W,D)$ is non-degenerate, namely no component of $C$ is mapped entirely into $D$, and locally around every marking $p_i$ we can find a chart
-  \bcd
-  \NN\ar[r,"\cdot c_i"]\ar[d] & \NN\ar[d] \\
-  f^*\pM^D\ar[r] & \pM^{p_i}
-  \ecd
-  for the restriction of $f^\flat$ to the $f^*\pM^D$ factor.
-  \end{enumerate}
-\end{definition}
-\begin{definition}
- A relative log prestable map as above is \emph{stable} if for every geometric point $\bar{s}\in S$ the group of automorphisms $(\sigma,\tau)$ is finite, where:
- \begin{enumerate}
-  \item $\sigma$ is an automorphism of $((C,\pM_C)\to (S,\pM_S))_{\bar{s}}$ preserving the markings $\mathbf p$;
-  \item $\tau$ is an automorphism of $((W,\pM_W)\to (S,\pM_S))_{\bar{s}}$ preserving $D$ and $\pi_X\colon W_{\bar{s}}\to X$;
-  \item $\tau\circ f_{\bar{s}}=f_{\bar{s}}\circ \sigma$.
- \end{enumerate}
-\end{definition}
-\begin{remark}
- The corank and simplicity condition imply the following: the rank of the locally free log structure $\pM_S$ at $\bar{s}$ amounts to the number of irreducible components of $W_{\bar{s}}^{\text{sing}}$ plus the number of non-distinguished nodes of $C_{\bar{s}}$; all the smoothing parameters of the distinguished nodes mapping to the same component of $W_{\bar{s}}^{\text{sing}}$ have been identified \emph{up to twisting}.
-In facts, at a distinguished node $q$ of $C$, letting $R$ be the local ring of $S$ at $\pi(q)$, we can find \'{e}tale local charts
- \bcd
- \NN^2\oplus_{\NN} \pM_{S}\ar[r,"{(id,\cdot m_q)}" below]\ar[d] & \NN^2\oplus_{\NN} \pM_{S}\ar[d] \\
- f^*\pM_W \ar[r,"f^\flat" below]\ar[d] & \pM_C\ar[d] \\
- R[z_1,\ldots,z_{\dim(X)-1},x,y]/(xy-t)\ar[r,"\left(\substack{x\mapsto a^{m_q}\\ y\mapsto b^{m_q}\\ t\mapsto s^{m_q}}\right)" below=.2cm] & R[a,b]/(ab-s)
- \ecd
- where the twist at $f(q)$ is given by $l$, the one at $q$ is given by $r_q$, and the equality $l=r_qm_q$ has to hold.
-\end{remark}
-
-\subsection{The desingularisation via central alignments} The following is a variation on \cite[\S 3.3]{RSPW2}.
-
-\section{Gathmann's recursive structure on the boundary of maps to expanded pairs}
-
-We find a natural line bundle with a section whose vanishing locus consists of those maps where the target splits and the marking $p_k$ is mapped to a higher level of the accordion.
-We express these boundary strata recursively as fibered products of desingularised relative and rubber spaces with lower numerical invariants; the multiplicity calcultion is performed for $\PP^1|\{\infty\}$ and rests on work of Vakil \cite{Vre}.
-Putting everything together we reobtain Gathmann's algorithm for computing relative invariants, or the invariants of a smooth hyperplane section.
+\textbf{Gathmann's recursion.} There is a morphism $\VZ_{1,\alpha}(\PP^N|H,d)\to \VZ_{1,n}(\PP^N,d)$, hitting Gathmann's relative space.
+We may therefore pullback Gathmann's line bundle and section, cutting out the locus where the $k$-th marking is tangent to $H$ to order $\alpha_k+1$.
+Because $\alpha$ was maximal ($\sum\alpha=d$) by assumption, this means that the curve has to break, and $x_k$ has to lie on an internal component - one which is entirely mapped into $H$.
+Here comes an interesting point: the combinatorics of such boundary loci is governed by tropical geometry, and it is otherwise very hard to districate the interaction between the relative condition and the exceptional loci of the Vakil--Zinger blow-up.
+\begin{cor}
+ $\VZ_{1,\alpha}(\PP^N|H,d)$ is smooth over its Artin fan, in particular codimension one logarithmic strata can be read off from the latter.\marginpar{why are we only interested in log strata?}
+\end{cor}
+The Artin fan is a tropical gadget.
+Its local structure is given by subdividing the ACGS minimal model according to the alignment.
+We are only interested in picking its rays.
+The upshot is that the combinatorics is slightly more involved than in the genus zero case: the alignment may force some teeth of the comb to break.
+\begin{thm}
+ \[(\alpha_k\psi_k+\ev_k*H)[\VZ_{1,\alpha}(\PP^N|H,d)]=[D_{\alpha,k}(\PP^N|H,d)],\]
+ where the latter is a sum of broken comb loci indexed by rays of the tropical fan.
+\end{thm}
+Importantly, the broken comb loci admit a very explicit description in terms of tautological integrals on the underlying boundary of Gathmann's relative space.
+\begin{thm}
+ Up to a finite cover of the underlying boundary stratum - which is just a combinatorially-determined product of moduli spaces of genus zero or one curves and absolute or relative maps with lower numerical invariants - every component of $D_{\alpha,k}(\PP^N|H,d)$ can be described as the transverse intersection of two loci in a projective bundle, where:
+ \begin{itemize}
+  \item the latter parametrises the possible line bundle isomorphisms imposed by the alignment of the log structure;
+  \item the first locus is a subbundle representing the residual isomorphisms after fixing the ones imposed by tropical continuity;
+  \item the second locus is determined by the factorisation conditions.
+ \end{itemize}
+\end{thm}
+The upshot is that we may then push the formula down to the Gathmann's space and we obtain multiplicities and tautological classes.
+\begin{cor}
+ \[(\alpha_k\psi_k+\ev_k*H)[\VZ^G_{1,\alpha}(\PP^N|H,d)]=[D^G_{\alpha,k}(\PP^N|H,d)],\]
+ where the latter is a weighted sum of tautological classes on Gathmann's comb loci.
+\end{cor}
+Once we have this formula, the following extensions are classical:
+\begin{itemize}
+ \item A similar formula for raising the tangency holds in the non-maximal case.
+It can be proven by adding auxiliary markings of contact order $1$; forgetting them is then a $(d-\sum\alpha)!:1$ cover because of the density of the nice locus inside Gathmann's spaces.
+ \item The formula holds more generally for any smooth projective target $X$ relative to a generic hyperplane section $Y=X\cap H\subseteq \PP^N$ by virtual pullback.
+\end{itemize}
+Finally the recursive structure of the boundary allows us to prove the following
+\begin{thm}[In-principle quantum Lefschetz]
+ The restricted reduced genus one invariants of $Y$ can be inductively deducted from the full descendant (reduced) genus zero and one Gromov-Witten theory of $X$.
+\end{thm}
+The computation is more delicate than its genus zero analogue because invariant with the same numerical data appear intertwined in the last steps of the recursion.
 
@@
 
-\begin{remark}
- Notice that gluing does not present the subtleties to which log geometry has made us used, since we endow the curves with the minimal centrally aligned structure, possibly after prescribing that the smoothing parameters for the newly created nodes are \emph{bigger} than the contraction radius $\delta$.
-\end{remark}
-
-\begin{remark}
- A dimensional computation shows that $\mathcal Y^b$ is never relevant to the purpose of the recursion formula.
-On the other hand the classes of $\mathcal Y^a$ and $\mathcal Y^c$ should be weighted with the coefficient $\frac{\prod m^{(i)}}{r!}$.
-Let $D_{1,\alpha,k}(\PP^N|H)$ be the union of all the $\mathcal Y^a$ and $\mathcal Y^c$ as above, for any choice of number of external components $r$, distribution of the markings $A$, and of the degree $D$, provided the marked point $x_k$ lies on the internal component $C^{(0)}$.
-Let each component be endowed with its fundamental class weighted as above and let $\virt{D_{1,\alpha,k}(\PP^N|H)}$ be the sum of all these classes.
-\end{remark}
-
-\begin{thm}
- Assume $\sum\alpha=d$. Then \[(\alpha_k\psi_k+\ev_k^*H)[\VZc{1}{\alpha}{\PP^N|H}{d}]=\virt{D_{1,\alpha,k}(\PP^N|H)}.\]
-\end{thm}
-\begin{proof}
-We perform a number of reductions.
- \begin{itemize}%[leftmargin=1cm]
-  \item \textbf{Reduction to the case of $\PP^1|\{\infty\}$:} by choosing a general $N-2$-plane $A\subseteq H$ and projecting away from it.
-Must show that the rational map $\rho_A\colon \VZc{1}{n}{\PP^N|H}{d}\dashrightarrow \VZc{1}{n}{\PP^1|\{\infty\}}{d}$ is defined and smooth at a general point of $D_{1,\alpha,k}(\PP^N|H)$.
-
-  \item \textbf{Reduction to an \'etale neighbourhood of $C^{(0)}$:} the plan is to understand the global perfect obstruction theory of $\VZc{1}{n}{\PP^1}{d}$ and see that the tangent to the latter is a sum of contributions from the \emph{special loci}, namely contracted components, ramification points, markings and nodes.
-
-  \begin{remark}
-   When we are studying the infinitesimal deformation theory of centrally aligned curves, notice that being centrally aligned must be checked on geometric points, and minimality is open, hence any deformation as a log smooth curve will automatically be minimal centrally aligned.
-The tangent space is then $H^1(C,T_C^{\rm{log}})$; notice that this is independent from the log structure on the base.
-  \end{remark}
-
-  \begin{example}
-   There are non-trivial deformations that are trivial on the underlying marked prestable curve.
-If $(C,\mathcal M_C)\to (\Spec(k),Q^{\rm{cen}})$ is a centrally aligned curve, then in order to define a deformation over $\Spec(k[\epsilon])$ we need to extend the log structure on the base by choosing a map $Q^{\rm{cen}}\to k[\epsilon]$.
-Notice that if we want the underlying curve to be a trivial deformation we better send all the smoothing parameters to $0$ in $k[\epsilon]$; on the other hand, if $Q^{\rm{cen}}$ contains an element such as $e_i-e_j$ (making $R_i$ further from the circuit than $R_j$), then we are free to map it to an invertible element in $k[\epsilon]$, which will kill it in the associated log structure;\sidenote{Invertible elements of $k[\epsilon]$ remain invertible when setting $\epsilon=0$, which seems to kill $e_i-e_j$ on the central fiber too.} this will make $R_i$ and $R_j$ be \emph{at the same distance} from the circuit in the deformation.
-Importantly, $Q^{\rm{log}}\to Q^{\rm{cen}}$ is an epimorphism only in the category of integral monoid (of which the multiplicative monoid of a ring is never an object, because it has a sink).
-  \end{example}
-
- \end{itemize}
-
-\end{proof}
-
-\appendix
-\section{Old}
-
-\subsection{Definition of the relative space} We now give a definition of the relative space inside the moduli space of centrally aligned stable maps.
-\begin{dfn}
-Let $X$ be a smooth projective variety with a smooth divisor $Y$.
-Fix a vector of tangency conditions $\alpha=(\alpha_1,\ldots,\alpha_n)$ with $\Sigma_{i=1}^n \alpha_i = Y \cdot \beta$.
-Then the \emph{centrally aligned relative space}
-\begin{equation*}\VZc{1}{\alpha}{X|Y}{\beta} \end{equation*}
-is defined to be the closed substack of $\VZc{1}{n}{X}{\beta}$ satisfying the following conditions:
-\begin{enumerate}
-\item \emph{Gathmann's relative condition:} for each connected component $Z$ of $f^{-1}(Y)$, either:
-\begin{enumerate}
-\item $Z$ is a single point of $C$, in which case if $Z=x_i$ is a marking then we require that the multiplicity of $f$ at $x_i$ along $Y$ is at least $\alpha_i$ (if $Z$ is not a marking then there is no condition);
-\item $Z$ is a subcurve $Z \subseteq C$, in which case we require that
-\begin{equation*} f^*[Y]|_Z -\sum_{x_i\in Z}\alpha_ix_i\end{equation*}
-is an effective class in $\Achow_0(Z)$.
-\end{enumerate}
-
-\item \emph{Compatibility condition:} this applies when the minimal subcurve of genus one (the \emph{circuit} or \emph{core}) is contracted to a point in $Y$.
-In this case we require that the following diagram of solid arrows may be completed to a commutative diagram:
-\bcd
-Q_{\rm{min}}^{\rm{prestable}}\ar[r]\ar[d] & Q_{\rm{min}}^{\rm{log.map}} \\
-Q_{\rm{min}}^{\rm{cen.align}}\ar[dashed,ur]
-\ecd
-\end{enumerate}
-\end{dfn}
-
-\begin{remark}[Explaining Gathmann]
-Gathmann's condition is promptly extended to the case that $\Sigma_{i=1}^n \alpha_i \leq Y \cdot \beta$.
-\textcolor{red}{Question: what is the correct generalisation of the compatibility condition?} Here we try to make the condition for a curve component of $f^{-1}(Y)$ into an easily verifiable criterion: if $Z$ is a smooth elliptic curve, recall that every line bundle of positive degree on it is effective, hence the relative condition can be rephrased as the following numerical criterion:
-\begin{equation*} f_*[Z]\cdot [Y]+\sum_{j=1}^r m^{(j)}\geq \sum_{x_i\in Z}\alpha_i \end{equation*}
-together with the additional requirement that, when the above is an equality, there is an isomorphism of line bundles:
-\begin{equation}\label{eqn:eq_in_Pic}
-(f|_{Z})^*\OO_X(Y) \otimes \OO_Z\left(\sum_{j=1}^r m^{(j)}y_j\right)=\OO_Z\left(\sum_{x_i\in Z}\alpha_ix_i\right) 
-\end{equation}
-
- If $Z$ is reducible, the correct extension is not to impose the same condition componentwise; rather, we should ask the numerical condition for the total degree, and, if $Z$ is obtained by gluing a smooth elliptic curve $E$ with a forest of rational trees $T_i$ at roots $q^E_i$, then the line bundle equality \eqref{eqn:eq_in_Pic} should be required in $\Pic(E)$ after counting each $q^E_i$ towards the left hand side with multiplicity
- \[f_*[T_i]\cdot [Y]+\sum_{\text{external components attached to $T_i$}} m^{(j)}- \sum_{x_j\in T_i}\alpha_j.\]
-
- %That this is the right thing to do follows from the proof that Gathmann's relative space is the projection of Jun Li's moduli space of maps to the expanded pair after contracting the higher levels of the accordion.
-\end{remark}
-
-\begin{remark}[Explaining compatibility]
-First we need to define the monoids and maps involved.
-We start with $Q_{\rm{min}}^{\rm{prestable}}\to Q_{\rm{min}}^{\rm{log.map}}$; when looking at a geometric point $\Spec(k=\bar k)$ it is well-known that \[ Q_{\rm{min}}^{\rm{prestable}}=\prod_{q\ \text{node}}\mathbb N_q.\]
-Let us assume that all the nodes are internal, i.e.
-map to $Y$, for all the action happens there, and also that there is only one internal connected component $Z$, which is a curve of arithmetic genus one.
-Then we define $Q_{\rm{min}}^{\rm{log.map}}$ as the saturation of the quotient of
-\begin{equation}\label{eq:logminmod} \prod_{q\ \text{node}}\mathbb N_q \times \prod_{S\ \text{internal irr. compo.}}\mathbb N_S\end{equation}
-by the relation generated in the groupification of the latter by
-\[\langle \rm{Rel}_q=(u_q,\ldots,1,\ldots,-1,\ldots),\ q\ \text{internal node} \rangle\]
-where $1$ is in position $S_q^+$ (adjacent to $q$ and further from the circuit), $-1$ in position $S_q^-$ (adjacent to $q$ and closer to the circuit), and $u_q$ in position $q$ is defined as to include the tropical balancing condition (I don't know whether this is standard):
-\[u_q=f_*[T_q]\cdot [Y]+\sum_{R_i \text{external compo. attached to }T_q} m^{(i)}- \sum_{x_j\in T_q}\alpha_j,\]
-where $T_q$ is the tree of internal components that $q$ separates from the circuit.
-Notice that the nodes between $Z$ and an external component $R_i$ have no $1$, so the corresponding relations look like \[(u_q,\ldots,-1,\ldots).\]
-The map $Q_{\rm{min}}^{\rm{prestable}}\to Q_{\rm{min}}^{\rm{log.map}}$ is induced by the inclusion of the node factors in \eqref{eq:logminmod}.
-If we call $e_q$ the image in $Q_{\rm{min}}^{\rm{log.map}}$ of the $q$-th basis vector, then we can verify that the following equations hold: chosen any internal component $S_i$ and any two external component $R_i^1, R_i^2$
-such that their path to the circuit goes through $S_i$, then
-\begin{equation}
- \sum_{q\in[R_i^1,S_i]}u_qe_q=\sum_{q\in[R_i^2,S_i]}u_qe_q.
-\end{equation}
-\textcolor{red}{Question: is this monoid factorisation condition a closed one?}
-\end{remark}
-
-\begin{remark}
- Here is a tidy example: start with an elliptic curve $E$ contracted to $Y$, with two external components $R_1, R_2$ attached to it and a single marking $x\in E$. The tropical picture would be:
-\begin{center}
- \begin{tikzpicture}[radius=2pt,scale=0.5]
- \draw[fill=black] (0,0) circle;
- \draw (0,0) -- (4,0);
- \draw[fill=black] (0,2) circle;
- \draw[fill=black] (0,4) circle;
- \draw (0,2) -- (2,3);
- \draw (0,4) -- (2,3);
- \draw (2,3) -- (4,3);
- \draw[fill=white] (2,3) circle;
- \draw[->] (2,1.5) -- (2,.5);
- \end{tikzpicture}
-\end{center}
-The dual monoids in the compatibility condition give us the following nice picture:
-\begin{center}
-\begin{tikzpicture}[scale=0.8]
- \draw (0,0) -- (0,2)  (0,0)--(2,0);
- \draw[->] (1,-1.3) -- (1,-.5);
- \fill[gray!30] (0,-4) -- (0,-2) -- (2,-2) -- (0,-4);
- \fill[gray!50] (0,-4) -- (2,-4) -- (2,-2) -- (0,-4);
- \draw (0,-4) -- (0,-2) (0,-4) -- (2,-4) (0,-4) -- (2,-2) node[above right]{$e_1=e_2$};
- \draw (1,-2) node[above]{$e_2>e_1$} (2,-3) node[right]{$e_1>e_2$};
- \draw[<-] (2.5,1)--(3.5,1);
- \draw[gray!=30] (4,0) -- (4,2)  (4,0)--(6,0);
- \draw (4,0) -- (4.6,2) node[above right]{$m_1/m_2$};
- \draw[<-,dashed] (2.7,-1.3)--(3.5,-.5);
-\end{tikzpicture}
-\end{center}
-So, for example, the factorisation exists for the subcone $e_2>e_1$ only when $m_1>m_2$, which is compatible with the fact that $\mathbb N^2=Q_{\rm{min}}^{\rm{prestable}}\to Q_{\rm{min}}^{\rm{log.map}}=\mathbb N$ is given by
-$e_1\mapsto m_2, e_2\mapsto m_1$.
-\end{remark}
-
-\section{The relative space is the closure of the nice locus for $(\PP^N,H)$}
-\noindent In general we do not know very much about the space we have just defined.
-The aim of this section is to show that, in the case where $X=\PP^N$ and $Y=H$ is a hyperplane, the space is proper and irreducible of the expected dimension.
-As such it has a fundamental class, which we can use to define reduced relative Gromov--Witten invariants in genus one.
-
-\begin{remark} In the case of a general pair $(X,Y)$ we will see that the moduli space is still proper, but is not in general irreducible or even equidimensional.
-Nevertheless, we can equip it with a virtual class by ``pulling back'' from the case of $(\PP^N,H)$; for details, see \S [REF].
-\end{remark}
-
-The strategy is as follows. We define (Definition \ref{Definition of nice locus}) an open subspace
-\begin{equation*}\VZc{1}{\alpha}{\PP^N|H}{d}^{\circ} \subseteq \VZc{1}{\alpha}{\PP^N|H}{d}\end{equation*}
-called the \emph{nice locus}, on which the source curve and the map take a particularly simple form.
-Because of this simplicity, it is easy to show that the nice locus is irreducible (Lemma \ref{Nice locus is irreducible}).
-We then prove that $\VZc{1}{\alpha}{\PP^N|H}{d}$ is equal to the closure of the nice locus inside $\VZc{1}{n}{\PP^N}{d}$.
-Thus it is proper, since it is a closed subspace of a proper space, and it is irreducible, since it is the closure of an irreducible space.
-
-\begin{definition} \label{Definition of nice locus} The \emph{nice locus} is defined as the open substack
-\begin{equation*}\VZc{1}{\alpha}{\PP^N|H}{d}^{\circ} \subseteq \VZc{1}{\alpha}{\PP^N|H}{d}\end{equation*}
-of centrally aligned maps satisfying the following two conditions:
-\begin{enumerate}
-\item the source curve $C$ is irreducible;
-\item $f$ does not map $C$ inside $H$.
-\end{enumerate}
-\end{definition}
-
-\begin{lem}\label{Nice locus is irreducible}
-The nice locus $\VZc{1}{\alpha}{\PP^N|H}{d}^{\circ}$ is irreducible.
-\end{lem}
-\begin{proof}
-By definition the contraction radius $\delta$ is compatible with the map, i.e.
-the subcurve $C_0\subseteq C$ where $\lambda<\delta$ is equal to the maximal connected genus one subcurve contracted by $f$.
-Hence when the source curve is irreducible we must have $\delta=0$, and we see that the central alignment on $C$ is uniquely and trivially determined.
-Thus to specify a point in the nice locus we only need to specify the source curve $C$ (as a scheme) and the map $f$.
-A parametrisation can be given from the vector bundle:
-\[ \operatorname{Vb}\left(\pi_*\OO_{\mathcal E}(\sum_{j=n+1}^{n+\delta}\sigma_j)\oplus\pi_*\OO_{\mathcal E}(\sum_{j=1}^{n+\delta}\sigma_j)^{\oplus r}\right) \quad \text{on} \quad \mathcal{M}_{1,n+\delta}\]
-where $\pi\colon\mathcal E\to\mathcal M$ is the universal curve and $\delta=d-\sum\alpha_i$.
-\end{proof}
-
-\subsection{Justifying the novel condition by dimensional reasons}
-Here is a dimensional computation in an explicit example which shows that being in the closure of the nice locus must impose some condition on the log structure.
-\begin{example}
-Consider $\M{1}{(3)}{\PP^1|H}{3}$.
-This moduli space has virtual dimension $6+1-3=4$.
-Here is a parametrisation of the nice locus: choose an object $(E,p) \in \mathcal{M}_{1,1}$, and let $s_0$ be the natural section $s_0 \colon\OO_E\hookrightarrow\OO_E(3p)$ and $s_1$ any other section of $\OO_E(3p)$ not vanishing at $p$ (notice that $\h^0(E,\OO_E(3p))=3$).
-Then $(E,p,[\lambda s_0,s_1])$ gives a well-defined element of the nice locus for $\lambda \neq 0$.
-
-Consider now the following weighted graph for a map in the boundary
-\begin{center}
-\begin{tikzpicture}
-\draw[color=brown] (0,0) node[left]{$E$} -- (4,0);
-\draw[fill=black] (1,0) circle[radius=2pt] node[above]{$x_1$};
-\draw[fill=black] (2,0) circle[radius=2pt] node[below right]{$y_1$};
-\draw[fill=black] (3,0) circle[radius=2pt] node[below right]{$y_2$};
-\draw (2,1.5) node[left]{$R_1$} (3,1.5) node[left]{$R_2$};
-\draw (2,-1) -- (2,2) node[above]{$2$} (3,-1) -- (3,2) node[above]{$1$};
-\draw[->] (5,0.5) -- (8,0.5);
-\draw (9,-1) -- (9,2) node[above]{$\PP^1$};
-\draw[fill=black] (9,0) circle[radius=2pt] node[right]{$H$};
-\end{tikzpicture}
-\end{center}
-where the brown line represents a contracted genus $1$ curve.
-Now $(E,x_1,y_1,y_2)$ is a point of $\mathcal{M}_{1,3}$ subject to the divisorial condition $3x_1-2y_1-y_2=0\in \Achow_0(E)$; furthermore we have to choose the second branch point of the $2:1$ map from $R_1$ to $\PP^1$.
-This already makes up for a $3$-dimensional moduli space of degenerate relative maps corresponding to such a graph.
-The minimal log structure for this curve has a chart from $\mathbb N^2$, with generators $e_1$ and $e_2$ corresponding to the smoothing parameters of the two nodes.
-If we allowed $e_1$ and $e_2$ to be identified in the characteristic sheaf, then we would get an extra $\Gm$ of choices for the log structure, so in total a $4$-dimensional moduli space.
-Thus if we don't impose the novel condition then we get a whole other component of the relative space, which of course for dimensional reasons cannot be contained in the closure of the nice locus.\qed
-\end{example}
-
-\begin{remark}
- For the reader who is unfamiliar with centrally aligned log curves, it might be convenient to recall that they provide a modular interpretation of the iterated blow-up procedure of Vakil and Zinger.
-In particular it is natural that not all of the exceptional divisors be contained in the closure of the nice locus for every $\alpha$; this geometric information is contained in the compatibility condition.
-\end{remark}
-
-\subsection{Proof sketch} \textcolor{red}{The compatibility condition should imply that the map admits a log-enhancement;} if we can prove that there is a smooth, connected and proper moduli space above, then we automatically get that the Gathmann-like relative space is closed and irreducible, and it obviously contains the nice locus; hence, if we can prove that the latter is dense, we win.
-
-It thus remains to show that, given a relative centrally aligned map, we can smooth it to one in the nice locus.
-The only interesting case \textcolor{red}{should be} that the core is contracted to a point of $Y$.
-Here is how we prove it:
-\begin{enumerate}
- \item we consider the core (say it's a smooth elliptic curve) marked with all the special points (markings and nodes); consider $E\times\dvr$ and blow it up in all the points of the central fiber that originally corresponded to nodes; we carefully and iteratively blow up smooth points of the central fiber in order to reconstruct the curve $C$ that we started with.
-In fact we may perform weighted instead of ordinary blow-ups, picking the ideal $(z,t^r)$ where $z$ is a vertical coordinate; this has the effect of introducing an $A_{r-1}$ surface singularity at the corresponding node of the central fiber.
-We do so by choosing a homomorphism $Q_{\rm{min}}^{\rm{log.map}}\to\mathbb N$ and composing it with $Q_{\rm{min}}^{\rm{prestable}}\to Q_{\rm{min}}^{\rm{log.map}}$ to determine the relevant $r$ for every node.
- \item Let $E,S_1,\ldots,S_k$ be the irreducible components of $f^{-1}(Y)$; we define a line bundle on the smoothing by
- \[\mathcal L=\OO_{\cC}\left(\sum \gamma_iS_i\right)\left(\sum \alpha_ix_i\right).\]
- Using intersection theory on the surface (recall that the local multiplicity of intersection of the two branches of the node underlying an $A_{r-1}$ singularity is $\frac{1}{r}$) we check that the compatibility condition is precisely what we need in order to be able to choose $\gamma_i$ adequately so that the following equations hold:
- \begin{align*}
-  0&=\deg(\mathcal L_{|S_i}) \\
-  m^{(i)}&=\deg(\mathcal L_{|R_i}) \\
-  \mathcal O_E&\cong\mathcal L_{|E}
- \end{align*}
- the last from Gathmann's condition.
- \item It is not clear that sections of $\mathcal L$ are unobstructed. In order to extend them we pass to $\overline{\mathcal C}$.
-\end{enumerate}
-
-\subsection{Basic facts about centrally aligned curves}
-\begin{prop}[{\cite[Proposition 4.6.2.2]{RSPW}}]
-The morphism $\MM^{\rm{ctr}}_{1,n}\to\MM^{\dagger}_{1,n}$ is a log-modification.
-\end{prop}
-
-Explanation: this is a local statement so I can probably reduce to an atomic neighbourhood $S$ of a point $p$.
-$S$ and the curve over it are endowed with the minimal log structure; let $P=\oM_p$ determine a chart for this log structure.
-Observe that the subcurve $\plC_0$ of the tropicalisation $\plC$ of $C_p$ determines a subset $\rm{MinPos}$ of the set of vertices, namely those adjacent to $\plC_0$.
-Perform the following log-blowups: consider the set of primitive values of the function $\lambda\colon \plC\to P$, and blow up the ideal that they generate; now locally the set of values of $\lambda$ is principal with generator $p$: blow up the ideal generated by $\{\lambda(v)-p\}\setminus\{-p\}$.
-Keep going until $\lambda(v_i)$ is reached for some $v_i\in\rm{MinPos}$; at this point stop and declare the contraction radius $\delta:=\lambda(v_i)$.
-Finish by adjoining $\lambda(v)-\delta$ for all the vertices untouched to this stage.
-This shows that the choice of $\delta$ is not an extra degree of freedom.\marginpar{do I sound like a physicist?}
-
-\subsection{Moral justification of the novel condition}
-
-\begin{example} In this example we will give further moral justification for the novel condition, using as motivation the expanded degenerations approach to relative stable maps.
-This is not strictly necessary for what we want to do (since our spaces don't involve expanded degenerations), but it helps to explain where this condition comes from.
-
-So, let us pretend that we have a good definition of the ``centrally aligned Li space'' of maps from centrally aligned curves to expanded degenerations:
-\begin{equation*} \VZcLi{1}{\alpha}{X|D}{\beta} \end{equation*}
-Objects of this moduli space should consist of maps $C \to X_l$ where $X_l \to X$ is an expansion (of some length $l$) of the pair $(X,D)$, together with a central alignment on $C$ which is compatible with this map.
-The factorisation property should say that the following diagram commutes:
-\bcd
-& \tilde{C} \ar[ld,"\nu" left] \ar[rd,"\tau"] & \\
-C \ar[d,"f" left] & & \overline{C} \ar[d,"\overline{f}", dotted] \\
-X_l \ar[rd,"\pi"] & & X_l \ar[ld,"\pi"] \\
-& X & 
-\ecd
-Morally speaking, the projection map
-\begin{equation*} \pi_* \colon \VZcLi{1}{\alpha}{X|D}{\beta} \to \VZc{1}{n}{X}{\beta} \end{equation*}
-should have as its image our space $\VZc{1}{\alpha}{X|D}{\beta}$.
-We will see that everything in the image of this space must satisfy the novel condition, thus providing further justification for us imposing it.
-
-We proceed by contradiction. Consider a genus one map $C \to \PP^1$ of the following form
-\begin{center}
-\begin{tikzpicture}
-\draw[fill=black] (0,0) node[left]{$E$} -- (4,0);
-\draw[fill=black] (0.7,0) circle[radius=2pt] node[below]{$5$};
-\draw[fill=black] (2,0) circle[radius=2pt] node[above right]{$2$};
-\draw[fill=black] (3,0) circle[radius=2pt] node[above right]{$3$};
-\draw (2,1.5) node[right]{$C_1$};
-\draw (3,1.5) node[right]{$C_2$};
-\draw (2,-1) -- (2,2) node[above]{$2$};
-\draw (3,-1) -- (3,2) node[above]{$3$};
-
-\draw[->] (4.5,0) -- (6.5,0);
-\draw (5.5,0) node[above]{$f$};
-\draw (7,-1) -- (7,2) node[above]{$\PP^1$};
-\draw[fill=black] (7,0) circle[radius=2pt] node[right]{$\infty$};
-\end{tikzpicture}
-\end{center}
-and equip the source curve $C$ with a central alignment which identifies the lengths of the components $C_1$ and $C_2$:
-\begin{center}
-\begin{tikzpicture}
-\draw[red,thick,dashed] (0,0) circle[radius=51pt];
-\draw[red] (-1.75,0) node[left]{$R_\delta$};
-\draw[fill=white] (0,0) circle[radius=4pt];
-\draw (0,0.1) node[above]{$E$};
-\draw[fill=black] (-1,-1.5) circle[radius=4pt];
-\draw (-1.1,-1.5) node[left]{$C_1$};
-\draw[fill=black] (-0.1,-0.1) -- (-1,-1.5);
-\draw[fill=black] (1,-1.5) circle[radius=4pt];
-\draw (1.1,-1.5) node[right]{$C_2$};
-\draw[fill=black] (0.1,-0.1) -- (1,-1.5);
-\end{tikzpicture}
-\end{center}
-This defines an ``object'' of $\VZc{1}{(5)}{\PP^1|\infty}{5}$, satisfying all the necessary conditions \emph{except for the novel condition}.
-We will show that this cannot belong to the image of $\pi_*$.
-
-First we have to identify what the possible lifts of this object to the centrally aligned Li space are. The map $C \to X_1$ takes the following form:
-
-\begin{center}
-\begin{tikzpicture}
-\draw (-1,-1) -- (1,-1);
-\draw (-1,-1) -- (-1,1);
-\draw (1,-1) -- (1,1);
-\draw (-1,1) -- (1,1);
-\draw (-1,-1) -- (-2,-2.5);
-\draw (-2,-2.5) -- (0,-2.5);
-\draw (0,-2.5) -- (1,-1);
-\draw[red,very thick] (-2,-2.5) -- (-0.5,-1);
-\draw[red] (-1,-1.5) node[right]{$C_1$};
-\draw[red,fill=red] (-0.5,-1) circle[radius=2pt];
-\draw[red] (-0.6,-1) node[above]{$2$};
-
-\draw[red,very thick] (0,-2.5) -- (0,-1);
-\draw[red] (-0.1,-1.5) node[right]{$C_2$};
-\draw[red,fill=red] (0,-1) circle[radius=2pt];
-\draw[red] (0.1,-1) node[above]{$3$};
-
-\draw[red,very thick] (-0.5,-1) to [out=90,in=180] (-0.25,-0.8) to [out=0,in=90] (0,-1);
-\draw[red,very thick] (-0.25,-0.8) -- (0,1);
-\draw[red] (0.1,0) node{$E$};
-\draw[red,fill=red] (0,1) circle[radius=2pt] node[above]{$5$};
-\end{tikzpicture}
-\end{center}
-(Here we use Navid's convention for drawing maps to expanded degenerations, so that the box at level $1$ represents a \emph{single fibre} of the expanded degeneration, i.e.
-$E$ is mapped into a fibre and has zero horizontal degree.) Now, $\widetilde{C}$ is obtained from $C$ by bubbling a rational component $C_3$ at the single marking, and so the map $\widetilde{C} \to X_2$ is given by:
-\begin{center}
-\begin{tikzpicture}
-\draw (-1,-1) -- (1,-1);
-\draw (-1,-1) -- (-1,1);
-\draw (1,-1) -- (1,1);
-\draw (-1,1) -- (1,1);
-\draw (-1,-1) -- (-2,-2.5);
-\draw (-2,-2.5) -- (0,-2.5);
-\draw (0,-2.5) -- (1,-1);
-\draw (-1,1) -- (-1,3);
-\draw (-1,3) -- (1,3);
-\draw (1,3) -- (1,1);
-\draw[red,very thick] (-2,-2.5) -- (-0.5,-1);
-\draw[red] (-1,-1.5) node[right]{$C_1$};
-\draw[red,fill=red] (-0.5,-1) circle[radius=2pt];
-\draw[red] (-0.6,-1) node[above]{$2$};
-
-\draw[red,very thick] (0,-2.5) -- (0,-1);
-\draw[red] (-0.1,-1.5) node[right]{$C_2$};
-\draw[red,fill=red] (0,-1) circle[radius=2pt];
-\draw[red] (0.1,-1) node[above]{$3$};
-
-\draw[red,very thick] (-0.5,-1) to [out=90,in=180] (-0.25,-0.8) to [out=0,in=90] (0,-1);
-\draw[red,very thick] (-0.25,-0.8) -- (0,1);
-\draw[red] (0.1,0) node{$E$};
-\draw[red,fill=red] (0,1) circle[radius=2pt];
-\draw[red] (-0.2,1) node[above]{$5$};
-
-\draw[red, very thick] (0,1) -- (0,3);
-\draw[red] (0,2) node[right]{$C_3$};
-\draw[red,fill=red] (0,3) circle[radius=2pt] node[above]{$5$};
-\end{tikzpicture}
-\end{center}
-The map $\widetilde{C} \to \overline{C}$ contracts the elliptic component $E$, and so the map $\overline{C} \to X_1$ \emph{should} take the form:
-\begin{center}
-\begin{tikzpicture}
-\draw (-1,-1) -- (1,-1);
-\draw (-1,-1) -- (-1,1);
-\draw (1,-1) -- (1,1);
-\draw (-1,1) -- (1,1);
-\draw (-1,-1) -- (-2,-2.5);
-\draw (-2,-2.5) -- (0,-2.5);
-\draw (0,-2.5) -- (1,-1);
-\draw[red,very thick] (-2,-2.5) -- (0,-1);
-\draw[red] (-0.8,-1.7) node[below]{$\overline{C}_1$};
-\draw[red,fill=red] (0,-1) circle[radius=2pt];
-
-\draw[red,very thick] (0,-2.5) -- (0,-1);
-\draw[red] (-0.05,-1.5) node[right]{$\overline{C}_2$};
-\draw[red,fill=red] (0,-1) circle[radius=2pt];
-
-\draw[red,very thick] (0,-1) -- (0,1);
-\draw[red] (0.35,0) node{$\overline{C}_3$};
-\draw[red,fill=red] (0,1) circle[radius=2pt] node[above]{$5$};
-\end{tikzpicture}
-\end{center}
-We will now see that, in this example, the map drawn above cannot actually exist, and that this occurs precisely because we have violated the novel condition.
-
-We start by choosing a one-parameter smoothing $\mathcal{C} \to \Aaff^1$ of the centrally aligned curve $C$.
-This induces one-parameter smoothings $\widetilde{\mathcal{C}}$ of $\widetilde{C}$ and $\overline{\mathcal{C}}$ of $\overline{C}$.
-Since the factorisation condition must also hold in families, we must have a map $\overline{\mathcal{C}} \to \mathfrak{X}$, whose general fibre maps to the space $X_0=X$ (with no expansion) and whose general fibre maps to $X_1=X \sqcup_D Y$.
-
-We thus have a map $\ovm{C} \to \mathfrak{X}$, where $\mathfrak{X}$ is the total space of the expanded degeneration.
-This is obtained as the toric blow-up of $\PP^1 \times \Aaff^1$ at the point $(\infty,0)$.
-Thus it is also a smooth toric variety, with fan given by:
-\begin{center}
-\begin{tikzpicture}
-\draw[fill=black] (0,0) circle[radius=2pt];
-\draw[thick] (0,0) -- (2,0) node[above]{$\rho_1$};
-\draw[thick] (0,0) -- (1.75,1.75) node[right]{$\rho_2$};
-\draw[thick] (0,0) -- (0,2) node[left]{$\rho_3$};
-\draw[thick] (0,0) -- (0,-1.75) node[left]{$\rho_4$};
-\end{tikzpicture}
-\end{center}
-There is a map $\mathfrak{X} \to \Aaff^1$ whose general fibre is isomorphic to $X$ and whose central fibre is isomorphic to $X_1$.
-We see from the fan above that $\Pic(\mathfrak{X})$ is generated by $\OO_{\mathfrak{X}}(D_{\rho_i})$ for $i=1,\ldots,4$, subject to the relations:
-\begin{align*}
-\OO_{\mathfrak{X}}(D_{\rho_1}) \otimes \OO_{\mathfrak{X}}(D_{\rho_2}) & \cong \OO_{\mathfrak{X}} \\
-\OO_{\mathfrak{X}}(D_{\rho_2}) \otimes \OO_{\mathfrak{X}}(D_{\rho_3}) & \cong \OO_{\mathfrak{X}}(D_{\rho_4})
-\end{align*}
-Choosing as $\{\OO_{\mathfrak{X}}(D_{\rho_1}), \OO_{\mathfrak{X}}(D_{\rho_3})\}$ our minimal set of generators, we see that a map $\overline{\mathcal{C}} \to \mathfrak{X}$ is given by the data of line bundes $L_1$ and $L_3$ on $\overline{\mathcal{C}}$ together with sections:
-\begin{align*}
-s_1 & \in \HH^0(\overline{\mathcal{C}},L_1) \\
-s_2 & \in \HH^0(\overline{\mathcal{C}},L_1^{-1}) \\
-s_3 & \in \HH^0(\overline{\mathcal{C}},L_3) \\
-s_4 & \in \HH^0(\overline{\mathcal{C}},L_1^{-1}\otimes L_3)
-\end{align*}
-The divisors $D_{\rho_1}$ and $D_{\rho_2}$ are, respectively, the level-$0$ and level-$1$ pieces of the central fibre of $\mathfrak{X}$. Therefore we must have
-\begin{align*} & L_1 \cong \OO_{\overline{\mathcal{C}}}(a_1 \ov{C}_1 + a_2 \ov{C}_2) \\
-& L_1^{-1} \cong \OO_{\ov{C}}(a_3 \ov{C}_3)
-\end{align*}
-for some positive integers $a_1,a_2$ and $a_3$.
-Here we are using the fact that each $\ov{C}_i$ is a $\QQ$-Cartier divisor on $\ovm{C}$, so that (after possibly multipltying by some positive integer) the corresponding line bundle makes sense.
-Furthermore, the intersection multiplicites of $\ov{C}_1$ and $\ov{C}_2$ with the level-$1$ piece mean that we must have:
-\begin{align*} \deg(L_1^{-1}|_{\ov{C}_1}) & = 2\\
-\deg(L_1^{-1}|_{\ov{C}_2}) & = 3 \end{align*}
-We thus obtain:
-\begin{align*} a_3 (\ov{C}_1 \cdot \ov{C}_3)&  = 2 \\
-a_3 (\ov{C}_2 \cdot \ov{C}_3)& = 3 \end{align*}
-However, we claim that in fact $\ov{C}_1 \cdot \ov{C}_3 = \ov{C}_2 \cdot \ov{C}_3$, so that the above equations cannot hold.
-To calculate these intersection numbers, we pass to the semistable model of $\ovm{C}$.
-This is obtained by performing further blow-ups to $\ovt{C}$, resulting in a semistable model $\ovt{C}^{\operatorname{ss}}$of the following form:
-\begin{center}
-\begin{tikzpicture}
-\draw (-3,-3) -- (-3,2);
-\draw (-3,-2.5) node[left]{$E$};
-
-\draw (-3.5,1.5) -- (-0.5,1.5);
-\draw (-1.3,1.725) -- (0.5,0.5);
-\draw[fill=black] (0.8,0.5) circle[radius=0.5pt];
-\draw[fill=black] (0.9,0.5) circle[radius=0.5pt];
-\draw[fill=black] (1,0.5) circle[radius=0.5pt];
-\draw (3,1.725) -- (1.2,0.5);
-\draw (1.9,0.9) node[right]{$R_1^1$};
-\draw (2.5,1.5) -- (5,1.5);
-\draw (4,1.5) node[below]{$R_1$};
-
-\draw (-3.5,0) -- (-0.5,0);
-\draw (-1.3,0.225) -- (0.5,-1);
-\draw[fill=black] (0.8,-1) circle[radius=0.5pt];
-\draw[fill=black] (0.9,-1) circle[radius=0.5pt];
-\draw[fill=black] (1,-1) circle[radius=0.5pt];
-\draw (3,0.225) -- (1.2,-1);
-\draw (1.9,-0.6) node[right]{$R_2^1$};
-\draw (2.5,0) -- (5,0);
-\draw (4,0) node[below]{$R_2$};
-
-\draw (-3.5,-1.5) -- (-0.5,-1.5);
-\draw (-1.3,-1.275) -- (0.5,-2.5);
-\draw[fill=black] (0.8,-2.5) circle[radius=0.5pt];
-\draw[fill=black] (0.9,-2.5) circle[radius=0.5pt];
-\draw[fill=black] (1,-2.5) circle[radius=0.5pt];
-\draw (3,-1.275) -- (1.2,-2.5);
-\draw (2.5,-1.5) -- (5,-1.5);
-\draw (4,-1.5) node[below]{$R_3$};
-\end{tikzpicture}
-\end{center}
-Here the component labeled $E$ is smooth elliptic and all the other components are smooth rational.
-The projection $\pi: \ovt{C}^{\operatorname{ss}} \to \ovm{C}$ sends each $R_i$ to $\ov{C}_i$ and contracts all the other components.
-The semistable model has the advantage that the total space is regular, so the intersections are precisely those that you ``see'' in the picture.
-In particular, any two adjacent components have intersection $1$, and the self-intersection of any component is equal to minus the number of adjacent components.
-
-Now, $\ov{C}_i \cdot \ov{C}_j = (\pi^* \ov{C}_i)\cdot(\pi^* \ov{C}_j)$, so we want to show that:
-\begin{equation*} (\pi^* \ov{C}_1)\cdot(\pi^*\ov{C}_3) = (\pi^* \ov{C}_2)\cdot(\pi^*\ov{C}_3) \end{equation*}
-For each $i$, $\pi^*\ov{C}_i$ is equal to $R_i$ plus a non-negative linear combination of the components in $\ovt{C}^{\operatorname{ss}}$ contracted by $\pi$.
-By the projection formula, any component contracted by $\pi$ will multiply to zero with a class pulled back along $\pi$.
-Thus
-\begin{equation*} (\pi^* \ov{C}_1)\cdot(\pi^*\ov{C}_3) = R_1 \cdot (\pi^*\ov{C}_3) = a_3(R_1^1) \end{equation*}
-the coefficient of $R_1^1$ in $\pi^* \ov{C}_3$. Similarly
-\begin{equation*} (\pi^* \ov{C}_2) \cdot (\pi^* \ov{C}_3) = a_3(R_2^1) \end{equation*}
-the coefficient of $R_2^1$ in $\pi^* \ov{C}_3$. So we need to show that:
-\begin{equation*} a_3(R_1^1) = a_3(R_1^2) \end{equation*}
-Now, we have
-\begin{equation*} 0 = R_1^1 \cdot (\pi^* \ov{C}_3) = a_3(R_1^2) - 2a_3(R_1^1) \end{equation*}
-because $(R_1^1)^2=-2$. So $a_3(R_1^1) = a_3(R_1^2)/2$. Similarly:
-\begin{equation*} 0 = R_1^2 \cdot (\pi^*\ov{C}_3) = a_3(R_1^1) - 2a_3(R_1^2) + a_3(R_1^3) = -3a_3(R_1^1) + a_3(R_1^3) \end{equation*}
-So $a_3(R_1^1) = a_3(R_1^3)/3$. Continuing in this way, we find that
-\begin{equation*} a_3(R_1^1) = a_3(E)/l_1 \end{equation*}
-where $l_1$ is the length of the rational tail connecting $E$ to $R_1$.
-Similarly $a_3(R_1^2) = a_3(E)/l_2$.
-But by Smyth's balancing condition for the semistable model \cite[Proposition 2.11]{SMY1}, we must have $l_1=l_2$.
-This concludes the proof that $\ov{C}_1 \cdot \ov{C}_3 = \ov{C}_2 \cdot \ov{C}_3$, which shows the necessity of the novel condition in this example.
-
-Notice that here we used the fact that the rational tails $\ov{C}_1$ and $\ov{C}_2$ are adjacent to the same irreducible component (namely $E$) of the core.\qed
-\end{example}
-
-\subsection{Proof that the relative space equals the closure of the nice locus.}
-We now want to show that the relative space in the centrally aligned setting is equal to the closure of the nice locus; irreducibility then follows immediately. We start with one direction:
-
-\begin{lem}
-The closure of the nice locus is contained in the relative space.
-\end{lem}
-\begin{proof}
-We address the relative conditions one at a time.
-Notice that they are all obviously satisfied on the nice locus.
-Also, Gathmann's relative condition is obviously closed; see \cite[Proposition 4.9]{Vre}.
-
-It remains to show that the novel condition is satisfied on the closure of the nice locus. Here is no proof but rather some heuristics. Consider for example a map similar to the one above
-\begin{center}
-\begin{tikzpicture}
-\draw[color=brown] (0,0) node[left]{$E$} -- (4,0);
-\draw[fill=black] (1,0) circle[radius=2pt] node[above]{$x_1$};
-\draw[fill=black] (2,0) circle[radius=2pt] node[below right]{$y_1$};
-\draw[fill=black] (3,0) circle[radius=2pt] node[below right]{$y_2$};
-\draw (2,1.5) node[left]{$R_1$} (3,1.5) node[left]{$R_2$};
-\draw (2,-1) -- (2,2) node[above]{$3$} (3,-1) -- (3,2) node[above]{$2$};
-\draw[->] (5,0.5) -- (8,0.5);
-\draw (9,-1) -- (9,2) node[above]{$\PP^1$};
-\draw[fill=black] (9,0) circle[radius=2pt] node[right]{$H$};
-\draw[fill=black] (9,1.5) circle[radius=2pt] node[right]{$H'$};
-\end{tikzpicture}
-\end{center}
-and assume that it is in the closure of the nice locus; I want to argue that the two smoothing parameters cannot be identified.
-By the previous points I may assume that the factorisation property and Gathmann's relative conditions hold.
-I have a diagram:
-\bcd
-\cC^{\rm{ss}}\ar[r]\ar[dr] & \widetilde \cC\ar[r]\ar[d] & \overline \cC\ar[d,"\bar f"] \\
-& \cC\ar[r,"f"] & X
-\ecd
-where I have included the semistable model of $\cC$ (and $\widetilde \cC$), thought of as a curve marked with $f^{-1}(H')$ as well, where $H\neq H'\in\PP^1$.
-
-Notice that $\cC$ is a normal surface with at worst singular points at the nodes of $C=\cC_0$ (the central fibre $C=E+R_1+R_2$ is Cartier and a variety is smooth at any smooth point of a Cartier divisor) and the singularities are of type $A_{n_i},\ i=1,2$ (from the deformation theory of nodal curves).
-
-I assume maximal multiplicity $\sum\alpha=d$, i.e.
-I am looking at the moduli space $\M{1}{(5)}{\PP^1|H}{5}$.
-Hence the line bundle and $s_0$ are determined as $f^*\OO_{\PP^1}(1)=\OO_{\cC}(5x_1)\otimes\OO_{\cC}(\beta E)$ for some (positive rational) $\beta$ and $s_0$ is the natural inclusion of $\OO_{\cC}$ (up to $\Gm$).
-
-The map is totally ramified at $y_i$ by Gathmann's condition. We conclude:
-\[ \frac{\beta}{n_i+1}=(\beta E)\cdot R_i=m^{(i)}\]
-Hence, having fixed the multiplicities, the two possible singularities of $\cC$ determine each other.
-In our example we may pick $n_1=1,\ n_2=2,\ \beta=6$.
-But knowing the singularity determines the semistable model: in our case $y_1$ is replaced by a $(-2)$-curve and $y_2$ by a chain of two $(-2)$-curves.
-Now we know from the work of Smyth \cite[Proposition 2.12]{SMY1} that the exceptional locus of $\cC^{\rm{ss}}\to\overline\cC$ is balanced, therefore we may deduce that $\bar f$ is constant on the branch of the genus $1$ singularity to which $R_2$ is joined, so $\overline C$ looks like this:
-
-\begin{center}
-\begin{tikzpicture}
-\draw (-1,0) -- (1,0) node[right]{$\overline R_1$};
-\draw[color=gray!50] (-1,-1) -- (1,1);
-\draw[fill=black] (-.75,-.75) circle[radius=2pt] node[left]{$x_1$};
-\draw[color=gray!50] (0,-1) -- (0,1);
-\draw (-1,1.5) node[above left]{$\overline R_2$} -- (.25,.5);
-\end{tikzpicture}
-\end{center}
-where a gray line is contracted by the map.
-On the other hand if $\delta=\lambda(v_1)=\lambda(v_2)$ then the prescription of \cite[Proposition 3.6.1]{RSPW} implies that $\tilde C\to \overline C$ looks like:
-\begin{center}
-\begin{tikzpicture}
-\draw[color=brown] (0,0) node[left]{$E$} -- (4,0);
-\draw[color=gray!50] (1,-1) -- (1,2);
-\draw[fill=black] (1,1) circle[radius=2pt] node[left]{$x_1$};
-\draw (2,1.5) node[left]{$R_1$} (3,1.5) node[left]{$R_2$};
-\draw (2,-1) -- (2,2) node[above]{$3$} (3,-1) -- (3,2) node[above]{$2$};
-\draw[->] (5,0.5) -- (7,0.5);
-\draw (8,0.5) -- (10,0.5) node[right]{$\overline R_1$};
-\draw[color=gray!50] (8,-.5) -- (10,1.5);
-\draw[fill=black] (8.25,-.25) circle[radius=2pt] node[left]{$x_1$};
-\draw (9,-.5) -- (9,1.5) node[above left]{$\overline R_2$};
-\end{tikzpicture}
-\end{center}
-which is a contradiction.
-\end{proof}
-
-\subsection{Novel Condition 2.0}
-
-This is done with $(\PP^1,H)$ in mind; in general it will need to be modified to account for internal components of positive degree.
-
-\textbf{Novel condition 2.0:} if $v_1,v_2$ are two vertices belonging to $R_\delta$, then the corresponding tangencies $m^{(j_1)}$ and $m^{(j_2)}$ to $H$ must be equal \emph{if the corresponding rational tails are attached to the same irreducible component of $\plC_0$}.
-Here $R_\delta$ is the set of vertices $v \in \plC$ with $\lambda(v)=\delta$ and $\plC_0$ is the set of vertices with $\lambda(v)<\delta$.
-
-\textbf{Sketch of ``sufficient'' direction}: Denote by $S_0=E,S_1,\ldots,S_k$ the irreducible components of $Z$ and assume $E$ is smooth elliptic (or the core).
-Every $S_i$ for $i\geq 0$ comes with a bunch of special points: divide them into $B^-(i)=$ the singleton representing the only node separating $S_i$ from $S_0$ (this is not defined for $i=0$); $B^+(i)=$ the set of remaining nodes; and $A(i)=$ the set of markings on $S_i$.
-Start with the trivial family $E\times\Aaff^1$, where $E$ is marked with the points of $B(0)=B^+(0)$ and $A(0)$.
-Now perform a weighted blow-up at the points $\{q\in B(0)\}\times\{0\in\Aaff^1\}$ of weight $r_q$; call each resulting rational tail $S_i$ correspondingly to the original picture.
-On $S_i$ we may mark points $B^+(i)$ and $A(i)$ in such a way that the resulting point of $\oM_{0,1+|B^+(i)|+|A(i)|}$ corresponds to the one we started with.
-Now blow up this family in all the $B^+(i)\times\{0\}$ with a weight.
-Keep going until you have recreated $C$.
-Call $R_j$ the first external components, namely those corresponding to the vertices with $\lambda(v)\geq\delta$, $\nexists v'$ with $\lambda(v)>\lambda(v')\geq\delta$.
-
-We define the line bundle $\mathcal L=\OO_{\cC}(\sum \beta_iS_i)(\sum \alpha_ix_i)$; let's look at the equations that it gives us, starting from the outside.
-\begin{enumerate}
- \item $m^{(j)}=\mathcal L_{|R_j}=\frac{\beta^-(j)}{r_{q^-(j)}}$;
- \item on every $S_i, i\geq1$ we can prove inductively that:
- \[0=\mathcal L_{|S_i}=\frac{\beta^-(i)-\beta_i}{r_{q^-(i)}}+\sum_{x_h\in A(i)}\alpha_i+\sum_{y_h\in B^+(i)}M^{(h)},\]
- where I have denoted by $M^{(h)}$ the sum of all the contributions (both $\alpha_l$ and $m^{(l)}$) coming from the rational tree attached to the corresponding point of $B^+(i)$;
- \item it turns out that $\OO_{S_0}\simeq\mathcal L_{|S_0}$ is precisely Gathmann's condition (in the numeric form if $S_0$ is a circle of rational curves). 
-\end{enumerate}
-Now notice that $\lambda(v_j)=\lambda(v_j')$ may happen only at the first external components; \marginpar{is this true?
-if not, probably there are contributions $M^{(h)}$ and $M^{(h')}$ to equate} in this case $r_{q^-(j)}=r_{q^-(j')}$, and from the first equation we see that $m^{(j)}=m^{(j')}$ if they are attached to the same component ($\beta^-(j)=\beta^-(j')$).
-The second equation can be made to hold for every $S_i$ by appropriately choosing $\beta^-(i), r_{q^-(i)}$. The last equation is automatically satisfied.
-
-Extending sections is the usual business of exploiting the fatorisation through the elliptic $m$-fold.
-
-\textbf{Sketch of ``necessary'' direction}: pick a smoothing $\cC$ of $(C,f)$.
-Suppose that $\lambda(v)=\lambda(v')$ and the corresponding $R$, $R'$ are attached to the same $S_i$, i.e.
-they share the same the tree separating them from $C_0$.
-Notice that $R$ and $R'$ map to two branches of the Smyth singularity.
-Looking at the semistable model of $\cC$, it follows that (the strict transforms of) $R$ and $R'$ still share the same tree there.
-Then by writing $(f^{\rm{ss}})^*\OO_{\PP}(1)=\OO_{\cC^{\rm{ss}}}(\sum \beta_iS_i)(\sum \alpha_ix_i)$ and intersecting with $R$, $R'$, we see that they must have the same contact order to $H$.
-
-\subsection{Details of the proof}
-
-\subsection*{Case 1: non-contracted genus one internal component} Assume that the curve takes the form
-\begin{equation*} C = C_0 \cup C_1 \cup \ldots \cup C_k \end{equation*}
-where all the $C_i$ are smooth, $C_0$ has genus one, all the other $C_i$ have genus zero, and for $i \in \{1,\ldots,k\}$, $C_i$ intersects $C_0$ at a single node (denoted $q_i$) and does not intersect any other components.
-
-Suppose furthermore that $C_0$ is a non-contracted \emph{internal component}, meaning that it is mapped into $H$ via $f$, and that $C_1$,\ldots,$C_k$ are \emph{external components}, meaning that they are not mapped into $H$ via $f$.
-The picture is:
-
-[FIGURE]
-
-Suppose that this is a relative stable map.
-This means that [BLAH].
-We claim that it can be smoothed to a relative stable map in the nice locus.
-The construction depends on choosing an appropriate smoothing of the curve $C$, so that the map also smooths.
-
-We start with $W = C_0 \times \Aaff^1_t$ (where $t$ denotes a fixed co-ordinate on the affine line).
-This is a smooth surface, fibred over $\Aaff^1_t$, with fibre equal to the elliptic curve $C_0$.
-Consider the points $q_1, \ldots, q_k$ on $C_0$.
-We will perform a series of weighted blow-ups at the points $(q_i,0) \in W$, in order to obtain a surface whose general fibre is smooth (in fact, isomorphic to $C_0$) and whose central fibre is isomorphic to $C$.
-
-Fix $i \in \{1,\ldots,k\}$ and let $m_i$ be the multiplicity of $f$ with $H$ at $q_i \in C_i$. We define:
-\begin{equation*} l = \operatorname{lcm}(m_1,\ldots,m_k) \qquad r_i = l/m_i \end{equation*}
-We now blow-up the surface $W$ at the points $(q_i,0)$ with weight $r_i$ in the horizontal direction and weight $1$ in the vertical direction: if $x_i$ is a local co-ordinate for the fibre around $q_i$, this means that we blow-up in the ideal $(x_i,t^{r_i})$.
-
-The result is a fibred surface $W^\prime \to \Aaff^1_t$ with general fibre equal to $C_0$ and central fibre $W^\prime_0 \cong C$.
-The total space of $W^\prime$ is no longer smooth (its singular points are [BLAH]), but this is not a problem since the projection to $\Aaff^1_t$ is still flat.
-The central fibre is a linearly trivial Cartier divisor:
-\begin{equation*} W^\prime_0 = C_0 + C_1 + \ldots + C_k = 0 \in \Pic W^\prime \end{equation*}
-For $i \in \{1,\ldots,k\}$ we have that $r_i C_i$ is Cartier, although the same is not necessarily true of $C_i$. Furthermore, since
-\begin{equation*} l C_0 = - \sum_{i=1}^k l C_i = - \sum_{i=1}^k m_i (r_i C_i) \end{equation*}
-in $A_1(W^\prime)$, it follows that $lC_0$ is Cartier. Finally, a local computation shows that
-\begin{equation*} r_i C_i \cdot C_0 = 1 \end{equation*}
-for $i \in \{1,\ldots,k\}$.
-Now, let $x_1,\ldots,x_n$ denote the marked points of $C$.
-These are smooth points of the central fibre $W^\prime_0$, and hence can be extended to Cartier divisors $\tilde{x}_1,\ldots,\tilde{x}_n$ on $W^\prime$.
-Consider the line bundle:
-\begin{equation*} \tilde{L} = \OO_{W^\prime}(l C_0 + \Sigma_{j=1}^n \alpha_j \tilde{x}_j) \end{equation*}
-on $W^\prime$.
-We claim that this gives a smoothing of the line bundle $L=f^*\OO(1)$ on $C$, i.e.
-that $\tilde{L}|_{W^\prime_0} = L$.
-We show this by first restricting $\tilde{L}$ to each of the components $C_i$ of $W^\prime_0 \cong C$.
-For $i \in \{1,\ldots,k\}$, we have
-\begin{align*} \tilde{L}|_{C_i} & = \OO_{C_i} \left( (l C_0 \cdot C_i) q_i + \sum_{x_j \in C_i} \alpha_j x_j \right) = \OO_{C_i} \left( (l/r_i) q_i + \sum_{x_j \in C_i} \alpha_j x_j \right)\\
-& = \OO_{C_i} \left( m_i q_i + \sum_{x_j \in C_i} \alpha_j x_j \right) = L|_{C_i} \end{align*}
-while for $i=0$ we have:
-\begin{align*} \tilde{L}|_{C_0} & = \OO_{C_0} \left( - \sum_{i=1}^k (l C_i \cdot C_0) q_i + \sum_{x_j \in C_0} \alpha_j x_j \right) = \OO_{C_0} \left( - \sum_{i=1}^k m_i q_i + \sum_{x_j \in C_0} \alpha_j x_j \right)  = L|_{C_0} \end{align*}
-Finally the fact that $\tilde{L}|_{W^\prime_0} = L$ follows from the fact that the dual intersection graph of $C$ has genus zero.
-
-Now, $\tilde{L}$ comes with a unique section whose restriction to $W^\prime_0 \cong C$ is $s_0$.
-After we extend the sections $s_1,\ldots,s_N$, it is clear that the resulting stable map is in the nice locus (i.e.
-that it is not mapped into $H$).
-
-In order to extend the sections $s_1,\ldots,s_N$, we simply check that they are unobstructed. The space containing the obstructions to extending the sections is \cite[Theorem 3.1]{WangDeformations}:
-\begin{equation*} \HH^1(C,L) \end{equation*}
-By taking the normalisation exact sequence for $C$, tensoring with $L$ and passing to cohomology, we obtain an exact sequence:
-\begin{align*} 0 \to & \HH^0(C,L) \to \bigoplus_{i=0}^k \HH^0(C_i,L) \xrightarrow{\theta} \bigoplus_{i=1}^k L_{q_i} \to \\
-\to & \HH^1(C,L) \to \bigoplus_{i=0}^k \HH^1(C_i,L) \to 0 \end{align*}
-Now, each of $C_1,\ldots,C_k$ is isomorphic to $\PP^1$ and $L|_{C_i}$ has non-negative degree; hence the map $\theta$ is surjective. Thus the map
-\begin{equation*} \HH^1(C,L) \to \bigoplus_{i=0}^k \HH^1(C_i,L) \end{equation*}
-is an isomorphism. But $\HH^1(C_i,L)=0$ for $i \in \{1,\ldots,k\}$ since $C_i \cong \PP^1$ and $L|_{C_i}$ has non-negative degree; also we have by Serre duality
-\begin{equation*} \HH^1(C_0,L) \cong \HH^0(C_0, L^\vee \otimes \omega_{C_0}) = \HH^0(C_0,L^\vee) = 0 \end{equation*}
-where the penultimate equality holds because $\operatorname{g}(C_0)=1$ and the last equality holds because $L|_{C_0}$ has \emph{strictly} positive degree (here we are using the fact that $f|_{C_0}$ is non-constant).
-
-To conclude, we have a family $\tilde{C} = W^\prime$ of nodal curves and a map from this family to $\PP^N$
-\bcd
-\tilde{C} \ar[r,"\tilde{f}"] \ar[d,"\pi"] & \PP^N \\
-\Aaff^1_t & \,
-\ecd
-such that when we restrict to $0 \in \Aaff^1_t$ we recover the map $f\colon C \to \PP^N$ and such that the general fibre is an element of the nice locus.
-
-\textcolor{red}{Address the case that $C_0$ is not irreducible, and that $C_i,\ i\neq 0$ are chains of $\PP^1$'s.}\marginpar{This should follow from gluing, whatever that means.}
-
-\subsection*{Case 2: contracted genus one internal component} This is similar to the previous case, but slightly more delicate.
-The smoothing $W'$, the line bundle $\tilde L$ and the section $s_0$ are constructed as before.
-Now, however, $\HH^1(C,L)\neq 0$, so we need to work harder to show that we can extend the other sections.
-
-Before extending the sections let us first extend the centrally aligned log structure.
-On the base $\Aaff^1_t$ the chart sends $e_i \in \N^r$ to $t^{r_i}$.
-By the novel condition, if $e_i=e_j$ in the minimal centrally aligned structure that we start with on $C$, then $r_i=r_j$, so the chart that we have just defined factors indeed through the sharpening of the submonoid of $\mathbb Z^r$ generated by $\N^r$ and the differences $\lambda(v) - \lambda(w)$.
-We declare the contraction radius $\delta$ to be $e_i$ for those $i$'s corresponding to branches of the genus $1$ singularity on which $\bar f$ is non-constant.
-\marginpar{actually this sounds like bs and I probably have $\delta$ already?}
-
-The central alignment provides us with a diagram:
-\bcd
-\widetilde \cC\ar[r]\ar[d] & \overline \cC \\
-\cC & 
-\ecd
-We can now extend the sections $\bar s_1,\ldots,\bar s_N$ onto $\overline \cC$ because $\HH^1(\overline C,\bar L)=0$, so we get a map $\bar F\colon\overline\cC\to\PP^N$ deforming $\bar f$.
-Finally we claim that $F\colon\cC\to\PP^N$ is the stable model of $\bar F$.
-
 \bibliographystyle{alpha}

### 2018-11-17 genus-one-relative-maps.tex

--- 2018-11-13 genus-one-relative-maps.tex
@@
 
+\newcommand{\basenote}[1]{\footnote{\color{red}#1}}
+
 \newcommand{\plC}{\scalebox{0.8}[1.3]{$\sqsubset$}}
@@
 
+\newcommand{\formLine}{\spec \mathbbm{k}\llbracket t \rrbracket}
+\newcommand{\spec}{\operatorname{Spec}}
 \newcommand{\pM}{\pazocal{M}}
+
 \newcommand{\TT}{\operatorname{T}}
@@
 \newcommand{\VZc}[4]{\mathcal{V\!Z}^{\rm{ctr}}_{#1,#2}(#3,#4)}
+\newcommand{\VZclb}[4]{\mathcal{V\!Z}^{\rm{ctr,lb}}_{#1,#2}(#3,#4)}
+\newcommand{\VZco}[4]{\mathcal{V\!Z}^{\rm{ctr},\circ}_{#1,#2}(#3,#4)}
 \newcommand{\VZcLi}[4]{\mathcal{V\!Z}^{\rm{ctr, Li}}_{#1,#2}(#3,#4)}
@@
 \section{Definition of centrally aligned relative space}
+Fix a vector $\alpha=(\alpha_1,\ldots,\alpha_n)$ of tangency conditions, and suppose for the moment that $\Sigma \alpha = d$.
+We consider the so-called \emph{nice locus} of relative centrally aligned maps.
+This is the locally closed substack of $\VZc{1}{n}{\PP^N}{d}$ consisting of centrally aligned maps $(C,x_1,\ldots,x_n,\Mcal_C,\delta,f)$ such that:
+\begin{enumerate}
+\item the source curve $C$ is smooth;
+\item $C$ is not mapped entirely into $H$ by $f$;
+\item the points of $C$ which are mapped into $H$ (necessarily a finite number by the previous condition) are all marked, with the map having tangency $\alpha_i$ to $H$ at the marking $x_i$.
+\end{enumerate}
+These conditions mean that $\delta=0$ and that the log structure $\Mcal_C$ (which is a minimal centrally aligned log structure) is equal to the minimal structure for a log smooth curve, which in this case (since there are no nodes) is just the divisorial log structure with respect to the markings $x_1,\ldots,x_n$.
+
+This is a locally closed substack of expected codimension $\Sigma \alpha=d$, and is denoted:
+\begin{equation*} \VZco{1}{\alpha}{\PP^N|H}{d} \end{equation*}
+It has a well-defined stack structure since it is a moduli space. Note that it is irreducible, since we can find a parametrisation for it over $\Mfrak_{1,n}$.
+
+We now define the \emph{centrally aligned relative space} to be the closure of the nice locus:
+\begin{equation*} \VZc{1}{\alpha}{\PP^N|H}{d} := \overline{\VZco{1}{\alpha}{\PP^N|H}{d}} \subseteq \VZc{1}{n}{\PP^N}{d} \end{equation*}
+This inherits the natural structure of a stack from the stack structure of the nice locus.
+It is proper since it is a closed substack of a proper stack, and it is irreducible because it is the closure of an irreducible stack.
+Hence it admits a fundamental class, which we can use to define \emph{reduced relative Gromov--Witten invariants}:
+\begin{equation*} \langle \tau_{k_1}(\gamma_1), \ldots, \tau_{k_n}(\gamma_n) \rangle^{\PP^N|H, \operatorname{red}}_{0,\alpha,d} := \int_{[\VZc{1}{\alpha}{\PP^N|H}{d}]} \prod_{i=1}^n \ev_i^*(\gamma_i) \cdot \psi_i^{k_i} \end{equation*}
+
 \section{Characterisation of the closed points of the relative space}
+It will be important for our purposes to have an understanding of the boundary of the relative space, i.e.
+what we add in when we take the closure of the nice locus.
+In this section we will describe this boundary on the level of closed points.
+
+\begin{prop} \label{closed pts of relative space} A centrally aligned map over a closed point $\spec \mathbbm{k}$ is in the relative space if and only if the following two conditions are satisfied:
+\begin{enumerate}
+\item \emph{Gathmann's relative condition:} for each connected component $Z$ of $f^{-1}(Y)$, either:
+\begin{enumerate}
+\item $Z$ is a single point of $C$, in which case if $Z=x_i$ is a marking then we require that the multiplicity of $f$ at $x_i$ along $Y$ is at least $\alpha_i$ (if $Z$ is not a marking then there is no condition);
+\item $Z$ is a subcurve $Z \subseteq C$, in which case we require that
+\begin{equation*} f^*[Y]|_Z -\sum_{x_i\in Z}\alpha_ix_i\end{equation*}
+is an effective class in $\Achow_0(Z)$.
+\end{enumerate}
+
+\item \emph{Compatibility condition:} this applies when the minimal subcurve of genus one (the \emph{circuit}) is contracted to a point in $Y$.
+In this case we require that there is a local morphism of monoids:
+\begin{equation*} Q^{\operatorname{GS}} \to \N\end{equation*}
+such that the dashed arrow can be filled in to make the following square commutative:
+\bcd
+Q^{\operatorname{log}} \ar[r]\ar[d] & Q^{\operatorname{GS}} \ar[d] \\
+Q^{\operatorname{ctr}}\ar[r,dashed] & \N
+\ecd
+It is obvious from the construction that the map $Q^{\operatorname{ctr}} \to \N$ is unique if it exists
+\end{enumerate}
+\end{prop}
+
+\begin{remark} The monoid $Q^{\operatorname{GS}}$ depends on a choice of \emph{type}, in this case a choice of the $u_q$ (the $u_p$ are already determined by the choice of $\alpha$).
+Here we are not allowed to choose a random type, but have to choose one which is compatible with the underlying stable map, in the sense that the modified tropical balancing condition is satisfied.
+The Gathmann-style condition (1) is a necessary condition for the existence of a compatible type (on the level of $\Pic C$).
+
+Remember that we get one balancing condition for each generator of $\Gamma(C, f^* \overline{\Mcal}_H)$, so as well as there being a balancing condition for each internal component there is also one wherever the curve intersects the divisor in an isolate point (where for instance we get that $u_q = m_q$ at nodes connecting an external to an internal component).
+Also we require this condition to take place in $\Pic(C)$, but we are entitled at any point to restrict to components of $C$ or take degrees to get (in general weaker) conditions.
+\end{remark}
+
+\begin{remark} Gathmann's condition obviously extends to the case $\Sigma \alpha \leq d$.
+\basenote{What is the correct generalisation of the compatibility condition?} Here we try to make the condition for a curve component of $f^{-1}(Y)$ into an easily verifiable criterion: if $Z$ is a smooth elliptic curve, recall that every line bundle of positive degree on it is effective, hence the relative condition can be rephrased as the following numerical criterion:
+\begin{equation*} f_*[Z]\cdot [Y]+\sum_{j=1}^r m^{(j)}\geq \sum_{x_i\in Z}\alpha_i \end{equation*}
+together with the additional requirement that, when the above is an equality, there is an isomorphism of line bundles:
+\begin{equation}\label{eqn:eq_in_Pic}
+(f|_{Z})^*\OO_X(Y) \otimes \OO_Z\left(\sum_{j=1}^r m^{(j)}y_j\right)=\OO_Z\left(\sum_{x_i\in Z}\alpha_ix_i\right) 
+\end{equation}
+
+If $Z$ is reducible, the correct extension is not to impose the same condition componentwise; rather, we should ask the numerical condition for the total degree, and, if $Z$ is obtained by gluing a smooth elliptic curve $E$ with a forest of rational trees $T_i$ at roots $q^E_i$, then the line bundle equality \eqref{eqn:eq_in_Pic} should be required in $\Pic(E)$ after counting each $q^E_i$ towards the left hand side with multiplicity:
+\[f_*[T_i]\cdot [Y]+\sum_{\text{external components attached to $T_i$}} m^{(j)} \geq \sum_{x_j\in T_i}\alpha_j\]
+%That this is the right thing to do follows from the proof that Gathmann's relative space is the projection of Jun Li's moduli space of maps to the expanded pair after contracting the higher levels of the accordion.
+\end{remark}
+
+\begin{proof}[Proof of Proposition \ref{closed pts of relative space}]
+First suppose that the conditions (1) and (2) of the Proposition are satisfied; so we have Gathmann's condition on the level of line bundles and a factorisation:
+\bcd
+Q^{\operatorname{log}} \ar[r]\ar[d] & Q^{\operatorname{GS}} \ar[d] \\
+Q^{\operatorname{ctr}}\ar[r] & \N
+\ecd
+We will construct a smoothing of the centrally aligned map, i.e.
+a $1$-parameter family whose central fibre is the map we started with and whose general fibre is in the nice locus.
+The construction proceeds in the following order:
+\begin{enumerate}
+\item construct the smoothing $\Ccal$ of the source curve $C$, as a scheme;
+\item construct the extension $(\Mcal_{\Ccal},\delta)$ of the central alignment on $C$;
+\item construct the extension $\Lcal$ of the line bundle $L=f^*\OO_{\PP^N}(H)$ from $C$ to $\Ccal$;
+\item construct the extension of the section $u_0 \in \HH^0(C,L)$;
+\item construct the extensions of the sections $u_1,\ldots,u_N$.
+\end{enumerate}
+
+We start with (1), i.e.
+the construction of the source curve $\Ccal$ as a family over $\spec \mathbbm{k}\llbracket t \rrbracket$.
+Let $E \subseteq C$ be the circuit, i.e.
+the minimal genus one subcurve.
+This is either a smooth elliptic curve or a wheel of rational curves.
+Look at the corresponding moduli point $[E] \in \Mfrak_{1,n}$.
+Since this is a smooth stack, we may choose an \'etale chart which locally looks like the tangent space of the stack, which in this case is the deformation space of the elliptic curve.
+This contains a factor $\Aaff^p$ where $p$ is the number of nodes of $C$; the $i$th co-ordinate axis corresponds to a smoothing of the $i$th node, keeping the others fixed, while the generic point of the corresponding orthogonal hyperplane corresponds to a deformation which smooths all the nodes except the $i$th one.
+
+We need to choose a map $\formLine \to \Mfrak_{1,n}$ which sends the closed point to $[E]$ and the generic point to the locus of smooth curves.
+By the discussion of the previous paragraph, we can do this by choosing a map $\formLine \to \Aaff^p$ which sends the closed point to the origin and the generic point to the complmenet $\Gm^p \subseteq \Aaff^p$ of the co-ordinate axes.
+We can certainly choose such a map; furthermore, if for each node $q$ we choose a positive integer $r_q$, then we can choose the map so that it has tangency order $r_q$ to the hyperplane of $\Aaff^p$ corresponding to $q$.
+In terms of the resulting curve $\Ccal$ over $\formLine$, this means that if $C_1, C_2 \subseteq \Ccal$ are the two branches of $C$ around $q$, then these are $\QQ$-Cartier divisors in $\Ccal$, with:
+\begin{equation*} C_1 \cdot C_2 = 1/r_q \end{equation*}
+The weights $r_q$ are chosen by looking at the map $Q^{\operatorname{log}} \to \N$; this map is local since the map $Q^{\operatorname{log}} \to Q^{\operatorname{GS}}$ is local\basenote{Is this always true?
+Isn't this only true if there exists a log lifting?
+But maybe it's always true for Deligne--Faltings pairs.} and the map $Q^{\operatorname{GS}} \to \N$ is local by assumption.
+Thus each generator $e_q \in Q^{\operatorname{log}}$ maps to a positive integer $r_q$, and this is the weight we choose.
+We have thus constructed the smoothing $\Ccal$ of $C$.
+
+We now move on to step (2), which involves extending the central alignment from $C$ to $\Ccal$.
+This is a relative trivial step: since the general fibre of $\Ccal$ is smooth, there is no choice of ordering of the markings or of contraction radius, and its minimal centrally aligned monoid is trivial.
+We can thus take the log structures on the central fibre as charts for the log structures on the deformation.
+To be more precise, in the base we have a chart:
+\begin{align*} Q^{\operatorname{ctr}} & \to \mathbbm{k} \llbracket t \rrbracket \\
+e_q & \mapsto t^{r_q} \end{align*}
+Note that this is well-defined by the fact that we have the factorisation $Q^{\operatorname{ctr}} \to \N$.
+This defines a log structure $\Mcal_S^{\operatorname{ctr}}$ on $S$.
+On the other hand the morphism $S \to \Mfrak_{1,n}$ defines another log structure $\Mcal_S^{\operatorname{log}}$ on $S$ corresponding to the minimal structure of a log smooth curve on $\Ccal$.
+There is a map $\Mcal_S^{\operatorname{log}} \to \Mcal_S^{\operatorname{ctr}}$ induced by the map of charts $Q^{\operatorname{log}} \to Q^{\operatorname{ctr}}$, and this gives a diagram:
+\bcd
+& (C,\Mcal_C^{\operatorname{log}}) \ar[d] \\
+(S,\Mcal_S^{\operatorname{ctr}}) \ar[r] & (S,\Mcal_S^{\operatorname{log}})
+\ecd
+We define $(\Ccal,\Mcal_{\Ccal}^{\operatorname{ctr}})$ to be the fibre product.
+This is clearly a log smooth centrally aligned curve over $(S,\Mcal_S^{\operatorname{ctr}})$, with radius $\delta$ given by the radius on the central fibre (note that $\overline{\Mcal_S}^{\operatorname{ctr}}$ is supported on the closed point).
+This completes step (2).
+
+We now begin step (3), that of extending the line bundle $L=f^*\OO_{\PP^N}(H)$ on $C$ to a line bundle $\Lcal$ on $\Ccal$.
+In case it hasn't been mentioned already, we assume that $H=\{ z_0=0\}$ is a co-ordinate hyperplane.
+
+Let us write $C$ in terms of its irreducible components as $C = C_1 \cup \ldots \cup C_m$ with $C_1,\ldots,C_r$ internal and the rest external. We define the line bundle $\Lcal$ as
+\begin{equation*} \Lcal = \OO_{\Ccal}\left(\sum_{i=1}^r \gamma_i C_i + \sum_{i=1}^n \alpha_i \tilde{x}_i \right) \end{equation*}
+where each $\gamma_i$ is a positive integer obtained as the image under $Q^{\operatorname{GS}} \to \N$ of the generator corresponding to $C_i$, and the $\tilde{x}_i$ are extensions of the Cartier divisors $x_i$ to all of $\Ccal$.
+
+This comes with a natural section (or rather, a $\CC^*$-equivalence class of sections) $\tilde{u}_0$ given by the divisor in brackets above, and this can be chosen in a unique way so that it restricts to $u_0$ on the central fibre of $\Ccal$.
+This completes step (4).
+
+Now we must verify that $\Lcal|_C=L$. For each external component $C_j$, we have
+\begin{equation*} \Lcal|_{C_j} = \OO_{C_j} \left( \sum_{x_i \in C_j} \alpha_i x_i + \sum_{q_i \in C_j} (\gamma_i/r_i) q_j \right) \end{equation*}
+where the latter sum is over nodes of $C_j$ which connect $C_j$ to an internal component $C_i$. We thus need
+\begin{equation*} m_i = \gamma_i / r_i \end{equation*}
+in order to conclude that $\Lcal|_{C_j} = L|_{C_j}$.
+But this is true, because in $Q^{\operatorname{GS}}$ the generator corresponding to the internal component $C_i$ is identified with $u_{q_i}$ times the generator corresponding to $q_i$, and $u_{q_i}=m_i$ by the fact that the type we chose to define $Q^{\operatorname{GS}}$ must satisfy the tropical balancing condition.
+Pushing forward this relation from $Q^{\operatorname{GS}}$ to $\N$ gives the equation above.
+This argument also applies when we have an external subcurve $Z \subseteq C$ which is a wheel of rational components.
+
+Now let us consider an internal component $C_j$. We have
+\begin{align*} \Lcal|_{C_j} & = \OO_{C_j} \left( \sum_{x_i \in C_j} \alpha_i x_i + \sum_{\tilde{q}_i \in C_j} (\gamma_i/r_i) \tilde{q}_i \right) \otimes \OO_{\mathcal{C}}\left(- \gamma_j \sum_{i \neq j} C_i \right) \\
+& = \OO_{C_j}\left( \sum_{x_i \in C_j} \alpha_i x_i + \sum_{q_i \in C_j} \left(\frac{\gamma_i - \gamma_j}{r_i}\right) q_i - \sum_{\tilde{q}_i \in C_j} m_i \tilde{q}_i \right)\end{align*}
+where the middle sum is over adjacent internal components and the final sum is over adjacent external components. The fact that $\gamma_j/r_i = m_i$ follows as in the previous case.
+
+We must argue that $\Lcal|_{C_j} = L|_{C_j}$. Suppose for the moment that $C_j$ is genus zero, so that we only need to check the degrees. We must show:
+\begin{equation*} \deg L|_{C_j} = \sum_{x_i \in C_j} \alpha_i - \sum_{q_i \in C_j} \left( \dfrac{\gamma_j - \gamma_i}{r_i}\right) - \sum_{\tilde{q}_i \in C_j} u_{\tilde{q}_i}\end{equation*}
+But by the definition of $Q^{\operatorname{GS}}$ we have:
+\begin{equation*} (\gamma_j - \gamma_i)/r_i = u_{q_i} \end{equation*}
+From which the above formula holds because of the tropical balancing condition we imposed when choosing the type.
+
+Similarly if $C_j$ is smooth of genus one we must show:
+\begin{equation*} L|_{C_j} = \OO_{C_j} \left( \sum_{x_i \in C_j} \alpha_i x_i - \sum_{q_i \in C_j} u_{q_i} q_i - \sum_{\tilde{q}_i \in C_j} u_{\tilde{q}_i} \tilde{q}_i \right) \end{equation*}
+But this is just the balancing condition on the level of $\Pic(C_j)$.
+
+What about if $C_j$ is a wheel of rational components?
+Then it isn't irreducible, so let's write it as $Z= C_1 \cup \ldots \cup C_k$.
+So there are other internal components $C_{k+1},\ldots,C_r$ and external components $C_{r+1},\ldots,C_m$.
+We assume that $C_1,\ldots,C_k$ are ordered so that $C_i$ intersects $C_{i-1}$, $C_{i+1}$ and none others.
+Notice that this means that:
+\begin{equation*} C_i^2 = -1/r_{i-1} - 1/r_{i+1} - \sum_{q_j \in C_i} 1/r_j \end{equation*}
+for all $i \in \{1,\ldots,k\}$, where the sum is over all nodes $q_j$ which connect $Z$ to the rest of the curve. Thus we obtain:
+\begin{align*} \Lcal|_Z & = \OO_Z \left( \sum_{x_i \in Z} \alpha_i x_i\right) \otimes \OO_{\Ccal} \left( \sum_{i=1}^r \gamma_i C_i \right)\bigg|_Z \\
+& = \OO_Z \left( \sum_{x_i \in Z} \alpha_i x_i + \sum_{\substack{q_i \in Z \\ \text{$q_i$ joins $Z$} \\ \text{to int.
+cpt.}}} (\gamma_i/r_i) q_i \right) \otimes \OO_{\Ccal} \left( \sum_{i=1}^k \gamma_i C_i \right) \bigg|_Z \\
+& = \OO_Z \left( \sum_{x_i \in Z} \alpha_i x_i + \sum_{\substack{q_i \in Z \\ \text{$q_i$ joins $Z$} \\ \text{to int.
+cpt.}}} (\gamma_i/r_i) q_i + \sum_{i=1}^k \gamma_i \left( \frac{1}{r_{i,i-1}} q_{i-1} + \frac{1}{r_{i,i+1}} q_{i+1} + (C_i^2) s_i \right)\right)
+\end{align*}
+where $q_{i-1}$ is the node connecting $C_{i-1}$ and $C_i$ (and similarly for $q_{i+1}$) and $s_i$ is some point of $C_i$ (doesn't really matter which, since $C_i$ is rational).
+
+Using the description of $C_i^2$ given above, we see that the terms $q_{i-1}/r_{i,i-1}$ and $q_{i+1}/r_{i,i+1}$ cancel, and we are left with
+\begin{align*} \Lcal|_Z & = \OO_Z \left( \sum_{x_i \in Z} \alpha_i x_i + \sum_{\substack{q_i \in Z \\ \text{$q_i$ joins $Z$} \\ \text{to int.
+cpt.}}} (\gamma_i/r_i) q_i + \sum_{\substack{q_i \in Z \\ \text{$q_i$ joins $Z$} \\ \text{to rest of curve}}} (\gamma_i/r_i) q_i \right) \\
+& = \OO_Z \left( \sum_{x_i \in Z} \alpha_i x_i + \sum_{\substack{q_i \in Z \\ \text{$q_i$ joins $Z$} \\ \text{to int.
+cpt.}}} \left( \dfrac{\gamma_i-\gamma_j}{r_i} \right) q_i - \sum_{\substack{q_i \in Z \\ \text{$q_i$ joins $Z$} \\ \text{to ext.
+cpt}}} (\gamma_i/r_i) q_i \right)
+\end{align*}
+and this is precisely the balancing condition on the level of $\Pic(Z)$.
+This proves that $\Lcal|_C = L$, except for one case which we haven't yet considered, namely when there is a wheel of rational curves which is partially internal and partially external.
+In this case essentially the same argument as given above applies.
+
+We have thus shown that we can break $C$ up into pieces (mostly into its irreducible components, unless there is a rational wheel in which case we treat this as a single piece) such that the corresponding intersection graph has genus zero and such that $\Lcal$ restricts to $L$ on each of the pieces.
+The fact that $\Lcal|_C = L$ then immediately follows (since the intersection graph has genus zero, so the Picard group of $C$ is equal to the direct sum of the Picard groups of the pieces).
+This completes the proof of step (3).
+
+As mentioned above, step (4) is immediate by the construction of $\Lcal$.
+It remains to carry out step (5), i.e.
+to extend the sections $u_1,\ldots,u_N$.
+By standard results in deformation theory, obstructions to extending sections of a deformation of $L$ are contained in $\HH^1(C,L)$.
+If $L$ is non-trivial on the circuit, then this space vanishes and so the sections extend immediately.
+
+Thus the only case we need to check is when $L$ is trivial on the circuit, which means that the circuit $E$ (again, either a smooth elliptic curve or a wheel of rational components) is contracted by the map $f$.
+In this case we want to extend the sections by referring to the corresponding Smyth curve.
+From the centrally aligned curve $\Ccal$ we obtain a diagram:
+\bcd
+& \tilde{\Ccal} \ar[ld] \ar[rd] & \\
+\Ccal & & \overline{\Ccal}
+\ecd
+\basenote{Finish this}
+
+We have thus constructed the smoothing, which shows that conditions (1) and (2) above are sufficient to characterise points in the closure of the nice locus.
+
+We will now show that these conditions are necessary.
+Suppose therefore that there is a family $\Ccal \to \formLine$ and consider the central fibre $\Ccal_0 = C$.
+Condition (1) for $C$ follows immediately from continuity of intersection products.
+
+To show condition (2), let $u_0 = f^*(z_0) \in \HH^0(\Ccal,f^* \OO_{\PP^N}(H))$.
+For each component $C_i$ of the central fibre $C$, let $\gamma_i$ be the vanishing order of $u_0$ along the Weil divisor $C_i$.
+For each internal component of $C$ this defines a non-zero map $\gamma_i \colon \N \to \N$.
+On the other hand, for each node $q$ consider the corresponding generator $e_q \in Q^{\operatorname{ctr}}$.
+A chart for the log structure on the base is given by a map
+\begin{equation*} Q^{\operatorname{ctr}} \to \mathbbm{k} \llbracket t \rrbracket \end{equation*}
+which we can compose with the valuation on $\mathbbm{k} \llbracket t \rrbracket$ to get a map:
+\begin{equation*} Q^{\operatorname{ctr}} \to \N \end{equation*}
+Let $r_q$ be the image of $e_q$ along this map.
+This is always non-zero because every node is smoothed in the family $\Ccal$; thus we have a non-zero map $r_q \colon \N \to \N$.
+These, together with the $\gamma_i$ defined above, give a local morphism
+\begin{equation*} \prod_{q \in C} \N_q \times \prod_{C_i} \N_{\eta_i} \to \N \end{equation*}
+where the second product is over the internal components of $C$.
+We claim that this descends to the quotient $Q^{\operatorname{GS}}$ (recall again that this quotient depends on a choice of type).
+We have to check that for every node $q$ we have
+\begin{equation*} u_q r_q = \gamma_i - \gamma_j \end{equation*}
+where $C_i$ and $C_j$ are the adjacent components (this makes for all nodes, since $\gamma_i=0$ for any external component).
+Remember that the $u_q$ are not fixed a priori; thus we can think of the above formula as determining the $u_q$.
+What we then need to check is that the $u_q$ thus defined are all integers, and that they satisfy the tropical balancing condition on the level of $\Pic (C)$.
+
+Consider the dual graph of $C$, treating the circuit $E$ as a single node of this graph, so that the graph has genus zero.
+Start from a leaf $C_i$ of this graph, so that there is only one node $q$ of the corresponding component.
+Let $C_j$ be the unique component of $C$ which is adjacent to $C_i$ (via $q$).
+Then we have:
+\begin{equation*} \deg f|_{C_i} = \deg \Lcal|_{C_i} = (\gamma_i - \gamma_j)/r_q + \sum_{x_k \in C_i} \alpha_k \end{equation*}
+Rearranging, we see that $(\gamma_i - \gamma_i)/r_q$ is an integer.
+Substiting in $u_q$ for this value, we obtain precisely the balancing condition, which we can view as happening on the level of $\Pic (C_j)$ (if we refrain from taking the degree first).
+
+We now proceed by induction.
+The process is as follows: having determined $q$, we pass to the next component $C_j$.
+If this has only one other node $r$ besides $q$, we apply the same argument as before to show that $u_r$ is an integer and satisfies the balancing condition.
+If it contains more than one other node, we pick one of them and follow the resulting path through the dual graph until we arrive at a leaf with a single undetermined node (which must exist, since otherwise the node we started with would have been determined).
+We then start the process again from there.
+
+This procedure proves that all the $u_q$ are integers and that the balancing condition is satisfied on every component, except for those nodes and those components belonging to the circuit $E$.
+If the circuit is smooth there is nothing additional to prove, except to note that the Gathmann-like condition (1) ensures that the balancing condition will be satisfied on the level of $\Pic(E)$ (rather than just on the level of degree), so that it is satisfied for $\Pic(C)$.
+
+It remains to consider the case when $E$ is a wheel of rational components.
+Again the Gathmann-like condition (1) ensures we have balancing on the level of $\Pic(E)$, once we show that all the $u_q$ for the nodes internal to $E$ are integers.
+Labelling the components of $E$ as $C_1,\ldots,C_k$ with $C_i$ intersecting $C_{i-1}$ and $C_{i+1}$, we obtain relations:
+\begin{equation*} u_{q_i} r_{q_i} = \gamma_{i+1} - \gamma_{i-1} \end{equation*}
+Thus $u_{q_i} \in r_{q_i}^{-1} \cdot \Z$.
+But if we restrict $\Lcal$ to each component and look at the resulting equation, we see that in fact $u_{q_i} \in (1/r_{q_j}) \Z$ for all $j$.
+Thus $u_{q_i} \in (1/g) \Z$ where $g = \operatorname{gcd}(r_{q_1},\ldots,r_{q_k})$.
+\basenote{Maybe we can fix this using saturation: note that we only need a map from the saturation of the quotient to $\N$, not from the quotient itself.}
+
+\end{proof}
+\newpage
+
+\section{Recursion formula for $\PP^1|\infty$, $\Sigma \alpha = d$.}
+As in the genus zero case, we construct a line bundle (a quotient of jet bundles) and a section of that line bundle whose vanishing locus equals a union of boundary components (comb loci).
+(The moduli space for $\alpha+e_k$ does not appear because we are assuming maximal tangency.) These fit into the following families:
+\subsection{$\mathcal{Y}^a$}
+The first family is where the circuit is external:
+\begin{equation*} \mathcal{Y}^a=\oM_{0,\lvert\alpha^{(0)}\rvert+r} \times\left(\VZc{1}{\alpha^{(1)}\cup\{m^{(1)}\}}{\PP^1|\infty}{d_1}\times_H {\prod_{i=2}^r} {}_H \M{0}{\alpha^{(i)}\cup\{m^{(i)}\}}{\PP^1|\infty}{d_i}\right) \end{equation*}
+
+\subsection{$\mathcal{Y}^b$}
+The second family is where the circuit is partly internal, partly external (and hence is a wheel of rational curves).
+\begin{equation*} \mathcal Y^b=\oM_{0,\lvert\alpha^{(0)}\rvert+r}\times \left(\M{0}{\alpha^{(1)}\cup\{m^{(1)},m^{(2)}\}}{\PP^1|\infty}{d_1}\times_H \prod_{i=3}^r {}_H \M{0}{\alpha^{(i)}\cup\{m^{(i)}\}}{\PP^1|\infty}{d_i}\right)\end{equation*}
+
+\subsection{$\mathcal{Y}^c$}
+The third family is where the circuit is internal (and thus has zero degree, since we are working with $\PP^1$ relative $\infty$).
+\begin{equation*} \mathcal Y^c = \oM^{\operatorname{ctr,lb}}_{1,\lvert\alpha^{(0)}\rvert+r} \times \prod_{i=1}^r {}_H \M{0}{\alpha^{(i)}\cup\{m^{(i)}\}}{\PP^1|\infty}{d_i} \end{equation*}
+In the above, the first factor
+\begin{equation*} \oM^{\operatorname{ctr,lb}}_{1,\lvert\alpha^{(0)}\rvert+r} \subseteq \oM^{\operatorname{ctr}}_{1,\lvert\alpha^{(0)}\rvert+r}  \end{equation*}
+consists of those centrally aligned curves satisfying Gathmann's condition in $\Achow_0(C)$:
+\begin{equation*} \sum_{x_j\in C}\alpha_jx_j-\sum_{i=1}^r m^{(i)}y_i= 0 \in \Achow_0(C)\end{equation*}
+We saw before how to express this as a condition in $\Pic(E)$ where $E \subseteq C$ is the circuit.
+Notice that the condition above epends on the choice of $m^{(i)}$ but is really just a condition on the first factor of the product, so $\mathcal Y^c$ itself can be expressed as a product.
+\sidenote{Express the line bundle condition in terms of tautological classes?}
+
+In this third case there is also a degeneracy condition that must be imposed on the second factor, which ensures that the map factors through the Smyth curve.
+To be more precise, the condition is that the derivatives
+\begin{equation*} (\operatorname{d}\!f)|_{q_i} \in \operatorname{T}|_{\PP^1} \qquad i=1,\ldots,r \end{equation*}
+are linearly dependent. Note that if $m_i > 1$ for any $i$, or if $r \geq 2$, then this is automatically satisfied. Thus the only case in which we have to impose this is for
+\begin{equation*} \mathcal{Y}^c = \oM^{\operatorname{ctr,lb}}_{1,|\alpha^{(0)}|+r} \times {\M{0}{\alpha^{(i)}\cup (1}{\PP^1|\infty}{d}}^{\operatorname{degen}} \end{equation*}
+where ``degen'' indicates that we impose degeneracy.
+
+These spaces are all irreducible of the expected dimension, and it can be checked that they define divisors inside:
+\begin{equation*} \VZc{1}{\alpha}{\PP^1|\infty}{d} \end{equation*}
+In fact, this applies to all of the above spaces \emph{except} for the special case mentioned above (where we impose degeneracy).
+This has too small dimension, and hence will not appear in the recursion formula.
+
 \section{Recursion formula}
@@
 \end{itemize}
-
 \end{proof}
 
+\newpage
 \appendix

### 2018-11-17 new.tex

@@
 
-\textbf{Gathmann's recursion.} There is a morphism $\VZ_{1,\alpha}(\PP^N|H,d)\to \VZ_{1,n}(\PP^N,d)$, hitting Gathmann's relative space.
+\textbf{Gathmann-type recursion.} There is a forgetful morphism \[\VZ_{1,\alpha}(\PP^N|H,d)\to \VZ_{1,n}(\PP^N,d),\] hitting Gathmann's relative space.
 We may therefore pullback Gathmann's line bundle and section, cutting out the locus where the $k$-th marking is tangent to $H$ to order $\alpha_k+1$.
 Because $\alpha$ was maximal ($\sum\alpha=d$) by assumption, this means that the curve has to break, and $x_k$ has to lie on an internal component - one which is entirely mapped into $H$.
-Here comes an interesting point: the combinatorics of such boundary loci is governed by tropical geometry, and it is otherwise very hard to districate the interaction between the relative condition and the exceptional loci of the Vakil--Zinger blow-up.
+We identify the zero locus of Gathmann's section explicitly.
+Here is an interesting remark: the combinatorics of such boundary loci is governed by tropical geometry, and it is otherwise very hard to districate the interaction between the relative condition and the exceptional loci of the Vakil--Zinger blow-up.
 \begin{cor}
@@
 The Artin fan is a tropical gadget.
-Its local structure is given by subdividing the ACGS minimal model according to the alignment.
+Its local structure is given by subdividing the ACGS minimal monoid according to the alignment.
 We are only interested in picking its rays.
 The upshot is that the combinatorics is slightly more involved than in the genus zero case: the alignment may force some teeth of the comb to break.
-\begin{thm}
- \[(\alpha_k\psi_k+\ev_k*H)[\VZ_{1,\alpha}(\PP^N|H,d)]=[D_{\alpha,k}(\PP^N|H,d)],\]
- where the latter is a sum of broken comb loci indexed by rays of the tropical fan.
+\begin{thm}[Gathmann-type formula, maximal tangency, $(\PP^N|H)$ case]
+ \[(\alpha_k\psi_k+\ev_k^*H)[\VZ_{1,\alpha}(\PP^N|H,d)]=[D_{1,\alpha;k}(\PP^N|H,d)],\]
+ the latter being a sum of broken comb loci indexed by rays of the tropical fan.
 \end{thm}
@@
 \begin{thm}
- Up to a finite cover of the underlying boundary stratum - which is just a combinatorially-determined product of moduli spaces of genus zero or one curves and absolute or relative maps with lower numerical invariants - every component of $D_{\alpha,k}(\PP^N|H,d)$ can be described as the transverse intersection of two loci in a projective bundle, where:
+ Up to a finite cover of the underlying boundary stratum - which is a combinatorially-determined fiber product of moduli spaces of genus zero and one, absolute and relative maps with lower numerical invariants - every component of $D_{\alpha,k}(\PP^N|H,d)$ can be described as the transverse intersection of two loci in a projective bundle, where:
  \begin{itemize}
   \item the latter parametrises the possible line bundle isomorphisms imposed by the alignment of the log structure;
-  \item the first locus is a subbundle representing the residual isomorphisms after fixing the ones imposed by tropical continuity;
+  \item the first locus is a subbundle representing the residual isomorphisms after fixing the ones virtually imposed by tropical continuity;
   \item the second locus is determined by the factorisation conditions.
@@
 \end{thm}
-The upshot is that we may then push the formula down to the Gathmann's space and we obtain multiplicities and tautological classes.
+The upshot is that we may then push the formula down to the Gathmann's space, so as to obtain multiplicities and tautological classes.
 \begin{cor}
- \[(\alpha_k\psi_k+\ev_k*H)[\VZ^G_{1,\alpha}(\PP^N|H,d)]=[D^G_{\alpha,k}(\PP^N|H,d)],\]
- where the latter is a weighted sum of tautological classes on Gathmann's comb loci.
+ \[(\alpha_k\psi_k+\ev_k^*H)[\VZ^G_{1,\alpha}(\PP^N|H,d)]=[D^G_{1,\alpha;k}(\PP^N|H,d)],\]
+ the latter being expressible as a weighted sum of tautological classes on Gathmann's comb loci.
 \end{cor}
@@
 \begin{itemize}
- \item A similar formula for raising the tangency holds in the non-maximal case.
-It can be proven by adding auxiliary markings of contact order $1$; forgetting them is then a $(d-\sum\alpha)!:1$ cover because of the density of the nice locus inside Gathmann's spaces.
- \item The formula holds more generally for any smooth projective target $X$ relative to a generic hyperplane section $Y=X\cap H\subseteq \PP^N$ by virtual pullback.
+ \item A similar formula for raising the tangency holds in the non-maximal tangency case.
+It can be proven by adding auxiliary markings of contact order $1$; forgetting them is then a $(d-\sum\alpha)!:1$ cover because the nice locus is dense inside Gathmann's relative spaces.
+ \item The formula holds more generally for any smooth projective target $X$ relative to a generic hyperplane section $Y=X\cap H\subseteq \PP^N$. This follows via virtual pullback.
 \end{itemize}
@@
 \begin{thm}[In-principle quantum Lefschetz]
- The restricted reduced genus one invariants of $Y$ can be inductively deducted from the full descendant (reduced) genus zero and one Gromov-Witten theory of $X$.
+ The restricted reduced genus one invariants of $Y$ can be inductively deducted from the full descendant genus zero and one (reduced) Gromov-Witten theory of $X$.
 \end{thm}
-The computation is more delicate than its genus zero analogue because invariant with the same numerical data appear intertwined in the last steps of the recursion.
+The proof is more delicate than its genus zero analogue because invariants with the same numerical data appear intertwined in the last steps of the recursion.
+
+\section{A desingularisation of the log space}
+The ultimate goal of the paper is to apply Gathmann's techniques to the Vakil-Zinger desingularisation $\VZ_{1,n}(\PP^N,d)$ and to obtain a quantum Lefschetz result for reduced invariants under some positivity assumption.
+The key step is to study the unobstructed case $(\PP^N|H)$.
+We approach the problem by lifting it to the ACGS space of log stable maps.
+This allows us to exploit the tools developed in \cite{RSPW,RSPW2}.
+We are in an intermediate situation between those two papers, and indeed we get an intermediate answer.
+
+\subsection{The ACGS minimal monoid and central alignments}
+
+\begin{prop}
+ The map $\oM_{1,\alpha}^{\mathrm{cen}}(\PP^N|H,d)\to\oM_{1,\alpha}(\PP^N|H,d)$ is a log modification. In particular $\oM_{1,\alpha}^{\mathrm{cen}}(\PP^N|H,d)$ is a log algebraic stack.
+\end{prop}
+
+{\color{gray} possibly start pointing out that the log structure is already partially aligned by the map to $(\PP^N|H)$}
+
+\subsection{Factorisation conditions}
+
+\begin{prop}
+ Factoring through the Smyth curve is a closed condition. In particular $\VZ_{1,\alpha}(\PP^N|H,d)\subseteq_{\mathrm{cl}}\oM_{1,\alpha}^{\mathrm{cen}}(\PP^N|H,d)$ is a log algebraic stack.
+\end{prop}
+
+\subsection{Log smoothness}
+\begin{thm}
+ $\VZ_{1,\alpha}(\PP^N|H,d)$ is log smooth.
+\end{thm}
+\begin{proof}
+ We reduce to the situation dealt with in \cite{RSPW2} by adding generic extra hyperplanes $H_1,\ldots, H_N$.
+
+ First, note that, for divisors $D_1\subseteq D_2$ in $X$, there is a morphism of log schemes $(X,\pazocal M_{D_2})\to (X,\pazocal M_{D_1})$, or equivalently a morphism of log structures $\pazocal M_{D_1}\to\pazocal M_{D_2}$ over $i\!d_X$, because functions invertible off $D_1$ are in particular invertible off $D_2$ as well, and divisorial log structures are subsheaves of the structure sheaf $\pazocal M_{D}\subseteq\OO_X$.
+
+ Now fix a point $[(C,f)]\in\VZ_{1,\alpha}(\PP^N|H,d)$.
+Choose hyperplanes $H_1,\ldots, H_N$ in such a way that they intersect the image of $f$ transversally, namely $f^{-1}(H_1\cup\ldots\cup H_N)$ is a reduced collection of points $\{q^i_j\}_{\substack{i=1,\ldots,N \\ j=1,\ldots,d}}$ in the smooth locus of $C$.
+This condition will then hold in an open neighbourhood of $[(C,f)]$.
+Mark $C$ at these points, end endow it with the pullback along $f$ of the divisorial log structure $(\PP^N,\Delta)$, where $\Delta=H+\sum_{i=1}^N H_i$.
+Then \[f\colon (C,\{p_k\}_{k=1,\ldots,n}\{q^i_j\}_{\substack{i=1,\ldots,N \\ j=1,\ldots,d}})\to(\PP^N,\Delta)\]
+ is a lift of $[(C,f)]$ to $\oM_{1,\alpha}(\PP^N|\Delta,d)$ (under the forgetful morphism discussed in the previous paragraph).
+
+ Looking at the associated tropical map $\phi$, observe that:
+ \begin{itemize}
+  \item new flags have been attached only to vertices of positive degree, and these already have a flag escaping $\phi^{-1}\phi(v)$, because the sum of the incoming slopes is not zero (by modified balancing);
+  \item the image of the new tropical map $\tilde\phi$ is entirely contained in the ray of the tropicalisation of $(\PP^N,\Delta)$ corresponding to $H$, with new flags going off to infinity in all the new ray directions from every vertex of positive degree.
+ \end{itemize}
+ In particular, for every quotient $N'$ of the lattice $N$, the associated tropical map $\tilde\phi'$ will either
+ \begin{enumerate}
+  \item have image contained in the ray corresponding to $H$, isomorphically to the original $\phi$, so the contraction radius can be seen to coincide with $\delta_2$, or
+  \item collapse the entire curve to the zero-cell of the fan, in which case we argue from the previous remarks that the contraction radius is $\delta$.
+ \end{enumerate}
+
+ Hence the lift of $[(C,f)]$ is centrally aligned and satisfies the factorisation property for every subtorus $H<T$, therefore it is well-spaced (see \cite[Definition 3.4.2]{RSPW2}) and it belongs to $\VZ_{1,\tilde\alpha}(\PP^N|\Delta,d)$.
+Note that the deformation spaces of $(C,f)$ and its lift are isomorphic by construction, as can be checked by the infinitesimal criterion - an infinitesimal deformation of $(C,f)$ brings along a unique deformation of the $\{q^i_j\}$ compatible with the map to $(\PP^N,\Delta)$.
+At the logarithmic level, observe that the ACGS minimal monoid is the same, because no component of $C$ is entirely mapped into any of the newly added hyperplanes; since the global contraction radius $\delta$ is the same, the subdivisions corresponding to the alignment procedure do coincide as well.
+This shows that the forgetful morphism is (log) \'etale in a neighbourhood of the lift of $[(C,f)]$, hence we may conclude by appealing to \cite[Theorem 3.5.1]{RSPW2}.
+\end{proof}
+
+\begin{cor}
+ $\VZ_{1,\alpha}(\PP^N|H,d)$ is smooth over its Artin fan.
+\end{cor}
+
+{\color{gray} describe the latter as explicitly as possible; comment on the cones that are (possibly?) not there because of the compatibility of the alignment with the log map (this is probably awkward, useless, and superceded by saying ``we align subdivide the ACGS minimal dual monoid'') and because of smoothability/factorisation (this is probably related to tropical well-spacedness)}
+
+\section{An explicit description of Gathmann's boundary}
 

### 2018-11-17 new.tex
Shortened new by getting rid of all of old stuff, and changes institution contact details

@@
 
-\section{An explicit description of Gathmann's boundary}
-
-\subsection{The line bundle and section}
-On $\VZrel{1}{\alpha}{X}{\beta}$, as on any space of maps to an expansion really, there is not only a universal curve $C$ with universal map $f$ to the expansion $W$, but also the stabilisation of the collapsed map obtained by composing $f$ with $\pi_X\colon W\to X$:
-\bcd
-C\ar[r,"f"]\ar[d,"\stab"] & W \ar[d,"\pi_X"] \\
-\stC\ar[r,"\stf"] & X
-\ecd
-Notice that the image of the marking $p_k$ on $\stC$ has either contact order $\alpha_k$ to $Y$, or it lies on an internal component.
-The section $s\in\Gamma(X,\OO_X(Y))$ whose vanishing locus defines $Y$, induces a section $\sts$ of $\stpi_*\stf^*\OO_X(Y)$.
-By the previous discussion, the image of $\sts$ in $\ev_k^*\mathcal P^{\alpha_k}\OO_X(Y)$ vanishes, hence by the principal parts exact sequence
-\[ 0\to p_k^*\Omega_{\stC}^{\otimes\alpha_k+1}\otimes\ev_k^*\OO_X(Y)\to \ev_k^*\mathcal P^{\alpha_k+1}\OO_X(Y)\to \ev_k^*\mathcal P^{\alpha_k}\OO_X(Y)\to 0\]
-we obtain a section $\sts_k$ of the line bundle $p_k^*\Omega_{\stC}^{\otimes\alpha_k+1}\otimes\ev_k^*\OO_X(Y)$.
-
-It is apparent that, set-theoretically at least, the vanishing locus of $\sts_k$ consists of those maps such that $p_k$ lies on an internal component of $\stC$, or, equivalently, it is mapped to higher level in the expansion and lies not on a ``trivial bubble'' in $C$.
-
-\subsection{Boundary loci}
-We follow in Vakil's footsteps in setting the following notation:
-\begin{enumerate}[label=(\alph*)]
- \item \[\mathcal Y^a=\M{0}{\lvert\alpha^{(0)}\rvert+r}{H}{d_0}\times_{H^r}\left(\VZc{1}{\alpha^{(1)}\cup\{m^{(1)}\}}{\PP^N|H}{d_1}\times\prod_{i=2}^r\M{0}{\alpha^{(i)}\cup\{m^{(i)}\}}{\PP^N|H}{d_i}\right)\]
- \item \[\mathcal Y^b=\M{0}{\lvert\alpha^{(0)}\rvert+r}{H}{d_0}\times_{H^r}\left(\M{0}{\alpha^{(1)}\cup\{m^{(1)},m^{(2)}\}}{\PP^N|H}{d_1}\times\prod_{i=3}^r\M{0}{\alpha^{(i)}\cup\{m^{(i)}\}}{\PP^N|H}{d_i}\right)\]
- \item \[\mathcal Y^c\subseteq \VZc{1}{\lvert\alpha^{(0)}\rvert+r}{H}{d_0}\times_{H^r}\prod_{i=1}^r\M{0}{\alpha^{(i)}\cup\{m^{(i)}\}}{\PP^N|H}{d_i}\]
- $\mathcal Y^c$ is cut within the latter by Gathmann's condition on line bundles:
- \[f_{|E}^*\mathcal O_H(1)\cong\mathcal O_E\left(\sum_{x_j\in E}\alpha_jx_j-\sum_{i=1}^r m^{(i)}y_i\right)\]\sidenote{Express the line bundle condition in terms of tautological classes?}
- Notice that such condition depends on the choice of $m^{(i)}$ but is really just a condition on the first factor of the product, so $\mathcal Y^c$ itself can be expressed as a product.
-\end{enumerate}
-
-\section{The space of relative centrally aligned maps}
-\noindent Recall \cite{RSPW} that the moduli space of maps from centrally aligned curves is obtained by considering the  Cartesian diagram
-\bcd
-\tVZc{1}{n}{X}{\beta}\ar[d]\ar[r]\ar[dr,phantom,"\Box"] & \M{1}{n}{X}{\beta}\ar[d] \\
-\MM_{1,n}^{\rm{ctr}}\ar[r] & \MM_{1,n}^{\dagger}
-\ecd
-so that objects of $\tVZc{1}{n}{X}{\beta}$ consist of
-\begin{enumerate}
-\item a centrally aligned curve $(C,M_C,\delta)$;
-\item a stable map $f\colon C \to X$;
-\end{enumerate}
-subject to the condition that the subcurve $C_0 \subseteq C$, consisting of those components $C_v$ for which $\lambda(v) < \delta$, coincides with the maximal connected genus one subcurve contracted by $f$.
-They then define
-\begin{equation*} \VZc{1}{n}{X}{\beta} \subseteq \tVZc{1}{n}{X}{\beta} \end{equation*}
-to be the closed substack consisting of maps satisfying the \emph{factorisation condition}, namely that the map $f\colon C\to X$ factors through the associated contraction to a Smyth curve, i.e.
-there exists a map $\bar{f}$ making the following square commute:
-\bcd
-\widetilde C\ar[r]\ar[d] & \overline C\ar[d,"\bar f" left,dotted] \\
-C\ar[r,"f"] & X
-\ecd
-One should think of the factorisation condition as identifying the main component of the moduli space.
-
-\section{Definition of centrally aligned relative space}
-\section{Characterisation of the closed points of the relative space}
-\section{Recursion formula}
-
-\subsection{The case $\sum\alpha=d$}
-
-\subsection{Definition of the boundary components} According to Vakil's article there should be three sorts of boundary components.
-\begin{enumerate}[label=(\alph*)]
- \item \[\mathcal Y^a=\M{0}{\lvert\alpha^{(0)}\rvert+r}{H}{d_0}\times_{H^r}\left(\VZc{1}{\alpha^{(1)}\cup\{m^{(1)}\}}{\PP^N|H}{d_1}\times\prod_{i=2}^r\M{0}{\alpha^{(i)}\cup\{m^{(i)}\}}{\PP^N|H}{d_i}\right)\]
- \item \[\mathcal Y^b=\M{0}{\lvert\alpha^{(0)}\rvert+r}{H}{d_0}\times_{H^r}\left(\M{0}{\alpha^{(1)}\cup\{m^{(1)},m^{(2)}\}}{\PP^N|H}{d_1}\times\prod_{i=3}^r\M{0}{\alpha^{(i)}\cup\{m^{(i)}\}}{\PP^N|H}{d_i}\right)\]
- \item \[\mathcal Y^c\subseteq \VZc{1}{\lvert\alpha^{(0)}\rvert+r}{H}{d_0}\times_{H^r}\prod_{i=1}^r\M{0}{\alpha^{(i)}\cup\{m^{(i)}\}}{\PP^N|H}{d_i}\]
- $\mathcal Y^c$ is cut within the latter by Gathmann's condition on line bundles:
- \[f_{|E}^*\mathcal O_H(1)\cong\mathcal O_E\left(\sum_{x_j\in E}\alpha_jx_j-\sum_{i=1}^r m^{(i)}y_i\right)\]\sidenote{Express the line bundle condition in terms of tautological classes?}
- Notice that such condition depends on the choice of $m^{(i)}$ but is really just a condition on the first factor of the product, so $\mathcal Y^c$ itself can be expressed as a product.
-\end{enumerate}
-
 \bibliographystyle{alpha}
@@
 \noindent Luca Battistella\\
-Department of Mathematics, Imperial College London \\
-\texttt{l.battistella14@imperial.ac.uk}\\
+Max-Planck-Institut f\"ur Mathematik\\
+\texttt{battistella@mpim-bonn.mpg.de}\\
 
 \noindent Navid Nabijou \\
-Department of Mathematics, Imperial College London \\
-\texttt{navid.nabijou09@imperial.ac.uk}\\
+School of Mathematics and Statistics, University of Glasgow \\
+\texttt{navid.nabijou@glasgow.ac.uk}\\
 
 \noindent Dhruv Ranganathan \\
-Department of Mathematics, Massachusetts Institute of Technology \\
-\texttt{dhruvr@mit.edu}
+DPMMS, University of Cambridge \\
+\texttt{dr508@cam.ac.uk}
 

### 2018-11-30 new.tex
started the fight against the boundary

--- 2018-11-17 new.tex
@@
 \newcommand{\sidenote}[1]{\marginpar{\textbf{\color{red}#1}}}
+
+\def\Yagraph{\tikz[baseline=-3pt,scale=.8]{
+\draw (2,0) -- (0,1) (2,0) -- (0,.5) (2,0) -- (0,-1);
+\draw (2,0) circle(2pt)[fill=black];
+\draw (0,1) circle(2pt)[fill=white];
+\draw (0,.5) circle(2pt)[fill=black];
+\draw (0,-.5) node{$\ldots$};
+\draw (0,-1) circle(2pt)[fill=black];
+\draw (-1,1.5) -- (1,1.5) -- (1,-1.5) -- (-1,-1.5) -- (-1,1.5);
+\draw (1,1.5) -- (3,2) -- (3,-1) -- (1,-1.5);
+}}
+
+\def\Ybgraph{\tikz[baseline=-3pt,scale=.8]{
+\draw (2,0) to[out=120,in=0] (0,1) (2,0) -- (0,1) (2,0) -- (0,.5) (2,0) -- (0,-1);
+\draw (2,0) circle(2pt)[fill=black];
+\draw (0,1) circle(2pt)[fill=black];
+\draw (0,.5) circle(2pt)[fill=black];
+\draw (0,-.5) node{$\ldots$};
+\draw (0,-1) circle(2pt)[fill=black];
+\draw (-1,1.5) -- (1,1.5) -- (1,-1.5) -- (-1,-1.5) -- (-1,1.5);
+\draw (1,1.5) -- (3,2) -- (3,-1) -- (1,-1.5);
+}}
+
+\def\Ycgraph{\tikz[baseline=-3pt,scale=.8]{
+\draw (2,0) -- (0,1) (2,0) -- (0,.5) (2,0) -- (0,-1);
+\draw (2,0) circle(2pt)[fill=white];
+\draw (0,1) circle(2pt)[fill=black];
+\draw (0,.5) circle(2pt)[fill=black];
+\draw (0,-.5) node{$\ldots$};
+\draw (0,-1) circle(2pt)[fill=black];
+\draw (-1,1.5) -- (1,1.5) -- (1,-1.5) -- (-1,-1.5) -- (-1,1.5);
+\draw (1,1.5) -- (3,2) -- (3,-1) -- (1,-1.5);
+}}
 
@@
 
-\begin{cor}
+\begin{cor}\label{cor:log_smooth}
  $\VZ_{1,\alpha}(\PP^N|H,d)$ is smooth over its Artin fan.
@@
 
-\section{An explicit description of Gathmann's boundary}
+\section{Description of the boundary}
 
-\subsection{The line bundle and section}
-On $\VZrel{1}{\alpha}{X}{\beta}$, as on any space of maps to an expansion really, there is not only a universal curve $C$ with universal map $f$ to the expansion $W$, but also the stabilisation of the collapsed map obtained by composing $f$ with $\pi_X\colon W\to X$:
-\bcd
-C\ar[r,"f"]\ar[d,"\stab"] & W \ar[d,"\pi_X"] \\
-\stC\ar[r,"\stf"] & X
-\ecd
-Notice that the image of the marking $p_k$ on $\stC$ has either contact order $\alpha_k$ to $Y$, or it lies on an internal component.
-The section $s\in\Gamma(X,\OO_X(Y))$ whose vanishing locus defines $Y$, induces a section $\sts$ of $\stpi_*\stf^*\OO_X(Y)$.
-By the previous discussion, the image of $\sts$ in $\ev_k^*\mathcal P^{\alpha_k}\OO_X(Y)$ vanishes, hence by the principal parts exact sequence
-\[ 0\to p_k^*\Omega_{\stC}^{\otimes\alpha_k+1}\otimes\ev_k^*\OO_X(Y)\to \ev_k^*\mathcal P^{\alpha_k+1}\OO_X(Y)\to \ev_k^*\mathcal P^{\alpha_k}\OO_X(Y)\to 0\]
-we obtain a section $\sts_k$ of the line bundle $p_k^*\Omega_{\stC}^{\otimes\alpha_k+1}\otimes\ev_k^*\OO_X(Y)$.
+Note that $f$ has contact order with $H$ exactly equal to $\alpha_k$ at the marking $p_k$, or else the irreducible component of $C$ on which $x_k$ lies is mapped entirely inside $H$.
+By pulling back along $f$ the equation defining $H$, and taking its $\alpha_k+1$-st derivative at $x_k$ (which makes sense because all the lower order derivatives do vanish by assumption) we single out the latter locus.
+By staring at the exact sequence of jet bundles
+\[0\to p_k^*\Omega_{C}^{\otimes\alpha_k}\otimes\ev_k^*\OO_{\PP^N}(H)\to p_k^*\mathcal J^{\alpha_k}(f^*\OO_{\PP^N}(H))\to p_k^*\mathcal J^{\alpha_k-1}(f^*\OO_{\PP^N}(H))\to 0\]
+we realise that there is on $\VZ_{1,\alpha}(\PP^N|H,d)$ a line bundle (the leftmost term in the exact sequence) with a natural section cutting the locus where the curve breaks, and the piece containing $p_k$ is mapped inside $H$.
+\begin{lem}
+ \[(\alpha_k\psi_k+\ev_k^*H)[\VZ_{1,\alpha}(\PP^N|H,d)]=[D_{1,\alpha;k}(\PP^N|H,d)],\]
+\end{lem}
+In what follows we shall give an explicit (recursive) description of the right-hand side, in terms of tautological classes on spaces of maps with lower numerical invariants.
+\begin{remark}
+ The divisors we are after are a union of logarithmic strata, because the locus where the log structure is trivial coincides precisely with the nice locus.
+\end{remark}
+By Corollary \ref{cor:log_smooth}, the divisorial logarithmic strata correspond to rays of the Artin fan.
 
-It is apparent that, set-theoretically at least, the vanishing locus of $\sts_k$ consists of those maps such that $p_k$ lies on an internal component of $\stC$, or, equivalently, it is mapped to higher level in the expansion and lies not on a ``trivial bubble'' in $C$.
+\subsection{Combinatorial description}
+As long as the minimal subcurve of genus one has positive degree, the picture is classical: the dual graph of the curve is bipartite - vertices mapped inside $H$ are distinguished from the others.
+In fact there is only one such vertex, because, if there were more, the relative position of their image in $\mathbb R_{\geq 0}$ under the tropical map would be unconstrained, therefore spanning a locus larger than a ray in the tropical moduli space.
+We follow in R.
+Vakil's footsteps in setting the following notation:
+\begin{figure}[h]
+    \centering
+    \begin{minipage}{0.3\textwidth}
+        \centering
+        \Yagraph
+        \caption{$\mathcal Y_a$}
+    \end{minipage}\hfill
+    \begin{minipage}{0.3\textwidth}
+        \centering
+        \Ybgraph
+        \caption{$\mathcal Y_b$}
+    \end{minipage}\hfill
+    \begin{minipage}{0.3\textwidth}
+        \centering
+        \Ycgraph
+        \caption{$\mathcal Y_c^+$}
+    \end{minipage}
+\end{figure}
+
+Notice that continuity of the tropical map determines the mutual relationship among the edge lengths.
+
+On the other hand, when there is a contracted elliptic subcurve - and it will be contracted into the hyperplane, because otherwise it wouldn't be generic, by density of the nice locus in $\VZ_{1,\tilde\alpha}(\PP^N|H,\tilde d)$ - the picture becomes much more complicated due to the alignment.
+The combs may break multiple times and they may even point in opposite directions.
+\begin{figure}
+ \tikz{
+ \draw (0,0) circle(2pt)[fill=black] (0,2) circle(2pt)[fill=black] (0,4) circle(2pt)[fill=black] (0,6) circle(2pt)[fill=black] (0,-2) circle(2pt)[fill=black] (2,0) circle(2pt)[fill=white] (1.1,1.78) circle(2pt)[fill=black] (3.42,1.42) circle(2pt)[fill=black] (.58,-1.42) circle(2pt)[fill=black];
+ \draw (2,0) -- node[above]{4} (0,0) (2,0) --node[above]{2} (1.1,1.78) --node[above]{2} (0,2) (1.1,1.78) --node[above]{1} (0,4) (2,0) --node[above]{1} (3.42,1.42) (2,0) --node[above]{1} (.58,-1.42) (3.42,1.42) --node[above]{5} (0,6) (.58,-1.42) --node[above]{3} (0,-2);
+ \draw[red] (2,0) circle(2);
+ }
+\end{figure}
 

### 2018-12-03 new.tex
started combinatorial and explicit description

@@
 \newcommand{\M}[4]{\overline{\mathcal{M}}_{#1,#2}(#3,#4)}
+\newcommand{\MG}[4]{\overline{\mathcal{M}}^{\rm G}_{#1,#2}(#3,#4)}
 \newcommand{\Q}[4]{\mathcal{Q}_{#1,#2}(#3,#4)}
@@
 \newcommand{\tVZc}[4]{\widetilde{\mathcal{V\!Z}}^{\rm{ctr}}_{#1,#2}(#3,#4)}
-\newcommand{\VZc}[4]{\mathcal{V\!Z}^{\rm{ctr}}_{#1,#2}(#3,#4)}
+\newcommand{\VZc}[4]{\mathcal{V\!Z}_{#1,#2}(#3,#4)}
 \newcommand{\VZcLi}[4]{\mathcal{V\!Z}^{\rm{ctr, Li}}_{#1,#2}(#3,#4)}
@@
 \newcommand{\ev}{\operatorname{ev}}
+\newcommand{\fgt}{\operatorname{fgt}}
 \newcommand{\codim}{\operatorname{codim}}
@@
 \begin{cor}
- $\VZ_{1,\alpha}(\PP^N|H,d)$ is smooth over its Artin fan, in particular codimension one logarithmic strata can be read off from the latter.\marginpar{why are we only interested in log strata?}
+ $\VZ_{1,\alpha}(\PP^N|H,d)$ is smooth over its Artin fan, in particular codimension one logarithmic strata can be read off from the latter.
 \end{cor}
@@
 
-Note that $f$ has contact order with $H$ exactly equal to $\alpha_k$ at the marking $p_k$, or else the irreducible component of $C$ on which $x_k$ lies is mapped entirely inside $H$.
-By pulling back along $f$ the equation defining $H$, and taking its $\alpha_k+1$-st derivative at $x_k$ (which makes sense because all the lower order derivatives do vanish by assumption) we single out the latter locus.
+Note that $f$ has contact order with $H$ exactly equal to $\alpha_k$ at the marking $p_k$, or else the irreducible component of $C$ on which $p_k$ lies is mapped entirely inside $H$.
+By pulling back along $f$ the equation defining $H$, and taking its $\alpha_k$-th derivative at $p_k$ (which makes sense because all the lower order derivatives do vanish by assumption) we single out the latter locus.
 By staring at the exact sequence of jet bundles
 \[0\to p_k^*\Omega_{C}^{\otimes\alpha_k}\otimes\ev_k^*\OO_{\PP^N}(H)\to p_k^*\mathcal J^{\alpha_k}(f^*\OO_{\PP^N}(H))\to p_k^*\mathcal J^{\alpha_k-1}(f^*\OO_{\PP^N}(H))\to 0\]
-we realise that there is on $\VZ_{1,\alpha}(\PP^N|H,d)$ a line bundle (the leftmost term in the exact sequence) with a natural section cutting the locus where the curve breaks, and the piece containing $p_k$ is mapped inside $H$.
+we realise that there is on $\VZ_{1,\alpha}(\PP^N|H,d)$ a line bundle (the leftmost term in the exact sequence above) with a natural section cutting the locus where the curve breaks, and the piece containing $p_k$ is mapped inside $H$.
 \begin{lem}
@@
 \end{remark}
-By Corollary \ref{cor:log_smooth}, the divisorial logarithmic strata correspond to rays of the Artin fan.
+By Corollary \ref{cor:log_smooth}, the logarithmic strata of codimension one correspond to rays of the Artin fan.
 
@@
 In fact there is only one such vertex, because, if there were more, the relative position of their image in $\mathbb R_{\geq 0}$ under the tropical map would be unconstrained, therefore spanning a locus larger than a ray in the tropical moduli space.
-We follow in R.
+\marginpar{say something about rigid tropical curves as in ACGS and KLR} We follow in R.
 Vakil's footsteps in setting the following notation:
@@
 
-On the other hand, when there is a contracted elliptic subcurve - and it will be contracted into the hyperplane, because otherwise it wouldn't be generic, by density of the nice locus in $\VZ_{1,\tilde\alpha}(\PP^N|H,\tilde d)$ - the picture becomes much more complicated due to the alignment.
-The combs may break multiple times and they may even point in opposite directions.
+On the other hand, when there is a contracted elliptic subcurve - and it will be contracted into the hyperplane, because otherwise it wouldn't be generic, by density of the nice locus in $\VZ_{1,\alpha^\prime}(\PP^N|H,d^\prime)$ - the picture becomes more complicated due to the alignment.
+The combs may break (multiple times) and they may point in opposite directions.
+We label these loci $\mathcal{Y}_c^0$.
 \begin{figure}
  \tikz{
- \draw (0,0) circle(2pt)[fill=black] (0,2) circle(2pt)[fill=black] (0,4) circle(2pt)[fill=black] (0,6) circle(2pt)[fill=black] (0,-2) circle(2pt)[fill=black] (2,0) circle(2pt)[fill=white] (1.1,1.78) circle(2pt)[fill=black] (3.42,1.42) circle(2pt)[fill=black] (.58,-1.42) circle(2pt)[fill=black];
+ \draw (0,0) circle(2pt)[fill=black] (0,2) circle(2pt)[fill=black] (0,4) circle(2pt)[fill=black] (0,6) circle(2pt)[fill=black] (0,-2) circle(2pt)[fill=black] (1.1,1.78) circle(2pt)[fill=black] (3.42,1.42) circle(2pt)[fill=black] (.58,-1.42) circle(2pt)[fill=black];
  \draw (2,0) -- node[above]{4} (0,0) (2,0) --node[above]{2} (1.1,1.78) --node[above]{2} (0,2) (1.1,1.78) --node[above]{1} (0,4) (2,0) --node[above]{1} (3.42,1.42) (2,0) --node[above]{1} (.58,-1.42) (3.42,1.42) --node[above]{5} (0,6) (.58,-1.42) --node[above]{3} (0,-2);
  \draw[red] (2,0) circle(2);
+ \draw (2,0) circle(2pt)[fill=white];
+ \draw[->] (0,-3) circle(2pt)[fill=black] edge (4,-3);
  }
 \end{figure}
+\begin{dfn}
+ A degree-aligned genus one tropical map $\phi$ to $\mathbb R_{\geq 0}$ is ... with a circle of radius $\delta$ around the core satisfying:
+ \begin{enumerate}
+  \item the circle of radius $\delta$ passes through at least one vertex of positive degree, and no vertex of positive degree is contained in its strict interior;
+  \item every circle of radius $<\delta$ around the core passes through (either none or) at least two vertices;\footnote{The subdivisions we perform before picking a ray correspond to aligning the log structure, i.e.
+imposing $\lambda(v)=\lambda(v^\prime)$ for some $v,v^\prime$.}
+  \item every edge heading out of the circle of radius $\delta$ goes directly to a vertex in $\phi^{-1}(0)$.
+ \end{enumerate}
+\end{dfn}
 
-\subsection{Boundary loci}
-We follow in Vakil's footsteps in setting the following notation:
+\begin{remark}
+ The core being contracted in the fiber of the tropical map is not a phenomenon that we should worry about in codimension one.
+Indeed, assume that the core is contracted in the fiber along a ray.
+Then all the edges departing from the core have expansion factor $0$; call the corresponding coordinates $U=\{u_i\}_{i\in I}$.
+Call the remaining coordinates $E=\{e_j\}_{j\in J}$.
+Note that tropical continuity involves only $E$.
+Alignments on the other hand assume the form $\lambda(v)=\lambda(v^\prime)$, where $\lambda(v)=\sum_{i\in I(v)}u_i\sum_{j\in J(v)}e_j$.
+Pick the shortest elements of $U$; then these can be shortened to zero without affecting the rest (by hypothesis, alignments can only identify them among themselves).
+This shows that we could not have started with a ray.
+\end{remark}
+
+\subsection{Explicit realisation}
+The description of the first three types is relatively easy:
 \begin{enumerate}[label=(\alph*)]
- \item \[\mathcal Y^a=\M{0}{\lvert\alpha^{(0)}\rvert+r}{H}{d_0}\times_{H^r}\left(\VZc{1}{\alpha^{(1)}\cup\{m^{(1)}\}}{\PP^N|H}{d_1}\times\prod_{i=2}^r\M{0}{\alpha^{(i)}\cup\{m^{(i)}\}}{\PP^N|H}{d_i}\right)\]
- \item \[\mathcal Y^b=\M{0}{\lvert\alpha^{(0)}\rvert+r}{H}{d_0}\times_{H^r}\left(\M{0}{\alpha^{(1)}\cup\{m^{(1)},m^{(2)}\}}{\PP^N|H}{d_1}\times\prod_{i=3}^r\M{0}{\alpha^{(i)}\cup\{m^{(i)}\}}{\PP^N|H}{d_i}\right)\]
- \item \[\mathcal Y^c\subseteq \VZc{1}{\lvert\alpha^{(0)}\rvert+r}{H}{d_0}\times_{H^r}\prod_{i=1}^r\M{0}{\alpha^{(i)}\cup\{m^{(i)}\}}{\PP^N|H}{d_i}\]
- $\mathcal Y^c$ is cut within the latter by Gathmann's condition on line bundles:
- \[f_{|E}^*\mathcal O_H(1)\cong\mathcal O_E\left(\sum_{x_j\in E}\alpha_jx_j-\sum_{i=1}^r m^{(i)}y_i\right)\]\sidenote{Express the line bundle condition in terms of tautological classes?}
- Notice that such condition depends on the choice of $m^{(i)}$ but is really just a condition on the first factor of the product, so $\mathcal Y^c$ itself can be expressed as a product.
+ \item \[\mathcal Y_a=\M{0}{\{-m^{(1)},\ldots,-m^{(r)}\}\cup\alpha^{(0)}}{H}{d_0}^\sim\times_{H^r}\left(\VZc{1}{\alpha^{(1)}\cup\{m^{(1)}\}}{\PP^N|H}{d_1}\times\prod_{i=2}^r\M{0}{\alpha^{(i)}\cup\{m^{(i)}\}}{\PP^N|H}{d_i}\right)\]
+ \item \[\mathcal Y_b=\M{0}{\{-m^{(1)},\ldots,-m^{(r)}\}\cup\alpha^{(0)}}{H}{d_0}^\sim\times_{H^r}\left(\M{0}{\alpha^{(1)}\cup\{m^{(1)},m^{(2)}\}}{\PP^N|H}{d_1}\times\prod_{i=3}^r\M{0}{\alpha^{(i)}\cup\{m^{(i)}\}}{\PP^N|H}{d_i}\right)\]
+ \item \[\mathcal Y_c^+= \VZc{1}{\{-m^{(1)},\ldots,-m^{(r)}\}\cup\alpha^{(0)}}{H}{d_0}^{\sim} \times_{H^r}\prod_{i=1}^r\M{0}{\alpha^{(i)}\cup\{m^{(i)}\}}{\PP^N|H}{d_i}\]
 \end{enumerate}
+where $\M{0}{\mu}{H}{d}^\sim$ denotes the space of genus zero punctured maps, while $\VZc{0}{\mu}{H}{d}$ denotes the desingularisation of the main component of the space of punctured maps discussed in Section ???.
+The numerical data run over all splitting $A$ of the tangency conditions (resp.
+$B$ of the degree) in $r+1$ parts, such that:
+\begin{enumerate}
+ \item $d_0+\sum_{i=1}^r m^{(i)}=\sum\alpha^{(0)}$;
+ \item $d_i=m^{(i)}+\sum\alpha^{(i)}$;
+ \item $d_0>0$ in case $c$.
+\end{enumerate}
+
+Review here the process of gluing for punctured maps.
+In particular the basic monoid should be modified in order to make the relevant evaluations log morphisms.
+Claim: evaluations are strict.
+Consequence: the fiber product in the category of log stacks is fine.
+We have then to apply saturation.
+This is a finite morphism of degree...
+(I think it could be $\frac{\prod m^{(i)}}{lcm(m^{(i)}}$).
+
+\begin{lemma}[Virtual pushforward] The following hold.
+ \begin{itemize}
+  \item $\fgt_*[\M{0}{\alpha}{\PP^N|H}{d}]=[\MG{0}{\alpha}{\PP^N|H}{d}]$ (follows from \cite{GathmannThesis,AbramovichMarcusWiseComparison}).
+  \item $\fgt_*[\VZc{1}{\alpha}{\PP^N|H}{d}]$ computes the reduced relative invariants by definition.
+  \item $\fgt_*[\M{0}{\mu}{H}{d_0}^\sim]=[\M{0}{\lvert\mu\rvert}{H}{d_0}]$ (follows from \cite{GathmannThesis} and... comparison of punctured with rubber invariants).
+  \item $\fgt_*[\VZc{1}{\mu}{H}{d_0}^\sim]$ here we should need a variation on Pixton's DRC formula; hopefully it's enough to avoid the graphs that tropical well-spacedness discards.
+ \end{itemize}
+\end{lemma}
 

### 2018-12-04 new.tex
punctured maps?

@@
 
-\section{Description of the boundary}
+\subsection{A desingularisation of punctured log maps}
+Describe an analogous desingularisation for punctured log maps.
+The degree zero case seems more delicate and complicated, even though it should just be a substack of a moduli space of marked curves after all (the log structure is possibly trickier).
+\begin{dfn}
+ A $(z,g,n)$-punctured log map is a punctured log map where the markings with negative contact order to $H$ have an extra label, either $z$ (the tropical map sends them to $z$ero), or $g$ (stands for gluing), or $n$ (stands for nihil, nothing...)
+\end{dfn}
+We would like to extend the minimal monoid in order to account for some of the punctures, i.e.
+take the sum of $p^*\mathcal M_{C^\circ}$ (for every such puncture $p$) fibered over the log structure of the base, which seems to have the same effect as topping those edges with a uertex (which doesn't carry any other information).
+This looks to me like sprouting a $\PP^1$ at those puncture.
+Now, the point of the $(z,g,n)$-labelling is that: we only extend the log structure at the $z$ and $g$ punctures; uertices labelled with a $z$ are sent under the tropical map to $0$, so continuity applies to them (therefore the extension of the log structure is fake because that edge length is determined by the position of the adjacent vertex); while uertices labelled with an $n$ are free to roam about.
+Finally, we perform a radial alignment (and we take rays).
+This distinction comes about when you split your centrally aligned map according to the strict interior of the $\delta$-circle and the outside; the intersection of a tree with the $\delta$-circle can either be a vertex over $0$, or another vertex (corresponding to a degeneration of the genus zero map outside), or not a vertex.
+
+\section{The boundary}
 
@@
 This is a finite morphism of degree...
-(I think it could be $\frac{\prod m^{(i)}}{lcm(m^{(i)}}$).
+(I think it could be $\frac{\prod m^{(i)}}{lcm(m^{(i)})}$).
 

### 2018-12-30 GenusOneRelativeMaps.tex

--- 2018-12-04 new.tex
@@
 
+\subsection{$\mathcal{Y}_c^0$}
+\begin{ex}
+ We look at the following example in some detail.
+ \begin{figure}[h]
+  \tikz{
+  \draw (0,1) circle(2pt)[fill=black] --node[above]{2} (2,0);
+  \draw (0,-1) circle(2pt)[fill=black] --node[above]{2} (2,0);
+  \draw (2,0) -- (2.5,0) node[right]{4};
+  \draw (2,0)  circle(2pt)[fill=white];
+  \draw (0,1) -- (.33,1.33) node[above right]{0};
+  \draw (0,-1) -- (.33,-1.33) node[below right]{0};
+  \draw[red] (2,0) circle(2.23);
+  \draw[->] (0,-2.5)node[left]{0} circle(2pt)[fill=black] edge (4,-2.5);
+  }
+ \end{figure}
+ The ambient space is $\VZc{1}{(4,0,0)}{\PP^N|H}{4}$, of dimension $4N+3$.
+The underlying moduli space is $X=\M{0}{(2,0)}{\PP^N|H}{2}\times_H\M{0}{(2,0)}{\PP^N|H}{2}\times\VZ_{1,(-2,-2,4)}$ of dimension $5N+1$.
+Consider the fiber product:
+ \bcd
+ F\ar[r]\ar[d]& \M{0}{(2,0)}{\PP^N|H}{2}\times\M{0}{(2,0)}{\PP^N|H}{2}\ar[d]\\
+ H\ar[r] & H\times H
+ \ecd
+ At the level of ghost sheaves, $\oM_F=\mathbb N\oplus_{\mathbb N^2}\oM_1^{\rm{enl}}\oplus\oM_2^{\rm{enl}}$, where the map $\mathbb N^2\to\mathbb N$ is the sum, and the map $\mathbb N^2\to\oM_1^{\rm{enl}}\oplus\oM_2^{\rm{enl}}$ generically is multiplication by $2$, so $\oM_F=\mathbb N^2/(2e=2f)$ generically.
+Saturation gives a finite cover $G\to F$ with $\oM_G=\mathbb N_{e=f}$ generically.
+Lifting this to actual log structures, what we are doing (again generically) is taking a square root of the isomorphism $T_{R_1,q_1}^{\otimes 2}\simeq T_{R_2,q_2}^{\otimes 2}$, which is obtained passing through $N_{H/\PP^N,f(Z)}$ via $\operatorname{d}f_{|R_i,q_i}$.
+This breaks when $f_{|R_i}$ is not tangent to $H$ of order exactly $2$ at $q_i$, for either $i$; but by the maximality assumption this happens precisely along Gathmann's comb loci $\Delta_i$.
+So in fact, rather than with $T_{R_i,q_i}^{\otimes 2}$, we should be working with $T_{R_i,q_i}^{\otimes 2}(-\Delta_i)$: but this is exactly $\ev_i^*(-H)$ by Gathmann's genus zero formula, and the isomorphism $\ev_1^*(H)=\ev_2^*(H)$ holds on all of $F$.
+
+ On the other hand, generically on $\VZ_{1,(-2,-2,4)}$ we have $T_{q_1}Z\simeq T_{q_2}Z$ by exploiting the group structure on the elliptic curve.
+This breaks when either (but not both) is on a rational tail.
+Yet we have $T_{q_1}Z(\Delta_{1\in P})\simeq T_{q_2}Z(\Delta_{2\in P})$ by Vakil-Zinger's construction of a universal $\psi$-class (i.e.
+by comparing both with $\pi_*\omega(\Delta)$; notice that our further blow-up has the only effect of twisting \emph{all} the relevant line bundles by $\Delta_{1,2\notin P}$).
+
+ Now, the fiber of the Vakil-Zinger blow-up over $X$ can be described as follows. Generically it looks like \[\PP(T_{q_1}R_1\otimes T_{q_1}Z\oplus T_{q_2}R_2\otimes T_{q_2}Z)\]
+ but this has to be modified along the boundary:
+ \begin{itemize}
+  \item this has to do with the fact that the normal bundle of the strict transform is the pullback of the normal bundle twisted by the intersection with the exceptional divisor (so it relates with previous steps of the blow-up);
+  \item it is not globally a $\PP^1$-bundle (so it relates with further stages of the blow-up; it also has to do with a choice of compactification for the moduli space of attachments);
+  \item it has the effect of replacing $T_{q_i}Z$ with Vakil-Zinger's universal $\mathbb T$, so that this can be factored out of the projective bundle, and in fact we are left with a projective bundle $\mathbb P=\PP(T_{q_1}R_1\oplus T_{q_2}R_2)$ over $F$, and its open part $\operatorname{Iso}(T_{q_1}R_1\oplus T_{q_2}R_2)$ represents the attachment data for a contraction to a tacnode $R_1\sqcup_q R_2\to\bar{C}$.
+ \end{itemize}
+On $\PP$ there is a natural vector bundle map \[s\colon \OO_{\PP}(-1)\hookrightarrow p^*(T_{q_1}R_1\oplus T_{q_2}R_2)\xrightarrow{+\operatorname{d}f}\ev_q^*T\PP^N\]
+that vanishes along the locus where $f$ descends to $\bar C$. In general, it is not a transversal section:
+\begin{itemize}
+ \item we should replace $T\PP^N$ by $TH$ as long as all the $m^{(i)}$ are $\geq2$;
+ \item Vakil and Zinger construct a blow-up of $\PP$ along the vanishing loci of $s$ of low codimension, and twist $s$ by the exceptional divisors, so that it becomes a transverse section $\tilde{s}$.
+\end{itemize}
+On the other hand, the finite cover $G\to F$ factors through $\PP$, because the two vertices are already aligned on $G$.
+We claim that the boundary locus of $\VZc{1}{(4,0,0)}{\PP^N|H}{4}$ corresponding to the combinatorial type of the tropical map above is the transverse intersection
+\[\left(G\cap V(\tilde{s})\subseteq\PP\right)\times\VZ_{1,(-2,-2,4)}.\]
+This has the expected dimension (codimension $N-1$ with respect to $X$).
+To compute its class, we can pull $\PP$ back to $G$, and then notice that $G\hookrightarrow\PP_G$ is the inclusion of a (trivial) subbundle.
+\begin{lem}
+ The class of $\PP(\mathcal F)\subseteq\PP(\mathcal E)$ is $c_{\rm{top}}(\OO_\mathcal{E}(1)\otimes p^*(\mathcal{E}/\mathcal{F}))$.
+\end{lem}
+See \cite[Prop.
+9.13]{EH3264}.
+It is a good time to remember that $\mathcal E$ was in fact $(\bigoplus_{i=1}^rTR_{i,q_i})\otimes\mathbb T$.
+By writing $c$ for $c_1(\OO_\mathcal{E}(1))$, $\psi_i$ for $c_1(T^*R_{i,q_i})$, $\psi_Z$ for Vakil-Zinger's universal psi class, and $H$ for $\ev_q^*H$, we need to compute
+\begin{align*}
+p_*\left((c-\psi_1-\psi_2-2\psi_Z)[(1+c+H)^N(1+c)^{-1}]_{N-1}\right)= \\
+p_*\left((c-\psi_1-\psi_2-2\psi_Z)(\sum_{k=0}^{N-1}\binom{N}{1+k}c^kH^{N-1-k})\right)=\\
+\sum_{k=0}^{N-1}\binom{N}{k}H^{N-1-k}\big(s_k(\mathcal E)-s_{k-1}(\mathcal E)(\psi_1+\psi_2+\psi_Z)\big)
+\end{align*}
+
+\end{ex}
+
 \section{The space of relative centrally aligned maps}

### 2018-12-30 GenusOneRelativeMaps.tex
Started recursive description of boundary section

@@
 \newcommand{\Aut}{\operatorname{Aut}}
-\newcommand{\RR}{\textbf{R}}
+\newcommand{\Acal}{\mathcal{A}}
+\newcommand{\Mcal}{\mathcal{M}}
+\newcommand{\ol}[1]{\overline{#1}}
+\newcommand{\op}[1]{\operatorname{#1}}
+\newcommand{\gp}{\operatorname{gp}}
+\newcommand{\RR}{\mathbb{R}}
 \newcommand{\NN}{\mathbb{N}}
@@
 
-\textbf{Statement of the problem.} Contrary to the genus zero case, the moduli space of genus one maps to projective space - with or without markings - is far from smooth; indeed it has various boundary components of different dimensions, representing maps that contract a genus one curve and have all the degree supported on a number of rational tails.
+\subsection{Statement of the problem} Contrary to the genus zero case, the moduli space of genus one maps to projective space - with or without markings - is far from smooth; indeed it has various boundary components of different dimensions, representing maps that contract a genus one curve and have all the degree supported on a number of rational tails.
 The many incarnations of relative moduli spaces also suffer of the same undesirable feature.
@@
 
-\textbf{Choice of relative space and desingularisation.} We focus on the space of logarithmic stable maps to $(\PP^N|H)$, following ACGS.
+\subsection{Choice of relative space and desingularisation} We focus on the space of logarithmic stable maps to $(\PP^N|H)$, following ACGS.
 We perform a log modification of this space as detailed below.
@@
 
-\textbf{Gathmann-type recursion.} There is a forgetful morphism \[\VZ_{1,\alpha}(\PP^N|H,d)\to \VZ_{1,n}(\PP^N,d),\] hitting Gathmann's relative space.
+\subsection{Gathmann-type recursion} There is a forgetful morphism \[\VZ_{1,\alpha}(\PP^N|H,d)\to \VZ_{1,n}(\PP^N,d),\] hitting Gathmann's relative space.
 We may therefore pullback Gathmann's line bundle and section, cutting out the locus where the $k$-th marking is tangent to $H$ to order $\alpha_k+1$.
@@
 
-\section{A desingularisation of the log space}
+\section{Desingularisation of the moduli space of log stable maps}
 The ultimate goal of the paper is to apply Gathmann's techniques to the Vakil-Zinger desingularisation $\VZ_{1,n}(\PP^N,d)$ and to obtain a quantum Lefschetz result for reduced invariants under some positivity assumption.
@@
 
-\section{The boundary}
+\newpage
+
+\section{Recursive description of the boundary}
+Let $\VZ = \VZ_{1,\alpha}(\PP^N|H,d)$ and let $\Acal$ denote the Artin fan of $\VZ$. Since the map
+\begin{equation*} \VZ \to \Acal \end{equation*}
+is smooth and strict, we see that the codimension-$k$ logarithmic strata in $\VZ$ are in bijective correspondene (via pull-back) with the codimension-$k$ logarithmic strata in $\Acal$.
+The logarithmic strata in $\Acal$, on the other hand, have a purely combinatorial description (at least locally) in terms of the associated moduli spaces of tropical curves, coming from the fact that $\VZ$ is a logarithmic blow-up of the usual moduli space of log stable maps.
+In this section we discuss this circle of ideas, and show how it plays out in a number of examples.
+
+Let $\Mcal = \ol{\Mcal}^{\op{log}}_{1,\alpha}(\PP^N|H,d)$ denote the Abramovich--Chen--Gross--Siebert moduli space of log stable maps.
+Recall that $\VZ$ is obtained as a closed substack of a log modification
+\begin{equation*} \widetilde{\VZ} \to \Mcal .\end{equation*}
+Since the map $\VZ \hookrightarrow \widetilde{\VZ}$ is strict, their Artin fans agree, so for the moment let us focus on $\widetilde{\VZ}$. We have a commutative square:
+\bcd
+\widetilde{\VZ} \ar[r] \ar[d] & \Mcal \ar[d] \\
+\Acal \ar[r] & \Acal_{\Mcal}.
+\ecd
+Note that neither of the vertical maps are smooth, since the moduli spaces on the top row are not log smooth.
+The construction of $\widetilde{\VZ} \to \Mcal$ as the log modification obtained by imposing an alignment condition gives us a combinatorial description of the map $\Acal \to \Acal_{\Mcal}$ which we will use to study $\Acal$.
+Recall that $\Acal$ is locally isomorphic to the stack quotient
+\begin{equation*} \left[ \Spec \kfield[Q] / \Spec\kfield [Q^{\gp}] \right]\end{equation*}
+where $Q$ is a monoid giving a\footnote{(Navid) Neat?} local chart for $\Mcal$, which we may take to be the minimal monoid of \cite[\S 1.5]{GrossSiebertLog}.
+The real dual $Q^\vee_{\RR} = \Hom(Q,\RR_{\geq 0})$ of this monoid can be viewed as a moduli space of tropical maps; see \cite[Remark 1.12]{GrossSiebertLog}.
+We call this \emph{the tropical moduli space}; belonging to the tropical moduli space are the edge lengths of the associated tropical curve (corresponding to the smoothing parameters of the nodes of the logarithmic curve).
+Since the alignemnt condition amounts to imposing a partial ordering amongst certain sums of these edge lengths, it produces a polyhedral decomposition of the tropical moduli space into chambers where different partial order relations hold.
+If we only consider the integral points, this produces a polyhedral decomposition of the cone $Q^\vee = \Hom(Q,\N)$.
+Dualising, we obtain a toric blow-up
+\begin{equation*} Z \to \Spec \kfield[Q] \end{equation*}
+which, since it is equivariant, descends to a morphism of the associated $0$-dimensional stacks:
+\begin{equation*} \left[Z/T_Z \right] \to \left[ \Spec \kfield[Q] / \Spec\kfield [Q^{\gp}] \right]. \end{equation*}
+This gives an affine-local description of the map $\Acal \to \Acal_\Mcal$ and in particular of the Artin fan $\Acal$.
+By the orbit-cone correspondence, the codimension-$k$ strata of $\Acal$ (locally) correspond to the $k$-dimensional cones in the polyhedral decomposition of $Q^\vee$.
+This is best understood through examples: we now present a number of these.
+
+\newpage
+
+\section{Recursion formula for $(\PP^N|H)$}
 
@@
 \end{align*}
-
 \end{ex}
 
-\section{The space of relative centrally aligned maps}
-\noindent Recall \cite{RSPW} that the moduli space of maps from centrally aligned curves is obtained by considering the  Cartesian diagram
+\section{Recursion formula in general}
+Now let $(X|Y)$ be a smooth pair with $Y$ very ample. The complete linear system $|\OO_X(Y)|$ defines an embedding $X \hookrightarrow \PP^N$ with $Y=X\cap H$ for $H$ some hyperplane.
+
+\begin{lemma} The following square is cartesian (in the category of ordinary stacks):
 \bcd
-\tVZc{1}{n}{X}{\beta}\ar[d]\ar[r]\ar[dr,phantom,"\Box"] & \M{1}{n}{X}{\beta}\ar[d] \\
-\MM_{1,n}^{\rm{ctr}}\ar[r] & \MM_{1,n}^{\dagger}
+\VZ_{1,\alpha}(X|Y,\beta) \ar[r] \ar[d] \ar[rd,phantom,"\square"] & \VZ_{1,\alpha}(\PP^N|H,d) \ar[d] \\
+\VZ_{1,n}(X,\beta) \ar[r,"i"] & \VZ_{1,n}(\PP^N,d).
 \ecd
-so that objects of $\tVZc{1}{n}{X}{\beta}$ consist of
-\begin{enumerate}
-\item a centrally aligned curve $(C,M_C,\delta)$;
-\item a stable map $f\colon C \to X$;
-\end{enumerate}
-subject to the condition that the subcurve $C_0 \subseteq C$, consisting of those components $C_v$ for which $\lambda(v) < \delta$, coincides with the maximal connected genus one subcurve contracted by $f$.
-They then define
-\begin{equation*} \VZc{1}{n}{X}{\beta} \subseteq \tVZc{1}{n}{X}{\beta} \end{equation*}
-to be the closed substack consisting of maps satisfying the \emph{factorisation condition}, namely that the map $f\colon C\to X$ factors through the associated contraction to a Smyth curve, i.e.
-there exists a map $\bar{f}$ making the following square commute:
-\bcd
-\widetilde C\ar[r]\ar[d] & \overline C\ar[d,"\bar f" left,dotted] \\
-C\ar[r,"f"] & X
-\ecd
-One should think of the factorisation condition as identifying the main component of the moduli space.
+\end{lemma}
+Since $\VZ_{1,n}(\PP^N,d)$ is smooth and $\VZ_{1,n}(X,\beta)$ carries a natural virtual class, there is a diagonal pull-back morphism which we use to define the virtual class on the space of maps to $(X|Y)$:
+\begin{equation*} \virt{\VZ_{1,\alpha}(X|Y,\beta)} := i_\Delta^! [\VZ_{1,\alpha}(\PP^N|H,d)]. \end{equation*}
+The recursion formula in $\VZ_{1,\alpha}(\PP^N|H,d)$ immediately pulls back along $i$ to give a recursion formula in $\VZ_{1,\alpha}(X|Y,\beta)$.
+\footnote{(Navid) Is it clear how to compute integrals over the pulled back classes?}
 
-\section{Definition of centrally aligned relative space}
-\section{Characterisation of the closed points of the relative space}
-\section{Recursion formula}
-
-\subsection{The case $\sum\alpha=d$}
-
-\subsection{Definition of the boundary components} According to Vakil's article there should be three sorts of boundary components.
-\begin{enumerate}[label=(\alph*)]
- \item \[\mathcal Y^a=\M{0}{\lvert\alpha^{(0)}\rvert+r}{H}{d_0}\times_{H^r}\left(\VZc{1}{\alpha^{(1)}\cup\{m^{(1)}\}}{\PP^N|H}{d_1}\times\prod_{i=2}^r\M{0}{\alpha^{(i)}\cup\{m^{(i)}\}}{\PP^N|H}{d_i}\right)\]
- \item \[\mathcal Y^b=\M{0}{\lvert\alpha^{(0)}\rvert+r}{H}{d_0}\times_{H^r}\left(\M{0}{\alpha^{(1)}\cup\{m^{(1)},m^{(2)}\}}{\PP^N|H}{d_1}\times\prod_{i=3}^r\M{0}{\alpha^{(i)}\cup\{m^{(i)}\}}{\PP^N|H}{d_i}\right)\]
- \item \[\mathcal Y^c\subseteq \VZc{1}{\lvert\alpha^{(0)}\rvert+r}{H}{d_0}\times_{H^r}\prod_{i=1}^r\M{0}{\alpha^{(i)}\cup\{m^{(i)}\}}{\PP^N|H}{d_i}\]
- $\mathcal Y^c$ is cut within the latter by Gathmann's condition on line bundles:
- \[f_{|E}^*\mathcal O_H(1)\cong\mathcal O_E\left(\sum_{x_j\in E}\alpha_jx_j-\sum_{i=1}^r m^{(i)}y_i\right)\]\sidenote{Express the line bundle condition in terms of tautological classes?}
- Notice that such condition depends on the choice of $m^{(i)}$ but is really just a condition on the first factor of the product, so $\mathcal Y^c$ itself can be expressed as a product.
-\end{enumerate}
+\section{Quantum Lefschetz in genus one}
 
 \bibliographystyle{alpha}
-\bibliography{relqm}
+\bibliography{Bibliography}
 

### 2018-12-30 GenusOneRelativeMaps.tex
Did first example

@@
 
+\newcommand{\mathsq}[1]{#1}
 \newcommand{\pM}{\pazocal{M}}
@@
 
-\section{Recursive description of the boundary}
-Let $\VZ = \VZ_{1,\alpha}(\PP^N|H,d)$ and let $\Acal$ denote the Artin fan of $\VZ$. Since the map
+\section{Determination of the logarithmic strata}
+\subsection{Logarithmic strata of the Artin fan}
+Let $\VZ = \VZ_{1,\alpha}(\PP^N|H,d)$ and let $\Acal$ denote the Artin fan of $\VZ$. Since the map of log stacks
 \begin{equation*} \VZ \to \Acal \end{equation*}
-is smooth and strict, we see that the codimension-$k$ logarithmic strata in $\VZ$ are in bijective correspondene (via pull-back) with the codimension-$k$ logarithmic strata in $\Acal$.
+is smooth, we see that the codimension-$k$ logarithmic strata in $\VZ$ are in bijective correspondene (via pull-back) with the codimension-$k$ logarithmic strata in $\Acal$.
 The logarithmic strata in $\Acal$, on the other hand, have a purely combinatorial description (at least locally) in terms of the associated moduli spaces of tropical curves, coming from the fact that $\VZ$ is a logarithmic blow-up of the usual moduli space of log stable maps.
@@
 \begin{equation*} \widetilde{\VZ} \to \Mcal .\end{equation*}
-Since the map $\VZ \hookrightarrow \widetilde{\VZ}$ is strict, their Artin fans agree, so for the moment let us focus on $\widetilde{\VZ}$. We have a commutative square:
+Since the map $\VZ \hookrightarrow \widetilde{\VZ}$ is strict, the Artin fan $\Acal$ of $\VZ$ is locally isomorphic to the Artin fan of $\widetilde{\VZ}$ (with the latter being, in general, larger).
+Since the following discussion is entirely local, we will ignore the distinction between the two, and pretend as though $\Acal$ is the Artin fan of $\widetilde{\VZ}$.
+There is then a commuting square:
 \bcd
@@
 We call this \emph{the tropical moduli space}; belonging to the tropical moduli space are the edge lengths of the associated tropical curve (corresponding to the smoothing parameters of the nodes of the logarithmic curve).
-Since the alignemnt condition amounts to imposing a partial ordering amongst certain sums of these edge lengths, it produces a polyhedral decomposition of the tropical moduli space into chambers where different partial order relations hold.
+Since the alignment condition amounts to imposing a partial ordering amongst certain sums of these edge lengths, it produces a polyhedral decomposition of the tropical moduli space into chambers where different partial order relations hold.
 If we only consider the integral points, this produces a polyhedral decomposition of the cone $Q^\vee = \Hom(Q,\N)$.
@@
 This gives an affine-local description of the map $\Acal \to \Acal_\Mcal$ and in particular of the Artin fan $\Acal$.
-By the orbit-cone correspondence, the codimension-$k$ strata of $\Acal$ (locally) correspond to the $k$-dimensional cones in the polyhedral decomposition of $Q^\vee$.
-This is best understood through examples: we now present a number of these.
+By the orbit-cone correspondence, the codimension-$k$ strata of $\Acal$ which intersect this open locus correspond to the $k$-dimensional cones in the polyhedral decomposition of $Q^\vee$ described above.
+This is best understood through a number of examples, which we now present.
+
+\subsection{Examples of logarithmic strata} In these examples we will proceed in the following manner: we will start by fixing an element of the ordinary moduli space $\Mcal$ of log stable maps.
+We will then compute the associated tropical moduli space, giving a description of $\Acal_\Mcal$ local to our chosen element.
+We will then describe the necessary polyhedral subdivison, and thus give a description of $\Acal$ in a neighbourhood of the preimage in $\VZ$ of our chosen element of $\Mcal$.
+Finally we will use this to describe the logarithmic strata which intersect this neighbourhood.
+\begin{example} Consider an element of $\Mcal$ whose associated tropical map has the following combinatorial type:
+\begin{center}
+\begin{tikzpicture}
+\draw [fill] (0,3) circle[radius=2pt];
+\draw (0,3) node[left]{$\mathsq{C}_1$};
+\draw (0,3) -- (2,2);
+\draw (1,2.5) node[above,color=red]{$1$};
+\draw (1,2.5) node[below]{$e_1$};
+
+\draw [fill] (0,1) circle[radius=2pt];
+\draw (0,1) node[left]{$\mathsq{C}_2$};
+\draw (0,1) -- (2,2);
+\draw (1,1.5) node[below,color=red]{$2$};
+\draw (1,1.5) node[above]{$e_2$};
+
+\draw [->] (2,2) -- (3,2);
+\draw (3,2) node[above]{$x_1$};
+
+\draw [fill=white] (2,2) circle[radius=2pt];
+\draw (2,2) node[above]{$\mathsq{C}_0$};
+
+\draw [->,color=red] (2,1.5) -- (2,0.5);
+
+\draw [->,color=red] (0,0) -- (3,0);
+\draw (0,0) [fill=red,color=red] circle[radius=2pt];
+\draw (3,0) node[right,color=red]{$\Sigma(\PP^N|H)$};
+\end{tikzpicture}
+\end{center}
+Here each edge (corresponding to a node of the curve) has a length $e_i$ and an expansion factor $u_i$ (indicated in red).
+The moduli space of such tropical maps is generated by the edge lengths $e_1$ and $e_2$
+\begin{equation*} (\RR_{\geq 0})_{e_1} \times (\RR_{\geq 0})_{e_2} \end{equation*}
+subject to the continuity condition $e_1=2e_2$. So the tropical moduli space is simply $\RR_{\geq 0}$ generated by $e_2$. Note that for any $e_2 > 0$ we have:
+\begin{equation*} \lambda(\mathsq{C}_2) = e_2 = e_1/2 < e_1 = \lambda(\mathsq{C}_1). \end{equation*}
+Thus, any logarithmic map with combinatorial type given by the above picture is automatically aligned.
+This means that the map $\VZ \to \Mcal$ is an isomorphism in a neighbourhood of our chosen element (there is no blowing up necessary).
+Indeed, the tropical moduli space is $\RR_{\geq 0}$ and this cone does not admit a polyhedral decomposition (there is no non-trivial toric blow-up of $\Aaff^1$).
+\end{example}
+
+\begin{example}
+Consider now an element of $\Mcal$ whose associated tropical map has the corresponding combinatorial type:
+
+\end{example}
 
@@
 \section{Recursion formula for $(\PP^N|H)$}
+
+In the previous section we used tropical geometry to identify the logarithmic strata of $\VZ_{1,\alpha}(\PP^N|H,d)$.
+We now focus our attention on the logarithmic divisors, providing a recursive description for these loci: i.e.
+a description using a fibre product of smaller moduli spaces.
+This is the technically most difficult part of the paper.
+As a result, we obtain a Gathmann recursion formula in genus one.
 

### 2018-12-30 GenusOneRelativeMaps.tex
Finished second example

@@
 \draw (3,2) node[above]{$x_1$};
+\draw (2.5,2) node[below,red]{$3$};
 
@@
 Consider now an element of $\Mcal$ whose associated tropical map has the corresponding combinatorial type:
+\begin{center}
+\begin{tikzpicture}
+\draw [fill] (0,4) circle[radius=2pt];
+\draw (0,4) node[left]{$\mathsq{C}_1$};
+\draw (0,4) -- (2,3);
+\draw (1,3.5) node[above,color=red]{$1$};
+\draw (1,3.5) node[below]{$e_1$};
+
+\draw [fill] (0,1) circle[radius=2pt];
+\draw (0,1) node[left]{$\mathsq{C}_2$};
+\draw (0,1) -- (2,2);
+\draw (1,1.5) node[below,color=red]{$2$};
+\draw (1,1.5) node[above]{$e_2$};
+
+\draw [->] (2,3) -- (3,3);
+\draw (3,3) node[above]{$x_1$};
+\draw (2.5,3) node[above,red]{$1$};
+
+\draw (2,3) -- (2,2);
+\draw [fill] (2,2) circle[radius=2pt];
+\draw (2,2.5) node[right]{$e_3$};
+\draw (2.075,2.5) node[left,red]{$0$};
+\draw (2,2) node[below]{$\mathsq{C}_3$};
+
+\draw [->] (2,2) -- (3,2);
+\draw (3,2) node[above]{$x_2$};
+\draw (2.5,2) node[below,red]{$2$};
+
+\draw [fill=white] (2,3) circle[radius=2pt];
+\draw (2,3) node[above]{$\mathsq{C}_0$};
+
+\draw [->,color=red] (2,1.25) -- (2,0.5);
+
+\draw [->,color=red] (0,0) -- (3,0);
+\draw (0,0) [fill=red,color=red] circle[radius=2pt];
+\draw (3,0) node[right,color=red]{$\Sigma(\PP^N|H)$};
+\end{tikzpicture}
+\end{center}
+As before, expansion factors are indicated in red and the edge lengths are $e_1,e_2,e_3$.
+The tropical moduli space is $\RR_{\geq 0}^3$ generated by these three lengths, subject to the continuity condition $e_1=2e_2$.
+Thus the moduli space is isomorphic to $\RR_{\geq 0}^2$ generated by $e_2$ and $e_3$.
+In order to have an alignment, at least one of $\lambda(\mathsq{C}_1)$ and $\lambda(\mathsq{C}_2)$ must be equal to the radius $\delta$.
+Note that
+\begin{align*} \lambda(\mathsq{C}_1) & = e_1 = 2e_2 \\
+\lambda(\mathsq{C}_2) & = e_2 + e_3\end{align*}
+and without more information we cannot say which of these is larger.
+The subdivision of $(\RR_{\geq 0})^2$ is obtained by dividing the cone into regions where different order relations hold amongst the distances $\lambda(\mathsq{C}_1),\lambda(\mathsq{C}_2),\lambda(\mathsq{C}_3)$.
+The walls of this subdivison correspond to where some of these distances are equal.
+Note that in this setting we always have $\lambda(\mathsq{C}_2) > \lambda(\mathsq{C}_3)$ (at least, as long as we remain in the interior of the cone).
+The remaining possibilities are:
+\begin{align*} \lambda(\mathsq{C}_1) & = \lambda(\mathsq{C}_3) \qquad (\Leftrightarrow e_1 = e_3 \Leftrightarrow 2e_2 = e_3) \\
+\lambda(\mathsq{C}_1) & = \lambda(\mathsq{C}_2) \qquad (\Leftrightarrow e_1 = e_2 + e_3 \Leftrightarrow e_2 = e_3). \end{align*}
+Thus, the subdivision of the tropical moduli space $(\RR_{\geq 0}^2)_{e_2 e_3}$ is given by:
+\begin{center}
+\begin{tikzpicture}[scale=1]
+% Right-hand box
+\fill [fill=gray!30!white] (5,0) -- (8.75,0) -- (8.75,3.75) -- (5,3.75) -- cycle;
+\draw [fill] (5,0) circle[radius=2pt];
+\draw [->] (5,0) -- (9,0);
+\draw (9,0) node[right]{$e_2$};
+\draw [->] (5,0) -- (5,4);
+\draw (5,4) node[above]{$e_3$};
+
+% Left-hand box
+\fill [fill=gray!30!white] (-3,0) -- (0.75,0) -- (0.75,3.75) -- cycle;
+\fill [fill=gray!50!white] (-3,0) -- (0.75,3.75) -- (-1.125,3.75) -- cycle;
+\fill [fill=gray!30!white] (-3,0) -- (-1.125,3.75) -- (-3,3.75) -- cycle;
+\draw [fill] (-3,0) circle[radius=2pt];
+\draw [->] (-3,0) -- (1,0);
+\draw (1,0) node[right]{$e_2$};
+\draw [->] (-3,0) -- (-3,4);
+\draw (-3,4) node[above]{$e_3$};
+
+% 2e_2=e_3 line
+\draw [->] (-3,0) -- (-1,4);
+\draw (-1,4) node[above]{$2e_2=e_3$};
+
+% e_2=e_3 line
+\draw [->] (-3,0) -- (1,4);
+\draw (1,4) node[above]{$e_2=e_3$};
+
+% arrow
+\draw [->] (2,2) -- (4,2);
+\end{tikzpicture}
+\end{center}
+The cones of the subdivison index the logarithmic strata in a neighbourhood of the preimage in $\VZ$ of our chosen element of $\Mcal$. These can be described as follows:
+\begin{center}
+\begin{tikzpicture}[scale=1.8]
+% Left-hand box
+\fill [fill=gray!30!white] (-3,0) -- (0.75,0) -- (0.75,3.75) -- cycle;
+\fill [fill=gray!50!white] (-3,0) -- (0.75,3.75) -- (-1.125,3.75) -- cycle;
+\fill [fill=gray!30!white] (-3,0) -- (-1.125,3.75) -- (-3,3.75) -- cycle;
+\draw [fill] (-3,0) circle[radius=1pt];
+\draw (-3,0) -- (1,0);
+\draw (1,0) node[right,red]{$e_3=0$};
+\draw (-3,0) -- (-3,4);
+\draw (-3,4) node[above,red]{$e_1=e_2=0$};
+
+% 2e_2=e_3 line
+\draw (-3,0) -- (-1,4);
+\draw (-1,4) node[above,red]{$\lambda(\mathsq{C}_1)=\lambda(\mathsq{C}_3)$};
+
+% e_2=e_3 line
+\draw (-3,0) -- (1,4);
+\draw (1,4) node[above,red]{$\lambda(\mathsq{C}_1)=\lambda(\mathsq{C}_2)$};
+
+\draw (0,1.5) node[below,red]{$\lambda(\mathsq{C}_1) > \lambda(\mathsq{C}_2)$};
+
+\draw (-0.6,3.4) node[below,red]{$\lambda(\mathsq{C}_3) < \lambda(\mathsq{C}_1)$};
+\draw (-0.6,3.1) node[below,red]{$< \lambda(\mathsq{C}_2)$};
+
+\draw (-2.2,3.4) node[below,red]{$\lambda(\mathsq{C}_1) < \lambda(\mathsq{C}_3)$};
+\end{tikzpicture}
+\end{center}
+Geometrically, there are four codimension--$1$ logarithmic strata of $\VZ$ intersecting our chosen neighbourhood, corresponding to the rays in the above picture.
+Two of these -- those corresponding to $\{ e_1=e_2=0 \}$ and $\{ e_3=0 \}$ -- are the proper transforms of codimension--$1$ strata in $\Mcal$.
+Here some of the edge lengths are set to zero, and the corresponding logarithmic strata consist of  stable maps where the relevant nodes are smoothed.
+Notice that although the curve has three nodes, there are only two such strata: the nodes $q_1$ and $q_2$ cannot be smoothed independently because of the relation $e_1=2e_2$.
+
+The remaining two codimension--$1$ strata correspond to where certain of the vertex distances become equal.
+In these strata, none of the nodes are smoothed.
+From the construction of the subdvision, we see that they both map onto the codimension--$2$ stratum of $\Mcal$ in which all of the nodes persist; this coheres with the fact that they should be thought of as exceptional loci of the blow-up.
+The extra dimension of moduli comes from the choice of alignment.
+
+There are three codimension--$2$ strata corresponding to different strict orderings of the vertex distances.
+Note that the strata corresponding to $\{e_1=e_2=0\}$ and $\{e_3=0\}$, which intersected in $\Mcal$, no longer intersect in $\VZ$.
+The picture is something like:
+\begin{center}
+\begin{tikzpicture}[scale=0.5]
+\draw (-6.5,0.5) ellipse (4 and 2);
+\draw (-6.5,-1.5) node[below]{$\Mcal$};
+\draw [very thick] plot [smooth] coordinates{(-10,0.25) (-8,0.75) (-6,0)};
+\draw [very thick] plot [smooth] coordinates{(-7,0) (-5,0.75) (-3,0.5)};
+
+\draw (-21.5,0.5) ellipse (7 and 2);
+\draw (-21.5,-1.5) node[below]{$\VZ$};
+\draw [very thick] plot [smooth] coordinates{(-28,0.25) (-26,0.75) (-24,0)};
+\draw plot [smooth] coordinates{(-25,0) (-23,0.75) (-21,0)};
+\draw plot [smooth] coordinates{(-23,0) (-20,0.75) (-18,0)};
+\draw [very thick] plot [smooth] coordinates{(-20,0) (-17,0.75) (-15,0)};
+
+\draw [->] (-14,0.5) -- (-11,0.5);
+\end{tikzpicture}
+\end{center}
 

### 2019-01-01 GenusOneRelativeMaps.tex
Cleanup of Section 3

@@
 
-\section{Determination of the logarithmic strata}
-\subsection{Logarithmic strata of the Artin fan}
-Let $\VZ = \VZ_{1,\alpha}(\PP^N|H,d)$ and let $\Acal$ denote the Artin fan of $\VZ$. Since the map of log stacks
+\section{Indexing the logarithmic strata}
+\noindent Let $\VZ = \VZ_{1,\alpha}(\PP^N|H,d)$ and let $\Acal$ denote the Artin fan of $\VZ$. Since the map of log stacks
 \begin{equation*} \VZ \to \Acal \end{equation*}
-is smooth, we see that the codimension-$k$ logarithmic strata in $\VZ$ are in bijective correspondene (via pull-back) with the codimension-$k$ logarithmic strata in $\Acal$.
-The logarithmic strata in $\Acal$, on the other hand, have a purely combinatorial description (at least locally) in terms of the associated moduli spaces of tropical curves, coming from the fact that $\VZ$ is a logarithmic blow-up of the usual moduli space of log stable maps.
+is smooth, we see that the codimension-$k$ logarithmic strata in $\VZ$ are in bijective correspondence (via pull-back) with the codimension-$k$ logarithmic strata in $\Acal$.
+The logarithmic strata in $\Acal$, on the other hand, have a purely combinatorial description (at least locally) in terms of the associated moduli spaces of tropical maps, coming from the fact that $\VZ$ is a logarithmic blow-up of the usual moduli space of log stable maps.
 In this section we discuss this circle of ideas, and show how it plays out in a number of examples.
 
+\subsection{Blowing up the Artin fan}
 Let $\Mcal = \ol{\Mcal}^{\op{log}}_{1,\alpha}(\PP^N|H,d)$ denote the Abramovich--Chen--Gross--Siebert moduli space of log stable maps.
@@
 The construction of $\widetilde{\VZ} \to \Mcal$ as the log modification obtained by imposing an alignment condition gives us a combinatorial description of the map $\Acal \to \Acal_{\Mcal}$ which we will use to study $\Acal$.
-Recall that $\Acal$ is locally isomorphic to the stack quotient
+Recall that $\Acal_\Mcal$ is locally isomorphic to the stack quotient
 \begin{equation*} \left[ \Spec \kfield[Q] / \Spec\kfield [Q^{\gp}] \right]\end{equation*}
@@
 The real dual $Q^\vee_{\RR} = \Hom(Q,\RR_{\geq 0})$ of this monoid can be viewed as a moduli space of tropical maps; see \cite[Remark 1.12]{GrossSiebertLog}.
-We call this \emph{the tropical moduli space}; belonging to the tropical moduli space are the edge lengths of the associated tropical curve (corresponding to the smoothing parameters of the nodes of the logarithmic curve).
+We call this \emph{the tropical moduli space}; contained in the tropical moduli space are the edge lengths of the associated tropical curve (corresponding to the smoothing parameters of the nodes of the logarithmic curve).
 Since the alignment condition amounts to imposing a partial ordering amongst certain sums of these edge lengths, it produces a polyhedral decomposition of the tropical moduli space into chambers where different partial order relations hold.
@@
 \begin{equation*} Z \to \Spec \kfield[Q] \end{equation*}
-which, since it is equivariant, descends to a morphism of the associated $0$-dimensional stacks:
+which, since it is equivariant, descends to a morphism of the associated zero-dimensional stacks:
 \begin{equation*} \left[Z/T_Z \right] \to \left[ \Spec \kfield[Q] / \Spec\kfield [Q^{\gp}] \right]. \end{equation*}
-This gives an affine-local description of the map $\Acal \to \Acal_\Mcal$ and in particular of the Artin fan $\Acal$.
+This gives a local description of the map $\Acal \to \Acal_\Mcal$ and in particular of the Artin fan $\Acal$.
 By the orbit-cone correspondence, the codimension-$k$ strata of $\Acal$ which intersect this open locus correspond to the $k$-dimensional cones in the polyhedral decomposition of $Q^\vee$ described above.
-This is best understood through a number of examples, which we now present.
+These can be understood entirely in terms of tropical combinatorics.
+This is best explained through a number of examples, which we now present.
 
-\subsection{Examples of logarithmic strata} In these examples we will proceed in the following manner: we will start by fixing an element of the ordinary moduli space $\Mcal$ of log stable maps.
+\subsection{Examples of logarithmic strata} In these examples we will proceed as follows: we will start by fixing an element of the ordinary moduli space $\Mcal$ of log stable maps.
 We will then compute the associated tropical moduli space, giving a description of $\Acal_\Mcal$ local to our chosen element.
@@
 \begin{equation*} (\RR_{\geq 0})_{e_1} \times (\RR_{\geq 0})_{e_2} \end{equation*}
-subject to the continuity condition $e_1=2e_2$. So the tropical moduli space is simply $\RR_{\geq 0}$ generated by $e_2$. Note that for any $e_2 > 0$ we have:
+subject to the continuity condition $e_1=2e_2$. So the tropical moduli space is simply $\RR_{\geq 0}$ generated by $e_2$. Note that for any $e_2 > 0$ (i.e. on the interior of the cone) we have:
 \begin{equation*} \lambda(\mathsq{C}_2) = e_2 = e_1/2 < e_1 = \lambda(\mathsq{C}_1). \end{equation*}
@@
 This means that the map $\VZ \to \Mcal$ is an isomorphism in a neighbourhood of our chosen element (there is no blowing up necessary).
-Indeed, the tropical moduli space is $\RR_{\geq 0}$ and this cone does not admit a polyhedral decomposition (there is no non-trivial toric blow-up of $\Aaff^1$).
+Indeed, the tropical moduli space is $\RR_{\geq 0}$ and this cone does not admit a polyhedral subdivision (there is no non-trivial toric blow-up of $\Aaff^1$).
 \end{example}
@@
 \end{center}
-Geometrically, there are four codimension--$1$ logarithmic strata of $\VZ$ intersecting our chosen neighbourhood, corresponding to the rays in the above picture.
-Two of these -- those corresponding to $\{ e_1=e_2=0 \}$ and $\{ e_3=0 \}$ -- are the proper transforms of codimension--$1$ strata in $\Mcal$.
-Here some of the edge lengths are set to zero, and the corresponding logarithmic strata consist of  stable maps where the relevant nodes are smoothed.
+There are four codimension--$1$ logarithmic strata of $\VZ$ intersecting our chosen neighbourhood, corresponding to the rays in the above picture.
+Two of these -- those corresponding to the rays labeled $\{ e_1=e_2=0 \}$ and $\{ e_3=0 \}$ -- are the proper transforms of codimension--$1$ strata in $\Mcal$.
+These strata consist of log stable maps where some of the tropical edge lengths are equal to zero, meaning that the corresponding nodes have been smoothed.
 Notice that although the curve has three nodes, there are only two such strata: the nodes $q_1$ and $q_2$ cannot be smoothed independently because of the relation $e_1=2e_2$.
 
-The remaining two codimension--$1$ strata correspond to where certain of the vertex distances become equal.
-In these strata, none of the nodes are smoothed.
-From the construction of the subdvision, we see that they both map onto the codimension--$2$ stratum of $\Mcal$ in which all of the nodes persist; this coheres with the fact that they should be thought of as exceptional loci of the blow-up.
+The remaining two codimension--$1$ strata in $\VZ$ -- corresponding to the interior rays in the above picture -- consist of log stable maps where some of the vertex distances become equal.
+Here none of the nodes are smoothed.
+From the construction of the subdivision, we see that both these strata map onto a codimension--$2$ stratum of $\Mcal$ (namely, the locus in which all of the nodes persist); this coheres with the fact that they should be thought of as exceptional loci of the blow-up.
 The extra dimension of moduli comes from the choice of alignment.
 
-There are three codimension--$2$ strata corresponding to different strict orderings of the vertex distances.
-Note that the strata corresponding to $\{e_1=e_2=0\}$ and $\{e_3=0\}$, which intersected in $\Mcal$, no longer intersect in $\VZ$.
+Finally, there are three codimension--$2$ strata, corresponding to different \emph{strict} orderings of the vertex distances.
+Note that the divisorial strata corresponding to $\{e_1=e_2=0\}$ and $\{e_3=0\}$, which intersected in $\Mcal$, no longer intersect in $\VZ$, since we have blown up.
 The picture is something like:

### 2019-01-01 GenusOneRelativeMaps.tex
Started reorganising and rewriting Section 4

@@
 
+% FIGURES FOR USE LATER
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \def\Yagraph{\tikz[baseline=-3pt,scale=.8]{
@@
 \draw (0,.5) circle(2pt)[fill=black];
-\draw (0,-.5) node{$\ldots$};
+\draw (0,-.25) node{$\vdots$};
 \draw (0,-1) circle(2pt)[fill=black];
-\draw (-1,1.5) -- (1,1.5) -- (1,-1.5) -- (-1,-1.5) -- (-1,1.5);
-\draw (1,1.5) -- (3,2) -- (3,-1) -- (1,-1.5);
+\draw [red,fill=red] (0,-2) circle[radius=2pt];
+\draw [->,red,thick] (0,-2) -- (2,-2);
+\draw (2,-2) node[right,red]{\tiny{$\Sigma(\PP^N)$}};
+\draw [->,red] (1,-0.9) -- (1,-1.6);
 }}
@@
 \draw (0,.5) circle(2pt)[fill=black];
-\draw (0,-.5) node{$\ldots$};
+\draw (0,-.25) node{$\vdots$};
 \draw (0,-1) circle(2pt)[fill=black];
-\draw (-1,1.5) -- (1,1.5) -- (1,-1.5) -- (-1,-1.5) -- (-1,1.5);
-\draw (1,1.5) -- (3,2) -- (3,-1) -- (1,-1.5);
+\draw [red,fill=red] (0,-2) circle[radius=2pt];
+\draw [->,red,thick] (0,-2) -- (2,-2);
+\draw (2,-2) node[right,red]{\tiny{$\Sigma(\PP^N)$}};
+\draw [->,red] (1,-0.9) -- (1,-1.6);
 }}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \newcommand{\Mcal}{\mathcal{M}}
+\newcommand{\Dcal}{\mathcal{D}}
+\newcommand{\Ycal}{\mathcal{Y}}
 \newcommand{\ol}[1]{\overline{#1}}
@@
 
-In the previous section we used tropical geometry to identify the logarithmic strata of $\VZ_{1,\alpha}(\PP^N|H,d)$.
-We now focus our attention on the logarithmic divisors, providing a recursive description for these loci: i.e.
-a description using a fibre product of smaller moduli spaces.
+\noindent In the previous section we used tropical geometry to identify the logarithmic strata of $\VZ=\VZ_{1,\alpha}(\PP^N|H,d)$.
+We now focus our attention on the logarithmic divisors, providing a recursive description for these loci: that is, a description in terms of fibre products of smaller moduli spaces.
 This is the technically most difficult part of the paper.
-As a result, we obtain a Gathmann recursion formula in genus one.
+The recursive description bears some similarities with the recursive desription of the boundary of the absolute space $\VZ_{1,n}(\PP^N,d)$ given in \cite{VZ}; in keeping with the theme of this paper, however, we will see that the logarithmic structures provide a convenient framework for dealing with the combinatorics.
 
-Note that $f$ has contact order with $H$ exactly equal to $\alpha_k$ at the marking $p_k$, or else the irreducible component of $C$ on which $p_k$ lies is mapped entirely inside $H$.
-By pulling back along $f$ the equation defining $H$, and taking its $\alpha_k$-th derivative at $p_k$ (which makes sense because all the lower order derivatives do vanish by assumption) we single out the latter locus.
-By staring at the exact sequence of jet bundles
-\[0\to p_k^*\Omega_{C}^{\otimes\alpha_k}\otimes\ev_k^*\OO_{\PP^N}(H)\to p_k^*\mathcal J^{\alpha_k}(f^*\OO_{\PP^N}(H))\to p_k^*\mathcal J^{\alpha_k-1}(f^*\OO_{\PP^N}(H))\to 0\]
-we realise that there is on $\VZ_{1,\alpha}(\PP^N|H,d)$ a line bundle (the leftmost term in the exact sequence above) with a natural section cutting the locus where the curve breaks, and the piece containing $p_k$ is mapped inside $H$.
-\begin{lem}
- \[(\alpha_k\psi_k+\ev_k^*H)[\VZ_{1,\alpha}(\PP^N|H,d)]=[D_{1,\alpha;k}(\PP^N|H,d)],\]
-\end{lem}
-In what follows we shall give an explicit (recursive) description of the right-hand side, in terms of tautological classes on spaces of maps with lower numerical invariants.
-\begin{remark}
- The divisors we are after are a union of logarithmic strata, because the locus where the log structure is trivial coincides precisely with the nice locus.
-\end{remark}
-By Corollary \ref{cor:log_smooth}, the logarithmic strata of codimension one correspond to rays of the Artin fan.
+The end result is that we obtain an explicit formula for tautological integrals over these boundary loci. This produces a Gathmann recursion formula for relative invariants in genus one.
 
-\subsection{Combinatorial description}
-As long as the minimal subcurve of genus one has positive degree, the picture is classical: the dual graph of the curve is bipartite - vertices mapped inside $H$ are distinguished from the others.
-In fact there is only one such vertex, because, if there were more, the relative position of their image in $\mathbb R_{\geq 0}$ under the tropical map would be unconstrained, therefore spanning a locus larger than a ray in the tropical moduli space.
-\marginpar{say something about rigid tropical curves as in ACGS and KLR} We follow in R.
-Vakil's footsteps in setting the following notation:
+\subsection{Recursion setup} Consider an element of $\VZ$ and choose a marked point $x_k\in C$.
+We note that by the existence of a log morphism, either $f$ has contact order $\alpha_k$ to $H$ at the marking $x_k$, or else the irreducible component of $C$ containing $x_k$ is mapped entirely inside $H$ (we say ``$x_k$ belongs to an internal component'' in this case).
+
+By pulling back the equation defining $H$ along $f$ and then taking its $\alpha_k$-th derivative at $x_k$ (which makes sense since all the lower-order derivatives vanish by assumption) we obtain a section of a jet bundle on $\VZ$ whose vanishing locus coincides (set-theoretically) with the locus where $x_k$ belongs to an internal component.
+As in \cite[Construction 2.1]{Ga} there is an exact sequence of jet bundles
+\begin{equation*} 0\to x_k^*\omega_{\mathcal{C}/\VZ}^{\otimes\alpha_k}\otimes\ev_k^*\OO_{\PP^N}(H)\to x_k^*\mathcal J^{\alpha_k}(f^*\OO_{\PP^N}(H))\to x_k^*\mathcal J^{\alpha_k-1}(f^*\OO_{\PP^N}(H))\to 0 \end{equation*}
+and thus we obtain a section of the line bundle $x_k^*\omega_{\mathcal{C}/\VZ}^{\otimes\alpha_k}\otimes\ev_k^*\OO_{\PP^N}(H)$ with vanishing locus equal to the locus where $x_k$ belongs to an internal component.
+Writing this as
+\begin{equation*} \Dcal^k = \Dcal_{1,\alpha}^k(\PP^N|H,d) \subseteq \VZ_{1,\alpha}(\PP^N|H,d) = \VZ \end{equation*}
+we obtain:
+\begin{lem} $(\alpha_k\psi_k+\ev_k^*H)\cap[\VZ]=[\Dcal^k].\footnote{(Navid) Should we work out the vanishing orders of the section at this point?}$\end{lem}
+\noindent The remainder of this section will be devoted to providing an explicit (recursive) description of $[\Dcal^k]$ in terms of tautological classes on spaces of maps with smaller numerical invariants.
+As we will see, this provides an algorithm for computing reduced relative invariants, as well as a quantum Lefschetz algorithm for reduced (absolute) invariants in genus one.
+
+\subsection{Recursive description of the divisors: types $A,B$ and $C^+$}
+We begin by noting that every irreducible component of $\Dcal^k$ is a codimension--$1$ logarithmic stratum.
+This is obvious: the locus where the log structure is trivial coincides precisely with the nice locus, where the source curve is smooth and not mapped inside $H$.
+By definition $\Dcal^k$ is disjoint from this locus, and since it has codmension $1$ it must be equal to a union of logarithmic strata.
+
+As discussed at length in the previous section, the divisorial logarithmic strata of $\VZ$ correspond to the rays of the polyhedral subdivision of the tropical moduli space which produces the Artin fan $\Acal$.
+The logarithmic strata contained in $\Dcal^k$ correspond precisely to the rays of the tropical moduli space where the vertex of the tropicalisation containing $x_k$ is mapped into the interior of $\RR_{\geq 0}$ by the tropical map.
+
+We proceed as in the previous section, fixing an element of $\Mcal$ and considering the resulting subdivision of the tropical moduli space.
+As long as the minimal subcurve of genus one is not contracted, the picture is classical (i.e.
+the subdivision is trivial, and $\VZ=\Mcal$ locally).
+In this case there may only be one vertex of the tropical curve mapped into the interior of $\RR_{\geq 0}$; if there were more, the positions of their images in $\RR_{\geq 0}$ would be unconstrained and thus the corresponding maximal cone in the tropical moduli space would be at least $2$--dimensional, producing a locus in $\VZ$ of larger codimension.\footnote{(Luca) Say something about rigid tropical curves as in ACGS and KLR} We adopt the terminology of R.
+Vakil, distinguishing three cases as below:
+
 \begin{figure}[h]
@@
         \Yagraph
-        \caption{$\mathcal Y_a$}
+        \caption{$\mathcal Y_A$}
     \end{minipage}\hfill
@@
         \Ybgraph
-        \caption{$\mathcal Y_b$}
+        \caption{$\mathcal Y_B$}
     \end{minipage}\hfill
@@
         \Ycgraph
-        \caption{$\mathcal Y_c^+$}
+        \caption{$\Ycal_C^+$}
     \end{minipage}
 \end{figure}
+\noindent Notice that the continuity of the tropical map identifies all of the edge lengths up to scalars given by the expansion factors (i.e.
+tangency orders) at the edges; thus the tropical moduli space is isomorphic to $\RR_{\geq 0}$ and so we have a divisor (with no subdivision required).
 
-Notice that continuity of the tropical map determines the mutual relationship among the edge lengths.
+The description of the first three types is relatively easy:
+\begin{enumerate}[label=(\alph*)]
+ \item \[\mathcal Y_a=\M{0}{\{-m^{(1)},\ldots,-m^{(r)}\}\cup\alpha^{(0)}}{H}{d_0}^\sim\times_{H^r}\left(\VZc{1}{\alpha^{(1)}\cup\{m^{(1)}\}}{\PP^N|H}{d_1}\times\prod_{i=2}^r\M{0}{\alpha^{(i)}\cup\{m^{(i)}\}}{\PP^N|H}{d_i}\right)\]
+ \item \[\mathcal Y_b=\M{0}{\{-m^{(1)},\ldots,-m^{(r)}\}\cup\alpha^{(0)}}{H}{d_0}^\sim\times_{H^r}\left(\M{0}{\alpha^{(1)}\cup\{m^{(1)},m^{(2)}\}}{\PP^N|H}{d_1}\times\prod_{i=3}^r\M{0}{\alpha^{(i)}\cup\{m^{(i)}\}}{\PP^N|H}{d_i}\right)\]
+ \item \[\mathcal Y_c^+= \VZc{1}{\{-m^{(1)},\ldots,-m^{(r)}\}\cup\alpha^{(0)}}{H}{d_0}^{\sim} \times_{H^r}\prod_{i=1}^r\M{0}{\alpha^{(i)}\cup\{m^{(i)}\}}{\PP^N|H}{d_i}\]
+\end{enumerate}
+where $\M{0}{\mu}{H}{d}^\sim$ denotes the space of genus zero punctured maps, while $\VZc{0}{\mu}{H}{d}$ denotes the desingularisation of the main component of the space of punctured maps discussed in Section ???.
+The numerical data run over all splitting $A$ of the tangency conditions (resp.
+$B$ of the degree) in $r+1$ parts, such that:
+\begin{enumerate}
+ \item $d_0+\sum_{i=1}^r m^{(i)}=\sum\alpha^{(0)}$;
+ \item $d_i=m^{(i)}+\sum\alpha^{(i)}$;
+ \item $d_0>0$ in case $c$.
+\end{enumerate}
 
+Review here the process of gluing for punctured maps.
+In particular the basic monoid should be modified in order to make the relevant evaluations log morphisms.
+Claim: evaluations are strict.
+Consequence: the fiber product in the category of log stacks is fine.
+We have then to apply saturation.
+This is a finite morphism of degree...
+(I think it could be $\frac{\prod m^{(i)}}{lcm(m^{(i)})}$).
+
+\begin{lemma}[Virtual pushforward] The following hold.
+ \begin{itemize}
+  \item $\fgt_*[\M{0}{\alpha}{\PP^N|H}{d}]=[\MG{0}{\alpha}{\PP^N|H}{d}]$ (follows from \cite{GathmannThesis,AbramovichMarcusWiseComparison}).
+  \item $\fgt_*[\VZc{1}{\alpha}{\PP^N|H}{d}]$ computes the reduced relative invariants by definition.
+  \item $\fgt_*[\M{0}{\mu}{H}{d_0}^\sim]=[\M{0}{\lvert\mu\rvert}{H}{d_0}]$ (follows from \cite{GathmannThesis} and... comparison of punctured with rubber invariants).
+  \item $\fgt_*[\VZc{1}{\mu}{H}{d_0}^\sim]$ here we should need a variation on Pixton's DRC formula; hopefully it's enough to avoid the graphs that tropical well-spacedness discards.
+ \end{itemize}
+\end{lemma}
+
+\subsection{Recursive description of the divisors: type $C_0$}
 On the other hand, when there is a contracted elliptic subcurve - and it will be contracted into the hyperplane, because otherwise it wouldn't be generic, by density of the nice locus in $\VZ_{1,\alpha^\prime}(\PP^N|H,d^\prime)$ - the picture becomes more complicated due to the alignment.
@@
 
-\subsection{Explicit realisation}
-The description of the first three types is relatively easy:
-\begin{enumerate}[label=(\alph*)]
- \item \[\mathcal Y_a=\M{0}{\{-m^{(1)},\ldots,-m^{(r)}\}\cup\alpha^{(0)}}{H}{d_0}^\sim\times_{H^r}\left(\VZc{1}{\alpha^{(1)}\cup\{m^{(1)}\}}{\PP^N|H}{d_1}\times\prod_{i=2}^r\M{0}{\alpha^{(i)}\cup\{m^{(i)}\}}{\PP^N|H}{d_i}\right)\]
- \item \[\mathcal Y_b=\M{0}{\{-m^{(1)},\ldots,-m^{(r)}\}\cup\alpha^{(0)}}{H}{d_0}^\sim\times_{H^r}\left(\M{0}{\alpha^{(1)}\cup\{m^{(1)},m^{(2)}\}}{\PP^N|H}{d_1}\times\prod_{i=3}^r\M{0}{\alpha^{(i)}\cup\{m^{(i)}\}}{\PP^N|H}{d_i}\right)\]
- \item \[\mathcal Y_c^+= \VZc{1}{\{-m^{(1)},\ldots,-m^{(r)}\}\cup\alpha^{(0)}}{H}{d_0}^{\sim} \times_{H^r}\prod_{i=1}^r\M{0}{\alpha^{(i)}\cup\{m^{(i)}\}}{\PP^N|H}{d_i}\]
-\end{enumerate}
-where $\M{0}{\mu}{H}{d}^\sim$ denotes the space of genus zero punctured maps, while $\VZc{0}{\mu}{H}{d}$ denotes the desingularisation of the main component of the space of punctured maps discussed in Section ???.
-The numerical data run over all splitting $A$ of the tangency conditions (resp.
-$B$ of the degree) in $r+1$ parts, such that:
-\begin{enumerate}
- \item $d_0+\sum_{i=1}^r m^{(i)}=\sum\alpha^{(0)}$;
- \item $d_i=m^{(i)}+\sum\alpha^{(i)}$;
- \item $d_0>0$ in case $c$.
-\end{enumerate}
-
-Review here the process of gluing for punctured maps.
-In particular the basic monoid should be modified in order to make the relevant evaluations log morphisms.
-Claim: evaluations are strict.
-Consequence: the fiber product in the category of log stacks is fine.
-We have then to apply saturation.
-This is a finite morphism of degree...
-(I think it could be $\frac{\prod m^{(i)}}{lcm(m^{(i)})}$).
-
-\begin{lemma}[Virtual pushforward] The following hold.
- \begin{itemize}
-  \item $\fgt_*[\M{0}{\alpha}{\PP^N|H}{d}]=[\MG{0}{\alpha}{\PP^N|H}{d}]$ (follows from \cite{GathmannThesis,AbramovichMarcusWiseComparison}).
-  \item $\fgt_*[\VZc{1}{\alpha}{\PP^N|H}{d}]$ computes the reduced relative invariants by definition.
-  \item $\fgt_*[\M{0}{\mu}{H}{d_0}^\sim]=[\M{0}{\lvert\mu\rvert}{H}{d_0}]$ (follows from \cite{GathmannThesis} and... comparison of punctured with rubber invariants).
-  \item $\fgt_*[\VZc{1}{\mu}{H}{d_0}^\sim]$ here we should need a variation on Pixton's DRC formula; hopefully it's enough to avoid the graphs that tropical well-spacedness discards.
- \end{itemize}
-\end{lemma}
-
-\subsection{$\mathcal{Y}_c^0$}
 \begin{ex}

### 2019-01-01 GenusOneRelativeMaps.tex
Further improvements to Section 4

@@
 \begin{lem} $(\alpha_k\psi_k+\ev_k^*H)\cap[\VZ]=[\Dcal^k].\footnote{(Navid) Should we work out the vanishing orders of the section at this point?}$\end{lem}
-\noindent The remainder of this section will be devoted to providing an explicit (recursive) description of $[\Dcal^k]$ in terms of tautological classes on spaces of maps with smaller numerical invariants.
+\noindent The remainder of this section will be devoted to providing an explicit recursive description of $[\Dcal^k]$ in terms of tautological classes on spaces of maps with smaller numerical invariants.
 As we will see, this provides an algorithm for computing reduced relative invariants, as well as a quantum Lefschetz algorithm for reduced (absolute) invariants in genus one.
@@
 We proceed as in the previous section, fixing an element of $\Mcal$ and considering the resulting subdivision of the tropical moduli space.
-As long as the minimal subcurve of genus one is not contracted, the picture is classical (i.e.
+In fact, it makes sense to choose a locally closed substack of $\Mcal$ where the combinatorial type of the tropical curve (i.e.
+the ghost sheaf) is constant.
+Then as long as the minimal subcurve of genus one is not contracted, the picture is classical (i.e.
 the subdivision is trivial, and $\VZ=\Mcal$ locally).
-In this case there may only be one vertex of the tropical curve mapped into the interior of $\RR_{\geq 0}$; if there were more, the positions of their images in $\RR_{\geq 0}$ would be unconstrained and thus the corresponding maximal cone in the tropical moduli space would be at least $2$--dimensional, producing a locus in $\VZ$ of larger codimension.\footnote{(Luca) Say something about rigid tropical curves as in ACGS and KLR} We adopt the terminology of R.
-Vakil, distinguishing three cases as below:
+In this case there can only be one vertex of the tropical curve mapped into the interior of $\RR_{\geq 0}$; if there were more, the positions of their images in $\RR_{\geq 0}$ would be independent and thus the corresponding maximal cone in the tropical moduli space would be at least $2$~dimensional, producing a locus in $\VZ$ of larger codimension.\footnote{(Luca) Say something about rigid tropical curves as in ACGS and KLR} We adopt the terminology of Vakil, distinguishing three cases as below:
 
@@
 
-The description of the first three types is relatively easy:
-\begin{enumerate}[label=(\alph*)]
+These divisors live inside an open neighbourhood of the preimage in $\VZ$ of our chosen locus in $\Mcal$, and are thus locally closed substacks of $\VZ$.
+To obtain the desired components of $\Dcal^k$, we must take the closure of these locally closed substacks.
+We will analyse this procedure on a case-by-case basis, and see once again that the tropical picture gives a complete and recursive description of the closure.
+
+\subsubsection{Type A} By definition the locus $\Ycal_A$ contains those aligned maps which are in the closure of the locus of maps whose associated tropical curve has the same combinatorial type as Figure 1\footnote{(Navid) Bad LaTeX reference}.
+We will now argue that such an aligned map is always obtained by giving an alignment on the piece of the curve corresponding to the genus one vertex.
+
+We start by considering possible limiting points of our original locus in $\Mcal$. These correspond to further degenerations of the (combinatorial type of the) tropical map.
+
+\newpage
+Now we may use the recursive description of the boundary in $\Mcal$ using punctured maps \cite{PuncturedMaps} to obtain a description of these loci:
+\begin{enumerate}[label=(\Alph*)]
  \item \[\mathcal Y_a=\M{0}{\{-m^{(1)},\ldots,-m^{(r)}\}\cup\alpha^{(0)}}{H}{d_0}^\sim\times_{H^r}\left(\VZc{1}{\alpha^{(1)}\cup\{m^{(1)}\}}{\PP^N|H}{d_1}\times\prod_{i=2}^r\M{0}{\alpha^{(i)}\cup\{m^{(i)}\}}{\PP^N|H}{d_i}\right)\]

### 2019-01-01 GenusOneRelativeMaps.tex
Started description of Type A locus. Need to fix notation

@@
 \end{figure}
-\noindent Notice that the continuity of the tropical map identifies all of the edge lengths up to scalars given by the expansion factors (i.e.
+\noindent Notice that the continuity of the tropical map identifies all of the edge lengths, up to weights given by the expansion factors (i.e.
 tangency orders) at the edges; thus the tropical moduli space is isomorphic to $\RR_{\geq 0}$ and so we have a divisor (with no subdivision required).
@@
 To obtain the desired components of $\Dcal^k$, we must take the closure of these locally closed substacks.
-We will analyse this procedure on a case-by-case basis, and see once again that the tropical picture gives a complete and recursive description of the closure.
+We will analyse this procedure on a case-by-case basis, and see once again that the tropical picture gives a complete and recursive description of the combinatorics.
+As usual, this will be done by comparing loci in$\VZ$ with loci in $\Mcal$.
+To be more precise: we will take the closure of our locally closed substack in $\Mcal$ and relate it to the closure of our locally closed substack in $\VZ$.
+We will see that the induced map on closures is another blow-up.
+The closed locus in $\Mcal$ is understood by \cite{PuncturedMaps} as a fibre product of moduli spaces of punctured maps.
+\footnote{(Navid) Introduce notation for these locally closed substacks, because this shit is getting out of hand.}
 
-\subsubsection{Type A} By definition the locus $\Ycal_A$ contains those aligned maps which are in the closure of the locus of maps whose associated tropical curve has the same combinatorial type as Figure 1\footnote{(Navid) Bad LaTeX reference}.
-We will now argue that such an aligned map is always obtained by giving an alignment on the piece of the curve corresponding to the genus one vertex.
+\subsubsection{Type A} By definition the locus $\Ycal_A$ contains those elements of $\VZ$ which appear in the closure of the locus of aligned maps whose associated tropical curve has the same combinatorial type as Figure 1\footnote{(Navid) Bad LaTeX reference}.
+We will now argue that such an element restricts to give an aligned map on the piece of the curve corresponding to $\mathsq{C}_1$, and that conversely given an aligned map corresponding to $\mathsq{C}_1$ and ordinary punctured maps corresponding to $\mathsq{C}_0,\mathsq{C}_2,\ldots,\mathsq{C}_r$, the glued map is aligned.
+This shows that $\Ycal_A$ is equal, up to an \'etale quotient, to the fibre product:
+\begin{equation*}\M{0}{\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}{\PP^N|H}{d_0}\times_{H^r}\left(\VZ_{1,\alpha^{(1)}\cup(m_1)}(\PP^N|H,d_1)\times\prod_{i=2}^r\M{0}{\alpha^{(i)}\cup(m_i)}{\PP^N|H}{d_i}\right).
+\end{equation*}
+Put differently, the map from the closed locus in $\VZ$ to the closed locus in $\Mcal$ is given by blowing up one of the factors of the fibre product
+\begin{equation*}\M{0}{\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}{\PP^N|H}{d_0}\times_{H^r}\prod_{i=1}^r\M{0}{\alpha^{(i)}\cup(m_i)}{\PP^N|H}{d_i}. \end{equation*}
+and leaving the rest alone.
 
-We start by considering possible limiting points of our original locus in $\Mcal$. These correspond to further degenerations of the (combinatorial type of the) tropical map.
+Let us start by considering possible limiting points of our original locus in $\Mcal$. These correspond to further degenerations of the (combinatorial type of the) tropical map.
 

### 2019-01-02 GenusOneRelativeMaps.tex
Added subsection on global logarithmic strata (needs some work)

@@
 \newcommand{\Acal}{\mathcal{A}}
+\newcommand{\Scal}{\mathcal{S}}
 \newcommand{\Mcal}{\mathcal{M}}
@@
 \newtheorem*{acknowledgements}{Acknowledgements}
+
+\newlist{steps}{enumerate}{1}
+\setlist[steps, 1]{label = Step (\arabic*):}
 
@@
 
-\section{Indexing the logarithmic strata}
+\section{Description of the logarithmic strata}
 \noindent Let $\VZ = \VZ_{1,\alpha}(\PP^N|H,d)$ and let $\Acal$ denote the Artin fan of $\VZ$. Since the map of log stacks
@@
 
+\subsection{Global logarithmic strata}
+In the previous subsections we used tropical geometry to identify the logarithmic strata of $\VZ=\VZ_{1,\alpha}(\PP^N|H,d)$ local to the preimage of a point in $\Mcal$.
+In fact, the whole discussion carries over if we replace a point in $\Mcal$ by a locally closed logarithmic stratum.
+This fact will allow us to describe the logarithmic strata of $\VZ$ globally.
+
+As usual we start with $\Mcal$.
+The locally closed logarithmic strata of $\Mcal$ consist of loci where the combinatorial type of the associated tropical curve is constant.
+This is because the combinatorial type determines the minimal monoid $Q$, which coincides with the stalk of the ghost sheaf on $\Mcal$.
+
+Let us now pick such a stratum $\Scal \subseteq \Mcal$.
+In a sufficiently small open neighbourhood of $\Scal$, the combinatorial types of the associated tropical curves are obtained from the combinatorial type of $\Scal$ by contracting some edges (i.e.
+smoothing some nodes) and moving some of the vertices from the interior $\RR_{>0}$ of the tropicalisation of the target to the vertex $0 \in \RR_{\geq 0}$ (i.e.
+moving some components outside of $H$).
+In both cases, we see that the associated map on tropical moduli spaces is injective, and so the generisation map on the level of ghost sheaves is surjective.
+This allows us to produce a chart on the open neighbourhood of $\Scal$ with monoid given by $Q$.
+
+The previous discussion then applies to give a description of the logarithmic strata of $\VZ$ which intersect an open neighbourhood of the preimage of $\Scal$.
+Since logarithmic strata must map to logarithmic strata, this gives a procedure for enumerating all of the locally closed logarithmic strata of $\VZ$, namely:\medskip
+\begin{enumerate}[label=\textbf{Step \arabic*:},leftmargin=5\parindent]
+\item Enumerate the locally closed logarithmic strata of $\Mcal$ by enumerating all possible combinatorial types of tropical curves with the given numerical data.
+The dual intersection complex of these strata is specified by generisation of combinatorial types, as described earlier.\medskip
+\item For each locally closed stratum $\Scal\subseteq \Mcal$ identify the tropical moduli space $Q^\vee_{\RR}$ and perform the subdivision  specified by the alignment condition.
+The arguments of the previous subsections carry over \emph{mutatis mutandis} to give a description of the logarithmic strata of $\VZ$ which map to a neighbourhood of $\Scal$.
+The dual intersection complex of these strata is specified by the combinatorics of each subdivision together with the dual intersection complex of the strata of $\Mcal$.
+\end{enumerate}
+
+We now illustrate this is in some examples:
+\begin{example} Example of low-degree computation of logarithmic strata.
+(Note that for $\Mcal$ we can't read off the codimension from the dimension of the tropical moduli space because $\Mcal$ is not log smooth.)\footnote{(Navid) To be done.}\end{example}
+
 \newpage
@@
 
-\noindent In the previous section we used tropical geometry to identify the logarithmic strata of $\VZ=\VZ_{1,\alpha}(\PP^N|H,d)$.
+\noindent
+
 We now focus our attention on the logarithmic divisors, providing a recursive description for these loci: that is, a description in terms of fibre products of smaller moduli spaces.

### 2019-01-02 GenusOneRelativeMaps.tex
Wrote some more in Section 4. The amount of words is getting a bit mental, but with some massaging it will end up being more readable.

@@
 
-\noindent
+\noindent  In the previous section we explained how to determine the logarithmic strata of $\VZ$ along with their dual intersection complex.
+We now focus our attention on certain logarithmic divisors, providing a recursive description for these loci: that is, a description in terms of fibre products of smaller moduli spaces.
+This is the technically most difficult part of the paper.
+The recursive description bears some similarities with the recursive desription of the boundary of the absolute space $\VZ_{1,n}(\PP^N,d)$ given in \cite{VZ}; in keeping with the theme of this paper, however, we will see that log geometry provides a convenient framework for dealing with the combinatorics.
 
-We now focus our attention on the logarithmic divisors, providing a recursive description for these loci: that is, a description in terms of fibre products of smaller moduli spaces.
-This is the technically most difficult part of the paper.
-The recursive description bears some similarities with the recursive desription of the boundary of the absolute space $\VZ_{1,n}(\PP^N,d)$ given in \cite{VZ}; in keeping with the theme of this paper, however, we will see that the logarithmic structures provide a convenient framework for dealing with the combinatorics.
-
-The end result is that we obtain an explicit formula for tautological integrals over these boundary loci. This produces a Gathmann recursion formula for relative invariants in genus one.
+The end result is that we obtain an explicit formula for tautological integrals over these boundary loci. This produces a Gathmann recursion  for relative invariants in genus one.
 
@@
 and thus we obtain a section of the line bundle $x_k^*\omega_{\mathcal{C}/\VZ}^{\otimes\alpha_k}\otimes\ev_k^*\OO_{\PP^N}(H)$ with vanishing locus equal to the locus where $x_k$ belongs to an internal component.
-Writing this as
+Writing this locus as
 \begin{equation*} \Dcal^k = \Dcal_{1,\alpha}^k(\PP^N|H,d) \subseteq \VZ_{1,\alpha}(\PP^N|H,d) = \VZ \end{equation*}
@@
 We begin by noting that every irreducible component of $\Dcal^k$ is a codimension--$1$ logarithmic stratum.
-This is obvious: the locus where the log structure is trivial coincides precisely with the nice locus, where the source curve is smooth and not mapped inside $H$.
+This is not hard to see: the locus where the log structure is trivial coincides precisely with the nice locus, where the source curve is smooth and not mapped inside $H$.
 By definition $\Dcal^k$ is disjoint from this locus, and since it has codmension $1$ it must be equal to a union of logarithmic strata.
 
-As discussed at length in the previous section, the divisorial logarithmic strata of $\VZ$ correspond to the rays of the polyhedral subdivision of the tropical moduli space which produces the Artin fan $\Acal$.
-The logarithmic strata contained in $\Dcal^k$ correspond precisely to the rays of the tropical moduli space where the vertex of the tropicalisation containing $x_k$ is mapped into the interior of $\RR_{\geq 0}$ by the tropical map.
+In the previous section we discussed at length a procedure for determining all the logarithmic strata of $\VZ$.
+In particular, each divisorial logarithmic stratum is obtained by first choosing the combinatorial type of a tropical map, then subdividing its tropical moduli space, and finally choosing a ray in this subdivision.
+The logarithmic divisors which are contained in $\Dcal^k$ correspond precisely to the rays of the tropical moduli space where the vertex of the tropicalisation containing $x_k$ is mapped into the interior of $\RR_{\geq 0}$ by the tropical map.
 
-We proceed as in the previous section, fixing an element of $\Mcal$ and considering the resulting subdivision of the tropical moduli space.
-In fact, it makes sense to choose a locally closed substack of $\Mcal$ where the combinatorial type of the tropical curve (i.e.
-the ghost sheaf) is constant.
-Then as long as the minimal subcurve of genus one is not contracted, the picture is classical (i.e.
-the subdivision is trivial, and $\VZ=\Mcal$ locally).
-In this case there can only be one vertex of the tropical curve mapped into the interior of $\RR_{\geq 0}$; if there were more, the positions of their images in $\RR_{\geq 0}$ would be independent and thus the corresponding maximal cone in the tropical moduli space would be at least $2$~dimensional, producing a locus in $\VZ$ of larger codimension.\footnote{(Luca) Say something about rigid tropical curves as in ACGS and KLR} We adopt the terminology of Vakil, distinguishing three cases as below:
+Let us therefore choose a combinatorial type of a tropical map, corresponding to a logarithmic stratum $\Scal$.
+As long as the minimal subcurve of genus one has positive degree, the subdivision is trivial since there is no alignment necessary.
+In this case choose a ray of the tropical moduli space $\Q^\vee_{\RR}$.
+This corresponds to choosing a logarithmic divisor $\Dcal$ in $\Mcal$ containing our original logarithmic stratum $\Scal$ -- the corresponding divisor in $\VZ$ will then be the proper transform of $\Dcal$.
+In order to have $\Dcal \subseteq \Dcal^k$ we need that the vertex of the tropicalisation containing $x_k$ is mapped into the interior of $\RR_{\geq 0}$ by the tropical map.
+We claim that this can be the only vertex of the tropical curve mapped into the interior of $\RR_{\geq 0}$; if there were more, the positions of their images in $\RR_{\geq 0}$ would be independent and thus the corresponding maximal cone in the tropical moduli space would be at least $2$~dimensional, which is a contradiction since we assumed we had chosen a ray.\footnote{(Luca) Say something about rigid tropical curves as in ACGS and KLR} There are three cases to distinguish, depending on the position of the circuit.
+Adopting the terminology of Vakil, we write these as:
 
@@
 \end{figure}
-\noindent Notice that the continuity of the tropical map identifies all of the edge lengths, up to weights given by the expansion factors (i.e.
-tangency orders) at the edges; thus the tropical moduli space is isomorphic to $\RR_{\geq 0}$ and so we have a divisor (with no subdivision required).
+\noindent (These are just cartoon pictures: we have omitted the marked points and the expansion factors.) Notice that the continuity of the tropical map identifies all of the edge lengths, up to weights given by the expansion factors (i.e.
+tangency orders) at the edges; thus the tropical moduli space is isomorphic to $\RR_{\geq 0}$ and so we have a divisor as expected.
 
-These divisors live inside an open neighbourhood of the preimage in $\VZ$ of our chosen locus in $\Mcal$, and are thus locally closed substacks of $\VZ$.
-To obtain the desired components of $\Dcal^k$, we must take the closure of these locally closed substacks.
-We will analyse this procedure on a case-by-case basis, and see once again that the tropical picture gives a complete and recursive description of the combinatorics.
-As usual, this will be done by comparing loci in$\VZ$ with loci in $\Mcal$.
-To be more precise: we will take the closure of our locally closed substack in $\Mcal$ and relate it to the closure of our locally closed substack in $\VZ$.
-We will see that the induced map on closures is another blow-up.
-The closed locus in $\Mcal$ is understood by \cite{PuncturedMaps} as a fibre product of moduli spaces of punctured maps.
-\footnote{(Navid) Introduce notation for these locally closed substacks, because this shit is getting out of hand.}
+Let $\Dcal_{\Mcal}^\circ\subseteq \Mcal$ denote the locally closed stratum corresponding to one of these combinatorial types.
+The corresponding divisor in $\Mcal$ is $\Dcal_\Mcal = \overline{\Dcal^\circ}$.
+On the other hand, the corresponding divisor $\Dcal$ in $\VZ$ is the proper transform of $\Dcal_\Mcal$, which is obtained by taking the preimage $\Dcal^\circ$ of $\Dcal_\Mcal^\circ$ (since $\Dcal^\circ$ is disjoint from the blown-up locus) and then taking its closure in $\VZ$.
+This is different from taking the preimage of $\Dcal_\Mcal$ (the total transform), since in general $\Dcal_\Mcal$ will intersect the blown-up locus.
+We have an induced map
+\begin{equation*} \Dcal \to \Dcal_\Mcal \end{equation*}
+which we will see can also be interpreted as a blow-up.
+This is useful, because $\Dcal_\Mcal$ has a recursive description in terms of moduli spaces of punctured maps \cite{PuncturedMaps}, which in this case we are able to integrate over.
 

### 2019-01-02 GenusOneRelativeMaps.tex
Some cleaning up of section 3.3

@@
 We call this \emph{the tropical moduli space}; contained in the tropical moduli space are the edge lengths of the associated tropical curve (corresponding to the smoothing parameters of the nodes of the logarithmic curve).
-Since the alignment condition amounts to imposing a partial ordering amongst certain sums of these edge lengths, it produces a polyhedral decomposition of the tropical moduli space into chambers where different partial order relations hold.
+Since the alignment condition amounts to imposing a partial ordering amongst certain sums of these edge lengths, it produces a polyhedral decomposition of the tropical moduli space, into chambers where different partial order relations hold.
 If we only consider the integral points, this produces a polyhedral decomposition of the cone $Q^\vee = \Hom(Q,\N)$.
@@
 In the previous subsections we used tropical geometry to identify the logarithmic strata of $\VZ=\VZ_{1,\alpha}(\PP^N|H,d)$ local to the preimage of a point in $\Mcal$.
-In fact, the whole discussion carries over if we replace a point in $\Mcal$ by a locally closed logarithmic stratum.
+In fact, the whole discussion carries over if we replace a point in $\Mcal$ by a locally closed logarithmic stratum: the key observation is simply that the tropical moduli space does not vary if we move inside a locally closed logarithmic stratum, so the subdivision process makes sense over that whole stratum.
 This fact will allow us to describe the logarithmic strata of $\VZ$ globally.
 
-As usual we start with $\Mcal$.
-The locally closed logarithmic strata of $\Mcal$ consist of loci where the combinatorial type of the associated tropical curve is constant.
+\subsubsection{Logarithmic strata of $\Mcal$} The locally closed logarithmic strata of $\Mcal$ consist of loci where the combinatorial type of the associated tropical curve is constant\footnote{(Navid) Reference for this?}.
 This is because the combinatorial type determines the minimal monoid $Q$, which coincides with the stalk of the ghost sheaf on $\Mcal$.
 
-Let us now pick such a stratum $\Scal \subseteq \Mcal$.
-In a sufficiently small open neighbourhood of $\Scal$, the combinatorial types of the associated tropical curves are obtained from the combinatorial type of $\Scal$ by contracting some edges (i.e.
-smoothing some nodes) and moving some of the vertices from the interior $\RR_{>0}$ of the tropicalisation of the target to the vertex $0 \in \RR_{\geq 0}$ (i.e.
-moving some components outside of $H$).
-In both cases, we see that the associated map on tropical moduli spaces is injective, and so the generisation map on the level of ghost sheaves is surjective.
+If we have two strata $\Scal_1$ and $\Scal_2$ corresponding to combinatorial types $\Gamma_1$ and $\Gamma_2$, then $\Scal_2$ is contained in the closure of $\Scal_1$ if and only if the combinatorial type $\Gamma_1$ is obtained from $\Gamma_2$ by a process of generisation: namely, by contracting some edges (i.e.
+smoothing some nodes) and moving some of the vertices from the interior $\RR_{>0} \subseteq \RR_{\geq 0}$ of the tropicalisation $\Sigma(\PP^N|H)$ to the vertex $0 \in \RR_{\geq 0}$ (i.e.
+moving some components of the curve outside $H$).
+This allows us to completely describe the dual intersection complex of the logarithmic strata of $\Mcal$.
+
+Note that we are \emph{not} able to easily read off the codimension of a logarithmic stratum from the combinatorial data: the codimension of the associated stratum in the Artin fan $\Acal_\Mcal$ is given by the dimension of the tropical moduli space, but the map $\Mcal\to\Acal_\Mcal$ is not smooth (since $\Mcal$ is not log smooth) so we are not able to say anything about the locus in $\Mcal$.
+
+\subsubsection{Logarithmic strata of $\VZ$}
+Now let us pick a stratum $\Scal \subseteq \Mcal$ indexed by a combinatorial type $\Gamma$ and with associated monoid $Q$.
+We may choose a sufficiently small open neighbourhood of $\Scal$ which only intersects logarithmic strata $\Scal^\prime$ which contain $\Scal$ in their closures.
+The previous discussion then shows that if we pick any point in this open neighbourhood, the combinatorial type of the associated tropical curve is obtained from $\Gamma$ by contracting some edges and specialising some vertices.
+Thus we see that the associated map on tropical moduli spaces is injective, and so the generisation map on the level of ghost sheaves is surjective.
 This allows us to produce a chart on the open neighbourhood of $\Scal$ with monoid given by $Q$.
 
-The previous discussion then applies to give a description of the logarithmic strata of $\VZ$ which intersect an open neighbourhood of the preimage of $\Scal$.
-Since logarithmic strata must map to logarithmic strata, this gives a procedure for enumerating all of the locally closed logarithmic strata of $\VZ$, namely:\medskip
+The discussion in the previous subsections then applies \emph{mutatis mutandis} to this open set, giving a description of the logarithmic strata of $\VZ$ which intersect an open neighbourhood of the preimage of $\Scal$.
+Since log strata must map to log strata, this gives a procedure for enumerating all of the locally closed logarithmic strata of $\VZ$, namely:\medskip
 \begin{enumerate}[label=\textbf{Step \arabic*:},leftmargin=5\parindent]
@@
 The dual intersection complex of these strata is specified by generisation of combinatorial types, as described earlier.\medskip
-\item For each locally closed stratum $\Scal\subseteq \Mcal$ identify the tropical moduli space $Q^\vee_{\RR}$ and perform the subdivision  specified by the alignment condition.
-The arguments of the previous subsections carry over \emph{mutatis mutandis} to give a description of the logarithmic strata of $\VZ$ which map to a neighbourhood of $\Scal$.
+\item For each locally closed stratum $\Scal\subseteq \Mcal$ identify the tropical moduli space $Q^\vee_{\RR}$ associated to the given combinatorial type, and perform the subdivision specified by the alignment condition.
+The arguments of the previous subsections carry over to give a description of the logarithmic strata of $\VZ$ which map to a neighbourhood of $\Scal$.
 The dual intersection complex of these strata is specified by the combinatorics of each subdivision together with the dual intersection complex of the strata of $\Mcal$.

### 2019-01-02 GenusOneRelativeMaps.tex
Reorganised Section 4 again - getting closer

@@
 \newcommand{\mathsq}[1]{#1}
+
+\newcommand{\sqC}{\scalebox{0.8}[1.3]{$\sqsubset$}}
+
 \newcommand{\pM}{\pazocal{M}}
@@
 \newcommand{\M}[4]{\overline{\mathcal{M}}_{#1,#2}(#3,#4)}
+
+\newcommand{\Mlog}[4]{\overline{\mathcal{M}}^{\operatorname{log}}_{#1,#2}(#3,#4)}
+\newcommand{\Mpunct}[4]{\overline{\mathcal{M}}^{\operatorname{punct}}_{#1,#2}(#3,#4)}
 \newcommand{\MG}[4]{\overline{\mathcal{M}}^{\rm G}_{#1,#2}(#3,#4)}
@@
 \draw [fill] (0,3) circle[radius=2pt];
-\draw (0,3) node[left]{$\mathsq{C}_1$};
+\draw (0,3) node[left]{$\sqC_1$};
 \draw (0,3) -- (2,2);
@@
 \draw [fill] (0,1) circle[radius=2pt];
-\draw (0,1) node[left]{$\mathsq{C}_2$};
+\draw (0,1) node[left]{$\sqC_2$};
 \draw (0,1) -- (2,2);
@@
 \draw [fill=white] (2,2) circle[radius=2pt];
-\draw (2,2) node[above]{$\mathsq{C}_0$};
+\draw (2,2) node[above]{$\sqC_0$};
 
@@
 subject to the continuity condition $e_1=2e_2$. So the tropical moduli space is simply $\RR_{\geq 0}$ generated by $e_2$. Note that for any $e_2 > 0$ (i.e. on the interior of the cone) we have:
-\begin{equation*} \lambda(\mathsq{C}_2) = e_2 = e_1/2 < e_1 = \lambda(\mathsq{C}_1). \end{equation*}
+\begin{equation*} \lambda(\sqC_2) = e_2 = e_1/2 < e_1 = \lambda(\sqC_1). \end{equation*}
 Thus, any logarithmic map with combinatorial type given by the above picture is automatically aligned.
@@
 \draw [fill] (0,4) circle[radius=2pt];
-\draw (0,4) node[left]{$\mathsq{C}_1$};
+\draw (0,4) node[left]{$\sqC_1$};
 \draw (0,4) -- (2,3);
@@
 \draw (2.075,2.5) node[left,red]{$0$};
-\draw (2,2) node[below]{$\mathsq{C}_3$};
+\draw (2,2) node[below]{$\sqC_3$};
 
@@
 \draw [fill=white] (2,3) circle[radius=2pt];
-\draw (2,3) node[above]{$\mathsq{C}_0$};
+\draw (2,3) node[above]{$\sqC_0$};
 
@@
 Thus the moduli space is isomorphic to $\RR_{\geq 0}^2$ generated by $e_2$ and $e_3$.
-In order to have an alignment, at least one of $\lambda(\mathsq{C}_1)$ and $\lambda(\mathsq{C}_2)$ must be equal to the radius $\delta$.
+In order to have an alignment, at least one of $\lambda(\sqC_1)$ and $\lambda(\sqC_2)$ must be equal to the radius $\delta$.
 Note that
-\begin{align*} \lambda(\mathsq{C}_1) & = e_1 = 2e_2 \\
-\lambda(\mathsq{C}_2) & = e_2 + e_3\end{align*}
+\begin{align*} \lambda(\sqC_1) & = e_1 = 2e_2 \\
+\lambda(\sqC_2) & = e_2 + e_3\end{align*}
 and without more information we cannot say which of these is larger.
-The subdivision of $(\RR_{\geq 0})^2$ is obtained by dividing the cone into regions where different order relations hold amongst the distances $\lambda(\mathsq{C}_1),\lambda(\mathsq{C}_2),\lambda(\mathsq{C}_3)$.
+The subdivision of $(\RR_{\geq 0})^2$ is obtained by dividing the cone into regions where different order relations hold amongst the distances $\lambda(\sqC_1),\lambda(\sqC_2),\lambda(\sqC_3)$.
 The walls of this subdivison correspond to where some of these distances are equal.
-Note that in this setting we always have $\lambda(\mathsq{C}_2) > \lambda(\mathsq{C}_3)$ (at least, as long as we remain in the interior of the cone).
+Note that in this setting we always have $\lambda(\sqC_2) > \lambda(\sqC_3)$ (at least, as long as we remain in the interior of the cone).
 The remaining possibilities are:
-\begin{align*} \lambda(\mathsq{C}_1) & = \lambda(\mathsq{C}_3) \qquad (\Leftrightarrow e_1 = e_3 \Leftrightarrow 2e_2 = e_3) \\
-\lambda(\mathsq{C}_1) & = \lambda(\mathsq{C}_2) \qquad (\Leftrightarrow e_1 = e_2 + e_3 \Leftrightarrow e_2 = e_3). \end{align*}
+\begin{align*} \lambda(\sqC_1) & = \lambda(\sqC_3) \qquad (\Leftrightarrow e_1 = e_3 \Leftrightarrow 2e_2 = e_3) \\
+\lambda(\sqC_1) & = \lambda(\sqC_2) \qquad (\Leftrightarrow e_1 = e_2 + e_3 \Leftrightarrow e_2 = e_3). \end{align*}
 Thus, the subdivision of the tropical moduli space $(\RR_{\geq 0}^2)_{e_2 e_3}$ is given by:
@@
 \draw (-3,0) -- (-1,4);
-\draw (-1,4) node[above,red]{$\lambda(\mathsq{C}_1)=\lambda(\mathsq{C}_3)$};
+\draw (-1,4) node[above,red]{$\lambda(\sqC_1)=\lambda(\sqC_3)$};
 
@@
 \draw (-3,0) -- (1,4);
-\draw (1,4) node[above,red]{$\lambda(\mathsq{C}_1)=\lambda(\mathsq{C}_2)$};
+\draw (1,4) node[above,red]{$\lambda(\sqC_1)=\lambda(\sqC_2)$};
 
-\draw (0,1.5) node[below,red]{$\lambda(\mathsq{C}_1) > \lambda(\mathsq{C}_2)$};
+\draw (0,1.5) node[below,red]{$\lambda(\sqC_1) > \lambda(\sqC_2)$};
 
-\draw (-0.6,3.4) node[below,red]{$\lambda(\mathsq{C}_3) < \lambda(\mathsq{C}_1)$};
-\draw (-0.6,3.1) node[below,red]{$< \lambda(\mathsq{C}_2)$};
+\draw (-0.6,3.4) node[below,red]{$\lambda(\sqC_3) < \lambda(\sqC_1)$};
+\draw (-0.6,3.1) node[below,red]{$< \lambda(\sqC_2)$};
 
-\draw (-2.2,3.4) node[below,red]{$\lambda(\mathsq{C}_1) < \lambda(\mathsq{C}_3)$};
+\draw (-2.2,3.4) node[below,red]{$\lambda(\sqC_1) < \lambda(\sqC_3)$};
 \end{tikzpicture}
@@
 
-\subsection{Recursive description of the divisors: types $A,B$ and $C^+$}
-We begin by noting that every irreducible component of $\Dcal^k$ is a codimension--$1$ logarithmic stratum.
-This is not hard to see: the locus where the log structure is trivial coincides precisely with the nice locus, where the source curve is smooth and not mapped inside $H$.
-By definition $\Dcal^k$ is disjoint from this locus, and since it has codmension $1$ it must be equal to a union of logarithmic strata.
+\subsection{Identifying the components of $\Dcal^k$}
 
-In the previous section we discussed at length a procedure for determining all the logarithmic strata of $\VZ$.
+\subsubsection{Components of $\Dcal^k$ are log strata} We begin by noting that every irreducible component of $\Dcal^k$ is a codimension--$1$ logarithmic stratum.
+This is not hard to see: the locus where the log structure is trivial coincides precisely with the  locus where the source curve is smooth and not mapped inside $H$.
+Moreover since $\VZ$ is log smooth this locus is open and dense.
+By definition $\Dcal^k$ is disjoint from this locus, hence is contained in the closed complement.
+Since it has codmension $1$, it must thus be equal to a union of logarithmic strata.
+
+\subsubsection{Describing logarithmic divisors} In the previous section we discussed at length a procedure for determining all the logarithmic strata of $\VZ$.
 In particular, each divisorial logarithmic stratum is obtained by first choosing the combinatorial type of a tropical map, then subdividing its tropical moduli space, and finally choosing a ray in this subdivision.
@@
 
+\subsection{Recursive description of the divisors: types $A,B$ and $C^+$}
 Let us therefore choose a combinatorial type of a tropical map, corresponding to a logarithmic stratum $\Scal$.
-As long as the minimal subcurve of genus one has positive degree, the subdivision is trivial since there is no alignment necessary.
-In this case choose a ray of the tropical moduli space $\Q^\vee_{\RR}$.
-This corresponds to choosing a logarithmic divisor $\Dcal$ in $\Mcal$ containing our original logarithmic stratum $\Scal$ -- the corresponding divisor in $\VZ$ will then be the proper transform of $\Dcal$.
-In order to have $\Dcal \subseteq \Dcal^k$ we need that the vertex of the tropicalisation containing $x_k$ is mapped into the interior of $\RR_{\geq 0}$ by the tropical map.
-We claim that this can be the only vertex of the tropical curve mapped into the interior of $\RR_{\geq 0}$; if there were more, the positions of their images in $\RR_{\geq 0}$ would be independent and thus the corresponding maximal cone in the tropical moduli space would be at least $2$~dimensional, which is a contradiction since we assumed we had chosen a ray.\footnote{(Luca) Say something about rigid tropical curves as in ACGS and KLR} There are three cases to distinguish, depending on the position of the circuit.
-Adopting the terminology of Vakil, we write these as:
+In this section we will restrict ourselves to the situation where the minimal subcurve of genus one has positive degree (the other, more complicated, case will be taken up in the next section).
+
+In this situation, the subdivision is trivial since no alignment is necessary (both radii are zero).
+Following our procedure, we choose a ray of the tropical moduli space $Q^\vee_{\RR}$.
+This determines a generisation of our original combinatorial type, by setting certain edge lengths to zero.
+Replace the original combinatorial type with this generisation.
+In order to have $\Dcal \subseteq \Dcal^k$ we need that the vertex of the tropicalisation which contains the flag $x_k$ is mapped into the interior of $\RR_{\geq 0}$ by the tropical map.
+
+We claim that this can be the only vertex of the tropical curve mapped into the interior of $\RR_{\geq 0}$; if there were more, the positions of their images in $\RR_{\geq 0}$ would be independent and thus the corresponding maximal cone in the tropical moduli space would be at least $2$~dimensional, which is a contradiction since we assumed we had chosen a ray.\footnote{(Luca) Say something about rigid tropical curves as in ACGS and KLR} There are now three cases to distinguish, depending on the position of the circuit.
+These are illustrated in the figures below.
 
@@
 \end{figure}
-\noindent (These are just cartoon pictures: we have omitted the marked points and the expansion factors.) Notice that the continuity of the tropical map identifies all of the edge lengths, up to weights given by the expansion factors (i.e.
+Note that these are just cartoon pictures: we have omitted the marked points and the expansion factors.
+The continuity of the tropical map identifies all of the edge lengths, up to weights given by the expansion factors (i.e.
 tangency orders) at the edges; thus the tropical moduli space is isomorphic to $\RR_{\geq 0}$ and so we have a divisor as expected.
 
-Let $\Dcal_{\Mcal}^\circ\subseteq \Mcal$ denote the locally closed stratum corresponding to one of these combinatorial types.
+\subsubsection{Recursive description of the divisor}
+Let $\Dcal_{\Mcal}^\circ\subseteq \Mcal$ denote the (codimension-$1$) locally closed stratum corresponding to our combinatorial type.
 The corresponding divisor in $\Mcal$ is $\Dcal_\Mcal = \overline{\Dcal^\circ}$.
@@
 This is different from taking the preimage of $\Dcal_\Mcal$ (the total transform), since in general $\Dcal_\Mcal$ will intersect the blown-up locus.
-We have an induced map
-\begin{equation*} \Dcal \to \Dcal_\Mcal \end{equation*}
-which we will see can also be interpreted as a blow-up.
-This is useful, because $\Dcal_\Mcal$ has a recursive description in terms of moduli spaces of punctured maps \cite{PuncturedMaps}, which in this case we are able to integrate over.
+By continuity have an induced map:
+\begin{equation*} \Dcal \to \Dcal_\Mcal. \end{equation*}
+The remainder of this subsection will be dedicated to showing how the map $\Dcal \to \Dcal_\Mcal$ may be interpreted as a blow-up.
+This is an extremely useful fact, because $\Dcal_\Mcal$ has a recursive description in terms of moduli spaces of punctured maps \cite{PuncturedMaps}, which in our setting we are able to compute integrals over.
+We will consider the cases $A,B$ and $C^+$ separately in the next three subsections.
 
-\subsubsection{Type A} By definition the locus $\Ycal_A$ contains those elements of $\VZ$ which appear in the closure of the locus of aligned maps whose associated tropical curve has the same combinatorial type as Figure 1\footnote{(Navid) Bad LaTeX reference}.
-We will now argue that such an element restricts to give an aligned map on the piece of the curve corresponding to $\mathsq{C}_1$, and that conversely given an aligned map corresponding to $\mathsq{C}_1$ and ordinary punctured maps corresponding to $\mathsq{C}_0,\mathsq{C}_2,\ldots,\mathsq{C}_r$, the glued map is aligned.
-This shows that $\Ycal_A$ is equal, up to an \'etale quotient, to the fibre product:
-\begin{equation*}\M{0}{\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}{\PP^N|H}{d_0}\times_{H^r}\left(\VZ_{1,\alpha^{(1)}\cup(m_1)}(\PP^N|H,d_1)\times\prod_{i=2}^r\M{0}{\alpha^{(i)}\cup(m_i)}{\PP^N|H}{d_i}\right).
+\subsubsection{Type A} Choose an element of $\Dcal=\overline{\Dcal^\circ}$ where $\Dcal^\circ \subseteq \VZ$ is the locus of maps with combinatorial type equal to $\Gamma$, which itself is of type A.
+We will now argue that such an element restricts to give an aligned map on the piece of the curve corresponding to $\sqC_1$, and that conversely given an aligned map corresponding to $\sqC_1$ and ordinary punctured and logarithmic maps corresponding to $\sqC_0,\sqC_2,\ldots,\sqC_r$, the glued map is aligned.
+This shows that $\Dcal$ is equal, up to an \'etale quotient, to the fibre product:
+\begin{equation*}\Mpunct{0}{\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}{\PP^N|H}{d_0}\times_{H^r}\left(\VZ_{1,\alpha^{(1)}\cup(m_1)}(\PP^N|H,d_1)\times\prod_{i=2}^r\Mlog{0}{\alpha^{(i)}\cup(m_i)}{\PP^N|H}{d_i}\right).
 \end{equation*}
 Put differently, the map from the closed locus in $\VZ$ to the closed locus in $\Mcal$ is given by blowing up one of the factors of the fibre product
-\begin{equation*}\M{0}{\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}{\PP^N|H}{d_0}\times_{H^r}\prod_{i=1}^r\M{0}{\alpha^{(i)}\cup(m_i)}{\PP^N|H}{d_i}. \end{equation*}
-and leaving the rest alone.
+\begin{equation*}\Mpunct{0}{\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}{\PP^N|H}{d_0}\times_{H^r}\prod_{i=1}^r\Mlog{0}{\alpha^{(i)}\cup(m_i)}{\PP^N|H}{d_i}. \end{equation*}
+and leaving the rest alone. Note that only the moduli space corresponding to $\sqC_0$ is a moduli space of punctured maps: the rest are usual moduli spaces of log stable maps.
 

### 2019-01-02 GenusOneRelativeMaps.tex
Restructured section 4 again

@@
 \documentclass[11pt]{amsart}
+\linespread{1.25}
+\usepackage[margin=3cm]{geometry}
 
@@
 \draw (2,0) circle(2pt)[fill=black];
+\draw [->] (2,0) -- (2.7,0);
+\draw (2.6,0) node[right]{\tiny{$x_k$}};
 \draw (0,1) circle(2pt)[fill=white];
@@
 \draw [->,red,thick] (0,-2) -- (2,-2);
-\draw (2,-2) node[right,red]{\tiny{$\Sigma(\PP^N)$}};
+\draw (2,-2) node[right,red]{\tiny{$\Sigma(\PP^N|H)$}};
 \draw [->,red] (1,-0.9) -- (1,-1.6);
@@
 \draw (2,0) circle(2pt)[fill=black];
+\draw [->] (2,0) -- (2.7,0);
+\draw (2.6,0) node[right]{\tiny{$x_k$}};
 \draw (0,1) circle(2pt)[fill=black];
@@
 \draw (2,0) circle(2pt)[fill=white];
+\draw [->] (2,0) -- (2.7,0);
+\draw (2.6,0) node[right]{\tiny{$x_k$}};
 \draw (0,1) circle(2pt)[fill=black];
@@
 Since log strata must map to log strata, this gives a procedure for enumerating all of the locally closed logarithmic strata of $\VZ$, namely:\medskip
-\begin{enumerate}[label=\textbf{Step \arabic*:},leftmargin=5\parindent]
+\begin{enumerate}
 \item Enumerate the locally closed logarithmic strata of $\Mcal$ by enumerating all possible combinatorial types of tropical curves with the given numerical data.
@@
 \end{enumerate}
-
 We now illustrate this is in some examples:
@@
 
-\noindent  In the previous section we explained how to determine the logarithmic strata of $\VZ$ along with their dual intersection complex.
+\noindent  In the previous section we explained how to determine the logarithmic strata of $\VZ$.
 We now focus our attention on certain logarithmic divisors, providing a recursive description for these loci: that is, a description in terms of fibre products of smaller moduli spaces.
@@
 The end result is that we obtain an explicit formula for tautological integrals over these boundary loci. This produces a Gathmann recursion  for relative invariants in genus one.
+
+The plan for this section is as follows \footnote{(Navid) Finish this}
 
@@
 Writing this locus as
-\begin{equation*} \Dcal^k = \Dcal_{1,\alpha}^k(\PP^N|H,d) \subseteq \VZ_{1,\alpha}(\PP^N|H,d) = \VZ \end{equation*}
+\begin{equation*} \Dcal(k) = \Dcal_{1,\alpha}^k(\PP^N|H,d) \subseteq \VZ_{1,\alpha}(\PP^N|H,d) = \VZ \end{equation*}
 we obtain:
-\begin{lem} $(\alpha_k\psi_k+\ev_k^*H)\cap[\VZ]=[\Dcal^k].\footnote{(Navid) Should we work out the vanishing orders of the section at this point?}$\end{lem}
-\noindent The remainder of this section will be devoted to providing an explicit recursive description of $[\Dcal^k]$ in terms of tautological classes on spaces of maps with smaller numerical invariants.
+\begin{lem} $(\alpha_k\psi_k+\ev_k^*H)\cap[\VZ]=[\Dcal(k)].\footnote{(Navid) Should we work out the vanishing orders of the section at this point?}$\end{lem}
+\noindent The remainder of this section will be devoted to providing an explicit recursive description of the class $[\Dcal(k)]$ in terms of tautological classes on spaces of maps with smaller numerical invariants.
 As we will see, this provides an algorithm for computing reduced relative invariants, as well as a quantum Lefschetz algorithm for reduced (absolute) invariants in genus one.
 
-\subsection{Identifying the components of $\Dcal^k$}
+\subsection{Identifying the irreducible components of $\Dcal(k)$} Here we explain the strategy for identifying the irreducible components of $\Dcal(k)$ via tropical geometry.
 
-\subsubsection{Components of $\Dcal^k$ are log strata} We begin by noting that every irreducible component of $\Dcal^k$ is a codimension--$1$ logarithmic stratum.
-This is not hard to see: the locus where the log structure is trivial coincides precisely with the  locus where the source curve is smooth and not mapped inside $H$.
-Moreover since $\VZ$ is log smooth this locus is open and dense.
-By definition $\Dcal^k$ is disjoint from this locus, hence is contained in the closed complement.
-Since it has codmension $1$, it must thus be equal to a union of logarithmic strata.
+\begin{lemma} Every irreducible component of $\Dcal(k)$ is a codimension-$1$ logarithmic stratum.\end{lemma}
+\begin{proof} This is not hard to see: the locus where the log structure is trivial coincides precisely with the  locus where the source curve is smooth and not mapped inside $H$, and since $\VZ$ is log smooth this locus is open and dense.
+By definition $\Dcal(k)$ is disjoint from this locus, hence is contained in the  complement of this locus, which (by the very definition of logarithmic strata) can be written as a union of logarithmic strata of positive codimension.
+Since $\Dcal(k)$ has codmension $1$, it must therefore be equal to a union of logarithmic divisors.\end{proof}
 
-\subsubsection{Describing logarithmic divisors} In the previous section we discussed at length a procedure for determining all the logarithmic strata of $\VZ$.
-In particular, each divisorial logarithmic stratum is obtained by first choosing the combinatorial type of a tropical map, then subdividing its tropical moduli space, and finally choosing a ray in this subdivision.
-The logarithmic divisors which are contained in $\Dcal^k$ correspond precisely to the rays of the tropical moduli space where the vertex of the tropicalisation containing $x_k$ is mapped into the interior of $\RR_{\geq 0}$ by the tropical map.
+In the previous section we discussed at length a procedure for describing the logarithmic strata of $\VZ$. This shows that every divisorial logarithmic stratum is obtained via a three-step process:
+\begin{enumerate}
+\item choose the combinatorial type of a tropical map;
+\item subdivide the corresponding tropical moduli space;
+\item choose a ray in this subdivision.
+\end{enumerate}
+Notice that this process contains some redundancies: once we choose a ray of the tropical moduli space, we obtain a generisation of the intial combinatorial type, given by contracting some edges of the dual graph.
+
+\begin{example} \end{example}
+
+Whenever we consider a logarithmic stratum in $\VZ$, by its combinatorial type we will always mean the generisation of the ``original'' combinatorial type induced by our choice of cone in the polyhedral subdivision.
+This does not depend on the choice of original combinatorial type.
+
+Now, the logarithmic divisors which are contained in $\Dcal(k)$ are precisely those whose corresponding combinatorial type has the vertex of the dual graph containing $x_k$ mapped into the interior of $\RR_{\geq 0}$.
+
+Thus, via the above procedure, we are able to enumerate the irreducible components of $\Dcal(k)$ in a combinatorial manner.
+The combinatorial type and choice of ray allows us to describe the general element of such a component.
+What we are still lacking is a recursive description of the components which will allow us to compute integrals over them.
+This is the subject of the remainder of this section.
 
 \subsection{Recursive description of the divisors: types $A,B$ and $C^+$}
-Let us therefore choose a combinatorial type of a tropical map, corresponding to a logarithmic stratum $\Scal$.
-In this section we will restrict ourselves to the situation where the minimal subcurve of genus one has positive degree (the other, more complicated, case will be taken up in the next section).
 
-In this situation, the subdivision is trivial since no alignment is necessary (both radii are zero).
-Following our procedure, we choose a ray of the tropical moduli space $Q^\vee_{\RR}$.
-This determines a generisation of our original combinatorial type, by setting certain edge lengths to zero.
-Replace the original combinatorial type with this generisation.
-In order to have $\Dcal \subseteq \Dcal^k$ we need that the vertex of the tropicalisation which contains the flag $x_k$ is mapped into the interior of $\RR_{\geq 0}$ by the tropical map.
+The basic idea is as follows.
+Choose an irreducible component $\Dcal \subseteq \Dcal(k)$.
+As discussed above, we can obtain this by choosing an ``initial'' combinatorial type together with a ray of the resulting subdivision of the tropical moduli space.
+Without loss of generality we may assume that this ``initial'' combinatorial type coincides with the ``true'' combinatorial type of $\Dcal$ obtained by performing the edge contractions specified by the choice of ray.
 
-We claim that this can be the only vertex of the tropical curve mapped into the interior of $\RR_{\geq 0}$; if there were more, the positions of their images in $\RR_{\geq 0}$ would be independent and thus the corresponding maximal cone in the tropical moduli space would be at least $2$~dimensional, which is a contradiction since we assumed we had chosen a ray.\footnote{(Luca) Say something about rigid tropical curves as in ACGS and KLR} There are now three cases to distinguish, depending on the position of the circuit.
-These are illustrated in the figures below.
+Now, let $\Dcal_{\Mcal}^\circ\subseteq \Mcal$ denote the (codimension-$1$) locally closed stratum corresponding to our choice of combinatorial type, and let $\Dcal_\Mcal = \overline{\Dcal^\circ}$ be the corresponding logarithmic stratum in $\Mcal$.
+Our divisor $\Dcal\subseteq\VZ$ is the proper transform of $\Dcal_\Mcal$, which is obtained by taking the preimage $\Dcal^\circ$ of $\Dcal_\Mcal^\circ$ (since $\Dcal^\circ$ is disjoint from the blown-up locus) and then taking its closure in $\VZ$.
+This is, of course, different from taking the preimage of $\Dcal_\Mcal$, since in general $\Dcal_\Mcal$ will intersect the blown-up locus.
+By continuity we have an induced map:
+\begin{equation*} \Dcal \to \Dcal_\Mcal. \end{equation*}
+The remainder of this section will be dedicated to showing how the map $\Dcal \to \Dcal_\Mcal$ may be interpreted as a blow-up.
+The reason this is useful is that $\Dcal_\Mcal$ itself has a recursive description, in terms of moduli spaces of punctured maps \cite{PuncturedMaps}, which in our setting we are able to compute integrals over.
 
+For the remainder of this subsection, we will consider only the situation where the circuit has positive degree; the other, more complicated case, will be taken up in \S \ref{}.
+
+\begin{lemma} Let $\Dcal \subseteq \Dcal(k)$ be an irreducible component and let $\Delta$ be the corresponding combinatorial type.
+Suppose that $\Delta$ assigns circuit has positive degree to the circuit.
+Then $\Delta$ takes one of the following forms:
 \begin{figure}[h]
@@
 \end{figure}
-Note that these are just cartoon pictures: we have omitted the marked points and the expansion factors.
-The continuity of the tropical map identifies all of the edge lengths, up to weights given by the expansion factors (i.e.
+
+\noindent The terminology is due to Vakil, and the picture in this case is very similar to \cite{Vre} (as we will see later, when the circuit is contracted the picture becomes very different).
+Note that in these pictures we have omitted the marked points, the degree of each vertex, and the expansion factors.
+These combinatorial data can be distributed arbitrarily, as long as:
+\begin{enumerate}
+\item every vertex has positive degree;
+\item the balancing condition is satisfied.
+\end{enumerate}
+Note that since every vertex has positive degree, there is no need to impose stability.\end{lemma}
+
+\begin{proof}
+Recall that we have $\Dcal\subseteq\VZ$ obtained by a choice of combinatorial type and ray in the subdivison of the tropical moduli space.
+In this situation, the subdivision is trivial since no alignment is necessary (both radii are zero).
+Following our procedure, we choose a ray of the tropical moduli space $Q^\vee_{\RR}$.
+Since this is generated by edge lengths, and we are assuming that the initial and generised combinatorial types coincide, we conclude that the tropical moduli space must be $\RR_{\geq 0}$.
+Since we are assuming that $\Dcal \subseteq \Dcal(k)$, we know that the vertex of the tropicalisation which contains the flag $x_k$ must map into the interior $\RR_{>0}\subseteq \RR_{\geq 0}$.
+
+We claim that this is the only vertex of the tropical curve mapped into the interior; if there were more, the positions of their images in $\RR_{\geq 0}$ would be independent, and thus the tropical moduli space would have dimension $\geq 2$, a contradiction.\footnote{(Luca) Say something about rigid tropical curves as in ACGS and KLR}
+
+Thus there is a single vertex $\sqC_0$ mapped into the interior of $\RR_{\geq 0}$ and a number of vertices $\sqC_1,\ldots,\sqC_r$ mapped onto the vertex $0 \in \RR_{\geq 0}$.
+No pair of $\sqC_1,\ldots,\sqC_r$ can be connected by an edge, since this would introduce an extra edge length to the tropical moduli space, which then once again would have dimension $\geq 2$.
+Each of $\sqC_1,\ldots,\sqC_r$ must have positive degree by the tropical balancing condition and must be connected to $\sqC_0$ (since the tropical curve must be connected).
+
+Thus, we see that the combinatorial type takes the form of a bipartite graph, with $\sqC_0$ on the right-hand side and $\sqC_1,\ldots,\sqC_r$ on the left-hand side.
+Note that the continuity of the tropical map identifies all of the edge lengths, up to weights given by the expansion factors (i.e.
 tangency orders) at the edges; thus the tropical moduli space is isomorphic to $\RR_{\geq 0}$ and so we have a divisor as expected.
 
-\subsubsection{Recursive description of the divisor}
-Let $\Dcal_{\Mcal}^\circ\subseteq \Mcal$ denote the (codimension-$1$) locally closed stratum corresponding to our combinatorial type.
-The corresponding divisor in $\Mcal$ is $\Dcal_\Mcal = \overline{\Dcal^\circ}$.
-On the other hand, the corresponding divisor $\Dcal$ in $\VZ$ is the proper transform of $\Dcal_\Mcal$, which is obtained by taking the preimage $\Dcal^\circ$ of $\Dcal_\Mcal^\circ$ (since $\Dcal^\circ$ is disjoint from the blown-up locus) and then taking its closure in $\VZ$.
-This is different from taking the preimage of $\Dcal_\Mcal$ (the total transform), since in general $\Dcal_\Mcal$ will intersect the blown-up locus.
-By continuity have an induced map:
-\begin{equation*} \Dcal \to \Dcal_\Mcal. \end{equation*}
-The remainder of this subsection will be dedicated to showing how the map $\Dcal \to \Dcal_\Mcal$ may be interpreted as a blow-up.
-This is an extremely useful fact, because $\Dcal_\Mcal$ has a recursive description in terms of moduli spaces of punctured maps \cite{PuncturedMaps}, which in our setting we are able to compute integrals over.
-We will consider the cases $A,B$ and $C^+$ separately in the next three subsections.
+We distinguish three cases, depending on the position of the circuit, giving the three forms presented in the statement of the Lemma.\end{proof}
 
-\subsubsection{Type A} Choose an element of $\Dcal=\overline{\Dcal^\circ}$ where $\Dcal^\circ \subseteq \VZ$ is the locus of maps with combinatorial type equal to $\Gamma$, which itself is of type A.
-We will now argue that such an element restricts to give an aligned map on the piece of the curve corresponding to $\sqC_1$, and that conversely given an aligned map corresponding to $\sqC_1$ and ordinary punctured and logarithmic maps corresponding to $\sqC_0,\sqC_2,\ldots,\sqC_r$, the glued map is aligned.
-This shows that $\Dcal$ is equal, up to an \'etale quotient, to the fibre product:
-\begin{equation*}\Mpunct{0}{\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}{\PP^N|H}{d_0}\times_{H^r}\left(\VZ_{1,\alpha^{(1)}\cup(m_1)}(\PP^N|H,d_1)\times\prod_{i=2}^r\Mlog{0}{\alpha^{(i)}\cup(m_i)}{\PP^N|H}{d_i}\right).
-\end{equation*}
-Put differently, the map from the closed locus in $\VZ$ to the closed locus in $\Mcal$ is given by blowing up one of the factors of the fibre product
-\begin{equation*}\Mpunct{0}{\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}{\PP^N|H}{d_0}\times_{H^r}\prod_{i=1}^r\Mlog{0}{\alpha^{(i)}\cup(m_i)}{\PP^N|H}{d_i}. \end{equation*}
-and leaving the rest alone. Note that only the moduli space corresponding to $\sqC_0$ is a moduli space of punctured maps: the rest are usual moduli spaces of log stable maps.
+We now now investigate the three types $A,B,C^+$ separately, giving a recursive description of the boundary locus in each case.
+
+\subsubsection{Type A} Let $\Delta$ be a combinatorial type of type $A$ and let $\Dcal\subseteq\VZ$ be the corresponding logarithmic divisor (note there is no choice of ray here).
+The corresponding locus $\Dcal_\Mcal\subseteq\Mcal$ is given (up to a finite cover) by\footnote{(Navid) Include short appendix on integralisation/saturation when gluing punctured maps in our setting?}:
+\begin{equation*}\Dcal_\Mcal=\Mpunct{0}{\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}{\PP^N|H}{d_0}\times_{H^r}\prod_{i=1}^r\Mlog{0}{\alpha^{(i)}\cup(m_i)}{\PP^N|H}{d_i}. \end{equation*}
+In this subsection we will show that
+\begin{equation*}\Dcal_\Mcal=\Mpunct{0}{\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}{\PP^N|H}{d_0}\times_{H^r}\left(\VZ_{1,\alpha^{(1)}\cup(m_1)}(\PP^N|H,d_1)\times\prod_{i=2}^r\Mlog{0}{\alpha^{(i)}\cup(m_i)}{\PP^N|H}{d_i}\right) \end{equation*}
+i.e. that the map $\Dcal\to\Dcal_\Mcal$ is given by blowing up one of the factors of the fibre product.
 

### 2019-01-02 GenusOneRelativeMaps.tex
Looking good now
Finished Type A and I like my proof

@@
 \draw [->,red] (1,-0.9) -- (1,-1.6);
+
+\draw (2.05,0) node[above]{\tiny{$\sqC_0$}};
+\draw (0,1) node[left]{\tiny{$\sqC_1$}};
+\draw (0,.5) node[left]{\tiny{$\sqC_2$}};
+\draw (0,-1) node[left]{\tiny{$\sqC_r$}};
 }}
@@
 \draw (2,0) -- (0,1) (2,0) -- (0,.5) (2,0) -- (0,-1);
-\draw (2,0) circle(2pt)[fill=white];
 \draw [->] (2,0) -- (2.7,0);
 \draw (2.6,0) node[right]{\tiny{$x_k$}};
+\draw (2,0) circle(2pt)[fill=white];
 \draw (0,1) circle(2pt)[fill=black];
@@
 
-\noindent The terminology is due to Vakil, and the picture in this case is very similar to \cite{Vre} (as we will see later, when the circuit is contracted the picture becomes very different).
-Note that in these pictures we have omitted the marked points, the degree of each vertex, and the expansion factors.
+\noindent The terminology is due to Vakil, and the picture in this case is very similar to \cite{Vre} (as we will see later, when the circuit is contracted the picture becomes \emph{very} different).
+Note that in these pictures we have omitted the marked points (apart from $x_k$), the degree of each vertex, and the expansion factors of the edges.
 These combinatorial data can be distributed arbitrarily, as long as:
@@
 In this subsection we will show that
-\begin{equation*}\Dcal_\Mcal=\Mpunct{0}{\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}{\PP^N|H}{d_0}\times_{H^r}\left(\VZ_{1,\alpha^{(1)}\cup(m_1)}(\PP^N|H,d_1)\times\prod_{i=2}^r\Mlog{0}{\alpha^{(i)}\cup(m_i)}{\PP^N|H}{d_i}\right) \end{equation*}
-i.e. that the map $\Dcal\to\Dcal_\Mcal$ is given by blowing up one of the factors of the fibre product.
-
-Let us start by considering possible limiting points of our original locus in $\Mcal$. These correspond to further degenerations of the (combinatorial type of the) tropical map.
+\begin{equation}\label{type A splitting axiom}\Dcal=\Mpunct{0}{\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}{\PP^N|H}{d_0}\times_{H^r}\left(\VZ_{1,\alpha^{(1)}\cup(m_1)}(\PP^N|H,d_1)\times\prod_{i=2}^r\Mlog{0}{\alpha^{(i)}\cup(m_i)}{\PP^N|H}{d_i}\right) \end{equation}
+i.e.
+that the map $\Dcal\to\Dcal_\Mcal$ is given by blowing up one of the factors of the fibre product.
+Note that the map $\Dcal\to\Dcal_\Mcal$ is an isomorphism away from the blown-up locus, which lives inside the locus where the circuit is contracted.
+
+%DEPRECATED?/WRONG?
+
+%Note that if $\sqC_0$ degenerates further then it may be the case that there are components of $\sqC_0$ contained inside the contraction radius for $\sqC$, and thus once we contract to a Smyth curve there are components of $\sqC_0$ adjacent to the genus one singularity.
+However, in this case when we split off $\sqC_1$ these components disappear, and if the factorisation condition holds for $\sqC$ then it holds a fortiori for $\sqC_1$.\footnote{(Navid) I think this is right, but could someone check?
+Maybe there's a better way to say this.} Thus we obtain a morphism from $\Dcal$ to the fibre product on the right-hand side of \eqref{type A splitting axiom}.
+
+Given an element of $\Dcal$ we can split it along the nodes $q_1,\ldots,q_r$ as in \cite{PuncturedMaps}.
+It is then clear that $\sqC_1$ is aligned.
+We claim that $\sqC$ satisfies the factorisation property if and only if $\sqC_1$ does.
+This is enough to show \eqref{type A splitting axiom}.
+
+On $\sqC$ there is an associated contraction radius $\delta$ passing through a non-contracted vertex, such that the strict interior only contains contracted vertices.
+\begin{lemma}\label{type A radius lemma}$\lambda(\sqC^\prime) > \delta$ for any component $\sqC^\prime$ of $\sqC_0$.\end{lemma}
+\noindent Assuming this holds, we see as a consequence that $\sqC_0,\sqC_2,\ldots,\sqC_r$ must lie outside the contraction radius.
+Consequently the aligned curve $\sqC$ satisfies the factorisation condition if and only if $\sqC_1$ does, so \eqref{type A splitting axiom} holds.
+
+\begin{proof} The basic point is that $\Dcal$ consists of the union of the locally closed logarithmic strata adjacent to the locally closed stratum where all the $\sqC_i$ are irreducible.
+If we look at one of these boundary strata, the tropical moduli space contains a ray $\sigma$ corresponding to the stratum where all the $\sqC_i$ are irreducible; this amounts to setting all edge lengths other than $e_1,\ldots,e_r$ to zero.
+If $f_1,\ldots,f_l$ are some number of these additional edge lengths (corresponding to internal nodes in degenerations of the $\sqC_i$) then all of the cones of the subdivision adjacent to $\sigma$ will have $f_1+\ldots+f_l < e_j$ for all $j\in\{1,\ldots,r\}$, since $f_1=\ldots=f_l=0$ and $e_j \neq 0$ on $\sigma$.
+In particular, if $\sqC_1$ is degenerate and if $e$ denotes the minimal distance from the circuit to a non-contracted vertex of $\sqC_1$ (which certainly exists since $\sqC_1$ has positive degree) then $e < e_1 < \lambda(\sqC^\prime)$.
+Thus $\delta=e$ and $\delta < \lambda(\sqC^\prime)$ as claimed.\footnote{(Navid) Do an example?}\end{proof}
+
+\subsubsection{Type B}
 

### 2019-01-02 GenusOneRelativeMaps.tex
Did type B

@@
 \draw (0,1) node[left]{\tiny{$\sqC_1$}};
-\draw (0,.5) node[left]{\tiny{$\sqC_2$}};
+\draw (0,.5) node[left]{\tiny{$\sqC_3$}};
 \draw (0,-1) node[left]{\tiny{$\sqC_r$}};
@@
 
-\section{Recursion formula for $(\PP^N|H)$}
+\section{Splitting axiom and recursion formula for $(\PP^N|H)$}
 
@@
 \begin{lemma} Let $\Dcal \subseteq \Dcal(k)$ be an irreducible component and let $\Delta$ be the corresponding combinatorial type.
-Suppose that $\Delta$ assigns circuit has positive degree to the circuit.
+Suppose that $\Delta$ assigns positive degree to the circuit.
 Then $\Delta$ takes one of the following forms:
@@
 
-\subsubsection{Type A} Let $\Delta$ be a combinatorial type of type $A$ and let $\Dcal\subseteq\VZ$ be the corresponding logarithmic divisor (note there is no choice of ray here).
+\subsubsection{Type $A$} Let $\Delta$ be a combinatorial type of type $A$ and let $\Dcal\subseteq\VZ$ be the corresponding logarithmic divisor (note there is no choice of ray here).
 The corresponding locus $\Dcal_\Mcal\subseteq\Mcal$ is given (up to a finite cover) by\footnote{(Navid) Include short appendix on integralisation/saturation when gluing punctured maps in our setting?}:
@@
 Thus $\delta=e$ and $\delta < \lambda(\sqC^\prime)$ as claimed.\footnote{(Navid) Do an example?}\end{proof}
-
-\subsubsection{Type B}
+Notice we did not specify whether $\delta$ was the relative or absolute radius.
+The point is that it does not matter; the proof goes through the same in either case.
+Thus we see that $\sqC$ satisfies the (double) factorisation condition if and only if $\sqC_1$ does.
+
+\subsubsection{Type $B$}
+Now let $\Dcal\subseteq\VZ$ be a component of $\Dcal(k)$ with combinatorial type $\Delta$ of type $B$.
+In this case, it is impossible for the circuit to be contracted.
+Thus, $\Dcal_\Mcal \subseteq \Mcal$ is disjoint from the blown-up locus, and the map
+\begin{equation*} \Dcal \to \Dcal_\Mcal \end{equation*}
+is an isomorphism. Thus we obtain:
+\begin{equation*} \Dcal = \Mpunct{0}{\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}{\PP^N|H}{d_0}\times_{H^r}\left(\Mlog{0}{\alpha^{(1)}\cup(m_1,m_2)}{\PP^N|H}{d_1}\times\prod_{i=3}^r\Mlog{0}{\alpha^{(i)}\cup(m_i)}{\PP^N|H}{d_i}\right).\end{equation*}
+
+\subsubsection{Type $C^+$}
 
@@
 \begin{enumerate}[label=(\Alph*)]
- \item \[\mathcal Y_a=\M{0}{\{-m^{(1)},\ldots,-m^{(r)}\}\cup\alpha^{(0)}}{H}{d_0}^\sim\times_{H^r}\left(\VZc{1}{\alpha^{(1)}\cup\{m^{(1)}\}}{\PP^N|H}{d_1}\times\prod_{i=2}^r\M{0}{\alpha^{(i)}\cup\{m^{(i)}\}}{\PP^N|H}{d_i}\right)\]
+
  \item \[\mathcal Y_b=\M{0}{\{-m^{(1)},\ldots,-m^{(r)}\}\cup\alpha^{(0)}}{H}{d_0}^\sim\times_{H^r}\left(\M{0}{\alpha^{(1)}\cup\{m^{(1)},m^{(2)}\}}{\PP^N|H}{d_1}\times\prod_{i=3}^r\M{0}{\alpha^{(i)}\cup\{m^{(i)}\}}{\PP^N|H}{d_i}\right)\]

### 2019-01-04 GenusOneRelativeMaps.tex
Added something on punctured maps - a bit messy at the moment

@@
 
+\subsection{Splitting and gluing punctured logarithmic maps}\label{subsection punctured maps} We still start by considering the usual moduli space $\Mcal$ of log stable maps.
+In \cite{PuncturedMaps}, a recursive description of the logarithmic strata of $\Mcal$ is given, in terms of moduli spaces of punctured maps.
+As discussed above, the logarithmic strata of $\Mcal$ are indexed by combinatorial types of tropical curves.
+Given such a combinatorial type, each vertex of the associated graph defines a moduli space of punctured stable maps.
+This has a degree and genus given by the degree and genus of the vertex, and a target space given by the logarithmic stratum corresponding to the tropical stratum into which the vertex is mapped.
+It has marked points indexed by the edges and flags adjacent to that vertex, and these marked points have tangencies (which may be positive or negative) depending on the expansion factors of the associated edges and flags.
+If all of the tangencies are positive, then a punctured map is the same thing as a log stable map.
+
+In our setting, when dealing with truly punctured maps, the associated logarithmic stratum of the target will always be the divisor $H$. Consider a moduli space
+\begin{equation*} \Mpunct{g}{\alpha}{H}{d} \end{equation*}
+where $g \in \{0,1\}$ and $\alpha$ is a vector of tangency orders, some of which are negative.
+Here $H$ is given the log structure pulled back from $\PP^N$; since $H$ is not log smooth, the natural obstruction theory on the above moduli space is not necessarily perfect.
+On the other hand, we will see that this space is birational to the moduli space
+\begin{equation*} \ol\Mcal^{\alpha}_{g,n}(H,d) \subseteq \M{g}{n}{H}{d} \end{equation*}
+of ordinary stable maps to $H$ satisfying the condition:
+\begin{equation*} f^*\OO_H(1) \cong \OO_C(\Sigma_i \alpha_ix_i).\end{equation*}
+This is referred to as the \emph{double ramification locus} and has been studied extensively.
+It is a closed substack of virtual codimension $g$ in $\M{g}{n}{H}{d}$.
+In the genus zero case it is equal to the entire space
+\begin{equation*} \ol\Mcal^{\alpha}_{0,n}(H,d) = \M{0}{n}{H}{d} \end{equation*}
+which is smooth. Thus integrals over $\Mpunct{0}{\alpha}{H}{d}$ are the same as integrals over $\M{0}{n}{H}{d}$. The genus one case is more delicate; see \S \ref{} below.
+
+We will now use this recursive description of the logarithmic strata in $\Mcal$ to obtain a similar description of the strata in $\VZ$.
+
 \subsection{Recursive description of the divisors: types $A,B$ and $C^+$}
@@
 The remainder of this section will be dedicated to showing how the map $\Dcal \to \Dcal_\Mcal$ may be interpreted as a blow-up.
-The reason this is useful is that $\Dcal_\Mcal$ itself has a recursive description, in terms of moduli spaces of punctured maps \cite{PuncturedMaps}, which in our setting we are able to compute integrals over.
+The reason this is useful is that $\Dcal_\Mcal$ itself has a recursive description in terms of moduli spaces of punctured maps (see \S \ref{subsection punctured maps}), which in our setting we are able to compute integrals over.
 
@@
 
-We distinguish three cases, depending on the position of the circuit, giving the three forms presented in the statement of the Lemma.\end{proof}
+We distinguish three cases, depending on the position of the circuit, giving the three forms presented in the statement of the lemma.\end{proof}
 
@@
 The corresponding locus $\Dcal_\Mcal\subseteq\Mcal$ is given (up to a finite cover) by\footnote{(Navid) Include short appendix on integralisation/saturation when gluing punctured maps in our setting?}:
-\begin{equation*}\Dcal_\Mcal=\Mpunct{0}{\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}{\PP^N|H}{d_0}\times_{H^r}\prod_{i=1}^r\Mlog{0}{\alpha^{(i)}\cup(m_i)}{\PP^N|H}{d_i}. \end{equation*}
+\begin{equation*}\Dcal_\Mcal=\Mpunct{0}{\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}{H}{d_0}\times_{H^r}\prod_{i=1}^r\Mlog{0}{\alpha^{(i)}\cup(m_i)}{\PP^N|H}{d_i}. \end{equation*}
 In this subsection we will show that
-\begin{equation}\label{type A splitting axiom}\Dcal=\Mpunct{0}{\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}{\PP^N|H}{d_0}\times_{H^r}\left(\VZ_{1,\alpha^{(1)}\cup(m_1)}(\PP^N|H,d_1)\times\prod_{i=2}^r\Mlog{0}{\alpha^{(i)}\cup(m_i)}{\PP^N|H}{d_i}\right) \end{equation}
+\begin{equation}\label{type A splitting axiom}\Dcal=\Mpunct{0}{\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}{H}{d_0}\times_{H^r}\left(\VZ_{1,\alpha^{(1)}\cup(m_1)}(\PP^N|H,d_1)\times\prod_{i=2}^r\Mlog{0}{\alpha^{(i)}\cup(m_i)}{\PP^N|H}{d_i}\right) \end{equation}
 i.e.
@@
 Note that the map $\Dcal\to\Dcal_\Mcal$ is an isomorphism away from the blown-up locus, which lives inside the locus where the circuit is contracted.
+Note that there is a birational map which forgets the log structures
+\begin{equation*} \Mpunct{0}{\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}{H}{d_0} \to \M{0}{n_0+r}{H}{d_0} \end{equation*}
+and all of our insertions are pulled back from the latter space. Therefore the integrals over the punctured space are determined by the genus zero Gromov--Witten theory of $H\cong\PP^{N-1}$.
 
@@
 is an isomorphism. Thus we obtain:
-\begin{equation*} \Dcal = \Mpunct{0}{\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}{\PP^N|H}{d_0}\times_{H^r}\left(\Mlog{0}{\alpha^{(1)}\cup(m_1,m_2)}{\PP^N|H}{d_1}\times\prod_{i=3}^r\Mlog{0}{\alpha^{(i)}\cup(m_i)}{\PP^N|H}{d_i}\right).\end{equation*}
-
-\subsubsection{Type $C^+$}
+\begin{equation*} \Dcal = \Mpunct{0}{\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}{H}{d_0}\times_{H^r}\left(\Mlog{0}{\alpha^{(1)}\cup(m_1,m_2)}{\PP^N|H}{d_1}\times\prod_{i=3}^r\Mlog{0}{\alpha^{(i)}\cup(m_i)}{\PP^N|H}{d_i}\right).\end{equation*}
+As before, the integrals over the punctured space are determined by the Gromov--Witten theory of $H$.
+
+\subsubsection{Type $C^+$} Finally let $\Dcal \subseteq \VZ$ be a component of $\Dcal(k)$ with combinatorial type $\Delta$ of type $C^+$. The corresponding locus in $\Mcal$ can be written as:
+\begin{equation*} \Dcal_\Mcal = \Mpunct{1}{\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}{H}{d_0} \times_{H^r} \left( \prod_{i=1}^r \Mlog{0}{\alpha^{(i)}\cup(m_i)}{\PP^N|H}{d_i} \right). \end{equation*}
+Then the same argument as in Lemma \ref{type A radius lemma} shows that given any point in $\Dcal$ the interior of the radius can only contain components of $C_0$.
+Thus the alignment and factorisation condition apply exclusively to $C_0$, which shows that:
+\begin{equation*}\Dcal = \VZ^{\operatorname{punct}}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(H,d_0) \times_{H^r} \left( \prod_{i=1}^r \Mlog{0}{\alpha^{(i)}\cup(m_i)}{\PP^N|H}{d_i} \right).
+\end{equation*}
+Here the first factor
+\begin{equation*}\VZ^{\operatorname{punct}}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(H,d_0) \end{equation*}
+is the logarithmic blow-up of the moduli space of punctured maps, obtained by imposing an alignment and factorisation condition.
+To be more precise: its elements consist of punctured maps to $H$ which are aligned in the sense of Definition \ref{}, and satisfy the (double) factorisation condition (simply replace $\PP^N$ by $H$ everywhere in that definition).
+
+\begin{prop} $\VZ^{\operatorname{punct}}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(H,d_0)$ is irreducible of the expected dimension, and birational to the main component of the double ramification locus:
+\begin{equation*} \ol{\Mcal}_{1,n_0+r}^{\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(H,d_0) \subseteq \ol{\Mcal}_{1,n_0+r}(H,d_0) \end{equation*}\end{prop}
+
+Now, the double ramification locus carries a natural virtual class, and one can write
+\begin{equation*} \virt{\ol{\Mcal}_{1,n_0+r}^{\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(H,d_0)} = \gamma \cap \virt{\ol{\Mcal}_{1,n_0+r}(H,d_0)} \end{equation*}
+where $\gamma \in \Achow^1(\M{1}{n}{H}{d})$ is some explicit sum of tautological classes \cite{DRCBundle}.
+To identify the class of the main component, we split the virtual class of the double ramification locus as
+\begin{equation*} \virt{\ol\Mcal^{\alpha}_{1,n}(H,d)} = [\ol\Mcal^{\alpha,\text{main}}_{1,n}(H,d)] + \sum_{\Gamma} \virt{\ol\Mcal^{\alpha,\Gamma}_{1,n}(H,d)} \end{equation*}
+and this allows us to write
+\begin{equation*} [\ol\Mcal^{\alpha,\text{main}}_{1,n}(H,d)] = \gamma^\prime \cap [\ol\Mcal^{\text{main}}_{1,n}(H,d)]\end{equation*}
+where $\gamma^\prime$ is some other sum of tautological classes.
+This makes integrals over $\VZ^{\operatorname{punct}}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(H,d_0)$ computable in terms of the reduced Gromov--Witten theory of $H\cong\PP^{N-1}$.
 
 \newpage
-Now we may use the recursive description of the boundary in $\Mcal$ using punctured maps \cite{PuncturedMaps} to obtain a description of these loci:
-\begin{enumerate}[label=(\Alph*)]
-
- \item \[\mathcal Y_b=\M{0}{\{-m^{(1)},\ldots,-m^{(r)}\}\cup\alpha^{(0)}}{H}{d_0}^\sim\times_{H^r}\left(\M{0}{\alpha^{(1)}\cup\{m^{(1)},m^{(2)}\}}{\PP^N|H}{d_1}\times\prod_{i=3}^r\M{0}{\alpha^{(i)}\cup\{m^{(i)}\}}{\PP^N|H}{d_i}\right)\]
- \item \[\mathcal Y_c^+= \VZc{1}{\{-m^{(1)},\ldots,-m^{(r)}\}\cup\alpha^{(0)}}{H}{d_0}^{\sim} \times_{H^r}\prod_{i=1}^r\M{0}{\alpha^{(i)}\cup\{m^{(i)}\}}{\PP^N|H}{d_i}\]
-\end{enumerate}
-where $\M{0}{\mu}{H}{d}^\sim$ denotes the space of genus zero punctured maps, while $\VZc{0}{\mu}{H}{d}$ denotes the desingularisation of the main component of the space of punctured maps discussed in Section ???.
-The numerical data run over all splitting $A$ of the tangency conditions (resp.
-$B$ of the degree) in $r+1$ parts, such that:
-\begin{enumerate}
- \item $d_0+\sum_{i=1}^r m^{(i)}=\sum\alpha^{(0)}$;
- \item $d_i=m^{(i)}+\sum\alpha^{(i)}$;
- \item $d_0>0$ in case $c$.
-\end{enumerate}
 

### 2019-01-04 GenusOneRelativeMaps.tex
Minor changes

@@
 
-If we have two strata $\Scal_1$ and $\Scal_2$ corresponding to combinatorial types $\Gamma_1$ and $\Gamma_2$, then $\Scal_2$ is contained in the closure of $\Scal_1$ if and only if the combinatorial type $\Gamma_1$ is obtained from $\Gamma_2$ by a process of generisation: namely, by contracting some edges (i.e.
+If we have two strata $\Scal_1$ and $\Scal_2$ corresponding to combinatorial types $\Delta_1$ and $\Delta_2$, then $\Scal_2$ is contained in the closure of $\Scal_1$ if and only if the combinatorial type $\Delta_1$ is obtained from $\Delta_2$ by a process of generisation: namely, by contracting some edges (i.e.
 smoothing some nodes) and moving some of the vertices from the interior $\RR_{>0} \subseteq \RR_{\geq 0}$ of the tropicalisation $\Sigma(\PP^N|H)$ to the vertex $0 \in \RR_{\geq 0}$ (i.e.
@@
 \subsubsection{Logarithmic strata of $\VZ$}
-Now let us pick a stratum $\Scal \subseteq \Mcal$ indexed by a combinatorial type $\Gamma$ and with associated monoid $Q$.
+Now let us pick a stratum $\Scal \subseteq \Mcal$ indexed by a combinatorial type $\Delta$ and with associated monoid $Q$.
 We may choose a sufficiently small open neighbourhood of $\Scal$ which only intersects logarithmic strata $\Scal^\prime$ which contain $\Scal$ in their closures.
-The previous discussion then shows that if we pick any point in this open neighbourhood, the combinatorial type of the associated tropical curve is obtained from $\Gamma$ by contracting some edges and specialising some vertices.
+The previous discussion then shows that if we pick any point in this open neighbourhood, the combinatorial type of the associated tropical curve is obtained from $\Delta$ by contracting some edges and specialising some vertices.
 Thus we see that the associated map on tropical moduli spaces is injective, and so the generisation map on the level of ghost sheaves is surjective.
@@
 
-Whenever we consider a logarithmic stratum in $\VZ$, by its combinatorial type we will always mean the generisation of the ``original'' combinatorial type induced by our choice of cone in the polyhedral subdivision.
-This does not depend on the choice of original combinatorial type.
+Whenever we consider a logarithmic stratum in $\VZ$, by its combinatorial type we will always mean the generisation of the ``initial'' combinatorial type induced by our choice of cone in the polyhedral subdivision.
+This does not depend on the choice of initial combinatorial type.
 

### 2019-01-14 GenusOneRelativeMaps.tex
Minor corrections

@@
 This is the technically most difficult part of the paper.
-The recursive description bears some similarities with the recursive desription of the boundary of the absolute space $\VZ_{1,n}(\PP^N,d)$ given in \cite{VZ}; in keeping with the theme of this paper, however, we will see that log geometry provides a convenient framework for dealing with the combinatorics.
+The recursive description bears some similarities with the recursive description of the boundary of the absolute space $\VZ_{1,n}(\PP^N,d)$ given in \cite{VZ}; in keeping with the theme of this paper, however, we will see that log geometry provides a convenient framework for dealing with the combinatorics.
 
@@
 
-Now, let $\Dcal_{\Mcal}^\circ\subseteq \Mcal$ denote the (codimension-$1$) locally closed stratum corresponding to our choice of combinatorial type, and let $\Dcal_\Mcal = \overline{\Dcal^\circ}$ be the corresponding logarithmic stratum in $\Mcal$.
-Our divisor $\Dcal\subseteq\VZ$ is the proper transform of $\Dcal_\Mcal$, which is obtained by taking the preimage $\Dcal^\circ$ of $\Dcal_\Mcal^\circ$ (since $\Dcal^\circ$ is disjoint from the blown-up locus) and then taking its closure in $\VZ$.
+Now, let $\Dcal_{\Mcal}^\circ\subseteq \Mcal$ denote the (codimension-$1$) locally closed stratum corresponding to our choice of combinatorial type, and let $\Dcal_\Mcal = \overline{\Dcal^\circ_\Mcal}$ be the corresponding logarithmic stratum in $\Mcal$.
+Our divisor $\Dcal\subseteq\VZ$ is the proper transform of $\Dcal_\Mcal$, which is obtained by taking the preimage $\Dcal^\circ$ of $\Dcal_\Mcal^\circ$ (since $\Dcal^\circ_\Mcal$ is disjoint from the blown-up locus) and then taking its closure in $\VZ$.
 This is, of course, different from taking the preimage of $\Dcal_\Mcal$, since in general $\Dcal_\Mcal$ will intersect the blown-up locus.
@@
 The corresponding locus $\Dcal_\Mcal\subseteq\Mcal$ is given (up to a finite cover) by\footnote{(Navid) Include short appendix on integralisation/saturation when gluing punctured maps in our setting?}:
-\begin{equation*}\Dcal_\Mcal=\Mpunct{0}{\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}{H}{d_0}\times_{H^r}\prod_{i=1}^r\Mlog{0}{\alpha^{(i)}\cup(m_i)}{\PP^N|H}{d_i}. \end{equation*}
+\begin{equation*}\Dcal_\Mcal=\Mpunct{0}{\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}{H}{d_0}\times_{H^r}\left( \Mlog{1}{\alpha^{(1)}\cup(m_1)}{\PP^N|H}{d_1} \times \prod_{i=2}^r\Mlog{0}{\alpha^{(i)}\cup(m_i)}{\PP^N|H}{d_i} \right).
+\end{equation*}
 In this subsection we will show that
@@
 If $f_1,\ldots,f_l$ are some number of these additional edge lengths (corresponding to internal nodes in degenerations of the $\sqC_i$) then all of the cones of the subdivision adjacent to $\sigma$ will have $f_1+\ldots+f_l < e_j$ for all $j\in\{1,\ldots,r\}$, since $f_1=\ldots=f_l=0$ and $e_j \neq 0$ on $\sigma$.
-In particular, if $\sqC_1$ is degenerate and if $e$ denotes the minimal distance from the circuit to a non-contracted vertex of $\sqC_1$ (which certainly exists since $\sqC_1$ has positive degree) then $e < e_1 < \lambda(\sqC^\prime)$.
-Thus $\delta=e$ and $\delta < \lambda(\sqC^\prime)$ as claimed.\footnote{(Navid) Do an example?}\end{proof}
+In particular, if $\sqC_1$ is degenerate and if $f$ denotes the minimal distance from the circuit to a non-contracted vertex of $\sqC_1$ (which certainly exists since $\sqC_1$ has positive degree) then $f < e_1 \leq \lambda(\sqC^\prime)$.
+Thus $\delta=f$ and $\delta < \lambda(\sqC^\prime)$ as claimed.\footnote{(Navid) Do an example?}\end{proof}
 Notice we did not specify whether $\delta$ was the relative or absolute radius.

### 2019-01-28 GenusOneRelativeMaps.tex

@@
 
-Now, the logarithmic divisors which are contained in $\Dcal(k)$ are precisely those whose corresponding combinatorial type has the vertex of the dual graph containing $x_k$ mapped into the interior of $\RR_{\geq 0}$.
+Now, the logarithmic divisors which are contained in $\Dcal(k)$ are precisely those whose corresponding combinatorial type has the vertex of the dual graph containing $x_k$ mapped into the interior $\RR_{>0} \subseteq \RR_{\geq 0}$.
 
@@
 The combinatorial type and choice of ray allows us to describe the general element of such a component.
-What we are still lacking is a recursive description of the components which will allow us to compute integrals over them.
+What we are still lacking is a recursive description of the components, which we need in order to compute integrals over them.
 This is the subject of the remainder of this section.
@@
 
-Now, let $\Dcal_{\Mcal}^\circ\subseteq \Mcal$ denote the (codimension-$1$) locally closed stratum corresponding to our choice of combinatorial type, and let $\Dcal_\Mcal = \overline{\Dcal^\circ_\Mcal}$ be the corresponding logarithmic stratum in $\Mcal$.
-Our divisor $\Dcal\subseteq\VZ$ is the proper transform of $\Dcal_\Mcal$, which is obtained by taking the preimage $\Dcal^\circ$ of $\Dcal_\Mcal^\circ$ (since $\Dcal^\circ_\Mcal$ is disjoint from the blown-up locus) and then taking its closure in $\VZ$.
+Since $\VZ \to \Mcal$ is a log modification, the divisor $\Dcal$ is either exceptional or the proper transform of a logarithmic divisor on $\Mcal$.
+In this subsection, we will focus on the latter case.
+Then if we let $\Dcal_{\Mcal}^\circ\subseteq \Mcal$ denote the locally closed stratum corresponding to our choice of combinatorial type, and $\Dcal_\Mcal = \overline{\Dcal^\circ_\Mcal}$ denote the corresponding logarithmic divisor in $\Mcal$, then our divisor $\Dcal\subseteq\VZ$ is the proper transform of $\Dcal_\Mcal$, which is obtained by taking the preimage $\Dcal^\circ$ of $\Dcal_\Mcal^\circ$ (since $\Dcal^\circ_\Mcal$ is disjoint from the blown-up locus) and then taking its closure in $\VZ$.
 This is, of course, different from taking the preimage of $\Dcal_\Mcal$, since in general $\Dcal_\Mcal$ will intersect the blown-up locus.
@@
 
-For the remainder of this subsection, we will consider only the situation where the circuit has positive degree; the other, more complicated case, will be taken up in \S \ref{}.
+For the remainder of this subsection, we will consider only the situation where the circuit is assigned a positive degree by the combinatorial type; the other, more complicated case, will be taken up in \S \ref{}.
 
@@
 \begin{enumerate}
-\item every vertex has positive degree;
+\item the vertices $\sqC_1,\ldots,\sqC_r$ have positive degree (and $\sqC_0$ has positive degree in the $\Ycal_C^+$ case);
+\item every vertex is stable;
 \item the balancing condition is satisfied.
-\end{enumerate}
-Note that since every vertex has positive degree, there is no need to impose stability.\end{lemma}
+\end{enumerate}\end{lemma}
 
@@
 Recall that we have $\Dcal\subseteq\VZ$ obtained by a choice of combinatorial type and ray in the subdivison of the tropical moduli space.
-In this situation, the subdivision is trivial since no alignment is necessary (both radii are zero).
+In this situation, since the circuit has positive degree no alignment is necessary (both radii are zero), and hence the subdivision is trivial.
 Following our procedure, we choose a ray of the tropical moduli space $Q^\vee_{\RR}$.
@@
 
-We claim that this is the only vertex of the tropical curve mapped into the interior; if there were more, the positions of their images in $\RR_{\geq 0}$ would be independent, and thus the tropical moduli space would have dimension $\geq 2$, a contradiction.\footnote{(Luca) Say something about rigid tropical curves as in ACGS and KLR}
-
-Thus there is a single vertex $\sqC_0$ mapped into the interior of $\RR_{\geq 0}$ and a number of vertices $\sqC_1,\ldots,\sqC_r$ mapped onto the vertex $0 \in \RR_{\geq 0}$.
+We claim that this is the only vertex of the tropical curve mapped into the interior; if there were more, the positions of their images in $\RR_{> 0}$ would be independent, and thus the tropical moduli space would have dimension $\geq 2$, a contradiction.\footnote{(Luca) Say something about rigid tropical curves as in ACGS and KLR}
+
+Thus there is a single vertex $\sqC_0$ mapped into the interior $\RR_{>0} \subseteq \RR_{\geq 0}$ and a number of vertices $\sqC_1,\ldots,\sqC_r$ mapped onto the vertex $0 \in \RR_{\geq 0}$.
 No pair of $\sqC_1,\ldots,\sqC_r$ can be connected by an edge, since this would introduce an extra edge length to the tropical moduli space, which then once again would have dimension $\geq 2$.
@@
 \end{equation*}
-In this subsection we will show that
-\begin{equation}\label{type A splitting axiom}\Dcal=\Mpunct{0}{\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}{H}{d_0}\times_{H^r}\left(\VZ_{1,\alpha^{(1)}\cup(m_1)}(\PP^N|H,d_1)\times\prod_{i=2}^r\Mlog{0}{\alpha^{(i)}\cup(m_i)}{\PP^N|H}{d_i}\right) \end{equation}
-i.e.
-that the map $\Dcal\to\Dcal_\Mcal$ is given by blowing up one of the factors of the fibre product.
-Note that the map $\Dcal\to\Dcal_\Mcal$ is an isomorphism away from the blown-up locus, which lives inside the locus where the circuit is contracted.
-Note that there is a birational map which forgets the log structures
+\begin{lemma}We have the following description of $\Dcal$\begin{equation}\label{type A splitting axiom}\Dcal=\Mpunct{0}{\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}{H}{d_0}\times_{H^r}\left(\VZ_{1,\alpha^{(1)}\cup(m_1)}(\PP^N|H,d_1)\times\prod_{i=2}^r\Mlog{0}{\alpha^{(i)}\cup(m_i)}{\PP^N|H}{d_i}\right) \end{equation}
+i.e. the map $\Dcal\to\Dcal_\Mcal$ is given by blowing up one of the factors of the fibre product.\end{lemma} Note that there is a birational map which forgets the log structures
 \begin{equation*} \Mpunct{0}{\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}{H}{d_0} \to \M{0}{n_0+r}{H}{d_0} \end{equation*}
@@
 Maybe there's a better way to say this.} Thus we obtain a morphism from $\Dcal$ to the fibre product on the right-hand side of \eqref{type A splitting axiom}.
-
+\begin{proof}
+Note first of all that the map $\Dcal\to\Dcal_\Mcal$ is an isomorphism away from the blown-up locus, which is contained inside the locus where the circuit is contracted.
 Given an element of $\Dcal$ we can split it along the nodes $q_1,\ldots,q_r$ as in \cite{PuncturedMaps}.
@@
 Thus $\delta=f$ and $\delta < \lambda(\sqC^\prime)$ as claimed.\footnote{(Navid) Do an example?}\end{proof}
-Notice we did not specify whether $\delta$ was the relative or absolute radius.
+\noindent Notice we did not specify whether $\delta$ was the relative or absolute radius.
 The point is that it does not matter; the proof goes through the same in either case.
-Thus we see that $\sqC$ satisfies the (double) factorisation condition if and only if $\sqC_1$ does.
+Thus we see that $\sqC$ satisfies the (double) factorisation condition if and only if $\sqC_1$ does.\end{proof}
 

### 2019-01-28 GenusOneRelativeMaps.tex
fgt on drc, streamlined the description of tropical rays of type Yc0, added recursion procedure from my thesis

@@
 
-\subsection{A desingularisation of punctured log maps}
-Describe an analogous desingularisation for punctured log maps.
+%\subsection{A desingularisation of punctured log maps}
+%Describe an analogous desingularisation for punctured log maps.
 The degree zero case seems more delicate and complicated, even though it should just be a substack of a moduli space of marked curves after all (the log structure is possibly trickier).
-\begin{dfn}
- A $(z,g,n)$-punctured log map is a punctured log map where the markings with negative contact order to $H$ have an extra label, either $z$ (the tropical map sends them to $z$ero), or $g$ (stands for gluing), or $n$ (stands for nihil, nothing...)
-\end{dfn}
-We would like to extend the minimal monoid in order to account for some of the punctures, i.e.
+%\begin{dfn}
+% A $(z,g,n)$-punctured log map is a punctured log map where the markings with negative contact order to $H$ have an extra label, either $z$ (the tropical map sends them to $z$ero), or $g$ (stands for gluing), or $n$ (stands for nihil, nothing...)
+%\end{dfn}
+%We would like to extend the minimal monoid in order to account for some of the punctures, i.e.
 take the sum of $p^*\mathcal M_{C^\circ}$ (for every such puncture $p$) fibered over the log structure of the base, which seems to have the same effect as topping those edges with a uertex (which doesn't carry any other information).
@@
 \begin{equation*} \ol\Mcal^{\alpha}_{0,n}(H,d) = \M{0}{n}{H}{d} \end{equation*}
-which is smooth. Thus integrals over $\Mpunct{0}{\alpha}{H}{d}$ are the same as integrals over $\M{0}{n}{H}{d}$. The genus one case is more delicate; see \S \ref{} below.
+which is smooth.
+Thus integrals over $\Mpunct{0}{\alpha}{H}{d}$ are the same as integrals over $\M{0}{n}{H}{d}$.
+The genus one case is more delicate; yet, luckily, we are only interested in the main component of the punctured space.
+
+\begin{lem}
+ Alignment and factorisation single out the closure of the locus of punctured maps with smooth source curve.
+\end{lem}
+\begin{proof}
+ If it is true, we might be able to prove it via deformation theory.
+For this it might be useful to notice that there is a morphism $\Mpunct{g}{\alpha}{H}{d}\to \Mpunct{g}{\alpha}{\PP^N}{d}$ (because $H\subseteq\PP^N$ is strict), which is probably a closed immersion, and the loci with smooth source curve are isomorphic under this map.
+It seems plausible that the main omponent is log smooth over $B\Gm\subseteq[\Aaff^1/\Gm]$ (or the standard log point).
+\end{proof}
+
+\begin{lem}
+The main component of punctured maps is birational to the main component of the DR locus.
+\end{lem}
+We probably want the latter statement to hold under imposing alignment and factorisation (keeping the log structure on the source curve, but forgetting that the map is log).
+
+\begin{lem}
+ Forgetting a marking $\fgt_i\colon\ol\Mcal_{1,n}^\alpha(H,d)^{\rm{main}} \to\VZ_{1,n-1}(H,d)$ is generically finite of degree $\alpha_i^2$ - except in one case.
+\end{lem}
+\begin{proof}
+ Let us consider the case $d=0$ first.
+We may assume the source curve is smooth elliptic $E$.
+The map \[ \phi\colon E\to \Pic^0(E),\qquad x\mapsto\OO_E\left(\alpha_ix+\sum_{j=1,\ldots,\hat i\ldots,n}\alpha_jp_j\right)\]
+ is an isogeny of degree $\alpha_i^2$.
+The locus of $(C,p_1,\ldots,\hat{p_i},\ldots,p_n)$ such that the kernel of $\phi$ contains one of the points $\{p_1,\ldots,\hat{p_i},\ldots,p_n\}$ is itself a double ramification locus inside $\oM_{1,n}$, hence non-generic - with one exception: namely, when $n=2$, $x=p_1$ is always a solution, but the curve lying above such point bubbles off a $\PP^1$.
+To see that it does not belong to the closure of the nice locus, notice that the rational function trivialising $\OO_C(\alpha_1p_1-\alpha_2p_2)$ should descend to the cusp, thus having a ramification point at the node; yet its ramification profile is determined by Riemann-Hurwitz, and it is entirely supported on $p_1$ and $p_2$.
+
+ For a different proof: notice that we should obtain the class of the main component from the full double ramification cycle by subtracting the boundary class $[D_{1,\emptyset|0,\{1,\ldots,n\}}]$.
+The latter pushes forward to $0$ under $\fgt_i$, unless $n=2$.
+Therefore we may apply $\fgt_{i,*}$ to the Hain-Pixton formula:
+ \[DR_1(A)=\frac{1}{2}\left(\sum_{i=1}^na_i^2\psi_i-\sum_{\substack{I\subseteq\{1,\ldots,n\}\\|I|\geq 2}}a_I^2[D_{1,I^c|0,I}]-\frac{1}{12}\delta_0\right),\]
+ where $a_I=\sum_{i\in I}a_i$ and $\delta_0=\operatorname{glue}_*([\oM_{0,n+2}])$.
+From $\psi_j=\fgt_i^*\psi_j+[D_{i,j}]$ for $i\neq j$, and the dilaton equation, we see that $\fgt_{i,*}\psi_j=1$ and $\fgt_{i,*}\psi_i=n-1$.
+On the other hand, the only surviving boundary classes are $[D_{i,j}]$, and they push down to $1$.
+Hence the formula pushes down to $\frac{1}{2}\left(\sum_{j\neq i}\alpha_j^2+(n-1)\alpha_i^2-\sum_{j\neq i}(\alpha_j+\alpha_i)^2\right)=-\alpha_i\left(\sum_{j\neq i}\alpha_j\right)=\alpha_i^2.$
+\end{proof}
 
@@
 
-Review here the process of gluing for punctured maps.
+\footnote{(Luca) to be made homogeneous with what comes earlier} Review here the process of gluing for punctured maps.
 In particular the basic monoid should be modified in order to make the relevant evaluations log morphisms.
@@
 On the other hand, when there is a contracted elliptic subcurve - and it will be contracted into the hyperplane, because otherwise it wouldn't be generic, by density of the nice locus in $\VZ_{1,\alpha^\prime}(\PP^N|H,d^\prime)$ - the picture becomes more complicated due to the alignment.
-The combs may break (multiple times) and they may point in opposite directions.
-We label these loci $\mathcal{Y}_c^0$.
+The combs may break.
+We label these loci $\mathcal{Y}_C^0$.
 \begin{figure}
+
  \tikz{
- \draw (0,0) circle(2pt)[fill=black] (0,2) circle(2pt)[fill=black] (0,4) circle(2pt)[fill=black] (0,6) circle(2pt)[fill=black] (0,-2) circle(2pt)[fill=black] (1.1,1.78) circle(2pt)[fill=black] (3.42,1.42) circle(2pt)[fill=black] (.58,-1.42) circle(2pt)[fill=black];
- \draw (2,0) -- node[above]{4} (0,0) (2,0) --node[above]{2} (1.1,1.78) --node[above]{2} (0,2) (1.1,1.78) --node[above]{1} (0,4) (2,0) --node[above]{1} (3.42,1.42) (2,0) --node[above]{1} (.58,-1.42) (3.42,1.42) --node[above]{5} (0,6) (.58,-1.42) --node[above]{3} (0,-2);
- \draw[red] (2,0) circle(2);
- \draw (2,0) circle(2pt)[fill=white];
- \draw[->] (0,-3) circle(2pt)[fill=black] edge (4,-3);
+ \draw[red] (2,0) circle(2); %circle
+ \draw (0,0) circle(2pt)[fill=black] (0,2) circle(2pt)[fill=black] (0,4) circle(2pt)[fill=black] (0,6) circle(2pt)[fill=black] (0,-2) circle(2pt)[fill=black] (1.1,1.78) circle(2pt)[fill=black] (3.42,1.42) circle(2pt)[fill=black] (.58,-1.42) circle(2pt)[fill=black] (0,1) circle(2pt)[fill=black]; %black vertices
+ \draw (2,0) -- node[above]{4} (0,0) (2,0) --node[above]{2} (1.1,1.78) --node[above]{1} (0,2) (1.1,1.78) --node[above]{1} (0,4) (2,0) --node[above]{1} (3.42,1.42) (2,0) --node[above]{3} (.58,-1.42) (3.42,1.42) --node[above]{5} (0,6) (.58,-1.42) --node[above]{1} (0,-2) (2,0) -- node[above]{2} (0,1); %edges
+ \draw (.58,-1.42) -- (5,-1.42) node[right]{1} (3.42,1.42) -- (5,1.42) node[right]{2} (2,0) -- (5,.5) node[right]{3} (2,0) -- (5,-.5) node[right]{7}; %markings
+ \draw (2,0) circle(2pt)[fill=white]; %core
+ \draw[->] (0,-3) circle(2pt)[fill=black] edge (5,-3); %trop(P^N|H)
  }
+
+ \caption{The degrees can be figured out from the balancing equation.}
 \end{figure}
-\begin{dfn}
+
+In the following we describe the rays of the tropical moduli space.
+\begin{lem}
  A degree-aligned genus one tropical map $\phi$ to $\mathbb R_{\geq 0}$ is ... with a circle of radius $\delta$ around the core satisfying:
  \begin{enumerate}
-  \item the circle of radius $\delta$ passes through at least one vertex of positive degree, and no vertex of positive degree is contained in its strict interior;
-  \item every circle of radius $<\delta$ around the core passes through (either none or) at least two vertices;\footnote{The subdivisions we perform before picking a ray correspond to aligning the log structure, i.e.
-imposing $\lambda(v)=\lambda(v^\prime)$ for some $v,v^\prime$.}
-  \item every edge heading out of the circle of radius $\delta$ goes directly to a vertex in $\phi^{-1}(0)$.
+ \item the circle of radius $\delta$ passes through at least one vertex of $\phi^{-1}(0)$ - which necessarily has positive degree - call $m$ its contact order with $H$;
+ \item teeth may break only when they intersect the circle of radius $\delta$; in particular, $\circ$ is the only vertex contained in its strict interior, and every edge heading out from the circle goes directly to a vertex of $\phi^{-1}(0)$;
+ \item every tooth that starts with contact order $m$ goes directly to a vertex of $\operatorname{circle}(\circ,\delta)\cap\phi^{-1}(0)$, and every other tooth starts with contact order $<m$ (possibly negative).
  \end{enumerate}
-\end{dfn}
+\end{lem}
+\begin{proof}
+ Otherwise there would be more than one parameters.
+\end{proof}
 
@@
 
+ Assume \footnote{(Luca) copied and pasted from my thesis} we want to compute $\langle\tau_{h_1}H^{k_1},\ldots,\tau_{h_1}H^{k_1}\rangle^{\PP^{N-1},\rm{red}}_{1,n,d}$ by writing it as $\frac{1}{d^2}(\psi_1^{\{n+1\}})^{h_1}H^{k_1}\cdots(\psi_n^{\{n+1\}})^{h_n}H^{k_n}\cdot[\VZ{(0,\ldots,0,d)}{\PP^N|H}{d}^\thicksim]$.
+Let me start from the recursion step $H_1\cdot[\VZ{(0,\ldots,0,d)}{\PP^N|H}{d}]=\ldots:$
+
+ \begin{description}
+  \item[$\mathcal Y_a$:] $d\ {\tikz[baseline=-3pt,scale=.7]{
+\draw (2,0) node[above]{$\{x_1,x_{n+1}\}$} -- (0,0)node[below]{$d$};
+\draw (2,0) circle(2pt)[fill=black];
+\draw (0,0) circle(2pt)[fill=white];
+\draw (-1,1.5) -- (1,1.5) -- (1,-1.5) -- (-1,-1.5) -- (-1,1.5);
+\draw (1,1.5) -- (3,2) -- (3,-1) -- (1,-1.5);
+}}$ contributes $\frac{1}{d}\psi_1^{h_1}H^{k_1}\cdots\psi_n^{h_n}H^{k_n}\cdot[\VZ{(d,\ldots,0)}{\PP^N|H}{d}]$; if this is the curve configuration, while there is any other marking at level one, then $\fgt_{n+1}$ has positive dimensional fibers; otherwise there must be another component of positive horizontal degree (these contributions are computed inductively on $d$);
+\item[$\mathcal Y_b$:] is an entirely rational story;
+\item[$\mathcal Y_c$:] {\tikz[baseline=-3pt,scale=.7]{
+\draw (2,0) node[above]{$\{x_1,\ldots,x_{n+1}\}$} node[below]{$d$};
+\draw (2,0) circle(2pt)[fill=white];
+\draw (-1,1.5) -- (1,1.5) -- (1,-1.5) -- (-1,-1.5) -- (-1,1.5);
+\draw (1,1.5) -- (3,2) -- (3,-1) -- (1,-1.5);
+}} is the term we are meant to compute, while all other terms will include a DRC integral of lower degree.
+ \end{description}
+I shall look one step further into the recursion for computing $[\VZ{(0,\ldots,0,d)}{\PP^N|H}{d}]$: in order to do so consider the formula for $((d-1)\psi_{n+1}+H_{n+1})\cdot[\VZ{(0,\ldots,0,d-1,1)}{\PP^N|H}{d}]$.
+This produces:
+\begin{description}
+  \item[$\mathcal Y_a$:] $d\ {\tikz[baseline=-3pt,scale=.7]{
+\draw (2,0) node[above]{$\{x_{n+1},x_{n+2}\}$} -- (0,0)node[below]{$d$};
+\draw (2,0) circle(2pt)[fill=black];
+\draw (0,0) circle(2pt)[fill=white];
+\draw (-1,1.5) -- (1,1.5) -- (1,-1.5) -- (-1,-1.5) -- (-1,1.5);
+\draw (1,1.5) -- (3,2) -- (3,-1) -- (1,-1.5);
+}}$ this is the one we are after; while
+$(d-1){\tikz[baseline=-3pt,scale=.7]{
+\draw (2,.5) node[above]{$\{x_{k},x_{n+1}\}$} -- (0,0)node[below]{$d$};
+\draw (2,-.5) node[above]{$\{x_{n+2}\}$} -- (0,0);
+\draw (2,.5) circle(2pt)[fill=black];
+\draw (2,-.5) circle(2pt)[fill=black];
+\draw (0,0) circle(2pt)[fill=white];
+\draw (-1,1.5) -- (1,1.5) -- (1,-1.5) -- (-1,-1.5) -- (-1,1.5);
+\draw (1,1.5) -- (3,2) -- (3,-1) -- (1,-1.5);
+}}$ gives a lower tangency condition $[\VZ{(0,\ldots,d-1,\ldots,0)}{\PP^N|H}{d}]$; and all other terms have lower degree.
+\item[$\mathcal Y_c$:] {\tikz[baseline=-3pt,scale=.7]{
+\draw (2,0) node[above]{$\{x_1,\ldots,x_{n+1},x_{n+2}\}$} node[below]{$d$};
+\draw (2,0) circle(2pt)[fill=white];
+\draw (-1,1.5) -- (1,1.5) -- (1,-1.5) -- (-1,-1.5) -- (-1,1.5);
+\draw (1,1.5) -- (3,2) -- (3,-1) -- (1,-1.5);
+}} has positive dimensional fibers for $\fgt_{n+1,n+2}$, and all other terms have lower degree.
+ \end{description}
+ Finally, let me look one step further into the reduction of $[\VZ{(d,\ldots,0)}{\PP^N|H}{d}]$: we have $((d-1)\psi_1^{\{n+1\}}+H_1)\cdot[\VZ{(d-1,\ldots,0,1)}{\PP^N|H}{d}]=\ldots:$
+ \begin{description}
+  \item[$\mathcal Y_a$:] $d\ {\tikz[baseline=-3pt,scale=.7]{
+\draw (2,0) node[above]{$\{x_{1},x_{n+1}\}$} -- (0,0)node[below]{$d$};
+\draw (2,0) circle(2pt)[fill=black];
+\draw (0,0) circle(2pt)[fill=white];
+\draw (-1,1.5) -- (1,1.5) -- (1,-1.5) -- (-1,-1.5) -- (-1,1.5);
+\draw (1,1.5) -- (3,2) -- (3,-1) -- (1,-1.5);
+}}$ is the one we care about;
+$(d-1)\ {\tikz[baseline=-3pt,scale=.7]{
+\draw (2,.5) node[above]{$\{x_{k},x_{1}\}$} -- (0,0)node[below]{$d$};
+\draw (2,-.5) node[above]{$\{x_{n+1}\}$} -- (0,0);
+\draw (2,.5) circle(2pt)[fill=black];
+\draw (2,-.5) circle(2pt)[fill=black];
+\draw (0,0) circle(2pt)[fill=white];
+\draw (-1,1.5) -- (1,1.5) -- (1,-1.5) -- (-1,-1.5) -- (-1,1.5);
+\draw (1,1.5) -- (3,2) -- (3,-1) -- (1,-1.5);
+}}$ has a lower number of markings (indeed $\psi_1^{\{n+1\}}$ and $\psi_k^{\{n+1\}}$ restrict to $0$ on this locus, and $\ev_1\equiv\ev_k$); while all other terms have lower degree.
+\item[$\mathcal Y_c$:] {\tikz[baseline=-3pt,scale=.7]{
+\draw (2,0) node[above]{$\{x_1,\ldots,x_{n+1}\}$} node[below]{$d$};
+\draw (2,0) circle(2pt)[fill=white];
+\draw (-1,1.5) -- (1,1.5) -- (1,-1.5) -- (-1,-1.5) -- (-1,1.5);
+\draw (1,1.5) -- (3,2) -- (3,-1) -- (1,-1.5);
+}} contributes $\frac{1}{d}\psi_1^{h_1}H^{k_1}\cdots\psi_n^{h_n}H^{k_n}\cdot[\VZ{(0,\ldots,0,d)}{\PP^N|H}{d}^\thicksim]$ so \emph{there is no cancellation}, while all other terms have lower degree.
+ \end{description}
+ To sum up, it is possible to determine the reduced genus one restricted invariants of $H$ in terms of those of $\PP^N$ and the genus zero theory, by induction on the degree, number of markings, and total tangency order.
+
 \bibliographystyle{alpha}

### 2019-01-29 GenusOneRelativeMaps.tex
Proof that punctured maps is birational to DRC locus

@@
 \newcommand{\stab}{\rm{stab}}
+\newcommand{\st}{\star}
 \newcommand{\stC}{C'}
@@
 \newcommand{\Dcal}{\mathcal{D}}
+\newcommand{\Ncal}{\mathcal{N}}
+\newcommand{\Pcal}{\mathcal{P}}
 \newcommand{\Ycal}{\mathcal{Y}}
 \newcommand{\ol}[1]{\overline{#1}}
+\newcommand{\ul}[1]{\underline{#1}}
 \newcommand{\op}[1]{\operatorname{#1}}
@@
 In \cite{PuncturedMaps}, a recursive description of the logarithmic strata of $\Mcal$ is given, in terms of moduli spaces of punctured maps.
-As discussed above, the logarithmic strata of $\Mcal$ are indexed by combinatorial types of tropical curves.
-Given such a combinatorial type, each vertex of the associated graph defines a moduli space of punctured stable maps.
-This has a degree and genus given by the degree and genus of the vertex, and a target space given by the logarithmic stratum corresponding to the tropical stratum into which the vertex is mapped.
-It has marked points indexed by the edges and flags adjacent to that vertex, and these marked points have tangencies (which may be positive or negative) depending on the expansion factors of the associated edges and flags.
-If all of the tangencies are positive, then a punctured map is the same thing as a log stable map.
-
-In our setting, when dealing with truly punctured maps, the associated logarithmic stratum of the target will always be the divisor $H$. Consider a moduli space
+As discussed above, the logarithmic strata $\Scal$ of $\Mcal$ are indexed by combinatorial types of tropical curves.
+Given such a combinatorial type $\Delta$, each vertex $v$ of the associated graph defines a moduli space of punctured stable maps:
+\begin{equation*} \ol\Mcal_v = \Mpunct{g(v)}{\alpha(v)}{Z_v}{d_v}. \end{equation*}
+Here $g(v)$ and $d(v)$ are the genus and degree assigned to the vertex, while $Z_v$ is the logarithmic stratum of the target corresponding to the tropical stratum into which the vertex is mapped by the combinatorial type (in our setting, $Z_v=\PP^N$ or $H$).
+The length of the vector $\alpha(v)$ is given by the number of edges and flags adjacent to $v$, and the entries (which represent tangencies, and may be positive or negative) are given by the expansion factors along those edges and flags.
+Note that if all of the tangencies are positive, then this is nothing but an ordinary moduli space of log stable maps.
+The corresponding logarithmic stratum is then obtained as a fibre product over evaluation maps:
+\bcd
+\Scal \ar[r] \ar[d] \ar[rd,phantom,"\square"] & \prod_v \ol\Mcal_v \ar[d] \\
+\prod_{e} Z_e \ar[r] & \prod_{e} Z_e\times Z_e.
+\ecd
+This fibre product must be take in the fs log category.
+However, in our setting, the ordinary fibre product is automatically integral\footnote{(Navid) Justify this}, so all that is required is a saturation.
+This means that the fs fibre product is just a finite cover of the ordinary fibre product, and we may calculate the degree directly.\footnote{(Navid) How, again?}
+
+\subsection{Punctured maps and double ramification loci} We will now present some arguments and constructions aimed at demystifying the moduli spaces of punctured stable maps.
+In our context, we only ever encounter these spaces when the associated logarithmic stratum $Z_v$ of the target is the divisor $H$.
+Consider therefore a moduli space of punctured stable maps
 \begin{equation*} \Mpunct{g}{\alpha}{H}{d} \end{equation*}
-where $g \in \{0,1\}$ and $\alpha$ is a vector of tangency orders, some of which are negative.
-Here $H$ is given the log structure pulled back from $\PP^N$; since $H$ is not log smooth, the natural obstruction theory on the above moduli space is not necessarily perfect.
-On the other hand, we will see that this space is birational to the moduli space
+where $g \in \{0,1\}$ and $\alpha$ is a vector of tangency orders.
+The target $H$ is given the log structure pulled back from $\PP^N$, and consequently is not log smooth.
+As such, the natural obstruction theory on the above moduli space will not, in general, be perfect.
+This is not really a problem for us, since we are interested in studying the ``non-virtual'' geometry of our moduli spaces.
+
+We will see that this space is birational to the moduli space of ordinary stable maps to $H$ satisfying the condition:
+\begin{equation*} f^*[H] - \sum_{i=1}^n \alpha_ix_i =0 \in \Achow_0(C).\end{equation*}
+This forms a closed substack
 \begin{equation*} \ol\Mcal^{\alpha}_{g,n}(H,d) \subseteq \M{g}{n}{H}{d} \end{equation*}
-of ordinary stable maps to $H$ satisfying the condition:
-\begin{equation*} f^*\OO_H(1) \cong \OO_C(\Sigma_i \alpha_ix_i).\end{equation*}
-This is referred to as the \emph{double ramification locus} and has been studied extensively.
-It is a closed substack of virtual codimension $g$ in $\M{g}{n}{H}{d}$.
-In the genus zero case it is equal to the entire space
+referred to as the \emph{double ramification locus}.
+It has been studied in great detail in the past.
+It is a closed substack of virtual codimension $g$ in $\M{g}{n}{H}{d}$ (though, as with $\M{g}{n}{H}{d}$ itself, it typically has excess dimension).
+
+\begin{prop} Consider the forgetful morphism:
+\begin{equation*} \Mpunct{g}{\alpha}{H}{d} \to \M{g}{n}{H}{d}. \end{equation*}
+This factors through the double ramification locus, and is in fact birational onto its image.\end{prop}
+\begin{proof} The fact that the forgetful morphism factors through the double ramification locus is an immediate consequence of the balancing condition satisfied by punctured stable maps, interpreted as a condition in the Picard group of $C$.
+So we indeed have a map:
+\begin{equation*} \Mpunct{g}{\alpha}{H}{d} \xrightarrow{\varphi} \ol\Mcal^\alpha_{g,n}(H,d). \end{equation*}
+To show that $\varphi$ is birational, we will show that it induces a bijection on geometric points when restricted to an open dense locus.
+This locus will be taken to be the preimage of the locus in $\ol\Mcal^\alpha_{g,n}(H,d)$ consisting of curves of compact type (i.e.
+those whose dual graph has genus zero).
+Essentially here we are excluding stable maps whose source curve countains a cycle of $\PP^1$s.
+The fact that this is open dense in $\ol\Mcal^\alpha_{g,n}(H,d)$ is not hard to see: when $g=0$ the double ramification locus is equal to $\M{0}{n}{H}{d}$ which is smooth, and the locus of stable maps not of compact type is codimension $2$.
+When $g=1$ the double ramification locus has many components, but on every such component the maximal genus one subcurve of the source is generically smooth, which shows again that the locus of stable maps not of compact type is closed.
+
+So let us start with a compact type stable map which belongs to the double ramification locus:
+\bcd
+C \ar[r,"f"] \ar[d] & H \\
+S=\Spec\kfield
+\ecd
+We will show that there exists a unique lift of this to a punctured stable map.
+Since $C$ has compact type, there is a unique choice of associated combinatorial type $\Delta$.
+This determines a minimal monoid $Q$ such that any punctured map enhancing the given stable map has base log structure given by:
+\begin{align*}
+Q \oplus \kfield^\st & \to \kfield \\
+(q,\lambda) & \mapsto \begin{cases} \lambda \qquad \text{if } q =0 \\ 0 \qquad \text{otherwise} \end{cases}
+\end{align*}
+If we let $r$ denote the number of nodes of $C$ then there is a natural map $\N^r \to Q$ and by the universal property of minimality the punctured curve must be obtained by puncturing a log smooth curve pulled back along a log map
+\begin{equation*} (\Spec\kfield,Q \oplus \kfield^\st) \to (\Spec\kfield,\N^r\oplus\kfield^\st)\end{equation*}
+enhancing the given map $\N^r \to Q$ on the level of ghost sheaves.
+There is a $\Gm^r$ of moduli for such maps, but all these choices are canceled out by automorphisms of $(\Spec\kfield,Q\oplus\kfield^\st)$\footnote{(Navid) Here we are using the fact that $Q$ is in some sense bigger than $\N^r$.}.
+Therefore we obtain a unique log smooth curve:
+\begin{equation*} (C,\Mcal_C) \to (\Spec\kfield,Q\oplus\kfield^\st).\end{equation*}
+We must now construct the puncturing $\Mcal_{C^\circ}$.
+Let $\Pcal_C$ denote the divisorial log structure on $C$ with respect to the punctures.
+Then there is a unique log structure $\Mcal$ on $C$ such that
+\begin{equation*} \Mcal_C = \Mcal \oplus_{\OO_C^\st} \Pcal_C \end{equation*}
+where the pushout is taken in the category of monoid sheaves. We consider the sheaf:
+\begin{equation*} \Ncal_C = \Mcal \oplus_{\OO_C^\st} \Pcal^{\gp}_C. \end{equation*}
+By definition the puncturing $\Mcal_{C^\circ}$ should be an intermediate sheaf:
+\begin{equation*} \Mcal_C \subseteq \Mcal_{C^\circ} \subseteq \Ncal_C. \end{equation*}
+We will now construct this, whilst arguing that our construction gives the only puncturing possible.
+First we note that it is sufficient to define $\Mcal_{C^\circ}$ on a base for the topology on $C$.
+We choose a base such that for every base open set $U$:
+\begin{enumerate}
+\item $U$ contains at most one of the punctures of $C$;
+\item if $U$ contains a puncture $p \in C$, then $U$ does not contain any of the nodes or markings of $C$, and $\OO_C(p)|_U$ is trivial.
+\end{enumerate}
+Note that these properties are stable under taking subsets, so to obtain such a base we simply choose an open cover with this property (which is certainly possible) and then consider the collection of all open subsets of our chosen cover.
+
+Now let $U$ be such a base open set. If $U$ does not contain a puncture then we set
+\begin{equation*} \Mcal_{C^\circ}(U) = \Mcal_C(U).\end{equation*}
+If $U$ contains a puncture $p$ then by assumption $U \setminus \{ p\}$ consists of smooth, unmarked points, and hence we have
+\begin{equation*} \Ncal_C|_U = \left( \pi^\st \Mcal_S|_U \right) \oplus_{\OO_U^\st} \left(\Pcal_p^{\gp}|_U \right) \end{equation*}
+where $\Pcal_p$ is the divisorial log structure with respect to $p$. Now, we have $\Mcal_S = Q \oplus \kfield^\st$ from which it follows that:
+\begin{equation*} \pi^*\Mcal_S|_U = \ul{Q} \oplus \OO_U^\st.\end{equation*}
+Thus we see that
+\begin{equation*} \Ncal_C|_U = \ul{Q} \oplus \Pcal_p^{\gp}|_U\end{equation*}
+and similarly:
+\begin{equation*} \Mcal_C|_U = \ul{Q} \oplus \Pcal_p|_U.\end{equation*}
+We therefore have:
+\begin{equation*} \Ncal_C(U) = Q \oplus \Pcal_p^{\gp}(U) \end{equation*}
+Recall we are assuming that $\OO_C(p)|_U$ is trivial.
+Choosing a trivialisation, we obtain a function $s \in \OO_U(U)$ such that $p=\{s=0\}$.
+Then $\Pcal_p(U)$ consists of functions of the form $\lambda \cdot s^n$ for $n \in \N$ and $\lambda \in \OO_U^\st(U)$.
+Groupifying, we obtain:
+\begin{equation*} \Pcal^{\gp}_p(U) = \left\{ \lambda \cdot s^k \, \vert \, \lambda \in \OO_U^\st(U), k \in \Z \right\} \end{equation*}
+Recall that $p$ has attached to it a tangency order $\alpha_p \in \Z_{<0}$.
+If we let $\eta$ denote the generic point of the component of $C$ containing $p$, then we also have a pullback map $\ol\varphi_\eta \colon \N \to Q$.
+
+We define $\Mcal_{C^\circ}(U) \subseteq \Ncal_C(U)$ to be the submonoid generated by $Q \oplus \Pcal_p(U)$ and:
+\begin{equation*} (\ol\varphi_\eta(1),s^{\alpha_p}). \end{equation*}
+This clearly satisfies the condition to be a puncturing. Moreover, by the prestability condition for puncturings, this is the only possibility for $\Mcal_{C^\circ}$. We thus have a punctured curve:
+\begin{equation*} (C,\Mcal_{C^\circ}) \xrightarrow{\pi} (\Spec\kfield,Q\oplus\kfield^\st). \end{equation*}
+(Note that the log enhancement of $\pi$ comes for free by taking the composition $\pi^\st \Mcal_S \to \Mcal_C \to \Mcal_{C^\circ}$.) It remains to construct the log enhancement of the map $f \colon C \to H$.
+The map $f^\flat \colon f^\st \Mcal_H \to \Mcal_{C^\circ}$ is already determined on the level of ghost sheaves.
+To enhance this to a map on the level of log structures entails choosing an isomorphism of line bundles:
+\begin{equation*} f^* \OO_H(1) \cong \OO_C\left(\ol{f}^\flat(1)\right). \end{equation*}
+The component-wise description of the right-hand side in \cite{RSPW} (together with the fact that $C$ is compact type, so its Picard group is just the product of the Picard groups of its components) shows that such an isomorphism exists if and only if the original stable map is in the double ramification locus.
+
+There is a $\Gm$ of choices for such a map, but these are canceled out by the automorphisms of $(C,\Mcal_{C^\circ})$ induced by pulling back along (strict) automorphisms of $(\Spec\kfield,Q\oplus\kfield^\st)$.
+This completes the proof of unique punctured lifting.
+\end{proof}
+
+\subsection{Geometry of double ramification loci and their desingularisations} Thus, the spaces of punctured maps we encounter are always birational to double ramification loci.
+We will now discuss the geometry of these loci.
+In the genus zero case, the double ramification locus is equal to the entire space
 \begin{equation*} \ol\Mcal^{\alpha}_{0,n}(H,d) = \M{0}{n}{H}{d} \end{equation*}
-which is smooth.
-Thus integrals over $\Mpunct{0}{\alpha}{H}{d}$ are the same as integrals over $\M{0}{n}{H}{d}$.
-The genus one case is more delicate; yet, luckily, we are only interested in the main component of the punctured space.
+which is smooth. Thus integrals over $\Mpunct{0}{\alpha}{H}{d}$ are the same thing as integrals over $\M{0}{n}{H}{d}$.
+
+The genus one case is more delicate: there is a ``main component'' of the double ramification locus, obtained as the closure of the locus where the source curve is smooth.
+This forms a divisor inside the main component of the moduli space of stable maps:
+%\begin{equation*} \M
+
+Fortunately, we
+are only interested in the main component of the punctured space. As we did in \S \ref{}, we may define a logarithmic modification of
+$\Mpunct{1}{\alpha}{H}{d}$ by imposing an alignment and factorisation condition.
 

### 2019-01-29 GenusOneRelativeMaps.tex
More changes to section on DRC

@@
 \end{align*}
-If we let $r$ denote the number of nodes of $C$ then there is a natural map $\N^r \to Q$ and by the universal property of minimality the punctured curve must be obtained by puncturing a log smooth curve pulled back along a log map
-\begin{equation*} (\Spec\kfield,Q \oplus \kfield^\st) \to (\Spec\kfield,\N^r\oplus\kfield^\st)\end{equation*}
-enhancing the given map $\N^r \to Q$ on the level of ghost sheaves.
-There is a $\Gm^r$ of moduli for such maps, but all these choices are canceled out by automorphisms of $(\Spec\kfield,Q\oplus\kfield^\st)$\footnote{(Navid) Here we are using the fact that $Q$ is in some sense bigger than $\N^r$.}.
-Therefore we obtain a unique log smooth curve:
+If we let $r$ denote the number of nodes of $C$ then by construction there is a natural map $\N^r \to Q$ and by the universal property of minimality our punctured curve must be obtained by puncturing a log smooth curve pulled back along a log map
+\begin{equation*} (\Spec\kfield,Q \oplus \kfield^\st) \to (\Spec\kfield,\N^r\oplus\kfield^\st).\end{equation*}
+This log map must enhance the given map $\N^r \to Q$ on the level of ghost sheaves.
+The moduli for such a log map is $\Gm^r$, but all these choices are canceled out by automorphisms of $(\Spec\kfield,Q\oplus\kfield^\st)$\footnote{(Navid) Here we are using the fact that $Q$ is in some sense bigger than $\N^r$.}.
+Thus we obtain, by pulling back the minimal log smooth curve over $(\Spec\kfield,\N^r \oplus\kfield^\st)$, a unique log smooth curve:
 \begin{equation*} (C,\Mcal_C) \to (\Spec\kfield,Q\oplus\kfield^\st).\end{equation*}
@@
 Let $\Pcal_C$ denote the divisorial log structure on $C$ with respect to the punctures.
-Then there is a unique log structure $\Mcal$ on $C$ such that
+It is easy to see that there is a unique log structure $\Mcal$ on $C$ such that
 \begin{equation*} \Mcal_C = \Mcal \oplus_{\OO_C^\st} \Pcal_C \end{equation*}
@@
 \begin{equation*} \Mcal_C \subseteq \Mcal_{C^\circ} \subseteq \Ncal_C. \end{equation*}
-We will now construct this, whilst arguing that our construction gives the only puncturing possible.
+We will now construct this, and argue that our construction gives the only puncturing possible.
 First we note that it is sufficient to define $\Mcal_{C^\circ}$ on a base for the topology on $C$.
@@
 \begin{enumerate}
+\item $U$ is connected;
 \item $U$ contains at most one of the punctures of $C$;
@@
 \end{enumerate}
-Note that these properties are stable under taking subsets, so to obtain such a base we simply choose an open cover with this property (which is certainly possible) and then consider the collection of all open subsets of our chosen cover.
-
-Now let $U$ be such a base open set. If $U$ does not contain a puncture then we set
+Note that these properties are stable under taking subsets, so to obtain such a base we simply choose an open cover with this property (which is certainly possible) and then take the collection of all open subsets of our chosen cover.
+
+Now let $U$ be such an open set in our base. If $U$ does not contain a puncture then we set
 \begin{equation*} \Mcal_{C^\circ}(U) = \Mcal_C(U).\end{equation*}
-If $U$ contains a puncture $p$ then by assumption $U \setminus \{ p\}$ consists of smooth, unmarked points, and hence we have
+If $U$ contains a puncture $p$ then by assumption $U \setminus \{ p\}$ contains only smooth unmarked points, and hence we have
 \begin{equation*} \Ncal_C|_U = \left( \pi^\st \Mcal_S|_U \right) \oplus_{\OO_U^\st} \left(\Pcal_p^{\gp}|_U \right) \end{equation*}
-where $\Pcal_p$ is the divisorial log structure with respect to $p$. Now, we have $\Mcal_S = Q \oplus \kfield^\st$ from which it follows that:
-\begin{equation*} \pi^*\Mcal_S|_U = \ul{Q} \oplus \OO_U^\st.\end{equation*}
-Thus we see that
+where $\Pcal_p$ is the divisorial log structure with respect to $p$. Since $\Mcal_S = Q \oplus \kfield^\st$ it follows that $\pi^*\Mcal_S|_U = \ul{Q} \oplus \OO_U^\st$. Thus we see that
 \begin{equation*} \Ncal_C|_U = \ul{Q} \oplus \Pcal_p^{\gp}|_U\end{equation*}
@@
 \begin{equation*} \Pcal^{\gp}_p(U) = \left\{ \lambda \cdot s^k \, \vert \, \lambda \in \OO_U^\st(U), k \in \Z \right\} \end{equation*}
-Recall that $p$ has attached to it a tangency order $\alpha_p \in \Z_{<0}$.
+(Indeed $\Pcal_p^{\gp}$ may be described as the sheaf of rational functions which are regular and invertible outside of $p$.) Recall that $p$ has attached to it a tangency order $\alpha_p \in \Z_{<0}$.
 If we let $\eta$ denote the generic point of the component of $C$ containing $p$, then we also have a pullback map $\ol\varphi_\eta \colon \N \to Q$.
-
 We define $\Mcal_{C^\circ}(U) \subseteq \Ncal_C(U)$ to be the submonoid generated by $Q \oplus \Pcal_p(U)$ and:
@@
 \begin{equation*} (C,\Mcal_{C^\circ}) \xrightarrow{\pi} (\Spec\kfield,Q\oplus\kfield^\st). \end{equation*}
-(Note that the log enhancement of $\pi$ comes for free by taking the composition $\pi^\st \Mcal_S \to \Mcal_C \to \Mcal_{C^\circ}$.) It remains to construct the log enhancement of the map $f \colon C \to H$.
+(Note that the log enhancement of $\pi$ is uniquely determined by taking the composition $\pi^\st \Mcal_S \to \Mcal_C \to \Mcal_{C^\circ}$.) It remains to construct the log enhancement of the map $f \colon C \to H$.
 The map $f^\flat \colon f^\st \Mcal_H \to \Mcal_{C^\circ}$ is already determined on the level of ghost sheaves.
@@
 \begin{equation*} \ol\Mcal^{\alpha}_{0,n}(H,d) = \M{0}{n}{H}{d} \end{equation*}
-which is smooth. Thus integrals over $\Mpunct{0}{\alpha}{H}{d}$ are the same thing as integrals over $\M{0}{n}{H}{d}$.
+which is smooth. Thus tautological integrals over $\ol\Mcal^{\alpha}_{0,n}(H,d)$ are determined by the genus-zero Gromov--Witten theory of $H$.
 
@@
 This forms a divisor inside the main component of the moduli space of stable maps:
-%\begin{equation*} \M
-
-Fortunately, we
-are only interested in the main component of the punctured space. As we did in \S \ref{}, we may define a logarithmic modification of
-$\Mpunct{1}{\alpha}{H}{d}$ by imposing an alignment and factorisation condition.
-
-\begin{lem}
-Alignment and factorisation single out the closure of the locus of punctured maps with smooth source curve.
-\end{lem}
+\begin{equation*} \ol\Mcal^{\alpha,\circ}_{1,n}(H,d) \subseteq \ol\Mcal^\circ_{1,n}(H,d). \end{equation*}
+However, we know that $\M{1}{n}{H}{d}$ contains many other components besides $\ol\Mcal^\circ_{1,n}(H,d)$, some of which have excess dimension.
+Certainly the double ramification locus intersects these other components, and sometimes it does so in quite dramatic fashion.
+For instance, consider the locus where the source curve splits into a contracted elliptic component and a rational component containing all the markings.
+This locus forms an irreducible component of the moduli space, isomorphic to
+\begin{equation*}\ol\Mcal_{1,1} \times \M{0}{n+1}{H}{d} \end{equation*}
+which has excess dimension $N-2$. This entire component belongs to the double ramification locus, since the intersection-theoretic condition is entirely numerical here.
+
+Thus we see that the double ramification locus can be quite badly-behaved in genus one.
+Fortunately, we will only be interested in the main component of the punctured space (which is birational to the main component of the double ramification locus).
+As we did in \S \ref{}, we may produce a logarithmic modification
+\begin{equation*} \widetilde{\VZ}^{\operatorname{punct}}_{1,\alpha}(H,d) \to \Mpunct{1}{\alpha}{H}{d} \end{equation*}
+by requiring our maps to be centrally aligned. We may then define a closed substack
+\begin{equation*} \VZ^{\operatorname{punct}}_{1,\alpha}(H,d) \subseteq \widetilde{\VZ}^{\operatorname{punct}}_{1,\alpha}(H,d) \end{equation*}
+by imposing a factorisation condition. These moduli spaces will appear in our recursive description of the boundary of $\VZ$ given later in this section.
+\begin{lem} This process produces a birational modification
+\begin{equation*}\VZ^{\operatorname{punct}}_{1,\alpha}(H,d) \to \ol\Mcal^{\operatorname{punct},\circ}_{1,\alpha}(H,d)\end{equation*}
+of the main component of the moduli space of punctured maps (which, in turn, is birational to the main component of the double ramification locus).\end{lem}
 \begin{proof}
@@
 
-\begin{lem}
-The main component of punctured maps is birational to the main component of the DR locus.
-\end{lem}
-We probably want the latter statement to hold under imposing alignment and factorisation (keeping the log structure on the source curve, but forgetting that the map is log).
-
-\begin{lem}
- Forgetting a marking $\fgt_i\colon\ol\Mcal_{1,n}^\alpha(H,d)^{\rm{main}} \to\VZ_{1,n-1}(H,d)$ is generically finite of degree $\alpha_i^2$ - except in one case.
+%We probably want the latter statement to hold under imposing alignment and factorisation (keeping the log structure on the source curve, but forgetting that the map is log).
+Integrals over the main component of the double ramification locus can be computed using the following lemma.
+\begin{lem} The morphism which forgets a marking
+\begin{equation*} \fgt_i\colon\ol\Mcal_{1,n}^{\alpha,\circ}(H,d)\to\ol\Mcal^{\circ}_{1,n-1}(H,d)\end{equation*}
+is generically finite, of degree $\alpha_i^2$ (except in one special case, described in the proof).
 \end{lem}
@@
 To be more precise: its elements consist of punctured maps to $H$ which are aligned in the sense of Definition \ref{}, and satisfy the (double) factorisation condition (simply replace $\PP^N$ by $H$ everywhere in that definition).
-
-\begin{prop} $\VZ^{\operatorname{punct}}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(H,d_0)$ is irreducible of the expected dimension, and birational to the main component of the double ramification locus:
-\begin{equation*} \ol{\Mcal}_{1,n_0+r}^{\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(H,d_0) \subseteq \ol{\Mcal}_{1,n_0+r}(H,d_0) \end{equation*}\end{prop}
-
-Now, the double ramification locus carries a natural virtual class, and one can write
-\begin{equation*} \virt{\ol{\Mcal}_{1,n_0+r}^{\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(H,d_0)} = \gamma \cap \virt{\ol{\Mcal}_{1,n_0+r}(H,d_0)} \end{equation*}
-where $\gamma \in \Achow^1(\M{1}{n}{H}{d})$ is some explicit sum of tautological classes \cite{DRCBundle}.
-To identify the class of the main component, we split the virtual class of the double ramification locus as
-\begin{equation*} \virt{\ol\Mcal^{\alpha}_{1,n}(H,d)} = [\ol\Mcal^{\alpha,\text{main}}_{1,n}(H,d)] + \sum_{\Gamma} \virt{\ol\Mcal^{\alpha,\Gamma}_{1,n}(H,d)} \end{equation*}
-and this allows us to write
-\begin{equation*} [\ol\Mcal^{\alpha,\text{main}}_{1,n}(H,d)] = \gamma^\prime \cap [\ol\Mcal^{\text{main}}_{1,n}(H,d)]\end{equation*}
-where $\gamma^\prime$ is some other sum of tautological classes.
-This makes integrals over $\VZ^{\operatorname{punct}}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(H,d_0)$ computable in terms of the reduced Gromov--Witten theory of $H\cong\PP^{N-1}$.
 

### 2019-01-29 GenusOneRelativeMaps.tex
Restructured section 4 a bit. C+ description starting to look OK

@@
 
-\subsection{Geometry of double ramification loci and their desingularisations} Thus, the spaces of punctured maps we encounter are always birational to double ramification loci.
+Thus, the spaces of punctured maps we encounter are always birational to double ramification loci.
 We will now discuss the geometry of these loci.
@@
 Thus we see that the double ramification locus can be quite badly-behaved in genus one.
-Fortunately, we will only be interested in the main component of the punctured space (which is birational to the main component of the double ramification locus).
-As we did in \S \ref{}, we may produce a logarithmic modification
-\begin{equation*} \widetilde{\VZ}^{\operatorname{punct}}_{1,\alpha}(H,d) \to \Mpunct{1}{\alpha}{H}{d} \end{equation*}
-by requiring our maps to be centrally aligned. We may then define a closed substack
-\begin{equation*} \VZ^{\operatorname{punct}}_{1,\alpha}(H,d) \subseteq \widetilde{\VZ}^{\operatorname{punct}}_{1,\alpha}(H,d) \end{equation*}
-by imposing a factorisation condition. These moduli spaces will appear in our recursive description of the boundary of $\VZ$ given later in this section.
-\begin{lem} This process produces a birational modification
-\begin{equation*}\VZ^{\operatorname{punct}}_{1,\alpha}(H,d) \to \ol\Mcal^{\operatorname{punct},\circ}_{1,\alpha}(H,d)\end{equation*}
-of the main component of the moduli space of punctured maps (which, in turn, is birational to the main component of the double ramification locus).\end{lem}
-\begin{proof}
- If it is true, we might be able to prove it via deformation theory.
-For this it might be useful to notice that there is a morphism $\Mpunct{g}{\alpha}{H}{d}\to \Mpunct{g}{\alpha}{\PP^N}{d}$ (because $H\subseteq\PP^N$ is strict), which is probably a closed immersion, and the loci with smooth source curve are isomorphic under this map.
-It seems plausible that the main omponent is log smooth over $B\Gm\subseteq[\Aaff^1/\Gm]$ (or the standard log point).
-\end{proof}
-
-%We probably want the latter statement to hold under imposing alignment and factorisation (keeping the log structure on the source curve, but forgetting that the map is log).
-Integrals over the main component of the double ramification locus can be computed using the following lemma.
-\begin{lem} The morphism which forgets a marking
-\begin{equation*} \fgt_i\colon\ol\Mcal_{1,n}^{\alpha,\circ}(H,d)\to\ol\Mcal^{\circ}_{1,n-1}(H,d)\end{equation*}
-is generically finite, of degree $\alpha_i^2$ (except in one special case, described in the proof).
-\end{lem}
-\begin{proof}
- Let us consider the case $d=0$ first.
-We may assume the source curve is smooth elliptic $E$.
-The map \[ \phi\colon E\to \Pic^0(E),\qquad x\mapsto\OO_E\left(\alpha_ix+\sum_{j=1,\ldots,\hat i\ldots,n}\alpha_jp_j\right)\]
- is an isogeny of degree $\alpha_i^2$.
-The locus of $(C,p_1,\ldots,\hat{p_i},\ldots,p_n)$ such that the kernel of $\phi$ contains one of the points $\{p_1,\ldots,\hat{p_i},\ldots,p_n\}$ is itself a double ramification locus inside $\oM_{1,n}$, hence non-generic - with one exception: namely, when $n=2$, $x=p_1$ is always a solution, but the curve lying above such point bubbles off a $\PP^1$.
-To see that it does not belong to the closure of the nice locus, notice that the rational function trivialising $\OO_C(\alpha_1p_1-\alpha_2p_2)$ should descend to the cusp, thus having a ramification point at the node; yet its ramification profile is determined by Riemann-Hurwitz, and it is entirely supported on $p_1$ and $p_2$.
-
- For a different proof: notice that we should obtain the class of the main component from the full double ramification cycle by subtracting the boundary class $[D_{1,\emptyset|0,\{1,\ldots,n\}}]$.
-The latter pushes forward to $0$ under $\fgt_i$, unless $n=2$.
-Therefore we may apply $\fgt_{i,*}$ to the Hain-Pixton formula:
- \[DR_1(A)=\frac{1}{2}\left(\sum_{i=1}^na_i^2\psi_i-\sum_{\substack{I\subseteq\{1,\ldots,n\}\\|I|\geq 2}}a_I^2[D_{1,I^c|0,I}]-\frac{1}{12}\delta_0\right),\]
- where $a_I=\sum_{i\in I}a_i$ and $\delta_0=\operatorname{glue}_*([\oM_{0,n+2}])$.
-From $\psi_j=\fgt_i^*\psi_j+[D_{i,j}]$ for $i\neq j$, and the dilaton equation, we see that $\fgt_{i,*}\psi_j=1$ and $\fgt_{i,*}\psi_i=n-1$.
-On the other hand, the only surviving boundary classes are $[D_{i,j}]$, and they push down to $1$.
-Hence the formula pushes down to $\frac{1}{2}\left(\sum_{j\neq i}\alpha_j^2+(n-1)\alpha_i^2-\sum_{j\neq i}(\alpha_j+\alpha_i)^2\right)=-\alpha_i\left(\sum_{j\neq i}\alpha_j\right)=\alpha_i^2.$
-\end{proof}
+Fortunately, we will only be interested in the main component of this locus (which is birational to the main component of the moduli space of punctured maps); see \S \ref{} below.
 
@@
 To be more precise: its elements consist of punctured maps to $H$ which are aligned in the sense of Definition \ref{}, and satisfy the (double) factorisation condition (simply replace $\PP^N$ by $H$ everywhere in that definition).
+As in \S \ref{}, this construction produces a closed substack of a logarithmic modification
+\begin{equation*} \VZ^{\operatorname{punct}}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(H,d_0)\subseteq \widetilde{\VZ}^{\operatorname{punct}}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(H,d_0) \xrightarrow{\psi} \Mpunct{1}{\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}{H}{d_0} \end{equation*}
+
+\begin{lem} The logarithmic modification $\psi$ restricts to a birational map:
+\begin{equation*}\VZ^{\operatorname{punct}}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(H,d) \to \ol\Mcal^{\operatorname{punct},\circ}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(H,d).\end{equation*}
+\end{lem}
+Note that the latter space (the main component of the moduli space of punctured maps) is birational to the main component of the double ramification locus.
+In Lemma \ref{Lemma forget marking} below we explain how to compute integrals over this.
+\begin{proof}
+If it is true, we might be able to prove it via deformation theory.
+For this it might be useful to notice that there is a morphism $\Mpunct{g}{\alpha}{H}{d}\to \Mpunct{g}{\alpha}{\PP^N}{d}$ (because $H\subseteq\PP^N$ is strict), which is probably a closed immersion, and the loci with smooth source curve are isomorphic under this map.
+It seems plausible that the main omponent is log smooth over $B\Gm\subseteq[\Aaff^1/\Gm]$ (or the standard log point).
+\end{proof}
+
+%We probably want the latter statement to hold under imposing alignment and factorisation (keeping the log structure on the source curve, but forgetting that the map is log).
+Integrals over the main component of the double ramification locus can be computed using the following lemma.
+\begin{lem} \label{Lemma forget marking}The morphism which forgets a marking
+\begin{equation*} \fgt_i\colon\ol\Mcal_{1,n}^{\alpha,\circ}(H,d)\to\ol\Mcal^{\circ}_{1,n-1}(H,d)\end{equation*}
+is generically finite, of degree $\alpha_i^2$ (except in one special case, described in the proof).
+\end{lem}
+\begin{proof}
+ Let us consider the case $d=0$ first.
+We may assume the source curve is smooth elliptic $E$.
+The map \[ \phi\colon E\to \Pic^0(E),\qquad x\mapsto\OO_E\left(\alpha_ix+\sum_{j=1,\ldots,\hat i\ldots,n}\alpha_jp_j\right)\]
+ is an isogeny of degree $\alpha_i^2$.
+The locus of $(C,p_1,\ldots,\hat{p_i},\ldots,p_n)$ such that the kernel of $\phi$ contains one of the points $\{p_1,\ldots,\hat{p_i},\ldots,p_n\}$ is itself a double ramification locus inside $\oM_{1,n}$, hence non-generic - with one exception: namely, when $n=2$, $x=p_1$ is always a solution, but the curve lying above such point bubbles off a $\PP^1$.
+To see that it does not belong to the closure of the nice locus, notice that the rational function trivialising $\OO_C(\alpha_1p_1-\alpha_2p_2)$ should descend to the cusp, thus having a ramification point at the node; yet its ramification profile is determined by Riemann-Hurwitz, and it is entirely supported on $p_1$ and $p_2$.
+
+ For a different proof: notice that we should obtain the class of the main component from the full double ramification cycle by subtracting the boundary class $[D_{1,\emptyset|0,\{1,\ldots,n\}}]$.
+The latter pushes forward to $0$ under $\fgt_i$, unless $n=2$.
+Therefore we may apply $\fgt_{i,*}$ to the Hain-Pixton formula:
+ \[DR_1(A)=\frac{1}{2}\left(\sum_{i=1}^na_i^2\psi_i-\sum_{\substack{I\subseteq\{1,\ldots,n\}\\|I|\geq 2}}a_I^2[D_{1,I^c|0,I}]-\frac{1}{12}\delta_0\right),\]
+ where $a_I=\sum_{i\in I}a_i$ and $\delta_0=\operatorname{glue}_*([\oM_{0,n+2}])$.
+From $\psi_j=\fgt_i^*\psi_j+[D_{i,j}]$ for $i\neq j$, and the dilaton equation, we see that $\fgt_{i,*}\psi_j=1$ and $\fgt_{i,*}\psi_i=n-1$.
+On the other hand, the only surviving boundary classes are $[D_{i,j}]$, and they push down to $1$.
+Hence the formula pushes down to $\frac{1}{2}\left(\sum_{j\neq i}\alpha_j^2+(n-1)\alpha_i^2-\sum_{j\neq i}(\alpha_j+\alpha_i)^2\right)=-\alpha_i\left(\sum_{j\neq i}\alpha_j\right)=\alpha_i^2.$
+\end{proof}
 

### 2019-01-30 GenusOneRelativeMaps.tex
minor changes

@@
 
-\subsection{Punctured maps and double ramification loci} We will now present some arguments and constructions aimed at demystifying the moduli spaces of punctured stable maps.
+This gives a recursion description of the logarithmic strata in $\Mcal$.
+We will now\footnote{(Navid) Really, after the next section, which maybe we should move to an appendix} use this to obtain a similar (though somewhat more complicated) description of the strata in $\VZ$.
+
+\subsection{Punctured maps and double ramification loci}\footnote{(Navid) Move this to an appendix?} We will now present some arguments and constructions aimed at demystifying the moduli spaces of punctured stable maps.
 In our context, we only ever encounter these spaces when the associated logarithmic stratum $Z_v$ of the target is the divisor $H$.
 Consider therefore a moduli space of punctured stable maps
-\begin{equation*} \Mpunct{g}{\alpha}{H}{d} \end{equation*}
+\begin{equation}\label{punctured space} \Mpunct{g}{\alpha}{H}{d} \end{equation}
 where $g \in \{0,1\}$ and $\alpha$ is a vector of tangency orders.
@@
 As such, the natural obstruction theory on the above moduli space will not, in general, be perfect.
-This is not really a problem for us, since we are interested in studying the ``non-virtual'' geometry of our moduli spaces.
-
-We will see that this space is birational to the moduli space of ordinary stable maps to $H$ satisfying the condition:
-\begin{equation*} f^*[H] - \sum_{i=1}^n \alpha_ix_i =0 \in \Achow_0(C).\end{equation*}
-This forms a closed substack
+This is not really a problem for us, since we are mainly interested in studying the non-virtual geometry of our moduli spaces.
+Indeed, we will see that the space \eqref{punctured space} is birational to the moduli space of ordinary stable maps to $H$ satisfying the condition:
+\begin{equation}\label{DRC condition} f^*[H] - \sum_{i=1}^n \alpha_ix_i =0 \in \Achow_0(C).\end{equation}
+This space forms a closed substack
 \begin{equation*} \ol\Mcal^{\alpha}_{g,n}(H,d) \subseteq \M{g}{n}{H}{d} \end{equation*}
-referred to as the \emph{double ramification locus}.
-It has been studied in great detail in the past.
-It is a closed substack of virtual codimension $g$ in $\M{g}{n}{H}{d}$ (though, as with $\M{g}{n}{H}{d}$ itself, it typically has excess dimension).
-
-\begin{prop} Consider the forgetful morphism:
+and is referred to as the \emph{double ramification locus}.
+These moduli spaces have been the focus of intense study over the years (see, for instance, \cite{GathmannThesis} \cite{DRCBundle}).
+The double ramification locus is a closed substack of $\M{g}{n}{H}{d}$ of virtual codimension $g$ (though, as with $\M{g}{n}{H}{d}$ itself, it typically has excess dimension).
+
+\begin{prop} Suppose that $g \in \{0,1\}$ and consider the morphism forgetting all log structures:
 \begin{equation*} \Mpunct{g}{\alpha}{H}{d} \to \M{g}{n}{H}{d}. \end{equation*}
 This factors through the double ramification locus, and is in fact birational onto its image.\end{prop}
-\begin{proof} The fact that the forgetful morphism factors through the double ramification locus is an immediate consequence of the balancing condition satisfied by punctured stable maps, interpreted as a condition in the Picard group of $C$.
-So we indeed have a map:
-\begin{equation*} \Mpunct{g}{\alpha}{H}{d} \xrightarrow{\varphi} \ol\Mcal^\alpha_{g,n}(H,d). \end{equation*}
-To show that $\varphi$ is birational, we will show that it induces a bijection on geometric points when restricted to an open dense locus.
-This locus will be taken to be the preimage of the locus in $\ol\Mcal^\alpha_{g,n}(H,d)$ consisting of curves of compact type (i.e.
-those whose dual graph has genus zero).
-Essentially here we are excluding stable maps whose source curve countains a cycle of $\PP^1$s.
-The fact that this is open dense in $\ol\Mcal^\alpha_{g,n}(H,d)$ is not hard to see: when $g=0$ the double ramification locus is equal to $\M{0}{n}{H}{d}$ which is smooth, and the locus of stable maps not of compact type is codimension $2$.
-When $g=1$ the double ramification locus has many components, but on every such component the maximal genus one subcurve of the source is generically smooth, which shows again that the locus of stable maps not of compact type is closed.
-
-So let us start with a compact type stable map which belongs to the double ramification locus:
+\begin{proof} The fact that the forgetful morphism factors through the double ramification locus is an immediate consequence of the balancing condition satisfied by punctured stable maps, interpreted as a condition in $\Pic(C)$ (the more familiar balancing condition is obtained from this one by restricting to a component of $C$ and then taking degrees).
+Thus indeed we have a map:
+\begin{equation*} \varphi \colon \Mpunct{g}{\alpha}{H}{d} \to \ol\Mcal^\alpha_{g,n}(H,d). \end{equation*}
+To show that $\varphi$ is birational, we will choose an open dense locus of the domain and show that $\varphi$ induces an isomorphism on geometric points when restricted to this locus.
+The locus we take is the preimage of the locus inside $\ol\Mcal^\alpha_{g,n}(H,d)$ consisting of curves of compact type (i.e.
+those whose dual graph has genus zero); essentially we are excluding stable maps whose source curve contains a cycle of $\PP^1$s.
+The fact that this is open dense in $\ol\Mcal^\alpha_{g,n}(H,d)$ is not hard to see: when $g=1$ (the only case in which non-compact type curves can arise), the double ramification locus contains many components, but on every such component the maximal genus one subcurve of the source will be generically smooth, which shows again that the locus of stable maps not of compact type is closed inside $\ol\Mcal^\alpha_{g,n}(H,d)$.
+Once we show that $\varphi$ is bijective on geometric points when restricted to the preimage of this locus, it follows (since $\varphi$ is a finite morphism) that the preimage of this locus is dense in $\Mpunct{g}{\alpha}{H}{d}$, and hence that $\varphi$ is birational.
+
+So, let us start with a compact type stable map which belongs to the double ramification locus:
 \bcd
@@
 \end{align*}
-If we let $r$ denote the number of nodes of $C$ then by construction there is a natural map $\N^r \to Q$ and by the universal property of minimality our punctured curve must be obtained by puncturing a log smooth curve pulled back along a log map
+If we let $r$ denote the number of nodes of $C$ then by construction there is a natural map $\N^r \to Q$ and by the universal property of minimality our punctured curve must be obtained by puncturing a log smooth curve pulled back along a morphism of log schemes:
 \begin{equation*} (\Spec\kfield,Q \oplus \kfield^\st) \to (\Spec\kfield,\N^r\oplus\kfield^\st).\end{equation*}
-This log map must enhance the given map $\N^r \to Q$ on the level of ghost sheaves.
+This log morphism must enhance the given map $\N^r \to Q$ on the level of ghost sheaves.
 The moduli for such a log map is $\Gm^r$, but all these choices are canceled out by automorphisms of $(\Spec\kfield,Q\oplus\kfield^\st)$\footnote{(Navid) Here we are using the fact that $Q$ is in some sense bigger than $\N^r$.}.
@@
 First we note that it is sufficient to define $\Mcal_{C^\circ}$ on a base for the topology on $C$.
-We choose a base such that for every base open set $U$:
+We choose a base such that for each base open set $U$:
 \begin{enumerate}
@@
 
-Now let $U$ be such an open set in our base. If $U$ does not contain a puncture then we set
+Now let $U$ be such an open set in our base. If $U$ does not contain a puncture then $\Mcal_C|_U = \Ncal_C|_U$ and so we set
 \begin{equation*} \Mcal_{C^\circ}(U) = \Mcal_C(U).\end{equation*}
-If $U$ contains a puncture $p$ then by assumption $U \setminus \{ p\}$ contains only smooth unmarked points, and hence we have
+If $U$ contains a puncture $p$ then by assumption $U \setminus \{ p\}$ contains only smooth unmarked points, and hence we have a splitting
 \begin{equation*} \Ncal_C|_U = \left( \pi^\st \Mcal_S|_U \right) \oplus_{\OO_U^\st} \left(\Pcal_p^{\gp}|_U \right) \end{equation*}
@@
 \begin{equation*} \Mcal_C|_U = \ul{Q} \oplus \Pcal_p|_U.\end{equation*}
-We therefore have:
+We therefore have (since $U$ is connected):
 \begin{equation*} \Ncal_C(U) = Q \oplus \Pcal_p^{\gp}(U) \end{equation*}
 Recall we are assuming that $\OO_C(p)|_U$ is trivial.
-Choosing a trivialisation, we obtain a function $s \in \OO_U(U)$ such that $p=\{s=0\}$.
+Choosing a trivialisation, we obtain a function $s \in \OO_U(U)$ such that $p=\{s=0\}$ on $U$.
 Then $\Pcal_p(U)$ consists of functions of the form $\lambda \cdot s^n$ for $n \in \N$ and $\lambda \in \OO_U^\st(U)$.
 Groupifying, we obtain:
-\begin{equation*} \Pcal^{\gp}_p(U) = \left\{ \lambda \cdot s^k \, \vert \, \lambda \in \OO_U^\st(U), k \in \Z \right\} \end{equation*}
-(Indeed $\Pcal_p^{\gp}$ may be described as the sheaf of rational functions which are regular and invertible outside of $p$.) Recall that $p$ has attached to it a tangency order $\alpha_p \in \Z_{<0}$.
-If we let $\eta$ denote the generic point of the component of $C$ containing $p$, then we also have a pullback map $\ol\varphi_\eta \colon \N \to Q$.
-We define $\Mcal_{C^\circ}(U) \subseteq \Ncal_C(U)$ to be the submonoid generated by $Q \oplus \Pcal_p(U)$ and:
+\begin{equation*} \Pcal^{\gp}_p(U) = \left\{ \lambda \cdot s^k \, \vert \, \lambda \in \OO_U^\st(U), k \in \Z \right\}. \end{equation*}
+(Indeed, $\Pcal_p^{\gp}$ can be described as the sheaf of rational functions which are regular and invertible outside of $p$.) Recall that $p$ has attached to it a tangency order $\alpha_p \in \Z_{<0}$.
+If we let $\eta$ denote the generic point of the component of $C$ containing $p$, then we also have a pullback map $\ol\varphi_\eta \colon \N \to Q$ which is sharp (i.e.
+it is not the zero map).
+We define $\Mcal_{C^\circ}(U) \subseteq \Ncal_C(U)$ to be the submonoid generated by $Q \oplus \Pcal_p(U)$ and the element:
 \begin{equation*} (\ol\varphi_\eta(1),s^{\alpha_p}). \end{equation*}
-This clearly satisfies the condition to be a puncturing. Moreover, by the prestability condition for puncturings, this is the only possibility for $\Mcal_{C^\circ}$. We thus have a punctured curve:
-\begin{equation*} (C,\Mcal_{C^\circ}) \xrightarrow{\pi} (\Spec\kfield,Q\oplus\kfield^\st). \end{equation*}
-(Note that the log enhancement of $\pi$ is uniquely determined by taking the composition $\pi^\st \Mcal_S \to \Mcal_C \to \Mcal_{C^\circ}$.) It remains to construct the log enhancement of the map $f \colon C \to H$.
+This clearly satisfies the conditions to be a puncturing, and by the prestability condition it is the only possibility for $\Mcal_{C^\circ}$. We thus have a punctured curve:
+\begin{equation*} (C,\Mcal_{C^\circ}) \to (C,\Mcal_C) \to (\Spec\kfield,Q\oplus\kfield^\st). \end{equation*}
+It remains to construct the log enhancement of the map $f \colon C \to H$.
 The map $f^\flat \colon f^\st \Mcal_H \to \Mcal_{C^\circ}$ is already determined on the level of ghost sheaves.
@@
 \begin{equation*} f^* \OO_H(1) \cong \OO_C\left(\ol{f}^\flat(1)\right). \end{equation*}
-The component-wise description of the right-hand side in \cite{RSPW} (together with the fact that $C$ is compact type, so its Picard group is just the product of the Picard groups of its components) shows that such an isomorphism exists if and only if the original stable map is in the double ramification locus.
-
-There is a $\Gm$ of choices for such a map, but these are canceled out by the automorphisms of $(C,\Mcal_{C^\circ})$ induced by pulling back along (strict) automorphisms of $(\Spec\kfield,Q\oplus\kfield^\st)$.
+The component-wise description of the right-hand side in \cite{RSPW} (together with the fact that $C$ is compact type, so its Picard group is simply the product of the Picard groups of its components) shows that such an isomorphism exists if and only if the original stable map is in the double ramification locus.
+There is a $\Gm$ worth of choices for such a map, but these are canceled out by the automorphisms of $(C,\Mcal_{C^\circ})$ induced by pulling back along (strict) automorphisms of $(\Spec\kfield,Q\oplus\kfield^\st)$.
 This completes the proof of unique punctured lifting.
@@
 Thus, the spaces of punctured maps we encounter are always birational to double ramification loci.
-We will now discuss the geometry of these loci.
+We now briefly discuss the geometry of these loci.
 In the genus zero case, the double ramification locus is equal to the entire space
@@
 However, we know that $\M{1}{n}{H}{d}$ contains many other components besides $\ol\Mcal^\circ_{1,n}(H,d)$, some of which have excess dimension.
-Certainly the double ramification locus intersects these other components, and sometimes it does so in quite dramatic fashion.
+Certainly the double ramification locus intersects these other components, and sometimes it can do so in quite dramatic fashion.
 For instance, consider the locus where the source curve splits into a contracted elliptic component and a rational component containing all the markings.
@@
 \begin{equation*}\ol\Mcal_{1,1} \times \M{0}{n+1}{H}{d} \end{equation*}
-which has excess dimension $N-2$. This entire component belongs to the double ramification locus, since the intersection-theoretic condition is entirely numerical here.
-
-Thus we see that the double ramification locus can be quite badly-behaved in genus one.
+which has excess dimension $N-2$.
+This entire component belongs to the double ramification locus, since the condition \eqref{DRC condition} becomes entirely numerical here.
+Thus, we see that the double ramification locus can be quite badly-behaved in genus one.
 Fortunately, we will only be interested in the main component of this locus (which is birational to the main component of the moduli space of punctured maps); see \S \ref{} below.
-
-We will now use this recursive description of the logarithmic strata in $\Mcal$ to obtain a similar description of the strata in $\VZ$.
 
@@
 Note that the latter space (the main component of the moduli space of punctured maps) is birational to the main component of the double ramification locus.
-In Lemma \ref{Lemma forget marking} below we explain how to compute integrals over this.
+In Lemma \ref{Lemma forget marking} below we explain how to compute integrals over this.cd
 \begin{proof}

### 2019-01-30 GenusOneRelativeMaps.tex
minor changes

@@
 
-\begin{abstract} For a smooth projective variety $X$ and a smooth very ample hypersurface $Y \subseteq X$, we define moduli spaces of relative stable maps to $(X,Y)$ in genus one, as closed substacks of the moduli space of maps from centrally aligned curves, constructed in \cite{RSPW}.
+\begin{abstract} [OLD] For a smooth projective variety $X$ and a smooth very ample hypersurface $Y \subseteq X$, we define moduli spaces of relative stable maps to $(X,Y)$ in genus one, as closed substacks of the moduli space of maps from centrally aligned curves, constructed in \cite{RSPW}.
 We construct virtual classes for these moduli spaces, which we use to define \emph{reduced relative Gromov--Witten invariants} in genus one.
@@
 \begin{equation*} \widetilde{\VZ} \to \Mcal .\end{equation*}
-Since the map $\VZ \hookrightarrow \widetilde{\VZ}$ is strict, the Artin fan $\Acal$ of $\VZ$ is locally isomorphic to the Artin fan of $\widetilde{\VZ}$ (with the latter being, in general, larger).
+Since the map $\VZ \hookrightarrow \widetilde{\VZ}$ is strict, the Artin fan $\Acal$ of $\VZ$ is locally isomorphic to the Artin fan of $\widetilde{\VZ}$ (with the latter being, in general, larger)\footnote{(Navid) Make this more precise}.
 Since the following discussion is entirely local, we will ignore the distinction between the two, and pretend as though $\Acal$ is the Artin fan of $\widetilde{\VZ}$.
@@
 Here $g(v)$ and $d(v)$ are the genus and degree assigned to the vertex, while $Z_v$ is the logarithmic stratum of the target corresponding to the tropical stratum into which the vertex is mapped by the combinatorial type (in our setting, $Z_v=\PP^N$ or $H$).
-The length of the vector $\alpha(v)$ is given by the number of edges and flags adjacent to $v$, and the entries (which represent tangencies, and may be positive or negative) are given by the expansion factors along those edges and flags.
+The length of the vector $\alpha(v)$ is given by the number of edges and legs adjacent to $v$, and the entries (which represent tangencies, and may be positive or negative) are given by the expansion factors along those edges and legs.
 Note that if all of the tangencies are positive, then this is nothing but an ordinary moduli space of log stable maps.

### 2019-01-31 GenusOneRelativeMaps.tex
started a general description of Yc0

@@
 \begin{lem}
- A degree-aligned genus one tropical map $\phi$ to $\mathbb R_{\geq 0}$ is ... with a circle of radius $\delta$ around the core satisfying:
+ A one-parameter tropical map $\phi$ to $\mathbb R_{\geq 0}$ is a decorated tree (with expansion factors - \emph{contact orders} - along edges and legs, and degrees on vertices, satisfying the balancing condition) with a circle (of radius $\delta$) around the root (sometimes called the \emph{core} and denoted by $\circ$) satisfying:
  \begin{enumerate}
@@
 \end{ex}
+
+We now generalise this picture.
+Recall that the map $C\to\bar C$ is given by a (generic) line in the sum of the tangent spaces to the rational tails at the nodes that join them to the contracted curve of genus one.
+This is equivalent to an alignment, and it is parametrised by an open subset of a projective bundle over the moduli space for the tails corresponding to vertices of the dual graph lying on the circle of radius $\delta$.
+Yet, notice that those vertices lying in $\phi^{-1}(0)$ are already aligned among themselves.
+This is why we find it convenient to distinguish among four groups of vertices:
+\begin{enumerate}
+ \item the core;
+ \item\label{specialvertices} vertices on $\phi^{-1}(0)\cap\operatorname{circle}(\circ,\delta)$;
+ \item vertices on $\operatorname{circle}(\circ,\delta)\setminus\phi^{-1}(0)$;
+ \item\label{boringvertices} vertices on $\phi^{-1}(0)\setminus\operatorname{circle}(\circ,\delta)$.
+\end{enumerate}
+We shall first argue that gluing of log maps can be performed separately for the exterior and interior of the circle (the analogous classical picture is that, since the core is contracted, this moduli space is the product of a genus one curve, and a fiber product of genus zero maps under evaluation morphisms).
+
+\begin{lem}
+ $\VZ^{\operatorname{punct}}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(H,0)\simeq \VZ^{\operatorname{punct}}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(\Spec(k\oplus\mathbb N))\times H$.\footnote{(Luca) check log structure, could be fibered over std log point}
+\end{lem}
+
+Let us now deal with vertices of type \ref{specialvertices}.
+\begin{lem}
+ Consider the following fiber product in the category of fs log stacks:
+ \bcd
+ F\ar[d]\ar[r] & \prod_{i=1}^r\M{0}{\alpha^{(i)}\cup\{ m\}}{\PP^N|H}{d_i}\ar[d,"\ev_{q_i}"]\\
+ H\ar[r] & H^r
+ \ecd
+ On $F$ there is a canonical isomorphism $\mathbb L_{q_i}\cong\mathbb L_{q_j}$\footnote{(Luca) check how it degenerates}, the latter being the cotangent line bundles at the gluing markings on two different components $i$ and $j$.
+Furthermore, $\underline F$ is a finite cover of degree $m^{r-1}$ of the fiber product of the underlying stacks.
+\end{lem}
+\begin{proof}
+ Recall that each $\M{0}{\alpha^{(i)}\cup\{ m\}}{\PP^N|H}{d_i}$ is endowed with the log structure induced by pulling back along $q_i$ the divisorial log structure of the universal curve at the image of $q_i$ itself.
+Thus $\ev_{q_i}$ is made into a log morphism to $H$ with its induced DF(1) log structure.
+We claim that the subtext of such morphism is Gathmann's formula; namely, the log morphism to $H$ corresponds to an isomorphism betwee $\ev_{q_i}^*\OO_H(-H)$ on one side, and $\mathcal I_{D_i}\otimes\mathbb L_{q_i}^m$ on the other, where $\mathcal I_{D_i}$ is the ideal sheaf of the union of the comb loci $D_i$ in $\M{0}{\alpha^{(i)}\cup\{ m\}}{\PP^N|H}{d_i}$.
+
+ On the fiber product there is a canonical isomorphism between $\ev_{q_i}^*H$ and $\ev_{q_j}^*H$.
+
+ Say something about integrality.
+
+ Saturation is a local operation, as much as computing the degree, hence we can concentrate on the dense open locus where all the curves we are gluing are smooth, and they are not mapped entirely into $H$.
+There the minimal log structure on $\M{0}{\alpha^{(i)}\cup\{ m\}}{\PP^N|H}{d_i}$ is trivial, therefore the isomorphism between $\ev_{q_i}^*H$ and $\ev_{q_j}^*H$ translates into an isomorphism $\mathbb L_{q_i}^m\cong \mathbb L_{q_j}^m$.
+The saturation $F$ is obtained by taking an $m$-th root of this isomorphism.
+\end{proof}
+Let us denote by $\mathbb L_F$ the universal cotangent line at $q$.
+
+The projective bundle we are seeking has base
+\[\mathcal X=\left(F\times \prod_{i=1}^s\oM_{0,\tilde\alpha^{(i)}\cup\{m_i\}}^{\rm{punct}}(H,\tilde d_i)\right)\times_{H^{s+1}}H\]
+(with $m_i<m$) and it is \[\PP=\Proj_{\mathcal X}\left(\mathbb T_F\oplus\bigoplus_{i=1}^s\mathbb T_{\tilde q_i}\right).\]
+We are interested in the vanishing locus of the section
+\[s\colon\OO_{\PP}(-1)\hookrightarrow p^*\left(\mathbb T_F\oplus\bigoplus_{i=1}^s\mathbb T_{\tilde q_i}\right)\xrightarrow{+df_q} f^*(\operatorname{T}\PP^N)_q,\]
+because it represents the geometric condition that $f\colon C\to \PP^N$ factors through the normalisation map $C\to\bar C$ prescribed by the given point of $\PP$.
+As is, $s$ is not transverse to the zero section.
+First of all, unless $m=1$, $\operatorname{T}\PP^N$ can be replaced by $\operatorname{T}H$ in the definition of $s$ above, because the projection of all $\operatorname{d}f_i(\operatorname{T}_{q_i}R_i)$ to $N_{H/\PP^N}$ is zero.
+The case $m=1$ has to be dealt with separately and it turns out that, once $s$ is made transverse, the dimension of its zero locus is smaller than the expected dimension, hence the corresponding combinatorial types are in fact irrelevant.
+
+The procedure to make $s$ transverse is the same as described in \cite[\S 3]{VZ}, namely we need to blow up inside $\PP$ the projective subbundle $\PP(\mathcal E)$ of $\PP_{|\mathcal X_\sigma}$, where $\mathcal X_\sigma$ is the closed substack of $\mathcal X$ where some of the tails degenerate so that the corresponding gluing marking lies on a component contracted by $f$, and $\mathcal E$ is the sum of the tangent line bundles at such subset of the gluing markings.
+Because $\oM_{0,\tilde\alpha^{(i)}\cup\{m_i\}}^{\rm{punct}}(H,\tilde d_i)$ is isomorphic to $\M{0}{\tilde n_i}{H}{d_i}$, the construction of Vakil and Zinger in the section ``A blowup of a moduli space of genus-zero maps'' of their paper carries through unchanged.
+The result of the blow-up is to replace $T_{q_i}R_i$ with $T_{q_i}R_i\otimes\bigoplus_{j=1}^kT_{\tilde q_j}R_i\otimes T_{\tilde q_j} S_{ij}$.
+We interpret this in terms of alignments.\footnote{(Luca) this has to be written properly}
+
+We claim that $\tilde s$ obtained from $s$ by twisting by the exceptional divisors of the blowup is a transverse section.
+We also claim that comb loci of type $\mathcal Y_c^0$ can be described as a fibered product of
+\begin{itemize}
+ \item moduli of genus one punctured maps to the standard log point, radially aligned and satisfying factorisation;
+ \item $V(\tilde s)$;
+ \item moduli of genus zero maps relative to $(\PP^N|H)$, corresponding to vertices of type \ref{boringvertices} above.
+\end{itemize}
+Finally, we claim that integrals of psi and evaluation classes over these loci can be translated into tautological integrals, i.e.
+descendant Gromov-Witten invariants, whose numerics is governed by the combinatorial type of the tropical map.
 

### 2019-01-31 GenusOneRelativeMaps.tex
Expanded discussion of gluing

@@
 \linespread{1.25}
-\usepackage[margin=3cm]{geometry}
+\usepackage[margin=3.5cm]{geometry}
 
@@
 \newcommand{\Ncal}{\mathcal{N}}
+\newcommand{\Ccal}{\mathcal{C}}
 \newcommand{\Pcal}{\mathcal{P}}
@@
 Given such a combinatorial type $\Delta$, each vertex $v$ of the associated graph defines a moduli space of punctured stable maps:
-\begin{equation*} \ol\Mcal_v = \Mpunct{g(v)}{\alpha(v)}{Z_v}{d_v}. \end{equation*}
+\begin{equation*} \ol\Mcal_v = \Mpunct{g(v)}{\alpha(v)}{Z_v}{d(v)}. \end{equation*}
 Here $g(v)$ and $d(v)$ are the genus and degree assigned to the vertex, while $Z_v$ is the logarithmic stratum of the target corresponding to the tropical stratum into which the vertex is mapped by the combinatorial type (in our setting, $Z_v=\PP^N$ or $H$).
 The length of the vector $\alpha(v)$ is given by the number of edges and legs adjacent to $v$, and the entries (which represent tangencies, and may be positive or negative) are given by the expansion factors along those edges and legs.
-Note that if all of the tangencies are positive, then this is nothing but an ordinary moduli space of log stable maps.
-The corresponding logarithmic stratum is then obtained as a fibre product over evaluation maps:
+If all of the tangencies are positive, then this is nothing but an ordinary moduli space of log stable maps.
+
+The corresponding logarithmic stratum is then obtained as a follows.
+For each vertex $v$ and each adjacent edge $E \ni v$ we define $\widetilde\Mcal_v^E$ to be the stack $\ol\Mcal_v$ equipped with the log structure
+\begin{equation*} p_{v,E}^\st \Mcal_{\Ccal_v^\circ} \end{equation*}
+where $p_{v,E} \colon \ol\Mcal_v \to \Ccal_v^\circ$ is the marking section corresponding to $E$.
+This definition makes $p_{v,E}$ into a strict logarithmic map, and composing with the universal map produces a logarithmic evaluation morphism $\ev_{v,E} \colon \widetilde\Mcal_v^E \to Z_E$, where $Z_E \subseteq Z_v$ is the logarithmic stratum into which the marking corresponding to $E$ is mapped.
+
+If $E_1,\ldots,E_k$ are the edges adjacent to $v$ then we define
+\begin{equation*} \widetilde\Mcal_v = \widetilde\Mcal_v^{E_1} \times_{\ol\Mcal_v} \ldots \times_{\ol\Mcal_v} \widetilde\Mcal_v^{E_k} \end{equation*}
+where the fibre product is taken in the fs log category.
+With this definition, all the evaluation maps $\ev_{v,E} \colon \widetilde{\Mcal}_v \to Z_E$ are naturally logarithmic morphisms.
+Then the corresponding logarithmic stratum is obtained by taking the following fibre product (again, in the fs log category):
 \bcd
-\Scal \ar[r] \ar[d] \ar[rd,phantom,"\square"] & \prod_v \ol\Mcal_v \ar[d] \\
-\prod_{e} Z_e \ar[r] & \prod_{e} Z_e\times Z_e.
+\Scal \ar[r] \ar[d] \ar[rd,phantom,"\square"] & \prod_v \widetilde\Mcal_v \ar[d] \\
+\prod_{E} Z_E \ar[r] & \prod_{E} Z_E \times Z_E.
 \ecd
-This fibre product must be take in the fs log category.
-However, in our setting, the ordinary fibre product is automatically integral\footnote{(Navid) Justify this}, so all that is required is a saturation.
-This means that the fs fibre product is just a finite cover of the ordinary fibre product, and we may calculate the degree directly.\footnote{(Navid) How, again?}
+In the above discussion, there were two steps at which we needed to take fibre products in the fs log category: first, when constructing each $\widetilde{\Mcal}_v$ and second, when construction $\Scal$.
+Typically the fs fibre product does not agree with the usual fibre product of stacks; rather, one must take the fibre product in the category of coherent log stacks (which does agree with the usual fibre product) and then integralise and saturate the result.
+
+We will now argue that, in our situation, the fibre products of coherent log stacks are automatically integral.
+This means that the integralisation process is redundant, and so the fs fibre product is obtained from the ordinary fibre product by a process of saturation, which amounts to taking a finite cover of the underlying stack (whose degree we will compute).
+
+\begin{lemma}
+
+\end{lemma}
 

### 2019-01-31 GenusOneRelativeMaps.tex
Finished proof that M_v^tilde integral

@@
 Here $g(v)$ and $d(v)$ are the genus and degree assigned to the vertex, while $Z_v$ is the logarithmic stratum of the target corresponding to the tropical stratum into which the vertex is mapped by the combinatorial type (in our setting, $Z_v=\PP^N$ or $H$).
-The length of the vector $\alpha(v)$ is given by the number of edges and legs adjacent to $v$, and the entries (which represent tangencies, and may be positive or negative) are given by the expansion factors along those edges and legs.
+The length of the vector $\alpha(v)$ is given by the number of flags adjacent to $v$, and the entries (which represent tangencies, and may be positive or negative) are given by the expansion factors along those flags.
 If all of the tangencies are positive, then this is nothing but an ordinary moduli space of log stable maps.
@@
 The corresponding logarithmic stratum is then obtained as a follows.
-For each vertex $v$ and each adjacent edge $E \ni v$ we define $\widetilde\Mcal_v^E$ to be the stack $\ol\Mcal_v$ equipped with the log structure
+For each vertex $v$ and each adjacent flag $E \ni v$ we define $\widetilde\Mcal_v^E$ to be the stack $\ol\Mcal_v$ equipped with the log structure
 \begin{equation*} p_{v,E}^\st \Mcal_{\Ccal_v^\circ} \end{equation*}
@@
 
-If $E_1,\ldots,E_k$ are the edges adjacent to $v$ then we define
+If $E_1,\ldots,E_k$ are the flags adjacent to $v$ then we define
 \begin{equation*} \widetilde\Mcal_v = \widetilde\Mcal_v^{E_1} \times_{\ol\Mcal_v} \ldots \times_{\ol\Mcal_v} \widetilde\Mcal_v^{E_k} \end{equation*}
@@
 \ecd
-In the above discussion, there were two steps at which we needed to take fibre products in the fs log category: first, when constructing each $\widetilde{\Mcal}_v$ and second, when construction $\Scal$.
-Typically the fs fibre product does not agree with the usual fibre product of stacks; rather, one must take the fibre product in the category of coherent log stacks (which does agree with the usual fibre product) and then integralise and saturate the result.
-
-We will now argue that, in our situation, the fibre products of coherent log stacks are automatically integral.
-This means that the integralisation process is redundant, and so the fs fibre product is obtained from the ordinary fibre product by a process of saturation, which amounts to taking a finite cover of the underlying stack (whose degree we will compute).
-
-\begin{lemma}
-
+In the above discussion, there were two steps at which we needed to take fs fibre products: first, when constructing each $\widetilde{\Mcal}_v$ and second, when construction $\Scal$.
+Typically the fs fibre product does not agree with the usual fibre product of stacks; rather, one must take the fibre product in the category of coherent log stacks (which \emph{does} agree with the usual fibre product) and then integralise and saturate the result.
+
+We will now argue that in our situation, when we take fibre products of coherent log stacks, the result is automatically integral.
+This means that the integralisation process is redundant, and so the fs fibre product is obtained from the ordinary fibre product by a process of saturation.
+This amounts to taking a finite cover of the underlying stack (whose degree we will compute).
+
+The following lemma holds for arbitrary moduli spaces of punctured maps.
+
+\begin{lemma} Given a combinatorial type $\Delta$ indexing a stratum of $\Mcal$ and a vertex $v$ of the associated graph, consider the corresponding moduli space of punctured stable maps $\ol\Mcal_v$.
+As in the above discussion, define for each adjacent flag $E \ni v$ the log stack $\widetilde\Mcal_v^E$ by pulling back the log structure of the punctured curve along the marking section.
+Consider the fibre product \emph{in the category of coherent log stacks}:
+\begin{equation*} \widetilde\Mcal^{\operatorname{not-fs}}_v = \widetilde{\Mcal}_v^{E_1} \times_{\ol\Mcal_v} \ldots \times_{\ol\Mcal_v} \widetilde{\Mcal}_v^{E_k}. \end{equation*}
+Then $\widetilde\Mcal^{\operatorname{not-fs}}_v$ is integral (and consequently, the map $\widetilde\Mcal_v \to \widetilde\Mcal^{\operatorname{not-fs}}_v$ is finite).
 \end{lemma}
+\begin{proof} Locally we have a chart for $\ol\Mcal_v$ given by $Q$ (the minimal monoid as constructed, for instance, in \cite[Construction 1.16]{GrossSiebertLog}) and charts for $\widetilde\Mcal_v^{E_i}$ given by $Q_{E_i}$ where $Q_{E_i} = Q \oplus \N$ if $E_i$ corresponds to an ordinary marked point, and $Q_{E_i}$ is the submonoid of $Q \oplus \Z$ generated by $Q \oplus \N$ and $(\ol\varphi_{\eta_i}(1),u_{E_i})$ if $E_i$ corresponds to a puncturing (so that $u_{E_i} \in \Z_{<0}$).
+In either case, we have $Q_{E_i} \subseteq Q \oplus \Z \subseteq Q^{\operatorname{gp}} \oplus \Z$ (since $Q$ is integral) and so $Q_{E_i}$ is integral (recall that a monoid is integral if and only if it admits an injective homomorphism into a group).
+In this notation, $\widetilde\Mcal_v^{\operatorname{not-fs}}$ admits a chart given by the monoid:
+\begin{equation*} P = Q_{E_1} \oplus_Q Q_{E_2} \oplus_Q \ldots \oplus_Q Q_{E_k}.\end{equation*}
+If we consider the map $D \colon Q^{r-1} \to Q^r$ given by the $(r-1) \times r$ matrix
+\begin{equation*} D= \begin{pmatrix} 1 & 1 & 0 & 0 & \ldots & 0 \\
+0 & 1 & 1 & 0 & \ldots & 0 \\
+\, & \, & \, &\vdots & \, & \, \\
+0 & 0 & \ldots & 0 & 1 & 1 \end{pmatrix}\end{equation*}
+then the monoid $P$ can be expressed as a cokernel
+\begin{equation*} Q^{r-1} \to \oplus_{i=1}^r Q_{E_i} \to P \end{equation*}
+where the first map is obtained by composing $D$ with the natural inclusion $Q^r \to \oplus_{i=1}^r Q_{E_i}$. We may now form a diagram
+\bcd
+Q^{r-1} \ar[d,"\Id"] \ar[r] & \oplus_{i=1}^r Q_{E_i} \ar[r] \ar[d,hook] & P \ar[d] \\
+Q^{r-1} \ar[r] & Q^r \oplus \Z^r \ar[r] & S \oplus \Z^r
+\ecd
+where both rows are cokernel diagrams and the map $P \to S\oplus\Z^r$ is induced by the universal property. Here $S$ is the cokernel of $D$ and is given by:
+\begin{equation*} S = \begin{cases} Q \qquad \text{if } r=1 \\ Q^{\gp} \qquad \text{if } r \geq 2 \end{cases}.\end{equation*}
+In any case, $S$ is integral and the map $P \to S \oplus \Z^r$ is injective because the middle vertical maps in injective. Hence we conclude that $P$ is integral, as required. \end{proof}
+
+The previous lemma holds for arbitrary moduli spaces of punctured maps. The next lemma, on the other hand, is special to our setting.
+
+\begin{lemma} Consider the fibre product in the category of coherent log stacks:
+\bcd
+\Scal^{\operatorname{not-fs}} \ar[r] \ar[d] \ar[rd,phantom,"\square"] & \prod_v \widetilde\Mcal_v \ar[d] \\
+\prod_{E} Z_E \ar[r] & \prod_{E} Z_E \times Z_E.
+\ecd
+Then $\Scal^{\operatorname{not-fs}}$ is integral.\end{lemma}
 

### 2019-01-31 GenusOneRelativeMaps.tex
minor changes
Fixed proof that M_v is always integral (previous proof was wrong)

@@
 \end{lemma}
-\begin{proof} Locally we have a chart for $\ol\Mcal_v$ given by $Q$ (the minimal monoid as constructed, for instance, in \cite[Construction 1.16]{GrossSiebertLog}) and charts for $\widetilde\Mcal_v^{E_i}$ given by $Q_{E_i}$ where $Q_{E_i} = Q \oplus \N$ if $E_i$ corresponds to an ordinary marked point, and $Q_{E_i}$ is the submonoid of $Q \oplus \Z$ generated by $Q \oplus \N$ and $(\ol\varphi_{\eta_i}(1),u_{E_i})$ if $E_i$ corresponds to a puncturing (so that $u_{E_i} \in \Z_{<0}$).
+\begin{proof} Locally we have a chart for $\ol\Mcal_v$ given by $Q$ (the minimal monoid as constructed, for instance, in \cite[Construction 1.16]{GrossSiebertLog}) and charts for $\widetilde\Mcal_v^{E_i}$ given by $Q_{E_i}$, where $Q_{E_i} = Q \oplus \N$ if $E_i$ corresponds to an ordinary marked point, and $Q_{E_i}$ is the submonoid of $Q \oplus \Z$ generated by $Q \oplus \N$ and $(\ol\varphi_{\eta_i}(1),u_{E_i})$ if $E_i$ corresponds to a puncturing (so that $u_{E_i} \in \Z_{<0}$).
 In either case, we have $Q_{E_i} \subseteq Q \oplus \Z \subseteq Q^{\operatorname{gp}} \oplus \Z$ (since $Q$ is integral) and so $Q_{E_i}$ is integral (recall that a monoid is integral if and only if it admits an injective homomorphism into a group).
@@
 \begin{equation*} P = Q_{E_1} \oplus_Q Q_{E_2} \oplus_Q \ldots \oplus_Q Q_{E_k}.\end{equation*}
-If we consider the map $D \colon Q^{r-1} \to Q^r$ given by the $(r-1) \times r$ matrix
-\begin{equation*} D= \begin{pmatrix} 1 & 1 & 0 & 0 & \ldots & 0 \\
-0 & 1 & 1 & 0 & \ldots & 0 \\
-\, & \, & \, &\vdots & \, & \, \\
-0 & 0 & \ldots & 0 & 1 & 1 \end{pmatrix}\end{equation*}
-then the monoid $P$ can be expressed as a cokernel
-\begin{equation*} Q^{r-1} \to \oplus_{i=1}^r Q_{E_i} \to P \end{equation*}
-where the first map is obtained by composing $D$ with the natural inclusion $Q^r \to \oplus_{i=1}^r Q_{E_i}$. We may now form a diagram
-\bcd
-Q^{r-1} \ar[d,"\Id"] \ar[r] & \oplus_{i=1}^r Q_{E_i} \ar[r] \ar[d,hook] & P \ar[d] \\
-Q^{r-1} \ar[r] & Q^r \oplus \Z^r \ar[r] & S \oplus \Z^r
-\ecd
-where both rows are cokernel diagrams and the map $P \to S\oplus\Z^r$ is induced by the universal property. Here $S$ is the cokernel of $D$ and is given by:
-\begin{equation*} S = \begin{cases} Q \qquad \text{if } r=1 \\ Q^{\gp} \qquad \text{if } r \geq 2 \end{cases}.\end{equation*}
-In any case, $S$ is integral and the map $P \to S \oplus \Z^r$ is injective because the middle vertical maps in injective. Hence we conclude that $P$ is integral, as required. \end{proof}
-
-The previous lemma holds for arbitrary moduli spaces of punctured maps. The next lemma, on the other hand, is special to our setting.
+Suppose without loss of generality that $E_1,\ldots,E_r$ are punctures and $E_{r+1},\ldots,E_k$ are ordinary marked points; then $P$ is equal to the submonoid of
+\begin{equation*} Q \times \Z^r \times \N^{k-r} \end{equation*}
+generated by $Q \times \N^k$ and $(\ol\varphi_{\eta_i}(1),u_{E_i}\cdot e_i,0)$ where $e_i \in \Z^r$ is the $i$th basis element and $0 \in \N^r$.
+In particular, $P$ admits an injective homomorphism into the group
+\begin{equation*} Q^{\gp} \times \Z^r \times \Z^{k-r} \end{equation*}
+and hence is integral.\end{proof}
+
+\footnote{(Navid) Is this a good point to calculate the degree of $\widetilde\Mcal_v \to \widetilde\Mcal_v^{\operatorname{not-fs}}$?}The previous lemma holds for arbitrary moduli spaces of punctured maps.
+The next lemma, on the other hand, is special to our setting.
 
@@
 Then $\Scal^{\operatorname{not-fs}}$ is integral.\end{lemma}
+\begin{proof}\end{proof}
 

### 2019-01-31 GenusOneRelativeMaps.tex
minor changes

@@
 \begin{equation*} Q \times \Z^r \times \N^{k-r} \end{equation*}
-generated by $Q \times \N^k$ and $(\ol\varphi_{\eta_i}(1),u_{E_i}\cdot e_i,0)$ where $e_i \in \Z^r$ is the $i$th basis element and $0 \in \N^r$.
+generated by $Q \times \N^k$ and $(\ol\varphi_{\eta_i}(1),u_{E_i} e_i,0)$ for $i\in \{1,\ldots,r\}$, where $e_i \in \Z^r$ is the $i$th basis element and $0 \in \N^r$.
 In particular, $P$ admits an injective homomorphism into the group

### 2019-02-05 GenusOneRelativeMaps.tex
Added cheap trick for rubber integrals

@@
 
+\begin{definition} A combinatorial type $\Delta$ of a tropical curve consists of the following data:
+\begin{enumerate}
+\item $G$ a finite graph, with a set $V(G)$ of vertices, a set $F(G)$ of flags and an involution $\iota \colon F(G) \to F(G)$ with $\iota^2=\Id$.
+We let $L(G)$ denote the fixed set of $\iota$, and think of its elements as infinite legs; we let $E(G)$ denote the set of equivalence classes of elements not fixed by $\iota$, and think of them as finite edges connecting two (possibly equal) vertices of $G$;
+\item a genus assignment $g \colon V(G) \to \Z_{\geq 0}$;
+\item a degree assignment $\deg \colon V(G) \to \Z_{\geq 0}$;
+\item a weight assignment $u \colon F(G)  \to \Z$ such that for every edge $e \in E(G)$ we have $u(f_1)=-u(f_2)$ where $e=[f_1]=[f_2]$, and $u(l) \geq 0$ for any $l \in L(G)$;
+\end{enumerate}
+\end{definition}
+
 \footnote{(Luca) to be made homogeneous with what comes earlier} Review here the process of gluing for punctured maps.
@@
 
-\subsection{Recursive description of the divisors: type $C_0$}
+\subsection{Recursive description of the divisors: type $C_0$} Consider now a combinatorial type $\Delta$ such that the circuit is contracted into the divisor.
+The corresponding stratum $\Dcal_\Mcal \subseteq \Mcal$ is contained in the blown-up locus.
+Our task is to identify the logarithmic divisors in the preimage of $\Dcal_\Mcal$ under the map $\VZ \to \Mcal$.
+As discussed, these are indexed by choices of ray in the subdivision of the tropical moduli space.
+Suppose we have fixed such data.
+
+\begin{claim} The teeth of the comb can break at most once, along the circuit.\end{claim}
+
+\begin{proof} If not there would be more parameters in the tropical moduli space. \end{proof}
+
+\begin{prop} Let $\Delta$ be a combinatorial type as above. Then:
+\begin{enumerate}
+\item the circuit is a single vertex, and is mapped to the interior $\RR_{>0} \subseteq \RR_{\geq 0}$;
+\item the degree of the circuit is zero;
+\item there is a vertex which is adjacent to the circuit and mapped to the interior $0 \in \RR_{\geq 0}$;
+\item let $e \in E(\sqC)$ be an edge which is adjacent to the circuit, and such that $u(e)$ is maximal among the edges adjacent to the circuit.
+Then the other vertex $v$ contained in $e$ is mapped to $0 \in \RR_{\geq 0}$, and $v$ lies on the (absolute) radius;
+\item if $v \in V(\sqC)$ and $\lambda(v) > \delta$ then $f(v)=0$.
+\end{enumerate}
+\end{prop}
+
+There are 
+\newpage
+
+\subsection{Wonderful trick to compute reduced rubber integrals}
+
+Our method to compute the rubber VZ integrals which appear in the recursion:
+
+First, if the degree is zero, then it's Pixton's formula minus the locus with a single rational tail containing all the markings. So focus on positive degree case.
+
+If there is a relative marking with no insertion, we can forget that marking and compare to the main component of absolute maps to $H$.
+
+Suppose therefore that every relative marking has insertions.
+At least one of these must have only evaluation classes (since any of the nodal markings will only have evaluation classes).
+Fix that one: call it $x$.
+
+Consider the rubber VZ space with one additional marking $x_0$ with contact order zero. On this rubber space, take same as insertions as before, except replace $\ev_x$ with $\ev_{x_0}$.
+
+Consider the locus where the target splits.
+This can be expressed in terms of tautological classes by E.
+Katz's thesis (this gives us the left-hand side).
+Look at the right-hand side.
+One component of this is where the $x_0$ and $x$ are contained in a trivial bubble.
+Therefore $\ev_x = \ev_0$ and we recover the integral we are interested in.
+
+On the other components, the marking $x$ will always be insertion-free; hence we can forget $x$.
+So we get an integral over main component of maps to $H$.
+Note that this reduced invariant of $H$ will be of lower degree than the one we set out to compute.
+So the recursion is fixed.
+\newpage
+
 On the other hand, when there is a contracted elliptic subcurve - and it will be contracted into the hyperplane, because otherwise it wouldn't be generic, by density of the nice locus in $\VZ_{1,\alpha^\prime}(\PP^N|H,d^\prime)$ - the picture becomes more complicated due to the alignment.

### 2019-02-05 GenusOneRelativeMaps.tex
More on tropical line bundle approach to VZ rubber recursion

@@
 
-Consider the locus where the target splits.
-This can be expressed in terms of tautological classes by E.
-Katz's thesis (this gives us the left-hand side).
-Look at the right-hand side.
+Consider the locus where the target splits. This can be expressed in terms of tautological classes in several ways (which gives us the left-hand side).
+
+Firstly, by E.
+Katz's thesis (actually, this is an easy argument using $\MM_{0,2}$ Vakil--Zinger identification of tangent and cotangent spaces on a genus zero curve).
+We get $\Psi_0 + \Psi_\infty$ (target psi classes).
+
+Alternatively, take the piecewise-linear $\RR_{\geq 0}$-valued function on the tropical moduli space of the VZ rubber space which sends a tropical map to the weighted sum of the edge lengths (weighted by expansion factors).
+We can see that the Chern class is weighted sum of source psi classes (which agree with the target psi classes by pull-back), and we calculate the vanishing orders by the same locally toric method.
+
+Either way, the left-hand side is determined.
+Now look at the right-hand side.
 One component of this is where the $x_0$ and $x$ are contained in a trivial bubble.
@@
 Note that this reduced invariant of $H$ will be of lower degree than the one we set out to compute.
-So the recursion is fixed.
+So the recursion isn't circular.
 \newpage

### 2019-02-06 GenusOneRelativeMaps.tex
First pass on description of Gathmann's line bundle

@@
 \newcommand{\Mlog}[4]{\overline{\mathcal{M}}^{\operatorname{log}}_{#1,#2}(#3,#4)}
+\newcommand{\MLog}{\overline{\mathcal{M}}^{\operatorname{log}}}
 \newcommand{\Mpunct}[4]{\overline{\mathcal{M}}^{\operatorname{punct}}_{#1,#2}(#3,#4)}
@@
 \newcommand{\stC}{C'}
-\newcommand{\stf}{f'}
 \newcommand{\stpi}{\pi'}
@@
 \newcommand{\Ncal}{\mathcal{N}}
+\newcommand{\Lcal}{\mathcal{L}}
 \newcommand{\Ccal}{\mathcal{C}}
@@
 \newcommand{\Ycal}{\mathcal{Y}}
+\newcommand{\cchern}{\mathrm{c}}
 \newcommand{\ol}[1]{\overline{#1}}
@@
 
+\newpage
+
+\subsection{Wonderful trick to compute reduced rubber integrals}
+
+Our method to compute the rubber VZ integrals which appear in the recursion:
+
+First, if the degree is zero, then it's Pixton's formula minus the locus with a single rational tail containing all the markings. So focus on positive degree case.
+
+If there is a relative marking with no insertion, we can forget that marking and compare to the main component of absolute maps to $H$.
+
+Suppose therefore that every relative marking has insertions.
+At least one of these must have only evaluation classes (since any of the nodal markings will only have evaluation classes).
+Fix that one: call it $x$.
+
+Consider the rubber VZ space with one additional marking $x_0$ with contact order zero. On this rubber space, take same as insertions as before, except replace $\ev_x$ with $\ev_{x_0}$.
+
+Consider the locus where the target splits. This can be expressed in terms of tautological classes in several ways (which gives us the left-hand side).
+
+Firstly, by E.
+Katz's thesis (actually, this is an easy argument using $\MM_{0,2}$ Vakil--Zinger identification of tangent and cotangent spaces on a genus zero curve).
+We get $\Psi_0 + \Psi_\infty$ (target psi classes).
+
+Alternatively, take the piecewise-linear $\RR_{\geq 0}$-valued function on the tropical moduli space of the VZ rubber space which sends a tropical map to the weighted sum of the edge lengths (weighted by expansion factors).
+We can see that the Chern class is weighted sum of source psi classes (which agree with the target psi classes by pull-back), and we calculate the vanishing orders by the same locally toric method.
+
+Either way, the left-hand side is determined.
+Now look at the right-hand side.
+One component of this is where the $x_0$ and $x$ are contained in a trivial bubble.
+Therefore $\ev_x = \ev_0$ and we recover the integral we are interested in.
+
+On the other components, the marking $x$ will always be insertion-free; hence we can forget $x$.
+So we get an integral over main component of maps to $H$.
+Note that this reduced invariant of $H$ will be of lower degree than the one we set out to compute.
+So the recursion isn't circular.
+
+\textbf{Addendum} You have to be a bit careful about the target psi class on the larger space.
+We need to integrate over this, and the standard approach is to identify it with $\alpha_i \psi_i + \ev_i^\st H$ for $x_i$ any marking tangent to the corresponding divisor.
+Remember we are trying to move all the insertions off $x_k$.
+If there is some other marking $x_i$ tangent to the same divisor as $x_k$ then we're fine - just interpret the target psi class as an insertion on $x_i$.
+If not, we're forced to get an insertion at $x_k$ on the larger space, and we're stuck.
+In this case, we need to modify the recursion scheme slightly: instead of introducing an additional non-relative marking, split $x_k$ into two markings of tangency $1$ and $\alpha_k - 1$ (really, any splitting of $\alpha_k$ will probably do).
+Then we can safely move all the insertions (including the target psi class) onto one of these, and leave the other free to forget.
+Note this works even if $\alpha_k=1$.\medskip
+
+\textbf{Note} It might be worth noting that this idea of recursion on rubber spaces by taking $c_1$ of a line bundle appears to have already appeared in E.
+Katz's paper.
+Maybe he was right that there's a lot of good stuff there!
+
+\newpage
+
+\subsection{Gathmann's line bundle via tropical geometry} For each marking $x_k$ we consider the locus in $\VZ_{1,\alpha}(\PP^N|H)$ where $x_k$ belongs to an internal component of the collapsed map.
+We use the log structure on $\VZ_{1,\alpha}(\PP^N|H)$ to construct a line bundle $\Lcal_k$ together with a section $s_k$ vanishing along this locus.
+We use the correspondence with tropical geometry to identify $\cchern_1(\Lcal_k)$ in terms of tautological classes on $\VZ_{1,\alpha}(\PP^N|H)$, and we compute the vanishing order of $s_k$ along the components of its zero set.
+
+The pair $(\Lcal_k,s_k)$ is most naturally constructed on the moduli space $\MLog_{1,\alpha}(\PP^N|H)$ of non-expanded log maps; the corresponding pair on $\VZ_{1,\alpha}(\PP^N|H)$ will be obtained via pull-back.
+Consider therefore a moduli point in $\MLog_{1,\alpha}(\PP^N|H)$ and let $Q^\vee_{\RR}$ be the corresponding tropical moduli space (viewed as a rational polyhedral cone).
+Over this cone we have a universal tropical curve and map
+\bcd
+\sqC \ar[d,"\pi"] \ar[r,"f"] & \RR_{\geq 0} \\
+Q^\vee_{\RR} \ar[u, bend left=40pt, "x_k" left]
+\ecd
+where $x_k$ is the section which for every point $v \in Q^\vee_{\RR}$ picks out the vertex of $\sqC_v$ containing the leg $x_k$.
+The composition $f \circ x_k \colon Q^\vee_{\RR} \to \RR_{\geq 0}$ defines a piecewise-linear function on $Q_{\RR}^\vee$ whose preimage over the open cone $\RR_{>0}$ consists of those tropical maps where $x_k$ belongs to an internal component.
+Dually we obtain an element of the minimal monoid $Q$ and globally a section of the ghost sheaf on $\MLog_{1,\alpha}(\PP^N|H)$.
+In the usual way this induces a line bundle and section $(\Lcal_k,s_k)$ on the moduli space, and the tropical description above shows that the zero locus of $s_k$ is (set-theoretically) the locus where $x_k$ belongs to an internal component.
+
+We now calculate $\cchern_1(\Lcal_k)$.
+Choose a family of log stable maps over $S$ and let $\mu \in \Gamma(S,\ol{M}_S)$ be the global section of the ghost sheaf constructed in the previous paragraph.
+This pulls back along $\pi$ to give a global section $\pi^\flat(\mu) \in \Gamma(C,\ol{M}_C)$.
+Interpreted as a piecewise-linear function on the tropicalisation $\sqC$ with values in $\ol{M}_S$ \cite[Remark 7.3]{CavalieriChanUlirschWise}, this assigns $\mu$ to every vertex and has slope zero along every edge.
+By construction, the line bundle associated to this section is $\pi^\st \Lcal_k$.
+Consider on the other hand the generator $1 \in \N = \Gamma(\PP^N,\ol{M})$ with associated line bundle $\OO(H)$.
+The section $f^\flat(1) \in \Gamma(C,\ol{M}_C)$ has associated line bundle $f^\st\OO(H)$.
+By construction $f^\flat(1)$ assigns $\mu$ to $v$ and has slope $\alpha_k$ along the leg $x_k$.
+Thus if we consider the difference $f^\flat(1) - \pi^\flat(\mu)$ then this assigns $0$ to $v$ and still has slope $\alpha_k$ along $x_k$.
+Thus by \cite[Proposition 2.4.1]{RSPW} the corresponding line bundle restricted to $C_v$ is given by
+\begin{equation*} \OO_{C_v} \left(\alpha_k x_k + \sum_e \mu_e x_e \right) \end{equation*}
+where the sum is over the edges $e$ adjacent to $v$ and distinct from $x_k$. Thus we see that:
+\begin{equation*} \left( f^\st\OO(H) \otimes \pi^\st \Lcal_k^{-1} \right) \big|_{C_v} = \OO_{C_v} \left(\alpha_k x_k + \sum_e \mu_e x_e \right).\end{equation*}
+Since $x_k$ factors through $C_v$ we may pull back along $x_k$ to obtain
+\begin{equation*} \Lcal_k = x_k^\st\pi^\st \Lcal_k = x_k^\st \OO_\Ccal(\alpha_k x_k) \otimes x_k^\st f^\st\OO(H) = x_k^\st \omega_{\Ccal/S} \otimes \ev_k^\st \OO(H) \end{equation*}
+and taking Chern classes gives:
+\begin{equation*} \cchern_1(\Lcal_k) = \alpha_k \psi_k + \ev_k^\st H.\end{equation*}
+
+\begin{remark} This construction gives the natural logarithmic analogue of Gathmann's line bundle \cite[Construction 2.1]{Ga}.
+One of the benefits of the logarithmic approach is to make the computation of multiplicities entirely combinatorial; see \S \ref{} below.\end{remark}
+
+\newpage
+
 \section{Introduction}
@@
 \begin{thm}[Gathmann-type formula, maximal tangency, $(\PP^N|H)$ case]
- \[(\alpha_k\psi_k+\ev_k^*H)[\VZ_{1,\alpha}(\PP^N|H,d)]=[D_{1,\alpha;k}(\PP^N|H,d)],\]
+ \[(\alpha_k\psi_k+\ev_k^\st H)[\VZ_{1,\alpha}(\PP^N|H,d)]=[D_{1,\alpha;k}(\PP^N|H,d)],\]
  the latter being a sum of broken comb loci indexed by rays of the tropical fan.
@@
 \begin{cor}
- \[(\alpha_k\psi_k+\ev_k^*H)[\VZ^G_{1,\alpha}(\PP^N|H,d)]=[D^G_{1,\alpha;k}(\PP^N|H,d)],\]
+ \[(\alpha_k\psi_k+\ev_k^\st H)[\VZ^G_{1,\alpha}(\PP^N|H,d)]=[D^G_{1,\alpha;k}(\PP^N|H,d)],\]
  the latter being expressible as a weighted sum of tautological classes on Gathmann's comb loci.
@@
 %We would like to extend the minimal monoid in order to account for some of the punctures, i.e.
-take the sum of $p^*\mathcal M_{C^\circ}$ (for every such puncture $p$) fibered over the log structure of the base, which seems to have the same effect as topping those edges with a uertex (which doesn't carry any other information).
+take the sum of $p^\st\mathcal M_{C^\circ}$ (for every such puncture $p$) fibered over the log structure of the base, which seems to have the same effect as topping those edges with a uertex (which doesn't carry any other information).
 This looks to me like sprouting a $\PP^1$ at those puncture.
@@
 As in \cite[Construction 2.1]{Ga} there is an exact sequence of jet bundles
-\begin{equation*} 0\to x_k^*\omega_{\mathcal{C}/\VZ}^{\otimes\alpha_k}\otimes\ev_k^*\OO_{\PP^N}(H)\to x_k^*\mathcal J^{\alpha_k}(f^*\OO_{\PP^N}(H))\to x_k^*\mathcal J^{\alpha_k-1}(f^*\OO_{\PP^N}(H))\to 0 \end{equation*}
-and thus we obtain a section of the line bundle $x_k^*\omega_{\mathcal{C}/\VZ}^{\otimes\alpha_k}\otimes\ev_k^*\OO_{\PP^N}(H)$ with vanishing locus equal to the locus where $x_k$ belongs to an internal component.
+\begin{equation*} 0\to x_k^\st\omega_{\mathcal{C}/\VZ}^{\otimes\alpha_k}\otimes\ev_k^\st\OO_{\PP^N}(H)\to x_k^\st\mathcal J^{\alpha_k}(f^\st\OO_{\PP^N}(H))\to x_k^\st\mathcal J^{\alpha_k-1}(f^\st\OO_{\PP^N}(H))\to 0 \end{equation*}
+and thus we obtain a section of the line bundle $x_k^\st\omega_{\mathcal{C}/\VZ}^{\otimes\alpha_k}\otimes\ev_k^\st\OO_{\PP^N}(H)$ with vanishing locus equal to the locus where $x_k$ belongs to an internal component.
 Writing this locus as
@@
 we obtain:
-\begin{lem} $(\alpha_k\psi_k+\ev_k^*H)\cap[\VZ]=[\Dcal(k)].\footnote{(Navid) Should we work out the vanishing orders of the section at this point?}$\end{lem}
+\begin{lem} $(\alpha_k\psi_k+\ev_k^\st H)\cap[\VZ]=[\Dcal(k)].\footnote{(Navid) Should we work out the vanishing orders of the section at this point?}$\end{lem}
 \noindent The remainder of this section will be devoted to providing an explicit recursive description of the class $[\Dcal(k)]$ in terms of tautological classes on spaces of maps with smaller numerical invariants.
@@
 Indeed, we will see that the space \eqref{punctured space} is birational to the moduli space of ordinary stable maps to $H$ satisfying the condition:
-\begin{equation}\label{DRC condition} f^*[H] - \sum_{i=1}^n \alpha_ix_i =0 \in \Achow_0(C).\end{equation}
+\begin{equation}\label{DRC condition} f^\st[H] - \sum_{i=1}^n \alpha_ix_i =0 \in \Achow_0(C).\end{equation}
 This space forms a closed substack
@@
 \begin{equation*} \Ncal_C|_U = \left( \pi^\st \Mcal_S|_U \right) \oplus_{\OO_U^\st} \left(\Pcal_p^{\gp}|_U \right) \end{equation*}
-where $\Pcal_p$ is the divisorial log structure with respect to $p$. Since $\Mcal_S = Q \oplus \kfield^\st$ it follows that $\pi^*\Mcal_S|_U = \ul{Q} \oplus \OO_U^\st$. Thus we see that
+where $\Pcal_p$ is the divisorial log structure with respect to $p$. Since $\Mcal_S = Q \oplus \kfield^\st$ it follows that $\pi^\st\Mcal_S|_U = \ul{Q} \oplus \OO_U^\st$. Thus we see that
 \begin{equation*} \Ncal_C|_U = \ul{Q} \oplus \Pcal_p^{\gp}|_U\end{equation*}
@@
 To enhance this to a map on the level of log structures entails choosing an isomorphism of line bundles:
-\begin{equation*} f^* \OO_H(1) \cong \OO_C\left(\ol{f}^\flat(1)\right). \end{equation*}
+\begin{equation*} f^\st \OO_H(1) \cong \OO_C\left(\ol{f}^\flat(1)\right). \end{equation*}
 The component-wise description of the right-hand side in \cite{RSPW} (together with the fact that $C$ is compact type, so its Picard group is simply the product of the Picard groups of its components) shows that such an isomorphism exists if and only if the original stable map is in the double ramification locus.
@@
  where $a_I=\sum_{i\in I}a_i$ and $\delta_0=\operatorname{glue}_*([\oM_{0,n+2}])$.
-From $\psi_j=\fgt_i^*\psi_j+[D_{i,j}]$ for $i\neq j$, and the dilaton equation, we see that $\fgt_{i,*}\psi_j=1$ and $\fgt_{i,*}\psi_i=n-1$.
+From $\psi_j=\fgt_i^\st\psi_j+[D_{i,j}]$ for $i\neq j$, and the dilaton equation, we see that $\fgt_{i,*}\psi_j=1$ and $\fgt_{i,*}\psi_i=n-1$.
 On the other hand, the only surviving boundary classes are $[D_{i,j}]$, and they push down to $1$.
@@
 This breaks when $f_{|R_i}$ is not tangent to $H$ of order exactly $2$ at $q_i$, for either $i$; but by the maximality assumption this happens precisely along Gathmann's comb loci $\Delta_i$.
-So in fact, rather than with $T_{R_i,q_i}^{\otimes 2}$, we should be working with $T_{R_i,q_i}^{\otimes 2}(-\Delta_i)$: but this is exactly $\ev_i^*(-H)$ by Gathmann's genus zero formula, and the isomorphism $\ev_1^*(H)=\ev_2^*(H)$ holds on all of $F$.
+So in fact, rather than with $T_{R_i,q_i}^{\otimes 2}$, we should be working with $T_{R_i,q_i}^{\otimes 2}(-\Delta_i)$: but this is exactly $\ev_i^\st(-H)$ by Gathmann's genus zero formula, and the isomorphism $\ev_1^\st(H)=\ev_2^\st(H)$ holds on all of $F$.
 
@@
  \end{itemize}
-On $\PP$ there is a natural vector bundle map \[s\colon \OO_{\PP}(-1)\hookrightarrow p^*(T_{q_1}R_1\oplus T_{q_2}R_2)\xrightarrow{+\operatorname{d}f}\ev_q^*T\PP^N\]
+On $\PP$ there is a natural vector bundle map \[s\colon \OO_{\PP}(-1)\hookrightarrow p^\st(T_{q_1}R_1\oplus T_{q_2}R_2)\xrightarrow{+\operatorname{d}f}\ev_q^\st T\PP^N\]
 that vanishes along the locus where $f$ descends to $\bar C$. In general, it is not a transversal section:
@@
 \begin{lem}
- The class of $\PP(\mathcal F)\subseteq\PP(\mathcal E)$ is $c_{\rm{top}}(\OO_\mathcal{E}(1)\otimes p^*(\mathcal{E}/\mathcal{F}))$.
+ The class of $\PP(\mathcal F)\subseteq\PP(\mathcal E)$ is $c_{\rm{top}}(\OO_\mathcal{E}(1)\otimes p^\st(\mathcal{E}/\mathcal{F}))$.
 \end{lem}
@@
 It is a good time to remember that $\mathcal E$ was in fact $(\bigoplus_{i=1}^rTR_{i,q_i})\otimes\mathbb T$.
-By writing $c$ for $c_1(\OO_\mathcal{E}(1))$, $\psi_i$ for $c_1(T^*R_{i,q_i})$, $\psi_Z$ for Vakil-Zinger's universal psi class, and $H$ for $\ev_q^*H$, we need to compute
+By writing $c$ for $c_1(\OO_\mathcal{E}(1))$, $\psi_i$ for $c_1(T^\st R_{i,q_i})$, $\psi_Z$ for Vakil-Zinger's universal psi class, and $H$ for $\ev_q^\st H$, we need to compute
 \begin{align*}
@@
 Thus $\ev_{q_i}$ is made into a log morphism to $H$ with its induced DF(1) log structure.
-We claim that the subtext of such morphism is Gathmann's formula; namely, the log morphism to $H$ corresponds to an isomorphism betwee $\ev_{q_i}^*\OO_H(-H)$ on one side, and $\mathcal I_{D_i}\otimes\mathbb L_{q_i}^m$ on the other, where $\mathcal I_{D_i}$ is the ideal sheaf of the union of the comb loci $D_i$ in $\M{0}{\alpha^{(i)}\cup\{ m\}}{\PP^N|H}{d_i}$.
-
- On the fiber product there is a canonical isomorphism between $\ev_{q_i}^*H$ and $\ev_{q_j}^*H$.
+We claim that the subtext of such morphism is Gathmann's formula; namely, the log morphism to $H$ corresponds to an isomorphism betwee $\ev_{q_i}^\st\OO_H(-H)$ on one side, and $\mathcal I_{D_i}\otimes\mathbb L_{q_i}^m$ on the other, where $\mathcal I_{D_i}$ is the ideal sheaf of the union of the comb loci $D_i$ in $\M{0}{\alpha^{(i)}\cup\{ m\}}{\PP^N|H}{d_i}$.
+
+ On the fiber product there is a canonical isomorphism between $\ev_{q_i}^\st H$ and $\ev_{q_j}^\st H$.
 
@@
  Saturation is a local operation, as much as computing the degree, hence we can concentrate on the dense open locus where all the curves we are gluing are smooth, and they are not mapped entirely into $H$.
-There the minimal log structure on $\M{0}{\alpha^{(i)}\cup\{ m\}}{\PP^N|H}{d_i}$ is trivial, therefore the isomorphism between $\ev_{q_i}^*H$ and $\ev_{q_j}^*H$ translates into an isomorphism $\mathbb L_{q_i}^m\cong \mathbb L_{q_j}^m$.
+There the minimal log structure on $\M{0}{\alpha^{(i)}\cup\{ m\}}{\PP^N|H}{d_i}$ is trivial, therefore the isomorphism between $\ev_{q_i}^\st H$ and $\ev_{q_j}^\st H$ translates into an isomorphism $\mathbb L_{q_i}^m\cong \mathbb L_{q_j}^m$.
 The saturation $F$ is obtained by taking an $m$-th root of this isomorphism.
@@
 We are interested in the vanishing locus of the section
-\[s\colon\OO_{\PP}(-1)\hookrightarrow p^*\left(\mathbb T_F\oplus\bigoplus_{i=1}^s\mathbb T_{\tilde q_i}\right)\xrightarrow{+df_q} f^*(\operatorname{T}\PP^N)_q,\]
+\[s\colon\OO_{\PP}(-1)\hookrightarrow p^\st\left(\mathbb T_F\oplus\bigoplus_{i=1}^s\mathbb T_{\tilde q_i}\right)\xrightarrow{+df_q} f^\st(\operatorname{T}\PP^N)_q,\]
 because it represents the geometric condition that $f\colon C\to \PP^N$ factors through the normalisation map $C\to\bar C$ prescribed by the given point of $\PP$.

### 2019-02-06 GenusOneRelativeMaps.tex
minor changes

@@
 
-\title[Genus One Reduced Relative Invariants]{Relative Stable Maps in Genus One via Central Alignments}
+\title{Gromov--Witten theory of hypersurfaces in genus one}
 \author{Luca Battistella, Navid Nabijou and Dhruv Ranganathan}
@@
 
-\begin{abstract} [OLD] For a smooth projective variety $X$ and a smooth very ample hypersurface $Y \subseteq X$, we define moduli spaces of relative stable maps to $(X,Y)$ in genus one, as closed substacks of the moduli space of maps from centrally aligned curves, constructed in \cite{RSPW}.
-We construct virtual classes for these moduli spaces, which we use to define \emph{reduced relative Gromov--Witten invariants} in genus one.
-
-[GOALS: We prove a recursion formula which allows us to completely determine these invariants in terms of the reduced Gromov--Witten invariants, as defined in [REF].
-We also prove a relative version of the Li--Zinger formula, relating our invariants to the usual relative Gromov--Witten invariants.
-Also say something about quasimaps.]
+\begin{abstract}
 \end{abstract}
@@
 \begin{equation*} \cchern_1(\Lcal_k) = \alpha_k \psi_k + \ev_k^\st H.\end{equation*}
+This gives the construction of $(\Lcal_k,s_k)$ on $\MLog_{1,\alpha}(\PP^N|H)$; the construction on $\VZ_{1,\alpha}(\PP^N|H)$ is given by pull-back.
+Notice in particular that $\psi_k$ should be interpreted as a \emph{collapsed psi class} on $\VZ_{1,\alpha}(\PP^N|H)$, i.e.
+a psi class coming from the stabilised curve of the collapsed map.
+All of the psi classes we deal with will be collapsed psi classes.
 

### 2019-02-07 Dhruv files/main.tex
Added Dhruv files (doesn't compile yet, though)

\documentclass[11pt]{amsart}
\linespread{1.25}
\usepackage[margin=3.5cm]{geometry}

\usepackage[english]{babel}
\usepackage{appendix}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
%\usepackage{showlabels}
\usepackage{hyperref}
\usepackage{amsthm}
\usepackage{marginnote}

\usepackage{stmaryrd}
\usepackage{enumitem}
\usepackage[english]{babel}
\usepackage{yfonts}
\usepackage[T1]{fontenc}
\usepackage[utf8x]{inputenc}

\usepackage{calrsfs}
\DeclareMathAlphabet{\pazocal}{OMS}{zplm}{m}{n}

\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{faktor}
\usepackage{xcolor}
\usepackage{xfrac}
\usepackage{tikz,tikz-cd}
\usetikzlibrary{decorations.pathmorphing,decorations.pathreplacing,patterns}

\usepackage[all]{xy}
\usepackage{bbm}
\usepackage{tabularx}
\usepackage{longtable}
\usepackage{tabu}
\usepackage{booktabs}
\usepackage{mathtools}

\usepackage[]{textcomp}
\usepackage[sups]{Baskervaldx}
\usepackage{cabin}
\usepackage[varqu,varl]{inconsolata}
\usepackage[baskervaldx,bigdelims,vvarbb]{newtxmath}
\usepackage[cal=cm]{mathalfa}

\newcommand{\plC}{\scalebox{0.8}[1.3]{$\sqsubset$}}
\newcommand{\sidenote}[1]{\marginpar{\textbf{\color{red}#1}}}

\theoremstyle{definition}
\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{lemma}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary}
\newtheorem*{teo*}{Theorem}
\newtheorem{ipotesi}{ipotesi}
\newtheorem*{nota}{Nota}
\newtheorem{claim}{Claim}
\newtheorem{question}[thm]{Question}
\newtheorem{conj}[thm]{Conjecture}

\newtheorem{innercustomthm}{Theorem}
\newenvironment{customthm}[1]
  {\renewcommand\theinnercustomthm{#1}\innercustomthm}
  {\endinnercustomthm}

\theoremstyle{definition}
\newtheorem{example}[thm]{Example}
\newtheorem{ex}[thm]{Example}
\newtheorem{dfn}[thm]{Definition}
\newtheorem{definition}[thm]{Definition}
\newtheorem{aside}[thm]{Aside}
\newtheorem{remark}[thm]{Remark}
\newtheorem{com}[thm]{Comment}
\newtheorem{num}{Number}
\newtheorem*{sketch}{Sketch}
\newtheorem*{rem}{Remark}
\newtheorem*{aside*}{Aside}
\newtheorem*{acknowledgements}{Acknowledgements}

\title{Gromov-Witten theory of hypersurfaces in genus one}
\author{Dhruv Ranganathan}
\date{February 2019}

\begin{document}

\maketitle

\begin{abstract}
    This is a section of the working draft of Battistella--Nabijou--Ranganathan. We construct reduced Gromov--Witten theory or projective in genus one, relative to a hyperplane, its rubber variant, establish its unobstructedness, and describe the stratification by boundary strata.
\end{abstract}

\section{The moduli space and deformation theory}

Let $\mathfrak M_{1,n}$ be the logarithmic algebraic stack of genus $1$ $n$-pointed prestable curves. Let $\plC$ be a $n$-pointed genus $1$ tropical curve. Let $C$ be a logarithmic curve over $S$, let $\plC$ denote its tropicalization, and let $\lambda$ be the section of $\overline{M}_{C/S}$ giving the distance from the circuit.

We begin by recalling the logarithmic moduli spaces of genus $1$ curves constructed in~\cite[Sections 2 \& 4]{RSPW}. Given a family of tropical curves over a base $\sigma$, a central alignment is a piecewise-linearly varying choice of radius $\delta_s$ for $s\in\sigma$, together with a consistent ordering of the vertices that lie inside the circle of radius $s$ around the circuit components. Precisely, let $T$ be a geometric point with logarithmic structure.

\begin{definition}
A \textbf{central alignment} of $C/T$ is an element $\delta\in\overline{M}_S$ such that
\begin{enumerate}
    \item the section $\delta$ is comparable to $\lambda(v)$ for all vertices $v$ of $\plC$,
    \item for any pair of vertices $v$ and $w$ at distance less than $\delta$, the sections $\lambda(v)$ and $\lambda(w)$ are comparable.
\end{enumerate}
\end{definition}

The moduli stack $\mathfrak M_{1,n}^{\mathrm{cen}}$ is a logarithmic algebraic stack in the smooth topology. The main construction of~\cite{RSPW} canonically associates to any radially aligned family of curves $\mathscr C_S$ a partial destabilization $\widetilde{\mathscr C_S}$ and a contraction
\[
\widetilde{\mathscr C_S}\to \overline{\mathscr C_S},
\]
where $\overline{\mathscr C_S}$ is a Gorenstein elliptic singular curve. The number of branches is equal to the number of excident edges at the circle of radius $\delta$. This data uniquely determines the singularity.

The space of stable maps $\overline{\mathcal M}^{\mathrm{cen}}_{1,n}(\mathbb P^N,d)$ from the universal nodal curve $\mathscr C$ over the stack $\mathfrak M_{1,n}^{\mathrm{cen}}$ is a proper and algebraic, with projective coarse moduli. The \textbf{factorization condition} that the map $\mathscr C\to \mathbb P^N$ factors through the contraction $\widetilde{\mathscr C}\to \overline{\mathscr C}$ is a closed condition. 
\begin{thm}[{\cite[Theorem B]{RSPW}}]
The substack $\mathcal{VZ}_{1,n}(\mathbb P^N,d)$ of $\overline{\mathcal M}^{\mathrm{cen}}_{1,n}(\mathbb P^N,d)$ parameterizing maps to $\mathbb P^N$ that satisfy the factorization property is smooth and proper of the expected dimension.
\end{thm}

\subsection{Relative geometry: compactification} Fix $H\subset \mathbb P^N$ be a hyperplane. Let $\alpha$ be a partition of the degree $d$. Consider the moduli space $\mathcal M_{1,\alpha}^\circ(\mathbb P^N|H)$ of maps from smooth elliptic curves $C\to \mathbb P^N$ that meet $H$ at finitely many marked points with vanishing orders given by the partition $\alpha$. This is a smooth non-compact Deligne--Mumford stack.

We will first compactify the space described above, and then desingularize it. For the compactification, we begin with Abramovich--Chen--Gross--Siebert's space of logarithmic stable maps, though we will typically work with various subcategories and variants.

The moduli space $\overline{\mathcal M}^{\mathrm{log}}_{1,\alpha}(\PP^N|H)$ is a fibered category over logarithmic schemes, whose fiber over $(S,M_S)$ is the groupoid of logarithmic curves of genus $1$ over (S,M_S)$ equipped with a map to $\mathbb P^N$ of degree $d$ and contact order $\alpha$. It is a fundamental fact in the subject that this category is representable by a proper algebraic stack with logarithmic structure.

There is a representable finite logarithmic morphism to the Kontsevich space, forgetting the logarithmic structure on the target:
$$
\overline{\mathcal M}^{\mathrm{log}}_{1,\alpha}(\mathbb P^N|H) \to \overline{\mathcal M}_{1,n}(\mathbb P^N,d).
$$
The space of centrally aligned maps is a logarithmic modification
$$
\overline{\mathcal M}^{\mathrm{cen}}_{1,n}(\mathbb P^N,d)\to\overline{ \mathcal M}_{1,n}(\mathbb P^N,d)
$$ 
The fiber product leads to a fourth moduli space of \textbf{centrally aligned logarithmic maps to $(\mathbb P^n,H)$}, which we denote $\widetilde{\mathcal{VZ}}_{1,\alpha}(\mathbb P^N|H)$.

\subsection{Relative geometry: expansions} Our next task is to pick out a non-singular principal component in $\widetilde{\mathcal{VZ}}_{1,\alpha}(\mathbb P^N|H)$. The principal component of this space, consisting of the closure of the space of maps from nonsingular curves, maps into the principal component of $\overline{\mathcal M}^{\mathrm{cen}}_{1,n}(\mathbb P^N,d)$. Indeed, smoothable logarithmic maps are, in particular, smoothable as ordinary maps. However, an additional condition is required to isolate the principal component of the space of logarithmic maps.

In order make the obstruction theory more geometric, we expand the target. To elucidate the connection with the static target, consider a logarithmic stable map $[C\to (\mathbb P|H)]$ over $\mathrm{Spec} \ (\mathbb N\to \mathbb C)$. At the level of tropicalizations, we have a map of fans
\[
\plC\to \mathbb R_{\geq 0}.
\]
Choose a subdivision of $\mathbb R_{\geq 0}$ whose vertices consist of the images of vertices of $\plC$. Pull this subdivision back to $\plC$ by marking all preimages of the vertices of $\mathbb R_{\geq 0}$. Denote the resulting map $\widetilde \plC \to \widetilde{\mathbb R}_{\geq 0}$.

These subdivisions induce logarithmic modifications
\[
\widetilde C\to \mathbb P^N[s],
\]
see~\cite{AW}. Here the latter is the $s$-times iterated deformation to the normal cone of $H$ in $\mathbb P^N$. The number of components is equal to the number of vertices in $\widetilde{\mathbb R}_{\geq 0}$. The curve is modified by adding rational components corresponding to the newly introduced vertices.

The result is a logarithmic stable map to an expanded target $\mathbb P^N[s]$, together with a contraction to the main target component $\mathbb P^N[s]\to\mathbb P^N$. More generally, this construction is easily modified for any family of logarithmic maps, such that the vertices of $\plC$ are totally ordered in the family, see~\cite{} for details.

Globally, Kim constructs a moduli space of logarithmic stable maps to expanded degenerations, which on logarithmic points, reduces to the above construction~\cite{KimLog}. Indeed, by above description, Kim's space is identified with a subcategory of the Abramovich--Chen--Gross--Siebert space, and its minimal objects are identified with a logarithmic modification of the unexpanded space.

\subsection{Relative geometry: factorization} Let $[C\to \mathbb P^N[s]\to \mathbb P^N]$ be a logarithmic map from a centrally aligned curve to an expansion. Recall that $\mathbb P^N[s]$ consists of a union of $\mathbb P^N$ with the projective bundle $\mathbb P(\mathcal O\oplus \mathcal O(1))$. We refer to these latter components as \textbf{the higher levels}. Thus, we will say that subcurve $D\subset C$ maps to \textbf{higher level} if the collapsed map
\[
D\to \mathbb P^N
\]
is contained in $H\subset \mathbb P^N$.

Let $D_1\subset C$ be the maximal genus $1$ subcurve that is mapped to higher level contracted by the map $C\to \mathbb P^N[s]$ in the fiber direction. Let $\delta_1$ be the associated radius from the circuit to the nearest non-contract component. Let $D_2$ be the maximal genus $1$ subcurve that is contracted by the collapsed map to $\mathbb P^N$, and let $\delta_2$ be the associated radius. This coincides with the radius of the underlying map to $\mathbb P^N$. Of course, $\delta_1\leq \delta_2$.

The datum $(\delta_1,\delta_2)$ determines a destabilization $\widetilde C$ of $C$ together with successive contractions $\widetilde C\to \overline C_1\to\overline C_2$. Keeping this definition, we come to the key definition.

\begin{definition}
The map $[C\to \mathbb P^N[s]\to \mathbb P^N]$ \textbf{factorizes completely} if
\begin{itemize}
\item the map $C\to \mathbb P^N[s]$ factors through $\overline C_1$ such that at least one branch of $\overline C_1$ has positive degree in the fiber direction. 
\item the collapsed map to $\mathbb P^N$ factorizes through $\overline C_2$ such that at least one branch of $\overline C_2$ has positive degree.
\end{itemize}
\end{definition}

In particular, if $[C\to \mathbb P^N[s]\to \mathbb P^N]$ is a family of centrally aligned maps over $S$ that factorizes completely, there is a forgetful moduli map $S\to \mathcal{VZ}_{1,n}(\mathbb P^N,d)$, to the principal component of the space of absolute maps.

Let $\mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)$ be stack of maps from centrally aligned curves to expansions of $\mathbb P^N$ that factorize completely.

\begin{thm}\label{thm: log-smoothness}
The stack $\mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)$ is proper and logarithmically non-singular over $\mathrm{Spec} \ \mathbb C$. 
\end{thm}

\begin{proof}
We prove the results via the forgetful morphism
$$
\nu: \mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)\to \mathcal{VZ}_{1,n}(\mathbb P^N,d),
$$
which remembers only the stabilization of the collapsed map. The map is certainly centrally aligned, and we have already argued above that it satisfies the factorization property for $\mathbb P^N$ after composition. The morphism $\nu$ is in fact proper: the verification for the valuative criterion is the essential content of Vakil's Lemma~\cite[Lemma~5.9]{Vak}, and a detailed proof may be found in~\cite[Theorem~4.3]{RSPW}.

We come to logarithmic smoothness. Assume first that the elliptic curve maps into higher level. Note that the relative logarithmic tangent bundle of the expansion, over the base $\mathbb P^N$ is a trivial line bundle of rank $1$, as the fibers are toric. Consider an $S$-family of maps. After replacing the source $C$ by a destabilization, we have maps
\[
C\to \overline{C}_1\to\overline{C}_2\to \mathbb P^N[s]\to \mathbb P^N
\]
factorizing completely. Let $f_B$ and $f_T$ be the maps from $C$ to the base and total space respectively. Examining the morphism $\nu$, we see that there is a map
\[
\mathrm{Def}(C,f_B)\to \mathrm{Obs}(f_T) = H^1(\overline{C}_1,\mathcal O_{\overline{C}_1}),
\]
where the former is the space of deformations of the curve and map to the base, as a factorized centrally aligned map. The latter is the space of obstructions to lifting a map to the base into the total space. The cokernel of this map are the absolute obstructions, which we will show vanishes, proving logarithmic smoothness.

We recall how the group $H^1(\overline{C}_1,\mathcal O_{\overline{C}_1})$ functions as the obstruction group for the lifting. It suffices to work near the minimal grnus $1$ subcurve $D_1$ of $C_1$, since the rest of the curve is rational. This lifting is given by a rational function with prescribed orders of poles given by the slopes of the tropicalization map. That is, if $\alpha$ be the piecewise linear function giving this tropical map, then the lifting is described by a section of the associated bundle $\mathcal O_{C_1}(-\alpha)$.

Given a strict square-zero extension $S'$ of $S$, the piecewise linear function $\alpha$ extends uniquely by strictness to any deformation of the curve. The resulting deformation of $\mathcal O_{C_1}(-\alpha)$ produces an infinitesimal deformation of the trivial bundle in the Picard group, whose class in $H^1(\overline{C}_1,\mathcal O_{\overline{C}_1})$, is the obstruction to deformation. We will show that it is possible to choose a deformation of $(C,f_B)$ that cancels out the obstruction to lifting to $f_T$, and thus the map to the obstruction space above is surjective.

The line bundle $\mathcal O_{C_1}(-\alpha)$ is equivalent to the divisor $\sum a_i x_i$ where $x_i$ are the points connecting $D_1$ to the rest of the curve, and $a_i$ are the slopes of $\alpha$ along the edges corresponding to the $x_i$. Infinitesimally moving the point $x_i$ is a deformation of the curve that is unobstructed by the map $f_B$, since the map is constant on the interiors of the circuits. By deforming the $x_i$, at least one of which is nonzero, we produce a one-dimensional space of obstructions. The absolute obstructions therefore vanish, since they are the cokernel of a surjective map, so the result follows.  
%Consider an $S$-family of expanded maps $[F: C\to \mathbb P^N[s]$. Choose $N$ generic hyperplanes in and let $\Delta = \{H\}\cup\{H_1,\ldots,H_N}$ be this set of hyperplanes. There is a morphism of logarithmic schemes $(\mathbb P^N,\Delta)\to (\mathbb P^N,H)$. This induces a new expansion $\mathbb P^N[\Delta,s]$. Moreover, by the genericity of the $H_i$, they each intersect the image of $C$ in finitely many reduced points. Pulling back the logarithmic structure, we obtain a new logarithmic map 
%\[
%F': C'\to \mathbb P^N[\Delta,s].
%\]
%We make two observations. First, since the logarithmic structure on $C'$ is strict away from $H$, unobstructedness of deformations for $F'$ is equivalent to unobstructedness for $F$. Second, the target degeneration is now a toric degeneration, and the logarithmic tangent bundle is trivial.

\end{proof}

The above theorem guarantees that the singularities of the space of totally factorized maps to expansions is logarithmically smooth. In fact, one can say more in this case.

\begin{cor}
The logarithmically smooth stack $\mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)$ has at worst orbifold singularities, and consequently admits a non-representable cover by a smooth Deligne--Mumford stack.
\end{cor}

\begin{proof}
Since $\mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)$ is logarithmically smooth, it will suffice to show that the cones of its tropicalization are simplicial. To see this, consider a logarithmic stable map to an expansion $C\to \mathbb P^N[s]$ without a central alignment. The tropical moduli cone obtained as the dual of the minimal base monoid can be identified with $\mathbb R_{\geq 0}^{s}$, see for instance~\cite[Section~2.2]{ChenDegeneration}. The alignment procedure is an iterated barycentric subdivision at the level of tropical moduli spaces, as explained in~\cite[Section 4.6]{RSPW}, and such subdivisions preserve the property of being simplicial. We conclude from this that the blowup $\widetilde{\mathcal{VZ}}^{\mathrm{exp}}_{1,\alpha}(\mathbb P^N|H)$ obtained by centrally aligning Kim's spaces has simplicial cones. Finally, the morphism $\mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)\to \widetilde{\mathcal{VZ}}^{\mathrm{exp}}_{1,\alpha}(\mathbb P^N|H)$ is strict, so the cones of $\mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)$ are simplicial, as claimed.
\end{proof}

\subsection{Stratification} The logarithmic smoothness established in Theorem~\ref{thm: log-smoothness} allows us to index the strata of

\subsection{Rigidified rubber and variants}

\bibliographystyle{siam}
\bibliography{Bibliography.bib}

\end{document}

### 2019-02-07 GenusOneRelativeMaps.tex
Added Dhruv files (doesn't compile yet, though)

@@
 \ecd
-where $x_k$ is the section which for every point $v \in Q^\vee_{\RR}$ picks out the vertex of $\sqC_v$ containing the leg $x_k$.
+where $x_k$ is the section which for every point $\kappa \in Q^\vee_{\RR}$ picks out the vertex of $\sqC_\kappa$ containing the leg $x_k$.
 The composition $f \circ x_k \colon Q^\vee_{\RR} \to \RR_{\geq 0}$ defines a piecewise-linear function on $Q_{\RR}^\vee$ whose preimage over the open cone $\RR_{>0}$ consists of those tropical maps where $x_k$ belongs to an internal component.
@@
 Since $x_k$ factors through $C_v$ we may pull back along $x_k$ to obtain
-\begin{equation*} \Lcal_k = x_k^\st\pi^\st \Lcal_k = x_k^\st \OO_\Ccal(\alpha_k x_k) \otimes x_k^\st f^\st\OO(H) = x_k^\st \omega_{\Ccal/S} \otimes \ev_k^\st \OO(H) \end{equation*}
+\begin{equation*} \Lcal_k = x_k^\st\pi^\st \Lcal_k = x_k^\st \OO_\Ccal(\alpha_k x_k) \otimes x_k^\st f^\st\OO(H) = x_k^\st \omega_{\Ccal/S}^{\otimes \alpha_k} \otimes \ev_k^\st \OO(H) \end{equation*}
 and taking Chern classes gives:
@@
 \end{prop}
-
-There are 
-\newpage
-
-\subsection{Wonderful trick to compute reduced rubber integrals}
-
-Our method to compute the rubber VZ integrals which appear in the recursion:
-
-First, if the degree is zero, then it's Pixton's formula minus the locus with a single rational tail containing all the markings. So focus on positive degree case.
-
-If there is a relative marking with no insertion, we can forget that marking and compare to the main component of absolute maps to $H$.
-
-Suppose therefore that every relative marking has insertions.
-At least one of these must have only evaluation classes (since any of the nodal markings will only have evaluation classes).
-Fix that one: call it $x$.
-
-Consider the rubber VZ space with one additional marking $x_0$ with contact order zero. On this rubber space, take same as insertions as before, except replace $\ev_x$ with $\ev_{x_0}$.
-
-Consider the locus where the target splits. This can be expressed in terms of tautological classes in several ways (which gives us the left-hand side).
-
-Firstly, by E.
-Katz's thesis (actually, this is an easy argument using $\MM_{0,2}$ Vakil--Zinger identification of tangent and cotangent spaces on a genus zero curve).
-We get $\Psi_0 + \Psi_\infty$ (target psi classes).
-
-Alternatively, take the piecewise-linear $\RR_{\geq 0}$-valued function on the tropical moduli space of the VZ rubber space which sends a tropical map to the weighted sum of the edge lengths (weighted by expansion factors).
-We can see that the Chern class is weighted sum of source psi classes (which agree with the target psi classes by pull-back), and we calculate the vanishing orders by the same locally toric method.
-
-Either way, the left-hand side is determined.
-Now look at the right-hand side.
-One component of this is where the $x_0$ and $x$ are contained in a trivial bubble.
-Therefore $\ev_x = \ev_0$ and we recover the integral we are interested in.
-
-On the other components, the marking $x$ will always be insertion-free; hence we can forget $x$.
-So we get an integral over main component of maps to $H$.
-Note that this reduced invariant of $H$ will be of lower degree than the one we set out to compute.
-So the recursion isn't circular.
-\newpage
 

### 2019-02-07 GenusOneRelativeMaps.tex
Started cleaning up DRC recursion

--- 2019-02-06 GenusOneRelativeMaps.tex
@@
 
-\subsection{Wonderful trick to compute reduced rubber integrals}
-
-Our method to compute the rubber VZ integrals which appear in the recursion:
-
-First, if the degree is zero, then it's Pixton's formula minus the locus with a single rational tail containing all the markings. So focus on positive degree case.
+\subsection{Recursion formula for reduced rubber integrals} In the recursion above, certain terms appear which are integrals over moduli spaces of reduced log stable maps to rubber (as defined in \S \ref{}):
+\begin{equation*}\VZ_{1,\alpha}(P|H_0+H_\infty)_{\Gm}.\end{equation*}
+In this section we provide a recursive algorithm for computing such integrals. For convenience we denote the \textbf{horizontal degree} of the rubber map by:
+\begin{equation*} d := \sum_{i=1}^n \alpha_i .\end{equation*}
+Recall that the $\alpha_i$ may be positive or negative (recording tangencies with respect to $H_\infty$ and $H_0$, respectively) and that $d \geq 0$ always.
+First suppose that $d=0$.
+Then the usual rubber moduli space decomposes as
+\begin{equation*} \MLog_{1,\alpha}(P|H_0 + H_\infty)_{\Gm} = \MLog_{1,\alpha}(\PP^1|0+\infty)_{\Gm} \times H \end{equation*}
+and the first term on the right-hand side is birational to the double ramification locus in $\ol\Mcal_{1,n}$.
+This locus has a main component (the closure of the locus of smooth curves) and one other ``exceptional'' component, consisting of split curves where all the markings belong to the rational tail.
+The corresponding reduced rubber space is birational to the main component, and thus we can identify its class by subtracting off the class of the exceptional component.
+This gives
+\begin{equation*} \pi_\st [\VZ_{1,\alpha}(P|H_0+H_\infty)_{\Gm}] = \left( [\ol\Mcal_{1,n}^\alpha] - [D] \right) \times [H] \in \Achow_\st ( \ol\Mcal_{1,n} \times H ) = \Achow_\st ( \ol\Mcal_{1,n}(H,0) ) \end{equation*}
+where $\pi \colon \VZ_{1,\alpha}(P|H_0+H_\infty)_{\Gm} \to \ol\Mcal_{1,n}(H,0)$ is the map which forgets the log structure and collapses the map, $D$ is the boundary locus of split curves described above, and $[\ol\Mcal_{1,n}^\alpha]$ is the classical double ramification cycle, which has an explicit formula in terms of tautological classes \cite{Hain,JPPZ}.
+This allows us to compute the integral over the rubber space as a tautological integral on the moduli space of curves.
+
+Now suppose that $d>0$. If there is a marking $x_k$ which carries no insertion and has $\alpha_k \neq 0$, then consider the morphism which forgets $x_k$ and collapses the map:
+\begin{equation*} \VZ_{1,\alpha}(P|H_0+H_\infty)_{\Gm} \to \VZ_{1,n-1}(H). \end{equation*}
+
+\newpage
 
@@
 We use the log structure on $\VZ_{1,\alpha}(\PP^N|H)$ to construct a line bundle $\Lcal_k$ together with a section $s_k$ vanishing along this locus.
-We use the correspondence with tropical geometry to identify $\cchern_1(\Lcal_k)$ in terms of tautological classes on $\VZ_{1,\alpha}(\PP^N|H)$, and we compute the vanishing order of $s_k$ along the components of its zero set.
+We use the correspondence with tropical geometry to identify $\cchern_1(\Lcal_k)$ in terms of tautological classes on $\VZ_{1,\alpha}(\PP^N|H)$, and to compute the vanishing order of $s_k$ along the components of its zero set.
 
@@
 \ecd
-where $x_k$ is the section which for every point $v \in Q^\vee_{\RR}$ picks out the vertex of $\sqC_v$ containing the leg $x_k$.
+where $x_k$ is the section which for every point $\lambda \in Q^\vee_{\RR}$ picks out the vertex of $\sqC_\lambda$ containing the leg $x_k$.
 The composition $f \circ x_k \colon Q^\vee_{\RR} \to \RR_{\geq 0}$ defines a piecewise-linear function on $Q_{\RR}^\vee$ whose preimage over the open cone $\RR_{>0}$ consists of those tropical maps where $x_k$ belongs to an internal component.
-Dually we obtain an element of the minimal monoid $Q$ and globally a section of the ghost sheaf on $\MLog_{1,\alpha}(\PP^N|H)$.
+Dually we obtain an element of the minimal monoid $Q$ at the moduli point, and this globalises to produce a section of the ghost sheaf on $\MLog_{1,\alpha}(\PP^N|H)$.
 In the usual way this induces a line bundle and section $(\Lcal_k,s_k)$ on the moduli space, and the tropical description above shows that the zero locus of $s_k$ is (set-theoretically) the locus where $x_k$ belongs to an internal component.
@@
 The section $f^\flat(1) \in \Gamma(C,\ol{M}_C)$ has associated line bundle $f^\st\OO(H)$.
-By construction $f^\flat(1)$ assigns $\mu$ to $v$ and has slope $\alpha_k$ along the leg $x_k$.
+If we let $v$ denote the vertex containing $x_k$, then by construction $f^\flat(1)$ assigns $\mu$ to $v$ and has slope $\alpha_k$ along the leg $x_k$.
 Thus if we consider the difference $f^\flat(1) - \pi^\flat(\mu)$ then this assigns $0$ to $v$ and still has slope $\alpha_k$ along $x_k$.
@@
 Since $x_k$ factors through $C_v$ we may pull back along $x_k$ to obtain
-\begin{equation*} \Lcal_k = x_k^\st\pi^\st \Lcal_k = x_k^\st \OO_\Ccal(\alpha_k x_k) \otimes x_k^\st f^\st\OO(H) = x_k^\st \omega_{\Ccal/S} \otimes \ev_k^\st \OO(H) \end{equation*}
+\begin{equation*} \Lcal_k = x_k^\st\pi^\st \Lcal_k = x_k^\st \OO_{C_k}(-\alpha_k x_k) \otimes x_k^\st f^\st\OO(H) = x_k^\st \OO_{C_k}(-\alpha_k x_k) \otimes \ev_k^\st \OO(H) \end{equation*}
 and taking Chern classes gives:
@@
 This gives the construction of $(\Lcal_k,s_k)$ on $\MLog_{1,\alpha}(\PP^N|H)$; the construction on $\VZ_{1,\alpha}(\PP^N|H)$ is given by pull-back.
-Notice in particular that $\psi_k$ should be interpreted as a \emph{collapsed psi class} on $\VZ_{1,\alpha}(\PP^N|H)$, i.e.
+Notice in particular that $\psi_k$ should be interpreted as a \textbf{collapsed psi class} on $\VZ_{1,\alpha}(\PP^N|H)$, i.e.
 a psi class coming from the stabilised curve of the collapsed map.
@@
 
-\begin{remark} This construction gives the natural logarithmic analogue of Gathmann's line bundle \cite[Construction 2.1]{Ga}.
-One of the benefits of the logarithmic approach is to make the computation of multiplicities entirely combinatorial; see \S \ref{} below.\end{remark}
+\begin{remark} This construction gives the natural logarithmic analogue of Gathmann's line bundle and section \cite[Construction 2.1]{Ga}.
+A benefit of the logarithmic approach is to make the computation of vanishing orders entirely combinatorial (see \S \ref{} below), circumventing the difficult technical calculation given by Gathmann.
+\end{remark}
 
@@
 We perform a log modification of this space as detailed below.
-For a log curve $C\to S=\Spec(k=\bar k)$, modify the dual graph of $C$ by replacing the minimal genus one subcurve (in case it is a circle of $\PP^1$) by a single vertex of genus one, called the \emph{core} and denoted by $\circ$, and define a piecewise linear function with values in $\overline{\pazocal M}_S$ on such a graph by setting \[\lambda(v)=\sum_{q\in[\circ,v]}\rho_q,\]
+For a log curve $C\to S=\Spec(k=\bar k)$, modify the dual graph of $C$ by replacing the minimal genus one subcurve (in case it is a circle of $\PP^1$) by a single vertex of genus one, called the \textbf{core} and denoted by $\circ$, and define a piecewise linear function with values in $\overline{\pazocal M}_S$ on such a graph by setting \[\lambda(v)=\sum_{q\in[\circ,v]}\rho_q,\]
 where the $\rho_q$ are the smoothing parameters of the nodes $q$ separating $v$ from the core.
@@
 
-(*) \emph{the circle of radius $\delta$ around $\circ$ passes through $\geq1$ vertex of positive $f$-degree}.
+(*) \textbf{the circle of radius $\delta$ around $\circ$ passes through $\geq1$ vertex of positive $f$-degree}.
 
 \noindent Furthermore, we require all the values of $\lambda$ to be comparable with $\delta$, and among themselves whenever they are $\leq \delta$.
-This is called a \emph{centrally aligned} log structure and carries enough information to define a contraction $\nu\colon C\to \bar{C}$, possibly after a semistabilisation of $(C,f)$ - in fact even more.
+This is called a \textbf{centrally aligned} log structure and carries enough information to define a contraction $\nu\colon C\to \bar{C}$, possibly after a semistabilisation of $(C,f)$ - in fact even more.
 The space thus obtained, $\widetilde \VZ_{1,\alpha}(\PP^N|H,d)$, is a log modification of $\M{1}{\alpha}{\PP^N|H}{d}$.

### 2019-02-07 GenusOneRelativeMaps.tex
Almost finished reduced rubber section

@@
 
-\subsection{Recursion formula for reduced rubber integrals} In the recursion above, certain terms appear which are integrals over moduli spaces of reduced log stable maps to rubber (as defined in \S \ref{}):
+\subsection{Recursion procedure for reduced rubber integrals} In the recursion above, certain terms appear which are integrals over moduli spaces of reduced log stable maps to rubber (as defined in \S \ref{}):
 \begin{equation*}\VZ_{1,\alpha}(P|H_0+H_\infty)_{\Gm}.\end{equation*}
@@
 Now suppose that $d>0$. If there is a marking $x_k$ which carries no insertion and has $\alpha_k \neq 0$, then consider the morphism which forgets $x_k$ and collapses the map:
-\begin{equation*} \VZ_{1,\alpha}(P|H_0+H_\infty)_{\Gm} \to \VZ_{1,n-1}(H). \end{equation*}
+\begin{equation*} \VZ_{1,\alpha}(P|H_0+H_\infty)_{\Gm} \xrightarrow{\pi} \VZ_{1,n-1}(H,d). \end{equation*}
+These moduli spaces are log smooth and of the same dimension.
+Over the nice locus in $\VZ_{1,n-1}(H,d)$, $\pi$ has degree $\alpha_k^2$, arising from a choice of $\alpha_k$-torsion point on the source elliptic curve.
+Thus we have:
+\begin{equation*} \pi_\st [\VZ_{1,\alpha}(P|H_0+H_\infty)_{\Gm}] = \alpha_k^2\cdot [\VZ_{1,n-1}(H,d)].\end{equation*}
+Since all the insertions are pulled back from the right-hand side (up to modifying psi classes by some boundary strata which we can then also compute recursively) we can perform the integral on $\VZ_{1,n-1}(H,d)$ inductively.\footnote{(Navid) Say something here about the degree being smaller}
+
+It remains to deal with the case where all of the relative markings carry insertions.
+The idea is to reduce to the case above by introducing an additional marking.
+Note first that every reduced rubber integral which appears in our recursion must either have a marking of negative tangency (i.e.
+tangent to $H_0$), or a marking with no insertions: indeed, the only boundary locus with no negative-tangency marking occurs when the entire curve is mapped to higher level, in which case (since we are assuming $d>0$) the curve is generically irreducible, and on this curve we have at least one fictitious marking (of positive tangency $1$) with no insertion.
+
+Therefore we may assume that there is at least one point of negative tangency, corresponding to a node at which we will glue.
+Notice that in our recursion these points only ever carry evaluation classes.
+Consider the following rubber space of dimension one higher, obtained by introducing an additional non-relative marking:
+\begin{equation} \label{bigger rubber space}\VZ_{1,\alpha \cup (0)}(P|H_0+H_\infty)_{\Gm}. \end{equation}
+Given a moduli point in this space, consider the piecewise-linear function on the associated tropical moduli space which sends a tropical map to the sum of the target edge lengths.
+This defines a line bundle and section on the space \eqref{bigger rubber space} which vanishes precisely on the locus where the target splits; moreover the vanishing orders may be read off from the tropical data as in \S \ref{}.
+It is not hard to see \cite{EKatz} that the first Chern class of the line bundle is
+$\Psi_0 + \Psi_\infty$, a sum of target psi classes which may be identified with evaluation and psi classes on the source curve as in \cite[Construction 5.1.17]{GathmannThesis}.
+
+Now choose a point $x_1$ which carries only evaluation classes, and let $x_0$ denote the new non-relative marking we have introduced.
+If $\gamma$ was the class we were originally trying to integrate, consider the class $\tilde\gamma$ on \eqref{bigger rubber space} obtained from $\gamma$ by replacing $\ev_1$ by $\ev_0$.
+We obtain a recursion formula:
+\begin{equation*} (\Psi_0+\Psi_\infty)\cdot \tilde\gamma \cap [\VZ_{1,\alpha\cup(0)}(P|H_0+H_\infty)_{\Gm}] = \sum_{\Gamma} m_\Gamma \cdot \tilde\gamma \cap [\ol\Mcal_{\Gamma}]. \end{equation*}
+The right-hand side is a sum over irreducible components $\ol\Mcal_\Gamma$ of the locus where the target splits, with multiplicites $m_\Gamma$ calculated from the tropical picture.
+Each of these components can be written as a fibre product of (reduced) rubber spaces.
+One of these components is the locus where $x_0$ and $x_1$ belong to a trivial rational bubble:
+
+[FIGURE]
+
+The corresponding moduli space is $\VZ_{1,\alpha}(P|H_0+H_\infty)_{\Gm}$ and we have $\ev_0=\ev_1$ here, so the contribution of this locus is precisely the original rubber integral we were trying to calculate.
+The remaining terms on the right-hand side have, by design, no insertion at $x_1$ and hence can be computed via the trick described previously.
+Finally, the left-hand side also has no insertion at $x_1$ and so can be computed by the same method.
+Here we are assuming that $x_1$ is not the only negative-tangency marking, so that $\Psi_0$ can be interpreted as an insertion on a marking different from $x_1$; if this is not the case, then a similar argument works by splitting $x_1$ into two markings of tangency $(\alpha_1+1,-1)$.
+
+\textbf{What if $\alpha_1=-1$?}
 

### 2019-02-08 GenusOneRelativeMaps.tex
Finished description of rubber recursion

@@
 \begin{equation*}\VZ_{1,\alpha}(P|H_0+H_\infty)_{\Gm}.\end{equation*}
-In this section we provide a recursive algorithm for computing such integrals. For convenience we denote the \textbf{horizontal degree} of the rubber map by:
+In this section we provide a recursive algorithm for computing such integrals.
+We have three main techniques at our disposal: direct comparison with the double ramification cycle, forgetting of a marking with no insertion, and rubber recursion.
+Each technique has its own domain of applicability, and these domains have non-trivial intersection.
+For convenience we denote the \textbf{horizontal degree} of the rubber map by:
 \begin{equation*} d := \sum_{i=1}^n \alpha_i .\end{equation*}
@@
 where $\pi \colon \VZ_{1,\alpha}(P|H_0+H_\infty)_{\Gm} \to \ol\Mcal_{1,n}(H,0)$ is the map which forgets the log structure and collapses the map, $D$ is the boundary locus of split curves described above, and $[\ol\Mcal_{1,n}^\alpha]$ is the classical double ramification cycle, which has an explicit formula in terms of tautological classes \cite{Hain,JPPZ}.
-This allows us to compute the integral over the rubber space as a tautological integral on the moduli space of curves.
+These observations allow us to compute the integral over the rubber space as a tautological integral on the moduli space of curves.
 
@@
 \begin{equation*} \VZ_{1,\alpha}(P|H_0+H_\infty)_{\Gm} \xrightarrow{\pi} \VZ_{1,n-1}(H,d). \end{equation*}
-These moduli spaces are log smooth and of the same dimension.
+The moduli spaces above are log smooth and of the same dimension.
 Over the nice locus in $\VZ_{1,n-1}(H,d)$, $\pi$ has degree $\alpha_k^2$, arising from a choice of $\alpha_k$-torsion point on the source elliptic curve.
@@
 \begin{equation*} \pi_\st [\VZ_{1,\alpha}(P|H_0+H_\infty)_{\Gm}] = \alpha_k^2\cdot [\VZ_{1,n-1}(H,d)].\end{equation*}
-Since all the insertions are pulled back from the right-hand side (up to modifying psi classes by some boundary strata which we can then also compute recursively) we can perform the integral on $\VZ_{1,n-1}(H,d)$ inductively.\footnote{(Navid) Say something here about the degree being smaller}
+Since all the insertions are pulled back from the right-hand side (up to modifying psi classes by some boundary strata which we can then also compute recursively) we can perform the integral on $\VZ_{1,n-1}(H,d)$ inductively.
+Notice that, when we apply our recursion \ref{} to compute a reduced invariant of $H$, the only non-trivial reduced rubber integrals which appear will have smaller degree than the one we started with, so the calculation is not circular.
 
@@
 Note first that every reduced rubber integral which appears in our recursion must either have a marking of negative tangency (i.e.
-tangent to $H_0$), or a marking with no insertions: indeed, the only boundary locus with no negative-tangency marking occurs when the entire curve is mapped to higher level, in which case (since we are assuming $d>0$) the curve is generically irreducible, and on this curve we have at least one fictitious marking (of positive tangency $1$) with no insertion.
+tangent to $H_0$), or a marking with no insertions: indeed, the only boundary loci with no negative-tangency markings have the entire curve mapped to higher level, in which case (since we are assuming $d>0$, so we are not in the $C_0$ case) the curve is generically irreducible, and on this curve we have at least one fictitious marking (of positive tangency $1$) with no insertion.
 
@@
 
-Now choose a point $x_1$ which carries only evaluation classes, and let $x_0$ denote the new non-relative marking we have introduced.
-If $\gamma$ was the class we were originally trying to integrate, consider the class $\tilde\gamma$ on \eqref{bigger rubber space} obtained from $\gamma$ by replacing $\ev_1$ by $\ev_0$.
+Now choose a negative-tangency point $x_1$ which carries only evaluation classes, and let $x_0$ denote the new non-relative marking we have introduced.
+If $\gamma$ was the class we were originally trying to integrate, consider the class $\tilde\gamma$ on \eqref{bigger rubber space} obtained from $\gamma$ by replacing $\ev_1^\st$ by $\ev_0^\st$.
 We obtain a recursion formula:
 \begin{equation*} (\Psi_0+\Psi_\infty)\cdot \tilde\gamma \cap [\VZ_{1,\alpha\cup(0)}(P|H_0+H_\infty)_{\Gm}] = \sum_{\Gamma} m_\Gamma \cdot \tilde\gamma \cap [\ol\Mcal_{\Gamma}]. \end{equation*}
-The right-hand side is a sum over irreducible components $\ol\Mcal_\Gamma$ of the locus where the target splits, with multiplicites $m_\Gamma$ calculated from the tropical picture.
+The right-hand side is a sum over irreducible components $\ol\Mcal_\Gamma$ of the locus where the target splits, with multiplicites $m_\Gamma$ calculated from the tropical data.
 Each of these components can be written as a fibre product of (reduced) rubber spaces.
@@
 The corresponding moduli space is $\VZ_{1,\alpha}(P|H_0+H_\infty)_{\Gm}$ and we have $\ev_0=\ev_1$ here, so the contribution of this locus is precisely the original rubber integral we were trying to calculate.
-The remaining terms on the right-hand side have, by design, no insertion at $x_1$ and hence can be computed via the trick described previously.
+The remaining terms on the right-hand side can be written either as a product of rubber integrals of smaller degree (which we can compute recursively), or rubber integrals of the same degree but with no insertion at $x_1$ (which we can compute by forgetting $x_1$).
 Finally, the left-hand side also has no insertion at $x_1$ and so can be computed by the same method.
-Here we are assuming that $x_1$ is not the only negative-tangency marking, so that $\Psi_0$ can be interpreted as an insertion on a marking different from $x_1$; if this is not the case, then a similar argument works by splitting $x_1$ into two markings of tangency $(\alpha_1+1,-1)$.
-
-\textbf{What if $\alpha_1=-1$?}
+Here we are assuming that $x_1$ is not the only negative-tangency marking, so that $\Psi_0$ can be interpreted as an insertion on a marking different from $x_1$.
+
+If $x_1$ is in fact the only negative-tangency marking, then we can modify the above argument by considering the following rubber space of dimension two larger:
+\begin{equation}\label{rubber space two extra markings} \VZ_{1,\alpha\cup(0,0)}(P|H_0+H_\infty)_{\Gm} \end{equation}
+Let us denote the newly-introduced non-relative markings by $x_0$ and $x_{n+1}$.
+We now let $\tilde\gamma$ denote the class obtained from $\gamma$ by replacing $\ev_1^\st$ by $\ev_0^\st$ and then multiplying by $\psi_{n+1}$.
+Following \cite{EKatz}\footnote{(Navid) Tropica interpretation of this?
+Vanishing multiplicities?}, there is a line bundle with a section cutting out the locus where $x_{n+1}$ does not belong to the leftmost component of the target.
+The first Chern class of this line bundle is $\Psi_\infty+\ev_{n+1}^*H$, which we may multiply with $\tilde\gamma$ and integrate over \eqref{rubber space two extra markings} to obtain a rubber integral with no insertion at $x_1$ (which we may then compute by forgetting $x_1$).
+On the right-hand side we obtain the integral of $\tilde\gamma$ over the loci where $x_{n+1}$ does not belong to the leftmost component of the target (this is just a union of some of the irreducible components of the split locus described above).
+One such locus is the following
+[FIGURE]
+and integrating $\tilde\gamma$ over this locus gives
+\begin{equation*} \gamma\cdot\psi_{n+1}\cap [\VZ_{1,\alpha\cup(0)}(P|H_0+H_\infty)_{\Gm}] \end{equation*}
+which we may identify with a (nonzero) multiple of our original rubber integral via the rubber dilaton equation (see\cite{MaulikPandharipande}; the same proof carries over to the reduced setting\footnote{(Navid) Think about this a bit}).
+The remaining loci may be computed recursively exactly as before, and thus we obtain a complete recursion procedure.
+
+\begin{remark} This idea --- of finding a section of a line bundle cutting out the locus of split curves, and using this to derive recursion formulae for rubber integrals --- has been pursued in the non-reduced setting in \cite{EKatz}.\end{remark}
 
@@
 Then we can safely move all the insertions (including the target psi class) onto one of these, and leave the other free to forget.
-Note this works even if $\alpha_k=1$.\medskip
+\medskip
 

### 2019-02-08 GenusOneRelativeMaps.tex
minor changes

@@
 
-If there is a relative marking with no insertion, we can forget that marking and compare to the main component of absolute maps to $H$.
-
-Suppose therefore that every relative marking has insertions.
-At least one of these must have only evaluation classes (since any of the nodal markings will only have evaluation classes).
-Fix that one: call it $x$.
-
-Consider the rubber VZ space with one additional marking $x_0$ with contact order zero. On this rubber space, take same as insertions as before, except replace $\ev_x$ with $\ev_{x_0}$.
-
-Consider the locus where the target splits. This can be expressed in terms of tautological classes in several ways (which gives us the left-hand side).
-
-Firstly, by E.
-Katz's thesis (actually, this is an easy argument using $\MM_{0,2}$ Vakil--Zinger identification of tangent and cotangent spaces on a genus zero curve).
-We get $\Psi_0 + \Psi_\infty$ (target psi classes).
-
-Alternatively, take the piecewise-linear $\RR_{\geq 0}$-valued function on the tropical moduli space of the VZ rubber space which sends a tropical map to the weighted sum of the edge lengths (weighted by expansion factors).
-We can see that the Chern class is weighted sum of source psi classes (which agree with the target psi classes by pull-back), and we calculate the vanishing orders by the same locally toric method.
-
-Either way, the left-hand side is determined.
-Now look at the right-hand side.
-One component of this is where the $x_0$ and $x$ are contained in a trivial bubble.
-Therefore $\ev_x = \ev_0$ and we recover the integral we are interested in.
-
-On the other components, the marking $x$ will always be insertion-free; hence we can forget $x$.
-So we get an integral over main component of maps to $H$.
-Note that this reduced invariant of $H$ will be of lower degree than the one we set out to compute.
-So the recursion isn't circular.
-
-\textbf{Addendum} You have to be a bit careful about the target psi class on the larger space.
-We need to integrate over this, and the standard approach is to identify it with $\alpha_i \psi_i + \ev_i^\st H$ for $x_i$ any marking tangent to the corresponding divisor.
-Remember we are trying to move all the insertions off $x_k$.
-If there is some other marking $x_i$ tangent to the same divisor as $x_k$ then we're fine - just interpret the target psi class as an insertion on $x_i$.
-If not, we're forced to get an insertion at $x_k$ on the larger space, and we're stuck.
-In this case, we need to modify the recursion scheme slightly: instead of introducing an additional non-relative marking, split $x_k$ into two markings of tangency $1$ and $\alpha_k - 1$ (really, any splitting of $\alpha_k$ will probably do).
-Then we can safely move all the insertions (including the target psi class) onto one of these, and leave the other free to forget.
-\medskip
-
-\textbf{Note} It might be worth noting that this idea of recursion on rubber spaces by taking $c_1$ of a line bundle appears to have already appeared in E.
-Katz's paper.
-Maybe he was right that there's a lot of good stuff there!
-
-\newpage
-
 \subsection{Gathmann's line bundle via tropical geometry} For each marking $x_k$ we consider the locus in $\VZ_{1,\alpha}(\PP^N|H)$ where $x_k$ belongs to an internal component of the collapsed map.

### 2019-02-18 GenusOneRelativeMaps.tex
Brutal edit: keeping only what we need

@@
 
-\subsection{Recursion procedure for reduced rubber integrals} In the recursion above, certain terms appear which are integrals over moduli spaces of reduced log stable maps to rubber (as defined in \S \ref{}):
-\begin{equation*}\VZ_{1,\alpha}(P|H_0+H_\infty)_{\Gm}.\end{equation*}
-In this section we provide a recursive algorithm for computing such integrals.
-We have three main techniques at our disposal: direct comparison with the double ramification cycle, forgetting of a marking with no insertion, and rubber recursion.
-Each technique has its own domain of applicability, and these domains have non-trivial intersection.
-For convenience we denote the \textbf{horizontal degree} of the rubber map by:
-\begin{equation*} d := \sum_{i=1}^n \alpha_i .\end{equation*}
-Recall that the $\alpha_i$ may be positive or negative (recording tangencies with respect to $H_\infty$ and $H_0$, respectively) and that $d \geq 0$ always.
-First suppose that $d=0$.
-Then the usual rubber moduli space decomposes as
-\begin{equation*} \MLog_{1,\alpha}(P|H_0 + H_\infty)_{\Gm} = \MLog_{1,\alpha}(\PP^1|0+\infty)_{\Gm} \times H \end{equation*}
-and the first term on the right-hand side is birational to the double ramification locus in $\ol\Mcal_{1,n}$.
-This locus has a main component (the closure of the locus of smooth curves) and one other ``exceptional'' component, consisting of split curves where all the markings belong to the rational tail.
-The corresponding reduced rubber space is birational to the main component, and thus we can identify its class by subtracting off the class of the exceptional component.
-This gives
-\begin{equation*} \pi_\st [\VZ_{1,\alpha}(P|H_0+H_\infty)_{\Gm}] = \left( [\ol\Mcal_{1,n}^\alpha] - [D] \right) \times [H] \in \Achow_\st ( \ol\Mcal_{1,n} \times H ) = \Achow_\st ( \ol\Mcal_{1,n}(H,0) ) \end{equation*}
-where $\pi \colon \VZ_{1,\alpha}(P|H_0+H_\infty)_{\Gm} \to \ol\Mcal_{1,n}(H,0)$ is the map which forgets the log structure and collapses the map, $D$ is the boundary locus of split curves described above, and $[\ol\Mcal_{1,n}^\alpha]$ is the classical double ramification cycle, which has an explicit formula in terms of tautological classes \cite{Hain,JPPZ}.
-These observations allow us to compute the integral over the rubber space as a tautological integral on the moduli space of curves.
-
-Now suppose that $d>0$. If there is a marking $x_k$ which carries no insertion and has $\alpha_k \neq 0$, then consider the morphism which forgets $x_k$ and collapses the map:
-\begin{equation*} \VZ_{1,\alpha}(P|H_0+H_\infty)_{\Gm} \xrightarrow{\pi} \VZ_{1,n-1}(H,d). \end{equation*}
-The moduli spaces above are log smooth and of the same dimension.
-Over the nice locus in $\VZ_{1,n-1}(H,d)$, $\pi$ has degree $\alpha_k^2$, arising from a choice of $\alpha_k$-torsion point on the source elliptic curve.
-Thus we have:
-\begin{equation*} \pi_\st [\VZ_{1,\alpha}(P|H_0+H_\infty)_{\Gm}] = \alpha_k^2\cdot [\VZ_{1,n-1}(H,d)].\end{equation*}
-Since all the insertions are pulled back from the right-hand side (up to modifying psi classes by some boundary strata which we can then also compute recursively) we can perform the integral on $\VZ_{1,n-1}(H,d)$ inductively.
-Notice that, when we apply our recursion \ref{} to compute a reduced invariant of $H$, the only non-trivial reduced rubber integrals which appear will have smaller degree than the one we started with, so the calculation is not circular.
-
-It remains to deal with the case where all of the relative markings carry insertions.
-The idea is to reduce to the case above by introducing an additional marking.
-Note first that every reduced rubber integral which appears in our recursion must either have a marking of negative tangency (i.e.
-tangent to $H_0$), or a marking with no insertions: indeed, the only boundary loci with no negative-tangency markings have the entire curve mapped to higher level, in which case (since we are assuming $d>0$, so we are not in the $C_0$ case) the curve is generically irreducible, and on this curve we have at least one fictitious marking (of positive tangency $1$) with no insertion.
-
-Therefore we may assume that there is at least one point of negative tangency, corresponding to a node at which we will glue.
-Notice that in our recursion these points only ever carry evaluation classes.
-Consider the following rubber space of dimension one higher, obtained by introducing an additional non-relative marking:
-\begin{equation} \label{bigger rubber space}\VZ_{1,\alpha \cup (0)}(P|H_0+H_\infty)_{\Gm}. \end{equation}
-Given a moduli point in this space, consider the piecewise-linear function on the associated tropical moduli space which sends a tropical map to the sum of the target edge lengths.
-This defines a line bundle and section on the space \eqref{bigger rubber space} which vanishes precisely on the locus where the target splits; moreover the vanishing orders may be read off from the tropical data as in \S \ref{}.
-It is not hard to see \cite{EKatz} that the first Chern class of the line bundle is
-$\Psi_0 + \Psi_\infty$, a sum of target psi classes which may be identified with evaluation and psi classes on the source curve as in \cite[Construction 5.1.17]{GathmannThesis}.
-
-Now choose a negative-tangency point $x_1$ which carries only evaluation classes, and let $x_0$ denote the new non-relative marking we have introduced.
-If $\gamma$ was the class we were originally trying to integrate, consider the class $\tilde\gamma$ on \eqref{bigger rubber space} obtained from $\gamma$ by replacing $\ev_1^\st$ by $\ev_0^\st$.
-We obtain a recursion formula:
-\begin{equation*} (\Psi_0+\Psi_\infty)\cdot \tilde\gamma \cap [\VZ_{1,\alpha\cup(0)}(P|H_0+H_\infty)_{\Gm}] = \sum_{\Gamma} m_\Gamma \cdot \tilde\gamma \cap [\ol\Mcal_{\Gamma}]. \end{equation*}
-The right-hand side is a sum over irreducible components $\ol\Mcal_\Gamma$ of the locus where the target splits, with multiplicites $m_\Gamma$ calculated from the tropical data.
-Each of these components can be written as a fibre product of (reduced) rubber spaces.
-One of these components is the locus where $x_0$ and $x_1$ belong to a trivial rational bubble:
-
-[FIGURE]
-
-The corresponding moduli space is $\VZ_{1,\alpha}(P|H_0+H_\infty)_{\Gm}$ and we have $\ev_0=\ev_1$ here, so the contribution of this locus is precisely the original rubber integral we were trying to calculate.
-The remaining terms on the right-hand side can be written either as a product of rubber integrals of smaller degree (which we can compute recursively), or rubber integrals of the same degree but with no insertion at $x_1$ (which we can compute by forgetting $x_1$).
-Finally, the left-hand side also has no insertion at $x_1$ and so can be computed by the same method.
-Here we are assuming that $x_1$ is not the only negative-tangency marking, so that $\Psi_0$ can be interpreted as an insertion on a marking different from $x_1$.
-
-If $x_1$ is in fact the only negative-tangency marking, then we can modify the above argument by considering the following rubber space of dimension two larger:
-\begin{equation}\label{rubber space two extra markings} \VZ_{1,\alpha\cup(0,0)}(P|H_0+H_\infty)_{\Gm} \end{equation}
-Let us denote the newly-introduced non-relative markings by $x_0$ and $x_{n+1}$.
-We now let $\tilde\gamma$ denote the class obtained from $\gamma$ by replacing $\ev_1^\st$ by $\ev_0^\st$ and then multiplying by $\psi_{n+1}$.
-Following \cite{EKatz}\footnote{(Navid) Tropica interpretation of this?
-Vanishing multiplicities?}, there is a line bundle with a section cutting out the locus where $x_{n+1}$ does not belong to the leftmost component of the target.
-The first Chern class of this line bundle is $\Psi_\infty+\ev_{n+1}^*H$, which we may multiply with $\tilde\gamma$ and integrate over \eqref{rubber space two extra markings} to obtain a rubber integral with no insertion at $x_1$ (which we may then compute by forgetting $x_1$).
-On the right-hand side we obtain the integral of $\tilde\gamma$ over the loci where $x_{n+1}$ does not belong to the leftmost component of the target (this is just a union of some of the irreducible components of the split locus described above).
-One such locus is the following
-[FIGURE]
-and integrating $\tilde\gamma$ over this locus gives
-\begin{equation*} \gamma\cdot\psi_{n+1}\cap [\VZ_{1,\alpha\cup(0)}(P|H_0+H_\infty)_{\Gm}] \end{equation*}
-which we may identify with a (nonzero) multiple of our original rubber integral via the rubber dilaton equation (see\cite{MaulikPandharipande}; the same proof carries over to the reduced setting\footnote{(Navid) Think about this a bit}).
-The remaining loci may be computed recursively exactly as before, and thus we obtain a complete recursion procedure.
-
-\begin{remark} This idea --- of finding a section of a line bundle cutting out the locus of split curves, and using this to derive recursion formulae for rubber integrals --- has been pursued in the non-reduced setting in \cite{EKatz}.\end{remark}
-
-\newpage
-
-\subsection{Gathmann's line bundle via tropical geometry} For each marking $x_k$ we consider the locus in $\VZ_{1,\alpha}(\PP^N|H)$ where $x_k$ belongs to an internal component of the collapsed map.
+\section{Gathmann's line bundle via tropical geometry} For each marking $x_k$ we consider the locus in $\VZ_{1,\alpha}(\PP^N|H)$ where $x_k$ belongs to an internal component of the collapsed map.
 We use the log structure on $\VZ_{1,\alpha}(\PP^N|H)$ to construct a line bundle $\Lcal_k$ together with a section $s_k$ vanishing along this locus.
@@
 
-\section{Introduction}
-
-\subsection{Statement of the problem} Contrary to the genus zero case, the moduli space of genus one maps to projective space - with or without markings - is far from smooth; indeed it has various boundary components of different dimensions, representing maps that contract a genus one curve and have all the degree supported on a number of rational tails.
-The many incarnations of relative moduli spaces also suffer of the same undesirable feature.
-
-Since the work of Vakil--Zinger and Ranganathan--Santos-Parker--Wise, it has been clear that it is possible to identify a desingularisation of the main component by adding the extra data of a contraction of the source curve $\nu\colon C\to \bar{C}$ - where the latter is allowed to acquire a Smyth singularity - and requiring the stable map $f\colon C\to \PP^N$ to factor through $\nu$.
-
-\subsection{Choice of relative space and desingularisation} We focus on the space of logarithmic stable maps to $(\PP^N|H)$, following ACGS.
-We perform a log modification of this space as detailed below.
-For a log curve $C\to S=\Spec(k=\bar k)$, modify the dual graph of $C$ by replacing the minimal genus one subcurve (in case it is a circle of $\PP^1$) by a single vertex of genus one, called the \textbf{core} and denoted by $\circ$, and define a piecewise linear function with values in $\overline{\pazocal M}_S$ on such a graph by setting \[\lambda(v)=\sum_{q\in[\circ,v]}\rho_q,\]
-where the $\rho_q$ are the smoothing parameters of the nodes $q$ separating $v$ from the core.
-Such a function is related to the log canonical bundle of $C\to S$.
-When the map contracts a subcurve of genus one, we endow it with the extra data of a radius $\delta\in\overline{\pazocal M}_S$ subject to the following compatibility condition:
-
-(*) \textbf{the circle of radius $\delta$ around $\circ$ passes through $\geq1$ vertex of positive $f$-degree}.
-
-\noindent Furthermore, we require all the values of $\lambda$ to be comparable with $\delta$, and among themselves whenever they are $\leq \delta$.
-This is called a \textbf{centrally aligned} log structure and carries enough information to define a contraction $\nu\colon C\to \bar{C}$, possibly after a semistabilisation of $(C,f)$ - in fact even more.
-The space thus obtained, $\widetilde \VZ_{1,\alpha}(\PP^N|H,d)$, is a log modification of $\M{1}{\alpha}{\PP^N|H}{d}$.
-
-The main component $\VZ_{1,\alpha}(\PP^N|H,d)$ is then identified by a double factorisation condition:
-\begin{enumerate}
- \item If $f$ contracts a genus one subcurve, then $f$ is required to factor through the Smyth singularity $\nu\colon C\to \bar C$ determined by the contraction radius $\delta$ as above.
- \item If furthermore the core is contracted by the associated tropical map $\phi$, let $\delta_2$ be the minimal distance from $\circ$ to a vertex supporting a flag that escapes $\phi^{-1}(\phi(\circ))$; we require $f$ to factor through $\nu_2\colon C\to\bar C_2$.
-\end{enumerate}
-The main result is that
-\begin{thm}
- $\VZ_{1,\alpha}(\PP^N|H,d)$ is (log) smooth.
-\end{thm}
-
-\subsection{Gathmann-type recursion} There is a forgetful morphism \[\VZ_{1,\alpha}(\PP^N|H,d)\to \VZ_{1,n}(\PP^N,d),\] hitting Gathmann's relative space.
-We may therefore pullback Gathmann's line bundle and section, cutting out the locus where the $k$-th marking is tangent to $H$ to order $\alpha_k+1$.
-Because $\alpha$ was maximal ($\sum\alpha=d$) by assumption, this means that the curve has to break, and $x_k$ has to lie on an internal component - one which is entirely mapped into $H$.
-We identify the zero locus of Gathmann's section explicitly.
-Here is an interesting remark: the combinatorics of such boundary loci is governed by tropical geometry, and it is otherwise very hard to districate the interaction between the relative condition and the exceptional loci of the Vakil--Zinger blow-up.
-\begin{cor}
- $\VZ_{1,\alpha}(\PP^N|H,d)$ is smooth over its Artin fan, in particular codimension one logarithmic strata can be read off from the latter.
-\end{cor}
-The Artin fan is a tropical gadget.
-Its local structure is given by subdividing the ACGS minimal monoid according to the alignment.
-We are only interested in picking its rays.
-The upshot is that the combinatorics is slightly more involved than in the genus zero case: the alignment may force some teeth of the comb to break.
-\begin{thm}[Gathmann-type formula, maximal tangency, $(\PP^N|H)$ case]
- \[(\alpha_k\psi_k+\ev_k^\st H)[\VZ_{1,\alpha}(\PP^N|H,d)]=[D_{1,\alpha;k}(\PP^N|H,d)],\]
- the latter being a sum of broken comb loci indexed by rays of the tropical fan.
-\end{thm}
-Importantly, the broken comb loci admit a very explicit description in terms of tautological integrals on the underlying boundary of Gathmann's relative space.
-\begin{thm}
- Up to a finite cover of the underlying boundary stratum - which is a combinatorially-determined fiber product of moduli spaces of genus zero and one, absolute and relative maps with lower numerical invariants - every component of $D_{\alpha,k}(\PP^N|H,d)$ can be described as the transverse intersection of two loci in a projective bundle, where:
- \begin{itemize}
-  \item the latter parametrises the possible line bundle isomorphisms imposed by the alignment of the log structure;
-  \item the first locus is a subbundle representing the residual isomorphisms after fixing the ones virtually imposed by tropical continuity;
-  \item the second locus is determined by the factorisation conditions.
- \end{itemize}
-\end{thm}
-The upshot is that we may then push the formula down to the Gathmann's space, so as to obtain multiplicities and tautological classes.
-\begin{cor}
- \[(\alpha_k\psi_k+\ev_k^\st H)[\VZ^G_{1,\alpha}(\PP^N|H,d)]=[D^G_{1,\alpha;k}(\PP^N|H,d)],\]
- the latter being expressible as a weighted sum of tautological classes on Gathmann's comb loci.
-\end{cor}
-Once we have this formula, the following extensions are classical:
-\begin{itemize}
- \item A similar formula for raising the tangency holds in the non-maximal tangency case.
-It can be proven by adding auxiliary markings of contact order $1$; forgetting them is then a $(d-\sum\alpha)!:1$ cover because the nice locus is dense inside Gathmann's relative spaces.
- \item The formula holds more generally for any smooth projective target $X$ relative to a generic hyperplane section $Y=X\cap H\subseteq \PP^N$. This follows via virtual pullback.
-\end{itemize}
-Finally the recursive structure of the boundary allows us to prove the following
-\begin{thm}[In-principle quantum Lefschetz]
- The restricted reduced genus one invariants of $Y$ can be inductively deducted from the full descendant genus zero and one (reduced) Gromov-Witten theory of $X$.
-\end{thm}
-The proof is more delicate than its genus zero analogue because invariants with the same numerical data appear intertwined in the last steps of the recursion.
-
-\section{Desingularisation of the moduli space of log stable maps}
-The ultimate goal of the paper is to apply Gathmann's techniques to the Vakil-Zinger desingularisation $\VZ_{1,n}(\PP^N,d)$ and to obtain a quantum Lefschetz result for reduced invariants under some positivity assumption.
-The key step is to study the unobstructed case $(\PP^N|H)$.
-We approach the problem by lifting it to the ACGS space of log stable maps.
-This allows us to exploit the tools developed in \cite{RSPW,RSPW2}.
-We are in an intermediate situation between those two papers, and indeed we get an intermediate answer.
-
-\subsection{The ACGS minimal monoid and central alignments}
-
-\begin{prop}
- The map $\oM_{1,\alpha}^{\mathrm{cen}}(\PP^N|H,d)\to\oM_{1,\alpha}(\PP^N|H,d)$ is a log modification. In particular $\oM_{1,\alpha}^{\mathrm{cen}}(\PP^N|H,d)$ is a log algebraic stack.
-\end{prop}
-
-{\color{gray} possibly start pointing out that the log structure is already partially aligned by the map to $(\PP^N|H)$}
-
-\subsection{Factorisation conditions}
-
-\begin{prop}
- Factoring through the Smyth curve is a closed condition. In particular $\VZ_{1,\alpha}(\PP^N|H,d)\subseteq_{\mathrm{cl}}\oM_{1,\alpha}^{\mathrm{cen}}(\PP^N|H,d)$ is a log algebraic stack.
-\end{prop}
-
-\subsection{Log smoothness}
-\begin{thm}
- $\VZ_{1,\alpha}(\PP^N|H,d)$ is log smooth.
-\end{thm}
-\begin{proof}
- We reduce to the situation dealt with in \cite{RSPW2} by adding generic extra hyperplanes $H_1,\ldots, H_N$.
-
- First, note that, for divisors $D_1\subseteq D_2$ in $X$, there is a morphism of log schemes $(X,\pazocal M_{D_2})\to (X,\pazocal M_{D_1})$, or equivalently a morphism of log structures $\pazocal M_{D_1}\to\pazocal M_{D_2}$ over $i\!d_X$, because functions invertible off $D_1$ are in particular invertible off $D_2$ as well, and divisorial log structures are subsheaves of the structure sheaf $\pazocal M_{D}\subseteq\OO_X$.
-
- Now fix a point $[(C,f)]\in\VZ_{1,\alpha}(\PP^N|H,d)$.
-Choose hyperplanes $H_1,\ldots, H_N$ in such a way that they intersect the image of $f$ transversally, namely $f^{-1}(H_1\cup\ldots\cup H_N)$ is a reduced collection of points $\{q^i_j\}_{\substack{i=1,\ldots,N \\ j=1,\ldots,d}}$ in the smooth locus of $C$.
-This condition will then hold in an open neighbourhood of $[(C,f)]$.
-Mark $C$ at these points, end endow it with the pullback along $f$ of the divisorial log structure $(\PP^N,\Delta)$, where $\Delta=H+\sum_{i=1}^N H_i$.
-Then \[f\colon (C,\{p_k\}_{k=1,\ldots,n}\{q^i_j\}_{\substack{i=1,\ldots,N \\ j=1,\ldots,d}})\to(\PP^N,\Delta)\]
- is a lift of $[(C,f)]$ to $\oM_{1,\alpha}(\PP^N|\Delta,d)$ (under the forgetful morphism discussed in the previous paragraph).
-
- Looking at the associated tropical map $\phi$, observe that:
- \begin{itemize}
-  \item new flags have been attached only to vertices of positive degree, and these already have a flag escaping $\phi^{-1}\phi(v)$, because the sum of the incoming slopes is not zero (by modified balancing);
-  \item the image of the new tropical map $\tilde\phi$ is entirely contained in the ray of the tropicalisation of $(\PP^N,\Delta)$ corresponding to $H$, with new flags going off to infinity in all the new ray directions from every vertex of positive degree.
- \end{itemize}
- In particular, for every quotient $N'$ of the lattice $N$, the associated tropical map $\tilde\phi'$ will either
- \begin{enumerate}
-  \item have image contained in the ray corresponding to $H$, isomorphically to the original $\phi$, so the contraction radius can be seen to coincide with $\delta_2$, or
-  \item collapse the entire curve to the zero-cell of the fan, in which case we argue from the previous remarks that the contraction radius is $\delta$.
- \end{enumerate}
-
- Hence the lift of $[(C,f)]$ is centrally aligned and satisfies the factorisation property for every subtorus $H<T$, therefore it is well-spaced (see \cite[Definition 3.4.2]{RSPW2}) and it belongs to $\VZ_{1,\tilde\alpha}(\PP^N|\Delta,d)$.
-Note that the deformation spaces of $(C,f)$ and its lift are isomorphic by construction, as can be checked by the infinitesimal criterion - an infinitesimal deformation of $(C,f)$ brings along a unique deformation of the $\{q^i_j\}$ compatible with the map to $(\PP^N,\Delta)$.
-At the logarithmic level, observe that the ACGS minimal monoid is the same, because no component of $C$ is entirely mapped into any of the newly added hyperplanes; since the global contraction radius $\delta$ is the same, the subdivisions corresponding to the alignment procedure do coincide as well.
-This shows that the forgetful morphism is (log) \'etale in a neighbourhood of the lift of $[(C,f)]$, hence we may conclude by appealing to \cite[Theorem 3.5.1]{RSPW2}.
-\end{proof}
-
-\begin{cor}\label{cor:log_smooth}
- $\VZ_{1,\alpha}(\PP^N|H,d)$ is smooth over its Artin fan.
-\end{cor}
-
-{\color{gray} describe the latter as explicitly as possible; comment on the cones that are (possibly?) not there because of the compatibility of the alignment with the log map (this is probably awkward, useless, and superceded by saying ``we align subdivide the ACGS minimal dual monoid'') and because of smoothability/factorisation (this is probably related to tropical well-spacedness)}
-
-%\subsection{A desingularisation of punctured log maps}
-%Describe an analogous desingularisation for punctured log maps.
-The degree zero case seems more delicate and complicated, even though it should just be a substack of a moduli space of marked curves after all (the log structure is possibly trickier).
-%\begin{dfn}
-% A $(z,g,n)$-punctured log map is a punctured log map where the markings with negative contact order to $H$ have an extra label, either $z$ (the tropical map sends them to $z$ero), or $g$ (stands for gluing), or $n$ (stands for nihil, nothing...)
-%\end{dfn}
-%We would like to extend the minimal monoid in order to account for some of the punctures, i.e.
-take the sum of $p^\st\mathcal M_{C^\circ}$ (for every such puncture $p$) fibered over the log structure of the base, which seems to have the same effect as topping those edges with a uertex (which doesn't carry any other information).
-This looks to me like sprouting a $\PP^1$ at those puncture.
-Now, the point of the $(z,g,n)$-labelling is that: we only extend the log structure at the $z$ and $g$ punctures; uertices labelled with a $z$ are sent under the tropical map to $0$, so continuity applies to them (therefore the extension of the log structure is fake because that edge length is determined by the position of the adjacent vertex); while uertices labelled with an $n$ are free to roam about.
-Finally, we perform a radial alignment (and we take rays).
-This distinction comes about when you split your centrally aligned map according to the strict interior of the $\delta$-circle and the outside; the intersection of a tree with the $\delta$-circle can either be a vertex over $0$, or another vertex (corresponding to a degeneration of the genus zero map outside), or not a vertex.
+\subsection{Recursion procedure for reduced rubber integrals} \footnote{(Navid) To be superseded by general recursion section} In the recursion above, certain terms appear which are integrals over moduli spaces of reduced log stable maps to rubber (as defined in \S \ref{}):
+\begin{equation*}\VZ_{1,\alpha}(P|H_0+H_\infty)_{\Gm}.\end{equation*}
+In this section we provide a recursive algorithm for computing such integrals.
+We have three main techniques at our disposal: direct comparison with the double ramification cycle, forgetting of a marking with no insertion, and rubber recursion.
+Each technique has its own domain of applicability, and these domains have non-trivial intersection.
+For convenience we denote the \textbf{horizontal degree} of the rubber map by:
+\begin{equation*} d := \sum_{i=1}^n \alpha_i .\end{equation*}
+Recall that the $\alpha_i$ may be positive or negative (recording tangencies with respect to $H_\infty$ and $H_0$, respectively) and that $d \geq 0$ always.
+First suppose that $d=0$.
+Then the usual rubber moduli space decomposes as
+\begin{equation*} \MLog_{1,\alpha}(P|H_0 + H_\infty)_{\Gm} = \MLog_{1,\alpha}(\PP^1|0+\infty)_{\Gm} \times H \end{equation*}
+and the first term on the right-hand side is birational to the double ramification locus in $\ol\Mcal_{1,n}$.
+This locus has a main component (the closure of the locus of smooth curves) and one other ``exceptional'' component, consisting of split curves where all the markings belong to the rational tail.
+The corresponding reduced rubber space is birational to the main component, and thus we can identify its class by subtracting off the class of the exceptional component.
+This gives
+\begin{equation*} \pi_\st [\VZ_{1,\alpha}(P|H_0+H_\infty)_{\Gm}] = \left( [\ol\Mcal_{1,n}^\alpha] - [D] \right) \times [H] \in \Achow_\st ( \ol\Mcal_{1,n} \times H ) = \Achow_\st ( \ol\Mcal_{1,n}(H,0) ) \end{equation*}
+where $\pi \colon \VZ_{1,\alpha}(P|H_0+H_\infty)_{\Gm} \to \ol\Mcal_{1,n}(H,0)$ is the map which forgets the log structure and collapses the map, $D$ is the boundary locus of split curves described above, and $[\ol\Mcal_{1,n}^\alpha]$ is the classical double ramification cycle, which has an explicit formula in terms of tautological classes \cite{Hain,JPPZ}.
+These observations allow us to compute the integral over the rubber space as a tautological integral on the moduli space of curves.
+
+Now suppose that $d>0$. If there is a marking $x_k$ which carries no insertion and has $\alpha_k \neq 0$, then consider the morphism which forgets $x_k$ and collapses the map:
+\begin{equation*} \VZ_{1,\alpha}(P|H_0+H_\infty)_{\Gm} \xrightarrow{\pi} \VZ_{1,n-1}(H,d). \end{equation*}
+The moduli spaces above are log smooth and of the same dimension.
+Over the nice locus in $\VZ_{1,n-1}(H,d)$, $\pi$ has degree $\alpha_k^2$, arising from a choice of $\alpha_k$-torsion point on the source elliptic curve.
+Thus we have:
+\begin{equation*} \pi_\st [\VZ_{1,\alpha}(P|H_0+H_\infty)_{\Gm}] = \alpha_k^2\cdot [\VZ_{1,n-1}(H,d)].\end{equation*}
+Since all the insertions are pulled back from the right-hand side (up to modifying psi classes by some boundary strata which we can then also compute recursively) we can perform the integral on $\VZ_{1,n-1}(H,d)$ inductively.
+Notice that, when we apply our recursion \ref{} to compute a reduced invariant of $H$, the only non-trivial reduced rubber integrals which appear will have smaller degree than the one we started with, so the calculation is not circular.
+
+It remains to deal with the case where all of the relative markings carry insertions.
+The idea is to reduce to the case above by introducing an additional marking.
+Note first that every reduced rubber integral which appears in our recursion must either have a marking of negative tangency (i.e.
+tangent to $H_0$), or a marking with no insertions: indeed, the only boundary loci with no negative-tangency markings have the entire curve mapped to higher level, in which case (since we are assuming $d>0$, so we are not in the $C_0$ case) the curve is generically irreducible, and on this curve we have at least one fictitious marking (of positive tangency $1$) with no insertion.
+
+Therefore we may assume that there is at least one point of negative tangency, corresponding to a node at which we will glue.
+Notice that in our recursion these points only ever carry evaluation classes.
+Consider the following rubber space of dimension one higher, obtained by introducing an additional non-relative marking:
+\begin{equation} \label{bigger rubber space}\VZ_{1,\alpha \cup (0)}(P|H_0+H_\infty)_{\Gm}. \end{equation}
+Given a moduli point in this space, consider the piecewise-linear function on the associated tropical moduli space which sends a tropical map to the sum of the target edge lengths.
+This defines a line bundle and section on the space \eqref{bigger rubber space} which vanishes precisely on the locus where the target splits; moreover the vanishing orders may be read off from the tropical data as in \S \ref{}.
+It is not hard to see \cite{EKatz} that the first Chern class of the line bundle is
+$\Psi_0 + \Psi_\infty$, a sum of target psi classes which may be identified with evaluation and psi classes on the source curve as in \cite[Construction 5.1.17]{GathmannThesis}.
+
+Now choose a negative-tangency point $x_1$ which carries only evaluation classes, and let $x_0$ denote the new non-relative marking we have introduced.
+If $\gamma$ was the class we were originally trying to integrate, consider the class $\tilde\gamma$ on \eqref{bigger rubber space} obtained from $\gamma$ by replacing $\ev_1^\st$ by $\ev_0^\st$.
+We obtain a recursion formula:
+\begin{equation*} (\Psi_0+\Psi_\infty)\cdot \tilde\gamma \cap [\VZ_{1,\alpha\cup(0)}(P|H_0+H_\infty)_{\Gm}] = \sum_{\Gamma} m_\Gamma \cdot \tilde\gamma \cap [\ol\Mcal_{\Gamma}]. \end{equation*}
+The right-hand side is a sum over irreducible components $\ol\Mcal_\Gamma$ of the locus where the target splits, with multiplicites $m_\Gamma$ calculated from the tropical data.
+Each of these components can be written as a fibre product of (reduced) rubber spaces.
+One of these components is the locus where $x_0$ and $x_1$ belong to a trivial rational bubble:
+
+[FIGURE]
+
+The corresponding moduli space is $\VZ_{1,\alpha}(P|H_0+H_\infty)_{\Gm}$ and we have $\ev_0=\ev_1$ here, so the contribution of this locus is precisely the original rubber integral we were trying to calculate.
+The remaining terms on the right-hand side can be written either as a product of rubber integrals of smaller degree (which we can compute recursively), or rubber integrals of the same degree but with no insertion at $x_1$ (which we can compute by forgetting $x_1$).
+Finally, the left-hand side also has no insertion at $x_1$ and so can be computed by the same method.
+Here we are assuming that $x_1$ is not the only negative-tangency marking, so that $\Psi_0$ can be interpreted as an insertion on a marking different from $x_1$.
+
+If $x_1$ is in fact the only negative-tangency marking, then we can modify the above argument by considering the following rubber space of dimension two larger:
+\begin{equation}\label{rubber space two extra markings} \VZ_{1,\alpha\cup(0,0)}(P|H_0+H_\infty)_{\Gm} \end{equation}
+Let us denote the newly-introduced non-relative markings by $x_0$ and $x_{n+1}$.
+We now let $\tilde\gamma$ denote the class obtained from $\gamma$ by replacing $\ev_1^\st$ by $\ev_0^\st$ and then multiplying by $\psi_{n+1}$.
+Following \cite{EKatz}\footnote{(Navid) Tropica interpretation of this?
+Vanishing multiplicities?}, there is a line bundle with a section cutting out the locus where $x_{n+1}$ does not belong to the leftmost component of the target.
+The first Chern class of this line bundle is $\Psi_\infty+\ev_{n+1}^\st H$, which we may multiply with $\tilde\gamma$ and integrate over \eqref{rubber space two extra markings} to obtain a rubber integral with no insertion at $x_1$ (which we may then compute by forgetting $x_1$).
+On the right-hand side we obtain the integral of $\tilde\gamma$ over the loci where $x_{n+1}$ does not belong to the leftmost component of the target (this is just a union of some of the irreducible components of the split locus described above).
+One such locus is the following
+[FIGURE]
+and integrating $\tilde\gamma$ over this locus gives
+\begin{equation*} \gamma\cdot\psi_{n+1}\cap [\VZ_{1,\alpha\cup(0)}(P|H_0+H_\infty)_{\Gm}] \end{equation*}
+which we may identify with a (nonzero) multiple of our original rubber integral via the rubber dilaton equation (see\cite{MaulikPandharipande}; the same proof carries over to the reduced setting\footnote{(Navid) Think about this a bit}).
+The remaining loci may be computed recursively exactly as before, and thus we obtain a complete recursion procedure.
+
+\begin{remark} This idea --- of finding a section of a line bundle cutting out the locus of split curves, and using this to derive recursion formulae for rubber integrals --- has been pursued in the non-reduced setting in \cite{EKatz}.\end{remark}
 
@@
 \section{Splitting axiom and recursion formula for $(\PP^N|H)$}
-
-\noindent  In the previous section we explained how to determine the logarithmic strata of $\VZ$.
-We now focus our attention on certain logarithmic divisors, providing a recursive description for these loci: that is, a description in terms of fibre products of smaller moduli spaces.
-This is the technically most difficult part of the paper.
-The recursive description bears some similarities with the recursive description of the boundary of the absolute space $\VZ_{1,n}(\PP^N,d)$ given in \cite{VZ}; in keeping with the theme of this paper, however, we will see that log geometry provides a convenient framework for dealing with the combinatorics.
-
-The end result is that we obtain an explicit formula for tautological integrals over these boundary loci. This produces a Gathmann recursion  for relative invariants in genus one.
-
-The plan for this section is as follows \footnote{(Navid) Finish this}
-
-\subsection{Recursion setup} Consider an element of $\VZ$ and choose a marked point $x_k\in C$.
-We note that by the existence of a log morphism, either $f$ has contact order $\alpha_k$ to $H$ at the marking $x_k$, or else the irreducible component of $C$ containing $x_k$ is mapped entirely inside $H$ (we say ``$x_k$ belongs to an internal component'' in this case).
-
-By pulling back the equation defining $H$ along $f$ and then taking its $\alpha_k$-th derivative at $x_k$ (which makes sense since all the lower-order derivatives vanish by assumption) we obtain a section of a jet bundle on $\VZ$ whose vanishing locus coincides (set-theoretically) with the locus where $x_k$ belongs to an internal component.
-As in \cite[Construction 2.1]{Ga} there is an exact sequence of jet bundles
-\begin{equation*} 0\to x_k^\st\omega_{\mathcal{C}/\VZ}^{\otimes\alpha_k}\otimes\ev_k^\st\OO_{\PP^N}(H)\to x_k^\st\mathcal J^{\alpha_k}(f^\st\OO_{\PP^N}(H))\to x_k^\st\mathcal J^{\alpha_k-1}(f^\st\OO_{\PP^N}(H))\to 0 \end{equation*}
-and thus we obtain a section of the line bundle $x_k^\st\omega_{\mathcal{C}/\VZ}^{\otimes\alpha_k}\otimes\ev_k^\st\OO_{\PP^N}(H)$ with vanishing locus equal to the locus where $x_k$ belongs to an internal component.
-Writing this locus as
-\begin{equation*} \Dcal(k) = \Dcal_{1,\alpha}^k(\PP^N|H,d) \subseteq \VZ_{1,\alpha}(\PP^N|H,d) = \VZ \end{equation*}
-we obtain:
-\begin{lem} $(\alpha_k\psi_k+\ev_k^\st H)\cap[\VZ]=[\Dcal(k)].\footnote{(Navid) Should we work out the vanishing orders of the section at this point?}$\end{lem}
-\noindent The remainder of this section will be devoted to providing an explicit recursive description of the class $[\Dcal(k)]$ in terms of tautological classes on spaces of maps with smaller numerical invariants.
-As we will see, this provides an algorithm for computing reduced relative invariants, as well as a quantum Lefschetz algorithm for reduced (absolute) invariants in genus one.
-
-\subsection{Identifying the irreducible components of $\Dcal(k)$} Here we explain the strategy for identifying the irreducible components of $\Dcal(k)$ via tropical geometry.
-
-\begin{lemma} Every irreducible component of $\Dcal(k)$ is a codimension-$1$ logarithmic stratum.\end{lemma}
-\begin{proof} This is not hard to see: the locus where the log structure is trivial coincides precisely with the  locus where the source curve is smooth and not mapped inside $H$, and since $\VZ$ is log smooth this locus is open and dense.
-By definition $\Dcal(k)$ is disjoint from this locus, hence is contained in the  complement of this locus, which (by the very definition of logarithmic strata) can be written as a union of logarithmic strata of positive codimension.
-Since $\Dcal(k)$ has codmension $1$, it must therefore be equal to a union of logarithmic divisors.\end{proof}
-
-In the previous section we discussed at length a procedure for describing the logarithmic strata of $\VZ$. This shows that every divisorial logarithmic stratum is obtained via a three-step process:
-\begin{enumerate}
-\item choose the combinatorial type of a tropical map;
-\item subdivide the corresponding tropical moduli space;
-\item choose a ray in this subdivision.
-\end{enumerate}
-Notice that this process contains some redundancies: once we choose a ray of the tropical moduli space, we obtain a generisation of the intial combinatorial type, given by contracting some edges of the dual graph.
-
-\begin{example} \end{example}
-
-Whenever we consider a logarithmic stratum in $\VZ$, by its combinatorial type we will always mean the generisation of the ``initial'' combinatorial type induced by our choice of cone in the polyhedral subdivision.
-This does not depend on the choice of initial combinatorial type.
-
-Now, the logarithmic divisors which are contained in $\Dcal(k)$ are precisely those whose corresponding combinatorial type has the vertex of the dual graph containing $x_k$ mapped into the interior $\RR_{>0} \subseteq \RR_{\geq 0}$.
-
-Thus, via the above procedure, we are able to enumerate the irreducible components of $\Dcal(k)$ in a combinatorial manner.
-The combinatorial type and choice of ray allows us to describe the general element of such a component.
-What we are still lacking is a recursive description of the components, which we need in order to compute integrals over them.
-This is the subject of the remainder of this section.
-
-\subsection{Splitting and gluing punctured logarithmic maps}\label{subsection punctured maps} We still start by considering the usual moduli space $\Mcal$ of log stable maps.
-In \cite{PuncturedMaps}, a recursive description of the logarithmic strata of $\Mcal$ is given, in terms of moduli spaces of punctured maps.
-As discussed above, the logarithmic strata $\Scal$ of $\Mcal$ are indexed by combinatorial types of tropical curves.
-Given such a combinatorial type $\Delta$, each vertex $v$ of the associated graph defines a moduli space of punctured stable maps:
-\begin{equation*} \ol\Mcal_v = \Mpunct{g(v)}{\alpha(v)}{Z_v}{d(v)}. \end{equation*}
-Here $g(v)$ and $d(v)$ are the genus and degree assigned to the vertex, while $Z_v$ is the logarithmic stratum of the target corresponding to the tropical stratum into which the vertex is mapped by the combinatorial type (in our setting, $Z_v=\PP^N$ or $H$).
-The length of the vector $\alpha(v)$ is given by the number of flags adjacent to $v$, and the entries (which represent tangencies, and may be positive or negative) are given by the expansion factors along those flags.
-If all of the tangencies are positive, then this is nothing but an ordinary moduli space of log stable maps.
-
-The corresponding logarithmic stratum is then obtained as a follows.
-For each vertex $v$ and each adjacent flag $E \ni v$ we define $\widetilde\Mcal_v^E$ to be the stack $\ol\Mcal_v$ equipped with the log structure
-\begin{equation*} p_{v,E}^\st \Mcal_{\Ccal_v^\circ} \end{equation*}
-where $p_{v,E} \colon \ol\Mcal_v \to \Ccal_v^\circ$ is the marking section corresponding to $E$.
-This definition makes $p_{v,E}$ into a strict logarithmic map, and composing with the universal map produces a logarithmic evaluation morphism $\ev_{v,E} \colon \widetilde\Mcal_v^E \to Z_E$, where $Z_E \subseteq Z_v$ is the logarithmic stratum into which the marking corresponding to $E$ is mapped.
-
-If $E_1,\ldots,E_k$ are the flags adjacent to $v$ then we define
-\begin{equation*} \widetilde\Mcal_v = \widetilde\Mcal_v^{E_1} \times_{\ol\Mcal_v} \ldots \times_{\ol\Mcal_v} \widetilde\Mcal_v^{E_k} \end{equation*}
-where the fibre product is taken in the fs log category.
-With this definition, all the evaluation maps $\ev_{v,E} \colon \widetilde{\Mcal}_v \to Z_E$ are naturally logarithmic morphisms.
-Then the corresponding logarithmic stratum is obtained by taking the following fibre product (again, in the fs log category):
-\bcd
-\Scal \ar[r] \ar[d] \ar[rd,phantom,"\square"] & \prod_v \widetilde\Mcal_v \ar[d] \\
-\prod_{E} Z_E \ar[r] & \prod_{E} Z_E \times Z_E.
-\ecd
-In the above discussion, there were two steps at which we needed to take fs fibre products: first, when constructing each $\widetilde{\Mcal}_v$ and second, when construction $\Scal$.
-Typically the fs fibre product does not agree with the usual fibre product of stacks; rather, one must take the fibre product in the category of coherent log stacks (which \emph{does} agree with the usual fibre product) and then integralise and saturate the result.
-
-We will now argue that in our situation, when we take fibre products of coherent log stacks, the result is automatically integral.
-This means that the integralisation process is redundant, and so the fs fibre product is obtained from the ordinary fibre product by a process of saturation.
-This amounts to taking a finite cover of the underlying stack (whose degree we will compute).
-
-The following lemma holds for arbitrary moduli spaces of punctured maps.
-
-\begin{lemma} Given a combinatorial type $\Delta$ indexing a stratum of $\Mcal$ and a vertex $v$ of the associated graph, consider the corresponding moduli space of punctured stable maps $\ol\Mcal_v$.
-As in the above discussion, define for each adjacent flag $E \ni v$ the log stack $\widetilde\Mcal_v^E$ by pulling back the log structure of the punctured curve along the marking section.
-Consider the fibre product \emph{in the category of coherent log stacks}:
-\begin{equation*} \widetilde\Mcal^{\operatorname{not-fs}}_v = \widetilde{\Mcal}_v^{E_1} \times_{\ol\Mcal_v} \ldots \times_{\ol\Mcal_v} \widetilde{\Mcal}_v^{E_k}. \end{equation*}
-Then $\widetilde\Mcal^{\operatorname{not-fs}}_v$ is integral (and consequently, the map $\widetilde\Mcal_v \to \widetilde\Mcal^{\operatorname{not-fs}}_v$ is finite).
-\end{lemma}
-\begin{proof} Locally we have a chart for $\ol\Mcal_v$ given by $Q$ (the minimal monoid as constructed, for instance, in \cite[Construction 1.16]{GrossSiebertLog}) and charts for $\widetilde\Mcal_v^{E_i}$ given by $Q_{E_i}$, where $Q_{E_i} = Q \oplus \N$ if $E_i$ corresponds to an ordinary marked point, and $Q_{E_i}$ is the submonoid of $Q \oplus \Z$ generated by $Q \oplus \N$ and $(\ol\varphi_{\eta_i}(1),u_{E_i})$ if $E_i$ corresponds to a puncturing (so that $u_{E_i} \in \Z_{<0}$).
-In either case, we have $Q_{E_i} \subseteq Q \oplus \Z \subseteq Q^{\operatorname{gp}} \oplus \Z$ (since $Q$ is integral) and so $Q_{E_i}$ is integral (recall that a monoid is integral if and only if it admits an injective homomorphism into a group).
-In this notation, $\widetilde\Mcal_v^{\operatorname{not-fs}}$ admits a chart given by the monoid:
-\begin{equation*} P = Q_{E_1} \oplus_Q Q_{E_2} \oplus_Q \ldots \oplus_Q Q_{E_k}.\end{equation*}
-Suppose without loss of generality that $E_1,\ldots,E_r$ are punctures and $E_{r+1},\ldots,E_k$ are ordinary marked points; then $P$ is equal to the submonoid of
-\begin{equation*} Q \times \Z^r \times \N^{k-r} \end{equation*}
-generated by $Q \times \N^k$ and $(\ol\varphi_{\eta_i}(1),u_{E_i} e_i,0)$ for $i\in \{1,\ldots,r\}$, where $e_i \in \Z^r$ is the $i$th basis element and $0 \in \N^r$.
-In particular, $P$ admits an injective homomorphism into the group
-\begin{equation*} Q^{\gp} \times \Z^r \times \Z^{k-r} \end{equation*}
-and hence is integral.\end{proof}
-
-\footnote{(Navid) Is this a good point to calculate the degree of $\widetilde\Mcal_v \to \widetilde\Mcal_v^{\operatorname{not-fs}}$?}The previous lemma holds for arbitrary moduli spaces of punctured maps.
-The next lemma, on the other hand, is special to our setting.
-
-\begin{lemma} Consider the fibre product in the category of coherent log stacks:
-\bcd
-\Scal^{\operatorname{not-fs}} \ar[r] \ar[d] \ar[rd,phantom,"\square"] & \prod_v \widetilde\Mcal_v \ar[d] \\
-\prod_{E} Z_E \ar[r] & \prod_{E} Z_E \times Z_E.
-\ecd
-Then $\Scal^{\operatorname{not-fs}}$ is integral.\end{lemma}
-\begin{proof}\end{proof}
-
-This gives a recursion description of the logarithmic strata in $\Mcal$.
-We will now\footnote{(Navid) Really, after the next section, which maybe we should move to an appendix} use this to obtain a similar (though somewhat more complicated) description of the strata in $\VZ$.
-
-\subsection{Punctured maps and double ramification loci}\footnote{(Navid) Move this to an appendix?} We will now present some arguments and constructions aimed at demystifying the moduli spaces of punctured stable maps.
-In our context, we only ever encounter these spaces when the associated logarithmic stratum $Z_v$ of the target is the divisor $H$.
-Consider therefore a moduli space of punctured stable maps
-\begin{equation}\label{punctured space} \Mpunct{g}{\alpha}{H}{d} \end{equation}
-where $g \in \{0,1\}$ and $\alpha$ is a vector of tangency orders.
-The target $H$ is given the log structure pulled back from $\PP^N$, and consequently is not log smooth.
-As such, the natural obstruction theory on the above moduli space will not, in general, be perfect.
-This is not really a problem for us, since we are mainly interested in studying the non-virtual geometry of our moduli spaces.
-Indeed, we will see that the space \eqref{punctured space} is birational to the moduli space of ordinary stable maps to $H$ satisfying the condition:
-\begin{equation}\label{DRC condition} f^\st[H] - \sum_{i=1}^n \alpha_ix_i =0 \in \Achow_0(C).\end{equation}
-This space forms a closed substack
-\begin{equation*} \ol\Mcal^{\alpha}_{g,n}(H,d) \subseteq \M{g}{n}{H}{d} \end{equation*}
-and is referred to as the \emph{double ramification locus}.
-These moduli spaces have been the focus of intense study over the years (see, for instance, \cite{GathmannThesis} \cite{DRCBundle}).
-The double ramification locus is a closed substack of $\M{g}{n}{H}{d}$ of virtual codimension $g$ (though, as with $\M{g}{n}{H}{d}$ itself, it typically has excess dimension).
-
-\begin{prop} Suppose that $g \in \{0,1\}$ and consider the morphism forgetting all log structures:
-\begin{equation*} \Mpunct{g}{\alpha}{H}{d} \to \M{g}{n}{H}{d}. \end{equation*}
-This factors through the double ramification locus, and is in fact birational onto its image.\end{prop}
-\begin{proof} The fact that the forgetful morphism factors through the double ramification locus is an immediate consequence of the balancing condition satisfied by punctured stable maps, interpreted as a condition in $\Pic(C)$ (the more familiar balancing condition is obtained from this one by restricting to a component of $C$ and then taking degrees).
-Thus indeed we have a map:
-\begin{equation*} \varphi \colon \Mpunct{g}{\alpha}{H}{d} \to \ol\Mcal^\alpha_{g,n}(H,d). \end{equation*}
-To show that $\varphi$ is birational, we will choose an open dense locus of the domain and show that $\varphi$ induces an isomorphism on geometric points when restricted to this locus.
-The locus we take is the preimage of the locus inside $\ol\Mcal^\alpha_{g,n}(H,d)$ consisting of curves of compact type (i.e.
-those whose dual graph has genus zero); essentially we are excluding stable maps whose source curve contains a cycle of $\PP^1$s.
-The fact that this is open dense in $\ol\Mcal^\alpha_{g,n}(H,d)$ is not hard to see: when $g=1$ (the only case in which non-compact type curves can arise), the double ramification locus contains many components, but on every such component the maximal genus one subcurve of the source will be generically smooth, which shows again that the locus of stable maps not of compact type is closed inside $\ol\Mcal^\alpha_{g,n}(H,d)$.
-Once we show that $\varphi$ is bijective on geometric points when restricted to the preimage of this locus, it follows (since $\varphi$ is a finite morphism) that the preimage of this locus is dense in $\Mpunct{g}{\alpha}{H}{d}$, and hence that $\varphi$ is birational.
-
-So, let us start with a compact type stable map which belongs to the double ramification locus:
-\bcd
-C \ar[r,"f"] \ar[d] & H \\
-S=\Spec\kfield
-\ecd
-We will show that there exists a unique lift of this to a punctured stable map.
-Since $C$ has compact type, there is a unique choice of associated combinatorial type $\Delta$.
-This determines a minimal monoid $Q$ such that any punctured map enhancing the given stable map has base log structure given by:
-\begin{align*}
-Q \oplus \kfield^\st & \to \kfield \\
-(q,\lambda) & \mapsto \begin{cases} \lambda \qquad \text{if } q =0 \\ 0 \qquad \text{otherwise} \end{cases}
-\end{align*}
-If we let $r$ denote the number of nodes of $C$ then by construction there is a natural map $\N^r \to Q$ and by the universal property of minimality our punctured curve must be obtained by puncturing a log smooth curve pulled back along a morphism of log schemes:
-\begin{equation*} (\Spec\kfield,Q \oplus \kfield^\st) \to (\Spec\kfield,\N^r\oplus\kfield^\st).\end{equation*}
-This log morphism must enhance the given map $\N^r \to Q$ on the level of ghost sheaves.
-The moduli for such a log map is $\Gm^r$, but all these choices are canceled out by automorphisms of $(\Spec\kfield,Q\oplus\kfield^\st)$\footnote{(Navid) Here we are using the fact that $Q$ is in some sense bigger than $\N^r$.}.
-Thus we obtain, by pulling back the minimal log smooth curve over $(\Spec\kfield,\N^r \oplus\kfield^\st)$, a unique log smooth curve:
-\begin{equation*} (C,\Mcal_C) \to (\Spec\kfield,Q\oplus\kfield^\st).\end{equation*}
-We must now construct the puncturing $\Mcal_{C^\circ}$.
-Let $\Pcal_C$ denote the divisorial log structure on $C$ with respect to the punctures.
-It is easy to see that there is a unique log structure $\Mcal$ on $C$ such that
-\begin{equation*} \Mcal_C = \Mcal \oplus_{\OO_C^\st} \Pcal_C \end{equation*}
-where the pushout is taken in the category of monoid sheaves. We consider the sheaf:
-\begin{equation*} \Ncal_C = \Mcal \oplus_{\OO_C^\st} \Pcal^{\gp}_C. \end{equation*}
-By definition the puncturing $\Mcal_{C^\circ}$ should be an intermediate sheaf:
-\begin{equation*} \Mcal_C \subseteq \Mcal_{C^\circ} \subseteq \Ncal_C. \end{equation*}
-We will now construct this, and argue that our construction gives the only puncturing possible.
-First we note that it is sufficient to define $\Mcal_{C^\circ}$ on a base for the topology on $C$.
-We choose a base such that for each base open set $U$:
-\begin{enumerate}
-\item $U$ is connected;
-\item $U$ contains at most one of the punctures of $C$;
-\item if $U$ contains a puncture $p \in C$, then $U$ does not contain any of the nodes or markings of $C$, and $\OO_C(p)|_U$ is trivial.
-\end{enumerate}
-Note that these properties are stable under taking subsets, so to obtain such a base we simply choose an open cover with this property (which is certainly possible) and then take the collection of all open subsets of our chosen cover.
-
-Now let $U$ be such an open set in our base. If $U$ does not contain a puncture then $\Mcal_C|_U = \Ncal_C|_U$ and so we set
-\begin{equation*} \Mcal_{C^\circ}(U) = \Mcal_C(U).\end{equation*}
-If $U$ contains a puncture $p$ then by assumption $U \setminus \{ p\}$ contains only smooth unmarked points, and hence we have a splitting
-\begin{equation*} \Ncal_C|_U = \left( \pi^\st \Mcal_S|_U \right) \oplus_{\OO_U^\st} \left(\Pcal_p^{\gp}|_U \right) \end{equation*}
-where $\Pcal_p$ is the divisorial log structure with respect to $p$. Since $\Mcal_S = Q \oplus \kfield^\st$ it follows that $\pi^\st\Mcal_S|_U = \ul{Q} \oplus \OO_U^\st$. Thus we see that
-\begin{equation*} \Ncal_C|_U = \ul{Q} \oplus \Pcal_p^{\gp}|_U\end{equation*}
-and similarly:
-\begin{equation*} \Mcal_C|_U = \ul{Q} \oplus \Pcal_p|_U.\end{equation*}
-We therefore have (since $U$ is connected):
-\begin{equation*} \Ncal_C(U) = Q \oplus \Pcal_p^{\gp}(U) \end{equation*}
-Recall we are assuming that $\OO_C(p)|_U$ is trivial.
-Choosing a trivialisation, we obtain a function $s \in \OO_U(U)$ such that $p=\{s=0\}$ on $U$.
-Then $\Pcal_p(U)$ consists of functions of the form $\lambda \cdot s^n$ for $n \in \N$ and $\lambda \in \OO_U^\st(U)$.
-Groupifying, we obtain:
-\begin{equation*} \Pcal^{\gp}_p(U) = \left\{ \lambda \cdot s^k \, \vert \, \lambda \in \OO_U^\st(U), k \in \Z \right\}. \end{equation*}
-(Indeed, $\Pcal_p^{\gp}$ can be described as the sheaf of rational functions which are regular and invertible outside of $p$.) Recall that $p$ has attached to it a tangency order $\alpha_p \in \Z_{<0}$.
-If we let $\eta$ denote the generic point of the component of $C$ containing $p$, then we also have a pullback map $\ol\varphi_\eta \colon \N \to Q$ which is sharp (i.e.
-it is not the zero map).
-We define $\Mcal_{C^\circ}(U) \subseteq \Ncal_C(U)$ to be the submonoid generated by $Q \oplus \Pcal_p(U)$ and the element:
-\begin{equation*} (\ol\varphi_\eta(1),s^{\alpha_p}). \end{equation*}
-This clearly satisfies the conditions to be a puncturing, and by the prestability condition it is the only possibility for $\Mcal_{C^\circ}$. We thus have a punctured curve:
-\begin{equation*} (C,\Mcal_{C^\circ}) \to (C,\Mcal_C) \to (\Spec\kfield,Q\oplus\kfield^\st). \end{equation*}
-It remains to construct the log enhancement of the map $f \colon C \to H$.
-The map $f^\flat \colon f^\st \Mcal_H \to \Mcal_{C^\circ}$ is already determined on the level of ghost sheaves.
-To enhance this to a map on the level of log structures entails choosing an isomorphism of line bundles:
-\begin{equation*} f^\st \OO_H(1) \cong \OO_C\left(\ol{f}^\flat(1)\right). \end{equation*}
-The component-wise description of the right-hand side in \cite{RSPW} (together with the fact that $C$ is compact type, so its Picard group is simply the product of the Picard groups of its components) shows that such an isomorphism exists if and only if the original stable map is in the double ramification locus.
-There is a $\Gm$ worth of choices for such a map, but these are canceled out by the automorphisms of $(C,\Mcal_{C^\circ})$ induced by pulling back along (strict) automorphisms of $(\Spec\kfield,Q\oplus\kfield^\st)$.
-This completes the proof of unique punctured lifting.
-\end{proof}
-
-Thus, the spaces of punctured maps we encounter are always birational to double ramification loci.
-We now briefly discuss the geometry of these loci.
-In the genus zero case, the double ramification locus is equal to the entire space
-\begin{equation*} \ol\Mcal^{\alpha}_{0,n}(H,d) = \M{0}{n}{H}{d} \end{equation*}
-which is smooth. Thus tautological integrals over $\ol\Mcal^{\alpha}_{0,n}(H,d)$ are determined by the genus-zero Gromov--Witten theory of $H$.
-
-The genus one case is more delicate: there is a ``main component'' of the double ramification locus, obtained as the closure of the locus where the source curve is smooth.
-This forms a divisor inside the main component of the moduli space of stable maps:
-\begin{equation*} \ol\Mcal^{\alpha,\circ}_{1,n}(H,d) \subseteq \ol\Mcal^\circ_{1,n}(H,d). \end{equation*}
-However, we know that $\M{1}{n}{H}{d}$ contains many other components besides $\ol\Mcal^\circ_{1,n}(H,d)$, some of which have excess dimension.
-Certainly the double ramification locus intersects these other components, and sometimes it can do so in quite dramatic fashion.
-For instance, consider the locus where the source curve splits into a contracted elliptic component and a rational component containing all the markings.
-This locus forms an irreducible component of the moduli space, isomorphic to
-\begin{equation*}\ol\Mcal_{1,1} \times \M{0}{n+1}{H}{d} \end{equation*}
-which has excess dimension $N-2$.
-This entire component belongs to the double ramification locus, since the condition \eqref{DRC condition} becomes entirely numerical here.
-Thus, we see that the double ramification locus can be quite badly-behaved in genus one.
-Fortunately, we will only be interested in the main component of this locus (which is birational to the main component of the moduli space of punctured maps); see \S \ref{} below.
 
@@
 
-\section{Quantum Lefschetz in genus one}
-
- Assume \footnote{(Luca) copied and pasted from my thesis} we want to compute $\langle\tau_{h_1}H^{k_1},\ldots,\tau_{h_1}H^{k_1}\rangle^{\PP^{N-1},\rm{red}}_{1,n,d}$ by writing it as $\frac{1}{d^2}(\psi_1^{\{n+1\}})^{h_1}H^{k_1}\cdots(\psi_n^{\{n+1\}})^{h_n}H^{k_n}\cdot[\VZ{(0,\ldots,0,d)}{\PP^N|H}{d}^\thicksim]$.
-Let me start from the recursion step $H_1\cdot[\VZ{(0,\ldots,0,d)}{\PP^N|H}{d}]=\ldots:$
-
- \begin{description}
-  \item[$\mathcal Y_a$:] $d\ {\tikz[baseline=-3pt,scale=.7]{
-\draw (2,0) node[above]{$\{x_1,x_{n+1}\}$} -- (0,0)node[below]{$d$};
-\draw (2,0) circle(2pt)[fill=black];
-\draw (0,0) circle(2pt)[fill=white];
-\draw (-1,1.5) -- (1,1.5) -- (1,-1.5) -- (-1,-1.5) -- (-1,1.5);
-\draw (1,1.5) -- (3,2) -- (3,-1) -- (1,-1.5);
-}}$ contributes $\frac{1}{d}\psi_1^{h_1}H^{k_1}\cdots\psi_n^{h_n}H^{k_n}\cdot[\VZ{(d,\ldots,0)}{\PP^N|H}{d}]$; if this is the curve configuration, while there is any other marking at level one, then $\fgt_{n+1}$ has positive dimensional fibers; otherwise there must be another component of positive horizontal degree (these contributions are computed inductively on $d$);
-\item[$\mathcal Y_b$:] is an entirely rational story;
-\item[$\mathcal Y_c$:] {\tikz[baseline=-3pt,scale=.7]{
-\draw (2,0) node[above]{$\{x_1,\ldots,x_{n+1}\}$} node[below]{$d$};
-\draw (2,0) circle(2pt)[fill=white];
-\draw (-1,1.5) -- (1,1.5) -- (1,-1.5) -- (-1,-1.5) -- (-1,1.5);
-\draw (1,1.5) -- (3,2) -- (3,-1) -- (1,-1.5);
-}} is the term we are meant to compute, while all other terms will include a DRC integral of lower degree.
- \end{description}
-I shall look one step further into the recursion for computing $[\VZ{(0,\ldots,0,d)}{\PP^N|H}{d}]$: in order to do so consider the formula for $((d-1)\psi_{n+1}+H_{n+1})\cdot[\VZ{(0,\ldots,0,d-1,1)}{\PP^N|H}{d}]$.
-This produces:
-\begin{description}
-  \item[$\mathcal Y_a$:] $d\ {\tikz[baseline=-3pt,scale=.7]{
-\draw (2,0) node[above]{$\{x_{n+1},x_{n+2}\}$} -- (0,0)node[below]{$d$};
-\draw (2,0) circle(2pt)[fill=black];
-\draw (0,0) circle(2pt)[fill=white];
-\draw (-1,1.5) -- (1,1.5) -- (1,-1.5) -- (-1,-1.5) -- (-1,1.5);
-\draw (1,1.5) -- (3,2) -- (3,-1) -- (1,-1.5);
-}}$ this is the one we are after; while
-$(d-1){\tikz[baseline=-3pt,scale=.7]{
-\draw (2,.5) node[above]{$\{x_{k},x_{n+1}\}$} -- (0,0)node[below]{$d$};
-\draw (2,-.5) node[above]{$\{x_{n+2}\}$} -- (0,0);
-\draw (2,.5) circle(2pt)[fill=black];
-\draw (2,-.5) circle(2pt)[fill=black];
-\draw (0,0) circle(2pt)[fill=white];
-\draw (-1,1.5) -- (1,1.5) -- (1,-1.5) -- (-1,-1.5) -- (-1,1.5);
-\draw (1,1.5) -- (3,2) -- (3,-1) -- (1,-1.5);
-}}$ gives a lower tangency condition $[\VZ{(0,\ldots,d-1,\ldots,0)}{\PP^N|H}{d}]$; and all other terms have lower degree.
-\item[$\mathcal Y_c$:] {\tikz[baseline=-3pt,scale=.7]{
-\draw (2,0) node[above]{$\{x_1,\ldots,x_{n+1},x_{n+2}\}$} node[below]{$d$};
-\draw (2,0) circle(2pt)[fill=white];
-\draw (-1,1.5) -- (1,1.5) -- (1,-1.5) -- (-1,-1.5) -- (-1,1.5);
-\draw (1,1.5) -- (3,2) -- (3,-1) -- (1,-1.5);
-}} has positive dimensional fibers for $\fgt_{n+1,n+2}$, and all other terms have lower degree.
- \end{description}
- Finally, let me look one step further into the reduction of $[\VZ{(d,\ldots,0)}{\PP^N|H}{d}]$: we have $((d-1)\psi_1^{\{n+1\}}+H_1)\cdot[\VZ{(d-1,\ldots,0,1)}{\PP^N|H}{d}]=\ldots:$
- \begin{description}
-  \item[$\mathcal Y_a$:] $d\ {\tikz[baseline=-3pt,scale=.7]{
-\draw (2,0) node[above]{$\{x_{1},x_{n+1}\}$} -- (0,0)node[below]{$d$};
-\draw (2,0) circle(2pt)[fill=black];
-\draw (0,0) circle(2pt)[fill=white];
-\draw (-1,1.5) -- (1,1.5) -- (1,-1.5) -- (-1,-1.5) -- (-1,1.5);
-\draw (1,1.5) -- (3,2) -- (3,-1) -- (1,-1.5);
-}}$ is the one we care about;
-$(d-1)\ {\tikz[baseline=-3pt,scale=.7]{
-\draw (2,.5) node[above]{$\{x_{k},x_{1}\}$} -- (0,0)node[below]{$d$};
-\draw (2,-.5) node[above]{$\{x_{n+1}\}$} -- (0,0);
-\draw (2,.5) circle(2pt)[fill=black];
-\draw (2,-.5) circle(2pt)[fill=black];
-\draw (0,0) circle(2pt)[fill=white];
-\draw (-1,1.5) -- (1,1.5) -- (1,-1.5) -- (-1,-1.5) -- (-1,1.5);
-\draw (1,1.5) -- (3,2) -- (3,-1) -- (1,-1.5);
-}}$ has a lower number of markings (indeed $\psi_1^{\{n+1\}}$ and $\psi_k^{\{n+1\}}$ restrict to $0$ on this locus, and $\ev_1\equiv\ev_k$); while all other terms have lower degree.
-\item[$\mathcal Y_c$:] {\tikz[baseline=-3pt,scale=.7]{
-\draw (2,0) node[above]{$\{x_1,\ldots,x_{n+1}\}$} node[below]{$d$};
-\draw (2,0) circle(2pt)[fill=white];
-\draw (-1,1.5) -- (1,1.5) -- (1,-1.5) -- (-1,-1.5) -- (-1,1.5);
-\draw (1,1.5) -- (3,2) -- (3,-1) -- (1,-1.5);
-}} contributes $\frac{1}{d}\psi_1^{h_1}H^{k_1}\cdots\psi_n^{h_n}H^{k_n}\cdot[\VZ{(0,\ldots,0,d)}{\PP^N|H}{d}^\thicksim]$ so \emph{there is no cancellation}, while all other terms have lower degree.
- \end{description}
- To sum up, it is possible to determine the reduced genus one restricted invariants of $H$ in terms of those of $\PP^N$ and the genus zero theory, by induction on the degree, number of markings, and total tangency order.
-
 \bibliographystyle{alpha}

### 2019-02-18 GenusOneRelativeMaps.tex
Started description of recursion: need to format algorithm description

@@
 \usepackage[margin=3.5cm]{geometry}
+\usepackage[noend,boxruled]{algorithm2e}
 
@@
 
-\subsection{Recursion procedure for reduced rubber integrals} \footnote{(Navid) To be superseded by general recursion section} In the recursion above, certain terms appear which are integrals over moduli spaces of reduced log stable maps to rubber (as defined in \S \ref{}):
+\section{Quantum Lefschetz recursion}
+Consider a smooth pair $(X,Y)$ with $Y$ very ample, and let $P$ be the projective bundle $P=\PP_Y(\OO(Y)\oplus\OO)$.
+We assume that the genus zero and reduced genus one Gromov--Witten theories of $X$ are known.
+From this starting data, we will apply our recursion formula to compute:
+\begin{enumerate}
+\item the genus one \textbf{reduced restricted absolute Gromov--Witten theory} of $Y$;
+\item the genus one \textbf{reduced relative Gromov--Witten theory} of the pair $(X,Y)$;
+\item a certain slice of the genus one \textbf{reduced rubber theory} of $P$.
+\end{enumerate}
+
+\subsection{Reduced absolute, relative and special rubber invariants} To be precise: by a reduced invariant of $Y$ we mean an integral over $\VZ_{1,n}(Y,\beta)$ of products of pullbacks of evaluation and psi classes along morphisms which forget a subset $S$ of the marked points (taking $S=\emptyset$ gives the ordinary evaluation and psi classes).
+Here the evaluation maps are viewed as mapping into $X$ (hence the adjective ``restricted'').
+Reduced relative invariants of $(X,Y)$ are defined in the same way, except now the forgetful morphism maps into a space of absolute maps:
+\begin{equation*} \fgt_S \colon \VZ_{1,\alpha}(X|Y,\beta) \to \VZ_{1,n-\#S}(X,\beta).\end{equation*}
+In particular, all the psi classes which we consider are \emph{collapsed psi classes}, meaning that they are relative cotangent line classes for the corresponding collapsed stable map.
+Note that, unlike in the absolute case, in the relative case it may well be the case that the entire insertion is pulled back along a forgetful map $\fgt_S$.
+
+The reduced rubber invariants of $P$ are defined similarly (again using collapsed psi classes).
+The particular slice we are interested in is the theory of \textbf{special reduced rubber invariants}.
+These are by definition the rubber invariants which involve at least one marked point of negative tangency (meaning nonzero tangency to $Y_0$), and such that the negative-tangency markings carry only primary insertions.
+The significance of this class of rubber invariants will become clear during the recursion.
+
+The systems of invariants defined above are equivalent to the classical systems of invariants (which do not use forgetful morphisms) by well-known topological recursion relations.
+
+\subsection{Fictitious and true markings} The recursion procedure is rather delicate.
+Roughly speaking, we will induct on the degree (meaning $d=Y\cdot\beta$), number of marked points and total tangency.
+To make sense of these last two in the relative setting, we introduce the notion of \textbf{fictitious markings}.
+Consider a moduli space $\VZ_{1,\alpha}(X|Y,\beta)$ of reduced relative stable maps and a corresponding integrand $\gamma$.
+We let $F \subseteq \{1,\ldots,m\}$ be the maximal subset of marked points such that:
+\begin{enumerate}
+\item $\alpha_i = 1$ for all $i \in F$;
+\item the integrand $\gamma$ is pulled back along $\fgt_F$.
+\end{enumerate}
+This subset is uniquely determined, and its elements are referred to as \textbf{fictitious markings}.
+Markings which are not fictitious are referred to as \textbf{true}.
+When inducing on relative invariants we will always be interested in the number of true markings (as opposed to the total number of markings) and the true tangency
+\begin{equation*} \sum_{i \in T} \alpha_i \leq d=Y\cdot \beta \end{equation*}
+where $T = \{1,\ldots,m\} \setminus F$ is the set of true markings.
+
+\subsection{Structure of the recursion} Given the genus-zero Gromov--Witten theory of $X$, the arguments of \cite{Ga} give an effective algorithm to reconstruct the genus-zero theories of $Y$ and $(X,Y)$.
+Moreover, the genus-zero rubber theory of $P$ is identical to the genus-zero theory of $Y$ \cite{GathmannThesis}.
+Thus we may assume that all genus-zero data is known.
+We assume in addition that we know the genus one reduced theory of $X$.
+The structure of the recursion is then as follows:
+
+\begin{algorithm}
+\DontPrintSemicolon
+\For{$d \geq 0$}{
+\For{$n \geq 0$}{
+\For{$t \geq 0$\medskip}{
+\textbf{\, Step 1: } Compute forgetful relative invariants of $(X,Y)$ (degree~$d$, $n+1$ true markings, true tangency $t$).
+}
+\medskip \textbf{Step 2: } Compute absolute invariants of $Y$ (degree $d$, $n$ markings).\;
+\For{$t \geq 0$\medskip}{
+\textbf{\, Step 3: } Compute relative invariants of $(X,Y)$ (degree $d$, $n$ true markings, true tangency $t$).\;
+}
+}
+\For{$n \geq 0$\medskip}{
+\textbf{\, Step 4: } Compute special rubber invariants of $P$ (degree $d$, $n$ relative markings).
+}
+}
+\end{algorithm}
+\noindent Here a \textbf{forgetful relative invariant} of $(X,Y)$ is by definition a reduced relative invariant with a marked point $x_0$ such that all of the insertions are pulled back along $\fgt_{x_0}$.
+In our recursion, we first deal with this special class of relative invariants (with $n+1$ true markings), before computing the absolute invariants (with $n$ markings) and then returning to compute the general relative invariants (with $n$ true markings).
+The separate treatment of a particular subclass of relative invariants is an inescapable feature of the genus one recursion.
+
+The base terms of the recursion all have $d=0$ and as such are easy to compute: the relative invariants of $(X,Y)$ are nothing but absolute invariants of $X$, the absolute invariants of $Y$ are given by obstruction bundle integrals over Deligne--Mumford spaces, and the special rubber invariants of $P$ are also given by integrals over Deligne--Mumford spaces, using the formula for the double ramification cycle \cite{Hain,JPPZ}.
+We will now explain how to perform each of the four steps outlined above.
+
+\subsection*{Step 1: } Suppose we are given a relative space $\VZ_{1,\alpha}(X|Y,\beta)$ of degree $d$, with $n+1$ relative markings and true tangency $t$, and a special marking $x_0$ such that the insertion $\gamma$ is pulled back along $\fgt_{x_0}$.
+
+\newpage
+
+\section{Recursion procedure for reduced rubber integrals} \footnote{(Navid) To be superseded by general recursion section} In the recursion above, certain terms appear which are integrals over moduli spaces of reduced log stable maps to rubber (as defined in \S \ref{}):
 \begin{equation*}\VZ_{1,\alpha}(P|H_0+H_\infty)_{\Gm}.\end{equation*}

### 2019-02-18 GenusOneRelativeMaps.tex
Finished description of general structure. Started detailing steps

@@
 \usepackage[margin=3.5cm]{geometry}
+
 \usepackage[noend,boxruled]{algorithm2e}
+%Customize appearance using line below:
+\SetKwFor{For}{\normalfont{for}}{:}{endfor}
 
@@
 \newtheorem{conj}[thm]{Conjecture}
+\newtheorem{notation}[thm]{Notation}
 
@@
 In particular, all the psi classes which we consider are \emph{collapsed psi classes}, meaning that they are relative cotangent line classes for the corresponding collapsed stable map.
-Note that, unlike in the absolute case, in the relative case it may well be the case that the entire insertion is pulled back along a forgetful map $\fgt_S$.
+Note that, unlike in the absolute case, in the relative case it may well be the case that the entire insertion is pulled back along a single forgetful map $\fgt_S$.
 
@@
 \item $\alpha_i = 1$ for all $i \in F$;
-\item the integrand $\gamma$ is pulled back along $\fgt_F$.
+\item the entire integrand $\gamma$ is pulled back along $\fgt_F$.
 \end{enumerate}
@@
 Markings which are not fictitious are referred to as \textbf{true}.
-When inducing on relative invariants we will always be interested in the number of true markings (as opposed to the total number of markings) and the true tangency
-\begin{equation*} \sum_{i \in T} \alpha_i \leq d=Y\cdot \beta \end{equation*}
-where $T = \{1,\ldots,m\} \setminus F$ is the set of true markings.
-
-\subsection{Structure of the recursion} Given the genus-zero Gromov--Witten theory of $X$, the arguments of \cite{Ga} give an effective algorithm to reconstruct the genus-zero theories of $Y$ and $(X,Y)$.
-Moreover, the genus-zero rubber theory of $P$ is identical to the genus-zero theory of $Y$ \cite{GathmannThesis}.
+When inducting on relative invariants we will always be interested in the number of true markings (as opposed to the total number of markings) and the true tangency
+\begin{equation*} \sum_{i \not\in F} \alpha_i \leq d=Y\cdot \beta \end{equation*}
+as opposed to the total tangency, which is always $d$.
+
+\subsection{Structure of the recursion} Given the genus-zero Gromov--Witten theory of $X$, the arguments of \cite{Ga} give an effective algorithm to reconstruct the genus-zero theories of $Y$ and $(X,Y)$; moreover, the genus-zero rubber theory of $P$ is identical to the genus-zero theory of $Y$ \cite{GathmannThesis}.
 Thus we may assume that all genus-zero data is known.
@@
 \end{algorithm}
-\noindent Here a \textbf{forgetful relative invariant} of $(X,Y)$ is by definition a reduced relative invariant with a marked point $x_0$ such that all of the insertions are pulled back along $\fgt_{x_0}$.
+\noindent Although the loops involving $d$ and $n$ have infinite length, in order to compute any single invariant it is only necessarily to iterate the preceding loops for a finite amount of time.
+Here a \textbf{forgetful relative invariant} of $(X,Y)$ is by definition a reduced relative invariant with a marked point $x_0$ such that all of the insertions are pulled back along $\fgt_{x_0}$.
 In our recursion, we first deal with this special class of relative invariants (with $n+1$ true markings), before computing the absolute invariants (with $n$ markings) and then returning to compute the general relative invariants (with $n$ true markings).
-The separate treatment of a particular subclass of relative invariants is an inescapable feature of the genus one recursion.
-
-The base terms of the recursion all have $d=0$ and as such are easy to compute: the relative invariants of $(X,Y)$ are nothing but absolute invariants of $X$, the absolute invariants of $Y$ are given by obstruction bundle integrals over Deligne--Mumford spaces, and the special rubber invariants of $P$ are also given by integrals over Deligne--Mumford spaces, using the formula for the double ramification cycle \cite{Hain,JPPZ}.
+This separate treatment of a particular subclass of relative invariants is an inescapable feature of the genus one recursion.
+
+The base terms of the recursion all have $d=0$ and as such are easy to compute: the relative invariants of $(X,Y)$ are nothing but absolute invariants of $X$, the absolute invariants of $Y$ are given by obstruction bundle integrals over Deligne--Mumford spaces, and the special rubber invariants of $P$ are also given by integrals over Deligne--Mumford spaces, using the formula for the double ramification cycle \cite{Hain,JPPZ} in terms of tautological classes.
 We will now explain how to perform each of the four steps outlined above.
 
-\subsection*{Step 1: } Suppose we are given a relative space $\VZ_{1,\alpha}(X|Y,\beta)$ of degree $d$, with $n+1$ relative markings and true tangency $t$, and a special marking $x_0$ such that the insertion $\gamma$ is pulled back along $\fgt_{x_0}$.
+\begin{notation}Given tuples $\mathbf{a}=(a_1,\ldots,a_n)$ and $\mathbf{b}=(b_1,\ldots,b_n)$, we say that $\mathbf{a}<\mathbf{b}$ if there exists an $i \in \{1,\ldots,n\}$ such that $a_j = b_j$ for $j < i$ and $a_i < b_i$.\end{notation}
+
+\subsection*{Step 1: } Suppose we are given a forgetful relative invariant to compute.
+That is, we have a relative space $\VZ_{1,\alpha}(X|Y,\beta)$ of degree $d$, with $n+1$ relative markings and true tangency $t$, and a special marking $x_0$ such that the insertion $\gamma$ is pulled back along $\fgt_{x_0}$, and we are trying to compute the integral $G$ of $\gamma$ over the relative space.
+We assume inductively that every absolute, relative and special rubber invariant with $(d^\prime,n^\prime) < (d,n)$ is known, and also that every forgetful relative invariant with $(d^\prime,n^\prime,t^\prime) < (d,n+1,t)$ is known.
+Choose a true marking $x_1$ with $\alpha_1 \geq 1$ and consider the space:
+\begin{equation*} \VZ_{1,(\alpha-e_1) \cup (1)}(X|Y,\beta). \end{equation*}
+Denote the newly-introduced marking by $y$ and consider the integrand $\tilde\gamma$ obtained from $\gamma$ by introducing $\fgt_y^\st$ everywhere. Applying our recursion formula to $x_1$, we obtain:
+\begin{equation*}\left( (\alpha_1-1)\psi_1 + \ev_1^\st H\right) \tilde\gamma \cap [\VZ_{1,(\alpha-e_1) \cup (1)}(X|Y,\beta)] = \tilde\gamma \cap [\Dcal(1)].\end{equation*}
+Let us first examine the left-hand side.
+The class $\psi_1$ differs from $\fgt_y^\st \psi_1$ by the locus where $x_1$ and $y$ are contained on a contracted rational bubble.
+This locus consists of reduced relative stable maps of the form \medskip
+
+\begin{center}
+\begin{tikzpicture}[scale=2]
+\draw (0,0) -- (3,0) -- (3,2) -- (0,2) -- (0,0);
+\draw [blue] plot [smooth cycle, tension=0.5] coordinates{(3,1) (1,1.7) (0.5,1) (1,0.3)};
+\draw [blue] plot [smooth] coordinates {(1.1,0.9) (1.4,1.1) (1.7,0.9)};
+
+\draw (3,0) -- (6,0) -- (6,2) -- (3,2) -- (3,0);
+\end{tikzpicture}
+\end{center}
 
@@
 \noindent Luca Battistella\\
-Department of Mathematics, Imperial College London \\
-\texttt{l.battistella14@imperial.ac.uk}\\
+Max-Planck-Institut f\"ur Mathematik, Bonn \\
+\href{mailto:battistella@mpim-bonn.mpg.de}{battistella@mpim-bonn.mpg.de}\\
 
 \noindent Navid Nabijou \\
-Department of Mathematics, Imperial College London \\
-\texttt{navid.nabijou09@imperial.ac.uk}\\
+School of Mathematics and Statistics, University of Glasgow \\
+\href{mailto:Navid.Nabijou@glasgow.ac.uk}{navid.nabijou@glasgow.ac.uk}\\
 
 \noindent Dhruv Ranganathan \\
-Department of Mathematics, Massachusetts Institute of Technology \\
-\texttt{dhruvr@mit.edu}
+DPMMS, University of Cambridge \\
+\href{mailto:dr508@cam.ac.uk}{dr508@cam.ac.uk}
 

### 2019-02-18 GenusOneRelativeMaps.tex
Completed Step 1

@@
 \subsection*{Step 1: } Suppose we are given a forgetful relative invariant to compute.
-That is, we have a relative space $\VZ_{1,\alpha}(X|Y,\beta)$ of degree $d$, with $n+1$ relative markings and true tangency $t$, and a special marking $x_0$ such that the insertion $\gamma$ is pulled back along $\fgt_{x_0}$, and we are trying to compute the integral $G$ of $\gamma$ over the relative space.
+That is, we have a relative space $\VZ_{1,\alpha}(X|Y,\beta)$ of degree $d$, with $n+1$ relative markings and true tangency $t$, and a marking $x_0$ such that the insertion $\gamma$ is pulled back along $\fgt_{x_0}$.
 We assume inductively that every absolute, relative and special rubber invariant with $(d^\prime,n^\prime) < (d,n)$ is known, and also that every forgetful relative invariant with $(d^\prime,n^\prime,t^\prime) < (d,n+1,t)$ is known.
@@
 Denote the newly-introduced marking by $y$ and consider the integrand $\tilde\gamma$ obtained from $\gamma$ by introducing $\fgt_y^\st$ everywhere. Applying our recursion formula to $x_1$, we obtain:
-\begin{equation*}\left( (\alpha_1-1)\psi_1 + \ev_1^\st H\right) \tilde\gamma \cap [\VZ_{1,(\alpha-e_1) \cup (1)}(X|Y,\beta)] = \tilde\gamma \cap [\Dcal(1)].\end{equation*}
+\begin{equation}\label{step 1 recursion}\left( (\alpha_1-1)\psi_1 + \ev_1^\st Y\right) \tilde\gamma \cap [\VZ_{1,(\alpha-e_1) \cup (1)}(X|Y,\beta)] = \tilde\gamma \cap [\Dcal(1)].\end{equation}
 Let us first examine the left-hand side.
@@
 \begin{center}
-\begin{tikzpicture}[scale=2]
+\begin{tikzpicture}[scale=1.5]
+%Draw target
 \draw (0,0) -- (3,0) -- (3,2) -- (0,2) -- (0,0);
-\draw [blue] plot [smooth cycle, tension=0.5] coordinates{(3,1) (1,1.7) (0.5,1) (1,0.3)};
-\draw [blue] plot [smooth] coordinates {(1.1,0.9) (1.4,1.1) (1.7,0.9)};
-
 \draw (3,0) -- (6,0) -- (6,2) -- (3,2) -- (3,0);
+
+%Draw genus one curve on left-hand side
+\draw [blue] (3,0.5) to [out=90,in=270] (2.7,1) to [out=90,in=270] (3,1.5) to [out=90,in=0] (1,1.7) to [out=180,in=90] (0.5,1) to [out=270,in=180] (1,0.3) to [out=0,in=270] (3,0.5);
+\draw [blue] (1.1,0.9) to [out=40, in=180] (1.4,1.1) to [out=0,in=140] (1.7,0.9);
+\draw [blue] (1.2,1) to [out=300, in=180] (1.4,0.9) to [out=0,in=240] (1.6,1);
+
+%Draw nodal blobs
+\draw [fill=blue,color=blue] (3,0.5) circle[radius=1pt];
+\draw [color=blue] (3,0.5) node[left]{\small$\alpha_2$};
+\draw [fill=blue,color=blue] (3,1.5) circle[radius=1pt];
+\draw [color=blue] (3,1.5) node[left]{\small$\alpha_1$};
+%Draw rational bubble with x_1 and y
+\draw [blue] (3,1.5) to [out=70,in=190] (5.5,1.9) to [out=0,in=90] (6,1.8) to [out=270,in=90] (5.75,1.5) to [out=270,in=90] (6,1.2) to [out=270,in=10] (5.5,1.1) to [out=180,in=290] (3,1.5);
+
+%Draw right-hand markings
+\draw [fill=blue,color=blue] (6,1.8) circle[radius=1pt];
+\draw [color=blue] (6,1.8) node[left]{\small{$\alpha_1-1$}};
+\draw (6,1.8) node[right]{$x_1$};
+\draw [fill=blue,color=blue] (6,1.2) circle[radius=1pt];
+\draw [color=blue] (6,1.2) node[left]{\small{$1$}};
+\draw (6,1.2) node[right]{$y$};
+
+%Draw ldots
+\draw [color=blue] (4,0.5) node[right]{$\ldots$};
 \end{tikzpicture}
 \end{center}
+with only trivial bubbles mapping to higher level.
+This is isomorphic to $\VZ_{1,\alpha}(X|Y,\beta)$ and when we restrict $\tilde\gamma$ to this locus we obtain precisely the class $\gamma$ which we started with.
+Thus the left-hand side of \eqref{step 1 recursion} may be written as
+\begin{equation*} (\alpha_1-1) I + \fgt_y^\st \left( (\alpha_1-1)\psi_1 + \ev_1^\st Y\right)  \tilde\gamma \cap [\VZ_{1,(\alpha-e_1)\cup(1)}(X|Y,\beta)]\end{equation*}
+where $I$ is the invariant we are trying to compute.
+The second term is a forgetful relative invariant with the same degree and number of true markings (since $y$ is fictitious), and strictly smaller true tangency.
+Hence it is recursively known.
+We now examine the right-hand side of \eqref{step 1 recursion}.
+Recall that all of the genus zero data has already been computed, so we only need to focus on the genus one pieces.
+First consider the type $A$ loci.
+The genus one piece has strictly smaller degree (and hence is recursively known) exept in the following situation (with some stable distribution of the remaining markings):
+\begin{center}
+\begin{tikzpicture}[scale=1]
+\draw (0,0) to (2,0);
+\draw [fill=white] (0,0) circle[radius=3pt];
+\draw (0,-0.1) node[below]{\small$d$};
+\draw [fill=black] (2,0) circle[radius=3pt];
+\draw (2,-0.1) node[below]{\small$0$};
+\draw [->] (2,0) -- (3,0);
+\draw (2.9,0) node[right]{$x_1$};
+\end{tikzpicture}
+\end{center}
+In this situation, $C_1$ contains at most $n+1$ true markings.
+If it has $n-1$ or fewer, than it is known recursively.
+If it has exactly $n$ this means that $C_0$ contains exactly one true marking (besides $x_1$, which may be true or fictitious).
+We claim that in this situation we must have $y \in C_1$: otherwise, we have a moduli space $\ol\Mcal_{0,k}$ for $C_0$ with $k \geq 4$, and  applying the projection formula with $\fgt_y$ we conclude that the contribution is zero.
+Thus we have $y \in C_1$, and so the genus one contribution is a forgetful relative invariant with $n$ true markings, and hence is recursively known.
+
+Finally, if $C_1$ contains exactly $n+1$ true markings, then the only additional markings $C_0$ are fictitious, and by the same argument as in the previous paragraph there can only be one.
+Thus for each fictitious marked point we obtain a locus isomorphic to $\VZ_{1,\alpha}(X|Y,\beta)$ and $\tilde\gamma$ restricts to $\gamma$ here (from the point of view of computing invariants the fictitious marked points are indistinguishable, meaning that the contributions are all the same).
+Thus for each fictitious marked point (of which there is at least one, namely $y$) we get a contribution of $\alpha_1 I$.
+
+The contributions of the type $B$ loci only involve genus zero data and hence are known.
+The contributions of the type $C^0$ loci are determined by genus zero data and tautological integrals on Deligne--Mumford space, hence are also known.
+It remains to consider type $C^+$ loci.
+If the degree of the genus one piece is less than $d$ then we have a reduced rubber integral of strictly smaller degree.
+The only other possibility is that the entire curve is mapped into the divisor.
+In this case we may apply the projection formula with $\fgt_y$ to identify this with an integral over $\VZ_{1,m}(Y,\beta)$ for some (possibly large) number $m$ of marked points.
+But by assumption there is another marked point $x_0$ with all of the insertions pulled back along $\fgt_{x_0}$, so a further application of the projection formula shows that this contribution vanishes.
+To conclude, we may rearrange \eqref{step 1 recursion} to obtain an expression of the form
+\begin{equation*} \lambda I = \text{recursively known terms} \end{equation*}
+where $\lambda$ is an explicit scalar which is always nonzero; we have thus determined $I$, which completes Step 1.
 

### 2019-02-19 GenusOneRelativeMaps.tex
Minor changes to tropical pictures in Step 1

@@
 \section{Quantum Lefschetz recursion}
-Consider a smooth pair $(X,Y)$ with $Y$ very ample, and let $P$ be the projective bundle $P=\PP_Y(\OO(Y)\oplus\OO)$.
+Consider a smooth pair $(X,Y)$ with $Y$ very ample, and let $P$ be the projective bundle $P=\PP_Y(\operatorname{N}_{Y|X} \oplus\OO_Y)$.
 We assume that the genus zero and reduced genus one Gromov--Witten theories of $X$ are known.
@@
 Reduced relative invariants of $(X,Y)$ are defined in the same way, except now the forgetful morphism maps into a space of absolute maps:
-\begin{equation*} \fgt_S \colon \VZ_{1,\alpha}(X|Y,\beta) \to \VZ_{1,n-\#S}(X,\beta).\end{equation*}
+\begin{equation*} \fgt_S \colon \VZ_{1,\alpha}(X|Y,\beta) \to \VZ_{1,m-\#S}(X,\beta).\end{equation*}
 In particular, all the psi classes which we consider are \emph{collapsed psi classes}, meaning that they are relative cotangent line classes for the corresponding collapsed stable map.
@@
 \subsection{Fictitious and true markings} The recursion procedure is rather delicate.
-Roughly speaking, we will induct on the degree (meaning $d=Y\cdot\beta$), number of marked points and total tangency.
+Roughly speaking, we will induct on the degree (meaning $Y\cdot\beta$), number of marked points and total tangency.
 To make sense of these last two in the relative setting, we introduce the notion of \textbf{fictitious markings}.
@@
 as opposed to the total tangency, which is always $d$.
-
-\subsection{Structure of the recursion} Given the genus-zero Gromov--Witten theory of $X$, the arguments of \cite{Ga} give an effective algorithm to reconstruct the genus-zero theories of $Y$ and $(X,Y)$; moreover, the genus-zero rubber theory of $P$ is identical to the genus-zero theory of $Y$ \cite{GathmannThesis}.
+This formalises the idea that relative invariants with non-maximal tangency $t<d$ can be obtained by adding $d-t$ fictitious markings of tangency $1$; see \cite[Lemma 1.15(i)]{Ga}.
+
+\subsection{Structure of the recursion} Given the genus-zero Gromov--Witten theory of $X$, the arguments of \cite{Ga} give an effective algorithm to reconstruct the genus-zero theories of $Y$ and $(X,Y)$; moreover, the genus-zero rubber theory of $P$ is identical to the genus-zero theory of $Y$ \cite[]{GathmannThesis}.
 Thus we may assume that all genus-zero data is known.
@@
 \For{$t \geq 0$\medskip}{
-\textbf{\, Step 1: } Compute forgetful relative invariants of $(X,Y)$ (degree~$d$, $n+1$ true markings, true tangency $t$).
+\textbf{\, Step 1: } Compute forgetful relative invariants of $(X,Y)$ (degree~$d$, $n+1$ true markings, true tangency $t$); see below.
 }
@@
 \noindent Although the loops involving $d$ and $n$ have infinite length, in order to compute any single invariant it is only necessarily to iterate the preceding loops for a finite amount of time.
-Here a \textbf{forgetful relative invariant} of $(X,Y)$ is by definition a reduced relative invariant with a marked point $x_0$ such that all of the insertions are pulled back along $\fgt_{x_0}$.
-In our recursion, we first deal with this special class of relative invariants (with $n+1$ true markings), before computing the absolute invariants (with $n$ markings) and then returning to compute the general relative invariants (with $n$ true markings).
-This separate treatment of a particular subclass of relative invariants is an inescapable feature of the genus one recursion.
+A \textbf{forgetful relative invariant} of $(X,Y)$ is by definition a reduced relative invariant with a marked point $x_0$ such that all of the insertions are pulled back along $\fgt_{x_0}$.
+In our recursion, we first deal with this special class of relative invariants (with $n+1$ true markings), before computing the absolute invariants (with $n$ markings) and then returning to compute the relative invariants (with $n$ true markings).
+This need to treat separately a particular subclass of the relative invariants is an inescapable feature of the genus one recursion.
 
 The base terms of the recursion all have $d=0$ and as such are easy to compute: the relative invariants of $(X,Y)$ are nothing but absolute invariants of $X$, the absolute invariants of $Y$ are given by obstruction bundle integrals over Deligne--Mumford spaces, and the special rubber invariants of $P$ are also given by integrals over Deligne--Mumford spaces, using the formula for the double ramification cycle \cite{Hain,JPPZ} in terms of tautological classes.
-We will now explain how to perform each of the four steps outlined above.
+We will now explain how to perform each of the four inductive steps outlined above.
 
@@
 \begin{center}
+\begin{tikzpicture}[scale=1]
+%edge
+\draw (0,0) to (2,0);
+\draw [color=blue] (1,0) node[above]{\tiny$\alpha_1$};
+
+%C_1
+\draw [fill=white] (0,0) circle[radius=3pt];
+\draw (0,-0.1) node[below]{\small$d$};
+\draw (0,0) node[above]{\small$\sqC_1$};
+
+%C_0
+\draw [fill=black] (2,0) circle[radius=3pt];
+\draw (2,-0.1) node[below]{\small$0$};
+\draw (2,0) node[above]{\small$\sqC_0$};
+
+%x_1
+\draw [->] (2,0.1) -- (4,0.1);
+\draw (3.9,0.1) node[above]{\small$x_1$};
+\draw [color=blue](3,0.1) node[above]{\tiny$\alpha_1-1$};
+
+%y
+\draw [->] (2,-0.1) -- (4,-0.1);
+\draw (3.9,-0.1) node[below]{\small$y$};
+\draw [color=blue] (3,-0.1) node[below]{\tiny$1$};
+
+%down arrow
+\draw [color=blue,->] (1,-0.3) -- (1,-0.7);
+
+%target
+\draw [color=blue,->] (0,-1) to (2,-1);
+\draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
+\draw [color=blue] (2,-1) node[right]{\small$\Sigma(X|Y)$};
+\end{tikzpicture}
+\end{center}
+% Algebro-geometric picture; replaced by tropical picture.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{comment}
+\begin{center}
 \begin{tikzpicture}[scale=1.5]
@@
 \end{center}
-with only trivial bubbles mapping to higher level.
+\end{comment}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+with all other marked points contained on $\sqC_1$.
 This is isomorphic to $\VZ_{1,\alpha}(X|Y,\beta)$ and when we restrict $\tilde\gamma$ to this locus we obtain precisely the class $\gamma$ which we started with.
@@
 \draw (0,-0.1) node[below]{\small$d$};
+\draw (0,0) node[above]{\small$\sqC_1$};
 \draw [fill=black] (2,0) circle[radius=3pt];
 \draw (2,-0.1) node[below]{\small$0$};
+\draw (2,0) node[above]{\small$\sqC_0$};
 \draw [->] (2,0) -- (3,0);
 \draw (2.9,0) node[right]{$x_1$};
+
+\draw [color=blue,->] (1,-0.3) -- (1,-0.7);
+
+\draw [color=blue,->] (0,-1) to (2,-1);
+\draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
+\draw [color=blue] (2,-1) node[right]{\small$\Sigma(X|Y)$};
 \end{tikzpicture}
@@
 If it has exactly $n$ this means that $C_0$ contains exactly one true marking (besides $x_1$, which may be true or fictitious).
-We claim that in this situation we must have $y \in C_1$: otherwise, we have a moduli space $\ol\Mcal_{0,k}$ for $C_0$ with $k \geq 4$, and  applying the projection formula with $\fgt_y$ we conclude that the contribution is zero.
+We claim that in this situation we must have $y \in C_1$, since otherwise we would have a moduli space for $C_0$ given by $\ol\Mcal_{0,k}$ with $k \geq 4$, and  applying the projection formula with $\fgt_y$ we would conclude that the contribution is zero.
 Thus we have $y \in C_1$, and so the genus one contribution is a forgetful relative invariant with $n$ true markings, and hence is recursively known.
 
-Finally, if $C_1$ contains exactly $n+1$ true markings, then the only additional markings $C_0$ are fictitious, and by the same argument as in the previous paragraph there can only be one.
+Finally, if $C_1$ contains exactly $n+1$ true markings, then the only additional markings on $C_0$ are fictitious, and by the same argument as in the previous paragraph there can only be one.
 Thus for each fictitious marked point we obtain a locus isomorphic to $\VZ_{1,\alpha}(X|Y,\beta)$ and $\tilde\gamma$ restricts to $\gamma$ here (from the point of view of computing invariants the fictitious marked points are indistinguishable, meaning that the contributions are all the same).
-Thus for each fictitious marked point (of which there is at least one, namely $y$) we get a contribution of $\alpha_1 I$.
+Thus for each fictitious marked point (of which there is at least one, namely $y$) we get a contribution of $\alpha_1 I$ to the right-hand side of \eqref{step 1 recursion}.
 

### 2019-02-19 GenusOneRelativeMaps.tex
Finished Step 2, except for mistake! Need to revisit

@@
 
+\subsection*{Step 2} Consider now the absolute space $\VZ_{1,n}(Y,\beta)$ with an insertion $\gamma$, and suppose inductively that we have computed all forgetful relative invariants with $(d^\prime,n^\prime) \leq (d,n+1)$, all relative invariants and absolute invariants with $(d^\prime,n^\prime) < (d,n)$, and all special rubber invariants with $d^\prime < d$.
+Consider the following moduli space with $n+1$ markings:
+\begin{equation*} \VZ_{1,(d,0,\ldots,0)}(X|Y,\beta). \end{equation*}
+Let $x_0$ denote the relative marking and consider the integrand $\tilde\gamma$ obtained from $\gamma$ by introducing $\fgt^\st_{x_0}$ everywhere. Now recurse at $x_1$ to obtain:
+\begin{equation}\label{step 2 recursion} \ev_1^\st Y \cdot \tilde\gamma \cap [\VZ_{1,(d,0,\ldots,0)}(X|Y,\beta)] = \tilde\gamma\cap[\Dcal(1)].\end{equation}
+The left-hand side is a forgetful relative invariant of degree $d$ and $\leq n+1$ true markings, and so has already been computed.
+For the right-hand, let us begin with loci of type $A$.
+The genus one contributions from each loci have $(d^\prime,n^\prime) < (d,n)$ except in the following case
+\begin{center}
+\begin{tikzpicture}[scale=1]
+%edge
+\draw (0,0) to (2,0);
+\draw [color=blue] (1,0) node[above]{\tiny$d$};
+
+%C_1
+\draw [fill=white] (0,0) circle[radius=3pt];
+\draw (0,-0.1) node[below]{\small$d$};
+\draw (0,0) node[above]{\small$\sqC_1$};
+
+%C_0
+\draw [fill=black] (2,0) circle[radius=3pt];
+\draw (2,-0.1) node[below]{\small$0$};
+\draw (2,0) node[above]{\small$\sqC_0$};
+
+%x_1
+\draw [->] (2,0.1) -- (4,0.1);
+\draw (3.9,0.1) node[above]{\small$x_1$};
+\draw [color=blue](3,0.1) node[above]{\tiny$0$};
+
+%y
+\draw [->] (2,-0.1) -- (4,-0.1);
+\draw (3.9,-0.1) node[below]{\small$x_0$};
+\draw [color=blue] (3,-0.1) node[below]{\tiny$d$};
+
+%down arrow
+\draw [color=blue,->] (1,-0.3) -- (1,-0.7);
+
+%target
+\draw [color=blue,->] (0,-1) to (2,-1);
+\draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
+\draw [color=blue] (2,-1) node[right]{\small$\Sigma(X|Y)$};
+\end{tikzpicture}
+\end{center}
+which gives a contribution of
+\begin{equation*} d\cdot \tilde\gamma \cap [\VZ_{1,(d,\underbrace{0,\ldots,0}_{n-1})}(X|Y,\beta)] \end{equation*}
+to the right-hand side of \eqref{step 2 recursion}.
+The type $B$ and $C^0$ loci are recursively determined as in Step~1, and similarly the type $C^+$ loci are recursively determined except for the locus where the entire curve is mapped into the divisor.
+On this locus we may apply $\fgt_{x_0}$ and identify the contribution with
+\begin{equation*} d^2 \cdot \gamma \cap [\VZ_{1,n}(Y,\beta)] = d^2 \cdot I \end{equation*}
+where $I$ is the invariant we are trying to compute. Putting this all together, we obtain
+\begin{equation}\label{step 2 recursion 2} I = (-\tilde\gamma/d) \cap [\VZ_{1,(d,0,\ldots,0)}(X|Y,\beta)] + \text{recursively known terms} \end{equation}
+where on the right-hand side there are $n-1$ non-relative markings $x_2,\ldots,x_n$, and a relative marking $x_1$. We now apply the recursion again to the right-hand side, by considering the space
+\begin{equation*} \VZ_{1,(d-1,1,0,\ldots,0)}(X|Y,\beta) \end{equation*}
+where $x_1$ now has tangency $d-1$ and we have introduced a new marking $y$ with tangency $1$.
+We obtain a new insertion, also denoted $\tilde\gamma$, by introducing $\fgt_y^\st$ everywhere.
+Recursing at $x_1$ we obtain:
+\begin{equation*} \left( (d-1)\psi_1 + \ev_1^\st Y \right)(-\tilde\gamma/d) \cap [\VZ_{1,(d-1,1,0,\ldots,0)}(X|Y,\beta)] = (-\tilde\gamma/d) \cap [\Dcal(1)].\end{equation*}
+The left-hand side is a forgetful relative invariant of degree $d$ and $n+1$ markings ($y$ being the ``forgetful'' marking), hence is recursively known.
+On the right-hand side, the type $A$ loci are recursively known except possibly in the following special cases (with some stable distribution of the remaining markings):
+\begin{center}
+\begin{minipage}{0.4\textwidth}
+\begin{tikzpicture}[scale=1]
+%edge
+\draw (0,-0.1) to (2,-0.1);
+\draw [color=blue] (1,-0.1) node[below]{\tiny$d-1$};
+
+%C_1
+\draw [fill=white] (0,0) circle[radius=3pt];
+\draw (0,-0.1) node[below]{\small$d$};
+\draw (0,0) node[above]{\small$\sqC_1$};
+
+%C_0
+\draw [fill=black] (2,0) circle[radius=3pt];
+\draw (2,-0.1) node[below]{\small$0$};
+\draw (2,0) node[above]{\small$\sqC_0$};
+
+%x_1
+\draw [->] (0,0.1) -- (1.5,0.1);
+\draw (1.5,0.1) node[above]{\small$y$};
+\draw [color=blue](0.75,0.1) node[above]{\tiny$1$};
+
+%y
+\draw [->] (2,0) -- (4,0);
+\draw (3.9,0) node[below]{\small$x_1$};
+\draw [color=blue] (3,0) node[below]{\tiny$d-1$};
+
+%down arrow
+\draw [color=blue,->] (1,-0.5) -- (1,-0.9);
+
+%target
+\draw [color=blue,->] (0,-1) to (2,-1);
+\draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
+\draw [color=blue] (2,-1) node[right]{\small$\Sigma(X|Y)$};
+
+\draw (2,-1.5) node[below]{\small{Case 1}};
+\end{tikzpicture}
+\end{minipage}
+\begin{minipage}{0.4\textwidth}
+\begin{tikzpicture}[scale=1]
+%edge
+\draw (0,0) to (2,0);
+\draw [color=blue] (1,0) node[above]{\tiny$d$};
+
+%C_1
+\draw [fill=white] (0,0) circle[radius=3pt];
+\draw (0,-0.1) node[below]{\small$d$};
+\draw (0,0) node[above]{\small$\sqC_1$};
+
+%C_0
+\draw [fill=black] (2,0) circle[radius=3pt];
+\draw (2,-0.1) node[below]{\small$0$};
+\draw (2,0) node[above]{\small$\sqC_0$};
+
+%x_1
+\draw [->] (2,0.1) -- (4,0.1);
+\draw (3.9,0.1) node[above]{\small$y$};
+\draw [color=blue](3,0.1) node[above]{\tiny$1$};
+
+%y
+\draw [->] (2,-0.1) -- (4,-0.1);
+\draw (3.9,-0.1) node[below]{\small$x_1$};
+\draw [color=blue] (3,-0.1) node[below]{\tiny$d-1$};
+
+%down arrow
+\draw [color=blue,->] (1,-0.3) -- (1,-0.7);
+
+%target
+\draw [color=blue,->] (0,-1) to (2,-1);
+\draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
+\draw [color=blue] (2,-1) node[right]{\small$\Sigma(X|Y)$};
+
+\draw (2,-1.5) node[below]{\small{Case 2}};
+\end{tikzpicture}
+\end{minipage}
+\end{center}
+In Case 1 the contribution from $\sqC_1$ is a forgetful relative invariant with $\leq n+1$ markings, hence is recursively known.
+In Case 2, we first note that there cannot be any more markings on $\sqC_0$ (since otherwise we could apply $\fgt_y$ to conclude that the contribution vanishes).
+Thus we obtain a single locus, which contributes precisely
+\begin{equation*} d\cdot(-\tilde\gamma/d) \cap [\VZ_{1,(d,0,\ldots,0)}(X|Y,\beta)] = -\tilde\gamma\cap[\VZ_{1,(d,0,\ldots,0)}(X|Y,\beta)]\end{equation*}
+which is the first term on the right-hand side of \eqref{step 2 recursion 2}.
+As usual the type $B$ and $C^0$ contributions are known recursively, and the only type $C^+$ contribution not known recursively occurs when the entire curve is mapped into the divisor, in which case we obtain:
+\begin{equation*} d^2\cdot(-\gamma/d) \cap [\VZ_{1,n}(X|Y,\beta)] = -d\cdot\gamma \cap [\VZ_{1,n}(X|Y,\beta)].\end{equation*}
+Rearranging in \eqref{step 2 recursion 2} we end up with:
+
+WHOOPS! WE'VE CANCELED OUT! NEED TO TRY HARDER.
+
 \newpage

### 2019-02-19 GenusOneRelativeMaps.tex
Finished Step 2 - it was actually fine in the end

@@
 which gives a contribution of
-\begin{equation*} d\cdot \tilde\gamma \cap [\VZ_{1,(d,\underbrace{0,\ldots,0}_{n-1})}(X|Y,\beta)] \end{equation*}
+\begin{equation*} d\cdot \gamma \cap [\VZ_{1,(d,0,\ldots,0)}(X|Y,\beta)] \end{equation*}
 to the right-hand side of \eqref{step 2 recursion}.
+Here $\gamma$ is the insertion we started with; the difference is that we are now considering relative maps with maximal tangency at $x_1$, rather than absolute maps.
 The type $B$ and $C^0$ loci are recursively determined as in Step~1, and similarly the type $C^+$ loci are recursively determined except for the locus where the entire curve is mapped into the divisor.
@@
 where $x_1$ now has tangency $d-1$ and we have introduced a new marking $y$ with tangency $1$.
-We obtain a new insertion, also denoted $\tilde\gamma$, by introducing $\fgt_y^\st$ everywhere.
+We consider a new insertion, denoted $\tilde\gamma$ as usual, by introducing $\fgt_y^\st$ everywhere.
 Recursing at $x_1$ we obtain:
-\begin{equation*} \left( (d-1)\psi_1 + \ev_1^\st Y \right)(-\tilde\gamma/d) \cap [\VZ_{1,(d-1,1,0,\ldots,0)}(X|Y,\beta)] = (-\tilde\gamma/d) \cap [\Dcal(1)].\end{equation*}
+\begin{equation*} \left( (d-1)\psi_1 + \ev_1^\st Y \right)\cdot(-\tilde\gamma/d) \cap [\VZ_{1,(d-1,1,0,\ldots,0)}(X|Y,\beta)] = (-\tilde\gamma/d) \cap [\Dcal(1)].\end{equation*}
 The left-hand side is a forgetful relative invariant of degree $d$ and $n+1$ markings ($y$ being the ``forgetful'' marking), hence is recursively known.
@@
 
-\draw (2,-1.5) node[below]{\small{Case 1}};
+\draw (2,-1.3) node[below]{\small{Case 1}};
 \end{tikzpicture}
@@
 
-\draw (2,-1.5) node[below]{\small{Case 2}};
+\draw (2,-1.3) node[below]{\small{Case 2}};
 \end{tikzpicture}
@@
 \end{center}
-In Case 1 the contribution from $\sqC_1$ is a forgetful relative invariant with $\leq n+1$ markings, hence is recursively known.
-In Case 2, we first note that there cannot be any more markings on $\sqC_0$ (since otherwise we could apply $\fgt_y$ to conclude that the contribution vanishes).
+In Case 1 the contribution from $C_1$ is a forgetful relative invariant with $\leq n$ true markings, hence is recursively known.
+In Case 2, we first note that there cannot be any more markings on $C_0$ (since otherwise we could apply $\fgt_y$ and conclude that the contribution vanishes).
 Thus we obtain a single locus, which contributes precisely
 \begin{equation*} d\cdot(-\tilde\gamma/d) \cap [\VZ_{1,(d,0,\ldots,0)}(X|Y,\beta)] = -\tilde\gamma\cap[\VZ_{1,(d,0,\ldots,0)}(X|Y,\beta)]\end{equation*}
-which is the first term on the right-hand side of \eqref{step 2 recursion 2}.
-As usual the type $B$ and $C^0$ contributions are known recursively, and the only type $C^+$ contribution not known recursively occurs when the entire curve is mapped into the divisor, in which case we obtain:
-\begin{equation*} d^2\cdot(-\gamma/d) \cap [\VZ_{1,n}(X|Y,\beta)] = -d\cdot\gamma \cap [\VZ_{1,n}(X|Y,\beta)].\end{equation*}
-Rearranging in \eqref{step 2 recursion 2} we end up with:
-
-WHOOPS! WE'VE CANCELED OUT! NEED TO TRY HARDER.
+which gives us the first term on the right-hand side of \eqref{step 2 recursion 2}.
+As usual the type $B$ and $C^0$ contributions are known recursively, and the only type $C^+$ contribution not known recursively occurs when the entire curve is mapped into the divisor, in which case we apply $\fgt_y$ to calculate the contribution as:
+\begin{equation*} (-\gamma/d) \cap [\VZ_{1,n}(X|Y,\beta)] = -I/d.\end{equation*}
+Substituting into \eqref{step 2 recursion 2} we end up with
+\begin{equation*} I(1-d^{-2}) = \text{recursively known terms} \end{equation*}
+which completes the recursion step as long as $d \neq 1$.
+But since $\VZ_{1,n}(H,1)=\emptyset$ it follows that $\VZ_{1,n}(Y,\beta)=\emptyset$ if $d=Y\cdot\beta=1$, so we may always assume $d \geq 2$ in the recursion.
 

### 2019-02-26 GenusOneRelativeMaps.tex
Almost finished writing up Step 4

@@
 Roughly speaking, we will induct on the degree (meaning $Y\cdot\beta$), number of marked points and total tangency.
-To make sense of these last two in the relative setting, we introduce the notion of \textbf{fictitious markings}.
+To get the correct notion of number of markings and total tangency in  the relative setting, we introduce the concept of \textbf{fictitious markings}.
 Consider a moduli space $\VZ_{1,\alpha}(X|Y,\beta)$ of reduced relative stable maps and a corresponding integrand $\gamma$.
@@
 
-\subsection{Structure of the recursion} Given the genus-zero Gromov--Witten theory of $X$, the arguments of \cite{Ga} give an effective algorithm to reconstruct the genus-zero theories of $Y$ and $(X,Y)$; moreover, the genus-zero rubber theory of $P$ is identical to the genus-zero theory of $Y$ \cite[]{GathmannThesis}.
+\subsection{Structure of the recursion} Given the genus-zero Gromov--Witten theory of $X$, the arguments of \cite{Ga} give an effective algorithm to reconstruct the genus-zero theories of $Y$ and $(X,Y)$; moreover, the genus-zero rubber theory of $P$ is identical to the genus-zero theory of $Y$ \cite{GathmannThesis}.
 Thus we may assume that all genus-zero data is known.
@@
 A \textbf{forgetful relative invariant} of $(X,Y)$ is by definition a reduced relative invariant with a marked point $x_0$ such that all of the insertions are pulled back along $\fgt_{x_0}$.
-In our recursion, we first deal with this special class of relative invariants (with $n+1$ true markings), before computing the absolute invariants (with $n$ markings) and then returning to compute the relative invariants (with $n$ true markings).
+In our recursion, we first deal with this special class of relative invariants (with $n+1$ true markings), before computing the absolute invariants (with $n$ markings) and then returning to compute all of the relative invariants (with $n$ true markings).
 This need to treat separately a particular subclass of the relative invariants is an inescapable feature of the genus one recursion.
@@
 
-\subsection*{Step 1: } Suppose we are given a forgetful relative invariant to compute.
-That is, we have a relative space $\VZ_{1,\alpha}(X|Y,\beta)$ of degree $d$, with $n+1$ relative markings and true tangency $t$, and a marking $x_0$ such that the insertion $\gamma$ is pulled back along $\fgt_{x_0}$.
+\subsection*{Step 1} Suppose we are given a forgetful relative invariant to compute.
+That is, we have a relative space $\VZ_{1,\alpha}(X|Y,\beta)$ of degree $d$, with $n+1$ true markings and true tangency $t$, and a marking $x_0$ such that the insertion $\gamma$ is pulled back along $\fgt_{x_0}$.
 We assume inductively that every absolute, relative and special rubber invariant with $(d^\prime,n^\prime) < (d,n)$ is known, and also that every forgetful relative invariant with $(d^\prime,n^\prime,t^\prime) < (d,n+1,t)$ is known.
@@
 where $I$ is the invariant we are trying to compute.
-The second term is a forgetful relative invariant with the same degree and number of true markings (since $y$ is fictitious), and strictly smaller true tangency.
-Hence it is recursively known.
+The second term is a forgetful relative invariant with the same degree and number of true markings (since $y$ is fictitious), and strictly smaller true tangency; hence it is recursively known.
 We now examine the right-hand side of \eqref{step 1 recursion}.
@@
 Finally, if $C_1$ contains exactly $n+1$ true markings, then the only additional markings on $C_0$ are fictitious, and by the same argument as in the previous paragraph there can only be one.
-Thus for each fictitious marked point we obtain a locus isomorphic to $\VZ_{1,\alpha}(X|Y,\beta)$ and $\tilde\gamma$ restricts to $\gamma$ here (from the point of view of computing invariants the fictitious marked points are indistinguishable, meaning that the contributions are all the same).
+Thus for each fictitious marked point we obtain a locus isomorphic to $\VZ_{1,\alpha}(X|Y,\beta)$ and $\tilde\gamma$ restricts to $\gamma$ here (from the point of view of computing invariants, the fictitious marked points are indistinguishable, meaning that the contributions are all the same).
 Thus for each fictitious marked point (of which there is at least one, namely $y$) we get a contribution of $\alpha_1 I$ to the right-hand side of \eqref{step 1 recursion}.
@@
 It remains to consider type $C^+$ loci.
-If the degree of the genus one piece is less than $d$ then we have a reduced rubber integral of strictly smaller degree.
+Notice that the rubber integrals which appear are always special rubber invariants, as defined above.
+If the degree of the genus one piece is less than $d$ then we have a special rubber invariant of strictly smaller degree.
 The only other possibility is that the entire curve is mapped into the divisor.
@@
 The left-hand side is a forgetful relative invariant of degree $d$ and $\leq n+1$ true markings, and so has already been computed.
-For the right-hand, let us begin with loci of type $A$.
+For the right-hand side, let us begin with loci of type $A$.
 The genus one contributions from each loci have $(d^\prime,n^\prime) < (d,n)$ except in the following case
@@
 which gives a contribution of
-\begin{equation*} d\cdot \gamma \cap [\VZ_{1,(d,0,\ldots,0)}(X|Y,\beta)] \end{equation*}
+\begin{equation*} d\cdot \gamma \cap [\VZ_{1,(d,\underbrace{0,\ldots,0}_{n-1})}(X|Y,\beta)] \footnote{(Navid) Fix formatting}\end{equation*}
 to the right-hand side of \eqref{step 2 recursion}.
-Here $\gamma$ is the insertion we started with; the difference is that we are now considering relative maps with maximal tangency at $x_1$, rather than absolute maps.
+Here $\gamma$ is the insertion we started with; the difference is that we are now considering relative maps to $(X,Y)$ with maximal tangency at $x_1$, rather than absolute maps to $Y$.
 The type $B$ and $C^0$ loci are recursively determined as in Step~1, and similarly the type $C^+$ loci are recursively determined except for the locus where the entire curve is mapped into the divisor.
@@
 where $I$ is the invariant we are trying to compute. Putting this all together, we obtain
-\begin{equation}\label{step 2 recursion 2} I = (-\tilde\gamma/d) \cap [\VZ_{1,(d,0,\ldots,0)}(X|Y,\beta)] + \text{recursively known terms} \end{equation}
+\begin{equation}\label{step 2 recursion 2} I = (-\gamma/d) \cap [\VZ_{1,(d,\underbrace{0,\ldots,0}_{n-1})}(X|Y,\beta)] + \text{recursively known terms} \end{equation}
 where on the right-hand side there are $n-1$ non-relative markings $x_2,\ldots,x_n$, and a relative marking $x_1$. We now apply the recursion again to the right-hand side, by considering the space
@@
 \begin{equation*} \left( (d-1)\psi_1 + \ev_1^\st Y \right)\cdot(-\tilde\gamma/d) \cap [\VZ_{1,(d-1,1,0,\ldots,0)}(X|Y,\beta)] = (-\tilde\gamma/d) \cap [\Dcal(1)].\end{equation*}
-The left-hand side is a forgetful relative invariant of degree $d$ and $n+1$ markings ($y$ being the ``forgetful'' marking), hence is recursively known.
-On the right-hand side, the type $A$ loci are recursively known except possibly in the following special cases (with some stable distribution of the remaining markings):
+The left-hand side is a forgetful relative invariant of degree $d$ and $\leq n+1$ true markings ($y$ being the ``forgetful'' marking), hence is recursively known.
+On the right-hand side, the type $A$ loci are recursively known except possibly in the following special cases (with some stable distribution of the remaining non-relative markings):
 \begin{center}
@@
 Thus we obtain a single locus, which contributes precisely
-\begin{equation*} d\cdot(-\tilde\gamma/d) \cap [\VZ_{1,(d,0,\ldots,0)}(X|Y,\beta)] = -\tilde\gamma\cap[\VZ_{1,(d,0,\ldots,0)}(X|Y,\beta)]\end{equation*}
+\begin{equation*} d\cdot(-\gamma/d) \cap [\VZ_{1,(d,\underbrace{0,\ldots,0}_{n-1})}(X|Y,\beta)] = -\gamma\cap[\VZ_{1,(d,\underbrace{0,\ldots,0}_{n-1})}(X|Y,\beta)]\end{equation*}
 which gives us the first term on the right-hand side of \eqref{step 2 recursion 2}.
@@
 But since $\VZ_{1,n}(H,1)=\emptyset$ it follows that $\VZ_{1,n}(Y,\beta)=\emptyset$ if $d=Y\cdot\beta=1$, so we may always assume $d \geq 2$ in the recursion.
+
+\subsection*{Step 3} Now suppose we are given a relative space $\VZ_{1,\alpha}(X|Y,\beta)$ with an insertion $\gamma$, and suppose inductively that we have computed all forgetful relative invariants with $(d^\prime,n^\prime) \leq (d,n+1)$, all absolute invariants with $(d^\prime,n^\prime) \leq (d,n)$, all relative invariants with $(d^\prime,n^\prime,t^\prime)<(d,n,t)$ and all special rubber invariants with $d^\prime < d$.
+Choose a true marking $x_1$ with $\alpha_1 \geq 1$ and consider the moduli space
+\begin{equation*} \VZ_{1,(\alpha-e_1)\cup(1)}(X|Y,\beta) \end{equation*}
+where $y$ is the newly-introduced marking. As usual consider the insertion $\tilde\gamma$ obtained from $\gamma$ by introducing $\fgt_y$ everywhere. Recursing at $x_1$ we obtain:
+\begin{equation*} \left( (\alpha_1-1)\psi_1 + \ev_1^\st H\right) \tilde\gamma \cap [\VZ_{1,(\alpha-e_1)\cup(1)}(X|Y,\beta)] = \tilde\gamma \cap [\Dcal(1)].\end{equation*}
+The left-hand side is a relative invariant with the same degree and number of true markings, but smaller true tangency: hence it is recursively known.
+On the right-hand side, the type $A$ contributions are recursively known except for those of the following form
+
+\begin{center}
+\begin{tikzpicture}[scale=1]
+\draw (0,0) to (2,0);
+\draw [color=blue] (1,-0.05) node[above]{\tiny$\alpha_1$};
+\draw [fill=white] (0,0) circle[radius=3pt];
+\draw (0,-0.1) node[below]{\small$d$};
+\draw (0,0) node[above]{\small$\sqC_1$};
+\draw [fill=black] (2,0) circle[radius=3pt];
+\draw (2,-0.1) node[below]{\small$0$};
+\draw (2,0) node[above]{\small$\sqC_0$};
+\draw [->] (2,0) -- (4,0);
+\draw (3.9,0) node[right]{$x_1$};
+\draw [color=blue] (3,-0.05) node[above]{\tiny$\alpha_1-1$};
+
+\draw [color=blue,->] (1,-0.3) -- (1,-0.7);
+
+\draw [color=blue,->] (0,-1) to (2,-1);
+\draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
+\draw [color=blue] (2,-1) node[right]{\small$\Sigma(X|Y)$};
+\end{tikzpicture}
+\end{center}
+where $C_0$ contains a single fictitious marking (if it had multiple fictitious markings then the contribution would vanish by projection formula) and all the other markings are on $C_1$.
+Thus for each fictitious marking we get a contribution of $\alpha_1 I$ where $I$ is the invariant we are trying to compute.
+Note that $\alpha_1 \neq 0$, and that this term appears at least once since $y$ is a fictitious marking; so we get a nonzero multiple of $I$.
+
+As usual the type $B$ and $C^0$ contributions are recursively known.
+The type $C^+$ contributions are determined by lower-degree special rubber invariants, except for when the whole curve is mapped into $Y$; however in this case we may apply $\fgt_y$ to identify the contribution with an absolute invariant of $Y$ with degree $d$ and $n$ markings, which is also recursively known.
+Thus we have determined the invariant $I$.
+
+\subsection*{Step 4} Finally, suppose we are given a special reduced rubber invariant to compute.
+So we have a reduced rubber space $\VZ_{1,\alpha}(P|Y_0+Y_\infty,\beta)_{\Gm}$ together with an insertion $\gamma$ satisfying the conditions outlined above.
+We first note that if there exists a relative marking with no insertion, we may forget this marking and identify the rubber invariant with a recursively-known absolute invariant (up to some boundary terms which can also be computed recursively).
+This approach will suffice for the majority of computations.
+
+If such a relative marking does not exist, we will instead compute the invariant by recursing on the following space:
+\begin{equation*} \VZ_{1,\alpha \cup (0,0)}(P|Y_0+Y_\infty,\beta)_{\Gm}. \end{equation*}
+We denote the newly-introduced markings by $x_0$ and $y$.
+Choose a negative-tangency marking $x_1$ and consider the insertion $\tilde\gamma$ obtained from $\gamma$ by replacing every $\ev_1^\st$ by $\ev_0^\st$ and introducing $\fgt_{x_1}^\st$ everywhere.
+
+Following \cite{EKatz}, there is a line bundle $L_{y}^{\neq\operatorname{bot}}$ equipped with a section whose vanishing locus $\Dcal(y)$ consists of boundary strata where the marking $y$ is not mapped into the bottom level of the expansion.\footnote{(Navid) Can we actually find a tropical description of this} The first Chern class of this line bundle is given by $\Psi_\infty + \ev_y^\st Y$ and $\Psi_\infty$ may be identified with $\alpha_2 \hat\psi_2 + \ev_2^\st Y$ where $x_2$ is any positive-tangency marking.
+Here $\hat\psi_2$ is a \emph{non-collapsed psi class} (recall that previously all our psi classes have been collapsed).
+Multiplying this by the insertion $\tilde\gamma \cdot \fgt_{x_1}^\st y$ we obtain:
+\begin{equation}\label{step 4 recursion} \left( \alpha_2 \hat\psi_2 + \ev_2^\st Y + \ev_y^\st Y \right) \tilde\gamma \cdot \fgt_{x_1}^\st \psi_y \cap [\VZ_{1,\alpha \cup (0,0)}(P|Y_0+Y_\infty,\beta)_{\Gm}] = \tilde\gamma \cdot \fgt_{x_1}^\st \psi_y \cap [\Dcal(y)].\end{equation}
+Start by examining the left-hand side; everything is pulled back along $\fgt_{x_1}$ except for $\hat\psi_2$.
+The difference between $\hat\psi_2$ and $\psi_2$ is given by the locus where $x_2$ belongs to a trivial bubble.
+In this case the curve must split into a number of pieces, and these are all known recursively except perhaps when all of the genus and degree is supported on one of these pieces $C^\prime$.
+When this happens we distinguish two cases, depending on whether $C^\prime$ is mapped into the top or the bottom piece of the expansion.
+
+In the former case, we have a special reduced rubber invariant with the same degree and strictly fewer relative markings, so this is recursively known.
+In the latter case we must have $x_1 \in C^\prime$ and since all the insertions are pulled back along $\fgt_{x_1}$ we may apply the projection formula to identify the contribution with an absolute invariant of $Y$.
+Note that this absolute invariant may have more than $n$ markings (since $n$ is only the number of \emph{relative} markings) but the structure of the recursion is such that we are assuming we have computed \emph{all} absolute invariants of $Y$ of degree $d$.
+So this term is recursively known.
+
+Thus, up to recursively known terms, we may replace $\hat\psi_2$ by $\psi_2$ in the left-hand side of \eqref{step 4 recursion}.
+In the same vein, the difference between $\psi_2$ and $\fgt_{x_1}^\st \psi_2$ is given by the locus where $x_1$ and $x_2$ are contained on a collapsed rational bubble.
+In this case the contribution of this locus is given by a special rubber invariant with $n-2$ relative markings, and hence is recursively known.
+So we may further replace $\psi_2$ by $\fgt_{x_1}^\st \psi_2$.
+Then the left-hand side of \eqref{step 4 recursion} has all its insertions pulled back along $\fgt_{x_1}$ and so we may apply the projection formula to identify this with a (recursively-known) absolute invariant of $Y$.
+Now examine the right-hand side.
+There is a locus where the curve breaks as follows
+\begin{center}
+\begin{tikzpicture}[scale=1]
+%edge
+\draw (0,0) to (2,0);
+\draw [color=blue] (1,0) node[below]{\tiny$\alpha_1$};
+
+%C_1
+\draw [fill=black] (0,0) circle[radius=3pt];
+\draw (0,-0.1) node[below]{\small$0$};
+
+%x_0
+\draw [->] (0,0) -- (0,1);
+\draw (0,0.9) node[left]{$x_0$};
+\draw [color=blue] (0,0.5) node[right]{\tiny$0$};
+
+%x_1
+\draw [->] (0,0) -- (-1.5,0);
+\draw (-1.5,0) node[above]{\small$x_1$};
+\draw [color=blue](-0.75,0) node[below]{\tiny$\alpha_1$};
+
+%y
+\draw [->] (2,0) -- (2,1);
+\draw (2,0.9) node[left]{$y$};
+\draw [color=blue] (2,0.5) node[right]{\tiny$0$};
+
+%C_0
+\draw [fill=white] (2,0) circle[radius=3pt];
+\draw (2,-0.1) node[below]{\small$\alpha_1$};
+
+%down arrow
+\draw [color=blue,->] (1,-0.5) -- (1,-0.9);
+
+%target
+\draw [color=blue] (0,-1) to (2,-1);
+\draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
+\draw [fill=blue,color=blue] (2,-1) circle[radius=3pt];
+\draw [color=blue,->] (2,-1) -- (3,-1);
+\draw [color=blue,->] (0,-1) -- (-1,-1);
+\end{tikzpicture}
+\end{center}
+with all other markings concentrated on the genus one piece. The contribution of this locus is given by
+\begin{equation*} \alpha_1 \cdot \psi_y \cdot \gamma \cap [\VZ_{1,\alpha\cup(0)}(P|Y_0+Y_\infty)]_{\Gm} \end{equation*}
+and by the dilaton equation for reduced rubber invariants (see \S \ref{}) we may identify this with a (nonzero) multiple of the invariant $I$ we are trying to compute (note that $\psi_y = \hat\psi_y$ because $y$ is a non-relative marking).
+
+Now consider the other loci which contribute to the right-hand side of \eqref{step 4 recursion}.
+Their contributions are recursively known except for when one of the curve pieces $C^\prime$ has degree $d$ and $n$ relative points.
+If $C^\prime$ is mapped to the bottom level of the expanded target, then we may apply the projection formula with $\fgt_{x_1}$ to identify the contribution with an absolute invariant of $Y$.
+If $C^\prime$ is mapped to the top level, then we must have $x_1$ contained in a collapsed rational bubble on the left-hand side.
+This bubble has at most three special points; any more and the projection formula with $\fgt_{x_1}$ will cause the contribution to vanish.
+Thus the bubble contains at most one non-relative marking.
+
+[DOESN'T SEEM LIKE WE CAN CONTROL THIS?]
 

### 2019-02-26 GenusOneRelativeMaps.tex
Fixed some things in Step 2

@@
 Recursing at $x_1$ we obtain:
-\begin{equation*} \left( (d-1)\psi_1 + \ev_1^\st Y \right)\cdot(-\tilde\gamma/d) \cap [\VZ_{1,(d-1,1,0,\ldots,0)}(X|Y,\beta)] = (-\tilde\gamma/d) \cap [\Dcal(1)].\end{equation*}
-The left-hand side is a forgetful relative invariant of degree $d$ and $\leq n+1$ true markings ($y$ being the ``forgetful'' marking), hence is recursively known.
+\begin{equation}\label{step 2 recursion 2} \left( (d-1)\psi_1 + \ev_1^\st Y \right)\cdot(-\tilde\gamma/d) \cap [\VZ_{1,(d-1,1,0,\ldots,0)}(X|Y,\beta)] = (-\tilde\gamma/d) \cap [\Dcal(1)].\end{equation}
+The difference between $\psi_1$ and $\fgt_y^\st \psi_1$ is given by the locus where $x_1$ and $y$ belong to a collapsed rational bubble:
+\begin{center}
+\begin{tikzpicture}[scale=1]
+%edge
+\draw (0,0) to (2,0);
+\draw [color=blue] (1,0) node[above]{\tiny$d$};
+
+%C_1
+\draw [fill=white] (0,0) circle[radius=3pt];
+\draw (0,-0.1) node[below]{\small$d$};
+\draw (0,0) node[above]{\small$\sqC_1$};
+
+%C_0
+\draw [fill=black] (2,0) circle[radius=3pt];
+\draw (2,-0.1) node[below]{\small$0$};
+\draw (2,0) node[above]{\small$\sqC_0$};
+
+%x_1
+\draw [->] (2,0.1) -- (4,0.1);
+\draw (3.9,0.1) node[above]{\small$y$};
+\draw [color=blue](3,0.1) node[above]{\tiny$1$};
+
+%y
+\draw [->] (2,-0.1) -- (4,-0.1);
+\draw (3.9,-0.1) node[below]{\small$x_1$};
+\draw [color=blue] (3,-0.1) node[below]{\tiny$d-1$};
+
+%down arrow
+\draw [color=blue,->] (1,-0.3) -- (1,-0.7);
+
+%target
+\draw [color=blue,->] (0,-1) to (2,-1);
+\draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
+\draw [color=blue] (2,-1) node[right]{\small$\Sigma(X|Y)$};
+\end{tikzpicture}
+\end{center}
+The contribution of this locus to the left-hand side of \eqref{step 2 recursion 2} is:
+\begin{equation*} (d-1)\cdot(-\gamma/d) \cap [\VZ_{1,(d,\underbrace{0,\ldots,0}_{n-1})}(X|Y,\beta)].\end{equation*}
+What remains on the left-hand side is a forgetful relative invariant of degree $d$ and $\leq n+1$ true markings ($y$ being the ``forgetful'' marking), hence is recursively known.
 On the right-hand side, the type $A$ loci are recursively known except possibly in the following special cases (with some stable distribution of the remaining non-relative markings):
@@
 As usual the type $B$ and $C^0$ contributions are known recursively, and the only type $C^+$ contribution not known recursively occurs when the entire curve is mapped into the divisor, in which case we apply $\fgt_y$ to calculate the contribution as:
-\begin{equation*} (-\gamma/d) \cap [\VZ_{1,n}(X|Y,\beta)] = -I/d.\end{equation*}
+\begin{equation*} (-\gamma/d) \cap [\VZ_{1,n}(Y,\beta)] = -I/d.\end{equation*}
 Substituting into \eqref{step 2 recursion 2} we end up with
-\begin{equation*} I(1-d^{-2}) = \text{recursively known terms} \end{equation*}
+\begin{equation*} I(1-d^{-1}) = \text{recursively known terms} \end{equation*}
 which completes the recursion step as long as $d \neq 1$.

### 2019-03-01 GenusOneRelativeMaps.tex
removed incorrect step 4 recursion description

@@
 
-If such a relative marking does not exist, we will instead compute the invariant by recursing on the following space:
-\begin{equation*} \VZ_{1,\alpha \cup (0,0)}(P|Y_0+Y_\infty,\beta)_{\Gm}. \end{equation*}
-We denote the newly-introduced markings by $x_0$ and $y$.
-Choose a negative-tangency marking $x_1$ and consider the insertion $\tilde\gamma$ obtained from $\gamma$ by replacing every $\ev_1^\st$ by $\ev_0^\st$ and introducing $\fgt_{x_1}^\st$ everywhere.
-
-Following \cite{EKatz}, there is a line bundle $L_{y}^{\neq\operatorname{bot}}$ equipped with a section whose vanishing locus $\Dcal(y)$ consists of boundary strata where the marking $y$ is not mapped into the bottom level of the expansion.\footnote{(Navid) Can we actually find a tropical description of this} The first Chern class of this line bundle is given by $\Psi_\infty + \ev_y^\st Y$ and $\Psi_\infty$ may be identified with $\alpha_2 \hat\psi_2 + \ev_2^\st Y$ where $x_2$ is any positive-tangency marking.
-Here $\hat\psi_2$ is a \emph{non-collapsed psi class} (recall that previously all our psi classes have been collapsed).
-Multiplying this by the insertion $\tilde\gamma \cdot \fgt_{x_1}^\st y$ we obtain:
-\begin{equation}\label{step 4 recursion} \left( \alpha_2 \hat\psi_2 + \ev_2^\st Y + \ev_y^\st Y \right) \tilde\gamma \cdot \fgt_{x_1}^\st \psi_y \cap [\VZ_{1,\alpha \cup (0,0)}(P|Y_0+Y_\infty,\beta)_{\Gm}] = \tilde\gamma \cdot \fgt_{x_1}^\st \psi_y \cap [\Dcal(y)].\end{equation}
-Start by examining the left-hand side; everything is pulled back along $\fgt_{x_1}$ except for $\hat\psi_2$.
-The difference between $\hat\psi_2$ and $\psi_2$ is given by the locus where $x_2$ belongs to a trivial bubble.
-In this case the curve must split into a number of pieces, and these are all known recursively except perhaps when all of the genus and degree is supported on one of these pieces $C^\prime$.
-When this happens we distinguish two cases, depending on whether $C^\prime$ is mapped into the top or the bottom piece of the expansion.
-
-In the former case, we have a special reduced rubber invariant with the same degree and strictly fewer relative markings, so this is recursively known.
-In the latter case we must have $x_1 \in C^\prime$ and since all the insertions are pulled back along $\fgt_{x_1}$ we may apply the projection formula to identify the contribution with an absolute invariant of $Y$.
-Note that this absolute invariant may have more than $n$ markings (since $n$ is only the number of \emph{relative} markings) but the structure of the recursion is such that we are assuming we have computed \emph{all} absolute invariants of $Y$ of degree $d$.
-So this term is recursively known.
-
-Thus, up to recursively known terms, we may replace $\hat\psi_2$ by $\psi_2$ in the left-hand side of \eqref{step 4 recursion}.
-In the same vein, the difference between $\psi_2$ and $\fgt_{x_1}^\st \psi_2$ is given by the locus where $x_1$ and $x_2$ are contained on a collapsed rational bubble.
-In this case the contribution of this locus is given by a special rubber invariant with $n-2$ relative markings, and hence is recursively known.
-So we may further replace $\psi_2$ by $\fgt_{x_1}^\st \psi_2$.
-Then the left-hand side of \eqref{step 4 recursion} has all its insertions pulled back along $\fgt_{x_1}$ and so we may apply the projection formula to identify this with a (recursively-known) absolute invariant of $Y$.
-Now examine the right-hand side.
-There is a locus where the curve breaks as follows
-\begin{center}
-\begin{tikzpicture}[scale=1]
-%edge
-\draw (0,0) to (2,0);
-\draw [color=blue] (1,0) node[below]{\tiny$\alpha_1$};
-
-%C_1
-\draw [fill=black] (0,0) circle[radius=3pt];
-\draw (0,-0.1) node[below]{\small$0$};
-
-%x_0
-\draw [->] (0,0) -- (0,1);
-\draw (0,0.9) node[left]{$x_0$};
-\draw [color=blue] (0,0.5) node[right]{\tiny$0$};
-
-%x_1
-\draw [->] (0,0) -- (-1.5,0);
-\draw (-1.5,0) node[above]{\small$x_1$};
-\draw [color=blue](-0.75,0) node[below]{\tiny$\alpha_1$};
-
-%y
-\draw [->] (2,0) -- (2,1);
-\draw (2,0.9) node[left]{$y$};
-\draw [color=blue] (2,0.5) node[right]{\tiny$0$};
-
-%C_0
-\draw [fill=white] (2,0) circle[radius=3pt];
-\draw (2,-0.1) node[below]{\small$\alpha_1$};
-
-%down arrow
-\draw [color=blue,->] (1,-0.5) -- (1,-0.9);
-
-%target
-\draw [color=blue] (0,-1) to (2,-1);
-\draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
-\draw [fill=blue,color=blue] (2,-1) circle[radius=3pt];
-\draw [color=blue,->] (2,-1) -- (3,-1);
-\draw [color=blue,->] (0,-1) -- (-1,-1);
-\end{tikzpicture}
-\end{center}
-with all other markings concentrated on the genus one piece. The contribution of this locus is given by
-\begin{equation*} \alpha_1 \cdot \psi_y \cdot \gamma \cap [\VZ_{1,\alpha\cup(0)}(P|Y_0+Y_\infty)]_{\Gm} \end{equation*}
-and by the dilaton equation for reduced rubber invariants (see \S \ref{}) we may identify this with a (nonzero) multiple of the invariant $I$ we are trying to compute (note that $\psi_y = \hat\psi_y$ because $y$ is a non-relative marking).
-
-Now consider the other loci which contribute to the right-hand side of \eqref{step 4 recursion}.
-Their contributions are recursively known except for when one of the curve pieces $C^\prime$ has degree $d$ and $n$ relative points.
-If $C^\prime$ is mapped to the bottom level of the expanded target, then we may apply the projection formula with $\fgt_{x_1}$ to identify the contribution with an absolute invariant of $Y$.
-If $C^\prime$ is mapped to the top level, then we must have $x_1$ contained in a collapsed rational bubble on the left-hand side.
-This bubble has at most three special points; any more and the projection formula with $\fgt_{x_1}$ will cause the contribution to vanish.
-Thus the bubble contains at most one non-relative marking.
-
-[DOESN'T SEEM LIKE WE CAN CONTROL THIS?]
+[TO BE FINISHED]
 

### 2019-03-01 GenusOneRelativeMaps.tex
started step 4 - rubber recursion

@@
 
-\subsection*{Step 4} Finally, suppose we are given a special reduced rubber invariant to compute.
-So we have a reduced rubber space $\VZ_{1,\alpha}(P|Y_0+Y_\infty,\beta)_{\Gm}$ together with an insertion $\gamma$ satisfying the conditions outlined above.
-We first note that if there exists a relative marking with no insertion, we may forget this marking and identify the rubber invariant with a recursively-known absolute invariant (up to some boundary terms which can also be computed recursively).
-This approach will suffice for the majority of computations.
-
-[TO BE FINISHED]
-
+\subsection*{Step 4} Finally, we show how to compute any rubber invariant (even if, for the recursion to keep going, we would only need the special ones).
+From the previous steps we effectively use only the knowledge of absolute invariants of $Y$ with not higher $(d,n)$ than the current step.
+We proceed by induction on $(d,n,n^\prime)$, where $n^\prime$ is the number of markings with non-zero tangency requirement.
+
+Recall that there is a map $\epsilon\colon \VZ_{1,\alpha}(P|H_b+H_t)^\sim\to \VZ_{1,\alpha}(H)$ projecting down to the base and stabilising the curve, i.e.
+collapsing rational bridges; we always assume our insertions to be pulled back along $\epsilon$, in particular the psi classes are \emph{collapsed}.
+Forgetting a marking may be thought of as a map to a different rubber space only if it is a non-relative one; otherwise it will always be considered as a map to the collapsed space.
+
+We start by recalling some useful constructions on the space of maps to rubber \cite{EKatz}.
+\begin{enumerate}[leftmargin=15pt]
+ \item The moduli space of targets is isomorphic to the semistable locus in $\mathfrak M_{0,2}$.
+Pulling back the cotangent line bundles at $p_b,\ p_t$ we obtain $\mathbb L_b,\ \mathbb L_t$, whose $c_1$ are the so-called \emph{target psi classes} $\Psi_b,\ \Psi_t$.
+The subscripts stand for \emph{bottom} and \emph{top}.
+ \item The line bundle $\mathrm{Split}=\mathbb L_b\otimes\mathbb L_t$ admits a section, whose vanishing locus consists precisely of those maps whose target has more than one irreducible component.
+This can be seen as the pullback of the topological recursion relation on the moduli space of targets.
+$\mathrm{Split}$ admits a tropical description as the piecewise-linear function assigning the sum of the finite edge-lengths of the target.
+ \item Whenever there is a marking $x_k$ of positive tangency $\alpha_k$ (i.e.
+mapping to $D_t$), we may express the target psi class $\Psi_t$ as $\alpha_k\hat\psi_k+\ev_k^*H$.
+Importantly, here $\hat\psi_k$ denotes the expanded psi class at $x_k$, which differs from the collapsed psi class - that we usually consider - on the locus $\delta_{k,\rm{triv}}$ where $x_k$ lies on a trivial bubble.
+Similarly $\Psi_b=-\alpha_h\hat\psi_h-\ev_h^*H$ for a marking $x_h$ with $\alpha_h<0$.
+See also \cite[Construction 5.1.17]{GathmannThesis}.
+ \item\label{claim:trivialPsib} $\Psi_b=0$ whenever there are no negative markings.
+ \item For every non-relative marking (with $\alpha_i=0$), there is a line bundle $L_{i,\rm{not\ bot}}=\mathbb L_b\otimes\ev_i^*\OO(H)$ with a section vanishing on the locus where (the target splits and) $x_i$ does not map to the bottom component of the target.
+This line bundle has a tropical interpretation by taking the distance between $\phi(v_i)$ and the left-most component in the target, where $v_i$ is the vertex of the curve supporting the $i$-th flag.
+
+ \noindent Similarly, $L_{i,\rm{not\ top}}=\mathbb L_t\otimes\ev_i^*\OO(-H)$ has a section cutting out the locus where $x_i$ does not map to the top component of the target.
+\end{enumerate}
+
+\emph{First reduction}: assume there is an index (wlog $1$) such that no insertion involves $x_1$.
+Then we would like to replace the whole insertion $\gamma$ by $\fgt_{x_1}^*(\gamma)$.
+We only need to notice that, for $k\neq1$, the difference $\psi_k-\fgt_{x_1}^*(\psi_k)$ is supported on the locus where $x_1$ and $x_k$ alone lie on a rational component of trivial horizontal degree; the invariants arising from $\delta_{1,k}$ can be computed recursively as they have lower $n$.
+
+The base for the induction is the case of a single relative marking $x_1$ with full tangency $\alpha_1=d$.
+Write the insertion as $\gamma=\tau_{b_1}(\gamma_1)\tau(\gamma)_{\geq 2}$.
+We shall add a non-relative marking $x_0$ and, starting from the equality $c_1(L_{0,\rm{not\ bot}})\cdot[\VZ_{1,\alpha}(P|H_0+H_\infty)^\sim]=\ldots$ (the boundary classes described above), intersect it with $\bar\gamma=\fgt_{x_1}^*\left(\psi_0^{b_1}\ev_0^*(\gamma_1)\tau(\gamma)_{\geq 2}\right)$.
+\begin{comment}{$\bar\gamma=\fgt_{x_1}^*\left(\psi_0^{b_1}\ev_0^*(\gamma_1)\tau(\gamma)_{\geq 2}\right)$\end{comment}
+On the right-hand side, all the not recursively known terms consist of an elliptic curve of degree $d$ in the bottom level, and a rational tail of horizontal degree $0$ in the top level.
+The rational tail supports $x_0$ by assumption, and it must support $x_1$ as well by balancing: if any other marking is on it, the invariant is recursively known (lower $n$); otherwise, we recover the invariant we are trying to compute (up to corrections from comparing $\psi_k$ and $\fgt_{x_1}^*\psi_k$, which again involve invariants with lower $n$).
+On the left hand side, write $c_1(L_{0,\rm{not\ bot}})=\Psi_b-\ev_0^*H=-\ev_0^*H$ by \ref{claim:trivialPsib} above.
+We can therefore compute the left-hand side by forgetting $x_1$ and the \emph{first reduction}: the result is the absolute invariant $-d^2\langle\tau_{b_1}(H\cdot\gamma_1)\tau(\gamma)_{\geq2}\rangle^{H,\rm{red}}_{1,n,d}$, which is recursively known.
 \newpage

### 2019-03-01 GenusOneRelativeMaps.tex
finished step 4, except for triviality of Psi_b when no negative markings

@@
 Write the insertion as $\gamma=\tau_{b_1}(\gamma_1)\tau(\gamma)_{\geq 2}$.
-We shall add a non-relative marking $x_0$ and, starting from the equality $c_1(L_{0,\rm{not\ bot}})\cdot[\VZ_{1,\alpha}(P|H_0+H_\infty)^\sim]=\ldots$ (the boundary classes described above), intersect it with $\bar\gamma=\fgt_{x_1}^*\left(\psi_0^{b_1}\ev_0^*(\gamma_1)\tau(\gamma)_{\geq 2}\right)$.
-\begin{comment}{$\bar\gamma=\fgt_{x_1}^*\left(\psi_0^{b_1}\ev_0^*(\gamma_1)\tau(\gamma)_{\geq 2}\right)$\end{comment}
+We shall add a non-relative marking $x_0$ and, starting from the equality $c_1(L_{0,\rm{not\ bot}})\cdot[\VZ_{1,(0)\cup\alpha}(P|H_0+H_\infty)^\sim]=\ldots$ (the boundary classes described above), intersect it with $\bar\gamma=\fgt_{x_1}^*\left(\psi_0^{b_1}\ev_0^*(\gamma_1)\tau(\gamma)_{\geq 2}\right)$.
 On the right-hand side, all the not recursively known terms consist of an elliptic curve of degree $d$ in the bottom level, and a rational tail of horizontal degree $0$ in the top level.
@@
 We can therefore compute the left-hand side by forgetting $x_1$ and the \emph{first reduction}: the result is the absolute invariant $-d^2\langle\tau_{b_1}(H\cdot\gamma_1)\tau(\gamma)_{\geq2}\rangle^{H,\rm{red}}_{1,n,d}$, which is recursively known.
+
+The general induction step is similar: say $x_1$ is a positive marking.
+Introduce a non-relative marking $x_0$ and, starting from the equality $c_1(L_{0,\rm{not\ bot}})\cdot[\VZ_{1,(0)\cup\alpha}(P|H_0+H_\infty)^\sim]=\ldots$ (the boundary classes described above), intersect it with $\bar\gamma=\fgt_{x_1}^*\left(\psi_0^{b_1}\ev_0^*(\gamma_1)\tau(\gamma)_{\geq 2}\right)$.
+On the right hand side, the interesting terms have a $(g,d)$ splitting equal to $\{(1,d),(0,0)\}$, and the top component contains $x_0$.
+If the rational tail is top: either it contains only $x_0$ and $x_1$, and we recover the invariant we want to compute (up to correction terms with less than $n$ markings); or it contains $x_0$ and another positive marking, in which case the genus one invariant can be computed by $\fgt_{x_1}$ and the first reduction; or it contains more than two markings, which leaves less than $n$ on the genus one component.
+On the other hand, if genus one is top: either it contains $x_1$ and can therefore be computed by forgetting it; or it doesn't, but then the bottom component needs to support at least a negative marking, so the genus one component contains less than $n^\prime$ relative markings.
+
+We shall now address the left-hand side: assume there is a negative marking $x_2$ (if not, $\Psi_b$ is trivial and we conclude as above).
+Write $c_1(L_{0,\rm{not\ bot}})=\Psi_b+\ev_0^*H=-\alpha_2\hat\psi_2-\ev_2^*H+\ev_0^*H=-\alpha_2\fgt_{x_1}^*\psi_2-\ev_2^*H+\ev_0^*H-\alpha_2(\delta_{2,\rm{triv}}+\delta_{1,2})$.
+The issue is to control the latter terms.
+Let us start from $\delta_{2,\rm{triv}}$: the curve splits into a bottom and a top component ($C_b$ and $C_t$), with $x_2$ attached to $C_t$.
+As usual we are interested in the case that there is a component of genus one and degree $d$.
+If $C_b$ is rational, it must contain at least two markings, one of which is negative: either it contains $x_1$ as well (then $C_t$ has less than $n^\prime$ relative markings), or it doesn't (then the top invariant can be computed by $\fgt_{x_1}$).
+If $C_t$ is rational, the argument is symmetric.
+Finally, the invariants from $\delta_{1,2}$ can again be computed by induction on $n^\prime$.
+This concludes the inductive procedure.
 \newpage

### 2019-03-04 GenusOneRelativeMaps.tex
Added remark on how fibre product is automatically fs when defining invariants of (X,Y)

--- 2019-03-01 GenusOneRelativeMaps.tex
@@
 \end{lemma}
+\begin{proof} It is clear from the modular description that this square is cartesian in the category of fs log stacks.
+But the morphism $i$ is strict, which implies that the square is also cartesian in the category of coherent log stacks.
+Since fibre products in the latter category are compatible with the functor forgetting log structures, the claim follows.\end{proof}
+
 Since $\VZ_{1,n}(\PP^N,d)$ is smooth and $\VZ_{1,n}(X,\beta)$ carries a natural virtual class, there is a diagonal pull-back morphism which we use to define the virtual class on the space of maps to $(X|Y)$:
@@
 The recursion formula in $\VZ_{1,\alpha}(\PP^N|H,d)$ immediately pulls back along $i$ to give a recursion formula in $\VZ_{1,\alpha}(X|Y,\beta)$.
-\footnote{(Navid) Is it clear how to compute integrals over the pulled back classes?}
 

### 2019-03-04 GenusOneRelativeMaps.tex
Some changes to step 4 recursion

--- 2019-03-04 GenusOneRelativeMaps.tex
@@
 \item the genus one \textbf{reduced relative Gromov--Witten theory} of the pair $(X,Y)$;
-\item a certain slice of the genus one \textbf{reduced rubber theory} of $P$.
+\item the genus one \textbf{reduced rubber theory} of $P$.
 \end{enumerate}
 
-\subsection{Reduced absolute, relative and special rubber invariants} To be precise: by a reduced invariant of $Y$ we mean an integral over $\VZ_{1,n}(Y,\beta)$ of products of pullbacks of evaluation and psi classes along morphisms which forget a subset $S$ of the marked points (taking $S=\emptyset$ gives the ordinary evaluation and psi classes).
+\subsection{Reduced absolute, relative and rubber invariants} To be precise: by a reduced invariant of $Y$ we mean an integral over $\VZ_{1,n}(Y,\beta)$ of products of pullbacks of evaluation and psi classes along morphisms which forget a subset $S$ of the marked points (taking $S=\emptyset$ gives the ordinary evaluation and psi classes).
 Here the evaluation maps are viewed as mapping into $X$ (hence the adjective ``restricted'').
@@
 Note that, unlike in the absolute case, in the relative case it may well be the case that the entire insertion is pulled back along a single forgetful map $\fgt_S$.
-
 The reduced rubber invariants of $P$ are defined similarly (again using collapsed psi classes).
-The particular slice we are interested in is the theory of \textbf{special reduced rubber invariants}.
-These are by definition the rubber invariants which involve at least one marked point of negative tangency (meaning nonzero tangency to $Y_0$), and such that the negative-tangency markings carry only primary insertions.
-The significance of this class of rubber invariants will become clear during the recursion.
 
@@
 \For{$n \geq 0$\medskip}{
-\textbf{\, Step 4: } Compute special rubber invariants of $P$ (degree $d$, $n$ relative markings).
+\For{$m \geq 0$\medskip}{
+\textbf{\, Step 4: } Compute rubber invariants of $P$ (degree $d$, $n$ relative markings, $m$ non-relative markings).
+}
 }
@@
 \end{algorithm}
-\noindent Although the loops involving $d$ and $n$ have infinite length, in order to compute any single invariant it is only necessarily to iterate the preceding loops for a finite amount of time.
+\noindent Although the loops involving $d, n$ and $m$ have infinite length, in order to compute any single invariant it is only necessarily to iterate the preceding loops for a finite amount of time.
 A \textbf{forgetful relative invariant} of $(X,Y)$ is by definition a reduced relative invariant with a marked point $x_0$ such that all of the insertions are pulled back along $\fgt_{x_0}$.
@@
 
-The base terms of the recursion all have $d=0$ and as such are easy to compute: the relative invariants of $(X,Y)$ are nothing but absolute invariants of $X$, the absolute invariants of $Y$ are given by obstruction bundle integrals over Deligne--Mumford spaces, and the special rubber invariants of $P$ are also given by integrals over Deligne--Mumford spaces, using the formula for the double ramification cycle \cite{Hain,JPPZ} in terms of tautological classes.
+The base terms of the recursion all have $d=0$ and as such are easy to compute: the relative invariants of $(X,Y)$ are nothing but absolute invariants of $X$, the absolute invariants of $Y$ are given by obstruction bundle integrals over Deligne--Mumford spaces, and the  rubber invariants of $P$ are also given by integrals over Deligne--Mumford spaces, using the formula for the double ramification cycle \cite{Hain,JPPZ} in terms of tautological classes.
 We will now explain how to perform each of the four inductive steps outlined above.
@@
 That is, we have a relative space $\VZ_{1,\alpha}(X|Y,\beta)$ of degree $d$, with $n+1$ true markings and true tangency $t$, and a marking $x_0$ such that the insertion $\gamma$ is pulled back along $\fgt_{x_0}$.
-We assume inductively that every absolute, relative and special rubber invariant with $(d^\prime,n^\prime) < (d,n)$ is known, and also that every forgetful relative invariant with $(d^\prime,n^\prime,t^\prime) < (d,n+1,t)$ is known.
+We assume inductively that every absolute, relative and rubber invariant with $(d^\prime,n^\prime) < (d,n)$ is known, and also that every forgetful relative invariant with $(d^\prime,n^\prime,t^\prime) < (d,n+1,t)$ is known.
 Choose a true marking $x_1$ with $\alpha_1 \geq 1$ and consider the space:
@@
 It remains to consider type $C^+$ loci.
-Notice that the rubber integrals which appear are always special rubber invariants, as defined above.
-If the degree of the genus one piece is less than $d$ then we have a special rubber invariant of strictly smaller degree.
+If the degree of the genus one piece is less than $d$ then we have a rubber invariant of strictly smaller degree.
 The only other possibility is that the entire curve is mapped into the divisor.
@@
 
-\subsection*{Step 3} Now suppose we are given a relative space $\VZ_{1,\alpha}(X|Y,\beta)$ with an insertion $\gamma$, and suppose inductively that we have computed all forgetful relative invariants with $(d^\prime,n^\prime) \leq (d,n+1)$, all absolute invariants with $(d^\prime,n^\prime) \leq (d,n)$, all relative invariants with $(d^\prime,n^\prime,t^\prime)<(d,n,t)$ and all special rubber invariants with $d^\prime < d$.
+\subsection*{Step 3} Now suppose we are given a relative space $\VZ_{1,\alpha}(X|Y,\beta)$ with an insertion $\gamma$, and suppose inductively that we have computed all forgetful relative invariants with $(d^\prime,n^\prime) \leq (d,n+1)$, all absolute invariants with $(d^\prime,n^\prime) \leq (d,n)$, all relative invariants with $(d^\prime,n^\prime,t^\prime)<(d,n,t)$ and all rubber invariants with $d^\prime < d$.
 Choose a true marking $x_1$ with $\alpha_1 \geq 1$ and consider the moduli space
@@
 As usual the type $B$ and $C^0$ contributions are recursively known.
-The type $C^+$ contributions are determined by lower-degree special rubber invariants, except for when the whole curve is mapped into $Y$; however in this case we may apply $\fgt_y$ to identify the contribution with an absolute invariant of $Y$ with degree $d$ and $n$ markings, which is also recursively known.
+The type $C^+$ contributions are determined by lower-degree rubber invariants, except for when the whole curve is mapped into $Y$; however in this case we may apply $\fgt_y$ to identify the contribution with an absolute invariant of $Y$ with degree $d$ and $n$ markings, which is also recursively known.
 Thus we have determined the invariant $I$.
 
-\subsection*{Step 4} Finally, suppose we are given a special reduced rubber invariant to compute.
-So we have a reduced rubber space $\VZ_{1,\alpha}(P|Y_0+Y_\infty,\beta)_{\Gm}$ together with an insertion $\gamma$ satisfying the conditions outlined above.
-We first note that if there exists a relative marking with no insertion, we may forget this marking and identify the rubber invariant with a recursively-known absolute invariant (up to some boundary terms which can also be computed recursively).
-This approach will suffice for the majority of computations.
-
-[TO BE FINISHED]
-
+\subsection*{Step 4} Finally, consider a rubber space $\VZ_{1,\alpha}(P|Y_0+Y_\infty,\beta)_{\Gm}$ with insertion $\gamma$.
+Suppose inductively that we have computed all absolute and relative invariants with $d^\prime \leq d$ and all rubber invariants with $(d^\prime,n^\prime,m^\prime) < (d,n,m)$.
+
+We first note the following important reduction: if there exists a relative marking $x_k$ such that all insertions are pulled back along $\fgt_{x_k}$, then we may apply the projection formula, together with the fact that
+\begin{equation*} (\fgt_{x_k})_\st [\VZ_{1,\alpha}(P|Y_0+Y_\infty,\beta)_{\Gm}] = \alpha_k^2 \cdot [\VZ_{1,n+m-1}(Y,\beta)] \end{equation*}
+to identify the rubber invariant with a multiple of a reduced invariant of $Y$, which has the same degree and hence is known recursively.
+
+We will deal with the general case by reducing to the one above. Consider the moduli space
+\begin{equation*} \VZ_{1,\alpha\cup (0)}(P|Y_0+Y_\infty,\beta)_{\Gm}\end{equation*}
+obtained by introducing a marked point $y$ with no tangency.
+Let $x_1$ be a positive-tangency marking (such a marking always exists since $d \geq 2$) and let $\tilde\gamma$ be the insertion obtained from $\gamma$ by replacing $\ev_1$ and $\psi_1$ by $\ev_y$ and $\psi_y$, and then introducing $\fgt_{x_1}^\st$ everywhere.
+Following \cite{EKatz}, there is a line bundle $L_y^{\not\in \operatorname{bot}}$ together with a section $s_y^{\not\in\operatorname{bot}}$ whose vanishing locus consists of the locus $\Dcal(y)$ of maps where $y$ is not mapped into the bottom level of the expanded target.
+As in \S \ref{}, we can give a logarithmic interpretation of this data: it corresponds to the piecewise-linear function on the tropical moduli space which associates, to every rubber tropical map, the distance between $\varphi(\sqC_y)$ and the leftmost vertex of the tropical target, where $\sqC_y$ is the vertex of the source curve containing the flag corresponding to $y$.
+Using this tropical description, we may easily calculate the vanshing orders of $s_y^{\not\in\operatorname{bot}}$ along the various components of $\Dcal(y)$.
+Moreover we may use this description to show (see also \cite{EKatzLB}) that $\cchern_1(L_y^{\not\in\operatorname{bot}}) = \Psi_0 - \ev_y^\st Y$, from which we conclude
+\begin{equation}\label{step 4 recursion} (\Psi_0 - \ev_y^\st Y) \tilde\gamma \cap [VZ_{1,\alpha\cup(0)}(P|Y_0+Y_\infty,\beta)_{\Gm}] = \tilde\gamma \cap [\Dcal(y)]\end{equation}
+where the fundamental class $[\Dcal(y)]$ is weighted by vanishing orders.
+We will first show that the left-hand side is recursively known.
+By construction the class $\tilde\gamma$ is pulled back along $\fgt_{x_0}$, and the same is true for $\ev_y^\st Y$.
+Let us examine $\Psi_0$.
+If there exists a negative-tangency marking $x_2$, then we have \cite{GathmannThesis}
+\begin{equation*} \Psi_0 = -\alpha_2 \hat\psi_2 - \ev_2^\st Y \end{equation*}
+where $\hat\psi_2$ is a \emph{non-collapsed} psi class. (If there are no negative-tangency markings then the construction \cite[\S 1.5.2]{MaulikPandharipande} gives $\Psi_0=0$.)
 \newpage

### 2019-03-04 GenusOneRelativeMaps.tex
Changes to Step 4 recursion

@@
 
-We first note the following important reduction: if there exists a relative marking $x_k$ such that all insertions are pulled back along $\fgt_{x_k}$, then we may apply the projection formula, together with the fact that
-\begin{equation*} (\fgt_{x_k})_\st [\VZ_{1,\alpha}(P|Y_0+Y_\infty,\beta)_{\Gm}] = \alpha_k^2 \cdot [\VZ_{1,n+m-1}(Y,\beta)] \end{equation*}
+We first note the following important reduction: if there exists a relative marking $x_k$ such that all insertions are pulled back along $\fgt_{k}$, then we may apply the projection formula, together with the fact that
+\begin{equation*} (\fgt_{k})_\st [\VZ_{1,\alpha}(P|Y_0+Y_\infty,\beta)_{\Gm}] = \alpha_k^2 \cdot [\VZ_{1,n+m-1}(Y,\beta)] \end{equation*}
 to identify the rubber invariant with a multiple of a reduced invariant of $Y$, which has the same degree and hence is known recursively.
@@
 We will deal with the general case by reducing to the one above. Consider the moduli space
-\begin{equation*} \VZ_{1,\alpha\cup (0)}(P|Y_0+Y_\infty,\beta)_{\Gm}\end{equation*}
+\begin{equation*}\label{step 4 recursion space} \VZ_{1,\alpha\cup (0)}(P|Y_0+Y_\infty,\beta)_{\Gm}\end{equation*}
 obtained by introducing a marked point $y$ with no tangency.
-Let $x_1$ be a positive-tangency marking (such a marking always exists since $d \geq 2$) and let $\tilde\gamma$ be the insertion obtained from $\gamma$ by replacing $\ev_1$ and $\psi_1$ by $\ev_y$ and $\psi_y$, and then introducing $\fgt_{x_1}^\st$ everywhere.
-Following \cite{EKatz}, there is a line bundle $L_y^{\not\in \operatorname{bot}}$ together with a section $s_y^{\not\in\operatorname{bot}}$ whose vanishing locus consists of the locus $\Dcal(y)$ of maps where $y$ is not mapped into the bottom level of the expanded target.
-As in \S \ref{}, we can give a logarithmic interpretation of this data: it corresponds to the piecewise-linear function on the tropical moduli space which associates, to every rubber tropical map, the distance between $\varphi(\sqC_y)$ and the leftmost vertex of the tropical target, where $\sqC_y$ is the vertex of the source curve containing the flag corresponding to $y$.
-Using this tropical description, we may easily calculate the vanshing orders of $s_y^{\not\in\operatorname{bot}}$ along the various components of $\Dcal(y)$.
-Moreover we may use this description to show (see also \cite{EKatzLB}) that $\cchern_1(L_y^{\not\in\operatorname{bot}}) = \Psi_0 - \ev_y^\st Y$, from which we conclude
-\begin{equation}\label{step 4 recursion} (\Psi_0 - \ev_y^\st Y) \tilde\gamma \cap [VZ_{1,\alpha\cup(0)}(P|Y_0+Y_\infty,\beta)_{\Gm}] = \tilde\gamma \cap [\Dcal(y)]\end{equation}
-where the fundamental class $[\Dcal(y)]$ is weighted by vanishing orders.
+Let $x_1$ be a positive-tangency marking (such a marking always exists since $d \geq 2$) and let $\tilde\gamma$ be the insertion obtained from $\gamma$ by replacing $\ev_1$ and $\psi_1$ by $\ev_y$ and $\psi_y$, and then introducing $\fgt_{1}^\st$ everywhere.
+
+We will make use of a recursion formula for rubber spaces analogous to the recursion formula for relative spaces used in Steps 1--3.
+Following \cite{EKatz}, there is a line bundle $L_y^{\not\in \operatorname{bot}}$ on $\VZ_{1,\alpha\cup (0)}(P|Y_0+Y_\infty,\beta)_{\Gm}$, together with a section $s_y^{\not\in\operatorname{bot}}$ whose vanishing locus consists of the locus $\Dcal(y)$ of rubber maps where $y$ is not mapped into the bottom level of the expanded target.
+As in \S \ref{}, we can give a logarithmic interpretation of this: it corresponds to the piecewise-linear function on the tropical moduli space which associates, to every rubber tropical map, the distance between $\varphi(\sqC_y)$ and the leftmost vertex of the tropical target, where $\sqC_y$ is the vertex of the source curve containing the flag corresponding to $y$.
+Using this tropical description, we may easily calculate the vanshing orders of $s_y^{\not\in\operatorname{bot}}$ along the various components of $\Dcal(y)$, and show that $\cchern_1(L_y^{\not\in\operatorname{bot}}) = \Psi_0 - \ev_y^\st Y$ (see also \cite{EKatzLB}, where similar results in the non-reduced setting are obtained, using different methods).
+From this, we obtain a rubber recursion formula
+\begin{equation}\label{step 4 recursion} (\Psi_0 - \ev_y^\st Y) \tilde\gamma \cap [\VZ_{1,\alpha\cup(0)}(P|Y_0+Y_\infty,\beta)_{\Gm}] = \tilde\gamma \cap [\Dcal(y)]\end{equation}
+where the fundamental class $[\Dcal(y)]$ is weighted by vanishing orders on the components.
 We will first show that the left-hand side is recursively known.
-By construction the class $\tilde\gamma$ is pulled back along $\fgt_{x_0}$, and the same is true for $\ev_y^\st Y$.
-Let us examine $\Psi_0$.
-If there exists a negative-tangency marking $x_2$, then we have \cite{GathmannThesis}
-\begin{equation*} \Psi_0 = -\alpha_2 \hat\psi_2 - \ev_2^\st Y \end{equation*}
-where $\hat\psi_2$ is a \emph{non-collapsed} psi class. (If there are no negative-tangency markings then the construction \cite[\S 1.5.2]{MaulikPandharipande} gives $\Psi_0=0$.)
-\newpage
-
-\section{Recursion procedure for reduced rubber integrals} \footnote{(Navid) To be superseded by general recursion section} In the recursion above, certain terms appear which are integrals over moduli spaces of reduced log stable maps to rubber (as defined in \S \ref{}):
-\begin{equation*}\VZ_{1,\alpha}(P|H_0+H_\infty)_{\Gm}.\end{equation*}
-In this section we provide a recursive algorithm for computing such integrals.
-We have three main techniques at our disposal: direct comparison with the double ramification cycle, forgetting of a marking with no insertion, and rubber recursion.
-Each technique has its own domain of applicability, and these domains have non-trivial intersection.
-For convenience we denote the \textbf{horizontal degree} of the rubber map by:
-\begin{equation*} d := \sum_{i=1}^n \alpha_i .\end{equation*}
-Recall that the $\alpha_i$ may be positive or negative (recording tangencies with respect to $H_\infty$ and $H_0$, respectively) and that $d \geq 0$ always.
-First suppose that $d=0$.
-Then the usual rubber moduli space decomposes as
-\begin{equation*} \MLog_{1,\alpha}(P|H_0 + H_\infty)_{\Gm} = \MLog_{1,\alpha}(\PP^1|0+\infty)_{\Gm} \times H \end{equation*}
-and the first term on the right-hand side is birational to the double ramification locus in $\ol\Mcal_{1,n}$.
-This locus has a main component (the closure of the locus of smooth curves) and one other ``exceptional'' component, consisting of split curves where all the markings belong to the rational tail.
-The corresponding reduced rubber space is birational to the main component, and thus we can identify its class by subtracting off the class of the exceptional component.
-This gives
-\begin{equation*} \pi_\st [\VZ_{1,\alpha}(P|H_0+H_\infty)_{\Gm}] = \left( [\ol\Mcal_{1,n}^\alpha] - [D] \right) \times [H] \in \Achow_\st ( \ol\Mcal_{1,n} \times H ) = \Achow_\st ( \ol\Mcal_{1,n}(H,0) ) \end{equation*}
-where $\pi \colon \VZ_{1,\alpha}(P|H_0+H_\infty)_{\Gm} \to \ol\Mcal_{1,n}(H,0)$ is the map which forgets the log structure and collapses the map, $D$ is the boundary locus of split curves described above, and $[\ol\Mcal_{1,n}^\alpha]$ is the classical double ramification cycle, which has an explicit formula in terms of tautological classes \cite{Hain,JPPZ}.
-These observations allow us to compute the integral over the rubber space as a tautological integral on the moduli space of curves.
-
-Now suppose that $d>0$. If there is a marking $x_k$ which carries no insertion and has $\alpha_k \neq 0$, then consider the morphism which forgets $x_k$ and collapses the map:
-\begin{equation*} \VZ_{1,\alpha}(P|H_0+H_\infty)_{\Gm} \xrightarrow{\pi} \VZ_{1,n-1}(H,d). \end{equation*}
-The moduli spaces above are log smooth and of the same dimension.
-Over the nice locus in $\VZ_{1,n-1}(H,d)$, $\pi$ has degree $\alpha_k^2$, arising from a choice of $\alpha_k$-torsion point on the source elliptic curve.
-Thus we have:
-\begin{equation*} \pi_\st [\VZ_{1,\alpha}(P|H_0+H_\infty)_{\Gm}] = \alpha_k^2\cdot [\VZ_{1,n-1}(H,d)].\end{equation*}
-Since all the insertions are pulled back from the right-hand side (up to modifying psi classes by some boundary strata which we can then also compute recursively) we can perform the integral on $\VZ_{1,n-1}(H,d)$ inductively.
-Notice that, when we apply our recursion \ref{} to compute a reduced invariant of $H$, the only non-trivial reduced rubber integrals which appear will have smaller degree than the one we started with, so the calculation is not circular.
-
-It remains to deal with the case where all of the relative markings carry insertions.
-The idea is to reduce to the case above by introducing an additional marking.
-Note first that every reduced rubber integral which appears in our recursion must either have a marking of negative tangency (i.e.
-tangent to $H_0$), or a marking with no insertions: indeed, the only boundary loci with no negative-tangency markings have the entire curve mapped to higher level, in which case (since we are assuming $d>0$, so we are not in the $C_0$ case) the curve is generically irreducible, and on this curve we have at least one fictitious marking (of positive tangency $1$) with no insertion.
-
-Therefore we may assume that there is at least one point of negative tangency, corresponding to a node at which we will glue.
-Notice that in our recursion these points only ever carry evaluation classes.
-Consider the following rubber space of dimension one higher, obtained by introducing an additional non-relative marking:
-\begin{equation} \label{bigger rubber space}\VZ_{1,\alpha \cup (0)}(P|H_0+H_\infty)_{\Gm}. \end{equation}
-Given a moduli point in this space, consider the piecewise-linear function on the associated tropical moduli space which sends a tropical map to the sum of the target edge lengths.
-This defines a line bundle and section on the space \eqref{bigger rubber space} which vanishes precisely on the locus where the target splits; moreover the vanishing orders may be read off from the tropical data as in \S \ref{}.
-It is not hard to see \cite{EKatz} that the first Chern class of the line bundle is
-$\Psi_0 + \Psi_\infty$, a sum of target psi classes which may be identified with evaluation and psi classes on the source curve as in \cite[Construction 5.1.17]{GathmannThesis}.
-
-Now choose a negative-tangency point $x_1$ which carries only evaluation classes, and let $x_0$ denote the new non-relative marking we have introduced.
-If $\gamma$ was the class we were originally trying to integrate, consider the class $\tilde\gamma$ on \eqref{bigger rubber space} obtained from $\gamma$ by replacing $\ev_1^\st$ by $\ev_0^\st$.
-We obtain a recursion formula:
-\begin{equation*} (\Psi_0+\Psi_\infty)\cdot \tilde\gamma \cap [\VZ_{1,\alpha\cup(0)}(P|H_0+H_\infty)_{\Gm}] = \sum_{\Gamma} m_\Gamma \cdot \tilde\gamma \cap [\ol\Mcal_{\Gamma}]. \end{equation*}
-The right-hand side is a sum over irreducible components $\ol\Mcal_\Gamma$ of the locus where the target splits, with multiplicites $m_\Gamma$ calculated from the tropical data.
-Each of these components can be written as a fibre product of (reduced) rubber spaces.
-One of these components is the locus where $x_0$ and $x_1$ belong to a trivial rational bubble:
-
-[FIGURE]
-
-The corresponding moduli space is $\VZ_{1,\alpha}(P|H_0+H_\infty)_{\Gm}$ and we have $\ev_0=\ev_1$ here, so the contribution of this locus is precisely the original rubber integral we were trying to calculate.
-The remaining terms on the right-hand side can be written either as a product of rubber integrals of smaller degree (which we can compute recursively), or rubber integrals of the same degree but with no insertion at $x_1$ (which we can compute by forgetting $x_1$).
-Finally, the left-hand side also has no insertion at $x_1$ and so can be computed by the same method.
-Here we are assuming that $x_1$ is not the only negative-tangency marking, so that $\Psi_0$ can be interpreted as an insertion on a marking different from $x_1$.
-
-If $x_1$ is in fact the only negative-tangency marking, then we can modify the above argument by considering the following rubber space of dimension two larger:
-\begin{equation}\label{rubber space two extra markings} \VZ_{1,\alpha\cup(0,0)}(P|H_0+H_\infty)_{\Gm} \end{equation}
-Let us denote the newly-introduced non-relative markings by $x_0$ and $x_{n+1}$.
-We now let $\tilde\gamma$ denote the class obtained from $\gamma$ by replacing $\ev_1^\st$ by $\ev_0^\st$ and then multiplying by $\psi_{n+1}$.
-Following \cite{EKatz}\footnote{(Navid) Tropica interpretation of this?
-Vanishing multiplicities?}, there is a line bundle with a section cutting out the locus where $x_{n+1}$ does not belong to the leftmost component of the target.
-The first Chern class of this line bundle is $\Psi_\infty+\ev_{n+1}^\st H$, which we may multiply with $\tilde\gamma$ and integrate over \eqref{rubber space two extra markings} to obtain a rubber integral with no insertion at $x_1$ (which we may then compute by forgetting $x_1$).
-On the right-hand side we obtain the integral of $\tilde\gamma$ over the loci where $x_{n+1}$ does not belong to the leftmost component of the target (this is just a union of some of the irreducible components of the split locus described above).
-One such locus is the following
-[FIGURE]
-and integrating $\tilde\gamma$ over this locus gives
-\begin{equation*} \gamma\cdot\psi_{n+1}\cap [\VZ_{1,\alpha\cup(0)}(P|H_0+H_\infty)_{\Gm}] \end{equation*}
-which we may identify with a (nonzero) multiple of our original rubber integral via the rubber dilaton equation (see\cite{MaulikPandharipande}; the same proof carries over to the reduced setting\footnote{(Navid) Think about this a bit}).
-The remaining loci may be computed recursively exactly as before, and thus we obtain a complete recursion procedure.
-
-\begin{remark} This idea --- of finding a section of a line bundle cutting out the locus of split curves, and using this to derive recursion formulae for rubber integrals --- has been pursued in the non-reduced setting in \cite{EKatz}.\end{remark}
+By construction the class $\tilde\gamma$ is pulled back via $\fgt_{1}^\st$, and the same is true for $\ev_y^\st Y$.
+It remains to examine $\Psi_0$.
+If there exists a negative-tangency marking $x_2$, then we have \cite[Construction 5.1.17]{GathmannThesis}
+\begin{equation*}\label{Psi0 formula} \Psi_0 = -\alpha_2 \hat\psi_2 - \ev_2^\st Y \end{equation*}
+where $\hat\psi_2$ is a \emph{non-collapsed} psi class.
+(If there are no negative-tangency markings, then the construction given in \cite[\S 1.5.2]{MaulikPandharipande} shows that $\Psi_0=0$.) Now, $\hat\psi_2 - \psi_2$ is given by the loci where $x_2$ belongs to a trivial bubble.
+This entails a splitting of the curve into pieces, each of which contributes a rubber integral.
+Typically each of these pieces will have $(g^\prime,d^\prime,n^\prime,m^\prime) < (1,d,n,m)$ and hence be recursively known.
+The one exception is when all of the genus and degree is concentrated on the top level of the expansion, with the bottom level containing only a single non-relative marking in addition to all the negative-tangency markings.
+But in this case the contribution is a rubber invariant where all of the insertions are pulled back via $\fgt_1^\st$, and hence we may apply the projection formula to identify this with an absolute invariant of $Y$ which is recursively known.
+We conclude that, up to recursively knwon terms, we may replace $\hat\psi_2$ by $\psi_2$ in the left-hand side of \eqref{step 4 recursion}.
+If we now compare $\psi_2$ with $\fgt_1^\st \psi_2$ we see that the difference is given by the locus where $x_1$ and $x_2$ belong to a collapsed rational piece.
+The contribution of this locus consists of rubber invariant with strictly fewer relative markings, and hence is recursively known.
+So up to recursively-known terms \eqref{step 4 recursion} becomes
+\begin{equation*} \fgt_1^\st (-\alpha_2\psi_2 - \ev_y^\st Y)\tilde\gamma \cap [\VZ_{1,\alpha\cup(0)}(P|Y_0+Y_\infty,\beta)_{\Gm}] = \tilde\gamma\cap[\Dcal(y)]\end{equation*}
+and now the left-hand side is also recursively known, by the projection formula.
+Let us now examine the right-hand side.
+The components of $\Dcal(y)$ are indexed by splittings of the curve, and certainly the contributions are recursively known unless there is a piece of the curve carrying all of the genus and degree, so we may restrict to examining these contributions.
+
+Let us denote the piece of the curve carrying all of the genus and degree by $C^\prime\subseteq C$.
+If $C^\prime$ is mapped to top level, then either it contains $x_1$, in which case we apply $\fgt_1$ to compute the contribution, or it does not contains $x_1$, in which case it has fewer than $n$ relative markings and is known recursively.
+If on the other hand $C^\prime$ is not mapped to top level, then generically it is mapped to the bottom level (since generically the circuit is not contracted on this locus, so the desingularisation process does nothing).
+One possible contribution is given by the following locus
+\begin{center}
+\begin{tikzpicture}[scale=1]
+%edge
+\draw (0,0) to (2,0);
+\draw [color=blue] (1,0) node[below]{\tiny$\alpha_1$};
+
+%C_1
+\draw [fill=white] (0,0) circle[radius=3pt];
+\draw (0,-0.1) node[below]{\small$d$};
+
+%y
+\draw [->] (2,0) -- (2,1);
+\draw (2,0.9) node[left]{$y$};
+\draw [color=blue] (2,0.5) node[right]{\tiny$0$};
+
+%x_1
+\draw [->] (2,0) -- (3,0);
+\draw (3,0) node[right]{$x_1$};
+\draw [color=blue] (2.5,0) node[below]{\tiny$\alpha_1$};
+
+%C_0
+\draw [fill=black] (2,0) circle[radius=3pt];
+\draw (2,-0.1) node[below]{\small$0$};
+
+%down arrow
+\draw [color=blue,->] (1,-0.5) -- (1,-0.9);
+
+%target
+\draw [color=blue] (0,-1) to (2,-1);
+\draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
+\draw [fill=blue,color=blue] (2,-1) circle[radius=3pt];
+\draw [color=blue,->] (2,-1) -- (3,-1);
+\draw [color=blue,->] (0,-1) -- (-1,-1);
+\end{tikzpicture}
+\end{center}
+which contributes a nonzero multiple of the invariant $I$ we are trying to compute.
+For the other possibilities, first note that, unless every component at the top level contains a single positive-tangency marking and a single node (together with possibly some tangency-zero markings), then $C^\prime$ has fewer than $n$ relative markings and hence the contribution is known recursively.
+On the other hand, if any non-relative marking other than $y$ is mapped to the top level, $C^\prime$ has $\leq n$ relative markings and less than $m$ non-relative markings, and hence again the contribution is known recursively.
+The only remaining possibilities are when $x_1$ is replaced by another positive-tangency marking $x_k$ in the above picture; but then the contribution can be calculated by applying the projection formula to $\fgt_{1}$.
+We therefore conclude that the only contribution to the right-hand side of \eqref{step 4 recursion} which is not known recursively is a nonzero multiple of the invariant we were trying to compute.
+This completes the recursion step.
 

### 2019-03-04 GenusOneRelativeMaps.tex
incorporated Dhruv files (not in correct order yet)

@@
 \documentclass[11pt]{amsart}
-\linespread{1.25}
+%\linespread{1.25}
 \usepackage[margin=3.5cm]{geometry}
@@
 
+\section{Introduction}
+
+\noindent Gromov-Witten theory in genus zero has been studied intensely using a large assortment of techniques, many of which rely crucially on the remarkable geometry of the Kontsevich space of genus zero maps to projective space.
+On the other hand, the higher genus spaces have uncontrollable singularities, and an entirely different set of techniques must be appealed to.
+Indeed, much less is known in higher genus, though the last few years have seen remarkable progress.
+
+\subsection{The transition point in genus one} The singularities of the space of maps in genus one are delicate, but understandable.
+Vakil and Zinger exhibited this by giving an explicit blowup algorithmic that desingularized the space of maps to projective space, giving rise to ``reduced’’ Gromov—Witten invariants, which are closer to enumerative counts~\cite{VZ}.
+Certain tools, such as localization and quantum Lefschetz, can thus be extended to genus one.
+However, there is as yet no degeneration formula for the Vakil—Zinger invariants.
+
+Recently, a more conceptual and geometric understanding of Vakil and Zinger’s construction has come out of tropical geometry and logarithmic Gromov—Witten theory.
+Specifically, Ranganathan, Santos-Parker, and Wise give a modular interpretation of the construction and a deformation theoretic proof its smoothness by using the geometry of elliptic singularities~\cite{RSPW,RSPW2}.
+In this paper we seek an understanding of Vakil—Zinger invariants in relative geometries and the degeneration formula.
+
+\subsection{Results} Our first contribution is a definition and construction of relative reduced Gromov-Witten theory of projective space relative to a hyperplane.
+The geometric content is the following.
+
+\begin{customthm}{A}
+There exists a smooth and proper Deligne—Mumford stack giving a modular compactification for the space of genus $1$ maps to projective space with fixed contact order with a hyperplane. 
+\end{customthm}
+
+With regards to the degeneration formula, we pursue the strategy laid out by Vakil and Gathmann, building on work of Caporaso and Harris.
+We reinterpret and extend their methods using logarithmic geometry and tropical techniques.
+We present a recursive scheme to calculate the invariants of a hypersurface from the invariants of projective space.
+
+\begin{customthm}{B}
+There is an explicit recursive algorithm to calculate the reduced genus one Gromov--Witten invariants of a hypersurface from that of the ambient variety. 
+\end{customthm}
+
+By standard virtual pullback techniques, virtual versions of our results apply for smooth ample pairs $(X,D)$.
+
+\subsection{Broader contributions} Beyond genus one, we pass through a number of seemingly useful general techniques.
+First, we explain how to describe degenerate moduli spaces as fiber products.
+This is substantially more delicate than the standard situation because of the need to work with elliptic singularities and aligned logarithmic structures.
+This interaction of the degeneration formula with the geometry of curve singularities is a new phenomenon.
+The results of~\cite{RSPW} suggest the existence of a reduced higher genus Gromov--Witten theory formed by replacing contracted elliptic components with singularities.
+The discussion here is likely to carry over to this setting.
+
+Second, a key step in our recursion is a description of the locus of maps with higher than prescribed tangency, which was identified by Gathmann.
+We realize the locus as the vanishing locus of a section of a line bundle that comes from tropical geometry — from a piecewise linear function on the fan.
+The systematic understanding of logarithmic line bundles arising in this fashion is likely to play an important in logarithmic enumerative geometry.
+
+Our analysis leads naturally to a study of a ``main component’’ double ramification cycle for target manifolds in genus one.
+The virtual geometry of this was studied in recent work of Janda, Pandharipande, Pixton, and Zvonkine~\cite{DRCBundle}.
+We do not know how to calculate an expression for this main component contribution but we repurpose Maulik and Pandharipande’s rubber calculus techniques, and relations coming from the stack of target expansions, to complete our recursion.
+We note that even in genus one, an understanding of the main component contributions of the double ramification cycle for target manifolds would be interesting.
+
+Finally, we note that our results require us to encounter several variants of the space of relative/logarithmic stable maps, with both fixed and expanded target.
+The conceptual features of one space are often computational bugs, and vice versa, and we believe that the techniques developed in the genus one case here will be used repeatedly in logarithmic Gromov--Witten theory calculations.
+In particular, we use frequently use Kato's perspective on logarithmic blowups as subfunctors that was applied in~\cite{RSPW,RSPW2}.
+
+\section{The moduli space and its deformation theory}
+
+Let $\mathfrak M_{1,n}$ be the logarithmic algebraic stack of genus $1$ $n$-pointed prestable curves.
+Let $\plC$ be a $n$-pointed genus $1$ tropical curve.
+Let $C$ be a logarithmic curve over $S$, let $\plC$ denote its tropicalization, and let $\lambda$ be the section of $\overline{M}_{C/S}$ giving the distance from the circuit.
+
+We begin by recalling the logarithmic moduli spaces of genus $1$ curves constructed in~\cite[Sections 2 \& 4]{RSPW}.
+Given a family of tropical curves over a base $\sigma$, a central alignment is a piecewise-linearly varying choice of radius $\delta_s$ for $s\in\sigma$, together with a consistent ordering of the vertices that lie inside the circle of radius $s$ around the circuit components.
+Precisely, let $T$ be a geometric point with logarithmic structure.
+
+\begin{definition}
+A \textbf{central alignment} of $C/T$ is an element $\delta\in\overline{M}_S$ such that
+\begin{enumerate}
+    \item the section $\delta$ is comparable to $\lambda(v)$ for all vertices $v$ of $\plC$,
+    \item for any pair of vertices $v$ and $w$ at distance less than $\delta$, the sections $\lambda(v)$ and $\lambda(w)$ are comparable.
+\end{enumerate}
+\end{definition}
+
+The moduli stack $\mathfrak M_{1,n}^{\mathrm{cen}}$ is a logarithmic algebraic stack in the smooth topology.
+The main construction of~\cite{RSPW} canonically associates to any radially aligned family of curves $\mathcal C_S$ a partial destabilization $\widetilde{\mathcal C_S}$ and a contraction
+\[
+\widetilde{\mathcal C_S}\to \overline{\mathcal C_S},
+\]
+where $\overline{\mathcal C_S}$ is a Gorenstein elliptic singular curve.
+The number of branches is equal to the number of excident edges at the circle of radius $\delta$.
+This data uniquely determines the singularity.
+
+The space of stable maps $\overline{\mathcal M}^{\mathrm{cen}}_{1,n}(\mathbb P^N,d)$ from the universal nodal curve $\mathcal C$ over the stack $\mathfrak M_{1,n}^{\mathrm{cen}}$ is a proper and algebraic, with projective coarse moduli.
+The \textbf{factorization condition} that the map $\mathcal C\to \mathbb P^N$ factors through the contraction $\widetilde{\mathcal C}\to \overline{\mathcal C}$ is a closed condition.
+\begin{thm}[{\cite[Theorem B]{RSPW}}]
+The substack $\mathcal{VZ}_{1,n}(\mathbb P^N,d)$ of $\overline{\mathcal M}^{\mathrm{cen}}_{1,n}(\mathbb P^N,d)$ parameterizing maps to $\mathbb P^N$ that satisfy the factorization property is smooth and proper of the expected dimension.
+\end{thm}
+
+\subsection{Relative geometry: compactification} Fix $H\subset \mathbb P^N$ be a hyperplane.
+Let $\alpha$ be a partition of the degree $d$.
+Consider the moduli space $\mathcal M_{1,\alpha}^\circ(\mathbb P^N|H)$ of maps from smooth elliptic curves $C\to \mathbb P^N$ that meet $H$ at finitely many marked points with vanishing orders given by the partition $\alpha$.
+This is a smooth non-compact Deligne--Mumford stack.
+
+We will first compactify the space described above, and then desingularize it.
+For the compactification, we begin with Abramovich--Chen--Gross--Siebert's space of logarithmic stable maps, though we will typically work with various subcategories and variants.
+
+The moduli space $\overline{\mathcal{M}}^{\operatorname{log}}_{1,\alpha}(\mathbb P^N|H)$ is a fibred category over logarithmic schemes, whose fiber over $(S,M_S)$ is the groupoid of logarithmic curves of genus $1$ over $(S,M_S)$ equipped with a map to $\mathbb P^N$ of degree $d$ and contact order $\alpha$.
+It is a fundamental fact in the subject that this category is representable by a proper algebraic stack with logarithmic structure.
+
+There is a representable finite logarithmic morphism to the Kontsevich space, forgetting the logarithmic structure on the target:
+$$
+\overline{\mathcal M}^{\mathrm{log}}_{1,\alpha}(\mathbb P^N|H) \to \overline{\mathcal M}_{1,n}(\mathbb P^N,d).
+$$
+The space of centrally aligned maps is a logarithmic modification
+$$
+\overline{\mathcal M}^{\mathrm{cen}}_{1,n}(\mathbb P^N,d)\to\overline{ \mathcal M}_{1,n}(\mathbb P^N,d)
+$$ 
+The fiber product leads to a fourth moduli space of \textbf{centrally aligned logarithmic maps to $(\mathbb P^n,H)$}, which we denote $\widetilde{\mathcal{VZ}}_{1,\alpha}(\mathbb P^N|H)$.
+
+\subsection{Relative geometry: expansions} Our next task is to pick out a non-singular principal component in $\widetilde{\mathcal{VZ}}_{1,\alpha}(\mathbb P^N|H)$.
+The principal component of this space, consisting of the closure of the space of maps from nonsingular curves, maps into the principal component of $\overline{\mathcal M}^{\mathrm{cen}}_{1,n}(\mathbb P^N,d)$.
+Indeed, smoothable logarithmic maps are, in particular, smoothable as ordinary maps.
+However, an additional condition is required to isolate the principal component of the space of logarithmic maps.
+
+In order make the obstruction theory more geometric, we expand the target.
+To elucidate the connection with the static target, consider a logarithmic stable map $[C\to (\mathbb P|H)]$ over $\mathrm{Spec} \ (\mathbb N\to \mathbb C)$.
+At the level of tropicalizations, we have a map of fans
+\[
+\plC\to \mathbb R_{\geq 0}.
+\]
+Choose a subdivision of $\mathbb R_{\geq 0}$ whose vertices consist of the images of vertices of $\plC$.
+Pull this subdivision back to $\plC$ by marking all preimages of the vertices of $\mathbb R_{\geq 0}$.
+Denote the resulting map $\widetilde \plC \to \widetilde{\mathbb R}_{\geq 0}$.
+
+These subdivisions induce logarithmic modifications
+\[
+\widetilde C\to \mathbb P^N[s],
+\]
+see~\cite{AW}.
+Here the latter is the $s$-times iterated deformation to the normal cone of $H$ in $\mathbb P^N$.
+The number of components is equal to the number of vertices in $\widetilde{\mathbb R}_{\geq 0}$.
+The curve is modified by adding rational components corresponding to the newly introduced vertices.
+
+The result is a logarithmic stable map to an expanded target $\mathbb P^N[s]$, together with a contraction to the main target component $\mathbb P^N[s]\to\mathbb P^N$.
+More generally, this construction is easily modified for any family of logarithmic maps, such that the vertices of $\plC$ are totally ordered in the family, see~\cite{} for details.
+
+Globally, Kim constructs a moduli space of logarithmic stable maps to expanded degenerations, which on logarithmic points, reduces to the above construction~\cite{KimLog}.
+Indeed, by above description, Kim's space is identified with a subcategory of the Abramovich--Chen--Gross--Siebert space, and its minimal objects are identified with a logarithmic modification of the unexpanded space.
+
+\subsection{Relative geometry: factorization} Let $[C\to \mathbb P^N[s]\to \mathbb P^N]$ be a logarithmic map from a centrally aligned curve to an expansion.
+Recall that $\mathbb P^N[s]$ consists of a union of $\mathbb P^N$ with the projective bundle $\mathbb P(\mathcal O\oplus \mathcal O(1))$.
+We refer to these latter components as \textbf{the higher levels}.
+Thus, we will say that subcurve $D\subset C$ maps to \textbf{higher level} if the collapsed map
+\[
+D\to \mathbb P^N
+\]
+is contained in $H\subset \mathbb P^N$.
+
+Let $D_1\subset C$ be the maximal genus $1$ subcurve that is mapped to higher level contracted by the map $C\to \mathbb P^N[s]$ in the fiber direction.
+Let $\delta_1$ be the associated radius from the circuit to the nearest non-contract component.
+Let $D_2$ be the maximal genus $1$ subcurve that is contracted by the collapsed map to $\mathbb P^N$, and let $\delta_2$ be the associated radius.
+This coincides with the radius of the underlying map to $\mathbb P^N$.
+Of course, $\delta_1\leq \delta_2$.
+
+The datum $(\delta_1,\delta_2)$ determines a destabilization $\widetilde C$ of $C$ together with successive contractions $\widetilde C\to \overline C_1\to\overline C_2$.
+Keeping this definition, we come to the key definition.
+
+\begin{definition}
+The map $[C\to \mathbb P^N[s]\to \mathbb P^N]$ \textbf{factorizes completely} if
+\begin{itemize}
+\item the map $C\to \mathbb P^N[s]$ factors through $\overline C_1$ such that at least one branch of $\overline C_1$ has positive degree in the fiber direction. 
+\item the collapsed map to $\mathbb P^N$ factorizes through $\overline C_2$ such that at least one branch of $\overline C_2$ has positive degree.
+\end{itemize}
+\end{definition}
+
+In particular, if $[C\to \mathbb P^N[s]\to \mathbb P^N]$ is a family of centrally aligned maps over $S$ that factorizes completely, there is a forgetful moduli map $S\to \mathcal{VZ}_{1,n}(\mathbb P^N,d)$, to the principal component of the space of absolute maps.
+
+Let $\mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)$ be stack of maps from centrally aligned curves to expansions of $\mathbb P^N$ that factorize completely.
+
+\begin{thm}\label{thm: log-smoothness}
+The stack $\mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)$ is proper and logarithmically non-singular over $\mathrm{Spec} \ \mathbb C$. 
+\end{thm}
+
+\begin{proof}
+We prove the results via the forgetful morphism
+$$
+\nu: \mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)\to \mathcal{VZ}_{1,n}(\mathbb P^N,d),
+$$
+which remembers only the stabilization of the collapsed map.
+The map is certainly centrally aligned, and we have already argued above that it satisfies the factorization property for $\mathbb P^N$ after composition.
+The morphism $\nu$ is in fact proper: the verification for the valuative criterion is the essential content of Vakil's Lemma~\cite[Lemma~5.9]{Vak}, and a detailed proof may be found in~\cite[Theorem~4.3]{RSPW}.
+
+We come to logarithmic smoothness.
+Assume first that the elliptic curve maps into higher level.
+Note that the relative logarithmic tangent bundle of the expansion, over the base $\mathbb P^N$ is a trivial line bundle of rank $1$, as the fibers are toric.
+Consider an $S$-family of maps.
+After replacing the source $C$ by a destabilization, we have maps
+\[
+C\to \overline{C}_1\to\overline{C}_2\to \mathbb P^N[s]\to \mathbb P^N
+\]
+factorizing completely. Let $f_B$ and $f_T$ be the maps from $C$ to the base and total space respectively. Examining the morphism $\nu$, we see that there is a map
+\[
+\mathrm{Def}(C,f_B)\to \mathrm{Obs}(f_T) = H^1(\overline{C}_1,\mathcal O_{\overline{C}_1}),
+\]
+where the former is the space of deformations of the curve and map to the base, as a factorized centrally aligned map.
+The latter is the space of obstructions to lifting a map to the base into the total space.
+The cokernel of this map are the absolute obstructions, which we will show vanishes, proving logarithmic smoothness.
+
+We recall how the group $H^1(\overline{C}_1,\mathcal O_{\overline{C}_1})$ functions as the obstruction group for the lifting.
+It suffices to work near the minimal grnus $1$ subcurve $D_1$ of $C_1$, since the rest of the curve is rational.
+This lifting is given by a rational function with prescribed orders of poles given by the slopes of the tropicalization map.
+That is, if $\alpha$ be the piecewise linear function giving this tropical map, then the lifting is described by a section of the associated bundle $\mathcal O_{C_1}(-\alpha)$.
+
+Given a strict square-zero extension $S'$ of $S$, the piecewise linear function $\alpha$ extends uniquely by strictness to any deformation of the curve.
+The resulting deformation of $\mathcal O_{C_1}(-\alpha)$ produces an infinitesimal deformation of the trivial bundle in the Picard group, whose class in $H^1(\overline{C}_1,\mathcal O_{\overline{C}_1})$, is the obstruction to deformation.
+We will show that it is possible to choose a deformation of $(C,f_B)$ that cancels out the obstruction to lifting to $f_T$, and thus the map to the obstruction space above is surjective.
+
+The line bundle $\mathcal O_{C_1}(-\alpha)$ is equivalent to the divisor $\sum a_i x_i$ where $x_i$ are the points connecting $D_1$ to the rest of the curve, and $a_i$ are the slopes of $\alpha$ along the edges corresponding to the $x_i$.
+Infinitesimally moving the point $x_i$ is a deformation of the curve that is unobstructed by the map $f_B$, since the map is constant on the interiors of the circuits.
+By deforming the $x_i$, at least one of which is nonzero, we produce a one-dimensional space of obstructions.
+The absolute obstructions therefore vanish, since they are the cokernel of a surjective map, so the result follows.
+%Consider an $S$-family of expanded maps $[F: C\to \mathbb P^N[s]$.
+Choose $N$ generic hyperplanes in and let $\Delta = \{H\}\cup\{H_1,\ldots,H_N}$ be this set of hyperplanes.
+There is a morphism of logarithmic schemes $(\mathbb P^N,\Delta)\to (\mathbb P^N,H)$.
+This induces a new expansion $\mathbb P^N[\Delta,s]$.
+Moreover, by the genericity of the $H_i$, they each intersect the image of $C$ in finitely many reduced points.
+Pulling back the logarithmic structure, we obtain a new logarithmic map
+%\[
+%F': C'\to \mathbb P^N[\Delta,s].
+%\]
+%We make two observations.
+First, since the logarithmic structure on $C'$ is strict away from $H$, unobstructedness of deformations for $F'$ is equivalent to unobstructedness for $F$.
+Second, the target degeneration is now a toric degeneration, and the logarithmic tangent bundle is trivial.
+
+\end{proof}
+
+The above theorem guarantees that the singularities of the space of totally factorized maps to expansions is logarithmically smooth. In fact, one can say more in this case.
+
+\begin{cor}
+The logarithmically smooth stack $\mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)$ has at worst orbifold singularities, and consequently admits a non-representable cover by a smooth Deligne--Mumford stack.
+\end{cor}
+
+\begin{proof}
+Since $\mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)$ is logarithmically smooth, it will suffice to show that the cones of its tropicalization are simplicial.
+To see this, consider a logarithmic stable map to an expansion $C\to \mathbb P^N[s]$ without a central alignment.
+The tropical moduli cone obtained as the dual of the minimal base monoid can be identified with $\mathbb R_{\geq 0}^{s}$, see for instance~\cite[Section~2.2]{ChenDegeneration}.
+The alignment procedure is an iterated barycentric subdivision at the level of tropical moduli spaces, as explained in~\cite[Section 4.6]{RSPW}, and such subdivisions preserve the property of being simplicial.
+We conclude from this that the blowup $\widetilde{\mathcal{VZ}}^{\mathrm{exp}}_{1,\alpha}(\mathbb P^N|H)$ obtained by centrally aligning Kim's spaces has simplicial cones.
+Finally, the morphism $\mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)\to \widetilde{\mathcal{VZ}}^{\mathrm{exp}}_{1,\alpha}(\mathbb P^N|H)$ is strict, so the cones of $\mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)$ are simplicial, as claimed.
+\end{proof}
+
+\subsection{Stratification} The logarithmic smoothness established in Theorem~\ref{thm: log-smoothness} implies that $\mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)$ is an orbifold toroidal embeddeding.
+Consequently, the irreducible components of its boundary and their intersections form a stratification of the space.
+This stratification will be important in the sequel.
+
+The tropicalizations of logarithmic maps that factorize completely satisfy a natural combinatorial condition known as well-spacedness. The version we use here is essentially identical to~
+\cite{RSPW2}.
+
+\begin{definition}
+Let $\plC$ be a tropical curve of genus $1$ and let $\plC_0$ be its minimal subcurve of genus $1$.
+A tropical map $F: \plC\to \mathbb R_{\geq 0}$ is said to be \textbf{well-spaced} if one of the following two conditions are satisfied:
+\begin{enumerate}
+    \item no open neighborhood of $\plC_0$ is contracted to a point in $\mathbb R_{>0}$, or
+    \item if an open neighborhood of $\plC_0$ is contracted and $t_1,\ldots,t_k$ are the vertex-edge direction flags whose vertex is mapped to $F(\plC_0)$, but along which $F$ has nonzero slope; then, the minimum of the distances from $\plC_0$ to $t_i$ occurs for at least two indices $i$.
+\end{enumerate}
+\end{definition}
+
+\begin{prop}\label{prop: well-spaced}
+Let $[C\to \mathbb P^N]$ be a logarithmic stable map from a centrally aligned curve to an expansion, that factorizes completely. Then the tropicalization $\plC\to \mathbb R_{\geq 0}$ is well-spaced.
+\end{prop}
+
+\begin{proof}
+The required result is essentially contained in~\cite[Section 4]{RSPW2}, so we explain how to deduce the requisite result from the one in loc.
+cit.
+We may focus on a single component of the expansion $\mathbb P^N[s]$ that contains the image of a contracted genus $1$ subcurve, as this is the only relevant case.
+We may thus replace the target with the projective bundle $\mathbb P(\mathcal O(1)\oplus \mathcal O)$ over $\mathbb P^{N-1}$ equipped with the divisorial logarithmic structure from the $0$ and $\infty$ sections.
+Let $p$ be the point to which the genus $1$ subcurve is contracted.
+Passing to an open neighborhood of $p$, the map to the bundle is given by a rational function $f$ on an open curve $C^\circ$, determined by the the subgraph formed by $\plC_0$ and the flags $t_i$ described in the definition above.
+To describe the tropical map to $\mathbb R_{>0}$, we observe that $\plC_0$ is contracted to a fixed point $q\in\mathbb R_{>0}$.
+The flags at the vertex bases at $t_i$ correspond to nodes or markings of $C$.
+The pole orders of $f$ at these distinguished points determine the slopes of the tropical map.
+We are now exactly in the situation considered in~\cite[Second Paragraph of Section~4.6]{RSPW2}, and Lemma~4.6.1 of loc.
+cit.
+guarantees the well-spacedness as required.
+\end{proof}
+
+\subsubsection{The cone complex} To understand the stratification via combinatorial data, we will build the straification from known objects.
+
+\noindent
+\textbf{Step 1}.
+Let $\Sigma^{\mathrm{log}}$ be the tropical moduli space of genus $1$ tropical stable maps to $\mathbb R_{\geq 0}$.
+This is naturally identified with the tropicalization (in the logarithmic sense) of the Abramovich--Chen--Gross--Siebert space of logarithmic stable maps to the pair $(\mathbb P^N,H)$.
+\\
+
+\noindent
+\textbf{Step 2}.
+Given such a tropical stable map, we may subdivide $\mathbb R_{\geq 0}$ such that the image of every vertex of $\plC$ is a vertex of $\mathbb R_{\geq 0}$.
+Call this subdivision $\widetilde{\mathbb R}_{\geq 0}$.
+The preimages of vertices of the subdivision form a subdivision of $\plC$.
+After this procedure, the vertices of $\plC$ with positive image are totally ordered in a manner extending the partial order obtained from the map to $\mathbb R_{\geq 0}$.
+The combinatorial types of such \textbf{ordered} maps produce the cones of a subdivision of $\Sigma^{\mathrm{log}}$ which we denote $\Sigma^{\mathrm{Kim}}$.\\
+
+\noindent
+\textbf{Step 3}.
+Given a tropical map $F: \plC\to \mathbb R_{\geq 0}$ parameterized by $\Sigma^{\mathrm{Kim}}$, there is a largest radius $\delta$ (possible equal to $0$) such that every vertex strictly contained in the circle of radius $\delta$ around the core is contracted to a point in $\mathbb R_{>0}$.
+Let $
+\Sigma^{\mathrm{cen}}$ be the subdivision obtained by requiring that the vertices contained with the circle of radius $\delta$ around the core of $\plC$ are totally ordered. \\
+
+\noindent
+\textbf{Step 4}. Let $
+\Sigma_{1,\alpha}(\mathbb P^N|H)$ be the subcomplex of $\Sigma^{\mathrm{cen}}$ obtained by passing to the subcomplex of $\Sigma^{\mathrm{cen}}$ that consists of well-spaced tropical maps.
+
+\begin{prop}
+The cone complex $
+\Sigma_{1,\alpha}(\mathbb P^N|H)$ is the fan of the toroidal embedding $
+\mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)$. In particular, the codimension $k$ strata of $
+\mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)$ are in inclusion reversing bijection with the dimension $k$ cones in $
+\Sigma_{1,\alpha}(\mathbb P^N|H)$.
+\end{prop}
+
+\begin{proof}
+The construction above has been given to mimic the construction of the space $
+\mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)$.
+Specifically, the fact that cone complex $\Sigma^{\mathrm{cen}}$ is the cone complex attached to the logarithmic stack $\widetilde{\mathcal{VZ}}_{1,\alpha}(\mathbb P^N|H)$ of centrally aligned maps to expansions, follows immediately from its description as a subcategory of the fibered category (over logarithmic schemes) of $\mathcal M^{\mathrm{log}}_{1,\alpha}(\mathbb P^N|H)$.
+To complete the result, we note that $
+\mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)$ has a strict map to $
+\mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)$, so its cone complex is a subcomplex of $\Sigma^{\mathrm{cen}}$.
+The fact that it must be contained in the subcomplex of well-spaced curves is immediate from Proposition~\ref{prop: well-spaced}.
+\end{proof}
+
+\subsection{Rubber variants} In our implementation of the relative theory, we will need the naturally ``rubber'' variant of the space of maps $
+\mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)$, where the entire curve is mapped into higher levels.
+
 \newpage

### 2019-03-05 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
organised everything

--- 2019-03-04 GenusOneRelativeMaps.tex
@@
 
-\title{Gromov--Witten theory of hypersurfaces in genus one}
+\title{Reduced Gromov--Witten theory of hypersurfaces in genus one}
 \author{Luca Battistella, Navid Nabijou and Dhruv Ranganathan}
@@
 
-\section{Introduction}
-
-\noindent Gromov-Witten theory in genus zero has been studied intensely using a large assortment of techniques, many of which rely crucially on the remarkable geometry of the Kontsevich space of genus zero maps to projective space.
+\section*{Introduction}
+
+\noindent Gromov--Witten theory in genus zero has been studied intensely using a large assortment of techniques, many of which rely crucially on the remarkable geometry of the Kontsevich space of genus zero maps to projective space.
 On the other hand, the higher genus spaces have uncontrollable singularities, and an entirely different set of techniques must be appealed to.
@@
 
-\subsection{Results} Our first contribution is a definition and construction of relative reduced Gromov-Witten theory of projective space relative to a hyperplane.
+\subsection{Results} Our first contribution is a definition and construction of relative reduced Gromov--Witten theory of projective space relative to a hyperplane.
 The geometric content is the following.
@@
 
-By standard virtual pullback techniques, virtual versions of our results apply for smooth ample pairs $(X,D)$.
+By standard virtual pullback techniques, virtual versions of our results apply for smooth very ample pairs $(X,Y)$.
 
@@
 
-\section{The moduli space and its deformation theory}
-
-Let $\mathfrak M_{1,n}$ be the logarithmic algebraic stack of genus $1$ $n$-pointed prestable curves.
+\part{The moduli space and its deformation theory}
+
+\section{Construction and logarithmic smoothness}
+
+\subsection{The absolute story} Let $\mathfrak M_{1,n}$ be the logarithmic algebraic stack of genus $1$ $n$-pointed prestable curves.
 Let $\plC$ be a $n$-pointed genus $1$ tropical curve.
@@
 
-\subsection{Relative geometry: factorization} Let $[C\to \mathbb P^N[s]\to \mathbb P^N]$ be a logarithmic map from a centrally aligned curve to an expansion.
+\subsection{Relative geometry: factorization}\label{subsection factorisation} Let $[C\to \mathbb P^N[s]\to \mathbb P^N]$ be a logarithmic map from a centrally aligned curve to an expansion.
 Recall that $\mathbb P^N[s]$ consists of a union of $\mathbb P^N$ with the projective bundle $\mathbb P(\mathcal O\oplus \mathcal O(1))$.
@@
 
-\subsection{Stratification} The logarithmic smoothness established in Theorem~\ref{thm: log-smoothness} implies that $\mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)$ is an orbifold toroidal embeddeding.
+\section{Stratification} The logarithmic smoothness established in Theorem~\ref{thm: log-smoothness} implies that $\mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)$ is an orbifold toroidal embeddeding.
 Consequently, the irreducible components of its boundary and their intersections form a stratification of the space.
@@
 
-\subsection{Rubber variants} In our implementation of the relative theory, we will need the naturally ``rubber'' variant of the space of maps $
+\section{Rubber variants and virtual geometry}
+
+\subsection{The rubber space} In our implementation of the relative theory, we will need the naturally ``rubber'' variant of the space of maps $
 \mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)$, where the entire curve is mapped into higher levels.
 
-\newpage
-
-\section{Gathmann's line bundle via tropical geometry} For each marking $x_k$ we consider the locus in $\VZ_{1,\alpha}(\PP^N|H)$ where $x_k$ belongs to an internal component of the collapsed map.
+\subsection{Virtual geometry for very ample pairs}
+Now let $(X,Y)$ be a smooth pair with $Y$ very ample.
+The definition given in \S \ref{subsection factorisation} applies in this setting as well, producing a moduli space $\VZ_{1,\alpha}(X|Y,\beta)$ together with a morphism
+\begin{equation*} \VZ_{1,\alpha}(X|Y,\beta) \to \ol\Mcal^{\operatorname{log}}_{1,\alpha}(X|Y,\beta)\end{equation*}
+obtained by performing a logarithmic modification and then passing to a closed substack.
+This moduli space will not in general be logarithmically smooth, but we may equip it with a virtual class as follows.
+The complete linear system $|\OO_X(Y)|$ defines an embedding $X \hookrightarrow \PP^N$ with $Y=X\cap H$ for $H$ some hyperplane.
+
+\begin{lemma} The following square is cartesian (in the category of ordinary stacks):
+\bcd
+\VZ_{1,\alpha}(X|Y,\beta) \ar[r] \ar[d] \ar[rd,phantom,"\square"] & \VZ_{1,\alpha}(\PP^N|H,d) \ar[d] \\
+\VZ_{1,n}(X,\beta) \ar[r,"i"] & \VZ_{1,n}(\PP^N,d).
+\ecd
+\end{lemma}
+\begin{proof} It is clear from the modular description that this square is cartesian in the category of fs log stacks.
+But the morphism $i$ is strict, which implies that the square is also cartesian in the category of coherent log stacks.
+Since fibre products in the latter category are compatible with the functor forgetting log structures, the claim follows.\end{proof}
+
+Since $\VZ_{1,n}(\PP^N,d)$ is smooth and $\VZ_{1,n}(X,\beta)$ carries a natural virtual class \cite[Theorem 4.4.1]{RSPW} there is a diagonal pull-back morphism \cite{Ga} \cite[Appendix C]{BattistellaNabijou}, which we use to define the virtual class on the space of maps to $(X,Y)$:
+\begin{equation*} \virt{\VZ_{1,\alpha}(X|Y,\beta)} := i_\Delta^! [\VZ_{1,\alpha}(\PP^N|H,d)]. \end{equation*}
+Since $\VZ_{1,\alpha}(X|Y,\beta)$ comes equipped with evaluation maps and cotangent line classes, we immediately arrive at a definition of reduced Gromov--Witten invariants for the pair $(X,Y)$.
+
+The recursion formula in $\VZ_{1,\alpha}(\PP^N|H,d)$ proved in \S\S \ref{}-\ref{} below immediately pulls back along $i$ to give a recursion formula in $\VZ_{1,\alpha}(X|Y,\beta)$.
+
+\part{The recursion formula and applications}
+
+\section{Gathmann's line bundle through tropical geometry} For each marking $x_k$ we consider the locus in $\VZ_{1,\alpha}(\PP^N|H)$ where $x_k$ belongs to an internal component of the collapsed map.
 We use the log structure on $\VZ_{1,\alpha}(\PP^N|H)$ to construct a line bundle $\Lcal_k$ together with a section $s_k$ vanishing along this locus.
@@
 
-\newpage
-
-\section{Quantum Lefschetz recursion}
-Consider a smooth pair $(X,Y)$ with $Y$ very ample, and let $P$ be the projective bundle $P=\PP_Y(\operatorname{N}_{Y|X} \oplus\OO_Y)$.
-We assume that the genus zero and reduced genus one Gromov--Witten theories of $X$ are known.
-From this starting data, we will apply our recursion formula to compute:
-\begin{enumerate}
-\item the genus one \textbf{reduced restricted absolute Gromov--Witten theory} of $Y$;
-\item the genus one \textbf{reduced relative Gromov--Witten theory} of the pair $(X,Y)$;
-\item the genus one \textbf{reduced rubber theory} of $P$.
-\end{enumerate}
-
-\subsection{Reduced absolute, relative and rubber invariants} To be precise: by a reduced invariant of $Y$ we mean an integral over $\VZ_{1,n}(Y,\beta)$ of products of pullbacks of evaluation and psi classes along morphisms which forget a subset $S$ of the marked points (taking $S=\emptyset$ gives the ordinary evaluation and psi classes).
-Here the evaluation maps are viewed as mapping into $X$ (hence the adjective ``restricted'').
-Reduced relative invariants of $(X,Y)$ are defined in the same way, except now the forgetful morphism maps into a space of absolute maps:
-\begin{equation*} \fgt_S \colon \VZ_{1,\alpha}(X|Y,\beta) \to \VZ_{1,m-\#S}(X,\beta).\end{equation*}
-In particular, all the psi classes which we consider are \emph{collapsed psi classes}, meaning that they are relative cotangent line classes for the corresponding collapsed stable map.
-Note that, unlike in the absolute case, in the relative case it may well be the case that the entire insertion is pulled back along a single forgetful map $\fgt_S$.
-The reduced rubber invariants of $P$ are defined similarly (again using collapsed psi classes).
-
-The systems of invariants defined above are equivalent to the classical systems of invariants (which do not use forgetful morphisms) by well-known topological recursion relations.
-
-\subsection{Fictitious and true markings} The recursion procedure is rather delicate.
-Roughly speaking, we will induct on the degree (meaning $Y\cdot\beta$), number of marked points and total tangency.
-To get the correct notion of number of markings and total tangency in  the relative setting, we introduce the concept of \textbf{fictitious markings}.
-Consider a moduli space $\VZ_{1,\alpha}(X|Y,\beta)$ of reduced relative stable maps and a corresponding integrand $\gamma$.
-We let $F \subseteq \{1,\ldots,m\}$ be the maximal subset of marked points such that:
-\begin{enumerate}
-\item $\alpha_i = 1$ for all $i \in F$;
-\item the entire integrand $\gamma$ is pulled back along $\fgt_F$.
-\end{enumerate}
-This subset is uniquely determined, and its elements are referred to as \textbf{fictitious markings}.
-Markings which are not fictitious are referred to as \textbf{true}.
-When inducting on relative invariants we will always be interested in the number of true markings (as opposed to the total number of markings) and the true tangency
-\begin{equation*} \sum_{i \not\in F} \alpha_i \leq d=Y\cdot \beta \end{equation*}
-as opposed to the total tangency, which is always $d$.
-This formalises the idea that relative invariants with non-maximal tangency $t<d$ can be obtained by adding $d-t$ fictitious markings of tangency $1$; see \cite[Lemma 1.15(i)]{Ga}.
-
-\subsection{Structure of the recursion} Given the genus-zero Gromov--Witten theory of $X$, the arguments of \cite{Ga} give an effective algorithm to reconstruct the genus-zero theories of $Y$ and $(X,Y)$; moreover, the genus-zero rubber theory of $P$ is identical to the genus-zero theory of $Y$ \cite{GathmannThesis}.
-Thus we may assume that all genus-zero data is known.
-We assume in addition that we know the genus one reduced theory of $X$.
-The structure of the recursion is then as follows:
-
-\begin{algorithm}
-\DontPrintSemicolon
-\For{$d \geq 0$}{
-\For{$n \geq 0$}{
-\For{$t \geq 0$\medskip}{
-\textbf{\, Step 1: } Compute forgetful relative invariants of $(X,Y)$ (degree~$d$, $n+1$ true markings, true tangency $t$); see below.
-}
-\medskip \textbf{Step 2: } Compute absolute invariants of $Y$ (degree $d$, $n$ markings).\;
-\For{$t \geq 0$\medskip}{
-\textbf{\, Step 3: } Compute relative invariants of $(X,Y)$ (degree $d$, $n$ true markings, true tangency $t$).\;
-}
-}
-\For{$n \geq 0$\medskip}{
-\For{$m \geq 0$\medskip}{
-\textbf{\, Step 4: } Compute rubber invariants of $P$ (degree $d$, $n$ relative markings, $m$ non-relative markings).
-}
-}
-}
-\end{algorithm}
-\noindent Although the loops involving $d, n$ and $m$ have infinite length, in order to compute any single invariant it is only necessarily to iterate the preceding loops for a finite amount of time.
-A \textbf{forgetful relative invariant} of $(X,Y)$ is by definition a reduced relative invariant with a marked point $x_0$ such that all of the insertions are pulled back along $\fgt_{x_0}$.
-In our recursion, we first deal with this special class of relative invariants (with $n+1$ true markings), before computing the absolute invariants (with $n$ markings) and then returning to compute all of the relative invariants (with $n$ true markings).
-This need to treat separately a particular subclass of the relative invariants is an inescapable feature of the genus one recursion.
-
-The base terms of the recursion all have $d=0$ and as such are easy to compute: the relative invariants of $(X,Y)$ are nothing but absolute invariants of $X$, the absolute invariants of $Y$ are given by obstruction bundle integrals over Deligne--Mumford spaces, and the  rubber invariants of $P$ are also given by integrals over Deligne--Mumford spaces, using the formula for the double ramification cycle \cite{Hain,JPPZ} in terms of tautological classes.
-We will now explain how to perform each of the four inductive steps outlined above.
-
-\begin{notation}Given tuples $\mathbf{a}=(a_1,\ldots,a_n)$ and $\mathbf{b}=(b_1,\ldots,b_n)$, we say that $\mathbf{a}<\mathbf{b}$ if there exists an $i \in \{1,\ldots,n\}$ such that $a_j = b_j$ for $j < i$ and $a_i < b_i$.\end{notation}
-
-\subsection*{Step 1} Suppose we are given a forgetful relative invariant to compute.
-That is, we have a relative space $\VZ_{1,\alpha}(X|Y,\beta)$ of degree $d$, with $n+1$ true markings and true tangency $t$, and a marking $x_0$ such that the insertion $\gamma$ is pulled back along $\fgt_{x_0}$.
-We assume inductively that every absolute, relative and rubber invariant with $(d^\prime,n^\prime) < (d,n)$ is known, and also that every forgetful relative invariant with $(d^\prime,n^\prime,t^\prime) < (d,n+1,t)$ is known.
-Choose a true marking $x_1$ with $\alpha_1 \geq 1$ and consider the space:
-\begin{equation*} \VZ_{1,(\alpha-e_1) \cup (1)}(X|Y,\beta). \end{equation*}
-Denote the newly-introduced marking by $y$ and consider the integrand $\tilde\gamma$ obtained from $\gamma$ by introducing $\fgt_y^\st$ everywhere. Applying our recursion formula to $x_1$, we obtain:
-\begin{equation}\label{step 1 recursion}\left( (\alpha_1-1)\psi_1 + \ev_1^\st Y\right) \tilde\gamma \cap [\VZ_{1,(\alpha-e_1) \cup (1)}(X|Y,\beta)] = \tilde\gamma \cap [\Dcal(1)].\end{equation}
-Let us first examine the left-hand side.
-The class $\psi_1$ differs from $\fgt_y^\st \psi_1$ by the locus where $x_1$ and $y$ are contained on a contracted rational bubble.
-This locus consists of reduced relative stable maps of the form \medskip
-
-\begin{center}
-\begin{tikzpicture}[scale=1]
-%edge
-\draw (0,0) to (2,0);
-\draw [color=blue] (1,0) node[above]{\tiny$\alpha_1$};
-
-%C_1
-\draw [fill=white] (0,0) circle[radius=3pt];
-\draw (0,-0.1) node[below]{\small$d$};
-\draw (0,0) node[above]{\small$\sqC_1$};
-
-%C_0
-\draw [fill=black] (2,0) circle[radius=3pt];
-\draw (2,-0.1) node[below]{\small$0$};
-\draw (2,0) node[above]{\small$\sqC_0$};
-
-%x_1
-\draw [->] (2,0.1) -- (4,0.1);
-\draw (3.9,0.1) node[above]{\small$x_1$};
-\draw [color=blue](3,0.1) node[above]{\tiny$\alpha_1-1$};
-
-%y
-\draw [->] (2,-0.1) -- (4,-0.1);
-\draw (3.9,-0.1) node[below]{\small$y$};
-\draw [color=blue] (3,-0.1) node[below]{\tiny$1$};
-
-%down arrow
-\draw [color=blue,->] (1,-0.3) -- (1,-0.7);
-
-%target
-\draw [color=blue,->] (0,-1) to (2,-1);
-\draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
-\draw [color=blue] (2,-1) node[right]{\small$\Sigma(X|Y)$};
-\end{tikzpicture}
-\end{center}
-% Algebro-geometric picture; replaced by tropical picture.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{comment}
-\begin{center}
-\begin{tikzpicture}[scale=1.5]
-%Draw target
-\draw (0,0) -- (3,0) -- (3,2) -- (0,2) -- (0,0);
-\draw (3,0) -- (6,0) -- (6,2) -- (3,2) -- (3,0);
-
-%Draw genus one curve on left-hand side
-\draw [blue] (3,0.5) to [out=90,in=270] (2.7,1) to [out=90,in=270] (3,1.5) to [out=90,in=0] (1,1.7) to [out=180,in=90] (0.5,1) to [out=270,in=180] (1,0.3) to [out=0,in=270] (3,0.5);
-\draw [blue] (1.1,0.9) to [out=40, in=180] (1.4,1.1) to [out=0,in=140] (1.7,0.9);
-\draw [blue] (1.2,1) to [out=300, in=180] (1.4,0.9) to [out=0,in=240] (1.6,1);
-
-%Draw nodal blobs
-\draw [fill=blue,color=blue] (3,0.5) circle[radius=1pt];
-\draw [color=blue] (3,0.5) node[left]{\small$\alpha_2$};
-\draw [fill=blue,color=blue] (3,1.5) circle[radius=1pt];
-\draw [color=blue] (3,1.5) node[left]{\small$\alpha_1$};
-%Draw rational bubble with x_1 and y
-\draw [blue] (3,1.5) to [out=70,in=190] (5.5,1.9) to [out=0,in=90] (6,1.8) to [out=270,in=90] (5.75,1.5) to [out=270,in=90] (6,1.2) to [out=270,in=10] (5.5,1.1) to [out=180,in=290] (3,1.5);
-
-%Draw right-hand markings
-\draw [fill=blue,color=blue] (6,1.8) circle[radius=1pt];
-\draw [color=blue] (6,1.8) node[left]{\small{$\alpha_1-1$}};
-\draw (6,1.8) node[right]{$x_1$};
-\draw [fill=blue,color=blue] (6,1.2) circle[radius=1pt];
-\draw [color=blue] (6,1.2) node[left]{\small{$1$}};
-\draw (6,1.2) node[right]{$y$};
-
-%Draw ldots
-\draw [color=blue] (4,0.5) node[right]{$\ldots$};
-\end{tikzpicture}
-\end{center}
-\end{comment}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-with all other marked points contained on $\sqC_1$.
-This is isomorphic to $\VZ_{1,\alpha}(X|Y,\beta)$ and when we restrict $\tilde\gamma$ to this locus we obtain precisely the class $\gamma$ which we started with.
-Thus the left-hand side of \eqref{step 1 recursion} may be written as
-\begin{equation*} (\alpha_1-1) I + \fgt_y^\st \left( (\alpha_1-1)\psi_1 + \ev_1^\st Y\right)  \tilde\gamma \cap [\VZ_{1,(\alpha-e_1)\cup(1)}(X|Y,\beta)]\end{equation*}
-where $I$ is the invariant we are trying to compute.
-The second term is a forgetful relative invariant with the same degree and number of true markings (since $y$ is fictitious), and strictly smaller true tangency; hence it is recursively known.
-We now examine the right-hand side of \eqref{step 1 recursion}.
-Recall that all of the genus zero data has already been computed, so we only need to focus on the genus one pieces.
-First consider the type $A$ loci.
-The genus one piece has strictly smaller degree (and hence is recursively known) exept in the following situation (with some stable distribution of the remaining markings):
-\begin{center}
-\begin{tikzpicture}[scale=1]
-\draw (0,0) to (2,0);
-\draw [fill=white] (0,0) circle[radius=3pt];
-\draw (0,-0.1) node[below]{\small$d$};
-\draw (0,0) node[above]{\small$\sqC_1$};
-\draw [fill=black] (2,0) circle[radius=3pt];
-\draw (2,-0.1) node[below]{\small$0$};
-\draw (2,0) node[above]{\small$\sqC_0$};
-\draw [->] (2,0) -- (3,0);
-\draw (2.9,0) node[right]{$x_1$};
-
-\draw [color=blue,->] (1,-0.3) -- (1,-0.7);
-
-\draw [color=blue,->] (0,-1) to (2,-1);
-\draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
-\draw [color=blue] (2,-1) node[right]{\small$\Sigma(X|Y)$};
-\end{tikzpicture}
-\end{center}
-In this situation, $C_1$ contains at most $n+1$ true markings.
-If it has $n-1$ or fewer, than it is known recursively.
-If it has exactly $n$ this means that $C_0$ contains exactly one true marking (besides $x_1$, which may be true or fictitious).
-We claim that in this situation we must have $y \in C_1$, since otherwise we would have a moduli space for $C_0$ given by $\ol\Mcal_{0,k}$ with $k \geq 4$, and  applying the projection formula with $\fgt_y$ we would conclude that the contribution is zero.
-Thus we have $y \in C_1$, and so the genus one contribution is a forgetful relative invariant with $n$ true markings, and hence is recursively known.
-
-Finally, if $C_1$ contains exactly $n+1$ true markings, then the only additional markings on $C_0$ are fictitious, and by the same argument as in the previous paragraph there can only be one.
-Thus for each fictitious marked point we obtain a locus isomorphic to $\VZ_{1,\alpha}(X|Y,\beta)$ and $\tilde\gamma$ restricts to $\gamma$ here (from the point of view of computing invariants, the fictitious marked points are indistinguishable, meaning that the contributions are all the same).
-Thus for each fictitious marked point (of which there is at least one, namely $y$) we get a contribution of $\alpha_1 I$ to the right-hand side of \eqref{step 1 recursion}.
-
-The contributions of the type $B$ loci only involve genus zero data and hence are known.
-The contributions of the type $C^0$ loci are determined by genus zero data and tautological integrals on Deligne--Mumford space, hence are also known.
-It remains to consider type $C^+$ loci.
-If the degree of the genus one piece is less than $d$ then we have a rubber invariant of strictly smaller degree.
-The only other possibility is that the entire curve is mapped into the divisor.
-In this case we may apply the projection formula with $\fgt_y$ to identify this with an integral over $\VZ_{1,m}(Y,\beta)$ for some (possibly large) number $m$ of marked points.
-But by assumption there is another marked point $x_0$ with all of the insertions pulled back along $\fgt_{x_0}$, so a further application of the projection formula shows that this contribution vanishes.
-To conclude, we may rearrange \eqref{step 1 recursion} to obtain an expression of the form
-\begin{equation*} \lambda I = \text{recursively known terms} \end{equation*}
-where $\lambda$ is an explicit scalar which is always nonzero; we have thus determined $I$, which completes Step 1.
-
-\subsection*{Step 2} Consider now the absolute space $\VZ_{1,n}(Y,\beta)$ with an insertion $\gamma$, and suppose inductively that we have computed all forgetful relative invariants with $(d^\prime,n^\prime) \leq (d,n+1)$, all relative invariants and absolute invariants with $(d^\prime,n^\prime) < (d,n)$, and all special rubber invariants with $d^\prime < d$.
-Consider the following moduli space with $n+1$ markings:
-\begin{equation*} \VZ_{1,(d,0,\ldots,0)}(X|Y,\beta). \end{equation*}
-Let $x_0$ denote the relative marking and consider the integrand $\tilde\gamma$ obtained from $\gamma$ by introducing $\fgt^\st_{x_0}$ everywhere. Now recurse at $x_1$ to obtain:
-\begin{equation}\label{step 2 recursion} \ev_1^\st Y \cdot \tilde\gamma \cap [\VZ_{1,(d,0,\ldots,0)}(X|Y,\beta)] = \tilde\gamma\cap[\Dcal(1)].\end{equation}
-The left-hand side is a forgetful relative invariant of degree $d$ and $\leq n+1$ true markings, and so has already been computed.
-For the right-hand side, let us begin with loci of type $A$.
-The genus one contributions from each loci have $(d^\prime,n^\prime) < (d,n)$ except in the following case
-\begin{center}
-\begin{tikzpicture}[scale=1]
-%edge
-\draw (0,0) to (2,0);
-\draw [color=blue] (1,0) node[above]{\tiny$d$};
-
-%C_1
-\draw [fill=white] (0,0) circle[radius=3pt];
-\draw (0,-0.1) node[below]{\small$d$};
-\draw (0,0) node[above]{\small$\sqC_1$};
-
-%C_0
-\draw [fill=black] (2,0) circle[radius=3pt];
-\draw (2,-0.1) node[below]{\small$0$};
-\draw (2,0) node[above]{\small$\sqC_0$};
-
-%x_1
-\draw [->] (2,0.1) -- (4,0.1);
-\draw (3.9,0.1) node[above]{\small$x_1$};
-\draw [color=blue](3,0.1) node[above]{\tiny$0$};
-
-%y
-\draw [->] (2,-0.1) -- (4,-0.1);
-\draw (3.9,-0.1) node[below]{\small$x_0$};
-\draw [color=blue] (3,-0.1) node[below]{\tiny$d$};
-
-%down arrow
-\draw [color=blue,->] (1,-0.3) -- (1,-0.7);
-
-%target
-\draw [color=blue,->] (0,-1) to (2,-1);
-\draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
-\draw [color=blue] (2,-1) node[right]{\small$\Sigma(X|Y)$};
-\end{tikzpicture}
-\end{center}
-which gives a contribution of
-\begin{equation*} d\cdot \gamma \cap [\VZ_{1,(d,\underbrace{0,\ldots,0}_{n-1})}(X|Y,\beta)] \footnote{(Navid) Fix formatting}\end{equation*}
-to the right-hand side of \eqref{step 2 recursion}.
-Here $\gamma$ is the insertion we started with; the difference is that we are now considering relative maps to $(X,Y)$ with maximal tangency at $x_1$, rather than absolute maps to $Y$.
-The type $B$ and $C^0$ loci are recursively determined as in Step~1, and similarly the type $C^+$ loci are recursively determined except for the locus where the entire curve is mapped into the divisor.
-On this locus we may apply $\fgt_{x_0}$ and identify the contribution with
-\begin{equation*} d^2 \cdot \gamma \cap [\VZ_{1,n}(Y,\beta)] = d^2 \cdot I \end{equation*}
-where $I$ is the invariant we are trying to compute. Putting this all together, we obtain
-\begin{equation}\label{step 2 recursion 2} I = (-\gamma/d) \cap [\VZ_{1,(d,\underbrace{0,\ldots,0}_{n-1})}(X|Y,\beta)] + \text{recursively known terms} \end{equation}
-where on the right-hand side there are $n-1$ non-relative markings $x_2,\ldots,x_n$, and a relative marking $x_1$. We now apply the recursion again to the right-hand side, by considering the space
-\begin{equation*} \VZ_{1,(d-1,1,0,\ldots,0)}(X|Y,\beta) \end{equation*}
-where $x_1$ now has tangency $d-1$ and we have introduced a new marking $y$ with tangency $1$.
-We consider a new insertion, denoted $\tilde\gamma$ as usual, by introducing $\fgt_y^\st$ everywhere.
-Recursing at $x_1$ we obtain:
-\begin{equation}\label{step 2 recursion 2} \left( (d-1)\psi_1 + \ev_1^\st Y \right)\cdot(-\tilde\gamma/d) \cap [\VZ_{1,(d-1,1,0,\ldots,0)}(X|Y,\beta)] = (-\tilde\gamma/d) \cap [\Dcal(1)].\end{equation}
-The difference between $\psi_1$ and $\fgt_y^\st \psi_1$ is given by the locus where $x_1$ and $y$ belong to a collapsed rational bubble:
-\begin{center}
-\begin{tikzpicture}[scale=1]
-%edge
-\draw (0,0) to (2,0);
-\draw [color=blue] (1,0) node[above]{\tiny$d$};
-
-%C_1
-\draw [fill=white] (0,0) circle[radius=3pt];
-\draw (0,-0.1) node[below]{\small$d$};
-\draw (0,0) node[above]{\small$\sqC_1$};
-
-%C_0
-\draw [fill=black] (2,0) circle[radius=3pt];
-\draw (2,-0.1) node[below]{\small$0$};
-\draw (2,0) node[above]{\small$\sqC_0$};
-
-%x_1
-\draw [->] (2,0.1) -- (4,0.1);
-\draw (3.9,0.1) node[above]{\small$y$};
-\draw [color=blue](3,0.1) node[above]{\tiny$1$};
-
-%y
-\draw [->] (2,-0.1) -- (4,-0.1);
-\draw (3.9,-0.1) node[below]{\small$x_1$};
-\draw [color=blue] (3,-0.1) node[below]{\tiny$d-1$};
-
-%down arrow
-\draw [color=blue,->] (1,-0.3) -- (1,-0.7);
-
-%target
-\draw [color=blue,->] (0,-1) to (2,-1);
-\draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
-\draw [color=blue] (2,-1) node[right]{\small$\Sigma(X|Y)$};
-\end{tikzpicture}
-\end{center}
-The contribution of this locus to the left-hand side of \eqref{step 2 recursion 2} is:
-\begin{equation*} (d-1)\cdot(-\gamma/d) \cap [\VZ_{1,(d,\underbrace{0,\ldots,0}_{n-1})}(X|Y,\beta)].\end{equation*}
-What remains on the left-hand side is a forgetful relative invariant of degree $d$ and $\leq n+1$ true markings ($y$ being the ``forgetful'' marking), hence is recursively known.
-On the right-hand side, the type $A$ loci are recursively known except possibly in the following special cases (with some stable distribution of the remaining non-relative markings):
-\begin{center}
-\begin{minipage}{0.4\textwidth}
-\begin{tikzpicture}[scale=1]
-%edge
-\draw (0,-0.1) to (2,-0.1);
-\draw [color=blue] (1,-0.1) node[below]{\tiny$d-1$};
-
-%C_1
-\draw [fill=white] (0,0) circle[radius=3pt];
-\draw (0,-0.1) node[below]{\small$d$};
-\draw (0,0) node[above]{\small$\sqC_1$};
-
-%C_0
-\draw [fill=black] (2,0) circle[radius=3pt];
-\draw (2,-0.1) node[below]{\small$0$};
-\draw (2,0) node[above]{\small$\sqC_0$};
-
-%x_1
-\draw [->] (0,0.1) -- (1.5,0.1);
-\draw (1.5,0.1) node[above]{\small$y$};
-\draw [color=blue](0.75,0.1) node[above]{\tiny$1$};
-
-%y
-\draw [->] (2,0) -- (4,0);
-\draw (3.9,0) node[below]{\small$x_1$};
-\draw [color=blue] (3,0) node[below]{\tiny$d-1$};
-
-%down arrow
-\draw [color=blue,->] (1,-0.5) -- (1,-0.9);
-
-%target
-\draw [color=blue,->] (0,-1) to (2,-1);
-\draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
-\draw [color=blue] (2,-1) node[right]{\small$\Sigma(X|Y)$};
-
-\draw (2,-1.3) node[below]{\small{Case 1}};
-\end{tikzpicture}
-\end{minipage}
-\begin{minipage}{0.4\textwidth}
-\begin{tikzpicture}[scale=1]
-%edge
-\draw (0,0) to (2,0);
-\draw [color=blue] (1,0) node[above]{\tiny$d$};
-
-%C_1
-\draw [fill=white] (0,0) circle[radius=3pt];
-\draw (0,-0.1) node[below]{\small$d$};
-\draw (0,0) node[above]{\small$\sqC_1$};
-
-%C_0
-\draw [fill=black] (2,0) circle[radius=3pt];
-\draw (2,-0.1) node[below]{\small$0$};
-\draw (2,0) node[above]{\small$\sqC_0$};
-
-%x_1
-\draw [->] (2,0.1) -- (4,0.1);
-\draw (3.9,0.1) node[above]{\small$y$};
-\draw [color=blue](3,0.1) node[above]{\tiny$1$};
-
-%y
-\draw [->] (2,-0.1) -- (4,-0.1);
-\draw (3.9,-0.1) node[below]{\small$x_1$};
-\draw [color=blue] (3,-0.1) node[below]{\tiny$d-1$};
-
-%down arrow
-\draw [color=blue,->] (1,-0.3) -- (1,-0.7);
-
-%target
-\draw [color=blue,->] (0,-1) to (2,-1);
-\draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
-\draw [color=blue] (2,-1) node[right]{\small$\Sigma(X|Y)$};
-
-\draw (2,-1.3) node[below]{\small{Case 2}};
-\end{tikzpicture}
-\end{minipage}
-\end{center}
-In Case 1 the contribution from $C_1$ is a forgetful relative invariant with $\leq n$ true markings, hence is recursively known.
-In Case 2, we first note that there cannot be any more markings on $C_0$ (since otherwise we could apply $\fgt_y$ and conclude that the contribution vanishes).
-Thus we obtain a single locus, which contributes precisely
-\begin{equation*} d\cdot(-\gamma/d) \cap [\VZ_{1,(d,\underbrace{0,\ldots,0}_{n-1})}(X|Y,\beta)] = -\gamma\cap[\VZ_{1,(d,\underbrace{0,\ldots,0}_{n-1})}(X|Y,\beta)]\end{equation*}
-which gives us the first term on the right-hand side of \eqref{step 2 recursion 2}.
-As usual the type $B$ and $C^0$ contributions are known recursively, and the only type $C^+$ contribution not known recursively occurs when the entire curve is mapped into the divisor, in which case we apply $\fgt_y$ to calculate the contribution as:
-\begin{equation*} (-\gamma/d) \cap [\VZ_{1,n}(Y,\beta)] = -I/d.\end{equation*}
-Substituting into \eqref{step 2 recursion 2} we end up with
-\begin{equation*} I(1-d^{-1}) = \text{recursively known terms} \end{equation*}
-which completes the recursion step as long as $d \neq 1$.
-But since $\VZ_{1,n}(H,1)=\emptyset$ it follows that $\VZ_{1,n}(Y,\beta)=\emptyset$ if $d=Y\cdot\beta=1$, so we may always assume $d \geq 2$ in the recursion.
-
-\subsection*{Step 3} Now suppose we are given a relative space $\VZ_{1,\alpha}(X|Y,\beta)$ with an insertion $\gamma$, and suppose inductively that we have computed all forgetful relative invariants with $(d^\prime,n^\prime) \leq (d,n+1)$, all absolute invariants with $(d^\prime,n^\prime) \leq (d,n)$, all relative invariants with $(d^\prime,n^\prime,t^\prime)<(d,n,t)$ and all rubber invariants with $d^\prime < d$.
-Choose a true marking $x_1$ with $\alpha_1 \geq 1$ and consider the moduli space
-\begin{equation*} \VZ_{1,(\alpha-e_1)\cup(1)}(X|Y,\beta) \end{equation*}
-where $y$ is the newly-introduced marking. As usual consider the insertion $\tilde\gamma$ obtained from $\gamma$ by introducing $\fgt_y$ everywhere. Recursing at $x_1$ we obtain:
-\begin{equation*} \left( (\alpha_1-1)\psi_1 + \ev_1^\st H\right) \tilde\gamma \cap [\VZ_{1,(\alpha-e_1)\cup(1)}(X|Y,\beta)] = \tilde\gamma \cap [\Dcal(1)].\end{equation*}
-The left-hand side is a relative invariant with the same degree and number of true markings, but smaller true tangency: hence it is recursively known.
-On the right-hand side, the type $A$ contributions are recursively known except for those of the following form
-
-\begin{center}
-\begin{tikzpicture}[scale=1]
-\draw (0,0) to (2,0);
-\draw [color=blue] (1,-0.05) node[above]{\tiny$\alpha_1$};
-\draw [fill=white] (0,0) circle[radius=3pt];
-\draw (0,-0.1) node[below]{\small$d$};
-\draw (0,0) node[above]{\small$\sqC_1$};
-\draw [fill=black] (2,0) circle[radius=3pt];
-\draw (2,-0.1) node[below]{\small$0$};
-\draw (2,0) node[above]{\small$\sqC_0$};
-\draw [->] (2,0) -- (4,0);
-\draw (3.9,0) node[right]{$x_1$};
-\draw [color=blue] (3,-0.05) node[above]{\tiny$\alpha_1-1$};
-
-\draw [color=blue,->] (1,-0.3) -- (1,-0.7);
-
-\draw [color=blue,->] (0,-1) to (2,-1);
-\draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
-\draw [color=blue] (2,-1) node[right]{\small$\Sigma(X|Y)$};
-\end{tikzpicture}
-\end{center}
-where $C_0$ contains a single fictitious marking (if it had multiple fictitious markings then the contribution would vanish by projection formula) and all the other markings are on $C_1$.
-Thus for each fictitious marking we get a contribution of $\alpha_1 I$ where $I$ is the invariant we are trying to compute.
-Note that $\alpha_1 \neq 0$, and that this term appears at least once since $y$ is a fictitious marking; so we get a nonzero multiple of $I$.
-
-As usual the type $B$ and $C^0$ contributions are recursively known.
-The type $C^+$ contributions are determined by lower-degree rubber invariants, except for when the whole curve is mapped into $Y$; however in this case we may apply $\fgt_y$ to identify the contribution with an absolute invariant of $Y$ with degree $d$ and $n$ markings, which is also recursively known.
-Thus we have determined the invariant $I$.
-
-\subsection*{Step 4} Finally, consider a rubber space $\VZ_{1,\alpha}(P|Y_0+Y_\infty,\beta)_{\Gm}$ with insertion $\gamma$.
-Suppose inductively that we have computed all absolute and relative invariants with $d^\prime \leq d$ and all rubber invariants with $(d^\prime,n^\prime,m^\prime) < (d,n,m)$.
-
-We first note the following important reduction: if there exists a relative marking $x_k$ such that all insertions are pulled back along $\fgt_{k}$, then we may apply the projection formula, together with the fact that
-\begin{equation*} (\fgt_{k})_\st [\VZ_{1,\alpha}(P|Y_0+Y_\infty,\beta)_{\Gm}] = \alpha_k^2 \cdot [\VZ_{1,n+m-1}(Y,\beta)] \end{equation*}
-to identify the rubber invariant with a multiple of a reduced invariant of $Y$, which has the same degree and hence is known recursively.
-
-We will deal with the general case by reducing to the one above. Consider the moduli space
-\begin{equation*}\label{step 4 recursion space} \VZ_{1,\alpha\cup (0)}(P|Y_0+Y_\infty,\beta)_{\Gm}\end{equation*}
-obtained by introducing a marked point $y$ with no tangency.
-Let $x_1$ be a positive-tangency marking (such a marking always exists since $d \geq 2$) and let $\tilde\gamma$ be the insertion obtained from $\gamma$ by replacing $\ev_1$ and $\psi_1$ by $\ev_y$ and $\psi_y$, and then introducing $\fgt_{1}^\st$ everywhere.
-
-We will make use of a recursion formula for rubber spaces analogous to the recursion formula for relative spaces used in Steps 1--3.
-Following \cite{EKatz}, there is a line bundle $L_y^{\not\in \operatorname{bot}}$ on $\VZ_{1,\alpha\cup (0)}(P|Y_0+Y_\infty,\beta)_{\Gm}$, together with a section $s_y^{\not\in\operatorname{bot}}$ whose vanishing locus consists of the locus $\Dcal(y)$ of rubber maps where $y$ is not mapped into the bottom level of the expanded target.
-As in \S \ref{}, we can give a logarithmic interpretation of this: it corresponds to the piecewise-linear function on the tropical moduli space which associates, to every rubber tropical map, the distance between $\varphi(\sqC_y)$ and the leftmost vertex of the tropical target, where $\sqC_y$ is the vertex of the source curve containing the flag corresponding to $y$.
-Using this tropical description, we may easily calculate the vanshing orders of $s_y^{\not\in\operatorname{bot}}$ along the various components of $\Dcal(y)$, and show that $\cchern_1(L_y^{\not\in\operatorname{bot}}) = \Psi_0 - \ev_y^\st Y$ (see also \cite{EKatzLB}, where similar results in the non-reduced setting are obtained, using different methods).
-From this, we obtain a rubber recursion formula
-\begin{equation}\label{step 4 recursion} (\Psi_0 - \ev_y^\st Y) \tilde\gamma \cap [\VZ_{1,\alpha\cup(0)}(P|Y_0+Y_\infty,\beta)_{\Gm}] = \tilde\gamma \cap [\Dcal(y)]\end{equation}
-where the fundamental class $[\Dcal(y)]$ is weighted by vanishing orders on the components.
-We will first show that the left-hand side is recursively known.
-By construction the class $\tilde\gamma$ is pulled back via $\fgt_{1}^\st$, and the same is true for $\ev_y^\st Y$.
-It remains to examine $\Psi_0$.
-If there exists a negative-tangency marking $x_2$, then we have \cite[Construction 5.1.17]{GathmannThesis}
-\begin{equation*}\label{Psi0 formula} \Psi_0 = -\alpha_2 \hat\psi_2 - \ev_2^\st Y \end{equation*}
-where $\hat\psi_2$ is a \emph{non-collapsed} psi class.
-(If there are no negative-tangency markings, then the construction given in \cite[\S 1.5.2]{MaulikPandharipande} shows that $\Psi_0=0$.) Now, $\hat\psi_2 - \psi_2$ is given by the loci where $x_2$ belongs to a trivial bubble.
-This entails a splitting of the curve into pieces, each of which contributes a rubber integral.
-Typically each of these pieces will have $(g^\prime,d^\prime,n^\prime,m^\prime) < (1,d,n,m)$ and hence be recursively known.
-The one exception is when all of the genus and degree is concentrated on the top level of the expansion, with the bottom level containing only a single non-relative marking in addition to all the negative-tangency markings.
-But in this case the contribution is a rubber invariant where all of the insertions are pulled back via $\fgt_1^\st$, and hence we may apply the projection formula to identify this with an absolute invariant of $Y$ which is recursively known.
-We conclude that, up to recursively knwon terms, we may replace $\hat\psi_2$ by $\psi_2$ in the left-hand side of \eqref{step 4 recursion}.
-If we now compare $\psi_2$ with $\fgt_1^\st \psi_2$ we see that the difference is given by the locus where $x_1$ and $x_2$ belong to a collapsed rational piece.
-The contribution of this locus consists of rubber invariant with strictly fewer relative markings, and hence is recursively known.
-So up to recursively-known terms \eqref{step 4 recursion} becomes
-\begin{equation*} \fgt_1^\st (-\alpha_2\psi_2 - \ev_y^\st Y)\tilde\gamma \cap [\VZ_{1,\alpha\cup(0)}(P|Y_0+Y_\infty,\beta)_{\Gm}] = \tilde\gamma\cap[\Dcal(y)]\end{equation*}
-and now the left-hand side is also recursively known, by the projection formula.
-Let us now examine the right-hand side.
-The components of $\Dcal(y)$ are indexed by splittings of the curve, and certainly the contributions are recursively known unless there is a piece of the curve carrying all of the genus and degree, so we may restrict to examining these contributions.
-
-Let us denote the piece of the curve carrying all of the genus and degree by $C^\prime\subseteq C$.
-If $C^\prime$ is mapped to top level, then either it contains $x_1$, in which case we apply $\fgt_1$ to compute the contribution, or it does not contains $x_1$, in which case it has fewer than $n$ relative markings and is known recursively.
-If on the other hand $C^\prime$ is not mapped to top level, then generically it is mapped to the bottom level (since generically the circuit is not contracted on this locus, so the desingularisation process does nothing).
-One possible contribution is given by the following locus
-\begin{center}
-\begin{tikzpicture}[scale=1]
-%edge
-\draw (0,0) to (2,0);
-\draw [color=blue] (1,0) node[below]{\tiny$\alpha_1$};
-
-%C_1
-\draw [fill=white] (0,0) circle[radius=3pt];
-\draw (0,-0.1) node[below]{\small$d$};
-
-%y
-\draw [->] (2,0) -- (2,1);
-\draw (2,0.9) node[left]{$y$};
-\draw [color=blue] (2,0.5) node[right]{\tiny$0$};
-
-%x_1
-\draw [->] (2,0) -- (3,0);
-\draw (3,0) node[right]{$x_1$};
-\draw [color=blue] (2.5,0) node[below]{\tiny$\alpha_1$};
-
-%C_0
-\draw [fill=black] (2,0) circle[radius=3pt];
-\draw (2,-0.1) node[below]{\small$0$};
-
-%down arrow
-\draw [color=blue,->] (1,-0.5) -- (1,-0.9);
-
-%target
-\draw [color=blue] (0,-1) to (2,-1);
-\draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
-\draw [fill=blue,color=blue] (2,-1) circle[radius=3pt];
-\draw [color=blue,->] (2,-1) -- (3,-1);
-\draw [color=blue,->] (0,-1) -- (-1,-1);
-\end{tikzpicture}
-\end{center}
-which contributes a nonzero multiple of the invariant $I$ we are trying to compute.
-For the other possibilities, first note that, unless every component at the top level contains a single positive-tangency marking and a single node (together with possibly some tangency-zero markings), then $C^\prime$ has fewer than $n$ relative markings and hence the contribution is known recursively.
-On the other hand, if any non-relative marking other than $y$ is mapped to the top level, $C^\prime$ has $\leq n$ relative markings and less than $m$ non-relative markings, and hence again the contribution is known recursively.
-The only remaining possibilities are when $x_1$ is replaced by another positive-tangency marking $x_k$ in the above picture; but then the contribution can be calculated by applying the projection formula to $\fgt_{1}$.
-We therefore conclude that the only contribution to the right-hand side of \eqref{step 4 recursion} which is not known recursively is a nonzero multiple of the invariant we were trying to compute.
-This completes the recursion step.
-
-\newpage
-
-\section{Description of the logarithmic strata}
-\noindent Let $\VZ = \VZ_{1,\alpha}(\PP^N|H,d)$ and let $\Acal$ denote the Artin fan of $\VZ$. Since the map of log stacks
-\begin{equation*} \VZ \to \Acal \end{equation*}
-is smooth, we see that the codimension-$k$ logarithmic strata in $\VZ$ are in bijective correspondence (via pull-back) with the codimension-$k$ logarithmic strata in $\Acal$.
-The logarithmic strata in $\Acal$, on the other hand, have a purely combinatorial description (at least locally) in terms of the associated moduli spaces of tropical maps, coming from the fact that $\VZ$ is a logarithmic blow-up of the usual moduli space of log stable maps.
-In this section we discuss this circle of ideas, and show how it plays out in a number of examples.
-
-\subsection{Blowing up the Artin fan}
-Let $\Mcal = \ol{\Mcal}^{\op{log}}_{1,\alpha}(\PP^N|H,d)$ denote the Abramovich--Chen--Gross--Siebert moduli space of log stable maps.
-Recall that $\VZ$ is obtained as a closed substack of a log modification
-\begin{equation*} \widetilde{\VZ} \to \Mcal .\end{equation*}
-Since the map $\VZ \hookrightarrow \widetilde{\VZ}$ is strict, the Artin fan $\Acal$ of $\VZ$ is locally isomorphic to the Artin fan of $\widetilde{\VZ}$ (with the latter being, in general, larger)\footnote{(Navid) Make this more precise}.
-Since the following discussion is entirely local, we will ignore the distinction between the two, and pretend as though $\Acal$ is the Artin fan of $\widetilde{\VZ}$.
-There is then a commuting square:
-\bcd
-\widetilde{\VZ} \ar[r] \ar[d] & \Mcal \ar[d] \\
-\Acal \ar[r] & \Acal_{\Mcal}.
-\ecd
-Note that neither of the vertical maps are smooth, since the moduli spaces on the top row are not log smooth.
-The construction of $\widetilde{\VZ} \to \Mcal$ as the log modification obtained by imposing an alignment condition gives us a combinatorial description of the map $\Acal \to \Acal_{\Mcal}$ which we will use to study $\Acal$.
-Recall that $\Acal_\Mcal$ is locally isomorphic to the stack quotient
-\begin{equation*} \left[ \Spec \kfield[Q] / \Spec\kfield [Q^{\gp}] \right]\end{equation*}
-where $Q$ is a monoid giving a\footnote{(Navid) Neat?} local chart for $\Mcal$, which we may take to be the minimal monoid of \cite[\S 1.5]{GrossSiebertLog}.
-The real dual $Q^\vee_{\RR} = \Hom(Q,\RR_{\geq 0})$ of this monoid can be viewed as a moduli space of tropical maps; see \cite[Remark 1.12]{GrossSiebertLog}.
-We call this \emph{the tropical moduli space}; contained in the tropical moduli space are the edge lengths of the associated tropical curve (corresponding to the smoothing parameters of the nodes of the logarithmic curve).
-Since the alignment condition amounts to imposing a partial ordering amongst certain sums of these edge lengths, it produces a polyhedral decomposition of the tropical moduli space, into chambers where different partial order relations hold.
-If we only consider the integral points, this produces a polyhedral decomposition of the cone $Q^\vee = \Hom(Q,\N)$.
-Dualising, we obtain a toric blow-up
-\begin{equation*} Z \to \Spec \kfield[Q] \end{equation*}
-which, since it is equivariant, descends to a morphism of the associated zero-dimensional stacks:
-\begin{equation*} \left[Z/T_Z \right] \to \left[ \Spec \kfield[Q] / \Spec\kfield [Q^{\gp}] \right]. \end{equation*}
-This gives a local description of the map $\Acal \to \Acal_\Mcal$ and in particular of the Artin fan $\Acal$.
-By the orbit-cone correspondence, the codimension-$k$ strata of $\Acal$ which intersect this open locus correspond to the $k$-dimensional cones in the polyhedral decomposition of $Q^\vee$ described above.
-These can be understood entirely in terms of tropical combinatorics.
-This is best explained through a number of examples, which we now present.
-
-\subsection{Examples of logarithmic strata} In these examples we will proceed as follows: we will start by fixing an element of the ordinary moduli space $\Mcal$ of log stable maps.
-We will then compute the associated tropical moduli space, giving a description of $\Acal_\Mcal$ local to our chosen element.
-We will then describe the necessary polyhedral subdivison, and thus give a description of $\Acal$ in a neighbourhood of the preimage in $\VZ$ of our chosen element of $\Mcal$.
-Finally we will use this to describe the logarithmic strata which intersect this neighbourhood.
-\begin{example} Consider an element of $\Mcal$ whose associated tropical map has the following combinatorial type:
-\begin{center}
-\begin{tikzpicture}
-\draw [fill] (0,3) circle[radius=2pt];
-\draw (0,3) node[left]{$\sqC_1$};
-\draw (0,3) -- (2,2);
-\draw (1,2.5) node[above,color=red]{$1$};
-\draw (1,2.5) node[below]{$e_1$};
-
-\draw [fill] (0,1) circle[radius=2pt];
-\draw (0,1) node[left]{$\sqC_2$};
-\draw (0,1) -- (2,2);
-\draw (1,1.5) node[below,color=red]{$2$};
-\draw (1,1.5) node[above]{$e_2$};
-
-\draw [->] (2,2) -- (3,2);
-\draw (3,2) node[above]{$x_1$};
-\draw (2.5,2) node[below,red]{$3$};
-
-\draw [fill=white] (2,2) circle[radius=2pt];
-\draw (2,2) node[above]{$\sqC_0$};
-
-\draw [->,color=red] (2,1.5) -- (2,0.5);
-
-\draw [->,color=red] (0,0) -- (3,0);
-\draw (0,0) [fill=red,color=red] circle[radius=2pt];
-\draw (3,0) node[right,color=red]{$\Sigma(\PP^N|H)$};
-\end{tikzpicture}
-\end{center}
-Here each edge (corresponding to a node of the curve) has a length $e_i$ and an expansion factor $u_i$ (indicated in red).
-The moduli space of such tropical maps is generated by the edge lengths $e_1$ and $e_2$
-\begin{equation*} (\RR_{\geq 0})_{e_1} \times (\RR_{\geq 0})_{e_2} \end{equation*}
-subject to the continuity condition $e_1=2e_2$. So the tropical moduli space is simply $\RR_{\geq 0}$ generated by $e_2$. Note that for any $e_2 > 0$ (i.e. on the interior of the cone) we have:
-\begin{equation*} \lambda(\sqC_2) = e_2 = e_1/2 < e_1 = \lambda(\sqC_1). \end{equation*}
-Thus, any logarithmic map with combinatorial type given by the above picture is automatically aligned.
-This means that the map $\VZ \to \Mcal$ is an isomorphism in a neighbourhood of our chosen element (there is no blowing up necessary).
-Indeed, the tropical moduli space is $\RR_{\geq 0}$ and this cone does not admit a polyhedral subdivision (there is no non-trivial toric blow-up of $\Aaff^1$).
-\end{example}
-
-\begin{example}
-Consider now an element of $\Mcal$ whose associated tropical map has the corresponding combinatorial type:
-\begin{center}
-\begin{tikzpicture}
-\draw [fill] (0,4) circle[radius=2pt];
-\draw (0,4) node[left]{$\sqC_1$};
-\draw (0,4) -- (2,3);
-\draw (1,3.5) node[above,color=red]{$1$};
-\draw (1,3.5) node[below]{$e_1$};
-
-\draw [fill] (0,1) circle[radius=2pt];
-\draw (0,1) node[left]{$\sqC_2$};
-\draw (0,1) -- (2,2);
-\draw (1,1.5) node[below,color=red]{$2$};
-\draw (1,1.5) node[above]{$e_2$};
-
-\draw [->] (2,3) -- (3,3);
-\draw (3,3) node[above]{$x_1$};
-\draw (2.5,3) node[above,red]{$1$};
-
-\draw (2,3) -- (2,2);
-\draw [fill] (2,2) circle[radius=2pt];
-\draw (2,2.5) node[right]{$e_3$};
-\draw (2.075,2.5) node[left,red]{$0$};
-\draw (2,2) node[below]{$\sqC_3$};
-
-\draw [->] (2,2) -- (3,2);
-\draw (3,2) node[above]{$x_2$};
-\draw (2.5,2) node[below,red]{$2$};
-
-\draw [fill=white] (2,3) circle[radius=2pt];
-\draw (2,3) node[above]{$\sqC_0$};
-
-\draw [->,color=red] (2,1.25) -- (2,0.5);
-
-\draw [->,color=red] (0,0) -- (3,0);
-\draw (0,0) [fill=red,color=red] circle[radius=2pt];
-\draw (3,0) node[right,color=red]{$\Sigma(\PP^N|H)$};
-\end{tikzpicture}
-\end{center}
-As before, expansion factors are indicated in red and the edge lengths are $e_1,e_2,e_3$.
-The tropical moduli space is $\RR_{\geq 0}^3$ generated by these three lengths, subject to the continuity condition $e_1=2e_2$.
-Thus the moduli space is isomorphic to $\RR_{\geq 0}^2$ generated by $e_2$ and $e_3$.
-In order to have an alignment, at least one of $\lambda(\sqC_1)$ and $\lambda(\sqC_2)$ must be equal to the radius $\delta$.
-Note that
-\begin{align*} \lambda(\sqC_1) & = e_1 = 2e_2 \\
-\lambda(\sqC_2) & = e_2 + e_3\end{align*}
-and without more information we cannot say which of these is larger.
-The subdivision of $(\RR_{\geq 0})^2$ is obtained by dividing the cone into regions where different order relations hold amongst the distances $\lambda(\sqC_1),\lambda(\sqC_2),\lambda(\sqC_3)$.
-The walls of this subdivison correspond to where some of these distances are equal.
-Note that in this setting we always have $\lambda(\sqC_2) > \lambda(\sqC_3)$ (at least, as long as we remain in the interior of the cone).
-The remaining possibilities are:
-\begin{align*} \lambda(\sqC_1) & = \lambda(\sqC_3) \qquad (\Leftrightarrow e_1 = e_3 \Leftrightarrow 2e_2 = e_3) \\
-\lambda(\sqC_1) & = \lambda(\sqC_2) \qquad (\Leftrightarrow e_1 = e_2 + e_3 \Leftrightarrow e_2 = e_3). \end{align*}
-Thus, the subdivision of the tropical moduli space $(\RR_{\geq 0}^2)_{e_2 e_3}$ is given by:
-\begin{center}
-\begin{tikzpicture}[scale=1]
-% Right-hand box
-\fill [fill=gray!30!white] (5,0) -- (8.75,0) -- (8.75,3.75) -- (5,3.75) -- cycle;
-\draw [fill] (5,0) circle[radius=2pt];
-\draw [->] (5,0) -- (9,0);
-\draw (9,0) node[right]{$e_2$};
-\draw [->] (5,0) -- (5,4);
-\draw (5,4) node[above]{$e_3$};
-
-% Left-hand box
-\fill [fill=gray!30!white] (-3,0) -- (0.75,0) -- (0.75,3.75) -- cycle;
-\fill [fill=gray!50!white] (-3,0) -- (0.75,3.75) -- (-1.125,3.75) -- cycle;
-\fill [fill=gray!30!white] (-3,0) -- (-1.125,3.75) -- (-3,3.75) -- cycle;
-\draw [fill] (-3,0) circle[radius=2pt];
-\draw [->] (-3,0) -- (1,0);
-\draw (1,0) node[right]{$e_2$};
-\draw [->] (-3,0) -- (-3,4);
-\draw (-3,4) node[above]{$e_3$};
-
-% 2e_2=e_3 line
-\draw [->] (-3,0) -- (-1,4);
-\draw (-1,4) node[above]{$2e_2=e_3$};
-
-% e_2=e_3 line
-\draw [->] (-3,0) -- (1,4);
-\draw (1,4) node[above]{$e_2=e_3$};
-
-% arrow
-\draw [->] (2,2) -- (4,2);
-\end{tikzpicture}
-\end{center}
-The cones of the subdivison index the logarithmic strata in a neighbourhood of the preimage in $\VZ$ of our chosen element of $\Mcal$. These can be described as follows:
-\begin{center}
-\begin{tikzpicture}[scale=1.8]
-% Left-hand box
-\fill [fill=gray!30!white] (-3,0) -- (0.75,0) -- (0.75,3.75) -- cycle;
-\fill [fill=gray!50!white] (-3,0) -- (0.75,3.75) -- (-1.125,3.75) -- cycle;
-\fill [fill=gray!30!white] (-3,0) -- (-1.125,3.75) -- (-3,3.75) -- cycle;
-\draw [fill] (-3,0) circle[radius=1pt];
-\draw (-3,0) -- (1,0);
-\draw (1,0) node[right,red]{$e_3=0$};
-\draw (-3,0) -- (-3,4);
-\draw (-3,4) node[above,red]{$e_1=e_2=0$};
-
-% 2e_2=e_3 line
-\draw (-3,0) -- (-1,4);
-\draw (-1,4) node[above,red]{$\lambda(\sqC_1)=\lambda(\sqC_3)$};
-
-% e_2=e_3 line
-\draw (-3,0) -- (1,4);
-\draw (1,4) node[above,red]{$\lambda(\sqC_1)=\lambda(\sqC_2)$};
-
-\draw (0,1.5) node[below,red]{$\lambda(\sqC_1) > \lambda(\sqC_2)$};
-
-\draw (-0.6,3.4) node[below,red]{$\lambda(\sqC_3) < \lambda(\sqC_1)$};
-\draw (-0.6,3.1) node[below,red]{$< \lambda(\sqC_2)$};
-
-\draw (-2.2,3.4) node[below,red]{$\lambda(\sqC_1) < \lambda(\sqC_3)$};
-\end{tikzpicture}
-\end{center}
-There are four codimension--$1$ logarithmic strata of $\VZ$ intersecting our chosen neighbourhood, corresponding to the rays in the above picture.
-Two of these -- those corresponding to the rays labeled $\{ e_1=e_2=0 \}$ and $\{ e_3=0 \}$ -- are the proper transforms of codimension--$1$ strata in $\Mcal$.
-These strata consist of log stable maps where some of the tropical edge lengths are equal to zero, meaning that the corresponding nodes have been smoothed.
-Notice that although the curve has three nodes, there are only two such strata: the nodes $q_1$ and $q_2$ cannot be smoothed independently because of the relation $e_1=2e_2$.
-
-The remaining two codimension--$1$ strata in $\VZ$ -- corresponding to the interior rays in the above picture -- consist of log stable maps where some of the vertex distances become equal.
-Here none of the nodes are smoothed.
-From the construction of the subdivision, we see that both these strata map onto a codimension--$2$ stratum of $\Mcal$ (namely, the locus in which all of the nodes persist); this coheres with the fact that they should be thought of as exceptional loci of the blow-up.
-The extra dimension of moduli comes from the choice of alignment.
-
-Finally, there are three codimension--$2$ strata, corresponding to different \emph{strict} orderings of the vertex distances.
-Note that the divisorial strata corresponding to $\{e_1=e_2=0\}$ and $\{e_3=0\}$, which intersected in $\Mcal$, no longer intersect in $\VZ$, since we have blown up.
-The picture is something like:
-\begin{center}
-\begin{tikzpicture}[scale=0.5]
-\draw (-6.5,0.5) ellipse (4 and 2);
-\draw (-6.5,-1.5) node[below]{$\Mcal$};
-\draw [very thick] plot [smooth] coordinates{(-10,0.25) (-8,0.75) (-6,0)};
-\draw [very thick] plot [smooth] coordinates{(-7,0) (-5,0.75) (-3,0.5)};
-
-\draw (-21.5,0.5) ellipse (7 and 2);
-\draw (-21.5,-1.5) node[below]{$\VZ$};
-\draw [very thick] plot [smooth] coordinates{(-28,0.25) (-26,0.75) (-24,0)};
-\draw plot [smooth] coordinates{(-25,0) (-23,0.75) (-21,0)};
-\draw plot [smooth] coordinates{(-23,0) (-20,0.75) (-18,0)};
-\draw [very thick] plot [smooth] coordinates{(-20,0) (-17,0.75) (-15,0)};
-
-\draw [->] (-14,0.5) -- (-11,0.5);
-\end{tikzpicture}
-\end{center}
-
-\end{example}
-
-\subsection{Global logarithmic strata}
-In the previous subsections we used tropical geometry to identify the logarithmic strata of $\VZ=\VZ_{1,\alpha}(\PP^N|H,d)$ local to the preimage of a point in $\Mcal$.
-In fact, the whole discussion carries over if we replace a point in $\Mcal$ by a locally closed logarithmic stratum: the key observation is simply that the tropical moduli space does not vary if we move inside a locally closed logarithmic stratum, so the subdivision process makes sense over that whole stratum.
-This fact will allow us to describe the logarithmic strata of $\VZ$ globally.
-
-\subsubsection{Logarithmic strata of $\Mcal$} The locally closed logarithmic strata of $\Mcal$ consist of loci where the combinatorial type of the associated tropical curve is constant\footnote{(Navid) Reference for this?}.
-This is because the combinatorial type determines the minimal monoid $Q$, which coincides with the stalk of the ghost sheaf on $\Mcal$.
-
-If we have two strata $\Scal_1$ and $\Scal_2$ corresponding to combinatorial types $\Delta_1$ and $\Delta_2$, then $\Scal_2$ is contained in the closure of $\Scal_1$ if and only if the combinatorial type $\Delta_1$ is obtained from $\Delta_2$ by a process of generisation: namely, by contracting some edges (i.e.
-smoothing some nodes) and moving some of the vertices from the interior $\RR_{>0} \subseteq \RR_{\geq 0}$ of the tropicalisation $\Sigma(\PP^N|H)$ to the vertex $0 \in \RR_{\geq 0}$ (i.e.
-moving some components of the curve outside $H$).
-This allows us to completely describe the dual intersection complex of the logarithmic strata of $\Mcal$.
-
-Note that we are \emph{not} able to easily read off the codimension of a logarithmic stratum from the combinatorial data: the codimension of the associated stratum in the Artin fan $\Acal_\Mcal$ is given by the dimension of the tropical moduli space, but the map $\Mcal\to\Acal_\Mcal$ is not smooth (since $\Mcal$ is not log smooth) so we are not able to say anything about the locus in $\Mcal$.
-
-\subsubsection{Logarithmic strata of $\VZ$}
-Now let us pick a stratum $\Scal \subseteq \Mcal$ indexed by a combinatorial type $\Delta$ and with associated monoid $Q$.
-We may choose a sufficiently small open neighbourhood of $\Scal$ which only intersects logarithmic strata $\Scal^\prime$ which contain $\Scal$ in their closures.
-The previous discussion then shows that if we pick any point in this open neighbourhood, the combinatorial type of the associated tropical curve is obtained from $\Delta$ by contracting some edges and specialising some vertices.
-Thus we see that the associated map on tropical moduli spaces is injective, and so the generisation map on the level of ghost sheaves is surjective.
-This allows us to produce a chart on the open neighbourhood of $\Scal$ with monoid given by $Q$.
-
-The discussion in the previous subsections then applies \emph{mutatis mutandis} to this open set, giving a description of the logarithmic strata of $\VZ$ which intersect an open neighbourhood of the preimage of $\Scal$.
-Since log strata must map to log strata, this gives a procedure for enumerating all of the locally closed logarithmic strata of $\VZ$, namely:\medskip
-\begin{enumerate}
-\item Enumerate the locally closed logarithmic strata of $\Mcal$ by enumerating all possible combinatorial types of tropical curves with the given numerical data.
-The dual intersection complex of these strata is specified by generisation of combinatorial types, as described earlier.\medskip
-\item For each locally closed stratum $\Scal\subseteq \Mcal$ identify the tropical moduli space $Q^\vee_{\RR}$ associated to the given combinatorial type, and perform the subdivision specified by the alignment condition.
-The arguments of the previous subsections carry over to give a description of the logarithmic strata of $\VZ$ which map to a neighbourhood of $\Scal$.
-The dual intersection complex of these strata is specified by the combinatorics of each subdivision together with the dual intersection complex of the strata of $\Mcal$.
-\end{enumerate}
-We now illustrate this is in some examples:
-\begin{example} Example of low-degree computation of logarithmic strata.
-(Note that for $\Mcal$ we can't read off the codimension from the dimension of the tropical moduli space because $\Mcal$ is not log smooth.)\footnote{(Navid) To be done.}\end{example}
-
-\newpage
-
-\section{Splitting axiom and recursion formula for $(\PP^N|H)$}
+\section{Recursive description of boundary strata: the reduced splitting axiom}
 
@@
 Finally, we claim that integrals of psi and evaluation classes over these loci can be translated into tautological integrals, i.e.
-descendant Gromov-Witten invariants, whose numerics is governed by the combinatorial type of the tropical map.
-
-\section{Recursion formula in general}
-Now let $(X|Y)$ be a smooth pair with $Y$ very ample. The complete linear system $|\OO_X(Y)|$ defines an embedding $X \hookrightarrow \PP^N$ with $Y=X\cap H$ for $H$ some hyperplane.
-
-\begin{lemma} The following square is cartesian (in the category of ordinary stacks):
-\bcd
-\VZ_{1,\alpha}(X|Y,\beta) \ar[r] \ar[d] \ar[rd,phantom,"\square"] & \VZ_{1,\alpha}(\PP^N|H,d) \ar[d] \\
-\VZ_{1,n}(X,\beta) \ar[r,"i"] & \VZ_{1,n}(\PP^N,d).
-\ecd
-\end{lemma}
-\begin{proof} It is clear from the modular description that this square is cartesian in the category of fs log stacks.
-But the morphism $i$ is strict, which implies that the square is also cartesian in the category of coherent log stacks.
-Since fibre products in the latter category are compatible with the functor forgetting log structures, the claim follows.\end{proof}
-
-Since $\VZ_{1,n}(\PP^N,d)$ is smooth and $\VZ_{1,n}(X,\beta)$ carries a natural virtual class, there is a diagonal pull-back morphism which we use to define the virtual class on the space of maps to $(X|Y)$:
-\begin{equation*} \virt{\VZ_{1,\alpha}(X|Y,\beta)} := i_\Delta^! [\VZ_{1,\alpha}(\PP^N|H,d)]. \end{equation*}
-The recursion formula in $\VZ_{1,\alpha}(\PP^N|H,d)$ immediately pulls back along $i$ to give a recursion formula in $\VZ_{1,\alpha}(X|Y,\beta)$.
+descendant Gromov--Witten invariants, whose numerics is governed by the combinatorial type of the tropical map.
+
+\section{Quantum Lefschetz algorithm}
+Consider a smooth pair $(X,Y)$ with $Y$ very ample, and let $P$ be the projective bundle $P=\PP_Y(\operatorname{N}_{Y|X} \oplus\OO_Y)$.
+We assume that the genus zero and reduced genus one Gromov--Witten theories of $X$ are known.
+From this starting data, we will apply our recursion formula to compute:
+\begin{enumerate}
+\item the genus one \textbf{reduced restricted absolute Gromov--Witten theory} of $Y$;
+\item the genus one \textbf{reduced relative Gromov--Witten theory} of the pair $(X,Y)$;
+\item the genus one \textbf{reduced rubber theory} of $P$.
+\end{enumerate}
+
+\subsection{Reduced absolute, relative and rubber invariants} To be precise: by a reduced invariant of $Y$ we mean an integral over $\VZ_{1,n}(Y,\beta)$ of products of pullbacks of evaluation and psi classes along morphisms which forget a subset $S$ of the marked points (taking $S=\emptyset$ gives the ordinary evaluation and psi classes).
+Here the evaluation maps are viewed as mapping into $X$ (hence the adjective ``restricted'').
+Reduced relative invariants of $(X,Y)$ are defined in the same way, except now the forgetful morphism maps into a space of absolute maps:
+\begin{equation*} \fgt_S \colon \VZ_{1,\alpha}(X|Y,\beta) \to \VZ_{1,m-\#S}(X,\beta).\end{equation*}
+In particular, all the psi classes which we consider are \emph{collapsed psi classes}, meaning that they are relative cotangent line classes for the corresponding collapsed stable map.
+Note that, unlike in the absolute case, in the relative case it may well be the case that the entire insertion is pulled back along a single forgetful map $\fgt_S$.
+The reduced rubber invariants of $P$ are defined similarly (again using collapsed psi classes).
+
+The systems of invariants defined above are equivalent to the classical systems of invariants (which do not use forgetful morphisms) by well-known topological recursion relations.
+
+\subsection{Fictitious and true markings} The recursion procedure is rather delicate.
+Roughly speaking, we will induct on the degree (meaning $Y\cdot\beta$), number of marked points and total tangency.
+To get the correct notion of number of markings and total tangency in  the relative setting, we introduce the concept of \textbf{fictitious markings}.
+Consider a moduli space $\VZ_{1,\alpha}(X|Y,\beta)$ of reduced relative stable maps and a corresponding integrand $\gamma$.
+We let $F \subseteq \{1,\ldots,m\}$ be the maximal subset of marked points such that:
+\begin{enumerate}
+\item $\alpha_i = 1$ for all $i \in F$;
+\item the entire integrand $\gamma$ is pulled back along $\fgt_F$.
+\end{enumerate}
+This subset is uniquely determined, and its elements are referred to as \textbf{fictitious markings}.
+Markings which are not fictitious are referred to as \textbf{true}.
+When inducting on relative invariants we will always be interested in the number of true markings (as opposed to the total number of markings) and the true tangency
+\begin{equation*} \sum_{i \not\in F} \alpha_i \leq d=Y\cdot \beta \end{equation*}
+as opposed to the total tangency, which is always $d$.
+This formalises the idea that relative invariants with non-maximal tangency $t<d$ can be obtained by adding $d-t$ fictitious markings of tangency $1$; see \cite[Lemma 1.15(i)]{Ga}.
+
+\subsection{Structure of the recursion} Given the genus-zero Gromov--Witten theory of $X$, the arguments of \cite{Ga} give an effective algorithm to reconstruct the genus-zero theories of $Y$ and $(X,Y)$; moreover, the genus-zero rubber theory of $P$ is identical to the genus-zero theory of $Y$ \cite{GathmannThesis}.
+Thus we may assume that all genus-zero data is known.
+We assume in addition that we know the genus one reduced theory of $X$.
+The structure of the recursion is then as follows:
+
+\begin{algorithm}
+\DontPrintSemicolon
+\For{$d \geq 0$}{
+\For{$n \geq 0$}{
+\For{$t \geq 0$\medskip}{
+\textbf{\, Step 1: } Compute forgetful relative invariants of $(X,Y)$ (degree~$d$, $n+1$ true markings, true tangency $t$); see below.
+}
+\medskip \textbf{Step 2: } Compute absolute invariants of $Y$ (degree $d$, $n$ markings).\;
+\For{$t \geq 0$\medskip}{
+\textbf{\, Step 3: } Compute relative invariants of $(X,Y)$ (degree $d$, $n$ true markings, true tangency $t$).\;
+}
+}
+\For{$n \geq 0$\medskip}{
+\For{$m \geq 0$\medskip}{
+\textbf{\, Step 4: } Compute rubber invariants of $P$ (degree $d$, $n$ relative markings, $m$ non-relative markings).
+}
+}
+}
+\end{algorithm}
+\noindent Although the loops involving $d, n$ and $m$ have infinite length, in order to compute any single invariant it is only necessarily to iterate the preceding loops for a finite amount of time.
+A \textbf{forgetful relative invariant} of $(X,Y)$ is by definition a reduced relative invariant with a marked point $x_0$ such that all of the insertions are pulled back along $\fgt_{x_0}$.
+In our recursion, we first deal with this special class of relative invariants (with $n+1$ true markings), before computing the absolute invariants (with $n$ markings) and then returning to compute all of the relative invariants (with $n$ true markings).
+This need to treat separately a particular subclass of the relative invariants is an inescapable feature of the genus one recursion.
+
+The base terms of the recursion all have $d=0$ and as such are easy to compute: the relative invariants of $(X,Y)$ are nothing but absolute invariants of $X$, the absolute invariants of $Y$ are given by obstruction bundle integrals over Deligne--Mumford spaces, and the  rubber invariants of $P$ are also given by integrals over Deligne--Mumford spaces, using the formula for the double ramification cycle \cite{Hain,JPPZ} in terms of tautological classes.
+We will now explain how to perform each of the four inductive steps outlined above.
+
+\begin{notation}Given tuples $\mathbf{a}=(a_1,\ldots,a_n)$ and $\mathbf{b}=(b_1,\ldots,b_n)$, we say that $\mathbf{a}<\mathbf{b}$ if there exists an $i \in \{1,\ldots,n\}$ such that $a_j = b_j$ for $j < i$ and $a_i < b_i$.\end{notation}
+
+\subsection*{Step 1} Suppose we are given a forgetful relative invariant to compute.
+That is, we have a relative space $\VZ_{1,\alpha}(X|Y,\beta)$ of degree $d$, with $n+1$ true markings and true tangency $t$, and a marking $x_0$ such that the insertion $\gamma$ is pulled back along $\fgt_{x_0}$.
+We assume inductively that every absolute, relative and rubber invariant with $(d^\prime,n^\prime) < (d,n)$ is known, and also that every forgetful relative invariant with $(d^\prime,n^\prime,t^\prime) < (d,n+1,t)$ is known.
+Choose a true marking $x_1$ with $\alpha_1 \geq 1$ and consider the space:
+\begin{equation*} \VZ_{1,(\alpha-e_1) \cup (1)}(X|Y,\beta). \end{equation*}
+Denote the newly-introduced marking by $y$ and consider the integrand $\tilde\gamma$ obtained from $\gamma$ by introducing $\fgt_y^\st$ everywhere. Applying our recursion formula to $x_1$, we obtain:
+\begin{equation}\label{step 1 recursion}\left( (\alpha_1-1)\psi_1 + \ev_1^\st Y\right) \tilde\gamma \cap [\VZ_{1,(\alpha-e_1) \cup (1)}(X|Y,\beta)] = \tilde\gamma \cap [\Dcal(1)].\end{equation}
+Let us first examine the left-hand side.
+The class $\psi_1$ differs from $\fgt_y^\st \psi_1$ by the locus where $x_1$ and $y$ are contained on a contracted rational bubble.
+This locus consists of reduced relative stable maps of the form \medskip
+
+\begin{center}
+\begin{tikzpicture}[scale=1]
+%edge
+\draw (0,0) to (2,0);
+\draw [color=blue] (1,0) node[above]{\tiny$\alpha_1$};
+
+%C_1
+\draw [fill=white] (0,0) circle[radius=3pt];
+\draw (0,-0.1) node[below]{\small$d$};
+\draw (0,0) node[above]{\small$\sqC_1$};
+
+%C_0
+\draw [fill=black] (2,0) circle[radius=3pt];
+\draw (2,-0.1) node[below]{\small$0$};
+\draw (2,0) node[above]{\small$\sqC_0$};
+
+%x_1
+\draw [->] (2,0.1) -- (4,0.1);
+\draw (3.9,0.1) node[above]{\small$x_1$};
+\draw [color=blue](3,0.1) node[above]{\tiny$\alpha_1-1$};
+
+%y
+\draw [->] (2,-0.1) -- (4,-0.1);
+\draw (3.9,-0.1) node[below]{\small$y$};
+\draw [color=blue] (3,-0.1) node[below]{\tiny$1$};
+
+%down arrow
+\draw [color=blue,->] (1,-0.3) -- (1,-0.7);
+
+%target
+\draw [color=blue,->] (0,-1) to (2,-1);
+\draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
+\draw [color=blue] (2,-1) node[right]{\small$\Sigma(X|Y)$};
+\end{tikzpicture}
+\end{center}
+% Algebro-geometric picture; replaced by tropical picture.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{comment}
+\begin{center}
+\begin{tikzpicture}[scale=1.5]
+%Draw target
+\draw (0,0) -- (3,0) -- (3,2) -- (0,2) -- (0,0);
+\draw (3,0) -- (6,0) -- (6,2) -- (3,2) -- (3,0);
+
+%Draw genus one curve on left-hand side
+\draw [blue] (3,0.5) to [out=90,in=270] (2.7,1) to [out=90,in=270] (3,1.5) to [out=90,in=0] (1,1.7) to [out=180,in=90] (0.5,1) to [out=270,in=180] (1,0.3) to [out=0,in=270] (3,0.5);
+\draw [blue] (1.1,0.9) to [out=40, in=180] (1.4,1.1) to [out=0,in=140] (1.7,0.9);
+\draw [blue] (1.2,1) to [out=300, in=180] (1.4,0.9) to [out=0,in=240] (1.6,1);
+
+%Draw nodal blobs
+\draw [fill=blue,color=blue] (3,0.5) circle[radius=1pt];
+\draw [color=blue] (3,0.5) node[left]{\small$\alpha_2$};
+\draw [fill=blue,color=blue] (3,1.5) circle[radius=1pt];
+\draw [color=blue] (3,1.5) node[left]{\small$\alpha_1$};
+%Draw rational bubble with x_1 and y
+\draw [blue] (3,1.5) to [out=70,in=190] (5.5,1.9) to [out=0,in=90] (6,1.8) to [out=270,in=90] (5.75,1.5) to [out=270,in=90] (6,1.2) to [out=270,in=10] (5.5,1.1) to [out=180,in=290] (3,1.5);
+
+%Draw right-hand markings
+\draw [fill=blue,color=blue] (6,1.8) circle[radius=1pt];
+\draw [color=blue] (6,1.8) node[left]{\small{$\alpha_1-1$}};
+\draw (6,1.8) node[right]{$x_1$};
+\draw [fill=blue,color=blue] (6,1.2) circle[radius=1pt];
+\draw [color=blue] (6,1.2) node[left]{\small{$1$}};
+\draw (6,1.2) node[right]{$y$};
+
+%Draw ldots
+\draw [color=blue] (4,0.5) node[right]{$\ldots$};
+\end{tikzpicture}
+\end{center}
+\end{comment}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+with all other marked points contained on $\sqC_1$.
+This is isomorphic to $\VZ_{1,\alpha}(X|Y,\beta)$ and when we restrict $\tilde\gamma$ to this locus we obtain precisely the class $\gamma$ which we started with.
+Thus the left-hand side of \eqref{step 1 recursion} may be written as
+\begin{equation*} (\alpha_1-1) I + \fgt_y^\st \left( (\alpha_1-1)\psi_1 + \ev_1^\st Y\right)  \tilde\gamma \cap [\VZ_{1,(\alpha-e_1)\cup(1)}(X|Y,\beta)]\end{equation*}
+where $I$ is the invariant we are trying to compute.
+The second term is a forgetful relative invariant with the same degree and number of true markings (since $y$ is fictitious), and strictly smaller true tangency; hence it is recursively known.
+We now examine the right-hand side of \eqref{step 1 recursion}.
+Recall that all of the genus zero data has already been computed, so we only need to focus on the genus one pieces.
+First consider the type $A$ loci.
+The genus one piece has strictly smaller degree (and hence is recursively known) exept in the following situation (with some stable distribution of the remaining markings):
+\begin{center}
+\begin{tikzpicture}[scale=1]
+\draw (0,0) to (2,0);
+\draw [fill=white] (0,0) circle[radius=3pt];
+\draw (0,-0.1) node[below]{\small$d$};
+\draw (0,0) node[above]{\small$\sqC_1$};
+\draw [fill=black] (2,0) circle[radius=3pt];
+\draw (2,-0.1) node[below]{\small$0$};
+\draw (2,0) node[above]{\small$\sqC_0$};
+\draw [->] (2,0) -- (3,0);
+\draw (2.9,0) node[right]{$x_1$};
+
+\draw [color=blue,->] (1,-0.3) -- (1,-0.7);
+
+\draw [color=blue,->] (0,-1) to (2,-1);
+\draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
+\draw [color=blue] (2,-1) node[right]{\small$\Sigma(X|Y)$};
+\end{tikzpicture}
+\end{center}
+In this situation, $C_1$ contains at most $n+1$ true markings.
+If it has $n-1$ or fewer, than it is known recursively.
+If it has exactly $n$ this means that $C_0$ contains exactly one true marking (besides $x_1$, which may be true or fictitious).
+We claim that in this situation we must have $y \in C_1$, since otherwise we would have a moduli space for $C_0$ given by $\ol\Mcal_{0,k}$ with $k \geq 4$, and  applying the projection formula with $\fgt_y$ we would conclude that the contribution is zero.
+Thus we have $y \in C_1$, and so the genus one contribution is a forgetful relative invariant with $n$ true markings, and hence is recursively known.
+
+Finally, if $C_1$ contains exactly $n+1$ true markings, then the only additional markings on $C_0$ are fictitious, and by the same argument as in the previous paragraph there can only be one.
+Thus for each fictitious marked point we obtain a locus isomorphic to $\VZ_{1,\alpha}(X|Y,\beta)$ and $\tilde\gamma$ restricts to $\gamma$ here (from the point of view of computing invariants, the fictitious marked points are indistinguishable, meaning that the contributions are all the same).
+Thus for each fictitious marked point (of which there is at least one, namely $y$) we get a contribution of $\alpha_1 I$ to the right-hand side of \eqref{step 1 recursion}.
+
+The contributions of the type $B$ loci only involve genus zero data and hence are known.
+The contributions of the type $C^0$ loci are determined by genus zero data and tautological integrals on Deligne--Mumford space, hence are also known.
+It remains to consider type $C^+$ loci.
+If the degree of the genus one piece is less than $d$ then we have a rubber invariant of strictly smaller degree.
+The only other possibility is that the entire curve is mapped into the divisor.
+In this case we may apply the projection formula with $\fgt_y$ to identify this with an integral over $\VZ_{1,m}(Y,\beta)$ for some (possibly large) number $m$ of marked points.
+But by assumption there is another marked point $x_0$ with all of the insertions pulled back along $\fgt_{x_0}$, so a further application of the projection formula shows that this contribution vanishes.
+To conclude, we may rearrange \eqref{step 1 recursion} to obtain an expression of the form
+\begin{equation*} \lambda I = \text{recursively known terms} \end{equation*}
+where $\lambda$ is an explicit scalar which is always nonzero; we have thus determined $I$, which completes Step 1.
+
+\subsection*{Step 2} Consider now the absolute space $\VZ_{1,n}(Y,\beta)$ with an insertion $\gamma$, and suppose inductively that we have computed all forgetful relative invariants with $(d^\prime,n^\prime) \leq (d,n+1)$, all relative invariants and absolute invariants with $(d^\prime,n^\prime) < (d,n)$, and all special rubber invariants with $d^\prime < d$.
+Consider the following moduli space with $n+1$ markings:
+\begin{equation*} \VZ_{1,(d,0,\ldots,0)}(X|Y,\beta). \end{equation*}
+Let $x_0$ denote the relative marking and consider the integrand $\tilde\gamma$ obtained from $\gamma$ by introducing $\fgt^\st_{x_0}$ everywhere. Now recurse at $x_1$ to obtain:
+\begin{equation}\label{step 2 recursion} \ev_1^\st Y \cdot \tilde\gamma \cap [\VZ_{1,(d,0,\ldots,0)}(X|Y,\beta)] = \tilde\gamma\cap[\Dcal(1)].\end{equation}
+The left-hand side is a forgetful relative invariant of degree $d$ and $\leq n+1$ true markings, and so has already been computed.
+For the right-hand side, let us begin with loci of type $A$.
+The genus one contributions from each loci have $(d^\prime,n^\prime) < (d,n)$ except in the following case
+\begin{center}
+\begin{tikzpicture}[scale=1]
+%edge
+\draw (0,0) to (2,0);
+\draw [color=blue] (1,0) node[above]{\tiny$d$};
+
+%C_1
+\draw [fill=white] (0,0) circle[radius=3pt];
+\draw (0,-0.1) node[below]{\small$d$};
+\draw (0,0) node[above]{\small$\sqC_1$};
+
+%C_0
+\draw [fill=black] (2,0) circle[radius=3pt];
+\draw (2,-0.1) node[below]{\small$0$};
+\draw (2,0) node[above]{\small$\sqC_0$};
+
+%x_1
+\draw [->] (2,0.1) -- (4,0.1);
+\draw (3.9,0.1) node[above]{\small$x_1$};
+\draw [color=blue](3,0.1) node[above]{\tiny$0$};
+
+%y
+\draw [->] (2,-0.1) -- (4,-0.1);
+\draw (3.9,-0.1) node[below]{\small$x_0$};
+\draw [color=blue] (3,-0.1) node[below]{\tiny$d$};
+
+%down arrow
+\draw [color=blue,->] (1,-0.3) -- (1,-0.7);
+
+%target
+\draw [color=blue,->] (0,-1) to (2,-1);
+\draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
+\draw [color=blue] (2,-1) node[right]{\small$\Sigma(X|Y)$};
+\end{tikzpicture}
+\end{center}
+which gives a contribution of
+\begin{equation*} d\cdot \gamma \cap [\VZ_{1,(d,\underbrace{0,\ldots,0}_{n-1})}(X|Y,\beta)] \footnote{(Navid) Fix formatting}\end{equation*}
+to the right-hand side of \eqref{step 2 recursion}.
+Here $\gamma$ is the insertion we started with; the difference is that we are now considering relative maps to $(X,Y)$ with maximal tangency at $x_1$, rather than absolute maps to $Y$.
+The type $B$ and $C^0$ loci are recursively determined as in Step~1, and similarly the type $C^+$ loci are recursively determined except for the locus where the entire curve is mapped into the divisor.
+On this locus we may apply $\fgt_{x_0}$ and identify the contribution with
+\begin{equation*} d^2 \cdot \gamma \cap [\VZ_{1,n}(Y,\beta)] = d^2 \cdot I \end{equation*}
+where $I$ is the invariant we are trying to compute. Putting this all together, we obtain
+\begin{equation}\label{step 2 recursion 2} I = (-\gamma/d) \cap [\VZ_{1,(d,\underbrace{0,\ldots,0}_{n-1})}(X|Y,\beta)] + \text{recursively known terms} \end{equation}
+where on the right-hand side there are $n-1$ non-relative markings $x_2,\ldots,x_n$, and a relative marking $x_1$. We now apply the recursion again to the right-hand side, by considering the space
+\begin{equation*} \VZ_{1,(d-1,1,0,\ldots,0)}(X|Y,\beta) \end{equation*}
+where $x_1$ now has tangency $d-1$ and we have introduced a new marking $y$ with tangency $1$.
+We consider a new insertion, denoted $\tilde\gamma$ as usual, by introducing $\fgt_y^\st$ everywhere.
+Recursing at $x_1$ we obtain:
+\begin{equation}\label{step 2 recursion 2} \left( (d-1)\psi_1 + \ev_1^\st Y \right)\cdot(-\tilde\gamma/d) \cap [\VZ_{1,(d-1,1,0,\ldots,0)}(X|Y,\beta)] = (-\tilde\gamma/d) \cap [\Dcal(1)].\end{equation}
+The difference between $\psi_1$ and $\fgt_y^\st \psi_1$ is given by the locus where $x_1$ and $y$ belong to a collapsed rational bubble:
+\begin{center}
+\begin{tikzpicture}[scale=1]
+%edge
+\draw (0,0) to (2,0);
+\draw [color=blue] (1,0) node[above]{\tiny$d$};
+
+%C_1
+\draw [fill=white] (0,0) circle[radius=3pt];
+\draw (0,-0.1) node[below]{\small$d$};
+\draw (0,0) node[above]{\small$\sqC_1$};
+
+%C_0
+\draw [fill=black] (2,0) circle[radius=3pt];
+\draw (2,-0.1) node[below]{\small$0$};
+\draw (2,0) node[above]{\small$\sqC_0$};
+
+%x_1
+\draw [->] (2,0.1) -- (4,0.1);
+\draw (3.9,0.1) node[above]{\small$y$};
+\draw [color=blue](3,0.1) node[above]{\tiny$1$};
+
+%y
+\draw [->] (2,-0.1) -- (4,-0.1);
+\draw (3.9,-0.1) node[below]{\small$x_1$};
+\draw [color=blue] (3,-0.1) node[below]{\tiny$d-1$};
+
+%down arrow
+\draw [color=blue,->] (1,-0.3) -- (1,-0.7);
+
+%target
+\draw [color=blue,->] (0,-1) to (2,-1);
+\draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
+\draw [color=blue] (2,-1) node[right]{\small$\Sigma(X|Y)$};
+\end{tikzpicture}
+\end{center}
+The contribution of this locus to the left-hand side of \eqref{step 2 recursion 2} is:
+\begin{equation*} (d-1)\cdot(-\gamma/d) \cap [\VZ_{1,(d,\underbrace{0,\ldots,0}_{n-1})}(X|Y,\beta)].\end{equation*}
+What remains on the left-hand side is a forgetful relative invariant of degree $d$ and $\leq n+1$ true markings ($y$ being the ``forgetful'' marking), hence is recursively known.
+On the right-hand side, the type $A$ loci are recursively known except possibly in the following special cases (with some stable distribution of the remaining non-relative markings):
+\begin{center}
+\begin{minipage}{0.4\textwidth}
+\begin{tikzpicture}[scale=1]
+%edge
+\draw (0,-0.1) to (2,-0.1);
+\draw [color=blue] (1,-0.1) node[below]{\tiny$d-1$};
+
+%C_1
+\draw [fill=white] (0,0) circle[radius=3pt];
+\draw (0,-0.1) node[below]{\small$d$};
+\draw (0,0) node[above]{\small$\sqC_1$};
+
+%C_0
+\draw [fill=black] (2,0) circle[radius=3pt];
+\draw (2,-0.1) node[below]{\small$0$};
+\draw (2,0) node[above]{\small$\sqC_0$};
+
+%x_1
+\draw [->] (0,0.1) -- (1.5,0.1);
+\draw (1.5,0.1) node[above]{\small$y$};
+\draw [color=blue](0.75,0.1) node[above]{\tiny$1$};
+
+%y
+\draw [->] (2,0) -- (4,0);
+\draw (3.9,0) node[below]{\small$x_1$};
+\draw [color=blue] (3,0) node[below]{\tiny$d-1$};
+
+%down arrow
+\draw [color=blue,->] (1,-0.5) -- (1,-0.9);
+
+%target
+\draw [color=blue,->] (0,-1) to (2,-1);
+\draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
+\draw [color=blue] (2,-1) node[right]{\small$\Sigma(X|Y)$};
+
+\draw (2,-1.3) node[below]{\small{Case 1}};
+\end{tikzpicture}
+\end{minipage}
+\begin{minipage}{0.4\textwidth}
+\begin{tikzpicture}[scale=1]
+%edge
+\draw (0,0) to (2,0);
+\draw [color=blue] (1,0) node[above]{\tiny$d$};
+
+%C_1
+\draw [fill=white] (0,0) circle[radius=3pt];
+\draw (0,-0.1) node[below]{\small$d$};
+\draw (0,0) node[above]{\small$\sqC_1$};
+
+%C_0
+\draw [fill=black] (2,0) circle[radius=3pt];
+\draw (2,-0.1) node[below]{\small$0$};
+\draw (2,0) node[above]{\small$\sqC_0$};
+
+%x_1
+\draw [->] (2,0.1) -- (4,0.1);
+\draw (3.9,0.1) node[above]{\small$y$};
+\draw [color=blue](3,0.1) node[above]{\tiny$1$};
+
+%y
+\draw [->] (2,-0.1) -- (4,-0.1);
+\draw (3.9,-0.1) node[below]{\small$x_1$};
+\draw [color=blue] (3,-0.1) node[below]{\tiny$d-1$};
+
+%down arrow
+\draw [color=blue,->] (1,-0.3) -- (1,-0.7);
+
+%target
+\draw [color=blue,->] (0,-1) to (2,-1);
+\draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
+\draw [color=blue] (2,-1) node[right]{\small$\Sigma(X|Y)$};
+
+\draw (2,-1.3) node[below]{\small{Case 2}};
+\end{tikzpicture}
+\end{minipage}
+\end{center}
+In Case 1 the contribution from $C_1$ is a forgetful relative invariant with $\leq n$ true markings, hence is recursively known.
+In Case 2, we first note that there cannot be any more markings on $C_0$ (since otherwise we could apply $\fgt_y$ and conclude that the contribution vanishes).
+Thus we obtain a single locus, which contributes precisely
+\begin{equation*} d\cdot(-\gamma/d) \cap [\VZ_{1,(d,\underbrace{0,\ldots,0}_{n-1})}(X|Y,\beta)] = -\gamma\cap[\VZ_{1,(d,\underbrace{0,\ldots,0}_{n-1})}(X|Y,\beta)]\end{equation*}
+which gives us the first term on the right-hand side of \eqref{step 2 recursion 2}.
+As usual the type $B$ and $C^0$ contributions are known recursively, and the only type $C^+$ contribution not known recursively occurs when the entire curve is mapped into the divisor, in which case we apply $\fgt_y$ to calculate the contribution as:
+\begin{equation*} (-\gamma/d) \cap [\VZ_{1,n}(Y,\beta)] = -I/d.\end{equation*}
+Substituting into \eqref{step 2 recursion 2} we end up with
+\begin{equation*} I(1-d^{-1}) = \text{recursively known terms} \end{equation*}
+which completes the recursion step as long as $d \neq 1$.
+But since $\VZ_{1,n}(H,1)=\emptyset$ it follows that $\VZ_{1,n}(Y,\beta)=\emptyset$ if $d=Y\cdot\beta=1$, so we may always assume $d \geq 2$ in the recursion.
+
+\subsection*{Step 3} Now suppose we are given a relative space $\VZ_{1,\alpha}(X|Y,\beta)$ with an insertion $\gamma$, and suppose inductively that we have computed all forgetful relative invariants with $(d^\prime,n^\prime) \leq (d,n+1)$, all absolute invariants with $(d^\prime,n^\prime) \leq (d,n)$, all relative invariants with $(d^\prime,n^\prime,t^\prime)<(d,n,t)$ and all rubber invariants with $d^\prime < d$.
+Choose a true marking $x_1$ with $\alpha_1 \geq 1$ and consider the moduli space
+\begin{equation*} \VZ_{1,(\alpha-e_1)\cup(1)}(X|Y,\beta) \end{equation*}
+where $y$ is the newly-introduced marking. As usual consider the insertion $\tilde\gamma$ obtained from $\gamma$ by introducing $\fgt_y$ everywhere. Recursing at $x_1$ we obtain:
+\begin{equation*} \left( (\alpha_1-1)\psi_1 + \ev_1^\st H\right) \tilde\gamma \cap [\VZ_{1,(\alpha-e_1)\cup(1)}(X|Y,\beta)] = \tilde\gamma \cap [\Dcal(1)].\end{equation*}
+The left-hand side is a relative invariant with the same degree and number of true markings, but smaller true tangency: hence it is recursively known.
+On the right-hand side, the type $A$ contributions are recursively known except for those of the following form
+
+\begin{center}
+\begin{tikzpicture}[scale=1]
+\draw (0,0) to (2,0);
+\draw [color=blue] (1,-0.05) node[above]{\tiny$\alpha_1$};
+\draw [fill=white] (0,0) circle[radius=3pt];
+\draw (0,-0.1) node[below]{\small$d$};
+\draw (0,0) node[above]{\small$\sqC_1$};
+\draw [fill=black] (2,0) circle[radius=3pt];
+\draw (2,-0.1) node[below]{\small$0$};
+\draw (2,0) node[above]{\small$\sqC_0$};
+\draw [->] (2,0) -- (4,0);
+\draw (3.9,0) node[right]{$x_1$};
+\draw [color=blue] (3,-0.05) node[above]{\tiny$\alpha_1-1$};
+
+\draw [color=blue,->] (1,-0.3) -- (1,-0.7);
+
+\draw [color=blue,->] (0,-1) to (2,-1);
+\draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
+\draw [color=blue] (2,-1) node[right]{\small$\Sigma(X|Y)$};
+\end{tikzpicture}
+\end{center}
+where $C_0$ contains a single fictitious marking (if it had multiple fictitious markings then the contribution would vanish by projection formula) and all the other markings are on $C_1$.
+Thus for each fictitious marking we get a contribution of $\alpha_1 I$ where $I$ is the invariant we are trying to compute.
+Note that $\alpha_1 \neq 0$, and that this term appears at least once since $y$ is a fictitious marking; so we get a nonzero multiple of $I$.
+
+As usual the type $B$ and $C^0$ contributions are recursively known.
+The type $C^+$ contributions are determined by lower-degree rubber invariants, except for when the whole curve is mapped into $Y$; however in this case we may apply $\fgt_y$ to identify the contribution with an absolute invariant of $Y$ with degree $d$ and $n$ markings, which is also recursively known.
+Thus we have determined the invariant $I$.
+
+\subsection*{Step 4} Finally, consider a rubber space $\VZ_{1,\alpha}(P|Y_0+Y_\infty,\beta)_{\Gm}$ with insertion $\gamma$.
+Suppose inductively that we have computed all absolute and relative invariants with $d^\prime \leq d$ and all rubber invariants with $(d^\prime,n^\prime,m^\prime) < (d,n,m)$.
+
+We first note the following important reduction: if there exists a relative marking $x_k$ such that all insertions are pulled back along $\fgt_{k}$, then we may apply the projection formula, together with the fact that
+\begin{equation*} (\fgt_{k})_\st [\VZ_{1,\alpha}(P|Y_0+Y_\infty,\beta)_{\Gm}] = \alpha_k^2 \cdot [\VZ_{1,n+m-1}(Y,\beta)] \end{equation*}
+to identify the rubber invariant with a multiple of a reduced invariant of $Y$, which has the same degree and hence is known recursively.
+
+We will deal with the general case by reducing to the one above. Consider the moduli space
+\begin{equation*}\label{step 4 recursion space} \VZ_{1,\alpha\cup (0)}(P|Y_0+Y_\infty,\beta)_{\Gm}\end{equation*}
+obtained by introducing a marked point $y$ with no tangency.
+Let $x_1$ be a positive-tangency marking (such a marking always exists since $d \geq 2$) and let $\tilde\gamma$ be the insertion obtained from $\gamma$ by replacing $\ev_1$ and $\psi_1$ by $\ev_y$ and $\psi_y$, and then introducing $\fgt_{1}^\st$ everywhere.
+
+We will make use of a recursion formula for rubber spaces analogous to the recursion formula for relative spaces used in Steps 1--3.
+Following \cite{EKatz}, there is a line bundle $L_y^{\not\in \operatorname{bot}}$ on $\VZ_{1,\alpha\cup (0)}(P|Y_0+Y_\infty,\beta)_{\Gm}$, together with a section $s_y^{\not\in\operatorname{bot}}$ whose vanishing locus consists of the locus $\Dcal(y)$ of rubber maps where $y$ is not mapped into the bottom level of the expanded target.
+As in \S \ref{}, we can give a logarithmic interpretation of this: it corresponds to the piecewise-linear function on the tropical moduli space which associates, to every rubber tropical map, the distance between $\varphi(\sqC_y)$ and the leftmost vertex of the tropical target, where $\sqC_y$ is the vertex of the source curve containing the flag corresponding to $y$.
+Using this tropical description, we may easily calculate the vanshing orders of $s_y^{\not\in\operatorname{bot}}$ along the various components of $\Dcal(y)$, and show that $\cchern_1(L_y^{\not\in\operatorname{bot}}) = \Psi_0 - \ev_y^\st Y$ (see also \cite{EKatzLB}, where similar results in the non-reduced setting are obtained, using different methods).
+From this, we obtain a rubber recursion formula
+\begin{equation}\label{step 4 recursion} (\Psi_0 - \ev_y^\st Y) \tilde\gamma \cap [\VZ_{1,\alpha\cup(0)}(P|Y_0+Y_\infty,\beta)_{\Gm}] = \tilde\gamma \cap [\Dcal(y)]\end{equation}
+where the fundamental class $[\Dcal(y)]$ is weighted by vanishing orders on the components.
+We will first show that the left-hand side is recursively known.
+By construction the class $\tilde\gamma$ is pulled back via $\fgt_{1}^\st$, and the same is true for $\ev_y^\st Y$.
+It remains to examine $\Psi_0$.
+If there exists a negative-tangency marking $x_2$, then we have \cite[Construction 5.1.17]{GathmannThesis}
+\begin{equation*}\label{Psi0 formula} \Psi_0 = -\alpha_2 \hat\psi_2 - \ev_2^\st Y \end{equation*}
+where $\hat\psi_2$ is a \emph{non-collapsed} psi class.
+(If there are no negative-tangency markings, then the construction given in \cite[\S 1.5.2]{MaulikPandharipande} shows that $\Psi_0=0$.) Now, $\hat\psi_2 - \psi_2$ is given by the loci where $x_2$ belongs to a trivial bubble.
+This entails a splitting of the curve into pieces, each of which contributes a rubber integral.
+Typically each of these pieces will have $(g^\prime,d^\prime,n^\prime,m^\prime) < (1,d,n,m)$ and hence be recursively known.
+The one exception is when all of the genus and degree is concentrated on the top level of the expansion, with the bottom level containing only a single non-relative marking in addition to all the negative-tangency markings.
+But in this case the contribution is a rubber invariant where all of the insertions are pulled back via $\fgt_1^\st$, and hence we may apply the projection formula to identify this with an absolute invariant of $Y$ which is recursively known.
+We conclude that, up to recursively knwon terms, we may replace $\hat\psi_2$ by $\psi_2$ in the left-hand side of \eqref{step 4 recursion}.
+If we now compare $\psi_2$ with $\fgt_1^\st \psi_2$ we see that the difference is given by the locus where $x_1$ and $x_2$ belong to a collapsed rational piece.
+The contribution of this locus consists of rubber invariant with strictly fewer relative markings, and hence is recursively known.
+So up to recursively-known terms \eqref{step 4 recursion} becomes
+\begin{equation*} \fgt_1^\st (-\alpha_2\psi_2 - \ev_y^\st Y)\tilde\gamma \cap [\VZ_{1,\alpha\cup(0)}(P|Y_0+Y_\infty,\beta)_{\Gm}] = \tilde\gamma\cap[\Dcal(y)]\end{equation*}
+and now the left-hand side is also recursively known, by the projection formula.
+Let us now examine the right-hand side.
+The components of $\Dcal(y)$ are indexed by splittings of the curve, and certainly the contributions are recursively known unless there is a piece of the curve carrying all of the genus and degree, so we may restrict to examining these contributions.
+
+Let us denote the piece of the curve carrying all of the genus and degree by $C^\prime\subseteq C$.
+If $C^\prime$ is mapped to top level, then either it contains $x_1$, in which case we apply $\fgt_1$ to compute the contribution, or it does not contains $x_1$, in which case it has fewer than $n$ relative markings and is known recursively.
+If on the other hand $C^\prime$ is not mapped to top level, then generically it is mapped to the bottom level (since generically the circuit is not contracted on this locus, so the desingularisation process does nothing).
+One possible contribution is given by the following locus
+\begin{center}
+\begin{tikzpicture}[scale=1]
+%edge
+\draw (0,0) to (2,0);
+\draw [color=blue] (1,0) node[below]{\tiny$\alpha_1$};
+
+%C_1
+\draw [fill=white] (0,0) circle[radius=3pt];
+\draw (0,-0.1) node[below]{\small$d$};
+
+%y
+\draw [->] (2,0) -- (2,1);
+\draw (2,0.9) node[left]{$y$};
+\draw [color=blue] (2,0.5) node[right]{\tiny$0$};
+
+%x_1
+\draw [->] (2,0) -- (3,0);
+\draw (3,0) node[right]{$x_1$};
+\draw [color=blue] (2.5,0) node[below]{\tiny$\alpha_1$};
+
+%C_0
+\draw [fill=black] (2,0) circle[radius=3pt];
+\draw (2,-0.1) node[below]{\small$0$};
+
+%down arrow
+\draw [color=blue,->] (1,-0.5) -- (1,-0.9);
+
+%target
+\draw [color=blue] (0,-1) to (2,-1);
+\draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
+\draw [fill=blue,color=blue] (2,-1) circle[radius=3pt];
+\draw [color=blue,->] (2,-1) -- (3,-1);
+\draw [color=blue,->] (0,-1) -- (-1,-1);
+\end{tikzpicture}
+\end{center}
+which contributes a nonzero multiple of the invariant $I$ we are trying to compute.
+For the other possibilities, first note that, unless every component at the top level contains a single positive-tangency marking and a single node (together with possibly some tangency-zero markings), then $C^\prime$ has fewer than $n$ relative markings and hence the contribution is known recursively.
+On the other hand, if any non-relative marking other than $y$ is mapped to the top level, $C^\prime$ has $\leq n$ relative markings and less than $m$ non-relative markings, and hence again the contribution is known recursively.
+The only remaining possibilities are when $x_1$ is replaced by another positive-tangency marking $x_k$ in the above picture; but then the contribution can be calculated by applying the projection formula to $\fgt_{1}$.
+We therefore conclude that the only contribution to the right-hand side of \eqref{step 4 recursion} which is not known recursively is a nonzero multiple of the invariant we were trying to compute.
+This completes the recursion step.
 
@@
 \noindent Dhruv Ranganathan \\
-DPMMS, University of Cambridge \\
+Department of Pure Mathematics and Mathematical Statistics, University of Cambridge \\
 \href{mailto:dr508@cam.ac.uk}{dr508@cam.ac.uk}

### 2019-03-05 Strata Description/Description of Strata.tex
organised everything

--- 2019-03-04 GenusOneRelativeMaps.tex
@@
 \appendixtitletocoff
-\tableofcontents
-
-\newpage
-
-\section{Gathmann's line bundle via tropical geometry} For each marking $x_k$ we consider the locus in $\VZ_{1,\alpha}(\PP^N|H)$ where $x_k$ belongs to an internal component of the collapsed map.
-We use the log structure on $\VZ_{1,\alpha}(\PP^N|H)$ to construct a line bundle $\Lcal_k$ together with a section $s_k$ vanishing along this locus.
-We use the correspondence with tropical geometry to identify $\cchern_1(\Lcal_k)$ in terms of tautological classes on $\VZ_{1,\alpha}(\PP^N|H)$, and to compute the vanishing order of $s_k$ along the components of its zero set.
-
-The pair $(\Lcal_k,s_k)$ is most naturally constructed on the moduli space $\MLog_{1,\alpha}(\PP^N|H)$ of non-expanded log maps; the corresponding pair on $\VZ_{1,\alpha}(\PP^N|H)$ will be obtained via pull-back.
-Consider therefore a moduli point in $\MLog_{1,\alpha}(\PP^N|H)$ and let $Q^\vee_{\RR}$ be the corresponding tropical moduli space (viewed as a rational polyhedral cone).
-Over this cone we have a universal tropical curve and map
-\bcd
-\sqC \ar[d,"\pi"] \ar[r,"f"] & \RR_{\geq 0} \\
-Q^\vee_{\RR} \ar[u, bend left=40pt, "x_k" left]
-\ecd
-where $x_k$ is the section which for every point $\lambda \in Q^\vee_{\RR}$ picks out the vertex of $\sqC_\lambda$ containing the leg $x_k$.
-The composition $f \circ x_k \colon Q^\vee_{\RR} \to \RR_{\geq 0}$ defines a piecewise-linear function on $Q_{\RR}^\vee$ whose preimage over the open cone $\RR_{>0}$ consists of those tropical maps where $x_k$ belongs to an internal component.
-Dually we obtain an element of the minimal monoid $Q$ at the moduli point, and this globalises to produce a section of the ghost sheaf on $\MLog_{1,\alpha}(\PP^N|H)$.
-In the usual way this induces a line bundle and section $(\Lcal_k,s_k)$ on the moduli space, and the tropical description above shows that the zero locus of $s_k$ is (set-theoretically) the locus where $x_k$ belongs to an internal component.
-
-We now calculate $\cchern_1(\Lcal_k)$.
-Choose a family of log stable maps over $S$ and let $\mu \in \Gamma(S,\ol{M}_S)$ be the global section of the ghost sheaf constructed in the previous paragraph.
-This pulls back along $\pi$ to give a global section $\pi^\flat(\mu) \in \Gamma(C,\ol{M}_C)$.
-Interpreted as a piecewise-linear function on the tropicalisation $\sqC$ with values in $\ol{M}_S$ \cite[Remark 7.3]{CavalieriChanUlirschWise}, this assigns $\mu$ to every vertex and has slope zero along every edge.
-By construction, the line bundle associated to this section is $\pi^\st \Lcal_k$.
-Consider on the other hand the generator $1 \in \N = \Gamma(\PP^N,\ol{M})$ with associated line bundle $\OO(H)$.
-The section $f^\flat(1) \in \Gamma(C,\ol{M}_C)$ has associated line bundle $f^\st\OO(H)$.
-If we let $v$ denote the vertex containing $x_k$, then by construction $f^\flat(1)$ assigns $\mu$ to $v$ and has slope $\alpha_k$ along the leg $x_k$.
-Thus if we consider the difference $f^\flat(1) - \pi^\flat(\mu)$ then this assigns $0$ to $v$ and still has slope $\alpha_k$ along $x_k$.
-Thus by \cite[Proposition 2.4.1]{RSPW} the corresponding line bundle restricted to $C_v$ is given by
-\begin{equation*} \OO_{C_v} \left(\alpha_k x_k + \sum_e \mu_e x_e \right) \end{equation*}
-where the sum is over the edges $e$ adjacent to $v$ and distinct from $x_k$. Thus we see that:
-\begin{equation*} \left( f^\st\OO(H) \otimes \pi^\st \Lcal_k^{-1} \right) \big|_{C_v} = \OO_{C_v} \left(\alpha_k x_k + \sum_e \mu_e x_e \right).\end{equation*}
-Since $x_k$ factors through $C_v$ we may pull back along $x_k$ to obtain
-\begin{equation*} \Lcal_k = x_k^\st\pi^\st \Lcal_k = x_k^\st \OO_{C_k}(-\alpha_k x_k) \otimes x_k^\st f^\st\OO(H) = x_k^\st \OO_{C_k}(-\alpha_k x_k) \otimes \ev_k^\st \OO(H) \end{equation*}
-and taking Chern classes gives:
-\begin{equation*} \cchern_1(\Lcal_k) = \alpha_k \psi_k + \ev_k^\st H.\end{equation*}
-This gives the construction of $(\Lcal_k,s_k)$ on $\MLog_{1,\alpha}(\PP^N|H)$; the construction on $\VZ_{1,\alpha}(\PP^N|H)$ is given by pull-back.
-Notice in particular that $\psi_k$ should be interpreted as a \textbf{collapsed psi class} on $\VZ_{1,\alpha}(\PP^N|H)$, i.e.
-a psi class coming from the stabilised curve of the collapsed map.
-All of the psi classes we deal with will be collapsed psi classes.
-
-\begin{remark} This construction gives the natural logarithmic analogue of Gathmann's line bundle and section \cite[Construction 2.1]{Ga}.
-A benefit of the logarithmic approach is to make the computation of vanishing orders entirely combinatorial (see \S \ref{} below), circumventing the difficult technical calculation given by Gathmann.
-\end{remark}
-
-\newpage
-
-\section{Quantum Lefschetz recursion}
-Consider a smooth pair $(X,Y)$ with $Y$ very ample, and let $P$ be the projective bundle $P=\PP_Y(\operatorname{N}_{Y|X} \oplus\OO_Y)$.
-We assume that the genus zero and reduced genus one Gromov--Witten theories of $X$ are known.
-From this starting data, we will apply our recursion formula to compute:
-\begin{enumerate}
-\item the genus one \textbf{reduced restricted absolute Gromov--Witten theory} of $Y$;
-\item the genus one \textbf{reduced relative Gromov--Witten theory} of the pair $(X,Y)$;
-\item the genus one \textbf{reduced rubber theory} of $P$.
-\end{enumerate}
-
-\subsection{Reduced absolute, relative and rubber invariants} To be precise: by a reduced invariant of $Y$ we mean an integral over $\VZ_{1,n}(Y,\beta)$ of products of pullbacks of evaluation and psi classes along morphisms which forget a subset $S$ of the marked points (taking $S=\emptyset$ gives the ordinary evaluation and psi classes).
-Here the evaluation maps are viewed as mapping into $X$ (hence the adjective ``restricted'').
-Reduced relative invariants of $(X,Y)$ are defined in the same way, except now the forgetful morphism maps into a space of absolute maps:
-\begin{equation*} \fgt_S \colon \VZ_{1,\alpha}(X|Y,\beta) \to \VZ_{1,m-\#S}(X,\beta).\end{equation*}
-In particular, all the psi classes which we consider are \emph{collapsed psi classes}, meaning that they are relative cotangent line classes for the corresponding collapsed stable map.
-Note that, unlike in the absolute case, in the relative case it may well be the case that the entire insertion is pulled back along a single forgetful map $\fgt_S$.
-The reduced rubber invariants of $P$ are defined similarly (again using collapsed psi classes).
-
-The systems of invariants defined above are equivalent to the classical systems of invariants (which do not use forgetful morphisms) by well-known topological recursion relations.
-
-\subsection{Fictitious and true markings} The recursion procedure is rather delicate.
-Roughly speaking, we will induct on the degree (meaning $Y\cdot\beta$), number of marked points and total tangency.
-To get the correct notion of number of markings and total tangency in  the relative setting, we introduce the concept of \textbf{fictitious markings}.
-Consider a moduli space $\VZ_{1,\alpha}(X|Y,\beta)$ of reduced relative stable maps and a corresponding integrand $\gamma$.
-We let $F \subseteq \{1,\ldots,m\}$ be the maximal subset of marked points such that:
-\begin{enumerate}
-\item $\alpha_i = 1$ for all $i \in F$;
-\item the entire integrand $\gamma$ is pulled back along $\fgt_F$.
-\end{enumerate}
-This subset is uniquely determined, and its elements are referred to as \textbf{fictitious markings}.
-Markings which are not fictitious are referred to as \textbf{true}.
-When inducting on relative invariants we will always be interested in the number of true markings (as opposed to the total number of markings) and the true tangency
-\begin{equation*} \sum_{i \not\in F} \alpha_i \leq d=Y\cdot \beta \end{equation*}
-as opposed to the total tangency, which is always $d$.
-This formalises the idea that relative invariants with non-maximal tangency $t<d$ can be obtained by adding $d-t$ fictitious markings of tangency $1$; see \cite[Lemma 1.15(i)]{Ga}.
-
-\subsection{Structure of the recursion} Given the genus-zero Gromov--Witten theory of $X$, the arguments of \cite{Ga} give an effective algorithm to reconstruct the genus-zero theories of $Y$ and $(X,Y)$; moreover, the genus-zero rubber theory of $P$ is identical to the genus-zero theory of $Y$ \cite{GathmannThesis}.
-Thus we may assume that all genus-zero data is known.
-We assume in addition that we know the genus one reduced theory of $X$.
-The structure of the recursion is then as follows:
-
-\begin{algorithm}
-\DontPrintSemicolon
-\For{$d \geq 0$}{
-\For{$n \geq 0$}{
-\For{$t \geq 0$\medskip}{
-\textbf{\, Step 1: } Compute forgetful relative invariants of $(X,Y)$ (degree~$d$, $n+1$ true markings, true tangency $t$); see below.
-}
-\medskip \textbf{Step 2: } Compute absolute invariants of $Y$ (degree $d$, $n$ markings).\;
-\For{$t \geq 0$\medskip}{
-\textbf{\, Step 3: } Compute relative invariants of $(X,Y)$ (degree $d$, $n$ true markings, true tangency $t$).\;
-}
-}
-\For{$n \geq 0$\medskip}{
-\For{$m \geq 0$\medskip}{
-\textbf{\, Step 4: } Compute rubber invariants of $P$ (degree $d$, $n$ relative markings, $m$ non-relative markings).
-}
-}
-}
-\end{algorithm}
-\noindent Although the loops involving $d, n$ and $m$ have infinite length, in order to compute any single invariant it is only necessarily to iterate the preceding loops for a finite amount of time.
-A \textbf{forgetful relative invariant} of $(X,Y)$ is by definition a reduced relative invariant with a marked point $x_0$ such that all of the insertions are pulled back along $\fgt_{x_0}$.
-In our recursion, we first deal with this special class of relative invariants (with $n+1$ true markings), before computing the absolute invariants (with $n$ markings) and then returning to compute all of the relative invariants (with $n$ true markings).
-This need to treat separately a particular subclass of the relative invariants is an inescapable feature of the genus one recursion.
-
-The base terms of the recursion all have $d=0$ and as such are easy to compute: the relative invariants of $(X,Y)$ are nothing but absolute invariants of $X$, the absolute invariants of $Y$ are given by obstruction bundle integrals over Deligne--Mumford spaces, and the  rubber invariants of $P$ are also given by integrals over Deligne--Mumford spaces, using the formula for the double ramification cycle \cite{Hain,JPPZ} in terms of tautological classes.
-We will now explain how to perform each of the four inductive steps outlined above.
-
-\begin{notation}Given tuples $\mathbf{a}=(a_1,\ldots,a_n)$ and $\mathbf{b}=(b_1,\ldots,b_n)$, we say that $\mathbf{a}<\mathbf{b}$ if there exists an $i \in \{1,\ldots,n\}$ such that $a_j = b_j$ for $j < i$ and $a_i < b_i$.\end{notation}
-
-\subsection*{Step 1} Suppose we are given a forgetful relative invariant to compute.
-That is, we have a relative space $\VZ_{1,\alpha}(X|Y,\beta)$ of degree $d$, with $n+1$ true markings and true tangency $t$, and a marking $x_0$ such that the insertion $\gamma$ is pulled back along $\fgt_{x_0}$.
-We assume inductively that every absolute, relative and rubber invariant with $(d^\prime,n^\prime) < (d,n)$ is known, and also that every forgetful relative invariant with $(d^\prime,n^\prime,t^\prime) < (d,n+1,t)$ is known.
-Choose a true marking $x_1$ with $\alpha_1 \geq 1$ and consider the space:
-\begin{equation*} \VZ_{1,(\alpha-e_1) \cup (1)}(X|Y,\beta). \end{equation*}
-Denote the newly-introduced marking by $y$ and consider the integrand $\tilde\gamma$ obtained from $\gamma$ by introducing $\fgt_y^\st$ everywhere. Applying our recursion formula to $x_1$, we obtain:
-\begin{equation}\label{step 1 recursion}\left( (\alpha_1-1)\psi_1 + \ev_1^\st Y\right) \tilde\gamma \cap [\VZ_{1,(\alpha-e_1) \cup (1)}(X|Y,\beta)] = \tilde\gamma \cap [\Dcal(1)].\end{equation}
-Let us first examine the left-hand side.
-The class $\psi_1$ differs from $\fgt_y^\st \psi_1$ by the locus where $x_1$ and $y$ are contained on a contracted rational bubble.
-This locus consists of reduced relative stable maps of the form \medskip
-
-\begin{center}
-\begin{tikzpicture}[scale=1]
-%edge
-\draw (0,0) to (2,0);
-\draw [color=blue] (1,0) node[above]{\tiny$\alpha_1$};
-
-%C_1
-\draw [fill=white] (0,0) circle[radius=3pt];
-\draw (0,-0.1) node[below]{\small$d$};
-\draw (0,0) node[above]{\small$\sqC_1$};
-
-%C_0
-\draw [fill=black] (2,0) circle[radius=3pt];
-\draw (2,-0.1) node[below]{\small$0$};
-\draw (2,0) node[above]{\small$\sqC_0$};
-
-%x_1
-\draw [->] (2,0.1) -- (4,0.1);
-\draw (3.9,0.1) node[above]{\small$x_1$};
-\draw [color=blue](3,0.1) node[above]{\tiny$\alpha_1-1$};
-
-%y
-\draw [->] (2,-0.1) -- (4,-0.1);
-\draw (3.9,-0.1) node[below]{\small$y$};
-\draw [color=blue] (3,-0.1) node[below]{\tiny$1$};
-
-%down arrow
-\draw [color=blue,->] (1,-0.3) -- (1,-0.7);
-
-%target
-\draw [color=blue,->] (0,-1) to (2,-1);
-\draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
-\draw [color=blue] (2,-1) node[right]{\small$\Sigma(X|Y)$};
-\end{tikzpicture}
-\end{center}
-% Algebro-geometric picture; replaced by tropical picture.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{comment}
-\begin{center}
-\begin{tikzpicture}[scale=1.5]
-%Draw target
-\draw (0,0) -- (3,0) -- (3,2) -- (0,2) -- (0,0);
-\draw (3,0) -- (6,0) -- (6,2) -- (3,2) -- (3,0);
-
-%Draw genus one curve on left-hand side
-\draw [blue] (3,0.5) to [out=90,in=270] (2.7,1) to [out=90,in=270] (3,1.5) to [out=90,in=0] (1,1.7) to [out=180,in=90] (0.5,1) to [out=270,in=180] (1,0.3) to [out=0,in=270] (3,0.5);
-\draw [blue] (1.1,0.9) to [out=40, in=180] (1.4,1.1) to [out=0,in=140] (1.7,0.9);
-\draw [blue] (1.2,1) to [out=300, in=180] (1.4,0.9) to [out=0,in=240] (1.6,1);
-
-%Draw nodal blobs
-\draw [fill=blue,color=blue] (3,0.5) circle[radius=1pt];
-\draw [color=blue] (3,0.5) node[left]{\small$\alpha_2$};
-\draw [fill=blue,color=blue] (3,1.5) circle[radius=1pt];
-\draw [color=blue] (3,1.5) node[left]{\small$\alpha_1$};
-%Draw rational bubble with x_1 and y
-\draw [blue] (3,1.5) to [out=70,in=190] (5.5,1.9) to [out=0,in=90] (6,1.8) to [out=270,in=90] (5.75,1.5) to [out=270,in=90] (6,1.2) to [out=270,in=10] (5.5,1.1) to [out=180,in=290] (3,1.5);
-
-%Draw right-hand markings
-\draw [fill=blue,color=blue] (6,1.8) circle[radius=1pt];
-\draw [color=blue] (6,1.8) node[left]{\small{$\alpha_1-1$}};
-\draw (6,1.8) node[right]{$x_1$};
-\draw [fill=blue,color=blue] (6,1.2) circle[radius=1pt];
-\draw [color=blue] (6,1.2) node[left]{\small{$1$}};
-\draw (6,1.2) node[right]{$y$};
-
-%Draw ldots
-\draw [color=blue] (4,0.5) node[right]{$\ldots$};
-\end{tikzpicture}
-\end{center}
-\end{comment}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-with all other marked points contained on $\sqC_1$.
-This is isomorphic to $\VZ_{1,\alpha}(X|Y,\beta)$ and when we restrict $\tilde\gamma$ to this locus we obtain precisely the class $\gamma$ which we started with.
-Thus the left-hand side of \eqref{step 1 recursion} may be written as
-\begin{equation*} (\alpha_1-1) I + \fgt_y^\st \left( (\alpha_1-1)\psi_1 + \ev_1^\st Y\right)  \tilde\gamma \cap [\VZ_{1,(\alpha-e_1)\cup(1)}(X|Y,\beta)]\end{equation*}
-where $I$ is the invariant we are trying to compute.
-The second term is a forgetful relative invariant with the same degree and number of true markings (since $y$ is fictitious), and strictly smaller true tangency; hence it is recursively known.
-We now examine the right-hand side of \eqref{step 1 recursion}.
-Recall that all of the genus zero data has already been computed, so we only need to focus on the genus one pieces.
-First consider the type $A$ loci.
-The genus one piece has strictly smaller degree (and hence is recursively known) exept in the following situation (with some stable distribution of the remaining markings):
-\begin{center}
-\begin{tikzpicture}[scale=1]
-\draw (0,0) to (2,0);
-\draw [fill=white] (0,0) circle[radius=3pt];
-\draw (0,-0.1) node[below]{\small$d$};
-\draw (0,0) node[above]{\small$\sqC_1$};
-\draw [fill=black] (2,0) circle[radius=3pt];
-\draw (2,-0.1) node[below]{\small$0$};
-\draw (2,0) node[above]{\small$\sqC_0$};
-\draw [->] (2,0) -- (3,0);
-\draw (2.9,0) node[right]{$x_1$};
-
-\draw [color=blue,->] (1,-0.3) -- (1,-0.7);
-
-\draw [color=blue,->] (0,-1) to (2,-1);
-\draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
-\draw [color=blue] (2,-1) node[right]{\small$\Sigma(X|Y)$};
-\end{tikzpicture}
-\end{center}
-In this situation, $C_1$ contains at most $n+1$ true markings.
-If it has $n-1$ or fewer, than it is known recursively.
-If it has exactly $n$ this means that $C_0$ contains exactly one true marking (besides $x_1$, which may be true or fictitious).
-We claim that in this situation we must have $y \in C_1$, since otherwise we would have a moduli space for $C_0$ given by $\ol\Mcal_{0,k}$ with $k \geq 4$, and  applying the projection formula with $\fgt_y$ we would conclude that the contribution is zero.
-Thus we have $y \in C_1$, and so the genus one contribution is a forgetful relative invariant with $n$ true markings, and hence is recursively known.
-
-Finally, if $C_1$ contains exactly $n+1$ true markings, then the only additional markings on $C_0$ are fictitious, and by the same argument as in the previous paragraph there can only be one.
-Thus for each fictitious marked point we obtain a locus isomorphic to $\VZ_{1,\alpha}(X|Y,\beta)$ and $\tilde\gamma$ restricts to $\gamma$ here (from the point of view of computing invariants, the fictitious marked points are indistinguishable, meaning that the contributions are all the same).
-Thus for each fictitious marked point (of which there is at least one, namely $y$) we get a contribution of $\alpha_1 I$ to the right-hand side of \eqref{step 1 recursion}.
-
-The contributions of the type $B$ loci only involve genus zero data and hence are known.
-The contributions of the type $C^0$ loci are determined by genus zero data and tautological integrals on Deligne--Mumford space, hence are also known.
-It remains to consider type $C^+$ loci.
-If the degree of the genus one piece is less than $d$ then we have a rubber invariant of strictly smaller degree.
-The only other possibility is that the entire curve is mapped into the divisor.
-In this case we may apply the projection formula with $\fgt_y$ to identify this with an integral over $\VZ_{1,m}(Y,\beta)$ for some (possibly large) number $m$ of marked points.
-But by assumption there is another marked point $x_0$ with all of the insertions pulled back along $\fgt_{x_0}$, so a further application of the projection formula shows that this contribution vanishes.
-To conclude, we may rearrange \eqref{step 1 recursion} to obtain an expression of the form
-\begin{equation*} \lambda I = \text{recursively known terms} \end{equation*}
-where $\lambda$ is an explicit scalar which is always nonzero; we have thus determined $I$, which completes Step 1.
-
-\subsection*{Step 2} Consider now the absolute space $\VZ_{1,n}(Y,\beta)$ with an insertion $\gamma$, and suppose inductively that we have computed all forgetful relative invariants with $(d^\prime,n^\prime) \leq (d,n+1)$, all relative invariants and absolute invariants with $(d^\prime,n^\prime) < (d,n)$, and all special rubber invariants with $d^\prime < d$.
-Consider the following moduli space with $n+1$ markings:
-\begin{equation*} \VZ_{1,(d,0,\ldots,0)}(X|Y,\beta). \end{equation*}
-Let $x_0$ denote the relative marking and consider the integrand $\tilde\gamma$ obtained from $\gamma$ by introducing $\fgt^\st_{x_0}$ everywhere. Now recurse at $x_1$ to obtain:
-\begin{equation}\label{step 2 recursion} \ev_1^\st Y \cdot \tilde\gamma \cap [\VZ_{1,(d,0,\ldots,0)}(X|Y,\beta)] = \tilde\gamma\cap[\Dcal(1)].\end{equation}
-The left-hand side is a forgetful relative invariant of degree $d$ and $\leq n+1$ true markings, and so has already been computed.
-For the right-hand side, let us begin with loci of type $A$.
-The genus one contributions from each loci have $(d^\prime,n^\prime) < (d,n)$ except in the following case
-\begin{center}
-\begin{tikzpicture}[scale=1]
-%edge
-\draw (0,0) to (2,0);
-\draw [color=blue] (1,0) node[above]{\tiny$d$};
-
-%C_1
-\draw [fill=white] (0,0) circle[radius=3pt];
-\draw (0,-0.1) node[below]{\small$d$};
-\draw (0,0) node[above]{\small$\sqC_1$};
-
-%C_0
-\draw [fill=black] (2,0) circle[radius=3pt];
-\draw (2,-0.1) node[below]{\small$0$};
-\draw (2,0) node[above]{\small$\sqC_0$};
-
-%x_1
-\draw [->] (2,0.1) -- (4,0.1);
-\draw (3.9,0.1) node[above]{\small$x_1$};
-\draw [color=blue](3,0.1) node[above]{\tiny$0$};
-
-%y
-\draw [->] (2,-0.1) -- (4,-0.1);
-\draw (3.9,-0.1) node[below]{\small$x_0$};
-\draw [color=blue] (3,-0.1) node[below]{\tiny$d$};
-
-%down arrow
-\draw [color=blue,->] (1,-0.3) -- (1,-0.7);
-
-%target
-\draw [color=blue,->] (0,-1) to (2,-1);
-\draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
-\draw [color=blue] (2,-1) node[right]{\small$\Sigma(X|Y)$};
-\end{tikzpicture}
-\end{center}
-which gives a contribution of
-\begin{equation*} d\cdot \gamma \cap [\VZ_{1,(d,\underbrace{0,\ldots,0}_{n-1})}(X|Y,\beta)] \footnote{(Navid) Fix formatting}\end{equation*}
-to the right-hand side of \eqref{step 2 recursion}.
-Here $\gamma$ is the insertion we started with; the difference is that we are now considering relative maps to $(X,Y)$ with maximal tangency at $x_1$, rather than absolute maps to $Y$.
-The type $B$ and $C^0$ loci are recursively determined as in Step~1, and similarly the type $C^+$ loci are recursively determined except for the locus where the entire curve is mapped into the divisor.
-On this locus we may apply $\fgt_{x_0}$ and identify the contribution with
-\begin{equation*} d^2 \cdot \gamma \cap [\VZ_{1,n}(Y,\beta)] = d^2 \cdot I \end{equation*}
-where $I$ is the invariant we are trying to compute. Putting this all together, we obtain
-\begin{equation}\label{step 2 recursion 2} I = (-\gamma/d) \cap [\VZ_{1,(d,\underbrace{0,\ldots,0}_{n-1})}(X|Y,\beta)] + \text{recursively known terms} \end{equation}
-where on the right-hand side there are $n-1$ non-relative markings $x_2,\ldots,x_n$, and a relative marking $x_1$. We now apply the recursion again to the right-hand side, by considering the space
-\begin{equation*} \VZ_{1,(d-1,1,0,\ldots,0)}(X|Y,\beta) \end{equation*}
-where $x_1$ now has tangency $d-1$ and we have introduced a new marking $y$ with tangency $1$.
-We consider a new insertion, denoted $\tilde\gamma$ as usual, by introducing $\fgt_y^\st$ everywhere.
-Recursing at $x_1$ we obtain:
-\begin{equation}\label{step 2 recursion 2} \left( (d-1)\psi_1 + \ev_1^\st Y \right)\cdot(-\tilde\gamma/d) \cap [\VZ_{1,(d-1,1,0,\ldots,0)}(X|Y,\beta)] = (-\tilde\gamma/d) \cap [\Dcal(1)].\end{equation}
-The difference between $\psi_1$ and $\fgt_y^\st \psi_1$ is given by the locus where $x_1$ and $y$ belong to a collapsed rational bubble:
-\begin{center}
-\begin{tikzpicture}[scale=1]
-%edge
-\draw (0,0) to (2,0);
-\draw [color=blue] (1,0) node[above]{\tiny$d$};
-
-%C_1
-\draw [fill=white] (0,0) circle[radius=3pt];
-\draw (0,-0.1) node[below]{\small$d$};
-\draw (0,0) node[above]{\small$\sqC_1$};
-
-%C_0
-\draw [fill=black] (2,0) circle[radius=3pt];
-\draw (2,-0.1) node[below]{\small$0$};
-\draw (2,0) node[above]{\small$\sqC_0$};
-
-%x_1
-\draw [->] (2,0.1) -- (4,0.1);
-\draw (3.9,0.1) node[above]{\small$y$};
-\draw [color=blue](3,0.1) node[above]{\tiny$1$};
-
-%y
-\draw [->] (2,-0.1) -- (4,-0.1);
-\draw (3.9,-0.1) node[below]{\small$x_1$};
-\draw [color=blue] (3,-0.1) node[below]{\tiny$d-1$};
-
-%down arrow
-\draw [color=blue,->] (1,-0.3) -- (1,-0.7);
-
-%target
-\draw [color=blue,->] (0,-1) to (2,-1);
-\draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
-\draw [color=blue] (2,-1) node[right]{\small$\Sigma(X|Y)$};
-\end{tikzpicture}
-\end{center}
-The contribution of this locus to the left-hand side of \eqref{step 2 recursion 2} is:
-\begin{equation*} (d-1)\cdot(-\gamma/d) \cap [\VZ_{1,(d,\underbrace{0,\ldots,0}_{n-1})}(X|Y,\beta)].\end{equation*}
-What remains on the left-hand side is a forgetful relative invariant of degree $d$ and $\leq n+1$ true markings ($y$ being the ``forgetful'' marking), hence is recursively known.
-On the right-hand side, the type $A$ loci are recursively known except possibly in the following special cases (with some stable distribution of the remaining non-relative markings):
-\begin{center}
-\begin{minipage}{0.4\textwidth}
-\begin{tikzpicture}[scale=1]
-%edge
-\draw (0,-0.1) to (2,-0.1);
-\draw [color=blue] (1,-0.1) node[below]{\tiny$d-1$};
-
-%C_1
-\draw [fill=white] (0,0) circle[radius=3pt];
-\draw (0,-0.1) node[below]{\small$d$};
-\draw (0,0) node[above]{\small$\sqC_1$};
-
-%C_0
-\draw [fill=black] (2,0) circle[radius=3pt];
-\draw (2,-0.1) node[below]{\small$0$};
-\draw (2,0) node[above]{\small$\sqC_0$};
-
-%x_1
-\draw [->] (0,0.1) -- (1.5,0.1);
-\draw (1.5,0.1) node[above]{\small$y$};
-\draw [color=blue](0.75,0.1) node[above]{\tiny$1$};
-
-%y
-\draw [->] (2,0) -- (4,0);
-\draw (3.9,0) node[below]{\small$x_1$};
-\draw [color=blue] (3,0) node[below]{\tiny$d-1$};
-
-%down arrow
-\draw [color=blue,->] (1,-0.5) -- (1,-0.9);
-
-%target
-\draw [color=blue,->] (0,-1) to (2,-1);
-\draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
-\draw [color=blue] (2,-1) node[right]{\small$\Sigma(X|Y)$};
-
-\draw (2,-1.3) node[below]{\small{Case 1}};
-\end{tikzpicture}
-\end{minipage}
-\begin{minipage}{0.4\textwidth}
-\begin{tikzpicture}[scale=1]
-%edge
-\draw (0,0) to (2,0);
-\draw [color=blue] (1,0) node[above]{\tiny$d$};
-
-%C_1
-\draw [fill=white] (0,0) circle[radius=3pt];
-\draw (0,-0.1) node[below]{\small$d$};
-\draw (0,0) node[above]{\small$\sqC_1$};
-
-%C_0
-\draw [fill=black] (2,0) circle[radius=3pt];
-\draw (2,-0.1) node[below]{\small$0$};
-\draw (2,0) node[above]{\small$\sqC_0$};
-
-%x_1
-\draw [->] (2,0.1) -- (4,0.1);
-\draw (3.9,0.1) node[above]{\small$y$};
-\draw [color=blue](3,0.1) node[above]{\tiny$1$};
-
-%y
-\draw [->] (2,-0.1) -- (4,-0.1);
-\draw (3.9,-0.1) node[below]{\small$x_1$};
-\draw [color=blue] (3,-0.1) node[below]{\tiny$d-1$};
-
-%down arrow
-\draw [color=blue,->] (1,-0.3) -- (1,-0.7);
-
-%target
-\draw [color=blue,->] (0,-1) to (2,-1);
-\draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
-\draw [color=blue] (2,-1) node[right]{\small$\Sigma(X|Y)$};
-
-\draw (2,-1.3) node[below]{\small{Case 2}};
-\end{tikzpicture}
-\end{minipage}
-\end{center}
-In Case 1 the contribution from $C_1$ is a forgetful relative invariant with $\leq n$ true markings, hence is recursively known.
-In Case 2, we first note that there cannot be any more markings on $C_0$ (since otherwise we could apply $\fgt_y$ and conclude that the contribution vanishes).
-Thus we obtain a single locus, which contributes precisely
-\begin{equation*} d\cdot(-\gamma/d) \cap [\VZ_{1,(d,\underbrace{0,\ldots,0}_{n-1})}(X|Y,\beta)] = -\gamma\cap[\VZ_{1,(d,\underbrace{0,\ldots,0}_{n-1})}(X|Y,\beta)]\end{equation*}
-which gives us the first term on the right-hand side of \eqref{step 2 recursion 2}.
-As usual the type $B$ and $C^0$ contributions are known recursively, and the only type $C^+$ contribution not known recursively occurs when the entire curve is mapped into the divisor, in which case we apply $\fgt_y$ to calculate the contribution as:
-\begin{equation*} (-\gamma/d) \cap [\VZ_{1,n}(Y,\beta)] = -I/d.\end{equation*}
-Substituting into \eqref{step 2 recursion 2} we end up with
-\begin{equation*} I(1-d^{-1}) = \text{recursively known terms} \end{equation*}
-which completes the recursion step as long as $d \neq 1$.
-But since $\VZ_{1,n}(H,1)=\emptyset$ it follows that $\VZ_{1,n}(Y,\beta)=\emptyset$ if $d=Y\cdot\beta=1$, so we may always assume $d \geq 2$ in the recursion.
-
-\subsection*{Step 3} Now suppose we are given a relative space $\VZ_{1,\alpha}(X|Y,\beta)$ with an insertion $\gamma$, and suppose inductively that we have computed all forgetful relative invariants with $(d^\prime,n^\prime) \leq (d,n+1)$, all absolute invariants with $(d^\prime,n^\prime) \leq (d,n)$, all relative invariants with $(d^\prime,n^\prime,t^\prime)<(d,n,t)$ and all rubber invariants with $d^\prime < d$.
-Choose a true marking $x_1$ with $\alpha_1 \geq 1$ and consider the moduli space
-\begin{equation*} \VZ_{1,(\alpha-e_1)\cup(1)}(X|Y,\beta) \end{equation*}
-where $y$ is the newly-introduced marking. As usual consider the insertion $\tilde\gamma$ obtained from $\gamma$ by introducing $\fgt_y$ everywhere. Recursing at $x_1$ we obtain:
-\begin{equation*} \left( (\alpha_1-1)\psi_1 + \ev_1^\st H\right) \tilde\gamma \cap [\VZ_{1,(\alpha-e_1)\cup(1)}(X|Y,\beta)] = \tilde\gamma \cap [\Dcal(1)].\end{equation*}
-The left-hand side is a relative invariant with the same degree and number of true markings, but smaller true tangency: hence it is recursively known.
-On the right-hand side, the type $A$ contributions are recursively known except for those of the following form
-
-\begin{center}
-\begin{tikzpicture}[scale=1]
-\draw (0,0) to (2,0);
-\draw [color=blue] (1,-0.05) node[above]{\tiny$\alpha_1$};
-\draw [fill=white] (0,0) circle[radius=3pt];
-\draw (0,-0.1) node[below]{\small$d$};
-\draw (0,0) node[above]{\small$\sqC_1$};
-\draw [fill=black] (2,0) circle[radius=3pt];
-\draw (2,-0.1) node[below]{\small$0$};
-\draw (2,0) node[above]{\small$\sqC_0$};
-\draw [->] (2,0) -- (4,0);
-\draw (3.9,0) node[right]{$x_1$};
-\draw [color=blue] (3,-0.05) node[above]{\tiny$\alpha_1-1$};
-
-\draw [color=blue,->] (1,-0.3) -- (1,-0.7);
-
-\draw [color=blue,->] (0,-1) to (2,-1);
-\draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
-\draw [color=blue] (2,-1) node[right]{\small$\Sigma(X|Y)$};
-\end{tikzpicture}
-\end{center}
-where $C_0$ contains a single fictitious marking (if it had multiple fictitious markings then the contribution would vanish by projection formula) and all the other markings are on $C_1$.
-Thus for each fictitious marking we get a contribution of $\alpha_1 I$ where $I$ is the invariant we are trying to compute.
-Note that $\alpha_1 \neq 0$, and that this term appears at least once since $y$ is a fictitious marking; so we get a nonzero multiple of $I$.
-
-As usual the type $B$ and $C^0$ contributions are recursively known.
-The type $C^+$ contributions are determined by lower-degree rubber invariants, except for when the whole curve is mapped into $Y$; however in this case we may apply $\fgt_y$ to identify the contribution with an absolute invariant of $Y$ with degree $d$ and $n$ markings, which is also recursively known.
-Thus we have determined the invariant $I$.
-
-\subsection*{Step 4} Finally, consider a rubber space $\VZ_{1,\alpha}(P|Y_0+Y_\infty,\beta)_{\Gm}$ with insertion $\gamma$.
-Suppose inductively that we have computed all absolute and relative invariants with $d^\prime \leq d$ and all rubber invariants with $(d^\prime,n^\prime,m^\prime) < (d,n,m)$.
-
-We first note the following important reduction: if there exists a relative marking $x_k$ such that all insertions are pulled back along $\fgt_{k}$, then we may apply the projection formula, together with the fact that
-\begin{equation*} (\fgt_{k})_\st [\VZ_{1,\alpha}(P|Y_0+Y_\infty,\beta)_{\Gm}] = \alpha_k^2 \cdot [\VZ_{1,n+m-1}(Y,\beta)] \end{equation*}
-to identify the rubber invariant with a multiple of a reduced invariant of $Y$, which has the same degree and hence is known recursively.
-
-We will deal with the general case by reducing to the one above. Consider the moduli space
-\begin{equation*}\label{step 4 recursion space} \VZ_{1,\alpha\cup (0)}(P|Y_0+Y_\infty,\beta)_{\Gm}\end{equation*}
-obtained by introducing a marked point $y$ with no tangency.
-Let $x_1$ be a positive-tangency marking (such a marking always exists since $d \geq 2$) and let $\tilde\gamma$ be the insertion obtained from $\gamma$ by replacing $\ev_1$ and $\psi_1$ by $\ev_y$ and $\psi_y$, and then introducing $\fgt_{1}^\st$ everywhere.
-
-We will make use of a recursion formula for rubber spaces analogous to the recursion formula for relative spaces used in Steps 1--3.
-Following \cite{EKatz}, there is a line bundle $L_y^{\not\in \operatorname{bot}}$ on $\VZ_{1,\alpha\cup (0)}(P|Y_0+Y_\infty,\beta)_{\Gm}$, together with a section $s_y^{\not\in\operatorname{bot}}$ whose vanishing locus consists of the locus $\Dcal(y)$ of rubber maps where $y$ is not mapped into the bottom level of the expanded target.
-As in \S \ref{}, we can give a logarithmic interpretation of this: it corresponds to the piecewise-linear function on the tropical moduli space which associates, to every rubber tropical map, the distance between $\varphi(\sqC_y)$ and the leftmost vertex of the tropical target, where $\sqC_y$ is the vertex of the source curve containing the flag corresponding to $y$.
-Using this tropical description, we may easily calculate the vanshing orders of $s_y^{\not\in\operatorname{bot}}$ along the various components of $\Dcal(y)$, and show that $\cchern_1(L_y^{\not\in\operatorname{bot}}) = \Psi_0 - \ev_y^\st Y$ (see also \cite{EKatzLB}, where similar results in the non-reduced setting are obtained, using different methods).
-From this, we obtain a rubber recursion formula
-\begin{equation}\label{step 4 recursion} (\Psi_0 - \ev_y^\st Y) \tilde\gamma \cap [\VZ_{1,\alpha\cup(0)}(P|Y_0+Y_\infty,\beta)_{\Gm}] = \tilde\gamma \cap [\Dcal(y)]\end{equation}
-where the fundamental class $[\Dcal(y)]$ is weighted by vanishing orders on the components.
-We will first show that the left-hand side is recursively known.
-By construction the class $\tilde\gamma$ is pulled back via $\fgt_{1}^\st$, and the same is true for $\ev_y^\st Y$.
-It remains to examine $\Psi_0$.
-If there exists a negative-tangency marking $x_2$, then we have \cite[Construction 5.1.17]{GathmannThesis}
-\begin{equation*}\label{Psi0 formula} \Psi_0 = -\alpha_2 \hat\psi_2 - \ev_2^\st Y \end{equation*}
-where $\hat\psi_2$ is a \emph{non-collapsed} psi class.
-(If there are no negative-tangency markings, then the construction given in \cite[\S 1.5.2]{MaulikPandharipande} shows that $\Psi_0=0$.) Now, $\hat\psi_2 - \psi_2$ is given by the loci where $x_2$ belongs to a trivial bubble.
-This entails a splitting of the curve into pieces, each of which contributes a rubber integral.
-Typically each of these pieces will have $(g^\prime,d^\prime,n^\prime,m^\prime) < (1,d,n,m)$ and hence be recursively known.
-The one exception is when all of the genus and degree is concentrated on the top level of the expansion, with the bottom level containing only a single non-relative marking in addition to all the negative-tangency markings.
-But in this case the contribution is a rubber invariant where all of the insertions are pulled back via $\fgt_1^\st$, and hence we may apply the projection formula to identify this with an absolute invariant of $Y$ which is recursively known.
-We conclude that, up to recursively knwon terms, we may replace $\hat\psi_2$ by $\psi_2$ in the left-hand side of \eqref{step 4 recursion}.
-If we now compare $\psi_2$ with $\fgt_1^\st \psi_2$ we see that the difference is given by the locus where $x_1$ and $x_2$ belong to a collapsed rational piece.
-The contribution of this locus consists of rubber invariant with strictly fewer relative markings, and hence is recursively known.
-So up to recursively-known terms \eqref{step 4 recursion} becomes
-\begin{equation*} \fgt_1^\st (-\alpha_2\psi_2 - \ev_y^\st Y)\tilde\gamma \cap [\VZ_{1,\alpha\cup(0)}(P|Y_0+Y_\infty,\beta)_{\Gm}] = \tilde\gamma\cap[\Dcal(y)]\end{equation*}
-and now the left-hand side is also recursively known, by the projection formula.
-Let us now examine the right-hand side.
-The components of $\Dcal(y)$ are indexed by splittings of the curve, and certainly the contributions are recursively known unless there is a piece of the curve carrying all of the genus and degree, so we may restrict to examining these contributions.
-
-Let us denote the piece of the curve carrying all of the genus and degree by $C^\prime\subseteq C$.
-If $C^\prime$ is mapped to top level, then either it contains $x_1$, in which case we apply $\fgt_1$ to compute the contribution, or it does not contains $x_1$, in which case it has fewer than $n$ relative markings and is known recursively.
-If on the other hand $C^\prime$ is not mapped to top level, then generically it is mapped to the bottom level (since generically the circuit is not contracted on this locus, so the desingularisation process does nothing).
-One possible contribution is given by the following locus
-\begin{center}
-\begin{tikzpicture}[scale=1]
-%edge
-\draw (0,0) to (2,0);
-\draw [color=blue] (1,0) node[below]{\tiny$\alpha_1$};
-
-%C_1
-\draw [fill=white] (0,0) circle[radius=3pt];
-\draw (0,-0.1) node[below]{\small$d$};
-
-%y
-\draw [->] (2,0) -- (2,1);
-\draw (2,0.9) node[left]{$y$};
-\draw [color=blue] (2,0.5) node[right]{\tiny$0$};
-
-%x_1
-\draw [->] (2,0) -- (3,0);
-\draw (3,0) node[right]{$x_1$};
-\draw [color=blue] (2.5,0) node[below]{\tiny$\alpha_1$};
-
-%C_0
-\draw [fill=black] (2,0) circle[radius=3pt];
-\draw (2,-0.1) node[below]{\small$0$};
-
-%down arrow
-\draw [color=blue,->] (1,-0.5) -- (1,-0.9);
-
-%target
-\draw [color=blue] (0,-1) to (2,-1);
-\draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
-\draw [fill=blue,color=blue] (2,-1) circle[radius=3pt];
-\draw [color=blue,->] (2,-1) -- (3,-1);
-\draw [color=blue,->] (0,-1) -- (-1,-1);
-\end{tikzpicture}
-\end{center}
-which contributes a nonzero multiple of the invariant $I$ we are trying to compute.
-For the other possibilities, first note that, unless every component at the top level contains a single positive-tangency marking and a single node (together with possibly some tangency-zero markings), then $C^\prime$ has fewer than $n$ relative markings and hence the contribution is known recursively.
-On the other hand, if any non-relative marking other than $y$ is mapped to the top level, $C^\prime$ has $\leq n$ relative markings and less than $m$ non-relative markings, and hence again the contribution is known recursively.
-The only remaining possibilities are when $x_1$ is replaced by another positive-tangency marking $x_k$ in the above picture; but then the contribution can be calculated by applying the projection formula to $\fgt_{1}$.
-We therefore conclude that the only contribution to the right-hand side of \eqref{step 4 recursion} which is not known recursively is a nonzero multiple of the invariant we were trying to compute.
-This completes the recursion step.
-
-\newpage
+%\tableofcontents
 
@@
 
-\newpage
-
-\section{Splitting axiom and recursion formula for $(\PP^N|H)$}
-
-\subsection{Recursive description of the divisors: types $A,B$ and $C^+$}
-
-The basic idea is as follows.
-Choose an irreducible component $\Dcal \subseteq \Dcal(k)$.
-As discussed above, we can obtain this by choosing an ``initial'' combinatorial type together with a ray of the resulting subdivision of the tropical moduli space.
-Without loss of generality we may assume that this ``initial'' combinatorial type coincides with the ``true'' combinatorial type of $\Dcal$ obtained by performing the edge contractions specified by the choice of ray.
-
-Since $\VZ \to \Mcal$ is a log modification, the divisor $\Dcal$ is either exceptional or the proper transform of a logarithmic divisor on $\Mcal$.
-In this subsection, we will focus on the latter case.
-Then if we let $\Dcal_{\Mcal}^\circ\subseteq \Mcal$ denote the locally closed stratum corresponding to our choice of combinatorial type, and $\Dcal_\Mcal = \overline{\Dcal^\circ_\Mcal}$ denote the corresponding logarithmic divisor in $\Mcal$, then our divisor $\Dcal\subseteq\VZ$ is the proper transform of $\Dcal_\Mcal$, which is obtained by taking the preimage $\Dcal^\circ$ of $\Dcal_\Mcal^\circ$ (since $\Dcal^\circ_\Mcal$ is disjoint from the blown-up locus) and then taking its closure in $\VZ$.
-This is, of course, different from taking the preimage of $\Dcal_\Mcal$, since in general $\Dcal_\Mcal$ will intersect the blown-up locus.
-By continuity we have an induced map:
-\begin{equation*} \Dcal \to \Dcal_\Mcal. \end{equation*}
-The remainder of this section will be dedicated to showing how the map $\Dcal \to \Dcal_\Mcal$ may be interpreted as a blow-up.
-The reason this is useful is that $\Dcal_\Mcal$ itself has a recursive description in terms of moduli spaces of punctured maps (see \S \ref{subsection punctured maps}), which in our setting we are able to compute integrals over.
-
-For the remainder of this subsection, we will consider only the situation where the circuit is assigned a positive degree by the combinatorial type; the other, more complicated case, will be taken up in \S \ref{}.
-
-\begin{lemma} Let $\Dcal \subseteq \Dcal(k)$ be an irreducible component and let $\Delta$ be the corresponding combinatorial type.
-Suppose that $\Delta$ assigns positive degree to the circuit.
-Then $\Delta$ takes one of the following forms:
-\begin{figure}[h]
-    \centering
-    \begin{minipage}{0.3\textwidth}
-        \centering
-        \Yagraph
-        \caption{$\mathcal Y_A$}
-    \end{minipage}\hfill
-    \begin{minipage}{0.3\textwidth}
-        \centering
-        \Ybgraph
-        \caption{$\mathcal Y_B$}
-    \end{minipage}\hfill
-    \begin{minipage}{0.3\textwidth}
-        \centering
-        \Ycgraph
-        \caption{$\Ycal_C^+$}
-    \end{minipage}
-\end{figure}
-
-\noindent The terminology is due to Vakil, and the picture in this case is very similar to \cite{Vre} (as we will see later, when the circuit is contracted the picture becomes \emph{very} different).
-Note that in these pictures we have omitted the marked points (apart from $x_k$), the degree of each vertex, and the expansion factors of the edges.
-These combinatorial data can be distributed arbitrarily, as long as:
-\begin{enumerate}
-\item the vertices $\sqC_1,\ldots,\sqC_r$ have positive degree (and $\sqC_0$ has positive degree in the $\Ycal_C^+$ case);
-\item every vertex is stable;
-\item the balancing condition is satisfied.
-\end{enumerate}\end{lemma}
-
-\begin{proof}
-Recall that we have $\Dcal\subseteq\VZ$ obtained by a choice of combinatorial type and ray in the subdivison of the tropical moduli space.
-In this situation, since the circuit has positive degree no alignment is necessary (both radii are zero), and hence the subdivision is trivial.
-Following our procedure, we choose a ray of the tropical moduli space $Q^\vee_{\RR}$.
-Since this is generated by edge lengths, and we are assuming that the initial and generised combinatorial types coincide, we conclude that the tropical moduli space must be $\RR_{\geq 0}$.
-Since we are assuming that $\Dcal \subseteq \Dcal(k)$, we know that the vertex of the tropicalisation which contains the flag $x_k$ must map into the interior $\RR_{>0}\subseteq \RR_{\geq 0}$.
-
-We claim that this is the only vertex of the tropical curve mapped into the interior; if there were more, the positions of their images in $\RR_{> 0}$ would be independent, and thus the tropical moduli space would have dimension $\geq 2$, a contradiction.\footnote{(Luca) Say something about rigid tropical curves as in ACGS and KLR}
-
-Thus there is a single vertex $\sqC_0$ mapped into the interior $\RR_{>0} \subseteq \RR_{\geq 0}$ and a number of vertices $\sqC_1,\ldots,\sqC_r$ mapped onto the vertex $0 \in \RR_{\geq 0}$.
-No pair of $\sqC_1,\ldots,\sqC_r$ can be connected by an edge, since this would introduce an extra edge length to the tropical moduli space, which then once again would have dimension $\geq 2$.
-Each of $\sqC_1,\ldots,\sqC_r$ must have positive degree by the tropical balancing condition and must be connected to $\sqC_0$ (since the tropical curve must be connected).
-
-Thus, we see that the combinatorial type takes the form of a bipartite graph, with $\sqC_0$ on the right-hand side and $\sqC_1,\ldots,\sqC_r$ on the left-hand side.
-Note that the continuity of the tropical map identifies all of the edge lengths, up to weights given by the expansion factors (i.e.
-tangency orders) at the edges; thus the tropical moduli space is isomorphic to $\RR_{\geq 0}$ and so we have a divisor as expected.
-
-We distinguish three cases, depending on the position of the circuit, giving the three forms presented in the statement of the lemma.\end{proof}
-
-We now now investigate the three types $A,B,C^+$ separately, giving a recursive description of the boundary locus in each case.
-
-\subsubsection{Type $A$} Let $\Delta$ be a combinatorial type of type $A$ and let $\Dcal\subseteq\VZ$ be the corresponding logarithmic divisor (note there is no choice of ray here).
-The corresponding locus $\Dcal_\Mcal\subseteq\Mcal$ is given (up to a finite cover) by\footnote{(Navid) Include short appendix on integralisation/saturation when gluing punctured maps in our setting?}:
-\begin{equation*}\Dcal_\Mcal=\Mpunct{0}{\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}{H}{d_0}\times_{H^r}\left( \Mlog{1}{\alpha^{(1)}\cup(m_1)}{\PP^N|H}{d_1} \times \prod_{i=2}^r\Mlog{0}{\alpha^{(i)}\cup(m_i)}{\PP^N|H}{d_i} \right).
-\end{equation*}
-\begin{lemma}We have the following description of $\Dcal$\begin{equation}\label{type A splitting axiom}\Dcal=\Mpunct{0}{\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}{H}{d_0}\times_{H^r}\left(\VZ_{1,\alpha^{(1)}\cup(m_1)}(\PP^N|H,d_1)\times\prod_{i=2}^r\Mlog{0}{\alpha^{(i)}\cup(m_i)}{\PP^N|H}{d_i}\right) \end{equation}
-i.e. the map $\Dcal\to\Dcal_\Mcal$ is given by blowing up one of the factors of the fibre product.\end{lemma} Note that there is a birational map which forgets the log structures
-\begin{equation*} \Mpunct{0}{\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}{H}{d_0} \to \M{0}{n_0+r}{H}{d_0} \end{equation*}
-and all of our insertions are pulled back from the latter space. Therefore the integrals over the punctured space are determined by the genus zero Gromov--Witten theory of $H\cong\PP^{N-1}$.
-
-%DEPRECATED?/WRONG?
-
-%Note that if $\sqC_0$ degenerates further then it may be the case that there are components of $\sqC_0$ contained inside the contraction radius for $\sqC$, and thus once we contract to a Smyth curve there are components of $\sqC_0$ adjacent to the genus one singularity.
-However, in this case when we split off $\sqC_1$ these components disappear, and if the factorisation condition holds for $\sqC$ then it holds a fortiori for $\sqC_1$.\footnote{(Navid) I think this is right, but could someone check?
-Maybe there's a better way to say this.} Thus we obtain a morphism from $\Dcal$ to the fibre product on the right-hand side of \eqref{type A splitting axiom}.
-\begin{proof}
-Note first of all that the map $\Dcal\to\Dcal_\Mcal$ is an isomorphism away from the blown-up locus, which is contained inside the locus where the circuit is contracted.
-Given an element of $\Dcal$ we can split it along the nodes $q_1,\ldots,q_r$ as in \cite{PuncturedMaps}.
-It is then clear that $\sqC_1$ is aligned.
-We claim that $\sqC$ satisfies the factorisation property if and only if $\sqC_1$ does.
-This is enough to show \eqref{type A splitting axiom}.
-
-On $\sqC$ there is an associated contraction radius $\delta$ passing through a non-contracted vertex, such that the strict interior only contains contracted vertices.
-\begin{lemma}\label{type A radius lemma}$\lambda(\sqC^\prime) > \delta$ for any component $\sqC^\prime$ of $\sqC_0$.\end{lemma}
-\noindent Assuming this holds, we see as a consequence that $\sqC_0,\sqC_2,\ldots,\sqC_r$ must lie outside the contraction radius.
-Consequently the aligned curve $\sqC$ satisfies the factorisation condition if and only if $\sqC_1$ does, so \eqref{type A splitting axiom} holds.
-
-\begin{proof} The basic point is that $\Dcal$ consists of the union of the locally closed logarithmic strata adjacent to the locally closed stratum where all the $\sqC_i$ are irreducible.
-If we look at one of these boundary strata, the tropical moduli space contains a ray $\sigma$ corresponding to the stratum where all the $\sqC_i$ are irreducible; this amounts to setting all edge lengths other than $e_1,\ldots,e_r$ to zero.
-If $f_1,\ldots,f_l$ are some number of these additional edge lengths (corresponding to internal nodes in degenerations of the $\sqC_i$) then all of the cones of the subdivision adjacent to $\sigma$ will have $f_1+\ldots+f_l < e_j$ for all $j\in\{1,\ldots,r\}$, since $f_1=\ldots=f_l=0$ and $e_j \neq 0$ on $\sigma$.
-In particular, if $\sqC_1$ is degenerate and if $f$ denotes the minimal distance from the circuit to a non-contracted vertex of $\sqC_1$ (which certainly exists since $\sqC_1$ has positive degree) then $f < e_1 \leq \lambda(\sqC^\prime)$.
-Thus $\delta=f$ and $\delta < \lambda(\sqC^\prime)$ as claimed.\footnote{(Navid) Do an example?}\end{proof}
-\noindent Notice we did not specify whether $\delta$ was the relative or absolute radius.
-The point is that it does not matter; the proof goes through the same in either case.
-Thus we see that $\sqC$ satisfies the (double) factorisation condition if and only if $\sqC_1$ does.\end{proof}
-
-\subsubsection{Type $B$}
-Now let $\Dcal\subseteq\VZ$ be a component of $\Dcal(k)$ with combinatorial type $\Delta$ of type $B$.
-In this case, it is impossible for the circuit to be contracted.
-Thus, $\Dcal_\Mcal \subseteq \Mcal$ is disjoint from the blown-up locus, and the map
-\begin{equation*} \Dcal \to \Dcal_\Mcal \end{equation*}
-is an isomorphism. Thus we obtain:
-\begin{equation*} \Dcal = \Mpunct{0}{\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}{H}{d_0}\times_{H^r}\left(\Mlog{0}{\alpha^{(1)}\cup(m_1,m_2)}{\PP^N|H}{d_1}\times\prod_{i=3}^r\Mlog{0}{\alpha^{(i)}\cup(m_i)}{\PP^N|H}{d_i}\right).\end{equation*}
-As before, the integrals over the punctured space are determined by the Gromov--Witten theory of $H$.
-
-\subsubsection{Type $C^+$} Finally let $\Dcal \subseteq \VZ$ be a component of $\Dcal(k)$ with combinatorial type $\Delta$ of type $C^+$. The corresponding locus in $\Mcal$ can be written as:
-\begin{equation*} \Dcal_\Mcal = \Mpunct{1}{\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}{H}{d_0} \times_{H^r} \left( \prod_{i=1}^r \Mlog{0}{\alpha^{(i)}\cup(m_i)}{\PP^N|H}{d_i} \right). \end{equation*}
-Then the same argument as in Lemma \ref{type A radius lemma} shows that given any point in $\Dcal$ the interior of the radius can only contain components of $C_0$.
-Thus the alignment and factorisation condition apply exclusively to $C_0$, which shows that:
-\begin{equation*}\Dcal = \VZ^{\operatorname{punct}}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(H,d_0) \times_{H^r} \left( \prod_{i=1}^r \Mlog{0}{\alpha^{(i)}\cup(m_i)}{\PP^N|H}{d_i} \right).
-\end{equation*}
-Here the first factor
-\begin{equation*}\VZ^{\operatorname{punct}}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(H,d_0) \end{equation*}
-is the logarithmic blow-up of the moduli space of punctured maps, obtained by imposing an alignment and factorisation condition.
-To be more precise: its elements consist of punctured maps to $H$ which are aligned in the sense of Definition \ref{}, and satisfy the (double) factorisation condition (simply replace $\PP^N$ by $H$ everywhere in that definition).
-As in \S \ref{}, this construction produces a closed substack of a logarithmic modification
-\begin{equation*} \VZ^{\operatorname{punct}}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(H,d_0)\subseteq \widetilde{\VZ}^{\operatorname{punct}}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(H,d_0) \xrightarrow{\psi} \Mpunct{1}{\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}{H}{d_0} \end{equation*}
-
-\begin{lem} The logarithmic modification $\psi$ restricts to a birational map:
-\begin{equation*}\VZ^{\operatorname{punct}}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(H,d) \to \ol\Mcal^{\operatorname{punct},\circ}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(H,d).\end{equation*}
-\end{lem}
-Note that the latter space (the main component of the moduli space of punctured maps) is birational to the main component of the double ramification locus.
-In Lemma \ref{Lemma forget marking} below we explain how to compute integrals over this.cd
-\begin{proof}
-If it is true, we might be able to prove it via deformation theory.
-For this it might be useful to notice that there is a morphism $\Mpunct{g}{\alpha}{H}{d}\to \Mpunct{g}{\alpha}{\PP^N}{d}$ (because $H\subseteq\PP^N$ is strict), which is probably a closed immersion, and the loci with smooth source curve are isomorphic under this map.
-It seems plausible that the main omponent is log smooth over $B\Gm\subseteq[\Aaff^1/\Gm]$ (or the standard log point).
-\end{proof}
-
-%We probably want the latter statement to hold under imposing alignment and factorisation (keeping the log structure on the source curve, but forgetting that the map is log).
-Integrals over the main component of the double ramification locus can be computed using the following lemma.
-\begin{lem} \label{Lemma forget marking}The morphism which forgets a marking
-\begin{equation*} \fgt_i\colon\ol\Mcal_{1,n}^{\alpha,\circ}(H,d)\to\ol\Mcal^{\circ}_{1,n-1}(H,d)\end{equation*}
-is generically finite, of degree $\alpha_i^2$ (except in one special case, described in the proof).
-\end{lem}
-\begin{proof}
- Let us consider the case $d=0$ first.
-We may assume the source curve is smooth elliptic $E$.
-The map \[ \phi\colon E\to \Pic^0(E),\qquad x\mapsto\OO_E\left(\alpha_ix+\sum_{j=1,\ldots,\hat i\ldots,n}\alpha_jp_j\right)\]
- is an isogeny of degree $\alpha_i^2$.
-The locus of $(C,p_1,\ldots,\hat{p_i},\ldots,p_n)$ such that the kernel of $\phi$ contains one of the points $\{p_1,\ldots,\hat{p_i},\ldots,p_n\}$ is itself a double ramification locus inside $\oM_{1,n}$, hence non-generic - with one exception: namely, when $n=2$, $x=p_1$ is always a solution, but the curve lying above such point bubbles off a $\PP^1$.
-To see that it does not belong to the closure of the nice locus, notice that the rational function trivialising $\OO_C(\alpha_1p_1-\alpha_2p_2)$ should descend to the cusp, thus having a ramification point at the node; yet its ramification profile is determined by Riemann-Hurwitz, and it is entirely supported on $p_1$ and $p_2$.
-
- For a different proof: notice that we should obtain the class of the main component from the full double ramification cycle by subtracting the boundary class $[D_{1,\emptyset|0,\{1,\ldots,n\}}]$.
-The latter pushes forward to $0$ under $\fgt_i$, unless $n=2$.
-Therefore we may apply $\fgt_{i,*}$ to the Hain-Pixton formula:
- \[DR_1(A)=\frac{1}{2}\left(\sum_{i=1}^na_i^2\psi_i-\sum_{\substack{I\subseteq\{1,\ldots,n\}\\|I|\geq 2}}a_I^2[D_{1,I^c|0,I}]-\frac{1}{12}\delta_0\right),\]
- where $a_I=\sum_{i\in I}a_i$ and $\delta_0=\operatorname{glue}_*([\oM_{0,n+2}])$.
-From $\psi_j=\fgt_i^\st\psi_j+[D_{i,j}]$ for $i\neq j$, and the dilaton equation, we see that $\fgt_{i,*}\psi_j=1$ and $\fgt_{i,*}\psi_i=n-1$.
-On the other hand, the only surviving boundary classes are $[D_{i,j}]$, and they push down to $1$.
-Hence the formula pushes down to $\frac{1}{2}\left(\sum_{j\neq i}\alpha_j^2+(n-1)\alpha_i^2-\sum_{j\neq i}(\alpha_j+\alpha_i)^2\right)=-\alpha_i\left(\sum_{j\neq i}\alpha_j\right)=\alpha_i^2.$
-\end{proof}
-
-\newpage
-
-\begin{definition} A combinatorial type $\Delta$ of a tropical curve consists of the following data:
-\begin{enumerate}
-\item $G$ a finite graph, with a set $V(G)$ of vertices, a set $F(G)$ of flags and an involution $\iota \colon F(G) \to F(G)$ with $\iota^2=\Id$.
-We let $L(G)$ denote the fixed set of $\iota$, and think of its elements as infinite legs; we let $E(G)$ denote the set of equivalence classes of elements not fixed by $\iota$, and think of them as finite edges connecting two (possibly equal) vertices of $G$;
-\item a genus assignment $g \colon V(G) \to \Z_{\geq 0}$;
-\item a degree assignment $\deg \colon V(G) \to \Z_{\geq 0}$;
-\item a weight assignment $u \colon F(G)  \to \Z$ such that for every edge $e \in E(G)$ we have $u(f_1)=-u(f_2)$ where $e=[f_1]=[f_2]$, and $u(l) \geq 0$ for any $l \in L(G)$;
-\end{enumerate}
-\end{definition}
-
-\footnote{(Luca) to be made homogeneous with what comes earlier} Review here the process of gluing for punctured maps.
-In particular the basic monoid should be modified in order to make the relevant evaluations log morphisms.
-Claim: evaluations are strict.
-Consequence: the fiber product in the category of log stacks is fine.
-We have then to apply saturation.
-This is a finite morphism of degree...
-(I think it could be $\frac{\prod m^{(i)}}{lcm(m^{(i)})}$).
-
-\begin{lemma}[Virtual pushforward] The following hold.
- \begin{itemize}
-  \item $\fgt_*[\M{0}{\alpha}{\PP^N|H}{d}]=[\MG{0}{\alpha}{\PP^N|H}{d}]$ (follows from \cite{GathmannThesis,AbramovichMarcusWiseComparison}).
-  \item $\fgt_*[\VZc{1}{\alpha}{\PP^N|H}{d}]$ computes the reduced relative invariants by definition.
-  \item $\fgt_*[\M{0}{\mu}{H}{d_0}^\sim]=[\M{0}{\lvert\mu\rvert}{H}{d_0}]$ (follows from \cite{GathmannThesis} and... comparison of punctured with rubber invariants).
-  \item $\fgt_*[\VZc{1}{\mu}{H}{d_0}^\sim]$ here we should need a variation on Pixton's DRC formula; hopefully it's enough to avoid the graphs that tropical well-spacedness discards.
- \end{itemize}
-\end{lemma}
-
-\subsection{Recursive description of the divisors: type $C_0$} Consider now a combinatorial type $\Delta$ such that the circuit is contracted into the divisor.
-The corresponding stratum $\Dcal_\Mcal \subseteq \Mcal$ is contained in the blown-up locus.
-Our task is to identify the logarithmic divisors in the preimage of $\Dcal_\Mcal$ under the map $\VZ \to \Mcal$.
-As discussed, these are indexed by choices of ray in the subdivision of the tropical moduli space.
-Suppose we have fixed such data.
-
-\begin{claim} The teeth of the comb can break at most once, along the circuit.\end{claim}
-
-\begin{proof} If not there would be more parameters in the tropical moduli space. \end{proof}
-
-\begin{prop} Let $\Delta$ be a combinatorial type as above. Then:
-\begin{enumerate}
-\item the circuit is a single vertex, and is mapped to the interior $\RR_{>0} \subseteq \RR_{\geq 0}$;
-\item the degree of the circuit is zero;
-\item there is a vertex which is adjacent to the circuit and mapped to the interior $0 \in \RR_{\geq 0}$;
-\item let $e \in E(\sqC)$ be an edge which is adjacent to the circuit, and such that $u(e)$ is maximal among the edges adjacent to the circuit.
-Then the other vertex $v$ contained in $e$ is mapped to $0 \in \RR_{\geq 0}$, and $v$ lies on the (absolute) radius;
-\item if $v \in V(\sqC)$ and $\lambda(v) > \delta$ then $f(v)=0$.
-\end{enumerate}
-\end{prop}
-
-On the other hand, when there is a contracted elliptic subcurve - and it will be contracted into the hyperplane, because otherwise it wouldn't be generic, by density of the nice locus in $\VZ_{1,\alpha^\prime}(\PP^N|H,d^\prime)$ - the picture becomes more complicated due to the alignment.
-The combs may break.
-We label these loci $\mathcal{Y}_C^0$.
-\begin{figure}
-
- \tikz{
- \draw[red] (2,0) circle(2); %circle
- \draw (0,0) circle(2pt)[fill=black] (0,2) circle(2pt)[fill=black] (0,4) circle(2pt)[fill=black] (0,6) circle(2pt)[fill=black] (0,-2) circle(2pt)[fill=black] (1.1,1.78) circle(2pt)[fill=black] (3.42,1.42) circle(2pt)[fill=black] (.58,-1.42) circle(2pt)[fill=black] (0,1) circle(2pt)[fill=black]; %black vertices
- \draw (2,0) -- node[above]{4} (0,0) (2,0) --node[above]{2} (1.1,1.78) --node[above]{1} (0,2) (1.1,1.78) --node[above]{1} (0,4) (2,0) --node[above]{1} (3.42,1.42) (2,0) --node[above]{3} (.58,-1.42) (3.42,1.42) --node[above]{5} (0,6) (.58,-1.42) --node[above]{1} (0,-2) (2,0) -- node[above]{2} (0,1); %edges
- \draw (.58,-1.42) -- (5,-1.42) node[right]{1} (3.42,1.42) -- (5,1.42) node[right]{2} (2,0) -- (5,.5) node[right]{3} (2,0) -- (5,-.5) node[right]{7}; %markings
- \draw (2,0) circle(2pt)[fill=white]; %core
- \draw[->] (0,-3) circle(2pt)[fill=black] edge (5,-3); %trop(P^N|H)
- }
-
- \caption{The degrees can be figured out from the balancing equation.}
-\end{figure}
-
-In the following we describe the rays of the tropical moduli space.
-\begin{lem}
- A one-parameter tropical map $\phi$ to $\mathbb R_{\geq 0}$ is a decorated tree (with expansion factors - \emph{contact orders} - along edges and legs, and degrees on vertices, satisfying the balancing condition) with a circle (of radius $\delta$) around the root (sometimes called the \emph{core} and denoted by $\circ$) satisfying:
- \begin{enumerate}
- \item the circle of radius $\delta$ passes through at least one vertex of $\phi^{-1}(0)$ - which necessarily has positive degree - call $m$ its contact order with $H$;
- \item teeth may break only when they intersect the circle of radius $\delta$; in particular, $\circ$ is the only vertex contained in its strict interior, and every edge heading out from the circle goes directly to a vertex of $\phi^{-1}(0)$;
- \item every tooth that starts with contact order $m$ goes directly to a vertex of $\operatorname{circle}(\circ,\delta)\cap\phi^{-1}(0)$, and every other tooth starts with contact order $<m$ (possibly negative).
- \end{enumerate}
-\end{lem}
-\begin{proof}
- Otherwise there would be more than one parameters.
-\end{proof}
-
-\begin{remark}
- The core being contracted in the fiber of the tropical map is not a phenomenon that we should worry about in codimension one.
-Indeed, assume that the core is contracted in the fiber along a ray.
-Then all the edges departing from the core have expansion factor $0$; call the corresponding coordinates $U=\{u_i\}_{i\in I}$.
-Call the remaining coordinates $E=\{e_j\}_{j\in J}$.
-Note that tropical continuity involves only $E$.
-Alignments on the other hand assume the form $\lambda(v)=\lambda(v^\prime)$, where $\lambda(v)=\sum_{i\in I(v)}u_i\sum_{j\in J(v)}e_j$.
-Pick the shortest elements of $U$; then these can be shortened to zero without affecting the rest (by hypothesis, alignments can only identify them among themselves).
-This shows that we could not have started with a ray.
-\end{remark}
-
-\begin{ex}
- We look at the following example in some detail.
- \begin{figure}[h]
-  \tikz{
-  \draw (0,1) circle(2pt)[fill=black] --node[above]{2} (2,0);
-  \draw (0,-1) circle(2pt)[fill=black] --node[above]{2} (2,0);
-  \draw (2,0) -- (2.5,0) node[right]{4};
-  \draw (2,0)  circle(2pt)[fill=white];
-  \draw (0,1) -- (.33,1.33) node[above right]{0};
-  \draw (0,-1) -- (.33,-1.33) node[below right]{0};
-  \draw[red] (2,0) circle(2.23);
-  \draw[->] (0,-2.5)node[left]{0} circle(2pt)[fill=black] edge (4,-2.5);
-  }
- \end{figure}
- The ambient space is $\VZc{1}{(4,0,0)}{\PP^N|H}{4}$, of dimension $4N+3$.
-The underlying moduli space is $X=\M{0}{(2,0)}{\PP^N|H}{2}\times_H\M{0}{(2,0)}{\PP^N|H}{2}\times\VZ_{1,(-2,-2,4)}$ of dimension $5N+1$.
-Consider the fiber product:
- \bcd
- F\ar[r]\ar[d]& \M{0}{(2,0)}{\PP^N|H}{2}\times\M{0}{(2,0)}{\PP^N|H}{2}\ar[d]\\
- H\ar[r] & H\times H
- \ecd
- At the level of ghost sheaves, $\oM_F=\mathbb N\oplus_{\mathbb N^2}\oM_1^{\rm{enl}}\oplus\oM_2^{\rm{enl}}$, where the map $\mathbb N^2\to\mathbb N$ is the sum, and the map $\mathbb N^2\to\oM_1^{\rm{enl}}\oplus\oM_2^{\rm{enl}}$ generically is multiplication by $2$, so $\oM_F=\mathbb N^2/(2e=2f)$ generically.
-Saturation gives a finite cover $G\to F$ with $\oM_G=\mathbb N_{e=f}$ generically.
-Lifting this to actual log structures, what we are doing (again generically) is taking a square root of the isomorphism $T_{R_1,q_1}^{\otimes 2}\simeq T_{R_2,q_2}^{\otimes 2}$, which is obtained passing through $N_{H/\PP^N,f(Z)}$ via $\operatorname{d}f_{|R_i,q_i}$.
-This breaks when $f_{|R_i}$ is not tangent to $H$ of order exactly $2$ at $q_i$, for either $i$; but by the maximality assumption this happens precisely along Gathmann's comb loci $\Delta_i$.
-So in fact, rather than with $T_{R_i,q_i}^{\otimes 2}$, we should be working with $T_{R_i,q_i}^{\otimes 2}(-\Delta_i)$: but this is exactly $\ev_i^\st(-H)$ by Gathmann's genus zero formula, and the isomorphism $\ev_1^\st(H)=\ev_2^\st(H)$ holds on all of $F$.
-
- On the other hand, generically on $\VZ_{1,(-2,-2,4)}$ we have $T_{q_1}Z\simeq T_{q_2}Z$ by exploiting the group structure on the elliptic curve.
-This breaks when either (but not both) is on a rational tail.
-Yet we have $T_{q_1}Z(\Delta_{1\in P})\simeq T_{q_2}Z(\Delta_{2\in P})$ by Vakil-Zinger's construction of a universal $\psi$-class (i.e.
-by comparing both with $\pi_*\omega(\Delta)$; notice that our further blow-up has the only effect of twisting \emph{all} the relevant line bundles by $\Delta_{1,2\notin P}$).
-
- Now, the fiber of the Vakil-Zinger blow-up over $X$ can be described as follows. Generically it looks like \[\PP(T_{q_1}R_1\otimes T_{q_1}Z\oplus T_{q_2}R_2\otimes T_{q_2}Z)\]
- but this has to be modified along the boundary:
- \begin{itemize}
-  \item this has to do with the fact that the normal bundle of the strict transform is the pullback of the normal bundle twisted by the intersection with the exceptional divisor (so it relates with previous steps of the blow-up);
-  \item it is not globally a $\PP^1$-bundle (so it relates with further stages of the blow-up; it also has to do with a choice of compactification for the moduli space of attachments);
-  \item it has the effect of replacing $T_{q_i}Z$ with Vakil-Zinger's universal $\mathbb T$, so that this can be factored out of the projective bundle, and in fact we are left with a projective bundle $\mathbb P=\PP(T_{q_1}R_1\oplus T_{q_2}R_2)$ over $F$, and its open part $\operatorname{Iso}(T_{q_1}R_1\oplus T_{q_2}R_2)$ represents the attachment data for a contraction to a tacnode $R_1\sqcup_q R_2\to\bar{C}$.
- \end{itemize}
-On $\PP$ there is a natural vector bundle map \[s\colon \OO_{\PP}(-1)\hookrightarrow p^\st(T_{q_1}R_1\oplus T_{q_2}R_2)\xrightarrow{+\operatorname{d}f}\ev_q^\st T\PP^N\]
-that vanishes along the locus where $f$ descends to $\bar C$. In general, it is not a transversal section:
-\begin{itemize}
- \item we should replace $T\PP^N$ by $TH$ as long as all the $m^{(i)}$ are $\geq2$;
- \item Vakil and Zinger construct a blow-up of $\PP$ along the vanishing loci of $s$ of low codimension, and twist $s$ by the exceptional divisors, so that it becomes a transverse section $\tilde{s}$.
-\end{itemize}
-On the other hand, the finite cover $G\to F$ factors through $\PP$, because the two vertices are already aligned on $G$.
-We claim that the boundary locus of $\VZc{1}{(4,0,0)}{\PP^N|H}{4}$ corresponding to the combinatorial type of the tropical map above is the transverse intersection
-\[\left(G\cap V(\tilde{s})\subseteq\PP\right)\times\VZ_{1,(-2,-2,4)}.\]
-This has the expected dimension (codimension $N-1$ with respect to $X$).
-To compute its class, we can pull $\PP$ back to $G$, and then notice that $G\hookrightarrow\PP_G$ is the inclusion of a (trivial) subbundle.
-\begin{lem}
- The class of $\PP(\mathcal F)\subseteq\PP(\mathcal E)$ is $c_{\rm{top}}(\OO_\mathcal{E}(1)\otimes p^\st(\mathcal{E}/\mathcal{F}))$.
-\end{lem}
-See \cite[Prop.
-9.13]{EH3264}.
-It is a good time to remember that $\mathcal E$ was in fact $(\bigoplus_{i=1}^rTR_{i,q_i})\otimes\mathbb T$.
-By writing $c$ for $c_1(\OO_\mathcal{E}(1))$, $\psi_i$ for $c_1(T^\st R_{i,q_i})$, $\psi_Z$ for Vakil-Zinger's universal psi class, and $H$ for $\ev_q^\st H$, we need to compute
-\begin{align*}
-p_*\left((c-\psi_1-\psi_2-2\psi_Z)[(1+c+H)^N(1+c)^{-1}]_{N-1}\right)= \\
-p_*\left((c-\psi_1-\psi_2-2\psi_Z)(\sum_{k=0}^{N-1}\binom{N}{1+k}c^kH^{N-1-k})\right)=\\
-\sum_{k=0}^{N-1}\binom{N}{k}H^{N-1-k}\big(s_k(\mathcal E)-s_{k-1}(\mathcal E)(\psi_1+\psi_2+\psi_Z)\big)
-\end{align*}
-\end{ex}
-
-We now generalise this picture.
-Recall that the map $C\to\bar C$ is given by a (generic) line in the sum of the tangent spaces to the rational tails at the nodes that join them to the contracted curve of genus one.
-This is equivalent to an alignment, and it is parametrised by an open subset of a projective bundle over the moduli space for the tails corresponding to vertices of the dual graph lying on the circle of radius $\delta$.
-Yet, notice that those vertices lying in $\phi^{-1}(0)$ are already aligned among themselves.
-This is why we find it convenient to distinguish among four groups of vertices:
-\begin{enumerate}
- \item the core;
- \item\label{specialvertices} vertices on $\phi^{-1}(0)\cap\operatorname{circle}(\circ,\delta)$;
- \item vertices on $\operatorname{circle}(\circ,\delta)\setminus\phi^{-1}(0)$;
- \item\label{boringvertices} vertices on $\phi^{-1}(0)\setminus\operatorname{circle}(\circ,\delta)$.
-\end{enumerate}
-We shall first argue that gluing of log maps can be performed separately for the exterior and interior of the circle (the analogous classical picture is that, since the core is contracted, this moduli space is the product of a genus one curve, and a fiber product of genus zero maps under evaluation morphisms).
-
-\begin{lem}
- $\VZ^{\operatorname{punct}}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(H,0)\simeq \VZ^{\operatorname{punct}}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(\Spec(k\oplus\mathbb N))\times H$.\footnote{(Luca) check log structure, could be fibered over std log point}
-\end{lem}
-
-Let us now deal with vertices of type \ref{specialvertices}.
-\begin{lem}
- Consider the following fiber product in the category of fs log stacks:
- \bcd
- F\ar[d]\ar[r] & \prod_{i=1}^r\M{0}{\alpha^{(i)}\cup\{ m\}}{\PP^N|H}{d_i}\ar[d,"\ev_{q_i}"]\\
- H\ar[r] & H^r
- \ecd
- On $F$ there is a canonical isomorphism $\mathbb L_{q_i}\cong\mathbb L_{q_j}$\footnote{(Luca) check how it degenerates}, the latter being the cotangent line bundles at the gluing markings on two different components $i$ and $j$.
-Furthermore, $\underline F$ is a finite cover of degree $m^{r-1}$ of the fiber product of the underlying stacks.
-\end{lem}
-\begin{proof}
- Recall that each $\M{0}{\alpha^{(i)}\cup\{ m\}}{\PP^N|H}{d_i}$ is endowed with the log structure induced by pulling back along $q_i$ the divisorial log structure of the universal curve at the image of $q_i$ itself.
-Thus $\ev_{q_i}$ is made into a log morphism to $H$ with its induced DF(1) log structure.
-We claim that the subtext of such morphism is Gathmann's formula; namely, the log morphism to $H$ corresponds to an isomorphism betwee $\ev_{q_i}^\st\OO_H(-H)$ on one side, and $\mathcal I_{D_i}\otimes\mathbb L_{q_i}^m$ on the other, where $\mathcal I_{D_i}$ is the ideal sheaf of the union of the comb loci $D_i$ in $\M{0}{\alpha^{(i)}\cup\{ m\}}{\PP^N|H}{d_i}$.
-
- On the fiber product there is a canonical isomorphism between $\ev_{q_i}^\st H$ and $\ev_{q_j}^\st H$.
-
- Say something about integrality.
-
- Saturation is a local operation, as much as computing the degree, hence we can concentrate on the dense open locus where all the curves we are gluing are smooth, and they are not mapped entirely into $H$.
-There the minimal log structure on $\M{0}{\alpha^{(i)}\cup\{ m\}}{\PP^N|H}{d_i}$ is trivial, therefore the isomorphism between $\ev_{q_i}^\st H$ and $\ev_{q_j}^\st H$ translates into an isomorphism $\mathbb L_{q_i}^m\cong \mathbb L_{q_j}^m$.
-The saturation $F$ is obtained by taking an $m$-th root of this isomorphism.
-\end{proof}
-Let us denote by $\mathbb L_F$ the universal cotangent line at $q$.
-
-The projective bundle we are seeking has base
-\[\mathcal X=\left(F\times \prod_{i=1}^s\oM_{0,\tilde\alpha^{(i)}\cup\{m_i\}}^{\rm{punct}}(H,\tilde d_i)\right)\times_{H^{s+1}}H\]
-(with $m_i<m$) and it is \[\PP=\Proj_{\mathcal X}\left(\mathbb T_F\oplus\bigoplus_{i=1}^s\mathbb T_{\tilde q_i}\right).\]
-We are interested in the vanishing locus of the section
-\[s\colon\OO_{\PP}(-1)\hookrightarrow p^\st\left(\mathbb T_F\oplus\bigoplus_{i=1}^s\mathbb T_{\tilde q_i}\right)\xrightarrow{+df_q} f^\st(\operatorname{T}\PP^N)_q,\]
-because it represents the geometric condition that $f\colon C\to \PP^N$ factors through the normalisation map $C\to\bar C$ prescribed by the given point of $\PP$.
-As is, $s$ is not transverse to the zero section.
-First of all, unless $m=1$, $\operatorname{T}\PP^N$ can be replaced by $\operatorname{T}H$ in the definition of $s$ above, because the projection of all $\operatorname{d}f_i(\operatorname{T}_{q_i}R_i)$ to $N_{H/\PP^N}$ is zero.
-The case $m=1$ has to be dealt with separately and it turns out that, once $s$ is made transverse, the dimension of its zero locus is smaller than the expected dimension, hence the corresponding combinatorial types are in fact irrelevant.
-
-The procedure to make $s$ transverse is the same as described in \cite[\S 3]{VZ}, namely we need to blow up inside $\PP$ the projective subbundle $\PP(\mathcal E)$ of $\PP_{|\mathcal X_\sigma}$, where $\mathcal X_\sigma$ is the closed substack of $\mathcal X$ where some of the tails degenerate so that the corresponding gluing marking lies on a component contracted by $f$, and $\mathcal E$ is the sum of the tangent line bundles at such subset of the gluing markings.
-Because $\oM_{0,\tilde\alpha^{(i)}\cup\{m_i\}}^{\rm{punct}}(H,\tilde d_i)$ is isomorphic to $\M{0}{\tilde n_i}{H}{d_i}$, the construction of Vakil and Zinger in the section ``A blowup of a moduli space of genus-zero maps'' of their paper carries through unchanged.
-The result of the blow-up is to replace $T_{q_i}R_i$ with $T_{q_i}R_i\otimes\bigoplus_{j=1}^kT_{\tilde q_j}R_i\otimes T_{\tilde q_j} S_{ij}$.
-We interpret this in terms of alignments.\footnote{(Luca) this has to be written properly}
-
-We claim that $\tilde s$ obtained from $s$ by twisting by the exceptional divisors of the blowup is a transverse section.
-We also claim that comb loci of type $\mathcal Y_c^0$ can be described as a fibered product of
-\begin{itemize}
- \item moduli of genus one punctured maps to the standard log point, radially aligned and satisfying factorisation;
- \item $V(\tilde s)$;
- \item moduli of genus zero maps relative to $(\PP^N|H)$, corresponding to vertices of type \ref{boringvertices} above.
-\end{itemize}
-Finally, we claim that integrals of psi and evaluation classes over these loci can be translated into tautological integrals, i.e.
-descendant Gromov-Witten invariants, whose numerics is governed by the combinatorial type of the tropical map.
-
-\section{Recursion formula in general}
-Now let $(X|Y)$ be a smooth pair with $Y$ very ample. The complete linear system $|\OO_X(Y)|$ defines an embedding $X \hookrightarrow \PP^N$ with $Y=X\cap H$ for $H$ some hyperplane.
-
-\begin{lemma} The following square is cartesian (in the category of ordinary stacks):
-\bcd
-\VZ_{1,\alpha}(X|Y,\beta) \ar[r] \ar[d] \ar[rd,phantom,"\square"] & \VZ_{1,\alpha}(\PP^N|H,d) \ar[d] \\
-\VZ_{1,n}(X,\beta) \ar[r,"i"] & \VZ_{1,n}(\PP^N,d).
-\ecd
-\end{lemma}
-\begin{proof} It is clear from the modular description that this square is cartesian in the category of fs log stacks.
-But the morphism $i$ is strict, which implies that the square is also cartesian in the category of coherent log stacks.
-Since fibre products in the latter category are compatible with the functor forgetting log structures, the claim follows.\end{proof}
-
-Since $\VZ_{1,n}(\PP^N,d)$ is smooth and $\VZ_{1,n}(X,\beta)$ carries a natural virtual class, there is a diagonal pull-back morphism which we use to define the virtual class on the space of maps to $(X|Y)$:
-\begin{equation*} \virt{\VZ_{1,\alpha}(X|Y,\beta)} := i_\Delta^! [\VZ_{1,\alpha}(\PP^N|H,d)]. \end{equation*}
-The recursion formula in $\VZ_{1,\alpha}(\PP^N|H,d)$ immediately pulls back along $i$ to give a recursion formula in $\VZ_{1,\alpha}(X|Y,\beta)$.
-
 \bibliographystyle{alpha}

### 2019-03-05 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
Started rewriting description of boundary strata

@@
 
-The recursion formula in $\VZ_{1,\alpha}(\PP^N|H,d)$ proved in \S\S \ref{}-\ref{} below immediately pulls back along $i$ to give a recursion formula in $\VZ_{1,\alpha}(X|Y,\beta)$.
-
-\part{The recursion formula and applications}
-
-\section{Gathmann's line bundle through tropical geometry} For each marking $x_k$ we consider the locus in $\VZ_{1,\alpha}(\PP^N|H)$ where $x_k$ belongs to an internal component of the collapsed map.
-We use the log structure on $\VZ_{1,\alpha}(\PP^N|H)$ to construct a line bundle $\Lcal_k$ together with a section $s_k$ vanishing along this locus.
-We use the correspondence with tropical geometry to identify $\cchern_1(\Lcal_k)$ in terms of tautological classes on $\VZ_{1,\alpha}(\PP^N|H)$, and to compute the vanishing order of $s_k$ along the components of its zero set.
-
-The pair $(\Lcal_k,s_k)$ is most naturally constructed on the moduli space $\MLog_{1,\alpha}(\PP^N|H)$ of non-expanded log maps; the corresponding pair on $\VZ_{1,\alpha}(\PP^N|H)$ will be obtained via pull-back.
-Consider therefore a moduli point in $\MLog_{1,\alpha}(\PP^N|H)$ and let $Q^\vee_{\RR}$ be the corresponding tropical moduli space (viewed as a rational polyhedral cone).
+\part{The recursion formula and applications} \noindent In this part we derive topological recursion relations on the moduli space of reduced stable maps (Theorem \ref{theorem recursion}), inspired by the constructions of Vakil and Gathmann, but going beyond theirs in several key respects.
+We apply these to produce a quantum Lefschetz algorithm in genus one, which reconstructs the absolute theory of $Y$ and the relative theory of $(X,Y)$ from the absolute theory of $X$.
+Along the way we prove a splitting axiom for the reduced relative theory, in which involves non-trivial obstruction bundle terms make an appearance.
+
+The strategy is to first prove everything in the unobstructed case $(\PP^N,H)$; the general case follows by pullback along $i$.
+
+\section{Gathmann's line bundle through tropical geometry} Consider a reduced relative space $\VZ_{1,\alpha}(\PP^N|H,d)$.
+For each marking $x_k$ we consider the locus $\Dcal(k) \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$ where $x_k$ belongs to an internal component of the collapsed map.
+In this section, we use the log structure on $\VZ_{1,\alpha}(\PP^N|H,d)$ to construct a line bundle $\Lcal_k$ together with a section $s_k$ which vanishes precisely along $\Dcal(k)$.
+We use the correspondence with tropical geometry to identify $\cchern_1(\Lcal_k)$ in terms of tautological classes on $\VZ_{1,\alpha}(\PP^N|H,d)$, and to compute the vanishing order of $s_k$ along the components of $\Dcal(k)$.
+Combined with the splitting axioms established in the next section, we obtain a recursion relation inside $\VZ_{1,\alpha}(\PP^N|H,d)$
+
+The pair $(\Lcal_k,s_k)$ is most naturally constructed on the moduli space $\MLog_{1,\alpha}(\PP^N|H,d)$ of non-expanded log maps; the corresponding pair on $\VZ_{1,\alpha}(\PP^N|H,d)$ will be obtained via pull-back.
+Consider therefore a moduli point in $\MLog_{1,\alpha}(\PP^N|H,d)$ and let $Q^\vee_{\RR}$ be the corresponding tropical moduli space (viewed as a rational polyhedral cone).
 Over this cone we have a universal tropical curve and map
@@
 The composition $f \circ x_k \colon Q^\vee_{\RR} \to \RR_{\geq 0}$ defines a piecewise-linear function on $Q_{\RR}^\vee$ whose preimage over the open cone $\RR_{>0}$ consists of those tropical maps where $x_k$ belongs to an internal component.
-Dually we obtain an element of the minimal monoid $Q$ at the moduli point, and this globalises to produce a section of the ghost sheaf on $\MLog_{1,\alpha}(\PP^N|H)$.
+Dually we obtain an element of the minimal monoid $Q$ at the moduli point, which globalises to produce a section of the ghost sheaf on $\MLog_{1,\alpha}(\PP^N|H,d)$.
 In the usual way this induces a line bundle and section $(\Lcal_k,s_k)$ on the moduli space, and the tropical description above shows that the zero locus of $s_k$ is (set-theoretically) the locus where $x_k$ belongs to an internal component.
@@
 \begin{equation*} \cchern_1(\Lcal_k) = \alpha_k \psi_k + \ev_k^\st H.\end{equation*}
-This gives the construction of $(\Lcal_k,s_k)$ on $\MLog_{1,\alpha}(\PP^N|H)$; the construction on $\VZ_{1,\alpha}(\PP^N|H)$ is given by pull-back.
-Notice in particular that $\psi_k$ should be interpreted as a \textbf{collapsed psi class} on $\VZ_{1,\alpha}(\PP^N|H)$, i.e.
+This gives the construction of $(\Lcal_k,s_k)$ on $\MLog_{1,\alpha}(\PP^N|H,d)$; the construction on $\VZ_{1,\alpha}(\PP^N|H,d)$ is given by pull-back.
+Notice in particular that $\psi_k$ should be interpreted as a \textbf{collapsed psi class} on $\VZ_{1,\alpha}(\PP^N|H,d)$, i.e.
 a psi class coming from the stabilised curve of the collapsed map.
 All of the psi classes we deal with will be collapsed psi classes.
+We immediately arrive at:
+
+\begin{thm} \label{theorem recursion} We have the following relation in the Chow ring of $\VZ_{1,\alpha}(\PP^N|H,d)$:
+\begin{equation}\label{equation recursion} (\alpha_k \psi_k + \ev_k^\st H) \cap [\VZ_{1,\alpha}(\PP^N|H,d)] = \sum_{\Dcal} \lambda_\Dcal [ \Dcal ].\end{equation}
+The sum is over irreducible components $\Dcal$ of the divisor $\Dcal(k) \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$, and $\lambda_\Dcal$ is the vanishing order of $s_k$ along this component.
+By pull-back we obtain the same formula with $(\PP^N,H)$ replaced by $(X,Y)$.
+\end{thm}
 
@@
 \section{Recursive description of boundary strata: the reduced splitting axiom}
+In this section, the most technically difficult in the entire paper, we provide an explicit description of the terms appearing on the right-hand side of \eqref{equation recursion} above.
+For each term, we provide a combinatorial means to calculate the vanishing order $\lambda_\Dcal$, and a recursive description of the stratum $\Dcal$ in terms of fibre products of moduli spaces with smaller numerical data.
 

### 2019-03-05 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
added a bit more from old-2 on irreducible cpts of D

@@
 
+\subsection{Identifying the irreducible components of $\Dcal(k)$} Here we explain the strategy for identifying the irreducible components of $\Dcal(k)$ via tropical geometry.
+
+\begin{lemma} Every irreducible component of $\Dcal(k)$ is a codimension-$1$ logarithmic stratum.\end{lemma}
+\begin{proof} This is not hard to see: the locus where the log structure is trivial coincides precisely with the  locus where the source curve is smooth and not mapped inside $H$, and since $\VZ$ is log smooth this locus is open and dense.
+By definition $\Dcal(k)$ is disjoint from this locus, hence is contained in the  complement of this locus, which (by the very definition of logarithmic strata) can be written as a union of logarithmic strata of positive codimension.
+Since $\Dcal(k)$ has codmension $1$, it must therefore be equal to a union of logarithmic divisors.\end{proof}
+
+In the previous section we discussed at length a procedure for describing the logarithmic strata of $\VZ$. This shows that every divisorial logarithmic stratum is obtained via a three-step process:
+\begin{enumerate}
+\item choose the combinatorial type of a tropical map;
+\item subdivide the corresponding tropical moduli space;
+\item choose a ray in this subdivision.
+\end{enumerate}
+Notice that this process contains some redundancies: once we choose a ray of the tropical moduli space, we obtain a generisation of the intial combinatorial type, given by contracting some edges of the dual graph.
+
+\begin{example} \end{example}
+
+Whenever we consider a logarithmic stratum in $\VZ$, by its combinatorial type we will always mean the generisation of the ``initial'' combinatorial type induced by our choice of cone in the polyhedral subdivision.
+This does not depend on the choice of initial combinatorial type.
+
+Now, the logarithmic divisors which are contained in $\Dcal(k)$ are precisely those whose corresponding combinatorial type has the vertex of the dual graph containing $x_k$ mapped into the interior $\RR_{>0} \subseteq \RR_{\geq 0}$.
+
+Thus, via the above procedure, we are able to enumerate the irreducible components of $\Dcal(k)$ in a combinatorial manner.
+The combinatorial type and choice of ray allows us to describe the general element of such a component.
+What we are still lacking is a recursive description of the components, which we need in order to compute integrals over them.
+This is the subject of the remainder of this section.
+
 \subsection{Recursive description of the divisors: types $A,B$ and $C^+$}

### 2019-03-05 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
minor changes

@@
 \begin{customthm}{A}
-There exists a smooth and proper Deligne—Mumford stack giving a modular compactification for the space of genus $1$ maps to projective space with fixed contact order with a hyperplane. 
+There exists a log smooth and proper Deligne—Mumford stack giving a modular compactification for the space of genus $1$ maps to projective space with fixed contact order with a hyperplane. 
 \end{customthm}
@@
 We reinterpret and extend their methods using logarithmic geometry and tropical techniques.
-We present a recursive scheme to calculate the invariants of a hypersurface from the invariants of projective space.
+Our main result is the following.
 
 \begin{customthm}{B}
-There is an explicit recursive algorithm to calculate the reduced genus one Gromov--Witten invariants of a hypersurface from that of the ambient variety. 
+Given a smooth pair $(X,Y)$ with $Y$ very ample, there is an explicit recursive algorithm to calculate
+\begin{enumerate}
+\item the reduced genus one Gromov--Witten invariants of $Y$;
+\item the reduced genus one relative Gromov--Witten invariants of $(X,Y)$; 
+\item the reduced genus one rubber invariants of $P=\PP_Y(\operatorname{N}_{Y|X} \oplus \OO_Y)$
+\end{enumerate}
+from the invariants of the ambient variety $X$.
 \end{customthm}
-
-By standard virtual pullback techniques, virtual versions of our results apply for smooth very ample pairs $(X,Y)$.
 
@@
 The virtual geometry of this was studied in recent work of Janda, Pandharipande, Pixton, and Zvonkine~\cite{DRCBundle}.
-We do not know how to calculate an expression for this main component contribution but we repurpose Maulik and Pandharipande’s rubber calculus techniques, and relations coming from the stack of target expansions, to complete our recursion.
+We do not know how to calculate an expression for this main component contribution, but we repurpose E.~Katz's topological recursion relations \cite{EKatz} to complete the algorithm.
 We note that even in genus one, an understanding of the main component contributions of the double ramification cycle for target manifolds would be interesting.

### 2019-03-08 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
Added bit on indexing strata, and tweaked Gathmann lb section

@@
 Second, the target degeneration is now a toric degeneration, and the logarithmic tangent bundle is trivial.
-
 \end{proof}
@@
 
-\section{Stratification} The logarithmic smoothness established in Theorem~\ref{thm: log-smoothness} implies that $\mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)$ is an orbifold toroidal embeddeding.
+\section{Stratification} The logarithmic smoothness established in Theorem~\ref{thm: log-smoothness} implies that $\mathcal{VZ}_{1,\alpha}(\mathbb P^N|H,d)$ is an orbifold toroidal embeddeding.
 Consequently, the irreducible components of its boundary and their intersections form a stratification of the space.
@@
 
-\subsubsection{The cone complex} To understand the stratification via combinatorial data, we will build the straification from known objects.
+\subsection{The cone complex} To understand the stratification via combinatorial data, we will build the straification from known objects. \\
 
@@
 The preimages of vertices of the subdivision form a subdivision of $\plC$.
-After this procedure, the vertices of $\plC$ with positive image are totally ordered in a manner extending the partial order obtained from the map to $\mathbb R_{\geq 0}$.
-The combinatorial types of such \textbf{ordered} maps produce the cones of a subdivision of $\Sigma^{\mathrm{log}}$ which we denote $\Sigma^{\mathrm{Kim}}$.\\
+After this procedure, the images of vertices of $\plC$ which lie in $\RR_{>0}$ are totally ordered, in a manner extending the partial order obtained from the map to $\mathbb R_{\geq 0}$.
+The combinatorial types of such \textbf{image-ordered} maps produce the cones of a subdivision of $\Sigma^{\mathrm{log}}$ which we denote $\Sigma^{\mathrm{Kim}}$.\\
 
@@
 \textbf{Step 3}.
-Given a tropical map $F: \plC\to \mathbb R_{\geq 0}$ parameterized by $\Sigma^{\mathrm{Kim}}$, there is a largest radius $\delta$ (possible equal to $0$) such that every vertex strictly contained in the circle of radius $\delta$ around the core is contracted to a point in $\mathbb R_{>0}$.
+Given a tropical map $F: \plC\to \mathbb R_{\geq 0}$ parameterized by $\Sigma^{\mathrm{Kim}}$, there is a largest radius $\delta$ (possible equal to $0$) such that every vertex strictly contained in the circle of radius $\delta$ around the core has degree-marking $d=0$.
 Let $
-\Sigma^{\mathrm{cen}}$ be the subdivision obtained by requiring that the vertices contained with the circle of radius $\delta$ around the core of $\plC$ are totally ordered. \\
+\Sigma^{\mathrm{cen}}$ be the subdivision obtained by requiring that the vertices contained with the circle of radius $\delta$ around the core of $\plC$ are totally ordered.
+This involves introducing cones along which certain $\Z$-linear combinations of edge lengths are identified.\\
 
@@
 \textbf{Step 4}. Let $
-\Sigma_{1,\alpha}(\mathbb P^N|H)$ be the subcomplex of $\Sigma^{\mathrm{cen}}$ obtained by passing to the subcomplex of $\Sigma^{\mathrm{cen}}$ that consists of well-spaced tropical maps.
+\Sigma_{1,\alpha}(\mathbb P^N|H,d)$ be the subcomplex of $\Sigma^{\mathrm{cen}}$ obtained by passing to the subcomplex of $\Sigma^{\mathrm{cen}}$ that consists of well-spaced tropical maps.
 
@@
 The cone complex $
-\Sigma_{1,\alpha}(\mathbb P^N|H)$ is the fan of the toroidal embedding $
+\Sigma_{1,\alpha}(\mathbb P^N|H,d)$ is the fan of the toroidal embedding $
 \mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)$. In particular, the codimension $k$ strata of $
 \mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)$ are in inclusion reversing bijection with the dimension $k$ cones in $
-\Sigma_{1,\alpha}(\mathbb P^N|H)$.
+\Sigma_{1,\alpha}(\mathbb P^N|H,d)$.
 \end{prop}
@@
 
-\section{Rubber variants and virtual geometry}
+\subsection{Indexing the strata} The dimension-$k$ cones in $\Sigma_{1,\alpha}(\PP^N|H,d)$ can be enumerated as follows.
+First, the cones in $\Sigma^{\operatorname{log}}$ are indexed by \textbf{combinatorial types} of tropical maps to $\RR_{\geq 0}$.
+Here a combinatorial type encodes all of the data of a tropical map, except for the edge lengths and precise vertex positions.
+To be more precise, a combinatorial type $\Delta$ consists of:
+\begin{enumerate}
+\item a finite graph;
+\item genus, degree and marking assignments on the vertices
+\item the data of which stratum of $\RR_{\geq 0}$ each vertex is mapped to;
+\item integral slopes along the edges (both finite and infinite).
+\end{enumerate}
+The corresponding cone $\sigma \in \Sigma^{\operatorname{log}}$ is then given by the resulting moduli space of tropical maps, given by choices of edge lengths and vertex positions which produce a continuous tropical map.
+Given $\sigma\in \Sigma^{\operatorname{log}}$ we then produce all the cones in $\Sigma_{1,\alpha}(\PP^N|H,d)$ mapping to $\sigma$ by performing Steps 2--4 outlined above.
+This amounts to taking a particular subdivision of $\sigma$.
+Note that in this process, new cones are created which map into larger-dimensional cones of $\Sigma^{\operatorname{log}}$.
+The process for enumerating the codimension $k$ strata of $\VZ_{1,\alpha}(\PP^N|H,d)$ is therefore:
+\begin{enumerate}
+\item fix a combinatorial type $\Delta$;
+\item perform the subdvidision of the resulting cone $\sigma \in \Sigma^{\operatorname{log}}$;
+\item identify the dimension $k$ cones of that subdivision.
+\end{enumerate}
+In \S \ref{} we will perform this analysis in the case $k=1$.
+
+\section{Rubber variants and virtual construction}
 
@@
 
-\subsection{Virtual geometry for very ample pairs}
+\subsection{Virtual construction for very ample pairs}
 Now let $(X,Y)$ be a smooth pair with $Y$ very ample.
@@
 
-The strategy is to first prove everything in the unobstructed case $(\PP^N,H)$; the general case follows by pullback along $i$.
+The strategy is to first prove everything in the unobstructed case $(\PP^N,H)$; the general case follows by pullback along $i$ (see \S \ref{}).
 
@@
 The pair $(\Lcal_k,s_k)$ is most naturally constructed on the moduli space $\MLog_{1,\alpha}(\PP^N|H,d)$ of non-expanded log maps; the corresponding pair on $\VZ_{1,\alpha}(\PP^N|H,d)$ will be obtained via pull-back.
-Consider therefore a moduli point in $\MLog_{1,\alpha}(\PP^N|H,d)$ and let $Q^\vee_{\RR}$ be the corresponding tropical moduli space (viewed as a rational polyhedral cone).
-Over this cone we have a universal tropical curve and map
+Consider therefore the tropicalisation $\Sigma^{\log}$ of $\MLog_{1,\alpha}(\PP^N|H,d)$, identified as usual with the moduli space of tropical maps to $\RR_{\geq 0}$.
+We have a universal family
 \bcd
 \sqC \ar[d,"\pi"] \ar[r,"f"] & \RR_{\geq 0} \\
-Q^\vee_{\RR} \ar[u, bend left=40pt, "x_k" left]
+\Sigma^{\log} \ar[u, bend left=40pt, "x_k" left]
 \ecd
-where $x_k$ is the section which for every point $\lambda \in Q^\vee_{\RR}$ picks out the vertex of $\sqC_\lambda$ containing the leg $x_k$.
-The composition $f \circ x_k \colon Q^\vee_{\RR} \to \RR_{\geq 0}$ defines a piecewise-linear function on $Q_{\RR}^\vee$ whose preimage over the open cone $\RR_{>0}$ consists of those tropical maps where $x_k$ belongs to an internal component.
-Dually we obtain an element of the minimal monoid $Q$ at the moduli point, which globalises to produce a section of the ghost sheaf on $\MLog_{1,\alpha}(\PP^N|H,d)$.
-In the usual way this induces a line bundle and section $(\Lcal_k,s_k)$ on the moduli space, and the tropical description above shows that the zero locus of $s_k$ is (set-theoretically) the locus where $x_k$ belongs to an internal component.
+where $x_k$ is the section which for every point $\lambda \in \Sigma^{\log}$ picks out the vertex of $\sqC_\lambda$ containing the leg $x_k$.
+The composition $f \circ x_k \colon \Sigma^{\log} \to \RR_{\geq 0}$ defines a piecewise-linear function on $\Sigma^{\log}$ whose preimage over the open cone $\RR_{>0}$ consists of those tropical maps where $x_k$ belongs to an internal component.
+This produces a section of the ghost sheaf on $\MLog_{1,\alpha}(\PP^N|H,d)$, which in the usual way induces a line bundle and section $(\Lcal_k,s_k)$ on the moduli space, and the tropical description above shows that the zero locus of $s_k$ is (set-theoretically) the locus where $x_k$ belongs to an internal component.
 
@@
 By construction, the line bundle associated to this section is $\pi^\st \Lcal_k$.
-Consider on the other hand the generator $1 \in \N = \Gamma(\PP^N,\ol{M})$ with associated line bundle $\OO(H)$.
+Consider on the other hand the generator $1 \in \N = \Gamma(\PP^N,\ol{M}_{\PP^N})$ with associated line bundle $\OO(H)$.
 The section $f^\flat(1) \in \Gamma(C,\ol{M}_C)$ has associated line bundle $f^\st\OO(H)$.
@@
 \begin{equation}\label{equation recursion} (\alpha_k \psi_k + \ev_k^\st H) \cap [\VZ_{1,\alpha}(\PP^N|H,d)] = \sum_{\Dcal} \lambda_\Dcal [ \Dcal ].\end{equation}
-The sum is over irreducible components $\Dcal$ of the divisor $\Dcal(k) \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$, and $\lambda_\Dcal$ is the vanishing order of $s_k$ along this component.
-By pull-back we obtain the same formula with $(\PP^N,H)$ replaced by $(X,Y)$.
-\end{thm}
+The sum is over irreducible components $\Dcal$ of the divisor $\Dcal(k) \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$, and $\lambda_\Dcal$ is the vanishing order of $s_k$ along this component. \end{thm}
 
@@
 
+\section{Recursion for general $(X,Y)$}
+
 \section{Quantum Lefschetz algorithm}

### 2019-03-08 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
started fixing up A,B,C+ description

@@
 \newcommand{\sqC}{\scalebox{0.8}[1.3]{$\sqsubset$}}
+\newcommand{\Kim}{\operatorname{Kim}}
 
@@
 \section{Recursive description of boundary strata: the reduced splitting axiom}
-In this section, the most technically difficult in the entire paper, we provide an explicit description of the terms appearing on the right-hand side of \eqref{equation recursion} above.
+In this section, the most technically difficult of the paper, we provide an explicit description of the terms appearing on the right-hand side of \eqref{equation recursion} above.
 For each term, we provide a combinatorial means to calculate the vanishing order $\lambda_\Dcal$, and a recursive description of the stratum $\Dcal$ in terms of fibre products of moduli spaces with smaller numerical data.
@@
 
-\begin{lemma} Every irreducible component of $\Dcal(k)$ is a codimension-$1$ logarithmic stratum.\end{lemma}
-\begin{proof} This is not hard to see: the locus where the log structure is trivial coincides precisely with the  locus where the source curve is smooth and not mapped inside $H$, and since $\VZ$ is log smooth this locus is open and dense.
-By definition $\Dcal(k)$ is disjoint from this locus, hence is contained in the  complement of this locus, which (by the very definition of logarithmic strata) can be written as a union of logarithmic strata of positive codimension.
-Since $\Dcal(k)$ has codmension $1$, it must therefore be equal to a union of logarithmic divisors.\end{proof}
-
-In the previous section we discussed at length a procedure for describing the logarithmic strata of $\VZ$. This shows that every divisorial logarithmic stratum is obtained via a three-step process:
+\begin{lemma} Every irreducible component of $\Dcal(k)$ is a codimension $1$ log stratum.\end{lemma}
+\begin{proof} This is not hard to see: the locus where the log structure is trivial coincides precisely with the  locus where the source curve is smooth and not mapped inside $H$, and since $\VZ_{1,\alpha}(\PP^N|H,d)$ is log smooth this locus is open and dense \cite{Niziol}.
+By definition $\Dcal(k)$ is contained in the  complement of this locus, which (by the very definition of logarithmic strata) can be written as a union of log strata of positive codimension.
+Since $\Dcal(k)$ has codmension $1$, it must therefore be equal to a union of log divisors.\end{proof}
+In \S \ref{} we discussed a procedure for enumerating the log strata of $\VZ_{1,\alpha}(\PP^N|H,d)$, using the cones of the tropicalisation $\Sigma_{1,\alpha}(\PP^N|H,d)$..
+This shows that every divisorial logarithmic stratum is obtained via a three-step process:
 \begin{enumerate}
-\item choose the combinatorial type of a tropical map;
-\item subdivide the corresponding tropical moduli space;
+\item choose a combinatorial type $\Delta$ of a tropical map;
+\item subdivide the corresponding tropical moduli space $\sigma$;
 \item choose a ray in this subdivision.
 \end{enumerate}
-Notice that this process contains some redundancies: once we choose a ray of the tropical moduli space, we obtain a generisation of the intial combinatorial type, given by contracting some edges of the dual graph.
-
-\begin{example} \end{example}
-
-Whenever we consider a logarithmic stratum in $\VZ$, by its combinatorial type we will always mean the generisation of the ``initial'' combinatorial type induced by our choice of cone in the polyhedral subdivision.
-This does not depend on the choice of initial combinatorial type.
-
-Now, the logarithmic divisors which are contained in $\Dcal(k)$ are precisely those whose corresponding combinatorial type has the vertex of the dual graph containing $x_k$ mapped into the interior $\RR_{>0} \subseteq \RR_{\geq 0}$.
-
-Thus, via the above procedure, we are able to enumerate the irreducible components of $\Dcal(k)$ in a combinatorial manner.
-The combinatorial type and choice of ray allows us to describe the general element of such a component.
+Notice that this process contains some redundancies: once we choose a ray of the tropical moduli space, we obtain a \textbf{generisation} of the intial combinatorial type, given by contracting some edges of the dual graph and/or moving some vertices from $\RR_{>0}$ to $0$.
+By the combinatorial type of a stratum in $\VZ_{1,\alpha}(\PP^N|H,d)$ we will always mean this generisation of the ``initial'' combinatorial type $\Delta$; this is independent of the choice of $\Delta$.
+
+The log divisors contained in $\Dcal(k)$ are precisely those whose  combinatorial type has the vertex of the dual graph containing $x_k$ mapped into the interior $\RR_{>0} \subseteq \RR_{\geq 0}$.
+Thus via the above procedure, we are able to enumerate the irreducible components of $\Dcal(k)$ in a combinatorial manner.
+The combinatorial type allows us to describe the general element of such a component.
 What we are still lacking is a recursive description of the components, which we need in order to compute integrals over them.
@@
 
-\subsection{Recursive description of the divisors: types $A,B$ and $C^+$}
-
-The basic idea is as follows.
-Choose an irreducible component $\Dcal \subseteq \Dcal(k)$.
-As discussed above, we can obtain this by choosing an ``initial'' combinatorial type together with a ray of the resulting subdivision of the tropical moduli space.
-Without loss of generality we may assume that this ``initial'' combinatorial type coincides with the ``true'' combinatorial type of $\Dcal$ obtained by performing the edge contractions specified by the choice of ray.
-
-Since $\VZ \to \Mcal$ is a log modification, the divisor $\Dcal$ is either exceptional or the proper transform of a logarithmic divisor on $\Mcal$.
-In this subsection, we will focus on the latter case.
-Then if we let $\Dcal_{\Mcal}^\circ\subseteq \Mcal$ denote the locally closed stratum corresponding to our choice of combinatorial type, and $\Dcal_\Mcal = \overline{\Dcal^\circ_\Mcal}$ denote the corresponding logarithmic divisor in $\Mcal$, then our divisor $\Dcal\subseteq\VZ$ is the proper transform of $\Dcal_\Mcal$, which is obtained by taking the preimage $\Dcal^\circ$ of $\Dcal_\Mcal^\circ$ (since $\Dcal^\circ_\Mcal$ is disjoint from the blown-up locus) and then taking its closure in $\VZ$.
-This is, of course, different from taking the preimage of $\Dcal_\Mcal$, since in general $\Dcal_\Mcal$ will intersect the blown-up locus.
-By continuity we have an induced map:
-\begin{equation*} \Dcal \to \Dcal_\Mcal. \end{equation*}
-The remainder of this section will be dedicated to showing how the map $\Dcal \to \Dcal_\Mcal$ may be interpreted as a blow-up.
-The reason this is useful is that $\Dcal_\Mcal$ itself has a recursive description in terms of moduli spaces of punctured maps (see \S \ref{subsection punctured maps}), which in our setting we are able to compute integrals over.
-
-For the remainder of this subsection, we will consider only the situation where the circuit is assigned a positive degree by the combinatorial type; the other, more complicated case, will be taken up in \S \ref{}.
+\subsection{Recursive description of the divisors: types $A,B$ and $C^+$} Choose an irreducible component $\Dcal \subseteq \Dcal(k)$. This is a log divisor, and hence may be written as:
+\begin{equation*} \Dcal = \widetilde\Dcal \cap \VZ_{1,\alpha}(\PP^N|H,d) \end{equation*}
+for a unique log stratum $\widetilde\Dcal \subseteq \widetilde{\VZ}_{1,\alpha}(\PP^N|H,d)$. Since
+\begin{equation*}\widetilde{\VZ}_{1,\alpha}(\PP^N|H,d) \to \ol\Mcal^{\Kim}_{1,\alpha}(\PP^N|H,d)\end{equation*}
+is a log modification, $\widetilde{\Dcal}$ is either exceptional or the proper transform of a log divisor.
+These cases correspond, respectively, to when the circuit is assigned zero degree or nonzero degree by the combinatorial type.
+To begin with we will focus on the latter case.
+Suppose therefore that $\widetilde{\Dcal}$ is the proper transform of a divisor:
+\begin{equation*} \Dcal_\Mcal \subseteq \ol\Mcal^{\Kim}_{1,\alpha}(\PP^N|H,d). \end{equation*}
+The birational map $\widetilde{\Dcal} \to \Dcal_\Mcal$ induces a morphism $\rho \colon \Dcal \to \Dcal_\Mcal$.
+The remainder of this subsection will be devoted to showing how $\rho$ may be interpreted as a ``desingularisation of the main component''.
+Since $\Dcal_\Mcal$ admits a recursive description (in terms of relative and rubber moduli spaces), this will allow us to compute integrals over $\Dcal$ recursively.
 
@@
 \begin{enumerate}
-\item the vertices $\sqC_1,\ldots,\sqC_r$ have positive degree (and $\sqC_0$ has positive degree in the $\Ycal_C^+$ case);
+\item the vertices $\sqC_1,\ldots,\sqC_r$ have positive degree (and the circuit always has positive degree);
 \item every vertex is stable;

### 2019-03-11 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
Fixed proof of enumeration of type A,B,C+ loci

@@
 \draw [red,fill=red] (0,-2) circle[radius=2pt];
-\draw [->,red,thick] (0,-2) -- (2,-2);
-\draw (2,-2) node[right,red]{\tiny{$\Sigma(\PP^N|H)$}};
+\draw [->,red,thick] (0,-2) -- (3,-2);
+\draw [red,fill=red] (2,-2) circle[radius=2pt];
 \draw [->,red] (1,-0.9) -- (1,-1.6);
+
+\draw [red] (2,-2) node[above]{\tiny$\diamond$};
+\draw [red] (0,-2) node[above]{\tiny$0$};
 
@@
 \draw [red,fill=red] (0,-2) circle[radius=2pt];
-\draw [->,red,thick] (0,-2) -- (2,-2);
-\draw (2,-2) node[right,red]{\tiny{$\Sigma(\PP^N|H)$}};
+\draw [->,red,thick] (0,-2) -- (3,-2);
+\draw [red,fill=red] (2,-2) circle[radius=2pt];
 \draw [->,red] (1,-0.9) -- (1,-1.6);
+\draw [red] (2,-2) node[above]{\tiny$\diamond$};
+\draw [red] (0,-2) node[above]{\tiny$0$};
 
@@
 \draw [red,fill=red] (0,-2) circle[radius=2pt];
-\draw [->,red,thick] (0,-2) -- (2,-2);
-\draw (2,-2) node[right,red]{\tiny{$\Sigma(\PP^N|H)$}};
+\draw [->,red,thick] (0,-2) -- (3,-2);
+\draw [red,fill=red] (2,-2) circle[radius=2pt];
+\draw [red] (2,-2) node[above]{\tiny$\diamond$};
+\draw [red] (0,-2) node[above]{\tiny$0$};
 \draw [->,red] (1,-0.9) -- (1,-1.6);
@@
 \newcommand{\Kim}{\operatorname{Kim}}
+\newcommand{\ACGS}{\operatorname{ACGS}}
 
@@
 \section{Recursive description of boundary strata: the reduced splitting axiom}
-In this section, the most technically difficult of the paper, we provide an explicit description of the terms appearing on the right-hand side of \eqref{equation recursion} above.
-For each term, we provide a combinatorial means to calculate the vanishing order $\lambda_\Dcal$, and a recursive description of the stratum $\Dcal$ in terms of fibre products of moduli spaces with smaller numerical data.
+In this section we provide an explicit description of the terms appearing on the right-hand side of \eqref{equation recursion} above.
+For each such term, we provide a combinatorial method to calculate the vanishing order $\lambda_\Dcal$, and a recursive description of the stratum $\Dcal$ in terms of fibre products of moduli spaces with smaller numerical data.
+This constitutes the most technically difficult part of the paper.
 
@@
 
-\begin{lemma} Every irreducible component of $\Dcal(k)$ is a codimension $1$ log stratum.\end{lemma}
+\begin{lemma} \label{Lemma components are log divisors} Every irreducible component of $\Dcal(k)$ is a codimension $1$ log stratum.\end{lemma}
 \begin{proof} This is not hard to see: the locus where the log structure is trivial coincides precisely with the  locus where the source curve is smooth and not mapped inside $H$, and since $\VZ_{1,\alpha}(\PP^N|H,d)$ is log smooth this locus is open and dense \cite{Niziol}.
@@
 Since $\Dcal(k)$ has codmension $1$, it must therefore be equal to a union of log divisors.\end{proof}
-In \S \ref{} we discussed a procedure for enumerating the log strata of $\VZ_{1,\alpha}(\PP^N|H,d)$, using the cones of the tropicalisation $\Sigma_{1,\alpha}(\PP^N|H,d)$..
-This shows that every divisorial logarithmic stratum is obtained via a three-step process:
+In \S \ref{} we discussed a procedure for enumerating the log strata of $\VZ_{1,\alpha}(\PP^N|H,d)$, using the cones of the tropicalisation $\Sigma_{1,\alpha}(\PP^N|H,d)$.
+To recap: every divisorial logarithmic stratum is obtained via a three-step process:
 \begin{enumerate}
@@
 \end{enumerate}
-Notice that this process contains some redundancies: once we choose a ray of the tropical moduli space, we obtain a \textbf{generisation} of the intial combinatorial type, given by contracting some edges of the dual graph and/or moving some vertices from $\RR_{>0}$ to $0$.
-By the combinatorial type of a stratum in $\VZ_{1,\alpha}(\PP^N|H,d)$ we will always mean this generisation of the ``initial'' combinatorial type $\Delta$; this is independent of the choice of $\Delta$.
-
-The log divisors contained in $\Dcal(k)$ are precisely those whose  combinatorial type has the vertex of the dual graph containing $x_k$ mapped into the interior $\RR_{>0} \subseteq \RR_{\geq 0}$.
-Thus via the above procedure, we are able to enumerate the irreducible components of $\Dcal(k)$ in a combinatorial manner.
-The combinatorial type allows us to describe the general element of such a component.
+Notice that this process contains some redundancies: upon choosing a ray in the tropical moduli space, some of the edge lengths or vertex positions may get set to $0$.
+This induces a generisation of the intial combinatorial type $\Delta$, given by contracting the corresponding edges of the dual graph and moving the corresponding vertices from $\RR_{>0}$ to $0$.
+By the combinatorial type of a stratum in $\VZ_{1,\alpha}(\PP^N|H,d)$ we will always mean this generisation.
+This is independent of the choice of $\Delta$, and in fact we can (and will) always choose $\Delta$ to coincide with the generisation.
+
+The log divisors contained in $\Dcal(k)$ are precisely those whose  combinatorial types map the vertex of the dual graph containing $x_k$  into the interior $\RR_{>0} \subseteq \RR_{\geq 0}$.
+Thus via the above procedure, we are able to enumerate the irreducible components of $\Dcal(k)$ in a combinatorial manner, and the combinatorial type $\Delta$ allows us to describe the general element of such a component.
 What we are still lacking is a recursive description of the components, which we need in order to compute integrals over them.
@@
 
-\subsection{Recursive description of the divisors: types $A,B$ and $C^+$} Choose an irreducible component $\Dcal \subseteq \Dcal(k)$. This is a log divisor, and hence may be written as:
+\subsection{Recursive description of the divisors: types $A,B$ and $C^+$} Choose an irreducible component $\Dcal \subseteq \Dcal(k)$.
+By Lemma \ref{Lemma components are log divisors} this is a log divisor, and hence may be written as:
 \begin{equation*} \Dcal = \widetilde\Dcal \cap \VZ_{1,\alpha}(\PP^N|H,d) \end{equation*}
@@
 Suppose therefore that $\widetilde{\Dcal}$ is the proper transform of a divisor:
-\begin{equation*} \Dcal_\Mcal \subseteq \ol\Mcal^{\Kim}_{1,\alpha}(\PP^N|H,d). \end{equation*}
-The birational map $\widetilde{\Dcal} \to \Dcal_\Mcal$ induces a morphism $\rho \colon \Dcal \to \Dcal_\Mcal$.
+\begin{equation*} \Dcal^{\Kim} \subseteq \ol\Mcal^{\Kim}_{1,\alpha}(\PP^N|H,d). \end{equation*}
+The birational map $\widetilde{\Dcal} \to \Dcal^{\Kim}$ induces a morphism $\rho \colon \Dcal \to \Dcal^{\Kim}$.
 The remainder of this subsection will be devoted to showing how $\rho$ may be interpreted as a ``desingularisation of the main component''.
-Since $\Dcal_\Mcal$ admits a recursive description (in terms of relative and rubber moduli spaces), this will allow us to compute integrals over $\Dcal$ recursively.
-
-\begin{lemma} Let $\Dcal \subseteq \Dcal(k)$ be an irreducible component and let $\Delta$ be the corresponding combinatorial type.
+Since $\Dcal^{\Kim}$ admits a recursive description (in terms of relative and rubber moduli spaces), this will allow us to compute integrals over $\Dcal$.
+
+\begin{lemma} Let $\Dcal \subseteq \Dcal(k)$ be an irreducible component which contributes nontrivially to the recursion, and let $\Delta$ be the corresponding combinatorial type.
 Suppose that $\Delta$ assigns positive degree to the circuit.
@@
         \Yagraph
-        \caption{$\mathcal Y_A$}
+        \caption{$A$}
     \end{minipage}\hfill
@@
         \Ybgraph
-        \caption{$\mathcal Y_B$}
+        \caption{$B$}
     \end{minipage}\hfill
@@
         \Ycgraph
-        \caption{$\Ycal_C^+$}
+        \caption{$C^+$}
     \end{minipage}
@@
 \noindent The terminology is due to Vakil, and the picture in this case is very similar to \cite{Vre} (as we will see later, when the circuit is contracted the picture becomes \emph{very} different).
-Note that in these pictures we have omitted the marked points (apart from $x_k$), the degree of each vertex, and the expansion factors of the edges.
-These combinatorial data can be distributed arbitrarily, as long as:
+Note that in these pictures we have deliberately omitted the marked points (except for $x_k$), the degree of each vertex, and the expansion factors of the edges.
+The omitted combinatorial data can be distributed arbitrarily, as long as:
 \begin{enumerate}
-\item the vertices $\sqC_1,\ldots,\sqC_r$ have positive degree (and the circuit always has positive degree);
+\item the vertices $\sqC_1,\ldots,\sqC_r$ have positive degree;
+\item the ellipse\footnote{(Navid) Didn't we decide this was our new terminology for the circuit?} has positive degree;
 \item every vertex is stable;
@@
 
-\begin{proof}
-Recall that we have $\Dcal\subseteq\VZ$ obtained by a choice of combinatorial type and ray in the subdivison of the tropical moduli space.
-In this situation, since the circuit has positive degree no alignment is necessary (both radii are zero), and hence the subdivision is trivial.
-Following our procedure, we choose a ray of the tropical moduli space $Q^\vee_{\RR}$.
-Since this is generated by edge lengths, and we are assuming that the initial and generised combinatorial types coincide, we conclude that the tropical moduli space must be $\RR_{\geq 0}$.
-Since we are assuming that $\Dcal \subseteq \Dcal(k)$, we know that the vertex of the tropicalisation which contains the flag $x_k$ must map into the interior $\RR_{>0}\subseteq \RR_{\geq 0}$.
-
-We claim that this is the only vertex of the tropical curve mapped into the interior; if there were more, the positions of their images in $\RR_{> 0}$ would be independent, and thus the tropical moduli space would have dimension $\geq 2$, a contradiction.\footnote{(Luca) Say something about rigid tropical curves as in ACGS and KLR}
-
-Thus there is a single vertex $\sqC_0$ mapped into the interior $\RR_{>0} \subseteq \RR_{\geq 0}$ and a number of vertices $\sqC_1,\ldots,\sqC_r$ mapped onto the vertex $0 \in \RR_{\geq 0}$.
-No pair of $\sqC_1,\ldots,\sqC_r$ can be connected by an edge, since this would introduce an extra edge length to the tropical moduli space, which then once again would have dimension $\geq 2$.
-Each of $\sqC_1,\ldots,\sqC_r$ must have positive degree by the tropical balancing condition and must be connected to $\sqC_0$ (since the tropical curve must be connected).
-
-Thus, we see that the combinatorial type takes the form of a bipartite graph, with $\sqC_0$ on the right-hand side and $\sqC_1,\ldots,\sqC_r$ on the left-hand side.
-Note that the continuity of the tropical map identifies all of the edge lengths, up to weights given by the expansion factors (i.e.
-tangency orders) at the edges; thus the tropical moduli space is isomorphic to $\RR_{\geq 0}$ and so we have a divisor as expected.
-
-We distinguish three cases, depending on the position of the circuit, giving the three forms presented in the statement of the lemma.\end{proof}
+\begin{proof} Let $\sigma \in \Sigma^{\Kim}$ be the cone corresponding to the stratum $\Dcal^{\Kim} \subseteq \ol\Mcal^{\Kim}_{1,\alpha}(\PP^N|H,d)$.
+By the discussion above $\Dcal$ corresponds to a ray in the subdivision of $\sigma$ given by imposing the central alignment condition.
+But since the ellipse is assigned positive degree, both radii are equal to $0$ and the subdivision is trivial.
+We conclude that $\sigma=\RR_{\geq 0}$ (recall we are assuming that the initial and generised combinatorial types coincide).
+Since there must be at least one vertex mapped to higher level, we conclude that the tropical target $\tilde\RR_{\geq 0}$ is obtained from $\RR_{\geq 0}$ by subdividing at a single point $\diamond \in \RR_{> 0}$.
+
+In order to have $\sigma=\RR_{\geq 0}$, the dual graph $\Gamma$ must be a bipartite graph with vertices over $0$ and $\diamond$.
+The cases $A,B$ and $C^+$ enumerated above cover situations where there is a single vertex mapped to $\diamond$.
+We claim that if there is more than one such vertex, then the contribution to the recursion is trivial.
+To see this, we consider the locus
+\begin{equation*} \Dcal^{\ACGS} \subseteq \ol\Mcal^{\log}_{1,\alpha}(\PP^N|H,d) \end{equation*}
+to which $\Dcal^{\Kim}$ maps under the collapsing map.
+The codimension of $\Dcal^{\ACGS}$ is given by the dimension of the associated tropical moduli space; if there is more than one vertex mapped to higher level then this is strictly larger than $1$, which is the codimension of $\Dcal^{\Kim}$.
+Thus the map $\Dcal^{\Kim} \to \Dcal^{\ACGS}$ has positive-dimensional fibres, and since all insertions are pulled back from the latter space the contribution vanishes by the projection formula.\end{proof}
+
+\begin{remark} The difference in dimensions between $\Dcal^{\Kim}$ and $\Dcal^{\ACGS}$ may be interpreted as the difference in dimensions between moduli spaces of \emph{disonnected} rubber and their images under the collapsing map (see \ref{} below).
+\end{remark}
 

### 2019-03-12 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
Finished type A description first new pass. Need to go back and make notation less painful

@@
 \newcommand{\sidenote}[1]{\marginpar{\textbf{\color{red}#1}}}
+\newcommand{\lcm}{\operatorname{lcm}}
 
@@
 \draw (0,-1) circle(2pt)[fill=black];
-\draw [red,fill=red] (0,-2) circle[radius=2pt];
-\draw [->,red,thick] (0,-2) -- (3,-2);
-\draw [red,fill=red] (2,-2) circle[radius=2pt];
-\draw [->,red] (1,-0.9) -- (1,-1.6);
-
-\draw [red] (2,-2) node[above]{\tiny$\diamond$};
-\draw [red] (0,-2) node[above]{\tiny$0$};
+\draw [blue,fill=blue] (0,-2) circle[radius=2pt];
+\draw [->,blue,thick] (0,-2) -- (3,-2);
+\draw [blue,fill=blue] (2,-2) circle[radius=2pt];
+\draw [->,blue] (1,-0.9) -- (1,-1.6);
+
+\draw [blue] (2,-2) node[above]{\tiny$\diamond$};
+\draw [blue] (0,-2) node[above]{\tiny$0$};
 
@@
 \draw (0,-1) circle(2pt)[fill=black];
-\draw [red,fill=red] (0,-2) circle[radius=2pt];
-\draw [->,red,thick] (0,-2) -- (3,-2);
-\draw [red,fill=red] (2,-2) circle[radius=2pt];
-\draw [->,red] (1,-0.9) -- (1,-1.6);
-\draw [red] (2,-2) node[above]{\tiny$\diamond$};
-\draw [red] (0,-2) node[above]{\tiny$0$};
+\draw [blue,fill=blue] (0,-2) circle[radius=2pt];
+\draw [->,blue,thick] (0,-2) -- (3,-2);
+\draw [blue,fill=blue] (2,-2) circle[radius=2pt];
+\draw [->,blue] (1,-0.9) -- (1,-1.6);
+\draw [blue] (2,-2) node[above]{\tiny$\diamond$};
+\draw [blue] (0,-2) node[above]{\tiny$0$};
 
@@
 \draw (0,-1) circle(2pt)[fill=black];
-\draw [red,fill=red] (0,-2) circle[radius=2pt];
-\draw [->,red,thick] (0,-2) -- (3,-2);
-\draw [red,fill=red] (2,-2) circle[radius=2pt];
-\draw [red] (2,-2) node[above]{\tiny$\diamond$};
-\draw [red] (0,-2) node[above]{\tiny$0$};
-\draw [->,red] (1,-0.9) -- (1,-1.6);
+\draw [blue,fill=blue] (0,-2) circle[radius=2pt];
+\draw [->,blue,thick] (0,-2) -- (3,-2);
+\draw [blue,fill=blue] (2,-2) circle[radius=2pt];
+\draw [blue] (2,-2) node[above]{\tiny$\diamond$};
+\draw [blue] (0,-2) node[above]{\tiny$0$};
+\draw [->,blue] (1,-0.9) -- (1,-1.6);
 
@@
 
-\section{Gathmann's line bundle through tropical geometry} Consider a reduced relative space $\VZ_{1,\alpha}(\PP^N|H,d)$.
+\section{Gathmann's line bundle through tropical geometry}\label{Section Gathmann line bundle} Consider a reduced relative space $\VZ_{1,\alpha}(\PP^N|H,d)$.
 For each marking $x_k$ we consider the locus $\Dcal(k) \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$ where $x_k$ belongs to an internal component of the collapsed map.
@@
 For each such term, we provide a combinatorial method to calculate the vanishing order $\lambda_\Dcal$, and a recursive description of the stratum $\Dcal$ in terms of fibre products of moduli spaces with smaller numerical data.
+The form which this recursive description takes is non-obvious, in the sense that additional tautological classes appear, which must be calculated.
 This constitutes the most technically difficult part of the paper.
@@
 The cases $A,B$ and $C^+$ enumerated above cover situations where there is a single vertex mapped to $\diamond$.
-We claim that if there is more than one such vertex, then the contribution to the recursion is trivial.
-To see this, we consider the locus
+We claim that if there is more than one such vertex, then the contribution to the recursion vanishes.
+To see this, we consider the stratum
 \begin{equation*} \Dcal^{\ACGS} \subseteq \ol\Mcal^{\log}_{1,\alpha}(\PP^N|H,d) \end{equation*}
-to which $\Dcal^{\Kim}$ maps under the collapsing map.
-The codimension of $\Dcal^{\ACGS}$ is given by the dimension of the associated tropical moduli space; if there is more than one vertex mapped to higher level then this is strictly larger than $1$, which is the codimension of $\Dcal^{\Kim}$.
-Thus the map $\Dcal^{\Kim} \to \Dcal^{\ACGS}$ has positive-dimensional fibres, and since all insertions are pulled back from the latter space the contribution vanishes by the projection formula.\end{proof}
+to which $\Dcal^{\Kim}$ maps under the collapsing morphism.
+The codimension of $\Dcal^{\ACGS}$ is given by the dimension of the associated cone in the tropicalisation $\Sigma^{\log}$; if there is more than one vertex mapped to higher level then this is strictly greater than $1$, in contrast to the cone in $\Sigma^{\Kim}$.
+Therefore the map $\Dcal^{\Kim} \to \Dcal^{\ACGS}$ has positive-dimensional fibres, and since all insertions are pulled back from the latter space the contribution vanishes by the projection formula.\end{proof}
 
@@
 
-\subsubsection{Type $A$} Let $\Delta$ be a combinatorial type of type $A$ and let $\Dcal\subseteq\VZ$ be the corresponding logarithmic divisor (note there is no choice of ray here).
-The corresponding locus $\Dcal_\Mcal\subseteq\Mcal$ is given (up to a finite cover) by\footnote{(Navid) Include short appendix on integralisation/saturation when gluing punctured maps in our setting?}:
-\begin{equation*}\Dcal_\Mcal=\Mpunct{0}{\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}{H}{d_0}\times_{H^r}\left( \Mlog{1}{\alpha^{(1)}\cup(m_1)}{\PP^N|H}{d_1} \times \prod_{i=2}^r\Mlog{0}{\alpha^{(i)}\cup(m_i)}{\PP^N|H}{d_i} \right).
-\end{equation*}
-\begin{lemma}We have the following description of $\Dcal$\begin{equation}\label{type A splitting axiom}\Dcal=\Mpunct{0}{\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}{H}{d_0}\times_{H^r}\left(\VZ_{1,\alpha^{(1)}\cup(m_1)}(\PP^N|H,d_1)\times\prod_{i=2}^r\Mlog{0}{\alpha^{(i)}\cup(m_i)}{\PP^N|H}{d_i}\right) \end{equation}
-i.e. the map $\Dcal\to\Dcal_\Mcal$ is given by blowing up one of the factors of the fibre product.\end{lemma} Note that there is a birational map which forgets the log structures
-\begin{equation*} \Mpunct{0}{\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}{H}{d_0} \to \M{0}{n_0+r}{H}{d_0} \end{equation*}
-and all of our insertions are pulled back from the latter space. Therefore the integrals over the punctured space are determined by the genus zero Gromov--Witten theory of $H\cong\PP^{N-1}$.
-
-%DEPRECATED?/WRONG?
-
-%Note that if $\sqC_0$ degenerates further then it may be the case that there are components of $\sqC_0$ contained inside the contraction radius for $\sqC$, and thus once we contract to a Smyth curve there are components of $\sqC_0$ adjacent to the genus one singularity.
-However, in this case when we split off $\sqC_1$ these components disappear, and if the factorisation condition holds for $\sqC$ then it holds a fortiori for $\sqC_1$.\footnote{(Navid) I think this is right, but could someone check?
-Maybe there's a better way to say this.} Thus we obtain a morphism from $\Dcal$ to the fibre product on the right-hand side of \eqref{type A splitting axiom}.
+\subsubsection{Type $A$} Let $\Delta$ be a combinatorial type of type $A$ and let $\Dcal\subseteq\VZ_{1,\alpha}(\PP^N|H,d)$ be the corresponding logarithmic divisor.
+The corresponding locus $\Dcal^{\Kim} \subseteq \ol\Mcal^{\Kim}_{1,\alpha}(\PP^N|H,d)$ admits a finite splitting morphism to the fibre product
+\begin{equation*} \Dcal^{\Kim} \xrightarrow{\rho^{\Kim}} \ol\Mcal^{\Kim \leftrightarrow}_{0,\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}(P|H_0+H_\infty,d_0)\times_{H^r}\left( \ol\Mcal^{\Kim}_{1,\alpha^{(1)}\cup(m_1)}(\PP^N|H,d_1) \times \prod_{i=2}^r \ol\Mcal^{\Kim}_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i) \right) \end{equation*}
+where the degree of $\rho^{\Kim}$ is given by
+\begin{equation} \label{degree of gluing} \dfrac{\prod_{i=1}^r m_i}{\lcm(m_1,\ldots,m_r)} \end{equation}
+and is calculated in the usual way, by examining the base order of the corresponding family of targets \cite[\S 5]{ACGSDecomposition}.
+
+\begin{lemma} \label{Lemma type A gluing} $\Dcal$ admits a natural morphism
+\begin{equation*}\Dcal \xrightarrow{\rho} \ol\Mcal^{\Kim \leftrightarrow}_{0,\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}(P|H_0+H_\infty,d_0)\times_{H^r}\left(\VZ_{1,\alpha^{(1)}\cup(m_1)}(\PP^N|H,d_1)\times\prod_{i=2}^r \ol\Mcal^{\Kim}_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i)\right) \end{equation*}
+of degree the same given by the same formula \eqref{degree of gluing}, such that the map $\Dcal \to \Dcal^{\Kim}$ covers the map on fibre products obtained by desingularising the main component of the $C_1$ factor.\end{lemma}
+
 \begin{proof}
-Note first of all that the map $\Dcal\to\Dcal_\Mcal$ is an isomorphism away from the blown-up locus, which is contained inside the locus where the circuit is contracted.
-Given an element of $\Dcal$ we can split it along the nodes $q_1,\ldots,q_r$ as in \cite{PuncturedMaps}.
+Note first of all that the map $\Dcal\to\Dcal^{\Kim}$ is an isomorphism away from the blown-up locus, which is contained inside the locus where the circuit is contracted.
+Given an element of $\Dcal$ we can split it along the nodes $q_1,\ldots,q_r$ as in \cite{}.
 It is then clear that $\sqC_1$ is aligned.
 We claim that $\sqC$ satisfies the factorisation property if and only if $\sqC_1$ does.
-This is enough to show \eqref{type A splitting axiom}.
-
-On $\sqC$ there is an associated contraction radius $\delta$ passing through a non-contracted vertex, such that the strict interior only contains contracted vertices.
-\begin{lemma}\label{type A radius lemma}$\lambda(\sqC^\prime) > \delta$ for any component $\sqC^\prime$ of $\sqC_0$.\end{lemma}
-\noindent Assuming this holds, we see as a consequence that $\sqC_0,\sqC_2,\ldots,\sqC_r$ must lie outside the contraction radius.
-Consequently the aligned curve $\sqC$ satisfies the factorisation condition if and only if $\sqC_1$ does, so \eqref{type A splitting axiom} holds.
-
-\begin{proof} The basic point is that $\Dcal$ consists of the union of the locally closed logarithmic strata adjacent to the locally closed stratum where all the $\sqC_i$ are irreducible.
-If we look at one of these boundary strata, the tropical moduli space contains a ray $\sigma$ corresponding to the stratum where all the $\sqC_i$ are irreducible; this amounts to setting all edge lengths other than $e_1,\ldots,e_r$ to zero.
-If $f_1,\ldots,f_l$ are some number of these additional edge lengths (corresponding to internal nodes in degenerations of the $\sqC_i$) then all of the cones of the subdivision adjacent to $\sigma$ will have $f_1+\ldots+f_l < e_j$ for all $j\in\{1,\ldots,r\}$, since $f_1=\ldots=f_l=0$ and $e_j \neq 0$ on $\sigma$.
-In particular, if $\sqC_1$ is degenerate and if $f$ denotes the minimal distance from the circuit to a non-contracted vertex of $\sqC_1$ (which certainly exists since $\sqC_1$ has positive degree) then $f < e_1 \leq \lambda(\sqC^\prime)$.
-Thus $\delta=f$ and $\delta < \lambda(\sqC^\prime)$ as claimed.\footnote{(Navid) Do an example?}\end{proof}
-\noindent Notice we did not specify whether $\delta$ was the relative or absolute radius.
-The point is that it does not matter; the proof goes through the same in either case.
-Thus we see that $\sqC$ satisfies the (double) factorisation condition if and only if $\sqC_1$ does.\end{proof}
+This immediately implies the lemma.
+
+On $\sqC$ there are associated contraction radii $\delta_1,\delta_2$.
+Let $\delta \in \{\delta_1,\delta_2\}$.
+By Lemma \ref{type A radius lemma} below, we have $\lambda(\sqC^\prime) > \delta$ for any component $\sqC^\prime$ of $\sqC_0$.
+This means that $\sqC_0,\sqC_2,\sqC_3,\ldots,\sqC_r$ lie outside both contraction radii, and so the aligned curve $\sqC$ satisfies the factorisation condition if and only if $\sqC_1$ does.
+\end{proof}
+
+\begin{lemma}\label{type A radius lemma} $\lambda(\sqC^\prime) > \delta$ for any component $\sqC^\prime$ of $\sqC_0$ (with notation as in the proof above).\end{lemma}
+\begin{proof} The basic point is that $\Dcal$ is obtained as the disjoint union of the locally closed logarithmic strata contained in the closure of the stratum where all of the $\sqC_i$ are irreducible.
+If we look at one of these boundary strata, then by definition the associated cone $\sigma \in \Sigma_{1,\alpha}(\PP^N|H,d)$ contains a ray $\tau$ corresponding to the stratum where all the $\sqC_i$ are irreducible; this amounts to setting all edge lengths other than $e_1,\ldots,e_r$ to zero.
+If $f_1,\ldots,f_l$ are some collection of additional edge lengths in $\sigma$ (corresponding to internal nodes in degenerations of the $\sqC_i$) then since $\sigma$ is adjacent to $\tau$ we must have (by construction of the subdivision) $f_1+\ldots+f_l < e_j$ for all $j\in\{1,\ldots,r\}$, since $f_1=\ldots=f_l=0$ and $e_j \neq 0$ on $\tau$.
+In particular, if $\sqC_1$ is degenerate and if $\delta$ denotes the minimal distance from the circuit to a non-contracted vertex of $\sqC_1$ (which certainly exists since $\sqC_1$ has positive degree) then $\delta < e_1 \leq \lambda(\sqC^\prime)$, as claimed.\end{proof}
+
+Lemma \ref{Lemma type A gluing} provides a means to calculate integrals over $\Dcal$ in terms of integrals over the factors in the fibre product.
+The missing piece is the vanishing order $\lambda_\Dcal$ of the section $s_k$ (constructed in \S \ref{Section Gathmann line bundle} above) along $\Dcal$.
+
+\begin{lemma} \label{lemma vanishing order type A} $\lambda_\Dcal = \lcm(m_1,\ldots,m_r).$ \end{lemma}
+\begin{proof} Let $\tau \in \Sigma_{1,\alpha}(\PP^N|H,d)$ be the cone corresponding to $\Dcal$ and let
+\begin{equation*} \varphi \colon \Sigma_{1,\alpha}(\PP^N|H,d) \to \Sigma^{\log} \to \RR_{\geq 0} \end{equation*}
+be the piecewise-linear function constructed in \S \ref{Section Gathmann line bundle}.
+It follows from the tropical description that $\lambda_\Dcal$ is equal to the index of the map $\tau \to \RR_{\geq 0}$ obtained by restricting $\varphi$.
+The cone $\tau$ has as an integral generator $f=m_i e_i/\lcm(m_1,\ldots,m_r)$.
+Given $v \in \tau$ the target edge length $\varphi(v)$ is given by
+\begin{equation*} l=m_i e_i = \lcm(m_1,\ldots,m_r) f \end{equation*}
+which shows that the index $\lambda_\Dcal = \lcm(m_1,\ldots,m_r)$.\end{proof}
+
+Lemma \ref{lemma vanishing order type A} together with the degree calculation \eqref{degree of gluing} determines the numerics of integrals over $\lambda_\Dcal [\Dcal]$.
 

### 2019-03-12 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
Finished type A,B,C+ description, up to some major overhaul of the notation

@@
 
-We now now investigate the three types $A,B,C^+$ separately, giving a recursive description of the boundary locus in each case.
-
-\subsubsection{Type $A$} Let $\Delta$ be a combinatorial type of type $A$ and let $\Dcal\subseteq\VZ_{1,\alpha}(\PP^N|H,d)$ be the corresponding logarithmic divisor.
-The corresponding locus $\Dcal^{\Kim} \subseteq \ol\Mcal^{\Kim}_{1,\alpha}(\PP^N|H,d)$ admits a finite splitting morphism to the fibre product
+We now now investigate the three types $A,B,C^+$ separately, giving a recursive description of the boundary divisor in each case.
+For the remainder of this subsection, therefore, we fix a one-dimensional cone $\tau \in \Sigma_{1,\alpha}(\PP^N|H,d)$, let $\Dcal \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$ be the associated log divisor, and assume that $\Dcal \subseteq \Dcal(k)$ and is of type $A,B$ or $C^+$.
+We let $\Dcal^{\Kim} \subseteq \ol\Mcal_{1,\alpha}^{\Kim}(\PP^N|H,d)$ be the log stratum into which $\Dcal$ is mapped.
+Note that (since we are restricting to the type $A,B,C^+$ cases), $\Dcal^{\Kim}$ is also a log divisor, indexed by a cone $\epsilon \in \Sigma^{\Kim}$ which corresponds to a combinatorial type $\Delta$.
+Moreover, $\Dcal$ is the proper transform of $\Dcal^{\Kim}$ under the blow-up map.
+
+\subsubsection{Type $A$}\label{subsubsection type A} Suppose $\Delta$ is of type $A$. Then \cite[\S 7]{ChenDegeneration} $\Dcal^{\Kim}$ admits a finite splitting morphism onto the fibre product
 \begin{equation*} \Dcal^{\Kim} \xrightarrow{\rho^{\Kim}} \ol\Mcal^{\Kim \leftrightarrow}_{0,\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}(P|H_0+H_\infty,d_0)\times_{H^r}\left( \ol\Mcal^{\Kim}_{1,\alpha^{(1)}\cup(m_1)}(\PP^N|H,d_1) \times \prod_{i=2}^r \ol\Mcal^{\Kim}_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i) \right) \end{equation*}
-where the degree of $\rho^{\Kim}$ is given by
-\begin{equation} \label{degree of gluing} \dfrac{\prod_{i=1}^r m_i}{\lcm(m_1,\ldots,m_r)} \end{equation}
-and is calculated in the usual way, by examining the base order of the corresponding family of targets \cite[\S 5]{ACGSDecomposition}.
+where the degree of $\rho^{\Kim}$ is given by:
+\begin{equation} \label{degree of gluing} \dfrac{\prod_{i=1}^r m_i}{\lcm(m_1,\ldots,m_r)}. \end{equation}
+This is calculated in the usual way, by examining the base order of the corresponding family of targets.
 
@@
 \begin{equation*}\Dcal \xrightarrow{\rho} \ol\Mcal^{\Kim \leftrightarrow}_{0,\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}(P|H_0+H_\infty,d_0)\times_{H^r}\left(\VZ_{1,\alpha^{(1)}\cup(m_1)}(\PP^N|H,d_1)\times\prod_{i=2}^r \ol\Mcal^{\Kim}_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i)\right) \end{equation*}
-of degree the same given by the same formula \eqref{degree of gluing}, such that the map $\Dcal \to \Dcal^{\Kim}$ covers the map on fibre products obtained by desingularising the main component of the $C_1$ factor.\end{lemma}
+of degree given by the same formula \eqref{degree of gluing}, such that the map $\Dcal \to \Dcal^{\Kim}$ covers the map on fibre products obtained by desingularising the main component of the factor corresponding to $\sqC_1$.\end{lemma}
 
 \begin{proof}
-Note first of all that the map $\Dcal\to\Dcal^{\Kim}$ is an isomorphism away from the blown-up locus, which is contained inside the locus where the circuit is contracted.
+The choices involved in gluing log maps to expansions (which accounts for the degrees of the splitting morphisms above) is not affected by the introduction of alignments, so for the purposes of this proof we may act as if $\rho$ and $\rho^{\Kim}$ are the identity maps.
+
+Note that the map $\Dcal\to\Dcal^{\Kim}$ is an isomorphism away from the blown-up locus, which is contained inside the locus where the circuit is contracted.
 Given an element of $\Dcal$ we can split it along the nodes $q_1,\ldots,q_r$ as in \cite{}.
@@
 be the piecewise-linear function constructed in \S \ref{Section Gathmann line bundle}.
-It follows from the tropical description that $\lambda_\Dcal$ is equal to the index of the map $\tau \to \RR_{\geq 0}$ obtained by restricting $\varphi$.
-The cone $\tau$ has as an integral generator $f=m_i e_i/\lcm(m_1,\ldots,m_r)$.
-Given $v \in \tau$ the target edge length $\varphi(v)$ is given by
-\begin{equation*} l=m_i e_i = \lcm(m_1,\ldots,m_r) f \end{equation*}
-which shows that the index $\lambda_\Dcal = \lcm(m_1,\ldots,m_r)$.\end{proof}
-
-Lemma \ref{lemma vanishing order type A} together with the degree calculation \eqref{degree of gluing} determines the numerics of integrals over $\lambda_\Dcal [\Dcal]$.
+It follows from the tropical description that $\lambda_\Dcal$ is equal to the index of the map of integral cones $\tau \to \RR_{\geq 0}$ obtained by restricting $\varphi$.
+By tropical continuity we have $\tau \subseteq \RR_{\geq 0}^r$ with integral generator:
+\begin{equation*} w = \left( \dfrac{\lcm(m_1,\ldots,m_r)}{m_1},\ldots,\dfrac{\lcm(m_1,\ldots,m_r)}{m_r} \right).\end{equation*}
+The map $\tau \to \RR_{\geq 0}$ is given by projecting onto the $i$th factor and then multiplying by $m_i$ (this is independent of $i$).
+Thus we conclude that the index is equal to $\lcm(m_1,\ldots,m_r)$ as claimed.\end{proof}
+
+\noindent This lemma, together with the degree calculation \eqref{degree of gluing}, determines the numerics of integrals over $\lambda_\Dcal [\Dcal]$.
 
 \subsubsection{Type $B$}
-Now let $\Dcal\subseteq\VZ$ be a component of $\Dcal(k)$ with combinatorial type $\Delta$ of type $B$.
-In this case, it is impossible for the circuit to be contracted.
-Thus, $\Dcal_\Mcal \subseteq \Mcal$ is disjoint from the blown-up locus, and the map
-\begin{equation*} \Dcal \to \Dcal_\Mcal \end{equation*}
-is an isomorphism. Thus we obtain:
-\begin{equation*} \Dcal = \Mpunct{0}{\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}{H}{d_0}\times_{H^r}\left(\Mlog{0}{\alpha^{(1)}\cup(m_1,m_2)}{\PP^N|H}{d_1}\times\prod_{i=3}^r\Mlog{0}{\alpha^{(i)}\cup(m_i)}{\PP^N|H}{d_i}\right).\end{equation*}
-As before, the integrals over the punctured space are determined by the Gromov--Witten theory of $H$.
-
-\subsubsection{Type $C^+$} Finally let $\Dcal \subseteq \VZ$ be a component of $\Dcal(k)$ with combinatorial type $\Delta$ of type $C^+$. The corresponding locus in $\Mcal$ can be written as:
-\begin{equation*} \Dcal_\Mcal = \Mpunct{1}{\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}{H}{d_0} \times_{H^r} \left( \prod_{i=1}^r \Mlog{0}{\alpha^{(i)}\cup(m_i)}{\PP^N|H}{d_i} \right). \end{equation*}
-Then the same argument as in Lemma \ref{type A radius lemma} shows that given any point in $\Dcal$ the interior of the radius can only contain components of $C_0$.
-Thus the alignment and factorisation condition apply exclusively to $C_0$, which shows that:
-\begin{equation*}\Dcal = \VZ^{\operatorname{punct}}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(H,d_0) \times_{H^r} \left( \prod_{i=1}^r \Mlog{0}{\alpha^{(i)}\cup(m_i)}{\PP^N|H}{d_i} \right).
+Now suppose $\Delta$ is of type $B$.
+Note that in this case, it is impossible for the circuit to be contracted.
+Hence $\Dcal^{\Kim}$ is disjoint from the blown-up locus, and the map $\Dcal \to \Dcal_\Mcal$ is an isomorphism.
+We thus obtain a finite map
+\begin{equation*} \Dcal = \ol\Mcal^{\Kim \leftrightarrow}_{0,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(P|H_0+H_\infty,d_0)\times_{H^r}\left(\ol\Mcal^{\Kim}_{0,\alpha^{(1)}\cup(m_1,m_2)}(\PP^N|H,d_1)\times\prod_{i=3}^r \ol\Mcal^{\Kim}_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i)\right).\end{equation*}
+The degree of $\rho$ and the vanishing order $\lambda_\Dcal$ are identical to the type $A$ case treated in \S \ref{subsubsection type A} above.
+
+\subsubsection{Type $C^+$} Finally suppose that $\Delta$ is of type $C^+$. As before we have a finite morphism:
+\begin{equation*} \Dcal^{\Kim} \to \ol\Mcal^{\Kim \leftrightarrow}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(P|H_0+H_\infty,d_0) \times_{H^r} \left( \prod_{i=1}^r \ol\Mcal^{\Kim}_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i) \right).
 \end{equation*}
-Here the first factor
-\begin{equation*}\VZ^{\operatorname{punct}}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(H,d_0) \end{equation*}
-is the logarithmic blow-up of the moduli space of punctured maps, obtained by imposing an alignment and factorisation condition.
-To be more precise: its elements consist of punctured maps to $H$ which are aligned in the sense of Definition \ref{}, and satisfy the (double) factorisation condition (simply replace $\PP^N$ by $H$ everywhere in that definition).
-As in \S \ref{}, this construction produces a closed substack of a logarithmic modification
-\begin{equation*} \VZ^{\operatorname{punct}}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(H,d_0)\subseteq \widetilde{\VZ}^{\operatorname{punct}}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(H,d_0) \xrightarrow{\psi} \Mpunct{1}{\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}{H}{d_0} \end{equation*}
+The same arguments as in \S \ref{subsubsection type A} apply to give a map
+\begin{equation*}\Dcal \to \VZ^{\leftrightarrow}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(P|H_0+H_\infty,d_0) \times_{H^r} \left( \prod_{i=1}^r \ol\Mcal^{\Kim}_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i) \right).
+\end{equation*}
+of degree given by \eqref{degree of gluing}, such that $\Dcal \to \Dcal^{\Kim}$ corresponds to the obvious map on fibre products.
+The vanishing order $\lambda_\Dcal$ is the same as in the previous two cases.
+Here the first factor in the fibre product is the logarithmic blow-up of the moduli space of rubber maps constructed in \S \ref{}.
+We will compute integrals over such spaces as part of the recursion (see \S \ref{section recursion algorithm}).\newpage
+
+\subsection{Recursive description of the divisors: type $C^0$} It remains to consider the components $\Dcal \subseteq \Dcal(k)$ contained in the exceptional locus of
+\begin{equation*} \VZ_{1,\alpha}(\PP^N|H,d) \to \ol\Mcal^{\Kim}_{1,\alpha}(\PP^N|H,d). \end{equation*}
+In this case the corresponding cone $\tau \in \Sigma_{1,\alpha}(\PP^N|H,d)$ is a ray in the subdivision of a larger-dimensional cone $\sigma \in \Sigma^{\Kim}$, corresponding to a combinatorial type $\Delta$ which assigns degree zero to the circuit.
+The associated stratum $\Dcal^{\Kim} \subseteq \ol\Mcal^{\Kim}_{1,\alpha}(\PP^N|H,d)$ has smaller dimension than $\Dcal$.
 
@@
 
-\section{Quantum Lefschetz algorithm}
+\section{Quantum Lefschetz algorithm}\label{section recursion algorithm}
 Consider a smooth pair $(X,Y)$ with $Y$ very ample, and let $P$ be the projective bundle $P=\PP_Y(\operatorname{N}_{Y|X} \oplus\OO_Y)$.

### 2019-03-12 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
minor changes

@@
 
-\part{The recursion formula and applications} \noindent In this part we derive topological recursion relations on the moduli space of reduced stable maps (Theorem \ref{theorem recursion}), inspired by the constructions of Vakil and Gathmann, but going beyond theirs in several key respects.
-We apply these to produce a quantum Lefschetz algorithm in genus one, which reconstructs the absolute theory of $Y$ and the relative theory of $(X,Y)$ from the absolute theory of $X$.
-Along the way we prove a splitting axiom for the reduced relative theory, in which involves non-trivial obstruction bundle terms make an appearance.
-
-The strategy is to first prove everything in the unobstructed case $(\PP^N,H)$; the general case follows by pullback along $i$ (see \S \ref{}).
+\part{The recursion formula and applications} \noindent In this part we derive recursion relations on the moduli space of reduced stable maps (Theorem \ref{theorem recursion}).
+These are inspired by the constructions of Vakil and Gathmann, but go beyond these in several key respects, one of which is a full treatment of descendant invariants.
+We apply the recursions to produce a quantum Lefschetz algorithm in genus one, reconstructing the absolute theory of $Y$ and the relative theory of $(X,Y)$ from the absolute theory of $X$.
+Along the way we prove a splitting axiom for the reduced relative theory,  whose statement is nontrivial insofar as it involves the introduction of additional tautological classes.
+
+[FINISH THIS]
 
@@
 This gives the construction of $(\Lcal_k,s_k)$ on $\MLog_{1,\alpha}(\PP^N|H,d)$; the construction on $\VZ_{1,\alpha}(\PP^N|H,d)$ is given by pull-back.
+The relevant piecewise-linear function is the composition:
+\begin{equation*} \Sigma_{1,\alpha}(\PP^N|H,d) \to \Sigma^{\log} \to \RR_{\geq 0}.\end{equation*}
 Notice in particular that $\psi_k$ should be interpreted as a \textbf{collapsed psi class} on $\VZ_{1,\alpha}(\PP^N|H,d)$, i.e.
 a psi class coming from the stabilised curve of the collapsed map.
-All of the psi classes we deal with will be collapsed psi classes.
+In this paper, all psi classes are collapsed unless stated otherwise.
 We immediately arrive at:

### 2019-03-13 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
additional tweaks to A,B,C+ section. Quite happy with it now

@@
 \newcommand{\Dcal}{\mathcal{D}}
+\newcommand{\Ecal}{\mathcal{E}}
 \newcommand{\Ncal}{\mathcal{N}}
+\newcommand{\Fcal}{\mathcal{F}}
 \newcommand{\Lcal}{\mathcal{L}}
@@
 After replacing the source $C$ by a destabilization, we have maps
-\[
-C\to \overline{C}_1\to\overline{C}_2\to \mathbb P^N[s]\to \mathbb P^N
-\]
+\bcd
+C \ar[r] & \overline{C}_1 \ar[r] \ar[d] & \overline{C}_2 \ar[d] \\
+& \mathbb P^N[s] \ar[r] & \mathbb P^N
+\ecd
 factorizing completely. Let $f_B$ and $f_T$ be the maps from $C$ to the base and total space respectively. Examining the morphism $\nu$, we see that there is a map
 \[
-\mathrm{Def}(C,f_B)\to \mathrm{Obs}(f_T) = H^1(\overline{C}_1,\mathcal O_{\overline{C}_1}),
+\mathrm{Def}(C,f_B)\to \mathrm{Obs}(f_T/(C,f_B)) = H^1(\overline{C}_1,\mathcal O_{\overline{C}_1}),
 \]
@@
 \mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)$, so its cone complex is a subcomplex of $\Sigma^{\mathrm{cen}}$.
-The fact that it must be contained in the subcomplex of well-spaced curves is immediate from Proposition~\ref{prop: well-spaced}.
+The fact that it must be contained in the subcomplex of well-spaced curves is immediate from Proposition~\ref{prop: well-spaced}.l
 \end{proof}
 
-\subsection{Indexing the strata} The dimension-$k$ cones in $\Sigma_{1,\alpha}(\PP^N|H,d)$ can be enumerated as follows.
+\subsection{Indexing the strata} \label{subsection indexing strata} The dimension-$k$ cones in $\Sigma_{1,\alpha}(\PP^N|H,d)$ can be enumerated as follows.
 First, the cones in $\Sigma^{\operatorname{log}}$ are indexed by \textbf{combinatorial types} of tropical maps to $\RR_{\geq 0}$.
@@
 
-\part{The recursion formula and applications} \noindent In this part we derive recursion relations on the moduli space of reduced stable maps (Theorem \ref{theorem recursion}).
-These are inspired by the constructions of Vakil and Gathmann, but go beyond these in several key respects, one of which is a full treatment of descendant invariants.
+\part{The recursion formula and applications}\footnote{(Navid) From here on, when I write a relative space without any decoration, I mean a Kim space.
+We should establish this convention from the start} \noindent In this part we prove recursion relations on the moduli space of reduced stable maps (Theorem \ref{theorem recursion}).
+These are inspired by the constructions of Vakil and Gathmann, but go beyond these in several key respects, giving a full treatment of descendant invariants for very ample pairs.
 We apply the recursions to produce a quantum Lefschetz algorithm in genus one, reconstructing the absolute theory of $Y$ and the relative theory of $(X,Y)$ from the absolute theory of $X$.
-Along the way we prove a splitting axiom for the reduced relative theory,  whose statement is nontrivial insofar as it involves the introduction of additional tautological classes.
-
-[FINISH THIS]
-
-\section{Gathmann's line bundle through tropical geometry}\label{Section Gathmann line bundle} Consider a reduced relative space $\VZ_{1,\alpha}(\PP^N|H,d)$.
-For each marking $x_k$ we consider the locus $\Dcal(k) \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$ where $x_k$ belongs to an internal component of the collapsed map.
-In this section, we use the log structure on $\VZ_{1,\alpha}(\PP^N|H,d)$ to construct a line bundle $\Lcal_k$ together with a section $s_k$ which vanishes precisely along $\Dcal(k)$.
-We use the correspondence with tropical geometry to identify $\cchern_1(\Lcal_k)$ in terms of tautological classes on $\VZ_{1,\alpha}(\PP^N|H,d)$, and to compute the vanishing order of $s_k$ along the components of $\Dcal(k)$.
+Along the way we prove a splitting axiom for the reduced relative theory; the form of this splitting axiom is nontrivial, insofar as it involves the introduction of additional tautological classes.
+
+In \S\S \ref{Section Gathmann line bundle}--\ref{section reduced splitting axiom} we prove the recursion formula for $(\PP^N,H)$.
+In \S \ref{section recursion for general pair} we indicate how to obtain from this the recursion formula for an arbitrary very ample pair $(X,Y)$.
+Finally in \S \ref{section recursion algorithm} we describe the quantum Lefschetz algorithm.
+
+\section{Gathmann's line bundle via tropical geometry}\label{Section Gathmann line bundle} Consider a reduced relative space $\VZ_{1,\alpha}(\PP^N|H,d)$.
+For each marking $x_k$ we consider the locus $\Dcal_{1,\alpha,k}(\PP^N|H,d) \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$ where $x_k$ belongs to an internal component of the collapsed map.
+In this section, we use the log structure on $\VZ_{1,\alpha}(\PP^N|H,d)$ to construct a line bundle $\Lcal_k$ together with a section $s_k$ which vanishes precisely along $\Dcal_{1,\alpha,k}(\PP^N|H,d)$.
+We use the correspondence with tropical geometry to identify $\cchern_1(\Lcal_k)$ in terms of tautological classes on $\VZ_{1,\alpha}(\PP^N|H,d)$, and to compute the vanishing order of $s_k$ along the components of $\Dcal_{1,\alpha,k}(\PP^N|H,d)$.
 Combined with the splitting axioms established in the next section, we obtain a recursion relation inside $\VZ_{1,\alpha}(\PP^N|H,d)$
@@
 \begin{equation}\label{equation recursion} (\alpha_k \psi_k + \ev_k^\st H) \cap [\VZ_{1,\alpha}(\PP^N|H,d)] = \sum_{\Dcal} \lambda_\Dcal [ \Dcal ].\end{equation}
-The sum is over irreducible components $\Dcal$ of the divisor $\Dcal(k) \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$, and $\lambda_\Dcal$ is the vanishing order of $s_k$ along this component. \end{thm}
+The sum is over irreducible components $\Dcal$ of the divisor $\Dcal_{1,\alpha,k}(\PP^N|H,d) \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$, and $\lambda_\Dcal$ is the vanishing order of $s_k$ along this component.
+\end{thm}
 
@@
 
-\section{Recursive description of boundary strata: the reduced splitting axiom}
+\section{Recursive description of boundary strata: the reduced splitting axiom}\label{section reduced splitting axiom}
 In this section we provide an explicit description of the terms appearing on the right-hand side of \eqref{equation recursion} above.
@@
 
-\subsection{Identifying the irreducible components of $\Dcal(k)$} Here we explain the strategy for identifying the irreducible components of $\Dcal(k)$ via tropical geometry.
-
-\begin{lemma} \label{Lemma components are log divisors} Every irreducible component of $\Dcal(k)$ is a codimension $1$ log stratum.\end{lemma}
+\subsection{Identifying the irreducible components of $\Dcal_{1,\alpha,k}(\PP^N|H,d)$} Here we explain the strategy for identifying the irreducible components of $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ via tropical geometry.
+
+\begin{lemma} \label{Lemma components are log divisors} Every irreducible component of $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ is a codimension $1$ log stratum.\end{lemma}
 \begin{proof} This is not hard to see: the locus where the log structure is trivial coincides precisely with the  locus where the source curve is smooth and not mapped inside $H$, and since $\VZ_{1,\alpha}(\PP^N|H,d)$ is log smooth this locus is open and dense \cite{Niziol}.
-By definition $\Dcal(k)$ is contained in the  complement of this locus, which (by the very definition of logarithmic strata) can be written as a union of log strata of positive codimension.
-Since $\Dcal(k)$ has codmension $1$, it must therefore be equal to a union of log divisors.\end{proof}
-In \S \ref{} we discussed a procedure for enumerating the log strata of $\VZ_{1,\alpha}(\PP^N|H,d)$, using the cones of the tropicalisation $\Sigma_{1,\alpha}(\PP^N|H,d)$.
+By definition $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ is contained in the  complement of this locus, which (by the very definition of logarithmic strata) can be written as a union of log strata of positive codimension.
+Since $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ has codmension $1$, it must therefore be equal to a union of log divisors.\end{proof}
+In \S \ref{subsection indexing strata} we discussed a procedure for enumerating the log strata of $\VZ_{1,\alpha}(\PP^N|H,d)$, using the cones of the tropicalisation $\Sigma_{1,\alpha}(\PP^N|H,d)$.
 To recap: every divisorial logarithmic stratum is obtained via a three-step process:
@@
 
-The log divisors contained in $\Dcal(k)$ are precisely those whose  combinatorial types map the vertex of the dual graph containing $x_k$  into the interior $\RR_{>0} \subseteq \RR_{\geq 0}$.
-Thus via the above procedure, we are able to enumerate the irreducible components of $\Dcal(k)$ in a combinatorial manner, and the combinatorial type $\Delta$ allows us to describe the general element of such a component.
+The log divisors contained in $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ are precisely those whose  combinatorial types map the vertex of the dual graph containing $x_k$  into the interior $\RR_{>0} \subseteq \RR_{\geq 0}$.
+Thus via the above procedure, we are able to enumerate the irreducible components of $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ in a combinatorial manner, and the combinatorial type $\Delta$ allows us to describe the general element of such a component.
 What we are still lacking is a recursive description of the components, which we need in order to compute integrals over them.
@@
 
-\subsection{Recursive description of the divisors: types $A,B$ and $C^+$} Choose an irreducible component $\Dcal \subseteq \Dcal(k)$.
+\subsection{Recursive description of the divisors: types $A,B$ and $C^+$} Choose an irreducible component $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$.
 By Lemma \ref{Lemma components are log divisors} this is a log divisor, and hence may be written as:
@@
 for a unique log stratum $\widetilde\Dcal \subseteq \widetilde{\VZ}_{1,\alpha}(\PP^N|H,d)$. Since
-\begin{equation*}\widetilde{\VZ}_{1,\alpha}(\PP^N|H,d) \to \ol\Mcal^{\Kim}_{1,\alpha}(\PP^N|H,d)\end{equation*}
+\begin{equation*}\widetilde{\VZ}_{1,\alpha}(\PP^N|H,d) \to \ol\Mcal_{1,\alpha}(\PP^N|H,d)\end{equation*}
 is a log modification, $\widetilde{\Dcal}$ is either exceptional or the proper transform of a log divisor.
@@
 To begin with we will focus on the latter case.
-Suppose therefore that $\widetilde{\Dcal}$ is the proper transform of a divisor:
-\begin{equation*} \Dcal^{\Kim} \subseteq \ol\Mcal^{\Kim}_{1,\alpha}(\PP^N|H,d). \end{equation*}
-The birational map $\widetilde{\Dcal} \to \Dcal^{\Kim}$ induces a morphism $\rho \colon \Dcal \to \Dcal^{\Kim}$.
-The remainder of this subsection will be devoted to showing how $\rho$ may be interpreted as a ``desingularisation of the main component''.
-Since $\Dcal^{\Kim}$ admits a recursive description (in terms of relative and rubber moduli spaces), this will allow us to compute integrals over $\Dcal$.
-
-\begin{lemma} Let $\Dcal \subseteq \Dcal(k)$ be an irreducible component which contributes nontrivially to the recursion, and let $\Delta$ be the corresponding combinatorial type.
+Suppose therefore that $\widetilde{\Dcal}$ is the proper transform of a log divisor:
+\begin{equation*} \Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d). \end{equation*}
+The birational map $\widetilde{\Dcal} \to \Ecal$ induces a morphism $\Dcal \to \Ecal$.
+In the remainder of this subsection, we will show how to interpret this morphism as a ``desingularisation of the main component''.
+Since $\Ecal$ admits a recursive description in terms of relative and rubber moduli spaces, this will allow us to compute integrals over $\Dcal$.
+
+\begin{lemma} Let $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ be an irreducible component which contributes nontrivially to the recursion, and let $\Delta$ be the corresponding combinatorial type.
 Suppose that $\Delta$ assigns positive degree to the circuit.
@@
 
-\noindent The terminology is due to Vakil, and the picture in this case is very similar to \cite{Vre} (as we will see later, when the circuit is contracted the picture becomes \emph{very} different).
+\noindent The terminology is due to Vakil, and the pictures in this case are very similar to \cite{Vre} (we will see later that when the circuit is assigned zero degree the picture becomes \emph{very} different).
 Note that in these pictures we have deliberately omitted the marked points (except for $x_k$), the degree of each vertex, and the expansion factors of the edges.
@@
 
-\begin{proof} Let $\sigma \in \Sigma^{\Kim}$ be the cone corresponding to the stratum $\Dcal^{\Kim} \subseteq \ol\Mcal^{\Kim}_{1,\alpha}(\PP^N|H,d)$.
+\begin{proof} Let $\sigma \in \Sigma$ be the cone corresponding to the stratum $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$.
 By the discussion above $\Dcal$ corresponds to a ray in the subdivision of $\sigma$ given by imposing the central alignment condition.
@@
 We conclude that $\sigma=\RR_{\geq 0}$ (recall we are assuming that the initial and generised combinatorial types coincide).
-Since there must be at least one vertex mapped to higher level, we conclude that the tropical target $\tilde\RR_{\geq 0}$ is obtained from $\RR_{\geq 0}$ by subdividing at a single point $\diamond \in \RR_{> 0}$.
+Since there must be at least one vertex mapped to higher level, we conclude that the tropical target $\widetilde\RR_{\geq 0}$ is obtained from $\RR_{\geq 0}$ by subdividing at a single point $\diamond \in \RR_{> 0}$.
 
@@
 To see this, we consider the stratum
-\begin{equation*} \Dcal^{\ACGS} \subseteq \ol\Mcal^{\log}_{1,\alpha}(\PP^N|H,d) \end{equation*}
-to which $\Dcal^{\Kim}$ maps under the collapsing morphism.
-The codimension of $\Dcal^{\ACGS}$ is given by the dimension of the associated cone in the tropicalisation $\Sigma^{\log}$; if there is more than one vertex mapped to higher level then this is strictly greater than $1$, in contrast to the cone in $\Sigma^{\Kim}$.
-Therefore the map $\Dcal^{\Kim} \to \Dcal^{\ACGS}$ has positive-dimensional fibres, and since all insertions are pulled back from the latter space the contribution vanishes by the projection formula.\end{proof}
-
-\begin{remark} The difference in dimensions between $\Dcal^{\Kim}$ and $\Dcal^{\ACGS}$ may be interpreted as the difference in dimensions between moduli spaces of \emph{disonnected} rubber and their images under the collapsing map (see \ref{} below).
+\begin{equation*} \Ecal^{\text{\tiny{log}}} \subseteq \ol\Mcal^{\text{\tiny{log}}}_{1,\alpha}(\PP^N|H,d) \end{equation*}
+to which $\Ecal$ maps under the collapsing morphism, and examine the composition $\Dcal \to \Ecal \to \Ecal^{\text{\tiny{log}}}$.
+If we let $\Fcal^{\text{\tiny{log}}}$ denote the intersection of $\Ecal^{\text{\tiny{log}}}$ with the main component of the moduli space, then we obtain a factorisation $\Dcal \to \Fcal^{\text{\tiny{log}}} \hookrightarrow \Ecal^{\text{\tiny{log}}}$.
+Since the moduli space is generically unobstructed along $\Fcal^{\text{\tiny{log}}}$, the codimension of $\Fcal^{\text{\tiny{log}}}$ is given by the dimension of the associated cone in the tropicalisation $\Sigma^{\text{\tiny{log}}}$.
+If there is more than one vertex mapped to higher level, then this cone has dimension $\geq 2$.
+Therefore the map $\Dcal \to \Fcal^{\text{\tiny{log}}}$ has positive-dimensional fibres, and since all insertions are pulled back from the latter space the contribution vanishes by the projection formula.\end{proof}
+
+\begin{remark} The difference in dimensions between $\Dcal$ and $\Fcal^{\text{\tiny{log}}}$ (or equivalently, the difference in virtual dimensions between $\Ecal$ and $\Ecal^{\text{\tiny{log}}}$) may be interpreted as the difference in dimensions between moduli spaces of \emph{disconnected} rubber and their images under the collapsing morphisms (see \ref{} below).
 \end{remark}
 
-We now now investigate the three types $A,B,C^+$ separately, giving a recursive description of the boundary divisor in each case.
-For the remainder of this subsection, therefore, we fix a one-dimensional cone $\tau \in \Sigma_{1,\alpha}(\PP^N|H,d)$, let $\Dcal \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$ be the associated log divisor, and assume that $\Dcal \subseteq \Dcal(k)$ and is of type $A,B$ or $C^+$.
-We let $\Dcal^{\Kim} \subseteq \ol\Mcal_{1,\alpha}^{\Kim}(\PP^N|H,d)$ be the log stratum into which $\Dcal$ is mapped.
-Note that (since we are restricting to the type $A,B,C^+$ cases), $\Dcal^{\Kim}$ is also a log divisor, indexed by a cone $\epsilon \in \Sigma^{\Kim}$ which corresponds to a combinatorial type $\Delta$.
-Moreover, $\Dcal$ is the proper transform of $\Dcal^{\Kim}$ under the blow-up map.
-
-\subsubsection{Type $A$}\label{subsubsection type A} Suppose $\Delta$ is of type $A$. Then \cite[\S 7]{ChenDegeneration} $\Dcal^{\Kim}$ admits a finite splitting morphism onto the fibre product
-\begin{equation*} \Dcal^{\Kim} \xrightarrow{\rho^{\Kim}} \ol\Mcal^{\Kim \leftrightarrow}_{0,\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}(P|H_0+H_\infty,d_0)\times_{H^r}\left( \ol\Mcal^{\Kim}_{1,\alpha^{(1)}\cup(m_1)}(\PP^N|H,d_1) \times \prod_{i=2}^r \ol\Mcal^{\Kim}_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i) \right) \end{equation*}
-where the degree of $\rho^{\Kim}$ is given by:
-\begin{equation} \label{degree of gluing} \dfrac{\prod_{i=1}^r m_i}{\lcm(m_1,\ldots,m_r)}. \end{equation}
-This is calculated in the usual way, by examining the base order of the corresponding family of targets.
-
-\begin{lemma} \label{Lemma type A gluing} $\Dcal$ admits a natural morphism
-\begin{equation*}\Dcal \xrightarrow{\rho} \ol\Mcal^{\Kim \leftrightarrow}_{0,\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}(P|H_0+H_\infty,d_0)\times_{H^r}\left(\VZ_{1,\alpha^{(1)}\cup(m_1)}(\PP^N|H,d_1)\times\prod_{i=2}^r \ol\Mcal^{\Kim}_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i)\right) \end{equation*}
-of degree given by the same formula \eqref{degree of gluing}, such that the map $\Dcal \to \Dcal^{\Kim}$ covers the map on fibre products obtained by desingularising the main component of the factor corresponding to $\sqC_1$.\end{lemma}
+We now investigate the three types $A,B,C^+$ separately, giving a recursive description of the boundary divisor in each case.
+For the remainder of this subsection, therefore, we fix a one-dimensional cone $\tau \in \Sigma_{1,\alpha}(\PP^N|H,d)$, let $\Dcal \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$ be the associated log divisor, and assume that $\Dcal$ is contained in $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ and is of type $A,B$ or $C^+$.
+We let $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$ be the log stratum into which $\Dcal$ is mapped; this is indexed by a cone $\epsilon \in \Sigma$ corresponding to a combinatorial type $\Delta$, and $\epsilon$ is one-dimensional since we are restricting to the type $A,B,C^+$ cases.
+
+\subsubsection{Type $A$}\label{subsubsection type A} Suppose $\Delta$ is of type $A$. Then $\Ecal$ admits a finite splitting morphism onto the fibre product:
+\begin{equation*} \Ecal \to \ol\Mcal_{0,\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}(P|H_0+H_\infty,d_0)\times_{H^r}\left( \ol\Mcal_{1,\alpha^{(1)}\cup(m_1)}(\PP^N|H,d_1) \times \prod_{i=2}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i) \right).
+\end{equation*}
+
+\begin{lemma} \label{Lemma type A gluing} $\Dcal$ admits a natural splitting morphism
+\begin{equation*}\Dcal \xrightarrow{\rho} \ol\Mcal^{\leftrightarrow}_{0,\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}(P|H_0+H_\infty,d_0)\times_{H^r}\left(\VZ_{1,\alpha^{(1)}\cup(m_1)}(\PP^N|H,d_1)\times\prod_{i=2}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i)\right) \end{equation*}
+such that the map $\Dcal \to \Ecal$ covers the map on fibre products obtained by desingularising the main component of the factor corresponding to $\sqC_1$.\end{lemma}
 
 \begin{proof}
-The choices involved in gluing log maps to expansions (which accounts for the degrees of the splitting morphisms above) is not affected by the introduction of alignments, so for the purposes of this proof we may act as if $\rho$ and $\rho^{\Kim}$ are the identity maps.
-
-Note that the map $\Dcal\to\Dcal^{\Kim}$ is an isomorphism away from the blown-up locus, which is contained inside the locus where the circuit is contracted.
+The choices involved in gluing log maps to expansions (which accounts for the degrees of the splitting morphisms above) is not affected by the introduction of alignments, so for the purposes of this proof we may pretend as if these splitting morphisms are the identity maps.
+
+Note that the map $\Dcal\to\Ecal$ is an isomorphism away from the blown-up locus, which is contained inside the locus where the circuit is contracted.
 Given an element of $\Dcal$ we can split it along the nodes $q_1,\ldots,q_r$ as in \cite{}.
@@
 
-Lemma \ref{Lemma type A gluing} provides a means to calculate integrals over $\Dcal$ in terms of integrals over the factors in the fibre product.
-The missing piece is the vanishing order $\lambda_\Dcal$ of the section $s_k$ (constructed in \S \ref{Section Gathmann line bundle} above) along $\Dcal$.
-
-\begin{lemma} \label{lemma vanishing order type A} $\lambda_\Dcal = \lcm(m_1,\ldots,m_r).$ \end{lemma}
+Lemma \ref{Lemma type A gluing} provides a means to calculate integrals over the class $\lambda_\Dcal[\Dcal]$ appearing on the right-hand side of Theorem \ref{theorem recursion}, provided that we can calculate $\lambda_\Dcal$ and the degree of the splitting morphism.
+Simple closed formulae for these are given in \S \ref{subsubsection splitting degree} below.
+
+\subsubsection{Type $B$}
+Now suppose $\Delta$ is of type $B$.
+Note that in this case, it is impossible for the circuit to be contracted.
+Hence $\Ecal$ is disjoint from the blown-up locus, and the map $\Dcal \to \Ecal$ is an isomorphism.
+We thus obtain a finite splitting morphism:
+\begin{equation*} \Dcal \xrightarrow{\rho} \ol\Mcal^{\leftrightarrow}_{0,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(P|H_0+H_\infty,d_0)\times_{H^r}\left(\ol\Mcal_{0,\alpha^{(1)}\cup(m_1,m_2)}(\PP^N|H,d_1)\times\prod_{i=3}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i)\right).\end{equation*}
+
+\subsubsection{Type $C^+$} \label{subsubsection type C+} Finally suppose that $\Delta$ is of type $C^+$. As before we have a finite morphism:
+\begin{equation*} \Ecal \to \ol\Mcal^{\leftrightarrow}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(P|H_0+H_\infty,d_0) \times_{H^r} \left( \prod_{i=1}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i) \right).
+\end{equation*}
+The same arguments as in \S \ref{subsubsection type A} then apply to give a finite morphism map
+\begin{equation*}\Dcal \xrightarrow{\rho} \VZ^{\leftrightarrow}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(P|H_0+H_\infty,d_0) \times_{H^r} \left( \prod_{i=1}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i) \right).
+\end{equation*}
+ such that $\Dcal \to \Ecal$ corresponds to the obvious map on fibre products.
+Here the first factor in the fibre product is the logarithmic blow-up of the moduli space of rubber maps constructed in \S \ref{}.
+We will compute integrals over such spaces as part of the recursion (see \S \ref{section recursion algorithm}).
+
+\subsubsection{Splitting degree and vanishing order} \label{subsubsection splitting degree} In each of the subsections \ref{subsubsection type A}--\ref{subsubsection type C+} above, we obtained a finite splitting morphism $\rho$ from $\Dcal$ to a fibre product of moduli spaces with smaller numerical data.
+Here we explain the degree of $\rho$ and calculate the vanishing order $\lambda_\Dcal$ of the section $s_k$ constructed in \S \ref{Section Gathmann line bundle}.
+This gives a complete recursive description of the terms appearing on the right-hand side of Theorem \ref{theorem recursion} which are of type $A,B$ or $C^+$.
+
+\begin{lemma} The degree of $\rho$ is given by:
+\begin{equation*} \label{degree of gluing} \dfrac{\prod_{i=1}^r m_i}{\lcm(m_1,\ldots,m_r)}. \end{equation*}\end{lemma}
+\begin{proof} This is calculated in the usual way, by examining the base order of the corresponding family of targets. See, for instance \cite{ChenDegeneration}, \cite{ACGSDecomposition}.
+\end{proof}
+
+\begin{lemma} \label{lemma vanishing order} $\lambda_\Dcal = \lcm(m_1,\ldots,m_r).$ \end{lemma}
 \begin{proof} Let $\tau \in \Sigma_{1,\alpha}(\PP^N|H,d)$ be the cone corresponding to $\Dcal$ and let
@@
 Thus we conclude that the index is equal to $\lcm(m_1,\ldots,m_r)$ as claimed.\end{proof}
-
-\noindent This lemma, together with the degree calculation \eqref{degree of gluing}, determines the numerics of integrals over $\lambda_\Dcal [\Dcal]$.
-
-\subsubsection{Type $B$}
-Now suppose $\Delta$ is of type $B$.
-Note that in this case, it is impossible for the circuit to be contracted.
-Hence $\Dcal^{\Kim}$ is disjoint from the blown-up locus, and the map $\Dcal \to \Dcal_\Mcal$ is an isomorphism.
-We thus obtain a finite map
-\begin{equation*} \Dcal = \ol\Mcal^{\Kim \leftrightarrow}_{0,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(P|H_0+H_\infty,d_0)\times_{H^r}\left(\ol\Mcal^{\Kim}_{0,\alpha^{(1)}\cup(m_1,m_2)}(\PP^N|H,d_1)\times\prod_{i=3}^r \ol\Mcal^{\Kim}_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i)\right).\end{equation*}
-The degree of $\rho$ and the vanishing order $\lambda_\Dcal$ are identical to the type $A$ case treated in \S \ref{subsubsection type A} above.
-
-\subsubsection{Type $C^+$} Finally suppose that $\Delta$ is of type $C^+$. As before we have a finite morphism:
-\begin{equation*} \Dcal^{\Kim} \to \ol\Mcal^{\Kim \leftrightarrow}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(P|H_0+H_\infty,d_0) \times_{H^r} \left( \prod_{i=1}^r \ol\Mcal^{\Kim}_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i) \right).
-\end{equation*}
-The same arguments as in \S \ref{subsubsection type A} apply to give a map
-\begin{equation*}\Dcal \to \VZ^{\leftrightarrow}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(P|H_0+H_\infty,d_0) \times_{H^r} \left( \prod_{i=1}^r \ol\Mcal^{\Kim}_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i) \right).
-\end{equation*}
-of degree given by \eqref{degree of gluing}, such that $\Dcal \to \Dcal^{\Kim}$ corresponds to the obvious map on fibre products.
-The vanishing order $\lambda_\Dcal$ is the same as in the previous two cases.
-Here the first factor in the fibre product is the logarithmic blow-up of the moduli space of rubber maps constructed in \S \ref{}.
-We will compute integrals over such spaces as part of the recursion (see \S \ref{section recursion algorithm}).\newpage
-
-\subsection{Recursive description of the divisors: type $C^0$} It remains to consider the components $\Dcal \subseteq \Dcal(k)$ contained in the exceptional locus of
-\begin{equation*} \VZ_{1,\alpha}(\PP^N|H,d) \to \ol\Mcal^{\Kim}_{1,\alpha}(\PP^N|H,d). \end{equation*}
-In this case the corresponding cone $\tau \in \Sigma_{1,\alpha}(\PP^N|H,d)$ is a ray in the subdivision of a larger-dimensional cone $\sigma \in \Sigma^{\Kim}$, corresponding to a combinatorial type $\Delta$ which assigns degree zero to the circuit.
-The associated stratum $\Dcal^{\Kim} \subseteq \ol\Mcal^{\Kim}_{1,\alpha}(\PP^N|H,d)$ has smaller dimension than $\Dcal$.
+Thus, the contribution of each term $\lambda_\Dcal [\Dcal]$ is given by integrating over the appropriate fibre product and then multiplying the result by $\lambda_\Dcal \cdot \deg\rho = \prod_{i=1}^r m_i$.
+
+\newpage
+
+\subsection{Recursive description of the divisors: type $C^0$} It remains to consider the components $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ contained in the exceptional locus of
+\begin{equation*} \VZ_{1,\alpha}(\PP^N|H,d) \to \ol\Mcal_{1,\alpha}(\PP^N|H,d). \end{equation*}
+In this case the corresponding cone $\tau \in \Sigma_{1,\alpha}(\PP^N|H,d)$ is a ray in the subdivision of a larger-dimensional cone $\sigma \in \Sigma$, corresponding to a combinatorial type $\Delta$ which assigns degree zero to the circuit.
+The associated stratum $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$ has smaller dimension than $\Dcal$.
 
@@
 
-\section{Recursion for general $(X,Y)$}
+\section{Recursion for general $(X,Y)$}\label{section recursion for general pair}
 

### 2019-03-13 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
minor changes

@@
 Hence $\Ecal$ is disjoint from the blown-up locus, and the map $\Dcal \to \Ecal$ is an isomorphism.
-We thus obtain a finite splitting morphism:
-\begin{equation*} \Dcal \xrightarrow{\rho} \ol\Mcal^{\leftrightarrow}_{0,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(P|H_0+H_\infty,d_0)\times_{H^r}\left(\ol\Mcal_{0,\alpha^{(1)}\cup(m_1,m_2)}(\PP^N|H,d_1)\times\prod_{i=3}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i)\right).\end{equation*}
+We thus obtain:
+\begin{lemma} $\Dcal$ admits a finite splitting morphism:
+\begin{equation*} \Dcal \xrightarrow{\rho} \ol\Mcal^{\leftrightarrow}_{0,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(P|H_0+H_\infty,d_0)\times_{H^r}\left(\ol\Mcal_{0,\alpha^{(1)}\cup(m_1,m_2)}(\PP^N|H,d_1)\times\prod_{i=3}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i)\right).\end{equation*}\end{lemma}
 
@@
 \end{equation*}
-The same arguments as in \S \ref{subsubsection type A} then apply to give a finite morphism map
-\begin{equation*}\Dcal \xrightarrow{\rho} \VZ^{\leftrightarrow}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(P|H_0+H_\infty,d_0) \times_{H^r} \left( \prod_{i=1}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i) \right).
-\end{equation*}
- such that $\Dcal \to \Ecal$ corresponds to the obvious map on fibre products.
+The same arguments as in \S \ref{subsubsection type A} then apply to give:
+\begin{lemma} $\Dcal$ admits a finite splitting morphism
+\begin{equation*}\Dcal \xrightarrow{\rho} \VZ^{\leftrightarrow}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(P|H_0+H_\infty,d_0) \times_{H^r} \left( \prod_{i=1}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i) \right)\end{equation*}
+such that $\Dcal \to \Ecal$ corresponds to the obvious map on fibre products.\end{lemma}
 Here the first factor in the fibre product is the logarithmic blow-up of the moduli space of rubber maps constructed in \S \ref{}.

### 2019-03-13 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
minor changes

@@
 
+\subsection{Recursive description of the divisors: type $C^0$}
+
 \newpage
-
-\subsection{Recursive description of the divisors: type $C^0$} It remains to consider the components $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ contained in the exceptional locus of
-\begin{equation*} \VZ_{1,\alpha}(\PP^N|H,d) \to \ol\Mcal_{1,\alpha}(\PP^N|H,d). \end{equation*}
-In this case the corresponding cone $\tau \in \Sigma_{1,\alpha}(\PP^N|H,d)$ is a ray in the subdivision of a larger-dimensional cone $\sigma \in \Sigma$, corresponding to a combinatorial type $\Delta$ which assigns degree zero to the circuit.
-The associated stratum $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$ has smaller dimension than $\Dcal$.
 

### 2019-03-17 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
minor changes

@@
 \subsubsection{Type $A$}\label{subsubsection type A} Suppose $\Delta$ is of type $A$. Then $\Ecal$ admits a finite splitting morphism onto the fibre product:
-\begin{equation*} \Ecal \to \ol\Mcal_{0,\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}(P|H_0+H_\infty,d_0)\times_{H^r}\left( \ol\Mcal_{1,\alpha^{(1)}\cup(m_1)}(\PP^N|H,d_1) \times \prod_{i=2}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i) \right).
-\end{equation*}
+\begin{equation*} \Ecal \to \left( \ol\Mcal_{1,\alpha^{(1)}\cup(m_1)}(\PP^N|H,d_1) \times \prod_{i=2}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i) \right) \times_{H^r} \ol\Mcal^{\leftrightarrow}_{0,\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}(P|H_0+H_\infty,d_0).\end{equation*}
 
 \begin{lemma} \label{Lemma type A gluing} $\Dcal$ admits a natural splitting morphism
-\begin{equation*}\Dcal \xrightarrow{\rho} \ol\Mcal^{\leftrightarrow}_{0,\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}(P|H_0+H_\infty,d_0)\times_{H^r}\left(\VZ_{1,\alpha^{(1)}\cup(m_1)}(\PP^N|H,d_1)\times\prod_{i=2}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i)\right) \end{equation*}
+\begin{equation*}\Dcal \xrightarrow{\rho} \left(\VZ_{1,\alpha^{(1)}\cup(m_1)}(\PP^N|H,d_1)\times\prod_{i=2}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i)\right) \times_{H^r} \ol\Mcal^{\leftrightarrow}_{0,\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}(P|H_0+H_\infty,d_0)\end{equation*}
 such that the map $\Dcal \to \Ecal$ covers the map on fibre products obtained by desingularising the main component of the factor corresponding to $\sqC_1$.\end{lemma}
@@
 \begin{lemma} $\Dcal$ admits a finite splitting morphism:
-\begin{equation*} \Dcal \xrightarrow{\rho} \ol\Mcal^{\leftrightarrow}_{0,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(P|H_0+H_\infty,d_0)\times_{H^r}\left(\ol\Mcal_{0,\alpha^{(1)}\cup(m_1,m_2)}(\PP^N|H,d_1)\times\prod_{i=3}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i)\right).\end{equation*}\end{lemma}
+\begin{equation*} \Dcal \xrightarrow{\rho} \left(\ol\Mcal_{0,\alpha^{(1)}\cup(m_1,m_2)}(\PP^N|H,d_1)\times\prod_{i=3}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i)\right) \times_{H^r} \ol\Mcal^{\leftrightarrow}_{0,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(P|H_0+H_\infty,d_0).\end{equation*}\end{lemma}
 
 \subsubsection{Type $C^+$} \label{subsubsection type C+} Finally suppose that $\Delta$ is of type $C^+$. As before we have a finite morphism:
-\begin{equation*} \Ecal \to \ol\Mcal^{\leftrightarrow}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(P|H_0+H_\infty,d_0) \times_{H^r} \left( \prod_{i=1}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i) \right).
+\begin{equation*} \Ecal \to  \left( \prod_{i=1}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i) \right) \times_{H^r} \ol\Mcal^{\leftrightarrow}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(P|H_0+H_\infty,d_0).
 \end{equation*}
@@
 \begin{lemma} $\Dcal$ admits a finite splitting morphism
-\begin{equation*}\Dcal \xrightarrow{\rho} \VZ^{\leftrightarrow}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(P|H_0+H_\infty,d_0) \times_{H^r} \left( \prod_{i=1}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i) \right)\end{equation*}
+\begin{equation*}\Dcal \xrightarrow{\rho} \left( \prod_{i=1}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i) \right) \times_{H^r} \VZ^{\leftrightarrow}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(P|H_0+H_\infty,d_0)\end{equation*}
 such that $\Dcal \to \Ecal$ corresponds to the obvious map on fibre products.\end{lemma}

### 2019-03-19 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
minor changes

@@
 
-\title{Reduced Gromov--Witten theory of hypersurfaces in genus one}
+\title{Absolute, relative and rubber Gromov--Witten theory of hypersurfaces in genus one}
 \author{Luca Battistella, Navid Nabijou and Dhruv Ranganathan}
@@
 We use the correspondence with tropical geometry to identify $\cchern_1(\Lcal_k)$ in terms of tautological classes on $\VZ_{1,\alpha}(\PP^N|H,d)$, and to compute the vanishing order of $s_k$ along the components of $\Dcal_{1,\alpha,k}(\PP^N|H,d)$.
-Combined with the splitting axioms established in the next section, we obtain a recursion relation inside $\VZ_{1,\alpha}(\PP^N|H,d)$
+Combined with the relative splitting axioms established in the next section, we obtain a recursion relation inside $\VZ_{1,\alpha}(\PP^N|H,d)$
 
@@
 
-\section{Recursive description of boundary strata: the reduced splitting axiom}\label{section reduced splitting axiom}
+\section{Recursive description of boundary strata: the relative splitting axiom}\label{section reduced splitting axiom}
 In this section we provide an explicit description of the terms appearing on the right-hand side of \eqref{equation recursion} above.

### 2019-03-20 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
minor changes (again)

@@
 Hence $\Ecal$ is disjoint from the blown-up locus, and the map $\Dcal \to \Ecal$ is an isomorphism.
-We thus obtain:
+We thus obtain the following description, entirely in terms of genus zero data:
 \begin{lemma} $\Dcal$ admits a finite splitting morphism:
@@
 \subsubsection{Splitting degree and vanishing order} \label{subsubsection splitting degree} In each of the subsections \ref{subsubsection type A}--\ref{subsubsection type C+} above, we obtained a finite splitting morphism $\rho$ from $\Dcal$ to a fibre product of moduli spaces with smaller numerical data.
-Here we explain the degree of $\rho$ and calculate the vanishing order $\lambda_\Dcal$ of the section $s_k$ constructed in \S \ref{Section Gathmann line bundle}.
+Here we describe the degree of $\rho$ and calculate the vanishing order $\lambda_\Dcal$ of the section $s_k$ constructed in \S \ref{Section Gathmann line bundle}.
 This gives a complete recursive description of the terms appearing on the right-hand side of Theorem \ref{theorem recursion} which are of type $A,B$ or $C^+$.
@@
 \begin{equation*} \label{degree of gluing} \dfrac{\prod_{i=1}^r m_i}{\lcm(m_1,\ldots,m_r)}. \end{equation*}\end{lemma}
-\begin{proof} This is calculated in the usual way, by examining the base order of the corresponding family of targets. See, for instance \cite{ChenDegeneration}, \cite{ACGSDecomposition}.
+\begin{proof} This calculation is by now standard, and is given by examining the base order of the corresponding family of targets. See, for instance \cite{ChenDegeneration}, \cite{ACGSDecomposition}.
 \end{proof}
@@
 \begin{equation*} w = \left( \dfrac{\lcm(m_1,\ldots,m_r)}{m_1},\ldots,\dfrac{\lcm(m_1,\ldots,m_r)}{m_r} \right).\end{equation*}
-The map $\tau \to \RR_{\geq 0}$ is given by projecting onto the $i$th factor and then multiplying by $m_i$ (this is independent of $i$).
+The map $\tau \to \RR_{\geq 0}$ is given by projecting onto the $i$th factor and then multiplying by $m_i$ (this is independent of $i$ by continuity of the tropical map).
 Thus we conclude that the index is equal to $\lcm(m_1,\ldots,m_r)$ as claimed.\end{proof}
-Thus, the contribution of each term $\lambda_\Dcal [\Dcal]$ is given by integrating over the appropriate fibre product and then multiplying the result by $\lambda_\Dcal \cdot \deg\rho = \prod_{i=1}^r m_i$.
+In summary, then: the contribution of each term $\lambda_\Dcal [\Dcal]$ is given by integrating over the appropriate fibre product and then multiplying the result by $\lambda_\Dcal \cdot \deg\rho = \prod_{i=1}^r m_i$.
 

### 2019-04-16 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
imported Dhruv changes to introduction and rubber

@@
 \begin{customthm}{A}
-There exists a log smooth and proper Deligne—Mumford stack giving a modular compactification for the space of genus $1$ maps to projective space with fixed contact order with a hyperplane. 
+There exists a logarithmically smooth and proper Deligne--Mumford stack giving a modular compactification for the space of genus one maps to projective space with fixed contact order with a hyperplane.
 \end{customthm}
@@
 This interaction of the degeneration formula with the geometry of curve singularities is a new phenomenon.
-The results of~\cite{RSPW} suggest the existence of a reduced higher genus Gromov--Witten theory formed by replacing contracted elliptic components with singularities.
+The results of~\cite{RSPW} suggest the existence of a reduced higher genus Gromov--Witten theory formed by replacing contracted elliptic components with singularities\footnote{We have been informed by Jonathan Wise that his Ph.D.
+candidate Sebastian Bozlee has constructed these higher genus reduced Gromov--Witten invariants.
+A manuscript is in preparation.}.
 The discussion here is likely to carry over to this setting.
@@
 In particular, we use frequently use Kato's perspective on logarithmic blowups as subfunctors that was applied in~\cite{RSPW,RSPW2}.
+
+\subsection*{Acknowledgements} We have benefited from fruitful conversations with friends and colleagues, including Davesh Maulik, Jonathan Wise, and [other people].
+Important  aspects of this work were completed while L.B.
+and N.N.
+were visiting MIT in Spring 2018 and the University of Cambridge in Winter 2019, and we thank these institutions for their hospitality.
 
@@
 \begin{cor}
-The logarithmically smooth stack $\mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)$ has at worst orbifold singularities, and consequently admits a non-representable cover by a smooth Deligne--Mumford stack.
+The logarithmically smooth stack $\mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)$ has at worst orbifold singularities, i.e. admits a non-representable cover by a smooth Deligne--Mumford stack.
 \end{cor}
@@
 
-\section{Stratification} The logarithmic smoothness established in Theorem~\ref{thm: log-smoothness} implies that $\mathcal{VZ}_{1,\alpha}(\mathbb P^N|H,d)$ is an orbifold toroidal embeddeding.
+\section{Stratification}
+
+\noindent The logarithmic smoothness established in Theorem~\ref{thm: log-smoothness} implies that $\mathcal{VZ}_{1,\alpha}(\mathbb P^N|H,d)$ is an orbifold toroidal embeddeding.
 Consequently, the irreducible components of its boundary and their intersections form a stratification of the space.
@@
 
-\subsection{The rubber space} In our implementation of the relative theory, we will need the naturally ``rubber'' variant of the space of maps $
+\subsection{Rubber variants} In our implementation of the relative theory, we will need the naturally ``rubber'' variant of the space of maps $
 \mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)$, where the entire curve is mapped into higher levels.
+
+Specifically, let $\mathbb P$ denote the projective bundle $\mathbb P(\mathcal O(1)\oplus\mathcal O)$ on $\mathbb P^{N-1}$.
+Equip this space with the logarithmic structure coming from the $0$ and $\infty$ sections of the bundle.
+Consider the moduli space $\mathcal{VZ}_{1,\alpha}(\mathbb P/\mathbb G_m)$ of logarithmic maps
+\[
+C\to \mathbb P[s]\to \mathbb P^{N-1},
+\]
+which factorize completely, and where automorphisms are considered over the space of maps to $\mathbb P^{N-1}$.
+Specifically, two maps that differ by a $\mathbb G_m$ translate in the fiber direction are considered equivalent.
+Total factorization, similar to the previous case, means that the map to the bundle and the map to the base $\mathbb P^{N-1}$ both factorize through possibly different singularities.
+
+\begin{thm}
+The stack $\mathcal{VZ}_{1,\alpha}(\mathbb P/\mathbb G_m)$ is logarithmically smooth.
+\end{thm}
+
+It is convenient to work with the logarithmic multiplicative group and its torsors.
+Recall that the \textit{logarithmic multiplicative group} $\mathbb G_{\mathrm{log}}$ is the functor on logarithmic schemes whose value on a logarithmic scheme $S$ is the group of global sections $H^0(S,M_S^{\mathrm{gp}})$.
+This functor is representable only after a logarithmically \'etale cover.
+
+The bundle $\mathbb P\to \mathbb P^{N-1}$ gives rise to a $\mathbb G_m$-torsors by deleting the zero and infinity sections.
+Replacing these fibers by their $\mathbb G_{\mathrm{log}}$ compactifications, we obtain a non-representable functor on logarithmic schemes $\mathbb P_{\mathrm{log}}$ and a logarithmically \'etale modification
+\[
+\mathbb P\to \mathbb P_{\mathrm{log}}.
+\]
+
+{\bf Add reference to Wise--R '19 and Marcus--Wise '17 for the multiplicative group.}
+
+\begin{proof}
+Consider the stack over logarithmic schemes $\mathcal{VZ}_{1,\alpha}(\mathbb P_{\mathrm{log}})$ of stable logarithmic maps that factorize completely.
+Here, stability for the map coincides with stability for the projection to $\mathbb P^{N-1}$.
+The arguments in the previous section show that maps to $\mathbb P$ that factorize completely are unobstructed.
+Since this space is a logarithmically \'etale cover of $\mathcal{VZ}_{1,\alpha}(\mathbb P_{\mathrm{log}})$, logarithmic smoothness of the latter follows.
+
+The logarithmic multiplicative group $\mathbb G_{\mathrm{log}}$ acts on $\mathcal{VZ}_{1,\alpha}(\mathbb P_{\mathrm{log}})$ by translation.
+Tautologically, $\mathcal{VZ}_{1,\alpha}(\mathbb P_{\mathrm{log}})$ is a $\mathbb G_{\mathrm{log}}$-torsor over the moduli problem of maps up to this $\mathbb G_{\mathrm{log}}$ translation.
+It is representable after a logarithmically \'etale modification by a family of nodal curves.
+It follows that the space  $\mathcal{VZ}_{1,\alpha}(\mathbb P_{\mathrm{log}}/\mathbb G_{\mathrm{log}})$ of maps up to translation that factorize completely is logarithmically smooth.
+
+To conclude the main result, we compare the stacks $\mathcal{VZ}_{1,\alpha}(\mathbb P_{\mathrm{log}}/\mathbb G_{\mathrm{log}})$ and  $\mathcal{VZ}_{1,\alpha}(\mathbb P/\mathbb G_m)$.
+Since a map to $\mathbb P$ gives rise immediately to a map to $\mathbb P_{\mathrm{log}}$, there is a morphism
+\[
+\mathcal{VZ}_{1,\alpha}(\mathbb P/\mathbb G_m)\to \mathcal{VZ}_{1,\alpha}(\mathbb P_{\mathrm{log}}/\mathbb G_{\mathrm{log}}).
+\]
+A straightforward application of the infinitesimal lifting criterion shows that this map is logarithmically \'etale, so the result follows.
+\end{proof}
+
+The main point in the proof above is that on the space of non-degenerate maps with smooth domains, the map from $\mathcal{VZ}^\circ_{1,\alpha}(\mathbb P)\to \mathcal{VZ}^\circ_{1,\alpha}(\mathbb P/\mathbb G_m)$ is a $\mathbb G_m$ torsor, and correspondingly on the compact spaces it is a $\mathbb G_{\mathrm{log}}$-torsor.
+The logarithmically \'etale modification guarantee representability, and turn this into a nodal curve fibration.
 

### 2019-06-08 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
tentative description of Yc0 after discussion with Dhruv in Bonn

@@
 \usepackage{tikz,tikz-cd}
-\usetikzlibrary{decorations.pathmorphing,decorations.pathreplacing,patterns}
+\usetikzlibrary{decorations.pathmorphing,decorations.pathreplacing,patterns,arrows.meta}
+\usetikzlibrary{ipe} % ipe compatibility library
+
+\tikzstyle{ipe stylesheet} = [
+  ipe import,
+  even odd rule,
+  line join=round,
+  line cap=butt,
+  ipe pen normal/.style={line width=0.4},
+  ipe pen heavier/.style={line width=0.8},
+  ipe pen fat/.style={line width=1.2},
+  ipe pen ultrafat/.style={line width=2},
+  ipe pen normal,
+  ipe mark normal/.style={ipe mark scale=3},
+  ipe mark large/.style={ipe mark scale=5},
+  ipe mark small/.style={ipe mark scale=2},
+  ipe mark tiny/.style={ipe mark scale=1.1},
+  ipe mark normal,
+  /pgf/arrow keys/.cd,
+  ipe arrow normal/.style={scale=7},
+  ipe arrow large/.style={scale=10},
+  ipe arrow small/.style={scale=5},
+  ipe arrow tiny/.style={scale=3},
+  ipe arrow normal,
+  /tikz/.cd,
+  ipe arrows, % update arrows
+  <->/.tip = ipe normal,
+  ipe dash normal/.style={dash pattern=},
+  ipe dash dashed/.style={dash pattern=on 4bp off 4bp},
+  ipe dash dotted/.style={dash pattern=on 1bp off 3bp},
+  ipe dash dash dotted/.style={dash pattern=on 4bp off 2bp on 1bp off 2bp},
+  ipe dash dash dot dotted/.style={dash pattern=on 4bp off 2bp on 1bp off 2bp on 1bp off 2bp},
+  ipe dash normal,
+  ipe node/.append style={font=\normalsize},
+  ipe stretch normal/.style={ipe node stretch=1},
+  ipe stretch normal,
+  ipe opacity 10/.style={opacity=0.1},
+  ipe opacity 30/.style={opacity=0.3},
+  ipe opacity 50/.style={opacity=0.5},
+  ipe opacity 75/.style={opacity=0.75},
+  ipe opacity opaque/.style={opacity=1},
+  ipe opacity opaque,
+]
+
+\definecolor{red}{rgb}{1,0,0}
 
@@
 
-\begin{lemma} Let $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ be an irreducible component which contributes nontrivially to the recursion, and let $\Delta$ be the corresponding combinatorial type.
+\begin{lemma}\label{lem:combs} Let $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ be an irreducible component which contributes nontrivially to the recursion, and let $\Delta$ be the corresponding combinatorial type.
 Suppose that $\Delta$ assigns positive degree to the circuit.
@@
 
-\begin{lemma} The degree of $\rho$ is given by:
+\begin{lemma}\label{lem:saturation} The degree of $\rho$ is given by:
 \begin{equation*} \label{degree of gluing} \dfrac{\prod_{i=1}^r m_i}{\lcm(m_1,\ldots,m_r)}. \end{equation*}\end{lemma}
@@
 
-\begin{lemma} \label{lemma vanishing order} $\lambda_\Dcal = \lcm(m_1,\ldots,m_r).$ \end{lemma}
+\begin{lemma}\label{lemma vanishing order} $\lambda_\Dcal = \lcm(m_1,\ldots,m_r).$ \end{lemma}
 \begin{proof} Let $\tau \in \Sigma_{1,\alpha}(\PP^N|H,d)$ be the cone corresponding to $\Dcal$ and let
@@
 
-\subsection{Recursive description of the divisors: type $C^0$}
+\subsection{Recursive description of the divisors: type $C^0$} In this case, the core has (horizontal) degree $0$ and is mapped into $H$.
+We start by describing the relevant combinatorial types of rays in $\widetilde{\VZ}_{1,\alpha}(\PP^N|H,d)$.
+\begin{lemma} In what follows it is understood that we insert trivial bubbles whenever the curve or target need to be subdivided in order for the image and preimage of every polyhedral subcomplex to be a union of polyhedral subcomplexes.
+ \begin{enumerate}
+  \item The core is represented by a single vertex of genus one and degree zero, tropically mapped to $\RR_{>0}$.
+  \item The vertices adjacent to the core with maximal expansion factor are tropically mapped to $0$.
+  \item For every point of the target different from $0$, the fiber of the tropical map contains at most one stable vertex, which either is the core or lies on the circle.
+  \item $x_k$ is supported by a vertex tropically mapped to $\RR_{>0}$.
+ \end{enumerate}
+\end{lemma}
+\begin{proof}
+ By assumption, the core is mapped to $\RR_>0$, hence the distance of its image from $0$ is one parameter $\ell$; since we are describing a ray, all other parameters have to be related to $\ell$, and the only way it can be so is via the alignment.
+If the fiber over $c>0$ contains two stable vertices, because both the insertions and the factorisation condition are pulled back from the moduli space without expansions, it can be seen as in Lemma \ref{lem:combs} that the collapsing morphism $\Dcal\to\Fcal$ has positive-dimensional fibers (disconnected rubber), so the corresponding combinatorial type does not contribute to the invariants.
+We conclude that every stable vertex over $\RR_{>0}$ different from the core has to lie on the circle.
+\end{proof}
+\begin{center}
+\begin{figure}
+ \begin{tikzpicture}[ipe import]
+  %\useasboundingbox (0, 0) rectangle (595, 842);
+  \draw
+    (64, 672)
+     -- (128, 688)
+     -- (64, 704)
+     -- (64, 704);
+  \draw
+    (128, 688)
+     -- (64, 736)
+     -- (64, 736);
+  \draw[red]
+    (128, 688) circle[radius=65.9697];
+  \draw
+    (128, 688)
+     -- (112, 752)
+     -- (64, 768)
+     -- (64, 768);
+  \draw
+    (112, 752)
+     -- (64, 784)
+     -- (64, 784);
+  \pic
+     at (64, 672) {ipe disk};
+  \pic
+     at (64, 704) {ipe disk};
+  \pic
+     at (64, 736) {ipe disk};
+  \pic
+     at (64, 768) {ipe disk};
+  \pic
+     at (64, 784) {ipe disk};
+  \pic
+     at (112, 752) {ipe disk};
+  \pic
+     at (75.2242, 727.5818) {ipe cross};
+  \pic
+     at (112, 700) {ipe cross};
+  \pic
+     at (112, 692) {ipe cross};
+  \pic
+     at (112, 684) {ipe cross};
+  \pic
+     at (75.8121, 701.047) {ipe cross};
+  \pic
+     at (75.0705, 674.4385) {ipe cross};
+  \filldraw[fill=white,->]
+    (64, 608)
+     -- (208, 608);
+  \pic
+     at (64, 608) {ipe disk};
+  \draw
+    (128, 688)
+     -- (208, 688);
+  \pic
+     at (73.6978, 608.0203) {ipe cross};
+  \pic
+     at (111.8758, 608.0203) {ipe cross};
+  \pic
+     at (127.6736, 608.0203) {ipe cross};
+  \pic[fill=white]
+     at (128, 688) {ipe fdisk};
+  \node[ipe node]
+     at (86.863, 690.301) {$m$};
+  \node[ipe node]
+     at (87.521, 671.212) {$m$};
+  \node[ipe node]
+     at (48.026, 668.579) {$R_1$};
+  \node[ipe node]
+     at (48.026, 687.668) {$\ldots$};
+  \node[ipe node]
+     at (47.368, 700.832) {$R_k$};
+  \node[ipe node]
+     at (48.026, 725.846) {$R_{k+1}$};
+  \node[ipe node]
+     at (48.026, 784.429) {$R_s$};
+  \node[ipe node]
+     at (48.026, 766.657) {$\ldots$};
+  \node[ipe node]
+     at (108.585, 757.441) {$R_r$};
+  \node[ipe node]
+     at (80, 744.935) {$\ldots$};
+  \node[ipe node]
+     at (130.965, 677.794) {$E$};
+\end{tikzpicture}
+\caption{A ray of type $C^0$.}\label{fig:ray_example}
+\end{figure}
+\end{center}
+
+See Figure \ref{fig:ray_example}.
+We observe that the corresponding stratum $\Ecal$ of $\ol\Mcal_{1,\alpha}(\PP^N|H,d)$ has logarithmic codimension equal to the number of non-core vertices mapping to $\RR_{>0}$: indeed, the combinatorial type of $\Ecal$ can be read off by forgetting the circle, and the logarithmic codimension in $\ol\Mcal_{1,\alpha}(\PP^N|H,d)$ is accounted for by the number of subdivisions of the target.
+The discrepancy in dimension is to be expected, as the loci of type $C^0$ are contained in the exceptional locus of the blow-up.
+
+The geometry of $\widetilde\Dcal\to\Ecal$ is encoded by the combinatorics of the alignment.
+The reader should bear the following toric construction in mind: suppose we subdivide a fan, and we want to describe the relation between the varieties corresponding respectively to a cone $\rho$ of the subdivision, and the original cone $\sigma$ containing it.
+The fan of $X_\tau$ is obtained by projecting the star of $\tau$ to the quotient $N_\tau=N_{\RR}/\langle\tau\rangle_{\RR}$ of the ambient vector space by the linear span of the cone\footnote{We find it useful to encode this within the formalism of extended tropicalisations \cite{?}.}.
+Notice that the dimension of the vector spaces $N_\rho$ and $N_\sigma$ (or the corresponding toric varieties) is off by the difference $c$ between the dimension of the cones.
+Furthermore, we may need to subdivide the fan of $X_\sigma$ in order for cones of $\Sigma_\rho$ to be mapped surjectively to cones of $\Sigma_\sigma$.
+The geometric interpretation of this is that $X_\tau$ is obtained as an appropriate compactification of a toric bundle of dimension $c$ over $X_\sigma$; observe that the fiber dimension may not be constant (but it can be made so by blowing up $X_{\sigma}$, see \cite[Lemma 4.1]{AK}).
+It is a fundamental insight due to Tevelev \cite{Tevelev} that a good compactification of the toric bundle is suggested by the tropicalisation of the locus we are interested in: here, ``good'' means that the intersection of the interesting locus with the boundary is dimensionally transverse.
+In the case at hand, the interesting locus is that of maps satisfying the factorisation property (i.e.
+smoothable maps), and the tropicalisation has been worked out in \cite{RSPW2} to consist of well-spaced maps.
+
+We proceed to describe $\Dcal$ step-by-step, building on $\Ecal$.
+
+\subsubsection{The fiber product} We start from the finite splitting morphism
+\begin{multline}\label{eq:product}
+ \rho\colon \Ecal \to \left(\prod_{i=1}^k \ol\Mcal_{0,\alpha^{(i)}\cup(m)}(\PP^N|H,d_i) \times \prod_{i=k+1}^s \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i)\right)\times_{H^s} \\ \prod_{j=k+1}^{r}\ol\Mcal_{0,\alpha^{(j)}\cup(-m_i)_{i \in I_j\subseteq\{k+1,\ldots,s\}}\cup(\mu_j)}^{\leftrightarrow}(P|H_0+H_\infty,d_j)\times_{H^{r-k}} \\
+ \ol\Mcal_{1,\alpha^{(0)}\cup(-m,\ldots,-m,-\mu_{k+1},\ldots,-\mu_r)\cup(-m_i)_{i\in\{k+1,\ldots,s\}\setminus(\bigcup I_j)}}^{\leftrightarrow}(P|H_0+H_\infty,0)
+\end{multline}
+The degree of $\rho$ can be computed as in Lemma \ref{lem:saturation} above.
+From the logarithmic point of view, $\rho$ is a saturation map; generically it should be thought of as follows.
+On the fiber product, the tangent vectors of the components on level $0$ (corresponding to the factors in the first line above) are identified with the target tangent line up to finite powers; the saturation is taking roots of these isomorphisms (it is interesting to notice that it fails precisely on Gathmann's boundary comb loci).
+
+\subsubsection{The generic alignment} In the first line of the product above, we have grouped the $k$ factors adjacent to the core with maximal expansion factor $m$.
+It is fundamental to realise that, generically on $\Ecal$, the vertices corresponding to these factors are (equidistant and) already aligned with respect to the core.
+We can construct a modification $\widetilde\Ecal$ of $\mathcal E$ by:
+\begin{enumerate}
+ \item radially aligning the core, and imposing the double factorisation condition, thus effectively replacing the factor
+ \[\ol\Mcal_{1,\alpha^{(0)}\cup(-m,\ldots,-m,-\mu_{k+1},\ldots,-\mu_r)\cup(-m_i)_{i\in\{k+1,\ldots,s\}\setminus(\bigcup I_j)}}^{\leftrightarrow}(P|H_0+H_\infty,0)\]
+ by $\VZ_{1,\alpha^{(0)}\cup(-m,\ldots,-m,-\mu_{k+1},\ldots,-\mu_r)\cup(-m_i)_{i\in\{k+1,\ldots,s\}\setminus(\bigcup I_j)}}^{\leftrightarrow}(P|H_0+H_\infty,0)$ in the product above; in particular, there is a universal cotangent line bundle at the markings $\mathbb L_E$, obtained by suitably twisting any marking cotangent line (they are all isomorphic over a smooth elliptic curve) by the appropriate bubbling loci (see \cite[\S 2.3]{VZ});
+ \item aligning the first $k$ factors with respect to the core (this blows up some diagonal subloci of the product, so it is not enough to align the individual factors).
+\end{enumerate}
+See Figure \ref{fig:fwise_align} below.
+It is obvious that $\widetilde \Dcal\to \Ecal$ factors through $\widetilde\Ecal$.
+On $\widetilde\Ecal$, we have a tropical line bundle $\OO(\delta)$ representing the minimum distance from the core to the tropical preimage of $0$; generically, this line bundle coincides with the normal bundle of the locus where the node between the core and one (any) of the first $k$ vertices persists, but on the boundary this needs to be twisted by further smoothing parameters according to the (partial) alignment on $\widetilde\Ecal$.
+We can obtain a line bundle $\mathbb T_R$ accounting only for the behaviour of the rational side of the fiber product by twisting $\OO(\delta)$ with $\mathbb L_E$.
+\begin{figure}
+ \begin{tikzpicture}[ipe stylesheet,scale=.7]
+  %\useasboundingbox (0, 0) rectangle (595, 842);
+  \pic
+     at (129.8488, 703.2932) {ipe disk};
+  \pic
+     at (97.8488, 719.2932) {ipe disk};
+  \pic
+     at (97.8488, 687.2932) {ipe disk};
+  \draw
+    (97.8488, 719.2932)
+     -- (129.8488, 703.2932)
+     -- (97.8488, 687.2932);
+  \draw
+    (129.8488, 703.2932)
+     -- (161.8488, 687.2932);
+
+  \draw
+    (193.8488, 671.2932)
+     -- (225.8488, 655.2932);
+  \draw
+    (225.8488, 655.2932)
+     -- (193.8488, 639.2932);
+    \draw[ipe dash dashed]
+   (193.8488, 671)
+    -- (161.8488, 687);
+  \draw[ipe dash dashed]
+    (193.8488, 639.2932)
+     -- (161.8488, 623.2932);
+  \draw
+    (161.8488, 623.2932)
+     -- (129.8488, 607.2932);
+  \pic
+     at (146.637, 615.0615) {ipe disk};
+  \draw
+    (129.8488, 607.2932)
+     -- (97.8488, 591.2932)
+     -- (97.8488, 591.2932);
+  \draw
+    (147.2948, 615.0622)
+     -- (97.2686, 638.1002)
+     -- (97.2686, 638.1002);
+  \pic
+     at (96.6103, 637.4422) {ipe disk};
+  \pic
+     at (97.9268, 590.7072) {ipe disk};
+  \pic
+     at (130.1808, 622.9607) {ipe cross};
+  \pic
+     at (130.1808, 607.1635) {ipe cross};
+  \pic
+     at (145.9788, 695.3672) {ipe cross};
+  \draw[-ipe linear]
+    (97.8488, 575.2932)
+     -- (257.8488, 575.2932);
+  \pic
+     at (97.8488, 575.2932) {ipe disk};
+  \pic
+     at (129.8488, 575.2932) {ipe cross};
+  \pic
+     at (145.8488, 575.2932) {ipe cross};
+  \pic
+     at (225.8488, 575.2932) {ipe cross};
+  \draw
+    (129.8488, 703.2932)
+     -- (257.8488, 703.2932);
+  \draw
+    (225.8488, 655.2932)
+     -- (257.8488, 655.2932)
+     -- (257.8488, 655.2932);
+  \draw
+    (146.3018, 614.861)
+     -- (258.5378, 614.404);
+  \node[ipe node]
+     at (189.423, 676.278) {$m$};
+  \node[ipe node]
+     at (189.094, 629.543) {$m$};
+  \node[ipe node]
+     at (111.421, 715.773) {$m_1$};
+  \node[ipe node]
+     at (110.104, 590.707) {$m_2$};
+  \node[ipe node]
+     at (110.763, 564.378) {$\ell_1$};
+  \node[ipe node]
+     at (133.801, 564.377) {$\ell_2$};
+  \node[ipe node]
+     at (146.308, 543.972) {$\frac{\ell_1}{m_1}+\frac{\ell_2}{m} \lesseqgtr \frac{\ell_1+\ell_2}{m_2}$};
+  \pic
+     at (473.6651, 658.9228) {ipe disk};
+  \pic
+     at (353.8488, 719.2932) {ipe disk};
+  \pic
+     at (353.8488, 687.2932) {ipe disk};
+  \draw
+    (353.8488, 719.2932)
+     -- (385.8488, 703.2932)
+     -- (353.8488, 687.2932);
+  \draw
+    (386.7731, 703.2932)
+     -- (418.7731, 687.2932);
+  \draw[ipe dash dashed]
+    (417.8488, 687.2932)
+     -- (449.8488, 671.2932)
+     -- (449.8488, 671.2932);
+
+  \draw
+    (449.8488, 671.2932)
+     -- (481.8488, 655.2932)
+     -- (481.8488, 655.2932);
+  \draw
+    (481.8488, 655.2932)
+     -- (449.8488, 639.2932)
+     -- (449.8488, 639.2932);
+  \draw[ipe dash dashed]
+    (449.8488, 639.2932)
+     -- (417.8488, 623.2932);
+  \draw
+    (417.8488, 623.2932)
+     -- (385.8488, 607.2932);
+  \pic
+     at (457.1756, 642.7929) {ipe disk};
+  \draw
+    (385.8488, 607.2932)
+     -- (353.8488, 591.2932)
+     -- (353.8488, 591.2932);
+  \pic
+     at (352.6103, 622.6521) {ipe disk};
+  \pic
+     at (353.9268, 590.7072) {ipe disk};
+  \pic
+     at (458.2826, 667.3311) {ipe cross};
+  \pic
+     at (459.207, 575.7344) {ipe cross};
+  \draw[-ipe linear]
+    (353.8488, 575.2932)
+     -- (513.8488, 575.2932);
+  \pic
+     at (353.8488, 575.2932) {ipe disk};
+  \pic
+     at (385.8488, 575.2932) {ipe cross};
+  \pic
+     at (475.7994, 575.2932) {ipe cross};
+  \pic
+     at (481.8488, 575.2932) {ipe cross};
+  \draw[shift={(472.741, 659.847)}, xscale=0.3271, yscale=-1.7893]
+    (0, 0)
+     -- (128, 0);
+  \draw
+    (481.8488, 655.2932)
+     -- (513.8488, 655.2932)
+     -- (513.8488, 655.2932);
+  \draw[shift={(459.26, 642.878)}, xscale=0.4834, yscale=0.4807]
+    (0, 0)
+     -- (112.236, -0.457);
+  \draw[red]
+    (482.3765, 654.0394) circle[radius=9.9987];
+  \draw
+    (354.8117, 621.686)
+     -- (386.2407, 606.8958);
+  \pic
+     at (386.2407, 606.8958) {ipe disk};
+  \pic
+     at (386.2407, 703.956) {ipe disk};
+  \draw[red]
+    (360.3506, 584.6012)
+     arc[start angle=160.4967, end angle=217.0656, x radius=120.4239, y radius=-143.3401];
+  \pic
+     at (473.9974, 650.6919) {ipe cross};
+  \pic
+     at (364.92, 693.131) {ipe cross};
+  \pic
+     at (372.3151, 710.6943) {ipe cross};
+  \pic
+     at (359.3737, 593.2977) {ipe cross};
+  \draw
+    (226.3225, 655.8881)
+     -- (258.6759, 665.1319);
+  \draw
+    (226.3225, 654.0394)
+     -- (258.6759, 646.6443);
+  \draw[-ipe linear]
+    (271.6173, 766.814)
+     -- (337.2485, 767.7384);
+
+  \pic
+     at (272.5417, 782.5285) {ipe disk};
+  \pic
+     at (271.6173, 815.8063) {ipe disk};
+  \draw
+    (305.8194, 798.2431)
+     -- (272.5417, 815.8063);
+  \draw
+    (305.8194, 798.2431)
+     -- (272.5417, 782.5285)
+     -- (272.5417, 782.5285);
+  \draw
+    (272.5417, 782.5285)
+     -- (336.3241, 782.5285);
+  \draw
+    (272.5417, 815.8063)
+     -- (336.3241, 814.8819);
+  \draw
+    (304.8951, 799.1674)
+     -- (335.3997, 799.1674);
+  \draw
+    (305.8194, 799.1674)
+     -- (336.3241, 804.7137);
+  \draw
+    (305.8194, 798.2431)
+     -- (335.3997, 792.6968);
+  \draw
+    (387.1651, 703.956)
+     -- (511.0324, 703.956)
+     -- (511.0324, 703.0316);
+  \draw
+    (388.0895, 605.0471)
+     -- (511.9568, 605.0471);
+  \pic
+     at (272.5417, 766.814) {ipe disk};
+  \draw[red]
+    (304.8951, 797.3187) circle[radius=35.9679];
+
+    \pic[fill=white]
+     at (225.8488, 655.2932) {ipe fdisk};
+
+     \pic[fill=white]
+     at (481.8488, 655.2932) {ipe fdisk};
+
+     \pic[fill=white]
+     at (304.8951, 799.1674) {ipe fdisk};
+\end{tikzpicture}
+\caption{Two degenerations of the combinatorial type above, which represents a ray.
+On the left-hand side, the alignment holds only generically.
+On the right-hand side, it is not enough to align each individual factor.}\label{fig:fwise_align}
+\end{figure}
+
+\subsubsection{The projective bundle}\label{subs:proj_bun} Generically on $\widetilde\Ecal$, the compactified torus bundle $\widetilde \Dcal\to \widetilde\Ecal$ coincides with the following projective bundle:
+\[\mathcal P=\PP_{\widetilde\Ecal}(\mathbb T_R\oplus\bigoplus_{j=k+1}^r \mathbb T_{q_j}R_j),\]
+where $\mathbb T_{q_j}R_J$ is the tangent line at the gluing marking closest to the core on the $j$-th factor of the product in the second line of \eqref{eq:product}.
+The open stratum in the fiber consists of moduli of attachments (i.e.
+moduli for the contraction to the Smyth's singularity); the compactification is by adding strictly semistable Gorenstein singularities as in \cite[\S\S 2.2-2.3]{SMY2}.
+In terms of alignment, a coordinate hyperplane corresponds to pushing the corresponding vertex off the circle, and destabilising the corresponding edge to the core.
+Tropically, the fibers can be analysed as follows: pushing some of the vertices off the circle creates new finite length edges with coordinates $\ell_j\in\RR_{\geq_0}$ (see Figure \ref{fig:off_we_go}); not all of them can be strictly positive, because the circle needs to pass through at least one vertex of positive horizontal degree.
+This is patently the fan of a projective space.
+
+\begin{figure}
+\begin{tikzpicture}[ipe import,scale=.8]
+  %\useasboundingbox (0, 0) rectangle (595, 842);
+  \draw
+    (64, 672)
+     -- (128, 688)
+     -- (64, 704)
+     -- (64, 704);
+  \draw
+    (128, 688)
+     -- (64, 736)
+     -- (64, 736);
+  \draw[red]
+    (128, 688) circle[radius=65.9697];
+  \draw
+    (128, 688)
+     -- (112, 752)
+     -- (64, 768)
+     -- (64, 768);
+  \draw
+    (112, 752)
+     -- (64, 784)
+     -- (64, 784);
+  \pic
+     at (64, 672) {ipe disk};
+  \pic
+     at (64, 704) {ipe disk};
+  \pic
+     at (64, 736) {ipe disk};
+  \pic
+     at (64, 768) {ipe disk};
+  \pic
+     at (64, 784) {ipe disk};
+  \pic
+     at (112, 752) {ipe cross};
+  \pic
+     at (75.2242, 727.582) {ipe cross};
+  \pic
+     at (112, 700) {ipe cross};
+  \pic
+     at (112, 692) {ipe cross};
+  \pic
+     at (112, 684) {ipe cross};
+  \pic
+     at (75.8121, 701.047) {ipe cross};
+  \pic
+     at (75.0704, 674.4388) {ipe cross};
+  \filldraw[fill=white]
+    (64, 608)
+     -- (208, 608)
+     -- (208, 608);
+  \pic
+     at (64, 608) {ipe disk};
+  \draw
+    (128, 688)
+     -- (208, 688)
+     -- (208, 688);
+  \pic
+     at (73.6978, 608.02) {ipe cross};
+  \pic
+     at (111.876, 608.0202) {ipe cross};
+  \pic
+     at (127.674, 608.0205) {ipe cross};
+  \pic[fill=white]
+     at (128, 688) {ipe fdisk};
+  \node[ipe node]
+     at (86.863, 690.301) {$m$};
+  \node[ipe node]
+     at (87.521, 671.212) {$m$};
+  \draw
+    (128, 688)
+     -- (91.4703, 741.643);
+  \draw
+    (128, 688)
+     -- (160.586, 745.593)
+     -- (160.586, 745.593);
+  \pic
+     at (91.4703, 741.643) {ipe disk};
+  \pic
+     at (160.486, 745.417) {ipe disk};
+  \draw[shift={(91.47, 741.051)}, xscale=0.95, yscale=0.6996]
+    (0, 0)
+     -- (-26.9879, 7.241)
+     -- (-26.9879, 7.241);
+  \draw
+    (160.486, 745.417)
+     -- (64.4824, 799.569);
+  \draw
+    (160.486, 745.417)
+     -- (208.637, 745.593);
+  \draw
+    (92.1286, 740.985)
+     -- (64.4824, 754.15);
+  \pic
+     at (64.4824, 746.909) {ipe disk};
+  \pic
+     at (64.4824, 798.91) {ipe disk};
+  \pic
+     at (64.4824, 753.492) {ipe disk};
+  \draw
+    (289.118, 672.0005)
+     -- (353.118, 688.0005)
+     -- (289.118, 704.0005)
+     -- (289.118, 704.0005);
+  \draw
+    (353.118, 688.0005)
+     -- (289.118, 736.0005)
+     -- (289.118, 736.0005);
+  \draw[red]
+    (353.118, 688.0005) circle[radius=65.9697];
+  \draw
+    (353.118, 688.0005)
+     -- (337.118, 752.0005)
+     -- (289.118, 768.0005)
+     -- (289.118, 768.0005);
+  \draw
+    (337.118, 752.0005)
+     -- (289.118, 784.0005)
+     -- (289.118, 784.0005);
+  \pic
+     at (289.118, 672.0005) {ipe disk};
+  \pic
+     at (289.118, 704.0005) {ipe disk};
+  \pic
+     at (289.118, 736.0005) {ipe disk};
+  \pic
+     at (289.118, 768.0005) {ipe disk};
+  \pic
+     at (289.118, 784.0005) {ipe disk};
+  \pic
+     at (337.118, 752.0005) {ipe cross};
+  \pic
+     at (300.3422, 727.5825) {ipe cross};
+  \pic
+     at (337.118, 700.0005) {ipe cross};
+  \pic
+     at (337.118, 692.0005) {ipe cross};
+  \pic
+     at (337.118, 684.0005) {ipe cross};
+  \pic
+     at (300.9301, 701.0475) {ipe cross};
+  \pic
+     at (300.1889, 674.4392) {ipe cross};
+  \filldraw[fill=white]
+    (289.118, 608.0005)
+     -- (433.118, 608.0005)
+     -- (433.118, 608.0005);
+  \pic
+     at (289.118, 608.0005) {ipe disk};
+  \draw
+    (353.118, 688.0005)
+     -- (433.118, 688.0005)
+     -- (433.118, 688.0005);
+  \pic
+     at (298.8158, 608.0205) {ipe cross};
+  \pic
+     at (336.994, 608.0207) {ipe cross};
+  \pic
+     at (352.792, 608.0209) {ipe cross};
+  \pic[fill=white]
+     at (353.118, 688.0005) {ipe fdisk};
+  \node[ipe node]
+     at (311.98, 690.301) {$m$};
+  \node[ipe node]
+     at (312.639, 671.212) {$m$};
+  \draw[shift={(353.118, 687.999)}, xscale=1.1287, yscale=1.1615]
+    (0, 0)
+     -- (-36.5297, 53.643);
+  \draw[shift={(353.119, 687.997)}, xscale=1.4269, yscale=1.3567]
+    (0, 0)
+     -- (32.586, 57.593)
+     -- (32.586, 57.593);
+  \pic
+     at (310.6643, 751.5171) {ipe disk};
+  \pic
+     at (400.086, 767.1394) {ipe disk};
+  \draw[shift={(311.745, 750.197)}, xscale=0.8205, yscale=-0.5452]
+    (0, 0)
+     -- (-26.9879, 7.241)
+     -- (-26.9879, 7.241);
+  \draw[shift={(399.543, 767.54)}, xscale=1.1319, yscale=0.5704]
+    (0, 0)
+     -- (-96.0036, 54.152);
+  \draw[shift={(400.744, 767.146)}, xscale=0.6446, yscale=-1.3688]
+    (0, 0)
+     -- (48.151, 0.176);
+  \draw[shift={(311.717, 751.113)}, xscale=0.8, yscale=0.1453]
+    (0, 0)
+     -- (-27.6462, 13.165);
+  \pic
+     at (289.6004, 746.9095) {ipe disk};
+  \pic
+     at (289.6004, 798.9105) {ipe disk};
+  \pic
+     at (289.6004, 753.4925) {ipe disk};
+  \pic
+     at (387.02, 744.935) {ipe cross};
+  \pic
+     at (317.246, 742.961) {ipe cross};
+  \node[ipe node]
+     at (315.273, 748.884) {$\ell_{j_1}$};
+  \node[ipe node]
+     at (397.553, 752.175) {$\ell_{j_2}$};
+\end{tikzpicture}
+\caption{Moving vertices off the circle creates new tropical parameters.}\label{fig:off_we_go}
+\end{figure}
+
+\subsubsection{Factorisation} Assume $m\geq 2$. Over $\mathcal P$ we have a tautological sequence:
+\[\OO_{F}(-1)\hookrightarrow p^*(F)\xrightarrow{+\operatorname{d}f}\operatorname{ev}_E^*(TH),\]
+where $p\colon\mathcal P=\PP(F)\to\widetilde\Ecal$, and $+\operatorname{d}f$ should be interpreted as follows: $k$ copies of $\mathbb T_R$ are taken to account - via the preferred isomorphisms - for all factors of the first product in \eqref{eq:product}; then, the differential of the universal map to $\PP^N$ is applied to each tangent vector (possibly including some of the contracted rational bubbles in the boundary), and the sum of these contributions is taken in $T_{f(E)}\PP^N$ - it actually lies in $T_{f(E)}H$ because all the normal contributions are trivial by assumption.
+The composition is a section $s$ of $G=\OO_F(1)\otimes \operatorname{ev}_E^*(TH)$, and it vanishes precisely where $f$ factors through the Smyth's singularity determined by the point in the fiber of $p$.
+Generically on $\widetilde\Ecal$, this is exactly what we are after.
+
+\subsubsection{Dimensional transversality} In general, the vanishing locus of $s$ corresponds to maps $f\colon C\to\PP^N$ and diagrams $C\leftarrow \tilde C\to \bar C$ - with $\bar C$ the elliptic $r$-fold point determined by the position in the fiber of $p\colon\mathcal P\to\widetilde \Ecal$ - such that $f$ factors through $\bar C$.
+When the curve is allowed to degenerate (so, on the boundary of $\widetilde \Ecal$), this is not always what we want: indeed, due do the combined action of degeneration (in the base direction) and destabilisation (in the fiber direction), it may very well be that $f$ is constant along every component of the elliptic singularity, so that it factors trivially; in other words, the vanishing locus of $s$ is not dimensionally transverse to the boundary of $\mathcal P$.
+\begin{lemma}
+ For every $K\subseteq\{1,\ldots,r\}$ and $K^c=\{1,\ldots,r\}\setminus K$, $s$ vanishes along the loci where the factors corresponding to $K$ in $\widetilde \Ecal$ degenerate so that $f_k\colon R_k\to\PP^N$ is constant in a neighbourhood of $q_k$, and the fiber coordinates $(\lambda_{h})_{h\in K^c}$ along $p\colon\mathcal P\to\widetilde \Ecal$ are set to be $0$.
+\end{lemma}
+Call these loci $\Delta_i,i\in I$. See \cite[\S 3.2]{VZ} for a treatment of the analogous situation in the non-relative case; the study of the normal bundles is also dealt with there.
+
+It is clear that these loci are logarithmic substrata; therefore, there exists a logarithmic blow-up that principalizes them.
+We claim that $\widetilde\Dcal$ is (possibly a refinement of) this blow-up.
+This follows from the tropical discussion in Section \ref{subs:proj_bun}, and the fact that the degenerate circle that we are drawing on the $\Delta_i$ falls in the strict interior of the circle of radius $\delta$ on $\widetilde\Dcal$ (because the former only passes through vertices of horizontal degree $0$), thus all the distances from the vertices to the former circle are ordered.
+See Figure \ref{fig:principalisation} above.
+\begin{figure}
+\begin{tikzpicture}[ipe import]
+  %\useasboundingbox (0, 0) rectangle (595, 842);
+  \draw
+    (64, 720)
+     -- (112, 736)
+     -- (96, 752);
+  \draw[->]
+    (64, 704)
+     -- (128, 704);
+  \pic
+     at (64, 704) {ipe disk};
+  \pic
+     at (64, 720) {ipe disk};
+  \pic
+     at (96, 752) {ipe disk};
+  \draw[red, dotted]
+    (60.6969, 708.808)
+     arc[start angle=-161.5651, end angle=-71.5651, x radius=53.2078, y radius=-65.2105];
+  \pic[fill=white]
+     at (112, 736) {ipe fdisk};
+  \draw
+    (192, 720)
+     -- (240, 736)
+     -- (224, 752);
+  \draw[->]
+    (192, 704)
+     -- (256, 704);
+  \pic
+     at (192, 704) {ipe disk};
+  \pic
+     at (192, 720) {ipe disk};
+  \pic
+     at (224, 752) {ipe disk};
+  \pic[fill=white]
+     at (240, 736) {ipe fdisk};
+  \draw
+    (112, 736)
+     -- (128, 736);
+  \draw
+    (240, 736)
+     -- (256, 736);
+  \draw
+    (208.6374, 743.6181)
+     -- (224.4352, 750.8588);
+  \draw
+    (208.6374, 758.7577)
+     -- (225.0934, 751.517);
+  \pic
+     at (207.9791, 742.9599) {ipe disk};
+  \pic
+     at (207.9791, 758.7577) {ipe disk};
+  \pic
+     at (208, 704) {ipe cross};
+  \pic
+     at (224, 704) {ipe cross};
+  \pic
+     at (240, 704) {ipe cross};
+  \pic
+     at (96, 704) {ipe cross};
+  \pic
+     at (112, 704) {ipe cross};
+  \draw[red, dotted]
+    (231.0126, 755.9018)
+     { [rotate=-17.595] arc[start angle=135, end angle=225, x radius=21.7093, y radius=22.6274] };
+  \draw[red]
+    (188.9249, 712.0225)
+     arc[start angle=-156.5092, end angle=-115.3692, x radius=85.088, y radius=-96.462];
+\end{tikzpicture}
+\caption{On the left, a generic point of $\mathcal P$.
+On the right, a point $\Delta$.
+The dotted circle is what we have on $\mathcal P$.
+The continuous circle is the one of radius $\delta$ on $\widetilde\Dcal$; this principalises the degeneration.}\label{fig:principalisation}
+\end{figure}
+
+Finally, on $\widetilde\Dcal$ there are exceptional divisors $\widetilde \Delta_i$ corresponding to $\Delta_i$ in $\mathcal P$.
+By the preceding analysis, $s\in\Gamma(\mathcal P,G)$ induces a section $\tilde s\in\Gamma(\widetilde\Dcal,G(-\sum_i\widetilde\Delta_i))$ by pullback, whose vanishing locus is dimensionally transverse to the boundary, and whose open part coincides with the generic point of $\Dcal$, therefore $V(\tilde s)=\Dcal$.
+
+\subsection{Tautological contributions} Expressing the pushforward of the Chern classes of $\OO_F(1)$ and $\OO(\widetilde\Delta_i)$ in terms of tautological classes on the fiber product underlying $\Ecal$, get:
+\begin{cor}
+ After pushforward to $\Ecal$, the contribution of $\Dcal$ to the invariants can be computed in terms of tautological integrals on moduli spaces of maps with lower numerics.
+\end{cor}
 

### 2019-06-25 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
minor changes
changed combinatorial type bit, and some more structure

@@
 \usetikzlibrary{decorations.pathmorphing,decorations.pathreplacing,patterns,arrows.meta}
+
+%%%%%%%%%%%%%%%%%%%
+\begin{comment}
 \usetikzlibrary{ipe} % ipe compatibility library
-
 \tikzstyle{ipe stylesheet} = [
@@
 ]
+\end{comment}
 
 \definecolor{red}{rgb}{1,0,0}
-
 \usepackage[all]{xy}
@@
 
-\title{Absolute, relative and rubber Gromov--Witten theory of hypersurfaces in genus one}
+\title{Curve counting in genus one: elliptic singularities and relative geometry}
 \author{Luca Battistella, Navid Nabijou and Dhruv Ranganathan}
@@
 Let $\plC$ be a $n$-pointed genus $1$ tropical curve.
-Let $C$ be a logarithmic curve over $S$, let $\plC$ denote its tropicalization, and let $\lambda$ be the section of $\overline{M}_{C/S}$ giving the distance from the circuit.
+Let $C$ be a logarithmic curve over $S$, let $\plC$ denote its tropicalization, and let $\lambda$ be the section of $\overline{M}_{C/S}$ giving the distance from the core.
 
 We begin by recalling the logarithmic moduli spaces of genus $1$ curves constructed in~\cite[Sections 2 \& 4]{RSPW}.
-Given a family of tropical curves over a base $\sigma$, a central alignment is a piecewise-linearly varying choice of radius $\delta_s$ for $s\in\sigma$, together with a consistent ordering of the vertices that lie inside the circle of radius $s$ around the circuit components.
+Given a family of tropical curves over a base $\sigma$, a central alignment is a piecewise-linearly varying choice of radius $\delta_s$ for $s\in\sigma$, together with a consistent ordering of the vertices that lie inside the circle of radius $s$ around the core components.
 Precisely, let $T$ be a geometric point with logarithmic structure.
@@
 Let $D_1\subset C$ be the maximal genus $1$ subcurve that is mapped to higher level contracted by the map $C\to \mathbb P^N[s]$ in the fiber direction.
-Let $\delta_1$ be the associated radius from the circuit to the nearest non-contract component.
+Let $\delta_1$ be the associated radius from the core to the nearest non-contract component.
 Let $D_2$ be the maximal genus $1$ subcurve that is contracted by the collapsed map to $\mathbb P^N$, and let $\delta_2$ be the associated radius.
@@
 The pair $(\Lcal_k,s_k)$ is most naturally constructed on the moduli space $\MLog_{1,\alpha}(\PP^N|H,d)$ of non-expanded log maps; the corresponding pair on $\VZ_{1,\alpha}(\PP^N|H,d)$ will be obtained via pull-back.
-Consider therefore the tropicalisation $\Sigma^{\log}$ of $\MLog_{1,\alpha}(\PP^N|H,d)$, identified as usual with the moduli space of tropical maps to $\RR_{\geq 0}$.
-We have a universal family
+Consider therefore the tropicalisation $\Sigma^{\log}$ of $\MLog_{1,\alpha}(\PP^N|H,d)$.
+By tropicalising the universal family, we obtain a family of tropical maps
 \bcd
@@
 \begin{equation*} \cchern_1(\Lcal_k) = \alpha_k \psi_k + \ev_k^\st H.\end{equation*}
-This gives the construction of $(\Lcal_k,s_k)$ on $\MLog_{1,\alpha}(\PP^N|H,d)$; the construction on $\VZ_{1,\alpha}(\PP^N|H,d)$ is given by pull-back.
-The relevant piecewise-linear function is the composition:
+This gives the construction of $(\Lcal_k,s_k)$ on $\MLog_{1,\alpha}(\PP^N|H,d)$; the construction on $\VZ_{1,\alpha}(\PP^N|H,d)$ is obtained by pull-back.
+The relevant piecewise-linear function is simply the composition:
 \begin{equation*} \Sigma_{1,\alpha}(\PP^N|H,d) \to \Sigma^{\log} \to \RR_{\geq 0}.\end{equation*}
@@
 \end{enumerate}
-Notice that this process contains some redundancies: upon choosing a ray in the tropical moduli space, some of the edge lengths or vertex positions may get set to $0$.
-This induces a generisation of the intial combinatorial type $\Delta$, given by contracting the corresponding edges of the dual graph and moving the corresponding vertices from $\RR_{>0}$ to $0$.
+Notice that this process contains some redundancies: when we choose a ray in step (3) above, some of the edge lengths or vertex positions may get set to $0$.
+This induces a generisation of the intial combinatorial type $\Delta$, given by contracting appropriate edges of the dual graph and/or moving appropriate vertices from $\RR_{>0}$ to $0$.
 By the combinatorial type of a stratum in $\VZ_{1,\alpha}(\PP^N|H,d)$ we will always mean this generisation.
@@
 is a log modification, $\widetilde{\Dcal}$ is either exceptional or the proper transform of a log divisor.
-These cases correspond, respectively, to when the circuit is assigned zero degree or nonzero degree by the combinatorial type.
+These cases correspond, respectively, to when the core is assigned zero degree or nonzero degree by the combinatorial type.
 To begin with we will focus on the latter case.
@@
 \begin{lemma}\label{lem:combs} Let $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ be an irreducible component which contributes nontrivially to the recursion, and let $\Delta$ be the corresponding combinatorial type.
-Suppose that $\Delta$ assigns positive degree to the circuit.
+Suppose that $\Delta$ assigns positive degree to the core.
 Then $\Delta$ takes one of the following forms:
@@
 
-\noindent The terminology is due to Vakil, and the pictures in this case are very similar to \cite{Vre} (we will see later that when the circuit is assigned zero degree the picture becomes \emph{very} different).
-Note that in these pictures we have deliberately omitted the marked points (except for $x_k$), the degree of each vertex, and the expansion factors of the edges.
+\noindent The terminology is due to Vakil, and the pictures in this case are very similar to \cite{Vre} (as we will see later, when the core is assigned zero degree the picture becomes \emph{very} different).
+Note that in these pictures we have deliberately omitted  the degree of each vertex, the expansion factors of the edges and the marked points (except for $x_k$).
 The omitted combinatorial data can be distributed arbitrarily, as long as:
@@
 \item the vertices $\sqC_1,\ldots,\sqC_r$ have positive degree;
-\item the ellipse\footnote{(Navid) Didn't we decide this was our new terminology for the circuit?} has positive degree;
+\item the core has positive degree;
 \item every vertex is stable;
@@
 By the discussion above $\Dcal$ corresponds to a ray in the subdivision of $\sigma$ given by imposing the central alignment condition.
-But since the ellipse is assigned positive degree, both radii are equal to $0$ and the subdivision is trivial.
+But since the core is assigned positive degree, both radii are equal to $0$ and the subdivision is trivial.
 We conclude that $\sigma=\RR_{\geq 0}$ (recall we are assuming that the initial and generised combinatorial types coincide).
@@
 For the remainder of this subsection, therefore, we fix a one-dimensional cone $\tau \in \Sigma_{1,\alpha}(\PP^N|H,d)$, let $\Dcal \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$ be the associated log divisor, and assume that $\Dcal$ is contained in $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ and is of type $A,B$ or $C^+$.
-We let $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$ be the log stratum into which $\Dcal$ is mapped; this is indexed by a cone $\epsilon \in \Sigma$ corresponding to a combinatorial type $\Delta$, and $\epsilon$ is one-dimensional since we are restricting to the type $A,B,C^+$ cases.
+We let $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$ be the log stratum into which $\Dcal$ is mapped; this is indexed by a cone $\sigma \in \Sigma$ corresponding to a combinatorial type $\Delta$, and $\sigma$ is one-dimensional since we are restricting to the type $A,B,C^+$ cases.
 
@@
 \begin{proof}
-The choices involved in gluing log maps to expansions (which accounts for the degrees of the splitting morphisms above) is not affected by the introduction of alignments, so for the purposes of this proof we may pretend as if these splitting morphisms are the identity maps.
-
-Note that the map $\Dcal\to\Ecal$ is an isomorphism away from the blown-up locus, which is contained inside the locus where the circuit is contracted.
+The choices involved in gluing log maps to expansions (which account for the degrees of the splitting morphisms above) is not affected by the introduction of alignments, so for the purposes of this proof we may act as if these splitting morphisms are the identity maps.
+
+Note that the map $\Dcal\to\Ecal$ is an isomorphism away from the blown-up locus, which is contained inside the locus where the core is contracted.
 Given an element of $\Dcal$ we can split it along the nodes $q_1,\ldots,q_r$ as in \cite{}.
@@
 \begin{lemma}\label{type A radius lemma} $\lambda(\sqC^\prime) > \delta$ for any component $\sqC^\prime$ of $\sqC_0$ (with notation as in the proof above).\end{lemma}
-\begin{proof} The basic point is that $\Dcal$ is obtained as the disjoint union of the locally closed logarithmic strata contained in the closure of the stratum where all of the $\sqC_i$ are irreducible.
+\begin{proof} The basic point is that $\Dcal$ is obtained as the disjoint union of the locally closed logarithmic strata contained in the closure of the locally closed stratum on which all of the $\sqC_i$ are irreducible.
 If we look at one of these boundary strata, then by definition the associated cone $\sigma \in \Sigma_{1,\alpha}(\PP^N|H,d)$ contains a ray $\tau$ corresponding to the stratum where all the $\sqC_i$ are irreducible; this amounts to setting all edge lengths other than $e_1,\ldots,e_r$ to zero.
 If $f_1,\ldots,f_l$ are some collection of additional edge lengths in $\sigma$ (corresponding to internal nodes in degenerations of the $\sqC_i$) then since $\sigma$ is adjacent to $\tau$ we must have (by construction of the subdivision) $f_1+\ldots+f_l < e_j$ for all $j\in\{1,\ldots,r\}$, since $f_1=\ldots=f_l=0$ and $e_j \neq 0$ on $\tau$.
-In particular, if $\sqC_1$ is degenerate and if $\delta$ denotes the minimal distance from the circuit to a non-contracted vertex of $\sqC_1$ (which certainly exists since $\sqC_1$ has positive degree) then $\delta < e_1 \leq \lambda(\sqC^\prime)$, as claimed.\end{proof}
+In particular, if $\sqC_1$ is degenerate and if $\delta$ denotes the minimal distance from the core to a non-contracted vertex of $\sqC_1$ (which certainly exists since $\sqC_1$ has positive degree) then $\delta < e_1 \leq \lambda(\sqC^\prime)$, as claimed.\end{proof}
 
@@
 Now suppose $\Delta$ is of type $B$.
-Note that in this case, it is impossible for the circuit to be contracted.
+Note that in this case, it is impossible for the core to be contracted.
 Hence $\Ecal$ is disjoint from the blown-up locus, and the map $\Dcal \to \Ecal$ is an isomorphism.
@@
 Here the first factor in the fibre product is the logarithmic blow-up of the moduli space of rubber maps constructed in \S \ref{}.
-We will compute integrals over such spaces as part of the recursion (see \S \ref{section recursion algorithm}).
+We will compute integrals over such spaces as part of the recursion (see \S \ref{section recursion algorithm}).\footnote{(Navid) Say something about reduced rubber for target spaces here?}
 
@@
 Thus we conclude that the index is equal to $\lcm(m_1,\ldots,m_r)$ as claimed.\end{proof}
+
+\begin{remark} A similar line bundle and section is considered in \cite{Ga} in the genus zero setting.
+The computation of $\lambda_{\Dcal}$ is the most difficult technical part of that paper.
+One of our contributions here is to observe that the tropical description reduces this computation to simple combinatorics.\end{remark}
+
 In summary, then: the contribution of each term $\lambda_\Dcal [\Dcal]$ is given by integrating over the appropriate fibre product and then multiplying the result by $\lambda_\Dcal \cdot \deg\rho = \prod_{i=1}^r m_i$.
 
-\subsection{Recursive description of the divisors: type $C^0$} In this case, the core has (horizontal) degree $0$ and is mapped into $H$.
-We start by describing the relevant combinatorial types of rays in $\widetilde{\VZ}_{1,\alpha}(\PP^N|H,d)$.
-\begin{lemma} In what follows it is understood that we insert trivial bubbles whenever the curve or target need to be subdivided in order for the image and preimage of every polyhedral subcomplex to be a union of polyhedral subcomplexes.
- \begin{enumerate}
-  \item The core is represented by a single vertex of genus one and degree zero, tropically mapped to $\RR_{>0}$.
-  \item The vertices adjacent to the core with maximal expansion factor are tropically mapped to $0$.
-  \item For every point of the target different from $0$, the fiber of the tropical map contains at most one stable vertex, which either is the core or lies on the circle.
-  \item $x_k$ is supported by a vertex tropically mapped to $\RR_{>0}$.
- \end{enumerate}
+\subsection{Recursive description of the divisors: type $C^0$}
+
+\subsubsection{Restricting the possible combinatorial types} Recall that a boundary divisor $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ is said to be of \textbf{type $C^0$} if the core is assigned zero degree by the combinatorial type.
+In this case, the combinatorial type is not as tightly constrained as previously (it need not be a bipartite graph with a single interior vertex).
+Nevertheless, we have the following lemma:
+\begin{lemma} 
+Let $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ be a locus of type $C^0$ and let $\Delta$ be the corresponding combinatorial type.
+Then for every nonzero vertex $\diamond$ of the expanded target, the fibre of the tropical map over $\diamond$ contains exactly one stable vertex (together with a number of trivial bubbles), and at least one vertex which lies on the radius (which may or may not be stable).
 \end{lemma}
 \begin{proof}
- By assumption, the core is mapped to $\RR_>0$, hence the distance of its image from $0$ is one parameter $\ell$; since we are describing a ray, all other parameters have to be related to $\ell$, and the only way it can be so is via the alignment.
-If the fiber over $c>0$ contains two stable vertices, because both the insertions and the factorisation condition are pulled back from the moduli space without expansions, it can be seen as in Lemma \ref{lem:combs} that the collapsing morphism $\Dcal\to\Fcal$ has positive-dimensional fibers (disconnected rubber), so the corresponding combinatorial type does not contribute to the invariants.
-We conclude that every stable vertex over $\RR_{>0}$ different from the core has to lie on the circle.
-\end{proof}
+By stability we always need at least one stable vertex lying over each  vertex of the target.
+If there was more than one, then (since both the insertions and the factorisation condition are pulled back from the moduli space of maps without expansions) it can be seen, as in the proof of Lemma \ref{lem:combs}, that the contribution vanishes.
+
+Furthermore, for each vertex of the target there must always be a vertex in the preimage which lies on the radius, since otherwise there would be at least two independent tropical parameters, and so $\Dcal$ would not be a divisor.\end{proof}
+
+%%%%%%%%
+\begin{comment}
 \begin{center}
@@
 \end{center}
-
-See Figure \ref{fig:ray_example}.
-We observe that the corresponding stratum $\Ecal$ of $\ol\Mcal_{1,\alpha}(\PP^N|H,d)$ has logarithmic codimension equal to the number of non-core vertices mapping to $\RR_{>0}$: indeed, the combinatorial type of $\Ecal$ can be read off by forgetting the circle, and the logarithmic codimension in $\ol\Mcal_{1,\alpha}(\PP^N|H,d)$ is accounted for by the number of subdivisions of the target.
-The discrepancy in dimension is to be expected, as the loci of type $C^0$ are contained in the exceptional locus of the blow-up.
-
+\end{comment}
+%%%%%%%%%%
+
+We observe that the cone $\sigma \in \Sigma^{\Kim}$ corresponding to the stratum $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$ is isomorphic to $\N^r$ where $r$ is the number of target expansions.
+The discrepancy between the dimension of $\sigma$ and the dimension of the ray $\tau$ is to be expected, since the loci of type $C^0$ are contained in the exceptional locus of the blow-up.
+
+We write $\Delta_0$ for the collection of stable vertices of the combinatorial type which are mapped to $0$ by the tropical map, and $\Delta_{>0}$ for the stable vertices which are mapped to $\RR_{>0}$.
+For each vertex $v$ there is associated discrete data $\Gamma_v$, which defines a moduli space of relative stable maps if $v \in \Delta_0$ and a moduli space of rubber maps if $v \in \Delta_{>0}$.
+Then $\Ecal$ admits a finite splitting morphism onto the fibre product
+\begin{equation*} \Ecal \xrightarrow{\rho} \left( \prod_{v \in \Delta_0} \ol\Mcal_{\Gamma_v}(\PP^N|H) \times \prod_{v \in \Delta_{>0}} \ol\Mcal^{\leftrightarrow}_{\Gamma_v}(P|H_0+H_\infty) \right) \times_{H^{2E}} H^E \end{equation*}
+where $E$ is the number of edges of the (stabilised) dual graph, and the fibre product is taken over the appropriate evaluation maps.
+Note that only the factor corresponding to the core vertex has non-zero genus, and that it must have zero degree.
+
+\begin{remark}As in \S \ref{subsubsection splitting degree} above, we should calculate the degree of $\rho$ and the vanishing order $\lambda_{\Dcal}$ of the section $s_k$ along $\Dcal$.
+The degree of $\rho$ is given exactly as in Lemma \ref{lem:saturation}, where now we obtain one such factor for each bounded edge of the tropical target.
+The vanishing order $\lambda_{\Dcal}$ is slightly more delicate, but may be computed as the index of an explicit morphism of one-dimensional lattices, as explained in the proof of Lemma \ref{lemma vanishing order} above.
+\end{remark}
+
+Typically, $\Ecal$ will have true dimension larger than that of $\Dcal$.
+We will study the map $\Dcal \to \Ecal$ in two steps: first, we will describe the map $\widetilde\Dcal \to \Ecal$, and then we will explain how to express the class of the substack $\Dcal \subseteq \widetilde\Dcal$ in terms of tautological classes.
+
+\subsubsection{Constructing $\widetilde\Dcal$ from $\Ecal$}
 The geometry of $\widetilde\Dcal\to\Ecal$ is encoded by the combinatorics of the alignment.
@@
 We proceed to describe $\Dcal$ step-by-step, building on $\Ecal$.
-
-\subsubsection{The fiber product} We start from the finite splitting morphism
-\begin{multline}\label{eq:product}
- \rho\colon \Ecal \to \left(\prod_{i=1}^k \ol\Mcal_{0,\alpha^{(i)}\cup(m)}(\PP^N|H,d_i) \times \prod_{i=k+1}^s \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i)\right)\times_{H^s} \\ \prod_{j=k+1}^{r}\ol\Mcal_{0,\alpha^{(j)}\cup(-m_i)_{i \in I_j\subseteq\{k+1,\ldots,s\}}\cup(\mu_j)}^{\leftrightarrow}(P|H_0+H_\infty,d_j)\times_{H^{r-k}} \\
- \ol\Mcal_{1,\alpha^{(0)}\cup(-m,\ldots,-m,-\mu_{k+1},\ldots,-\mu_r)\cup(-m_i)_{i\in\{k+1,\ldots,s\}\setminus(\bigcup I_j)}}^{\leftrightarrow}(P|H_0+H_\infty,0)
-\end{multline}
-The degree of $\rho$ can be computed as in Lemma \ref{lem:saturation} above.
-From the logarithmic point of view, $\rho$ is a saturation map; generically it should be thought of as follows.
-On the fiber product, the tangent vectors of the components on level $0$ (corresponding to the factors in the first line above) are identified with the target tangent line up to finite powers; the saturation is taking roots of these isomorphisms (it is interesting to notice that it fails precisely on Gathmann's boundary comb loci).
 
@@
 We can obtain a line bundle $\mathbb T_R$ accounting only for the behaviour of the rational side of the fiber product by twisting $\OO(\delta)$ with $\mathbb L_E$.
+
+%%%%%%%%%%%%%
+\begin{comment}
 \begin{figure}
@@
 \end{figure}
+\end{comment}
+%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%
+\begin{comment}
 \begin{figure}
@@
 \end{figure}
-
-\subsubsection{Factorisation} Assume $m\geq 2$. Over $\mathcal P$ we have a tautological sequence:
+\end{comment}
+%%%%%%%%%%%%%
+
+\subsubsection{Factorisation: obtaining $\Dcal$ from $\widetilde\Dcal$} Assume $m\geq 2$. Over $\mathcal P$ we have a tautological sequence:
 \[\OO_{F}(-1)\hookrightarrow p^*(F)\xrightarrow{+\operatorname{d}f}\operatorname{ev}_E^*(TH),\]
@@
 See Figure \ref{fig:principalisation} above.
+
+%%%%%%%%%%%%%%%
+\begin{comment}
 \begin{figure}
@@
 \end{figure}
+\end{comment}
+%%%%%%%%%%%%%%%%
 
@@
 \end{cor}
-
-\newpage
-
-\begin{lem} The logarithmic modification $\psi$ restricts to a birational map:
-\begin{equation*}\VZ^{\operatorname{punct}}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(H,d) \to \ol\Mcal^{\operatorname{punct},\circ}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(H,d).\end{equation*}
-\end{lem}
-Note that the latter space (the main component of the moduli space of punctured maps) is birational to the main component of the double ramification locus.
-In Lemma \ref{Lemma forget marking} below we explain how to compute integrals over this.cd
-\begin{proof}
-If it is true, we might be able to prove it via deformation theory.
-For this it might be useful to notice that there is a morphism $\Mpunct{g}{\alpha}{H}{d}\to \Mpunct{g}{\alpha}{\PP^N}{d}$ (because $H\subseteq\PP^N$ is strict), which is probably a closed immersion, and the loci with smooth source curve are isomorphic under this map.
-It seems plausible that the main omponent is log smooth over $B\Gm\subseteq[\Aaff^1/\Gm]$ (or the standard log point).
-\end{proof}
-
-%We probably want the latter statement to hold under imposing alignment and factorisation (keeping the log structure on the source curve, but forgetting that the map is log).
-Integrals over the main component of the double ramification locus can be computed using the following lemma.
-\begin{lem} \label{Lemma forget marking}The morphism which forgets a marking
-\begin{equation*} \fgt_i\colon\ol\Mcal_{1,n}^{\alpha,\circ}(H,d)\to\ol\Mcal^{\circ}_{1,n-1}(H,d)\end{equation*}
-is generically finite, of degree $\alpha_i^2$ (except in one special case, described in the proof).
-\end{lem}
-\begin{proof}
- Let us consider the case $d=0$ first.
-We may assume the source curve is smooth elliptic $E$.
-The map \[ \phi\colon E\to \Pic^0(E),\qquad x\mapsto\OO_E\left(\alpha_ix+\sum_{j=1,\ldots,\hat i\ldots,n}\alpha_jp_j\right)\]
- is an isogeny of degree $\alpha_i^2$.
-The locus of $(C,p_1,\ldots,\hat{p_i},\ldots,p_n)$ such that the kernel of $\phi$ contains one of the points $\{p_1,\ldots,\hat{p_i},\ldots,p_n\}$ is itself a double ramification locus inside $\oM_{1,n}$, hence non-generic - with one exception: namely, when $n=2$, $x=p_1$ is always a solution, but the curve lying above such point bubbles off a $\PP^1$.
-To see that it does not belong to the closure of the nice locus, notice that the rational function trivialising $\OO_C(\alpha_1p_1-\alpha_2p_2)$ should descend to the cusp, thus having a ramification point at the node; yet its ramification profile is determined by Riemann-Hurwitz, and it is entirely supported on $p_1$ and $p_2$.
-
- For a different proof: notice that we should obtain the class of the main component from the full double ramification cycle by subtracting the boundary class $[D_{1,\emptyset|0,\{1,\ldots,n\}}]$.
-The latter pushes forward to $0$ under $\fgt_i$, unless $n=2$.
-Therefore we may apply $\fgt_{i,*}$ to the Hain-Pixton formula:
- \[DR_1(A)=\frac{1}{2}\left(\sum_{i=1}^na_i^2\psi_i-\sum_{\substack{I\subseteq\{1,\ldots,n\}\\|I|\geq 2}}a_I^2[D_{1,I^c|0,I}]-\frac{1}{12}\delta_0\right),\]
- where $a_I=\sum_{i\in I}a_i$ and $\delta_0=\operatorname{glue}_*([\oM_{0,n+2}])$.
-From $\psi_j=\fgt_i^\st\psi_j+[D_{i,j}]$ for $i\neq j$, and the dilaton equation, we see that $\fgt_{i,*}\psi_j=1$ and $\fgt_{i,*}\psi_i=n-1$.
-On the other hand, the only surviving boundary classes are $[D_{i,j}]$, and they push down to $1$.
-Hence the formula pushes down to $\frac{1}{2}\left(\sum_{j\neq i}\alpha_j^2+(n-1)\alpha_i^2-\sum_{j\neq i}(\alpha_j+\alpha_i)^2\right)=-\alpha_i\left(\sum_{j\neq i}\alpha_j\right)=\alpha_i^2.$
-\end{proof}
-
-\newpage
-
-\begin{definition} A combinatorial type $\Delta$ of a tropical curve consists of the following data:
-\begin{enumerate}
-\item $G$ a finite graph, with a set $V(G)$ of vertices, a set $F(G)$ of flags and an involution $\iota \colon F(G) \to F(G)$ with $\iota^2=\Id$.
-We let $L(G)$ denote the fixed set of $\iota$, and think of its elements as infinite legs; we let $E(G)$ denote the set of equivalence classes of elements not fixed by $\iota$, and think of them as finite edges connecting two (possibly equal) vertices of $G$;
-\item a genus assignment $g \colon V(G) \to \Z_{\geq 0}$;
-\item a degree assignment $\deg \colon V(G) \to \Z_{\geq 0}$;
-\item a weight assignment $u \colon F(G)  \to \Z$ such that for every edge $e \in E(G)$ we have $u(f_1)=-u(f_2)$ where $e=[f_1]=[f_2]$, and $u(l) \geq 0$ for any $l \in L(G)$;
-\end{enumerate}
-\end{definition}
-
-\footnote{(Luca) to be made homogeneous with what comes earlier} Review here the process of gluing for punctured maps.
-In particular the basic monoid should be modified in order to make the relevant evaluations log morphisms.
-Claim: evaluations are strict.
-Consequence: the fiber product in the category of log stacks is fine.
-We have then to apply saturation.
-This is a finite morphism of degree...
-(I think it could be $\frac{\prod m^{(i)}}{lcm(m^{(i)})}$).
-
-\begin{lemma}[Virtual pushforward] The following hold.
- \begin{itemize}
-  \item $\fgt_*[\M{0}{\alpha}{\PP^N|H}{d}]=[\MG{0}{\alpha}{\PP^N|H}{d}]$ (follows from \cite{GathmannThesis,AbramovichMarcusWiseComparison}).
-  \item $\fgt_*[\VZc{1}{\alpha}{\PP^N|H}{d}]$ computes the reduced relative invariants by definition.
-  \item $\fgt_*[\M{0}{\mu}{H}{d_0}^\sim]=[\M{0}{\lvert\mu\rvert}{H}{d_0}]$ (follows from \cite{GathmannThesis} and... comparison of punctured with rubber invariants).
-  \item $\fgt_*[\VZc{1}{\mu}{H}{d_0}^\sim]$ here we should need a variation on Pixton's DRC formula; hopefully it's enough to avoid the graphs that tropical well-spacedness discards.
- \end{itemize}
-\end{lemma}
-
-\subsection{Recursive description of the divisors: type $C_0$} Consider now a combinatorial type $\Delta$ such that the circuit is contracted into the divisor.
-The corresponding stratum $\Dcal_\Mcal \subseteq \Mcal$ is contained in the blown-up locus.
-Our task is to identify the logarithmic divisors in the preimage of $\Dcal_\Mcal$ under the map $\VZ \to \Mcal$.
-As discussed, these are indexed by choices of ray in the subdivision of the tropical moduli space.
-Suppose we have fixed such data.
-
-\begin{claim} The teeth of the comb can break at most once, along the circuit.\end{claim}
-
-\begin{proof} If not there would be more parameters in the tropical moduli space. \end{proof}
-
-\begin{prop} Let $\Delta$ be a combinatorial type as above. Then:
-\begin{enumerate}
-\item the circuit is a single vertex, and is mapped to the interior $\RR_{>0} \subseteq \RR_{\geq 0}$;
-\item the degree of the circuit is zero;
-\item there is a vertex which is adjacent to the circuit and mapped to the interior $0 \in \RR_{\geq 0}$;
-\item let $e \in E(\sqC)$ be an edge which is adjacent to the circuit, and such that $u(e)$ is maximal among the edges adjacent to the circuit.
-Then the other vertex $v$ contained in $e$ is mapped to $0 \in \RR_{\geq 0}$, and $v$ lies on the (absolute) radius;
-\item if $v \in V(\sqC)$ and $\lambda(v) > \delta$ then $f(v)=0$.
-\end{enumerate}
-\end{prop}
-
-On the other hand, when there is a contracted elliptic subcurve - and it will be contracted into the hyperplane, because otherwise it wouldn't be generic, by density of the nice locus in $\VZ_{1,\alpha^\prime}(\PP^N|H,d^\prime)$ - the picture becomes more complicated due to the alignment.
-The combs may break.
-We label these loci $\mathcal{Y}_C^0$.
-\begin{figure}
-
- \tikz{
- \draw[red] (2,0) circle(2); %circle
- \draw (0,0) circle(2pt)[fill=black] (0,2) circle(2pt)[fill=black] (0,4) circle(2pt)[fill=black] (0,6) circle(2pt)[fill=black] (0,-2) circle(2pt)[fill=black] (1.1,1.78) circle(2pt)[fill=black] (3.42,1.42) circle(2pt)[fill=black] (.58,-1.42) circle(2pt)[fill=black] (0,1) circle(2pt)[fill=black]; %black vertices
- \draw (2,0) -- node[above]{4} (0,0) (2,0) --node[above]{2} (1.1,1.78) --node[above]{1} (0,2) (1.1,1.78) --node[above]{1} (0,4) (2,0) --node[above]{1} (3.42,1.42) (2,0) --node[above]{3} (.58,-1.42) (3.42,1.42) --node[above]{5} (0,6) (.58,-1.42) --node[above]{1} (0,-2) (2,0) -- node[above]{2} (0,1); %edges
- \draw (.58,-1.42) -- (5,-1.42) node[right]{1} (3.42,1.42) -- (5,1.42) node[right]{2} (2,0) -- (5,.5) node[right]{3} (2,0) -- (5,-.5) node[right]{7}; %markings
- \draw (2,0) circle(2pt)[fill=white]; %core
- \draw[->] (0,-3) circle(2pt)[fill=black] edge (5,-3); %trop(P^N|H)
- }
-
- \caption{The degrees can be figured out from the balancing equation.}
-\end{figure}
-
-In the following we describe the rays of the tropical moduli space.
-\begin{lem}
- A one-parameter tropical map $\phi$ to $\mathbb R_{\geq 0}$ is a decorated tree (with expansion factors - \emph{contact orders} - along edges and legs, and degrees on vertices, satisfying the balancing condition) with a circle (of radius $\delta$) around the root (sometimes called the \emph{core} and denoted by $\circ$) satisfying:
- \begin{enumerate}
- \item the circle of radius $\delta$ passes through at least one vertex of $\phi^{-1}(0)$ - which necessarily has positive degree - call $m$ its contact order with $H$;
- \item teeth may break only when they intersect the circle of radius $\delta$; in particular, $\circ$ is the only vertex contained in its strict interior, and every edge heading out from the circle goes directly to a vertex of $\phi^{-1}(0)$;
- \item every tooth that starts with contact order $m$ goes directly to a vertex of $\operatorname{circle}(\circ,\delta)\cap\phi^{-1}(0)$, and every other tooth starts with contact order $<m$ (possibly negative).
- \end{enumerate}
-\end{lem}
-\begin{proof}
- Otherwise there would be more than one parameters.
-\end{proof}
-
-\begin{remark}
- The core being contracted in the fiber of the tropical map is not a phenomenon that we should worry about in codimension one.
-Indeed, assume that the core is contracted in the fiber along a ray.
-Then all the edges departing from the core have expansion factor $0$; call the corresponding coordinates $U=\{u_i\}_{i\in I}$.
-Call the remaining coordinates $E=\{e_j\}_{j\in J}$.
-Note that tropical continuity involves only $E$.
-Alignments on the other hand assume the form $\lambda(v)=\lambda(v^\prime)$, where $\lambda(v)=\sum_{i\in I(v)}u_i\sum_{j\in J(v)}e_j$.
-Pick the shortest elements of $U$; then these can be shortened to zero without affecting the rest (by hypothesis, alignments can only identify them among themselves).
-This shows that we could not have started with a ray.
-\end{remark}
-
-\begin{ex}
- We look at the following example in some detail.
- \begin{figure}[h]
-  \tikz{
-  \draw (0,1) circle(2pt)[fill=black] --node[above]{2} (2,0);
-  \draw (0,-1) circle(2pt)[fill=black] --node[above]{2} (2,0);
-  \draw (2,0) -- (2.5,0) node[right]{4};
-  \draw (2,0)  circle(2pt)[fill=white];
-  \draw (0,1) -- (.33,1.33) node[above right]{0};
-  \draw (0,-1) -- (.33,-1.33) node[below right]{0};
-  \draw[red] (2,0) circle(2.23);
-  \draw[->] (0,-2.5)node[left]{0} circle(2pt)[fill=black] edge (4,-2.5);
-  }
- \end{figure}
- The ambient space is $\VZc{1}{(4,0,0)}{\PP^N|H}{4}$, of dimension $4N+3$.
-The underlying moduli space is $X=\M{0}{(2,0)}{\PP^N|H}{2}\times_H\M{0}{(2,0)}{\PP^N|H}{2}\times\VZ_{1,(-2,-2,4)}$ of dimension $5N+1$.
-Consider the fiber product:
- \bcd
- F\ar[r]\ar[d]& \M{0}{(2,0)}{\PP^N|H}{2}\times\M{0}{(2,0)}{\PP^N|H}{2}\ar[d]\\
- H\ar[r] & H\times H
- \ecd
- At the level of ghost sheaves, $\oM_F=\mathbb N\oplus_{\mathbb N^2}\oM_1^{\rm{enl}}\oplus\oM_2^{\rm{enl}}$, where the map $\mathbb N^2\to\mathbb N$ is the sum, and the map $\mathbb N^2\to\oM_1^{\rm{enl}}\oplus\oM_2^{\rm{enl}}$ generically is multiplication by $2$, so $\oM_F=\mathbb N^2/(2e=2f)$ generically.
-Saturation gives a finite cover $G\to F$ with $\oM_G=\mathbb N_{e=f}$ generically.
-Lifting this to actual log structures, what we are doing (again generically) is taking a square root of the isomorphism $T_{R_1,q_1}^{\otimes 2}\simeq T_{R_2,q_2}^{\otimes 2}$, which is obtained passing through $N_{H/\PP^N,f(Z)}$ via $\operatorname{d}f_{|R_i,q_i}$.
-This breaks when $f_{|R_i}$ is not tangent to $H$ of order exactly $2$ at $q_i$, for either $i$; but by the maximality assumption this happens precisely along Gathmann's comb loci $\Delta_i$.
-So in fact, rather than with $T_{R_i,q_i}^{\otimes 2}$, we should be working with $T_{R_i,q_i}^{\otimes 2}(-\Delta_i)$: but this is exactly $\ev_i^\st(-H)$ by Gathmann's genus zero formula, and the isomorphism $\ev_1^\st(H)=\ev_2^\st(H)$ holds on all of $F$.
-
- On the other hand, generically on $\VZ_{1,(-2,-2,4)}$ we have $T_{q_1}Z\simeq T_{q_2}Z$ by exploiting the group structure on the elliptic curve.
-This breaks when either (but not both) is on a rational tail.
-Yet we have $T_{q_1}Z(\Delta_{1\in P})\simeq T_{q_2}Z(\Delta_{2\in P})$ by Vakil-Zinger's construction of a universal $\psi$-class (i.e.
-by comparing both with $\pi_*\omega(\Delta)$; notice that our further blow-up has the only effect of twisting \emph{all} the relevant line bundles by $\Delta_{1,2\notin P}$).
-
- Now, the fiber of the Vakil-Zinger blow-up over $X$ can be described as follows. Generically it looks like \[\PP(T_{q_1}R_1\otimes T_{q_1}Z\oplus T_{q_2}R_2\otimes T_{q_2}Z)\]
- but this has to be modified along the boundary:
- \begin{itemize}
-  \item this has to do with the fact that the normal bundle of the strict transform is the pullback of the normal bundle twisted by the intersection with the exceptional divisor (so it relates with previous steps of the blow-up);
-  \item it is not globally a $\PP^1$-bundle (so it relates with further stages of the blow-up; it also has to do with a choice of compactification for the moduli space of attachments);
-  \item it has the effect of replacing $T_{q_i}Z$ with Vakil-Zinger's universal $\mathbb T$, so that this can be factored out of the projective bundle, and in fact we are left with a projective bundle $\mathbb P=\PP(T_{q_1}R_1\oplus T_{q_2}R_2)$ over $F$, and its open part $\operatorname{Iso}(T_{q_1}R_1\oplus T_{q_2}R_2)$ represents the attachment data for a contraction to a tacnode $R_1\sqcup_q R_2\to\bar{C}$.
- \end{itemize}
-On $\PP$ there is a natural vector bundle map \[s\colon \OO_{\PP}(-1)\hookrightarrow p^\st(T_{q_1}R_1\oplus T_{q_2}R_2)\xrightarrow{+\operatorname{d}f}\ev_q^\st T\PP^N\]
-that vanishes along the locus where $f$ descends to $\bar C$. In general, it is not a transversal section:
-\begin{itemize}
- \item we should replace $T\PP^N$ by $TH$ as long as all the $m^{(i)}$ are $\geq2$;
- \item Vakil and Zinger construct a blow-up of $\PP$ along the vanishing loci of $s$ of low codimension, and twist $s$ by the exceptional divisors, so that it becomes a transverse section $\tilde{s}$.
-\end{itemize}
-On the other hand, the finite cover $G\to F$ factors through $\PP$, because the two vertices are already aligned on $G$.
-We claim that the boundary locus of $\VZc{1}{(4,0,0)}{\PP^N|H}{4}$ corresponding to the combinatorial type of the tropical map above is the transverse intersection
-\[\left(G\cap V(\tilde{s})\subseteq\PP\right)\times\VZ_{1,(-2,-2,4)}.\]
-This has the expected dimension (codimension $N-1$ with respect to $X$).
-To compute its class, we can pull $\PP$ back to $G$, and then notice that $G\hookrightarrow\PP_G$ is the inclusion of a (trivial) subbundle.
-\begin{lem}
- The class of $\PP(\mathcal F)\subseteq\PP(\mathcal E)$ is $c_{\rm{top}}(\OO_\mathcal{E}(1)\otimes p^\st(\mathcal{E}/\mathcal{F}))$.
-\end{lem}
-See \cite[Prop.
-9.13]{EH3264}.
-It is a good time to remember that $\mathcal E$ was in fact $(\bigoplus_{i=1}^rTR_{i,q_i})\otimes\mathbb T$.
-By writing $c$ for $c_1(\OO_\mathcal{E}(1))$, $\psi_i$ for $c_1(T^\st R_{i,q_i})$, $\psi_Z$ for Vakil-Zinger's universal psi class, and $H$ for $\ev_q^\st H$, we need to compute
-\begin{align*}
-p_*\left((c-\psi_1-\psi_2-2\psi_Z)[(1+c+H)^N(1+c)^{-1}]_{N-1}\right)= \\
-p_*\left((c-\psi_1-\psi_2-2\psi_Z)(\sum_{k=0}^{N-1}\binom{N}{1+k}c^kH^{N-1-k})\right)=\\
-\sum_{k=0}^{N-1}\binom{N}{k}H^{N-1-k}\big(s_k(\mathcal E)-s_{k-1}(\mathcal E)(\psi_1+\psi_2+\psi_Z)\big)
-\end{align*}
-\end{ex}
-
-We now generalise this picture.
-Recall that the map $C\to\bar C$ is given by a (generic) line in the sum of the tangent spaces to the rational tails at the nodes that join them to the contracted curve of genus one.
-This is equivalent to an alignment, and it is parametrised by an open subset of a projective bundle over the moduli space for the tails corresponding to vertices of the dual graph lying on the circle of radius $\delta$.
-Yet, notice that those vertices lying in $\phi^{-1}(0)$ are already aligned among themselves.
-This is why we find it convenient to distinguish among four groups of vertices:
-\begin{enumerate}
- \item the core;
- \item\label{specialvertices} vertices on $\phi^{-1}(0)\cap\operatorname{circle}(\circ,\delta)$;
- \item vertices on $\operatorname{circle}(\circ,\delta)\setminus\phi^{-1}(0)$;
- \item\label{boringvertices} vertices on $\phi^{-1}(0)\setminus\operatorname{circle}(\circ,\delta)$.
-\end{enumerate}
-We shall first argue that gluing of log maps can be performed separately for the exterior and interior of the circle (the analogous classical picture is that, since the core is contracted, this moduli space is the product of a genus one curve, and a fiber product of genus zero maps under evaluation morphisms).
-
-\begin{lem}
- $\VZ^{\operatorname{punct}}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(H,0)\simeq \VZ^{\operatorname{punct}}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(\Spec(k\oplus\mathbb N))\times H$.\footnote{(Luca) check log structure, could be fibered over std log point}
-\end{lem}
-
-Let us now deal with vertices of type \ref{specialvertices}.
-\begin{lem}
- Consider the following fiber product in the category of fs log stacks:
- \bcd
- F\ar[d]\ar[r] & \prod_{i=1}^r\M{0}{\alpha^{(i)}\cup\{ m\}}{\PP^N|H}{d_i}\ar[d,"\ev_{q_i}"]\\
- H\ar[r] & H^r
- \ecd
- On $F$ there is a canonical isomorphism $\mathbb L_{q_i}\cong\mathbb L_{q_j}$\footnote{(Luca) check how it degenerates}, the latter being the cotangent line bundles at the gluing markings on two different components $i$ and $j$.
-Furthermore, $\underline F$ is a finite cover of degree $m^{r-1}$ of the fiber product of the underlying stacks.
-\end{lem}
-\begin{proof}
- Recall that each $\M{0}{\alpha^{(i)}\cup\{ m\}}{\PP^N|H}{d_i}$ is endowed with the log structure induced by pulling back along $q_i$ the divisorial log structure of the universal curve at the image of $q_i$ itself.
-Thus $\ev_{q_i}$ is made into a log morphism to $H$ with its induced DF(1) log structure.
-We claim that the subtext of such morphism is Gathmann's formula; namely, the log morphism to $H$ corresponds to an isomorphism betwee $\ev_{q_i}^\st\OO_H(-H)$ on one side, and $\mathcal I_{D_i}\otimes\mathbb L_{q_i}^m$ on the other, where $\mathcal I_{D_i}$ is the ideal sheaf of the union of the comb loci $D_i$ in $\M{0}{\alpha^{(i)}\cup\{ m\}}{\PP^N|H}{d_i}$.
-
- On the fiber product there is a canonical isomorphism between $\ev_{q_i}^\st H$ and $\ev_{q_j}^\st H$.
-
- Say something about integrality.
-
- Saturation is a local operation, as much as computing the degree, hence we can concentrate on the dense open locus where all the curves we are gluing are smooth, and they are not mapped entirely into $H$.
-There the minimal log structure on $\M{0}{\alpha^{(i)}\cup\{ m\}}{\PP^N|H}{d_i}$ is trivial, therefore the isomorphism between $\ev_{q_i}^\st H$ and $\ev_{q_j}^\st H$ translates into an isomorphism $\mathbb L_{q_i}^m\cong \mathbb L_{q_j}^m$.
-The saturation $F$ is obtained by taking an $m$-th root of this isomorphism.
-\end{proof}
-Let us denote by $\mathbb L_F$ the universal cotangent line at $q$.
-
-The projective bundle we are seeking has base
-\[\mathcal X=\left(F\times \prod_{i=1}^s\oM_{0,\tilde\alpha^{(i)}\cup\{m_i\}}^{\rm{punct}}(H,\tilde d_i)\right)\times_{H^{s+1}}H\]
-(with $m_i<m$) and it is \[\PP=\Proj_{\mathcal X}\left(\mathbb T_F\oplus\bigoplus_{i=1}^s\mathbb T_{\tilde q_i}\right).\]
-We are interested in the vanishing locus of the section
-\[s\colon\OO_{\PP}(-1)\hookrightarrow p^\st\left(\mathbb T_F\oplus\bigoplus_{i=1}^s\mathbb T_{\tilde q_i}\right)\xrightarrow{+df_q} f^\st(\operatorname{T}\PP^N)_q,\]
-because it represents the geometric condition that $f\colon C\to \PP^N$ factors through the normalisation map $C\to\bar C$ prescribed by the given point of $\PP$.
-As is, $s$ is not transverse to the zero section.
-First of all, unless $m=1$, $\operatorname{T}\PP^N$ can be replaced by $\operatorname{T}H$ in the definition of $s$ above, because the projection of all $\operatorname{d}f_i(\operatorname{T}_{q_i}R_i)$ to $N_{H/\PP^N}$ is zero.
-The case $m=1$ has to be dealt with separately and it turns out that, once $s$ is made transverse, the dimension of its zero locus is smaller than the expected dimension, hence the corresponding combinatorial types are in fact irrelevant.
-
-The procedure to make $s$ transverse is the same as described in \cite[\S 3]{VZ}, namely we need to blow up inside $\PP$ the projective subbundle $\PP(\mathcal E)$ of $\PP_{|\mathcal X_\sigma}$, where $\mathcal X_\sigma$ is the closed substack of $\mathcal X$ where some of the tails degenerate so that the corresponding gluing marking lies on a component contracted by $f$, and $\mathcal E$ is the sum of the tangent line bundles at such subset of the gluing markings.
-Because $\oM_{0,\tilde\alpha^{(i)}\cup\{m_i\}}^{\rm{punct}}(H,\tilde d_i)$ is isomorphic to $\M{0}{\tilde n_i}{H}{d_i}$, the construction of Vakil and Zinger in the section ``A blowup of a moduli space of genus-zero maps'' of their paper carries through unchanged.
-The result of the blow-up is to replace $T_{q_i}R_i$ with $T_{q_i}R_i\otimes\bigoplus_{j=1}^kT_{\tilde q_j}R_i\otimes T_{\tilde q_j} S_{ij}$.
-We interpret this in terms of alignments.\footnote{(Luca) this has to be written properly}
-
-We claim that $\tilde s$ obtained from $s$ by twisting by the exceptional divisors of the blowup is a transverse section.
-We also claim that comb loci of type $\mathcal Y_c^0$ can be described as a fibered product of
-\begin{itemize}
- \item moduli of genus one punctured maps to the standard log point, radially aligned and satisfying factorisation;
- \item $V(\tilde s)$;
- \item moduli of genus zero maps relative to $(\PP^N|H)$, corresponding to vertices of type \ref{boringvertices} above.
-\end{itemize}
-Finally, we claim that integrals of psi and evaluation classes over these loci can be translated into tautological integrals, i.e.
-descendant Gromov--Witten invariants, whose numerics is governed by the combinatorial type of the tropical map.
 
@@
 If $C^\prime$ is mapped to top level, then either it contains $x_1$, in which case we apply $\fgt_1$ to compute the contribution, or it does not contains $x_1$, in which case it has fewer than $n$ relative markings and is known recursively.
-If on the other hand $C^\prime$ is not mapped to top level, then generically it is mapped to the bottom level (since generically the circuit is not contracted on this locus, so the desingularisation process does nothing).
+If on the other hand $C^\prime$ is not mapped to top level, then generically it is mapped to the bottom level (since generically the core is not contracted on this locus, so the desingularisation process does nothing).
 One possible contribution is given by the following locus

### 2019-06-25 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
started Yc0 revision/expansion

--- 2019-06-08 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
@@
 
-\subsection{Recursive description of the divisors: type $C^0$} In this case, the core has (horizontal) degree $0$ and is mapped into $H$.
-We start by describing the relevant combinatorial types of rays in $\widetilde{\VZ}_{1,\alpha}(\PP^N|H,d)$.
+\subsection{Recursive description of the divisors: type $C^0$}
+
+\subsubsection{Combinatorial types} Recall that a boundary divisor $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ is said to be of \textbf{type $C^0$} if the core is assigned zero degree by the combinatorial type.
+In this case, the combinatorial type is not as tightly constrained as previously (it need not be a bipartite graph with a single interior vertex).
+Nevertheless, we have the following lemmas:
+\begin{lemma} 
+Let $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ be a locus of type $C^0$ and let $\Delta$ be the corresponding combinatorial type.
+Then for every nonzero vertex $\diamond$ of the expanded target, the fibre of the tropical map over $\diamond$ contains exactly one stable vertex (together with a number of trivial bubbles), and at least one vertex which lies on the circle (which may or may not be stable).
+\end{lemma}
+\begin{proof}
+By stability, we always need at least one stable vertex lying over each vertex of the target.
+If there was more than one, then (since both the insertions and the factorisation condition are pulled back from the moduli space of maps without expansions) it could be seen, as in the proof of Lemma \ref{lem:combs}, that the contribution would vanish.
+
+Furthermore, for each vertex of the target there must always be a vertex in the preimage which lies on the radius, since otherwise there would be at least two independent tropical parameters, and so $\Dcal$ would not be a divisor.\end{proof}
+
+\begin{lemma}
+ If, for any nonzero vertex $\diamond$ of the expanded target, the only stable vertex in $\phi^{-1}(\diamond)$ is not the core, nor it lies on the circle, then the corresponding combinatorial type $\Delta$ does not contribute to the invariants.
+\end{lemma}
+\begin{proof}
+ By the previous Lemma, there must be a vertex $v$ lying on the circle and over $\diamond$; such a vertex is strictly semistable by assumption, in particular the map $f$ is constant along the corresponding component, therefore the fact that the factorisation condition is satisfied is unaffected by $\Gm$-scaling the coordinate corresponding to $v$ in the moduli space of attachments.
+We deduce that the generic fiber of $\Dcal\to\Ecal$ has positive dimension.
+\end{proof}
+
+%%%%%%%%
+\begin{center}
+\begin{figure}
+ \begin{tikzpicture}[ipe import]
+  %\useasboundingbox (0, 0) rectangle (595, 842);
+  \draw
+    (64, 672)
+     -- (128, 688)
+     -- (64, 704)
+     -- (64, 704);
+  \draw
+    (128, 688)
+     -- (64, 736)
+     -- (64, 736);
+  \draw[red]
+    (128, 688) circle[radius=65.9697];
+  \draw
+    (128, 688)
+     -- (112, 752)
+     -- (64, 768)
+     -- (64, 768);
+  \draw
+    (112, 752)
+     -- (64, 784)
+     -- (64, 784);
+  \pic
+     at (64, 672) {ipe disk};
+  \pic
+     at (64, 704) {ipe disk};
+  \pic
+     at (64, 736) {ipe disk};
+  \pic
+     at (64, 768) {ipe disk};
+  \pic
+     at (64, 784) {ipe disk};
+  \pic
+     at (112, 752) {ipe disk};
+  \pic
+     at (75.2242, 727.5818) {ipe cross};
+  \pic
+     at (112, 700) {ipe cross};
+  \pic
+     at (112, 692) {ipe cross};
+  \pic
+     at (112, 684) {ipe cross};
+  \pic
+     at (75.8121, 701.047) {ipe cross};
+  \pic
+     at (75.0705, 674.4385) {ipe cross};
+  \filldraw[fill=white,->]
+    (64, 608)
+     -- (208, 608);
+  \pic
+     at (64, 608) {ipe disk};
+  \draw
+    (128, 688)
+     -- (208, 688);
+  \pic
+     at (73.6978, 608.0203) {ipe cross};
+  \pic
+     at (111.8758, 608.0203) {ipe cross};
+  \pic
+     at (127.6736, 608.0203) {ipe cross};
+  \pic[fill=white]
+     at (128, 688) {ipe fdisk};
+  \node[ipe node]
+     at (86.863, 690.301) {$m$};
+  \node[ipe node]
+     at (87.521, 671.212) {$m$};
+  \node[ipe node]
+     at (48.026, 668.579) {$R_1$};
+  \node[ipe node]
+     at (48.026, 687.668) {$\ldots$};
+  \node[ipe node]
+     at (47.368, 700.832) {$R_k$};
+  \node[ipe node]
+     at (48.026, 725.846) {$R_{k+1}$};
+  \node[ipe node]
+     at (48.026, 784.429) {$R_s$};
+  \node[ipe node]
+     at (48.026, 766.657) {$\ldots$};
+  \node[ipe node]
+     at (108.585, 757.441) {$R_r$};
+  \node[ipe node]
+     at (80, 744.935) {$\ldots$};
+  \node[ipe node]
+     at (130.965, 677.794) {$E$};
+\end{tikzpicture}
+\caption{A ray of type $C^0$.}\label{fig:ray_example}
+\end{figure}
+\end{center}
+%%%%%%%%%%
+
+We observe that the cone $\sigma \in \Sigma^{\Kim}$ corresponding to the stratum $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$ is isomorphic to $\N^r$ where $r$ is the number of target expansions.
+The discrepancy between the dimension of $\sigma$ and the dimension of the ray $\tau$ is to be expected, since the loci of type $C^0$ are contained in the exceptional locus of the blow-up.
+
+We write $V_0$ for the collection of stable vertices of the combinatorial type which are mapped to $0$ by the tropical map, and $V_{>0}$ for the stable vertices which are mapped to $\RR_{>0}$.
+For each vertex $v$ there is associated discrete data $\Gamma_v$, which defines a moduli space of relative stable maps if $v \in V_0$ and a moduli space of rubber maps if $v \in V_{>0}$.
+Then $\Ecal$ admits a finite splitting morphism onto the fibre product
+\begin{equation*} \Ecal \xrightarrow{\rho} \left( \prod_{v \in V_0} \ol\Mcal_{\Gamma_v}(\PP^N|H) \times \prod_{v \in V_{>0}} \ol\Mcal^{\leftrightarrow}_{\Gamma_v}(P|H_0+H_\infty) \right) \times_{H^{2E}} H^E \end{equation*}
+where $E$ is the set of edges of the (stabilised) dual graph, and the fibre product is taken over the appropriate evaluation maps.
+Note that only the factor corresponding to the core vertex has non-zero genus, and that it must have zero degree.
+
+\begin{remark}As in \S \ref{subsubsection splitting degree} above, we should calculate the degree of $\rho$ and the vanishing order $\lambda_{\Dcal}$ of the section $s_k$ along $\Dcal$.
+The degree of $\rho$ is given exactly as in Lemma \ref{lem:saturation}, where now we obtain one such factor for each bounded edge of the tropical target.
+The vanishing order $\lambda_{\Dcal}$ is slightly more delicate, but may be computed as the index of an explicit morphism of one-dimensional lattices, as explained in the proof of Lemma \ref{lemma vanishing order}.
+\end{remark}
+
+Typically, $\Ecal$ will have true dimension larger than that of $\Dcal$.
+We will study the map $\Dcal \to \Ecal$ in two steps: first, we will describe the map $\widetilde\Dcal \to \Ecal$, and then we will explain how to express the class of the substack $\Dcal \subseteq \widetilde\Dcal$ in terms of tautological classes.
+
+\begin{comment}
+In this case, the core has (horizontal) degree $0$ and is mapped into $H$. We start by describing the relevant combinatorial types of rays in $\widetilde{\VZ}_{1,\alpha}(\PP^N|H,d)$.
 \begin{lemma} In what follows it is understood that we insert trivial bubbles whenever the curve or target need to be subdivided in order for the image and preimage of every polyhedral subcomplex to be a union of polyhedral subcomplexes.
@@
 On the fiber product, the tangent vectors of the components on level $0$ (corresponding to the factors in the first line above) are identified with the target tangent line up to finite powers; the saturation is taking roots of these isomorphisms (it is interesting to notice that it fails precisely on Gathmann's boundary comb loci).
-
+\end{comment}
+
+\subsubsection{From $\Ecal$ to $\widetilde{\Dcal}$} The reader should bear the following construction from toric geometry in mind: suppose we subdivide a fan, and we want to describe the relation between the varieties corresponding respectively to a cone $\rho$ of the subdivision, and the original cone $\sigma$ containing it.
+The fan of $X_\tau$ is obtained by projecting the star of $\tau$ to the quotient $N_\tau=N_{\RR}/\langle\tau\rangle_{\RR}$ of the ambient vector space by the linear span of the cone\footnote{We find it useful to encode this within the formalism of extended tropicalisations \cite{?}.}.
+Notice that the dimension of the vector spaces $N_\rho$ and $N_\sigma$ (or the corresponding toric varieties) is off by the difference $c$ between the dimension of the cones.
+The image of $\Sigma_\rho$ provides a subdivision of the fan of $X_\sigma$.
+The geometric content is that $X_\tau$ is obtained as an appropriate compactification of a toric bundle of dimension $c$ over $X_\sigma$.
+%observe that the fiber dimension may not be constant (but it can be made so by blowing up $X_{\sigma}$, see \cite[Lemma 4.1]{AK}).
+
+We start by describing the modification of $\Ecal$ corresponding to the subdivision of the last paragraph; really, we only need to unravel the combinatorics partially, in order to describe an intermediate blowup $\widetilde\Ecal\to \Ecal$, such that $\Dcal$ factors through $\widetilde\Ecal$, and all the structures that we need to name in what follows make sense on $\widetilde\Ecal$ already.
+
+Let $V_{0,\delta}\subseteq V_0$ be the subset of vertices lying on the circle (besides being sent to $0$ by the tropical map).
+Notice that they all have the same expansion factor $m$, therefore they are at the same distance from the core, generically on $\Ecal$.\footnote{Indeed, generically, these vertices do not contribute any subdivision of the target, i.e.
+they do not affect the relative dimension of $\widetilde\Dcal\to\Ecal$.} Another way to see the generic alignment is the following: the normal bundles corresponding to these nodes can be expressed as $\mathbb T_{R_v,q_v}\otimes\mathbb T_{E,q_v}$; for two different vertices, the right-hand factors are canonically identified thanks to the group structure on the elliptic curve, whereas the $m$-th powers of the left-hand factors are canonically identified by comparison with the target tangent line, and $\rho$ can be seen as taking an $m$-th root of this preferred isomophism.
+On the other hand, the alignment does not persist when the curves degenerate (see Figure \ref{fig:fwise_align}).
+
+\begin{figure}
+ \begin{tikzpicture}[ipe stylesheet,scale=.7]
+  %\useasboundingbox (0, 0) rectangle (595, 842);
+  \pic
+     at (129.8488, 703.2932) {ipe disk};
+  \pic
+     at (97.8488, 719.2932) {ipe disk};
+  \pic
+     at (97.8488, 687.2932) {ipe disk};
+  \draw
+    (97.8488, 719.2932)
+     -- (129.8488, 703.2932)
+     -- (97.8488, 687.2932);
+  \draw
+    (129.8488, 703.2932)
+     -- (161.8488, 687.2932);
+
+  \draw
+    (193.8488, 671.2932)
+     -- (225.8488, 655.2932);
+  \draw
+    (225.8488, 655.2932)
+     -- (193.8488, 639.2932);
+    \draw[ipe dash dashed]
+   (193.8488, 671)
+    -- (161.8488, 687);
+  \draw[ipe dash dashed]
+    (193.8488, 639.2932)
+     -- (161.8488, 623.2932);
+  \draw
+    (161.8488, 623.2932)
+     -- (129.8488, 607.2932);
+  \pic
+     at (146.637, 615.0615) {ipe disk};
+  \draw
+    (129.8488, 607.2932)
+     -- (97.8488, 591.2932)
+     -- (97.8488, 591.2932);
+  \draw
+    (147.2948, 615.0622)
+     -- (97.2686, 638.1002)
+     -- (97.2686, 638.1002);
+  \pic
+     at (96.6103, 637.4422) {ipe disk};
+  \pic
+     at (97.9268, 590.7072) {ipe disk};
+  \pic
+     at (130.1808, 622.9607) {ipe cross};
+  \pic
+     at (130.1808, 607.1635) {ipe cross};
+  \pic
+     at (145.9788, 695.3672) {ipe cross};
+  \draw[-ipe linear]
+    (97.8488, 575.2932)
+     -- (257.8488, 575.2932);
+  \pic
+     at (97.8488, 575.2932) {ipe disk};
+  \pic
+     at (129.8488, 575.2932) {ipe cross};
+  \pic
+     at (145.8488, 575.2932) {ipe cross};
+  \pic
+     at (225.8488, 575.2932) {ipe cross};
+  \draw
+    (129.8488, 703.2932)
+     -- (257.8488, 703.2932);
+  \draw
+    (225.8488, 655.2932)
+     -- (257.8488, 655.2932)
+     -- (257.8488, 655.2932);
+  \draw
+    (146.3018, 614.861)
+     -- (258.5378, 614.404);
+  \node[ipe node]
+     at (189.423, 676.278) {$m$};
+  \node[ipe node]
+     at (189.094, 629.543) {$m$};
+  \node[ipe node]
+     at (111.421, 715.773) {$m_1$};
+  \node[ipe node]
+     at (110.104, 590.707) {$m_2$};
+  \node[ipe node]
+     at (110.763, 564.378) {$\ell_1$};
+  \node[ipe node]
+     at (133.801, 564.377) {$\ell_2$};
+  \node[ipe node]
+     at (146.308, 543.972) {$\frac{\ell_1}{m_1}+\frac{\ell_2}{m} \lesseqgtr \frac{\ell_1+\ell_2}{m_2}$};
+  \pic
+     at (473.6651, 658.9228) {ipe disk};
+  \pic
+     at (353.8488, 719.2932) {ipe disk};
+  \pic
+     at (353.8488, 687.2932) {ipe disk};
+  \draw
+    (353.8488, 719.2932)
+     -- (385.8488, 703.2932)
+     -- (353.8488, 687.2932);
+  \draw
+    (386.7731, 703.2932)
+     -- (418.7731, 687.2932);
+  \draw[ipe dash dashed]
+    (417.8488, 687.2932)
+     -- (449.8488, 671.2932)
+     -- (449.8488, 671.2932);
+
+  \draw
+    (449.8488, 671.2932)
+     -- (481.8488, 655.2932)
+     -- (481.8488, 655.2932);
+  \draw
+    (481.8488, 655.2932)
+     -- (449.8488, 639.2932)
+     -- (449.8488, 639.2932);
+  \draw[ipe dash dashed]
+    (449.8488, 639.2932)
+     -- (417.8488, 623.2932);
+  \draw
+    (417.8488, 623.2932)
+     -- (385.8488, 607.2932);
+  \pic
+     at (457.1756, 642.7929) {ipe disk};
+  \draw
+    (385.8488, 607.2932)
+     -- (353.8488, 591.2932)
+     -- (353.8488, 591.2932);
+  \pic
+     at (352.6103, 622.6521) {ipe disk};
+  \pic
+     at (353.9268, 590.7072) {ipe disk};
+  \pic
+     at (458.2826, 667.3311) {ipe cross};
+  \pic
+     at (459.207, 575.7344) {ipe cross};
+  \draw[-ipe linear]
+    (353.8488, 575.2932)
+     -- (513.8488, 575.2932);
+  \pic
+     at (353.8488, 575.2932) {ipe disk};
+  \pic
+     at (385.8488, 575.2932) {ipe cross};
+  \pic
+     at (475.7994, 575.2932) {ipe cross};
+  \pic
+     at (481.8488, 575.2932) {ipe cross};
+  \draw[shift={(472.741, 659.847)}, xscale=0.3271, yscale=-1.7893]
+    (0, 0)
+     -- (128, 0);
+  \draw
+    (481.8488, 655.2932)
+     -- (513.8488, 655.2932)
+     -- (513.8488, 655.2932);
+  \draw[shift={(459.26, 642.878)}, xscale=0.4834, yscale=0.4807]
+    (0, 0)
+     -- (112.236, -0.457);
+  \draw[red]
+    (482.3765, 654.0394) circle[radius=9.9987];
+  \draw
+    (354.8117, 621.686)
+     -- (386.2407, 606.8958);
+  \pic
+     at (386.2407, 606.8958) {ipe disk};
+  \pic
+     at (386.2407, 703.956) {ipe disk};
+  \draw[red]
+    (360.3506, 584.6012)
+     arc[start angle=160.4967, end angle=217.0656, x radius=120.4239, y radius=-143.3401];
+  \pic
+     at (473.9974, 650.6919) {ipe cross};
+  \pic
+     at (364.92, 693.131) {ipe cross};
+  \pic
+     at (372.3151, 710.6943) {ipe cross};
+  \pic
+     at (359.3737, 593.2977) {ipe cross};
+  \draw
+    (226.3225, 655.8881)
+     -- (258.6759, 665.1319);
+  \draw
+    (226.3225, 654.0394)
+     -- (258.6759, 646.6443);
+  \draw[-ipe linear]
+    (271.6173, 766.814)
+     -- (337.2485, 767.7384);
+
+  \pic
+     at (272.5417, 782.5285) {ipe disk};
+  \pic
+     at (271.6173, 815.8063) {ipe disk};
+  \draw
+    (305.8194, 798.2431)
+     -- (272.5417, 815.8063);
+  \draw
+    (305.8194, 798.2431)
+     -- (272.5417, 782.5285)
+     -- (272.5417, 782.5285);
+  \draw
+    (272.5417, 782.5285)
+     -- (336.3241, 782.5285);
+  \draw
+    (272.5417, 815.8063)
+     -- (336.3241, 814.8819);
+  \draw
+    (304.8951, 799.1674)
+     -- (335.3997, 799.1674);
+  \draw
+    (305.8194, 799.1674)
+     -- (336.3241, 804.7137);
+  \draw
+    (305.8194, 798.2431)
+     -- (335.3997, 792.6968);
+  \draw
+    (387.1651, 703.956)
+     -- (511.0324, 703.956)
+     -- (511.0324, 703.0316);
+  \draw
+    (388.0895, 605.0471)
+     -- (511.9568, 605.0471);
+  \pic
+     at (272.5417, 766.814) {ipe disk};
+  \draw[red]
+    (304.8951, 797.3187) circle[radius=35.9679];
+
+    \pic[fill=white]
+     at (225.8488, 655.2932) {ipe fdisk};
+
+     \pic[fill=white]
+     at (481.8488, 655.2932) {ipe fdisk};
+
+     \pic[fill=white]
+     at (304.8951, 799.1674) {ipe fdisk};
+\end{tikzpicture}
+\caption{Two degenerations of the combinatorial type above, which represents a ray.
+On the left-hand side, the alignment holds only generically.
+On the right-hand side, it is not enough to align each individual factor.}\label{fig:fwise_align}
+\end{figure}
+
+We modify the boundary of $\Ecal$\footnote{With the log structure obtained by pulling back from Kim's space and modding out by $\mathbb N^{\codim (\sigma)}$, i.e.
+considering the edges of $E$ to have \emph{infinite length}.} as follows:
+\begin{enumerate}
+ \item radially aligning the core, and imposing factorisation, thus effectively replacing
+ \[\ol\Mcal^{\leftrightarrow}_{1,\mu}(P|H_0+H_\infty)\quad\text{by}\quad\VZ^{\leftrightarrow}_{1,\mu}(P|H_0+H_\infty)\]
+ in the product above, with the consequence of introducing a reduced rubber;
+ \item requiring that any degeneration of $V_{0,\delta}$ (resp.
+$\forall v\in V_{>0,\delta}$) remains centrally aligned with respect to the core;\footnote{Notice that this requires us to blow up some diagonal subloci of the product above, see Figure \ref{fig:fwise_align}} this has the effect that on the whole of $\widetilde E$ - including the boundary -, for each $v\in \{V_{0,\delta}\}\cup V_{>0,\delta}$, it is always possible to tell the components of the curve that are at distance $\delta$ from the core along the path denominated $v$, and, if there is more than one for the same $v$, the lengths of these paths are identified, so as to define line bundles $\OO(\delta_v), \forall v\in \{V_{0,\delta}\}\cup V_{>0,\delta}$.
+\end{enumerate}
+It is clear that $\widetilde \Dcal\to\widetilde\Ecal$ is generically a torus bundle of relative dimension $\codim(\sigma)-1$; the open locus is represented by the moduli space of attachments for the elliptic singularities.
+\begin{lemma}
+ Generically on $\Ecal$, $\widetilde \Dcal\to\widetilde\Ecal$ is isomorphic to $\mathcal P=\PP_{\widetilde\Ecal}(\bigoplus_{v\in \{V_{0,\delta}\}\cup V_{>0,\delta}}\OO(\delta_v))$.
+\end{lemma}
+\begin{proof}
+ All of the line bundles $\OO(\delta_v)$ share a common factor $\mathbb T_E$, the universal tangent line to the elliptic curve (appropriately twisted by bubbling loci as in \cite[\S 2.3]{VZ}); removing this, when the curve has the prescribed dual graph, $\OO(\delta_v)$ is isomorphic to the tangent line to the rational tail $R_v$ at the gluing node $q_v$ (with the caveat that all those corresponding to $V_{0,\delta}$ are canonically identified).
+This is the open stratum of the moduli space of attaching data \cite[\SS 2.2-2.3]{SMY2}.
+On the boundary, the circle of radius $\delta$ will pass through a subset of $\{V_{0,\delta}\}\cup V_{>0,\delta}$, while cutting the complementary subset along the edge between the core and $v$; correspondingly, there is a destabilisation of the curve, and an elliptic singularity containing strictly semistable branches.
+Tropically, pushing some of the vertices off the circle creates new finite-length edges with coordinates $\ell_v\in\RR_{\geq_0}$ (see Figure \ref{fig:off_we_go}); not all of them can be strictly positive, because the circle needs to pass through at least one vertex (of positive horizontal degree).
+This is patently the fan of a projective space.
+\end{proof}
+\begin{figure}
+\begin{tikzpicture}[ipe import,scale=.8]
+  %\useasboundingbox (0, 0) rectangle (595, 842);
+  \draw
+    (64, 672)
+     -- (128, 688)
+     -- (64, 704)
+     -- (64, 704);
+  \draw
+    (128, 688)
+     -- (64, 736)
+     -- (64, 736);
+  \draw[red]
+    (128, 688) circle[radius=65.9697];
+  \draw
+    (128, 688)
+     -- (112, 752)
+     -- (64, 768)
+     -- (64, 768);
+  \draw
+    (112, 752)
+     -- (64, 784)
+     -- (64, 784);
+  \pic
+     at (64, 672) {ipe disk};
+  \pic
+     at (64, 704) {ipe disk};
+  \pic
+     at (64, 736) {ipe disk};
+  \pic
+     at (64, 768) {ipe disk};
+  \pic
+     at (64, 784) {ipe disk};
+  \pic
+     at (112, 752) {ipe cross};
+  \pic
+     at (75.2242, 727.582) {ipe cross};
+  \pic
+     at (112, 700) {ipe cross};
+  \pic
+     at (112, 692) {ipe cross};
+  \pic
+     at (112, 684) {ipe cross};
+  \pic
+     at (75.8121, 701.047) {ipe cross};
+  \pic
+     at (75.0704, 674.4388) {ipe cross};
+  \filldraw[fill=white]
+    (64, 608)
+     -- (208, 608)
+     -- (208, 608);
+  \pic
+     at (64, 608) {ipe disk};
+  \draw
+    (128, 688)
+     -- (208, 688)
+     -- (208, 688);
+  \pic
+     at (73.6978, 608.02) {ipe cross};
+  \pic
+     at (111.876, 608.0202) {ipe cross};
+  \pic
+     at (127.674, 608.0205) {ipe cross};
+  \pic[fill=white]
+     at (128, 688) {ipe fdisk};
+  \node[ipe node]
+     at (86.863, 690.301) {$m$};
+  \node[ipe node]
+     at (87.521, 671.212) {$m$};
+  \draw
+    (128, 688)
+     -- (91.4703, 741.643);
+  \draw
+    (128, 688)
+     -- (160.586, 745.593)
+     -- (160.586, 745.593);
+  \pic
+     at (91.4703, 741.643) {ipe disk};
+  \pic
+     at (160.486, 745.417) {ipe disk};
+  \draw[shift={(91.47, 741.051)}, xscale=0.95, yscale=0.6996]
+    (0, 0)
+     -- (-26.9879, 7.241)
+     -- (-26.9879, 7.241);
+  \draw
+    (160.486, 745.417)
+     -- (64.4824, 799.569);
+  \draw
+    (160.486, 745.417)
+     -- (208.637, 745.593);
+  \draw
+    (92.1286, 740.985)
+     -- (64.4824, 754.15);
+  \pic
+     at (64.4824, 746.909) {ipe disk};
+  \pic
+     at (64.4824, 798.91) {ipe disk};
+  \pic
+     at (64.4824, 753.492) {ipe disk};
+  \draw
+    (289.118, 672.0005)
+     -- (353.118, 688.0005)
+     -- (289.118, 704.0005)
+     -- (289.118, 704.0005);
+  \draw
+    (353.118, 688.0005)
+     -- (289.118, 736.0005)
+     -- (289.118, 736.0005);
+  \draw[red]
+    (353.118, 688.0005) circle[radius=65.9697];
+  \draw
+    (353.118, 688.0005)
+     -- (337.118, 752.0005)
+     -- (289.118, 768.0005)
+     -- (289.118, 768.0005);
+  \draw
+    (337.118, 752.0005)
+     -- (289.118, 784.0005)
+     -- (289.118, 784.0005);
+  \pic
+     at (289.118, 672.0005) {ipe disk};
+  \pic
+     at (289.118, 704.0005) {ipe disk};
+  \pic
+     at (289.118, 736.0005) {ipe disk};
+  \pic
+     at (289.118, 768.0005) {ipe disk};
+  \pic
+     at (289.118, 784.0005) {ipe disk};
+  \pic
+     at (337.118, 752.0005) {ipe cross};
+  \pic
+     at (300.3422, 727.5825) {ipe cross};
+  \pic
+     at (337.118, 700.0005) {ipe cross};
+  \pic
+     at (337.118, 692.0005) {ipe cross};
+  \pic
+     at (337.118, 684.0005) {ipe cross};
+  \pic
+     at (300.9301, 701.0475) {ipe cross};
+  \pic
+     at (300.1889, 674.4392) {ipe cross};
+  \filldraw[fill=white]
+    (289.118, 608.0005)
+     -- (433.118, 608.0005)
+     -- (433.118, 608.0005);
+  \pic
+     at (289.118, 608.0005) {ipe disk};
+  \draw
+    (353.118, 688.0005)
+     -- (433.118, 688.0005)
+     -- (433.118, 688.0005);
+  \pic
+     at (298.8158, 608.0205) {ipe cross};
+  \pic
+     at (336.994, 608.0207) {ipe cross};
+  \pic
+     at (352.792, 608.0209) {ipe cross};
+  \pic[fill=white]
+     at (353.118, 688.0005) {ipe fdisk};
+  \node[ipe node]
+     at (311.98, 690.301) {$m$};
+  \node[ipe node]
+     at (312.639, 671.212) {$m$};
+  \draw[shift={(353.118, 687.999)}, xscale=1.1287, yscale=1.1615]
+    (0, 0)
+     -- (-36.5297, 53.643);
+  \draw[shift={(353.119, 687.997)}, xscale=1.4269, yscale=1.3567]
+    (0, 0)
+     -- (32.586, 57.593)
+     -- (32.586, 57.593);
+  \pic
+     at (310.6643, 751.5171) {ipe disk};
+  \pic
+     at (400.086, 767.1394) {ipe disk};
+  \draw[shift={(311.745, 750.197)}, xscale=0.8205, yscale=-0.5452]
+    (0, 0)
+     -- (-26.9879, 7.241)
+     -- (-26.9879, 7.241);
+  \draw[shift={(399.543, 767.54)}, xscale=1.1319, yscale=0.5704]
+    (0, 0)
+     -- (-96.0036, 54.152);
+  \draw[shift={(400.744, 767.146)}, xscale=0.6446, yscale=-1.3688]
+    (0, 0)
+     -- (48.151, 0.176);
+  \draw[shift={(311.717, 751.113)}, xscale=0.8, yscale=0.1453]
+    (0, 0)
+     -- (-27.6462, 13.165);
+  \pic
+     at (289.6004, 746.9095) {ipe disk};
+  \pic
+     at (289.6004, 798.9105) {ipe disk};
+  \pic
+     at (289.6004, 753.4925) {ipe disk};
+  \pic
+     at (387.02, 744.935) {ipe cross};
+  \pic
+     at (317.246, 742.961) {ipe cross};
+  \node[ipe node]
+     at (315.273, 748.884) {$\ell_{j_1}$};
+  \node[ipe node]
+     at (397.553, 752.175) {$\ell_{j_2}$};
+\end{tikzpicture}
+\caption{Moving vertices off the circle creates new tropical parameters.}\label{fig:off_we_go}
+\end{figure}
+
+Notice that $\mathcal P$ is well-defined on the whole of $\widetilde \Ecal$, while $\widetilde \Dcal\to \mathcal P$ is in fact a modification oof the boundary, as dictated by the alignment procedure.
+In the next section, we extrapolate what we need from this combinatorial setup in order to describe $\Dcal$ explicitly.
+\begin{comment}
 \subsubsection{The generic alignment} In the first line of the product above, we have grouped the $k$ factors adjacent to the core with maximal expansion factor $m$.
@@
 \end{figure}
+\end{comment}
+
+\subsubsection{From $\widetilde\Dcal$ to $\Dcal$}
 

### 2019-06-26 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex

@@
 
-\title{Absolute, relative and rubber Gromov--Witten theory of hypersurfaces in genus one}
+\title{Curve counting in genus one: elliptic singularities and the splitting formula}
 \author{Luca Battistella, Navid Nabijou and Dhruv Ranganathan}
@@
 
+\begin{lemma}\label{lem:m=1}
+ If the maximal contact order at the core is $m=1$, the corresponding combinatorial type does not contribute to the invariants.
+\end{lemma}
+\begin{proof}
+ It follows once again from a dimensional argument.
+\end{proof}
+
 %%%%%%%%
@@
 
-\subsubsection{From $\widetilde\Dcal$ to $\Dcal$}
-
+\subsubsection{From $\widetilde\Dcal$ to $\Dcal$} Let $F=\bigoplus_{v\in \{V_{0,\delta}\}\cup V_{>0,\delta}}\OO(\delta_v)$. On $\mathcal P$ we have a tautological sequence:
+\[\OO_{F}(-1)\hookrightarrow p^*(F)\xrightarrow{+\operatorname{d}f}\operatorname{ev}_E^*(TH),\]
+where $p\colon\mathcal P=\PP(F)\to\widetilde\Ecal$, and $+\operatorname{d}f$ should be interpreted as follows: for every $v\in \{V_{0,\delta}\}\cup V_{>0,\delta}$, as many copies of $\OO(\delta_v)$ are considered as there are components at distance $\delta$ from the core along the path $v$, and they are identified according to the preferred isomorphisms; then, the differential of the universal map to $\PP^N$ is applied to each tangent vector (possibly including some contracted rational bubbles on the path), and the sum of these contributions is taken in $T_{f(E)}\PP^N$ - it actually lies in $T_{f(E)}H$ because all the normal contributions can be assumed to be trivial by Lemma \ref{lem:m=1}.
+The composite, regarded as a section $s$ of $G=\OO_F(1)\otimes \operatorname{ev}_E^*(TH)$, vanishes precisely where $f$ factors through the Smyth's singularity determined by the point in the fiber of $p$.
+Generically on $\widetilde\Ecal$, this is exactly what we are after.
+On the boundary, though, it may happen that a simultaneous degeneration in the base and the fiber makes this factorisation trivial, in the sense that $\bar f$ would be constant on all the branches of the elliptic singularity.
+
+\begin{lemma}
+ For every $V_B\subseteq V_\delta$ and $V_F=V_\delta\setminus V_B$, $s$ vanishes along the loci where the factors corresponding to $V_B$ in $\widetilde \Ecal$ degenerate so that $f_v\colon R_v\to\PP^N$ is constant in a neighbourhood of $q_v$, and the fiber coordinates $(\lambda_{v^\prime})_{v^\prime\in V_F}$ along $p\colon\mathcal P\to\widetilde \Ecal$ are set to be $0$.
+\end{lemma}
+Call these loci $\Xi_i,i\in I$ (compare with \cite[\S 3.2]{VZ} for an analogous phenomenon in the non-relative case); it is clear that they may be in excess with respect to the expected codimension of $V(s)$, that is $N-1$.
+These loci are logarithmic substrata; therefore, there exists a logarithmic blow-up that principalizes them.
+We claim that $\widetilde\Dcal$ is (possibly a refinement of) such a blow-up.
+\begin{lemma}
+ The pullback of $\Xi_i$ is principal in $\widetilde\Dcal$.
+\end{lemma}
+\begin{proof}
+ Let us analyse the ideal of $\Xi_i$: it is generated by
+ \begin{enumerate}[leftmargin=.5 cm]
+  \item equations on $\widetilde\Ecal$ cutting the locus where $R_v$ degenerates so that $f_v$ is constant on a neighbourhood of $q_v$, $v\in V_B$: these correspond to the tropical functions $\delta_v-\operatorname{dist}(q_v,\circ)$;
+  \item equations on the fiber of $p$ for the linear subspace corresponding to $v\in V_F$: tropically, these correspond to the $\ell_v$ discussed above.
+ \end{enumerate}
+By construction, on $\widetilde \Dcal$ it is always possible to tell which of these tropical lengths is the shortest (the circle we have drawn on $\Xi$ is degenerate - it passes through no vertex of positive horizontal degree -, therefore we need to decide for a strictly larger circle in order to lift to $\widetilde D$), which corresponds to principalising the ideal (see Figure \ref{fig:principalisation}).
+\end{proof}
+
+\begin{figure}
+\begin{tikzpicture}[ipe import]
+  %\useasboundingbox (0, 0) rectangle (595, 842);
+  \draw
+    (64, 720)
+     -- (112, 736)
+     -- (96, 752);
+  \draw[->]
+    (64, 704)
+     -- (128, 704);
+  \pic
+     at (64, 704) {ipe disk};
+  \pic
+     at (64, 720) {ipe disk};
+  \pic
+     at (96, 752) {ipe disk};
+  \draw[red, dotted]
+    (60.6969, 708.808)
+     arc[start angle=-161.5651, end angle=-71.5651, x radius=53.2078, y radius=-65.2105];
+  \pic[fill=white]
+     at (112, 736) {ipe fdisk};
+  \draw
+    (192, 720)
+     -- (240, 736)
+     -- (224, 752);
+  \draw[->]
+    (192, 704)
+     -- (256, 704);
+  \pic
+     at (192, 704) {ipe disk};
+  \pic
+     at (192, 720) {ipe disk};
+  \pic
+     at (224, 752) {ipe disk};
+  \pic[fill=white]
+     at (240, 736) {ipe fdisk};
+  \draw
+    (112, 736)
+     -- (128, 736);
+  \draw
+    (240, 736)
+     -- (256, 736);
+  \draw
+    (208.6374, 743.6181)
+     -- (224.4352, 750.8588);
+  \draw
+    (208.6374, 758.7577)
+     -- (225.0934, 751.517);
+  \pic
+     at (207.9791, 742.9599) {ipe disk};
+  \pic
+     at (207.9791, 758.7577) {ipe disk};
+  \pic
+     at (208, 704) {ipe cross};
+  \pic
+     at (224, 704) {ipe cross};
+  \pic
+     at (240, 704) {ipe cross};
+  \pic
+     at (96, 704) {ipe cross};
+  \pic
+     at (112, 704) {ipe cross};
+  \draw[red, dotted]
+    (231.0126, 755.9018)
+     { [rotate=-17.595] arc[start angle=135, end angle=225, x radius=21.7093, y radius=22.6274] };
+  \draw[red]
+    (188.9249, 712.0225)
+     arc[start angle=-156.5092, end angle=-115.3692, x radius=85.088, y radius=-96.462];
+\end{tikzpicture}
+\caption{On the left, a generic point of $\mathcal P$.
+On the right, a point of $\Xi$.
+The dotted circle is the one we draw on $\mathcal P$.
+The continuous circle represents one of the possible choices of $\delta$ enlarging the dotted one (a stratum of $\widetilde\Dcal$).}\label{fig:principalisation}
+\end{figure}
+
+Finally, on $\widetilde\Dcal$ (or, in fact, on an intermediate blow-up $\widetilde{\mathcal P}\to\mathcal P$) there are exceptional divisors $\widetilde \Xi_i$ corresponding to $\Xi_i$ in $\mathcal P$.
+Since the $\Xi_i$ exhaust all the excess-dimensional components of the vanishing locus of $s\in\Gamma(\mathcal P,G)$, the latter induces a section $\tilde s\in\Gamma(\widetilde\Dcal,G(-\sum_i\widetilde\Xi_i))$ by pullback and twisting, whose vanishing locus is dimensionally transverse to the boundary, and whose open part coincides with the generic point of $\Dcal$, therefore $V(\tilde s)=\Dcal$.
+
+Notice that, expressing the pushforward of the Chern classes of $\OO_F(1)$ and $\OO(\widetilde\Xi_i)$ in terms of tautological classes on the fiber product underlying $\Ecal$, we get:
+\begin{cor}
+ After pushforward to $\Ecal$, the contribution of $\Dcal$ to the invariants can be computed in terms of tautological integrals on moduli spaces of maps with lower numerics.
+\end{cor}
+\begin{comment}
 \subsubsection{Factorisation} Assume $m\geq 2$. Over $\mathcal P$ we have a tautological sequence:
@@
 \end{cor}
+\end{comment}
 

### 2019-06-26 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
wrote some things

--- 2019-06-25 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
@@
 
-\subsection{Recursive description of the divisors: type $C^0$}
-
-\subsubsection{Restricting the possible combinatorial types} Recall that a boundary divisor $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ is said to be of \textbf{type $C^0$} if the core is assigned zero degree by the combinatorial type.
-In this case, the combinatorial type is not as tightly constrained as previously (it need not be a bipartite graph with a single interior vertex).
+\subsection{Recursive description of the divisors: type IIIb} The treatment of the type I, II and IIIa cases above is a fairly straightforward extension of the ideas of Vakil and Gathmann (albeit updated with logarithmic and tropical technology, which streamlines the presentation and simplifies the proofs).
+The remaining type IIIb case, however, is entirely new.
+In this section we provide a recursive description of these boundary divisors; this constitutes the technical heart of the paper.
+
+\subsubsection{Description of the possible combinatorial types} Recall that a boundary divisor $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ is said to be of type IIIb if the core is assigned degree zero by the combinatorial type (this is the only case which we did not treat in Lemma \ref{lem:combs}).
+In this case, the combinatorial type is not as tightly constrained as before; the target may expand multiple times, and as such the combinatorial type need not be a bipartite graph with a single interior vertex.
 Nevertheless, we have the following lemma:
 \begin{lemma} 
-Let $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ be a locus of type $C^0$ and let $\Delta$ be the corresponding combinatorial type.
-Then for every nonzero vertex $\diamond$ of the expanded target, the fibre of the tropical map over $\diamond$ contains exactly one stable vertex (together with a number of trivial bubbles), and at least one vertex which lies on the radius (which may or may not be stable).
+Let $\Dcal$ be a locus of type IIIb and let $\Delta$ be the corresponding combinatorial type.
+Then for every nonzero vertex $\diamond$ of the expanded tropical target, the fibre of the tropical map over $\diamond$ contains:
+\begin{enumerate}
+\item exactly one stable vertex (together with a number of trivial bubbles);
+\item at least one vertex which lies on the radius (which may or may not be stable).
+\end{enumerate}
 \end{lemma}
 \begin{proof}
-By stability we always need at least one stable vertex lying over each  vertex of the target.
-If there was more than one, then (since both the insertions and the factorisation condition are pulled back from the moduli space of maps without expansions) it can be seen, as in the proof of Lemma \ref{lem:combs}, that the contribution vanishes.
+By stability, we must always have at least one stable vertex lying over each  vertex of the target.
+If there was more than one, then (since both the insertions and the factorisation condition are pulled back from the moduli space of maps without expansions) we can show, as in the proof of Lemma \ref{lem:combs}, that the contribution vanishes.
 
@@
 
-%%%%%%%%
-\begin{comment}
-\begin{center}
-\begin{figure}
- \begin{tikzpicture}[ipe import]
-  %\useasboundingbox (0, 0) rectangle (595, 842);
-  \draw
-    (64, 672)
-     -- (128, 688)
-     -- (64, 704)
-     -- (64, 704);
-  \draw
-    (128, 688)
-     -- (64, 736)
-     -- (64, 736);
-  \draw[red]
-    (128, 688) circle[radius=65.9697];
-  \draw
-    (128, 688)
-     -- (112, 752)
-     -- (64, 768)
-     -- (64, 768);
-  \draw
-    (112, 752)
-     -- (64, 784)
-     -- (64, 784);
-  \pic
-     at (64, 672) {ipe disk};
-  \pic
-     at (64, 704) {ipe disk};
-  \pic
-     at (64, 736) {ipe disk};
-  \pic
-     at (64, 768) {ipe disk};
-  \pic
-     at (64, 784) {ipe disk};
-  \pic
-     at (112, 752) {ipe disk};
-  \pic
-     at (75.2242, 727.5818) {ipe cross};
-  \pic
-     at (112, 700) {ipe cross};
-  \pic
-     at (112, 692) {ipe cross};
-  \pic
-     at (112, 684) {ipe cross};
-  \pic
-     at (75.8121, 701.047) {ipe cross};
-  \pic
-     at (75.0705, 674.4385) {ipe cross};
-  \filldraw[fill=white,->]
-    (64, 608)
-     -- (208, 608);
-  \pic
-     at (64, 608) {ipe disk};
-  \draw
-    (128, 688)
-     -- (208, 688);
-  \pic
-     at (73.6978, 608.0203) {ipe cross};
-  \pic
-     at (111.8758, 608.0203) {ipe cross};
-  \pic
-     at (127.6736, 608.0203) {ipe cross};
-  \pic[fill=white]
-     at (128, 688) {ipe fdisk};
-  \node[ipe node]
-     at (86.863, 690.301) {$m$};
-  \node[ipe node]
-     at (87.521, 671.212) {$m$};
-  \node[ipe node]
-     at (48.026, 668.579) {$R_1$};
-  \node[ipe node]
-     at (48.026, 687.668) {$\ldots$};
-  \node[ipe node]
-     at (47.368, 700.832) {$R_k$};
-  \node[ipe node]
-     at (48.026, 725.846) {$R_{k+1}$};
-  \node[ipe node]
-     at (48.026, 784.429) {$R_s$};
-  \node[ipe node]
-     at (48.026, 766.657) {$\ldots$};
-  \node[ipe node]
-     at (108.585, 757.441) {$R_r$};
-  \node[ipe node]
-     at (80, 744.935) {$\ldots$};
-  \node[ipe node]
-     at (130.965, 677.794) {$E$};
-\end{tikzpicture}
-\caption{A ray of type $C^0$.}\label{fig:ray_example}
-\end{figure}
-\end{center}
-\end{comment}
-%%%%%%%%%%
-
-We observe that the cone $\sigma \in \Sigma^{\Kim}$ corresponding to the stratum $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$ is isomorphic to $\N^r$ where $r$ is the number of target expansions.
-The discrepancy between the dimension of $\sigma$ and the dimension of the ray $\tau$ is to be expected, since the loci of type $C^0$ are contained in the exceptional locus of the blow-up.
-
+\subsubsection{Recursive description of $\Ecal$}
+Similarly to before, we let $\tau \in \Sigma$ be the ray corresponding to $\Dcal \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$, $\sigma \in \Sigma^{\Kim}$ be the minimal cone containing $\tau$ and $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$ be the stratum corresponding to $\sigma$, so that we have a map $\Dcal \to \Ecal$ (and $\Ecal$ is the minimal stratum through which the map from $\Dcal$ factors).
+Recall that we also have a unique stratum $\widetilde\Dcal \subseteq \widetilde\VZ_{1,\alpha}(\PP^N|H,d)$ such that $\Dcal = \widetilde\Dcal \cap \VZ_{1,\alpha}(\PP^N|H,d)$.
+Note that the cone $\sigma$ has dimension equal to the number of levels of the target expansion in the combinatorial type, which in this case may well be strictly larger than $1$.
+
+We can describe the locus $\Ecal$ in a simple recursive manner.
 We write $\Delta_0$ for the collection of stable vertices of the combinatorial type which are mapped to $0$ by the tropical map, and $\Delta_{>0}$ for the stable vertices which are mapped to $\RR_{>0}$.
@@
 Then $\Ecal$ admits a finite splitting morphism onto the fibre product
-\begin{equation*} \Ecal \xrightarrow{\rho} \left( \prod_{v \in \Delta_0} \ol\Mcal_{\Gamma_v}(\PP^N|H) \times \prod_{v \in \Delta_{>0}} \ol\Mcal^{\leftrightarrow}_{\Gamma_v}(P|H_0+H_\infty) \right) \times_{H^{2E}} H^E \end{equation*}
-where $E$ is the number of edges of the (stabilised) dual graph, and the fibre product is taken over the appropriate evaluation maps.
-Note that only the factor corresponding to the core vertex has non-zero genus, and that it must have zero degree.
-
-\begin{remark}As in \S \ref{subsubsection splitting degree} above, we should calculate the degree of $\rho$ and the vanishing order $\lambda_{\Dcal}$ of the section $s_k$ along $\Dcal$.
+\begin{equation}\label{IIIa fibre product} \Ecal \xrightarrow{\rho} \left( \prod_{v \in \Delta_0} \ol\Mcal_{\Gamma_v}(\PP^N|H) \times \prod_{v \in \Delta_{>0}} \ol\Mcal^{\leftrightarrow}_{\Gamma_v}(P|H_0+H_\infty) \right) \times_{H^{2\epsilon}} H^{\epsilon} \end{equation}
+where $\epsilon$ is the number of edges of the (stabilised) dual graph, and the fibre product is taken over the appropriate evaluation maps.
+Thus, tautological integrals over $\Ecal$ are completely determined in terms of integrals over moduli spaces with ``smaller'' combinatorial data.
+
+Notice that the actual dimension of $\Ecal$ will typically be larger than that of $\Dcal$, since $\Ecal$ is contained inside the excess components of the moduli space.
+We will describe $\Dcal$ in terms of the map $\Dcal \to \Ecal$, proceeding in two steps:
+\begin{enumerate}
+\item obtaining $\widetilde\Dcal$ from $\Ecal$;
+\item expressing the class of $\Dcal \subseteq \widetilde\Dcal$ in terms of tautological classes.
+\end{enumerate}
+
+\begin{remark}[Splitting degree and vanishing order, revisited] Similarly to \S \ref{subsubsection splitting degree} above, we can calculate the degree of $\rho$ and the vanishing order $\lambda_{\Dcal}$ of the section $s_k$ along $\Dcal$.
 The degree of $\rho$ is given exactly as in Lemma \ref{lem:saturation}, where now we obtain one such factor for each bounded edge of the tropical target.
-The vanishing order $\lambda_{\Dcal}$ is slightly more delicate, but may be computed as the index of an explicit morphism of one-dimensional lattices, as explained in the proof of Lemma \ref{lemma vanishing order} above.
-\end{remark}
-
-Typically, $\Ecal$ will have true dimension larger than that of $\Dcal$.
-We will study the map $\Dcal \to \Ecal$ in two steps: first, we will describe the map $\widetilde\Dcal \to \Ecal$, and then we will explain how to express the class of the substack $\Dcal \subseteq \widetilde\Dcal$ in terms of tautological classes.
-
-\subsubsection{Constructing $\widetilde\Dcal$ from $\Ecal$}
-The geometry of $\widetilde\Dcal\to\Ecal$ is encoded by the combinatorics of the alignment.
-The reader should bear the following toric construction in mind: suppose we subdivide a fan, and we want to describe the relation between the varieties corresponding respectively to a cone $\rho$ of the subdivision, and the original cone $\sigma$ containing it.
-The fan of $X_\tau$ is obtained by projecting the star of $\tau$ to the quotient $N_\tau=N_{\RR}/\langle\tau\rangle_{\RR}$ of the ambient vector space by the linear span of the cone\footnote{We find it useful to encode this within the formalism of extended tropicalisations \cite{?}.}.
-Notice that the dimension of the vector spaces $N_\rho$ and $N_\sigma$ (or the corresponding toric varieties) is off by the difference $c$ between the dimension of the cones.
-Furthermore, we may need to subdivide the fan of $X_\sigma$ in order for cones of $\Sigma_\rho$ to be mapped surjectively to cones of $\Sigma_\sigma$.
-The geometric interpretation of this is that $X_\tau$ is obtained as an appropriate compactification of a toric bundle of dimension $c$ over $X_\sigma$; observe that the fiber dimension may not be constant (but it can be made so by blowing up $X_{\sigma}$, see \cite[Lemma 4.1]{AK}).
-It is a fundamental insight due to Tevelev \cite{Tevelev} that a good compactification of the toric bundle is suggested by the tropicalisation of the locus we are interested in: here, ``good'' means that the intersection of the interesting locus with the boundary is dimensionally transverse.
-In the case at hand, the interesting locus is that of maps satisfying the factorisation property (i.e.
-smoothable maps), and the tropicalisation has been worked out in \cite{RSPW2} to consist of well-spaced maps.
-
-We proceed to describe $\Dcal$ step-by-step, building on $\Ecal$.
-
-\subsubsection{The generic alignment} In the first line of the product above, we have grouped the $k$ factors adjacent to the core with maximal expansion factor $m$.
-It is fundamental to realise that, generically on $\Ecal$, the vertices corresponding to these factors are (equidistant and) already aligned with respect to the core.
-We can construct a modification $\widetilde\Ecal$ of $\mathcal E$ by:
-\begin{enumerate}
- \item radially aligning the core, and imposing the double factorisation condition, thus effectively replacing the factor
- \[\ol\Mcal_{1,\alpha^{(0)}\cup(-m,\ldots,-m,-\mu_{k+1},\ldots,-\mu_r)\cup(-m_i)_{i\in\{k+1,\ldots,s\}\setminus(\bigcup I_j)}}^{\leftrightarrow}(P|H_0+H_\infty,0)\]
- by $\VZ_{1,\alpha^{(0)}\cup(-m,\ldots,-m,-\mu_{k+1},\ldots,-\mu_r)\cup(-m_i)_{i\in\{k+1,\ldots,s\}\setminus(\bigcup I_j)}}^{\leftrightarrow}(P|H_0+H_\infty,0)$ in the product above; in particular, there is a universal cotangent line bundle at the markings $\mathbb L_E$, obtained by suitably twisting any marking cotangent line (they are all isomorphic over a smooth elliptic curve) by the appropriate bubbling loci (see \cite[\S 2.3]{VZ});
- \item aligning the first $k$ factors with respect to the core (this blows up some diagonal subloci of the product, so it is not enough to align the individual factors).
-\end{enumerate}
-See Figure \ref{fig:fwise_align} below.
-It is obvious that $\widetilde \Dcal\to \Ecal$ factors through $\widetilde\Ecal$.
-On $\widetilde\Ecal$, we have a tropical line bundle $\OO(\delta)$ representing the minimum distance from the core to the tropical preimage of $0$; generically, this line bundle coincides with the normal bundle of the locus where the node between the core and one (any) of the first $k$ vertices persists, but on the boundary this needs to be twisted by further smoothing parameters according to the (partial) alignment on $\widetilde\Ecal$.
-We can obtain a line bundle $\mathbb T_R$ accounting only for the behaviour of the rational side of the fiber product by twisting $\OO(\delta)$ with $\mathbb L_E$.
-
-%%%%%%%%%%%%%
-\begin{comment}
-\begin{figure}
- \begin{tikzpicture}[ipe stylesheet,scale=.7]
-  %\useasboundingbox (0, 0) rectangle (595, 842);
-  \pic
-     at (129.8488, 703.2932) {ipe disk};
-  \pic
-     at (97.8488, 719.2932) {ipe disk};
-  \pic
-     at (97.8488, 687.2932) {ipe disk};
-  \draw
-    (97.8488, 719.2932)
-     -- (129.8488, 703.2932)
-     -- (97.8488, 687.2932);
-  \draw
-    (129.8488, 703.2932)
-     -- (161.8488, 687.2932);
-
-  \draw
-    (193.8488, 671.2932)
-     -- (225.8488, 655.2932);
-  \draw
-    (225.8488, 655.2932)
-     -- (193.8488, 639.2932);
-    \draw[ipe dash dashed]
-   (193.8488, 671)
-    -- (161.8488, 687);
-  \draw[ipe dash dashed]
-    (193.8488, 639.2932)
-     -- (161.8488, 623.2932);
-  \draw
-    (161.8488, 623.2932)
-     -- (129.8488, 607.2932);
-  \pic
-     at (146.637, 615.0615) {ipe disk};
-  \draw
-    (129.8488, 607.2932)
-     -- (97.8488, 591.2932)
-     -- (97.8488, 591.2932);
-  \draw
-    (147.2948, 615.0622)
-     -- (97.2686, 638.1002)
-     -- (97.2686, 638.1002);
-  \pic
-     at (96.6103, 637.4422) {ipe disk};
-  \pic
-     at (97.9268, 590.7072) {ipe disk};
-  \pic
-     at (130.1808, 622.9607) {ipe cross};
-  \pic
-     at (130.1808, 607.1635) {ipe cross};
-  \pic
-     at (145.9788, 695.3672) {ipe cross};
-  \draw[-ipe linear]
-    (97.8488, 575.2932)
-     -- (257.8488, 575.2932);
-  \pic
-     at (97.8488, 575.2932) {ipe disk};
-  \pic
-     at (129.8488, 575.2932) {ipe cross};
-  \pic
-     at (145.8488, 575.2932) {ipe cross};
-  \pic
-     at (225.8488, 575.2932) {ipe cross};
-  \draw
-    (129.8488, 703.2932)
-     -- (257.8488, 703.2932);
-  \draw
-    (225.8488, 655.2932)
-     -- (257.8488, 655.2932)
-     -- (257.8488, 655.2932);
-  \draw
-    (146.3018, 614.861)
-     -- (258.5378, 614.404);
-  \node[ipe node]
-     at (189.423, 676.278) {$m$};
-  \node[ipe node]
-     at (189.094, 629.543) {$m$};
-  \node[ipe node]
-     at (111.421, 715.773) {$m_1$};
-  \node[ipe node]
-     at (110.104, 590.707) {$m_2$};
-  \node[ipe node]
-     at (110.763, 564.378) {$\ell_1$};
-  \node[ipe node]
-     at (133.801, 564.377) {$\ell_2$};
-  \node[ipe node]
-     at (146.308, 543.972) {$\frac{\ell_1}{m_1}+\frac{\ell_2}{m} \lesseqgtr \frac{\ell_1+\ell_2}{m_2}$};
-  \pic
-     at (473.6651, 658.9228) {ipe disk};
-  \pic
-     at (353.8488, 719.2932) {ipe disk};
-  \pic
-     at (353.8488, 687.2932) {ipe disk};
-  \draw
-    (353.8488, 719.2932)
-     -- (385.8488, 703.2932)
-     -- (353.8488, 687.2932);
-  \draw
-    (386.7731, 703.2932)
-     -- (418.7731, 687.2932);
-  \draw[ipe dash dashed]
-    (417.8488, 687.2932)
-     -- (449.8488, 671.2932)
-     -- (449.8488, 671.2932);
-
-  \draw
-    (449.8488, 671.2932)
-     -- (481.8488, 655.2932)
-     -- (481.8488, 655.2932);
-  \draw
-    (481.8488, 655.2932)
-     -- (449.8488, 639.2932)
-     -- (449.8488, 639.2932);
-  \draw[ipe dash dashed]
-    (449.8488, 639.2932)
-     -- (417.8488, 623.2932);
-  \draw
-    (417.8488, 623.2932)
-     -- (385.8488, 607.2932);
-  \pic
-     at (457.1756, 642.7929) {ipe disk};
-  \draw
-    (385.8488, 607.2932)
-     -- (353.8488, 591.2932)
-     -- (353.8488, 591.2932);
-  \pic
-     at (352.6103, 622.6521) {ipe disk};
-  \pic
-     at (353.9268, 590.7072) {ipe disk};
-  \pic
-     at (458.2826, 667.3311) {ipe cross};
-  \pic
-     at (459.207, 575.7344) {ipe cross};
-  \draw[-ipe linear]
-    (353.8488, 575.2932)
-     -- (513.8488, 575.2932);
-  \pic
-     at (353.8488, 575.2932) {ipe disk};
-  \pic
-     at (385.8488, 575.2932) {ipe cross};
-  \pic
-     at (475.7994, 575.2932) {ipe cross};
-  \pic
-     at (481.8488, 575.2932) {ipe cross};
-  \draw[shift={(472.741, 659.847)}, xscale=0.3271, yscale=-1.7893]
-    (0, 0)
-     -- (128, 0);
-  \draw
-    (481.8488, 655.2932)
-     -- (513.8488, 655.2932)
-     -- (513.8488, 655.2932);
-  \draw[shift={(459.26, 642.878)}, xscale=0.4834, yscale=0.4807]
-    (0, 0)
-     -- (112.236, -0.457);
-  \draw[red]
-    (482.3765, 654.0394) circle[radius=9.9987];
-  \draw
-    (354.8117, 621.686)
-     -- (386.2407, 606.8958);
-  \pic
-     at (386.2407, 606.8958) {ipe disk};
-  \pic
-     at (386.2407, 703.956) {ipe disk};
-  \draw[red]
-    (360.3506, 584.6012)
-     arc[start angle=160.4967, end angle=217.0656, x radius=120.4239, y radius=-143.3401];
-  \pic
-     at (473.9974, 650.6919) {ipe cross};
-  \pic
-     at (364.92, 693.131) {ipe cross};
-  \pic
-     at (372.3151, 710.6943) {ipe cross};
-  \pic
-     at (359.3737, 593.2977) {ipe cross};
-  \draw
-    (226.3225, 655.8881)
-     -- (258.6759, 665.1319);
-  \draw
-    (226.3225, 654.0394)
-     -- (258.6759, 646.6443);
-  \draw[-ipe linear]
-    (271.6173, 766.814)
-     -- (337.2485, 767.7384);
-
-  \pic
-     at (272.5417, 782.5285) {ipe disk};
-  \pic
-     at (271.6173, 815.8063) {ipe disk};
-  \draw
-    (305.8194, 798.2431)
-     -- (272.5417, 815.8063);
-  \draw
-    (305.8194, 798.2431)
-     -- (272.5417, 782.5285)
-     -- (272.5417, 782.5285);
-  \draw
-    (272.5417, 782.5285)
-     -- (336.3241, 782.5285);
-  \draw
-    (272.5417, 815.8063)
-     -- (336.3241, 814.8819);
-  \draw
-    (304.8951, 799.1674)
-     -- (335.3997, 799.1674);
-  \draw
-    (305.8194, 799.1674)
-     -- (336.3241, 804.7137);
-  \draw
-    (305.8194, 798.2431)
-     -- (335.3997, 792.6968);
-  \draw
-    (387.1651, 703.956)
-     -- (511.0324, 703.956)
-     -- (511.0324, 703.0316);
-  \draw
-    (388.0895, 605.0471)
-     -- (511.9568, 605.0471);
-  \pic
-     at (272.5417, 766.814) {ipe disk};
-  \draw[red]
-    (304.8951, 797.3187) circle[radius=35.9679];
-
-    \pic[fill=white]
-     at (225.8488, 655.2932) {ipe fdisk};
-
-     \pic[fill=white]
-     at (481.8488, 655.2932) {ipe fdisk};
-
-     \pic[fill=white]
-     at (304.8951, 799.1674) {ipe fdisk};
-\end{tikzpicture}
-\caption{Two degenerations of the combinatorial type above, which represents a ray.
-On the left-hand side, the alignment holds only generically.
-On the right-hand side, it is not enough to align each individual factor.}\label{fig:fwise_align}
-\end{figure}
-\end{comment}
-%%%%%%%%%%%%%%%%%%
-
-\subsubsection{The projective bundle}\label{subs:proj_bun} Generically on $\widetilde\Ecal$, the compactified torus bundle $\widetilde \Dcal\to \widetilde\Ecal$ coincides with the following projective bundle:
-\[\mathcal P=\PP_{\widetilde\Ecal}(\mathbb T_R\oplus\bigoplus_{j=k+1}^r \mathbb T_{q_j}R_j),\]
-where $\mathbb T_{q_j}R_J$ is the tangent line at the gluing marking closest to the core on the $j$-th factor of the product in the second line of \eqref{eq:product}.
-The open stratum in the fiber consists of moduli of attachments (i.e.
-moduli for the contraction to the Smyth's singularity); the compactification is by adding strictly semistable Gorenstein singularities as in \cite[\S\S 2.2-2.3]{SMY2}.
-In terms of alignment, a coordinate hyperplane corresponds to pushing the corresponding vertex off the circle, and destabilising the corresponding edge to the core.
-Tropically, the fibers can be analysed as follows: pushing some of the vertices off the circle creates new finite length edges with coordinates $\ell_j\in\RR_{\geq_0}$ (see Figure \ref{fig:off_we_go}); not all of them can be strictly positive, because the circle needs to pass through at least one vertex of positive horizontal degree.
-This is patently the fan of a projective space.
-
-%%%%%%%%%%%%%%%%
-\begin{comment}
-\begin{figure}
-\begin{tikzpicture}[ipe import,scale=.8]
-  %\useasboundingbox (0, 0) rectangle (595, 842);
-  \draw
-    (64, 672)
-     -- (128, 688)
-     -- (64, 704)
-     -- (64, 704);
-  \draw
-    (128, 688)
-     -- (64, 736)
-     -- (64, 736);
-  \draw[red]
-    (128, 688) circle[radius=65.9697];
-  \draw
-    (128, 688)
-     -- (112, 752)
-     -- (64, 768)
-     -- (64, 768);
-  \draw
-    (112, 752)
-     -- (64, 784)
-     -- (64, 784);
-  \pic
-     at (64, 672) {ipe disk};
-  \pic
-     at (64, 704) {ipe disk};
-  \pic
-     at (64, 736) {ipe disk};
-  \pic
-     at (64, 768) {ipe disk};
-  \pic
-     at (64, 784) {ipe disk};
-  \pic
-     at (112, 752) {ipe cross};
-  \pic
-     at (75.2242, 727.582) {ipe cross};
-  \pic
-     at (112, 700) {ipe cross};
-  \pic
-     at (112, 692) {ipe cross};
-  \pic
-     at (112, 684) {ipe cross};
-  \pic
-     at (75.8121, 701.047) {ipe cross};
-  \pic
-     at (75.0704, 674.4388) {ipe cross};
-  \filldraw[fill=white]
-    (64, 608)
-     -- (208, 608)
-     -- (208, 608);
-  \pic
-     at (64, 608) {ipe disk};
-  \draw
-    (128, 688)
-     -- (208, 688)
-     -- (208, 688);
-  \pic
-     at (73.6978, 608.02) {ipe cross};
-  \pic
-     at (111.876, 608.0202) {ipe cross};
-  \pic
-     at (127.674, 608.0205) {ipe cross};
-  \pic[fill=white]
-     at (128, 688) {ipe fdisk};
-  \node[ipe node]
-     at (86.863, 690.301) {$m$};
-  \node[ipe node]
-     at (87.521, 671.212) {$m$};
-  \draw
-    (128, 688)
-     -- (91.4703, 741.643);
-  \draw
-    (128, 688)
-     -- (160.586, 745.593)
-     -- (160.586, 745.593);
-  \pic
-     at (91.4703, 741.643) {ipe disk};
-  \pic
-     at (160.486, 745.417) {ipe disk};
-  \draw[shift={(91.47, 741.051)}, xscale=0.95, yscale=0.6996]
-    (0, 0)
-     -- (-26.9879, 7.241)
-     -- (-26.9879, 7.241);
-  \draw
-    (160.486, 745.417)
-     -- (64.4824, 799.569);
-  \draw
-    (160.486, 745.417)
-     -- (208.637, 745.593);
-  \draw
-    (92.1286, 740.985)
-     -- (64.4824, 754.15);
-  \pic
-     at (64.4824, 746.909) {ipe disk};
-  \pic
-     at (64.4824, 798.91) {ipe disk};
-  \pic
-     at (64.4824, 753.492) {ipe disk};
-  \draw
-    (289.118, 672.0005)
-     -- (353.118, 688.0005)
-     -- (289.118, 704.0005)
-     -- (289.118, 704.0005);
-  \draw
-    (353.118, 688.0005)
-     -- (289.118, 736.0005)
-     -- (289.118, 736.0005);
-  \draw[red]
-    (353.118, 688.0005) circle[radius=65.9697];
-  \draw
-    (353.118, 688.0005)
-     -- (337.118, 752.0005)
-     -- (289.118, 768.0005)
-     -- (289.118, 768.0005);
-  \draw
-    (337.118, 752.0005)
-     -- (289.118, 784.0005)
-     -- (289.118, 784.0005);
-  \pic
-     at (289.118, 672.0005) {ipe disk};
-  \pic
-     at (289.118, 704.0005) {ipe disk};
-  \pic
-     at (289.118, 736.0005) {ipe disk};
-  \pic
-     at (289.118, 768.0005) {ipe disk};
-  \pic
-     at (289.118, 784.0005) {ipe disk};
-  \pic
-     at (337.118, 752.0005) {ipe cross};
-  \pic
-     at (300.3422, 727.5825) {ipe cross};
-  \pic
-     at (337.118, 700.0005) {ipe cross};
-  \pic
-     at (337.118, 692.0005) {ipe cross};
-  \pic
-     at (337.118, 684.0005) {ipe cross};
-  \pic
-     at (300.9301, 701.0475) {ipe cross};
-  \pic
-     at (300.1889, 674.4392) {ipe cross};
-  \filldraw[fill=white]
-    (289.118, 608.0005)
-     -- (433.118, 608.0005)
-     -- (433.118, 608.0005);
-  \pic
-     at (289.118, 608.0005) {ipe disk};
-  \draw
-    (353.118, 688.0005)
-     -- (433.118, 688.0005)
-     -- (433.118, 688.0005);
-  \pic
-     at (298.8158, 608.0205) {ipe cross};
-  \pic
-     at (336.994, 608.0207) {ipe cross};
-  \pic
-     at (352.792, 608.0209) {ipe cross};
-  \pic[fill=white]
-     at (353.118, 688.0005) {ipe fdisk};
-  \node[ipe node]
-     at (311.98, 690.301) {$m$};
-  \node[ipe node]
-     at (312.639, 671.212) {$m$};
-  \draw[shift={(353.118, 687.999)}, xscale=1.1287, yscale=1.1615]
-    (0, 0)
-     -- (-36.5297, 53.643);
-  \draw[shift={(353.119, 687.997)}, xscale=1.4269, yscale=1.3567]
-    (0, 0)
-     -- (32.586, 57.593)
-     -- (32.586, 57.593);
-  \pic
-     at (310.6643, 751.5171) {ipe disk};
-  \pic
-     at (400.086, 767.1394) {ipe disk};
-  \draw[shift={(311.745, 750.197)}, xscale=0.8205, yscale=-0.5452]
-    (0, 0)
-     -- (-26.9879, 7.241)
-     -- (-26.9879, 7.241);
-  \draw[shift={(399.543, 767.54)}, xscale=1.1319, yscale=0.5704]
-    (0, 0)
-     -- (-96.0036, 54.152);
-  \draw[shift={(400.744, 767.146)}, xscale=0.6446, yscale=-1.3688]
-    (0, 0)
-     -- (48.151, 0.176);
-  \draw[shift={(311.717, 751.113)}, xscale=0.8, yscale=0.1453]
-    (0, 0)
-     -- (-27.6462, 13.165);
-  \pic
-     at (289.6004, 746.9095) {ipe disk};
-  \pic
-     at (289.6004, 798.9105) {ipe disk};
-  \pic
-     at (289.6004, 753.4925) {ipe disk};
-  \pic
-     at (387.02, 744.935) {ipe cross};
-  \pic
-     at (317.246, 742.961) {ipe cross};
-  \node[ipe node]
-     at (315.273, 748.884) {$\ell_{j_1}$};
-  \node[ipe node]
-     at (397.553, 752.175) {$\ell_{j_2}$};
-\end{tikzpicture}
-\caption{Moving vertices off the circle creates new tropical parameters.}\label{fig:off_we_go}
-\end{figure}
-\end{comment}
-%%%%%%%%%%%%%
-
-\subsubsection{Factorisation: obtaining $\Dcal$ from $\widetilde\Dcal$} Assume $m\geq 2$. Over $\mathcal P$ we have a tautological sequence:
-\[\OO_{F}(-1)\hookrightarrow p^*(F)\xrightarrow{+\operatorname{d}f}\operatorname{ev}_E^*(TH),\]
-where $p\colon\mathcal P=\PP(F)\to\widetilde\Ecal$, and $+\operatorname{d}f$ should be interpreted as follows: $k$ copies of $\mathbb T_R$ are taken to account - via the preferred isomorphisms - for all factors of the first product in \eqref{eq:product}; then, the differential of the universal map to $\PP^N$ is applied to each tangent vector (possibly including some of the contracted rational bubbles in the boundary), and the sum of these contributions is taken in $T_{f(E)}\PP^N$ - it actually lies in $T_{f(E)}H$ because all the normal contributions are trivial by assumption.
-The composition is a section $s$ of $G=\OO_F(1)\otimes \operatorname{ev}_E^*(TH)$, and it vanishes precisely where $f$ factors through the Smyth's singularity determined by the point in the fiber of $p$.
-Generically on $\widetilde\Ecal$, this is exactly what we are after.
-
-\subsubsection{Dimensional transversality} In general, the vanishing locus of $s$ corresponds to maps $f\colon C\to\PP^N$ and diagrams $C\leftarrow \tilde C\to \bar C$ - with $\bar C$ the elliptic $r$-fold point determined by the position in the fiber of $p\colon\mathcal P\to\widetilde \Ecal$ - such that $f$ factors through $\bar C$.
-When the curve is allowed to degenerate (so, on the boundary of $\widetilde \Ecal$), this is not always what we want: indeed, due do the combined action of degeneration (in the base direction) and destabilisation (in the fiber direction), it may very well be that $f$ is constant along every component of the elliptic singularity, so that it factors trivially; in other words, the vanishing locus of $s$ is not dimensionally transverse to the boundary of $\mathcal P$.
-\begin{lemma}
- For every $K\subseteq\{1,\ldots,r\}$ and $K^c=\{1,\ldots,r\}\setminus K$, $s$ vanishes along the loci where the factors corresponding to $K$ in $\widetilde \Ecal$ degenerate so that $f_k\colon R_k\to\PP^N$ is constant in a neighbourhood of $q_k$, and the fiber coordinates $(\lambda_{h})_{h\in K^c}$ along $p\colon\mathcal P\to\widetilde \Ecal$ are set to be $0$.
-\end{lemma}
-Call these loci $\Delta_i,i\in I$. See \cite[\S 3.2]{VZ} for a treatment of the analogous situation in the non-relative case; the study of the normal bundles is also dealt with there.
-
-It is clear that these loci are logarithmic substrata; therefore, there exists a logarithmic blow-up that principalizes them.
-We claim that $\widetilde\Dcal$ is (possibly a refinement of) this blow-up.
-This follows from the tropical discussion in Section \ref{subs:proj_bun}, and the fact that the degenerate circle that we are drawing on the $\Delta_i$ falls in the strict interior of the circle of radius $\delta$ on $\widetilde\Dcal$ (because the former only passes through vertices of horizontal degree $0$), thus all the distances from the vertices to the former circle are ordered.
-See Figure \ref{fig:principalisation} above.
-
-%%%%%%%%%%%%%%%
-\begin{comment}
-\begin{figure}
-\begin{tikzpicture}[ipe import]
-  %\useasboundingbox (0, 0) rectangle (595, 842);
-  \draw
-    (64, 720)
-     -- (112, 736)
-     -- (96, 752);
-  \draw[->]
-    (64, 704)
-     -- (128, 704);
-  \pic
-     at (64, 704) {ipe disk};
-  \pic
-     at (64, 720) {ipe disk};
-  \pic
-     at (96, 752) {ipe disk};
-  \draw[red, dotted]
-    (60.6969, 708.808)
-     arc[start angle=-161.5651, end angle=-71.5651, x radius=53.2078, y radius=-65.2105];
-  \pic[fill=white]
-     at (112, 736) {ipe fdisk};
-  \draw
-    (192, 720)
-     -- (240, 736)
-     -- (224, 752);
-  \draw[->]
-    (192, 704)
-     -- (256, 704);
-  \pic
-     at (192, 704) {ipe disk};
-  \pic
-     at (192, 720) {ipe disk};
-  \pic
-     at (224, 752) {ipe disk};
-  \pic[fill=white]
-     at (240, 736) {ipe fdisk};
-  \draw
-    (112, 736)
-     -- (128, 736);
-  \draw
-    (240, 736)
-     -- (256, 736);
-  \draw
-    (208.6374, 743.6181)
-     -- (224.4352, 750.8588);
-  \draw
-    (208.6374, 758.7577)
-     -- (225.0934, 751.517);
-  \pic
-     at (207.9791, 742.9599) {ipe disk};
-  \pic
-     at (207.9791, 758.7577) {ipe disk};
-  \pic
-     at (208, 704) {ipe cross};
-  \pic
-     at (224, 704) {ipe cross};
-  \pic
-     at (240, 704) {ipe cross};
-  \pic
-     at (96, 704) {ipe cross};
-  \pic
-     at (112, 704) {ipe cross};
-  \draw[red, dotted]
-    (231.0126, 755.9018)
-     { [rotate=-17.595] arc[start angle=135, end angle=225, x radius=21.7093, y radius=22.6274] };
-  \draw[red]
-    (188.9249, 712.0225)
-     arc[start angle=-156.5092, end angle=-115.3692, x radius=85.088, y radius=-96.462];
-\end{tikzpicture}
-\caption{On the left, a generic point of $\mathcal P$.
-On the right, a point $\Delta$.
-The dotted circle is what we have on $\mathcal P$.
-The continuous circle is the one of radius $\delta$ on $\widetilde\Dcal$; this principalises the degeneration.}\label{fig:principalisation}
-\end{figure}
-\end{comment}
-%%%%%%%%%%%%%%%%
-
-Finally, on $\widetilde\Dcal$ there are exceptional divisors $\widetilde \Delta_i$ corresponding to $\Delta_i$ in $\mathcal P$.
-By the preceding analysis, $s\in\Gamma(\mathcal P,G)$ induces a section $\tilde s\in\Gamma(\widetilde\Dcal,G(-\sum_i\widetilde\Delta_i))$ by pullback, whose vanishing locus is dimensionally transverse to the boundary, and whose open part coincides with the generic point of $\Dcal$, therefore $V(\tilde s)=\Dcal$.
-
-\subsection{Tautological contributions} Expressing the pushforward of the Chern classes of $\OO_F(1)$ and $\OO(\widetilde\Delta_i)$ in terms of tautological classes on the fiber product underlying $\Ecal$, get:
-\begin{cor}
- After pushforward to $\Ecal$, the contribution of $\Dcal$ to the invariants can be computed in terms of tautological integrals on moduli spaces of maps with lower numerics.
-\end{cor}
+The vanishing order $\lambda_{\Dcal}$ is slightly more delicate, but may be computed as the index of an explicit morphism of one-dimensional lattices, as explained in the proof of Lemma \ref{lemma vanishing order}.\end{remark}
+
+\subsubsection{$\widetilde\Dcal$ from $\Ecal$} Recall that the map $\widetilde\Dcal \to \Ecal$ is obtained by restricting the logarithmic blow-up
+\begin{equation*} \widetilde\VZ_{1,\alpha}(\PP^N|H,d) \to \ol\Mcal_{1,\alpha}(\PP^N|H,d)\end{equation*}
+to the locus $\widetilde\Dcal$.
+In toric geometry, the method for studying this restriction is as follows.
+The fan of $\widetilde\Dcal$ is obtained by projecting the star of the ray $\tau$ onto the quotient lattice, and similarly for $\Ecal$.
+The map $\widetilde\Dcal \to \Ecal$ is then a toric morphism, given by the obvious map of fans.
+In order to describe this morphism, we first subdivide the fan of $\Ecal$ so that every cone in the fan of $\widetilde\Dcal$ maps surjectively onto a cone.
+This amounts to taking a toric blow-up of $\Ecal$ which we denote by $\widetilde\Ecal$.
+There is a natural morphism $\widetilde\Dcal \to \widetilde\Ecal$ which is now flat, and this may be described as a compactification of a torus bundle on $\widetilde\Ecal$.
+
+In the logarithmic setting, we proceed as follows.
+The stratum $\widetilde\Dcal$ has a natural \emph{reduced} logarithmic structure, obtained by restricting the logarithmic structure on $\widetilde\VZ_{1,\alpha}(\PP^N|H,d)$ and then quotienting out by the normal direction to $\widetilde\Dcal$.
+Similarly, $\Ecal$ has a natural reduced logarithmic structure, which coincides with the pull-back of the product logarithmic structure on the fibre product \eqref{IIIa fibre product}.
+
+We would like to describe the tropicalisations of these logarithmic stacks.
+In fact, it is more convenient to describe the \emph{extended tropicalisations} \cite{}.
+Let $l_1,\ldots,l_m$ denote the edge lengths of the tropical target, forming co-ordinates on the cone $\sigma$.
+Then the extended tropicalisation of $\Ecal$ is obtained by intersecting the star of $\sigma$ with the face $l_1=\ldots=l_m=\infty$.
+
+For $\widetilde\Dcal$ we have on $\tau$ edge lengths $e_1=\ldots=e_r=e$ separating the core from the vertices on the radius.
+The extended tropicalisation of $\widetilde\Dcal$ is obtained by intersecting the star of $\tau$ with the face $e=\infty$.
+Since $l_1=\ldots=l_m=\infty$ implies $e=\infty$ there is certainly a morphism between these cone complexes, and it is clear this morphism is a subdivsion.
+
+Moreover we may describe the subdivision explicitly.
+
+\subsubsection{$\Dcal$ from $\widetilde\Dcal$}
 

### 2019-06-26 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
removed ipe and included png figures

--- 2019-06-26 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
@@
 \subsubsection{Combinatorial types} Recall that a boundary divisor $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ is said to be of \textbf{type $C^0$} if the core is assigned zero degree by the combinatorial type.
-In this case, the combinatorial type is not as tightly constrained as previously (it need not be a bipartite graph with a single interior vertex).
+In this case, the combinatorial type is not as tightly constrained as previously (it needs not be a bipartite graph with a single interior vertex).
 Nevertheless, we have the following lemmas:
 \begin{lemma} 
-Let $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ be a locus of type $C^0$ and let $\Delta$ be the corresponding combinatorial type.
-Then for every nonzero vertex $\diamond$ of the expanded target, the fibre of the tropical map over $\diamond$ contains exactly one stable vertex (together with a number of trivial bubbles), and at least one vertex which lies on the circle (which may or may not be stable).
+Let $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ be of type $C^0$ and let $\Delta$ be the corresponding combinatorial type.
+Then, for every vertex $\diamond\neq0$ of the expanded target, the fibre of the tropical map over $\diamond$ contains exactly one stable vertex (together with a number of trivial bubbles), and at least one vertex which lies on the circle (which may or may not be stable).
 \end{lemma}
@@
 
-Furthermore, for each vertex of the target there must always be a vertex in the preimage which lies on the radius, since otherwise there would be at least two independent tropical parameters, and so $\Dcal$ would not be a divisor.\end{proof}
+Furthermore, for each vertex of the target there must always be a vertex in the preimage which lies on the circle, since otherwise there would be at least two independent tropical parameters, and so $\Dcal$ would not be a divisor.\end{proof}
 
@@
 \begin{figure}
- \begin{tikzpicture}[ipe import]
-  %\useasboundingbox (0, 0) rectangle (595, 842);
-  \draw
-    (64, 672)
-     -- (128, 688)
-     -- (64, 704)
-     -- (64, 704);
-  \draw
-    (128, 688)
-     -- (64, 736)
-     -- (64, 736);
-  \draw[red]
-    (128, 688) circle[radius=65.9697];
-  \draw
-    (128, 688)
-     -- (112, 752)
-     -- (64, 768)
-     -- (64, 768);
-  \draw
-    (112, 752)
-     -- (64, 784)
-     -- (64, 784);
-  \pic
-     at (64, 672) {ipe disk};
-  \pic
-     at (64, 704) {ipe disk};
-  \pic
-     at (64, 736) {ipe disk};
-  \pic
-     at (64, 768) {ipe disk};
-  \pic
-     at (64, 784) {ipe disk};
-  \pic
-     at (112, 752) {ipe disk};
-  \pic
-     at (75.2242, 727.5818) {ipe cross};
-  \pic
-     at (112, 700) {ipe cross};
-  \pic
-     at (112, 692) {ipe cross};
-  \pic
-     at (112, 684) {ipe cross};
-  \pic
-     at (75.8121, 701.047) {ipe cross};
-  \pic
-     at (75.0705, 674.4385) {ipe cross};
-  \filldraw[fill=white,->]
-    (64, 608)
-     -- (208, 608);
-  \pic
-     at (64, 608) {ipe disk};
-  \draw
-    (128, 688)
-     -- (208, 688);
-  \pic
-     at (73.6978, 608.0203) {ipe cross};
-  \pic
-     at (111.8758, 608.0203) {ipe cross};
-  \pic
-     at (127.6736, 608.0203) {ipe cross};
-  \pic[fill=white]
-     at (128, 688) {ipe fdisk};
-  \node[ipe node]
-     at (86.863, 690.301) {$m$};
-  \node[ipe node]
-     at (87.521, 671.212) {$m$};
-  \node[ipe node]
-     at (48.026, 668.579) {$R_1$};
-  \node[ipe node]
-     at (48.026, 687.668) {$\ldots$};
-  \node[ipe node]
-     at (47.368, 700.832) {$R_k$};
-  \node[ipe node]
-     at (48.026, 725.846) {$R_{k+1}$};
-  \node[ipe node]
-     at (48.026, 784.429) {$R_s$};
-  \node[ipe node]
-     at (48.026, 766.657) {$\ldots$};
-  \node[ipe node]
-     at (108.585, 757.441) {$R_r$};
-  \node[ipe node]
-     at (80, 744.935) {$\ldots$};
-  \node[ipe node]
-     at (130.965, 677.794) {$E$};
-\end{tikzpicture}
+\includegraphics[scale=.6]{ray_example}
 \caption{A ray of type $C^0$.}\label{fig:ray_example}
@@
 where $E$ is the set of edges of the (stabilised) dual graph, and the fibre product is taken over the appropriate evaluation maps.
-Note that only the factor corresponding to the core vertex has non-zero genus, and that it must have zero degree.
+Note that only the factor corresponding to the core vertex has non-zero genus, and that it has zero degree by assumption.
 
@@
 
-\begin{comment}
-In this case, the core has (horizontal) degree $0$ and is mapped into $H$. We start by describing the relevant combinatorial types of rays in $\widetilde{\VZ}_{1,\alpha}(\PP^N|H,d)$.
-\begin{lemma} In what follows it is understood that we insert trivial bubbles whenever the curve or target need to be subdivided in order for the image and preimage of every polyhedral subcomplex to be a union of polyhedral subcomplexes.
- \begin{enumerate}
-  \item The core is represented by a single vertex of genus one and degree zero, tropically mapped to $\RR_{>0}$.
-  \item The vertices adjacent to the core with maximal expansion factor are tropically mapped to $0$.
-  \item For every point of the target different from $0$, the fiber of the tropical map contains at most one stable vertex, which either is the core or lies on the circle.
-  \item $x_k$ is supported by a vertex tropically mapped to $\RR_{>0}$.
- \end{enumerate}
-\end{lemma}
-\begin{proof}
- By assumption, the core is mapped to $\RR_>0$, hence the distance of its image from $0$ is one parameter $\ell$; since we are describing a ray, all other parameters have to be related to $\ell$, and the only way it can be so is via the alignment.
-If the fiber over $c>0$ contains two stable vertices, because both the insertions and the factorisation condition are pulled back from the moduli space without expansions, it can be seen as in Lemma \ref{lem:combs} that the collapsing morphism $\Dcal\to\Fcal$ has positive-dimensional fibers (disconnected rubber), so the corresponding combinatorial type does not contribute to the invariants.
-We conclude that every stable vertex over $\RR_{>0}$ different from the core has to lie on the circle.
-\end{proof}
-\begin{center}
+\subsubsection{From $\Ecal$ to $\widetilde{\Dcal}$} The reader should bear the following construction from toric geometry in mind: suppose we subdivide a fan, and we want to describe the relation between the varieties corresponding to a cone $\rho$ of the subdivision, and to the original cone $\sigma$ containing it, respectively.
+For any cone $\tau$, the fan of $X_\tau$ is obtained by projecting the star of $\tau$ to the quotient $N_\tau=N_{\RR}/\langle\tau\rangle_{\RR}$ of the ambient vector space by the linear span of $\tau$.\footnote{This can be encoded in the formalism of extended tropicalisations, see \cite{ACP} and references therein.} Notice that the dimension of the vector spaces $N_\rho$ and $N_\sigma$ (or the corresponding toric varieties) is off by the difference $c$ between the dimension of the cones.
+The image of $\Sigma_\rho$ provides a subdivision of $\Sigma_\sigma$.
+The geometric content is that $X_\rho$ is obtained as an appropriate compactification of a toric bundle of dimension $c$ over $X_\sigma$.
+%observe that the fiber dimension may not be constant (but it can be made so by blowing up $X_{\sigma}$, see \cite[Lemma 4.1]{AK}).
+
+We start by describing the modification of $\Ecal$ corresponding to the subdivision of the last paragraph; really, we only need to unravel the combinatorics partially, in order to describe an intermediate blowup $\widetilde\Ecal\to \Ecal$, such that $\Dcal$ factors through $\widetilde\Ecal$, and all the structures that we need to name in what follows make sense on $\widetilde\Ecal$ already.
+
+Let $V_{0,\delta}\subseteq V_0$ be the subset of vertices lying on the circle (besides being sent to $0$ by the tropical map).
+Notice that they all have the same expansion factor $m$, therefore they are at the same distance from the core, generically on $\Ecal$.\footnote{Indeed, generically, these vertices do not produce any subdivision of the target, so they contribute to the relative dimension of $\widetilde\Dcal\to\Ecal$ as one.} Another way to see the generic alignment is the following: the normal bundles corresponding to these nodes can be expressed as $\mathbb T_{R_v,q_v}\otimes\mathbb T_{E,q_v}$; for two different vertices, the right-hand factors are canonically identified thanks to the group structure on the elliptic curve, whereas the $m$-th powers of the left-hand factors are canonically identified by comparison with the target tangent line, and $\rho$ can be seen as taking an $m$-th root of this preferred isomophism.
+On the other hand, the alignment does not persist when the curves degenerate (see Figure \ref{fig:fwise_align}).
+
 \begin{figure}
- \begin{tikzpicture}[ipe import]
-  %\useasboundingbox (0, 0) rectangle (595, 842);
-  \draw
-    (64, 672)
-     -- (128, 688)
-     -- (64, 704)
-     -- (64, 704);
-  \draw
-    (128, 688)
-     -- (64, 736)
-     -- (64, 736);
-  \draw[red]
-    (128, 688) circle[radius=65.9697];
-  \draw
-    (128, 688)
-     -- (112, 752)
-     -- (64, 768)
-     -- (64, 768);
-  \draw
-    (112, 752)
-     -- (64, 784)
-     -- (64, 784);
-  \pic
-     at (64, 672) {ipe disk};
-  \pic
-     at (64, 704) {ipe disk};
-  \pic
-     at (64, 736) {ipe disk};
-  \pic
-     at (64, 768) {ipe disk};
-  \pic
-     at (64, 784) {ipe disk};
-  \pic
-     at (112, 752) {ipe disk};
-  \pic
-     at (75.2242, 727.5818) {ipe cross};
-  \pic
-     at (112, 700) {ipe cross};
-  \pic
-     at (112, 692) {ipe cross};
-  \pic
-     at (112, 684) {ipe cross};
-  \pic
-     at (75.8121, 701.047) {ipe cross};
-  \pic
-     at (75.0705, 674.4385) {ipe cross};
-  \filldraw[fill=white,->]
-    (64, 608)
-     -- (208, 608);
-  \pic
-     at (64, 608) {ipe disk};
-  \draw
-    (128, 688)
-     -- (208, 688);
-  \pic
-     at (73.6978, 608.0203) {ipe cross};
-  \pic
-     at (111.8758, 608.0203) {ipe cross};
-  \pic
-     at (127.6736, 608.0203) {ipe cross};
-  \pic[fill=white]
-     at (128, 688) {ipe fdisk};
-  \node[ipe node]
-     at (86.863, 690.301) {$m$};
-  \node[ipe node]
-     at (87.521, 671.212) {$m$};
-  \node[ipe node]
-     at (48.026, 668.579) {$R_1$};
-  \node[ipe node]
-     at (48.026, 687.668) {$\ldots$};
-  \node[ipe node]
-     at (47.368, 700.832) {$R_k$};
-  \node[ipe node]
-     at (48.026, 725.846) {$R_{k+1}$};
-  \node[ipe node]
-     at (48.026, 784.429) {$R_s$};
-  \node[ipe node]
-     at (48.026, 766.657) {$\ldots$};
-  \node[ipe node]
-     at (108.585, 757.441) {$R_r$};
-  \node[ipe node]
-     at (80, 744.935) {$\ldots$};
-  \node[ipe node]
-     at (130.965, 677.794) {$E$};
-\end{tikzpicture}
-\caption{A ray of type $C^0$.}\label{fig:ray_example}
-\end{figure}
-\end{center}
-
-See Figure \ref{fig:ray_example}.
-We observe that the corresponding stratum $\Ecal$ of $\ol\Mcal_{1,\alpha}(\PP^N|H,d)$ has logarithmic codimension equal to the number of non-core vertices mapping to $\RR_{>0}$: indeed, the combinatorial type of $\Ecal$ can be read off by forgetting the circle, and the logarithmic codimension in $\ol\Mcal_{1,\alpha}(\PP^N|H,d)$ is accounted for by the number of subdivisions of the target.
-The discrepancy in dimension is to be expected, as the loci of type $C^0$ are contained in the exceptional locus of the blow-up.
-
-The geometry of $\widetilde\Dcal\to\Ecal$ is encoded by the combinatorics of the alignment.
-The reader should bear the following toric construction in mind: suppose we subdivide a fan, and we want to describe the relation between the varieties corresponding respectively to a cone $\rho$ of the subdivision, and the original cone $\sigma$ containing it.
-The fan of $X_\tau$ is obtained by projecting the star of $\tau$ to the quotient $N_\tau=N_{\RR}/\langle\tau\rangle_{\RR}$ of the ambient vector space by the linear span of the cone\footnote{We find it useful to encode this within the formalism of extended tropicalisations \cite{?}.}.
-Notice that the dimension of the vector spaces $N_\rho$ and $N_\sigma$ (or the corresponding toric varieties) is off by the difference $c$ between the dimension of the cones.
-Furthermore, we may need to subdivide the fan of $X_\sigma$ in order for cones of $\Sigma_\rho$ to be mapped surjectively to cones of $\Sigma_\sigma$.
-The geometric interpretation of this is that $X_\tau$ is obtained as an appropriate compactification of a toric bundle of dimension $c$ over $X_\sigma$; observe that the fiber dimension may not be constant (but it can be made so by blowing up $X_{\sigma}$, see \cite[Lemma 4.1]{AK}).
-It is a fundamental insight due to Tevelev \cite{Tevelev} that a good compactification of the toric bundle is suggested by the tropicalisation of the locus we are interested in: here, ``good'' means that the intersection of the interesting locus with the boundary is dimensionally transverse.
-In the case at hand, the interesting locus is that of maps satisfying the factorisation property (i.e.
-smoothable maps), and the tropicalisation has been worked out in \cite{RSPW2} to consist of well-spaced maps.
-
-We proceed to describe $\Dcal$ step-by-step, building on $\Ecal$.
-
-\subsubsection{The fiber product} We start from the finite splitting morphism
-\begin{multline}\label{eq:product}
- \rho\colon \Ecal \to \left(\prod_{i=1}^k \ol\Mcal_{0,\alpha^{(i)}\cup(m)}(\PP^N|H,d_i) \times \prod_{i=k+1}^s \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i)\right)\times_{H^s} \\ \prod_{j=k+1}^{r}\ol\Mcal_{0,\alpha^{(j)}\cup(-m_i)_{i \in I_j\subseteq\{k+1,\ldots,s\}}\cup(\mu_j)}^{\leftrightarrow}(P|H_0+H_\infty,d_j)\times_{H^{r-k}} \\
- \ol\Mcal_{1,\alpha^{(0)}\cup(-m,\ldots,-m,-\mu_{k+1},\ldots,-\mu_r)\cup(-m_i)_{i\in\{k+1,\ldots,s\}\setminus(\bigcup I_j)}}^{\leftrightarrow}(P|H_0+H_\infty,0)
-\end{multline}
-The degree of $\rho$ can be computed as in Lemma \ref{lem:saturation} above.
-From the logarithmic point of view, $\rho$ is a saturation map; generically it should be thought of as follows.
-On the fiber product, the tangent vectors of the components on level $0$ (corresponding to the factors in the first line above) are identified with the target tangent line up to finite powers; the saturation is taking roots of these isomorphisms (it is interesting to notice that it fails precisely on Gathmann's boundary comb loci).
-\end{comment}
-
-\subsubsection{From $\Ecal$ to $\widetilde{\Dcal}$} The reader should bear the following construction from toric geometry in mind: suppose we subdivide a fan, and we want to describe the relation between the varieties corresponding respectively to a cone $\rho$ of the subdivision, and the original cone $\sigma$ containing it.
-The fan of $X_\tau$ is obtained by projecting the star of $\tau$ to the quotient $N_\tau=N_{\RR}/\langle\tau\rangle_{\RR}$ of the ambient vector space by the linear span of the cone\footnote{We find it useful to encode this within the formalism of extended tropicalisations \cite{?}.}.
-Notice that the dimension of the vector spaces $N_\rho$ and $N_\sigma$ (or the corresponding toric varieties) is off by the difference $c$ between the dimension of the cones.
-The image of $\Sigma_\rho$ provides a subdivision of the fan of $X_\sigma$.
-The geometric content is that $X_\tau$ is obtained as an appropriate compactification of a toric bundle of dimension $c$ over $X_\sigma$.
-%observe that the fiber dimension may not be constant (but it can be made so by blowing up $X_{\sigma}$, see \cite[Lemma 4.1]{AK}).
-
-We start by describing the modification of $\Ecal$ corresponding to the subdivision of the last paragraph; really, we only need to unravel the combinatorics partially, in order to describe an intermediate blowup $\widetilde\Ecal\to \Ecal$, such that $\Dcal$ factors through $\widetilde\Ecal$, and all the structures that we need to name in what follows make sense on $\widetilde\Ecal$ already.
-
-Let $V_{0,\delta}\subseteq V_0$ be the subset of vertices lying on the circle (besides being sent to $0$ by the tropical map).
-Notice that they all have the same expansion factor $m$, therefore they are at the same distance from the core, generically on $\Ecal$.\footnote{Indeed, generically, these vertices do not contribute any subdivision of the target, i.e.
-they do not affect the relative dimension of $\widetilde\Dcal\to\Ecal$.} Another way to see the generic alignment is the following: the normal bundles corresponding to these nodes can be expressed as $\mathbb T_{R_v,q_v}\otimes\mathbb T_{E,q_v}$; for two different vertices, the right-hand factors are canonically identified thanks to the group structure on the elliptic curve, whereas the $m$-th powers of the left-hand factors are canonically identified by comparison with the target tangent line, and $\rho$ can be seen as taking an $m$-th root of this preferred isomophism.
-On the other hand, the alignment does not persist when the curves degenerate (see Figure \ref{fig:fwise_align}).
-
-\begin{figure}
- \begin{tikzpicture}[ipe stylesheet,scale=.7]
-  %\useasboundingbox (0, 0) rectangle (595, 842);
-  \pic
-     at (129.8488, 703.2932) {ipe disk};
-  \pic
-     at (97.8488, 719.2932) {ipe disk};
-  \pic
-     at (97.8488, 687.2932) {ipe disk};
-  \draw
-    (97.8488, 719.2932)
-     -- (129.8488, 703.2932)
-     -- (97.8488, 687.2932);
-  \draw
-    (129.8488, 703.2932)
-     -- (161.8488, 687.2932);
-
-  \draw
-    (193.8488, 671.2932)
-     -- (225.8488, 655.2932);
-  \draw
-    (225.8488, 655.2932)
-     -- (193.8488, 639.2932);
-    \draw[ipe dash dashed]
-   (193.8488, 671)
-    -- (161.8488, 687);
-  \draw[ipe dash dashed]
-    (193.8488, 639.2932)
-     -- (161.8488, 623.2932);
-  \draw
-    (161.8488, 623.2932)
-     -- (129.8488, 607.2932);
-  \pic
-     at (146.637, 615.0615) {ipe disk};
-  \draw
-    (129.8488, 607.2932)
-     -- (97.8488, 591.2932)
-     -- (97.8488, 591.2932);
-  \draw
-    (147.2948, 615.0622)
-     -- (97.2686, 638.1002)
-     -- (97.2686, 638.1002);
-  \pic
-     at (96.6103, 637.4422) {ipe disk};
-  \pic
-     at (97.9268, 590.7072) {ipe disk};
-  \pic
-     at (130.1808, 622.9607) {ipe cross};
-  \pic
-     at (130.1808, 607.1635) {ipe cross};
-  \pic
-     at (145.9788, 695.3672) {ipe cross};
-  \draw[-ipe linear]
-    (97.8488, 575.2932)
-     -- (257.8488, 575.2932);
-  \pic
-     at (97.8488, 575.2932) {ipe disk};
-  \pic
-     at (129.8488, 575.2932) {ipe cross};
-  \pic
-     at (145.8488, 575.2932) {ipe cross};
-  \pic
-     at (225.8488, 575.2932) {ipe cross};
-  \draw
-    (129.8488, 703.2932)
-     -- (257.8488, 703.2932);
-  \draw
-    (225.8488, 655.2932)
-     -- (257.8488, 655.2932)
-     -- (257.8488, 655.2932);
-  \draw
-    (146.3018, 614.861)
-     -- (258.5378, 614.404);
-  \node[ipe node]
-     at (189.423, 676.278) {$m$};
-  \node[ipe node]
-     at (189.094, 629.543) {$m$};
-  \node[ipe node]
-     at (111.421, 715.773) {$m_1$};
-  \node[ipe node]
-     at (110.104, 590.707) {$m_2$};
-  \node[ipe node]
-     at (110.763, 564.378) {$\ell_1$};
-  \node[ipe node]
-     at (133.801, 564.377) {$\ell_2$};
-  \node[ipe node]
-     at (146.308, 543.972) {$\frac{\ell_1}{m_1}+\frac{\ell_2}{m} \lesseqgtr \frac{\ell_1+\ell_2}{m_2}$};
-  \pic
-     at (473.6651, 658.9228) {ipe disk};
-  \pic
-     at (353.8488, 719.2932) {ipe disk};
-  \pic
-     at (353.8488, 687.2932) {ipe disk};
-  \draw
-    (353.8488, 719.2932)
-     -- (385.8488, 703.2932)
-     -- (353.8488, 687.2932);
-  \draw
-    (386.7731, 703.2932)
-     -- (418.7731, 687.2932);
-  \draw[ipe dash dashed]
-    (417.8488, 687.2932)
-     -- (449.8488, 671.2932)
-     -- (449.8488, 671.2932);
-
-  \draw
-    (449.8488, 671.2932)
-     -- (481.8488, 655.2932)
-     -- (481.8488, 655.2932);
-  \draw
-    (481.8488, 655.2932)
-     -- (449.8488, 639.2932)
-     -- (449.8488, 639.2932);
-  \draw[ipe dash dashed]
-    (449.8488, 639.2932)
-     -- (417.8488, 623.2932);
-  \draw
-    (417.8488, 623.2932)
-     -- (385.8488, 607.2932);
-  \pic
-     at (457.1756, 642.7929) {ipe disk};
-  \draw
-    (385.8488, 607.2932)
-     -- (353.8488, 591.2932)
-     -- (353.8488, 591.2932);
-  \pic
-     at (352.6103, 622.6521) {ipe disk};
-  \pic
-     at (353.9268, 590.7072) {ipe disk};
-  \pic
-     at (458.2826, 667.3311) {ipe cross};
-  \pic
-     at (459.207, 575.7344) {ipe cross};
-  \draw[-ipe linear]
-    (353.8488, 575.2932)
-     -- (513.8488, 575.2932);
-  \pic
-     at (353.8488, 575.2932) {ipe disk};
-  \pic
-     at (385.8488, 575.2932) {ipe cross};
-  \pic
-     at (475.7994, 575.2932) {ipe cross};
-  \pic
-     at (481.8488, 575.2932) {ipe cross};
-  \draw[shift={(472.741, 659.847)}, xscale=0.3271, yscale=-1.7893]
-    (0, 0)
-     -- (128, 0);
-  \draw
-    (481.8488, 655.2932)
-     -- (513.8488, 655.2932)
-     -- (513.8488, 655.2932);
-  \draw[shift={(459.26, 642.878)}, xscale=0.4834, yscale=0.4807]
-    (0, 0)
-     -- (112.236, -0.457);
-  \draw[red]
-    (482.3765, 654.0394) circle[radius=9.9987];
-  \draw
-    (354.8117, 621.686)
-     -- (386.2407, 606.8958);
-  \pic
-     at (386.2407, 606.8958) {ipe disk};
-  \pic
-     at (386.2407, 703.956) {ipe disk};
-  \draw[red]
-    (360.3506, 584.6012)
-     arc[start angle=160.4967, end angle=217.0656, x radius=120.4239, y radius=-143.3401];
-  \pic
-     at (473.9974, 650.6919) {ipe cross};
-  \pic
-     at (364.92, 693.131) {ipe cross};
-  \pic
-     at (372.3151, 710.6943) {ipe cross};
-  \pic
-     at (359.3737, 593.2977) {ipe cross};
-  \draw
-    (226.3225, 655.8881)
-     -- (258.6759, 665.1319);
-  \draw
-    (226.3225, 654.0394)
-     -- (258.6759, 646.6443);
-  \draw[-ipe linear]
-    (271.6173, 766.814)
-     -- (337.2485, 767.7384);
-
-  \pic
-     at (272.5417, 782.5285) {ipe disk};
-  \pic
-     at (271.6173, 815.8063) {ipe disk};
-  \draw
-    (305.8194, 798.2431)
-     -- (272.5417, 815.8063);
-  \draw
-    (305.8194, 798.2431)
-     -- (272.5417, 782.5285)
-     -- (272.5417, 782.5285);
-  \draw
-    (272.5417, 782.5285)
-     -- (336.3241, 782.5285);
-  \draw
-    (272.5417, 815.8063)
-     -- (336.3241, 814.8819);
-  \draw
-    (304.8951, 799.1674)
-     -- (335.3997, 799.1674);
-  \draw
-    (305.8194, 799.1674)
-     -- (336.3241, 804.7137);
-  \draw
-    (305.8194, 798.2431)
-     -- (335.3997, 792.6968);
-  \draw
-    (387.1651, 703.956)
-     -- (511.0324, 703.956)
-     -- (511.0324, 703.0316);
-  \draw
-    (388.0895, 605.0471)
-     -- (511.9568, 605.0471);
-  \pic
-     at (272.5417, 766.814) {ipe disk};
-  \draw[red]
-    (304.8951, 797.3187) circle[radius=35.9679];
-
-    \pic[fill=white]
-     at (225.8488, 655.2932) {ipe fdisk};
-
-     \pic[fill=white]
-     at (481.8488, 655.2932) {ipe fdisk};
-
-     \pic[fill=white]
-     at (304.8951, 799.1674) {ipe fdisk};
-\end{tikzpicture}
+\includegraphics[scale=.5]{factorwise_alignment}
 \caption{Two degenerations of the combinatorial type above, which represents a ray.
@@
 
-We modify the boundary of $\Ecal$\footnote{With the log structure obtained by pulling back from Kim's space and modding out by $\mathbb N^{\codim (\sigma)}$, i.e.
-considering the edges of $E$ to have \emph{infinite length}.} as follows:
-\begin{enumerate}
- \item radially aligning the core, and imposing factorisation, thus effectively replacing
- \[\ol\Mcal^{\leftrightarrow}_{1,\mu}(P|H_0+H_\infty)\quad\text{by}\quad\VZ^{\leftrightarrow}_{1,\mu}(P|H_0+H_\infty)\]
- in the product above, with the consequence of introducing a reduced rubber;
+We modify $\Ecal$\footnote{With the log structure obtained by pulling back from Kim's space and modding out by $\mathbb N^{\codim (\sigma)}$, i.e.
+considering the edges of $E$ to have \emph{infinite length}.} along the boundary as follows:
+\begin{enumerate}[leftmargin=.5 cm]
+ \item radially aligning the core, and imposing fiberwise factorisation, thus replacing
+ \[\ol\Mcal^{\leftrightarrow}_{1,\mu}(P|H_0+H_\infty,d=0)\quad\text{by}\quad\VZ^{\leftrightarrow}_{1,\mu}(P|H_0+H_\infty,d=0)\]
+ in the product above, thus introducing a reduced rubber with point target;
  \item requiring that any degeneration of $V_{0,\delta}$ (resp.
-$\forall v\in V_{>0,\delta}$) remains centrally aligned with respect to the core;\footnote{Notice that this requires us to blow up some diagonal subloci of the product above, see Figure \ref{fig:fwise_align}} this has the effect that on the whole of $\widetilde E$ - including the boundary -, for each $v\in \{V_{0,\delta}\}\cup V_{>0,\delta}$, it is always possible to tell the components of the curve that are at distance $\delta$ from the core along the path denominated $v$, and, if there is more than one for the same $v$, the lengths of these paths are identified, so as to define line bundles $\OO(\delta_v), \forall v\in \{V_{0,\delta}\}\cup V_{>0,\delta}$.
+$\forall v\in V_{>0,\delta}$) remains centrally aligned with respect to the core;\footnote{Notice that this requires us to blow up some diagonal subloci of the product above, see Figure \ref{fig:fwise_align}} as a consequence, on the whole of $\widetilde \Ecal$ - including the boundary -, for each $v\in \{V_{0,\delta}\}\cup V_{>0,\delta}$, it is always possible to tell the components of the curve that are at distance $\delta$ from the core along the path denominated $v$, and, if there is more than one for the same $v$, the lengths of these paths are identified, so as to define line bundles $\OO(\delta_v), \forall v\in \{V_{0,\delta}\}\cup V_{>0,\delta}$.
 \end{enumerate}
@@
  All of the line bundles $\OO(\delta_v)$ share a common factor $\mathbb T_E$, the universal tangent line to the elliptic curve (appropriately twisted by bubbling loci as in \cite[\S 2.3]{VZ}); removing this, when the curve has the prescribed dual graph, $\OO(\delta_v)$ is isomorphic to the tangent line to the rational tail $R_v$ at the gluing node $q_v$ (with the caveat that all those corresponding to $V_{0,\delta}$ are canonically identified).
-This is the open stratum of the moduli space of attaching data \cite[\SS 2.2-2.3]{SMY2}.
-On the boundary, the circle of radius $\delta$ will pass through a subset of $\{V_{0,\delta}\}\cup V_{>0,\delta}$, while cutting the complementary subset along the edge between the core and $v$; correspondingly, there is a destabilisation of the curve, and an elliptic singularity containing strictly semistable branches.
+This is the open stratum of the moduli space of attaching data \cite[\S\S 2.2-2.3]{SMY2}.
+On the fiber boundary, the circle of radius $\delta$ will pass through a subset of $\{V_{0,\delta}\}\cup V_{>0,\delta}$, while cutting the complementary subset along the edge between the core and $v$; correspondingly, there is a destabilisation of the curve, and an elliptic singularity containing strictly semistable branches.
 Tropically, pushing some of the vertices off the circle creates new finite-length edges with coordinates $\ell_v\in\RR_{\geq_0}$ (see Figure \ref{fig:off_we_go}); not all of them can be strictly positive, because the circle needs to pass through at least one vertex (of positive horizontal degree).
@@
 \begin{figure}
-\begin{tikzpicture}[ipe import,scale=.8]
-  %\useasboundingbox (0, 0) rectangle (595, 842);
-  \draw
-    (64, 672)
-     -- (128, 688)
-     -- (64, 704)
-     -- (64, 704);
-  \draw
-    (128, 688)
-     -- (64, 736)
-     -- (64, 736);
-  \draw[red]
-    (128, 688) circle[radius=65.9697];
-  \draw
-    (128, 688)
-     -- (112, 752)
-     -- (64, 768)
-     -- (64, 768);
-  \draw
-    (112, 752)
-     -- (64, 784)
-     -- (64, 784);
-  \pic
-     at (64, 672) {ipe disk};
-  \pic
-     at (64, 704) {ipe disk};
-  \pic
-     at (64, 736) {ipe disk};
-  \pic
-     at (64, 768) {ipe disk};
-  \pic
-     at (64, 784) {ipe disk};
-  \pic
-     at (112, 752) {ipe cross};
-  \pic
-     at (75.2242, 727.582) {ipe cross};
-  \pic
-     at (112, 700) {ipe cross};
-  \pic
-     at (112, 692) {ipe cross};
-  \pic
-     at (112, 684) {ipe cross};
-  \pic
-     at (75.8121, 701.047) {ipe cross};
-  \pic
-     at (75.0704, 674.4388) {ipe cross};
-  \filldraw[fill=white]
-    (64, 608)
-     -- (208, 608)
-     -- (208, 608);
-  \pic
-     at (64, 608) {ipe disk};
-  \draw
-    (128, 688)
-     -- (208, 688)
-     -- (208, 688);
-  \pic
-     at (73.6978, 608.02) {ipe cross};
-  \pic
-     at (111.876, 608.0202) {ipe cross};
-  \pic
-     at (127.674, 608.0205) {ipe cross};
-  \pic[fill=white]
-     at (128, 688) {ipe fdisk};
-  \node[ipe node]
-     at (86.863, 690.301) {$m$};
-  \node[ipe node]
-     at (87.521, 671.212) {$m$};
-  \draw
-    (128, 688)
-     -- (91.4703, 741.643);
-  \draw
-    (128, 688)
-     -- (160.586, 745.593)
-     -- (160.586, 745.593);
-  \pic
-     at (91.4703, 741.643) {ipe disk};
-  \pic
-     at (160.486, 745.417) {ipe disk};
-  \draw[shift={(91.47, 741.051)}, xscale=0.95, yscale=0.6996]
-    (0, 0)
-     -- (-26.9879, 7.241)
-     -- (-26.9879, 7.241);
-  \draw
-    (160.486, 745.417)
-     -- (64.4824, 799.569);
-  \draw
-    (160.486, 745.417)
-     -- (208.637, 745.593);
-  \draw
-    (92.1286, 740.985)
-     -- (64.4824, 754.15);
-  \pic
-     at (64.4824, 746.909) {ipe disk};
-  \pic
-     at (64.4824, 798.91) {ipe disk};
-  \pic
-     at (64.4824, 753.492) {ipe disk};
-  \draw
-    (289.118, 672.0005)
-     -- (353.118, 688.0005)
-     -- (289.118, 704.0005)
-     -- (289.118, 704.0005);
-  \draw
-    (353.118, 688.0005)
-     -- (289.118, 736.0005)
-     -- (289.118, 736.0005);
-  \draw[red]
-    (353.118, 688.0005) circle[radius=65.9697];
-  \draw
-    (353.118, 688.0005)
-     -- (337.118, 752.0005)
-     -- (289.118, 768.0005)
-     -- (289.118, 768.0005);
-  \draw
-    (337.118, 752.0005)
-     -- (289.118, 784.0005)
-     -- (289.118, 784.0005);
-  \pic
-     at (289.118, 672.0005) {ipe disk};
-  \pic
-     at (289.118, 704.0005) {ipe disk};
-  \pic
-     at (289.118, 736.0005) {ipe disk};
-  \pic
-     at (289.118, 768.0005) {ipe disk};
-  \pic
-     at (289.118, 784.0005) {ipe disk};
-  \pic
-     at (337.118, 752.0005) {ipe cross};
-  \pic
-     at (300.3422, 727.5825) {ipe cross};
-  \pic
-     at (337.118, 700.0005) {ipe cross};
-  \pic
-     at (337.118, 692.0005) {ipe cross};
-  \pic
-     at (337.118, 684.0005) {ipe cross};
-  \pic
-     at (300.9301, 701.0475) {ipe cross};
-  \pic
-     at (300.1889, 674.4392) {ipe cross};
-  \filldraw[fill=white]
-    (289.118, 608.0005)
-     -- (433.118, 608.0005)
-     -- (433.118, 608.0005);
-  \pic
-     at (289.118, 608.0005) {ipe disk};
-  \draw
-    (353.118, 688.0005)
-     -- (433.118, 688.0005)
-     -- (433.118, 688.0005);
-  \pic
-     at (298.8158, 608.0205) {ipe cross};
-  \pic
-     at (336.994, 608.0207) {ipe cross};
-  \pic
-     at (352.792, 608.0209) {ipe cross};
-  \pic[fill=white]
-     at (353.118, 688.0005) {ipe fdisk};
-  \node[ipe node]
-     at (311.98, 690.301) {$m$};
-  \node[ipe node]
-     at (312.639, 671.212) {$m$};
-  \draw[shift={(353.118, 687.999)}, xscale=1.1287, yscale=1.1615]
-    (0, 0)
-     -- (-36.5297, 53.643);
-  \draw[shift={(353.119, 687.997)}, xscale=1.4269, yscale=1.3567]
-    (0, 0)
-     -- (32.586, 57.593)
-     -- (32.586, 57.593);
-  \pic
-     at (310.6643, 751.5171) {ipe disk};
-  \pic
-     at (400.086, 767.1394) {ipe disk};
-  \draw[shift={(311.745, 750.197)}, xscale=0.8205, yscale=-0.5452]
-    (0, 0)
-     -- (-26.9879, 7.241)
-     -- (-26.9879, 7.241);
-  \draw[shift={(399.543, 767.54)}, xscale=1.1319, yscale=0.5704]
-    (0, 0)
-     -- (-96.0036, 54.152);
-  \draw[shift={(400.744, 767.146)}, xscale=0.6446, yscale=-1.3688]
-    (0, 0)
-     -- (48.151, 0.176);
-  \draw[shift={(311.717, 751.113)}, xscale=0.8, yscale=0.1453]
-    (0, 0)
-     -- (-27.6462, 13.165);
-  \pic
-     at (289.6004, 746.9095) {ipe disk};
-  \pic
-     at (289.6004, 798.9105) {ipe disk};
-  \pic
-     at (289.6004, 753.4925) {ipe disk};
-  \pic
-     at (387.02, 744.935) {ipe cross};
-  \pic
-     at (317.246, 742.961) {ipe cross};
-  \node[ipe node]
-     at (315.273, 748.884) {$\ell_{j_1}$};
-  \node[ipe node]
-     at (397.553, 752.175) {$\ell_{j_2}$};
-\end{tikzpicture}
+\includegraphics[scale=.3]{off_we_go}
 \caption{Moving vertices off the circle creates new tropical parameters.}\label{fig:off_we_go}
@@
 
-Notice that $\mathcal P$ is well-defined on the whole of $\widetilde \Ecal$, while $\widetilde \Dcal\to \mathcal P$ is in fact a modification oof the boundary, as dictated by the alignment procedure.
+Notice that $\mathcal P$ is well-defined on the whole of $\widetilde \Ecal$, while $\widetilde \Dcal\to \mathcal P$ is in fact a modification along the boundary, as dictated by the alignment procedure.
 In the next section, we extrapolate what we need from this combinatorial setup in order to describe $\Dcal$ explicitly.
@@
 \begin{figure}
-\begin{tikzpicture}[ipe import]
-  %\useasboundingbox (0, 0) rectangle (595, 842);
-  \draw
-    (64, 720)
-     -- (112, 736)
-     -- (96, 752);
-  \draw[->]
-    (64, 704)
-     -- (128, 704);
-  \pic
-     at (64, 704) {ipe disk};
-  \pic
-     at (64, 720) {ipe disk};
-  \pic
-     at (96, 752) {ipe disk};
-  \draw[red, dotted]
-    (60.6969, 708.808)
-     arc[start angle=-161.5651, end angle=-71.5651, x radius=53.2078, y radius=-65.2105];
-  \pic[fill=white]
-     at (112, 736) {ipe fdisk};
-  \draw
-    (192, 720)
-     -- (240, 736)
-     -- (224, 752);
-  \draw[->]
-    (192, 704)
-     -- (256, 704);
-  \pic
-     at (192, 704) {ipe disk};
-  \pic
-     at (192, 720) {ipe disk};
-  \pic
-     at (224, 752) {ipe disk};
-  \pic[fill=white]
-     at (240, 736) {ipe fdisk};
-  \draw
-    (112, 736)
-     -- (128, 736);
-  \draw
-    (240, 736)
-     -- (256, 736);
-  \draw
-    (208.6374, 743.6181)
-     -- (224.4352, 750.8588);
-  \draw
-    (208.6374, 758.7577)
-     -- (225.0934, 751.517);
-  \pic
-     at (207.9791, 742.9599) {ipe disk};
-  \pic
-     at (207.9791, 758.7577) {ipe disk};
-  \pic
-     at (208, 704) {ipe cross};
-  \pic
-     at (224, 704) {ipe cross};
-  \pic
-     at (240, 704) {ipe cross};
-  \pic
-     at (96, 704) {ipe cross};
-  \pic
-     at (112, 704) {ipe cross};
-  \draw[red, dotted]
-    (231.0126, 755.9018)
-     { [rotate=-17.595] arc[start angle=135, end angle=225, x radius=21.7093, y radius=22.6274] };
-  \draw[red]
-    (188.9249, 712.0225)
-     arc[start angle=-156.5092, end angle=-115.3692, x radius=85.088, y radius=-96.462];
-\end{tikzpicture}
+\includegraphics[scale=.5]{principalisation}
 \caption{On the left, a generic point of $\mathcal P$.

### 2019-06-26 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
Wrote more on obtaining Dtilde from E

--- 2019-06-26 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
@@
 The remaining type IIIb case, however, is entirely new.
-In this section we provide a recursive description of these boundary divisors; this constitutes the technical heart of the paper.
-
-\subsubsection{Description of the possible combinatorial types} Recall that a boundary divisor $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ is said to be of type IIIb if the core is assigned degree zero by the combinatorial type (this is the only case which we did not treat in Lemma \ref{lem:combs}).
+In this section we provide a recursive description of these boundary divisors.
+This constitutes the technical heart of the paper.
+
+\subsubsection{Possible combinatorial types} Recall that a boundary divisor $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ is said to be of type IIIb if the core is assigned degree zero by the combinatorial type (this is the case which was ignored in Lemma \ref{lem:combs} and the subsequent discussion).
 In this case, the combinatorial type is not as tightly constrained as before; the target may expand multiple times, and as such the combinatorial type need not be a bipartite graph with a single interior vertex.
@@
 Let $\Dcal$ be a locus of type IIIb and let $\Delta$ be the corresponding combinatorial type.
-Then for every nonzero vertex $\diamond$ of the expanded tropical target, the fibre of the tropical map over $\diamond$ contains:
-\begin{enumerate}
-\item exactly one stable vertex (together with a number of trivial bubbles);
-\item at least one vertex which lies on the radius (which may or may not be stable).
-\end{enumerate}
+Then for every nonzero vertex $\diamond$ of the expanded tropical target, the fibre of the tropical map over $\diamond$ contains exactly one stable vertex, which lies on the radius.
 \end{lemma}
@@
 
-Furthermore, for each vertex of the target there must always be a vertex in the preimage which lies on the radius, since otherwise there would be at least two independent tropical parameters, and so $\Dcal$ would not be a divisor.\end{proof}
+Furthermore, for each vertex of the target there must always be at least one vertex in the preimage which lies on the radius, since otherwise there would be at least two independent tropical parameters, and so $\Dcal$ would not be a divisor.
+
+A priori it could be that the stable vertex is not amongst those vertices lying on the radius.
+But in this case the corresponding locus $\Fcal$ in the moduli space of unexpanded maps has larger codimension (for the same reason as before), and so the contribution vanishes by the projection formula.
+\end{proof}
 
 \subsubsection{Recursive description of $\Ecal$}
-Similarly to before, we let $\tau \in \Sigma$ be the ray corresponding to $\Dcal \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$, $\sigma \in \Sigma^{\Kim}$ be the minimal cone containing $\tau$ and $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$ be the stratum corresponding to $\sigma$, so that we have a map $\Dcal \to \Ecal$ (and $\Ecal$ is the minimal stratum through which the map from $\Dcal$ factors).
+Just as before, we let $\tau \in \Sigma$ be the ray corresponding to $\Dcal \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$, $\sigma \in \Sigma^{\Kim}$ be the minimal cone containing $\tau$ and $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$ be the stratum corresponding to $\sigma$, so that we have a map $\Dcal \to \Ecal$ (and $\Ecal$ is the minimal stratum through which the map from $\Dcal$ factors).
 Recall that we also have a unique stratum $\widetilde\Dcal \subseteq \widetilde\VZ_{1,\alpha}(\PP^N|H,d)$ such that $\Dcal = \widetilde\Dcal \cap \VZ_{1,\alpha}(\PP^N|H,d)$.
-Note that the cone $\sigma$ has dimension equal to the number of levels of the target expansion in the combinatorial type, which in this case may well be strictly larger than $1$.
+Note that the cone $\sigma$ has dimension equal to the number of levels of the target expansion in the combinatorial type, which in this case could possibly be larger than $1$.
 
@@
 Notice that the actual dimension of $\Ecal$ will typically be larger than that of $\Dcal$, since $\Ecal$ is contained inside the excess components of the moduli space.
-We will describe $\Dcal$ in terms of the map $\Dcal \to \Ecal$, proceeding in two steps:
+We will explain how to compute integrals over $\Dcal$ in two steps:
 \begin{enumerate}
-\item obtaining $\widetilde\Dcal$ from $\Ecal$;
-\item expressing the class of $\Dcal \subseteq \widetilde\Dcal$ in terms of tautological classes.
+\item we explain how to construct $\widetilde\Dcal$ from $\Ecal$ in \S \ref{};
+\item we explain how to express the class of $\Dcal \subseteq \widetilde\Dcal$ in terms of tautological classes in \S \ref{}.
 \end{enumerate}
@@
 In toric geometry, the method for studying this restriction is as follows.
-The fan of $\widetilde\Dcal$ is obtained by projecting the star of the ray $\tau$ onto the quotient lattice, and similarly for $\Ecal$.
-The map $\widetilde\Dcal \to \Ecal$ is then a toric morphism, given by the obvious map of fans.
-In order to describe this morphism, we first subdivide the fan of $\Ecal$ so that every cone in the fan of $\widetilde\Dcal$ maps surjectively onto a cone.
-This amounts to taking a toric blow-up of $\Ecal$ which we denote by $\widetilde\Ecal$.
-There is a natural morphism $\widetilde\Dcal \to \widetilde\Ecal$ which is now flat, and this may be described as a compactification of a torus bundle on $\widetilde\Ecal$.
-
-In the logarithmic setting, we proceed as follows.
-The stratum $\widetilde\Dcal$ has a natural \emph{reduced} logarithmic structure, obtained by restricting the logarithmic structure on $\widetilde\VZ_{1,\alpha}(\PP^N|H,d)$ and then quotienting out by the normal direction to $\widetilde\Dcal$.
-Similarly, $\Ecal$ has a natural reduced logarithmic structure, which coincides with the pull-back of the product logarithmic structure on the fibre product \eqref{IIIa fibre product}.
-
-We would like to describe the tropicalisations of these logarithmic stacks.
-In fact, it is more convenient to describe the \emph{extended tropicalisations} \cite{}.
-Let $l_1,\ldots,l_m$ denote the edge lengths of the tropical target, forming co-ordinates on the cone $\sigma$.
-Then the extended tropicalisation of $\Ecal$ is obtained by intersecting the star of $\sigma$ with the face $l_1=\ldots=l_m=\infty$.
-
-For $\widetilde\Dcal$ we have on $\tau$ edge lengths $e_1=\ldots=e_r=e$ separating the core from the vertices on the radius.
-The extended tropicalisation of $\widetilde\Dcal$ is obtained by intersecting the star of $\tau$ with the face $e=\infty$.
-Since $l_1=\ldots=l_m=\infty$ implies $e=\infty$ there is certainly a morphism between these cone complexes, and it is clear this morphism is a subdivsion.
-
-Moreover we may describe the subdivision explicitly.
-
-\subsubsection{$\Dcal$ from $\widetilde\Dcal$}
+The fan of $\widetilde\Dcal$ (respectively, $\Ecal$) is obtained by projecting the star of the ray $\tau$ (respectively, the cone $\sigma$) onto the quotient lattice.
+The map $\widetilde\Dcal \to \Ecal$ is then a toric morphism, induced by the obvious map of fans.
+In order to describe this morphism, we first subdivide the fan of $\Ecal$ by taking the images of cones in the fan of $\widetilde\Dcal$.
+This induces a toric blow-up of $\Ecal$ which we denote by $\widetilde\Ecal$.
+The morphism $\widetilde\Dcal \to \Ecal$ naturally factors through a morphism $\widetilde\Dcal \to \widetilde\Ecal$ which is now flat (in contrast to $\widetilde\Dcal \to \Ecal$), and now $\Dcal$ can be described as a compactification of a torus bundle over $\widetilde\Ecal$, with strata determined by the combinatorics of the fan.
+
+Returning to the logarithmic setting, the first step is to define appropriate logarithmic structures on $\widetilde\Dcal$ and $\Ecal$.
+We equip $\widetilde\Dcal$ with the logarithmic structure obtained by first restricting the logarithmic structure on $\widetilde\VZ_{1,\alpha}(\PP^N|H,d)$ and then quotienting by the normal direction to $\widetilde\Dcal$.
+By the same process we may also define a logarithmic structure on $\Ecal$, and this coincides with the pull-back along $\rho$ of the product logarithmic structure on the fibre product in \eqref{IIIa fibre product}.
+The map $\widetilde\Dcal \to \Ecal$ is then naturally a logarithmic map.
+
+The next step is to construct $\widetilde\Ecal$ as a logarithmic modification of $\Ecal$, and to do this we need to understand the tropicalisation of the map $\widetilde\Dcal \to \Ecal$.
+In fact, it is more convenient to consider the \emph{extended tropicalisation} \cite{}.
+We begin by fixing notation.
+Associated to the combinatorial type $\Delta$, we have stable vertices $\sqC_0,\sqC_1,\ldots,\sqC_r$ with $\sqC_0$ corresponding to the core and $\sqC_1,\ldots,\sqC_r$ corresponding to stable vertices which lie on the raidus (see Lemma \ref{} above).
+For $i \in \{1,\ldots,r\}$ let $e_i$ denote the sum of the edge lengths separating $\sqC_i$ from $\sqC_0$.
+These form co-ordinates on the cone $\sigma$, and in these co-ordinates $\tau$ is the ray given by the equations $e_1=\ldots=e_r$.
+Moreover, the $e_i$ define functions on any cone in the star of $\sigma$.
+
+Now consider the extended tropicalisation of $\widetilde\Dcal$.
+This is obtained inside the extended tropicalisation of $\widetilde\VZ_{1,\alpha}(\PP^N|H,d)$ by intersecting the star of $\tau$ with the locus $e_1=\ldots=e_r=\infty$.
+On the other hand, the extended tropicalisation of $\Ecal$ is obtained inside the extended tropicalisation of $\ol\Mcal_{1,\alpha}(\PP^N|H,d)$ by intersecting the star of $\sigma$ with the same locus.
+It is therefore clear that the extended tropicalisation of $\widetilde\Dcal$ is a subdivision of that of $\Ecal$.
+Moreover we claim that we can describe this subdivision explicitly.
+
+Consider any cone $\rho$ in the star of $\tau$.
+This is defined by a number of equalities and inequalities involving edge lengths coming from the combinatorial type on $\rho$.
+Amongst these edge lengths are $e_1,\ldots,e_r$ which corresponding to the separating nodes which persist on all of $\widetilde\Dcal$; there are also other edge lengths, corresponding to nodes over $\rho$ which are smoothed out on $\tau$.
+We first deal with the (in)equalities relating distances of vertices obtained by degenerating $\sqC_1,\ldots,\sqC_r$.
+By the definition of a well-spaced tropical map, we see that these are all of the form
+\begin{equation*} f + e_i = g + e_j \end{equation*}
+where $f$ and $g$ are positive linear combinations of additional edge length parameters which are set to zero in $\tau$.
+We may now pass to the subcone of $\rho$ obtained by imposing the additional equations $e_1=\ldots=e_r$.
+Note that this is \emph{not} a subcone of $\tau$ in general, since there are additional edge lengths which must be set to zero if one wishes to recover $\tau$.
+The additional equations mean that we can rewrite our previous (in)equalities in the form
+\begin{equation*} f = g \end{equation*}
+and this is now well-defined in the limit $e_1=\ldots=e_r=\infty$. We thus obtain a cone in the subdivision of the extended tropicalisation of $\Ecal$, and all such cones are obtained in this manner.
+
+Taking this subdivision amounts to the following modular blow-up of the fibre product of the moduli spaces attached to the vertices $\sqC_1,\ldots,\sqC_r$: given a logarithmic map with splitting nodes $q_1,\ldots,q_r$ as specified by the shape of $\Delta$, we glue together the $r$ vertices of the tropicalisation which carry the splitting nodes, and declare the resulting special vertex to be the root of the resulting tree.
+We then impose a central alignment condition, entirely analogous to the genus one construction, where the special root takes on the role previously occupied by the core.
+
+It remains to deal with the (in)equalities relating distances of vertices obtained by degenerating $\sqC_0$.
+These are not affected at all in the limit $e_1=\ldots=e_r=\infty$ and so the effect is to replace the factor of $\Ecal$ attached to the vertex $\sqC_0$
+\begin{equation*} \ol\Mcal^{\leftrightarrow}_{\Gamma_{\tiny{\sqC_0}}}(P|H_0+H_\infty) \end{equation*}
+with the centrally aligned rubber space:
+\begin{equation*} \VZ^{\leftrightarrow}_{\Gamma_{\tiny{\sqC_0}}}(P|H_0+H_\infty).\end{equation*}
+The factorisation condition here is accounting for the ``fibre-direction'' factorisation; the ``base-direction'' factorisation has not entered the picture yet, but will appear when we come to describe $\Dcal$.
+
+In this way, we obtain a logarithmic modification $\tilde\Ecal \to \Ecal$.
+By definition the map $\tilde\Dcal \to \Ecal$ is a compactification of a torus bundle over $\Ecal$, whose strata can be read off from the tropicalisation of $\tilde\Dcal$.
+
+[LUCA SAYS MORE HERE, ABOUT HOW IT'S GENERICALLY A PROJECTIVE BUNDLE.]
+
+\subsubsection{$\Dcal$ from $\widetilde\Dcal$} On $\widetilde\Dcal$ there is a natural vector bundle arising from the modular desription of $\widetilde\VZ_{1,\alpha}(\PP^N|H,d)$, namely:
+\begin{equation*} F = \OO(\delta)^{\oplus r}. \end{equation*}
+We may use this to identify tangent spaces.
 

### 2019-06-26 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
more things on D from Dtilde!

@@
 \begin{equation*} \ol\Mcal^{\leftrightarrow}_{\Gamma_{\tiny{\sqC_0}}}(P|H_0+H_\infty) \end{equation*}
-with the centrally aligned rubber space:
+with the radially aligned rubber space:
 \begin{equation*} \VZ^{\leftrightarrow}_{\Gamma_{\tiny{\sqC_0}}}(P|H_0+H_\infty).\end{equation*}
-The factorisation condition here is accounting for the ``fibre-direction'' factorisation; the ``base-direction'' factorisation has not entered the picture yet, but will appear when we come to describe $\Dcal$.
+The factorisation condition here is accounting for the ``fibre-direction'' factorisation; the ``base-direction'' factorisation has not entered the picture yet, and will appear when we come to describe $\Dcal$.
 
@@
 \begin{equation*} F = \OO(\delta)^{\oplus r}. \end{equation*}
-We may use this to identify tangent spaces.
+We claim that the fibre of $F$ over a moduli point can be naturally identified with
+\begin{equation*} \left( \bigoplus_{i=1}^r \TT_{p_i} C_i^\prime \right) \otimes \TT_{C_0} \end{equation*}
+where $C_i^\prime$ is a component of $C_i$ which lies on the radius, $p_i$ is the adjacent node which points towards the core, and $\TT_{C_0}$ is the universal tangent line bundle on the radially aligned rubber space.
+
+For let us choose a component $C_i^\prime$ of the curve which lies on the radius.
+Then $\OO(\delta)$ can be expressed as a tensor product of tangent line bundles along the path connecting $C_i^\prime$ to the core.
+However, this lage product of line bundles is telescoping: any vertex which appears in the middle of the path will have an incoming and outgoing node, and since the vertex corresponds to a smooth rational curve these tangent spaces are naturally isomorphic \ref{VZ}.
+Thus the product collapses into a contribution $\TT_{p_i}C_i^\prime$ from the left-hand side and a contribution from the right-hand side.
+Note that the final term on the right hand side is not given by $\TT_{q_i} C_0$ (where $q_i$ is the appropriate splitting node) but rather the tangent space to the core (which could be further away if $C_0$ has degenerated).
+Thus we obtain the universal tangent line bundle $\TT_{C_0}$ as the contribution to the right-hand side.
+
+[EXAMPLE]
+
+Note that $C_i^\prime$ is \emph{a} component of $C_i$ which lies on the radius.
+There may be more than one, but if this is the case then their tangent spaces are naturally identified by the logarithmic structure.
+Thus we obtain a natural morphism
+\begin{equation*} \sum \operatorname{d}\!f \colon F(-\TT_{C_0}) \to \ev_q^\st \TT_H \end{equation*}
+given by summing the derivatives at \emph{all} the inward-pointing nodes on the radius.
+Now, over $\widetilde\Dcal$ there is a natural section of the projective bundle $\PP(F) \to \widetilde\Dcal$ (obtained by projectivising the diagonal embedding).
+If we therefore lift the above morphism to the projectivisation, we obtain a composition:
+\begin{equation*} \OO_{\PP(F)}(-1) \to \pi^\st F \to \pi^\st(\ev_q^\st \TT_H (\TT_{C_0})).\end{equation*}
+The vanishing locus of this section is given by an Euler class calculation on $\PP(F)$.
+In order to obtain $\Dcal$ we must then intersect this vanishing locus with $\OO_{\PP(F)}(1)$ (which represents the natural section $\widetilde\Dcal \to \PP(F)$.
+
+Finally, we note that the class of $F$ is computable in terms of data pulled back from the base. To be more precise, we may consider the following bundle on $\Ecal$:
+\begin{equation*} E = \bigoplus_{i=1}^r \TT_{q_i}C_i \otimes \TT_{q_i}C_0. \end{equation*}
+We may then identify $F$ with the pullback of $E$ twisted by the exceptional loci.
+(This agrees with the more classical-minded description of $F$ as a bundle which resolves an otherwise non-transverse section of $E$.) We illustrate this in an example, which brings out the beauty of the interplay between logarithmic moduli and blow-ups.
+
+[EXAMPLE]
 

### 2019-06-26 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
minor changes

@@
 Then $\OO(\delta)$ can be expressed as a tensor product of tangent line bundles along the path connecting $C_i^\prime$ to the core.
-However, this lage product of line bundles is telescoping: any vertex which appears in the middle of the path will have an incoming and outgoing node, and since the vertex corresponds to a smooth rational curve these tangent spaces are naturally isomorphic \ref{VZ}.
-Thus the product collapses into a contribution $\TT_{p_i}C_i^\prime$ from the left-hand side and a contribution from the right-hand side.
+However, this lage product of line bundles is telescoping: any vertex which appears in the middle of the path will have an incoming and outgoing node, and since the vertex corresponds to a smooth rational curve these tangent spaces are naturally dual to each other \cite{VZ}.
+Thus these terms cancel, and product collapses into a contribution $\TT_{p_i}C_i^\prime$ from the left-hand side and a contribution from the right-hand side.
 Note that the final term on the right hand side is not given by $\TT_{q_i} C_0$ (where $q_i$ is the appropriate splitting node) but rather the tangent space to the core (which could be further away if $C_0$ has degenerated).

### 2019-06-26 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
minor changes to 5.3.3.

@@
 
-The next step is to construct $\widetilde\Ecal$ as a logarithmic modification of $\Ecal$, and to do this we need to understand the tropicalisation of the map $\widetilde\Dcal \to \Ecal$.
+The next step is to construct $\widetilde\Ecal$ as a logarithmic modification of $\Ecal$, and to do this we need to describe the tropicalisation of the map $\widetilde\Dcal \to \Ecal$.
 In fact, it is more convenient to consider the \emph{extended tropicalisation} \cite{}.
@@
 For $i \in \{1,\ldots,r\}$ let $e_i$ denote the sum of the edge lengths separating $\sqC_i$ from $\sqC_0$.
-These form co-ordinates on the cone $\sigma$, and in these co-ordinates $\tau$ is the ray given by the equations $e_1=\ldots=e_r$.
-Moreover, the $e_i$ define functions on any cone in the star of $\sigma$.
+These give functions on the cone $\sigma$, and $\tau$ is the ray given by the equations $e_1=\ldots=e_r$.
+Note that the $e_i$ also define functions on any cone in the star of $\sigma$.
 
 Now consider the extended tropicalisation of $\widetilde\Dcal$.
-This is obtained inside the extended tropicalisation of $\widetilde\VZ_{1,\alpha}(\PP^N|H,d)$ by intersecting the star of $\tau$ with the locus $e_1=\ldots=e_r=\infty$.
+This is obtained inside the extended tropicalisation of $\widetilde\VZ_{1,\alpha}(\PP^N|H,d)$ by intersecting the star of $\tau$ with the locus $e_1=\cdots=e_r=\infty$.
 On the other hand, the extended tropicalisation of $\Ecal$ is obtained inside the extended tropicalisation of $\ol\Mcal_{1,\alpha}(\PP^N|H,d)$ by intersecting the star of $\sigma$ with the same locus.
@@
 Consider any cone $\rho$ in the star of $\tau$.
-This is defined by a number of equalities and inequalities involving edge lengths coming from the combinatorial type on $\rho$.
-Amongst these edge lengths are $e_1,\ldots,e_r$ which corresponding to the separating nodes which persist on all of $\widetilde\Dcal$; there are also other edge lengths, corresponding to nodes over $\rho$ which are smoothed out on $\tau$.
-We first deal with the (in)equalities relating distances of vertices obtained by degenerating $\sqC_1,\ldots,\sqC_r$.
-By the definition of a well-spaced tropical map, we see that these are all of the form
-\begin{equation*} f + e_i = g + e_j \end{equation*}
-where $f$ and $g$ are positive linear combinations of additional edge length parameters which are set to zero in $\tau$.
+Since the tropicalisation of $\widetilde\VZ_{1,\alpha}(\PP^N|H,d)$ is a subdivision of the tropicalisation of $\ol\Mcal_{1,\alpha}(\PP^N|H,d)$ there is a unique minimal cone in the star of $\sigma$ which contains $\rho$.
+We denote this cone by $\theta$, and remark that $\theta$ arises from a choice of combinatorial type which specialises the combinatorial type $\Delta$ defining $\sigma$.
+On $\theta$ we have the edge length functions $e_1,\ldots,e_r$ as well as additional edge lengths corresponding to nodes on $\theta$ which are smoothed out on $\sigma$.
+
+Now, $\rho$ is defined inside $\theta$ by a number of equalities and inequalities involving these edge lengths.
+These (in)equalities relate the distances to the core of various vertices of the dual graph.
+There are three cases we must consider:
+\begin{enumerate}
+\item both vertices are components of $\sqC_1 \cup \ldots \cup \sqC_r$;
+\item both vertices are components of $\sqC_0$;
+\item one vertex is a component of $\sqC_0$ and one is a component of $\sqC_1 \cup \ldots \cup\sqC_r$.
+\end{enumerate}
+We start with case (1). By the definition of a well-spaced tropical map, we see that these are all of the form
+\begin{equation*} f_i + e_i = f_j + e_j \end{equation*}
+where $f_i$ and $f_j$ are positive linear combinations of additional edge length parameters which are set to zero in $\tau$.
 We may now pass to the subcone of $\rho$ obtained by imposing the additional equations $e_1=\ldots=e_r$.
@@
 The additional equations mean that we can rewrite our previous (in)equalities in the form
-\begin{equation*} f = g \end{equation*}
-and this is now well-defined in the limit $e_1=\ldots=e_r=\infty$. We thus obtain a cone in the subdivision of the extended tropicalisation of $\Ecal$, and all such cones are obtained in this manner.
+\begin{equation*} f_i = f_j \end{equation*}
+and these define a cone in the limiting locus $e_1=\ldots=e_r=\infty$.
+By definition this is one of the cones in the subdivision of the extended tropicalisation of $\Ecal$, and all such cones are obtained in this manner.
 
@@
 
-It remains to deal with the (in)equalities relating distances of vertices obtained by degenerating $\sqC_0$.
-These are not affected at all in the limit $e_1=\ldots=e_r=\infty$ and so the effect is to replace the factor of $\Ecal$ attached to the vertex $\sqC_0$
+We now deal with Case (2). These (in)equalities are not affected at all in the limit $e_1=\ldots=e_r=\infty$ and so the effect is to replace the factor of $\Ecal$ attached to the vertex $\sqC_0$
 \begin{equation*} \ol\Mcal^{\leftrightarrow}_{\Gamma_{\tiny{\sqC_0}}}(P|H_0+H_\infty) \end{equation*}
@@
 The factorisation condition here is accounting for the ``fibre-direction'' factorisation; the ``base-direction'' factorisation has not entered the picture yet, and will appear when we come to describe $\Dcal$.
+
+It remains to discuss Case (3).
+Here we have a relation of the form $f_i = f_j + e_j$, so in the limit $e_j =\infty$ there is no limiting cone.
+Therefore these relations to not appear in the modification of $\Ecal$.
 

### 2019-06-27 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
improvements to 5.3.3

@@
 
-\subsection{Recursive description of the divisors: types $A,B$ and $C^+$} Choose an irreducible component $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$.
+\subsection{Recursive description of the divisors: types $A,B$ and $C^+$}\label{subsection:ABC description} Choose an irreducible component $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$.
 By Lemma \ref{Lemma components are log divisors} this is a log divisor, and hence may be written as:
@@
 \subsubsection{Possible combinatorial types} Recall that a boundary divisor $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ is said to be of type IIIb if the core is assigned degree zero by the combinatorial type (this is the case which was ignored in Lemma \ref{lem:combs} and the subsequent discussion).
-In this case, the combinatorial type is not as tightly constrained as before; the target may expand multiple times, and as such the combinatorial type need not be a bipartite graph with a single interior vertex.
+In this case, the combinatorial type is not as tightly constrained as before; the generic target may expand multiple times, and as such the combinatorial type need not be a bipartite graph with a single interior vertex.
 Nevertheless, we have the following lemma:
-\begin{lemma} 
+\begin{lemma} \label{lemma type C0 combinatorial types}
 Let $\Dcal$ be a locus of type IIIb and let $\Delta$ be the corresponding combinatorial type.
@@
 By stability, we must always have at least one stable vertex lying over each  vertex of the target.
-If there was more than one, then (since both the insertions and the factorisation condition are pulled back from the moduli space of maps without expansions) we can show, as in the proof of Lemma \ref{lem:combs}, that the contribution vanishes.
+If there is more than one then, as in the proof of Lemma \ref{lem:combs} above, we see that the corresponding locus $\Fcal$ in the moduli space of unexpanded maps has larger codimension and so (since both the insertions and the factorisation condition are pulled back from the moduli space of maps without expansions) the contribution vanishes by the projection formula.
 
@@
 
-A priori it could be that the stable vertex is not amongst those vertices lying on the radius.
-But in this case the corresponding locus $\Fcal$ in the moduli space of unexpanded maps has larger codimension (for the same reason as before), and so the contribution vanishes by the projection formula.
+A priori it could be that the stable vertex is not among those vertices over $\diamond$ which lie on the radius.
+But in this case we we have a trivial bubble lying on the radius; this implies the map $\Dcal \to \Ecal$ has positive-dimensional fibres, since the derivative of the stable map on the trivial bubble will always be zero (for a more detailed discussion, see \S \ref{} below).
+Hence, the contribution from these loci vanishes.
 \end{proof}
@@
 \subsubsection{Recursive description of $\Ecal$}
-Just as before, we let $\tau \in \Sigma$ be the ray corresponding to $\Dcal \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$, $\sigma \in \Sigma^{\Kim}$ be the minimal cone containing $\tau$ and $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$ be the stratum corresponding to $\sigma$, so that we have a map $\Dcal \to \Ecal$ (and $\Ecal$ is the minimal stratum through which the map from $\Dcal$ factors).
+Just as in \S \ref{subsection:ABC description}, we let $\tau \in \Sigma$ be the ray corresponding to $\Dcal \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$, $\sigma \in \Sigma^{\Kim}$ be the minimal cone containing $\tau$ and $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$ be the stratum corresponding to $\sigma$, so that we have a map $\Dcal \to \Ecal$ and $\Ecal$ is the minimal stratum through which the map $\Dcal \to \ol\Mcal_{1,\alpha}(\PP^N|H,d)$ factors.
 Recall that we also have a unique stratum $\widetilde\Dcal \subseteq \widetilde\VZ_{1,\alpha}(\PP^N|H,d)$ such that $\Dcal = \widetilde\Dcal \cap \VZ_{1,\alpha}(\PP^N|H,d)$.
@@
 Notice that the actual dimension of $\Ecal$ will typically be larger than that of $\Dcal$, since $\Ecal$ is contained inside the excess components of the moduli space.
-We will explain how to compute integrals over $\Dcal$ in two steps:
+In the remainder of this section, we will reduce integrals over $\Dcal$ to certain excess integrals over $\Ecal$.
+We proceed in two steps:
 \begin{enumerate}
-\item we explain how to construct $\widetilde\Dcal$ from $\Ecal$ in \S \ref{};
-\item we explain how to express the class of $\Dcal \subseteq \widetilde\Dcal$ in terms of tautological classes in \S \ref{}.
+\item in \S \ref{subsection Dtilde from E} we explain how to construct $\widetilde\Dcal$ from $\Ecal$;
+\item in \S \ref{subsection D from Dtilde} we explain how to express the class of $\Dcal \subseteq \widetilde\Dcal$ in terms of tautological classes.
 \end{enumerate}
+To compute integrals over $\Dcal$ we simply push down the appropriate classes from $\widetilde\Dcal$ to $\Ecal$ and then integrate over $\Ecal$ using the ordinary splitting axiom.
 
@@
 
-\subsubsection{$\widetilde\Dcal$ from $\Ecal$} Recall that the map $\widetilde\Dcal \to \Ecal$ is obtained by restricting the logarithmic blow-up
+\subsubsection{$\widetilde\Dcal$ from $\Ecal$}\label{subsection Dtilde from E} Recall that the map $\widetilde\Dcal \to \Ecal$ is obtained by restricting the logarithmic blow-up
 \begin{equation*} \widetilde\VZ_{1,\alpha}(\PP^N|H,d) \to \ol\Mcal_{1,\alpha}(\PP^N|H,d)\end{equation*}
 to the locus $\widetilde\Dcal$.
-In toric geometry, the method for studying this restriction is as follows.
-The fan of $\widetilde\Dcal$ (respectively, $\Ecal$) is obtained by projecting the star of the ray $\tau$ (respectively, the cone $\sigma$) onto the quotient lattice.
-The map $\widetilde\Dcal \to \Ecal$ is then a toric morphism, induced by the obvious map of fans.
-In order to describe this morphism, we first subdivide the fan of $\Ecal$ by taking the images of cones in the fan of $\widetilde\Dcal$.
+In toric geometry, the means of studying this restriction is as follows.
+The fan of $\widetilde\Dcal$ (respectively, $\Ecal$) is obtained by projecting the star of the ray $\tau$ (respectively, the star of the cone $\sigma$) onto the quotient lattice.
+The map $\widetilde\Dcal \to \Ecal$ is then the toric morphism induced by the obvious map of fans.
+In order to describe this morphism more explicitly, we first subdivide the fan of $\Ecal$ by taking the images of cones in the fan of $\widetilde\Dcal$.
 This induces a toric blow-up of $\Ecal$ which we denote by $\widetilde\Ecal$.
-The morphism $\widetilde\Dcal \to \Ecal$ naturally factors through a morphism $\widetilde\Dcal \to \widetilde\Ecal$ which is now flat (in contrast to $\widetilde\Dcal \to \Ecal$), and now $\Dcal$ can be described as a compactification of a torus bundle over $\widetilde\Ecal$, with strata determined by the combinatorics of the fan.
+The morphism $\widetilde\Dcal \to \Ecal$ naturally factors through a morphism $\widetilde\Dcal \to \widetilde\Ecal$ which is now flat (in contrast to $\widetilde\Dcal \to \Ecal$), and  $\widetilde\Dcal$ may now be described as a compactification of a torus bundle over $\widetilde\Ecal$, with strata determined by the combinatorics of the fan.
 
@@
 We equip $\widetilde\Dcal$ with the logarithmic structure obtained by first restricting the logarithmic structure on $\widetilde\VZ_{1,\alpha}(\PP^N|H,d)$ and then quotienting by the normal direction to $\widetilde\Dcal$.
-By the same process we may also define a logarithmic structure on $\Ecal$, and this coincides with the pull-back along $\rho$ of the product logarithmic structure on the fibre product in \eqref{IIIa fibre product}.
+By the same process we may also define a logarithmic structure on $\Ecal$, and this coincides with the pull-back along the splitting morphism $\rho$ of the product logarithmic structure on the fibre product in \eqref{IIIa fibre product}.
 The map $\widetilde\Dcal \to \Ecal$ is then naturally a logarithmic map.
@@
 For $i \in \{1,\ldots,r\}$ let $e_i$ denote the sum of the edge lengths separating $\sqC_i$ from $\sqC_0$.
-These give functions on the cone $\sigma$, and $\tau$ is the ray given by the equations $e_1=\ldots=e_r$.
-Note that the $e_i$ also define functions on any cone in the star of $\sigma$.
+These give functions on the cone $\sigma$, and $\tau$ is the ray inside $\sigma$ given by the equations $e_1=\cdots=e_r$.
+Note that the $e_i$ also define functions on any cone belonging to the star of $\sigma$.
 
@@
 
-Consider any cone $\rho$ in the star of $\tau$.
+Consider therefore any cone $\rho$ belonging to the star of $\tau$.
 Since the tropicalisation of $\widetilde\VZ_{1,\alpha}(\PP^N|H,d)$ is a subdivision of the tropicalisation of $\ol\Mcal_{1,\alpha}(\PP^N|H,d)$ there is a unique minimal cone in the star of $\sigma$ which contains $\rho$.
 We denote this cone by $\theta$, and remark that $\theta$ arises from a choice of combinatorial type which specialises the combinatorial type $\Delta$ defining $\sigma$.
-On $\theta$ we have the edge length functions $e_1,\ldots,e_r$ as well as additional edge lengths corresponding to nodes on $\theta$ which are smoothed out on $\sigma$.
+This means that each vertex $\sqC_i$ of the combinatorial type $\Delta$ may degenerate into a subgraph of the combinatorial type on $\theta$.
+Thus, on $\theta$ we have the edge length functions $e_1,\ldots,e_r$ as well as additional edge length functions corresponding to nodes on $\theta$ which are smoothed out on $\sigma$.
 
@@
 These (in)equalities relate the distances to the core of various vertices of the dual graph.
-There are three cases we must consider:
+There are three cases which we must consider:
 \begin{enumerate}
-\item both vertices are components of $\sqC_1 \cup \ldots \cup \sqC_r$;
-\item both vertices are components of $\sqC_0$;
+\item both vertices are components of the subgraph $\sqC_1 \cup \ldots \cup \sqC_r$;
+\item both vertices are components of the subgraph $\sqC_0$;
 \item one vertex is a component of $\sqC_0$ and one is a component of $\sqC_1 \cup \ldots \cup\sqC_r$.
 \end{enumerate}
-We start with case (1). By the definition of a well-spaced tropical map, we see that these are all of the form
-\begin{equation*} f_i + e_i = f_j + e_j \end{equation*}
+We start with Case (1). By the definition of the subdivision, we see that all take the form
+\begin{equation*} f_i + e_i \st f_j + e_j, \qquad \st \in \{ =, < \} \end{equation*}
 where $f_i$ and $f_j$ are positive linear combinations of additional edge length parameters which are set to zero in $\tau$.
@@
 The additional equations mean that we can rewrite our previous (in)equalities in the form
-\begin{equation*} f_i = f_j \end{equation*}
+\begin{equation*} f_i \st f_j, \qquad \st \in \{=,<\}\end{equation*}
 and these define a cone in the limiting locus $e_1=\ldots=e_r=\infty$.
@@
 Taking this subdivision amounts to the following modular blow-up of the fibre product of the moduli spaces attached to the vertices $\sqC_1,\ldots,\sqC_r$: given a logarithmic map with splitting nodes $q_1,\ldots,q_r$ as specified by the shape of $\Delta$, we glue together the $r$ vertices of the tropicalisation which carry the splitting nodes, and declare the resulting special vertex to be the root of the resulting tree.
-We then impose a central alignment condition, entirely analogous to the genus one construction, where the special root takes on the role previously occupied by the core.
-
-We now deal with Case (2). These (in)equalities are not affected at all in the limit $e_1=\ldots=e_r=\infty$ and so the effect is to replace the factor of $\Ecal$ attached to the vertex $\sqC_0$
+We then impose a central alignment condition, entirely analogous to the genus one construction, where the special root takes on the r\^ole previously occupied by the core.
+
+We now address Case (2). These (in)equalities are not affected at all in the limit $e_1=\ldots=e_r=\infty$ and so the effect is to replace the factor of $\Ecal$ attached to the vertex $\sqC_0$
 \begin{equation*} \ol\Mcal^{\leftrightarrow}_{\Gamma_{\tiny{\sqC_0}}}(P|H_0+H_\infty) \end{equation*}
@@
 \begin{equation*} \VZ^{\leftrightarrow}_{\Gamma_{\tiny{\sqC_0}}}(P|H_0+H_\infty).\end{equation*}
-The factorisation condition here is accounting for the ``fibre-direction'' factorisation; the ``base-direction'' factorisation has not entered the picture yet, and will appear when we come to describe $\Dcal$.
+The factorisation condition here is accounting for the ``fibre-direction'' factorisation.
+The ``base-direction'' factorisation plays no role here, since $\sqC_0$ is assigned zero horizontal degree (the base direction factorisation will enter the picture when we come to describe $\Dcal$).
 
 It remains to discuss Case (3).
-Here we have a relation of the form $f_i = f_j + e_j$, so in the limit $e_j =\infty$ there is no limiting cone.
+Here we have a relation of the form $f_i = f_j + e_j$, so when we set $e_j =\infty$ there is no limiting cone.
 Therefore these relations to not appear in the modification of $\Ecal$.
 
-In this way, we obtain a logarithmic modification $\tilde\Ecal \to \Ecal$.
-By definition the map $\tilde\Dcal \to \Ecal$ is a compactification of a torus bundle over $\Ecal$, whose strata can be read off from the tropicalisation of $\tilde\Dcal$.
+To summarise: the subdivision induces a logarithmic modification $\widetilde\Ecal \to \Ecal$ which admits a modular description as a fibre product of genus zero centrally aligned maps (coming from the vertices $\sqC_1,\ldots,\sqC_r$) and genus one radially aligned rubber maps satisfying fibre-direction factorisation (coming from the vertex $\sqC_0$).
+
+By construction, we have a map $\widetilde\Dcal \to \widetilde\Ecal$ which is a compactification of a torus bundle over $\widetilde\Ecal$.
+The strata of $\widetilde\Dcal$ can be read off from its tropicalisation, and in particular we have the information of how (polynomials in) the classes of boundary strata push forward to $\widetilde\Ecal$.
 
@@
 
-\subsubsection{$\Dcal$ from $\widetilde\Dcal$} On $\widetilde\Dcal$ there is a natural vector bundle arising from the modular desription of $\widetilde\VZ_{1,\alpha}(\PP^N|H,d)$, namely:
+\subsubsection{$\Dcal$ from $\widetilde\Dcal$}\label{subsection D from Dtilde} On $\widetilde\Dcal$ there is a natural vector bundle arising from the modular desription of $\widetilde\VZ_{1,\alpha}(\PP^N|H,d)$, namely:
 \begin{equation*} F = \OO(\delta)^{\oplus r}. \end{equation*}

### 2019-06-27 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
Added remark about degree zero reduced rubber for base of induction

@@
 
-The base terms of the recursion all have $d=0$ and as such are easy to compute: the relative invariants of $(X,Y)$ are nothing but absolute invariants of $X$, the absolute invariants of $Y$ are given by obstruction bundle integrals over Deligne--Mumford spaces, and the  rubber invariants of $P$ are also given by integrals over Deligne--Mumford spaces, using the formula for the double ramification cycle \cite{Hain,JPPZ} in terms of tautological classes.
+The base terms of the recursion all have $d=0$ and as such are easy to compute: the relative invariants of $(X,Y)$ are nothing but absolute invariants of $X$ and the absolute invariants of $Y$ are given by obstruction bundle integrals over Deligne--Mumford spaces.
+The rubber invariants of $P$ in degree zero are given by integrals over the main component of the double ramification cycle; this can likewise be computed as an integral over Deligne--Mumford space, by correcting the formula for the ordinary double ramification cycle \cite{Hain,JPPZ} by the obvious contribution from the boundary irreducible component (the observation which makes this easy to do in genus one is that the rubber moduli space is pure-dimensional, so that the virtual class is simply the sum of the fundamental classes of the irreducible components).
 We will now explain how to perform each of the four inductive steps outlined above.

### 2019-06-27 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
suggested minor changes to intro and S1

--- 2019-06-26 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
@@
 %\usepackage{showlabels}
-\usepackage{hyperref}
 \usepackage{amsthm}
@@
 \usepackage[utf8x]{inputenc}
+\usepackage[normalem]{ulem}
+
+\renewcommand\thepart{\Roman{part}}
+
+%This reverse-links the references in the paper. Useful for large papers.
+\usepackage[backref]{hyperref}
+\hypersetup{
+  colorlinks   = true,          %Colors links instead of ugly boxes
+  urlcolor     = violet,          %Color for external hyperlinks
+  linkcolor    = violet,          %Color of internal links
+  citecolor   = blue             %Color of citations
+}
 
@@
 
-%%%%%%%%%%%%%%%%%%%
-\begin{comment}
-\usetikzlibrary{ipe} % ipe compatibility library
-\tikzstyle{ipe stylesheet} = [
-  ipe import,
-  even odd rule,
-  line join=round,
-  line cap=butt,
-  ipe pen normal/.style={line width=0.4},
-  ipe pen heavier/.style={line width=0.8},
-  ipe pen fat/.style={line width=1.2},
-  ipe pen ultrafat/.style={line width=2},
-  ipe pen normal,
-  ipe mark normal/.style={ipe mark scale=3},
-  ipe mark large/.style={ipe mark scale=5},
-  ipe mark small/.style={ipe mark scale=2},
-  ipe mark tiny/.style={ipe mark scale=1.1},
-  ipe mark normal,
-  /pgf/arrow keys/.cd,
-  ipe arrow normal/.style={scale=7},
-  ipe arrow large/.style={scale=10},
-  ipe arrow small/.style={scale=5},
-  ipe arrow tiny/.style={scale=3},
-  ipe arrow normal,
-  /tikz/.cd,
-  ipe arrows, % update arrows
-  <->/.tip = ipe normal,
-  ipe dash normal/.style={dash pattern=},
-  ipe dash dashed/.style={dash pattern=on 4bp off 4bp},
-  ipe dash dotted/.style={dash pattern=on 1bp off 3bp},
-  ipe dash dash dotted/.style={dash pattern=on 4bp off 2bp on 1bp off 2bp},
-  ipe dash dash dot dotted/.style={dash pattern=on 4bp off 2bp on 1bp off 2bp on 1bp off 2bp},
-  ipe dash normal,
-  ipe node/.append style={font=\normalsize},
-  ipe stretch normal/.style={ipe node stretch=1},
-  ipe stretch normal,
-  ipe opacity 10/.style={opacity=0.1},
-  ipe opacity 30/.style={opacity=0.3},
-  ipe opacity 50/.style={opacity=0.5},
-  ipe opacity 75/.style={opacity=0.75},
-  ipe opacity opaque/.style={opacity=1},
-  ipe opacity opaque,
-]
-\end{comment}
-
 \definecolor{red}{rgb}{1,0,0}
+
 \usepackage[all]{xy}
@@
 
+\newcommand{\tred}{\textcolor{red}}
 \newcommand{\mathsq}[1]{#1}
@@
 
-\title{Curve counting in genus one: elliptic singularities and relative geometry}
+\title[Reduced relative GW theory in genus 1]{Curve counting in genus one: elliptic singularities {\it \&} relative geometry}
 \author{Luca Battistella, Navid Nabijou and Dhruv Ranganathan}
@@
 \begin{abstract}
+We construct and study the reduced, relative, genus one Gromov--Witten theory of very ample pairs.
+These invariants form the principal part contribution to relative Gromov--Witten theory in genus one and are relative versions of Zinger's reduced Gromov--Witten invariants.
+The relative and absolute theories are related by degeneration of the tangency conditions, and the resulting formulas generalize a well-known recursive calculation scheme put forward by Gathmann in genus $0$.
+\sout{The geometric input is a desingularization of the principal component of the moduli space of genus one logarithmic stable maps to a very ample pair, using the geometry of elliptic singularities.
+Our study passes through a number of general techniques for calculating integrals on logarithmic blowups of moduli spaces of stable maps, which may be of independent interest.}
 \end{abstract}
@@
 
-\noindent Gromov--Witten theory in genus zero has been studied intensely using a large assortment of techniques, many of which rely crucially on the remarkable geometry of the Kontsevich space of genus zero maps to projective space.
-On the other hand, the higher genus spaces have uncontrollable singularities, and an entirely different set of techniques must be appealed to.
-Indeed, much less is known in higher genus, though the last few years have seen remarkable progress.
-
-\subsection{The transition point in genus one} The singularities of the space of maps in genus one are delicate, but understandable.
-Vakil and Zinger exhibited this by giving an explicit blowup algorithmic that desingularized the space of maps to projective space, giving rise to ``reduced’’ Gromov—Witten invariants, which are closer to enumerative counts~\cite{VZ}.
-Certain tools, such as localization and quantum Lefschetz, can thus be extended to genus one.
-However, there is as yet no degeneration formula for the Vakil—Zinger invariants.
-
-Recently, a more conceptual and geometric understanding of Vakil and Zinger’s construction has come out of tropical geometry and logarithmic Gromov—Witten theory.
-Specifically, Ranganathan, Santos-Parker, and Wise give a modular interpretation of the construction and a deformation theoretic proof its smoothness by using the geometry of elliptic singularities~\cite{RSPW,RSPW2}.
-In this paper we seek an understanding of Vakil—Zinger invariants in relative geometries and the degeneration formula.
+The Kontsevich moduli space of stable maps from genus $0$ curves to projective space exhibits \tred{remarkable} geometry -- it is a smooth orbifold with a ``self-similar'' normal crossings boundary.
+These facts have combined to produce a \tred{remarkable} understanding of Gromov--Witten theory in genus $0$.
+
+While the higher genus situation is \tred{substantially} more difficult, in the last several years, \tred{substantial} theory has been developed towards a conceptual understanding of the genus one case.
+This began over a decade ago with the pioneering work of \tred{Li}, Vakil, and Zinger~\cite{redgone,VZ,LZ,lz2,zingerstvsred,zingred}, \tred{and was recently reinvigorated involving ideas from logarithmic geometry and singularity theory}~\cite{BCM18,CM18,HL,RSPW,RSPW2,SMY1,VISC}.
+The result is a \textit{reduced} Gromov--Witten theory, which removes certain degenerate contributions from the ordinary theory.
+While the Atiyah--Bott localization for the reduced invariants was used to great effect by Zinger in his proof of the BCOV conjectures, two major components of the standard theory -- relative invariants and the degeneration formula -- have not been developed in this setting.
+Our results in this paper provide these as new \sout{structural} tools in reduced genus one Gromov--Witten theory\footnote{Further motivation to consider the genus one case specifically comes simply from the fact that for Calabi--Yau geometries in dimension larger than $3$, Gromov--Witten theory vanishes in genera greater than $1$.}.
 
 \subsection{Results} Our first contribution is a definition and construction of relative reduced Gromov--Witten theory of projective space relative to a hyperplane.
-The geometric content is the following.
-
-\begin{customthm}{A}
-There exists a logarithmically smooth and proper Deligne--Mumford stack giving a modular compactification for the space of genus one maps to projective space with fixed contact order with a hyperplane.
+The geometric content is the following, see Theorem~\ref{main-thm} for a precise statement.
+
+Let $\mathcal M_{1,\alpha}^\circ(\mathbb P^N|H)$ be the moduli space of positive degree maps from \tred{smooth} curves of genus $1$ to $\mathbb P^N$ with \tred{dimensionally transverse} contact order $\alpha\in\mathbb Z^n_{\geq 0}$ along $H$.
+
+\begin{customthm}{A}\label{thm: desingularization}
+There exists a logarithmically smooth and proper Deligne--Mumford stack $\VZ_{1,\alpha}^\circ(\mathbb P^N|H)$ having expected dimension, and containing $\mathcal M_{1,\alpha}^\circ(\mathbb P^N|H)$  as a dense open subset.
+A point in this moduli space parameterizes maps
+\[
+C\to \mathbb P^N[s]\to \mathbb P^N,
+\]
+to an $s$-fold expansion of $\mathbb P^N$ along $H$ such that the map to the expansion and composite map $C\to \mathbb P^N$ each factor nontrivially through an elliptic singularity. 
 \end{customthm}
 
-With regards to the degeneration formula, we pursue the strategy laid out by Vakil and Gathmann, building on work of Caporaso and Harris.
-We reinterpret and extend their methods using logarithmic geometry and tropical techniques.
-Our main result is the following.
-
-\begin{customthm}{B}
+The moduli space above is constructed by identifying two closed conditions that must be satisfied by the space of maps to the pair $(\mathbb P^N,H)$.
+Each condition requires the stable map to factor through an elliptic singularity.
+The behaviour mixes the geometry in~\cite{RSPW} and~\cite{RSPW2}.
+\sout{Together with an analysis of the deformation theory of such maps, we are led to Theorem~\ref{thm: desingularization}}.
+
+Our second result explains how to do practical calculations on this space of stable maps.
+
+\begin{customthm}{B}\label{thm: recursion}
 Given a smooth pair $(X,Y)$ with $Y$ very ample, there is an explicit recursive algorithm to calculate
 \begin{enumerate}
-\item the reduced genus one Gromov--Witten invariants of $Y$;
+\item the \tred{restricted} reduced genus one Gromov--Witten invariants of $Y$;
 \item the reduced genus one relative Gromov--Witten invariants of $(X,Y)$; 
-\item the reduced genus one rubber invariants of $P=\PP_Y(\operatorname{N}_{Y|X} \oplus \OO_Y)$
+\item the \tred{restricted} reduced genus one rubber invariants of $P=\PP_Y(\operatorname{N}_{Y|X} \oplus \OO_Y)$
 \end{enumerate}
-from the invariants of the ambient variety $X$.
+from the \tred{full genus zero and reduced genus one theory} of the ambient variety $X$.
 \end{customthm}
+
+We pursue a strategy laid out by Vakil and Gathmann, building on work of Caporaso and Harris~\cite{CH98,Ga,Vre}.
+The first step is to express the locus of maps where the contact order degenerates in terms of Chern classes of natural vector bundles.
+The second step is to describe that locus in terms of fiber products of moduli spaces with smaller invariants.
+Novelties are introduced in both steps.
+We achieve the first step using techniques that are entirely within tropical and logarithmic geometry, drastically simplifying Gathmann's calculation.
+For the second step, we contend with the interaction of the relative splitting formula and the geometry of elliptic singularities, which is entirely new (Section REFERNCE).
+We express the factorization property in terms of tautological classes and combinatorial manipulations, leading to Theorem~\ref{thm: recursion}.
 
@@
 We realize the locus as the vanishing locus of a section of a line bundle that comes from tropical geometry — from a piecewise linear function on the fan.
-The systematic understanding of logarithmic line bundles arising in this fashion is likely to play an important in logarithmic enumerative geometry.
-
-Our analysis leads naturally to a study of a ``main component’’ double ramification cycle for target manifolds in genus one.
+The systematic understanding of logarithmic line bundles arising in this fashion is likely to play an important \tred{role} in logarithmic enumerative geometry.
+
+Our analysis leads naturally to \tred{the} study of a ``main component’’ double ramification cycle for target manifolds in genus one.
 The virtual geometry of this was studied in recent work of Janda, Pandharipande, Pixton, and Zvonkine~\cite{DRCBundle}.
-We do not know how to calculate an expression for this main component contribution, but we repurpose E.~Katz's topological recursion relations \cite{EKatz} to complete the algorithm.
+We do not know how to calculate a \tred{closed formula} for this main component contribution, but we repurpose E.~Katz's topological recursion relations \cite{EKatz} to complete the algorithm.
 We note that even in genus one, an understanding of the main component contributions of the double ramification cycle for target manifolds would be interesting.
@@
 The conceptual features of one space are often computational bugs, and vice versa, and we believe that the techniques developed in the genus one case here will be used repeatedly in logarithmic Gromov--Witten theory calculations.
-In particular, we use frequently use Kato's perspective on logarithmic blowups as subfunctors that was applied in~\cite{RSPW,RSPW2}.
-
-\subsection*{Acknowledgements} We have benefited from fruitful conversations with friends and colleagues, including Davesh Maulik, Jonathan Wise, and [other people].
+In particular, we frequently use Kato's perspective on logarithmic blowups as subfunctors that was applied in~\cite{RSPW,RSPW2}.
+
+\subsection*{Acknowledgements} We have benefited from fruitful conversations with friends and colleagues, including \tred{Francesca Carocci,} Davesh Maulik, Jonathan Wise, and [other people].
 Important aspects of this work were completed while L.B.
@@
 were visiting MIT in Spring 2018 and the University of Cambridge in Winter 2019, and we thank these institutions for their hospitality.
-
-\part{The moduli space and its deformation theory}
-
-\section{Construction and logarithmic smoothness}
-
-\subsection{The absolute story} Let $\mathfrak M_{1,n}$ be the logarithmic algebraic stack of genus $1$ $n$-pointed prestable curves.
-Let $\plC$ be a $n$-pointed genus $1$ tropical curve.
-Let $C$ be a logarithmic curve over $S$, let $\plC$ denote its tropicalization, and let $\lambda$ be the section of $\overline{M}_{C/S}$ giving the distance from the core.
+\tred{L.B.
+would like to thank Imperial College London, the LSGNT, the Royal Society, 3CinG, the MSRI program ''Enumerative Geometry beyond Numbers``, and MPIM-Bonn for support.}
+
+\newpage
+
+%\part{ The moduli space and its deformation theory}
+
+\section{Constructions and logarithmic smoothness}
+
+\subsection{The absolute case} Let $\mathfrak M_{1,n}$ be the logarithmic algebraic stack of $n$-pointed prestable curves of genus $1$.
+Let $\plC$ be a $n$-pointed genus $1$ tropical curve; \tred{we formally replace the minimal subcurve of genus $1$ by a single vertex, called the \emph{core}}.
+Let $C$ be a logarithmic \tred{smooth} curve over $S$, let $\plC$ denote its tropicalization, and let $\lambda$ be the section of $\overline{M}_{C/S}$ giving the distance from the \tred{core}.
 
 We begin by recalling the logarithmic moduli spaces of genus $1$ curves constructed in~\cite[Sections 2 \& 4]{RSPW}.
-Given a family of tropical curves over a base $\sigma$, a central alignment is a piecewise-linearly varying choice of radius $\delta_s$ for $s\in\sigma$, together with a consistent ordering of the vertices that lie inside the circle of radius $s$ around the core components.
+Given a family of tropical curves over a base $\sigma$, a central alignment is a piecewise-linearly varying choice of radius $\delta_s\in \overline{M}_S$ for $s\in\sigma$, together with a consistent ordering of the vertices that lie inside the circle of radius $\delta_s$ around the core.
 Precisely, let $T$ be a geometric point with logarithmic structure.
@@
 \begin{definition}
-A \textbf{central alignment} of $C/T$ is an element $\delta\in\overline{M}_S$ such that
+A \textbf{centrally aligned curve} is a pair $(C/T,\delta)$, where $\delta\in\overline{M}_T$, such that:
 \begin{enumerate}
@@
 
-The moduli stack $\mathfrak M_{1,n}^{\mathrm{cen}}$ is a logarithmic algebraic stack in the smooth topology.
-The main construction of~\cite{RSPW} canonically associates to any radially aligned family of curves $\mathcal C_S$ a partial destabilization $\widetilde{\mathcal C_S}$ and a contraction
+\sout{In essence, this is a family of curves where every vertex of the tropical curve $\plC$ is either inside or outside the circle of radius $\delta$ around the core genus $1$ subcurve.}
+
+The moduli stack $\mathfrak M_{1,n}^{\mathrm{cen}}$ is a logarithmic algebraic stack in the smooth topology, \tred{and $\mathfrak M_{1,n}^{\mathrm{cen}}\to\mathfrak M_{1,n}$ is a logarithmic modification}.
+The main construction of~\cite{RSPW} canonically associates to any \tred{centrally} aligned family of curves $\mathcal C_S$ a partial destabilization $\widetilde{\mathcal C}_S$ and a contraction
 \[
-\widetilde{\mathcal C_S}\to \overline{\mathcal C_S},
+\widetilde{\mathcal C}_S\to \overline{\mathcal C}_S,
 \]
-where $\overline{\mathcal C_S}$ is a Gorenstein elliptic singular curve.
+where $\overline{\mathcal C}_S$ may contain a Gorenstein elliptic singularity \cite{SMY1}.
 The number of branches is equal to the number of excident edges at the circle of radius $\delta$.
@@
 
-The space of stable maps $\overline{\mathcal M}^{\mathrm{cen}}_{1,n}(\mathbb P^N,d)$ from the universal nodal curve $\mathcal C$ over the stack $\mathfrak M_{1,n}^{\mathrm{cen}}$ is a proper and algebraic, with projective coarse moduli.
-The \textbf{factorization condition} that the map $\mathcal C\to \mathbb P^N$ factors through the contraction $\widetilde{\mathcal C}\to \overline{\mathcal C}$ is a closed condition.
+The space of stable maps $\overline{\mathcal M}^{\mathrm{cen}}_{1,n}(\mathbb P^N,d)$ from the universal nodal curve $\mathcal C$ over the stack $\mathfrak M_{1,n}^{\mathrm{cen}}$ is a proper and algebraic, with projective coarse moduli space.
+\tred{A compatibility condition is required, namely that the circle of radius $\delta$ passes through at least one component of positive degree.} A stable map in this space is said to satisfy the \textbf{factorization condition} if the map $\mathcal C\to \mathbb P^N$ factors through the contraction $\widetilde{\mathcal C}\to \overline{\mathcal C}$.
+
 \begin{thm}[{\cite[Theorem B]{RSPW}}]
-The substack $\mathcal{VZ}_{1,n}(\mathbb P^N,d)$ of $\overline{\mathcal M}^{\mathrm{cen}}_{1,n}(\mathbb P^N,d)$ parameterizing maps to $\mathbb P^N$ that satisfy the factorization property is smooth and proper of the expected dimension.
+The substack $\VZ_{1,n}(\mathbb P^N,d)$ of $\overline{\mathcal M}^{\mathrm{cen}}_{1,n}(\mathbb P^N,d)$ parameterizing maps to $\mathbb P^N$ that satisfy the factorization property is smooth and proper of the expected dimension.
 \end{thm}
 
-\subsection{Relative geometry: compactification} Fix $H\subset \mathbb P^N$ be a hyperplane.
-Let $\alpha$ be a partition of the degree $d$.
+The remainder of this section lifts this condition to the category of relative maps to the pair $(\mathbb P^N,H)$.
+The core of the result is identifying the necessary factorization conditions that remove the obstructions.
+
+\subsection{Relative geometry: compactification} Fix a hyperplane $H\subset \mathbb P^N$.
+Let $\alpha$ be a partition of the degree $d>0$.
 Consider the moduli space $\mathcal M_{1,\alpha}^\circ(\mathbb P^N|H)$ of maps from smooth elliptic curves $C\to \mathbb P^N$ that meet $H$ at finitely many marked points with vanishing orders given by the partition $\alpha$.
-This is a smooth non-compact Deligne--Mumford stack.
+This is a smooth, but non-proper Deligne--Mumford stack.
 
 We will first compactify the space described above, and then desingularize it.
-For the compactification, we begin with Abramovich--Chen--Gross--Siebert's space of logarithmic stable maps, though we will typically work with various subcategories and variants.
+For the compactification, we begin with Abramovich--Chen--Gross--Siebert's space of logarithmic stable maps, though we will typically work with various subcategories and variants~\cite{AbramovichChenLog,ChenLog,GrossSiebertLog,KimLog}.
+\tred{Let $\PP^N$ be endowed with the divisorial logarithmic structure induced by $H$.}
 
 The moduli space $\overline{\mathcal{M}}^{\operatorname{log}}_{1,\alpha}(\mathbb P^N|H)$ is a fibred category over logarithmic schemes, whose fiber over $(S,M_S)$ is the groupoid of logarithmic curves of genus $1$ over $(S,M_S)$ equipped with a map to $\mathbb P^N$ of degree $d$ and contact order $\alpha$.
-It is a fundamental fact in the subject that this category is representable by a proper algebraic stack with logarithmic structure.
+It is a fundamental fact in the subject that this category is representable by a proper algebraic stack with logarithmic structure, parameterizing minimal objects~\cite{ChenLog}.
 
@@
 $$ 
-The fiber product leads to a fourth moduli space of \textbf{centrally aligned logarithmic maps to $(\mathbb P^n,H)$}, which we denote $\widetilde{\mathcal{VZ}}_{1,\alpha}(\mathbb P^N|H)$.
-
-\subsection{Relative geometry: expansions} Our next task is to pick out a non-singular principal component in $\widetilde{\mathcal{VZ}}_{1,\alpha}(\mathbb P^N|H)$.
+The fiber product leads to a fourth moduli space of \textbf{centrally aligned logarithmic maps to $(\mathbb P^n,H)$}, which we denote $\widetilde{\VZ}_{1,\alpha}(\mathbb P^N|H)$.
+
+\subsection{Relative geometry: expansions} Our next task is to pick out a non-singular principal component in $\widetilde{\VZ}_{1,\alpha}(\mathbb P^N|H)$.
 The principal component of this space, consisting of the closure of the space of maps from nonsingular curves, maps into the principal component of $\overline{\mathcal M}^{\mathrm{cen}}_{1,n}(\mathbb P^N,d)$.
 Indeed, smoothable logarithmic maps are, in particular, smoothable as ordinary maps.
-However, an additional condition is required to isolate the principal component of the space of logarithmic maps.
+An additional condition is required to isolate the principal component of the space of logarithmic maps.
 
@@
 To elucidate the connection with the static target, consider a logarithmic stable map $[C\to (\mathbb P|H)]$ over $\mathrm{Spec} \ (\mathbb N\to \mathbb C)$.
-At the level of tropicalizations, we have a map of fans
+At the level of tropicalizations, there is a map of fans
 \[
@@
 Here the latter is the $s$-times iterated deformation to the normal cone of $H$ in $\mathbb P^N$.
-The number of components is equal to the number of vertices in $\widetilde{\mathbb R}_{\geq 0}$.
+The components \tred{of the target} are in bijection with the number of vertices in $\widetilde{\mathbb R}_{\geq 0}$.
 The curve is modified by adding rational components corresponding to the newly introduced vertices.
@@
 The result is a logarithmic stable map to an expanded target $\mathbb P^N[s]$, together with a contraction to the main target component $\mathbb P^N[s]\to\mathbb P^N$.
-More generally, this construction is easily modified for any family of logarithmic maps, such that the vertices of $\plC$ are totally ordered in the family, see~\cite{} for details.
+\tred{Two maps are considered equivalent if they differ by $\Gm$-scaling the target at higher level.}
 
 Globally, Kim constructs a moduli space of logarithmic stable maps to expanded degenerations, which on logarithmic points, reduces to the above construction~\cite{KimLog}.
-Indeed, by above description, Kim's space is identified with a subcategory of the Abramovich--Chen--Gross--Siebert space, and its minimal objects are identified with a logarithmic modification of the unexpanded space.
+Indeed, by the above description, Kim's space is identified with a subcategory of the Abramovich--Chen--Gross--Siebert space, and its dual minimal monoids are cones in a subdivision of the dual minimal cones of the unexpanded space.
+This process is outlined in complete generality in~\cite[\S~2]{R19}.
 
 \subsection{Relative geometry: factorization}\label{subsection factorisation} Let $[C\to \mathbb P^N[s]\to \mathbb P^N]$ be a logarithmic map from a centrally aligned curve to an expansion.
-Recall that $\mathbb P^N[s]$ consists of a union of $\mathbb P^N$ with the projective bundle $\mathbb P(\mathcal O\oplus \mathcal O(1))$.
+Recall that $\mathbb P^N[s]$ consists of a union of $\mathbb P^N$ with \tred{$s$ copies of} the projective bundle $\mathbb P(\mathcal O_H\oplus \mathcal O_H(1))$.
 We refer to these latter components as \textbf{the higher levels}.
-Thus, we will say that subcurve $D\subset C$ maps to \textbf{higher level} if the collapsed map
+Thus, we will say that a subcurve $D\subset C$ maps to \textbf{higher level} if the collapsed map
 \[
-D\to \mathbb P^N
+C\to \mathbb P^N
 \]
-is contained in $H\subset \mathbb P^N$.
-
-Let $D_1\subset C$ be the maximal genus $1$ subcurve that is mapped to higher level contracted by the map $C\to \mathbb P^N[s]$ in the fiber direction.
-Let $\delta_1$ be the associated radius from the core to the nearest non-contract component.
-Let $D_2$ be the maximal genus $1$ subcurve that is contracted by the collapsed map to $\mathbb P^N$, and let $\delta_2$ be the associated radius.
+maps $D$ into $H\subset \mathbb P^N$.
+
+Let\marginpar{I replace $D_1,D_2$ by the more suggestive $D_F,D_B$.} $D_F\subset C$ be the maximal genus $1$ subcurve that is \sout{mapped to higher level} contracted by the map $C\to \mathbb P^N[s]$ \sout{in the fiber direction}.
+Let $\delta_F$ be the associated radius from the circuit to the nearest non-contracted component.
+Let $D_B$ be the maximal genus $1$ subcurve that is contracted by the collapsed map to $\mathbb P^N$, and let $\delta_B$ be the associated radius.
 This coincides with the radius of the underlying map to $\mathbb P^N$.
-Of course, $\delta_1\leq \delta_2$.
-
-The datum $(\delta_1,\delta_2)$ determines a destabilization $\widetilde C$ of $C$ together with successive contractions $\widetilde C\to \overline C_1\to\overline C_2$.
-Keeping this definition, we come to the key definition.
+Of course, $\delta_F\leq \delta_B$, \tred{so $(C,\delta_F)$ is centrally aligned too}.
+
+The datum $(\delta_F,\delta_B)$ determines a destabilization $\widetilde C$ of $C$ together with successive contractions $\widetilde C\to \overline C_F\to\overline C_B$.
+The contractions are constructed directly from~\cite[Section~3]{RSPW}.
+
+The following condition identifies the locus of smoothable maps.
 
@@
 \begin{itemize}
-\item the map $C\to \mathbb P^N[s]$ factors through $\overline C_1$ such that at least one branch of $\overline C_1$ has positive degree in the fiber direction. 
-\item the collapsed map to $\mathbb P^N$ factorizes through $\overline C_2$ such that at least one branch of $\overline C_2$ has positive degree.
+\item the map $C\to \mathbb P^N[s]$ factors through $\overline C_F$ such that at least one branch of $\overline C_F$ has positive degree in the fiber direction; 
+\item the collapsed map to $\mathbb P^N$ factorizes through $\overline C_B$ such that at least one branch of $\overline C_B$ has positive degree.
 \end{itemize}
@@
 
-In particular, if $[C\to \mathbb P^N[s]\to \mathbb P^N]$ is a family of centrally aligned maps over $S$ that factorizes completely, there is a forgetful moduli map $S\to \mathcal{VZ}_{1,n}(\mathbb P^N,d)$, to the principal component of the space of absolute maps.
-
-Let $\mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)$ be stack of maps from centrally aligned curves to expansions of $\mathbb P^N$ that factorize completely.
+In particular, if $[C\to \mathbb P^N[s]\to \mathbb P^N]$ is a family of centrally aligned maps over $S$ that factorizes completely, there is a forgetful moduli map $S\to \VZ_{1,n}(\mathbb P^N,d)$, to the principal component of the space of absolute maps.
+
+Let $\VZ_{1,\alpha}(\mathbb P^N|H)$ be the stack of maps from centrally aligned curves to expansions of $\mathbb P^N$ that factorize completely.
 
 \begin{thm}\label{thm: log-smoothness}
-The stack $\mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)$ is proper and logarithmically non-singular over $\mathrm{Spec} \ \mathbb C$. 
+The stack $\VZ_{1,\alpha}(\mathbb P^N|H)$ is proper and logarithmically \tred{smooth} over $\mathrm{Spec} \ \mathbb C$. 
 \end{thm}
@@
 $$
-\nu: \mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)\to \mathcal{VZ}_{1,n}(\mathbb P^N,d),
+\nu: \VZ_{1,\alpha}(\mathbb P^N|H)\to \VZ_{1,n}(\mathbb P^N,d),
 $$
@@
 The map is certainly centrally aligned, and we have already argued above that it satisfies the factorization property for $\mathbb P^N$ after composition.
-The morphism $\nu$ is in fact proper: the verification for the valuative criterion is the essential content of Vakil's Lemma~\cite[Lemma~5.9]{Vak}, and a detailed proof may be found in~\cite[Theorem~4.3]{RSPW}.
-
-We come to logarithmic smoothness.
-Assume first that the elliptic curve maps into higher level.
+The moduli space $\VZ_{1,\alpha}(\mathbb P^N|H)$ is proper.
+Indeed, the verification of the valuative criterion follows exactly as in Vakil's Lemma~\cite[Lemma~5.9]{Vre}.
+A direct proof that the factorization property is a closed condition may be found in~\cite[Theorem~4.3]{RSPW}.
+
+We come to logarithmic smoothness. If the elliptic curve does not map into higher level, then unobstructedness proceeds exactly as in~\cite[Section~4.5]{RSPW}.
+
+Assume now that the elliptic curve maps into higher level.
 Note that the relative logarithmic tangent bundle of the expansion, over the base $\mathbb P^N$ is a trivial line bundle of rank $1$, as the fibers are toric.
@@
 \bcd
-C \ar[r] & \overline{C}_1 \ar[r] \ar[d] & \overline{C}_2 \ar[d] \\
+C \ar[r] & \overline{C}_F \ar[r] \ar[d] & \overline{C}_B \ar[d] \\
 & \mathbb P^N[s] \ar[r] & \mathbb P^N
 \ecd
-factorizing completely. Let $f_B$ and $f_T$ be the maps from $C$ to the base and total space respectively. Examining the morphism $\nu$, we see that there is a map
+factorizing completely. Let $f_B$ and $f$ be the maps from $C$ to the base and total space respectively. Examining the morphism $\nu$, we see that there is a map
 \[
-\mathrm{Def}(C,f_B)\to \mathrm{Obs}(f_T/(C,f_B)) = H^1(\overline{C}_1,\mathcal O_{\overline{C}_1}),
+\mathrm{Def}(C,f_B)\to \mathrm{Obs}(f/(C,f_B)) = H^1(\overline{C}_F,\mathcal O_{\overline{C}_F}),
 \]
@@
 
-We recall how the group $H^1(\overline{C}_1,\mathcal O_{\overline{C}_1})$ functions as the obstruction group for the lifting.
-It suffices to work near the minimal grnus $1$ subcurve $D_1$ of $C_1$, since the rest of the curve is rational.
+We note the manner in which the group $H^1(\overline{C}_F,\mathcal O_{\overline{C}_F})$ functions as the obstruction group for the lifting.
+It suffices to work near the minimal genus $1$ subcurve $D_F$ of $C$, since the rest of the curve is rational.
 This lifting is given by a rational function with prescribed orders of poles given by the slopes of the tropicalization map.
-That is, if $\alpha$ be the piecewise linear function giving this tropical map, then the lifting is described by a section of the associated bundle $\mathcal O_{C_1}(-\alpha)$.
+That is, if $\alpha$ be the piecewise linear function giving this tropical map, then the lifting is described by a section of the associated bundle $\mathcal O_{C}(-\alpha)$.
 
 Given a strict square-zero extension $S'$ of $S$, the piecewise linear function $\alpha$ extends uniquely by strictness to any deformation of the curve.
-The resulting deformation of $\mathcal O_{C_1}(-\alpha)$ produces an infinitesimal deformation of the trivial bundle in the Picard group, whose class in $H^1(\overline{C}_1,\mathcal O_{\overline{C}_1})$, is the obstruction to deformation.
-We will show that it is possible to choose a deformation of $(C,f_B)$ that cancels out the obstruction to lifting to $f_T$, and thus the map to the obstruction space above is surjective.
-
-The line bundle $\mathcal O_{C_1}(-\alpha)$ is equivalent to the divisor $\sum a_i x_i$ where $x_i$ are the points connecting $D_1$ to the rest of the curve, and $a_i$ are the slopes of $\alpha$ along the edges corresponding to the $x_i$.
-Infinitesimally moving the point $x_i$ is a deformation of the curve that is unobstructed by the map $f_B$, since the map is constant on the interiors of the circuits.
-By deforming the $x_i$, at least one of which is nonzero, we produce a one-dimensional space of obstructions.
-The absolute obstructions therefore vanish, since they are the cokernel of a surjective map, so the result follows.
+The resulting deformation of $\mathcal O_{C}(-\alpha)$ produces an infinitesimal deformation of the trivial bundle in the Picard group, whose class in $H^1(\overline{C}_F,\mathcal O_{\overline{C}_F})$, is the obstruction to deformation.
+We will show that it is possible to choose a deformation of $(C,f_B)$ that cancels out the obstruction to lifting to $f$, and thus the map to the obstruction space above is surjective.
+
+The line bundle $\mathcal O_{C}(-\alpha)$ is equivalent to the divisor $\sum a_i x_i$ where $x_i$ are the points connecting $D_F$ to the rest of the curve, and $a_i$ are the slopes of $\alpha$ along the edges corresponding to the $x_i$.
+Infinitesimally moving the point $x_i$ is a deformation of the curve that is unobstructed by the map $f_B$, since the map is constant on the interior of the \tred{circle of radius $\delta_B$}.
+By deforming the $x_i$, at least one of which has nonzero $a_i$, we produce a one-dimensional space of obstructions.
+The absolute obstructions therefore vanish, \sout{since they are the cokernel of a surjective map,} so the result follows.
 %Consider an $S$-family of expanded maps $[F: C\to \mathbb P^N[s]$.
@@
 
-The above theorem guarantees that the singularities of the space of totally factorized maps to expansions is logarithmically smooth. In fact, one can say more in this case.
+The above theorem guarantees that the singularities of the space of totally factorized maps to expansions is logarithmically smooth.
+In fact, one can say more in this case.\marginpar{I don't understand the point of this Cor.
+Can we make it into a short remark?}
 
 \begin{cor}
-The logarithmically smooth stack $\mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)$ has at worst orbifold singularities, i.e. admits a non-representable cover by a smooth Deligne--Mumford stack.
+The logarithmically smooth stack $\VZ_{1,\alpha}(\mathbb P^N|H)$ has at worst orbifold singularities, i.e. admits a non-representable cover by a smooth Deligne--Mumford stack.
 \end{cor}
@@
 \begin{proof}
-Since $\mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)$ is logarithmically smooth, it will suffice to show that the cones of its tropicalization are simplicial.
+Since $\VZ_{1,\alpha}(\mathbb P^N|H)$ is logarithmically smooth, it will suffice to show that the cones of its tropicalization are simplicial.
 To see this, consider a logarithmic stable map to an expansion $C\to \mathbb P^N[s]$ without a central alignment.
@@
 The alignment procedure is an iterated barycentric subdivision at the level of tropical moduli spaces, as explained in~\cite[Section 4.6]{RSPW}, and such subdivisions preserve the property of being simplicial.
-We conclude from this that the blowup $\widetilde{\mathcal{VZ}}^{\mathrm{exp}}_{1,\alpha}(\mathbb P^N|H)$ obtained by centrally aligning Kim's spaces has simplicial cones.
-Finally, the morphism $\mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)\to \widetilde{\mathcal{VZ}}^{\mathrm{exp}}_{1,\alpha}(\mathbb P^N|H)$ is strict, so the cones of $\mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)$ are simplicial, as claimed.
+We conclude from this that the blowup $\widetilde{\VZ}^{\mathrm{exp}}_{1,\alpha}(\mathbb P^N|H)$ obtained by centrally aligning Kim's spaces has simplicial cones.
+Finally, the morphism $\VZ_{1,\alpha}(\mathbb P^N|H)\to \widetilde{\VZ}^{\mathrm{exp}}_{1,\alpha}(\mathbb P^N|H)$ is strict, so the cones of $\VZ_{1,\alpha}(\mathbb P^N|H)$ are simplicial, as claimed.
 \end{proof}
@@
 
-\noindent The logarithmic smoothness established in Theorem~\ref{thm: log-smoothness} implies that $\mathcal{VZ}_{1,\alpha}(\mathbb P^N|H,d)$ is an orbifold toroidal embeddeding.
+\noindent The logarithmic smoothness established in Theorem~\ref{thm: log-smoothness} implies that $\VZ_{1,\alpha}(\mathbb P^N|H,d)$ is an orbifold toroidal embeddeding.
 Consequently, the irreducible components of its boundary and their intersections form a stratification of the space.
@@
 \Sigma_{1,\alpha}(\mathbb P^N|H,d)$ is the fan of the toroidal embedding $
-\mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)$. In particular, the codimension $k$ strata of $
-\mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)$ are in inclusion reversing bijection with the dimension $k$ cones in $
+\VZ_{1,\alpha}(\mathbb P^N|H)$. In particular, the codimension $k$ strata of $
+\VZ_{1,\alpha}(\mathbb P^N|H)$ are in inclusion reversing bijection with the dimension $k$ cones in $
 \Sigma_{1,\alpha}(\mathbb P^N|H,d)$.
@@
 The construction above has been given to mimic the construction of the space $
-\mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)$.
-Specifically, the fact that cone complex $\Sigma^{\mathrm{cen}}$ is the cone complex attached to the logarithmic stack $\widetilde{\mathcal{VZ}}_{1,\alpha}(\mathbb P^N|H)$ of centrally aligned maps to expansions, follows immediately from its description as a subcategory of the fibered category (over logarithmic schemes) of $\mathcal M^{\mathrm{log}}_{1,\alpha}(\mathbb P^N|H)$.
+\VZ_{1,\alpha}(\mathbb P^N|H)$.
+Specifically, the fact that cone complex $\Sigma^{\mathrm{cen}}$ is the cone complex attached to the logarithmic stack $\widetilde{\VZ}_{1,\alpha}(\mathbb P^N|H)$ of centrally aligned maps to expansions, follows immediately from its description as a subcategory of the fibered category (over logarithmic schemes) of $\mathcal M^{\mathrm{log}}_{1,\alpha}(\mathbb P^N|H)$.
 To complete the result, we note that $
-\mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)$ has a strict map to $
-\mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)$, so its cone complex is a subcomplex of $\Sigma^{\mathrm{cen}}$.
+\VZ_{1,\alpha}(\mathbb P^N|H)$ has a strict map to $
+\VZ_{1,\alpha}(\mathbb P^N|H)$, so its cone complex is a subcomplex of $\Sigma^{\mathrm{cen}}$.
 The fact that it must be contained in the subcomplex of well-spaced curves is immediate from Proposition~\ref{prop: well-spaced}.l
@@
 
-\subsection{Rubber variants} In our implementation of the relative theory, we will need the naturally ``rubber'' variant of the space of maps $
-\mathcal{VZ}_{1,\alpha}(\mathbb P^N|H)$, where the entire curve is mapped into higher levels.
+\subsection{Rubber variants} In our implementation of the relative theory, we will need the ``rubber'' variant of the space of maps $
+\VZ_{1,\alpha}(\mathbb P^N|H)$, where the entire curve is mapped into higher levels.
 
@@
 Equip this space with the logarithmic structure coming from the $0$ and $\infty$ sections of the bundle.
-Consider the moduli space $\mathcal{VZ}_{1,\alpha}(\mathbb P/\mathbb G_m)$ of logarithmic maps
+Consider the moduli space $\VZ_{1,\alpha}(\mathbb P/\mathbb G_m)$ of logarithmic maps
 \[
@@
 \begin{thm}
-The stack $\mathcal{VZ}_{1,\alpha}(\mathbb P/\mathbb G_m)$ is logarithmically smooth.
+The stack $\VZ_{1,\alpha}(\mathbb P/\mathbb G_m)$ is logarithmically smooth.
 \end{thm}
 
-It is convenient to work with the logarithmic multiplicative group and its torsors.
+The main point in the proof of this statement is that on the space of non-degenerate maps with smooth domains, the map from $\VZ^\circ_{1,\alpha}(\mathbb P)\to \VZ^\circ_{1,\alpha}(\mathbb P/\mathbb G_m)$ is a $\mathbb G_m$ torsor.
+Correspondingly, the map on compact moduli spaces is a nodal curve fibration.
+To prove this, it is convenient to work with the logarithmic multiplicative group and its torsors.
 Recall that the \textit{logarithmic multiplicative group} $\mathbb G_{\mathrm{log}}$ is the functor on logarithmic schemes whose value on a logarithmic scheme $S$ is the group of global sections $H^0(S,M_S^{\mathrm{gp}})$.
 This functor is representable only after a logarithmically \'etale cover.
+Background may be found in~\cite{MW17,RW19}.
 
@@
 
-{\bf Add reference to Wise--R '19 and Marcus--Wise '17 for the multiplicative group.}
-
 \begin{proof}
-Consider the stack over logarithmic schemes $\mathcal{VZ}_{1,\alpha}(\mathbb P_{\mathrm{log}})$ of stable logarithmic maps that factorize completely.
+Consider the stack over logarithmic schemes $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}})$ of stable logarithmic maps that factorize completely.
 Here, stability for the map coincides with stability for the projection to $\mathbb P^{N-1}$.
 The arguments in the previous section show that maps to $\mathbb P$ that factorize completely are unobstructed.
-Since this space is a logarithmically \'etale cover of $\mathcal{VZ}_{1,\alpha}(\mathbb P_{\mathrm{log}})$, logarithmic smoothness of the latter follows.
-
-The logarithmic multiplicative group $\mathbb G_{\mathrm{log}}$ acts on $\mathcal{VZ}_{1,\alpha}(\mathbb P_{\mathrm{log}})$ by translation.
-Tautologically, $\mathcal{VZ}_{1,\alpha}(\mathbb P_{\mathrm{log}})$ is a $\mathbb G_{\mathrm{log}}$-torsor over the moduli problem of maps up to this $\mathbb G_{\mathrm{log}}$ translation.
+Since this space is a logarithmically \'etale cover of $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}})$, logarithmic smoothness of the latter follows.
+
+The logarithmic multiplicative group $\mathbb G_{\mathrm{log}}$ acts on $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}})$ by translation.
+Tautologically, $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}})$ is a $\mathbb G_{\mathrm{log}}$-torsor over the moduli problem of maps up to this $\mathbb G_{\mathrm{log}}$ translation.
 It is representable after a logarithmically \'etale modification by a family of nodal curves.
-It follows that the space  $\mathcal{VZ}_{1,\alpha}(\mathbb P_{\mathrm{log}}/\mathbb G_{\mathrm{log}})$ of maps up to translation that factorize completely is logarithmically smooth.
-
-To conclude the main result, we compare the stacks $\mathcal{VZ}_{1,\alpha}(\mathbb P_{\mathrm{log}}/\mathbb G_{\mathrm{log}})$ and  $\mathcal{VZ}_{1,\alpha}(\mathbb P/\mathbb G_m)$.
+It follows that the space  $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}}/\mathbb G_{\mathrm{log}})$ of maps up to translation that factorize completely is logarithmically smooth.
+
+To conclude the main result, we compare the stacks $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}}/\mathbb G_{\mathrm{log}})$ and  $\VZ_{1,\alpha}(\mathbb P/\mathbb G_m)$.
 Since a map to $\mathbb P$ gives rise immediately to a map to $\mathbb P_{\mathrm{log}}$, there is a morphism
 \[
-\mathcal{VZ}_{1,\alpha}(\mathbb P/\mathbb G_m)\to \mathcal{VZ}_{1,\alpha}(\mathbb P_{\mathrm{log}}/\mathbb G_{\mathrm{log}}).
+\VZ_{1,\alpha}(\mathbb P/\mathbb G_m)\to \VZ_{1,\alpha}(\mathbb P_{\mathrm{log}}/\mathbb G_{\mathrm{log}}).
 \]
-A straightforward application of the infinitesimal lifting criterion shows that this map is logarithmically \'etale, so the result follows.
+An application of the infinitesimal lifting criterion shows that this map is logarithmically \'etale, so the result follows.
 \end{proof}
-
-The main point in the proof above is that on the space of non-degenerate maps with smooth domains, the map from $\mathcal{VZ}^\circ_{1,\alpha}(\mathbb P)\to \mathcal{VZ}^\circ_{1,\alpha}(\mathbb P/\mathbb G_m)$ is a $\mathbb G_m$ torsor, and correspondingly on the compact spaces it is a $\mathbb G_{\mathrm{log}}$-torsor.
-The logarithmically \'etale modification guarantee representability, and turn this into a nodal curve fibration.
 
@@
 Now let $(X,Y)$ be a smooth pair with $Y$ very ample.
-The definition given in \S \ref{subsection factorisation} applies in this setting as well, producing a moduli space $\VZ_{1,\alpha}(X|Y,\beta)$ together with a morphism
+The definition given in \S \ref{subsection factorisation} applies in this setting, producing a moduli space $\VZ_{1,\alpha}(X|Y,\beta)$ together with a morphism
 \begin{equation*} \VZ_{1,\alpha}(X|Y,\beta) \to \ol\Mcal^{\operatorname{log}}_{1,\alpha}(X|Y,\beta)\end{equation*}
@@
 
-Since $\VZ_{1,n}(\PP^N,d)$ is smooth and $\VZ_{1,n}(X,\beta)$ carries a natural virtual class \cite[Theorem 4.4.1]{RSPW} there is a diagonal pull-back morphism \cite{Ga} \cite[Appendix C]{BattistellaNabijou}, which we use to define the virtual class on the space of maps to $(X,Y)$:
+Since $\VZ_{1,n}(\PP^N,d)$ is smooth and $\VZ_{1,n}(X,\beta)$ carries a natural virtual class \cite[Theorem 4.4.1]{RSPW} there is a diagonal pull-back morphism~\cite[Appendix C]{BattistellaNabijou}, which we use to define the virtual class on the space of maps to $(X,Y)$:
 \begin{equation*} \virt{\VZ_{1,\alpha}(X|Y,\beta)} := i_\Delta^! [\VZ_{1,\alpha}(\PP^N|H,d)]. \end{equation*}
 Since $\VZ_{1,\alpha}(X|Y,\beta)$ comes equipped with evaluation maps and cotangent line classes, we immediately arrive at a definition of reduced Gromov--Witten invariants for the pair $(X,Y)$.
+This is the same manner in which Gathmann defines his virtual classes~\cite{Ga}.
 
@@
 The pair $(\Lcal_k,s_k)$ is most naturally constructed on the moduli space $\MLog_{1,\alpha}(\PP^N|H,d)$ of non-expanded log maps; the corresponding pair on $\VZ_{1,\alpha}(\PP^N|H,d)$ will be obtained via pull-back.
-Consider therefore the tropicalisation $\Sigma^{\log}$ of $\MLog_{1,\alpha}(\PP^N|H,d)$.
-By tropicalising the universal family, we obtain a family of tropical maps
+Consider therefore the tropicalisation $\Sigma^{\log}$ of $\MLog_{1,\alpha}(\PP^N|H,d)$, identified as usual with the moduli space of tropical maps to $\RR_{\geq 0}$.
+We have a universal family
 \bcd
@@
 \begin{equation*} \cchern_1(\Lcal_k) = \alpha_k \psi_k + \ev_k^\st H.\end{equation*}
-This gives the construction of $(\Lcal_k,s_k)$ on $\MLog_{1,\alpha}(\PP^N|H,d)$; the construction on $\VZ_{1,\alpha}(\PP^N|H,d)$ is obtained by pull-back.
-The relevant piecewise-linear function is simply the composition:
+This gives the construction of $(\Lcal_k,s_k)$ on $\MLog_{1,\alpha}(\PP^N|H,d)$; the construction on $\VZ_{1,\alpha}(\PP^N|H,d)$ is given by pull-back.
+The relevant piecewise-linear function is the composition:
 \begin{equation*} \Sigma_{1,\alpha}(\PP^N|H,d) \to \Sigma^{\log} \to \RR_{\geq 0}.\end{equation*}
@@
 \end{enumerate}
-Notice that this process contains some redundancies: when we choose a ray in step (3) above, some of the edge lengths or vertex positions may get set to $0$.
-This induces a generisation of the intial combinatorial type $\Delta$, given by contracting appropriate edges of the dual graph and/or moving appropriate vertices from $\RR_{>0}$ to $0$.
+Notice that this process contains some redundancies: upon choosing a ray in the tropical moduli space, some of the edge lengths or vertex positions may get set to $0$.
+This induces a generisation of the intial combinatorial type $\Delta$, given by contracting the corresponding edges of the dual graph and moving the corresponding vertices from $\RR_{>0}$ to $0$.
 By the combinatorial type of a stratum in $\VZ_{1,\alpha}(\PP^N|H,d)$ we will always mean this generisation.
@@
 is a log modification, $\widetilde{\Dcal}$ is either exceptional or the proper transform of a log divisor.
-These cases correspond, respectively, to when the core is assigned zero degree or nonzero degree by the combinatorial type.
+These cases correspond, respectively, to when the circuit is assigned zero degree or nonzero degree by the combinatorial type.
 To begin with we will focus on the latter case.
@@
 \begin{lemma}\label{lem:combs} Let $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ be an irreducible component which contributes nontrivially to the recursion, and let $\Delta$ be the corresponding combinatorial type.
-Suppose that $\Delta$ assigns positive degree to the core.
+Suppose that $\Delta$ assigns positive degree to the circuit.
 Then $\Delta$ takes one of the following forms:
@@
 
-\noindent The terminology is due to Vakil, and the pictures in this case are very similar to \cite{Vre} (as we will see later, when the core is assigned zero degree the picture becomes \emph{very} different).
-Note that in these pictures we have deliberately omitted  the degree of each vertex, the expansion factors of the edges and the marked points (except for $x_k$).
+\noindent The terminology is due to Vakil, and the pictures in this case are very similar to \cite{Vre} (we will see later that when the circuit is assigned zero degree the picture becomes \emph{very} different).
+Note that in these pictures we have deliberately omitted the marked points (except for $x_k$), the degree of each vertex, and the expansion factors of the edges.
 The omitted combinatorial data can be distributed arbitrarily, as long as:
@@
 \item the vertices $\sqC_1,\ldots,\sqC_r$ have positive degree;
-\item the core has positive degree;
+\item the ellipse\footnote{(Navid) Didn't we decide this was our new terminology for the circuit?} has positive degree;
 \item every vertex is stable;
@@
 By the discussion above $\Dcal$ corresponds to a ray in the subdivision of $\sigma$ given by imposing the central alignment condition.
-But since the core is assigned positive degree, both radii are equal to $0$ and the subdivision is trivial.
+But since the ellipse is assigned positive degree, both radii are equal to $0$ and the subdivision is trivial.
 We conclude that $\sigma=\RR_{\geq 0}$ (recall we are assuming that the initial and generised combinatorial types coincide).
@@
 For the remainder of this subsection, therefore, we fix a one-dimensional cone $\tau \in \Sigma_{1,\alpha}(\PP^N|H,d)$, let $\Dcal \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$ be the associated log divisor, and assume that $\Dcal$ is contained in $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ and is of type $A,B$ or $C^+$.
-We let $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$ be the log stratum into which $\Dcal$ is mapped; this is indexed by a cone $\sigma \in \Sigma$ corresponding to a combinatorial type $\Delta$, and $\sigma$ is one-dimensional since we are restricting to the type $A,B,C^+$ cases.
+We let $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$ be the log stratum into which $\Dcal$ is mapped; this is indexed by a cone $\epsilon \in \Sigma$ corresponding to a combinatorial type $\Delta$, and $\epsilon$ is one-dimensional since we are restricting to the type $A,B,C^+$ cases.
 
@@
 \begin{proof}
-The choices involved in gluing log maps to expansions (which account for the degrees of the splitting morphisms above) is not affected by the introduction of alignments, so for the purposes of this proof we may act as if these splitting morphisms are the identity maps.
-
-Note that the map $\Dcal\to\Ecal$ is an isomorphism away from the blown-up locus, which is contained inside the locus where the core is contracted.
+The choices involved in gluing log maps to expansions (which accounts for the degrees of the splitting morphisms above) is not affected by the introduction of alignments, so for the purposes of this proof we may pretend as if these splitting morphisms are the identity maps.
+
+Note that the map $\Dcal\to\Ecal$ is an isomorphism away from the blown-up locus, which is contained inside the locus where the circuit is contracted.
 Given an element of $\Dcal$ we can split it along the nodes $q_1,\ldots,q_r$ as in \cite{}.
@@
 \begin{lemma}\label{type A radius lemma} $\lambda(\sqC^\prime) > \delta$ for any component $\sqC^\prime$ of $\sqC_0$ (with notation as in the proof above).\end{lemma}
-\begin{proof} The basic point is that $\Dcal$ is obtained as the disjoint union of the locally closed logarithmic strata contained in the closure of the locally closed stratum on which all of the $\sqC_i$ are irreducible.
+\begin{proof} The basic point is that $\Dcal$ is obtained as the disjoint union of the locally closed logarithmic strata contained in the closure of the stratum where all of the $\sqC_i$ are irreducible.
 If we look at one of these boundary strata, then by definition the associated cone $\sigma \in \Sigma_{1,\alpha}(\PP^N|H,d)$ contains a ray $\tau$ corresponding to the stratum where all the $\sqC_i$ are irreducible; this amounts to setting all edge lengths other than $e_1,\ldots,e_r$ to zero.
 If $f_1,\ldots,f_l$ are some collection of additional edge lengths in $\sigma$ (corresponding to internal nodes in degenerations of the $\sqC_i$) then since $\sigma$ is adjacent to $\tau$ we must have (by construction of the subdivision) $f_1+\ldots+f_l < e_j$ for all $j\in\{1,\ldots,r\}$, since $f_1=\ldots=f_l=0$ and $e_j \neq 0$ on $\tau$.
-In particular, if $\sqC_1$ is degenerate and if $\delta$ denotes the minimal distance from the core to a non-contracted vertex of $\sqC_1$ (which certainly exists since $\sqC_1$ has positive degree) then $\delta < e_1 \leq \lambda(\sqC^\prime)$, as claimed.\end{proof}
+In particular, if $\sqC_1$ is degenerate and if $\delta$ denotes the minimal distance from the circuit to a non-contracted vertex of $\sqC_1$ (which certainly exists since $\sqC_1$ has positive degree) then $\delta < e_1 \leq \lambda(\sqC^\prime)$, as claimed.\end{proof}
 
@@
 Now suppose $\Delta$ is of type $B$.
-Note that in this case, it is impossible for the core to be contracted.
+Note that in this case, it is impossible for the circuit to be contracted.
 Hence $\Ecal$ is disjoint from the blown-up locus, and the map $\Dcal \to \Ecal$ is an isomorphism.
@@
 Here the first factor in the fibre product is the logarithmic blow-up of the moduli space of rubber maps constructed in \S \ref{}.
-We will compute integrals over such spaces as part of the recursion (see \S \ref{section recursion algorithm}).\footnote{(Navid) Say something about reduced rubber for target spaces here?}
+We will compute integrals over such spaces as part of the recursion (see \S \ref{section recursion algorithm}).
 
@@
 Thus we conclude that the index is equal to $\lcm(m_1,\ldots,m_r)$ as claimed.\end{proof}
-
-\begin{remark} A similar line bundle and section is considered in \cite{Ga} in the genus zero setting.
-The computation of $\lambda_{\Dcal}$ is the most difficult technical part of that paper.
-One of our contributions here is to observe that the tropical description reduces this computation to simple combinatorics.\end{remark}
-
 In summary, then: the contribution of each term $\lambda_\Dcal [\Dcal]$ is given by integrating over the appropriate fibre product and then multiplying the result by $\lambda_\Dcal \cdot \deg\rho = \prod_{i=1}^r m_i$.
 
-\subsection{Recursive description of the divisors: type IIIb} The treatment of the type I, II and IIIa cases above is a fairly straightforward extension of the ideas of Vakil and Gathmann (albeit updated with logarithmic and tropical technology, which streamlines the presentation and simplifies the proofs).
-The remaining type IIIb case, however, is entirely new.
-In this section we provide a recursive description of these boundary divisors.
-This constitutes the technical heart of the paper.
-
-\subsubsection{Possible combinatorial types} Recall that a boundary divisor $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ is said to be of type IIIb if the core is assigned degree zero by the combinatorial type (this is the case which was ignored in Lemma \ref{lem:combs} and the subsequent discussion).
-In this case, the combinatorial type is not as tightly constrained as before; the target may expand multiple times, and as such the combinatorial type need not be a bipartite graph with a single interior vertex.
-Nevertheless, we have the following lemma:
+\subsection{Recursive description of the divisors: type $C^0$}
+
+\subsubsection{Combinatorial types} Recall that a boundary divisor $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ is said to be of \textbf{type $C^0$} if the core is assigned zero degree by the combinatorial type.
+In this case, the combinatorial type is not as tightly constrained as previously (it needs not be a bipartite graph with a single interior vertex).
+Nevertheless, we have the following lemmas:
 \begin{lemma} 
-Let $\Dcal$ be a locus of type IIIb and let $\Delta$ be the corresponding combinatorial type.
-Then for every nonzero vertex $\diamond$ of the expanded tropical target, the fibre of the tropical map over $\diamond$ contains exactly one stable vertex, which lies on the radius.
+Let $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ be of type $C^0$ and let $\Delta$ be the corresponding combinatorial type.
+Then, for every vertex $\diamond\neq0$ of the expanded target, the fibre of the tropical map over $\diamond$ contains exactly one stable vertex (together with a number of trivial bubbles), and at least one vertex which lies on the circle (which may or may not be stable).
 \end{lemma}
 \begin{proof}
-By stability, we must always have at least one stable vertex lying over each  vertex of the target.
-If there was more than one, then (since both the insertions and the factorisation condition are pulled back from the moduli space of maps without expansions) we can show, as in the proof of Lemma \ref{lem:combs}, that the contribution vanishes.
-
-Furthermore, for each vertex of the target there must always be at least one vertex in the preimage which lies on the radius, since otherwise there would be at least two independent tropical parameters, and so $\Dcal$ would not be a divisor.
-
-A priori it could be that the stable vertex is not amongst those vertices lying on the radius.
-But in this case the corresponding locus $\Fcal$ in the moduli space of unexpanded maps has larger codimension (for the same reason as before), and so the contribution vanishes by the projection formula.
+By stability, we always need at least one stable vertex lying over each vertex of the target.
+If there was more than one, then (since both the insertions and the factorisation condition are pulled back from the moduli space of maps without expansions) it could be seen, as in the proof of Lemma \ref{lem:combs}, that the contribution would vanish.
+
+Furthermore, for each vertex of the target there must always be a vertex in the preimage which lies on the circle, since otherwise there would be at least two independent tropical parameters, and so $\Dcal$ would not be a divisor.\end{proof}
+
+\begin{lemma}
+ If, for any nonzero vertex $\diamond$ of the expanded target, the only stable vertex in $\phi^{-1}(\diamond)$ is not the core, nor it lies on the circle, then the corresponding combinatorial type $\Delta$ does not contribute to the invariants.
+\end{lemma}
+\begin{proof}
+ By the previous Lemma, there must be a vertex $v$ lying on the circle and over $\diamond$; such a vertex is strictly semistable by assumption, in particular the map $f$ is constant along the corresponding component, therefore the fact that the factorisation condition is satisfied is unaffected by $\Gm$-scaling the coordinate corresponding to $v$ in the moduli space of attachments.
+We deduce that the generic fiber of $\Dcal\to\Ecal$ has positive dimension.
 \end{proof}
 
-\subsubsection{Recursive description of $\Ecal$}
-Just as before, we let $\tau \in \Sigma$ be the ray corresponding to $\Dcal \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$, $\sigma \in \Sigma^{\Kim}$ be the minimal cone containing $\tau$ and $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$ be the stratum corresponding to $\sigma$, so that we have a map $\Dcal \to \Ecal$ (and $\Ecal$ is the minimal stratum through which the map from $\Dcal$ factors).
-Recall that we also have a unique stratum $\widetilde\Dcal \subseteq \widetilde\VZ_{1,\alpha}(\PP^N|H,d)$ such that $\Dcal = \widetilde\Dcal \cap \VZ_{1,\alpha}(\PP^N|H,d)$.
-Note that the cone $\sigma$ has dimension equal to the number of levels of the target expansion in the combinatorial type, which in this case could possibly be larger than $1$.
-
-We can describe the locus $\Ecal$ in a simple recursive manner.
-We write $\Delta_0$ for the collection of stable vertices of the combinatorial type which are mapped to $0$ by the tropical map, and $\Delta_{>0}$ for the stable vertices which are mapped to $\RR_{>0}$.
-For each vertex $v$ there is associated discrete data $\Gamma_v$, which defines a moduli space of relative stable maps if $v \in \Delta_0$ and a moduli space of rubber maps if $v \in \Delta_{>0}$.
+\begin{lemma}\label{lem:m=1}
+ If the maximal contact order at the core is $m=1$, the corresponding combinatorial type does not contribute to the invariants.
+\end{lemma}
+\begin{proof}
+ It follows once again from a dimensional argument.
+\end{proof}
+
+%%%%%%%%
+\begin{center}
+\begin{figure}
+\includegraphics[scale=.6]{ray_example}
+\caption{A ray of type $C^0$.}\label{fig:ray_example}
+\end{figure}
+\end{center}
+%%%%%%%%%%
+
+We observe that the cone $\sigma \in \Sigma^{\Kim}$ corresponding to the stratum $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$ is isomorphic to $\N^r$ where $r$ is the number of target expansions.
+The discrepancy between the dimension of $\sigma$ and the dimension of the ray $\tau$ is to be expected, since the loci of type $C^0$ are contained in the exceptional locus of the blow-up.
+
+We write $V_0$ for the collection of stable vertices of the combinatorial type which are mapped to $0$ by the tropical map, and $V_{>0}$ for the stable vertices which are mapped to $\RR_{>0}$.
+For each vertex $v$ there is associated discrete data $\Gamma_v$, which defines a moduli space of relative stable maps if $v \in V_0$ and a moduli space of rubber maps if $v \in V_{>0}$.
 Then $\Ecal$ admits a finite splitting morphism onto the fibre product
-\begin{equation}\label{IIIa fibre product} \Ecal \xrightarrow{\rho} \left( \prod_{v \in \Delta_0} \ol\Mcal_{\Gamma_v}(\PP^N|H) \times \prod_{v \in \Delta_{>0}} \ol\Mcal^{\leftrightarrow}_{\Gamma_v}(P|H_0+H_\infty) \right) \times_{H^{2\epsilon}} H^{\epsilon} \end{equation}
-where $\epsilon$ is the number of edges of the (stabilised) dual graph, and the fibre product is taken over the appropriate evaluation maps.
-Thus, tautological integrals over $\Ecal$ are completely determined in terms of integrals over moduli spaces with ``smaller'' combinatorial data.
-
-Notice that the actual dimension of $\Ecal$ will typically be larger than that of $\Dcal$, since $\Ecal$ is contained inside the excess components of the moduli space.
-We will explain how to compute integrals over $\Dcal$ in two steps:
+\begin{equation*} \Ecal \xrightarrow{\rho} \left( \prod_{v \in V_0} \ol\Mcal_{\Gamma_v}(\PP^N|H) \times \prod_{v \in V_{>0}} \ol\Mcal^{\leftrightarrow}_{\Gamma_v}(P|H_0+H_\infty) \right) \times_{H^{2E}} H^E \end{equation*}
+where $E$ is the set of edges of the (stabilised) dual graph, and the fibre product is taken over the appropriate evaluation maps.
+Note that only the factor corresponding to the core vertex has non-zero genus, and that it has zero degree by assumption.
+
+\begin{remark}As in \S \ref{subsubsection splitting degree} above, we should calculate the degree of $\rho$ and the vanishing order $\lambda_{\Dcal}$ of the section $s_k$ along $\Dcal$.
+The degree of $\rho$ is given exactly as in Lemma \ref{lem:saturation}, where now we obtain one such factor for each bounded edge of the tropical target.
+The vanishing order $\lambda_{\Dcal}$ is slightly more delicate, but may be computed as the index of an explicit morphism of one-dimensional lattices, as explained in the proof of Lemma \ref{lemma vanishing order}.
+\end{remark}
+
+Typically, $\Ecal$ will have true dimension larger than that of $\Dcal$.
+We will study the map $\Dcal \to \Ecal$ in two steps: first, we will describe the map $\widetilde\Dcal \to \Ecal$, and then we will explain how to express the class of the substack $\Dcal \subseteq \widetilde\Dcal$ in terms of tautological classes.
+
+\subsubsection{From $\Ecal$ to $\widetilde{\Dcal}$} The reader should bear the following construction from toric geometry in mind: suppose we subdivide a fan, and we want to describe the relation between the varieties corresponding to a cone $\rho$ of the subdivision, and to the original cone $\sigma$ containing it, respectively.
+For any cone $\tau$, the fan of $X_\tau$ is obtained by projecting the star of $\tau$ to the quotient $N_\tau=N_{\RR}/\langle\tau\rangle_{\RR}$ of the ambient vector space by the linear span of $\tau$.\footnote{This can be encoded in the formalism of extended tropicalisations, see \cite{ACP} and references therein.} Notice that the dimension of the vector spaces $N_\rho$ and $N_\sigma$ (or the corresponding toric varieties) is off by the difference $c$ between the dimension of the cones.
+The image of $\Sigma_\rho$ provides a subdivision of $\Sigma_\sigma$.
+The geometric content is that $X_\rho$ is obtained as an appropriate compactification of a toric bundle of dimension $c$ over $X_\sigma$.
+%observe that the fiber dimension may not be constant (but it can be made so by blowing up $X_{\sigma}$, see \cite[Lemma 4.1]{AK}).
+
+We start by describing the modification of $\Ecal$ corresponding to the subdivision of the last paragraph; really, we only need to unravel the combinatorics partially, in order to describe an intermediate blowup $\widetilde\Ecal\to \Ecal$, such that $\Dcal$ factors through $\widetilde\Ecal$, and all the structures that we need to name in what follows make sense on $\widetilde\Ecal$ already.
+
+Let $V_{0,\delta}\subseteq V_0$ be the subset of vertices lying on the circle (besides being sent to $0$ by the tropical map).
+Notice that they all have the same expansion factor $m$, therefore they are at the same distance from the core, generically on $\Ecal$.\footnote{Indeed, generically, these vertices do not produce any subdivision of the target, so they contribute to the relative dimension of $\widetilde\Dcal\to\Ecal$ as one.} Another way to see the generic alignment is the following: the normal bundles corresponding to these nodes can be expressed as $\mathbb T_{R_v,q_v}\otimes\mathbb T_{E,q_v}$; for two different vertices, the right-hand factors are canonically identified thanks to the group structure on the elliptic curve, whereas the $m$-th powers of the left-hand factors are canonically identified by comparison with the target tangent line, and $\rho$ can be seen as taking an $m$-th root of this preferred isomophism.
+On the other hand, the alignment does not persist when the curves degenerate (see Figure \ref{fig:fwise_align}).
+
+\begin{figure}
+\includegraphics[scale=.5]{factorwise_alignment}
+\caption{Two degenerations of the combinatorial type above, which represents a ray.
+On the left-hand side, the alignment holds only generically.
+On the right-hand side, it is not enough to align each individual factor.}\label{fig:fwise_align}
+\end{figure}
+
+We modify $\Ecal$\footnote{With the log structure obtained by pulling back from Kim's space and modding out by $\mathbb N^{\codim (\sigma)}$, i.e.
+considering the edges of $E$ to have \emph{infinite length}.} along the boundary as follows:
+\begin{enumerate}[leftmargin=.5 cm]
+ \item radially aligning the core, and imposing fiberwise factorisation, thus replacing
+ \[\ol\Mcal^{\leftrightarrow}_{1,\mu}(P|H_0+H_\infty,d=0)\quad\text{by}\quad\VZ^{\leftrightarrow}_{1,\mu}(P|H_0+H_\infty,d=0)\]
+ in the product above, thus introducing a reduced rubber with point target;
+ \item requiring that any degeneration of $V_{0,\delta}$ (resp.
+$\forall v\in V_{>0,\delta}$) remains centrally aligned with respect to the core;\footnote{Notice that this requires us to blow up some diagonal subloci of the product above, see Figure \ref{fig:fwise_align}} as a consequence, on the whole of $\widetilde \Ecal$ - including the boundary -, for each $v\in \{V_{0,\delta}\}\cup V_{>0,\delta}$, it is always possible to tell the components of the curve that are at distance $\delta$ from the core along the path denominated $v$, and, if there is more than one for the same $v$, the lengths of these paths are identified, so as to define line bundles $\OO(\delta_v), \forall v\in \{V_{0,\delta}\}\cup V_{>0,\delta}$.
+\end{enumerate}
+It is clear that $\widetilde \Dcal\to\widetilde\Ecal$ is generically a torus bundle of relative dimension $\codim(\sigma)-1$; the open locus is represented by the moduli space of attachments for the elliptic singularities.
+\begin{lemma}
+ Generically on $\Ecal$, $\widetilde \Dcal\to\widetilde\Ecal$ is isomorphic to $\mathcal P=\PP_{\widetilde\Ecal}(\bigoplus_{v\in \{V_{0,\delta}\}\cup V_{>0,\delta}}\OO(\delta_v))$.
+\end{lemma}
+\begin{proof}
+ All of the line bundles $\OO(\delta_v)$ share a common factor $\mathbb T_E$, the universal tangent line to the elliptic curve (appropriately twisted by bubbling loci as in \cite[\S 2.3]{VZ}); removing this, when the curve has the prescribed dual graph, $\OO(\delta_v)$ is isomorphic to the tangent line to the rational tail $R_v$ at the gluing node $q_v$ (with the caveat that all those corresponding to $V_{0,\delta}$ are canonically identified).
+This is the open stratum of the moduli space of attaching data \cite[\S\S 2.2-2.3]{SMY2}.
+On the fiber boundary, the circle of radius $\delta$ will pass through a subset of $\{V_{0,\delta}\}\cup V_{>0,\delta}$, while cutting the complementary subset along the edge between the core and $v$; correspondingly, there is a destabilisation of the curve, and an elliptic singularity containing strictly semistable branches.
+Tropically, pushing some of the vertices off the circle creates new finite-length edges with coordinates $\ell_v\in\RR_{\geq_0}$ (see Figure \ref{fig:off_we_go}); not all of them can be strictly positive, because the circle needs to pass through at least one vertex (of positive horizontal degree).
+This is patently the fan of a projective space.
+\end{proof}
+\begin{figure}
+\includegraphics[scale=.3]{off_we_go}
+\caption{Moving vertices off the circle creates new tropical parameters.}\label{fig:off_we_go}
+\end{figure}
+
+Notice that $\mathcal P$ is well-defined on the whole of $\widetilde \Ecal$, while $\widetilde \Dcal\to \mathcal P$ is in fact a modification along the boundary, as dictated by the alignment procedure.
+In the next section, we extrapolate what we need from this combinatorial setup in order to describe $\Dcal$ explicitly.
+\begin{comment}
+\subsubsection{The generic alignment} In the first line of the product above, we have grouped the $k$ factors adjacent to the core with maximal expansion factor $m$.
+It is fundamental to realise that, generically on $\Ecal$, the vertices corresponding to these factors are (equidistant and) already aligned with respect to the core.
+We can construct a modification $\widetilde\Ecal$ of $\mathcal E$ by:
 \begin{enumerate}
-\item we explain how to construct $\widetilde\Dcal$ from $\Ecal$ in \S \ref{};
-\item we explain how to express the class of $\Dcal \subseteq \widetilde\Dcal$ in terms of tautological classes in \S \ref{}.
+ \item radially aligning the core, and imposing the double factorisation condition, thus effectively replacing the factor
+ \[\ol\Mcal_{1,\alpha^{(0)}\cup(-m,\ldots,-m,-\mu_{k+1},\ldots,-\mu_r)\cup(-m_i)_{i\in\{k+1,\ldots,s\}\setminus(\bigcup I_j)}}^{\leftrightarrow}(P|H_0+H_\infty,0)\]
+ by $\VZ_{1,\alpha^{(0)}\cup(-m,\ldots,-m,-\mu_{k+1},\ldots,-\mu_r)\cup(-m_i)_{i\in\{k+1,\ldots,s\}\setminus(\bigcup I_j)}}^{\leftrightarrow}(P|H_0+H_\infty,0)$ in the product above; in particular, there is a universal cotangent line bundle at the markings $\mathbb L_E$, obtained by suitably twisting any marking cotangent line (they are all isomorphic over a smooth elliptic curve) by the appropriate bubbling loci (see \cite[\S 2.3]{VZ});
+ \item aligning the first $k$ factors with respect to the core (this blows up some diagonal subloci of the product, so it is not enough to align the individual factors).
 \end{enumerate}
-
-\begin{remark}[Splitting degree and vanishing order, revisited] Similarly to \S \ref{subsubsection splitting degree} above, we can calculate the degree of $\rho$ and the vanishing order $\lambda_{\Dcal}$ of the section $s_k$ along $\Dcal$.
-The degree of $\rho$ is given exactly as in Lemma \ref{lem:saturation}, where now we obtain one such factor for each bounded edge of the tropical target.
-The vanishing order $\lambda_{\Dcal}$ is slightly more delicate, but may be computed as the index of an explicit morphism of one-dimensional lattices, as explained in the proof of Lemma \ref{lemma vanishing order}.\end{remark}
-
-\subsubsection{$\widetilde\Dcal$ from $\Ecal$} Recall that the map $\widetilde\Dcal \to \Ecal$ is obtained by restricting the logarithmic blow-up
-\begin{equation*} \widetilde\VZ_{1,\alpha}(\PP^N|H,d) \to \ol\Mcal_{1,\alpha}(\PP^N|H,d)\end{equation*}
-to the locus $\widetilde\Dcal$.
-In toric geometry, the method for studying this restriction is as follows.
-The fan of $\widetilde\Dcal$ (respectively, $\Ecal$) is obtained by projecting the star of the ray $\tau$ (respectively, the cone $\sigma$) onto the quotient lattice.
-The map $\widetilde\Dcal \to \Ecal$ is then a toric morphism, induced by the obvious map of fans.
-In order to describe this morphism, we first subdivide the fan of $\Ecal$ by taking the images of cones in the fan of $\widetilde\Dcal$.
-This induces a toric blow-up of $\Ecal$ which we denote by $\widetilde\Ecal$.
-The morphism $\widetilde\Dcal \to \Ecal$ naturally factors through a morphism $\widetilde\Dcal \to \widetilde\Ecal$ which is now flat (in contrast to $\widetilde\Dcal \to \Ecal$), and now $\Dcal$ can be described as a compactification of a torus bundle over $\widetilde\Ecal$, with strata determined by the combinatorics of the fan.
-
-Returning to the logarithmic setting, the first step is to define appropriate logarithmic structures on $\widetilde\Dcal$ and $\Ecal$.
-We equip $\widetilde\Dcal$ with the logarithmic structure obtained by first restricting the logarithmic structure on $\widetilde\VZ_{1,\alpha}(\PP^N|H,d)$ and then quotienting by the normal direction to $\widetilde\Dcal$.
-By the same process we may also define a logarithmic structure on $\Ecal$, and this coincides with the pull-back along $\rho$ of the product logarithmic structure on the fibre product in \eqref{IIIa fibre product}.
-The map $\widetilde\Dcal \to \Ecal$ is then naturally a logarithmic map.
-
-The next step is to construct $\widetilde\Ecal$ as a logarithmic modification of $\Ecal$, and to do this we need to describe the tropicalisation of the map $\widetilde\Dcal \to \Ecal$.
-In fact, it is more convenient to consider the \emph{extended tropicalisation} \cite{}.
-We begin by fixing notation.
-Associated to the combinatorial type $\Delta$, we have stable vertices $\sqC_0,\sqC_1,\ldots,\sqC_r$ with $\sqC_0$ corresponding to the core and $\sqC_1,\ldots,\sqC_r$ corresponding to stable vertices which lie on the raidus (see Lemma \ref{} above).
-For $i \in \{1,\ldots,r\}$ let $e_i$ denote the sum of the edge lengths separating $\sqC_i$ from $\sqC_0$.
-These give functions on the cone $\sigma$, and $\tau$ is the ray given by the equations $e_1=\ldots=e_r$.
-Note that the $e_i$ also define functions on any cone in the star of $\sigma$.
-
-Now consider the extended tropicalisation of $\widetilde\Dcal$.
-This is obtained inside the extended tropicalisation of $\widetilde\VZ_{1,\alpha}(\PP^N|H,d)$ by intersecting the star of $\tau$ with the locus $e_1=\cdots=e_r=\infty$.
-On the other hand, the extended tropicalisation of $\Ecal$ is obtained inside the extended tropicalisation of $\ol\Mcal_{1,\alpha}(\PP^N|H,d)$ by intersecting the star of $\sigma$ with the same locus.
-It is therefore clear that the extended tropicalisation of $\widetilde\Dcal$ is a subdivision of that of $\Ecal$.
-Moreover we claim that we can describe this subdivision explicitly.
-
-Consider any cone $\rho$ in the star of $\tau$.
-Since the tropicalisation of $\widetilde\VZ_{1,\alpha}(\PP^N|H,d)$ is a subdivision of the tropicalisation of $\ol\Mcal_{1,\alpha}(\PP^N|H,d)$ there is a unique minimal cone in the star of $\sigma$ which contains $\rho$.
-We denote this cone by $\theta$, and remark that $\theta$ arises from a choice of combinatorial type which specialises the combinatorial type $\Delta$ defining $\sigma$.
-On $\theta$ we have the edge length functions $e_1,\ldots,e_r$ as well as additional edge lengths corresponding to nodes on $\theta$ which are smoothed out on $\sigma$.
-
-Now, $\rho$ is defined inside $\theta$ by a number of equalities and inequalities involving these edge lengths.
-These (in)equalities relate the distances to the core of various vertices of the dual graph.
-There are three cases we must consider:
+See Figure \ref{fig:fwise_align} below.
+It is obvious that $\widetilde \Dcal\to \Ecal$ factors through $\widetilde\Ecal$.
+On $\widetilde\Ecal$, we have a tropical line bundle $\OO(\delta)$ representing the minimum distance from the core to the tropical preimage of $0$; generically, this line bundle coincides with the normal bundle of the locus where the node between the core and one (any) of the first $k$ vertices persists, but on the boundary this needs to be twisted by further smoothing parameters according to the (partial) alignment on $\widetilde\Ecal$.
+We can obtain a line bundle $\mathbb T_R$ accounting only for the behaviour of the rational side of the fiber product by twisting $\OO(\delta)$ with $\mathbb L_E$.
+\begin{figure}
+ \begin{tikzpicture}[ipe stylesheet,scale=.7]
+  %\useasboundingbox (0, 0) rectangle (595, 842);
+  \pic
+     at (129.8488, 703.2932) {ipe disk};
+  \pic
+     at (97.8488, 719.2932) {ipe disk};
+  \pic
+     at (97.8488, 687.2932) {ipe disk};
+  \draw
+    (97.8488, 719.2932)
+     -- (129.8488, 703.2932)
+     -- (97.8488, 687.2932);
+  \draw
+    (129.8488, 703.2932)
+     -- (161.8488, 687.2932);
+
+  \draw
+    (193.8488, 671.2932)
+     -- (225.8488, 655.2932);
+  \draw
+    (225.8488, 655.2932)
+     -- (193.8488, 639.2932);
+    \draw[ipe dash dashed]
+   (193.8488, 671)
+    -- (161.8488, 687);
+  \draw[ipe dash dashed]
+    (193.8488, 639.2932)
+     -- (161.8488, 623.2932);
+  \draw
+    (161.8488, 623.2932)
+     -- (129.8488, 607.2932);
+  \pic
+     at (146.637, 615.0615) {ipe disk};
+  \draw
+    (129.8488, 607.2932)
+     -- (97.8488, 591.2932)
+     -- (97.8488, 591.2932);
+  \draw
+    (147.2948, 615.0622)
+     -- (97.2686, 638.1002)
+     -- (97.2686, 638.1002);
+  \pic
+     at (96.6103, 637.4422) {ipe disk};
+  \pic
+     at (97.9268, 590.7072) {ipe disk};
+  \pic
+     at (130.1808, 622.9607) {ipe cross};
+  \pic
+     at (130.1808, 607.1635) {ipe cross};
+  \pic
+     at (145.9788, 695.3672) {ipe cross};
+  \draw[-ipe linear]
+    (97.8488, 575.2932)
+     -- (257.8488, 575.2932);
+  \pic
+     at (97.8488, 575.2932) {ipe disk};
+  \pic
+     at (129.8488, 575.2932) {ipe cross};
+  \pic
+     at (145.8488, 575.2932) {ipe cross};
+  \pic
+     at (225.8488, 575.2932) {ipe cross};
+  \draw
+    (129.8488, 703.2932)
+     -- (257.8488, 703.2932);
+  \draw
+    (225.8488, 655.2932)
+     -- (257.8488, 655.2932)
+     -- (257.8488, 655.2932);
+  \draw
+    (146.3018, 614.861)
+     -- (258.5378, 614.404);
+  \node[ipe node]
+     at (189.423, 676.278) {$m$};
+  \node[ipe node]
+     at (189.094, 629.543) {$m$};
+  \node[ipe node]
+     at (111.421, 715.773) {$m_1$};
+  \node[ipe node]
+     at (110.104, 590.707) {$m_2$};
+  \node[ipe node]
+     at (110.763, 564.378) {$\ell_1$};
+  \node[ipe node]
+     at (133.801, 564.377) {$\ell_2$};
+  \node[ipe node]
+     at (146.308, 543.972) {$\frac{\ell_1}{m_1}+\frac{\ell_2}{m} \lesseqgtr \frac{\ell_1+\ell_2}{m_2}$};
+  \pic
+     at (473.6651, 658.9228) {ipe disk};
+  \pic
+     at (353.8488, 719.2932) {ipe disk};
+  \pic
+     at (353.8488, 687.2932) {ipe disk};
+  \draw
+    (353.8488, 719.2932)
+     -- (385.8488, 703.2932)
+     -- (353.8488, 687.2932);
+  \draw
+    (386.7731, 703.2932)
+     -- (418.7731, 687.2932);
+  \draw[ipe dash dashed]
+    (417.8488, 687.2932)
+     -- (449.8488, 671.2932)
+     -- (449.8488, 671.2932);
+
+  \draw
+    (449.8488, 671.2932)
+     -- (481.8488, 655.2932)
+     -- (481.8488, 655.2932);
+  \draw
+    (481.8488, 655.2932)
+     -- (449.8488, 639.2932)
+     -- (449.8488, 639.2932);
+  \draw[ipe dash dashed]
+    (449.8488, 639.2932)
+     -- (417.8488, 623.2932);
+  \draw
+    (417.8488, 623.2932)
+     -- (385.8488, 607.2932);
+  \pic
+     at (457.1756, 642.7929) {ipe disk};
+  \draw
+    (385.8488, 607.2932)
+     -- (353.8488, 591.2932)
+     -- (353.8488, 591.2932);
+  \pic
+     at (352.6103, 622.6521) {ipe disk};
+  \pic
+     at (353.9268, 590.7072) {ipe disk};
+  \pic
+     at (458.2826, 667.3311) {ipe cross};
+  \pic
+     at (459.207, 575.7344) {ipe cross};
+  \draw[-ipe linear]
+    (353.8488, 575.2932)
+     -- (513.8488, 575.2932);
+  \pic
+     at (353.8488, 575.2932) {ipe disk};
+  \pic
+     at (385.8488, 575.2932) {ipe cross};
+  \pic
+     at (475.7994, 575.2932) {ipe cross};
+  \pic
+     at (481.8488, 575.2932) {ipe cross};
+  \draw[shift={(472.741, 659.847)}, xscale=0.3271, yscale=-1.7893]
+    (0, 0)
+     -- (128, 0);
+  \draw
+    (481.8488, 655.2932)
+     -- (513.8488, 655.2932)
+     -- (513.8488, 655.2932);
+  \draw[shift={(459.26, 642.878)}, xscale=0.4834, yscale=0.4807]
+    (0, 0)
+     -- (112.236, -0.457);
+  \draw[red]
+    (482.3765, 654.0394) circle[radius=9.9987];
+  \draw
+    (354.8117, 621.686)
+     -- (386.2407, 606.8958);
+  \pic
+     at (386.2407, 606.8958) {ipe disk};
+  \pic
+     at (386.2407, 703.956) {ipe disk};
+  \draw[red]
+    (360.3506, 584.6012)
+     arc[start angle=160.4967, end angle=217.0656, x radius=120.4239, y radius=-143.3401];
+  \pic
+     at (473.9974, 650.6919) {ipe cross};
+  \pic
+     at (364.92, 693.131) {ipe cross};
+  \pic
+     at (372.3151, 710.6943) {ipe cross};
+  \pic
+     at (359.3737, 593.2977) {ipe cross};
+  \draw
+    (226.3225, 655.8881)
+     -- (258.6759, 665.1319);
+  \draw
+    (226.3225, 654.0394)
+     -- (258.6759, 646.6443);
+  \draw[-ipe linear]
+    (271.6173, 766.814)
+     -- (337.2485, 767.7384);
+
+  \pic
+     at (272.5417, 782.5285) {ipe disk};
+  \pic
+     at (271.6173, 815.8063) {ipe disk};
+  \draw
+    (305.8194, 798.2431)
+     -- (272.5417, 815.8063);
+  \draw
+    (305.8194, 798.2431)
+     -- (272.5417, 782.5285)
+     -- (272.5417, 782.5285);
+  \draw
+    (272.5417, 782.5285)
+     -- (336.3241, 782.5285);
+  \draw
+    (272.5417, 815.8063)
+     -- (336.3241, 814.8819);
+  \draw
+    (304.8951, 799.1674)
+     -- (335.3997, 799.1674);
+  \draw
+    (305.8194, 799.1674)
+     -- (336.3241, 804.7137);
+  \draw
+    (305.8194, 798.2431)
+     -- (335.3997, 792.6968);
+  \draw
+    (387.1651, 703.956)
+     -- (511.0324, 703.956)
+     -- (511.0324, 703.0316);
+  \draw
+    (388.0895, 605.0471)
+     -- (511.9568, 605.0471);
+  \pic
+     at (272.5417, 766.814) {ipe disk};
+  \draw[red]
+    (304.8951, 797.3187) circle[radius=35.9679];
+
+    \pic[fill=white]
+     at (225.8488, 655.2932) {ipe fdisk};
+
+     \pic[fill=white]
+     at (481.8488, 655.2932) {ipe fdisk};
+
+     \pic[fill=white]
+     at (304.8951, 799.1674) {ipe fdisk};
+\end{tikzpicture}
+\caption{Two degenerations of the combinatorial type above, which represents a ray.
+On the left-hand side, the alignment holds only generically.
+On the right-hand side, it is not enough to align each individual factor.}\label{fig:fwise_align}
+\end{figure}
+
+\subsubsection{The projective bundle}\label{subs:proj_bun} Generically on $\widetilde\Ecal$, the compactified torus bundle $\widetilde \Dcal\to \widetilde\Ecal$ coincides with the following projective bundle:
+\[\mathcal P=\PP_{\widetilde\Ecal}(\mathbb T_R\oplus\bigoplus_{j=k+1}^r \mathbb T_{q_j}R_j),\]
+where $\mathbb T_{q_j}R_J$ is the tangent line at the gluing marking closest to the core on the $j$-th factor of the product in the second line of \eqref{eq:product}.
+The open stratum in the fiber consists of moduli of attachments (i.e.
+moduli for the contraction to the Smyth's singularity); the compactification is by adding strictly semistable Gorenstein singularities as in \cite[\S\S 2.2-2.3]{SMY2}.
+In terms of alignment, a coordinate hyperplane corresponds to pushing the corresponding vertex off the circle, and destabilising the corresponding edge to the core.
+Tropically, the fibers can be analysed as follows: pushing some of the vertices off the circle creates new finite length edges with coordinates $\ell_j\in\RR_{\geq_0}$ (see Figure \ref{fig:off_we_go}); not all of them can be strictly positive, because the circle needs to pass through at least one vertex of positive horizontal degree.
+This is patently the fan of a projective space.
+
+\begin{figure}
+\begin{tikzpicture}[ipe import,scale=.8]
+  %\useasboundingbox (0, 0) rectangle (595, 842);
+  \draw
+    (64, 672)
+     -- (128, 688)
+     -- (64, 704)
+     -- (64, 704);
+  \draw
+    (128, 688)
+     -- (64, 736)
+     -- (64, 736);
+  \draw[red]
+    (128, 688) circle[radius=65.9697];
+  \draw
+    (128, 688)
+     -- (112, 752)
+     -- (64, 768)
+     -- (64, 768);
+  \draw
+    (112, 752)
+     -- (64, 784)
+     -- (64, 784);
+  \pic
+     at (64, 672) {ipe disk};
+  \pic
+     at (64, 704) {ipe disk};
+  \pic
+     at (64, 736) {ipe disk};
+  \pic
+     at (64, 768) {ipe disk};
+  \pic
+     at (64, 784) {ipe disk};
+  \pic
+     at (112, 752) {ipe cross};
+  \pic
+     at (75.2242, 727.582) {ipe cross};
+  \pic
+     at (112, 700) {ipe cross};
+  \pic
+     at (112, 692) {ipe cross};
+  \pic
+     at (112, 684) {ipe cross};
+  \pic
+     at (75.8121, 701.047) {ipe cross};
+  \pic
+     at (75.0704, 674.4388) {ipe cross};
+  \filldraw[fill=white]
+    (64, 608)
+     -- (208, 608)
+     -- (208, 608);
+  \pic
+     at (64, 608) {ipe disk};
+  \draw
+    (128, 688)
+     -- (208, 688)
+     -- (208, 688);
+  \pic
+     at (73.6978, 608.02) {ipe cross};
+  \pic
+     at (111.876, 608.0202) {ipe cross};
+  \pic
+     at (127.674, 608.0205) {ipe cross};
+  \pic[fill=white]
+     at (128, 688) {ipe fdisk};
+  \node[ipe node]
+     at (86.863, 690.301) {$m$};
+  \node[ipe node]
+     at (87.521, 671.212) {$m$};
+  \draw
+    (128, 688)
+     -- (91.4703, 741.643);
+  \draw
+    (128, 688)
+     -- (160.586, 745.593)
+     -- (160.586, 745.593);
+  \pic
+     at (91.4703, 741.643) {ipe disk};
+  \pic
+     at (160.486, 745.417) {ipe disk};
+  \draw[shift={(91.47, 741.051)}, xscale=0.95, yscale=0.6996]
+    (0, 0)
+     -- (-26.9879, 7.241)
+     -- (-26.9879, 7.241);
+  \draw
+    (160.486, 745.417)
+     -- (64.4824, 799.569);
+  \draw
+    (160.486, 745.417)
+     -- (208.637, 745.593);
+  \draw
+    (92.1286, 740.985)
+     -- (64.4824, 754.15);
+  \pic
+     at (64.4824, 746.909) {ipe disk};
+  \pic
+     at (64.4824, 798.91) {ipe disk};
+  \pic
+     at (64.4824, 753.492) {ipe disk};
+  \draw
+    (289.118, 672.0005)
+     -- (353.118, 688.0005)
+     -- (289.118, 704.0005)
+     -- (289.118, 704.0005);
+  \draw
+    (353.118, 688.0005)
+     -- (289.118, 736.0005)
+     -- (289.118, 736.0005);
+  \draw[red]
+    (353.118, 688.0005) circle[radius=65.9697];
+  \draw
+    (353.118, 688.0005)
+     -- (337.118, 752.0005)
+     -- (289.118, 768.0005)
+     -- (289.118, 768.0005);
+  \draw
+    (337.118, 752.0005)
+     -- (289.118, 784.0005)
+     -- (289.118, 784.0005);
+  \pic
+     at (289.118, 672.0005) {ipe disk};
+  \pic
+     at (289.118, 704.0005) {ipe disk};
+  \pic
+     at (289.118, 736.0005) {ipe disk};
+  \pic
+     at (289.118, 768.0005) {ipe disk};
+  \pic
+     at (289.118, 784.0005) {ipe disk};
+  \pic
+     at (337.118, 752.0005) {ipe cross};
+  \pic
+     at (300.3422, 727.5825) {ipe cross};
+  \pic
+     at (337.118, 700.0005) {ipe cross};
+  \pic
+     at (337.118, 692.0005) {ipe cross};
+  \pic
+     at (337.118, 684.0005) {ipe cross};
+  \pic
+     at (300.9301, 701.0475) {ipe cross};
+  \pic
+     at (300.1889, 674.4392) {ipe cross};
+  \filldraw[fill=white]
+    (289.118, 608.0005)
+     -- (433.118, 608.0005)
+     -- (433.118, 608.0005);
+  \pic
+     at (289.118, 608.0005) {ipe disk};
+  \draw
+    (353.118, 688.0005)
+     -- (433.118, 688.0005)
+     -- (433.118, 688.0005);
+  \pic
+     at (298.8158, 608.0205) {ipe cross};
+  \pic
+     at (336.994, 608.0207) {ipe cross};
+  \pic
+     at (352.792, 608.0209) {ipe cross};
+  \pic[fill=white]
+     at (353.118, 688.0005) {ipe fdisk};
+  \node[ipe node]
+     at (311.98, 690.301) {$m$};
+  \node[ipe node]
+     at (312.639, 671.212) {$m$};
+  \draw[shift={(353.118, 687.999)}, xscale=1.1287, yscale=1.1615]
+    (0, 0)
+     -- (-36.5297, 53.643);
+  \draw[shift={(353.119, 687.997)}, xscale=1.4269, yscale=1.3567]
+    (0, 0)
+     -- (32.586, 57.593)
+     -- (32.586, 57.593);
+  \pic
+     at (310.6643, 751.5171) {ipe disk};
+  \pic
+     at (400.086, 767.1394) {ipe disk};
+  \draw[shift={(311.745, 750.197)}, xscale=0.8205, yscale=-0.5452]
+    (0, 0)
+     -- (-26.9879, 7.241)
+     -- (-26.9879, 7.241);
+  \draw[shift={(399.543, 767.54)}, xscale=1.1319, yscale=0.5704]
+    (0, 0)
+     -- (-96.0036, 54.152);
+  \draw[shift={(400.744, 767.146)}, xscale=0.6446, yscale=-1.3688]
+    (0, 0)
+     -- (48.151, 0.176);
+  \draw[shift={(311.717, 751.113)}, xscale=0.8, yscale=0.1453]
+    (0, 0)
+     -- (-27.6462, 13.165);
+  \pic
+     at (289.6004, 746.9095) {ipe disk};
+  \pic
+     at (289.6004, 798.9105) {ipe disk};
+  \pic
+     at (289.6004, 753.4925) {ipe disk};
+  \pic
+     at (387.02, 744.935) {ipe cross};
+  \pic
+     at (317.246, 742.961) {ipe cross};
+  \node[ipe node]
+     at (315.273, 748.884) {$\ell_{j_1}$};
+  \node[ipe node]
+     at (397.553, 752.175) {$\ell_{j_2}$};
+\end{tikzpicture}
+\caption{Moving vertices off the circle creates new tropical parameters.}\label{fig:off_we_go}
+\end{figure}
+\end{comment}
+
+\subsubsection{From $\widetilde\Dcal$ to $\Dcal$} Let $F=\bigoplus_{v\in \{V_{0,\delta}\}\cup V_{>0,\delta}}\OO(\delta_v)$. On $\mathcal P$ we have a tautological sequence:
+\[\OO_{F}(-1)\hookrightarrow p^*(F)\xrightarrow{+\operatorname{d}f}\operatorname{ev}_E^*(TH),\]
+where $p\colon\mathcal P=\PP(F)\to\widetilde\Ecal$, and $+\operatorname{d}f$ should be interpreted as follows: for every $v\in \{V_{0,\delta}\}\cup V_{>0,\delta}$, as many copies of $\OO(\delta_v)$ are considered as there are components at distance $\delta$ from the core along the path $v$, and they are identified according to the preferred isomorphisms; then, the differential of the universal map to $\PP^N$ is applied to each tangent vector (possibly including some contracted rational bubbles on the path), and the sum of these contributions is taken in $T_{f(E)}\PP^N$ - it actually lies in $T_{f(E)}H$ because all the normal contributions can be assumed to be trivial by Lemma \ref{lem:m=1}.
+The composite, regarded as a section $s$ of $G=\OO_F(1)\otimes \operatorname{ev}_E^*(TH)$, vanishes precisely where $f$ factors through the Smyth's singularity determined by the point in the fiber of $p$.
+Generically on $\widetilde\Ecal$, this is exactly what we are after.
+On the boundary, though, it may happen that a simultaneous degeneration in the base and the fiber makes this factorisation trivial, in the sense that $\bar f$ would be constant on all the branches of the elliptic singularity.
+
+\begin{lemma}
+ For every $V_B\subseteq V_\delta$ and $V_F=V_\delta\setminus V_B$, $s$ vanishes along the loci where the factors corresponding to $V_B$ in $\widetilde \Ecal$ degenerate so that $f_v\colon R_v\to\PP^N$ is constant in a neighbourhood of $q_v$, and the fiber coordinates $(\lambda_{v^\prime})_{v^\prime\in V_F}$ along $p\colon\mathcal P\to\widetilde \Ecal$ are set to be $0$.
+\end{lemma}
+Call these loci $\Xi_i,i\in I$ (compare with \cite[\S 3.2]{VZ} for an analogous phenomenon in the non-relative case); it is clear that they may be in excess with respect to the expected codimension of $V(s)$, that is $N-1$.
+These loci are logarithmic substrata; therefore, there exists a logarithmic blow-up that principalizes them.
+We claim that $\widetilde\Dcal$ is (possibly a refinement of) such a blow-up.
+\begin{lemma}
+ The pullback of $\Xi_i$ is principal in $\widetilde\Dcal$.
+\end{lemma}
+\begin{proof}
+ Let us analyse the ideal of $\Xi_i$: it is generated by
+ \begin{enumerate}[leftmargin=.5 cm]
+  \item equations on $\widetilde\Ecal$ cutting the locus where $R_v$ degenerates so that $f_v$ is constant on a neighbourhood of $q_v$, $v\in V_B$: these correspond to the tropical functions $\delta_v-\operatorname{dist}(q_v,\circ)$;
+  \item equations on the fiber of $p$ for the linear subspace corresponding to $v\in V_F$: tropically, these correspond to the $\ell_v$ discussed above.
+ \end{enumerate}
+By construction, on $\widetilde \Dcal$ it is always possible to tell which of these tropical lengths is the shortest (the circle we have drawn on $\Xi$ is degenerate - it passes through no vertex of positive horizontal degree -, therefore we need to decide for a strictly larger circle in order to lift to $\widetilde D$), which corresponds to principalising the ideal (see Figure \ref{fig:principalisation}).
+\end{proof}
+
+\begin{figure}
+\includegraphics[scale=.5]{principalisation}
+\caption{On the left, a generic point of $\mathcal P$.
+On the right, a point of $\Xi$.
+The dotted circle is the one we draw on $\mathcal P$.
+The continuous circle represents one of the possible choices of $\delta$ enlarging the dotted one (a stratum of $\widetilde\Dcal$).}\label{fig:principalisation}
+\end{figure}
+
+Finally, on $\widetilde\Dcal$ (or, in fact, on an intermediate blow-up $\widetilde{\mathcal P}\to\mathcal P$) there are exceptional divisors $\widetilde \Xi_i$ corresponding to $\Xi_i$ in $\mathcal P$.
+Since the $\Xi_i$ exhaust all the excess-dimensional components of the vanishing locus of $s\in\Gamma(\mathcal P,G)$, the latter induces a section $\tilde s\in\Gamma(\widetilde\Dcal,G(-\sum_i\widetilde\Xi_i))$ by pullback and twisting, whose vanishing locus is dimensionally transverse to the boundary, and whose open part coincides with the generic point of $\Dcal$, therefore $V(\tilde s)=\Dcal$.
+
+Notice that, expressing the pushforward of the Chern classes of $\OO_F(1)$ and $\OO(\widetilde\Xi_i)$ in terms of tautological classes on the fiber product underlying $\Ecal$, we get:
+\begin{cor}
+ After pushforward to $\Ecal$, the contribution of $\Dcal$ to the invariants can be computed in terms of tautological integrals on moduli spaces of maps with lower numerics.
+\end{cor}
+\begin{comment}
+\subsubsection{Factorisation} Assume $m\geq 2$. Over $\mathcal P$ we have a tautological sequence:
+\[\OO_{F}(-1)\hookrightarrow p^*(F)\xrightarrow{+\operatorname{d}f}\operatorname{ev}_E^*(TH),\]
+where $p\colon\mathcal P=\PP(F)\to\widetilde\Ecal$, and $+\operatorname{d}f$ should be interpreted as follows: $k$ copies of $\mathbb T_R$ are taken to account - via the preferred isomorphisms - for all factors of the first product in \eqref{eq:product}; then, the differential of the universal map to $\PP^N$ is applied to each tangent vector (possibly including some of the contracted rational bubbles in the boundary), and the sum of these contributions is taken in $T_{f(E)}\PP^N$ - it actually lies in $T_{f(E)}H$ because all the normal contributions are trivial by assumption.
+The composition is a section $s$ of $G=\OO_F(1)\otimes \operatorname{ev}_E^*(TH)$, and it vanishes precisely where $f$ factors through the Smyth's singularity determined by the point in the fiber of $p$.
+Generically on $\widetilde\Ecal$, this is exactly what we are after.
+
+\subsubsection{Dimensional transversality} In general, the vanishing locus of $s$ corresponds to maps $f\colon C\to\PP^N$ and diagrams $C\leftarrow \tilde C\to \bar C$ - with $\bar C$ the elliptic $r$-fold point determined by the position in the fiber of $p\colon\mathcal P\to\widetilde \Ecal$ - such that $f$ factors through $\bar C$.
+When the curve is allowed to degenerate (so, on the boundary of $\widetilde \Ecal$), this is not always what we want: indeed, due do the combined action of degeneration (in the base direction) and destabilisation (in the fiber direction), it may very well be that $f$ is constant along every component of the elliptic singularity, so that it factors trivially; in other words, the vanishing locus of $s$ is not dimensionally transverse to the boundary of $\mathcal P$.
+\begin{lemma}
+ For every $K\subseteq\{1,\ldots,r\}$ and $K^c=\{1,\ldots,r\}\setminus K$, $s$ vanishes along the loci where the factors corresponding to $K$ in $\widetilde \Ecal$ degenerate so that $f_k\colon R_k\to\PP^N$ is constant in a neighbourhood of $q_k$, and the fiber coordinates $(\lambda_{h})_{h\in K^c}$ along $p\colon\mathcal P\to\widetilde \Ecal$ are set to be $0$.
+\end{lemma}
+Call these loci $\Delta_i,i\in I$. See \cite[\S 3.2]{VZ} for a treatment of the analogous situation in the non-relative case; the study of the normal bundles is also dealt with there.
+
+It is clear that these loci are logarithmic substrata; therefore, there exists a logarithmic blow-up that principalizes them.
+We claim that $\widetilde\Dcal$ is (possibly a refinement of) this blow-up.
+This follows from the tropical discussion in Section \ref{subs:proj_bun}, and the fact that the degenerate circle that we are drawing on the $\Delta_i$ falls in the strict interior of the circle of radius $\delta$ on $\widetilde\Dcal$ (because the former only passes through vertices of horizontal degree $0$), thus all the distances from the vertices to the former circle are ordered.
+See Figure \ref{fig:principalisation} above.
+\begin{figure}
+\begin{tikzpicture}[ipe import]
+  %\useasboundingbox (0, 0) rectangle (595, 842);
+  \draw
+    (64, 720)
+     -- (112, 736)
+     -- (96, 752);
+  \draw[->]
+    (64, 704)
+     -- (128, 704);
+  \pic
+     at (64, 704) {ipe disk};
+  \pic
+     at (64, 720) {ipe disk};
+  \pic
+     at (96, 752) {ipe disk};
+  \draw[red, dotted]
+    (60.6969, 708.808)
+     arc[start angle=-161.5651, end angle=-71.5651, x radius=53.2078, y radius=-65.2105];
+  \pic[fill=white]
+     at (112, 736) {ipe fdisk};
+  \draw
+    (192, 720)
+     -- (240, 736)
+     -- (224, 752);
+  \draw[->]
+    (192, 704)
+     -- (256, 704);
+  \pic
+     at (192, 704) {ipe disk};
+  \pic
+     at (192, 720) {ipe disk};
+  \pic
+     at (224, 752) {ipe disk};
+  \pic[fill=white]
+     at (240, 736) {ipe fdisk};
+  \draw
+    (112, 736)
+     -- (128, 736);
+  \draw
+    (240, 736)
+     -- (256, 736);
+  \draw
+    (208.6374, 743.6181)
+     -- (224.4352, 750.8588);
+  \draw
+    (208.6374, 758.7577)
+     -- (225.0934, 751.517);
+  \pic
+     at (207.9791, 742.9599) {ipe disk};
+  \pic
+     at (207.9791, 758.7577) {ipe disk};
+  \pic
+     at (208, 704) {ipe cross};
+  \pic
+     at (224, 704) {ipe cross};
+  \pic
+     at (240, 704) {ipe cross};
+  \pic
+     at (96, 704) {ipe cross};
+  \pic
+     at (112, 704) {ipe cross};
+  \draw[red, dotted]
+    (231.0126, 755.9018)
+     { [rotate=-17.595] arc[start angle=135, end angle=225, x radius=21.7093, y radius=22.6274] };
+  \draw[red]
+    (188.9249, 712.0225)
+     arc[start angle=-156.5092, end angle=-115.3692, x radius=85.088, y radius=-96.462];
+\end{tikzpicture}
+\caption{On the left, a generic point of $\mathcal P$.
+On the right, a point $\Delta$.
+The dotted circle is what we have on $\mathcal P$.
+The continuous circle is the one of radius $\delta$ on $\widetilde\Dcal$; this principalises the degeneration.}\label{fig:principalisation}
+\end{figure}
+
+Finally, on $\widetilde\Dcal$ there are exceptional divisors $\widetilde \Delta_i$ corresponding to $\Delta_i$ in $\mathcal P$.
+By the preceding analysis, $s\in\Gamma(\mathcal P,G)$ induces a section $\tilde s\in\Gamma(\widetilde\Dcal,G(-\sum_i\widetilde\Delta_i))$ by pullback, whose vanishing locus is dimensionally transverse to the boundary, and whose open part coincides with the generic point of $\Dcal$, therefore $V(\tilde s)=\Dcal$.
+
+\subsection{Tautological contributions} Expressing the pushforward of the Chern classes of $\OO_F(1)$ and $\OO(\widetilde\Delta_i)$ in terms of tautological classes on the fiber product underlying $\Ecal$, get:
+\begin{cor}
+ After pushforward to $\Ecal$, the contribution of $\Dcal$ to the invariants can be computed in terms of tautological integrals on moduli spaces of maps with lower numerics.
+\end{cor}
+\end{comment}
+
+\newpage
+
+\begin{lem} The logarithmic modification $\psi$ restricts to a birational map:
+\begin{equation*}\VZ^{\operatorname{punct}}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(H,d) \to \ol\Mcal^{\operatorname{punct},\circ}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(H,d).\end{equation*}
+\end{lem}
+Note that the latter space (the main component of the moduli space of punctured maps) is birational to the main component of the double ramification locus.
+In Lemma \ref{Lemma forget marking} below we explain how to compute integrals over this.cd
+\begin{proof}
+If it is true, we might be able to prove it via deformation theory.
+For this it might be useful to notice that there is a morphism $\Mpunct{g}{\alpha}{H}{d}\to \Mpunct{g}{\alpha}{\PP^N}{d}$ (because $H\subseteq\PP^N$ is strict), which is probably a closed immersion, and the loci with smooth source curve are isomorphic under this map.
+It seems plausible that the main omponent is log smooth over $B\Gm\subseteq[\Aaff^1/\Gm]$ (or the standard log point).
+\end{proof}
+
+%We probably want the latter statement to hold under imposing alignment and factorisation (keeping the log structure on the source curve, but forgetting that the map is log).
+Integrals over the main component of the double ramification locus can be computed using the following lemma.
+\begin{lem} \label{Lemma forget marking}The morphism which forgets a marking
+\begin{equation*} \fgt_i\colon\ol\Mcal_{1,n}^{\alpha,\circ}(H,d)\to\ol\Mcal^{\circ}_{1,n-1}(H,d)\end{equation*}
+is generically finite, of degree $\alpha_i^2$ (except in one special case, described in the proof).
+\end{lem}
+\begin{proof}
+ Let us consider the case $d=0$ first.
+We may assume the source curve is smooth elliptic $E$.
+The map \[ \phi\colon E\to \Pic^0(E),\qquad x\mapsto\OO_E\left(\alpha_ix+\sum_{j=1,\ldots,\hat i\ldots,n}\alpha_jp_j\right)\]
+ is an isogeny of degree $\alpha_i^2$.
+The locus of $(C,p_1,\ldots,\hat{p_i},\ldots,p_n)$ such that the kernel of $\phi$ contains one of the points $\{p_1,\ldots,\hat{p_i},\ldots,p_n\}$ is itself a double ramification locus inside $\oM_{1,n}$, hence non-generic - with one exception: namely, when $n=2$, $x=p_1$ is always a solution, but the curve lying above such point bubbles off a $\PP^1$.
+To see that it does not belong to the closure of the nice locus, notice that the rational function trivialising $\OO_C(\alpha_1p_1-\alpha_2p_2)$ should descend to the cusp, thus having a ramification point at the node; yet its ramification profile is determined by Riemann-Hurwitz, and it is entirely supported on $p_1$ and $p_2$.
+
+ For a different proof: notice that we should obtain the class of the main component from the full double ramification cycle by subtracting the boundary class $[D_{1,\emptyset|0,\{1,\ldots,n\}}]$.
+The latter pushes forward to $0$ under $\fgt_i$, unless $n=2$.
+Therefore we may apply $\fgt_{i,*}$ to the Hain-Pixton formula:
+ \[DR_1(A)=\frac{1}{2}\left(\sum_{i=1}^na_i^2\psi_i-\sum_{\substack{I\subseteq\{1,\ldots,n\}\\|I|\geq 2}}a_I^2[D_{1,I^c|0,I}]-\frac{1}{12}\delta_0\right),\]
+ where $a_I=\sum_{i\in I}a_i$ and $\delta_0=\operatorname{glue}_*([\oM_{0,n+2}])$.
+From $\psi_j=\fgt_i^\st\psi_j+[D_{i,j}]$ for $i\neq j$, and the dilaton equation, we see that $\fgt_{i,*}\psi_j=1$ and $\fgt_{i,*}\psi_i=n-1$.
+On the other hand, the only surviving boundary classes are $[D_{i,j}]$, and they push down to $1$.
+Hence the formula pushes down to $\frac{1}{2}\left(\sum_{j\neq i}\alpha_j^2+(n-1)\alpha_i^2-\sum_{j\neq i}(\alpha_j+\alpha_i)^2\right)=-\alpha_i\left(\sum_{j\neq i}\alpha_j\right)=\alpha_i^2.$
+\end{proof}
+
+\newpage
+
+\begin{definition} A combinatorial type $\Delta$ of a tropical curve consists of the following data:
 \begin{enumerate}
-\item both vertices are components of $\sqC_1 \cup \ldots \cup \sqC_r$;
-\item both vertices are components of $\sqC_0$;
-\item one vertex is a component of $\sqC_0$ and one is a component of $\sqC_1 \cup \ldots \cup\sqC_r$.
+\item $G$ a finite graph, with a set $V(G)$ of vertices, a set $F(G)$ of flags and an involution $\iota \colon F(G) \to F(G)$ with $\iota^2=\Id$.
+We let $L(G)$ denote the fixed set of $\iota$, and think of its elements as infinite legs; we let $E(G)$ denote the set of equivalence classes of elements not fixed by $\iota$, and think of them as finite edges connecting two (possibly equal) vertices of $G$;
+\item a genus assignment $g \colon V(G) \to \Z_{\geq 0}$;
+\item a degree assignment $\deg \colon V(G) \to \Z_{\geq 0}$;
+\item a weight assignment $u \colon F(G)  \to \Z$ such that for every edge $e \in E(G)$ we have $u(f_1)=-u(f_2)$ where $e=[f_1]=[f_2]$, and $u(l) \geq 0$ for any $l \in L(G)$;
 \end{enumerate}
-We start with case (1). By the definition of a well-spaced tropical map, we see that these are all of the form
-\begin{equation*} f_i + e_i = f_j + e_j \end{equation*}
-where $f_i$ and $f_j$ are positive linear combinations of additional edge length parameters which are set to zero in $\tau$.
-We may now pass to the subcone of $\rho$ obtained by imposing the additional equations $e_1=\ldots=e_r$.
-Note that this is \emph{not} a subcone of $\tau$ in general, since there are additional edge lengths which must be set to zero if one wishes to recover $\tau$.
-The additional equations mean that we can rewrite our previous (in)equalities in the form
-\begin{equation*} f_i = f_j \end{equation*}
-and these define a cone in the limiting locus $e_1=\ldots=e_r=\infty$.
-By definition this is one of the cones in the subdivision of the extended tropicalisation of $\Ecal$, and all such cones are obtained in this manner.
-
-Taking this subdivision amounts to the following modular blow-up of the fibre product of the moduli spaces attached to the vertices $\sqC_1,\ldots,\sqC_r$: given a logarithmic map with splitting nodes $q_1,\ldots,q_r$ as specified by the shape of $\Delta$, we glue together the $r$ vertices of the tropicalisation which carry the splitting nodes, and declare the resulting special vertex to be the root of the resulting tree.
-We then impose a central alignment condition, entirely analogous to the genus one construction, where the special root takes on the role previously occupied by the core.
-
-We now deal with Case (2). These (in)equalities are not affected at all in the limit $e_1=\ldots=e_r=\infty$ and so the effect is to replace the factor of $\Ecal$ attached to the vertex $\sqC_0$
-\begin{equation*} \ol\Mcal^{\leftrightarrow}_{\Gamma_{\tiny{\sqC_0}}}(P|H_0+H_\infty) \end{equation*}
-with the radially aligned rubber space:
-\begin{equation*} \VZ^{\leftrightarrow}_{\Gamma_{\tiny{\sqC_0}}}(P|H_0+H_\infty).\end{equation*}
-The factorisation condition here is accounting for the ``fibre-direction'' factorisation; the ``base-direction'' factorisation has not entered the picture yet, and will appear when we come to describe $\Dcal$.
-
-It remains to discuss Case (3).
-Here we have a relation of the form $f_i = f_j + e_j$, so in the limit $e_j =\infty$ there is no limiting cone.
-Therefore these relations to not appear in the modification of $\Ecal$.
-
-In this way, we obtain a logarithmic modification $\tilde\Ecal \to \Ecal$.
-By definition the map $\tilde\Dcal \to \Ecal$ is a compactification of a torus bundle over $\Ecal$, whose strata can be read off from the tropicalisation of $\tilde\Dcal$.
-
-[LUCA SAYS MORE HERE, ABOUT HOW IT'S GENERICALLY A PROJECTIVE BUNDLE.]
-
-\subsubsection{$\Dcal$ from $\widetilde\Dcal$} On $\widetilde\Dcal$ there is a natural vector bundle arising from the modular desription of $\widetilde\VZ_{1,\alpha}(\PP^N|H,d)$, namely:
-\begin{equation*} F = \OO(\delta)^{\oplus r}. \end{equation*}
-We claim that the fibre of $F$ over a moduli point can be naturally identified with
-\begin{equation*} \left( \bigoplus_{i=1}^r \TT_{p_i} C_i^\prime \right) \otimes \TT_{C_0} \end{equation*}
-where $C_i^\prime$ is a component of $C_i$ which lies on the radius, $p_i$ is the adjacent node which points towards the core, and $\TT_{C_0}$ is the universal tangent line bundle on the radially aligned rubber space.
-
-For let us choose a component $C_i^\prime$ of the curve which lies on the radius.
-Then $\OO(\delta)$ can be expressed as a tensor product of tangent line bundles along the path connecting $C_i^\prime$ to the core.
-However, this lage product of line bundles is telescoping: any vertex which appears in the middle of the path will have an incoming and outgoing node, and since the vertex corresponds to a smooth rational curve these tangent spaces are naturally dual to each other \cite{VZ}.
-Thus these terms cancel, and product collapses into a contribution $\TT_{p_i}C_i^\prime$ from the left-hand side and a contribution from the right-hand side.
-Note that the final term on the right hand side is not given by $\TT_{q_i} C_0$ (where $q_i$ is the appropriate splitting node) but rather the tangent space to the core (which could be further away if $C_0$ has degenerated).
-Thus we obtain the universal tangent line bundle $\TT_{C_0}$ as the contribution to the right-hand side.
-
-[EXAMPLE]
-
-Note that $C_i^\prime$ is \emph{a} component of $C_i$ which lies on the radius.
-There may be more than one, but if this is the case then their tangent spaces are naturally identified by the logarithmic structure.
-Thus we obtain a natural morphism
-\begin{equation*} \sum \operatorname{d}\!f \colon F(-\TT_{C_0}) \to \ev_q^\st \TT_H \end{equation*}
-given by summing the derivatives at \emph{all} the inward-pointing nodes on the radius.
-Now, over $\widetilde\Dcal$ there is a natural section of the projective bundle $\PP(F) \to \widetilde\Dcal$ (obtained by projectivising the diagonal embedding).
-If we therefore lift the above morphism to the projectivisation, we obtain a composition:
-\begin{equation*} \OO_{\PP(F)}(-1) \to \pi^\st F \to \pi^\st(\ev_q^\st \TT_H (\TT_{C_0})).\end{equation*}
-The vanishing locus of this section is given by an Euler class calculation on $\PP(F)$.
-In order to obtain $\Dcal$ we must then intersect this vanishing locus with $\OO_{\PP(F)}(1)$ (which represents the natural section $\widetilde\Dcal \to \PP(F)$.
-
-Finally, we note that the class of $F$ is computable in terms of data pulled back from the base. To be more precise, we may consider the following bundle on $\Ecal$:
-\begin{equation*} E = \bigoplus_{i=1}^r \TT_{q_i}C_i \otimes \TT_{q_i}C_0. \end{equation*}
-We may then identify $F$ with the pullback of $E$ twisted by the exceptional loci.
-(This agrees with the more classical-minded description of $F$ as a bundle which resolves an otherwise non-transverse section of $E$.) We illustrate this in an example, which brings out the beauty of the interplay between logarithmic moduli and blow-ups.
-
-[EXAMPLE]
+\end{definition}
+
+\footnote{(Luca) to be made homogeneous with what comes earlier} Review here the process of gluing for punctured maps.
+In particular the basic monoid should be modified in order to make the relevant evaluations log morphisms.
+Claim: evaluations are strict.
+Consequence: the fiber product in the category of log stacks is fine.
+We have then to apply saturation.
+This is a finite morphism of degree...
+(I think it could be $\frac{\prod m^{(i)}}{lcm(m^{(i)})}$).
+
+\begin{lemma}[Virtual pushforward] The following hold.
+ \begin{itemize}
+  \item $\fgt_*[\M{0}{\alpha}{\PP^N|H}{d}]=[\MG{0}{\alpha}{\PP^N|H}{d}]$ (follows from \cite{GathmannThesis,AbramovichMarcusWiseComparison}).
+  \item $\fgt_*[\VZc{1}{\alpha}{\PP^N|H}{d}]$ computes the reduced relative invariants by definition.
+  \item $\fgt_*[\M{0}{\mu}{H}{d_0}^\sim]=[\M{0}{\lvert\mu\rvert}{H}{d_0}]$ (follows from \cite{GathmannThesis} and... comparison of punctured with rubber invariants).
+  \item $\fgt_*[\VZc{1}{\mu}{H}{d_0}^\sim]$ here we should need a variation on Pixton's DRC formula; hopefully it's enough to avoid the graphs that tropical well-spacedness discards.
+ \end{itemize}
+\end{lemma}
+
+\subsection{Recursive description of the divisors: type $C_0$} Consider now a combinatorial type $\Delta$ such that the circuit is contracted into the divisor.
+The corresponding stratum $\Dcal_\Mcal \subseteq \Mcal$ is contained in the blown-up locus.
+Our task is to identify the logarithmic divisors in the preimage of $\Dcal_\Mcal$ under the map $\VZ \to \Mcal$.
+As discussed, these are indexed by choices of ray in the subdivision of the tropical moduli space.
+Suppose we have fixed such data.
+
+\begin{claim} The teeth of the comb can break at most once, along the circuit.\end{claim}
+
+\begin{proof} If not there would be more parameters in the tropical moduli space. \end{proof}
+
+\begin{prop} Let $\Delta$ be a combinatorial type as above. Then:
+\begin{enumerate}
+\item the circuit is a single vertex, and is mapped to the interior $\RR_{>0} \subseteq \RR_{\geq 0}$;
+\item the degree of the circuit is zero;
+\item there is a vertex which is adjacent to the circuit and mapped to the interior $0 \in \RR_{\geq 0}$;
+\item let $e \in E(\sqC)$ be an edge which is adjacent to the circuit, and such that $u(e)$ is maximal among the edges adjacent to the circuit.
+Then the other vertex $v$ contained in $e$ is mapped to $0 \in \RR_{\geq 0}$, and $v$ lies on the (absolute) radius;
+\item if $v \in V(\sqC)$ and $\lambda(v) > \delta$ then $f(v)=0$.
+\end{enumerate}
+\end{prop}
+
+On the other hand, when there is a contracted elliptic subcurve - and it will be contracted into the hyperplane, because otherwise it wouldn't be generic, by density of the nice locus in $\VZ_{1,\alpha^\prime}(\PP^N|H,d^\prime)$ - the picture becomes more complicated due to the alignment.
+The combs may break.
+We label these loci $\mathcal{Y}_C^0$.
+\begin{figure}
+
+ \tikz{
+ \draw[red] (2,0) circle(2); %circle
+ \draw (0,0) circle(2pt)[fill=black] (0,2) circle(2pt)[fill=black] (0,4) circle(2pt)[fill=black] (0,6) circle(2pt)[fill=black] (0,-2) circle(2pt)[fill=black] (1.1,1.78) circle(2pt)[fill=black] (3.42,1.42) circle(2pt)[fill=black] (.58,-1.42) circle(2pt)[fill=black] (0,1) circle(2pt)[fill=black]; %black vertices
+ \draw (2,0) -- node[above]{4} (0,0) (2,0) --node[above]{2} (1.1,1.78) --node[above]{1} (0,2) (1.1,1.78) --node[above]{1} (0,4) (2,0) --node[above]{1} (3.42,1.42) (2,0) --node[above]{3} (.58,-1.42) (3.42,1.42) --node[above]{5} (0,6) (.58,-1.42) --node[above]{1} (0,-2) (2,0) -- node[above]{2} (0,1); %edges
+ \draw (.58,-1.42) -- (5,-1.42) node[right]{1} (3.42,1.42) -- (5,1.42) node[right]{2} (2,0) -- (5,.5) node[right]{3} (2,0) -- (5,-.5) node[right]{7}; %markings
+ \draw (2,0) circle(2pt)[fill=white]; %core
+ \draw[->] (0,-3) circle(2pt)[fill=black] edge (5,-3); %trop(P^N|H)
+ }
+
+ \caption{The degrees can be figured out from the balancing equation.}
+\end{figure}
+
+In the following we describe the rays of the tropical moduli space.
+\begin{lem}
+ A one-parameter tropical map $\phi$ to $\mathbb R_{\geq 0}$ is a decorated tree (with expansion factors - \emph{contact orders} - along edges and legs, and degrees on vertices, satisfying the balancing condition) with a circle (of radius $\delta$) around the root (sometimes called the \emph{core} and denoted by $\circ$) satisfying:
+ \begin{enumerate}
+ \item the circle of radius $\delta$ passes through at least one vertex of $\phi^{-1}(0)$ - which necessarily has positive degree - call $m$ its contact order with $H$;
+ \item teeth may break only when they intersect the circle of radius $\delta$; in particular, $\circ$ is the only vertex contained in its strict interior, and every edge heading out from the circle goes directly to a vertex of $\phi^{-1}(0)$;
+ \item every tooth that starts with contact order $m$ goes directly to a vertex of $\operatorname{circle}(\circ,\delta)\cap\phi^{-1}(0)$, and every other tooth starts with contact order $<m$ (possibly negative).
+ \end{enumerate}
+\end{lem}
+\begin{proof}
+ Otherwise there would be more than one parameters.
+\end{proof}
+
+\begin{remark}
+ The core being contracted in the fiber of the tropical map is not a phenomenon that we should worry about in codimension one.
+Indeed, assume that the core is contracted in the fiber along a ray.
+Then all the edges departing from the core have expansion factor $0$; call the corresponding coordinates $U=\{u_i\}_{i\in I}$.
+Call the remaining coordinates $E=\{e_j\}_{j\in J}$.
+Note that tropical continuity involves only $E$.
+Alignments on the other hand assume the form $\lambda(v)=\lambda(v^\prime)$, where $\lambda(v)=\sum_{i\in I(v)}u_i\sum_{j\in J(v)}e_j$.
+Pick the shortest elements of $U$; then these can be shortened to zero without affecting the rest (by hypothesis, alignments can only identify them among themselves).
+This shows that we could not have started with a ray.
+\end{remark}
+
+\begin{ex}
+ We look at the following example in some detail.
+ \begin{figure}[h]
+  \tikz{
+  \draw (0,1) circle(2pt)[fill=black] --node[above]{2} (2,0);
+  \draw (0,-1) circle(2pt)[fill=black] --node[above]{2} (2,0);
+  \draw (2,0) -- (2.5,0) node[right]{4};
+  \draw (2,0)  circle(2pt)[fill=white];
+  \draw (0,1) -- (.33,1.33) node[above right]{0};
+  \draw (0,-1) -- (.33,-1.33) node[below right]{0};
+  \draw[red] (2,0) circle(2.23);
+  \draw[->] (0,-2.5)node[left]{0} circle(2pt)[fill=black] edge (4,-2.5);
+  }
+ \end{figure}
+ The ambient space is $\VZc{1}{(4,0,0)}{\PP^N|H}{4}$, of dimension $4N+3$.
+The underlying moduli space is $X=\M{0}{(2,0)}{\PP^N|H}{2}\times_H\M{0}{(2,0)}{\PP^N|H}{2}\times\VZ_{1,(-2,-2,4)}$ of dimension $5N+1$.
+Consider the fiber product:
+ \bcd
+ F\ar[r]\ar[d]& \M{0}{(2,0)}{\PP^N|H}{2}\times\M{0}{(2,0)}{\PP^N|H}{2}\ar[d]\\
+ H\ar[r] & H\times H
+ \ecd
+ At the level of ghost sheaves, $\oM_F=\mathbb N\oplus_{\mathbb N^2}\oM_1^{\rm{enl}}\oplus\oM_2^{\rm{enl}}$, where the map $\mathbb N^2\to\mathbb N$ is the sum, and the map $\mathbb N^2\to\oM_1^{\rm{enl}}\oplus\oM_2^{\rm{enl}}$ generically is multiplication by $2$, so $\oM_F=\mathbb N^2/(2e=2f)$ generically.
+Saturation gives a finite cover $G\to F$ with $\oM_G=\mathbb N_{e=f}$ generically.
+Lifting this to actual log structures, what we are doing (again generically) is taking a square root of the isomorphism $T_{R_1,q_1}^{\otimes 2}\simeq T_{R_2,q_2}^{\otimes 2}$, which is obtained passing through $N_{H/\PP^N,f(Z)}$ via $\operatorname{d}f_{|R_i,q_i}$.
+This breaks when $f_{|R_i}$ is not tangent to $H$ of order exactly $2$ at $q_i$, for either $i$; but by the maximality assumption this happens precisely along Gathmann's comb loci $\Delta_i$.
+So in fact, rather than with $T_{R_i,q_i}^{\otimes 2}$, we should be working with $T_{R_i,q_i}^{\otimes 2}(-\Delta_i)$: but this is exactly $\ev_i^\st(-H)$ by Gathmann's genus zero formula, and the isomorphism $\ev_1^\st(H)=\ev_2^\st(H)$ holds on all of $F$.
+
+ On the other hand, generically on $\VZ_{1,(-2,-2,4)}$ we have $T_{q_1}Z\simeq T_{q_2}Z$ by exploiting the group structure on the elliptic curve.
+This breaks when either (but not both) is on a rational tail.
+Yet we have $T_{q_1}Z(\Delta_{1\in P})\simeq T_{q_2}Z(\Delta_{2\in P})$ by Vakil-Zinger's construction of a universal $\psi$-class (i.e.
+by comparing both with $\pi_*\omega(\Delta)$; notice that our further blow-up has the only effect of twisting \emph{all} the relevant line bundles by $\Delta_{1,2\notin P}$).
+
+ Now, the fiber of the Vakil-Zinger blow-up over $X$ can be described as follows. Generically it looks like \[\PP(T_{q_1}R_1\otimes T_{q_1}Z\oplus T_{q_2}R_2\otimes T_{q_2}Z)\]
+ but this has to be modified along the boundary:
+ \begin{itemize}
+  \item this has to do with the fact that the normal bundle of the strict transform is the pullback of the normal bundle twisted by the intersection with the exceptional divisor (so it relates with previous steps of the blow-up);
+  \item it is not globally a $\PP^1$-bundle (so it relates with further stages of the blow-up; it also has to do with a choice of compactification for the moduli space of attachments);
+  \item it has the effect of replacing $T_{q_i}Z$ with Vakil-Zinger's universal $\mathbb T$, so that this can be factored out of the projective bundle, and in fact we are left with a projective bundle $\mathbb P=\PP(T_{q_1}R_1\oplus T_{q_2}R_2)$ over $F$, and its open part $\operatorname{Iso}(T_{q_1}R_1\oplus T_{q_2}R_2)$ represents the attachment data for a contraction to a tacnode $R_1\sqcup_q R_2\to\bar{C}$.
+ \end{itemize}
+On $\PP$ there is a natural vector bundle map \[s\colon \OO_{\PP}(-1)\hookrightarrow p^\st(T_{q_1}R_1\oplus T_{q_2}R_2)\xrightarrow{+\operatorname{d}f}\ev_q^\st T\PP^N\]
+that vanishes along the locus where $f$ descends to $\bar C$. In general, it is not a transversal section:
+\begin{itemize}
+ \item we should replace $T\PP^N$ by $TH$ as long as all the $m^{(i)}$ are $\geq2$;
+ \item Vakil and Zinger construct a blow-up of $\PP$ along the vanishing loci of $s$ of low codimension, and twist $s$ by the exceptional divisors, so that it becomes a transverse section $\tilde{s}$.
+\end{itemize}
+On the other hand, the finite cover $G\to F$ factors through $\PP$, because the two vertices are already aligned on $G$.
+We claim that the boundary locus of $\VZc{1}{(4,0,0)}{\PP^N|H}{4}$ corresponding to the combinatorial type of the tropical map above is the transverse intersection
+\[\left(G\cap V(\tilde{s})\subseteq\PP\right)\times\VZ_{1,(-2,-2,4)}.\]
+This has the expected dimension (codimension $N-1$ with respect to $X$).
+To compute its class, we can pull $\PP$ back to $G$, and then notice that $G\hookrightarrow\PP_G$ is the inclusion of a (trivial) subbundle.
+\begin{lem}
+ The class of $\PP(\mathcal F)\subseteq\PP(\mathcal E)$ is $c_{\rm{top}}(\OO_\mathcal{E}(1)\otimes p^\st(\mathcal{E}/\mathcal{F}))$.
+\end{lem}
+See \cite[Prop.
+9.13]{EH3264}.
+It is a good time to remember that $\mathcal E$ was in fact $(\bigoplus_{i=1}^rTR_{i,q_i})\otimes\mathbb T$.
+By writing $c$ for $c_1(\OO_\mathcal{E}(1))$, $\psi_i$ for $c_1(T^\st R_{i,q_i})$, $\psi_Z$ for Vakil-Zinger's universal psi class, and $H$ for $\ev_q^\st H$, we need to compute
+\begin{align*}
+p_*\left((c-\psi_1-\psi_2-2\psi_Z)[(1+c+H)^N(1+c)^{-1}]_{N-1}\right)= \\
+p_*\left((c-\psi_1-\psi_2-2\psi_Z)(\sum_{k=0}^{N-1}\binom{N}{1+k}c^kH^{N-1-k})\right)=\\
+\sum_{k=0}^{N-1}\binom{N}{k}H^{N-1-k}\big(s_k(\mathcal E)-s_{k-1}(\mathcal E)(\psi_1+\psi_2+\psi_Z)\big)
+\end{align*}
+\end{ex}
+
+We now generalise this picture.
+Recall that the map $C\to\bar C$ is given by a (generic) line in the sum of the tangent spaces to the rational tails at the nodes that join them to the contracted curve of genus one.
+This is equivalent to an alignment, and it is parametrised by an open subset of a projective bundle over the moduli space for the tails corresponding to vertices of the dual graph lying on the circle of radius $\delta$.
+Yet, notice that those vertices lying in $\phi^{-1}(0)$ are already aligned among themselves.
+This is why we find it convenient to distinguish among four groups of vertices:
+\begin{enumerate}
+ \item the core;
+ \item\label{specialvertices} vertices on $\phi^{-1}(0)\cap\operatorname{circle}(\circ,\delta)$;
+ \item vertices on $\operatorname{circle}(\circ,\delta)\setminus\phi^{-1}(0)$;
+ \item\label{boringvertices} vertices on $\phi^{-1}(0)\setminus\operatorname{circle}(\circ,\delta)$.
+\end{enumerate}
+We shall first argue that gluing of log maps can be performed separately for the exterior and interior of the circle (the analogous classical picture is that, since the core is contracted, this moduli space is the product of a genus one curve, and a fiber product of genus zero maps under evaluation morphisms).
+
+\begin{lem}
+ $\VZ^{\operatorname{punct}}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(H,0)\simeq \VZ^{\operatorname{punct}}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(\Spec(k\oplus\mathbb N))\times H$.\footnote{(Luca) check log structure, could be fibered over std log point}
+\end{lem}
+
+Let us now deal with vertices of type \ref{specialvertices}.
+\begin{lem}
+ Consider the following fiber product in the category of fs log stacks:
+ \bcd
+ F\ar[d]\ar[r] & \prod_{i=1}^r\M{0}{\alpha^{(i)}\cup\{ m\}}{\PP^N|H}{d_i}\ar[d,"\ev_{q_i}"]\\
+ H\ar[r] & H^r
+ \ecd
+ On $F$ there is a canonical isomorphism $\mathbb L_{q_i}\cong\mathbb L_{q_j}$\footnote{(Luca) check how it degenerates}, the latter being the cotangent line bundles at the gluing markings on two different components $i$ and $j$.
+Furthermore, $\underline F$ is a finite cover of degree $m^{r-1}$ of the fiber product of the underlying stacks.
+\end{lem}
+\begin{proof}
+ Recall that each $\M{0}{\alpha^{(i)}\cup\{ m\}}{\PP^N|H}{d_i}$ is endowed with the log structure induced by pulling back along $q_i$ the divisorial log structure of the universal curve at the image of $q_i$ itself.
+Thus $\ev_{q_i}$ is made into a log morphism to $H$ with its induced DF(1) log structure.
+We claim that the subtext of such morphism is Gathmann's formula; namely, the log morphism to $H$ corresponds to an isomorphism betwee $\ev_{q_i}^\st\OO_H(-H)$ on one side, and $\mathcal I_{D_i}\otimes\mathbb L_{q_i}^m$ on the other, where $\mathcal I_{D_i}$ is the ideal sheaf of the union of the comb loci $D_i$ in $\M{0}{\alpha^{(i)}\cup\{ m\}}{\PP^N|H}{d_i}$.
+
+ On the fiber product there is a canonical isomorphism between $\ev_{q_i}^\st H$ and $\ev_{q_j}^\st H$.
+
+ Say something about integrality.
+
+ Saturation is a local operation, as much as computing the degree, hence we can concentrate on the dense open locus where all the curves we are gluing are smooth, and they are not mapped entirely into $H$.
+There the minimal log structure on $\M{0}{\alpha^{(i)}\cup\{ m\}}{\PP^N|H}{d_i}$ is trivial, therefore the isomorphism between $\ev_{q_i}^\st H$ and $\ev_{q_j}^\st H$ translates into an isomorphism $\mathbb L_{q_i}^m\cong \mathbb L_{q_j}^m$.
+The saturation $F$ is obtained by taking an $m$-th root of this isomorphism.
+\end{proof}
+Let us denote by $\mathbb L_F$ the universal cotangent line at $q$.
+
+The projective bundle we are seeking has base
+\[\mathcal X=\left(F\times \prod_{i=1}^s\oM_{0,\tilde\alpha^{(i)}\cup\{m_i\}}^{\rm{punct}}(H,\tilde d_i)\right)\times_{H^{s+1}}H\]
+(with $m_i<m$) and it is \[\PP=\Proj_{\mathcal X}\left(\mathbb T_F\oplus\bigoplus_{i=1}^s\mathbb T_{\tilde q_i}\right).\]
+We are interested in the vanishing locus of the section
+\[s\colon\OO_{\PP}(-1)\hookrightarrow p^\st\left(\mathbb T_F\oplus\bigoplus_{i=1}^s\mathbb T_{\tilde q_i}\right)\xrightarrow{+df_q} f^\st(\operatorname{T}\PP^N)_q,\]
+because it represents the geometric condition that $f\colon C\to \PP^N$ factors through the normalisation map $C\to\bar C$ prescribed by the given point of $\PP$.
+As is, $s$ is not transverse to the zero section.
+First of all, unless $m=1$, $\operatorname{T}\PP^N$ can be replaced by $\operatorname{T}H$ in the definition of $s$ above, because the projection of all $\operatorname{d}f_i(\operatorname{T}_{q_i}R_i)$ to $N_{H/\PP^N}$ is zero.
+The case $m=1$ has to be dealt with separately and it turns out that, once $s$ is made transverse, the dimension of its zero locus is smaller than the expected dimension, hence the corresponding combinatorial types are in fact irrelevant.
+
+The procedure to make $s$ transverse is the same as described in \cite[\S 3]{VZ}, namely we need to blow up inside $\PP$ the projective subbundle $\PP(\mathcal E)$ of $\PP_{|\mathcal X_\sigma}$, where $\mathcal X_\sigma$ is the closed substack of $\mathcal X$ where some of the tails degenerate so that the corresponding gluing marking lies on a component contracted by $f$, and $\mathcal E$ is the sum of the tangent line bundles at such subset of the gluing markings.
+Because $\oM_{0,\tilde\alpha^{(i)}\cup\{m_i\}}^{\rm{punct}}(H,\tilde d_i)$ is isomorphic to $\M{0}{\tilde n_i}{H}{d_i}$, the construction of Vakil and Zinger in the section ``A blowup of a moduli space of genus-zero maps'' of their paper carries through unchanged.
+The result of the blow-up is to replace $T_{q_i}R_i$ with $T_{q_i}R_i\otimes\bigoplus_{j=1}^kT_{\tilde q_j}R_i\otimes T_{\tilde q_j} S_{ij}$.
+We interpret this in terms of alignments.\footnote{(Luca) this has to be written properly}
+
+We claim that $\tilde s$ obtained from $s$ by twisting by the exceptional divisors of the blowup is a transverse section.
+We also claim that comb loci of type $\mathcal Y_c^0$ can be described as a fibered product of
+\begin{itemize}
+ \item moduli of genus one punctured maps to the standard log point, radially aligned and satisfying factorisation;
+ \item $V(\tilde s)$;
+ \item moduli of genus zero maps relative to $(\PP^N|H)$, corresponding to vertices of type \ref{boringvertices} above.
+\end{itemize}
+Finally, we claim that integrals of psi and evaluation classes over these loci can be translated into tautological integrals, i.e.
+descendant Gromov--Witten invariants, whose numerics is governed by the combinatorial type of the tropical map.
 
@@
 If $C^\prime$ is mapped to top level, then either it contains $x_1$, in which case we apply $\fgt_1$ to compute the contribution, or it does not contains $x_1$, in which case it has fewer than $n$ relative markings and is known recursively.
-If on the other hand $C^\prime$ is not mapped to top level, then generically it is mapped to the bottom level (since generically the core is not contracted on this locus, so the desingularisation process does nothing).
+If on the other hand $C^\prime$ is not mapped to top level, then generically it is mapped to the bottom level (since generically the circuit is not contracted on this locus, so the desingularisation process does nothing).
 One possible contribution is given by the following locus

### 2019-06-27 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
Wrote example comparing intrinsically-defined vector bundle to resolution of bundle pulled back from E

--- 2019-06-27 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
@@
 
-For let us choose a component $C_i^\prime$ of the curve which lies on the radius.
+Let us choose a component $C_i^\prime$ of the curve which lies on the radius.
 Then $\OO(\delta)$ can be expressed as a tensor product of tangent line bundles along the path connecting $C_i^\prime$ to the core.
@@
 Thus these terms cancel, and product collapses into a contribution $\TT_{p_i}C_i^\prime$ from the left-hand side and a contribution from the right-hand side.
-Note that the final term on the right hand side is not given by $\TT_{q_i} C_0$ (where $q_i$ is the appropriate splitting node) but rather the tangent space to the core (which could be further away if $C_0$ has degenerated).
-Thus we obtain the universal tangent line bundle $\TT_{C_0}$ as the contribution to the right-hand side.
-
-[EXAMPLE]
-
-Note that $C_i^\prime$ is \emph{a} component of $C_i$ which lies on the radius.
+Note that the final term on the right hand side is not given by $\TT_{q_i} C_0$ (where $q_i$ is the appropriate splitting node) but rather the tangent space to the core (which could be further away if $C_0$ degenerates).
+Therefore we obtain the universal tangent line bundle $\TT_{C_0}$ as the contribution to the right-hand side.
+
+We said that $C_i^\prime$ is \emph{a} component of $C_i$ which lies on the radius.
 There may be more than one, but if this is the case then their tangent spaces are naturally identified by the logarithmic structure.
@@
 Finally, we note that the class of $F$ is computable in terms of data pulled back from the base. To be more precise, we may consider the following bundle on $\Ecal$:
-\begin{equation*} E = \bigoplus_{i=1}^r \TT_{q_i}C_i \otimes \TT_{q_i}C_0. \end{equation*}
+\begin{equation*} E = \bigoplus_{i=1}^r \left( \TT_{q_i}C_i \otimes \TT_{q_i}C_0\right). \end{equation*}
 We may then identify $F$ with the pullback of $E$ twisted by the exceptional loci.
@@
 
-[EXAMPLE]
+Consider the following ray $\tau$ and sublocus $\rho$:
+\begin{figure}[h]
+
+\begin{minipage}{0.3\textwidth}
+\centering
+\begin{tikzpicture}
+\draw [red] plot [smooth cycle] coordinates {(0,-2) (-0.5,-1) (0,0) (1,0.5) (3,-1) (1,-2.5)};
+
+\draw[fill=black] (0,0) circle[radius=2pt];
+\draw (0,0) node[above]{\small$\sqC_1$};
+\draw[fill=black] (0,0) -- (2,-1);
+\draw (1,-0.95) node[above]{\small$e_1$};
+\draw[color=blue] (1,-0.5) node[above]{\small$2$};
+
+\draw[fill=black] (0,-2) circle[radius=2pt];
+\draw (0,-2) node[above]{\small$\sqC_2$};
+
+\draw[->] (0,-2) -- (0,-2.5);
+\draw[color=blue] (0,-2.5) node[below]{\small$0$};
+
+\draw[fill=black] (0,-2) -- (2,-1);
+\draw (1,-2) node[above]{\small$e_2$};
+\draw[color=blue] (1,-1.5) node[above]{\small$2$};
+
+\draw[fill=black,->] (2,-1) -- (3.5,-1);
+\draw[color=blue] (2.35,-1) node[above]{\small$4$};
+
+\draw[fill=white] (2,-1) circle[radius=2pt];
+\draw (2,-1) node[below]{\small$\sqC_0$};
+
+\draw[color=blue,->] (2,-2) -- (2,-3);
+
+\draw[color=blue,->] (0,-3.5) -- (3,-3.5);
+\draw[fill=blue] (0,-3.5) circle[radius=2pt];
+\draw[fill=blue] (2,-3.5) circle[radius=2pt];
+\end{tikzpicture}
+\caption{$\tau$}
+\end{minipage}\hfill
+\begin{minipage}{0.7\textwidth}
+\centering
+\begin{tikzpicture}
+\draw [red] plot [smooth cycle] coordinates {(-4,-2) (-2,-1) (-2,1) (0,1) (3,-1) (-1,-3.5)};
+
+\draw[fill=black] (0,0) circle[radius=2pt];
+\draw (0,0) node[above]{\small$\sqC_1^0$};
+\draw[fill=black] (0,0) -- (2,-1);
+\draw (1,-0.95) node[above]{\small$e_1$};
+\draw[color=blue] (1,-0.5) node[above]{\small$2$};
+
+\draw[fill=black] (0,-2) circle[radius=2pt];
+\draw (0,-2) node[above]{\small$\sqC_2^0$};
+\draw[fill=black] (0,-2) -- (2,-1);
+\draw (1,-2) node[above]{\small$e_2$};
+\draw[color=blue] (1,-1.5) node[above]{\small$2$};
+
+\draw[fill=black,->] (2,-1) -- (3.5,-1);
+\draw[color=blue] (2.35,-1) node[above]{\small$4$};
+
+\draw[fill=white] (2,-1) circle[radius=2pt];
+\draw (2,-1) node[below]{\small$\sqC_0$};
+
+\draw (-2,1) -- (0,0);
+\draw[fill=black] (-2,1) circle[radius=2pt];
+\draw (-2,1) node[above]{\small$\sqC_1^1$};
+\draw (-1,0.5) node[below]{\small$f_1$};
+\draw[color=blue] (-1,0.5) node[above]{\small$1$};
+
+\draw (-2,1) -- (-4,1);
+\draw[fill=black] (-4,1) circle[radius=2pt];
+\draw (-4,1) node[above]{\small$\sqC_1^3$};
+\draw (-3,1) node[below]{\small$g_1$};
+\draw[color=blue] (-3,1) node[above]{\small$1$};
+
+\draw (-2,-1) -- (0,0);
+\draw[fill=black] (-2,-1) circle[radius=2pt];
+\draw (-2,-1) node[above]{\small$\sqC_1^2$};
+\draw (-1,-0.5) node[below]{\small$f_2$};
+\draw[color=blue] (-1,-0.5) node[above]{\small$1$};
+
+\draw (-2,-1) -- (-4,-1);
+\draw[fill=black] (-4,-1) circle[radius=2pt];
+\draw (-4,-1) node[above]{\small$\sqC_1^4$};
+\draw (-3,-1) node[below]{\small$g_2$};
+\draw[color=blue] (-3,-1) node[above]{\small$1$};
+
+\draw (0,-2) -- (-2,-2);
+\draw[fill=black] (-2,-2) circle[radius=2pt];
+\draw (-2,-2) node[above]{\small$\sqC_2^1$};
+\draw (-1,-2) node[below]{\small$f_3$};
+\draw[color=blue] (-1,-2) node[above]{\small$2$};
+\draw[->] (-2,-2) -- (-2,-2.5);
+\draw[color=blue] (-2,-2.5) node[below]{\small$0$};
+
+\draw (-2,-2) -- (-4,-2);
+\draw[fill=black] (-4,-2) circle[radius=2pt];
+\draw (-4,-2) node[above]{\small$\sqC_2^2$};
+\draw (-3,-2) node[below]{\small$g_3$};
+\draw[color=blue] (-3,-2) node[above]{\small$2$};
+
+\draw[color=blue,->] (0,-2.5) -- (0,-3.5);
+
+\draw[color=blue,->] (-4,-4) -- (3,-4);
+\draw[fill=blue] (0,-4) circle[radius=2pt];
+\draw[fill=blue] (2,-4) circle[radius=2pt];
+\draw[fill=blue] (-2,-4) circle[radius=2pt];
+\draw[fill=blue] (-4,-4) circle[radius=2pt];
+\end{tikzpicture}
+\caption{$\rho$}
+\end{minipage}
+\end{figure}
+
+\noindent On the cone $\rho$ we have the following continuity equations
+\begin{align*}
+e:=e_1 = e_2 \\
+f:=f_1 = f_2 = 2f_3 \\
+g:=g_1 = g_2 = 2g_3
+\end{align*}
+together with the equation imposed by the choice of alignment:
+\begin{align*} & e_1 + f_1 = e_2 + f_3 + g_3 \\
+\Leftrightarrow \ & e + f = e + f/2 + g/2 \\
+\Leftrightarrow \ & f = g.
+\end{align*}
+Notice that setting $f=g=0$ we recover $\tau$. We claim that if we twist the bundle
+\begin{equation*} E = \left( \TT_{q_1} C_1 \otimes \TT_{q_1} C_0 \right) \oplus \left( \TT_{q_2} C_2 \otimes \TT_{q_2} C_0 \right) \end{equation*}
+by the line bundle corresponding to the divisor in $\widetilde\Dcal$ defined by $\rho$, we will obtain the bundle
+\begin{equation*} F = \left( \TT_{f_1}C_1^1 \otimes \TT_{e_1} C_0 \right) \oplus \left( \TT_{g_2} C_2^2 \otimes \TT_{e_2} C_0 \right). \end{equation*}
+described earlier. The line bundle corresponding to $\rho$ is simply $\OO(f)=\OO(g)$. We have:
+\begin{align*} \left( \TT_{q_1} C_1 \otimes \TT_{q_1} C_0 \right) \otimes \OO(f) & = \TT_{q_1}C_1 \otimes \TT_{q_1} C_0 \otimes \TT_{f_1} C_1^0 \otimes \TT_{f_1} C_1^1 \\
+& = \TT_{e_1} C_1^0 \otimes \TT_{e_1} C_0 \otimes \TT_{f_1} C_1^0 \otimes \TT_{f_1} C_1^1\\
+&  = \TT_{f_1} C_1^1 \otimes \TT_{e_1} C_0\end{align*}
+where we have used the telescoping trick $\TT_{f_1}C_1^0 \otimes \TT_{e_1} C_1^0 \cong \OO$. On the other hand, for the $C_2$ summand we write $f=f/2 + g/2=f_3+g_3$ to obtain:
+\begin{align*} \left( \TT_{q_2}C_2 \otimes \TT_{q_2}C_0\right) \otimes \OO(f) & = \TT_{e_2} C_0 \otimes \TT_{e_2} C_2^0 \otimes \OO(f_3) \otimes \OO(g_3) \\
+& = \TT_{e_2} C_0 \otimes \TT_{e_2} C_2^0 \otimes \TT_{f_3} C_2^0 \otimes \TT_{f_3} C_2^1 \otimes \TT_{g_3} C_2^1 \otimes \TT_{g_3} C_2^2 \\
+& = \TT_{g_3} C_2^2 \otimes \TT_{e_2} C_0.\end{align*}
+This observation generalises, giving a precise relation between the intrinsically-defined vector bundle $F$ on $\widetilde\Dcal$ (which we use to impose the factorisation condition) and the resolution of the vector bundle $E$ pulled back from $\Ecal$.
+This allows us to express the Chern classes of $F$ in terms of pull-backs of tautological classes from $\Ecal$ and boundary strata on $\widetilde\Dcal$, which is what we need in order to compute our integrals.
 

### 2019-06-27 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
partial reorganisation and minor comments on the first part (up to Gathmann's line bundle)

--- 2019-06-27 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
@@
 
-\section{Stratification}
+\subsection{Rubber variants} In our implementation of the relative theory, we will need the ``rubber'' variant of the space of maps $
+\VZ_{1,\alpha}(\mathbb P^N|H)$, where the entire curve is mapped into higher levels.
+
+Specifically, let $\mathbb P$ denote the projective bundle $\mathbb P(\mathcal O(1)\oplus\mathcal O)$ on $\mathbb P^{N-1}$.
+Equip this space with the logarithmic structure coming from the $0$ and $\infty$ sections of the bundle.
+Consider the moduli space $\VZ_{1,\alpha}(\mathbb P/\mathbb G_m)$ of logarithmic maps
+\[
+C\to \mathbb P[s]\to \mathbb P^{N-1},
+\]
+which factorize completely, and where automorphisms are considered over the space of maps to $\mathbb P^{N-1}$.
+Specifically, two maps that differ by a $\mathbb G_m$ translate in the fiber direction are considered equivalent.
+Total factorization, similar to the previous case, means that the map to the bundle and the map to the base $\mathbb P^{N-1}$ both factorize through possibly different singularities.
+
+\begin{thm}
+The stack $\VZ_{1,\alpha}(\mathbb P/\mathbb G_m)$ is logarithmically smooth.
+\end{thm}
+
+The main point in the proof of this statement is that on the space of non-degenerate maps with smooth domains, the map from $\VZ^\circ_{1,\alpha}(\mathbb P)\to \VZ^\circ_{1,\alpha}(\mathbb P/\mathbb G_m)$ is a $\mathbb G_m$ torsor.
+Correspondingly, the map on compact moduli spaces is a nodal curve fibration.
+To prove this, it is convenient to work with the logarithmic multiplicative group and its torsors.
+Recall that the \textit{logarithmic multiplicative group} $\mathbb G_{\mathrm{log}}$ is the functor on logarithmic schemes whose value on a logarithmic scheme $S$ is the group of global sections $H^0(S,M_S^{\mathrm{gp}})$; \tred{it is a proper group functor, and it contains $\Gm$ as a subfunctor}.
+This functor is representable only after a logarithmically \'etale cover.
+Background may be found in~\cite{MW17,RW19}.
+
+The bundle $\mathbb P\to \mathbb P^{N-1}$ gives rise to a $\mathbb G_m$-torsor by deleting the zero and infinity sections.
+Replacing these fibers by their $\mathbb G_{\mathrm{log}}$ compactifications, we obtain a non-representable functor on logarithmic schemes $\mathbb P_{\mathrm{log}}$ and a logarithmically \'etale modification
+\[
+\mathbb P\to \mathbb P_{\mathrm{log}}.
+\]
+
+\begin{proof}
+Consider the stack over logarithmic schemes $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}})$ of stable logarithmic maps that factorize completely.
+Here, stability for the map coincides with stability for the projection to $\mathbb P^{N-1}$.
+The arguments in the previous section show that maps to $\mathbb P$ that factorize completely are unobstructed.
+Since this space is a logarithmically \'etale cover of $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}})$, logarithmic smoothness of the latter follows.
+
+The logarithmic multiplicative group $\mathbb G_{\mathrm{log}}$ acts on $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}})$ by translation.
+Tautologically, $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}})$ is a $\mathbb G_{\mathrm{log}}$-torsor over the moduli problem of maps up to this $\mathbb G_{\mathrm{log}}$ translation.
+It is representable after a logarithmically \'etale modification by a family of nodal curves.
+It follows that the space  $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}}/\mathbb G_{\mathrm{log}})$ of maps up to translation that factorize completely is logarithmically smooth.
+
+To conclude the main result, we compare the stacks $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}}/\mathbb G_{\mathrm{log}})$ and  $\VZ_{1,\alpha}(\mathbb P/\mathbb G_m)$.
+Since a map to $\mathbb P$ gives rise immediately to a map to $\mathbb P_{\mathrm{log}}$, there is a morphism
+\[
+\VZ_{1,\alpha}(\mathbb P/\mathbb G_m)\to \VZ_{1,\alpha}(\mathbb P_{\mathrm{log}}/\mathbb G_{\mathrm{log}}).
+\]
+An application of the infinitesimal lifting criterion shows that this map is logarithmically \'etale, so the result follows.
+\end{proof}
+
+\subsection{Virtual construction for very ample pairs}
+Now let $(X,Y)$ be a smooth pair with $Y$ very ample.
+The definition given in \S \ref{subsection factorisation} applies in this setting, producing a moduli space $\VZ_{1,\alpha}(X|Y,\beta)$ together with a morphism
+\begin{equation*} \VZ_{1,\alpha}(X|Y,\beta) \to \ol\Mcal^{\operatorname{log}}_{1,\alpha}(X|Y,\beta)\end{equation*}
+obtained by performing a logarithmic modification and then passing to a closed substack.
+This moduli space will not in general be logarithmically smooth, but we may equip it with a virtual class as follows.
+The complete linear system $|\OO_X(Y)|$ defines an embedding $X \hookrightarrow \PP^N$ with $Y=X\cap H$ for $H$ some hyperplane.
+
+\begin{lemma} The following square is cartesian (in the category of ordinary stacks):
+\bcd
+\VZ_{1,\alpha}(X|Y,\beta) \ar[r] \ar[d] \ar[rd,phantom,"\square"] & \VZ_{1,\alpha}(\PP^N|H,d) \ar[d] \\
+\VZ_{1,n}(X,\beta) \ar[r,"i"] & \VZ_{1,n}(\PP^N,d).
+\ecd
+\end{lemma}
+\begin{proof} It is clear from the modular description that this square is cartesian in the category of fs logarithmic stacks.
+But the morphism $i$ is strict, which implies that the square is also cartesian in the category of coherent logarithmic stacks.
+Since fibre products in the latter category are compatible with the functor forgetting logarithmic structures, the claim follows.\end{proof}
+
+Since $\VZ_{1,n}(\PP^N,d)$ is smooth and $\VZ_{1,n}(X,\beta)$ carries a natural virtual class \cite[Theorem 4.4.1]{RSPW} there is a diagonal pull-back morphism~\cite[Appendix C]{BattistellaNabijou}, which we use to define the virtual class on the space of maps to $(X,Y)$:
+\begin{equation*} \virt{\VZ_{1,\alpha}(X|Y,\beta)} := i_\Delta^! [\VZ_{1,\alpha}(\PP^N|H,d)]. \end{equation*}
+Since $\VZ_{1,\alpha}(X|Y,\beta)$ comes equipped with evaluation maps and cotangent line classes, we immediately arrive at a definition of reduced Gromov--Witten invariants for the pair $(X,Y)$.
+This is the same manner in which Gathmann defines his virtual classes~\cite{Ga}.
+
+\section{Stratification and tropicalization}
 
@@
     \item no open neighborhood of $\plC_0$ is contracted to a point in $\mathbb R_{>0}$, or
-    \item if an open neighborhood of $\plC_0$ is contracted and $t_1,\ldots,t_k$ are the vertex-edge direction flags whose vertex is mapped to $F(\plC_0)$, but along which $F$ has nonzero slope; then, the minimum of the distances from $\plC_0$ to $t_i$ occurs for at least two indices $i$.
+    \item if an open neighborhood of $\plC_0$ is contracted and $t_1,\ldots,t_k$ are the \sout{vertex-edge direction} flags whose vertex is mapped to $F(\plC_0)$, but along which $F$ has nonzero slope; then, the minimum of the distances from $\plC_0$ to $t_i$ occurs for at least two indices $i$.
 \end{enumerate}
@@
 To describe the tropical map to $\mathbb R_{>0}$, we observe that $\plC_0$ is contracted to a fixed point $q\in\mathbb R_{>0}$.
-The flags at the vertex bases at $t_i$ correspond to nodes or markings of $C$.
+The flags at \sout{the vertex bases} at $t_i$ correspond to nodes or markings of $C$.
 The pole orders of $f$ at these distinguished points determine the slopes of the tropical map.
-We are now exactly in the situation considered in~\cite[Second Paragraph of Section~4.6]{RSPW2}, and Lemma~4.6.1 of loc.
+We are now exactly in the situation considered in~\cite[Second Paragraph of \S~4.6]{RSPW2}, and Lemma~4.6.1 of loc.
 cit.
@@
 
-\subsection{The cone complex} To understand the stratification via combinatorial data, we will build the straification from known objects. \\
+\subsection{The cone complex} To understand the stratification via combinatorial data, we will build the stratification from known objects. \\
 
@@
 \noindent
-\textbf{Step 3}.
-Given a tropical map $F: \plC\to \mathbb R_{\geq 0}$ parameterized by $\Sigma^{\mathrm{Kim}}$, there is a largest radius $\delta$ (possible equal to $0$) such that every vertex strictly contained in the circle of radius $\delta$ around the core has degree-marking $d=0$.
+\textbf{Step 3}.\marginpar{doesn' picking $\delta$ itself imply a subdivision?} Given a tropical map $F: \plC\to \mathbb R_{\geq 0}$ parameterized by $\Sigma^{\mathrm{Kim}}$, there is a largest radius $\delta$ (possibly equal to $0$) such that every vertex strictly contained in the circle of radius $\delta$ around the core has degree-marking $d=0$.
 Let $
-\Sigma^{\mathrm{cen}}$ be the subdivision obtained by requiring that the vertices contained with the circle of radius $\delta$ around the core of $\plC$ are totally ordered.
+\Sigma^{\mathrm{cen}}$ be the subdivision obtained by requiring that the vertices contained within the circle of radius $\delta$ around the core of $\plC$ are totally ordered.
 This involves introducing cones along which certain $\Z$-linear combinations of edge lengths are identified.\\
@@
 \noindent
-\textbf{Step 4}. Let $
-\Sigma_{1,\alpha}(\mathbb P^N|H,d)$ be the subcomplex of $\Sigma^{\mathrm{cen}}$ obtained by passing to the subcomplex of $\Sigma^{\mathrm{cen}}$ that consists of well-spaced tropical maps.
+\textbf{Step 4}.
+Let $\Sigma_{1,\alpha}(\mathbb P^N|H,d)$ be \sout{the subcomplex of $\Sigma^{\mathrm{cen}}$} obtained by passing to the subcomplex of $\Sigma^{\mathrm{cen}}$ that consists of well-spaced tropical maps.
 
@@
 \VZ_{1,\alpha}(\mathbb P^N|H)$.
-Specifically, the fact that cone complex $\Sigma^{\mathrm{cen}}$ is the cone complex attached to the logarithmic stack $\widetilde{\VZ}_{1,\alpha}(\mathbb P^N|H)$ of centrally aligned maps to expansions, follows immediately from its description as a subcategory of the fibered category (over logarithmic schemes) of $\mathcal M^{\mathrm{log}}_{1,\alpha}(\mathbb P^N|H)$.
+Specifically, the fact that the cone complex $\Sigma^{\mathrm{cen}}$ is the cone complex attached to the logarithmic stack $\widetilde{\VZ}_{1,\alpha}(\mathbb P^N|H)$ of centrally aligned maps to expansions, follows immediately from its description as a subcategory of the fibered category (over logarithmic schemes) of $\mathcal M^{\mathrm{log}}_{1,\alpha}(\mathbb P^N|H)$.
 To complete the result, we note that $
@@
 \VZ_{1,\alpha}(\mathbb P^N|H)$, so its cone complex is a subcomplex of $\Sigma^{\mathrm{cen}}$.
-The fact that it must be contained in the subcomplex of well-spaced curves is immediate from Proposition~\ref{prop: well-spaced}.l
+The fact that it must be contained in the subcomplex of well-spaced curves is immediate from Proposition~\ref{prop: well-spaced}.
 \end{proof}
@@
 \item a finite graph;
-\item genus, degree and marking assignments on the vertices
+\item genus, degree and marking assignments on the vertices;
 \item the data of which stratum of $\RR_{\geq 0}$ each vertex is mapped to;
@@
 \end{enumerate}
-In \S \ref{} we will perform this analysis in the case $k=1$.
-
-\section{Rubber variants and virtual construction}
-
-\subsection{Rubber variants} In our implementation of the relative theory, we will need the ``rubber'' variant of the space of maps $
-\VZ_{1,\alpha}(\mathbb P^N|H)$, where the entire curve is mapped into higher levels.
-
-Specifically, let $\mathbb P$ denote the projective bundle $\mathbb P(\mathcal O(1)\oplus\mathcal O)$ on $\mathbb P^{N-1}$.
-Equip this space with the logarithmic structure coming from the $0$ and $\infty$ sections of the bundle.
-Consider the moduli space $\VZ_{1,\alpha}(\mathbb P/\mathbb G_m)$ of logarithmic maps
-\[
-C\to \mathbb P[s]\to \mathbb P^{N-1},
-\]
-which factorize completely, and where automorphisms are considered over the space of maps to $\mathbb P^{N-1}$.
-Specifically, two maps that differ by a $\mathbb G_m$ translate in the fiber direction are considered equivalent.
-Total factorization, similar to the previous case, means that the map to the bundle and the map to the base $\mathbb P^{N-1}$ both factorize through possibly different singularities.
-
-\begin{thm}
-The stack $\VZ_{1,\alpha}(\mathbb P/\mathbb G_m)$ is logarithmically smooth.
-\end{thm}
-
-The main point in the proof of this statement is that on the space of non-degenerate maps with smooth domains, the map from $\VZ^\circ_{1,\alpha}(\mathbb P)\to \VZ^\circ_{1,\alpha}(\mathbb P/\mathbb G_m)$ is a $\mathbb G_m$ torsor.
-Correspondingly, the map on compact moduli spaces is a nodal curve fibration.
-To prove this, it is convenient to work with the logarithmic multiplicative group and its torsors.
-Recall that the \textit{logarithmic multiplicative group} $\mathbb G_{\mathrm{log}}$ is the functor on logarithmic schemes whose value on a logarithmic scheme $S$ is the group of global sections $H^0(S,M_S^{\mathrm{gp}})$.
-This functor is representable only after a logarithmically \'etale cover.
-Background may be found in~\cite{MW17,RW19}.
-
-The bundle $\mathbb P\to \mathbb P^{N-1}$ gives rise to a $\mathbb G_m$-torsors by deleting the zero and infinity sections.
-Replacing these fibers by their $\mathbb G_{\mathrm{log}}$ compactifications, we obtain a non-representable functor on logarithmic schemes $\mathbb P_{\mathrm{log}}$ and a logarithmically \'etale modification
-\[
-\mathbb P\to \mathbb P_{\mathrm{log}}.
-\]
-
-\begin{proof}
-Consider the stack over logarithmic schemes $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}})$ of stable logarithmic maps that factorize completely.
-Here, stability for the map coincides with stability for the projection to $\mathbb P^{N-1}$.
-The arguments in the previous section show that maps to $\mathbb P$ that factorize completely are unobstructed.
-Since this space is a logarithmically \'etale cover of $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}})$, logarithmic smoothness of the latter follows.
-
-The logarithmic multiplicative group $\mathbb G_{\mathrm{log}}$ acts on $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}})$ by translation.
-Tautologically, $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}})$ is a $\mathbb G_{\mathrm{log}}$-torsor over the moduli problem of maps up to this $\mathbb G_{\mathrm{log}}$ translation.
-It is representable after a logarithmically \'etale modification by a family of nodal curves.
-It follows that the space  $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}}/\mathbb G_{\mathrm{log}})$ of maps up to translation that factorize completely is logarithmically smooth.
-
-To conclude the main result, we compare the stacks $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}}/\mathbb G_{\mathrm{log}})$ and  $\VZ_{1,\alpha}(\mathbb P/\mathbb G_m)$.
-Since a map to $\mathbb P$ gives rise immediately to a map to $\mathbb P_{\mathrm{log}}$, there is a morphism
-\[
-\VZ_{1,\alpha}(\mathbb P/\mathbb G_m)\to \VZ_{1,\alpha}(\mathbb P_{\mathrm{log}}/\mathbb G_{\mathrm{log}}).
-\]
-An application of the infinitesimal lifting criterion shows that this map is logarithmically \'etale, so the result follows.
-\end{proof}
-
-\subsection{Virtual construction for very ample pairs}
-Now let $(X,Y)$ be a smooth pair with $Y$ very ample.
-The definition given in \S \ref{subsection factorisation} applies in this setting, producing a moduli space $\VZ_{1,\alpha}(X|Y,\beta)$ together with a morphism
-\begin{equation*} \VZ_{1,\alpha}(X|Y,\beta) \to \ol\Mcal^{\operatorname{log}}_{1,\alpha}(X|Y,\beta)\end{equation*}
-obtained by performing a logarithmic modification and then passing to a closed substack.
-This moduli space will not in general be logarithmically smooth, but we may equip it with a virtual class as follows.
-The complete linear system $|\OO_X(Y)|$ defines an embedding $X \hookrightarrow \PP^N$ with $Y=X\cap H$ for $H$ some hyperplane.
-
-\begin{lemma} The following square is cartesian (in the category of ordinary stacks):
-\bcd
-\VZ_{1,\alpha}(X|Y,\beta) \ar[r] \ar[d] \ar[rd,phantom,"\square"] & \VZ_{1,\alpha}(\PP^N|H,d) \ar[d] \\
-\VZ_{1,n}(X,\beta) \ar[r,"i"] & \VZ_{1,n}(\PP^N,d).
-\ecd
-\end{lemma}
-\begin{proof} It is clear from the modular description that this square is cartesian in the category of fs log stacks.
-But the morphism $i$ is strict, which implies that the square is also cartesian in the category of coherent log stacks.
-Since fibre products in the latter category are compatible with the functor forgetting log structures, the claim follows.\end{proof}
-
-Since $\VZ_{1,n}(\PP^N,d)$ is smooth and $\VZ_{1,n}(X,\beta)$ carries a natural virtual class \cite[Theorem 4.4.1]{RSPW} there is a diagonal pull-back morphism~\cite[Appendix C]{BattistellaNabijou}, which we use to define the virtual class on the space of maps to $(X,Y)$:
-\begin{equation*} \virt{\VZ_{1,\alpha}(X|Y,\beta)} := i_\Delta^! [\VZ_{1,\alpha}(\PP^N|H,d)]. \end{equation*}
-Since $\VZ_{1,\alpha}(X|Y,\beta)$ comes equipped with evaluation maps and cotangent line classes, we immediately arrive at a definition of reduced Gromov--Witten invariants for the pair $(X,Y)$.
-This is the same manner in which Gathmann defines his virtual classes~\cite{Ga}.
-
-\part{The recursion formula and applications}\footnote{(Navid) From here on, when I write a relative space without any decoration, I mean a Kim space.
-We should establish this convention from the start} \noindent In this part we prove recursion relations on the moduli space of reduced stable maps (Theorem \ref{theorem recursion}).
+In \S \ref{section reduced splitting axiom} we will perform this analysis in the case $k=1$.
+
+%\part{The recursion formula and applications}\footnote{(Navid) From here on, when I write a relative space without any decoration, I mean a Kim space.
+We should establish this convention from the start}
+
+\sout{\noindent In this part we prove recursion relations on the moduli space of reduced stable maps (Theorem \ref{theorem recursion}).
 These are inspired by the constructions of Vakil and Gathmann, but go beyond these in several key respects, giving a full treatment of descendant invariants for very ample pairs.
 We apply the recursions to produce a quantum Lefschetz algorithm in genus one, reconstructing the absolute theory of $Y$ and the relative theory of $(X,Y)$ from the absolute theory of $X$.
-Along the way we prove a splitting axiom for the reduced relative theory; the form of this splitting axiom is nontrivial, insofar as it involves the introduction of additional tautological classes.
-
-In \S\S \ref{Section Gathmann line bundle}--\ref{section reduced splitting axiom} we prove the recursion formula for $(\PP^N,H)$.
+Along the way we prove a splitting axiom for the reduced relative theory; the form of this splitting axiom is nontrivial, insofar as it involves the introduction of additional tautological classes.}
+
+\sout{In \S\S \ref{Section Gathmann line bundle}--\ref{section reduced splitting axiom} we prove the recursion formula for $(\PP^N,H)$.
 In \S \ref{section recursion for general pair} we indicate how to obtain from this the recursion formula for an arbitrary very ample pair $(X,Y)$.
-Finally in \S \ref{section recursion algorithm} we describe the quantum Lefschetz algorithm.
+Finally in \S \ref{section recursion algorithm} we describe the quantum Lefschetz algorithm.}
 
@@
 For each marking $x_k$ we consider the locus $\Dcal_{1,\alpha,k}(\PP^N|H,d) \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$ where $x_k$ belongs to an internal component of the collapsed map.
-In this section, we use the log structure on $\VZ_{1,\alpha}(\PP^N|H,d)$ to construct a line bundle $\Lcal_k$ together with a section $s_k$ which vanishes precisely along $\Dcal_{1,\alpha,k}(\PP^N|H,d)$.
+In this section, we use the logarithmic structure on $\VZ_{1,\alpha}(\PP^N|H,d)$ to construct a line bundle $\Lcal_k$ together with a section $s_k$ which vanishes precisely along $\Dcal_{1,\alpha,k}(\PP^N|H,d)$.
 We use the correspondence with tropical geometry to identify $\cchern_1(\Lcal_k)$ in terms of tautological classes on $\VZ_{1,\alpha}(\PP^N|H,d)$, and to compute the vanishing order of $s_k$ along the components of $\Dcal_{1,\alpha,k}(\PP^N|H,d)$.
@@
 
-The pair $(\Lcal_k,s_k)$ is most naturally constructed on the moduli space $\MLog_{1,\alpha}(\PP^N|H,d)$ of non-expanded log maps; the corresponding pair on $\VZ_{1,\alpha}(\PP^N|H,d)$ will be obtained via pull-back.
+The pair $(\Lcal_k,s_k)$ is most naturally constructed on the moduli space $\MLog_{1,\alpha}(\PP^N|H,d)$ of non-expanded logarithmic maps; the corresponding pair on $\VZ_{1,\alpha}(\PP^N|H,d)$ will be obtained via pull-back.
 Consider therefore the tropicalisation $\Sigma^{\log}$ of $\MLog_{1,\alpha}(\PP^N|H,d)$, identified as usual with the moduli space of tropical maps to $\RR_{\geq 0}$.
@@
 We now calculate $\cchern_1(\Lcal_k)$.
-Choose a family of log stable maps over $S$ and let $\mu \in \Gamma(S,\ol{M}_S)$ be the global section of the ghost sheaf constructed in the previous paragraph.
+Choose a family of logarithmic stable maps over $S$ and let $\mu \in \Gamma(S,\ol{M}_S)$ be the global section of the ghost sheaf constructed in the previous paragraph.
 This pulls back along $\pi$ to give a global section $\pi^\flat(\mu) \in \Gamma(C,\ol{M}_C)$.
@@
 \begin{remark} This construction gives the natural logarithmic analogue of Gathmann's line bundle and section \cite[Construction 2.1]{Ga}.
-A benefit of the logarithmic approach is to make the computation of vanishing orders entirely combinatorial (see \S \ref{} below), circumventing the difficult technical calculation given by Gathmann.
+A benefit of the logarithmic approach is to make the computation of vanishing orders entirely combinatorial (see \S \ref{subsubsection splitting degree} below), circumventing the difficult technical calculation given by Gathmann.
 \end{remark}
@@
 
-\begin{lemma} \label{Lemma components are log divisors} Every irreducible component of $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ is a codimension $1$ log stratum.\end{lemma}
-\begin{proof} This is not hard to see: the locus where the log structure is trivial coincides precisely with the  locus where the source curve is smooth and not mapped inside $H$, and since $\VZ_{1,\alpha}(\PP^N|H,d)$ is log smooth this locus is open and dense \cite{Niziol}.
-By definition $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ is contained in the  complement of this locus, which (by the very definition of logarithmic strata) can be written as a union of log strata of positive codimension.
-Since $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ has codmension $1$, it must therefore be equal to a union of log divisors.\end{proof}
-In \S \ref{subsection indexing strata} we discussed a procedure for enumerating the log strata of $\VZ_{1,\alpha}(\PP^N|H,d)$, using the cones of the tropicalisation $\Sigma_{1,\alpha}(\PP^N|H,d)$.
+\begin{lemma} \label{Lemma components are log divisors} Every irreducible component of $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ is a codimension $1$ logarithmic stratum.\end{lemma}
+\begin{proof} This is not hard to see: the locus where the logarithmic structure is trivial coincides precisely with the  locus where the source curve is smooth and not mapped inside $H$, and since $\VZ_{1,\alpha}(\PP^N|H,d)$ is log smooth this locus is open and dense \cite{Niziol}.
+By definition $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ is contained in the  complement of this locus, which (by the very definition of logarithmic strata) can be written as a union of logarithmic strata of positive codimension.
+Since $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ has codmension $1$, it must therefore be equal to a union of logarithmic divisors.\end{proof}
+In \S \ref{subsection indexing strata} we discussed a procedure for enumerating the logarithmic strata of $\VZ_{1,\alpha}(\PP^N|H,d)$, using the cones of the tropicalisation $\Sigma_{1,\alpha}(\PP^N|H,d)$.
 To recap: every divisorial logarithmic stratum is obtained via a three-step process:
@@
 
-The log divisors contained in $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ are precisely those whose  combinatorial types map the vertex of the dual graph containing $x_k$  into the interior $\RR_{>0} \subseteq \RR_{\geq 0}$.
+The logarithmic divisors contained in $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ are precisely those whose  combinatorial types map the vertex of the dual graph containing $x_k$  into the interior $\RR_{>0} \subseteq \RR_{\geq 0}$.
 Thus via the above procedure, we are able to enumerate the irreducible components of $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ in a combinatorial manner, and the combinatorial type $\Delta$ allows us to describe the general element of such a component.
@@
 \subsection{Recursive description of the divisors: types $A,B$ and $C^+$} Choose an irreducible component $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$.
-By Lemma \ref{Lemma components are log divisors} this is a log divisor, and hence may be written as:
+By Lemma \ref{Lemma components are log divisors} this is a logarithmic divisor, and hence may be written as:
 \begin{equation*} \Dcal = \widetilde\Dcal \cap \VZ_{1,\alpha}(\PP^N|H,d) \end{equation*}
-for a unique log stratum $\widetilde\Dcal \subseteq \widetilde{\VZ}_{1,\alpha}(\PP^N|H,d)$. Since
+for a unique logarithmic stratum $\widetilde\Dcal \subseteq \widetilde{\VZ}_{1,\alpha}(\PP^N|H,d)$. Since
 \begin{equation*}\widetilde{\VZ}_{1,\alpha}(\PP^N|H,d) \to \ol\Mcal_{1,\alpha}(\PP^N|H,d)\end{equation*}
-is a log modification, $\widetilde{\Dcal}$ is either exceptional or the proper transform of a log divisor.
+is a logarithmic modification, $\widetilde{\Dcal}$ is either exceptional or the proper transform of a logarithmic divisor.
 These cases correspond, respectively, to when the circuit is assigned zero degree or nonzero degree by the combinatorial type.
 To begin with we will focus on the latter case.
-Suppose therefore that $\widetilde{\Dcal}$ is the proper transform of a log divisor:
+Suppose therefore that $\widetilde{\Dcal}$ is the proper transform of a logarithmic divisor:
 \begin{equation*} \Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d). \end{equation*}
@@
 We now investigate the three types $A,B,C^+$ separately, giving a recursive description of the boundary divisor in each case.
-For the remainder of this subsection, therefore, we fix a one-dimensional cone $\tau \in \Sigma_{1,\alpha}(\PP^N|H,d)$, let $\Dcal \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$ be the associated log divisor, and assume that $\Dcal$ is contained in $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ and is of type $A,B$ or $C^+$.
-We let $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$ be the log stratum into which $\Dcal$ is mapped; this is indexed by a cone $\epsilon \in \Sigma$ corresponding to a combinatorial type $\Delta$, and $\epsilon$ is one-dimensional since we are restricting to the type $A,B,C^+$ cases.
+For the remainder of this subsection, therefore, we fix a one-dimensional cone $\tau \in \Sigma_{1,\alpha}(\PP^N|H,d)$, let $\Dcal \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$ be the associated logarithmic divisor, and assume that $\Dcal$ is contained in $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ and is of type $A,B$ or $C^+$.
+We let $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$ be the logarithmic stratum into which $\Dcal$ is mapped; this is indexed by a cone $\epsilon \in \Sigma$ corresponding to a combinatorial type $\Delta$, and $\epsilon$ is one-dimensional since we are restricting to the type $A,B,C^+$ cases.
 
@@
 
-We modify $\Ecal$\footnote{With the log structure obtained by pulling back from Kim's space and modding out by $\mathbb N^{\codim (\sigma)}$, i.e.
+We modify $\Ecal$\footnote{With the logarithmic structure obtained by pulling back from Kim's space and modding out by $\mathbb N^{\codim (\sigma)}$, i.e.
 considering the edges of $E$ to have \emph{infinite length}.} along the boundary as follows:
@@
 For this it might be useful to notice that there is a morphism $\Mpunct{g}{\alpha}{H}{d}\to \Mpunct{g}{\alpha}{\PP^N}{d}$ (because $H\subseteq\PP^N$ is strict), which is probably a closed immersion, and the loci with smooth source curve are isomorphic under this map.
-It seems plausible that the main omponent is log smooth over $B\Gm\subseteq[\Aaff^1/\Gm]$ (or the standard log point).
+It seems plausible that the main omponent is log smooth over $B\Gm\subseteq[\Aaff^1/\Gm]$ (or the standard logarithmic point).
 \end{proof}

### 2019-06-27 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
added a line to intro re: fictitious markings

@@
 
+\tred{We rephrase Gathmann's idea of increasing the tangency requirement within the framework of logarithmic stable maps (where maximal tangency is always assumed) by introducing \emph{fictitious markings}, and identifying the space of maps with higher contact order with a boundary stratum inside that of lower contact order and more (fictitious) markings.}
+
 Our analysis leads naturally to \tred{the} study of a ``main component’’ double ramification cycle for target manifolds in genus one.

### 2019-06-27 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
minor changes

--- 2019-06-27 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
@@
 
-\subsection{Recursive description of the divisors: type IIIb} The treatment of the type I, II and IIIa cases above is a fairly straightforward extension of the ideas of Vakil and Gathmann (albeit updated with logarithmic and tropical technology, which streamlines the presentation and simplifies the proofs).
+\subsection{Recursive description of the divisors: type IIIb}\label{subsection C0} The treatment of the type I, II and IIIa cases above is a fairly straightforward extension of the ideas of Vakil and Gathmann (albeit updated with logarithmic and tropical technology, which streamlines the presentation and simplifies the proofs).
 The remaining type IIIb case, however, is entirely new.
@@
 
-\section{Recursion for general $(X,Y)$}\label{section recursion for general pair}
+\section{Recursion for general $(X,Y)$}\label{section recursion for general pair} We now let $(X,Y)$ be a general smooth very ample pair.
+In \S \ref{} we studied the moduli space $\VZ_{1,\alpha}(X|Y,\beta)$ of centrally aligned maps to $(X,Y)$ and equipped it with a virtual fundamental class by diagonal pull-back from $\VZ_{1,\alpha}(\PP^N|H,d)$.
+
+This construction of the virtual fundamental class means that once we have established a recursion formula for $(\PP^N,H)$, it immediately pulls back to give a recursion formula for $(X,Y)$.
+To be more precise, Theorem \ref{theorem recursion} holds \emph{mutatis mutandis}, with the same values of $\lambda_\Dcal$.
+The computation of the splitting orders is exactly the same, and the recursive description of the boundary strata pulls back to give an entirely analogous description on $\VZ_{1,\alpha}(X|Y,\beta)$.
 

### 2019-06-27 EllipticSingularitiesSplitting.tex
Added Dhruv's synthesis

--- 2019-06-27 Reduced Gromov-Witten Theory of Hypersurfaces in Genus One.tex
@@
 The relative and absolute theories are related by degeneration of the tangency conditions, and the resulting formulas generalize a well-known recursive calculation scheme put forward by Gathmann in genus $0$.
-\sout{The geometric input is a desingularization of the principal component of the moduli space of genus one logarithmic stable maps to a very ample pair, using the geometry of elliptic singularities.
-Our study passes through a number of general techniques for calculating integrals on logarithmic blowups of moduli spaces of stable maps, which may be of independent interest.}
+{The geometric input is a desingularization of the principal component of the moduli space of genus one logarithmic stable maps to a very ample pair, using the geometry of elliptic singularities.
+Our study passes through general techniques for calculating integrals on logarithmic blowups of moduli spaces of stable maps, which may be of independent interest.}
 \end{abstract}
@@
 The Kontsevich moduli space of stable maps from genus $0$ curves to projective space exhibits \tred{remarkable} geometry -- it is a smooth orbifold with a ``self-similar'' normal crossings boundary.
-These facts have combined to produce a \tred{remarkable} understanding of Gromov--Witten theory in genus $0$.
+These facts have combined to produce a very {satisfactory} understanding of Gromov--Witten theory in genus $0$.
 
@@
 While the Atiyah--Bott localization for the reduced invariants was used to great effect by Zinger in his proof of the BCOV conjectures, two major components of the standard theory -- relative invariants and the degeneration formula -- have not been developed in this setting.
-Our results in this paper provide these as new \sout{structural} tools in reduced genus one Gromov--Witten theory\footnote{Further motivation to consider the genus one case specifically comes simply from the fact that for Calabi--Yau geometries in dimension larger than $3$, Gromov--Witten theory vanishes in genera greater than $1$.}.
+Our results in this paper provide these as new {structural} tools in reduced genus one Gromov--Witten theory\footnote{Further motivation to consider the genus one case specifically comes simply from the fact that for Calabi--Yau geometries in dimension larger than $3$, Gromov--Witten theory vanishes in genera greater than $1$.}.
 
@@
 The behaviour mixes the geometry in~\cite{RSPW} and~\cite{RSPW2}.
-\sout{Together with an analysis of the deformation theory of such maps, we are led to Theorem~\ref{thm: desingularization}}.
+{Together with an analysis of the deformation theory of such maps, we are led to Theorem~\ref{thm: desingularization}}.
 
@@
 
-\sout{In essence, this is a family of curves where every vertex of the tropical curve $\plC$ is either inside or outside the circle of radius $\delta$ around the core genus $1$ subcurve.}
+{In essence, this is a family of curves where every vertex of the tropical curve $\plC$ is either inside or outside the circle of radius $\delta$ around the core genus $1$ subcurve.}
 
@@
 Here the latter is the $s$-times iterated deformation to the normal cone of $H$ in $\mathbb P^N$.
-The components \tred{of the target} are in bijection with the number of vertices in $\widetilde{\mathbb R}_{\geq 0}$.
+The components \tred{of the target} are in bijection with the vertices in $\widetilde{\mathbb R}_{\geq 0}$.
 The curve is modified by adding rational components corresponding to the newly introduced vertices.
@@
 
-\section{Gathmann's line bundle via tropical geometry}\label{Section Gathmann line bundle} Consider a reduced relative space $\VZ_{1,\alpha}(\PP^N|H,d)$.
+\section{Degeneration of contact order}\label{Section Gathmann line bundle} Consider a reduced relative space $\VZ_{1,\alpha}(\PP^N|H,d)$.
 For each marking $x_k$ we consider the locus $\Dcal_{1,\alpha,k}(\PP^N|H,d) \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$ where $x_k$ belongs to an internal component of the collapsed map.
@@
 
-\section{Recursive description of boundary strata: the relative splitting axiom}\label{section reduced splitting axiom}
-In this section we provide an explicit description of the terms appearing on the right-hand side of \eqref{equation recursion} above.
-For each such term, we provide a combinatorial method to calculate the vanishing order $\lambda_\Dcal$, and a recursive description of the stratum $\Dcal$ in terms of fibre products of moduli spaces with smaller numerical data.
-The form which this recursive description takes is non-obvious, in the sense that additional tautological classes appear, which must be calculated.
-This constitutes the most technically difficult part of the paper.
-
-\subsection{Identifying the irreducible components of $\Dcal_{1,\alpha,k}(\PP^N|H,d)$} Here we explain the strategy for identifying the irreducible components of $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ via tropical geometry.
-
-\begin{lemma} \label{Lemma components are log divisors} Every irreducible component of $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ is a codimension $1$ logarithmic stratum.\end{lemma}
-\begin{proof} This is not hard to see: the locus where the logarithmic structure is trivial coincides precisely with the  locus where the source curve is smooth and not mapped inside $H$, and since $\VZ_{1,\alpha}(\PP^N|H,d)$ is log smooth this locus is open and dense \cite{Niziol}.
-By definition $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ is contained in the  complement of this locus, which (by the very definition of logarithmic strata) can be written as a union of logarithmic strata of positive codimension.
+\section{Splitting the boundary}
+
+A basic phenomenon is responsible for the nature of the forthcoming analysis.
+In contrast with nodal singularities, the functions on an elliptic singularity is not simply given as a collection of functions on the normalization subject to topological gluing conditions.
+As a consequence, in order to compute integrals, it is necessary to give a tautological description of this additional factorization condition.
+
+In what follows, we provide an explicit description of the terms appearing in the right-hand side of \eqref{equation recursion}.
+For each term, we provide a combinatorial formula for the vanishing order $\lambda_\Dcal$, and a recursive description of the stratum $\Dcal$.
+in terms of fibre products of moduli spaces with smaller numerical data.
+The tautological description of the factorization condition then leads to a recursive structure for calculating integrals.
+This last step is the heart of the analysis.
+
+\begin{remark}
+We remark that for the reduced relative theory of $(\mathbb P^N,H)$ with only primary fields, an analysis of the factorization condition can be avoided by dimension considerations.
+This leads to the main results in~\cite{Vre}.
+In order to add descendant fields, study with more general pairs, or indeed work cycle theoretically, an analysis of these tautological classes is crucial.
+\end{remark}
+
+\subsection{Irreducible components of the degenerate locus} We explain the tropical geometric procedure to identify irreducible components of $\Dcal_{1,\alpha,k}(\PP^N|H,d)$.
+
+\begin{lemma} \label{Lemma components are logarithmic divisors} Every irreducible component of $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ is a codimension $1$ log stratum.\end{lemma}
+
+\begin{proof} The locus where the log structure is trivial coincides precisely with the  locus where the source curve is smooth, and consequently not mapped inside $H$.
+Since $\VZ_{1,\alpha}(\PP^N|H,d)$ is toroidal this locus is open and dense.
+By definition $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ is contained in the  complement of this locus and can be expressed as a union of strata of positive codimension.
 Since $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ has codmension $1$, it must therefore be equal to a union of logarithmic divisors.\end{proof}
-In \S \ref{subsection indexing strata} we discussed a procedure for enumerating the logarithmic strata of $\VZ_{1,\alpha}(\PP^N|H,d)$, using the cones of the tropicalisation $\Sigma_{1,\alpha}(\PP^N|H,d)$.
-To recap: every divisorial logarithmic stratum is obtained via a three-step process:
+
+In \S \ref{subsection indexing strata} we discussed a procedure for enumerating the logarithmic strata of $\VZ_{1,\alpha}(\PP^N|H,d)$, using the cones of the tropicalization $\Sigma_{1,\alpha}(\PP^N|H,d)$.
+Every divisorial logarithmic stratum is obtained as follows:
 \begin{enumerate}
 \item choose a combinatorial type $\Delta$ of a tropical map;
-\item subdivide the corresponding tropical moduli space $\sigma$;
+\item subdivide the corresponding tropical moduli space $\sigma$ to align the type;
 \item choose a ray in this subdivision.
 \end{enumerate}
-Notice that this process contains some redundancies: upon choosing a ray in the tropical moduli space, some of the edge lengths or vertex positions may get set to $0$.
-This induces a generisation of the intial combinatorial type $\Delta$, given by contracting the corresponding edges of the dual graph and moving the corresponding vertices from $\RR_{>0}$ to $0$.
-By the combinatorial type of a stratum in $\VZ_{1,\alpha}(\PP^N|H,d)$ we will always mean this generisation.
-This is independent of the choice of $\Delta$, and in fact we can (and will) always choose $\Delta$ to coincide with the generisation.
+This process contains some redundancies: upon choosing a ray in the tropical moduli space, some of the edge lengths or vertex positions may get set to $0$.
+This induces a generization of the intial combinatorial type $\Delta$, given by contracting the corresponding edges of the dual graph and moving the corresponding vertices from $\RR_{>0}$ to $0$.
+When we speak of the combinatorial type of a stratum in $\VZ_{1,\alpha}(\PP^N|H,d)$, we will always mean this generisation.
+This is independent of the choice of $\Delta$, and in fact we can and will always choose $\Delta$ to coincide with the generization.
 
 The logarithmic divisors contained in $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ are precisely those whose  combinatorial types map the vertex of the dual graph containing $x_k$  into the interior $\RR_{>0} \subseteq \RR_{\geq 0}$.
-Thus via the above procedure, we are able to enumerate the irreducible components of $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ in a combinatorial manner, and the combinatorial type $\Delta$ allows us to describe the general element of such a component.
-What we are still lacking is a recursive description of the components, which we need in order to compute integrals over them.
-This is the subject of the remainder of this section.
+Thus via the above procedure, we enumerate the irreducible components of $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ in a combinatorial manner, and the combinatorial type $\Delta$ allows us to describe the general element of such a component.
+The remainder of this section gives a recursive description of the components, and a procedure to compute integrals over them in a recursive manner.
 
 \subsection{Recursive description of the divisors: types $A,B$ and $C^+$} Choose an irreducible component $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$.
-By Lemma \ref{Lemma components are log divisors} this is a logarithmic divisor, and hence may be written as:
+By Lemma \ref{Lemma components are logarithmic divisors} this is a logarithmic divisor, and hence may be written as:
 \begin{equation*} \Dcal = \widetilde\Dcal \cap \VZ_{1,\alpha}(\PP^N|H,d) \end{equation*}
-for a unique logarithmic stratum $\widetilde\Dcal \subseteq \widetilde{\VZ}_{1,\alpha}(\PP^N|H,d)$. Since
+for a unique log stratum $\widetilde\Dcal \subseteq \widetilde{\VZ}_{1,\alpha}(\PP^N|H,d)$. Since
 \begin{equation*}\widetilde{\VZ}_{1,\alpha}(\PP^N|H,d) \to \ol\Mcal_{1,\alpha}(\PP^N|H,d)\end{equation*}
-is a logarithmic modification, $\widetilde{\Dcal}$ is either exceptional or the proper transform of a logarithmic divisor.
-These cases correspond, respectively, to when the circuit is assigned zero degree or nonzero degree by the combinatorial type.
+is a log modification, the divisor $\widetilde{\Dcal}$ is either exceptional or the strict transform of a logarithmic divisor.
+These two cases correspond, respectively, to when the circuit is assigned zero degree or nonzero degree by the combinatorial type.
 To begin with we will focus on the latter case.
@@
 The birational map $\widetilde{\Dcal} \to \Ecal$ induces a morphism $\Dcal \to \Ecal$.
-In the remainder of this subsection, we will show how to interpret this morphism as a ``desingularisation of the main component''.
+We now show how to interpret this morphism as a desingularisation of the principal component.
 Since $\Ecal$ admits a recursive description in terms of relative and rubber moduli spaces, this will allow us to compute integrals over $\Dcal$.
 
-\begin{lemma}\label{lem:combs} Let $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ be an irreducible component which contributes nontrivially to the recursion, and let $\Delta$ be the corresponding combinatorial type.
+\begin{lemma}\label{lem:combs} Let $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ be an irreducible component which contributes nontrivially to the Gromov--Witten invariant, and let $\Delta$ be the corresponding combinatorial type.
 Suppose that $\Delta$ assigns positive degree to the circuit.
@@
 
-\noindent The terminology is due to Vakil, and the pictures in this case are very similar to \cite{Vre} (we will see later that when the circuit is assigned zero degree the picture becomes \emph{very} different).
-Note that in these pictures we have deliberately omitted the marked points (except for $x_k$), the degree of each vertex, and the expansion factors of the edges.
-The omitted combinatorial data can be distributed arbitrarily, as long as:
+\noindent The degrees of vertices, expansions factors, and remaining markings are distributed according to the following rules:
 \begin{enumerate}
@@
 
-\begin{proof} Let $\sigma \in \Sigma$ be the cone corresponding to the stratum $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$.
+The terminology above due to Vakil, and the configurations in this case are very similar to those analyzed in \cite{Vre}.
+
+\begin{proof} Let $\sigma \in \Sigma$ be the cone corresponding to the $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$.
 By the discussion above $\Dcal$ corresponds to a ray in the subdivision of $\sigma$ given by imposing the central alignment condition.
-But since the ellipse is assigned positive degree, both radii are equal to $0$ and the subdivision is trivial.
-We conclude that $\sigma=\RR_{\geq 0}$ (recall we are assuming that the initial and generised combinatorial types coincide).
-Since there must be at least one vertex mapped to higher level, we conclude that the tropical target $\widetilde\RR_{\geq 0}$ is obtained from $\RR_{\geq 0}$ by subdividing at a single point $\diamond \in \RR_{> 0}$.
-
-In order to have $\sigma=\RR_{\geq 0}$, the dual graph $\Gamma$ must be a bipartite graph with vertices over $0$ and $\diamond$.
+Since the elliptic core is assigned positive degree, both radii are equal to $0$ and the subdivision is trivial.
+We conclude that $\sigma=\RR_{\geq 0}$.
+Since there must be at least one vertex mapped to higher level, the tropical target $\widetilde\RR_{\geq 0}$ is obtained from $\RR_{\geq 0}$ by subdividing at a single point $\diamond \in \RR_{> 0}$.
+
+In order for the cone $\sigma$ to be $1$-dimensional, the dual graph $\Gamma$ must be bipartite, with vertices over $0$ and $\diamond$.
 The cases $A,B$ and $C^+$ enumerated above cover situations where there is a single vertex mapped to $\diamond$.
-We claim that if there is more than one such vertex, then the contribution to the recursion vanishes.
+If there is more than one such vertex, then the contribution to the Gromov--Witten invariant vanishes.
 To see this, we consider the stratum
@@
 If we let $\Fcal^{\text{\tiny{log}}}$ denote the intersection of $\Ecal^{\text{\tiny{log}}}$ with the main component of the moduli space, then we obtain a factorisation $\Dcal \to \Fcal^{\text{\tiny{log}}} \hookrightarrow \Ecal^{\text{\tiny{log}}}$.
-Since the moduli space is generically unobstructed along $\Fcal^{\text{\tiny{log}}}$, the codimension of $\Fcal^{\text{\tiny{log}}}$ is given by the dimension of the associated cone in the tropicalisation $\Sigma^{\text{\tiny{log}}}$.
+Since the moduli space is generically unobstructed along $\Fcal^{\text{\tiny{log}}}$, the codimension of $\Fcal^{\text{\tiny{log}}}$ is given by the dimension of the associated cone in the tropicalization $\Sigma^{\text{\tiny{log}}}$.
 If there is more than one vertex mapped to higher level, then this cone has dimension $\geq 2$.
@@
 For the remainder of this subsection, therefore, we fix a one-dimensional cone $\tau \in \Sigma_{1,\alpha}(\PP^N|H,d)$, let $\Dcal \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$ be the associated logarithmic divisor, and assume that $\Dcal$ is contained in $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ and is of type $A,B$ or $C^+$.
-We let $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$ be the logarithmic stratum into which $\Dcal$ is mapped; this is indexed by a cone $\epsilon \in \Sigma$ corresponding to a combinatorial type $\Delta$, and $\epsilon$ is one-dimensional since we are restricting to the type $A,B,C^+$ cases.
-
-\subsubsection{Type $A$}\label{subsubsection type A} Suppose $\Delta$ is of type $A$. Then $\Ecal$ admits a finite splitting morphism onto the fibre product:
+We let $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$ be the log stratum into which $\Dcal$ is mapped; this is indexed by a cone $\epsilon \in \Sigma$ corresponding to a combinatorial type $\Delta$, and $\epsilon$ is one-dimensional since we are restricting to the type $A,B,C^+$ cases.
+
+\subsubsection{Type $A$}\label{subsubsection type A} Suppose $\Delta$ is of type $A$. Then $\Ecal$ admits a finite and surjective \textit{splitting morphism} onto the fibre product:
 \begin{equation*} \Ecal \to \left( \ol\Mcal_{1,\alpha^{(1)}\cup(m_1)}(\PP^N|H,d_1) \times \prod_{i=2}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i) \right) \times_{H^r} \ol\Mcal^{\leftrightarrow}_{0,\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}(P|H_0+H_\infty,d_0).\end{equation*}
 
-\begin{lemma} \label{Lemma type A gluing} $\Dcal$ admits a natural splitting morphism
+{\color{red}\bf Has this notation $P$ and the notation for rubber been introduced before? Is this consistent?}
+
+\begin{lemma} \label{Lemma type A gluing} The divisor $\Dcal$ admits a natural splitting morphism
 \begin{equation*}\Dcal \xrightarrow{\rho} \left(\VZ_{1,\alpha^{(1)}\cup(m_1)}(\PP^N|H,d_1)\times\prod_{i=2}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i)\right) \times_{H^r} \ol\Mcal^{\leftrightarrow}_{0,\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}(P|H_0+H_\infty,d_0)\end{equation*}
@@
 \begin{proof}
-The choices involved in gluing log maps to expansions (which accounts for the degrees of the splitting morphisms above) is not affected by the introduction of alignments, so for the purposes of this proof we may pretend as if these splitting morphisms are the identity maps.
-
-Note that the map $\Dcal\to\Ecal$ is an isomorphism away from the blown-up locus, which is contained inside the locus where the circuit is contracted.
-Given an element of $\Dcal$ we can split it along the nodes $q_1,\ldots,q_r$ as in \cite{}.
+We first consider the statement of the lemma in the category of fine but not necessarily saturated logarithmic schemes, so that a relative stable map to an expansion admits a unique logarithmic lifting.
+The fiber product description preceding the lemma is an isomorphism in this category~\cite[Lemma~4.2.2]{AbramovichMarcusWiseComparison}.
+
+The map $\Dcal\to\Ecal$ is an isomorphism away from the exceptional centers, and the latter is contained in the locus where the circuit is contracted.
+Given an element of $\Dcal$ we can split it along the nodes $q_1,\ldots,q_r$.
 It is then clear that $\sqC_1$ is aligned.
-We claim that $\sqC$ satisfies the factorisation property if and only if $\sqC_1$ does.
+We claim that $\sqC$ satisfies the factorization property if and only if $\sqC_1$ does.
 This immediately implies the lemma.
 
-On $\sqC$ there are associated contraction radii $\delta_1,\delta_2$.
+On $\sqC$ there are two contraction radii $\delta_1,\delta_2$.
 Let $\delta \in \{\delta_1,\delta_2\}$.
-By Lemma \ref{type A radius lemma} below, we have $\lambda(\sqC^\prime) > \delta$ for any component $\sqC^\prime$ of $\sqC_0$.
+An examination of the stratification by combinatorial type of $\Dcal$ shows that $\lambda(\sqC^\prime) > \delta$ for any component $\sqC^\prime$ of $\sqC_0$.
 This means that $\sqC_0,\sqC_2,\sqC_3,\ldots,\sqC_r$ lie outside both contraction radii, and so the aligned curve $\sqC$ satisfies the factorisation condition if and only if $\sqC_1$ does.
@@
 
-\begin{lemma}\label{type A radius lemma} $\lambda(\sqC^\prime) > \delta$ for any component $\sqC^\prime$ of $\sqC_0$ (with notation as in the proof above).\end{lemma}
-\begin{proof} The basic point is that $\Dcal$ is obtained as the disjoint union of the locally closed logarithmic strata contained in the closure of the stratum where all of the $\sqC_i$ are irreducible.
-If we look at one of these boundary strata, then by definition the associated cone $\sigma \in \Sigma_{1,\alpha}(\PP^N|H,d)$ contains a ray $\tau$ corresponding to the stratum where all the $\sqC_i$ are irreducible; this amounts to setting all edge lengths other than $e_1,\ldots,e_r$ to zero.
+%\begin{lemma}\label{type A radius lemma} In the notation of the proof above, $\lambda(\sqC^\prime) > \delta$ for any component $\sqC^\prime$ of $\sqC_0$.\end{lemma}
+%
+%\begin{proof} Observe first that $\Dcal$ is obtained as the disjoint union of the locally closed logarithmic strata contained in the closure of the stratum where all of the $\sqC_i$ are irreducible.
+We choose and examine one of these boundary strataIf we look at one of these boundary strata, then by definition the associated cone $\sigma \in \Sigma_{1,\alpha}(\PP^N|H,d)$ contains a ray $\tau$ corresponding to the stratum where all the $\sqC_i$ are irreducible; this amounts to setting all edge lengths other than $e_1,\ldots,e_r$ to zero.
 If $f_1,\ldots,f_l$ are some collection of additional edge lengths in $\sigma$ (corresponding to internal nodes in degenerations of the $\sqC_i$) then since $\sigma$ is adjacent to $\tau$ we must have (by construction of the subdivision) $f_1+\ldots+f_l < e_j$ for all $j\in\{1,\ldots,r\}$, since $f_1=\ldots=f_l=0$ and $e_j \neq 0$ on $\tau$.
@@
 We thus obtain the following description, entirely in terms of genus zero data:
-\begin{lemma} $\Dcal$ admits a finite splitting morphism:
+\begin{lemma} $\Dcal$ admits a finite and surjective splitting morphism:
 \begin{equation*} \Dcal \xrightarrow{\rho} \left(\ol\Mcal_{0,\alpha^{(1)}\cup(m_1,m_2)}(\PP^N|H,d_1)\times\prod_{i=3}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i)\right) \times_{H^r} \ol\Mcal^{\leftrightarrow}_{0,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(P|H_0+H_\infty,d_0).\end{equation*}\end{lemma}
 
-\subsubsection{Type $C^+$} \label{subsubsection type C+} Finally suppose that $\Delta$ is of type $C^+$. As before we have a finite morphism:
+\subsubsection{Type $C^+$} \label{subsubsection type C+} Finally suppose that $\Delta$ is of type $C^+$. As before we have a finite and surjective morphism:
 \begin{equation*} \Ecal \to  \left( \prod_{i=1}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i) \right) \times_{H^r} \ol\Mcal^{\leftrightarrow}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(P|H_0+H_\infty,d_0).
@@
 \begin{equation*} \label{degree of gluing} \dfrac{\prod_{i=1}^r m_i}{\lcm(m_1,\ldots,m_r)}. \end{equation*}\end{lemma}
-\begin{proof} This calculation is by now standard, and is given by examining the base order of the corresponding family of targets. See, for instance \cite{ChenDegeneration}, \cite{ACGSDecomposition}.
+\begin{proof} The calculation is well known, and is recorded for instance in~\cite[Section~7.9]{ChenDegeneration}, \cite[Section~5.3]{ACGSDecomposition}.
 \end{proof}
 
-\begin{lemma}\label{lemma vanishing order} $\lambda_\Dcal = \lcm(m_1,\ldots,m_r).$ \end{lemma}
+\begin{lemma}\label{lemma vanishing order} The section $s_k$ vanishes along the divisor $\Dcal$ with order given by 
+\[
+\lambda_\Dcal = \lcm(m_1,\ldots,m_r).
+\] 
+\end{lemma}
 \begin{proof} Let $\tau \in \Sigma_{1,\alpha}(\PP^N|H,d)$ be the cone corresponding to $\Dcal$ and let
@@
 It follows from the tropical description that $\lambda_\Dcal$ is equal to the index of the map of integral cones $\tau \to \RR_{\geq 0}$ obtained by restricting $\varphi$.
-By tropical continuity we have $\tau \subseteq \RR_{\geq 0}^r$ with integral generator:
+Observe that $\tau \subseteq \RR_{\geq 0}^r$ with integral generator:
 \begin{equation*} w = \left( \dfrac{\lcm(m_1,\ldots,m_r)}{m_1},\ldots,\dfrac{\lcm(m_1,\ldots,m_r)}{m_r} \right).\end{equation*}
-The map $\tau \to \RR_{\geq 0}$ is given by projecting onto the $i$th factor and then multiplying by $m_i$ (this is independent of $i$ by continuity of the tropical map).
-Thus we conclude that the index is equal to $\lcm(m_1,\ldots,m_r)$ as claimed.\end{proof}
-In summary, then: the contribution of each term $\lambda_\Dcal [\Dcal]$ is given by integrating over the appropriate fibre product and then multiplying the result by $\lambda_\Dcal \cdot \deg\rho = \prod_{i=1}^r m_i$.
-
-\subsection{Recursive description of the divisors: type $C^0$}
-
-\subsubsection{Combinatorial types} Recall that a boundary divisor $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ is said to be of \textbf{type $C^0$} if the core is assigned zero degree by the combinatorial type.
-In this case, the combinatorial type is not as tightly constrained as previously (it needs not be a bipartite graph with a single interior vertex).
-Nevertheless, we have the following lemmas:
-\begin{lemma} 
-Let $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ be of type $C^0$ and let $\Delta$ be the corresponding combinatorial type.
-Then, for every vertex $\diamond\neq0$ of the expanded target, the fibre of the tropical map over $\diamond$ contains exactly one stable vertex (together with a number of trivial bubbles), and at least one vertex which lies on the circle (which may or may not be stable).
+The map $\tau \to \RR_{\geq 0}$ is given by projecting onto the $i$th factor and then multiplying by $m_i$.
+Note that by piecewise linear continuity of the tropical map, this is independent of $i$.
+We conclude that the index is equal to $\lcm(m_1,\ldots,m_r)$ as claimed.\end{proof}
+
+We summarize that the contribution of each term $\lambda_\Dcal [\Dcal]$ is given by integrating over the appropriate fibre product and then multiplying the result by $\lambda_\Dcal \cdot \deg\rho = \prod_{i=1}^r m_i$.
+
+\subsection{Recursive description of the divisors: type IIIb} The treatment of the type I, II and IIIa cases above is a fairly straightforward extension of the ideas of Vakil and Gathmann (albeit updated with logarithmic and tropical technology, which streamlines the presentation and simplifies the proofs).
+The remaining type IIIb case, however, is entirely new.
+In this section we provide a recursive description of these boundary divisors.
+This constitutes the technical heart of the paper.
+
+\subsubsection{Possible combinatorial types} A boundary divisor $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ is said to have \textit{type IIIb} if the core is assigned degree zero by the combinatorial type.
+Divisors of this type occur as principal components in compactified torus bundles over strata in the space of relative maps.
+As a result, their combinatorial types exhibit very degenerate behaviour.
+Precisely, over the generic point of such a divisor, the target may expand multiple times, and the source tropical curve need not be bipartite with a single interior vertex.
+We stress once again that such degenerate contributions are at the heart of the reduced theory and cannot be removed.
+
+We begin with the following lemma:
+\begin{lemma} \label{lemma type C0 combinatorial types}
+Let $\Dcal$ be a locus of type IIIb with combinatorial type $\Delta$ which contributes nontrivially to the Gromov--Witten invariant.
+For every nonzero vertex $\diamond$ of the tropical target, the fibre of the tropical map over $\diamond$ contains exactly one stable vertex, which lies on the radius.
 \end{lemma}
+
 \begin{proof}
-By stability, we always need at least one stable vertex lying over each vertex of the target.
-If there was more than one, then (since both the insertions and the factorisation condition are pulled back from the moduli space of maps without expansions) it could be seen, as in the proof of Lemma \ref{lem:combs}, that the contribution would vanish.
-
-Furthermore, for each vertex of the target there must always be a vertex in the preimage which lies on the circle, since otherwise there would be at least two independent tropical parameters, and so $\Dcal$ would not be a divisor.\end{proof}
-
-\begin{lemma}
- If, for any nonzero vertex $\diamond$ of the expanded target, the only stable vertex in $\phi^{-1}(\diamond)$ is not the core, nor it lies on the circle, then the corresponding combinatorial type $\Delta$ does not contribute to the invariants.
-\end{lemma}
-\begin{proof}
- By the previous Lemma, there must be a vertex $v$ lying on the circle and over $\diamond$; such a vertex is strictly semistable by assumption, in particular the map $f$ is constant along the corresponding component, therefore the fact that the factorisation condition is satisfied is unaffected by $\Gm$-scaling the coordinate corresponding to $v$ in the moduli space of attachments.
-We deduce that the generic fiber of $\Dcal\to\Ecal$ has positive dimension.
+Stability guarantees that at least one stable vertex lies over each vertex of the target.
+If there is more than one stable vertex, as in the proof of Lemma \ref{lem:combs}, the corresponding locus $\Fcal$ in the moduli space of unexpanded maps has high codimension.
+As both insertions and the factorization property for the collapsed map to $\mathbb P^N$ are pulled back from the moduli space of maps without expansions, the contribution vanishes by the projection formula.
+
+For each vertex of the target there must always be at least one vertex in the preimage which lies on the radius.
+This is implied by the fact that the combinatorial type $\Delta$ is a ray.
+In fact, we make the stronger assertion that the stable vertex mapping to $\diamond$ lies on the radius.
+The alternative is that a vertex dual to a trivial bubble lies on the radius.
+This latter condition implies that $\Dcal \to \Ecal$ has positive-dimensional fibres, so the contribution vanishes.
 \end{proof}
 
-\begin{lemma}\label{lem:m=1}
- If the maximal contact order at the core is $m=1$, the corresponding combinatorial type does not contribute to the invariants.
-\end{lemma}
-\begin{proof}
- It follows once again from a dimensional argument.
-\end{proof}
-
-%%%%%%%%
-\begin{center}
-\begin{figure}
-\includegraphics[scale=.6]{ray_example}
-\caption{A ray of type $C^0$.}\label{fig:ray_example}
-\end{figure}
-\end{center}
-%%%%%%%%%%
-
-We observe that the cone $\sigma \in \Sigma^{\Kim}$ corresponding to the stratum $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$ is isomorphic to $\N^r$ where $r$ is the number of target expansions.
-The discrepancy between the dimension of $\sigma$ and the dimension of the ray $\tau$ is to be expected, since the loci of type $C^0$ are contained in the exceptional locus of the blow-up.
-
-We write $V_0$ for the collection of stable vertices of the combinatorial type which are mapped to $0$ by the tropical map, and $V_{>0}$ for the stable vertices which are mapped to $\RR_{>0}$.
-For each vertex $v$ there is associated discrete data $\Gamma_v$, which defines a moduli space of relative stable maps if $v \in V_0$ and a moduli space of rubber maps if $v \in V_{>0}$.
-Then $\Ecal$ admits a finite splitting morphism onto the fibre product
-\begin{equation*} \Ecal \xrightarrow{\rho} \left( \prod_{v \in V_0} \ol\Mcal_{\Gamma_v}(\PP^N|H) \times \prod_{v \in V_{>0}} \ol\Mcal^{\leftrightarrow}_{\Gamma_v}(P|H_0+H_\infty) \right) \times_{H^{2E}} H^E \end{equation*}
-where $E$ is the set of edges of the (stabilised) dual graph, and the fibre product is taken over the appropriate evaluation maps.
-Note that only the factor corresponding to the core vertex has non-zero genus, and that it has zero degree by assumption.
-
-\begin{remark}As in \S \ref{subsubsection splitting degree} above, we should calculate the degree of $\rho$ and the vanishing order $\lambda_{\Dcal}$ of the section $s_k$ along $\Dcal$.
+\subsubsection{Recursive description of $\Ecal$} Recall that we have maps
+\[
+\VZ_{1,\alpha}(\PP^N|H,d)\hookrightarrow \widetilde{\VZ}_{1,\alpha}(\PP^N|H,d)\to \overline\Mcal_{1,\alpha}(\PP^N|H,d).
+\]
+The first morphism is a closed embedding cut out by the two factorization properties.
+The second morphism is a toroidal modification.
+Let $\tau \in \Sigma$ be a ray corresponding to $\Dcal \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$, and to the virtual divisor $\widetilde \Dcal \subseteq \widetilde{\VZ}_{1,\alpha}(\PP^N|H,d)$.
+\medskip
+
+Let $\sigma \in \Sigma^{\Kim}$ be the minimal cone containing the image $\tau$.
+The dimension of this cone could be large -- its dimension is equal to the the number of levels of the target expansion in the type $\tau$.
+The cone $\sigma$ determines a stratum $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$.
+The morphism above restricts to
+\[
+\Dcal \to \Ecal.
+\]
+
+\noindent
+{\bf Splitting in the ordinary geometry.} The locus $\Ecal$ has the following description.
+Let $\Lambda_0$ for the collection of stable vertices of the combinatorial type which are mapped to $0\in \RR_{\geq 0}$, and $\Lambda_{>0}$ for the stable vertices which are mapped to $\RR_{>0}$.
+Each vertex $v$ has associated discrete data $\Gamma_v$.
+The vertices over $0$ determine moduli space of ordinary relative stable maps, while the higher level vertices determine maps to rubber.
+Then $\Ecal$ admits a finite and surjective splitting morphism
+\begin{equation}\label{IIIa fibre product} \Ecal \xrightarrow{\rho} \left( \prod_{v \in \Lambda_0} \ol\Mcal_{\Gamma_v}(\PP^N|H) \times \prod_{v \in \Lambda_{>0}} \ol\Mcal^{\leftrightarrow}_{\Gamma_v}(P|H_0+H_\infty) \right) \times_{H^{2\epsilon}} H^{\epsilon} \end{equation}
+where $\epsilon$ is the number of edges of the stabilised dual graph, and the fibre product is taken over the appropriate evaluation maps.
+In conclusion, tautological integrals over $\Ecal$ are completely determined in terms of integrals over moduli spaces with ``smaller'' combinatorial data.\medskip
+
+\noindent
+{\bf Exportation to the ordinary geometry.}  Observe that we have a virtual divisor $\widetilde\Dcal \subseteq \widetilde\VZ_{1,\alpha}(\PP^N|H,d)$ such that 
+\[
+\Dcal = \widetilde\Dcal \cap \VZ_{1,\alpha}(\PP^N|H,d).
+\]
+We wish to use the splitting of $\Ecal$ in the ordinary geometry to recursively compute integrals in the reduced geometry.
+Noting that $\Dcal$ is cut out of the excess dimensional space $\widetilde \Dcal$ by the factorization properties, we make the reduction in two steps:
+\begin{enumerate}
+\item in \S \ref{subsection Dtilde from E} we explain how to construct $\widetilde\Dcal$ from $\Ecal$;
+\item in \S \ref{subsection D from Dtilde} we explain how to express the class of $\Dcal \subseteq \widetilde\Dcal$ in terms of tautological classes.
+\end{enumerate}
+To compute integrals over $\Dcal$ we simply push down the appropriate classes from $\widetilde\Dcal$ to $\Ecal$ and then integrate over $\Ecal$ using the ordinary splitting axiom.
+
+\begin{remark}[Splitting degree and vanishing order, revisited] Similarly to \S \ref{subsubsection splitting degree} above, we can calculate the degree of $\rho$ and the vanishing order $\lambda_{\Dcal}$ of the section $s_k$ along $\Dcal$.
 The degree of $\rho$ is given exactly as in Lemma \ref{lem:saturation}, where now we obtain one such factor for each bounded edge of the tropical target.
@@
 
-Typically, $\Ecal$ will have true dimension larger than that of $\Dcal$.
-We will study the map $\Dcal \to \Ecal$ in two steps: first, we will describe the map $\widetilde\Dcal \to \Ecal$, and then we will explain how to express the class of the substack $\Dcal \subseteq \widetilde\Dcal$ in terms of tautological classes.
-
-\subsubsection{From $\Ecal$ to $\widetilde{\Dcal}$} The reader should bear the following construction from toric geometry in mind: suppose we subdivide a fan, and we want to describe the relation between the varieties corresponding to a cone $\rho$ of the subdivision, and to the original cone $\sigma$ containing it, respectively.
-For any cone $\tau$, the fan of $X_\tau$ is obtained by projecting the star of $\tau$ to the quotient $N_\tau=N_{\RR}/\langle\tau\rangle_{\RR}$ of the ambient vector space by the linear span of $\tau$.\footnote{This can be encoded in the formalism of extended tropicalisations, see \cite{ACP} and references therein.} Notice that the dimension of the vector spaces $N_\rho$ and $N_\sigma$ (or the corresponding toric varieties) is off by the difference $c$ between the dimension of the cones.
-The image of $\Sigma_\rho$ provides a subdivision of $\Sigma_\sigma$.
-The geometric content is that $X_\rho$ is obtained as an appropriate compactification of a toric bundle of dimension $c$ over $X_\sigma$.
-%observe that the fiber dimension may not be constant (but it can be made so by blowing up $X_{\sigma}$, see \cite[Lemma 4.1]{AK}).
-
-We start by describing the modification of $\Ecal$ corresponding to the subdivision of the last paragraph; really, we only need to unravel the combinatorics partially, in order to describe an intermediate blowup $\widetilde\Ecal\to \Ecal$, such that $\Dcal$ factors through $\widetilde\Ecal$, and all the structures that we need to name in what follows make sense on $\widetilde\Ecal$ already.
-
-Let $V_{0,\delta}\subseteq V_0$ be the subset of vertices lying on the circle (besides being sent to $0$ by the tropical map).
-Notice that they all have the same expansion factor $m$, therefore they are at the same distance from the core, generically on $\Ecal$.\footnote{Indeed, generically, these vertices do not produce any subdivision of the target, so they contribute to the relative dimension of $\widetilde\Dcal\to\Ecal$ as one.} Another way to see the generic alignment is the following: the normal bundles corresponding to these nodes can be expressed as $\mathbb T_{R_v,q_v}\otimes\mathbb T_{E,q_v}$; for two different vertices, the right-hand factors are canonically identified thanks to the group structure on the elliptic curve, whereas the $m$-th powers of the left-hand factors are canonically identified by comparison with the target tangent line, and $\rho$ can be seen as taking an $m$-th root of this preferred isomophism.
-On the other hand, the alignment does not persist when the curves degenerate (see Figure \ref{fig:fwise_align}).
-
-\begin{figure}
-\includegraphics[scale=.5]{factorwise_alignment}
-\caption{Two degenerations of the combinatorial type above, which represents a ray.
-On the left-hand side, the alignment holds only generically.
-On the right-hand side, it is not enough to align each individual factor.}\label{fig:fwise_align}
-\end{figure}
-
-We modify $\Ecal$\footnote{With the logarithmic structure obtained by pulling back from Kim's space and modding out by $\mathbb N^{\codim (\sigma)}$, i.e.
-considering the edges of $E$ to have \emph{infinite length}.} along the boundary as follows:
-\begin{enumerate}[leftmargin=.5 cm]
- \item radially aligning the core, and imposing fiberwise factorisation, thus replacing
- \[\ol\Mcal^{\leftrightarrow}_{1,\mu}(P|H_0+H_\infty,d=0)\quad\text{by}\quad\VZ^{\leftrightarrow}_{1,\mu}(P|H_0+H_\infty,d=0)\]
- in the product above, thus introducing a reduced rubber with point target;
- \item requiring that any degeneration of $V_{0,\delta}$ (resp.
-$\forall v\in V_{>0,\delta}$) remains centrally aligned with respect to the core;\footnote{Notice that this requires us to blow up some diagonal subloci of the product above, see Figure \ref{fig:fwise_align}} as a consequence, on the whole of $\widetilde \Ecal$ - including the boundary -, for each $v\in \{V_{0,\delta}\}\cup V_{>0,\delta}$, it is always possible to tell the components of the curve that are at distance $\delta$ from the core along the path denominated $v$, and, if there is more than one for the same $v$, the lengths of these paths are identified, so as to define line bundles $\OO(\delta_v), \forall v\in \{V_{0,\delta}\}\cup V_{>0,\delta}$.
+\subsubsection{Compactified bundles over strata: $\widetilde\Dcal$ from $\Ecal$}\label{subsection Dtilde from E} Recall that the map $\widetilde\Dcal \to \Ecal$ is obtained by restricting the logarithmic blow-up
+\begin{equation*} \widetilde\VZ_{1,\alpha}(\PP^N|H,d) \to \ol\Mcal_{1,\alpha}(\PP^N|H,d)\end{equation*}
+to the locus $\widetilde\Dcal$.
+Toroidal geometry gives a construction of $\widetilde \Dcal$ as a compactification of a torus bundle over a locally closed stratum in $\overline\Mcal_{1,\alpha}(\PP^N|H,d)$.
+\medskip
+
+%In toric geometry, the means of studying this restriction is as follows.
+The fan of $\widetilde\Dcal$ (respectively, $\Ecal$) is obtained by projecting the star of the ray $\tau$ (respectively, the star of the cone $\sigma$) onto the quotient lattice.
+The map $\widetilde\Dcal \to \Ecal$ is then the toric morphism induced by the obvious map of fans.
+In order to describe this morphism more explicitly, we first subdivide the fan of $\Ecal$ by taking the images of cones in the fan of $\widetilde\Dcal$.
+This induces a toric blow-up of $\Ecal$ which we denote by $\widetilde\Ecal$.
+The morphism $\widetilde\Dcal \to \Ecal$ naturally factors through a morphism $\widetilde\Dcal \to \widetilde\Ecal$ which is now flat (in contrast to $\widetilde\Dcal \to \Ecal$), and  $\widetilde\Dcal$ may now be described as a compactification of a torus bundle over $\widetilde\Ecal$, with strata determined by the combinatorics of the fan.
+
+\noindent
+{\bf Logarithmic structures on strata.} Let $W\subset X$ be an irreducible stratum in a toroidal embedding $X$.
+The stratum itself is toroidal, and hence logarithmically smooth.
+If $X$ and $W$ are merely logarithmic and not toroidal, there is nonetheless a strict map
+\[
+X\to \mathcal A_X,
+\]
+where $ \mathcal A_X$ is the Artin fan of $X$, which is a toroidal Artin stack.
+If $W\subset X$ maps to a stratum $\mathcal A_W$ under this map, the pullback of the logarithmic structure from $\mathcal A_W$ to $W$ endows the stratum with a logarithmic structure.
+Note that the inclusion of a stratum $W\hookrightarrow X$ is \textit{not} a logarithmic morphism.
+
+Equipped with the strata logarithmic structures, the morphism
+\[
+\widetilde \Dcal\to \Ecal
+\]
+is a logarithmic morphism. The generic fiber of this morphism is toric variety.  \medskip
+
+\noindent
+{\bf Flattening the map to $\Ecal$.} The morphism $\widetilde \Dcal\to \Ecal$ is not flat.
+In order to push integrals forward, it will be convenient to flatten the map by blowing up $\Ecal$.
+This can be done in a universal manner, following~\cite{AK,Mol16}.
+
+The combinatorics of the flattening can be described explicitly. Consider the map on tropicalizations
+\[
+\widetilde{\Dcal}^{\mathrm{trop}}\to \Ecal^{\mathrm{trop}}.
+\]
+The tropical curves on the left inherit a central alignment from the moduli space $\widetilde{\VZ}_{1,\alpha}(\PP^N|H)$, which orders a certain subset of the edge lengths.
+The polyedral criterion for equidimensionality is that every cone of the source maps surjectively onto a cone of the target.
+
+By explicit but elementary polyhedral considerations, we are led to the following moduli theoretic description of the logarithmic modification $ \widetilde \Ecal$ such that the map $\widetilde \Dcal\to \widetilde \Ecal$ is flat.
+
+We keep in mind the fiber product description of $\Ecal$. Construct a modification $\widetilde \Ecal$ from $\Ecal$ as follows.
+
+\begin{enumerate}
+\item Given a logarithmic map with splitting nodes $q_1,\ldots,q_r$ of type $\Delta$, formally glue together the $r$ vertices of the tropicalization which carry the splitting nodes, and declare the resulting vertex to be the root of the resulting tree.
+Impose the central alignment condition, where the special root takes on the role previously occupied by the core.
+\item Replace the fiber product factor in $\Ecal$ associated to the vertex $\sqC_0$
+\begin{equation*} \ol\Mcal^{\leftrightarrow}_{\Gamma_{\tiny{\sqC_0}}}(P|H_0+H_\infty) \end{equation*}
+with the radially aligned rubber space:
+\begin{equation*} \VZ^{\leftrightarrow}_{\Gamma_{\tiny{\sqC_0}}}(P|H_0+H_\infty).\end{equation*}
 \end{enumerate}
-It is clear that $\widetilde \Dcal\to\widetilde\Ecal$ is generically a torus bundle of relative dimension $\codim(\sigma)-1$; the open locus is represented by the moduli space of attachments for the elliptic singularities.
+
+This procedure induces a logarithmic modification $\widetilde\Ecal \to \Ecal$ which admits a modular description as a fibre product of genus zero centrally aligned maps coming from the vertices $\sqC_1,\ldots,\sqC_r$, and genus one aligned rubber maps satisfying fibre-direction factorisation from the vertex $\sqC_0$).
+
+By construction, we have a map $\widetilde\Dcal \to \widetilde\Ecal$ which is a compactification of a torus bundle over $\widetilde\Ecal$.
+The strata of $\widetilde\Dcal$ can be read off from its tropicalisation, and in particular we have the information of how (polynomials in) the classes of boundary strata push forward to $\widetilde\Ecal$.
+
+We have produced a factorization
+\[
+\widetilde\Dcal\to\widetilde \Ecal\to\Ecal,
+\]
+where the first map is flat and the second map is a logarithmic modification. The generic fiber can be interpreted geometrically.
+
+{\bf \color{red} This lemma should be there, but the notation needs to be changed and the proof needs to be cleaned up. Luca?
+
 \begin{lemma}
@@
 \end{lemma}
+
 \begin{proof}
- All of the line bundles $\OO(\delta_v)$ share a common factor $\mathbb T_E$, the universal tangent line to the elliptic curve (appropriately twisted by bubbling loci as in \cite[\S 2.3]{VZ}); removing this, when the curve has the prescribed dual graph, $\OO(\delta_v)$ is isomorphic to the tangent line to the rational tail $R_v$ at the gluing node $q_v$ (with the caveat that all those corresponding to $V_{0,\delta}$ are canonically identified).
+ All of the line bundles $\OO(\delta_v)$ share a common factor $\mathbb T_E$, the universal tangent line to the elliptic curve.
+By removing this factor, we see that when the dual graph is fixed, $\OO(\delta_v)$ is isomorphic to the tangent line to the rational tail $R_v$ at the gluing node $q_v$.
+We make the caveat here that(with the caveat that all those corresponding to $V_{0,\delta}$ are canonically identified).
 This is the open stratum of the moduli space of attaching data \cite[\S\S 2.2-2.3]{SMY2}.
@@
 This is patently the fan of a projective space.
-\end{proof}
+\end{proof}}
+
 \begin{figure}
@@
 
-Notice that $\mathcal P$ is well-defined on the whole of $\widetilde \Ecal$, while $\widetilde \Dcal\to \mathcal P$ is in fact a modification along the boundary, as dictated by the alignment procedure.
-In the next section, we extrapolate what we need from this combinatorial setup in order to describe $\Dcal$ explicitly.
-\begin{comment}
-\subsubsection{The generic alignment} In the first line of the product above, we have grouped the $k$ factors adjacent to the core with maximal expansion factor $m$.
-It is fundamental to realise that, generically on $\Ecal$, the vertices corresponding to these factors are (equidistant and) already aligned with respect to the core.
-We can construct a modification $\widetilde\Ecal$ of $\mathcal E$ by:
-\begin{enumerate}
- \item radially aligning the core, and imposing the double factorisation condition, thus effectively replacing the factor
- \[\ol\Mcal_{1,\alpha^{(0)}\cup(-m,\ldots,-m,-\mu_{k+1},\ldots,-\mu_r)\cup(-m_i)_{i\in\{k+1,\ldots,s\}\setminus(\bigcup I_j)}}^{\leftrightarrow}(P|H_0+H_\infty,0)\]
- by $\VZ_{1,\alpha^{(0)}\cup(-m,\ldots,-m,-\mu_{k+1},\ldots,-\mu_r)\cup(-m_i)_{i\in\{k+1,\ldots,s\}\setminus(\bigcup I_j)}}^{\leftrightarrow}(P|H_0+H_\infty,0)$ in the product above; in particular, there is a universal cotangent line bundle at the markings $\mathbb L_E$, obtained by suitably twisting any marking cotangent line (they are all isomorphic over a smooth elliptic curve) by the appropriate bubbling loci (see \cite[\S 2.3]{VZ});
- \item aligning the first $k$ factors with respect to the core (this blows up some diagonal subloci of the product, so it is not enough to align the individual factors).
-\end{enumerate}
-See Figure \ref{fig:fwise_align} below.
-It is obvious that $\widetilde \Dcal\to \Ecal$ factors through $\widetilde\Ecal$.
-On $\widetilde\Ecal$, we have a tropical line bundle $\OO(\delta)$ representing the minimum distance from the core to the tropical preimage of $0$; generically, this line bundle coincides with the normal bundle of the locus where the node between the core and one (any) of the first $k$ vertices persists, but on the boundary this needs to be twisted by further smoothing parameters according to the (partial) alignment on $\widetilde\Ecal$.
-We can obtain a line bundle $\mathbb T_R$ accounting only for the behaviour of the rational side of the fiber product by twisting $\OO(\delta)$ with $\mathbb L_E$.
-\begin{figure}
- \begin{tikzpicture}[ipe stylesheet,scale=.7]
-  %\useasboundingbox (0, 0) rectangle (595, 842);
-  \pic
-     at (129.8488, 703.2932) {ipe disk};
-  \pic
-     at (97.8488, 719.2932) {ipe disk};
-  \pic
-     at (97.8488, 687.2932) {ipe disk};
-  \draw
-    (97.8488, 719.2932)
-     -- (129.8488, 703.2932)
-     -- (97.8488, 687.2932);
-  \draw
-    (129.8488, 703.2932)
-     -- (161.8488, 687.2932);
-
-  \draw
-    (193.8488, 671.2932)
-     -- (225.8488, 655.2932);
-  \draw
-    (225.8488, 655.2932)
-     -- (193.8488, 639.2932);
-    \draw[ipe dash dashed]
-   (193.8488, 671)
-    -- (161.8488, 687);
-  \draw[ipe dash dashed]
-    (193.8488, 639.2932)
-     -- (161.8488, 623.2932);
-  \draw
-    (161.8488, 623.2932)
-     -- (129.8488, 607.2932);
-  \pic
-     at (146.637, 615.0615) {ipe disk};
-  \draw
-    (129.8488, 607.2932)
-     -- (97.8488, 591.2932)
-     -- (97.8488, 591.2932);
-  \draw
-    (147.2948, 615.0622)
-     -- (97.2686, 638.1002)
-     -- (97.2686, 638.1002);
-  \pic
-     at (96.6103, 637.4422) {ipe disk};
-  \pic
-     at (97.9268, 590.7072) {ipe disk};
-  \pic
-     at (130.1808, 622.9607) {ipe cross};
-  \pic
-     at (130.1808, 607.1635) {ipe cross};
-  \pic
-     at (145.9788, 695.3672) {ipe cross};
-  \draw[-ipe linear]
-    (97.8488, 575.2932)
-     -- (257.8488, 575.2932);
-  \pic
-     at (97.8488, 575.2932) {ipe disk};
-  \pic
-     at (129.8488, 575.2932) {ipe cross};
-  \pic
-     at (145.8488, 575.2932) {ipe cross};
-  \pic
-     at (225.8488, 575.2932) {ipe cross};
-  \draw
-    (129.8488, 703.2932)
-     -- (257.8488, 703.2932);
-  \draw
-    (225.8488, 655.2932)
-     -- (257.8488, 655.2932)
-     -- (257.8488, 655.2932);
-  \draw
-    (146.3018, 614.861)
-     -- (258.5378, 614.404);
-  \node[ipe node]
-     at (189.423, 676.278) {$m$};
-  \node[ipe node]
-     at (189.094, 629.543) {$m$};
-  \node[ipe node]
-     at (111.421, 715.773) {$m_1$};
-  \node[ipe node]
-     at (110.104, 590.707) {$m_2$};
-  \node[ipe node]
-     at (110.763, 564.378) {$\ell_1$};
-  \node[ipe node]
-     at (133.801, 564.377) {$\ell_2$};
-  \node[ipe node]
-     at (146.308, 543.972) {$\frac{\ell_1}{m_1}+\frac{\ell_2}{m} \lesseqgtr \frac{\ell_1+\ell_2}{m_2}$};
-  \pic
-     at (473.6651, 658.9228) {ipe disk};
-  \pic
-     at (353.8488, 719.2932) {ipe disk};
-  \pic
-     at (353.8488, 687.2932) {ipe disk};
-  \draw
-    (353.8488, 719.2932)
-     -- (385.8488, 703.2932)
-     -- (353.8488, 687.2932);
-  \draw
-    (386.7731, 703.2932)
-     -- (418.7731, 687.2932);
-  \draw[ipe dash dashed]
-    (417.8488, 687.2932)
-     -- (449.8488, 671.2932)
-     -- (449.8488, 671.2932);
-
-  \draw
-    (449.8488, 671.2932)
-     -- (481.8488, 655.2932)
-     -- (481.8488, 655.2932);
-  \draw
-    (481.8488, 655.2932)
-     -- (449.8488, 639.2932)
-     -- (449.8488, 639.2932);
-  \draw[ipe dash dashed]
-    (449.8488, 639.2932)
-     -- (417.8488, 623.2932);
-  \draw
-    (417.8488, 623.2932)
-     -- (385.8488, 607.2932);
-  \pic
-     at (457.1756, 642.7929) {ipe disk};
-  \draw
-    (385.8488, 607.2932)
-     -- (353.8488, 591.2932)
-     -- (353.8488, 591.2932);
-  \pic
-     at (352.6103, 622.6521) {ipe disk};
-  \pic
-     at (353.9268, 590.7072) {ipe disk};
-  \pic
-     at (458.2826, 667.3311) {ipe cross};
-  \pic
-     at (459.207, 575.7344) {ipe cross};
-  \draw[-ipe linear]
-    (353.8488, 575.2932)
-     -- (513.8488, 575.2932);
-  \pic
-     at (353.8488, 575.2932) {ipe disk};
-  \pic
-     at (385.8488, 575.2932) {ipe cross};
-  \pic
-     at (475.7994, 575.2932) {ipe cross};
-  \pic
-     at (481.8488, 575.2932) {ipe cross};
-  \draw[shift={(472.741, 659.847)}, xscale=0.3271, yscale=-1.7893]
-    (0, 0)
-     -- (128, 0);
-  \draw
-    (481.8488, 655.2932)
-     -- (513.8488, 655.2932)
-     -- (513.8488, 655.2932);
-  \draw[shift={(459.26, 642.878)}, xscale=0.4834, yscale=0.4807]
-    (0, 0)
-     -- (112.236, -0.457);
-  \draw[red]
-    (482.3765, 654.0394) circle[radius=9.9987];
-  \draw
-    (354.8117, 621.686)
-     -- (386.2407, 606.8958);
-  \pic
-     at (386.2407, 606.8958) {ipe disk};
-  \pic
-     at (386.2407, 703.956) {ipe disk};
-  \draw[red]
-    (360.3506, 584.6012)
-     arc[start angle=160.4967, end angle=217.0656, x radius=120.4239, y radius=-143.3401];
-  \pic
-     at (473.9974, 650.6919) {ipe cross};
-  \pic
-     at (364.92, 693.131) {ipe cross};
-  \pic
-     at (372.3151, 710.6943) {ipe cross};
-  \pic
-     at (359.3737, 593.2977) {ipe cross};
-  \draw
-    (226.3225, 655.8881)
-     -- (258.6759, 665.1319);
-  \draw
-    (226.3225, 654.0394)
-     -- (258.6759, 646.6443);
-  \draw[-ipe linear]
-    (271.6173, 766.814)
-     -- (337.2485, 767.7384);
-
-  \pic
-     at (272.5417, 782.5285) {ipe disk};
-  \pic
-     at (271.6173, 815.8063) {ipe disk};
-  \draw
-    (305.8194, 798.2431)
-     -- (272.5417, 815.8063);
-  \draw
-    (305.8194, 798.2431)
-     -- (272.5417, 782.5285)
-     -- (272.5417, 782.5285);
-  \draw
-    (272.5417, 782.5285)
-     -- (336.3241, 782.5285);
-  \draw
-    (272.5417, 815.8063)
-     -- (336.3241, 814.8819);
-  \draw
-    (304.8951, 799.1674)
-     -- (335.3997, 799.1674);
-  \draw
-    (305.8194, 799.1674)
-     -- (336.3241, 804.7137);
-  \draw
-    (305.8194, 798.2431)
-     -- (335.3997, 792.6968);
-  \draw
-    (387.1651, 703.956)
-     -- (511.0324, 703.956)
-     -- (511.0324, 703.0316);
-  \draw
-    (388.0895, 605.0471)
-     -- (511.9568, 605.0471);
-  \pic
-     at (272.5417, 766.814) {ipe disk};
-  \draw[red]
-    (304.8951, 797.3187) circle[radius=35.9679];
-
-    \pic[fill=white]
-     at (225.8488, 655.2932) {ipe fdisk};
-
-     \pic[fill=white]
-     at (481.8488, 655.2932) {ipe fdisk};
-
-     \pic[fill=white]
-     at (304.8951, 799.1674) {ipe fdisk};
+\subsubsection{$\Dcal$ from $\widetilde\Dcal$}\label{subsection D from Dtilde} On $\widetilde\Dcal$ there is a tautological vector bundle arising from the modular description of $\widetilde\VZ_{1,\alpha}(\PP^N|H,d)$, namely:
+\begin{equation*} F = \OO(\delta)^{\oplus r}. \end{equation*}
+
+\begin{lemma}
+The fibre of $F$ over a moduli point can be identified with
+\begin{equation*} \left( \bigoplus_{i=1}^r \TT_{p_i} C_i^\prime \right) \otimes \TT_{C_0} \end{equation*}
+where $C_i^\prime$ is a component of $C_i$ which lies on the radius, $p_i$ is the adjacent node which points towards the core, and $\TT_{C_0}$ is the universal tangent line bundle.
+\end{lemma}
+
+\begin{proof}
+Choose a component $C_i^\prime$ of the curve which lies on the radius.
+Then $\OO(\delta)$ is equal to the tensor product of tangent line bundles along the path of edges connecting $C_i^\prime$ to the core.
+However, this tensor product of line bundles is telescoping: any vertex which appears in the middle of the path will have an incoming and outgoing node, and since the vertex corresponds to a smooth rational curve these tangent spaces are naturally dual to each other~\cite{VZ}.
+Standard manipulations lead to the result.
+
+%Note that the final term on the right hand side is not given by $\TT_{q_i} C_0$ (where $q_i$ is the appropriate splitting node) but rather the tangent space to the core. 
+\end{proof}
+
+We said that $C_i^\prime$ is \emph{a} component of $C_i$ which lies on the radius.
+There may be more than one, but if this is the case then their tangent spaces are naturally identified.
+We obtain a natural morphism
+\begin{equation*} \sum \operatorname{d}\!f \colon F(-\TT_{C_0}) \to \ev_q^\st \TT_H \end{equation*}
+given by summing the derivatives at \emph{all} the inward-pointing nodes on the radius.
+{\bf \color{red} What does this next part mean?} Now, over $\widetilde\Dcal$ there is a natural section of the projective bundle $\PP(F) \to \widetilde\Dcal$ (obtained by projectivising the diagonal embedding).
+If we therefore lift the above morphism to the projectivisation, we obtain a composition:
+\begin{equation*} \OO_{\PP(F)}(-1) \to \pi^\st F \to \pi^\st(\ev_q^\st \TT_H (\TT_{C_0})).\end{equation*}
+The vanishing locus of this section is given by an Euler class calculation on $\PP(F)$.
+In order to obtain $\Dcal$ we must then intersect this vanishing locus with $\OO_{\PP(F)}(1)$.
+%(which represents the natural section $\widetilde\Dcal \to \PP(F)$.
+
+Finally, we note that the class of $F$ {\bf \color{red} What class of $F$?} is computable in terms of data pulled back from the base. Consider the following bundle on $\Ecal$:
+\begin{equation*} E = \bigoplus_{i=1}^r \left( \TT_{q_i}C_i \otimes \TT_{q_i}C_0\right). \end{equation*}
+We may then identify $F$ with the pullback of $E$ twisted by the exceptional loci.
+
+{\bf \color{red} More needs to be said here.}
+
+The main features of the discussion above are visible in the following example, which brings out the interplay between logarithmic moduli and blow-ups.
+
+\begin{example}
+Consider the following ray $\tau$ and sublocus $\rho$:
+\begin{figure}[h]
+
+\begin{minipage}{0.3\textwidth}
+\centering
+\begin{tikzpicture}
+\draw [red] plot [smooth cycle] coordinates {(0,-2) (-0.5,-1) (0,0) (1,0.5) (3,-1) (1,-2.5)};
+
+\draw[fill=black] (0,0) circle[radius=2pt];
+\draw (0,0) node[above]{\small$\sqC_1$};
+\draw[fill=black] (0,0) -- (2,-1);
+\draw (1,-0.95) node[above]{\small$e_1$};
+\draw[color=blue] (1,-0.5) node[above]{\small$2$};
+
+\draw[fill=black] (0,-2) circle[radius=2pt];
+\draw (0,-2) node[above]{\small$\sqC_2$};
+
+\draw[->] (0,-2) -- (0,-2.5);
+\draw[color=blue] (0,-2.5) node[below]{\small$0$};
+
+\draw[fill=black] (0,-2) -- (2,-1);
+\draw (1,-2) node[above]{\small$e_2$};
+\draw[color=blue] (1,-1.5) node[above]{\small$2$};
+
+\draw[fill=black,->] (2,-1) -- (3.5,-1);
+\draw[color=blue] (2.35,-1) node[above]{\small$4$};
+
+\draw[fill=white] (2,-1) circle[radius=2pt];
+\draw (2,-1) node[below]{\small$\sqC_0$};
+
+\draw[color=blue,->] (2,-2) -- (2,-3);
+
+\draw[color=blue,->] (0,-3.5) -- (3,-3.5);
+\draw[fill=blue] (0,-3.5) circle[radius=2pt];
+\draw[fill=blue] (2,-3.5) circle[radius=2pt];
 \end{tikzpicture}
-\caption{Two degenerations of the combinatorial type above, which represents a ray.
-On the left-hand side, the alignment holds only generically.
-On the right-hand side, it is not enough to align each individual factor.}\label{fig:fwise_align}
+\caption{$\tau$}
+\end{minipage}\hfill
+\begin{minipage}{0.7\textwidth}
+\centering
+\begin{tikzpicture}
+\draw [red] plot [smooth cycle] coordinates {(-4,-2) (-2,-1) (-2,1) (0,1) (3,-1) (-1,-3.5)};
+
+\draw[fill=black] (0,0) circle[radius=2pt];
+\draw (0,0) node[above]{\small$\sqC_1^0$};
+\draw[fill=black] (0,0) -- (2,-1);
+\draw (1,-0.95) node[above]{\small$e_1$};
+\draw[color=blue] (1,-0.5) node[above]{\small$2$};
+
+\draw[fill=black] (0,-2) circle[radius=2pt];
+\draw (0,-2) node[above]{\small$\sqC_2^0$};
+\draw[fill=black] (0,-2) -- (2,-1);
+\draw (1,-2) node[above]{\small$e_2$};
+\draw[color=blue] (1,-1.5) node[above]{\small$2$};
+
+\draw[fill=black,->] (2,-1) -- (3.5,-1);
+\draw[color=blue] (2.35,-1) node[above]{\small$4$};
+
+\draw[fill=white] (2,-1) circle[radius=2pt];
+\draw (2,-1) node[below]{\small$\sqC_0$};
+
+\draw (-2,1) -- (0,0);
+\draw[fill=black] (-2,1) circle[radius=2pt];
+\draw (-2,1) node[above]{\small$\sqC_1^1$};
+\draw (-1,0.5) node[below]{\small$f_1$};
+\draw[color=blue] (-1,0.5) node[above]{\small$1$};
+
+\draw (-2,1) -- (-4,1);
+\draw[fill=black] (-4,1) circle[radius=2pt];
+\draw (-4,1) node[above]{\small$\sqC_1^3$};
+\draw (-3,1) node[below]{\small$g_1$};
+\draw[color=blue] (-3,1) node[above]{\small$1$};
+
+\draw (-2,-1) -- (0,0);
+\draw[fill=black] (-2,-1) circle[radius=2pt];
+\draw (-2,-1) node[above]{\small$\sqC_1^2$};
+\draw (-1,-0.5) node[below]{\small$f_2$};
+\draw[color=blue] (-1,-0.5) node[above]{\small$1$};
+
+\draw (-2,-1) -- (-4,-1);
+\draw[fill=black] (-4,-1) circle[radius=2pt];
+\draw (-4,-1) node[above]{\small$\sqC_1^4$};
+\draw (-3,-1) node[below]{\small$g_2$};
+\draw[color=blue] (-3,-1) node[above]{\small$1$};
+
+\draw (0,-2) -- (-2,-2);
+\draw[fill=black] (-2,-2) circle[radius=2pt];
+\draw (-2,-2) node[above]{\small$\sqC_2^1$};
+\draw (-1,-2) node[below]{\small$f_3$};
+\draw[color=blue] (-1,-2) node[above]{\small$2$};
+\draw[->] (-2,-2) -- (-2,-2.5);
+\draw[color=blue] (-2,-2.5) node[below]{\small$0$};
+
+\draw (-2,-2) -- (-4,-2);
+\draw[fill=black] (-4,-2) circle[radius=2pt];
+\draw (-4,-2) node[above]{\small$\sqC_2^2$};
+\draw (-3,-2) node[below]{\small$g_3$};
+\draw[color=blue] (-3,-2) node[above]{\small$2$};
+
+\draw[color=blue,->] (0,-2.5) -- (0,-3.5);
+
+\draw[color=blue,->] (-4,-4) -- (3,-4);
+\draw[fill=blue] (0,-4) circle[radius=2pt];
+\draw[fill=blue] (2,-4) circle[radius=2pt];
+\draw[fill=blue] (-2,-4) circle[radius=2pt];
+\draw[fill=blue] (-4,-4) circle[radius=2pt];
+\end{tikzpicture}
+\caption{$\rho$}
+\end{minipage}
 \end{figure}
 
-\subsubsection{The projective bundle}\label{subs:proj_bun} Generically on $\widetilde\Ecal$, the compactified torus bundle $\widetilde \Dcal\to \widetilde\Ecal$ coincides with the following projective bundle:
-\[\mathcal P=\PP_{\widetilde\Ecal}(\mathbb T_R\oplus\bigoplus_{j=k+1}^r \mathbb T_{q_j}R_j),\]
-where $\mathbb T_{q_j}R_J$ is the tangent line at the gluing marking closest to the core on the $j$-th factor of the product in the second line of \eqref{eq:product}.
-The open stratum in the fiber consists of moduli of attachments (i.e.
-moduli for the contraction to the Smyth's singularity); the compactification is by adding strictly semistable Gorenstein singularities as in \cite[\S\S 2.2-2.3]{SMY2}.
-In terms of alignment, a coordinate hyperplane corresponds to pushing the corresponding vertex off the circle, and destabilising the corresponding edge to the core.
-Tropically, the fibers can be analysed as follows: pushing some of the vertices off the circle creates new finite length edges with coordinates $\ell_j\in\RR_{\geq_0}$ (see Figure \ref{fig:off_we_go}); not all of them can be strictly positive, because the circle needs to pass through at least one vertex of positive horizontal degree.
-This is patently the fan of a projective space.
-
-\begin{figure}
-\begin{tikzpicture}[ipe import,scale=.8]
-  %\useasboundingbox (0, 0) rectangle (595, 842);
-  \draw
-    (64, 672)
-     -- (128, 688)
-     -- (64, 704)
-     -- (64, 704);
-  \draw
-    (128, 688)
-     -- (64, 736)
-     -- (64, 736);
-  \draw[red]
-    (128, 688) circle[radius=65.9697];
-  \draw
-    (128, 688)
-     -- (112, 752)
-     -- (64, 768)
-     -- (64, 768);
-  \draw
-    (112, 752)
-     -- (64, 784)
-     -- (64, 784);
-  \pic
-     at (64, 672) {ipe disk};
-  \pic
-     at (64, 704) {ipe disk};
-  \pic
-     at (64, 736) {ipe disk};
-  \pic
-     at (64, 768) {ipe disk};
-  \pic
-     at (64, 784) {ipe disk};
-  \pic
-     at (112, 752) {ipe cross};
-  \pic
-     at (75.2242, 727.582) {ipe cross};
-  \pic
-     at (112, 700) {ipe cross};
-  \pic
-     at (112, 692) {ipe cross};
-  \pic
-     at (112, 684) {ipe cross};
-  \pic
-     at (75.8121, 701.047) {ipe cross};
-  \pic
-     at (75.0704, 674.4388) {ipe cross};
-  \filldraw[fill=white]
-    (64, 608)
-     -- (208, 608)
-     -- (208, 608);
-  \pic
-     at (64, 608) {ipe disk};
-  \draw
-    (128, 688)
-     -- (208, 688)
-     -- (208, 688);
-  \pic
-     at (73.6978, 608.02) {ipe cross};
-  \pic
-     at (111.876, 608.0202) {ipe cross};
-  \pic
-     at (127.674, 608.0205) {ipe cross};
-  \pic[fill=white]
-     at (128, 688) {ipe fdisk};
-  \node[ipe node]
-     at (86.863, 690.301) {$m$};
-  \node[ipe node]
-     at (87.521, 671.212) {$m$};
-  \draw
-    (128, 688)
-     -- (91.4703, 741.643);
-  \draw
-    (128, 688)
-     -- (160.586, 745.593)
-     -- (160.586, 745.593);
-  \pic
-     at (91.4703, 741.643) {ipe disk};
-  \pic
-     at (160.486, 745.417) {ipe disk};
-  \draw[shift={(91.47, 741.051)}, xscale=0.95, yscale=0.6996]
-    (0, 0)
-     -- (-26.9879, 7.241)
-     -- (-26.9879, 7.241);
-  \draw
-    (160.486, 745.417)
-     -- (64.4824, 799.569);
-  \draw
-    (160.486, 745.417)
-     -- (208.637, 745.593);
-  \draw
-    (92.1286, 740.985)
-     -- (64.4824, 754.15);
-  \pic
-     at (64.4824, 746.909) {ipe disk};
-  \pic
-     at (64.4824, 798.91) {ipe disk};
-  \pic
-     at (64.4824, 753.492) {ipe disk};
-  \draw
-    (289.118, 672.0005)
-     -- (353.118, 688.0005)
-     -- (289.118, 704.0005)
-     -- (289.118, 704.0005);
-  \draw
-    (353.118, 688.0005)
-     -- (289.118, 736.0005)
-     -- (289.118, 736.0005);
-  \draw[red]
-    (353.118, 688.0005) circle[radius=65.9697];
-  \draw
-    (353.118, 688.0005)
-     -- (337.118, 752.0005)
-     -- (289.118, 768.0005)
-     -- (289.118, 768.0005);
-  \draw
-    (337.118, 752.0005)
-     -- (289.118, 784.0005)
-     -- (289.118, 784.0005);
-  \pic
-     at (289.118, 672.0005) {ipe disk};
-  \pic
-     at (289.118, 704.0005) {ipe disk};
-  \pic
-     at (289.118, 736.0005) {ipe disk};
-  \pic
-     at (289.118, 768.0005) {ipe disk};
-  \pic
-     at (289.118, 784.0005) {ipe disk};
-  \pic
-     at (337.118, 752.0005) {ipe cross};
-  \pic
-     at (300.3422, 727.5825) {ipe cross};
-  \pic
-     at (337.118, 700.0005) {ipe cross};
-  \pic
-     at (337.118, 692.0005) {ipe cross};
-  \pic
-     at (337.118, 684.0005) {ipe cross};
-  \pic
-     at (300.9301, 701.0475) {ipe cross};
-  \pic
-     at (300.1889, 674.4392) {ipe cross};
-  \filldraw[fill=white]
-    (289.118, 608.0005)
-     -- (433.118, 608.0005)
-     -- (433.118, 608.0005);
-  \pic
-     at (289.118, 608.0005) {ipe disk};
-  \draw
-    (353.118, 688.0005)
-     -- (433.118, 688.0005)
-     -- (433.118, 688.0005);
-  \pic
-     at (298.8158, 608.0205) {ipe cross};
-  \pic
-     at (336.994, 608.0207) {ipe cross};
-  \pic
-     at (352.792, 608.0209) {ipe cross};
-  \pic[fill=white]
-     at (353.118, 688.0005) {ipe fdisk};
-  \node[ipe node]
-     at (311.98, 690.301) {$m$};
-  \node[ipe node]
-     at (312.639, 671.212) {$m$};
-  \draw[shift={(353.118, 687.999)}, xscale=1.1287, yscale=1.1615]
-    (0, 0)
-     -- (-36.5297, 53.643);
-  \draw[shift={(353.119, 687.997)}, xscale=1.4269, yscale=1.3567]
-    (0, 0)
-     -- (32.586, 57.593)
-     -- (32.586, 57.593);
-  \pic
-     at (310.6643, 751.5171) {ipe disk};
-  \pic
-     at (400.086, 767.1394) {ipe disk};
-  \draw[shift={(311.745, 750.197)}, xscale=0.8205, yscale=-0.5452]
-    (0, 0)
-     -- (-26.9879, 7.241)
-     -- (-26.9879, 7.241);
-  \draw[shift={(399.543, 767.54)}, xscale=1.1319, yscale=0.5704]
-    (0, 0)
-     -- (-96.0036, 54.152);
-  \draw[shift={(400.744, 767.146)}, xscale=0.6446, yscale=-1.3688]
-    (0, 0)
-     -- (48.151, 0.176);
-  \draw[shift={(311.717, 751.113)}, xscale=0.8, yscale=0.1453]
-    (0, 0)
-     -- (-27.6462, 13.165);
-  \pic
-     at (289.6004, 746.9095) {ipe disk};
-  \pic
-     at (289.6004, 798.9105) {ipe disk};
-  \pic
-     at (289.6004, 753.4925) {ipe disk};
-  \pic
-     at (387.02, 744.935) {ipe cross};
-  \pic
-     at (317.246, 742.961) {ipe cross};
-  \node[ipe node]
-     at (315.273, 748.884) {$\ell_{j_1}$};
-  \node[ipe node]
-     at (397.553, 752.175) {$\ell_{j_2}$};
-\end{tikzpicture}
-\caption{Moving vertices off the circle creates new tropical parameters.}\label{fig:off_we_go}
-\end{figure}
-\end{comment}
-
-\subsubsection{From $\widetilde\Dcal$ to $\Dcal$} Let $F=\bigoplus_{v\in \{V_{0,\delta}\}\cup V_{>0,\delta}}\OO(\delta_v)$. On $\mathcal P$ we have a tautological sequence:
-\[\OO_{F}(-1)\hookrightarrow p^*(F)\xrightarrow{+\operatorname{d}f}\operatorname{ev}_E^*(TH),\]
-where $p\colon\mathcal P=\PP(F)\to\widetilde\Ecal$, and $+\operatorname{d}f$ should be interpreted as follows: for every $v\in \{V_{0,\delta}\}\cup V_{>0,\delta}$, as many copies of $\OO(\delta_v)$ are considered as there are components at distance $\delta$ from the core along the path $v$, and they are identified according to the preferred isomorphisms; then, the differential of the universal map to $\PP^N$ is applied to each tangent vector (possibly including some contracted rational bubbles on the path), and the sum of these contributions is taken in $T_{f(E)}\PP^N$ - it actually lies in $T_{f(E)}H$ because all the normal contributions can be assumed to be trivial by Lemma \ref{lem:m=1}.
-The composite, regarded as a section $s$ of $G=\OO_F(1)\otimes \operatorname{ev}_E^*(TH)$, vanishes precisely where $f$ factors through the Smyth's singularity determined by the point in the fiber of $p$.
-Generically on $\widetilde\Ecal$, this is exactly what we are after.
-On the boundary, though, it may happen that a simultaneous degeneration in the base and the fiber makes this factorisation trivial, in the sense that $\bar f$ would be constant on all the branches of the elliptic singularity.
-
-\begin{lemma}
- For every $V_B\subseteq V_\delta$ and $V_F=V_\delta\setminus V_B$, $s$ vanishes along the loci where the factors corresponding to $V_B$ in $\widetilde \Ecal$ degenerate so that $f_v\colon R_v\to\PP^N$ is constant in a neighbourhood of $q_v$, and the fiber coordinates $(\lambda_{v^\prime})_{v^\prime\in V_F}$ along $p\colon\mathcal P\to\widetilde \Ecal$ are set to be $0$.
-\end{lemma}
-Call these loci $\Xi_i,i\in I$ (compare with \cite[\S 3.2]{VZ} for an analogous phenomenon in the non-relative case); it is clear that they may be in excess with respect to the expected codimension of $V(s)$, that is $N-1$.
-These loci are logarithmic substrata; therefore, there exists a logarithmic blow-up that principalizes them.
-We claim that $\widetilde\Dcal$ is (possibly a refinement of) such a blow-up.
-\begin{lemma}
- The pullback of $\Xi_i$ is principal in $\widetilde\Dcal$.
-\end{lemma}
-\begin{proof}
- Let us analyse the ideal of $\Xi_i$: it is generated by
- \begin{enumerate}[leftmargin=.5 cm]
-  \item equations on $\widetilde\Ecal$ cutting the locus where $R_v$ degenerates so that $f_v$ is constant on a neighbourhood of $q_v$, $v\in V_B$: these correspond to the tropical functions $\delta_v-\operatorname{dist}(q_v,\circ)$;
-  \item equations on the fiber of $p$ for the linear subspace corresponding to $v\in V_F$: tropically, these correspond to the $\ell_v$ discussed above.
- \end{enumerate}
-By construction, on $\widetilde \Dcal$ it is always possible to tell which of these tropical lengths is the shortest (the circle we have drawn on $\Xi$ is degenerate - it passes through no vertex of positive horizontal degree -, therefore we need to decide for a strictly larger circle in order to lift to $\widetilde D$), which corresponds to principalising the ideal (see Figure \ref{fig:principalisation}).
-\end{proof}
-
-\begin{figure}
-\includegraphics[scale=.5]{principalisation}
-\caption{On the left, a generic point of $\mathcal P$.
-On the right, a point of $\Xi$.
-The dotted circle is the one we draw on $\mathcal P$.
-The continuous circle represents one of the possible choices of $\delta$ enlarging the dotted one (a stratum of $\widetilde\Dcal$).}\label{fig:principalisation}
-\end{figure}
-
-Finally, on $\widetilde\Dcal$ (or, in fact, on an intermediate blow-up $\widetilde{\mathcal P}\to\mathcal P$) there are exceptional divisors $\widetilde \Xi_i$ corresponding to $\Xi_i$ in $\mathcal P$.
-Since the $\Xi_i$ exhaust all the excess-dimensional components of the vanishing locus of $s\in\Gamma(\mathcal P,G)$, the latter induces a section $\tilde s\in\Gamma(\widetilde\Dcal,G(-\sum_i\widetilde\Xi_i))$ by pullback and twisting, whose vanishing locus is dimensionally transverse to the boundary, and whose open part coincides with the generic point of $\Dcal$, therefore $V(\tilde s)=\Dcal$.
-
-Notice that, expressing the pushforward of the Chern classes of $\OO_F(1)$ and $\OO(\widetilde\Xi_i)$ in terms of tautological classes on the fiber product underlying $\Ecal$, we get:
-\begin{cor}
- After pushforward to $\Ecal$, the contribution of $\Dcal$ to the invariants can be computed in terms of tautological integrals on moduli spaces of maps with lower numerics.
-\end{cor}
-\begin{comment}
-\subsubsection{Factorisation} Assume $m\geq 2$. Over $\mathcal P$ we have a tautological sequence:
-\[\OO_{F}(-1)\hookrightarrow p^*(F)\xrightarrow{+\operatorname{d}f}\operatorname{ev}_E^*(TH),\]
-where $p\colon\mathcal P=\PP(F)\to\widetilde\Ecal$, and $+\operatorname{d}f$ should be interpreted as follows: $k$ copies of $\mathbb T_R$ are taken to account - via the preferred isomorphisms - for all factors of the first product in \eqref{eq:product}; then, the differential of the universal map to $\PP^N$ is applied to each tangent vector (possibly including some of the contracted rational bubbles in the boundary), and the sum of these contributions is taken in $T_{f(E)}\PP^N$ - it actually lies in $T_{f(E)}H$ because all the normal contributions are trivial by assumption.
-The composition is a section $s$ of $G=\OO_F(1)\otimes \operatorname{ev}_E^*(TH)$, and it vanishes precisely where $f$ factors through the Smyth's singularity determined by the point in the fiber of $p$.
-Generically on $\widetilde\Ecal$, this is exactly what we are after.
-
-\subsubsection{Dimensional transversality} In general, the vanishing locus of $s$ corresponds to maps $f\colon C\to\PP^N$ and diagrams $C\leftarrow \tilde C\to \bar C$ - with $\bar C$ the elliptic $r$-fold point determined by the position in the fiber of $p\colon\mathcal P\to\widetilde \Ecal$ - such that $f$ factors through $\bar C$.
-When the curve is allowed to degenerate (so, on the boundary of $\widetilde \Ecal$), this is not always what we want: indeed, due do the combined action of degeneration (in the base direction) and destabilisation (in the fiber direction), it may very well be that $f$ is constant along every component of the elliptic singularity, so that it factors trivially; in other words, the vanishing locus of $s$ is not dimensionally transverse to the boundary of $\mathcal P$.
-\begin{lemma}
- For every $K\subseteq\{1,\ldots,r\}$ and $K^c=\{1,\ldots,r\}\setminus K$, $s$ vanishes along the loci where the factors corresponding to $K$ in $\widetilde \Ecal$ degenerate so that $f_k\colon R_k\to\PP^N$ is constant in a neighbourhood of $q_k$, and the fiber coordinates $(\lambda_{h})_{h\in K^c}$ along $p\colon\mathcal P\to\widetilde \Ecal$ are set to be $0$.
-\end{lemma}
-Call these loci $\Delta_i,i\in I$. See \cite[\S 3.2]{VZ} for a treatment of the analogous situation in the non-relative case; the study of the normal bundles is also dealt with there.
-
-It is clear that these loci are logarithmic substrata; therefore, there exists a logarithmic blow-up that principalizes them.
-We claim that $\widetilde\Dcal$ is (possibly a refinement of) this blow-up.
-This follows from the tropical discussion in Section \ref{subs:proj_bun}, and the fact that the degenerate circle that we are drawing on the $\Delta_i$ falls in the strict interior of the circle of radius $\delta$ on $\widetilde\Dcal$ (because the former only passes through vertices of horizontal degree $0$), thus all the distances from the vertices to the former circle are ordered.
-See Figure \ref{fig:principalisation} above.
-\begin{figure}
-\begin{tikzpicture}[ipe import]
-  %\useasboundingbox (0, 0) rectangle (595, 842);
-  \draw
-    (64, 720)
-     -- (112, 736)
-     -- (96, 752);
-  \draw[->]
-    (64, 704)
-     -- (128, 704);
-  \pic
-     at (64, 704) {ipe disk};
-  \pic
-     at (64, 720) {ipe disk};
-  \pic
-     at (96, 752) {ipe disk};
-  \draw[red, dotted]
-    (60.6969, 708.808)
-     arc[start angle=-161.5651, end angle=-71.5651, x radius=53.2078, y radius=-65.2105];
-  \pic[fill=white]
-     at (112, 736) {ipe fdisk};
-  \draw
-    (192, 720)
-     -- (240, 736)
-     -- (224, 752);
-  \draw[->]
-    (192, 704)
-     -- (256, 704);
-  \pic
-     at (192, 704) {ipe disk};
-  \pic
-     at (192, 720) {ipe disk};
-  \pic
-     at (224, 752) {ipe disk};
-  \pic[fill=white]
-     at (240, 736) {ipe fdisk};
-  \draw
-    (112, 736)
-     -- (128, 736);
-  \draw
-    (240, 736)
-     -- (256, 736);
-  \draw
-    (208.6374, 743.6181)
-     -- (224.4352, 750.8588);
-  \draw
-    (208.6374, 758.7577)
-     -- (225.0934, 751.517);
-  \pic
-     at (207.9791, 742.9599) {ipe disk};
-  \pic
-     at (207.9791, 758.7577) {ipe disk};
-  \pic
-     at (208, 704) {ipe cross};
-  \pic
-     at (224, 704) {ipe cross};
-  \pic
-     at (240, 704) {ipe cross};
-  \pic
-     at (96, 704) {ipe cross};
-  \pic
-     at (112, 704) {ipe cross};
-  \draw[red, dotted]
-    (231.0126, 755.9018)
-     { [rotate=-17.595] arc[start angle=135, end angle=225, x radius=21.7093, y radius=22.6274] };
-  \draw[red]
-    (188.9249, 712.0225)
-     arc[start angle=-156.5092, end angle=-115.3692, x radius=85.088, y radius=-96.462];
-\end{tikzpicture}
-\caption{On the left, a generic point of $\mathcal P$.
-On the right, a point $\Delta$.
-The dotted circle is what we have on $\mathcal P$.
-The continuous circle is the one of radius $\delta$ on $\widetilde\Dcal$; this principalises the degeneration.}\label{fig:principalisation}
-\end{figure}
-
-Finally, on $\widetilde\Dcal$ there are exceptional divisors $\widetilde \Delta_i$ corresponding to $\Delta_i$ in $\mathcal P$.
-By the preceding analysis, $s\in\Gamma(\mathcal P,G)$ induces a section $\tilde s\in\Gamma(\widetilde\Dcal,G(-\sum_i\widetilde\Delta_i))$ by pullback, whose vanishing locus is dimensionally transverse to the boundary, and whose open part coincides with the generic point of $\Dcal$, therefore $V(\tilde s)=\Dcal$.
-
-\subsection{Tautological contributions} Expressing the pushforward of the Chern classes of $\OO_F(1)$ and $\OO(\widetilde\Delta_i)$ in terms of tautological classes on the fiber product underlying $\Ecal$, get:
-\begin{cor}
- After pushforward to $\Ecal$, the contribution of $\Dcal$ to the invariants can be computed in terms of tautological integrals on moduli spaces of maps with lower numerics.
-\end{cor}
-\end{comment}
-
-\newpage
-
-\begin{lem} The logarithmic modification $\psi$ restricts to a birational map:
-\begin{equation*}\VZ^{\operatorname{punct}}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(H,d) \to \ol\Mcal^{\operatorname{punct},\circ}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(H,d).\end{equation*}
-\end{lem}
-Note that the latter space (the main component of the moduli space of punctured maps) is birational to the main component of the double ramification locus.
-In Lemma \ref{Lemma forget marking} below we explain how to compute integrals over this.cd
-\begin{proof}
-If it is true, we might be able to prove it via deformation theory.
-For this it might be useful to notice that there is a morphism $\Mpunct{g}{\alpha}{H}{d}\to \Mpunct{g}{\alpha}{\PP^N}{d}$ (because $H\subseteq\PP^N$ is strict), which is probably a closed immersion, and the loci with smooth source curve are isomorphic under this map.
-It seems plausible that the main omponent is log smooth over $B\Gm\subseteq[\Aaff^1/\Gm]$ (or the standard logarithmic point).
-\end{proof}
-
-%We probably want the latter statement to hold under imposing alignment and factorisation (keeping the log structure on the source curve, but forgetting that the map is log).
-Integrals over the main component of the double ramification locus can be computed using the following lemma.
-\begin{lem} \label{Lemma forget marking}The morphism which forgets a marking
-\begin{equation*} \fgt_i\colon\ol\Mcal_{1,n}^{\alpha,\circ}(H,d)\to\ol\Mcal^{\circ}_{1,n-1}(H,d)\end{equation*}
-is generically finite, of degree $\alpha_i^2$ (except in one special case, described in the proof).
-\end{lem}
-\begin{proof}
- Let us consider the case $d=0$ first.
-We may assume the source curve is smooth elliptic $E$.
-The map \[ \phi\colon E\to \Pic^0(E),\qquad x\mapsto\OO_E\left(\alpha_ix+\sum_{j=1,\ldots,\hat i\ldots,n}\alpha_jp_j\right)\]
- is an isogeny of degree $\alpha_i^2$.
-The locus of $(C,p_1,\ldots,\hat{p_i},\ldots,p_n)$ such that the kernel of $\phi$ contains one of the points $\{p_1,\ldots,\hat{p_i},\ldots,p_n\}$ is itself a double ramification locus inside $\oM_{1,n}$, hence non-generic - with one exception: namely, when $n=2$, $x=p_1$ is always a solution, but the curve lying above such point bubbles off a $\PP^1$.
-To see that it does not belong to the closure of the nice locus, notice that the rational function trivialising $\OO_C(\alpha_1p_1-\alpha_2p_2)$ should descend to the cusp, thus having a ramification point at the node; yet its ramification profile is determined by Riemann-Hurwitz, and it is entirely supported on $p_1$ and $p_2$.
-
- For a different proof: notice that we should obtain the class of the main component from the full double ramification cycle by subtracting the boundary class $[D_{1,\emptyset|0,\{1,\ldots,n\}}]$.
-The latter pushes forward to $0$ under $\fgt_i$, unless $n=2$.
-Therefore we may apply $\fgt_{i,*}$ to the Hain-Pixton formula:
- \[DR_1(A)=\frac{1}{2}\left(\sum_{i=1}^na_i^2\psi_i-\sum_{\substack{I\subseteq\{1,\ldots,n\}\\|I|\geq 2}}a_I^2[D_{1,I^c|0,I}]-\frac{1}{12}\delta_0\right),\]
- where $a_I=\sum_{i\in I}a_i$ and $\delta_0=\operatorname{glue}_*([\oM_{0,n+2}])$.
-From $\psi_j=\fgt_i^\st\psi_j+[D_{i,j}]$ for $i\neq j$, and the dilaton equation, we see that $\fgt_{i,*}\psi_j=1$ and $\fgt_{i,*}\psi_i=n-1$.
-On the other hand, the only surviving boundary classes are $[D_{i,j}]$, and they push down to $1$.
-Hence the formula pushes down to $\frac{1}{2}\left(\sum_{j\neq i}\alpha_j^2+(n-1)\alpha_i^2-\sum_{j\neq i}(\alpha_j+\alpha_i)^2\right)=-\alpha_i\left(\sum_{j\neq i}\alpha_j\right)=\alpha_i^2.$
-\end{proof}
-
-\newpage
-
-\begin{definition} A combinatorial type $\Delta$ of a tropical curve consists of the following data:
-\begin{enumerate}
-\item $G$ a finite graph, with a set $V(G)$ of vertices, a set $F(G)$ of flags and an involution $\iota \colon F(G) \to F(G)$ with $\iota^2=\Id$.
-We let $L(G)$ denote the fixed set of $\iota$, and think of its elements as infinite legs; we let $E(G)$ denote the set of equivalence classes of elements not fixed by $\iota$, and think of them as finite edges connecting two (possibly equal) vertices of $G$;
-\item a genus assignment $g \colon V(G) \to \Z_{\geq 0}$;
-\item a degree assignment $\deg \colon V(G) \to \Z_{\geq 0}$;
-\item a weight assignment $u \colon F(G)  \to \Z$ such that for every edge $e \in E(G)$ we have $u(f_1)=-u(f_2)$ where $e=[f_1]=[f_2]$, and $u(l) \geq 0$ for any $l \in L(G)$;
-\end{enumerate}
-\end{definition}
-
-\footnote{(Luca) to be made homogeneous with what comes earlier} Review here the process of gluing for punctured maps.
-In particular the basic monoid should be modified in order to make the relevant evaluations log morphisms.
-Claim: evaluations are strict.
-Consequence: the fiber product in the category of log stacks is fine.
-We have then to apply saturation.
-This is a finite morphism of degree...
-(I think it could be $\frac{\prod m^{(i)}}{lcm(m^{(i)})}$).
-
-\begin{lemma}[Virtual pushforward] The following hold.
- \begin{itemize}
-  \item $\fgt_*[\M{0}{\alpha}{\PP^N|H}{d}]=[\MG{0}{\alpha}{\PP^N|H}{d}]$ (follows from \cite{GathmannThesis,AbramovichMarcusWiseComparison}).
-  \item $\fgt_*[\VZc{1}{\alpha}{\PP^N|H}{d}]$ computes the reduced relative invariants by definition.
-  \item $\fgt_*[\M{0}{\mu}{H}{d_0}^\sim]=[\M{0}{\lvert\mu\rvert}{H}{d_0}]$ (follows from \cite{GathmannThesis} and... comparison of punctured with rubber invariants).
-  \item $\fgt_*[\VZc{1}{\mu}{H}{d_0}^\sim]$ here we should need a variation on Pixton's DRC formula; hopefully it's enough to avoid the graphs that tropical well-spacedness discards.
- \end{itemize}
-\end{lemma}
-
-\subsection{Recursive description of the divisors: type $C_0$} Consider now a combinatorial type $\Delta$ such that the circuit is contracted into the divisor.
-The corresponding stratum $\Dcal_\Mcal \subseteq \Mcal$ is contained in the blown-up locus.
-Our task is to identify the logarithmic divisors in the preimage of $\Dcal_\Mcal$ under the map $\VZ \to \Mcal$.
-As discussed, these are indexed by choices of ray in the subdivision of the tropical moduli space.
-Suppose we have fixed such data.
-
-\begin{claim} The teeth of the comb can break at most once, along the circuit.\end{claim}
-
-\begin{proof} If not there would be more parameters in the tropical moduli space. \end{proof}
-
-\begin{prop} Let $\Delta$ be a combinatorial type as above. Then:
-\begin{enumerate}
-\item the circuit is a single vertex, and is mapped to the interior $\RR_{>0} \subseteq \RR_{\geq 0}$;
-\item the degree of the circuit is zero;
-\item there is a vertex which is adjacent to the circuit and mapped to the interior $0 \in \RR_{\geq 0}$;
-\item let $e \in E(\sqC)$ be an edge which is adjacent to the circuit, and such that $u(e)$ is maximal among the edges adjacent to the circuit.
-Then the other vertex $v$ contained in $e$ is mapped to $0 \in \RR_{\geq 0}$, and $v$ lies on the (absolute) radius;
-\item if $v \in V(\sqC)$ and $\lambda(v) > \delta$ then $f(v)=0$.
-\end{enumerate}
-\end{prop}
-
-On the other hand, when there is a contracted elliptic subcurve - and it will be contracted into the hyperplane, because otherwise it wouldn't be generic, by density of the nice locus in $\VZ_{1,\alpha^\prime}(\PP^N|H,d^\prime)$ - the picture becomes more complicated due to the alignment.
-The combs may break.
-We label these loci $\mathcal{Y}_C^0$.
-\begin{figure}
-
- \tikz{
- \draw[red] (2,0) circle(2); %circle
- \draw (0,0) circle(2pt)[fill=black] (0,2) circle(2pt)[fill=black] (0,4) circle(2pt)[fill=black] (0,6) circle(2pt)[fill=black] (0,-2) circle(2pt)[fill=black] (1.1,1.78) circle(2pt)[fill=black] (3.42,1.42) circle(2pt)[fill=black] (.58,-1.42) circle(2pt)[fill=black] (0,1) circle(2pt)[fill=black]; %black vertices
- \draw (2,0) -- node[above]{4} (0,0) (2,0) --node[above]{2} (1.1,1.78) --node[above]{1} (0,2) (1.1,1.78) --node[above]{1} (0,4) (2,0) --node[above]{1} (3.42,1.42) (2,0) --node[above]{3} (.58,-1.42) (3.42,1.42) --node[above]{5} (0,6) (.58,-1.42) --node[above]{1} (0,-2) (2,0) -- node[above]{2} (0,1); %edges
- \draw (.58,-1.42) -- (5,-1.42) node[right]{1} (3.42,1.42) -- (5,1.42) node[right]{2} (2,0) -- (5,.5) node[right]{3} (2,0) -- (5,-.5) node[right]{7}; %markings
- \draw (2,0) circle(2pt)[fill=white]; %core
- \draw[->] (0,-3) circle(2pt)[fill=black] edge (5,-3); %trop(P^N|H)
- }
-
- \caption{The degrees can be figured out from the balancing equation.}
-\end{figure}
-
-In the following we describe the rays of the tropical moduli space.
-\begin{lem}
- A one-parameter tropical map $\phi$ to $\mathbb R_{\geq 0}$ is a decorated tree (with expansion factors - \emph{contact orders} - along edges and legs, and degrees on vertices, satisfying the balancing condition) with a circle (of radius $\delta$) around the root (sometimes called the \emph{core} and denoted by $\circ$) satisfying:
- \begin{enumerate}
- \item the circle of radius $\delta$ passes through at least one vertex of $\phi^{-1}(0)$ - which necessarily has positive degree - call $m$ its contact order with $H$;
- \item teeth may break only when they intersect the circle of radius $\delta$; in particular, $\circ$ is the only vertex contained in its strict interior, and every edge heading out from the circle goes directly to a vertex of $\phi^{-1}(0)$;
- \item every tooth that starts with contact order $m$ goes directly to a vertex of $\operatorname{circle}(\circ,\delta)\cap\phi^{-1}(0)$, and every other tooth starts with contact order $<m$ (possibly negative).
- \end{enumerate}
-\end{lem}
-\begin{proof}
- Otherwise there would be more than one parameters.
-\end{proof}
-
-\begin{remark}
- The core being contracted in the fiber of the tropical map is not a phenomenon that we should worry about in codimension one.
-Indeed, assume that the core is contracted in the fiber along a ray.
-Then all the edges departing from the core have expansion factor $0$; call the corresponding coordinates $U=\{u_i\}_{i\in I}$.
-Call the remaining coordinates $E=\{e_j\}_{j\in J}$.
-Note that tropical continuity involves only $E$.
-Alignments on the other hand assume the form $\lambda(v)=\lambda(v^\prime)$, where $\lambda(v)=\sum_{i\in I(v)}u_i\sum_{j\in J(v)}e_j$.
-Pick the shortest elements of $U$; then these can be shortened to zero without affecting the rest (by hypothesis, alignments can only identify them among themselves).
-This shows that we could not have started with a ray.
-\end{remark}
-
-\begin{ex}
- We look at the following example in some detail.
- \begin{figure}[h]
-  \tikz{
-  \draw (0,1) circle(2pt)[fill=black] --node[above]{2} (2,0);
-  \draw (0,-1) circle(2pt)[fill=black] --node[above]{2} (2,0);
-  \draw (2,0) -- (2.5,0) node[right]{4};
-  \draw (2,0)  circle(2pt)[fill=white];
-  \draw (0,1) -- (.33,1.33) node[above right]{0};
-  \draw (0,-1) -- (.33,-1.33) node[below right]{0};
-  \draw[red] (2,0) circle(2.23);
-  \draw[->] (0,-2.5)node[left]{0} circle(2pt)[fill=black] edge (4,-2.5);
-  }
- \end{figure}
- The ambient space is $\VZc{1}{(4,0,0)}{\PP^N|H}{4}$, of dimension $4N+3$.
-The underlying moduli space is $X=\M{0}{(2,0)}{\PP^N|H}{2}\times_H\M{0}{(2,0)}{\PP^N|H}{2}\times\VZ_{1,(-2,-2,4)}$ of dimension $5N+1$.
-Consider the fiber product:
- \bcd
- F\ar[r]\ar[d]& \M{0}{(2,0)}{\PP^N|H}{2}\times\M{0}{(2,0)}{\PP^N|H}{2}\ar[d]\\
- H\ar[r] & H\times H
- \ecd
- At the level of ghost sheaves, $\oM_F=\mathbb N\oplus_{\mathbb N^2}\oM_1^{\rm{enl}}\oplus\oM_2^{\rm{enl}}$, where the map $\mathbb N^2\to\mathbb N$ is the sum, and the map $\mathbb N^2\to\oM_1^{\rm{enl}}\oplus\oM_2^{\rm{enl}}$ generically is multiplication by $2$, so $\oM_F=\mathbb N^2/(2e=2f)$ generically.
-Saturation gives a finite cover $G\to F$ with $\oM_G=\mathbb N_{e=f}$ generically.
-Lifting this to actual log structures, what we are doing (again generically) is taking a square root of the isomorphism $T_{R_1,q_1}^{\otimes 2}\simeq T_{R_2,q_2}^{\otimes 2}$, which is obtained passing through $N_{H/\PP^N,f(Z)}$ via $\operatorname{d}f_{|R_i,q_i}$.
-This breaks when $f_{|R_i}$ is not tangent to $H$ of order exactly $2$ at $q_i$, for either $i$; but by the maximality assumption this happens precisely along Gathmann's comb loci $\Delta_i$.
-So in fact, rather than with $T_{R_i,q_i}^{\otimes 2}$, we should be working with $T_{R_i,q_i}^{\otimes 2}(-\Delta_i)$: but this is exactly $\ev_i^\st(-H)$ by Gathmann's genus zero formula, and the isomorphism $\ev_1^\st(H)=\ev_2^\st(H)$ holds on all of $F$.
-
- On the other hand, generically on $\VZ_{1,(-2,-2,4)}$ we have $T_{q_1}Z\simeq T_{q_2}Z$ by exploiting the group structure on the elliptic curve.
-This breaks when either (but not both) is on a rational tail.
-Yet we have $T_{q_1}Z(\Delta_{1\in P})\simeq T_{q_2}Z(\Delta_{2\in P})$ by Vakil-Zinger's construction of a universal $\psi$-class (i.e.
-by comparing both with $\pi_*\omega(\Delta)$; notice that our further blow-up has the only effect of twisting \emph{all} the relevant line bundles by $\Delta_{1,2\notin P}$).
-
- Now, the fiber of the Vakil-Zinger blow-up over $X$ can be described as follows. Generically it looks like \[\PP(T_{q_1}R_1\otimes T_{q_1}Z\oplus T_{q_2}R_2\otimes T_{q_2}Z)\]
- but this has to be modified along the boundary:
- \begin{itemize}
-  \item this has to do with the fact that the normal bundle of the strict transform is the pullback of the normal bundle twisted by the intersection with the exceptional divisor (so it relates with previous steps of the blow-up);
-  \item it is not globally a $\PP^1$-bundle (so it relates with further stages of the blow-up; it also has to do with a choice of compactification for the moduli space of attachments);
-  \item it has the effect of replacing $T_{q_i}Z$ with Vakil-Zinger's universal $\mathbb T$, so that this can be factored out of the projective bundle, and in fact we are left with a projective bundle $\mathbb P=\PP(T_{q_1}R_1\oplus T_{q_2}R_2)$ over $F$, and its open part $\operatorname{Iso}(T_{q_1}R_1\oplus T_{q_2}R_2)$ represents the attachment data for a contraction to a tacnode $R_1\sqcup_q R_2\to\bar{C}$.
- \end{itemize}
-On $\PP$ there is a natural vector bundle map \[s\colon \OO_{\PP}(-1)\hookrightarrow p^\st(T_{q_1}R_1\oplus T_{q_2}R_2)\xrightarrow{+\operatorname{d}f}\ev_q^\st T\PP^N\]
-that vanishes along the locus where $f$ descends to $\bar C$. In general, it is not a transversal section:
-\begin{itemize}
- \item we should replace $T\PP^N$ by $TH$ as long as all the $m^{(i)}$ are $\geq2$;
- \item Vakil and Zinger construct a blow-up of $\PP$ along the vanishing loci of $s$ of low codimension, and twist $s$ by the exceptional divisors, so that it becomes a transverse section $\tilde{s}$.
-\end{itemize}
-On the other hand, the finite cover $G\to F$ factors through $\PP$, because the two vertices are already aligned on $G$.
-We claim that the boundary locus of $\VZc{1}{(4,0,0)}{\PP^N|H}{4}$ corresponding to the combinatorial type of the tropical map above is the transverse intersection
-\[\left(G\cap V(\tilde{s})\subseteq\PP\right)\times\VZ_{1,(-2,-2,4)}.\]
-This has the expected dimension (codimension $N-1$ with respect to $X$).
-To compute its class, we can pull $\PP$ back to $G$, and then notice that $G\hookrightarrow\PP_G$ is the inclusion of a (trivial) subbundle.
-\begin{lem}
- The class of $\PP(\mathcal F)\subseteq\PP(\mathcal E)$ is $c_{\rm{top}}(\OO_\mathcal{E}(1)\otimes p^\st(\mathcal{E}/\mathcal{F}))$.
-\end{lem}
-See \cite[Prop.
-9.13]{EH3264}.
-It is a good time to remember that $\mathcal E$ was in fact $(\bigoplus_{i=1}^rTR_{i,q_i})\otimes\mathbb T$.
-By writing $c$ for $c_1(\OO_\mathcal{E}(1))$, $\psi_i$ for $c_1(T^\st R_{i,q_i})$, $\psi_Z$ for Vakil-Zinger's universal psi class, and $H$ for $\ev_q^\st H$, we need to compute
+\noindent On the cone $\rho$ we have the following tropical equations
 \begin{align*}
-p_*\left((c-\psi_1-\psi_2-2\psi_Z)[(1+c+H)^N(1+c)^{-1}]_{N-1}\right)= \\
-p_*\left((c-\psi_1-\psi_2-2\psi_Z)(\sum_{k=0}^{N-1}\binom{N}{1+k}c^kH^{N-1-k})\right)=\\
-\sum_{k=0}^{N-1}\binom{N}{k}H^{N-1-k}\big(s_k(\mathcal E)-s_{k-1}(\mathcal E)(\psi_1+\psi_2+\psi_Z)\big)
+e:=e_1 = e_2 \\
+f:=f_1 = f_2 = 2f_3 \\
+g:=g_1 = g_2 = 2g_3
 \end{align*}
-\end{ex}
-
-We now generalise this picture.
-Recall that the map $C\to\bar C$ is given by a (generic) line in the sum of the tangent spaces to the rational tails at the nodes that join them to the contracted curve of genus one.
-This is equivalent to an alignment, and it is parametrised by an open subset of a projective bundle over the moduli space for the tails corresponding to vertices of the dual graph lying on the circle of radius $\delta$.
-Yet, notice that those vertices lying in $\phi^{-1}(0)$ are already aligned among themselves.
-This is why we find it convenient to distinguish among four groups of vertices:
-\begin{enumerate}
- \item the core;
- \item\label{specialvertices} vertices on $\phi^{-1}(0)\cap\operatorname{circle}(\circ,\delta)$;
- \item vertices on $\operatorname{circle}(\circ,\delta)\setminus\phi^{-1}(0)$;
- \item\label{boringvertices} vertices on $\phi^{-1}(0)\setminus\operatorname{circle}(\circ,\delta)$.
-\end{enumerate}
-We shall first argue that gluing of log maps can be performed separately for the exterior and interior of the circle (the analogous classical picture is that, since the core is contracted, this moduli space is the product of a genus one curve, and a fiber product of genus zero maps under evaluation morphisms).
-
-\begin{lem}
- $\VZ^{\operatorname{punct}}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(H,0)\simeq \VZ^{\operatorname{punct}}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(\Spec(k\oplus\mathbb N))\times H$.\footnote{(Luca) check log structure, could be fibered over std log point}
-\end{lem}
-
-Let us now deal with vertices of type \ref{specialvertices}.
-\begin{lem}
- Consider the following fiber product in the category of fs log stacks:
- \bcd
- F\ar[d]\ar[r] & \prod_{i=1}^r\M{0}{\alpha^{(i)}\cup\{ m\}}{\PP^N|H}{d_i}\ar[d,"\ev_{q_i}"]\\
- H\ar[r] & H^r
- \ecd
- On $F$ there is a canonical isomorphism $\mathbb L_{q_i}\cong\mathbb L_{q_j}$\footnote{(Luca) check how it degenerates}, the latter being the cotangent line bundles at the gluing markings on two different components $i$ and $j$.
-Furthermore, $\underline F$ is a finite cover of degree $m^{r-1}$ of the fiber product of the underlying stacks.
-\end{lem}
-\begin{proof}
- Recall that each $\M{0}{\alpha^{(i)}\cup\{ m\}}{\PP^N|H}{d_i}$ is endowed with the log structure induced by pulling back along $q_i$ the divisorial log structure of the universal curve at the image of $q_i$ itself.
-Thus $\ev_{q_i}$ is made into a log morphism to $H$ with its induced DF(1) log structure.
-We claim that the subtext of such morphism is Gathmann's formula; namely, the log morphism to $H$ corresponds to an isomorphism betwee $\ev_{q_i}^\st\OO_H(-H)$ on one side, and $\mathcal I_{D_i}\otimes\mathbb L_{q_i}^m$ on the other, where $\mathcal I_{D_i}$ is the ideal sheaf of the union of the comb loci $D_i$ in $\M{0}{\alpha^{(i)}\cup\{ m\}}{\PP^N|H}{d_i}$.
-
- On the fiber product there is a canonical isomorphism between $\ev_{q_i}^\st H$ and $\ev_{q_j}^\st H$.
-
- Say something about integrality.
-
- Saturation is a local operation, as much as computing the degree, hence we can concentrate on the dense open locus where all the curves we are gluing are smooth, and they are not mapped entirely into $H$.
-There the minimal log structure on $\M{0}{\alpha^{(i)}\cup\{ m\}}{\PP^N|H}{d_i}$ is trivial, therefore the isomorphism between $\ev_{q_i}^\st H$ and $\ev_{q_j}^\st H$ translates into an isomorphism $\mathbb L_{q_i}^m\cong \mathbb L_{q_j}^m$.
-The saturation $F$ is obtained by taking an $m$-th root of this isomorphism.
-\end{proof}
-Let us denote by $\mathbb L_F$ the universal cotangent line at $q$.
-
-The projective bundle we are seeking has base
-\[\mathcal X=\left(F\times \prod_{i=1}^s\oM_{0,\tilde\alpha^{(i)}\cup\{m_i\}}^{\rm{punct}}(H,\tilde d_i)\right)\times_{H^{s+1}}H\]
-(with $m_i<m$) and it is \[\PP=\Proj_{\mathcal X}\left(\mathbb T_F\oplus\bigoplus_{i=1}^s\mathbb T_{\tilde q_i}\right).\]
-We are interested in the vanishing locus of the section
-\[s\colon\OO_{\PP}(-1)\hookrightarrow p^\st\left(\mathbb T_F\oplus\bigoplus_{i=1}^s\mathbb T_{\tilde q_i}\right)\xrightarrow{+df_q} f^\st(\operatorname{T}\PP^N)_q,\]
-because it represents the geometric condition that $f\colon C\to \PP^N$ factors through the normalisation map $C\to\bar C$ prescribed by the given point of $\PP$.
-As is, $s$ is not transverse to the zero section.
-First of all, unless $m=1$, $\operatorname{T}\PP^N$ can be replaced by $\operatorname{T}H$ in the definition of $s$ above, because the projection of all $\operatorname{d}f_i(\operatorname{T}_{q_i}R_i)$ to $N_{H/\PP^N}$ is zero.
-The case $m=1$ has to be dealt with separately and it turns out that, once $s$ is made transverse, the dimension of its zero locus is smaller than the expected dimension, hence the corresponding combinatorial types are in fact irrelevant.
-
-The procedure to make $s$ transverse is the same as described in \cite[\S 3]{VZ}, namely we need to blow up inside $\PP$ the projective subbundle $\PP(\mathcal E)$ of $\PP_{|\mathcal X_\sigma}$, where $\mathcal X_\sigma$ is the closed substack of $\mathcal X$ where some of the tails degenerate so that the corresponding gluing marking lies on a component contracted by $f$, and $\mathcal E$ is the sum of the tangent line bundles at such subset of the gluing markings.
-Because $\oM_{0,\tilde\alpha^{(i)}\cup\{m_i\}}^{\rm{punct}}(H,\tilde d_i)$ is isomorphic to $\M{0}{\tilde n_i}{H}{d_i}$, the construction of Vakil and Zinger in the section ``A blowup of a moduli space of genus-zero maps'' of their paper carries through unchanged.
-The result of the blow-up is to replace $T_{q_i}R_i$ with $T_{q_i}R_i\otimes\bigoplus_{j=1}^kT_{\tilde q_j}R_i\otimes T_{\tilde q_j} S_{ij}$.
-We interpret this in terms of alignments.\footnote{(Luca) this has to be written properly}
-
-We claim that $\tilde s$ obtained from $s$ by twisting by the exceptional divisors of the blowup is a transverse section.
-We also claim that comb loci of type $\mathcal Y_c^0$ can be described as a fibered product of
-\begin{itemize}
- \item moduli of genus one punctured maps to the standard log point, radially aligned and satisfying factorisation;
- \item $V(\tilde s)$;
- \item moduli of genus zero maps relative to $(\PP^N|H)$, corresponding to vertices of type \ref{boringvertices} above.
-\end{itemize}
-Finally, we claim that integrals of psi and evaluation classes over these loci can be translated into tautological integrals, i.e.
-descendant Gromov--Witten invariants, whose numerics is governed by the combinatorial type of the tropical map.
-
-\section{Recursion for general $(X,Y)$}\label{section recursion for general pair}
-
-\section{Quantum Lefschetz algorithm}\label{section recursion algorithm}
+together with the equation imposed by the choice of alignment:
+\begin{align*} & e_1 + f_1 = e_2 + f_3 + g_3 \\
+\Leftrightarrow \ & e + f = e + f/2 + g/2 \\
+\Leftrightarrow \ & f = g.
+\end{align*}
+Notice that setting $f=g=0$ we recover $\tau$. We claim that if we twist the bundle
+\begin{equation*} E = \left( \TT_{q_1} C_1 \otimes \TT_{q_1} C_0 \right) \oplus \left( \TT_{q_2} C_2 \otimes \TT_{q_2} C_0 \right) \end{equation*}
+by the line bundle corresponding to the divisor in $\widetilde\Dcal$ defined by $\rho$, we will obtain the bundle
+\begin{equation*} F = \left( \TT_{f_1}C_1^1 \otimes \TT_{e_1} C_0 \right) \oplus \left( \TT_{g_2} C_2^2 \otimes \TT_{e_2} C_0 \right). \end{equation*}
+described earlier. The line bundle corresponding to $\rho$ is simply $\OO(f)=\OO(g)$. We have:
+\begin{align*} \left( \TT_{q_1} C_1 \otimes \TT_{q_1} C_0 \right) \otimes \OO(f) & = \TT_{q_1}C_1 \otimes \TT_{q_1} C_0 \otimes \TT_{f_1} C_1^0 \otimes \TT_{f_1} C_1^1 \\
+& = \TT_{e_1} C_1^0 \otimes \TT_{e_1} C_0 \otimes \TT_{f_1} C_1^0 \otimes \TT_{f_1} C_1^1\\
+&  = \TT_{f_1} C_1^1 \otimes \TT_{e_1} C_0\end{align*}
+where we have used the telescoping trick $\TT_{f_1}C_1^0 \otimes \TT_{e_1} C_1^0 \cong \OO$. On the other hand, for the $C_2$ summand we write $f=f/2 + g/2=f_3+g_3$ to obtain:
+\begin{align*} \left( \TT_{q_2}C_2 \otimes \TT_{q_2}C_0\right) \otimes \OO(f) & = \TT_{e_2} C_0 \otimes \TT_{e_2} C_2^0 \otimes \OO(f_3) \otimes \OO(g_3) \\
+& = \TT_{e_2} C_0 \otimes \TT_{e_2} C_2^0 \otimes \TT_{f_3} C_2^0 \otimes \TT_{f_3} C_2^1 \otimes \TT_{g_3} C_2^1 \otimes \TT_{g_3} C_2^2 \\
+& = \TT_{g_3} C_2^2 \otimes \TT_{e_2} C_0.\end{align*}
+This observation generalises, giving a precise relation between the intrinsically-defined vector bundle $F$ on $\widetilde\Dcal$ (which we use to impose the factorisation condition) and the the vector bundle $E$ pulled back from $\Ecal$.
+This allows us to express the Chern classes of $F$ in terms of pull-backs of tautological classes from $\Ecal$ and boundary strata on $\widetilde\Dcal$, which is necessary to compute integrals.
+\end{example}
+
+\section{Lefschetz algorithm}\label{section recursion algorithm}
 Consider a smooth pair $(X,Y)$ with $Y$ very ample, and let $P$ be the projective bundle $P=\PP_Y(\operatorname{N}_{Y|X} \oplus\OO_Y)$.

### 2019-06-27 EllipticSingularitiesSplitting.tex
Did some changes on this branch - whoops

@@
 
-\title[Reduced relative GW theory in genus 1]{Curve counting in genus one: elliptic singularities {\it \&} relative geometry}
+\title[Curve counting in genus one: elliptic singularities and relative geometry]{Curve counting in genus one: elliptic singularities {\it \&} relative geometry}
 \author{Luca Battistella, Navid Nabijou and Dhruv Ranganathan}
@@
 We have produced a factorization
-\[
-\widetilde\Dcal\to\widetilde \Ecal\to\Ecal,
-\]
-where the first map is flat and the second map is a logarithmic modification. The generic fiber can be interpreted geometrically.
-
-{\bf \color{red} This lemma should be there, but the notation needs to be changed and the proof needs to be cleaned up. Luca?
+\begin{equation*}\widetilde\Dcal\to\widetilde \Ecal\to\Ecal,
+\end{equation*}
+where the first map is flat and the second map is a logarithmic modification.
+$\widetilde\Dcal$ is a compactification of a torus bundle over $\widetilde\Ecal$ whose strata can be read off from the tropicalization; in particular, we have the information of how (polynomials in) the classes of boundary strata push forward to $\widetilde\Ecal$.
+In fact, the generic fibre of $\widetilde\Dcal \to \widetilde\Ecal$ can be read off geometrically.
 
@@
 This is patently the fan of a projective space.
-\end{proof}}
+\end{proof}
 
@@
 \end{example}
+
+\subsection{Recursion for general $(X,Y)$}\label{section recursion for general pair} We now let $(X,Y)$ be a general smooth very ample pair.
+In \S \ref{} we studied the moduli space $\VZ_{1,\alpha}(X|Y,\beta)$ of centrally aligned maps to $(X,Y)$ and equipped it with a virtual fundamental class by diagonal pull-back from $\VZ_{1,\alpha}(\PP^N|H,d)$.
+
+This construction of the virtual fundamental class means that once we have established a recursion formula for $(\PP^N,H)$, it immediately pulls back to give a recursion formula for $(X,Y)$.
+To be more precise, Theorem \ref{theorem recursion} holds \emph{mutatis mutandis}, with the same values of $\lambda_\Dcal$.
+The computation of the splitting orders is exactly the same, and the recursive description of the boundary strata pulls back to give an entirely analogous description on $\VZ_{1,\alpha}(X|Y,\beta)$.
 

### 2019-06-27 EllipticSingularitiesSplitting.tex
Normalising notation

@@
 
-The Kontsevich moduli space of stable maps from genus $0$ curves to projective space exhibits \tred{remarkable} geometry -- it is a smooth orbifold with a ``self-similar'' normal crossings boundary.
+The Kontsevich moduli space of stable maps from genus $0$ curves to projective space exhibits remarkable geometry -- it is a smooth orbifold with a ``self-similar'' normal crossings boundary.
 These facts have combined to produce a very {satisfactory} understanding of Gromov--Witten theory in genus $0$.
 
-While the higher genus situation is \tred{substantially} more difficult, in the last several years, \tred{substantial} theory has been developed towards a conceptual understanding of the genus one case.
-This began over a decade ago with the pioneering work of \tred{Li}, Vakil, and Zinger~\cite{redgone,VZ,LZ,lz2,zingerstvsred,zingred}, \tred{and was recently reinvigorated involving ideas from logarithmic geometry and singularity theory}~\cite{BCM18,CM18,HL,RSPW,RSPW2,SMY1,VISC}.
+While the higher genus situation is much more difficult, in the last several years, substantial theory has been developed towards a conceptual understanding of the genus one case.
+This began over a decade ago with the pioneering work of \tred{Li}, Vakil, and Zinger~\cite{redgone,VZ,LZ,lz2,zingerstvsred,zingred}, and was recently reinvigorated involving ideas from logarithmic geometry and singularity theory~\cite{BCM18,CM18,HL,RSPW,RSPW2,SMY1,VISC}.
 The result is a \textit{reduced} Gromov--Witten theory, which removes certain degenerate contributions from the ordinary theory.
@@
 
-Let $\mathcal M_{1,\alpha}^\circ(\mathbb P^N|H)$ be the moduli space of positive degree maps from \tred{smooth} curves of genus $1$ to $\mathbb P^N$ with \tred{dimensionally transverse} contact order $\alpha\in\mathbb Z^n_{\geq 0}$ along $H$.
+Let $\mathcal M_{1,\alpha}^\circ(\mathbb P^N|H,d)$ be the moduli space of positive degree maps from smooth curves of genus $1$ to $\mathbb P^N$ with dimensionally transverse contact order $\alpha\in\mathbb Z^n_{\geq 0}$ along $H$.
 
 \begin{customthm}{A}\label{thm: desingularization}
-There exists a logarithmically smooth and proper Deligne--Mumford stack $\VZ_{1,\alpha}^\circ(\mathbb P^N|H)$ having expected dimension, and containing $\mathcal M_{1,\alpha}^\circ(\mathbb P^N|H)$  as a dense open subset.
+There exists a logarithmically smooth and proper Deligne--Mumford stack $\VZ_{1,\alpha}^\circ(\mathbb P^N|H,d)$ having expected dimension, and containing $\mathcal M_{1,\alpha}^\circ(\mathbb P^N|H,d)$  as a dense open subset.
 A point in this moduli space parameterizes maps
@@
 The first step is to express the locus of maps where the contact order degenerates in terms of Chern classes of natural vector bundles.
-The second step is to describe that locus in terms of fiber products of moduli spaces with smaller invariants.
+The second step is to describe that locus in terms of fibre products of moduli spaces with smaller invariants.
 Novelties are introduced in both steps.
 We achieve the first step using techniques that are entirely within tropical and logarithmic geometry, drastically simplifying Gathmann's calculation.
-For the second step, we contend with the interaction of the relative splitting formula and the geometry of elliptic singularities, which is entirely new (Section REFERNCE).
-We express the factorization property in terms of tautological classes and combinatorial manipulations, leading to Theorem~\ref{thm: recursion}.
+For the second step, we contend with the interaction of the relative splitting formula and the geometry of elliptic singularities, which is entirely new (\S \ref{subsection C0 splitting}).
+We express the factorisation property in terms of tautological classes and combinatorial manipulations, leading to Theorem~\ref{thm: recursion}.
 
 \subsection{Broader contributions} Beyond genus one, we pass through a number of seemingly useful general techniques.
-First, we explain how to describe degenerate moduli spaces as fiber products.
+First, we explain how to describe degenerate moduli spaces as fibre products.
 This is substantially more delicate than the standard situation because of the need to work with elliptic singularities and aligned logarithmic structures.
@@
 We realize the locus as the vanishing locus of a section of a line bundle that comes from tropical geometry — from a piecewise linear function on the fan.
-The systematic understanding of logarithmic line bundles arising in this fashion is likely to play an important \tred{role} in logarithmic enumerative geometry.
-
-Our analysis leads naturally to \tred{the} study of a ``main component’’ double ramification cycle for target manifolds in genus one.
+The systematic understanding of logarithmic line bundles arising in this fashion is likely to play an important r\^ole in logarithmic enumerative geometry.
+
+Our analysis leads naturally to the study of a ``main component’’ double ramification cycle for target manifolds in genus one.
 The virtual geometry of this was studied in recent work of Janda, Pandharipande, Pixton, and Zvonkine~\cite{DRCBundle}.
-We do not know how to calculate a \tred{closed formula} for this main component contribution, but we repurpose E.~Katz's topological recursion relations \cite{EKatz} to complete the algorithm.
+We do not know how to calculate a closed formula for this main component contribution, but we repurpose E.~Katz's topological recursion relations \cite{EKatz} to complete the algorithm.
 We note that even in genus one, an understanding of the main component contributions of the double ramification cycle for target manifolds would be interesting.
@@
 \subsection{The absolute case} Let $\mathfrak M_{1,n}$ be the logarithmic algebraic stack of $n$-pointed prestable curves of genus $1$.
-Let $\plC$ be a $n$-pointed genus $1$ tropical curve; \tred{we formally replace the minimal subcurve of genus $1$ by a single vertex, called the \emph{core}}.
-Let $C$ be a logarithmic \tred{smooth} curve over $S$, let $\plC$ denote its tropicalization, and let $\lambda$ be the section of $\overline{M}_{C/S}$ giving the distance from the \tred{core}.
+Let $C$ be a logarithmically smooth curve over $S$, let $\plC$ denote its tropicalization, and let $\lambda$ be the section of $\overline{M}_{C/S}$ giving the distance from each vertex to the minimal genus one subcurve.
 
@@
 
-The moduli stack $\mathfrak M_{1,n}^{\mathrm{cen}}$ is a logarithmic algebraic stack in the smooth topology, \tred{and $\mathfrak M_{1,n}^{\mathrm{cen}}\to\mathfrak M_{1,n}$ is a logarithmic modification}.
-The main construction of~\cite{RSPW} canonically associates to any \tred{centrally} aligned family of curves $\mathcal C_S$ a partial destabilization $\widetilde{\mathcal C}_S$ and a contraction
+The moduli stack $\mathfrak M_{1,n}^{\mathrm{cen}}$ is a logarithmic algebraic stack in the smooth topology, and $\mathfrak M_{1,n}^{\mathrm{cen}}\to\mathfrak M_{1,n}$ is a logarithmic modification.
+The main construction of~\cite{RSPW} canonically associates to any centrally aligned family of curves $\mathcal C_S$ a partial destabilisation $\widetilde{\mathcal C}_S$ and a contraction
 \[
@@
 where $\overline{\mathcal C}_S$ may contain a Gorenstein elliptic singularity \cite{SMY1}.
-The number of branches is equal to the number of excident edges at the circle of radius $\delta$.
+The number of branches is equal to the sum of the number of vertices which lie on the circle of radius $\delta$ and the number of edges which are split by the same circle.
 This data uniquely determines the singularity.
@@
 The space of stable maps $\overline{\mathcal M}^{\mathrm{cen}}_{1,n}(\mathbb P^N,d)$ from the universal nodal curve $\mathcal C$ over the stack $\mathfrak M_{1,n}^{\mathrm{cen}}$ is a proper and algebraic, with projective coarse moduli space.
-\tred{A compatibility condition is required, namely that the circle of radius $\delta$ passes through at least one component of positive degree.} A stable map in this space is said to satisfy the \textbf{factorization condition} if the map $\mathcal C\to \mathbb P^N$ factors through the contraction $\widetilde{\mathcal C}\to \overline{\mathcal C}$.
+A compatibility condition between the alignment and the map is required, namely that the circle of radius $\delta$ passes through at least one component of positive degree.
+A stable map in this space is said to satisfy the \textbf{factorisation condition} if the map $\mathcal C\to \mathbb P^N$ factors through the contraction $\widetilde{\mathcal C}\to \overline{\mathcal C}$.
 
 \begin{thm}[{\cite[Theorem B]{RSPW}}]
-The substack $\VZ_{1,n}(\mathbb P^N,d)$ of $\overline{\mathcal M}^{\mathrm{cen}}_{1,n}(\mathbb P^N,d)$ parameterizing maps to $\mathbb P^N$ that satisfy the factorization property is smooth and proper of the expected dimension.
+The substack $\VZ_{1,n}(\mathbb P^N,d)$ of $\overline{\mathcal M}^{\mathrm{cen}}_{1,n}(\mathbb P^N,d)$ parameterizing maps to $\mathbb P^N$ that satisfy the factorisation property is smooth and proper of the expected dimension.
 \end{thm}
@@
 The remainder of this section lifts this condition to the category of relative maps to the pair $(\mathbb P^N,H)$.
-The core of the result is identifying the necessary factorization conditions that remove the obstructions.
+The core of the result is identifying the necessary factorisation conditions that remove the obstructions.
 
@@
 Let $\alpha$ be a partition of the degree $d>0$.
-Consider the moduli space $\mathcal M_{1,\alpha}^\circ(\mathbb P^N|H)$ of maps from smooth elliptic curves $C\to \mathbb P^N$ that meet $H$ at finitely many marked points with vanishing orders given by the partition $\alpha$.
+Consider the moduli space $\mathcal M_{1,\alpha}^\circ(\mathbb P^N|H,d)$ of maps from smooth elliptic curves $C\to \mathbb P^N$ that meet $H$ at finitely many marked points with vanishing orders given by the partition $\alpha$.
 This is a smooth, but non-proper Deligne--Mumford stack.
@@
 For the compactification, we begin with Abramovich--Chen--Gross--Siebert's space of logarithmic stable maps, though we will typically work with various subcategories and variants~\cite{AbramovichChenLog,ChenLog,GrossSiebertLog,KimLog}.
-\tred{Let $\PP^N$ be endowed with the divisorial logarithmic structure induced by $H$.}
-
-The moduli space $\overline{\mathcal{M}}^{\operatorname{log}}_{1,\alpha}(\mathbb P^N|H)$ is a fibred category over logarithmic schemes, whose fiber over $(S,M_S)$ is the groupoid of logarithmic curves of genus $1$ over $(S,M_S)$ equipped with a map to $\mathbb P^N$ of degree $d$ and contact order $\alpha$.
+
+Let $\PP^N$ be endowed with the divisorial logarithmic structure induced by $H$.
+The moduli space $\overline{\mathcal{M}}^{\operatorname{log}}_{1,\alpha}(\mathbb P^N|H,d)$ is a fibred category over logarithmic schemes, whose fibre over $(S,M_S)$ is the groupoid of logarithmic curves of genus $1$ over $(S,M_S)$ equipped with a map to $\mathbb P^N$ of degree $d$ and contact order $\alpha$.
 It is a fundamental fact in the subject that this category is representable by a proper algebraic stack with logarithmic structure, parameterizing minimal objects~\cite{ChenLog}.
@@
 $$
-\overline{\mathcal M}^{\mathrm{log}}_{1,\alpha}(\mathbb P^N|H) \to \overline{\mathcal M}_{1,n}(\mathbb P^N,d).
+\overline{\mathcal M}^{\mathrm{log}}_{1,\alpha}(\mathbb P^N|H,d) \to \overline{\mathcal M}_{1,n}(\mathbb P^N,d).
 $$
-The space of centrally aligned maps is a logarithmic modification
+The space of centrally aligned maps is a logarithmic modification:
 $$
-\overline{\mathcal M}^{\mathrm{cen}}_{1,n}(\mathbb P^N,d)\to\overline{ \mathcal M}_{1,n}(\mathbb P^N,d)
+\overline{\mathcal M}^{\mathrm{cen}}_{1,n}(\mathbb P^N,d)\to\overline{ \mathcal M}_{1,n}(\mathbb P^N,d).
 $$ 
-The fiber product leads to a fourth moduli space of \textbf{centrally aligned logarithmic maps to $(\mathbb P^n,H)$}, which we denote $\widetilde{\VZ}_{1,\alpha}(\mathbb P^N|H)$.
-
-\subsection{Relative geometry: expansions} Our next task is to pick out a non-singular principal component in $\widetilde{\VZ}_{1,\alpha}(\mathbb P^N|H)$.
+The fibre product leads to a fourth moduli space of \textbf{centrally aligned logarithmic maps to $(\mathbb P^n,H)$}, which we denote $\widetilde{\VZ}_{1,\alpha}(\mathbb P^N|H,d)$.
+
+\subsection{Relative geometry: expansions} Our next task is to pick out a non-singular principal component in $\widetilde{\VZ}_{1,\alpha}(\mathbb P^N|H,d)$.
 The principal component of this space, consisting of the closure of the space of maps from nonsingular curves, maps into the principal component of $\overline{\mathcal M}^{\mathrm{cen}}_{1,n}(\mathbb P^N,d)$.
@@
 Here the latter is the $s$-times iterated deformation to the normal cone of $H$ in $\mathbb P^N$.
-The components \tred{of the target} are in bijection with the vertices in $\widetilde{\mathbb R}_{\geq 0}$.
+The components of the target are in bijection with the vertices in $\widetilde{\mathbb R}_{\geq 0}$.
 The curve is modified by adding rational components corresponding to the newly introduced vertices.
@@
 The result is a logarithmic stable map to an expanded target $\mathbb P^N[s]$, together with a contraction to the main target component $\mathbb P^N[s]\to\mathbb P^N$.
-\tred{Two maps are considered equivalent if they differ by $\Gm$-scaling the target at higher level.}
+Two maps are considered equivalent if they differ by $\Gm$-scaling the target at higher level.
 
@@
 
-\subsection{Relative geometry: factorization}\label{subsection factorisation} Let $[C\to \mathbb P^N[s]\to \mathbb P^N]$ be a logarithmic map from a centrally aligned curve to an expansion.
-Recall that $\mathbb P^N[s]$ consists of a union of $\mathbb P^N$ with \tred{$s$ copies of} the projective bundle $\mathbb P(\mathcal O_H\oplus \mathcal O_H(1))$.
+\subsection{Relative geometry: factorisation}\label{subsection factorisation} Let $[C\to \mathbb P^N[s]\to \mathbb P^N]$ be a logarithmic map from a centrally aligned curve to an expansion.
+Recall that $\mathbb P^N[s]$ consists of a union of $\mathbb P^N$ with $s$ copies of the projective bundle $\mathbb{P} = \mathbb P(\mathcal O_H\oplus \mathcal O_H(1))$.
 We refer to these latter components as \textbf{the higher levels}.
@@
 
-Let\marginpar{I replace $D_1,D_2$ by the more suggestive $D_F,D_B$.} $D_F\subset C$ be the maximal genus $1$ subcurve that is \sout{mapped to higher level} contracted by the map $C\to \mathbb P^N[s]$ \sout{in the fiber direction}.
-Let $\delta_F$ be the associated radius from the circuit to the nearest non-contracted component.
-Let $D_B$ be the maximal genus $1$ subcurve that is contracted by the collapsed map to $\mathbb P^N$, and let $\delta_B$ be the associated radius.
+Let $D_F\subseteq C$ be the maximal genus $1$ subcurve which is mapped to a higher level and contracted by the map $C\to \mathbb P^N[s]$.
+Let $\delta_F$ denote the distance from the core to the nearest component of $C \setminus D_F$.
+Similarly let $D_B\subseteq C$ be the maximal genus $1$ subcurve that is contracted by the collapsed map to $\mathbb P^N$ and let $\delta_B$ be the associated radius.
 This coincides with the radius of the underlying map to $\mathbb P^N$.
@@
 
-The datum $(\delta_F,\delta_B)$ determines a destabilization $\widetilde C$ of $C$ together with successive contractions $\widetilde C\to \overline C_F\to\overline C_B$.
+The datum $(\delta_F,\delta_B)$ determines a destabilisation $\widetilde C$ of $C$ together with successive contractions $\widetilde C\to \overline C_F\to\overline C_B$.
 The contractions are constructed directly from~\cite[Section~3]{RSPW}.
@@
 \begin{definition}
-The map $[C\to \mathbb P^N[s]\to \mathbb P^N]$ \textbf{factorizes completely} if
+The map $[C\to \mathbb P^N[s]\to \mathbb P^N]$ \textbf{factorises completely} if
 \begin{itemize}
-\item the map $C\to \mathbb P^N[s]$ factors through $\overline C_F$ such that at least one branch of $\overline C_F$ has positive degree in the fiber direction; 
-\item the collapsed map to $\mathbb P^N$ factorizes through $\overline C_B$ such that at least one branch of $\overline C_B$ has positive degree.
+\item the map $C\to \mathbb P^N[s]$ factors through $\overline C_F$ such that at least one branch of $\overline C_F$ has positive degree in the fibre direction; 
+\item the collapsed map to $\mathbb P^N$ factorises through $\overline C_B$ such that at least one branch of $\overline C_B$ has positive degree.
 \end{itemize}
@@
 
-In particular, if $[C\to \mathbb P^N[s]\to \mathbb P^N]$ is a family of centrally aligned maps over $S$ that factorizes completely, there is a forgetful moduli map $S\to \VZ_{1,n}(\mathbb P^N,d)$, to the principal component of the space of absolute maps.
-
-Let $\VZ_{1,\alpha}(\mathbb P^N|H)$ be the stack of maps from centrally aligned curves to expansions of $\mathbb P^N$ that factorize completely.
+In particular, if $[C\to \mathbb P^N[s]\to \mathbb P^N]$ is a family of centrally aligned maps over $S$ that factorises completely, there is a forgetful moduli map $S\to \VZ_{1,n}(\mathbb P^N,d)$, to the principal component of the space of absolute maps.
+
+Let $\VZ_{1,\alpha}(\mathbb P^N|H,d)$ be the stack of maps from centrally aligned curves to expansions of $\mathbb P^N$ that factorise completely.
 
 \begin{thm}\label{thm: log-smoothness}
-The stack $\VZ_{1,\alpha}(\mathbb P^N|H)$ is proper and logarithmically \tred{smooth} over $\mathrm{Spec} \ \mathbb C$. 
+The stack $\VZ_{1,\alpha}(\mathbb P^N|H,d)$ is proper and logarithmically smooth over $\mathrm{Spec} \ \mathbb C$. 
 \end{thm}
@@
 $$
-\nu: \VZ_{1,\alpha}(\mathbb P^N|H)\to \VZ_{1,n}(\mathbb P^N,d),
+\nu: \VZ_{1,\alpha}(\mathbb P^N|H,d)\to \VZ_{1,n}(\mathbb P^N,d),
 $$
 which remembers only the stabilization of the collapsed map.
-The map is certainly centrally aligned, and we have already argued above that it satisfies the factorization property for $\mathbb P^N$ after composition.
-The moduli space $\VZ_{1,\alpha}(\mathbb P^N|H)$ is proper.
+The map is certainly centrally aligned, and we have already argued above that it satisfies the factorisation property for $\mathbb P^N$ after composition.
+The moduli space $\VZ_{1,\alpha}(\mathbb P^N|H,d)$ is proper.
 Indeed, the verification of the valuative criterion follows exactly as in Vakil's Lemma~\cite[Lemma~5.9]{Vre}.
-A direct proof that the factorization property is a closed condition may be found in~\cite[Theorem~4.3]{RSPW}.
+A direct proof that the factorisation property is a closed condition may be found in~\cite[Theorem~4.3]{RSPW}.
 
@@
 Assume now that the elliptic curve maps into higher level.
-Note that the relative logarithmic tangent bundle of the expansion, over the base $\mathbb P^N$ is a trivial line bundle of rank $1$, as the fibers are toric.
+Note that the relative logarithmic tangent bundle of the expansion, over the base $\mathbb P^N$ is a trivial line bundle of rank $1$, as the fibres are toric.
 Consider an $S$-family of maps.
-After replacing the source $C$ by a destabilization, we have maps
+After replacing the source $C$ by a destabilisation, we have maps
 \bcd
@@
 \]
-where the former is the space of deformations of the curve and map to the base, as a factorized centrally aligned map.
+where the former is the space of deformations of the curve and map to the base, as a factorised centrally aligned map.
 The latter is the space of obstructions to lifting a map to the base into the total space.
@@
 The line bundle $\mathcal O_{C}(-\alpha)$ is equivalent to the divisor $\sum a_i x_i$ where $x_i$ are the points connecting $D_F$ to the rest of the curve, and $a_i$ are the slopes of $\alpha$ along the edges corresponding to the $x_i$.
-Infinitesimally moving the point $x_i$ is a deformation of the curve that is unobstructed by the map $f_B$, since the map is constant on the interior of the \tred{circle of radius $\delta_B$}.
+Infinitesimally moving the point $x_i$ is a deformation of the curve that is unobstructed by the map $f_B$, since the map is constant on the interior of the circle of radius $\delta_B$.
 By deforming the $x_i$, at least one of which has nonzero $a_i$, we produce a one-dimensional space of obstructions.
-The absolute obstructions therefore vanish, \sout{since they are the cokernel of a surjective map,} so the result follows.
+The absolute obstructions therefore vanish, so the result follows.
 %Consider an $S$-family of expanded maps $[F: C\to \mathbb P^N[s]$.
@@
 
-The above theorem guarantees that the singularities of the space of totally factorized maps to expansions is logarithmically smooth.
+The above theorem guarantees that the singularities of the space of totally factorised maps to expansions is logarithmically smooth.
 In fact, one can say more in this case.\marginpar{I don't understand the point of this Cor.
@@
 \begin{cor}
-The logarithmically smooth stack $\VZ_{1,\alpha}(\mathbb P^N|H)$ has at worst orbifold singularities, i.e. admits a non-representable cover by a smooth Deligne--Mumford stack.
+The logarithmically smooth stack $\VZ_{1,\alpha}(\mathbb P^N|H,d)$ has at worst orbifold singularities, i.e. admits a non-representable cover by a smooth Deligne--Mumford stack.
 \end{cor}
@@
 \begin{proof}
-Since $\VZ_{1,\alpha}(\mathbb P^N|H)$ is logarithmically smooth, it will suffice to show that the cones of its tropicalization are simplicial.
+Since $\VZ_{1,\alpha}(\mathbb P^N|H,d)$ is logarithmically smooth, it will suffice to show that the cones of its tropicalization are simplicial.
 To see this, consider a logarithmic stable map to an expansion $C\to \mathbb P^N[s]$ without a central alignment.
@@
 The alignment procedure is an iterated barycentric subdivision at the level of tropical moduli spaces, as explained in~\cite[Section 4.6]{RSPW}, and such subdivisions preserve the property of being simplicial.
-We conclude from this that the blowup $\widetilde{\VZ}^{\mathrm{exp}}_{1,\alpha}(\mathbb P^N|H)$ obtained by centrally aligning Kim's spaces has simplicial cones.
-Finally, the morphism $\VZ_{1,\alpha}(\mathbb P^N|H)\to \widetilde{\VZ}^{\mathrm{exp}}_{1,\alpha}(\mathbb P^N|H)$ is strict, so the cones of $\VZ_{1,\alpha}(\mathbb P^N|H)$ are simplicial, as claimed.
+We conclude from this that the blowup $\widetilde{\VZ}^{\mathrm{exp}}_{1,\alpha}(\mathbb P^N|H,d)$ obtained by centrally aligning Kim's spaces has simplicial cones.
+Finally, the morphism $\VZ_{1,\alpha}(\mathbb P^N|H,d)\to \widetilde{\VZ}^{\mathrm{exp}}_{1,\alpha}(\mathbb P^N|H,d)$ is strict, so the cones of $\VZ_{1,\alpha}(\mathbb P^N|H,d)$ are simplicial, as claimed.
 \end{proof}
@@
 \subsection{Rubber variants} In our implementation of the relative theory, we will need the ``rubber'' variant of the space of maps $
-\VZ_{1,\alpha}(\mathbb P^N|H)$, where the entire curve is mapped into higher levels.
+\VZ_{1,\alpha}(\mathbb P^N|H,d)$, where the entire curve is mapped into higher levels.
 
@@
 Equip this space with the logarithmic structure coming from the $0$ and $\infty$ sections of the bundle.
-Consider the moduli space $\VZ_{1,\alpha}(\mathbb P/\mathbb G_m)$ of logarithmic maps
+Consider the moduli space $\VZ^{\leftrightarrow}_{1,\alpha}(\mathbb P|H_0+H_\infty,d)$ of logarithmic maps
 \[
@@
 \]
-which factorize completely, and where automorphisms are considered over the space of maps to $\mathbb P^{N-1}$.
-Specifically, two maps that differ by a $\mathbb G_m$ translate in the fiber direction are considered equivalent.
-Total factorization, similar to the previous case, means that the map to the bundle and the map to the base $\mathbb P^{N-1}$ both factorize through possibly different singularities.
+which factorise completely, and where automorphisms are considered over the space of maps to $\mathbb P^{N-1}$.
+Specifically, two maps that differ by a $\mathbb G_{\operatorname{m}}$ translate in the fibre direction are considered equivalent.
+Total factorisation, similar to the previous case, means that the map to the bundle and the map to the base $\mathbb P^{N-1}$ both factorise through possibly different singularities.
 
 \begin{thm}
-The stack $\VZ_{1,\alpha}(\mathbb P/\mathbb G_m)$ is logarithmically smooth.
+The stack $\VZ^{\leftrightarrow}_{1,\alpha}(\mathbb P|H_0+H_\infty,d)$ is logarithmically smooth.
 \end{thm}
 
-The main point in the proof of this statement is that on the space of non-degenerate maps with smooth domains, the map from $\VZ^\circ_{1,\alpha}(\mathbb P)\to \VZ^\circ_{1,\alpha}(\mathbb P/\mathbb G_m)$ is a $\mathbb G_m$ torsor.
+The main point in the proof of this statement is that on the space of non-degenerate maps with smooth domains, the map from $\VZ^\circ_{1,\alpha}(\mathbb P|H_0+H_\infty,d)\to \VZ^{\leftrightarrow,\circ}_{1,\alpha}(\mathbb P|H_0+H_\infty,d)$ is a $\mathbb G_{\operatorname{m}}$ torsor.
 Correspondingly, the map on compact moduli spaces is a nodal curve fibration.
@@
 
-The bundle $\mathbb P\to \mathbb P^{N-1}$ gives rise to a $\mathbb G_m$-torsor by deleting the zero and infinity sections.
-Replacing these fibers by their $\mathbb G_{\mathrm{log}}$ compactifications, we obtain a non-representable functor on logarithmic schemes $\mathbb P_{\mathrm{log}}$ and a logarithmically \'etale modification
+The bundle $\mathbb P\to \mathbb P^{N-1}$ gives rise to a $\mathbb G_{\operatorname{m}}$-torsor by deleting the zero and infinity sections.
+Replacing these fibres by their $\mathbb G_{\mathrm{log}}$ compactifications, we obtain a non-representable functor on logarithmic schemes $\mathbb P_{\mathrm{log}}$ and a logarithmically \'etale modification
 \[
@@
 \begin{proof}
-Consider the stack over logarithmic schemes $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}})$ of stable logarithmic maps that factorize completely.
+Consider the stack over logarithmic schemes $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}},d)$ of stable logarithmic maps that factorise completely.
 Here, stability for the map coincides with stability for the projection to $\mathbb P^{N-1}$.
-The arguments in the previous section show that maps to $\mathbb P$ that factorize completely are unobstructed.
-Since this space is a logarithmically \'etale cover of $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}})$, logarithmic smoothness of the latter follows.
-
-The logarithmic multiplicative group $\mathbb G_{\mathrm{log}}$ acts on $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}})$ by translation.
-Tautologically, $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}})$ is a $\mathbb G_{\mathrm{log}}$-torsor over the moduli problem of maps up to this $\mathbb G_{\mathrm{log}}$ translation.
+The arguments in the previous section show that maps to $\mathbb P$ that factorise completely are unobstructed.
+Since this space is a logarithmically \'etale cover of $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}},d)$, logarithmic smoothness of the latter follows.
+
+The logarithmic multiplicative group $\mathbb G_{\mathrm{log}}$ acts on $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}},d)$ by translation.
+Tautologically, $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}},d)$ is a $\mathbb G_{\mathrm{log}}$-torsor over the moduli problem of maps up to this $\mathbb G_{\mathrm{log}}$ translation.
 It is representable after a logarithmically \'etale modification by a family of nodal curves.
-It follows that the space  $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}}/\mathbb G_{\mathrm{log}})$ of maps up to translation that factorize completely is logarithmically smooth.
-
-To conclude the main result, we compare the stacks $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}}/\mathbb G_{\mathrm{log}})$ and  $\VZ_{1,\alpha}(\mathbb P/\mathbb G_m)$.
+It follows that the space  $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}}/\mathbb G_{\mathrm{log}})$ of maps up to translation that factorise completely is logarithmically smooth.
+
+To conclude the main result, we compare the stacks $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}}/\mathbb G_{\mathrm{log}})$ and  $\VZ_{1,\alpha}(\mathbb P/\mathbb G_{\operatorname{m}})$.
 Since a map to $\mathbb P$ gives rise immediately to a map to $\mathbb P_{\mathrm{log}}$, there is a morphism
 \[
-\VZ_{1,\alpha}(\mathbb P/\mathbb G_m)\to \VZ_{1,\alpha}(\mathbb P_{\mathrm{log}}/\mathbb G_{\mathrm{log}}).
+\VZ_{1,\alpha}(\mathbb P/\mathbb G_{\operatorname{m}})\to \VZ_{1,\alpha}(\mathbb P_{\mathrm{log}}/\mathbb G_{\mathrm{log}}).
 \]
@@
 
-The tropicalizations of logarithmic maps that factorize completely satisfy a natural combinatorial condition known as well-spacedness. The version we use here is essentially identical to~
+The tropicalizations of logarithmic maps that factorise completely satisfy a natural combinatorial condition known as well-spacedness. The version we use here is essentially identical to~
 \cite{RSPW2}.
@@
     \item no open neighborhood of $\plC_0$ is contracted to a point in $\mathbb R_{>0}$, or
-    \item if an open neighborhood of $\plC_0$ is contracted and $t_1,\ldots,t_k$ are the \sout{vertex-edge direction} flags whose vertex is mapped to $F(\plC_0)$, but along which $F$ has nonzero slope; then, the minimum of the distances from $\plC_0$ to $t_i$ occurs for at least two indices $i$.
+    \item if an open neighborhood of $\plC_0$ is contracted and $t_1,\ldots,t_k$ are the flags whose vertex is mapped to $F(\plC_0)$, but along which $F$ has nonzero slope; then, the minimum of the distances from $\plC_0$ to $t_i$ occurs for at least two indices $i$.
 \end{enumerate}
@@
 \begin{prop}\label{prop: well-spaced}
-Let $[C\to \mathbb P^N]$ be a logarithmic stable map from a centrally aligned curve to an expansion, that factorizes completely. Then the tropicalization $\plC\to \mathbb R_{\geq 0}$ is well-spaced.
+Let $[C\to \mathbb P^N]$ be a logarithmic stable map from a centrally aligned curve to an expansion, that factorises completely. Then the tropicalization $\plC\to \mathbb R_{\geq 0}$ is well-spaced.
 \end{prop}
@@
 To describe the tropical map to $\mathbb R_{>0}$, we observe that $\plC_0$ is contracted to a fixed point $q\in\mathbb R_{>0}$.
-The flags at \sout{the vertex bases} at $t_i$ correspond to nodes or markings of $C$.
+The flags at $t_i$ correspond to nodes or markings of $C$.
 The pole orders of $f$ at these distinguished points determine the slopes of the tropical map.
@@
 \noindent
-\textbf{Step 4}.
-Let $\Sigma_{1,\alpha}(\mathbb P^N|H,d)$ be \sout{the subcomplex of $\Sigma^{\mathrm{cen}}$} obtained by passing to the subcomplex of $\Sigma^{\mathrm{cen}}$ that consists of well-spaced tropical maps.
+\textbf{Step 4}. Let $\Sigma_{1,\alpha}(\mathbb P^N|H,d)$ be the subcomplex of $\Sigma^{\mathrm{cen}}$ consisting of well-spaced tropical maps.
 
@@
 \Sigma_{1,\alpha}(\mathbb P^N|H,d)$ is the fan of the toroidal embedding $
-\VZ_{1,\alpha}(\mathbb P^N|H)$. In particular, the codimension $k$ strata of $
-\VZ_{1,\alpha}(\mathbb P^N|H)$ are in inclusion reversing bijection with the dimension $k$ cones in $
+\VZ_{1,\alpha}(\mathbb P^N|H,d)$. In particular, the codimension $k$ strata of $
+\VZ_{1,\alpha}(\mathbb P^N|H,d)$ are in inclusion reversing bijection with the dimension $k$ cones in $
 \Sigma_{1,\alpha}(\mathbb P^N|H,d)$.
@@
 The construction above has been given to mimic the construction of the space $
-\VZ_{1,\alpha}(\mathbb P^N|H)$.
-Specifically, the fact that the cone complex $\Sigma^{\mathrm{cen}}$ is the cone complex attached to the logarithmic stack $\widetilde{\VZ}_{1,\alpha}(\mathbb P^N|H)$ of centrally aligned maps to expansions, follows immediately from its description as a subcategory of the fibered category (over logarithmic schemes) of $\mathcal M^{\mathrm{log}}_{1,\alpha}(\mathbb P^N|H)$.
+\VZ_{1,\alpha}(\mathbb P^N|H,d)$.
+Specifically, the fact that the cone complex $\Sigma^{\mathrm{cen}}$ is the cone complex attached to the logarithmic stack $\widetilde{\VZ}_{1,\alpha}(\mathbb P^N|H,d)$ of centrally aligned maps to expansions, follows immediately from its description as a subcategory of the fibreed category (over logarithmic schemes) of $\mathcal M^{\mathrm{log}}_{1,\alpha}(\mathbb P^N|H,d)$.
 To complete the result, we note that $
-\VZ_{1,\alpha}(\mathbb P^N|H)$ has a strict map to $
-\VZ_{1,\alpha}(\mathbb P^N|H)$, so its cone complex is a subcomplex of $\Sigma^{\mathrm{cen}}$.
+\VZ_{1,\alpha}(\mathbb P^N|H,d)$ has a strict map to $
+\VZ_{1,\alpha}(\mathbb P^N|H,d)$, so its cone complex is a subcomplex of $\Sigma^{\mathrm{cen}}$.
 The fact that it must be contained in the subcomplex of well-spaced curves is immediate from Proposition~\ref{prop: well-spaced}.
@@
 
-%\part{The recursion formula and applications}\footnote{(Navid) From here on, when I write a relative space without any decoration, I mean a Kim space.
-We should establish this convention from the start}
-
-\sout{\noindent In this part we prove recursion relations on the moduli space of reduced stable maps (Theorem \ref{theorem recursion}).
-These are inspired by the constructions of Vakil and Gathmann, but go beyond these in several key respects, giving a full treatment of descendant invariants for very ample pairs.
-We apply the recursions to produce a quantum Lefschetz algorithm in genus one, reconstructing the absolute theory of $Y$ and the relative theory of $(X,Y)$ from the absolute theory of $X$.
-Along the way we prove a splitting axiom for the reduced relative theory; the form of this splitting axiom is nontrivial, insofar as it involves the introduction of additional tautological classes.}
-
-\sout{In \S\S \ref{Section Gathmann line bundle}--\ref{section reduced splitting axiom} we prove the recursion formula for $(\PP^N,H)$.
-In \S \ref{section recursion for general pair} we indicate how to obtain from this the recursion formula for an arbitrary very ample pair $(X,Y)$.
-Finally in \S \ref{section recursion algorithm} we describe the quantum Lefschetz algorithm.}
-
 \section{Degeneration of contact order}\label{Section Gathmann line bundle} Consider a reduced relative space $\VZ_{1,\alpha}(\PP^N|H,d)$.
@@
 The pair $(\Lcal_k,s_k)$ is most naturally constructed on the moduli space $\MLog_{1,\alpha}(\PP^N|H,d)$ of non-expanded logarithmic maps; the corresponding pair on $\VZ_{1,\alpha}(\PP^N|H,d)$ will be obtained via pull-back.
-Consider therefore the tropicalisation $\Sigma^{\log}$ of $\MLog_{1,\alpha}(\PP^N|H,d)$, identified as usual with the moduli space of tropical maps to $\RR_{\geq 0}$.
+Consider therefore the tropicalization $\Sigma^{\log}$ of $\MLog_{1,\alpha}(\PP^N|H,d)$, identified as usual with the moduli space of tropical maps to $\RR_{\geq 0}$.
 We have a universal family
@@
 This pulls back along $\pi$ to give a global section $\pi^\flat(\mu) \in \Gamma(C,\ol{M}_C)$.
-Interpreted as a piecewise-linear function on the tropicalisation $\sqC$ with values in $\ol{M}_S$ \cite[Remark 7.3]{CavalieriChanUlirschWise}, this assigns $\mu$ to every vertex and has slope zero along every edge.
+Interpreted as a piecewise-linear function on the tropicalization $\sqC$ with values in $\ol{M}_S$ \cite[Remark 7.3]{CavalieriChanUlirschWise}, this assigns $\mu$ to every vertex and has slope zero along every edge.
 By construction, the line bundle associated to this section is $\pi^\st \Lcal_k$.
@@
 In contrast with nodal singularities, the functions on an elliptic singularity is not simply given as a collection of functions on the normalization subject to topological gluing conditions.
-As a consequence, in order to compute integrals, it is necessary to give a tautological description of this additional factorization condition.
+As a consequence, in order to compute integrals, it is necessary to give a tautological description of this additional factorisation condition.
 
@@
 in terms of fibre products of moduli spaces with smaller numerical data.
-The tautological description of the factorization condition then leads to a recursive structure for calculating integrals.
+The tautological description of the factorisation condition then leads to a recursive structure for calculating integrals.
 This last step is the heart of the analysis.
@@
 \begin{remark}
-We remark that for the reduced relative theory of $(\mathbb P^N,H)$ with only primary fields, an analysis of the factorization condition can be avoided by dimension considerations.
+We remark that for the reduced relative theory of $(\mathbb P^N,H)$ with only primary fields, an analysis of the factorisation condition can be avoided by dimension considerations.
 This leads to the main results in~\cite{Vre}.
@@
 is a log modification, the divisor $\widetilde{\Dcal}$ is either exceptional or the strict transform of a logarithmic divisor.
-These two cases correspond, respectively, to when the circuit is assigned zero degree or nonzero degree by the combinatorial type.
+These two cases correspond, respectively, to when the core is assigned zero degree or nonzero degree by the combinatorial type.
 To begin with we will focus on the latter case.
@@
 \begin{lemma}\label{lem:combs} Let $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ be an irreducible component which contributes nontrivially to the Gromov--Witten invariant, and let $\Delta$ be the corresponding combinatorial type.
-Suppose that $\Delta$ assigns positive degree to the circuit.
+Suppose that $\Delta$ assigns positive degree to the core.
 Then $\Delta$ takes one of the following forms:
@@
 \subsubsection{Type $A$}\label{subsubsection type A} Suppose $\Delta$ is of type $A$. Then $\Ecal$ admits a finite and surjective \textit{splitting morphism} onto the fibre product:
-\begin{equation*} \Ecal \to \left( \ol\Mcal_{1,\alpha^{(1)}\cup(m_1)}(\PP^N|H,d_1) \times \prod_{i=2}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i) \right) \times_{H^r} \ol\Mcal^{\leftrightarrow}_{0,\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}(P|H_0+H_\infty,d_0).\end{equation*}
-
-{\color{red}\bf Has this notation $P$ and the notation for rubber been introduced before? Is this consistent?}
+\begin{equation*} \Ecal \to \left( \ol\Mcal_{1,\alpha^{(1)}\cup(m_1)}(\PP^N|H,d_1) \times \prod_{i=2}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i) \right) \times_{H^r} \ol\Mcal^{\leftrightarrow}_{0,\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}(\mathbb{P}|H_0+H_\infty,d_0).\end{equation*}
 
 \begin{lemma} \label{Lemma type A gluing} The divisor $\Dcal$ admits a natural splitting morphism
-\begin{equation*}\Dcal \xrightarrow{\rho} \left(\VZ_{1,\alpha^{(1)}\cup(m_1)}(\PP^N|H,d_1)\times\prod_{i=2}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i)\right) \times_{H^r} \ol\Mcal^{\leftrightarrow}_{0,\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}(P|H_0+H_\infty,d_0)\end{equation*}
+\begin{equation*}\Dcal \xrightarrow{\rho} \left(\VZ_{1,\alpha^{(1)}\cup(m_1)}(\PP^N|H,d_1)\times\prod_{i=2}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i)\right) \times_{H^r} \ol\Mcal^{\leftrightarrow}_{0,\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}(\mathbb{P}|H_0+H_\infty,d_0)\end{equation*}
 such that the map $\Dcal \to \Ecal$ covers the map on fibre products obtained by desingularising the main component of the factor corresponding to $\sqC_1$.\end{lemma}
@@
 We first consider the statement of the lemma in the category of fine but not necessarily saturated logarithmic schemes, so that a relative stable map to an expansion admits a unique logarithmic lifting.
-The fiber product description preceding the lemma is an isomorphism in this category~\cite[Lemma~4.2.2]{AbramovichMarcusWiseComparison}.
-
-The map $\Dcal\to\Ecal$ is an isomorphism away from the exceptional centers, and the latter is contained in the locus where the circuit is contracted.
+The fibre product description preceding the lemma is an isomorphism in this category~\cite[Lemma~4.2.2]{AbramovichMarcusWiseComparison}.
+
+The map $\Dcal\to\Ecal$ is an isomorphism away from the exceptional centers, and the latter is contained in the locus where the core is contracted.
 Given an element of $\Dcal$ we can split it along the nodes $q_1,\ldots,q_r$.
 It is then clear that $\sqC_1$ is aligned.
-We claim that $\sqC$ satisfies the factorization property if and only if $\sqC_1$ does.
+We claim that $\sqC$ satisfies the factorisation property if and only if $\sqC_1$ does.
 This immediately implies the lemma.
 
-On $\sqC$ there are two contraction radii $\delta_1,\delta_2$.
-Let $\delta \in \{\delta_1,\delta_2\}$.
+On $\sqC$ there are two contraction radii $\delta_F,\delta_B$.
+Let $\delta \in \{\delta_F,\delta_B\}$.
 An examination of the stratification by combinatorial type of $\Dcal$ shows that $\lambda(\sqC^\prime) > \delta$ for any component $\sqC^\prime$ of $\sqC_0$.
@@
 If $f_1,\ldots,f_l$ are some collection of additional edge lengths in $\sigma$ (corresponding to internal nodes in degenerations of the $\sqC_i$) then since $\sigma$ is adjacent to $\tau$ we must have (by construction of the subdivision) $f_1+\ldots+f_l < e_j$ for all $j\in\{1,\ldots,r\}$, since $f_1=\ldots=f_l=0$ and $e_j \neq 0$ on $\tau$.
-In particular, if $\sqC_1$ is degenerate and if $\delta$ denotes the minimal distance from the circuit to a non-contracted vertex of $\sqC_1$ (which certainly exists since $\sqC_1$ has positive degree) then $\delta < e_1 \leq \lambda(\sqC^\prime)$, as claimed.\end{proof}
+In particular, if $\sqC_1$ is degenerate and if $\delta$ denotes the minimal distance from the core to a non-contracted vertex of $\sqC_1$ (which certainly exists since $\sqC_1$ has positive degree) then $\delta < e_1 \leq \lambda(\sqC^\prime)$, as claimed.\end{proof}
 
@@
 \subsubsection{Type $C^+$} \label{subsubsection type C+} Finally suppose that $\Delta$ is of type $C^+$. As before we have a finite and surjective morphism:
-\begin{equation*} \Ecal \to  \left( \prod_{i=1}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i) \right) \times_{H^r} \ol\Mcal^{\leftrightarrow}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(P|H_0+H_\infty,d_0).
+\begin{equation*} \Ecal \to  \left( \prod_{i=1}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i) \right) \times_{H^r} \ol\Mcal^{\leftrightarrow}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(\mathbb{P}|H_0+H_\infty,d_0).
 \end{equation*}
@@
 \begin{lemma} $\Dcal$ admits a finite splitting morphism
-\begin{equation*}\Dcal \xrightarrow{\rho} \left( \prod_{i=1}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i) \right) \times_{H^r} \VZ^{\leftrightarrow}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(P|H_0+H_\infty,d_0)\end{equation*}
+\begin{equation*}\Dcal \xrightarrow{\rho} \left( \prod_{i=1}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i) \right) \times_{H^r} \VZ^{\leftrightarrow}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(\mathbb{P}|H_0+H_\infty,d_0)\end{equation*}
 such that $\Dcal \to \Ecal$ corresponds to the obvious map on fibre products.\end{lemma}
@@
 
-\subsection{Recursive description of the divisors: type IIIb} The treatment of the type I, II and IIIa cases above is a fairly straightforward extension of the ideas of Vakil and Gathmann (albeit updated with logarithmic and tropical technology, which streamlines the presentation and simplifies the proofs).
+\subsection{Recursive description of the divisors: type IIIb}\label{subsection C0 splitting} The treatment of the type I, II and IIIa cases above is a fairly straightforward extension of the ideas of Vakil and Gathmann (albeit updated with logarithmic and tropical technology, which streamlines the presentation and simplifies the proofs).
 The remaining type IIIb case, however, is entirely new.
@@
 If there is more than one stable vertex, as in the proof of Lemma \ref{lem:combs}, the corresponding locus $\Fcal$ in the moduli space of unexpanded maps has high codimension.
-As both insertions and the factorization property for the collapsed map to $\mathbb P^N$ are pulled back from the moduli space of maps without expansions, the contribution vanishes by the projection formula.
+As both insertions and the factorisation property for the collapsed map to $\mathbb P^N$ are pulled back from the moduli space of maps without expansions, the contribution vanishes by the projection formula.
 
@@
 \]
-The first morphism is a closed embedding cut out by the two factorization properties.
+The first morphism is a closed embedding cut out by the two factorisation properties.
 The second morphism is a toroidal modification.
@@
 
-Let $\sigma \in \Sigma^{\Kim}$ be the minimal cone containing the image $\tau$.
+Let $\sigma \in \Sigma^{\Kim}$ be the minimal cone containing the image of $\tau$.
 The dimension of this cone could be large -- its dimension is equal to the the number of levels of the target expansion in the type $\tau$.
@@
 Each vertex $v$ has associated discrete data $\Gamma_v$.
-The vertices over $0$ determine moduli space of ordinary relative stable maps, while the higher level vertices determine maps to rubber.
+The vertices over $0$ determine moduli spaces of ordinary relative stable maps, while the higher level vertices determine maps to rubber.
 Then $\Ecal$ admits a finite and surjective splitting morphism
@@
 where $\epsilon$ is the number of edges of the stabilised dual graph, and the fibre product is taken over the appropriate evaluation maps.
-In conclusion, tautological integrals over $\Ecal$ are completely determined in terms of integrals over moduli spaces with ``smaller'' combinatorial data.\medskip
+Splitting the diagonal of $H^{2\epsilon}$ we see that tautological integrals over $\Ecal$ are completely determined in terms of integrals over moduli spaces with ``smaller'' combinatorial data.\medskip
 
@@
 We wish to use the splitting of $\Ecal$ in the ordinary geometry to recursively compute integrals in the reduced geometry.
-Noting that $\Dcal$ is cut out of the excess dimensional space $\widetilde \Dcal$ by the factorization properties, we make the reduction in two steps:
+Noting that $\Dcal$ is cut out of the excess dimensional space $\widetilde \Dcal$ by the factorisation properties, we make the reduction in two steps:
 \begin{enumerate}
@@
 \]
-is a logarithmic morphism. The generic fiber of this morphism is toric variety.  \medskip
+is a logarithmic morphism. The generic fibre of this morphism is toric variety.  \medskip
 
@@
 
-We keep in mind the fiber product description of $\Ecal$. Construct a modification $\widetilde \Ecal$ from $\Ecal$ as follows.
+We keep in mind the fibre product description of $\Ecal$. Construct a modification $\widetilde \Ecal$ from $\Ecal$ as follows.
 
 \begin{enumerate}
-\item Given a logarithmic map with splitting nodes $q_1,\ldots,q_r$ of type $\Delta$, formally glue together the $r$ vertices of the tropicalization which carry the splitting nodes, and declare the resulting vertex to be the root of the resulting tree.
-Impose the central alignment condition, where the special root takes on the role previously occupied by the core.
-\item Replace the fiber product factor in $\Ecal$ associated to the vertex $\sqC_0$
+\item Given a logarithmic map of type $\Delta$ with splitting nodes $q_1,\ldots,q_r$, formally glue together the $r$ vertices of the tropicalization which carry the splitting nodes, and declare the resulting vertex to be the root of the resulting tree.
+Impose the central alignment condition, where the special root takes on the r\^ole previously occupied by the core.
+\item Replace the fibre product factor in $\Ecal$ associated to the vertex $\sqC_0$
 \begin{equation*} \ol\Mcal^{\leftrightarrow}_{\Gamma_{\tiny{\sqC_0}}}(P|H_0+H_\infty) \end{equation*}
@@
 This procedure induces a logarithmic modification $\widetilde\Ecal \to \Ecal$ which admits a modular description as a fibre product of genus zero centrally aligned maps coming from the vertices $\sqC_1,\ldots,\sqC_r$, and genus one aligned rubber maps satisfying fibre-direction factorisation from the vertex $\sqC_0$).
-
-By construction, we have a map $\widetilde\Dcal \to \widetilde\Ecal$ which is a compactification of a torus bundle over $\widetilde\Ecal$.
-The strata of $\widetilde\Dcal$ can be read off from its tropicalisation, and in particular we have the information of how (polynomials in) the classes of boundary strata push forward to $\widetilde\Ecal$.
-
-We have produced a factorization
+We have thus produced a factorisation
 \begin{equation*}\widetilde\Dcal\to\widetilde \Ecal\to\Ecal,
@@
 This is the open stratum of the moduli space of attaching data \cite[\S\S 2.2-2.3]{SMY2}.
-On the fiber boundary, the circle of radius $\delta$ will pass through a subset of $\{V_{0,\delta}\}\cup V_{>0,\delta}$, while cutting the complementary subset along the edge between the core and $v$; correspondingly, there is a destabilisation of the curve, and an elliptic singularity containing strictly semistable branches.
+On the fibre boundary, the circle of radius $\delta$ will pass through a subset of $\{V_{0,\delta}\}\cup V_{>0,\delta}$, while cutting the complementary subset along the edge between the core and $v$; correspondingly, there is a destabilisation of the curve, and an elliptic singularity containing strictly semistable branches.
 Tropically, pushing some of the vertices off the circle creates new finite-length edges with coordinates $\ell_v\in\RR_{\geq_0}$ (see Figure \ref{fig:off_we_go}); not all of them can be strictly positive, because the circle needs to pass through at least one vertex (of positive horizontal degree).
@@
 
-\section{Lefschetz algorithm}\label{section recursion algorithm}
+\section{Quantum Lefschetz algorithm}\label{section recursion algorithm}
 Consider a smooth pair $(X,Y)$ with $Y$ very ample, and let $P$ be the projective bundle $P=\PP_Y(\operatorname{N}_{Y|X} \oplus\OO_Y)$.

### 2019-06-27 EllipticSingularitiesSplitting.tex
More formatting improvements; fixed references, internal and external

@@
 While the higher genus situation is much more difficult, in the last several years, substantial theory has been developed towards a conceptual understanding of the genus one case.
-This began over a decade ago with the pioneering work of \tred{Li}, Vakil, and Zinger~\cite{redgone,VZ,LZ,lz2,zingerstvsred,zingred}, and was recently reinvigorated involving ideas from logarithmic geometry and singularity theory~\cite{BCM18,CM18,HL,RSPW,RSPW2,SMY1,VISC}.
+This began over a decade ago with the pioneering work of Li, Vakil, and Zinger~\cite{redgone,VZ,LZ,lz2,zingerstvsred,zingred}, and was recently reinvigorated involving ideas from logarithmic geometry and singularity theory~\cite{BCM18,CM18,HL,RSPW,RSPW2,SMY1,VISC}.
 The result is a \textit{reduced} Gromov--Witten theory, which removes certain degenerate contributions from the ordinary theory.
@@
 \subsection{Results} Our first contribution is a definition and construction of relative reduced Gromov--Witten theory of projective space relative to a hyperplane.
-The geometric content is the following, see Theorem~\ref{main-thm} for a precise statement.
+The geometric content is the following, see \S \ref{section construction} for a precise formulation.
 
@@
 
-\subsection*{Acknowledgements} We have benefited from fruitful conversations with friends and colleagues, including \tred{Francesca Carocci,} Davesh Maulik, Jonathan Wise, and [other people].
+\subsection*{Acknowledgements} We have benefited from fruitful conversations with friends and colleagues, including Francesca Carocci, Davesh Maulik, Jonathan Wise, and \tred{[other people]}.
 Important aspects of this work were completed while L.B.
@@
 
-\section{Constructions and logarithmic smoothness}
+\section{Constructions and logarithmic smoothness}\label{section construction}
 
@@
 
-\subsection{Rubber variants} In our implementation of the relative theory, we will need the ``rubber'' variant of the space of maps $
+\subsection{Rubber variants}\label{subsection rubber} In our implementation of the relative theory, we will need the ``rubber'' variant of the space of maps $
 \VZ_{1,\alpha}(\mathbb P^N|H,d)$, where the entire curve is mapped into higher levels.
@@
 
-\subsection{Virtual construction for very ample pairs}
+\subsection{Virtual construction for very ample pairs}\label{subsection virtual}
 Now let $(X,Y)$ be a smooth pair with $Y$ very ample.
@@
 \end{enumerate}
-In \S \ref{section reduced splitting axiom} we will perform this analysis in the case $k=1$.
+In \S \ref{section reduced splitting} we will perform this analysis in the case $k=1$.
 
@@
 
-\section{Splitting the boundary}
+\section{Splitting the boundary}\label{section reduced splitting}
 
 A basic phenomenon is responsible for the nature of the forthcoming analysis.
-In contrast with nodal singularities, the functions on an elliptic singularity is not simply given as a collection of functions on the normalization subject to topological gluing conditions.
+In contrast with nodal singularities, the functions on an elliptic singularity are not simply given as collections of functions on the normalisation subject to topological gluing conditions.
 As a consequence, in order to compute integrals, it is necessary to give a tautological description of this additional factorisation condition.
@@
 
-\begin{remark} The difference in dimensions between $\Dcal$ and $\Fcal^{\text{\tiny{log}}}$ (or equivalently, the difference in virtual dimensions between $\Ecal$ and $\Ecal^{\text{\tiny{log}}}$) may be interpreted as the difference in dimensions between moduli spaces of \emph{disconnected} rubber and their images under the collapsing morphisms (see \ref{} below).
+\begin{remark} The difference in dimensions between $\Dcal$ and $\Fcal^{\text{\tiny{log}}}$ (or equivalently, the difference in virtual dimensions between $\Ecal$ and $\Ecal^{\text{\tiny{log}}}$) may be interpreted as the difference in dimensions between moduli spaces of \emph{disconnected} rubber and their images under the collapsing morphisms.
 \end{remark}
@@
 such that $\Dcal \to \Ecal$ corresponds to the obvious map on fibre products.\end{lemma}
-Here the first factor in the fibre product is the logarithmic blow-up of the moduli space of rubber maps constructed in \S \ref{}.
+Here the first factor in the fibre product is the logarithmic blow-up of the moduli space of rubber maps constructed in \S \ref{subsection rubber}.
 We will compute integrals over such spaces as part of the recursion (see \S \ref{section recursion algorithm}).
@@
 \subsection{Recursion for general $(X,Y)$}\label{section recursion for general pair} We now let $(X,Y)$ be a general smooth very ample pair.
-In \S \ref{} we studied the moduli space $\VZ_{1,\alpha}(X|Y,\beta)$ of centrally aligned maps to $(X,Y)$ and equipped it with a virtual fundamental class by diagonal pull-back from $\VZ_{1,\alpha}(\PP^N|H,d)$.
+In \S \ref{subsection virtual} we studied the moduli space $\VZ_{1,\alpha}(X|Y,\beta)$ of centrally aligned maps to $(X,Y)$ and equipped it with a virtual fundamental class by diagonal pull-back from $\VZ_{1,\alpha}(\PP^N|H,d)$.
 
@@
 
-\subsection*{Step 4} Finally, consider a rubber space $\VZ_{1,\alpha}(P|Y_0+Y_\infty,\beta)_{\Gm}$ with insertion $\gamma$.
+\subsection*{Step 4} Finally, consider a rubber space $\VZ^{\leftrightarrow}_{1,\alpha}(P|Y_0+Y_\infty,\beta)$ with insertion $\gamma$.
 Suppose inductively that we have computed all absolute and relative invariants with $d^\prime \leq d$ and all rubber invariants with $(d^\prime,n^\prime,m^\prime) < (d,n,m)$.
@@
 We first note the following important reduction: if there exists a relative marking $x_k$ such that all insertions are pulled back along $\fgt_{k}$, then we may apply the projection formula, together with the fact that
-\begin{equation*} (\fgt_{k})_\st [\VZ_{1,\alpha}(P|Y_0+Y_\infty,\beta)_{\Gm}] = \alpha_k^2 \cdot [\VZ_{1,n+m-1}(Y,\beta)] \end{equation*}
+\begin{equation*} (\fgt_{k})_\st [\VZ^{\leftrightarrow}_{1,\alpha}(P|Y_0+Y_\infty,\beta)] = \alpha_k^2 \cdot [\VZ_{1,n+m-1}(Y,\beta)] \end{equation*}
 to identify the rubber invariant with a multiple of a reduced invariant of $Y$, which has the same degree and hence is known recursively.
@@
 We will deal with the general case by reducing to the one above. Consider the moduli space
-\begin{equation*}\label{step 4 recursion space} \VZ_{1,\alpha\cup (0)}(P|Y_0+Y_\infty,\beta)_{\Gm}\end{equation*}
+\begin{equation*}\label{step 4 recursion space} \VZ^{\leftrightarrow}_{1,\alpha\cup (0)}(P|Y_0+Y_\infty,\beta)\end{equation*}
 obtained by introducing a marked point $y$ with no tangency.
@@
 We will make use of a recursion formula for rubber spaces analogous to the recursion formula for relative spaces used in Steps 1--3.
-Following \cite{EKatz}, there is a line bundle $L_y^{\not\in \operatorname{bot}}$ on $\VZ_{1,\alpha\cup (0)}(P|Y_0+Y_\infty,\beta)_{\Gm}$, together with a section $s_y^{\not\in\operatorname{bot}}$ whose vanishing locus consists of the locus $\Dcal(y)$ of rubber maps where $y$ is not mapped into the bottom level of the expanded target.
-As in \S \ref{}, we can give a logarithmic interpretation of this: it corresponds to the piecewise-linear function on the tropical moduli space which associates, to every rubber tropical map, the distance between $\varphi(\sqC_y)$ and the leftmost vertex of the tropical target, where $\sqC_y$ is the vertex of the source curve containing the flag corresponding to $y$.
+Following \cite{EKatz}, there is a line bundle $L_y^{\not\in \operatorname{bot}}$ on $\VZ^{\leftrightarrow}_{1,\alpha\cup (0)}(P|Y_0+Y_\infty,\beta)$, together with a section $s_y^{\not\in\operatorname{bot}}$ whose vanishing locus consists of the locus $\Dcal(y)$ of rubber maps where $y$ is not mapped into the bottom level of the expanded target.
+As in \S \ref{Section Gathmann line bundle}, we can give a logarithmic interpretation of this: it corresponds to the piecewise-linear function on the tropical moduli space which associates, to every rubber tropical map, the distance between $\varphi(\sqC_y)$ and the leftmost vertex of the tropical target, where $\sqC_y$ is the vertex of the source curve containing the flag corresponding to $y$.
 Using this tropical description, we may easily calculate the vanshing orders of $s_y^{\not\in\operatorname{bot}}$ along the various components of $\Dcal(y)$, and show that $\cchern_1(L_y^{\not\in\operatorname{bot}}) = \Psi_0 - \ev_y^\st Y$ (see also \cite{EKatzLB}, where similar results in the non-reduced setting are obtained, using different methods).
 From this, we obtain a rubber recursion formula
-\begin{equation}\label{step 4 recursion} (\Psi_0 - \ev_y^\st Y) \tilde\gamma \cap [\VZ_{1,\alpha\cup(0)}(P|Y_0+Y_\infty,\beta)_{\Gm}] = \tilde\gamma \cap [\Dcal(y)]\end{equation}
+\begin{equation}\label{step 4 recursion} (\Psi_0 - \ev_y^\st Y) \tilde\gamma \cap [\VZ^{\leftrightarrow}_{1,\alpha\cup(0)}(P|Y_0+Y_\infty,\beta)] = \tilde\gamma \cap [\Dcal(y)]\end{equation}
 where the fundamental class $[\Dcal(y)]$ is weighted by vanishing orders on the components.
@@
 So up to recursively-known terms \eqref{step 4 recursion} becomes
-\begin{equation*} \fgt_1^\st (-\alpha_2\psi_2 - \ev_y^\st Y)\tilde\gamma \cap [\VZ_{1,\alpha\cup(0)}(P|Y_0+Y_\infty,\beta)_{\Gm}] = \tilde\gamma\cap[\Dcal(y)]\end{equation*}
+\begin{equation*} \fgt_1^\st (-\alpha_2\psi_2 - \ev_y^\st Y)\tilde\gamma \cap [\VZ^{\leftrightarrow}_{1,\alpha\cup(0)}(P|Y_0+Y_\infty,\beta)] = \tilde\gamma\cap[\Dcal(y)]\end{equation*}
 and now the left-hand side is also recursively known, by the projection formula.

### 2019-06-27 EllipticSingularitiesSplitting.tex
changed notation in lemma on moduli of attachments

--- 2019-06-27 EllipticSingularitiesSplitting.tex
@@
 \begin{lemma}
- Generically on $\Ecal$, $\widetilde \Dcal\to\widetilde\Ecal$ is isomorphic to $\mathcal P=\PP_{\widetilde\Ecal}(\bigoplus_{v\in \{V_{0,\delta}\}\cup V_{>0,\delta}}\OO(\delta_v))$.
+ Generically on $\Ecal$, $\widetilde \Dcal\to\widetilde\Ecal$ is given by an explicit projective bundle.
 \end{lemma}
@@
 \begin{proof}
- All of the line bundles $\OO(\delta_v)$ share a common factor $\mathbb T_E$, the universal tangent line to the elliptic curve.
-By removing this factor, we see that when the dual graph is fixed, $\OO(\delta_v)$ is isomorphic to the tangent line to the rational tail $R_v$ at the gluing node $q_v$.
-We make the caveat here that(with the caveat that all those corresponding to $V_{0,\delta}$ are canonically identified).
-This is the open stratum of the moduli space of attaching data \cite[\S\S 2.2-2.3]{SMY2}.
-On the fiber boundary, the circle of radius $\delta$ will pass through a subset of $\{V_{0,\delta}\}\cup V_{>0,\delta}$, while cutting the complementary subset along the edge between the core and $v$; correspondingly, there is a destabilisation of the curve, and an elliptic singularity containing strictly semistable branches.
-Tropically, pushing some of the vertices off the circle creates new finite-length edges with coordinates $\ell_v\in\RR_{\geq_0}$ (see Figure \ref{fig:off_we_go}); not all of them can be strictly positive, because the circle needs to pass through at least one vertex (of positive horizontal degree).
-This is patently the fan of a projective space.
+Let us assume that the curve does not degenerate, so that the dual graph is as prescribed by $\Delta$, in particular there are components $\sqC_1,\ldots\sqC_r$ generically lying on the circle of radius $\delta$; the moduli space of attachments for the elliptic singularity is the complement of the coordinate hyperplanes in $\PP(\bigoplus_{i=1}^rT_{q_i}C_i)$.
+On the boundary, the circle is allowed to miss some of the $\sqC_i$ - but not all of them!
+-, cutting the edge between them and the core (correspondingly, there is a destabilisation of the curve, and an elliptic singularity containing strictly semistable branches).
+Tropically, pushing some of the vertices off the circle creates new finite-length edges with coordinates $\ell_i\in\RR_{\geq_0}$ (see Figure \ref{fig:off_we_go}).
+Since not all of them can be strictly positive, this represents the fan of a projective space.
 \end{proof}

### 2019-06-27 EllipticSingularitiesSplitting.tex
Normalising more notation

--- 2019-06-27 EllipticSingularitiesSplitting.tex
@@
 \newcommand{\HH}{\operatorname{H}}
+\newcommand{\Glog}{\mathbb{G}_{\mathrm{log}}}
 \newcommand{\Achow}{\operatorname{A}}
@@
 
-\section*{Introduction}
+\setcounter{section}{-1}
+\section{Introduction}
 
@@
 \subsection{The absolute case} Let $\mathfrak M_{1,n}$ be the logarithmic algebraic stack of $n$-pointed prestable curves of genus $1$.
-Let $C$ be a logarithmically smooth curve over $S$, let $\plC$ denote its tropicalization, and let $\lambda$ be the section of $\overline{M}_{C/S}$ giving the distance from each vertex to the minimal genus one subcurve.
-
-We begin by recalling the logarithmic moduli spaces of genus $1$ curves constructed in~\cite[Sections 2 \& 4]{RSPW}.
+Let $C$ be a logarithmically smooth curve over $S$, let $\plC$ denote its tropicalization, and let $\lambda$ be the section of $\overline{M}_{C/S}$ given by the distance from each vertex to the minimal genus one subcurve.
+
+We begin by recalling the logarithmic moduli spaces of genus $1$ curves constructed in~\cite[\S\S 2 \& 4]{RSPW}.
 Given a family of tropical curves over a base $\sigma$, a central alignment is a piecewise-linearly varying choice of radius $\delta_s\in \overline{M}_S$ for $s\in\sigma$, together with a consistent ordering of the vertices that lie inside the circle of radius $\delta_s$ around the core.
@@
 
-{In essence, this is a family of curves where every vertex of the tropical curve $\plC$ is either inside or outside the circle of radius $\delta$ around the core genus $1$ subcurve.}
+\tred{In essence, this is a family of curves where every vertex of the tropical curve $\plC$ is either inside or outside the circle of radius $\delta$ around the core genus $1$ subcurve.}
 
@@
 
-\subsection{Relative geometry: compactification} Fix a hyperplane $H\subset \mathbb P^N$.
+\subsection{Relative geometry: compactification} Fix a hyperplane $H\subseteq \mathbb P^N$.
 Let $\alpha$ be a partition of the degree $d>0$.
@@
 We refer to these latter components as \textbf{the higher levels}.
-Thus, we will say that a subcurve $D\subset C$ maps to \textbf{higher level} if the collapsed map
+Thus, we will say that a subcurve $D\subseteq C$ maps to \textbf{higher level} if the collapsed map
 \[
@@
 \[
-\mathrm{Def}(C,f_B)\to \mathrm{Obs}(f/(C,f_B)) = H^1(\overline{C}_F,\mathcal O_{\overline{C}_F}),
+\mathrm{Def}(C,f_B)\to \mathrm{Obs}(f/(C,f_B)) = \HH^1(\overline{C}_F,\mathcal O_{\overline{C}_F}),
 \]
@@
 
-We note the manner in which the group $H^1(\overline{C}_F,\mathcal O_{\overline{C}_F})$ functions as the obstruction group for the lifting.
+We note the manner in which the group $\HH^1(\overline{C}_F,\mathcal O_{\overline{C}_F})$ functions as the obstruction group for the lifting.
 It suffices to work near the minimal genus $1$ subcurve $D_F$ of $C$, since the rest of the curve is rational.
@@
 Given a strict square-zero extension $S'$ of $S$, the piecewise linear function $\alpha$ extends uniquely by strictness to any deformation of the curve.
-The resulting deformation of $\mathcal O_{C}(-\alpha)$ produces an infinitesimal deformation of the trivial bundle in the Picard group, whose class in $H^1(\overline{C}_F,\mathcal O_{\overline{C}_F})$, is the obstruction to deformation.
+The resulting deformation of $\mathcal O_{C}(-\alpha)$ produces an infinitesimal deformation of the trivial bundle in the Picard group, whose class in $\HH^1(\overline{C}_F,\mathcal O_{\overline{C}_F})$, is the obstruction to deformation.
 We will show that it is possible to choose a deformation of $(C,f_B)$ that cancels out the obstruction to lifting to $f$, and thus the map to the obstruction space above is surjective.
@@
 To prove this, it is convenient to work with the logarithmic multiplicative group and its torsors.
-Recall that the \textit{logarithmic multiplicative group} $\mathbb G_{\mathrm{log}}$ is the functor on logarithmic schemes whose value on a logarithmic scheme $S$ is the group of global sections $H^0(S,M_S^{\mathrm{gp}})$; \tred{it is a proper group functor, and it contains $\Gm$ as a subfunctor}.
+Recall that the \textit{logarithmic multiplicative group} $\mathbb G_{\mathrm{log}}$ is the functor on logarithmic schemes whose value on a logarithmic scheme $S$ is the group of global sections $\HH^0(S,M_S^{\mathrm{gp}})$; \tred{it is a proper group functor, and it contains $\Gm$ as a subfunctor}.
 This functor is representable only after a logarithmically \'etale cover.
@@
 
-The bundle $\mathbb P\to \mathbb P^{N-1}$ gives rise to a $\mathbb G_{\operatorname{m}}$-torsor by deleting the zero and infinity sections.
+\marginnote{Bundle can have higher levels, so should rephrase this}The bundle $\mathbb P\to \mathbb P^{N-1}$ gives rise to a $\mathbb G_{\operatorname{m}}$-torsor by deleting the zero and infinity sections.
 Replacing these fibres by their $\mathbb G_{\mathrm{log}}$ compactifications, we obtain a non-representable functor on logarithmic schemes $\mathbb P_{\mathrm{log}}$ and a logarithmically \'etale modification
@@
 It is representable after a logarithmically \'etale modification by a family of nodal curves.
-It follows that the space  $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}}/\mathbb G_{\mathrm{log}})$ of maps up to translation that factorise completely is logarithmically smooth.
-
-To conclude the main result, we compare the stacks $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}}/\mathbb G_{\mathrm{log}})$ and  $\VZ_{1,\alpha}(\mathbb P/\mathbb G_{\operatorname{m}})$.
-Since a map to $\mathbb P$ gives rise immediately to a map to $\mathbb P_{\mathrm{log}}$, there is a morphism
+It follows that the space $\VZ^{\leftrightarrow}_{1,\alpha}(\mathbb P_{\mathrm{log}},d)$ of maps up to $\Glog$-translation that factorise completely is logarithmically smooth.
+
+To conclude the main result, we compare the stacks $\VZ^{\leftrightarrow}_{1,\alpha}(\mathbb P_{\mathrm{log}},d)$ and  $\VZ^{\leftrightarrow}_{1,\alpha}(\mathbb P|H_0+H_\infty,d)$.
+Since a map to $(\mathbb P,H_0+H_\infty)$ gives rise immediately to a map to $\mathbb P_{\mathrm{log}}$, there is a morphism
 \[
-\VZ_{1,\alpha}(\mathbb P/\mathbb G_{\operatorname{m}})\to \VZ_{1,\alpha}(\mathbb P_{\mathrm{log}}/\mathbb G_{\mathrm{log}}).
+\VZ^{\leftrightarrow}_{1,\alpha}(\mathbb P|H_0+H_\infty,d)\to \VZ^{\leftrightarrow}_{1,\alpha}(\mathbb P_{\mathrm{log}},d).
 \]
@@
 
-\begin{lemma} \label{Lemma components are logarithmic divisors} Every irreducible component of $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ is a codimension $1$ log stratum.\end{lemma}
-
-\begin{proof} The locus where the log structure is trivial coincides precisely with the  locus where the source curve is smooth, and consequently not mapped inside $H$.
+\begin{lemma} \label{Lemma components are logarithmic divisors} Every irreducible component of $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ is a codimension $1$ logarithmic stratum.\end{lemma}
+
+\begin{proof} The locus where the logarithmic structure is trivial coincides precisely with the  locus where the source curve is smooth, and consequently not mapped inside $H$.
 Since $\VZ_{1,\alpha}(\PP^N|H,d)$ is toroidal this locus is open and dense.
@@
 \begin{equation*} \Dcal = \widetilde\Dcal \cap \VZ_{1,\alpha}(\PP^N|H,d) \end{equation*}
-for a unique log stratum $\widetilde\Dcal \subseteq \widetilde{\VZ}_{1,\alpha}(\PP^N|H,d)$. Since
+for a unique logarithmic stratum $\widetilde\Dcal \subseteq \widetilde{\VZ}_{1,\alpha}(\PP^N|H,d)$. Since
 \begin{equation*}\widetilde{\VZ}_{1,\alpha}(\PP^N|H,d) \to \ol\Mcal_{1,\alpha}(\PP^N|H,d)\end{equation*}
-is a log modification, the divisor $\widetilde{\Dcal}$ is either exceptional or the strict transform of a logarithmic divisor.
+is a logarithmic modification, the divisor $\widetilde{\Dcal}$ is either exceptional or the strict transform of a logarithmic divisor.
 These two cases correspond, respectively, to when the core is assigned zero degree or nonzero degree by the combinatorial type.
@@
 
-\begin{proof} Let $\sigma \in \Sigma$ be the cone corresponding to the $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$.
+\begin{proof} Let $\sigma \in \Sigma_{1,\alpha}(\PP^N|H,d)$ be the cone corresponding to the $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$.
 By the discussion above $\Dcal$ corresponds to a ray in the subdivision of $\sigma$ given by imposing the central alignment condition.
@@
 For the remainder of this subsection, therefore, we fix a one-dimensional cone $\tau \in \Sigma_{1,\alpha}(\PP^N|H,d)$, let $\Dcal \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$ be the associated logarithmic divisor, and assume that $\Dcal$ is contained in $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ and is of type $A,B$ or $C^+$.
-We let $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$ be the log stratum into which $\Dcal$ is mapped; this is indexed by a cone $\epsilon \in \Sigma$ corresponding to a combinatorial type $\Delta$, and $\epsilon$ is one-dimensional since we are restricting to the type $A,B,C^+$ cases.
+We let $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$ be the logarithmic stratum into which $\Dcal$ is mapped; this is indexed by a cone $\epsilon \in \Sigma^{\Kim}$ corresponding to a combinatorial type $\Delta$, and $\epsilon$ is one-dimensional since we are restricting to the type $A,B,C^+$ cases.
 
@@
 The second morphism is a toroidal modification.
-Let $\tau \in \Sigma$ be a ray corresponding to $\Dcal \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$, and to the virtual divisor $\widetilde \Dcal \subseteq \widetilde{\VZ}_{1,\alpha}(\PP^N|H,d)$.
+Let $\tau \in \Sigma_{1,\alpha}(\PP^N|H,d)$ be the ray corresponding to $\Dcal \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$, and to the virtual divisor $\widetilde \Dcal \subseteq \widetilde{\VZ}_{1,\alpha}(\PP^N|H,d)$.
 \medskip
@@
 \noindent
-{\bf Logarithmic structures on strata.} Let $W\subset X$ be an irreducible stratum in a toroidal embedding $X$.
+{\bf Logarithmic structures on strata.} Let $W\subseteq X$ be an irreducible stratum in a toroidal embedding $X$.
 The stratum itself is toroidal, and hence logarithmically smooth.
@@
 where $ \mathcal A_X$ is the Artin fan of $X$, which is a toroidal Artin stack.
-If $W\subset X$ maps to a stratum $\mathcal A_W$ under this map, the pullback of the logarithmic structure from $\mathcal A_W$ to $W$ endows the stratum with a logarithmic structure.
+If $W\subseteq X$ maps to a stratum $\mathcal A_W$ under this map, the pullback of the logarithmic structure from $\mathcal A_W$ to $W$ endows the stratum with a logarithmic structure.
 Note that the inclusion of a stratum $W\hookrightarrow X$ is \textit{not} a logarithmic morphism.
@@
 \[
-\widetilde{\Dcal}^{\mathrm{trop}}\to \Ecal^{\mathrm{trop}}.
+\Sigma\widetilde{\Dcal}\to \Sigma\Ecal.
 \]
@@
 
-We keep in mind the fibre product description of $\Ecal$. Construct a modification $\widetilde \Ecal$ from $\Ecal$ as follows.
-
+We keep in mind the fibre product description of $\Ecal$. Construct a modification $\widetilde \Ecal$ from $\Ecal$ as follows:
 \begin{enumerate}

### 2019-06-28 EllipticSingularitiesSplitting.tex
reintegrated some lemmas

--- 2019-06-27 EllipticSingularitiesSplitting.tex
@@
 Let $\Dcal$ be a locus of type IIIb with combinatorial type $\Delta$ which contributes nontrivially to the Gromov--Witten invariant.
-For every nonzero vertex $\diamond$ of the tropical target, the fibre of the tropical map over $\diamond$ contains exactly one stable vertex, which lies on the radius.
+For every nonzero vertex $\diamond$ of the tropical target, the fibre of the tropical map over $\diamond$ contains exactly one stable vertex, which either is the core, or lies on the circle.
+Besides, the maximal contact order at the core is $m>1$.
 \end{lemma}
@@
 
-For each vertex of the target there must always be at least one vertex in the preimage which lies on the radius.
+For each vertex of the target there must always be at least one vertex in the preimage which lies on the circle.
 This is implied by the fact that the combinatorial type $\Delta$ is a ray.
-In fact, we make the stronger assertion that the stable vertex mapping to $\diamond$ lies on the radius.
-The alternative is that a vertex dual to a trivial bubble lies on the radius.
-This latter condition implies that $\Dcal \to \Ecal$ has positive-dimensional fibres, so the contribution vanishes.
+If the vertex on the circle is strictly semistable - in particular the collapsed map $f_B$ is constant along the corresponing component -, it can be seen that the factorisation condition is unaffected by $\Gm$-scaling the coordinate corresponding to that vertex in the moduli space of attachments, so the map $\Dcal\to\Ecal$ has generic fiber of positive dimension.
+
+In particular, notice that vertices lying on the circle and tropically mapped to $0\in\mathbb R_{\geq0}$ all have the same contact order at the core, because by the previous paragraph we may assume that only strictly semistable vertices are encountered on these paths.
+For the same reason, this contact order $m$ is maximal among those of the edges adjacent to the core.
+
+Finally, in case the maximal contact order is $m=1$, the image tangent vectors must be linearly dependent, in which case we can deduce as above that factorisation will be satisfied indepedently of the choice of alignment.
 \end{proof}
@@
 \]
-is a logarithmic morphism. The generic fiber of this morphism is toric variety.  \medskip
+is a logarithmic morphism. The generic fiber of this morphism is a toric variety.  \medskip
 
@@
 
-This procedure induces a logarithmic modification $\widetilde\Ecal \to \Ecal$ which admits a modular description as a fibre product of genus zero centrally aligned maps coming from the vertices $\sqC_1,\ldots,\sqC_r$, and genus one aligned rubber maps satisfying fibre-direction factorisation from the vertex $\sqC_0$).
+This procedure induces a logarithmic modification $\widetilde\Ecal \to \Ecal$ which admits a modular description as a fibre product of genus zero centrally aligned maps coming from the vertices $\sqC_1,\ldots,\sqC_r$, and genus one aligned rubber maps satisfying fibre-direction factorisation from the vertex $\sqC_0$.
 
@@
 
-\begin{lemma}
+\begin{lemma}\label{lem:generic_proj_bundle}
  Generically on $\Ecal$, $\widetilde \Dcal\to\widetilde\Ecal$ is given by an explicit projective bundle.
@@
 \begin{proof}
-Let us assume that the curve does not degenerate, so that the dual graph is as prescribed by $\Delta$, in particular there are components $\sqC_1,\ldots\sqC_r$ generically lying on the circle of radius $\delta$; the moduli space of attachments for the elliptic singularity is the complement of the coordinate hyperplanes in $\PP(\bigoplus_{i=1}^rT_{q_i}C_i)$.
+Let us assume that the curve does not degenerate, so that the dual graph is as prescribed by $\Delta$, in particular there are components $\sqC_1,\ldots,\sqC_r$ generically lying on the circle of radius $\delta$; the moduli space of attachments for the elliptic singularity is the complement of the coordinate hyperplanes in $\PP(\bigoplus_{i=1}^rT_{q_i}C_i)$.
 On the boundary, the circle is allowed to miss some of the $\sqC_i$ - but not all of them!
@@
 Since not all of them can be strictly positive, this represents the fan of a projective space.
+
+A slight modification of this argument is required to account for the fact that all vertices that lie on the circle and are mapped to $0\in\mathbb R_{\geq0}$ by the tropical map are generically aligned on $\Ecal$: indeed, by Lemma \ref{lemma type C0 combinatorial types}, they all have the same contact order $m$, therefore their $T_{q_i}C_i^{\otimes m}$ can be identified via the target tangent line on the fiber product \eqref{IIIa fibre product}, and, after saturation, the $T_{q_i}C_i$ themselves are canonically isomorphic on $\Ecal$.
+Thus, only one factor should be taken to represent all of them in the projective bundle above.
 \end{proof}
@@
 
-We said that $C_i^\prime$ is \emph{a} component of $C_i$ which lies on the radius.
-There may be more than one, but if this is the case then their tangent spaces are naturally identified.
+We said that $C_i^\prime$ is \emph{a} component of $C_i$ which lies on the radius. There may be more than one, but if this is the case then their tangent spaces are naturally identified.
+
+The following construction allows us to give a canonical description of $\Dcal$ inside $\widetilde\Dcal$.
+Over $\widetilde\Dcal$ there is a natural section of the projective bundle $\PP(F) \to \widetilde\Dcal$ (obtained by projectivising the diagonal embedding).
+We may then pullback to $\widetilde\Dcal$ the map of vector bundles
+\begin{equation}\label{eq:factorisation} \OO_{\PP(F)}(-1)(-\TT_{C_0}) \xrightarrow{\text{can}(-\TT_{C_0})} \pi^\st F(-\TT_{C_0}) \xrightarrow{\pi^*\sum\operatorname{d}f} \pi^\st(\ev_q^\st \TT_H),\end{equation}\footnote{We may assume the latter factors through $\ev_q^\st \TT_H\subseteq\ev_q^\st \TT_{\PP^N}$ by virtue of Lemma \ref{lemma type C0 combinatorial types}.}
+whose vanishing tautologically expresses the condition that the stable map $f$ descend to the elliptic singularity associated to a point of $\widetilde\Dcal$.
+Thus, the class of $\Dcal$ can be represented via an Euler class computation.
+Note that the vector bundle $F$ can be explicitly realised by twisting the pullback of $\bigoplus_{i=1}^rT_{q_i}C_i$ from $\Ecal$ with a number of exceptional boundary corrections.
+
+\begin{comment}
 We obtain a natural morphism
@@
 {\bf \color{red} More needs to be said here.}
+\end{comment}
 
@@
 \end{example}
+
+To establish a more direct connection with the geometry of the fibre product \eqref{IIIa fibre product}, recall that $\widetilde\Ecal$ has been built as an explicit modification of a finite cover of \eqref{IIIa fibre product}.
+For every $v\in\{\sqC_1,\ldots,\sqC_r\}$ - with the convention established at the end of Lemma \ref{lem:generic_proj_bundle} -, on $\widetilde\Ecal$ it makes sense to consider the line bundle $\OO(\delta_v)$ associated to a shortest path from the core to the circle in the $v$-direction.
+Construct $\mathcal P=\PP_{\widetilde\Ecal}(\bigoplus_{v\in \{\sqC_1,\ldots,\sqC_r\}}\OO(\delta_v))$; since $\sqC_1,\ldots,\sqC_r$ are always ordered on $\widetilde \Dcal$ (they may lie on the circle, be the first component off the circle, or degenerate and lie in the strict interior), there is a morphism $\widetilde \Dcal\to\mathcal P$ lifting $\widetilde \Dcal\to\widetilde\Ecal$.
+Consider the map of vector bundles on $\mathcal P$ (analogous to \eqref{eq:factorisation}):
+\[ \OO_{\mathcal P}(-1)\to p^*(\bigoplus_{v\in \{\sqC_1,\ldots,\sqC_r\}}\OO(\delta_v))\xrightarrow{\sum\operatorname{d}f}\ev_{C_0}^*T_H.\]
+
+The composite, regarded as a section $s$ of $G=\OO_{\mathcal P}(1)\otimes \operatorname{ev}_{C_0}^*(T_H)$, vanishes precisely where $f$ factors through the Smyth's singularity determined by the point in the fiber of $p$.
+Generically on $\widetilde\Ecal$, this is exactly what we are after - compare with Lemma \ref{lem:generic_proj_bundle}.
+On the boundary, though, it may happen that a simultaneous degeneration in the base and the fiber makes this factorisation trivial, in the sense that $\bar f$ would be constant on all the branches of the elliptic singularity.
+
+\begin{lemma}
+ For every $\Lambda_B\subseteq \{\sqC_1,\ldots,\sqC_r\}$ and $\Lambda_F=\{\sqC_1,\ldots,\sqC_r\}\setminus \Lambda_B$, $s$ vanishes along the loci where the factors corresponding to $\Lambda_B$ in $\widetilde \Ecal$ degenerate so that $f_i\colon C_i\to\PP^N$ is constant in a neighbourhood of $q_i$, and the fiber coordinates $(\lambda_j)_{j\in\Lambda_F}$ along $p\colon\mathcal P\to\widetilde \Ecal$ are set to be $0$.
+\end{lemma}
+Call these loci $\Xi_i,i\in I$ (compare with \cite[\S 3.2]{VZ} for an analogous phenomenon in the non-relative case); clearly, they may be in excess with respect to the expected codimension of $V(s)$, that is $N-1$.
+These loci are logarithmic substrata; therefore, there exists a logarithmic blow-up that principalizes them.
+We claim that $\widetilde\Dcal$ is (possibly a refinement of) such a blow-up.
+\begin{lemma}
+ The pullback of $\Xi_i$ is principal in $\widetilde\Dcal$.
+\end{lemma}
+\begin{proof}
+ Let us analyse the ideal of $\Xi_i$: it is generated by
+ \begin{enumerate}[leftmargin=.5 cm]
+  \item equations on $\widetilde\Ecal$ cutting the locus where $C_i$ degenerates so that $f_i$ is constant on a neighbourhood of $q_v$, $i\in \Lambda_B$: these correspond to the tropical functions $\delta_i-\operatorname{dist}(q_i,\circ)$;
+  \item equations on the fiber of $p$ for the linear subspace corresponding to $j\in \Lambda_F$: tropically, these correspond to the $\ell_j$ discussed above.
+ \end{enumerate}
+By construction, on $\widetilde \Dcal$ it is always possible to tell which of these tropical lengths is the shortest (the circle we have drawn on $\Xi$ is degenerate - it passes through no vertex of positive horizontal degree -, therefore we need to decide for a strictly larger circle in order to lift to $\widetilde D$), which corresponds to principalising the ideal (see Figure \ref{fig:principalisation}).
+\end{proof}
+
+\begin{figure}
+\includegraphics[scale=.5]{principalisation}
+\caption{On the left, a generic point of $\mathcal P$.
+On the right, a point of $\Xi$.
+The dotted circle is the one we draw on $\mathcal P$.
+The continuous circle represents one of the possible choices of $\delta$ enlarging the dotted one (a stratum of $\widetilde\Dcal$).}\label{fig:principalisation}
+\end{figure}
+
+Finally, on $\widetilde\Dcal$ (or, in fact, on an intermediate blow-up $\widetilde{\mathcal P}\to\mathcal P$) there are exceptional divisors $\widetilde \Xi_i$ corresponding to $\Xi_i$ in $\mathcal P$.
+Since the $\Xi_i$ exhaust all the excess-dimensional components of the vanishing locus of $s\in\Gamma(\mathcal P,G)$, the latter induces a section $\tilde s\in\Gamma(\widetilde\Dcal,G(-\sum_i\widetilde\Xi_i))$ by pullback and twisting, whose vanishing locus is dimensionally transverse to the boundary, and whose open part coincides with the generic point of $\Dcal$, therefore $V(\tilde s)=\Dcal$.
+
+Expressing the pushforward of the Chern classes of $\OO_F(1)$ and $\OO(\widetilde\Xi_i)$ in terms of tautological classes on the fiber product underlying $\Ecal$, we get:
+\begin{cor}
+ After pushforward to $\Ecal$, the contribution of $\Dcal$ to the invariants can be computed in terms of tautological integrals on moduli spaces of maps with lower numerics.
+\end{cor}
 

### 2019-06-28 EllipticSingularitiesSplitting.tex
minor changes

@@
 
-\subsection*{Acknowledgements} We have benefited from fruitful conversations with friends and colleagues, including \tred{Francesca Carocci,} Davesh Maulik, Jonathan Wise, and [other people].
+\subsection*{Acknowledgements} We have benefited from fruitful conversations with friends and colleagues, including \tred{Francesca Carocci, Cristina Manolache,} Davesh Maulik, Jonathan Wise, and [other people].
 Important aspects of this work were completed while L.B.

### 2019-06-28 EllipticSingularitiesSplitting.tex

--- 2019-06-27 EllipticSingularitiesSplitting.tex
@@
 
-Our analysis leads naturally to the study of a ``main component’’ double ramification cycle for target manifolds in genus one.
+\tred{We rephrase Gathmann's idea of increasing the tangency requirement within the framework of logarithmic stable maps (where maximal tangency is always assumed) by introducing \emph{fictitious markings}, and identifying the space of maps with higher contact order with a boundary stratum inside that of lower contact order and more (fictitious) markings.}
+
+Our analysis leads naturally to \tred{the} study of a ``main component’’ double ramification cycle for target manifolds in genus one.
 The virtual geometry of this was studied in recent work of Janda, Pandharipande, Pixton, and Zvonkine~\cite{DRCBundle}.
-We do not know how to calculate a closed formula for this main component contribution, but we repurpose E.~Katz's topological recursion relations \cite{EKatz} to complete the algorithm.
+We do not know how to calculate a \tred{closed formula} for this main component contribution, but we repurpose E.~Katz's topological recursion relations \cite{EKatz} to complete the algorithm.
 We note that even in genus one, an understanding of the main component contributions of the double ramification cycle for target manifolds would be interesting.
@@
 
-\subsection*{Acknowledgements} We have benefited from fruitful conversations with friends and colleagues, including Francesca Carocci, Davesh Maulik, Jonathan Wise, and \tred{[other people]}.
+\subsection*{Acknowledgements} We have benefited from fruitful conversations with friends and colleagues, including Francesca Carocci, Cristina Manolache, Davesh Maulik, Jonathan Wise, and [other people].
 Important aspects of this work were completed while L.B.
@@
 were visiting MIT in Spring 2018 and the University of Cambridge in Winter 2019, and we thank these institutions for their hospitality.
-\tred{L.B.
-would like to thank Imperial College London, the LSGNT, the Royal Society, 3CinG, the MSRI program ''Enumerative Geometry beyond Numbers``, and MPIM-Bonn for support.}
+L.B.
+would like to thank Imperial College London, the LSGNT, the Royal Society, 3CinG, the MSRI program ''Enumerative Geometry beyond Numbers``, and MPIM-Bonn for support.
 
@@
 
-The above theorem guarantees that the singularities of the space of totally factorised maps to expansions is logarithmically smooth.
-In fact, one can say more in this case.\marginpar{I don't understand the point of this Cor.
-Can we make it into a short remark?}
+The above theorem guarantees that the singularities of the space of totally factorised maps to expansions is logarithmically smooth. In fact, one can say more in this case.
 
@@
 \]
-is a logarithmic morphism. The generic fibre of this morphism is toric variety.  \medskip
+
+is a logarithmic morphism. The generic fiber of this morphism is a toric variety.  \medskip
 
@@
 
-This procedure induces a logarithmic modification $\widetilde\Ecal \to \Ecal$ which admits a modular description as a fibre product of genus zero centrally aligned maps coming from the vertices $\sqC_1,\ldots,\sqC_r$, and genus one aligned rubber maps satisfying fibre-direction factorisation from the vertex $\sqC_0$).
-We have thus produced a factorisation
+This procedure induces a logarithmic modification $\widetilde\Ecal \to \Ecal$ which admits a modular description as a fibre product of genus zero centrally aligned maps coming from the vertices $\sqC_1,\ldots,\sqC_r$, and genus one aligned rubber maps satisfying fibre-direction factorisation from the vertex $\sqC_0$.
+
+By construction, we have a map $\widetilde\Dcal \to \widetilde\Ecal$ which is a compactification of a torus bundle over $\widetilde\Ecal$.
+The strata of $\widetilde\Dcal$ can be read off from its tropicalisation, and in particular we have the information of how (polynomials in) the classes of boundary strata push forward to $\widetilde\Ecal$.
+
+We have produced a factorization
 \begin{equation*}\widetilde\Dcal\to\widetilde \Ecal\to\Ecal,
@@
 
-\begin{lemma}
- Generically on $\Ecal$, $\widetilde \Dcal\to\widetilde\Ecal$ is isomorphic to $\mathcal P=\PP_{\widetilde\Ecal}(\bigoplus_{v\in \{V_{0,\delta}\}\cup V_{>0,\delta}}\OO(\delta_v))$.
+\begin{lemma}\label{lem:generic_proj_bundle}
+ Generically on $\Ecal$, $\widetilde \Dcal\to\widetilde\Ecal$ is given by an explicit projective bundle.
 \end{lemma}
@@
 \begin{proof}
- All of the line bundles $\OO(\delta_v)$ share a common factor $\mathbb T_E$, the universal tangent line to the elliptic curve.
-By removing this factor, we see that when the dual graph is fixed, $\OO(\delta_v)$ is isomorphic to the tangent line to the rational tail $R_v$ at the gluing node $q_v$.
-We make the caveat here that(with the caveat that all those corresponding to $V_{0,\delta}$ are canonically identified).
-This is the open stratum of the moduli space of attaching data \cite[\S\S 2.2-2.3]{SMY2}.
-On the fibre boundary, the circle of radius $\delta$ will pass through a subset of $\{V_{0,\delta}\}\cup V_{>0,\delta}$, while cutting the complementary subset along the edge between the core and $v$; correspondingly, there is a destabilisation of the curve, and an elliptic singularity containing strictly semistable branches.
-Tropically, pushing some of the vertices off the circle creates new finite-length edges with coordinates $\ell_v\in\RR_{\geq_0}$ (see Figure \ref{fig:off_we_go}); not all of them can be strictly positive, because the circle needs to pass through at least one vertex (of positive horizontal degree).
-This is patently the fan of a projective space.
+Let us assume that the curve does not degenerate, so that the dual graph is as prescribed by $\Delta$, in particular there are components $\sqC_1,\ldots,\sqC_r$ generically lying on the circle of radius $\delta$; the moduli space of attachments for the elliptic singularity is the complement of the coordinate hyperplanes in $\PP(\bigoplus_{i=1}^rT_{q_i}C_i)$.
+On the boundary, the circle is allowed to miss some of the $\sqC_i$ - but not all of them!
+-, cutting the edge between them and the core (correspondingly, there is a destabilisation of the curve, and an elliptic singularity containing strictly semistable branches).
+Tropically, pushing some of the vertices off the circle creates new finite-length edges with coordinates $\ell_i\in\RR_{\geq_0}$ (see Figure \ref{fig:off_we_go}).
+Since not all of them can be strictly positive, this represents the fan of a projective space.
+
+A slight modification of this argument is required to account for the fact that all vertices that lie on the circle and are mapped to $0\in\mathbb R_{\geq0}$ by the tropical map are generically aligned on $\Ecal$: indeed, by Lemma \ref{lemma type C0 combinatorial types}, they all have the same contact order $m$, therefore their $T_{q_i}C_i^{\otimes m}$ can be identified via the target tangent line on the fiber product \eqref{IIIa fibre product}, and, after saturation, the $T_{q_i}C_i$ themselves are canonically isomorphic on $\Ecal$.
+Thus, only one factor should be taken to represent all of them in the projective bundle above.
 \end{proof}
@@
 
+To establish a more direct connection with the geometry of the fibre product \eqref{IIIa fibre product}, recall that $\widetilde\Ecal$ has been built as an explicit modification of a finite cover of \eqref{IIIa fibre product}.
+For every $v\in\{\sqC_1,\ldots,\sqC_r\}$ - with the convention established at the end of Lemma \ref{lem:generic_proj_bundle} -, on $\widetilde\Ecal$ it makes sense to consider the line bundle $\OO(\delta_v)$ associated to a shortest path from the core to the circle in the $v$-direction.
+Construct $\mathcal P=\PP_{\widetilde\Ecal}(\bigoplus_{v\in \{\sqC_1,\ldots,\sqC_r\}}\OO(\delta_v))$; since $\sqC_1,\ldots,\sqC_r$ are always ordered on $\widetilde \Dcal$ (they may lie on the circle, be the first component off the circle, or degenerate and lie in the strict interior), there is a morphism $\widetilde \Dcal\to\mathcal P$ lifting $\widetilde \Dcal\to\widetilde\Ecal$.
+Consider the map of vector bundles on $\mathcal P$ (analogous to \eqref{eq:factorisation}):
+\[ \OO_{\mathcal P}(-1)\to p^*(\bigoplus_{v\in \{\sqC_1,\ldots,\sqC_r\}}\OO(\delta_v))\xrightarrow{\sum\operatorname{d}f}\ev_{C_0}^*T_H.\]
+
+The composite, regarded as a section $s$ of $G=\OO_{\mathcal P}(1)\otimes \operatorname{ev}_{C_0}^*(T_H)$, vanishes precisely where $f$ factors through the Smyth's singularity determined by the point in the fiber of $p$.
+Generically on $\widetilde\Ecal$, this is exactly what we are after - compare with Lemma \ref{lem:generic_proj_bundle}.
+On the boundary, though, it may happen that a simultaneous degeneration in the base and the fiber makes this factorisation trivial, in the sense that $\bar f$ would be constant on all the branches of the elliptic singularity.
+
+\begin{lemma}
+ For every $\Lambda_B\subseteq \{\sqC_1,\ldots,\sqC_r\}$ and $\Lambda_F=\{\sqC_1,\ldots,\sqC_r\}\setminus \Lambda_B$, $s$ vanishes along the loci where the factors corresponding to $\Lambda_B$ in $\widetilde \Ecal$ degenerate so that $f_i\colon C_i\to\PP^N$ is constant in a neighbourhood of $q_i$, and the fiber coordinates $(\lambda_j)_{j\in\Lambda_F}$ along $p\colon\mathcal P\to\widetilde \Ecal$ are set to be $0$.
+\end{lemma}
+Call these loci $\Xi_i,i\in I$ (compare with \cite[\S 3.2]{VZ} for an analogous phenomenon in the non-relative case); clearly, they may be in excess with respect to the expected codimension of $V(s)$, that is $N-1$.
+These loci are logarithmic substrata; therefore, there exists a logarithmic blow-up that principalizes them.
+We claim that $\widetilde\Dcal$ is (possibly a refinement of) such a blow-up.
+\begin{lemma}
+ The pullback of $\Xi_i$ is principal in $\widetilde\Dcal$.
+\end{lemma}
+\begin{proof}
+ Let us analyse the ideal of $\Xi_i$: it is generated by
+ \begin{enumerate}[leftmargin=.5 cm]
+  \item equations on $\widetilde\Ecal$ cutting the locus where $C_i$ degenerates so that $f_i$ is constant on a neighbourhood of $q_v$, $i\in \Lambda_B$: these correspond to the tropical functions $\delta_i-\operatorname{dist}(q_i,\circ)$;
+  \item equations on the fiber of $p$ for the linear subspace corresponding to $j\in \Lambda_F$: tropically, these correspond to the $\ell_j$ discussed above.
+ \end{enumerate}
+By construction, on $\widetilde \Dcal$ it is always possible to tell which of these tropical lengths is the shortest (the circle we have drawn on $\Xi$ is degenerate - it passes through no vertex of positive horizontal degree -, therefore we need to decide for a strictly larger circle in order to lift to $\widetilde D$), which corresponds to principalising the ideal (see Figure \ref{fig:principalisation}).
+\end{proof}
+
+\begin{figure}
+\includegraphics[scale=.5]{principalisation}
+\caption{On the left, a generic point of $\mathcal P$.
+On the right, a point of $\Xi$.
+The dotted circle is the one we draw on $\mathcal P$.
+The continuous circle represents one of the possible choices of $\delta$ enlarging the dotted one (a stratum of $\widetilde\Dcal$).}\label{fig:principalisation}
+\end{figure}
+
+Finally, on $\widetilde\Dcal$ (or, in fact, on an intermediate blow-up $\widetilde{\mathcal P}\to\mathcal P$) there are exceptional divisors $\widetilde \Xi_i$ corresponding to $\Xi_i$ in $\mathcal P$.
+Since the $\Xi_i$ exhaust all the excess-dimensional components of the vanishing locus of $s\in\Gamma(\mathcal P,G)$, the latter induces a section $\tilde s\in\Gamma(\widetilde\Dcal,G(-\sum_i\widetilde\Xi_i))$ by pullback and twisting, whose vanishing locus is dimensionally transverse to the boundary, and whose open part coincides with the generic point of $\Dcal$, therefore $V(\tilde s)=\Dcal$.
+
+Expressing the pushforward of the Chern classes of $\OO_F(1)$ and $\OO(\widetilde\Xi_i)$ in terms of tautological classes on the fiber product underlying $\Ecal$, we get:
+\begin{cor}
+ After pushforward to $\Ecal$, the contribution of $\Dcal$ to the invariants can be computed in terms of tautological integrals on moduli spaces of maps with lower numerics.
+\end{cor}
+
 \subsection{Recursion for general $(X,Y)$}\label{section recursion for general pair} We now let $(X,Y)$ be a general smooth very ample pair.
-In \S \ref{subsection virtual} we studied the moduli space $\VZ_{1,\alpha}(X|Y,\beta)$ of centrally aligned maps to $(X,Y)$ and equipped it with a virtual fundamental class by diagonal pull-back from $\VZ_{1,\alpha}(\PP^N|H,d)$.
+In \S \ref{} we studied the moduli space $\VZ_{1,\alpha}(X|Y,\beta)$ of centrally aligned maps to $(X,Y)$ and equipped it with a virtual fundamental class by diagonal pull-back from $\VZ_{1,\alpha}(\PP^N|H,d)$.
 

### 2019-06-28 EllipticSingularitiesSplitting.tex
improved description of D from Dtilde

@@
 
-\subsubsection{$\Dcal$ from $\widetilde\Dcal$}\label{subsection D from Dtilde} On $\widetilde\Dcal$ there is a tautological vector bundle arising from the modular description of $\widetilde\VZ_{1,\alpha}(\PP^N|H,d)$, namely:
-\begin{equation*} F = \OO(\delta)^{\oplus r}. \end{equation*}
-
-\begin{lemma}
-The fibre of $F$ over a moduli point can be identified with
-\begin{equation*} \left( \bigoplus_{i=1}^r \TT_{p_i} C_i^\prime \right) \otimes \TT_{C_0} \end{equation*}
-where $C_i^\prime$ is a component of $C_i$ which lies on the radius, $p_i$ is the adjacent node which points towards the core, and $\TT_{C_0}$ is the universal tangent line bundle.
+\subsubsection{$\Dcal$ from $\widetilde\Dcal$: first way}\label{subsection D from Dtilde} On $\widetilde\Dcal$ there is a tautological line bundle arising from the modular description of $\widetilde\VZ_{1,\alpha}(\PP^N|H,d)$, namely $\OO(\delta)$.
+
+\begin{lemma}\label{lemma fibres of Odelta}
+The fibre of $\OO(\delta)$ over a moduli point is naturally isomorphic to
+\begin{equation*} T_{p}C^\prime \otimes T C_0\end{equation*}
+where $C^\prime$ is any component of $C$ which lies on the radius, $p$ is the adjacent node which points towards the core, and $\TT_{C_0}$ is the universal tangent line bundle on the moduli space for $\sqC_0$.
 \end{lemma}
@@
 \begin{proof}
-Choose a component $C_i^\prime$ of the curve which lies on the radius.
-Then $\OO(\delta)$ is equal to the tensor product of tangent line bundles along the path of edges connecting $C_i^\prime$ to the core.
-However, this tensor product of line bundles is telescoping: any vertex which appears in the middle of the path will have an incoming and outgoing node, and since the vertex corresponds to a smooth rational curve these tangent spaces are naturally dual to each other~\cite{VZ}.
-Standard manipulations lead to the result.
-
+Choose a component $C^\prime$ of the curve which lies on the circle.
+Then $\OO(\delta)$ is equal to the tensor product of tangent line bundles along the path of edges connecting $C^\prime$ to the core.
+However, this tensor product of line bundles is telescoping: any vertex which appears in the middle of the path will have an incoming and outgoing node, and since the vertex corresponds to a smooth rational curve these tangent spaces are naturally dual to each other~\cite[\S 2.2]{VZ}.
+Thus these factors cancel, and the result follows.
 %Note that the final term on the right hand side is not given by $\TT_{q_i} C_0$ (where $q_i$ is the appropriate splitting node) but rather the tangent space to the core. 
 \end{proof}
-
-We said that $C_i^\prime$ is \emph{a} component of $C_i$ which lies on the radius. There may be more than one, but if this is the case then their tangent spaces are naturally identified.
-
-The following construction allows us to give a canonical description of $\Dcal$ inside $\widetilde\Dcal$.
-Over $\widetilde\Dcal$ there is a natural section of the projective bundle $\PP(F) \to \widetilde\Dcal$ (obtained by projectivising the diagonal embedding).
-We may then pullback to $\widetilde\Dcal$ the map of vector bundles
-\begin{equation}\label{eq:factorisation} \OO_{\PP(F)}(-1)(-\TT_{C_0}) \xrightarrow{\text{can}(-\TT_{C_0})} \pi^\st F(-\TT_{C_0}) \xrightarrow{\pi^*\sum\operatorname{d}f} \pi^\st(\ev_q^\st \TT_H),\end{equation}\footnote{We may assume the latter factors through $\ev_q^\st \TT_H\subseteq\ev_q^\st \TT_{\PP^N}$ by virtue of Lemma \ref{lemma type C0 combinatorial types}.}
-whose vanishing tautologically expresses the condition that the stable map $f$ descend to the elliptic singularity associated to a point of $\widetilde\Dcal$.
-Thus, the class of $\Dcal$ can be represented via an Euler class computation.
-Note that the vector bundle $F$ can be explicitly realised by twisting the pullback of $\bigoplus_{i=1}^rT_{q_i}C_i$ from $\Ecal$ with a number of exceptional boundary corrections.
-
-\begin{comment}
-We obtain a natural morphism
-\begin{equation*} \sum \operatorname{d}\!f \colon F(-\TT_{C_0}) \to \ev_q^\st \TT_H \end{equation*}
-given by summing the derivatives at \emph{all} the inward-pointing nodes on the radius.
-{\bf \color{red} What does this next part mean?} Now, over $\widetilde\Dcal$ there is a natural section of the projective bundle $\PP(F) \to \widetilde\Dcal$ (obtained by projectivising the diagonal embedding).
-If we therefore lift the above morphism to the projectivisation, we obtain a composition:
-\begin{equation*} \OO_{\PP(F)}(-1) \to \pi^\st F \to \pi^\st(\ev_q^\st \TT_H (\TT_{C_0})).\end{equation*}
-The vanishing locus of this section is given by an Euler class calculation on $\PP(F)$.
-In order to obtain $\Dcal$ we must then intersect this vanishing locus with $\OO_{\PP(F)}(1)$.
-%(which represents the natural section $\widetilde\Dcal \to \PP(F)$.
-
-Finally, we note that the class of $F$ {\bf \color{red} What class of $F$?} is computable in terms of data pulled back from the base. Consider the following bundle on $\Ecal$:
-\begin{equation*} E = \bigoplus_{i=1}^r \left( \TT_{q_i}C_i \otimes \TT_{q_i}C_0\right). \end{equation*}
-We may then identify $F$ with the pullback of $E$ twisted by the exceptional loci.
-
-{\bf \color{red} More needs to be said here.}
-\end{comment}
-
-The main features of the discussion above are visible in the following example, which brings out the interplay between logarithmic moduli and blow-ups.
-
+The content of Lemma \ref{lemma fibres of Odelta} is that the choice of point in the fibre of $\widetilde\Dcal \to \widetilde\Ecal$ provides a natural identification between the inward-pointing tangent spaces on the circle.
+This identification amounts to a specific linear dependence relation between the tangent vectors, which gives a point in the moduli space of attaching data for the corresponding elliptic singularity \cite[\S 2.2]{SMY2}.
+We may therefore express the factorisation condition in terms of the following natural morphism of vector bundles on $\widetilde\Dcal$:
+\begin{equation*} \Sigma \operatorname{d}\!f \colon \OO(\delta)\otimes TC_0^\vee \to \ev_q^\st T H. \end{equation*}
+Here $\Sigma \operatorname{d}\!f$ is defined by summing the images of the tangent vectors at the inward-pointing nodes on the circle, using the natural identification of each of these tangent spaces with $\OO(\delta)\otimes TC_0^\vee$ established above.
+This gives a section of the vector bundle
+\begin{equation*} V = (\ev_q^\st TH) \otimes (TC_0) \otimes \OO(-\delta) \end{equation*}
+which is transverse and whose vanishing locus coincides with $\Dcal$. Thus we obtain:
+\begin{prop} \label{class of D} $[\Dcal] = \operatorname{e}(V) \cap [\widetilde\Dcal]$.\end{prop}
+We claim that the class $\operatorname{e}(V)$ is tautological and computable.
+The only part which needs justification is $\OO(\delta)$.
+We claim that this can be obtained by pulling back a line bundle from $\Ecal$ and twisting by exceptional divisors.
+\begin{lemma} For $i\in \{1,\ldots,r\}$ consider the line bundle
+\begin{equation*} T_i = T_{q_i} C_i \otimes T_{q_i} C_0 \end{equation*}
+on $\Ecal$, where $q_i$ is the splitting node. Then $\OO(\delta)$ is isomorphic to the pull-back of $T_i$ to $\widetilde\Dcal$ twisted by all exceptional divisors.\end{lemma}
+We illustrate this lemma in the following example, which brings out the interplay between logarithmic moduli and blow-ups.
 \begin{example}
@@
 
-To establish a more direct connection with the geometry of the fibre product \eqref{IIIa fibre product}, recall that $\widetilde\Ecal$ has been built as an explicit modification of a finite cover of \eqref{IIIa fibre product}.
+\subsubsection{$\Dcal$ from $\widetilde\Dcal$: second way} To establish a more direct connection with the geometry of the fibre product \eqref{IIIa fibre product}, recall that $\widetilde\Ecal$ has been built as an explicit modification of a finite cover of \eqref{IIIa fibre product}.
 For every $v\in\{\sqC_1,\ldots,\sqC_r\}$ - with the convention established at the end of Lemma \ref{lem:generic_proj_bundle} -, on $\widetilde\Ecal$ it makes sense to consider the line bundle $\OO(\delta_v)$ associated to a shortest path from the core to the circle in the $v$-direction.

### 2019-06-28 EllipticSingularitiesSplitting.tex
finished my description of D from Dtilde

@@
 \begin{example}
-Consider the following ray $\tau$ and sublocus $\rho$:
-\begin{figure}[h]
-
+Consider the locus $\Ecal$ given by $\sigma$ below, and the exceptional divisor $\widetilde\Dcal_\rho \subseteq \widetilde\Dcal$ given by $\rho$:
+\begin{figure}[!htbp]
 \begin{minipage}{0.3\textwidth}
@@
 \begin{tikzpicture}
-\draw [red] plot [smooth cycle] coordinates {(0,-2) (-0.5,-1) (0,0) (1,0.5) (3,-1) (1,-2.5)};
+%\draw [red] plot [smooth cycle] coordinates {(0,-2) (-0.5,-1) (0,0) (1,0.5) (3,-1) (1,-2.5)};
 
@@
 \end{tikzpicture}
-\caption{$\tau$}
+\caption{$\sigma$}
 \end{minipage}\hfill
@@
 
-\noindent On the cone $\rho$ we have the following tropical equations
+On the cone $\rho$ we have the following tropical continuity equations
 \begin{align*}
-e:=e_1 = e_2 \\
-f:=f_1 = f_2 = 2f_3 \\
-g:=g_1 = g_2 = 2g_3
+e:=e_1 = e_2, \qquad f:=f_1 = f_2 = 2f_3, \qquad g:=g_1 = g_2 = 2g_3
 \end{align*}
 together with the equation imposed by the choice of alignment:
-\begin{align*} & e_1 + f_1 = e_2 + f_3 + g_3 \\
-\Leftrightarrow \ & e + f = e + f/2 + g/2 \\
-\Leftrightarrow \ & f = g.
+\begin{align*} e_1 + f_1 = e_2 + f_3 + g_3 \qquad (\Longleftrightarrow f = g).
 \end{align*}
-Notice that setting $f=g=0$ we recover $\tau$. We claim that if we twist the bundle
-\begin{equation*} E = \left( \TT_{q_1} C_1 \otimes \TT_{q_1} C_0 \right) \oplus \left( \TT_{q_2} C_2 \otimes \TT_{q_2} C_0 \right) \end{equation*}
-by the line bundle corresponding to the divisor in $\widetilde\Dcal$ defined by $\rho$, we will obtain the bundle
-\begin{equation*} F = \left( \TT_{f_1}C_1^1 \otimes \TT_{e_1} C_0 \right) \oplus \left( \TT_{g_2} C_2^2 \otimes \TT_{e_2} C_0 \right). \end{equation*}
-described earlier. The line bundle corresponding to $\rho$ is simply $\OO(f)=\OO(g)$. We have:
-\begin{align*} \left( \TT_{q_1} C_1 \otimes \TT_{q_1} C_0 \right) \otimes \OO(f) & = \TT_{q_1}C_1 \otimes \TT_{q_1} C_0 \otimes \TT_{f_1} C_1^0 \otimes \TT_{f_1} C_1^1 \\
-& = \TT_{e_1} C_1^0 \otimes \TT_{e_1} C_0 \otimes \TT_{f_1} C_1^0 \otimes \TT_{f_1} C_1^1\\
-&  = \TT_{f_1} C_1^1 \otimes \TT_{e_1} C_0\end{align*}
-where we have used the telescoping trick $\TT_{f_1}C_1^0 \otimes \TT_{e_1} C_1^0 \cong \OO$. On the other hand, for the $C_2$ summand we write $f=f/2 + g/2=f_3+g_3$ to obtain:
-\begin{align*} \left( \TT_{q_2}C_2 \otimes \TT_{q_2}C_0\right) \otimes \OO(f) & = \TT_{e_2} C_0 \otimes \TT_{e_2} C_2^0 \otimes \OO(f_3) \otimes \OO(g_3) \\
-& = \TT_{e_2} C_0 \otimes \TT_{e_2} C_2^0 \otimes \TT_{f_3} C_2^0 \otimes \TT_{f_3} C_2^1 \otimes \TT_{g_3} C_2^1 \otimes \TT_{g_3} C_2^2 \\
-& = \TT_{g_3} C_2^2 \otimes \TT_{e_2} C_0.\end{align*}
-This observation generalises, giving a precise relation between the intrinsically-defined vector bundle $F$ on $\widetilde\Dcal$ (which we use to impose the factorisation condition) and the the vector bundle $E$ pulled back from $\Ecal$.
-This allows us to express the Chern classes of $F$ in terms of pull-backs of tautological classes from $\Ecal$ and boundary strata on $\widetilde\Dcal$, which is necessary to compute integrals.
+From now on we use the same symbol to denote an edge length and the corresponding node on $\widetilde\Dcal_\rho$. On this locus we have line bundles pulled back from $\Ecal$
+\begin{align*} T_1 & = T_{e_1} C_1^0 \otimes T_{e_1} C_0 \\
+T_2 & = T_{e_2} C_2^0 \otimes T_{e_2} C_0\end{align*}
+as well as the logarithmic line bundle
+\begin{equation*} \OO(\delta) = T_{f_1} C_1^1 \otimes T_{e_1} C_0 = T_{f_2} C_1^2 \otimes T_{e_1} C_0 = T_{g_3} C_2^2 \otimes T_{e_2}C_0 
+\end{equation*}
+where the identifications follow from Lemma \ref{lemma fibres of Odelta}. We claim that: 
+\begin{equation} \label{Odelta eqn} \OO(\delta) = T_1\otimes \OO(\widetilde\Dcal_\rho) = T_2 \otimes \OO(\widetilde\Dcal_\rho).\end{equation}
+Notice that $\OO(\widetilde\Dcal_\rho) = \OO(f)=\OO(g)$. Thus we have
+\begin{align*} T_1 \otimes \OO(\widetilde\Dcal_\rho) & = \OO(f_1) \otimes T_{e_1} C_1^0 \otimes T_{e_1}C_0 \\
+& = T_{f_1}C_1^1 \otimes T_{f_1} C_1^0 \otimes T_{e_1} C_1^0 \otimes T_{e_1}C_0  \\
+& = T_{f_1}C_1^1\otimes T_{e_1}C_0 \qquad (= \OO(\delta))
+\end{align*}
+where in the last line we have used the same telescoping trick $\TT_{f_1}C_1^0 \otimes \TT_{e_1} C_1^0 = \OO$ used in the proof of Lemma \ref{lemma fibres of Odelta}.
+On the other hand, for $T_2$ we may write $f=f/2 + g/2=f_3+g_3$ in order to obtain:
+\begin{equation*} T_2 \otimes \OO(\widetilde\Dcal_\rho) = \OO(g_3) \otimes \OO(f_3) \otimes T_{e_2} C_2^0 \otimes T_{e_2} C_0 = T_{g_3}C_2^2 \otimes T_{e_2}C_0 = \OO(\delta) \end{equation*}
+where we have used the same telescoping trick.
+Thus we have proven \eqref{Odelta eqn}.
+This observation generalises, giving a precise relation between the intrinsically-defined line bundle $\OO(\delta)$ on $\widetilde\Dcal$ (which we use to impose the factorisation condition) and the the line bundles $T_i$ pulled back from $\Ecal$.
+This allows us to express the Chern classes of $\OO(\delta)$ (and hence $V$) in terms of pull-backs of tautological classes from $\Ecal$ and boundary strata on $\widetilde\Dcal$, which is sufficient in order to compute integrals.
 \end{example}

### 2019-06-28 EllipticSingularitiesSplitting.tex
minor changes

@@
 We stress once again that such degenerate contributions are at the heart of the reduced theory and cannot be removed.
-
 We begin with the following lemma:
@@
 For every nonzero vertex $\diamond$ of the tropical target, the fibre of the tropical map over $\diamond$ contains exactly one stable vertex, which either is the core, or lies on the circle.
-Besides, the maximal contact order at the core is $m>1$.
+Moreover, the maximal contact order at the core is $m>1$.
 \end{lemma}
@@
 For each vertex of the target there must always be at least one vertex in the preimage which lies on the circle.
-This is implied by the fact that the combinatorial type $\Delta$ is a ray.
-If the vertex on the circle is strictly semistable - in particular the collapsed map $f_B$ is constant along the corresponing component -, it can be seen that the factorisation condition is unaffected by $\Gm$-scaling the coordinate corresponding to that vertex in the moduli space of attachments, so the map $\Dcal\to\Ecal$ has generic fiber of positive dimension.
-
-In particular, notice that vertices lying on the circle and tropically mapped to $0\in\mathbb R_{\geq0}$ all have the same contact order at the core, because by the previous paragraph we may assume that only strictly semistable vertices are encountered on these paths.
+This is implied by the fact that the cone $\tau$ corresponding to $\Dcal$ is a ray.
+If the vertex on the circle is strictly semistable -- so that in particular the collapsed map $f_B$ is constant along the corresponing component -- it can be seen that the factorisation condition is unaffected by $\Gm$-scaling the coordinate corresponding to that vertex in the moduli space of attachments, so the map $\Dcal\to\Ecal$ has generic fiber of positive dimension and the contribution vanishes.
+
+In particular, notice that vertices lying on the circle and tropically mapped to $0\in\mathbb R_{\geq0}$ all have the same contact order at the core, because by the previous paragraph we may assume that only strictly semistable vertices are encountered on the paths from these vertices to the core.
 For the same reason, this contact order $m$ is maximal among those of the edges adjacent to the core.
@@
 Let $\tau \in \Sigma_{1,\alpha}(\PP^N|H,d)$ be the ray corresponding to $\Dcal \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$, and to the virtual divisor $\widetilde \Dcal \subseteq \widetilde{\VZ}_{1,\alpha}(\PP^N|H,d)$.
-\medskip
 
 Let $\sigma \in \Sigma^{\Kim}$ be the minimal cone containing the image of $\tau$.
-The dimension of this cone could be large -- its dimension is equal to the the number of levels of the target expansion in the type $\tau$.
-The cone $\sigma$ determines a stratum $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$.
-The morphism above restricts to
+The dimension of this cone could be large -- its dimension is equal to the the number of levels of the target expansion in the type $\Delta$.
+The cone $\sigma$ determines a stratum $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$, and the morphism above restricts to
 \[
@@
 Then $\Ecal$ admits a finite and surjective splitting morphism
-\begin{equation}\label{IIIa fibre product} \Ecal \xrightarrow{\rho} \left( \prod_{v \in \Lambda_0} \ol\Mcal_{\Gamma_v}(\PP^N|H) \times \prod_{v \in \Lambda_{>0}} \ol\Mcal^{\leftrightarrow}_{\Gamma_v}(P|H_0+H_\infty) \right) \times_{H^{2\epsilon}} H^{\epsilon} \end{equation}
+\begin{equation}\label{IIIa fibre product} \Ecal \xrightarrow{\rho} \left( \prod_{v \in \Lambda_0} \ol\Mcal_{\Gamma_v}(\PP^N|H) \times \prod_{v \in \Lambda_{>0}} \ol\Mcal^{\leftrightarrow}_{\Gamma_v}(\mathbb{P}|H_0+H_\infty) \right) \times_{H^{2\epsilon}} H^{\epsilon} \end{equation}
 where $\epsilon$ is the number of edges of the stabilised dual graph, and the fibre product is taken over the appropriate evaluation maps.
@@
 \]
-
 is a logarithmic morphism. The generic fiber of this morphism is a toric variety.  \medskip
@@
 \[
-\Sigma\widetilde{\Dcal}\to \Sigma\Ecal.
+\widetilde{\Dcal}^{\operatorname{trop}} \to \Ecal^{\operatorname{trop}}.
 \]
-The tropical curves on the left inherit a central alignment from the moduli space $\widetilde{\VZ}_{1,\alpha}(\PP^N|H)$, which orders a certain subset of the edge lengths.
-The polyedral criterion for equidimensionality is that every cone of the source maps surjectively onto a cone of the target.
+The tropical curves on the left inherit a central alignment from the moduli space $\widetilde{\VZ}_{1,\alpha}(\PP^N|H,d)$, which orders a certain subset of the edge lengths.
+The polyhedral criterion for equidimensionality is that every cone of the source maps surjectively onto a cone of the target.
+The logarithmic modification $\widetilde\Ecal \to \Ecal$ is constructed by taking the minimal subdivison of $\Ecal^{\operatorname{trop}}$ such that this condition is satisfied.
 
@@
 
-\subsection{Recursion for general $(X,Y)$}\label{section recursion for general pair} We now let $(X,Y)$ be a general smooth very ample pair.
+\subsection{Recursion for general $(X,Y)$}\label{section recursion for general pair} Now let $(X,Y)$ be a general smooth very ample pair.
 In \S \ref{} we studied the moduli space $\VZ_{1,\alpha}(X|Y,\beta)$ of centrally aligned maps to $(X,Y)$ and equipped it with a virtual fundamental class by diagonal pull-back from $\VZ_{1,\alpha}(\PP^N|H,d)$.

### 2019-06-28 EllipticSingularitiesSplitting.tex
minor changes to \S from D tilde to D

@@
 Here $\Sigma \operatorname{d}\!f$ is defined by summing the images of the tangent vectors at the inward-pointing nodes on the circle, using the natural identification of each of these tangent spaces with $\OO(\delta)\otimes TC_0^\vee$ established above.
-This gives a section of the vector bundle
+\tred{We may assume it lands in $TH$ (rather than $T\PP^N$) thanks to Lemma \ref{lemma type C0 combinatorial types}.} This gives a section of the vector bundle
 \begin{equation*} V = (\ev_q^\st TH) \otimes (TC_0) \otimes \OO(-\delta) \end{equation*}
@@
 Construct $\mathcal P=\PP_{\widetilde\Ecal}(\bigoplus_{v\in \{\sqC_1,\ldots,\sqC_r\}}\OO(\delta_v))$; since $\sqC_1,\ldots,\sqC_r$ are always ordered on $\widetilde \Dcal$ (they may lie on the circle, be the first component off the circle, or degenerate and lie in the strict interior), there is a morphism $\widetilde \Dcal\to\mathcal P$ lifting $\widetilde \Dcal\to\widetilde\Ecal$.
-Consider the map of vector bundles on $\mathcal P$ (analogous to \eqref{eq:factorisation}):
-\[ \OO_{\mathcal P}(-1)\to p^*(\bigoplus_{v\in \{\sqC_1,\ldots,\sqC_r\}}\OO(\delta_v))\xrightarrow{\sum\operatorname{d}f}\ev_{C_0}^*T_H.\]
-
-The composite, regarded as a section $s$ of $G=\OO_{\mathcal P}(1)\otimes \operatorname{ev}_{C_0}^*(T_H)$, vanishes precisely where $f$ factors through the Smyth's singularity determined by the point in the fiber of $p$.
+Consider the map of vector bundles on $\mathcal P$:
+\[ \OO_{\mathcal P}(-1)\to p^*(\bigoplus_{v\in \{\sqC_1,\ldots,\sqC_r\}}\OO(\delta_v))\xrightarrow{\sum\operatorname{d}f}\ev_{C_0}^*TH.\]
+
+The composite, regarded as a section $s$ of $G=\OO_{\mathcal P}(1)\otimes \operatorname{ev}_{C_0}^*(TH)$, vanishes precisely where $f$ factors through the elliptic singularity determined by the point in the fiber of $p$.
 Generically on $\widetilde\Ecal$, this is exactly what we are after - compare with Lemma \ref{lem:generic_proj_bundle}.
@@
  \begin{enumerate}[leftmargin=.5 cm]
-  \item equations on $\widetilde\Ecal$ cutting the locus where $C_i$ degenerates so that $f_i$ is constant on a neighbourhood of $q_v$, $i\in \Lambda_B$: these correspond to the tropical functions $\delta_i-\operatorname{dist}(q_i,\circ)$;
-  \item equations on the fiber of $p$ for the linear subspace corresponding to $j\in \Lambda_F$: tropically, these correspond to the $\ell_j$ discussed above.
+  \item equations on $\widetilde\Ecal$ cutting the locus where $C_i$ degenerates so that $f_i$ is constant on a neighbourhood of $q_i$, $i\in \Lambda_B$: these correspond to the tropical functions $\delta_i-\operatorname{dist}(q_i,\circ)$;
+  \item equations on the fiber of $p$ for the linear subspace corresponding to $j\in \Lambda_F$: tropically, these correspond to the $\ell_j$ discussed in Lemma Lemma \ref{lem:generic_proj_bundle}.
  \end{enumerate}

### 2019-06-28 EllipticSingularitiesSplitting.tex
put back in a bit more discussion of Etilde

--- 2019-06-28 EllipticSingularitiesSplitting.tex
@@
 \begin{lemma} $\Dcal$ admits a finite and surjective splitting morphism:
-\begin{equation*} \Dcal \xrightarrow{\rho} \left(\ol\Mcal_{0,\alpha^{(1)}\cup(m_1,m_2)}(\PP^N|H,d_1)\times\prod_{i=3}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i)\right) \times_{H^r} \ol\Mcal^{\leftrightarrow}_{0,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(P|H_0+H_\infty,d_0).\end{equation*}\end{lemma}
+\begin{equation*} \Dcal \xrightarrow{\rho} \left(\ol\Mcal_{0,\alpha^{(1)}\cup(m_1,m_2)}(\PP^N|H,d_1)\times\prod_{i=3}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i)\right) \times_{H^r} \ol\Mcal^{\leftrightarrow}_{0,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(\mathbb P|H_0+H_\infty,d_0).\end{equation*}\end{lemma}
 
@@
 The polyhedral criterion for equidimensionality is that every cone of the source maps surjectively onto a cone of the target.
-The logarithmic modification $\widetilde\Ecal \to \Ecal$ is constructed by taking the minimal subdivison of $\Ecal^{\operatorname{trop}}$ such that this condition is satisfied.
-
-By explicit but elementary polyhedral considerations, we are led to the following moduli theoretic description of the logarithmic modification $ \widetilde \Ecal$ such that the map $\widetilde \Dcal\to \widetilde \Ecal$ is flat.
-
-We keep in mind the fibre product description of $\Ecal$. Construct a modification $\widetilde \Ecal$ from $\Ecal$ as follows:
+There is a universal logarithmic modification $\widetilde\Ecal \to \Ecal$ such that $\widetilde\Dcal \to \widetilde\Ecal$ is flat, constructed by taking the minimal subdivison of $\Ecal^{\operatorname{trop}}$ such that cones map surjectively to cones.
+
+This subdivision is best described using the formalism of extended tropicalisations \cite{}.
+The subdividing cones are obtained from cones in the star of $\tau$ under the limit $e_1=\cdots=e_r=\infty$.
+The cones in the star of $\tau$ are given by (in)equalities relating distances of pairs of vertices, and there are three cases to consider:
 \begin{enumerate}
-\item Given a logarithmic map of type $\Delta$ with splitting nodes $q_1,\ldots,q_r$, formally glue together the $r$ vertices of the tropicalization which carry the splitting nodes, and declare the resulting vertex to be the root of the resulting tree.
+\item both vertices are components of the subgraph $\sqC \setminus \sqC_0$;
+\item both vertices are components of the subgraph $\sqC_0$;
+\item one vertex is a component of $\sqC_0$ and one is a component of $\sqC \setminus \sqC_0$.
+\end{enumerate}
+As we pass to the limit, the first relations impose a central alignment condition on the genus zero moduli, the second relations impose a radial alignment condition on the genus one moduli, and the third relations disappear entirely.
+We are therefore led to the following moduli theoretic description of the logarithmic modification $ \widetilde \Ecal$.
+
+Keeping in mind the fibre product description of $\Ecal$, construct a modification $\widetilde \Ecal$ from $\Ecal$ as follows:
+\begin{enumerate}
+\item Given a logarithmic map of type $\Delta$ with splitting nodes $q_1,\ldots,q_r$, remove the genus one piece $\sqC_0$ and formally glue together the $r$ vertices of the tropicalization which carry the splitting nodes, and declare the resulting vertex to be the root of the resulting tree.
 Impose the central alignment condition, where the special root takes on the r\^ole previously occupied by the core.
 \item Replace the fibre product factor in $\Ecal$ associated to the vertex $\sqC_0$
-\begin{equation*} \ol\Mcal^{\leftrightarrow}_{\Gamma_{\tiny{\sqC_0}}}(P|H_0+H_\infty) \end{equation*}
+\begin{equation*} \ol\Mcal^{\leftrightarrow}_{\Gamma_{\tiny{\sqC_0}}}(\mathbb P|H_0+H_\infty) \end{equation*}
 with the radially aligned rubber space:
-\begin{equation*} \VZ^{\leftrightarrow}_{\Gamma_{\tiny{\sqC_0}}}(P|H_0+H_\infty).\end{equation*}
+\begin{equation*} \VZ^{\leftrightarrow}_{\Gamma_{\tiny{\sqC_0}}}(\mathbb P|H_0+H_\infty).\end{equation*}
+(Here we are imposing fibre-direction factorisation in order to isolate the main component.)
 \end{enumerate}
-
 This procedure induces a logarithmic modification $\widetilde\Ecal \to \Ecal$ which admits a modular description as a fibre product of genus zero centrally aligned maps coming from the vertices $\sqC_1,\ldots,\sqC_r$, and genus one aligned rubber maps satisfying fibre-direction factorisation from the vertex $\sqC_0$.
@@
 $\widetilde\Dcal$ is a compactification of a torus bundle over $\widetilde\Ecal$ whose strata can be read off from the tropicalization; in particular, we have the information of how (polynomials in) the classes of boundary strata push forward to $\widetilde\Ecal$.
-In fact, the generic fibre of $\widetilde\Dcal \to \widetilde\Ecal$ can be read off geometrically.
-
+In fact, we can say more and describe the generic fibre of $\widetilde\Dcal \to \widetilde\Ecal$:
 \begin{lemma}\label{lem:generic_proj_bundle}
@@
 
-\subsection*{Step 4} Finally, consider a rubber space $\VZ^{\leftrightarrow}_{1,\alpha}(P|Y_0+Y_\infty,\beta)$ with insertion $\gamma$.
+\subsection*{Step 4} Finally, consider a rubber space $\VZ^{\leftrightarrow}_{1,\alpha}(\mathbb P|Y_0+Y_\infty,\beta)$ with insertion $\gamma$.
 Suppose inductively that we have computed all absolute and relative invariants with $d^\prime \leq d$ and all rubber invariants with $(d^\prime,n^\prime,m^\prime) < (d,n,m)$.
@@
 We first note the following important reduction: if there exists a relative marking $x_k$ such that all insertions are pulled back along $\fgt_{k}$, then we may apply the projection formula, together with the fact that
-\begin{equation*} (\fgt_{k})_\st [\VZ^{\leftrightarrow}_{1,\alpha}(P|Y_0+Y_\infty,\beta)] = \alpha_k^2 \cdot [\VZ_{1,n+m-1}(Y,\beta)] \end{equation*}
+\begin{equation*} (\fgt_{k})_\st [\VZ^{\leftrightarrow}_{1,\alpha}(\mathbb P|Y_0+Y_\infty,\beta)] = \alpha_k^2 \cdot [\VZ_{1,n+m-1}(Y,\beta)] \end{equation*}
 to identify the rubber invariant with a multiple of a reduced invariant of $Y$, which has the same degree and hence is known recursively.
@@
 We will deal with the general case by reducing to the one above. Consider the moduli space
-\begin{equation*}\label{step 4 recursion space} \VZ^{\leftrightarrow}_{1,\alpha\cup (0)}(P|Y_0+Y_\infty,\beta)\end{equation*}
+\begin{equation*}\label{step 4 recursion space} \VZ^{\leftrightarrow}_{1,\alpha\cup (0)}(\mathbb P|Y_0+Y_\infty,\beta)\end{equation*}
 obtained by introducing a marked point $y$ with no tangency.
@@
 We will make use of a recursion formula for rubber spaces analogous to the recursion formula for relative spaces used in Steps 1--3.
-Following \cite{EKatz}, there is a line bundle $L_y^{\not\in \operatorname{bot}}$ on $\VZ^{\leftrightarrow}_{1,\alpha\cup (0)}(P|Y_0+Y_\infty,\beta)$, together with a section $s_y^{\not\in\operatorname{bot}}$ whose vanishing locus consists of the locus $\Dcal(y)$ of rubber maps where $y$ is not mapped into the bottom level of the expanded target.
+Following \cite{EKatz}, there is a line bundle $L_y^{\not\in \operatorname{bot}}$ on $\VZ^{\leftrightarrow}_{1,\alpha\cup (0)}(\mathbb P|Y_0+Y_\infty,\beta)$, together with a section $s_y^{\not\in\operatorname{bot}}$ whose vanishing locus consists of the locus $\Dcal(y)$ of rubber maps where $y$ is not mapped into the bottom level of the expanded target.
 As in \S \ref{Section Gathmann line bundle}, we can give a logarithmic interpretation of this: it corresponds to the piecewise-linear function on the tropical moduli space which associates, to every rubber tropical map, the distance between $\varphi(\sqC_y)$ and the leftmost vertex of the tropical target, where $\sqC_y$ is the vertex of the source curve containing the flag corresponding to $y$.
@@
 From this, we obtain a rubber recursion formula
-\begin{equation}\label{step 4 recursion} (\Psi_0 - \ev_y^\st Y) \tilde\gamma \cap [\VZ^{\leftrightarrow}_{1,\alpha\cup(0)}(P|Y_0+Y_\infty,\beta)] = \tilde\gamma \cap [\Dcal(y)]\end{equation}
+\begin{equation}\label{step 4 recursion} (\Psi_0 - \ev_y^\st Y) \tilde\gamma \cap [\VZ^{\leftrightarrow}_{1,\alpha\cup(0)}(\mathbb P|Y_0+Y_\infty,\beta)] = \tilde\gamma \cap [\Dcal(y)]\end{equation}
 where the fundamental class $[\Dcal(y)]$ is weighted by vanishing orders on the components.
@@
 So up to recursively-known terms \eqref{step 4 recursion} becomes
-\begin{equation*} \fgt_1^\st (-\alpha_2\psi_2 - \ev_y^\st Y)\tilde\gamma \cap [\VZ^{\leftrightarrow}_{1,\alpha\cup(0)}(P|Y_0+Y_\infty,\beta)] = \tilde\gamma\cap[\Dcal(y)]\end{equation*}
+\begin{equation*} \fgt_1^\st (-\alpha_2\psi_2 - \ev_y^\st Y)\tilde\gamma \cap [\VZ^{\leftrightarrow}_{1,\alpha\cup(0)}(\mathbb P|Y_0+Y_\infty,\beta)] = \tilde\gamma\cap[\Dcal(y)]\end{equation*}
 and now the left-hand side is also recursively known, by the projection formula.

### 2019-06-28 EllipticSingularitiesSplitting.tex
minor changes

@@
 \section{Quantum Lefschetz algorithm}\label{section recursion algorithm}
-Consider a smooth pair $(X,Y)$ with $Y$ very ample, and let $P$ be the projective bundle $P=\PP_Y(\operatorname{N}_{Y|X} \oplus\OO_Y)$.
+Consider a smooth pair $(X,Y)$ with $Y$ very ample, and let $\mathbb{P}$ be the projective bundle $\mathbb{P}=\PP_Y(\operatorname{N}_{Y|X} \oplus\OO_Y)$.
 We assume that the genus zero and reduced genus one Gromov--Witten theories of $X$ are known.
@@
 \item the genus one \textbf{reduced relative Gromov--Witten theory} of the pair $(X,Y)$;
-\item the genus one \textbf{reduced rubber theory} of $P$.
+\item the genus one \textbf{reduced rubber theory} of $\mathbb{P}$.
 \end{enumerate}
@@
 Note that, unlike in the absolute case, in the relative case it may well be the case that the entire insertion is pulled back along a single forgetful map $\fgt_S$.
-The reduced rubber invariants of $P$ are defined similarly (again using collapsed psi classes).
+The reduced rubber invariants of $\mathbb{P}$ are defined similarly (again using collapsed psi classes).
 
@@
 
-\subsection{Structure of the recursion} Given the genus-zero Gromov--Witten theory of $X$, the arguments of \cite{Ga} give an effective algorithm to reconstruct the genus-zero theories of $Y$ and $(X,Y)$; moreover, the genus-zero rubber theory of $P$ is identical to the genus-zero theory of $Y$ \cite{GathmannThesis}.
+\subsection{Structure of the recursion} Given the genus-zero Gromov--Witten theory of $X$, the arguments of \cite{Ga} give an effective algorithm to reconstruct the genus-zero theories of $Y$ and $(X,Y)$; moreover, the genus-zero rubber theory of $\mathbb{P}$ is identical to the genus-zero theory of $Y$ \cite{GathmannThesis}.
 Thus we may assume that all genus-zero data is known.
@@
 \For{$m \geq 0$\medskip}{
-\textbf{\, Step 4: } Compute rubber invariants of $P$ (degree $d$, $n$ relative markings, $m$ non-relative markings).
+\textbf{\, Step 4: } Compute rubber invariants of $\mathbb{P}$ (degree $d$, $n$ relative markings, $m$ non-relative markings).
 }
@@
 The base terms of the recursion all have $d=0$ and as such are easy to compute: the relative invariants of $(X,Y)$ are nothing but absolute invariants of $X$ and the absolute invariants of $Y$ are given by obstruction bundle integrals over Deligne--Mumford spaces.
-The rubber invariants of $P$ in degree zero are given by integrals over the main component of the double ramification cycle; this can likewise be computed as an integral over Deligne--Mumford space, by correcting the formula for the ordinary double ramification cycle \cite{Hain,JPPZ} by the obvious contribution from the boundary irreducible component (the observation which makes this easy to do in genus one is that the rubber moduli space is pure-dimensional, so that the virtual class is simply the sum of the fundamental classes of the irreducible components).
+The rubber invariants of $\mathbb{P}$ in degree zero are given by integrals over the main component of the double ramification cycle; this can likewise be computed as an integral over Deligne--Mumford space, by correcting the formula for the ordinary double ramification cycle \cite{Hain,JPPZ} by the obvious contribution from the boundary irreducible component (the observation which makes this easy to do in genus one is that the rubber moduli space is pure-dimensional, so that the virtual class is simply the sum of the fundamental classes of the irreducible components).
 We will now explain how to perform each of the four inductive steps outlined above.

### 2019-06-28 EllipticSingularitiesSplitting.tex
minor changes

@@
 
-The space of stable maps $\overline{\mathcal M}^{\mathrm{cen}}_{1,n}(\mathbb P^N,d)$ from the universal nodal curve $\mathcal C$ over the stack $\mathfrak M_{1,n}^{\mathrm{cen}}$ is a proper and algebraic, with projective coarse moduli space.
+The space of stable maps $\widetilde\VZ_{1,n}(\PP^N,d)$ from the universal nodal curve $\mathcal C$ over the stack $\mathfrak M_{1,n}^{\mathrm{cen}}$ is a proper and algebraic, with projective coarse moduli space.
 A compatibility condition between the alignment and the map is required, namely that the circle of radius $\delta$ passes through at least one component of positive degree.
@@
 \begin{thm}[{\cite[Theorem B]{RSPW}}]
-The substack $\VZ_{1,n}(\mathbb P^N,d)$ of $\overline{\mathcal M}^{\mathrm{cen}}_{1,n}(\mathbb P^N,d)$ parameterizing maps to $\mathbb P^N$ that satisfy the factorisation property is smooth and proper of the expected dimension.
+The substack $\VZ_{1,n}(\mathbb P^N,d)$ of $\widetilde\VZ_{1,n}(\PP^N,d)$ parameterizing maps to $\mathbb P^N$ that satisfy the factorisation property is smooth and proper of the expected dimension.
 \end{thm}
@@
 $$
-\overline{\mathcal M}^{\mathrm{cen}}_{1,n}(\mathbb P^N,d)\to\overline{ \mathcal M}_{1,n}(\mathbb P^N,d).
+\widetilde\VZ_{1,n}(\PP^N,d)\to\overline{ \mathcal M}_{1,n}(\mathbb P^N,d).
 $$ 
@@
 \subsection{Relative geometry: expansions} Our next task is to pick out a non-singular principal component in $\widetilde{\VZ}_{1,\alpha}(\mathbb P^N|H,d)$.
-The principal component of this space, consisting of the closure of the space of maps from nonsingular curves, maps into the principal component of $\overline{\mathcal M}^{\mathrm{cen}}_{1,n}(\mathbb P^N,d)$.
+The principal component of this space, consisting of the closure of the space of maps from nonsingular curves, maps into the principal component of $\widetilde\VZ_{1,n}(\PP^N,d)$.
 Indeed, smoothable logarithmic maps are, in particular, smoothable as ordinary maps.
@@
 \begin{equation*} T_{p}C^\prime \otimes T C_0\end{equation*}
-where $C^\prime$ is any component of $C$ which lies on the radius, $p$ is the adjacent node which points towards the core, and $\TT_{C_0}$ is the universal tangent line bundle on the moduli space for $\sqC_0$.
+where $C^\prime$ is any component of $C$ which lies on the radius, $p$ is the adjacent node which points towards the core, and $T C_0$ is the universal tangent line bundle on the moduli space for $\sqC_0$.
 \end{lemma}
@@
 Here $\Sigma \operatorname{d}\!f$ is defined by summing the images of the tangent vectors at the inward-pointing nodes on the circle, using the natural identification of each of these tangent spaces with $\OO(\delta)\otimes TC_0^\vee$ established above.
-\tred{We may assume it lands in $TH$ (rather than $T\PP^N$) thanks to Lemma \ref{lemma type C0 combinatorial types}.} This gives a section of the vector bundle
+By Lemma \ref{lemma type C0 combinatorial types} we have that it takes values in $TH$, rather than $T\PP^N$.
+This gives a section of the vector bundle
 \begin{equation*} V = (\ev_q^\st TH) \otimes (TC_0) \otimes \OO(-\delta) \end{equation*}
@@
 \subsection{Recursion for general $(X,Y)$}\label{section recursion for general pair} Now let $(X,Y)$ be a general smooth very ample pair.
-In \S \ref{} we studied the moduli space $\VZ_{1,\alpha}(X|Y,\beta)$ of centrally aligned maps to $(X,Y)$ and equipped it with a virtual fundamental class by diagonal pull-back from $\VZ_{1,\alpha}(\PP^N|H,d)$.
+In \S \ref{subsection virtual} we studied the moduli space $\VZ_{1,\alpha}(X|Y,\beta)$ of centrally aligned maps to $(X,Y)$ and equipped it with a virtual fundamental class by diagonal pull-back from $\VZ_{1,\alpha}(\PP^N|H,d)$.
 

### 2019-06-28 EllipticSingularitiesSplitting.tex
changed description of types

@@
 These invariants form the principal part contribution to relative Gromov--Witten theory in genus one and are relative versions of Zinger's reduced Gromov--Witten invariants.
-The relative and absolute theories are related by degeneration of the tangency conditions, and the resulting formulas generalize a well-known recursive calculation scheme put forward by Gathmann in genus $0$.
+The relative and absolute theories are related by degeneration of the tangency conditions, and the resulting formulas generalize a well-known recursive calculation scheme put forward by Gathmann in genus zero.
 {The geometric input is a desingularization of the principal component of the moduli space of genus one logarithmic stable maps to a very ample pair, using the geometry of elliptic singularities.
@@
 
-The Kontsevich moduli space of stable maps from genus $0$ curves to projective space exhibits remarkable geometry -- it is a smooth orbifold with a ``self-similar'' normal crossings boundary.
-These facts have combined to produce a very {satisfactory} understanding of Gromov--Witten theory in genus $0$.
+The Kontsevich moduli space of stable maps from genus zero curves to projective space exhibits remarkable geometry -- it is a smooth orbifold with a ``self-similar'' normal crossings boundary.
+These facts have combined to produce a very {satisfactory} understanding of Gromov--Witten theory in genus zero.
 
@@
 
-Let $\mathcal M_{1,\alpha}^\circ(\mathbb P^N|H,d)$ be the moduli space of positive degree maps from smooth curves of genus $1$ to $\mathbb P^N$ with dimensionally transverse contact order $\alpha\in\mathbb Z^n_{\geq 0}$ along $H$.
+Let $\mathcal M_{1,\alpha}^\circ(\mathbb P^N|H,d)$ be the moduli space of positive degree maps from smooth curves of genus one to $\mathbb P^N$ with dimensionally transverse contact order $\alpha\in\mathbb Z^n_{\geq 0}$ along $H$.
 
@@
 
-\subsection{The absolute case} Let $\mathfrak M_{1,n}$ be the logarithmic algebraic stack of $n$-pointed prestable curves of genus $1$.
+\subsection{The absolute case} Let $\mathfrak M_{1,n}$ be the logarithmic algebraic stack of $n$-pointed prestable curves of genus one.
 Let $C$ be a logarithmically smooth curve over $S$, let $\plC$ denote its tropicalization, and let $\lambda$ be the section of $\overline{M}_{C/S}$ given by the distance from each vertex to the minimal genus one subcurve.
 
-We begin by recalling the logarithmic moduli spaces of genus $1$ curves constructed in~\cite[\S\S 2 \& 4]{RSPW}.
+We begin by recalling the logarithmic moduli spaces of genus one curves constructed in~\cite[\S\S 2 \& 4]{RSPW}.
 Given a family of tropical curves over a base $\sigma$, a central alignment is a piecewise-linearly varying choice of radius $\delta_s\in \overline{M}_S$ for $s\in\sigma$, together with a consistent ordering of the vertices that lie inside the circle of radius $\delta_s$ around the core.
@@
 
-\tred{In essence, this is a family of curves where every vertex of the tropical curve $\plC$ is either inside or outside the circle of radius $\delta$ around the core genus $1$ subcurve.}
+\tred{In essence, this is a family of curves where every vertex of the tropical curve $\plC$ is either inside or outside the circle of radius $\delta$ around the core genus one subcurve.}
 
@@
 Let $\PP^N$ be endowed with the divisorial logarithmic structure induced by $H$.
-The moduli space $\overline{\mathcal{M}}^{\operatorname{log}}_{1,\alpha}(\mathbb P^N|H,d)$ is a fibred category over logarithmic schemes, whose fibre over $(S,M_S)$ is the groupoid of logarithmic curves of genus $1$ over $(S,M_S)$ equipped with a map to $\mathbb P^N$ of degree $d$ and contact order $\alpha$.
+The moduli space $\overline{\mathcal{M}}^{\operatorname{log}}_{1,\alpha}(\mathbb P^N|H,d)$ is a fibred category over logarithmic schemes, whose fibre over $(S,M_S)$ is the groupoid of logarithmic curves of genus one over $(S,M_S)$ equipped with a map to $\mathbb P^N$ of degree $d$ and contact order $\alpha$.
 It is a fundamental fact in the subject that this category is representable by a proper algebraic stack with logarithmic structure, parameterizing minimal objects~\cite{ChenLog}.
@@
 
-Let $D_F\subseteq C$ be the maximal genus $1$ subcurve which is mapped to a higher level and contracted by the map $C\to \mathbb P^N[s]$.
+Let $D_F\subseteq C$ be the maximal genus one subcurve which is mapped to a higher level and contracted by the map $C\to \mathbb P^N[s]$.
 Let $\delta_F$ denote the distance from the core to the nearest component of $C \setminus D_F$.
-Similarly let $D_B\subseteq C$ be the maximal genus $1$ subcurve that is contracted by the collapsed map to $\mathbb P^N$ and let $\delta_B$ be the associated radius.
+Similarly let $D_B\subseteq C$ be the maximal genus one subcurve that is contracted by the collapsed map to $\mathbb P^N$ and let $\delta_B$ be the associated radius.
 This coincides with the radius of the underlying map to $\mathbb P^N$.
@@
 \[
-\mathrm{Def}(C,f_B)\to \mathrm{Obs}(f/(C,f_B)) = \HH^1(\overline{C}_F,\mathcal O_{\overline{C}_F}),
+\mathrm{Def}(C,f_B)\to \mathrm{Obs}(f/(C,f_B)) = H^1(\overline{C}_F,\mathcal O_{\overline{C}_F}),
 \]
@@
 
-We note the manner in which the group $\HH^1(\overline{C}_F,\mathcal O_{\overline{C}_F})$ functions as the obstruction group for the lifting.
-It suffices to work near the minimal genus $1$ subcurve $D_F$ of $C$, since the rest of the curve is rational.
+We note the manner in which the group $H^1(\overline{C}_F,\mathcal O_{\overline{C}_F})$ functions as the obstruction group for the lifting.
+It suffices to work near the minimal genus one subcurve $D_F$ of $C$, since the rest of the curve is rational.
 This lifting is given by a rational function with prescribed orders of poles given by the slopes of the tropicalization map.
@@
 Given a strict square-zero extension $S'$ of $S$, the piecewise linear function $\alpha$ extends uniquely by strictness to any deformation of the curve.
-The resulting deformation of $\mathcal O_{C}(-\alpha)$ produces an infinitesimal deformation of the trivial bundle in the Picard group, whose class in $\HH^1(\overline{C}_F,\mathcal O_{\overline{C}_F})$, is the obstruction to deformation.
+The resulting deformation of $\mathcal O_{C}(-\alpha)$ produces an infinitesimal deformation of the trivial bundle in the Picard group, whose class in $H^1(\overline{C}_F,\mathcal O_{\overline{C}_F})$, is the obstruction to deformation.
 We will show that it is possible to choose a deformation of $(C,f_B)$ that cancels out the obstruction to lifting to $f$, and thus the map to the obstruction space above is surjective.
@@
 To prove this, it is convenient to work with the logarithmic multiplicative group and its torsors.
-Recall that the \textit{logarithmic multiplicative group} $\mathbb G_{\mathrm{log}}$ is the functor on logarithmic schemes whose value on a logarithmic scheme $S$ is the group of global sections $\HH^0(S,M_S^{\mathrm{gp}})$; \tred{it is a proper group functor, and it contains $\Gm$ as a subfunctor}.
+Recall that the \textit{logarithmic multiplicative group} $\mathbb G_{\mathrm{log}}$ is the functor on logarithmic schemes whose value on a logarithmic scheme $S$ is the group of global sections $H^0(S,M_S^{\mathrm{gp}})$; it is a proper group functor, and it contains $\Gm$ as a subfunctor.
 This functor is representable only after a logarithmically \'etale cover.
@@
 \begin{definition}
-Let $\plC$ be a tropical curve of genus $1$ and let $\plC_0$ be its minimal subcurve of genus $1$.
+Let $\plC$ be a tropical curve of genus one and let $\plC_0$ be its minimal subcurve of genus one.
 A tropical map $F: \plC\to \mathbb R_{\geq 0}$ is said to be \textbf{well-spaced} if one of the following two conditions are satisfied:
@@
 cit.
-We may focus on a single component of the expansion $\mathbb P^N[s]$ that contains the image of a contracted genus $1$ subcurve, as this is the only relevant case.
+We may focus on a single component of the expansion $\mathbb P^N[s]$ that contains the image of a contracted genus one subcurve, as this is the only relevant case.
 We may thus replace the target with the projective bundle $\mathbb P(\mathcal O(1)\oplus \mathcal O)$ over $\mathbb P^{N-1}$ equipped with the divisorial logarithmic structure from the $0$ and $\infty$ sections.
-Let $p$ be the point to which the genus $1$ subcurve is contracted.
+Let $p$ be the point to which the genus one subcurve is contracted.
 Passing to an open neighborhood of $p$, the map to the bundle is given by a rational function $f$ on an open curve $C^\circ$, determined by the the subgraph formed by $\plC_0$ and the flags $t_i$ described in the definition above.
@@
 \textbf{Step 1}.
-Let $\Sigma^{\mathrm{log}}$ be the tropical moduli space of genus $1$ tropical stable maps to $\mathbb R_{\geq 0}$.
+Let $\Sigma^{\mathrm{log}}$ be the tropical moduli space of genus one tropical stable maps to $\mathbb R_{\geq 0}$.
 This is naturally identified with the tropicalization (in the logarithmic sense) of the Abramovich--Chen--Gross--Siebert space of logarithmic stable maps to the pair $(\mathbb P^N,H)$.
@@
 
-\subsection{Recursive description of the divisors: types $A,B$ and $C^+$} Choose an irreducible component $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$.
+\subsection{Recursive description of the divisors: types I,II and III} Choose an irreducible component $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$.
 By Lemma \ref{Lemma components are logarithmic divisors} this is a logarithmic divisor, and hence may be written as:
@@
         \Yagraph
-        \caption{$A$}
+        \caption{I}
     \end{minipage}\hfill
@@
         \Ybgraph
-        \caption{$B$}
+        \caption{II}
     \end{minipage}\hfill
@@
         \Ycgraph
-        \caption{$C^+$}
+        \caption{III}
     \end{minipage}
@@
 
-\noindent The degrees of vertices, expansions factors, and remaining markings are distributed according to the following rules:
+\noindent The degrees of vertices, expansions factors, and remaining markings are distributed arbitrarily, subject to the following constraints:
 \begin{enumerate}
@@
 \end{enumerate}\end{lemma}
-
-The terminology above due to Vakil, and the configurations in this case are very similar to those analyzed in \cite{Vre}.
+In \cite{Vre} these cases are referred to, respectively, as types $A,B$ and $C^+$.
 
@@
 In order for the cone $\sigma$ to be $1$-dimensional, the dual graph $\Gamma$ must be bipartite, with vertices over $0$ and $\diamond$.
-The cases $A,B$ and $C^+$ enumerated above cover situations where there is a single vertex mapped to $\diamond$.
+The cases I,II and III enumerated above cover situations where there is a single vertex mapped to $\diamond$.
 If there is more than one such vertex, then the contribution to the Gromov--Witten invariant vanishes.
@@
 
-We now investigate the three types $A,B,C^+$ separately, giving a recursive description of the boundary divisor in each case.
-For the remainder of this subsection, therefore, we fix a one-dimensional cone $\tau \in \Sigma_{1,\alpha}(\PP^N|H,d)$, let $\Dcal \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$ be the associated logarithmic divisor, and assume that $\Dcal$ is contained in $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ and is of type $A,B$ or $C^+$.
-We let $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$ be the logarithmic stratum into which $\Dcal$ is mapped; this is indexed by a cone $\epsilon \in \Sigma^{\Kim}$ corresponding to a combinatorial type $\Delta$, and $\epsilon$ is one-dimensional since we are restricting to the type $A,B,C^+$ cases.
-
-\subsubsection{Type $A$}\label{subsubsection type A} Suppose $\Delta$ is of type $A$. Then $\Ecal$ admits a finite and surjective \textit{splitting morphism} onto the fibre product:
+We now investigate the three types I,II and III separately, giving a recursive description of the boundary divisor in each case.
+For the remainder of this subsection, therefore, we fix a one-dimensional cone $\tau \in \Sigma_{1,\alpha}(\PP^N|H,d)$, let $\Dcal \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$ be the associated logarithmic divisor, and assume that $\Dcal$ is contained in $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ and is of type I, II or III.
+We let $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$ be the logarithmic stratum into which $\Dcal$ is mapped; this is indexed by a cone $\epsilon \in \Sigma^{\Kim}$ corresponding to a combinatorial type $\Delta$, and $\epsilon$ is one-dimensional since we are restricting to the type I,II,III cases.
+
+\subsubsection{Type I}\label{subsubsection type A} Suppose $\Delta$ is of type I. Then $\Ecal$ admits a finite and surjective \textit{splitting morphism} onto the fibre product:
 \begin{equation*} \Ecal \to \left( \ol\Mcal_{1,\alpha^{(1)}\cup(m_1)}(\PP^N|H,d_1) \times \prod_{i=2}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i) \right) \times_{H^r} \ol\Mcal^{\leftrightarrow}_{0,\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}(\mathbb{P}|H_0+H_\infty,d_0).\end{equation*}
@@
 
-\subsubsection{Type $B$}
-Now suppose $\Delta$ is of type $B$.
+\subsubsection{Type II}
+Now suppose $\Delta$ is of type II.
 Note that in this case, it is impossible for the core to be contracted.
@@
 
-\subsubsection{Type $C^+$} \label{subsubsection type C+} Finally suppose that $\Delta$ is of type $C^+$. As before we have a finite and surjective morphism:
+\subsubsection{Type III} \label{subsubsection type C+} Finally suppose that $\Delta$ is of type III. As before we have a finite and surjective morphism:
 \begin{equation*} \Ecal \to  \left( \prod_{i=1}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i) \right) \times_{H^r} \ol\Mcal^{\leftrightarrow}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(\mathbb{P}|H_0+H_\infty,d_0).
@@
 Here we describe the degree of $\rho$ and calculate the vanishing order $\lambda_\Dcal$ of the section $s_k$ constructed in \S \ref{Section Gathmann line bundle}.
-This gives a complete recursive description of the terms appearing on the right-hand side of Theorem \ref{theorem recursion} which are of type $A,B$ or $C^+$.
+This gives a complete recursive description of the terms appearing on the right-hand side of Theorem \ref{theorem recursion} which are of type I,II or III.
 
@@
 
-\subsection{Recursive description of the divisors: type IIIb}\label{subsection C0 splitting} The treatment of the type I, II and IIIa cases above is a fairly straightforward extension of the ideas of Vakil and Gathmann (albeit updated with logarithmic and tropical technology, which streamlines the presentation and simplifies the proofs).
-The remaining type IIIb case, however, is entirely new.
+\subsection{Recursive description of the divisors: type $\dag$}\label{subsection C0 splitting} The treatment of the type I, II and III cases above is a fairly straightforward extension of the ideas of Vakil and Gathmann (albeit updated with logarithmic and tropical technology, which streamlines the presentation and simplifies the proofs).
+The remaining type $\dag$ case, however, is entirely new.
 In this section we provide a recursive description of these boundary divisors.
@@
 
-\subsubsection{Possible combinatorial types} A boundary divisor $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ is said to have \textit{type IIIb} if the core is assigned degree zero by the combinatorial type.
+\subsubsection{Possible combinatorial types} A boundary divisor $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ is said to have \textit{type $\dag$} if the core is assigned degree zero by the combinatorial type.
 Divisors of this type occur as principal components in compactified torus bundles over strata in the space of relative maps.
@@
 \begin{lemma} \label{lemma type C0 combinatorial types}
-Let $\Dcal$ be a locus of type IIIb with combinatorial type $\Delta$ which contributes nontrivially to the Gromov--Witten invariant.
+Let $\Dcal$ be a locus of type $\dag$ with combinatorial type $\Delta$ which contributes nontrivially to the Gromov--Witten invariant.
 For every nonzero vertex $\diamond$ of the tropical target, the fibre of the tropical map over $\diamond$ contains exactly one stable vertex, which either is the core, or lies on the circle.
@@
 The first morphism is a closed embedding cut out by the two factorisation properties.
-The second morphism is a toroidal modification.
+The second morphism is a logarithmic modification.
 Let $\tau \in \Sigma_{1,\alpha}(\PP^N|H,d)$ be the ray corresponding to $\Dcal \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$, and to the virtual divisor $\widetilde \Dcal \subseteq \widetilde{\VZ}_{1,\alpha}(\PP^N|H,d)$.
@@
 \begin{equation*} T_{p}C^\prime \otimes T C_0\end{equation*}
-where $C^\prime$ is any component of $C$ which lies on the radius, $p$ is the adjacent node which points towards the core, and $T C_0$ is the universal tangent line bundle on the moduli space for $\sqC_0$.
+where $C^\prime$ is any component of $C$ which lies on the circle, $p$ is the adjacent node which points towards the core, and $T C_0$ is the universal tangent line bundle on the moduli space for $\sqC_0$.
 \end{lemma}
@@
 \end{align*}
-where in the last line we have used the same telescoping trick $\TT_{f_1}C_1^0 \otimes \TT_{e_1} C_1^0 = \OO$ used in the proof of Lemma \ref{lemma fibres of Odelta}.
+where in the last line we have used the same telescoping trick T$T_{f_1}C_1^0 \otimes T_{e_1} C_1^0 = \OO$ used in the proof of Lemma \ref{lemma fibres of Odelta}.
 On the other hand, for $T_2$ we may write $f=f/2 + g/2=f_3+g_3$ in order to obtain:
@@
 Recall that all of the genus zero data has already been computed, so we only need to focus on the genus one pieces.
-First consider the type $A$ loci.
+First consider the type I loci.
 The genus one piece has strictly smaller degree (and hence is recursively known) exept in the following situation (with some stable distribution of the remaining markings):
@@
 
-The contributions of the type $B$ loci only involve genus zero data and hence are known.
-The contributions of the type $C^0$ loci are determined by genus zero data and tautological integrals on Deligne--Mumford space, hence are also known.
-It remains to consider type $C^+$ loci.
+The contributions of the type II loci only involve genus zero data and hence are known.
+The contributions of the type $\dag$ loci are determined by genus zero data and tautological integrals on Deligne--Mumford space, hence are also known.
+It remains to consider type III loci.
 If the degree of the genus one piece is less than $d$ then we have a rubber invariant of strictly smaller degree.
@@
 The left-hand side is a forgetful relative invariant of degree $d$ and $\leq n+1$ true markings, and so has already been computed.
-For the right-hand side, let us begin with loci of type $A$.
+For the right-hand side, let us begin with loci of type I.
 The genus one contributions from each loci have $(d^\prime,n^\prime) < (d,n)$ except in the following case
@@
 Here $\gamma$ is the insertion we started with; the difference is that we are now considering relative maps to $(X,Y)$ with maximal tangency at $x_1$, rather than absolute maps to $Y$.
-The type $B$ and $C^0$ loci are recursively determined as in Step~1, and similarly the type $C^+$ loci are recursively determined except for the locus where the entire curve is mapped into the divisor.
+The type II and $\dag$ loci are recursively determined as in Step~1, and similarly the type III loci are recursively determined except for the locus where the entire curve is mapped into the divisor.
 On this locus we may apply $\fgt_{x_0}$ and identify the contribution with
@@
 What remains on the left-hand side is a forgetful relative invariant of degree $d$ and $\leq n+1$ true markings ($y$ being the ``forgetful'' marking), hence is recursively known.
-On the right-hand side, the type $A$ loci are recursively known except possibly in the following special cases (with some stable distribution of the remaining non-relative markings):
+On the right-hand side, the type I loci are recursively known except possibly in the following special cases (with some stable distribution of the remaining non-relative markings):
 \begin{center}
@@
 which gives us the first term on the right-hand side of \eqref{step 2 recursion 2}.
-As usual the type $B$ and $C^0$ contributions are known recursively, and the only type $C^+$ contribution not known recursively occurs when the entire curve is mapped into the divisor, in which case we apply $\fgt_y$ to calculate the contribution as:
+As usual the type II and $\dag$ contributions are known recursively, and the only type III contribution not known recursively occurs when the entire curve is mapped into the divisor, in which case we apply $\fgt_y$ to calculate the contribution as:
 \begin{equation*} (-\gamma/d) \cap [\VZ_{1,n}(Y,\beta)] = -I/d.\end{equation*}
@@
 The left-hand side is a relative invariant with the same degree and number of true markings, but smaller true tangency: hence it is recursively known.
-On the right-hand side, the type $A$ contributions are recursively known except for those of the following form
+On the right-hand side, the type I contributions are recursively known except for those of the following form
 
@@
 
-As usual the type $B$ and $C^0$ contributions are recursively known.
-The type $C^+$ contributions are determined by lower-degree rubber invariants, except for when the whole curve is mapped into $Y$; however in this case we may apply $\fgt_y$ to identify the contribution with an absolute invariant of $Y$ with degree $d$ and $n$ markings, which is also recursively known.
+As usual the type II and $\dag$ contributions are recursively known.
+The type $III$ contributions are determined by lower-degree rubber invariants, except for when the whole curve is mapped into $Y$; however in this case we may apply $\fgt_y$ to identify the contribution with an absolute invariant of $Y$ with degree $d$ and $n$ markings, which is also recursively known.
 Thus we have determined the invariant $I$.

### 2019-06-28 EllipticSingularitiesSplitting.tex
minor changes to second way of D from Dtilde

@@
 This is implied by the fact that the cone $\tau$ corresponding to $\Dcal$ is a ray.
-If the vertex on the circle is strictly semistable -- so that in particular the collapsed map $f_B$ is constant along the corresponing component -- it can be seen that the factorisation condition is unaffected by $\Gm$-scaling the coordinate corresponding to that vertex in the moduli space of attachments, so the map $\Dcal\to\Ecal$ has generic fiber of positive dimension and the contribution vanishes.
+If the vertex on the circle is strictly semistable -- so that in particular the collapsed map $f_B$ is constant along the corresponing component -- it can be seen that the factorisation condition is unaffected by $\Gm$-scaling the coordinate corresponding to that vertex in the moduli space of attaching data, so the map $\Dcal\to\Ecal$ has generic fibre of positive dimension and the contribution vanishes.
 
@@
 \end{proof}
+For the remainder of this section we use the following notation for the combinatorial type $\Delta$; we let $\sqC_0$ denotes the vertex of dual graph corresponding to the core, $\sqC_1,\ldots,\sqC_r$ the other stable vertices (genus zero and lying on the circle, by the previous lemma) and $q_1,\ldots,q_r$ the corresponding splitting nodes.
 
@@
 \]
-is a logarithmic morphism. The generic fiber of this morphism is a toric variety.  \medskip
+is a logarithmic morphism. The generic fibre of this morphism is a toric variety.  \medskip
 
@@
 \begin{lemma}\label{lem:generic_proj_bundle}
- Generically on $\Ecal$, $\widetilde \Dcal\to\widetilde\Ecal$ is given by an explicit projective bundle.
+Generically over $\Ecal$, $\widetilde \Dcal\to\widetilde\Ecal$ is the projectivisation of a tautological vector bundle.
 \end{lemma}
@@
 \begin{proof}
-Let us assume that the curve does not degenerate, so that the dual graph is as prescribed by $\Delta$, in particular there are components $\sqC_1,\ldots,\sqC_r$ generically lying on the circle of radius $\delta$; the moduli space of attachments for the elliptic singularity is the complement of the coordinate hyperplanes in $\PP(\bigoplus_{i=1}^rT_{q_i}C_i)$.
-On the boundary, the circle is allowed to miss some of the $\sqC_i$ - but not all of them!
--, cutting the edge between them and the core (correspondingly, there is a destabilisation of the curve, and an elliptic singularity containing strictly semistable branches).
+Let us assume that the curve does not degenerate, so that the dual graph is as prescribed by $\Delta$.
+In particular there are components $\sqC_1,\ldots,\sqC_r$ generically lying on the circle of radius $\delta$.
+The moduli space of attaching data for the elliptic singularity is the complement of the coordinate hyperplanes in
+$$\PP(\bigoplus_{i=1}^rT_{q_i}C_i).$$
+On the boundary, the circle is allowed to miss some of the $\sqC_i$ -- but not all of them!
+--  cutting the edge between them and the core (correspondingly, there is a destabilisation of the curve, and an elliptic singularity containing strictly semistable branches).
 Tropically, pushing some of the vertices off the circle creates new finite-length edges with coordinates $\ell_i\in\RR_{\geq_0}$ (see Figure \ref{fig:off_we_go}).
@@
 
-A slight modification of this argument is required to account for the fact that all vertices that lie on the circle and are mapped to $0\in\mathbb R_{\geq0}$ by the tropical map are generically aligned on $\Ecal$: indeed, by Lemma \ref{lemma type C0 combinatorial types}, they all have the same contact order $m$, therefore their $T_{q_i}C_i^{\otimes m}$ can be identified via the target tangent line on the fiber product \eqref{IIIa fibre product}, and, after saturation, the $T_{q_i}C_i$ themselves are canonically isomorphic on $\Ecal$.
-Thus, only one factor should be taken to represent all of them in the projective bundle above.
+A slight modification of the argument above is required to account for the fact that all vertices that lie on the circle and are mapped to $0\in\mathbb R_{\geq0}$ by the tropical map are generically aligned on $\Ecal$: indeed, by Lemma \ref{lemma type C0 combinatorial types}, they all have the same contact order $m$, therefore their $T_{q_i}C_i^{\otimes m}$ can be identified via the target tangent line on the fibre product \eqref{IIIa fibre product}, and, after saturation, the $T_{q_i}C_i$ themselves are canonically isomorphic on $\Ecal$.
+Thus, only one summand should be taken to represent all of them in the projective bundle above.
 \end{proof}
@@
 
-\subsubsection{$\Dcal$ from $\widetilde\Dcal$: second way} To establish a more direct connection with the geometry of the fibre product \eqref{IIIa fibre product}, recall that $\widetilde\Ecal$ has been built as an explicit modification of a finite cover of \eqref{IIIa fibre product}.
-For every $v\in\{\sqC_1,\ldots,\sqC_r\}$ - with the convention established at the end of Lemma \ref{lem:generic_proj_bundle} -, on $\widetilde\Ecal$ it makes sense to consider the line bundle $\OO(\delta_v)$ associated to a shortest path from the core to the circle in the $v$-direction.
-Construct $\mathcal P=\PP_{\widetilde\Ecal}(\bigoplus_{v\in \{\sqC_1,\ldots,\sqC_r\}}\OO(\delta_v))$; since $\sqC_1,\ldots,\sqC_r$ are always ordered on $\widetilde \Dcal$ (they may lie on the circle, be the first component off the circle, or degenerate and lie in the strict interior), there is a morphism $\widetilde \Dcal\to\mathcal P$ lifting $\widetilde \Dcal\to\widetilde\Ecal$.
+\subsubsection{$\Dcal$ from $\widetilde\Dcal$: second way} To establish a more direct connection with the geometry of the fibre product \eqref{IIIa fibre product}, recall that $\widetilde\Ecal$ is built as an explicit modification of a finite cover of \eqref{IIIa fibre product}.
+For $i \in\{1,\ldots,r\}$ (with the convention established at the end of Lemma \ref{lem:generic_proj_bundle}), it makes sense on $\widetilde\Ecal$ to consider the line bundle $\OO(\delta_i)$ associated to a shortest path from the core to the circle in the $\sqC_i$-direction.
+Construct
+\begin{equation*}\mathcal P=\PP_{\widetilde\Ecal}\left(\bigoplus_{i=1}^r\OO(\delta_i)\right).\end{equation*}
+Since $\sqC_1,\ldots,\sqC_r$ are always ordered on $\widetilde \Dcal$ (they may lie on the circle, be the first component off the circle, or degenerate and lie in the strict interior), there is a morphism $\widetilde \Dcal\to\mathcal P$ lifting $\widetilde \Dcal\to\widetilde\Ecal$.
 Consider the map of vector bundles on $\mathcal P$:
-\[ \OO_{\mathcal P}(-1)\to p^*(\bigoplus_{v\in \{\sqC_1,\ldots,\sqC_r\}}\OO(\delta_v))\xrightarrow{\sum\operatorname{d}f}\ev_{C_0}^*TH.\]
-
-The composite, regarded as a section $s$ of $G=\OO_{\mathcal P}(1)\otimes \operatorname{ev}_{C_0}^*(TH)$, vanishes precisely where $f$ factors through the elliptic singularity determined by the point in the fiber of $p$.
-Generically on $\widetilde\Ecal$, this is exactly what we are after - compare with Lemma \ref{lem:generic_proj_bundle}.
-On the boundary, though, it may happen that a simultaneous degeneration in the base and the fiber makes this factorisation trivial, in the sense that $\bar f$ would be constant on all the branches of the elliptic singularity.
+\begin{equation*}  \OO_{\mathcal P}(-1)\to p^*\left(\bigoplus_{i=1}^r\OO(\delta_i)\right)\xrightarrow{\sum\operatorname{d}\!f}\ev_q^*TH.\end{equation*}
+The composite, regarded as a section $s$ of $W=\OO_{\mathcal P}(1)\otimes \operatorname{ev}_q^*(TH)$, vanishes precisely where $f$ factors through the elliptic singularity determined by the point in the fibre of $p$.
+Generically on $\widetilde\Ecal$, this is exactly what we are after (compare with Lemma \ref{lem:generic_proj_bundle}).
+On the boundary, though, it may happen that a simultaneous degeneration in the base and the fibre makes this factorisation trivial, in the sense that the map $\bar f$ is constant on all the branches of the elliptic singularity.
 
 \begin{lemma}
- For every $\Lambda_B\subseteq \{\sqC_1,\ldots,\sqC_r\}$ and $\Lambda_F=\{\sqC_1,\ldots,\sqC_r\}\setminus \Lambda_B$, $s$ vanishes along the loci where the factors corresponding to $\Lambda_B$ in $\widetilde \Ecal$ degenerate so that $f_i\colon C_i\to\PP^N$ is constant in a neighbourhood of $q_i$, and the fiber coordinates $(\lambda_j)_{j\in\Lambda_F}$ along $p\colon\mathcal P\to\widetilde \Ecal$ are set to be $0$.
+ For every $\Lambda_B\subseteq \{\sqC_1,\ldots,\sqC_r\}$ and $\Lambda_F=\{\sqC_1,\ldots,\sqC_r\}\setminus \Lambda_B$, $s$ vanishes along the loci where the factors corresponding to $\Lambda_B$ in $\widetilde \Ecal$ degenerate so that $f_i\colon C_i\to\PP^N$ is constant in a neighbourhood of $q_i$, and the fibre coordinates $(\lambda_j)_{j\in\Lambda_F}$ along $p\colon\mathcal P\to\widetilde \Ecal$ are set to be $0$.
 \end{lemma}
-Call these loci $\Xi_i,i\in I$ (compare with \cite[\S 3.2]{VZ} for an analogous phenomenon in the non-relative case); clearly, they may be in excess with respect to the expected codimension of $V(s)$, that is $N-1$.
+Call these loci $\Xi_\Lambda$ for $\Lambda=(\Lambda_B,\Lambda_F)$ (compare with \cite[\S 3.2]{VZ} for an analogous phenomenon in the non-relative case); clearly, they may be in excess with respect to the expected codimension of $V(s)$, that is $N-1$.
 These loci are logarithmic substrata; therefore, there exists a logarithmic blow-up that principalizes them.
-We claim that $\widetilde\Dcal$ is (possibly a refinement of) such a blow-up.
+We claim which $\widetilde\Dcal$ is (possibly a refinement of) such a blow-up.
 \begin{lemma}
- The pullback of $\Xi_i$ is principal in $\widetilde\Dcal$.
+ The pullback of $\Xi_\Lambda$ is principal in $\widetilde\Dcal$.
 \end{lemma}
-\begin{proof}
- Let us analyse the ideal of $\Xi_i$: it is generated by
- \begin{enumerate}[leftmargin=.5 cm]
-  \item equations on $\widetilde\Ecal$ cutting the locus where $C_i$ degenerates so that $f_i$ is constant on a neighbourhood of $q_i$, $i\in \Lambda_B$: these correspond to the tropical functions $\delta_i-\operatorname{dist}(q_i,\circ)$;
-  \item equations on the fiber of $p$ for the linear subspace corresponding to $j\in \Lambda_F$: tropically, these correspond to the $\ell_j$ discussed in Lemma Lemma \ref{lem:generic_proj_bundle}.
+\begin{proof}We analyse the ideal of $\Xi_\Lambda$: it is generated by
+ \begin{enumerate}
+  \item equations on $\widetilde\Ecal$ cutting the locus where $C_i$ degenerates so that $f_i$ is constant on a neighbourhood of $q_i$ for $i\in \Lambda_B$: these correspond to the tropical functions $\delta_i-\lambda(q_i)$ where $\lambda$ is the distance function to the core;
+  \item equations on the fibre of $p$ for the linear subspace corresponding to $i\in \Lambda_F$: tropically, these correspond to the $\ell_i$ discussed in Lemma \ref{lem:generic_proj_bundle}.
  \end{enumerate}
-By construction, on $\widetilde \Dcal$ it is always possible to tell which of these tropical lengths is the shortest (the circle we have drawn on $\Xi$ is degenerate - it passes through no vertex of positive horizontal degree -, therefore we need to decide for a strictly larger circle in order to lift to $\widetilde D$), which corresponds to principalising the ideal (see Figure \ref{fig:principalisation}).
+By construction, on $\widetilde \Dcal$ it is always possible to tell which of these tropical lengths is the shortest (the circle we have drawn on $\Xi_\Lambda$ is degenerate -- it passes through no vertex of positive horizontal degree -- therefore we need to decide for a strictly larger circle in order to lift to $\widetilde D$), which corresponds to principalising the ideal (see Figure \ref{fig:principalisation}).
 \end{proof}
@@
 
-Finally, on $\widetilde\Dcal$ (or, in fact, on an intermediate blow-up $\widetilde{\mathcal P}\to\mathcal P$) there are exceptional divisors $\widetilde \Xi_i$ corresponding to $\Xi_i$ in $\mathcal P$.
-Since the $\Xi_i$ exhaust all the excess-dimensional components of the vanishing locus of $s\in\Gamma(\mathcal P,G)$, the latter induces a section $\tilde s\in\Gamma(\widetilde\Dcal,G(-\sum_i\widetilde\Xi_i))$ by pullback and twisting, whose vanishing locus is dimensionally transverse to the boundary, and whose open part coincides with the generic point of $\Dcal$, therefore $V(\tilde s)=\Dcal$.
-
-Expressing the pushforward of the Chern classes of $\OO_F(1)$ and $\OO(\widetilde\Xi_i)$ in terms of tautological classes on the fiber product underlying $\Ecal$, we get:
+Finally, on $\widetilde\Dcal$ (or, in fact, on an intermediate blow-up $\widetilde{\mathcal P}\to\mathcal P$) there are exceptional divisors $\widetilde \Xi_\Lambda$ corresponding to $\Xi_\Lambda$ in $\mathcal P$.
+Since the $\Xi_\Lambda$ exhaust all the excess-dimensional components of the vanishing locus of $s\in H^0(\mathcal P,W)$, the latter induces a section $\tilde s\in H^0(\widetilde\Dcal,W(-\Sigma_\Lambda \widetilde\Xi_\Lambda))$ by pullback and twisting, whose vanishing locus is dimensionally transverse to the boundary, and whose open part coincides with the generic point of $\Dcal$, therefore $V(\tilde s)=\Dcal$.
+
+Expressing the pushforward of the Chern classes of $\OO_W(1)$ and $\OO(\widetilde\Xi_\Lambda)$ in terms of tautological classes on the fibre product underlying $\Ecal$, we get:
 \begin{cor}

### 2019-06-28 EllipticSingularitiesSplitting.tex
minor changes

@@
 While the Atiyah--Bott localization for the reduced invariants was used to great effect by Zinger in his proof of the BCOV conjectures, two major components of the standard theory -- relative invariants and the degeneration formula -- have not been developed in this setting.
-Our results in this paper provide these as new {structural} tools in reduced genus one Gromov--Witten theory\footnote{Further motivation to consider the genus one case specifically comes simply from the fact that for Calabi--Yau geometries in dimension larger than $3$, Gromov--Witten theory vanishes in genera greater than $1$.}.
+Our results in this paper provide these as new {structural} tools in reduced genus one Gromov--Witten theory\footnote{Further motivation to consider the genus one case specifically comes simply from the fact that for Calabi--Yau geometries in dimension larger than $3$, Gromov--Witten theory vanishes in genera greater than one.}.
 
@@
 \begin{enumerate}
-\item the \tred{restricted} reduced genus one Gromov--Witten invariants of $Y$;
+\item the (restricted) reduced genus one Gromov--Witten invariants of $Y$;
 \item the reduced genus one relative Gromov--Witten invariants of $(X,Y)$; 
-\item the \tred{restricted} reduced genus one rubber invariants of $P=\PP_Y(\operatorname{N}_{Y|X} \oplus \OO_Y)$
+\item the (restricted) reduced genus one rubber invariants of $\mathbb{P}=\PP_Y(\operatorname{N}_{Y|X} \oplus \OO_Y)$
 \end{enumerate}
-from the \tred{full genus zero and reduced genus one theory} of the ambient variety $X$.
+from the full genus zero and reduced genus one invariants of the ambient variety $X$.
 \end{customthm}
@@
 
-Our analysis leads naturally to \tred{the} study of a ``main component’’ double ramification cycle for target manifolds in genus one.
+Our analysis leads naturally to the study of a ``main component’’ double ramification cycle for target manifolds in genus one.
 The virtual geometry of this was studied in recent work of Janda, Pandharipande, Pixton, and Zvonkine~\cite{DRCBundle}.
-We do not know how to calculate a \tred{closed formula} for this main component contribution, but we repurpose E.~Katz's topological recursion relations \cite{EKatz} to complete the algorithm.
+We do not know how to calculate a closed formula for this main component contribution (except in the case where the target manifold is a point), but we repurpose E.~Katz's topological recursion relations \cite{EKatz} to complete the algorithm.
 We note that even in genus one, an understanding of the main component contributions of the double ramification cycle for target manifolds would be interesting.
@@
 
-\subsection*{Acknowledgements} We have benefited from fruitful conversations with friends and colleagues, including Francesca Carocci, Cristina Manolache, Davesh Maulik, Jonathan Wise, and [other people].
+\subsection*{Acknowledgements} We have benefited from fruitful conversations with friends and colleagues, including Francesca Carocci, Cristina Manolache, Davesh Maulik, Jonathan Wise, and \tred{[other people]}.
 Important aspects of this work were completed while L.B.
@@
 
-\begin{thm}
+\begin{thm}\label{thm rubber log smooth}
 The stack $\VZ^{\leftrightarrow}_{1,\alpha}(\mathbb P|H_0+H_\infty,d)$ is logarithmically smooth.
@@
 
-The main point in the proof of this statement is that on the space of non-degenerate maps with smooth domains, the map from $\VZ^\circ_{1,\alpha}(\mathbb P|H_0+H_\infty,d)\to \VZ^{\leftrightarrow,\circ}_{1,\alpha}(\mathbb P|H_0+H_\infty,d)$ is a $\mathbb G_{\operatorname{m}}$ torsor.
+The main point in the proof of this statement is that on the space of non-degenerate maps with smooth domains, the map from $\VZ^\circ_{1,\alpha}(\mathbb P|H_0+H_\infty,d)\to \VZ^{\leftrightarrow,\circ}_{1,\alpha}(\mathbb P|H_0+H_\infty,d)$ is a $\mathbb G_{\operatorname{m}}$-torsor.
 Correspondingly, the map on compact moduli spaces is a nodal curve fibration.
@@
 
-\marginnote{Bundle can have higher levels, so should rephrase this}The bundle $\mathbb P\to \mathbb P^{N-1}$ gives rise to a $\mathbb G_{\operatorname{m}}$-torsor by deleting the zero and infinity sections.
+Each fibre of the bundle $\mathbb P \to \mathbb P^{N-1}$ admits a natural log \'etale morphism to $\mathbb G_{\mathrm{log}}$.
+Replacing these fibres by $\mathbb G_{\mathrm{log}}$, we obtain a non-representable functor on logarithmic schemes $\mathbb P_{\mathrm{log}}$ and a logarithmically \'etale modification
+\[
+\mathbb P\to \mathbb P_{\mathrm{log}}.
+\]
+
+%%%%%%%%%%%%%%%
+\begin{comment}
+%Bundle can have higher levels, so should rephrase this
+The bundle $\mathbb P\to \mathbb P^{N-1}$ gives rise to a $\mathbb G_{\operatorname{m}}$-torsor by deleting the zero and infinity sections.
 Replacing these fibres by their $\mathbb G_{\mathrm{log}}$ compactifications, we obtain a non-representable functor on logarithmic schemes $\mathbb P_{\mathrm{log}}$ and a logarithmically \'etale modification
@@
 \]
-
-\begin{proof}
+\end{comment}
+%%%%%%%%%%%%%%
+
+\begin{proof}[Proof of Theorem \ref{thm rubber log smooth}]
 Consider the stack over logarithmic schemes $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}},d)$ of stable logarithmic maps that factorise completely.
@@
 The moduli space of attaching data for the elliptic singularity is the complement of the coordinate hyperplanes in
-$$\PP(\bigoplus_{i=1}^rT_{q_i}C_i).$$
+$$\PP\left(\bigoplus_{i=1}^rT_{q_i}C_i\right).$$
 On the boundary, the circle is allowed to miss some of the $\sqC_i$ -- but not all of them!
@@
 \end{align*}
-where in the last line we have used the same telescoping trick T$T_{f_1}C_1^0 \otimes T_{e_1} C_1^0 = \OO$ used in the proof of Lemma \ref{lemma fibres of Odelta}.
+where in the last line we have used the same telescoping trick used in the proof of Lemma \ref{lemma fibres of Odelta}, namely that $T_{f_1}C_1^0 \otimes T_{e_1} C_1^0 = \OO$.
 On the other hand, for $T_2$ we may write $f=f/2 + g/2=f_3+g_3$ in order to obtain:

### 2019-06-28 EllipticSingularitiesSplitting.tex
minor changes to \S1

--- 2019-06-28 EllipticSingularitiesSplitting.tex
@@
 These invariants form the principal part contribution to relative Gromov--Witten theory in genus one and are relative versions of Zinger's reduced Gromov--Witten invariants.
-The relative and absolute theories are related by degeneration of the tangency conditions, and the resulting formulas generalize a well-known recursive calculation scheme put forward by Gathmann in genus zero.
+The relative and absolute theories are related by degeneration of the tangency conditions, and the resulting formulas generalize a well-known recursive calculation scheme put forward by Gathmann in genus $0$.
 {The geometric input is a desingularization of the principal component of the moduli space of genus one logarithmic stable maps to a very ample pair, using the geometry of elliptic singularities.
@@
 
-The Kontsevich moduli space of stable maps from genus zero curves to projective space exhibits remarkable geometry -- it is a smooth orbifold with a ``self-similar'' normal crossings boundary.
-These facts have combined to produce a very {satisfactory} understanding of Gromov--Witten theory in genus zero.
+The Kontsevich moduli space of stable maps from genus $0$ curves to projective space exhibits remarkable geometry -- it is a smooth orbifold with a ``self-similar'' normal crossings boundary.
+These facts have combined to produce a very {satisfactory} understanding of Gromov--Witten theory in genus $0$.
 
@@
 
-Let $\mathcal M_{1,\alpha}^\circ(\mathbb P^N|H,d)$ be the moduli space of positive degree maps from smooth curves of genus one to $\mathbb P^N$ with dimensionally transverse contact order $\alpha\in\mathbb Z^n_{\geq 0}$ along $H$.
+Let $\mathcal M_{1,\alpha}^\circ(\mathbb P^N|H,d)$ be the moduli space of positive degree maps from smooth curves of genus $1$ to $\mathbb P^N$ with dimensionally transverse contact order $\alpha\in\mathbb Z^n_{\geq 0}$ along $H$.
 
@@
 
-\tred{In essence, this is a family of curves where every vertex of the tropical curve $\plC$ is either inside or outside the circle of radius $\delta$ around the core genus one subcurve.}
+\sout{In essence, this is a family of curves where every vertex of the tropical curve $\plC$ is either inside or outside the circle of radius $\delta$ around the core genus $1$ subcurve.}
 
@@
 where $\overline{\mathcal C}_S$ may contain a Gorenstein elliptic singularity \cite{SMY1}.
-The number of branches is equal to the sum of the number of vertices which lie on the circle of radius $\delta$ and the number of edges which are split by the same circle.
+The number of branches is equal to the sum of the number of vertices \tred{of $\widetilde{\sqC}$} which lie on the circle of radius $\delta$ \sout{and the number of edges which are split by the same circle}.
 This data uniquely determines the singularity.
 
-The space of stable maps $\widetilde\VZ_{1,n}(\PP^N,d)$ from the universal nodal curve $\mathcal C$ over the stack $\mathfrak M_{1,n}^{\mathrm{cen}}$ is a proper and algebraic, with projective coarse moduli space.
+The space of stable maps $\widetilde\VZ_{1,n}(\PP^N,d)$ from the universal nodal curve $\mathcal C$ over the stack $\mathfrak M_{1,n}^{\mathrm{cen}}$ is algebraic and proper, with projective coarse moduli space.
 A compatibility condition between the alignment and the map is required, namely that the circle of radius $\delta$ passes through at least one component of positive degree.
@@
 Let $\PP^N$ be endowed with the divisorial logarithmic structure induced by $H$.
-The moduli space $\overline{\mathcal{M}}^{\operatorname{log}}_{1,\alpha}(\mathbb P^N|H,d)$ is a fibred category over logarithmic schemes, whose fibre over $(S,M_S)$ is the groupoid of logarithmic curves of genus one over $(S,M_S)$ equipped with a map to $\mathbb P^N$ of degree $d$ and contact order $\alpha$.
+The moduli space $\overline{\mathcal{M}}^{\operatorname{log}}_{1,\alpha}(\mathbb P^N|H,d)$ is a fibred category over logarithmic schemes, whose fibre over $(S,M_S)$ is the groupoid of logarithmically smooth curves of genus one over $(S,M_S)$ equipped with a logarithmic map to $\mathbb P^N$ of degree $d$ and contact order $\alpha$.
 It is a fundamental fact in the subject that this category is representable by a proper algebraic stack with logarithmic structure, parameterizing minimal objects~\cite{ChenLog}.
@@
 $$
-The space of centrally aligned maps is a logarithmic modification:
-$$
-\widetilde\VZ_{1,n}(\PP^N,d)\to\overline{ \mathcal M}_{1,n}(\mathbb P^N,d).
-$$ 
-The fibre product leads to a fourth moduli space of \textbf{centrally aligned logarithmic maps to $(\mathbb P^n,H)$}, which we denote $\widetilde{\VZ}_{1,\alpha}(\mathbb P^N|H,d)$.
+We require the logarithmic structure of the source curve to be aligned in a compatible way with the map to $\PP^N$.
+We thus get the moduli space of \textbf{centrally aligned logarithmic maps to $(\mathbb P^n,H)$}, which we denote $\widetilde{\VZ}_{1,\alpha}(\mathbb P^N|H,d)$.
+It is a logarithmic modification of $\overline{\mathcal M}^{\mathrm{log}}_{1,\alpha}(\mathbb P^N|H,d)$, and it maps down to $\widetilde\VZ_{1,n}(\PP^N,d)$ under forgetting the logarithmic structure of the target.
 
@@
 
-Let $D_F\subseteq C$ be the maximal genus one subcurve which is mapped to a higher level and contracted by the map $C\to \mathbb P^N[s]$.
+Let $D_F\subseteq C$ be the maximal genus $1$ subcurve which is mapped to a higher level and contracted by the map $C\to \mathbb P^N[s]$.
 Let $\delta_F$ denote the distance from the core to the nearest component of $C \setminus D_F$.
-Similarly let $D_B\subseteq C$ be the maximal genus one subcurve that is contracted by the collapsed map to $\mathbb P^N$ and let $\delta_B$ be the associated radius.
+Similarly let $D_B\subseteq C$ be the maximal genus $1$ subcurve that is contracted by the collapsed map to $\mathbb P^N$ and let $\delta_B$ be the associated radius.
 This coincides with the radius of the underlying map to $\mathbb P^N$.
@@
 
-We note the manner in which the group $H^1(\overline{C}_F,\mathcal O_{\overline{C}_F})$ functions as the obstruction group for the lifting.
-It suffices to work near the minimal genus one subcurve $D_F$ of $C$, since the rest of the curve is rational.
+We note the manner in which the group $\HH^1(\overline{C}_F,\mathcal O_{\overline{C}_F})$ functions as the obstruction group for the lifting.
+It suffices to work near the minimal genus $1$ subcurve $D_F$ of $C$, since the rest of the curve is rational.
 This lifting is given by a rational function with prescribed orders of poles given by the slopes of the tropicalization map.
@@
 To prove this, it is convenient to work with the logarithmic multiplicative group and its torsors.
-Recall that the \textit{logarithmic multiplicative group} $\mathbb G_{\mathrm{log}}$ is the functor on logarithmic schemes whose value on a logarithmic scheme $S$ is the group of global sections $H^0(S,M_S^{\mathrm{gp}})$; it is a proper group functor, and it contains $\Gm$ as a subfunctor.
+Recall that the \textit{logarithmic multiplicative group} $\mathbb G_{\mathrm{log}}$ is the functor on logarithmic schemes whose value on a logarithmic scheme $S$ is the group of global sections $\HH^0(S,M_S^{\mathrm{gp}})$; \tred{it is a proper group functor, and it contains $\Gm$ as a subfunctor}.
 This functor is representable only after a logarithmically \'etale cover.
@@
 \begin{definition}
-Let $\plC$ be a tropical curve of genus one and let $\plC_0$ be its minimal subcurve of genus one.
+Let $\plC$ be a tropical curve of genus $1$ and let $\plC_0$ be its minimal subcurve of genus $1$.
 A tropical map $F: \plC\to \mathbb R_{\geq 0}$ is said to be \textbf{well-spaced} if one of the following two conditions are satisfied:
@@
 cit.
-We may focus on a single component of the expansion $\mathbb P^N[s]$ that contains the image of a contracted genus one subcurve, as this is the only relevant case.
+We may focus on a single component of the expansion $\mathbb P^N[s]$ that contains the image of a contracted genus $1$ subcurve, as this is the only relevant case.
 We may thus replace the target with the projective bundle $\mathbb P(\mathcal O(1)\oplus \mathcal O)$ over $\mathbb P^{N-1}$ equipped with the divisorial logarithmic structure from the $0$ and $\infty$ sections.
-Let $p$ be the point to which the genus one subcurve is contracted.
+Let $p$ be the point to which the genus $1$ subcurve is contracted.
 Passing to an open neighborhood of $p$, the map to the bundle is given by a rational function $f$ on an open curve $C^\circ$, determined by the the subgraph formed by $\plC_0$ and the flags $t_i$ described in the definition above.
@@
 \textbf{Step 1}.
-Let $\Sigma^{\mathrm{log}}$ be the tropical moduli space of genus one tropical stable maps to $\mathbb R_{\geq 0}$.
+Let $\Sigma^{\mathrm{log}}$ be the tropical moduli space of genus $1$ tropical stable maps to $\mathbb R_{\geq 0}$.
 This is naturally identified with the tropicalization (in the logarithmic sense) of the Abramovich--Chen--Gross--Siebert space of logarithmic stable maps to the pair $(\mathbb P^N,H)$.
@@
 
-\subsection{Recursive description of the divisors: types I,II and III} Choose an irreducible component $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$.
+\subsection{Recursive description of the divisors: types $A,B$ and $C^+$} Choose an irreducible component $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$.
 By Lemma \ref{Lemma components are logarithmic divisors} this is a logarithmic divisor, and hence may be written as:
@@
         \Yagraph
-        \caption{I}
+        \caption{$A$}
     \end{minipage}\hfill
@@
         \Ybgraph
-        \caption{II}
+        \caption{$B$}
     \end{minipage}\hfill
@@
         \Ycgraph
-        \caption{III}
+        \caption{$C^+$}
     \end{minipage}
@@
 
-\noindent The degrees of vertices, expansions factors, and remaining markings are distributed arbitrarily, subject to the following constraints:
+\noindent The degrees of vertices, expansions factors, and remaining markings are distributed according to the following rules:
 \begin{enumerate}
@@
 \end{enumerate}\end{lemma}
-In \cite{Vre} these cases are referred to, respectively, as types $A,B$ and $C^+$.
+
+The terminology above due to Vakil, and the configurations in this case are very similar to those analyzed in \cite{Vre}.
 
@@
 In order for the cone $\sigma$ to be $1$-dimensional, the dual graph $\Gamma$ must be bipartite, with vertices over $0$ and $\diamond$.
-The cases I,II and III enumerated above cover situations where there is a single vertex mapped to $\diamond$.
+The cases $A,B$ and $C^+$ enumerated above cover situations where there is a single vertex mapped to $\diamond$.
 If there is more than one such vertex, then the contribution to the Gromov--Witten invariant vanishes.
@@
 
-We now investigate the three types I,II and III separately, giving a recursive description of the boundary divisor in each case.
-For the remainder of this subsection, therefore, we fix a one-dimensional cone $\tau \in \Sigma_{1,\alpha}(\PP^N|H,d)$, let $\Dcal \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$ be the associated logarithmic divisor, and assume that $\Dcal$ is contained in $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ and is of type I, II or III.
-We let $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$ be the logarithmic stratum into which $\Dcal$ is mapped; this is indexed by a cone $\epsilon \in \Sigma^{\Kim}$ corresponding to a combinatorial type $\Delta$, and $\epsilon$ is one-dimensional since we are restricting to the type I,II,III cases.
-
-\subsubsection{Type I}\label{subsubsection type A} Suppose $\Delta$ is of type I. Then $\Ecal$ admits a finite and surjective \textit{splitting morphism} onto the fibre product:
+We now investigate the three types $A,B,C^+$ separately, giving a recursive description of the boundary divisor in each case.
+For the remainder of this subsection, therefore, we fix a one-dimensional cone $\tau \in \Sigma_{1,\alpha}(\PP^N|H,d)$, let $\Dcal \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$ be the associated logarithmic divisor, and assume that $\Dcal$ is contained in $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ and is of type $A,B$ or $C^+$.
+We let $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$ be the logarithmic stratum into which $\Dcal$ is mapped; this is indexed by a cone $\epsilon \in \Sigma^{\Kim}$ corresponding to a combinatorial type $\Delta$, and $\epsilon$ is one-dimensional since we are restricting to the type $A,B,C^+$ cases.
+
+\subsubsection{Type $A$}\label{subsubsection type A} Suppose $\Delta$ is of type $A$. Then $\Ecal$ admits a finite and surjective \textit{splitting morphism} onto the fibre product:
 \begin{equation*} \Ecal \to \left( \ol\Mcal_{1,\alpha^{(1)}\cup(m_1)}(\PP^N|H,d_1) \times \prod_{i=2}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i) \right) \times_{H^r} \ol\Mcal^{\leftrightarrow}_{0,\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}(\mathbb{P}|H_0+H_\infty,d_0).\end{equation*}
@@
 
-\subsubsection{Type II}
-Now suppose $\Delta$ is of type II.
+\subsubsection{Type $B$}
+Now suppose $\Delta$ is of type $B$.
 Note that in this case, it is impossible for the core to be contracted.
@@
 
-\subsubsection{Type III} \label{subsubsection type C+} Finally suppose that $\Delta$ is of type III. As before we have a finite and surjective morphism:
+\subsubsection{Type $C^+$} \label{subsubsection type C+} Finally suppose that $\Delta$ is of type $C^+$. As before we have a finite and surjective morphism:
 \begin{equation*} \Ecal \to  \left( \prod_{i=1}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i) \right) \times_{H^r} \ol\Mcal^{\leftrightarrow}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(\mathbb{P}|H_0+H_\infty,d_0).
@@
 Here we describe the degree of $\rho$ and calculate the vanishing order $\lambda_\Dcal$ of the section $s_k$ constructed in \S \ref{Section Gathmann line bundle}.
-This gives a complete recursive description of the terms appearing on the right-hand side of Theorem \ref{theorem recursion} which are of type I,II or III.
+This gives a complete recursive description of the terms appearing on the right-hand side of Theorem \ref{theorem recursion} which are of type $A,B$ or $C^+$.
 
@@
 
-\subsection{Recursive description of the divisors: type $\dag$}\label{subsection C0 splitting} The treatment of the type I, II and III cases above is a fairly straightforward extension of the ideas of Vakil and Gathmann (albeit updated with logarithmic and tropical technology, which streamlines the presentation and simplifies the proofs).
-The remaining type $\dag$ case, however, is entirely new.
+\subsection{Recursive description of the divisors: type IIIb}\label{subsection C0 splitting} The treatment of the type I, II and IIIa cases above is a fairly straightforward extension of the ideas of Vakil and Gathmann (albeit updated with logarithmic and tropical technology, which streamlines the presentation and simplifies the proofs).
+The remaining type IIIb case, however, is entirely new.
 In this section we provide a recursive description of these boundary divisors.
@@
 
-\subsubsection{Possible combinatorial types} A boundary divisor $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ is said to have \textit{type $\dag$} if the core is assigned degree zero by the combinatorial type.
+\subsubsection{Possible combinatorial types} A boundary divisor $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ is said to have \textit{type IIIb} if the core is assigned degree zero by the combinatorial type.
 Divisors of this type occur as principal components in compactified torus bundles over strata in the space of relative maps.
@@
 \begin{lemma} \label{lemma type C0 combinatorial types}
-Let $\Dcal$ be a locus of type $\dag$ with combinatorial type $\Delta$ which contributes nontrivially to the Gromov--Witten invariant.
+Let $\Dcal$ be a locus of type IIIb with combinatorial type $\Delta$ which contributes nontrivially to the Gromov--Witten invariant.
 For every nonzero vertex $\diamond$ of the tropical target, the fibre of the tropical map over $\diamond$ contains exactly one stable vertex, which either is the core, or lies on the circle.
@@
 The first morphism is a closed embedding cut out by the two factorisation properties.
-The second morphism is a logarithmic modification.
+The second morphism is a toroidal modification.
 Let $\tau \in \Sigma_{1,\alpha}(\PP^N|H,d)$ be the ray corresponding to $\Dcal \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$, and to the virtual divisor $\widetilde \Dcal \subseteq \widetilde{\VZ}_{1,\alpha}(\PP^N|H,d)$.
@@
 \begin{equation*} T_{p}C^\prime \otimes T C_0\end{equation*}
-where $C^\prime$ is any component of $C$ which lies on the circle, $p$ is the adjacent node which points towards the core, and $T C_0$ is the universal tangent line bundle on the moduli space for $\sqC_0$.
+where $C^\prime$ is any component of $C$ which lies on the radius, $p$ is the adjacent node which points towards the core, and $T C_0$ is the universal tangent line bundle on the moduli space for $\sqC_0$.
 \end{lemma}
@@
 \end{align*}
-where in the last line we have used the same telescoping trick T$T_{f_1}C_1^0 \otimes T_{e_1} C_1^0 = \OO$ used in the proof of Lemma \ref{lemma fibres of Odelta}.
+where in the last line we have used the same telescoping trick $\TT_{f_1}C_1^0 \otimes \TT_{e_1} C_1^0 = \OO$ used in the proof of Lemma \ref{lemma fibres of Odelta}.
 On the other hand, for $T_2$ we may write $f=f/2 + g/2=f_3+g_3$ in order to obtain:
@@
 Recall that all of the genus zero data has already been computed, so we only need to focus on the genus one pieces.
-First consider the type I loci.
+First consider the type $A$ loci.
 The genus one piece has strictly smaller degree (and hence is recursively known) exept in the following situation (with some stable distribution of the remaining markings):
@@
 
-The contributions of the type II loci only involve genus zero data and hence are known.
-The contributions of the type $\dag$ loci are determined by genus zero data and tautological integrals on Deligne--Mumford space, hence are also known.
-It remains to consider type III loci.
+The contributions of the type $B$ loci only involve genus zero data and hence are known.
+The contributions of the type $C^0$ loci are determined by genus zero data and tautological integrals on Deligne--Mumford space, hence are also known.
+It remains to consider type $C^+$ loci.
 If the degree of the genus one piece is less than $d$ then we have a rubber invariant of strictly smaller degree.
@@
 The left-hand side is a forgetful relative invariant of degree $d$ and $\leq n+1$ true markings, and so has already been computed.
-For the right-hand side, let us begin with loci of type I.
+For the right-hand side, let us begin with loci of type $A$.
 The genus one contributions from each loci have $(d^\prime,n^\prime) < (d,n)$ except in the following case
@@
 Here $\gamma$ is the insertion we started with; the difference is that we are now considering relative maps to $(X,Y)$ with maximal tangency at $x_1$, rather than absolute maps to $Y$.
-The type II and $\dag$ loci are recursively determined as in Step~1, and similarly the type III loci are recursively determined except for the locus where the entire curve is mapped into the divisor.
+The type $B$ and $C^0$ loci are recursively determined as in Step~1, and similarly the type $C^+$ loci are recursively determined except for the locus where the entire curve is mapped into the divisor.
 On this locus we may apply $\fgt_{x_0}$ and identify the contribution with
@@
 What remains on the left-hand side is a forgetful relative invariant of degree $d$ and $\leq n+1$ true markings ($y$ being the ``forgetful'' marking), hence is recursively known.
-On the right-hand side, the type I loci are recursively known except possibly in the following special cases (with some stable distribution of the remaining non-relative markings):
+On the right-hand side, the type $A$ loci are recursively known except possibly in the following special cases (with some stable distribution of the remaining non-relative markings):
 \begin{center}
@@
 which gives us the first term on the right-hand side of \eqref{step 2 recursion 2}.
-As usual the type II and $\dag$ contributions are known recursively, and the only type III contribution not known recursively occurs when the entire curve is mapped into the divisor, in which case we apply $\fgt_y$ to calculate the contribution as:
+As usual the type $B$ and $C^0$ contributions are known recursively, and the only type $C^+$ contribution not known recursively occurs when the entire curve is mapped into the divisor, in which case we apply $\fgt_y$ to calculate the contribution as:
 \begin{equation*} (-\gamma/d) \cap [\VZ_{1,n}(Y,\beta)] = -I/d.\end{equation*}
@@
 The left-hand side is a relative invariant with the same degree and number of true markings, but smaller true tangency: hence it is recursively known.
-On the right-hand side, the type I contributions are recursively known except for those of the following form
+On the right-hand side, the type $A$ contributions are recursively known except for those of the following form
 
@@
 
-As usual the type II and $\dag$ contributions are recursively known.
-The type $III$ contributions are determined by lower-degree rubber invariants, except for when the whole curve is mapped into $Y$; however in this case we may apply $\fgt_y$ to identify the contribution with an absolute invariant of $Y$ with degree $d$ and $n$ markings, which is also recursively known.
+As usual the type $B$ and $C^0$ contributions are recursively known.
+The type $C^+$ contributions are determined by lower-degree rubber invariants, except for when the whole curve is mapped into $Y$; however in this case we may apply $\fgt_y$ to identify the contribution with an absolute invariant of $Y$ with degree $d$ and $n$ markings, which is also recursively known.
 Thus we have determined the invariant $I$.

### 2019-06-28 EllipticSingularitiesSplitting.tex
changed start of 1.1. to make it make more sense

--- 2019-06-28 EllipticSingularitiesSplitting.tex
@@
 \subsection{The absolute case} Let $\mathfrak M_{1,n}$ be the logarithmic algebraic stack of $n$-pointed prestable curves of genus one.
-Let $C$ be a logarithmically smooth curve over $S$, let $\plC$ denote its tropicalization, and let $\lambda$ be the section of $\overline{M}_{C/S}$ given by the distance from each vertex to the minimal genus one subcurve.
-
-We begin by recalling the logarithmic moduli spaces of genus one curves constructed in~\cite[\S\S 2 \& 4]{RSPW}.
-Given a family of tropical curves over a base $\sigma$, a central alignment is a piecewise-linearly varying choice of radius $\delta_s\in \overline{M}_S$ for $s\in\sigma$, together with a consistent ordering of the vertices that lie inside the circle of radius $\delta_s$ around the core.
-Precisely, let $T$ be a geometric point with logarithmic structure.
-
+We begin by recalling the logarithmic moduli spaces of genus one curves constructed in~\cite[\S 2 \& \S 4]{RSPW}.
+Given a logarithmically smooth curve $C$ over a logarithmic geometric point $S$, let $\plC$ denote its tropicalization, and let $\lambda \in \overline{M}_{S}$ be the piecewise-linear function giving the distance from each vertex of $\sqC$ to the minimal genus one subcurve.
 \begin{definition}
-A \textbf{centrally aligned curve} is a pair $(C/T,\delta)$, where $\delta\in\overline{M}_T$, such that:
+A \textbf{centrally aligned curve} is a pair $(C/S,\delta)$, where $\delta\in\overline{M}_S$, such that:
 \begin{enumerate}
-    \item the section $\delta$ is comparable to $\lambda(v)$ for all vertices $v$ of $\plC$,
-    \item for any pair of vertices $v$ and $w$ at distance less than $\delta$, the sections $\lambda(v)$ and $\lambda(w)$ are comparable.
+    \item the section $\delta$ is comparable to $\lambda(v)$ for all vertices $v$ of $\plC$;
+    \item for any pair of vertices $v$ and $w$ of distance less than $\delta$, the sections $\lambda(v)$ and $\lambda(w)$ are comparable.
 \end{enumerate}
@@
 
-The moduli stack $\mathfrak M_{1,n}^{\mathrm{cen}}$ is a logarithmic algebraic stack in the smooth topology, and $\mathfrak M_{1,n}^{\mathrm{cen}}\to\mathfrak M_{1,n}$ is a logarithmic modification.
+The moduli stack $\mathfrak M_{1,n}^{\mathrm{cen}}$  of centrally aligned curves is a logarithmic algebraic stack in the smooth topology, and $\mathfrak M_{1,n}^{\mathrm{cen}}\to\mathfrak M_{1,n}$ is a logarithmic modification.
 The main construction of~\cite{RSPW} canonically associates to any centrally aligned family of curves $\mathcal C_S$ a partial destabilisation $\widetilde{\mathcal C}_S$ and a contraction
@@
 
-The space of stable maps $\widetilde\VZ_{1,n}(\PP^N,d)$ from the universal nodal curve $\mathcal C$ over the stack $\mathfrak M_{1,n}^{\mathrm{cen}}$ is a proper and algebraic, with projective coarse moduli space.
+The space of stable maps $\widetilde\VZ_{1,n}(\PP^N,d)$ from the universal nodal curve $\mathcal C$ over the stack $\mathfrak M_{1,n}^{\mathrm{cen}}$ is proper and algebraic, with projective coarse moduli space.
 A compatibility condition between the alignment and the map is required, namely that the circle of radius $\delta$ passes through at least one component of positive degree.
@@
 \begin{thm}[{\cite[Theorem B]{RSPW}}]
-The substack $\VZ_{1,n}(\mathbb P^N,d)$ of $\widetilde\VZ_{1,n}(\PP^N,d)$ parameterizing maps to $\mathbb P^N$ that satisfy the factorisation property is smooth and proper of the expected dimension.
+The substack $\VZ_{1,n}(\mathbb P^N,d)$ of $\widetilde\VZ_{1,n}(\PP^N,d)$ parameterizing maps to $\mathbb P^N$ that satisfy the factorisation condition is smooth and proper of the expected dimension.
 \end{thm}
 
-The remainder of this section lifts this condition to the category of relative maps to the pair $(\mathbb P^N,H)$.
+The remainder of this section lifts this construction to the category of relative maps to the pair $(\mathbb P^N,H)$.
 The core of the result is identifying the necessary factorisation conditions that remove the obstructions.

### 2019-06-28 EllipticSingularitiesSplitting.tex
minor changes

@@
 \begin{equation*} \fgt_S \colon \VZ_{1,\alpha}(X|Y,\beta) \to \VZ_{1,m-\#S}(X,\beta).\end{equation*}
-In particular, all the psi classes which we consider are \emph{collapsed psi classes}, meaning that they are relative cotangent line classes for the corresponding collapsed stable map.
+In particular, all the psi classes which we consider are \textbf{collapsed psi classes}, meaning that they are relative cotangent line classes for the corresponding collapsed stable map.
 Note that, unlike in the absolute case, in the relative case it may well be the case that the entire insertion is pulled back along a single forgetful map $\fgt_S$.
@@
 \begin{equation*}\label{Psi0 formula} \Psi_0 = -\alpha_2 \hat\psi_2 - \ev_2^\st Y \end{equation*}
-where $\hat\psi_2$ is a \emph{non-collapsed} psi class.
+where $\hat\psi_2$ is a \textbf{non-collapsed} psi class.
 (If there are no negative-tangency markings, then the construction given in \cite[\S 1.5.2]{MaulikPandharipande} shows that $\Psi_0=0$.) Now, $\hat\psi_2 - \psi_2$ is given by the loci where $x_2$ belongs to a trivial bubble.

### 2019-06-28 EllipticSingularitiesSplitting.tex

@@
 where $\overline{\mathcal C}_S$ may contain a Gorenstein elliptic singularity \cite{SMY1}.
-The number of branches is equal to the sum of the number of vertices which lie on the circle of radius $\delta$ and the number of edges which are split by the same circle.
+The number of branches is equal to the sum of the number of vertices \tred{of $\widetilde{\sqC}$} which lie on the circle of radius $\delta$ \sout{and the number of edges which are split by the same circle}.
 This data uniquely determines the singularity.
@@
 
-This subdivision is best described using the formalism of extended tropicalisations \cite{}.
+This subdivision is best described using the formalism of extended tropicalizations \cite{}.
 The subdividing cones are obtained from cones in the star of $\tau$ under the limit $e_1=\cdots=e_r=\infty$.
@@
 By construction, we have a map $\widetilde\Dcal \to \widetilde\Ecal$ which is a compactification of a torus bundle over $\widetilde\Ecal$.
-The strata of $\widetilde\Dcal$ can be read off from its tropicalisation, and in particular we have the information of how (polynomials in) the classes of boundary strata push forward to $\widetilde\Ecal$.
+The strata of $\widetilde\Dcal$ can be read off from its tropicalization, and in particular we have the information of how (polynomials in) the classes of boundary strata push forward to $\widetilde\Ecal$.
 

### 2019-06-28 EllipticSingularitiesSplitting.tex
minor changes

@@
 where $\overline{\mathcal C}_S$ may contain a Gorenstein elliptic singularity \cite{SMY1}.
-The number of branches is equal to the sum of the number of vertices \tred{of $\widetilde{\sqC}$} which lie on the circle of radius $\delta$ \sout{and the number of edges which are split by the same circle}.
+The number of branches is equal to the sum of the number of vertices of $\widetilde{\sqC}$ which lie on the circle of radius $\delta$.
 This data uniquely determines the singularity.

### 2019-06-28 EllipticSingularitiesSplitting.tex
Some changes to \S 1 and added remark about VZtilde mapping to KIm

@@
 This began over a decade ago with the pioneering work of Li, Vakil, and Zinger~\cite{redgone,VZ,LZ,lz2,zingerstvsred,zingred}, and was recently reinvigorated involving ideas from logarithmic geometry and singularity theory~\cite{BCM18,CM18,HL,RSPW,RSPW2,SMY1,VISC}.
-The result is a \textit{reduced} Gromov--Witten theory, which removes certain degenerate contributions from the ordinary theory.
+The result is a \textbf{reduced} Gromov--Witten theory, which removes certain degenerate contributions from the ordinary theory.
 While the Atiyah--Bott localization for the reduced invariants was used to great effect by Zinger in his proof of the BCOV conjectures, two major components of the standard theory -- relative invariants and the degeneration formula -- have not been developed in this setting.
@@
 \end{definition}
-
-\tred{In essence, this is a family of curves where every vertex of the tropical curve $\plC$ is either inside or outside the circle of radius $\delta$ around the core genus one subcurve.}
+In essence, this says that the curve $\sqC$ is such that all vertices are either inside, outside, or on the circle of radius $\delta$, and that the collection of vertices inside the circle is totally ordered.
 
@@
 
+%%%%%
+\begin{comment}
 There is a representable finite logarithmic morphism to the Kontsevich space, forgetting the logarithmic structure on the target:
@@
 $$
-We require the logarithmic structure of the source curve to be aligned in a compatible way with the map to $\PP^N$.
-We thus get the moduli space of \textbf{centrally aligned logarithmic maps to $(\mathbb P^n,H)$}, which we denote $\widetilde{\VZ}_{1,\alpha}(\mathbb P^N|H,d)$.
-It is a logarithmic modification of $\overline{\mathcal M}^{\mathrm{log}}_{1,\alpha}(\mathbb P^N|H,d)$, and it maps down to $\widetilde\VZ_{1,n}(\PP^N,d)$ under forgetting the logarithmic structure of the target.
+\end{comment}
+%%%%%%%%%%%%%%
+As in the absolute setting, we consider the space of logarithmic morphisms from the universal curve $\mathcal{C} \to \mathfrak{M}_{1,n}^{\mathrm{cen}}$ to the logarithmic scheme $(\PP^N,H)$.
+We impose a compatibility condition, which says that the radius must pass through a vertex of positive degree in $\PP^N$ and contain only vertices of degree zero in its strict interior.
+In this way we obtain a logarithmic modification
+\begin{equation*} \widetilde\VZ_{1,\alpha}(\PP^N|H,d) \to \ol\Mcal^{\mathrm{log}}_{1,\alpha}(\PP^N|H,d)\end{equation*}
+which we refer to as the \textbf{moduli space of centrally aligned maps to $(\PP^N,H)$}.
+It is a logarithmic modification of $\overline{\mathcal M}^{\mathrm{log}}_{1,\alpha}(\mathbb P^N|H,d)$.
+We note that by definition this space maps down to $\widetilde\VZ_{1,n}(\PP^N,d)$, by forgetting the logarithmic structure of the target.
 
@@
 In order make the obstruction theory more geometric, we expand the target.
-To elucidate the connection with the static target, consider a logarithmic stable map $[C\to (\mathbb P|H)]$ over $\mathrm{Spec} \ (\mathbb N\to \mathbb C)$.
+To elucidate the connection with the static target, consider a logarithmic stable map $[C\to (\mathbb P^N,H)]$ over $\mathrm{Spec} \ (\mathbb N\to \mathbb C)$.
 At the level of tropicalizations, there is a map of fans
@@
 Here the latter is the $s$-times iterated deformation to the normal cone of $H$ in $\mathbb P^N$.
-The components of the target are in bijection with the vertices in $\widetilde{\mathbb R}_{\geq 0}$.
+The irreducible components of the target are in bijection with the vertices in $\widetilde{\mathbb R}_{\geq 0}$.
 The curve is modified by adding rational components corresponding to the newly introduced vertices.
@@
 This process is outlined in complete generality in~\cite[\S~2]{R19}.
+
+Since we will work mostly with expansions, we will use the notation
+\begin{equation*} \ol\Mcal_{1,\alpha}(\PP^N|H,d) \end{equation*}
+for Kim's space of logarithmic stable maps, with the understanding that this may just as easily be viewed as a logarithmic modification of the Abramovich--Chen--Gross--Siebert space.
 
@@
 The map $[C\to \mathbb P^N[s]\to \mathbb P^N]$ \textbf{factorises completely} if
-\begin{itemize}
+\begin{enumerate}
 \item the map $C\to \mathbb P^N[s]$ factors through $\overline C_F$ such that at least one branch of $\overline C_F$ has positive degree in the fibre direction; 
 \item the collapsed map to $\mathbb P^N$ factorises through $\overline C_B$ such that at least one branch of $\overline C_B$ has positive degree.
-\end{itemize}
+\end{enumerate}
 \end{definition}
@@
 To prove this, it is convenient to work with the logarithmic multiplicative group and its torsors.
-Recall that the \textit{logarithmic multiplicative group} $\mathbb G_{\mathrm{log}}$ is the functor on logarithmic schemes whose value on a logarithmic scheme $S$ is the group of global sections $H^0(S,M_S^{\mathrm{gp}})$; it is a proper group functor, and it contains $\Gm$ as a subfunctor.
+Recall that the \textbf{logarithmic multiplicative group} $\mathbb G_{\mathrm{log}}$ is the functor on logarithmic schemes whose value on a logarithmic scheme $S$ is the group of global sections $H^0(S,M_S^{\mathrm{gp}})$; it is a proper group functor, and it contains $\Gm$ as a subfunctor.
 This functor is representable only after a logarithmically \'etale cover.
@@
 After this procedure, the images of vertices of $\plC$ which lie in $\RR_{>0}$ are totally ordered, in a manner extending the partial order obtained from the map to $\mathbb R_{\geq 0}$.
-The combinatorial types of such \textbf{image-ordered} maps produce the cones of a subdivision of $\Sigma^{\mathrm{log}}$ which we denote $\Sigma^{\mathrm{Kim}}$.\\
+The combinatorial types of such \textbf{image-ordered} maps produce the cones of a subdivision of $\Sigma^{\mathrm{log}}$ which we denote $\Sigma^{\mathrm{Kim}}$.
+As the notation suggests, $\Sigma^{\Kim}$ is the tropicalization of Kim's moduli space of logarithmic maps to $(\PP^N,H)$.\\
 
@@
 \end{proof}
+
+\begin{remark} An important observation is that the subdivison $\Sigma_{1,\alpha}(\PP^N|H,d)$ of $\Sigma^{\operatorname{log}}$ is a further refinement of the subdivision $\Sigma^{\Kim}$ of $\Sigma^{\operatorname{log}}$.
+Thus we have a sequence of logarithmic modifications:
+\begin{equation*} \widetilde\VZ_{1,\alpha}(\PP^N|H,d) \to \ol\Mcal_{1,\alpha}(\PP^N|H,d) \to \ol\Mcal^{\operatorname{log}}_{1,\alpha}(\PP^N|H,d).\end{equation*}
+Consequently, we may view the moduli space of centrally aligned maps as a moduli space of maps to the expanded target. This point of view will be useful in what follows.\end{remark}
 
@@
 
-\subsubsection{Possible combinatorial types} A boundary divisor $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ is said to have \textit{type $\dag$} if the core is assigned degree zero by the combinatorial type.
+\subsubsection{Possible combinatorial types} A boundary divisor $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ is said to have \textbf{type $\dag$} if the core is assigned degree zero by the combinatorial type.
 Divisors of this type occur as principal components in compactified torus bundles over strata in the space of relative maps.

### 2019-06-28 EllipticSingularitiesSplitting.tex
did nicer structure for section 3

@@
 The composition $f \circ x_k \colon \Sigma^{\log} \to \RR_{\geq 0}$ defines a piecewise-linear function on $\Sigma^{\log}$ whose preimage over the open cone $\RR_{>0}$ consists of those tropical maps where $x_k$ belongs to an internal component.
-This produces a section of the ghost sheaf on $\MLog_{1,\alpha}(\PP^N|H,d)$, which in the usual way induces a line bundle and section $(\Lcal_k,s_k)$ on the moduli space, and the tropical description above shows that the zero locus of $s_k$ is (set-theoretically) the locus where $x_k$ belongs to an internal component.
+This produces a section of the ghost sheaf on $\MLog_{1,\alpha}(\PP^N|H,d)$, which in the usual way induces a line bundle and section $(\Lcal_k,s_k)$ on the moduli space, and the tropical description above shows that the zero locus of $s_k$ is (set-theoretically) the locus where $x_k$ belongs to an internal component.\medskip
 
 We now calculate $\cchern_1(\Lcal_k)$. 
+\begin{thm} $\cchern_1(\Lcal_k) = \alpha_k \psi_k + \ev_k^\st H.$\end{thm}
+\begin{proof}
 Choose a family of logarithmic stable maps over $S$ and let $\mu \in \Gamma(S,\ol{M}_S)$ be the global section of the ghost sheaf constructed in the previous paragraph.
@@
 \begin{equation*} \Lcal_k = x_k^\st\pi^\st \Lcal_k = x_k^\st \OO_{C_k}(-\alpha_k x_k) \otimes x_k^\st f^\st\OO(H) = x_k^\st \OO_{C_k}(-\alpha_k x_k) \otimes \ev_k^\st \OO(H) \end{equation*}
-and taking Chern classes gives:
+and taking Chern classes gives
 \begin{equation*} \cchern_1(\Lcal_k) = \alpha_k \psi_k + \ev_k^\st H.\end{equation*}
-This gives the construction of $(\Lcal_k,s_k)$ on $\MLog_{1,\alpha}(\PP^N|H,d)$; the construction on $\VZ_{1,\alpha}(\PP^N|H,d)$ is given by pull-back.
+as required.\end{proof}
+This gives the construction of $(\Lcal_k,s_k)$ and the calculation of $\cchern_1(\Lcal_k)$ on $\MLog_{1,\alpha}(\PP^N|H,d)$; the construction on $\VZ_{1,\alpha}(\PP^N|H,d)$ is given by pull-back.
 The relevant piecewise-linear function is the composition:

### 2019-06-28 EllipticSingularitiesSplitting.tex
some changes to section 1 to make use of expansions clearer

@@
 %%%%%%%%%%%%%%
+
+\begin{comment}
 As in the absolute setting, we consider the space of logarithmic morphisms from the universal curve $\mathcal{C} \to \mathfrak{M}_{1,n}^{\mathrm{cen}}$ to the logarithmic scheme $(\PP^N,H)$.
@@
 We note that by definition this space maps down to $\widetilde\VZ_{1,n}(\PP^N,d)$, by forgetting the logarithmic structure of the target.
-
-\subsection{Relative geometry: expansions} Our next task is to pick out a non-singular principal component in $\widetilde{\VZ}_{1,\alpha}(\mathbb P^N|H,d)$.
+\end{comment}
+
+\subsection{Relative geometry: expansions}
+
+\begin{comment}Our next task is to pick out a non-singular principal component in $\widetilde{\VZ}_{1,\alpha}(\mathbb P^N|H,d)$.
 The principal component of this space, consisting of the closure of the space of maps from nonsingular curves, maps into the principal component of $\widetilde\VZ_{1,n}(\PP^N,d)$.
@@
 An additional condition is required to isolate the principal component of the space of logarithmic maps.
+\end{comment}
 
@@
 Since we will work mostly with expansions, we will use the notation
-\begin{equation*} \ol\Mcal_{1,\alpha}(\PP^N|H,d) \end{equation*}
+$\ol\Mcal_{1,\alpha}(\PP^N|H,d)$
 for Kim's space of logarithmic stable maps, with the understanding that this may just as easily be viewed as a logarithmic modification of the Abramovich--Chen--Gross--Siebert space.
 
-\subsection{Relative geometry: factorisation}\label{subsection factorisation} Let $[C\to \mathbb P^N[s]\to \mathbb P^N]$ be a logarithmic map from a centrally aligned curve to an expansion.
+\subsection{Relative geometry: alignment} As in the absolute setting, we consider the space of logarithmic morphisms from the universal curve $\mathcal{C} \to \mathfrak{M}_{1,n}^{\mathrm{cen}}$ to the logarithmic scheme $(\PP^N,H)$.
+Also as in the absolute case, we impose a compatibility condition, which says that the radius must pass through a vertex of positive degree in $\PP^N$ and contain only vertices of degree zero in its strict interior.
+In this way we obtain a logarithmic modification of the Abramovich--Chen--Gross--Siebert space.
+If we further perform the subdivisions of target and source outlined in the previous section, we obtain a logarithmic modification of Kim's space:
+\begin{equation*} \widetilde\VZ_{1,\alpha}(\PP^N|H,d) \to \ol\Mcal_{1,\alpha}(\PP^N|H,d)\end{equation*}
+which we refer to as the \textbf{moduli space of centrally aligned maps} to $(\PP^N,H)$.
+It parametrises transverse logarithmic maps to the expanded target with an alignment which is compatible with the collapsed map $C \to \PP^N$.
+Because of this compatibility condition, there is a morphism
+\begin{equation*} \widetilde\VZ_{1,\alpha}(\PP^N|H,d) \to \widetilde\VZ_{1,n}(\PP^N,d)\end{equation*}
+obtained by forgetting the logarithmic structure on the target and collapsing the map.
+
+\subsection{Relative geometry: factorisation}\label{subsection factorisation} Let $[C\to \mathbb P^N[s]\to \mathbb P^N]$ be a centrally aligned logarithmic map.
 Recall that $\mathbb P^N[s]$ consists of a union of $\mathbb P^N$ with $s$ copies of the projective bundle $\mathbb{P} = \mathbb P(\mathcal O_H\oplus \mathcal O_H(1))$.
@@
 This coincides with the radius of the underlying map to $\mathbb P^N$.
-Of course, $\delta_F\leq \delta_B$, \tred{so $(C,\delta_F)$ is centrally aligned too}.
+Of course, $\delta_F\leq \delta_B$, so $(C,\delta_F)$ is centrally aligned also.
 
@@
 In particular, if $[C\to \mathbb P^N[s]\to \mathbb P^N]$ is a family of centrally aligned maps over $S$ that factorises completely, there is a forgetful moduli map $S\to \VZ_{1,n}(\mathbb P^N,d)$, to the principal component of the space of absolute maps.
-
-Let $\VZ_{1,\alpha}(\mathbb P^N|H,d)$ be the stack of maps from centrally aligned curves to expansions of $\mathbb P^N$ that factorise completely.
+Let
+\begin{equation*} \VZ_{1,\alpha}(\mathbb P^N|H,d) \subseteq \widetilde\VZ_{1,\alpha}(\PP^N|H,d) \end{equation*}
+be the stack of maps from centrally aligned curves to expansions of $\mathbb P^N$ that factorise completely.
 
@@
 
-\begin{remark} An important observation is that the subdivison $\Sigma_{1,\alpha}(\PP^N|H,d)$ of $\Sigma^{\operatorname{log}}$ is a further refinement of the subdivision $\Sigma^{\Kim}$ of $\Sigma^{\operatorname{log}}$.
-Thus we have a sequence of logarithmic modifications:
-\begin{equation*} \widetilde\VZ_{1,\alpha}(\PP^N|H,d) \to \ol\Mcal_{1,\alpha}(\PP^N|H,d) \to \ol\Mcal^{\operatorname{log}}_{1,\alpha}(\PP^N|H,d).\end{equation*}
-Consequently, we may view the moduli space of centrally aligned maps as a moduli space of maps to the expanded target. This point of view will be useful in what follows.\end{remark}
-
 \subsection{Indexing the strata} \label{subsection indexing strata} The dimension-$k$ cones in $\Sigma_{1,\alpha}(\PP^N|H,d)$ can be enumerated as follows.
-First, the cones in $\Sigma^{\operatorname{log}}$ are indexed by \textbf{combinatorial types} of tropical maps to $\RR_{\geq 0}$.
-Here a combinatorial type encodes all of the data of a tropical map, except for the edge lengths and precise vertex positions.
+First, the cones in $\Sigma=\Sigma^{\Kim}$ are indexed by \textbf{combinatorial types} of tropical maps to $\RR_{\geq 0}$.
+Here a combinatorial type encodes all of the data of a tropical map, except for the edge lengths.
 To be more precise, a combinatorial type $\Delta$ consists of:
 \begin{enumerate}
-\item a finite graph;
+\item a finite graph $\sqC$ and topological (not metric) subdivision $\widetilde\RR_{\geq 0}$ of $\RR_{\geq 0}$;
 \item genus, degree and marking assignments on the vertices;
-\item the data of which stratum of $\RR_{\geq 0}$ each vertex is mapped to;
+\item the data of which vertex of $\widetilde\RR_{\geq 0}$ each vertex of $\sqC$ is mapped to;
 \item integral slopes along the edges (both finite and infinite).
 \end{enumerate}
-The corresponding cone $\sigma \in \Sigma^{\operatorname{log}}$ is then given by the resulting moduli space of tropical maps, given by choices of edge lengths and vertex positions which produce a continuous tropical map.
-Given $\sigma\in \Sigma^{\operatorname{log}}$ we then produce all the cones in $\Sigma_{1,\alpha}(\PP^N|H,d)$ mapping to $\sigma$ by performing Steps 2--4 outlined above.
+The corresponding cone $\sigma \in \Sigma^{\operatorname{Kim}}$ is then given by the resulting moduli space of tropical maps, given by choices of edge lengths on source and target which produce a continuous tropical map.
+Given $\sigma\in \Sigma^{\operatorname{Kim}}$ we then produce all the cones in $\Sigma_{1,\alpha}(\PP^N|H,d)$ mapping to $\sigma$ by performing Steps 3--4 outlined above.
 This amounts to taking a particular subdivision of $\sigma$.
-Note that in this process, new cones are created which map into larger-dimensional cones of $\Sigma^{\operatorname{log}}$.
+Note that in this process, new cones are created which map into larger-dimensional cones of $\Sigma^{\operatorname{Kim}}$.
 The process for enumerating the codimension $k$ strata of $\VZ_{1,\alpha}(\PP^N|H,d)$ is therefore:
@@
 \item fix a combinatorial type $\Delta$;
-\item perform the subdvidision of the resulting cone $\sigma \in \Sigma^{\operatorname{log}}$;
+\item perform the subdvidision of the resulting cone $\sigma \in \Sigma^{\operatorname{Kim}}$;
 \item identify the dimension $k$ cones of that subdivision.

### 2019-06-28 EllipticSingularitiesSplitting.tex
Minor changes/improvements

@@
 We construct and study the reduced, relative, genus one Gromov--Witten theory of very ample pairs.
-These invariants form the principal part contribution to relative Gromov--Witten theory in genus one and are relative versions of Zinger's reduced Gromov--Witten invariants.
-The relative and absolute theories are related by degeneration of the tangency conditions, and the resulting formulas generalize a well-known recursive calculation scheme put forward by Gathmann in genus zero.
-{The geometric input is a desingularization of the principal component of the moduli space of genus one logarithmic stable maps to a very ample pair, using the geometry of elliptic singularities.
-Our study passes through general techniques for calculating integrals on logarithmic blowups of moduli spaces of stable maps, which may be of independent interest.}
+These invariants form the principal component contribution to relative Gromov--Witten theory in genus one and are relative versions of Zinger's reduced Gromov--Witten invariants.
+We relate the relative and absolute theories by degeneration of the tangency conditions, and the resulting formulas generalise a well-known recursive calculation scheme put forward by Gathmann in genus zero.
+The geometric input is a desingularisation of the principal component of the moduli space of genus one logarithmic stable maps to a very ample pair, using the geometry of elliptic singularities.
+Our study passes through general techniques for calculating integrals on logarithmic blowups of moduli spaces of stable maps, which may be of independent interest.
 \end{abstract}
@@
 The conceptual features of one space are often computational bugs, and vice versa, and we believe that the techniques developed in the genus one case here will be used repeatedly in logarithmic Gromov--Witten theory calculations.
-In particular, we frequently use Kato's perspective on logarithmic blowups as subfunctors that was applied in~\cite{RSPW,RSPW2}.
-
-\subsection*{Acknowledgements} We have benefited from fruitful conversations with friends and colleagues, including Francesca Carocci, Cristina Manolache, Davesh Maulik, Jonathan Wise, and \tred{[other people]}.
+In particular, we frequently use Kato's perspective on logarithmic blowups as subfunctors \cite{KatoExactness} that was applied in~\cite{RSPW,RSPW2}.
+
+\subsection*{Acknowledgements} We have benefited from fruitful conversations with friends and colleagues, including Pierrick Bousseau, Francesca Carocci, Cristina Manolache, Davesh Maulik and Jonathan Wise.
 Important aspects of this work were completed while L.B.
@@
 L.B.
-would like to thank Imperial College London, the LSGNT, the Royal Society, 3CinG, the MSRI program ''Enumerative Geometry beyond Numbers``, and MPIM-Bonn for support.
+and N.N.
+would like to thank Imperial College London, the University of Glasgow, the LSGNT, the Royal Society and 3CinG for support.
+L.B.
+would in addition like to thank the MSRI program ''Enumerative Geometry Beyond Numbers'' and MPIM-Bonn for support.
 
@@
 Two maps are considered equivalent if they differ by $\Gm$-scaling the target at higher level.
+This is the logarithmic enhancement of the classical theory of relative stable maps, due to Li \cite{Li1,Li2}.
 
@@
 
-This subdivision is best described using the formalism of extended tropicalizations \cite{}.
+This subdivision is best described using the formalism of extended tropicalizations \cite{Thuillier,ACP}.
 The subdividing cones are obtained from cones in the star of $\tau$ under the limit $e_1=\cdots=e_r=\infty$.

### 2019-06-28 EllipticSingularitiesSplitting.tex
implemented Dhruv's changes to introduction

@@
 While the higher genus situation is much more difficult, in the last several years, substantial theory has been developed towards a conceptual understanding of the genus one case.
-This began over a decade ago with the pioneering work of Li, Vakil, and Zinger~\cite{redgone,VZ,LZ,lz2,zingerstvsred,zingred}, and was recently reinvigorated involving ideas from logarithmic geometry and singularity theory~\cite{BCM18,CM18,HL,RSPW,RSPW2,SMY1,VISC}.
+This began over a decade ago with the pioneering work of Li, Vakil, and Zinger~\cite{redgone,VZ,LZ,lz2,zingerstvsred,zingred}, and was recently reinvigorated involving ideas from singularity theory~\cite{BCM18,CM18,HL,SMY1,VISC} and logarithmic geometry~\cite{RSPW,RSPW2}.
 The result is a \textbf{reduced} Gromov--Witten theory, which removes certain degenerate contributions from the ordinary theory.
@@
 
-\subsection{Results} Our first contribution is a definition and construction of relative reduced Gromov--Witten theory of projective space relative to a hyperplane.
+\subsection{Results} Our first contribution is a definition and construction of reduced Gromov--Witten theory of projective space relative to a hyperplane.
 The geometric content is the following, see \S \ref{section construction} for a precise formulation.
@@
 \begin{customthm}{A}\label{thm: desingularization}
-There exists a logarithmically smooth and proper Deligne--Mumford stack $\VZ_{1,\alpha}^\circ(\mathbb P^N|H,d)$ having expected dimension, and containing $\mathcal M_{1,\alpha}^\circ(\mathbb P^N|H,d)$  as a dense open subset.
+There exists a logarithmically smooth and proper Deligne--Mumford stack $\VZ_{1,\alpha}(\mathbb P^N|H,d)$ having expected dimension, and containing $\mathcal M_{1,\alpha}^\circ(\mathbb P^N|H,d)$  as a dense open subset.
 A point in this moduli space parameterizes maps
@@
 \item the reduced genus one relative Gromov--Witten invariants of $(X,Y)$; 
-\item the (restricted) reduced genus one rubber invariants of $\mathbb{P}=\PP_Y(\operatorname{N}_{Y|X} \oplus \OO_Y)$
+\item the (restrirccted) reduced genus one rubber invariants of $\mathbb{P}=\PP_Y(\operatorname{N}_{Y|X} \oplus \OO_Y)$
 \end{enumerate}
@@
 
-We pursue a strategy laid out by Vakil and Gathmann, building on work of Caporaso and Harris~\cite{CH98,Ga,Vre}.
-The first step is to express the locus of maps where the contact order degenerates in terms of Chern classes of natural vector bundles.
+This reconstruction result is most directly a generalization of Gathmann's calculation~\cite{Ga}.
+A higher genus reconstruction result for the ordinary theory is proved in a paper of Maulik and Pandharipande~\cite{MaulikPandharipande}, but is of a fundamentally different approach than ours.
+In particular, localization is never used in the analysis here, nor in the work of Gathmann.
+
+We pursue a strategy laid out by Vakil, building on work of Caporaso and Harris~\cite{CH98,Vre}.
+The first step is to express the locus of maps where the contact order degenerates in terms of Chern classes of tautological vector bundles.
 The second step is to describe that locus in terms of fibre products of moduli spaces with smaller invariants.
+
 Novelties are introduced in both steps.
-We achieve the first step using techniques that are entirely within tropical and logarithmic geometry, drastically simplifying Gathmann's calculation.
+In the first, we describe the locus of degenerate maps as the zero locus of a logarithmic line bundle, arising from a piecewise linear function with a simple moduli theoretic description.
+The use of tropical techniques substantially simplifies Gathmann's calculations
+
+We achieve the first step using techniques that are entirely within tropical and logarithmic geometry, substantially simplifying Gathmann's calculation.
 For the second step, we contend with the interaction of the relative splitting formula and the geometry of elliptic singularities, which is entirely new (\S \ref{subsection C0 splitting}).
-We express the factorisation property in terms of tautological classes and combinatorial manipulations, leading to Theorem~\ref{thm: recursion}.
-
-\subsection{Broader contributions} Beyond genus one, we pass through a number of seemingly useful general techniques.
+We express the factorisation condition -- central to the constructions in~\cite{RSPW,RSPW2} -- in terms of tautological classes, leading to Theorem~\ref{thm: recursion}.
+
+\subsection{Broader contributions} Beyond genus one, we pass through some useful general techniques.
 First, we explain how to describe degenerate moduli spaces as fibre products.
-This is substantially more delicate than the standard situation because of the need to work with elliptic singularities and aligned logarithmic structures.
-This interaction of the degeneration formula with the geometry of curve singularities is a new phenomenon.
-The results of~\cite{RSPW} suggest the existence of a reduced higher genus Gromov--Witten theory formed by replacing contracted elliptic components with singularities\footnote{We have been informed by Jonathan Wise that his Ph.D.
+This is substantially more delicate than the standard situation for two reasons.
+On the one hand, we need to study the interaction of the relative geometry with elliptic singularities, which involves a study of the factorization condition in terms of tautological vector bundles.
+On the other hand, the degenerate strata of moduli spaces are not simply fiber products of spaces with smaller numerical invariants, but compactified torus bundles over these strata, due to the introduction of logarithmic blowups.
+This geometry is present throughout logarithmic enumerative geometry, particularly in the degeneration formula, and we provide a first systematic procedure that explains how to use tropical geometry to calculate with these torus bundles~\cite{R19}.
+In addition, the results of~\cite{RSPW} suggest the existence of a reduced higher genus Gromov--Witten theory formed by replacing contracted elliptic components with singularities\footnote{We have been informed by Jonathan Wise that his Ph.D.
 candidate Sebastian Bozlee has constructed these higher genus reduced Gromov--Witten invariants.
@@
 We realize the locus as the vanishing locus of a section of a line bundle that comes from tropical geometry — from a piecewise linear function on the fan.
-The systematic understanding of logarithmic line bundles arising in this fashion is likely to play an important r\^ole in logarithmic enumerative geometry.
-
-\tred{We rephrase Gathmann's idea of increasing the tangency requirement within the framework of logarithmic stable maps (where maximal tangency is always assumed) by introducing \emph{fictitious markings}, and identifying the space of maps with higher contact order with a boundary stratum inside that of lower contact order and more (fictitious) markings.}
+The systematic understanding of logarithmic line bundles arising in this fashion is likely to play an important role in logarithmic enumerative geometry.
+
+We rephrase Gathmann's idea of increasing the tangency requirement within the framework of logarithmic stable maps (where maximal tangency is always assumed) by introducing \emph{fictitious markings}, and identifying the space of maps with higher contact order with a boundary stratum inside that of lower contact order and more (fictitious) markings.
 
@@
 
-Finally, we note that our results require us to encounter several variants of the space of relative/logarithmic stable maps, with both fixed and expanded target.
+Finally, we note that our methods require us to encounter several variants of the space of relative/logarithmic stable maps, with both fixed and expanded target.
 The conceptual features of one space are often computational bugs, and vice versa, and we believe that the techniques developed in the genus one case here will be used repeatedly in logarithmic Gromov--Witten theory calculations.
-In particular, we frequently use Kato's perspective on logarithmic blowups as subfunctors \cite{KatoExactness} that was applied in~\cite{RSPW,RSPW2}.
-
-\subsection*{Acknowledgements} We have benefited from fruitful conversations with friends and colleagues, including Pierrick Bousseau, Francesca Carocci, Cristina Manolache, Davesh Maulik and Jonathan Wise.
+In particular, we frequently use Kato's perspective on logarithmic blowups as subfunctors that was applied in~\cite{RSPW,RSPW2}.
+
+\subsection*{Acknowledgements} We have benefited from fruitful conversations with friends and colleagues, including Pierrick Bousseau, Francesca Carocci, Cristina Manolache, Davesh Maulik, Keli Santos-Parker, and Jonathan Wise.
 Important aspects of this work were completed while L.B.
@@
 and N.N.
-would like to thank Imperial College London, the University of Glasgow, the LSGNT, the Royal Society and 3CinG for support.
+would like to thank Imperial College London, the LSGNT, the Royal Society, 3CinG and the University of Glasgow for support.
 L.B.
-would in addition like to thank the MSRI program ''Enumerative Geometry Beyond Numbers'' and MPIM-Bonn for support.
-
-\newpage
+would in addition like to thank the MSRI program ''Enumerative Geometry beyond Numbers'', and MPIM-Bonn.
 
@@
 \noindent
-\textbf{Step 3}.\marginpar{doesn' picking $\delta$ itself imply a subdivision?} Given a tropical map $F: \plC\to \mathbb R_{\geq 0}$ parameterized by $\Sigma^{\mathrm{Kim}}$, there is a largest radius $\delta$ (possibly equal to $0$) such that every vertex strictly contained in the circle of radius $\delta$ around the core has degree-marking $d=0$.
+\textbf{Step 3.} Given a tropical map $F: \plC\to \mathbb R_{\geq 0}$ parameterized by $\Sigma^{\mathrm{Kim}}$, there is a largest radius $\delta$ (possibly equal to $0$) such that every vertex strictly contained in the circle of radius $\delta$ around the core has degree-marking $d=0$.
 Let $

### 2019-06-28 EllipticSingularitiesSplitting.tex
minor changes

@@
 A higher genus reconstruction result for the ordinary theory is proved in a paper of Maulik and Pandharipande~\cite{MaulikPandharipande}, but is of a fundamentally different approach than ours.
-In particular, localization is never used in the analysis here, nor in the work of Gathmann.
+In particular, localisation is never used in the analysis here, nor in the work of Gathmann.
 
@@
 
-We achieve the first step using techniques that are entirely within tropical and logarithmic geometry, substantially simplifying Gathmann's calculation.
 For the second step, we contend with the interaction of the relative splitting formula and the geometry of elliptic singularities, which is entirely new (\S \ref{subsection C0 splitting}).
@@
 This is substantially more delicate than the standard situation for two reasons.
-On the one hand, we need to study the interaction of the relative geometry with elliptic singularities, which involves a study of the factorization condition in terms of tautological vector bundles.
+On the one hand, we need to study the interaction of the relative geometry with elliptic singularities, which involves a study of the factorisation condition in terms of tautological vector bundles.
 On the other hand, the degenerate strata of moduli spaces are not simply fiber products of spaces with smaller numerical invariants, but compactified torus bundles over these strata, due to the introduction of logarithmic blowups.
@@
 
-We have produced a factorization
+We have produced a factorisation
 \begin{equation*}\widetilde\Dcal\to\widetilde \Ecal\to\Ecal,

### 2019-06-28 EllipticSingularitiesSplitting.tex
spell check

--- 2019-06-28 EllipticSingularitiesSplitting.tex
@@
 $$
-which remembers only the stabilization of the collapsed map.
+which remembers only the stabilisation of the collapsed map.
 The map is certainly centrally aligned, and we have already argued above that it satisfies the factorisation property for $\mathbb P^N$ after composition.
@@
 \ecd
-factorizing completely. Let $f_B$ and $f$ be the maps from $C$ to the base and total space respectively. Examining the morphism $\nu$, we see that there is a map
+factorising completely. Let $f_B$ and $f$ be the maps from $C$ to the base and total space respectively. Examining the morphism $\nu$, we see that there is a map
 \[
@@
 
-\noindent The logarithmic smoothness established in Theorem~\ref{thm: log-smoothness} implies that $\VZ_{1,\alpha}(\mathbb P^N|H,d)$ is an orbifold toroidal embeddeding.
+\noindent The logarithmic smoothness established in Theorem~\ref{thm: log-smoothness} implies that $\VZ_{1,\alpha}(\mathbb P^N|H,d)$ is an orbifold toroidal embedding.
 Consequently, the irreducible components of its boundary and their intersections form a stratification of the space.
@@
 \begin{enumerate}
-    \item no open neighborhood of $\plC_0$ is contracted to a point in $\mathbb R_{>0}$, or
-    \item if an open neighborhood of $\plC_0$ is contracted and $t_1,\ldots,t_k$ are the flags whose vertex is mapped to $F(\plC_0)$, but along which $F$ has nonzero slope; then, the minimum of the distances from $\plC_0$ to $t_i$ occurs for at least two indices $i$.
+    \item no open neighbourhood of $\plC_0$ is contracted to a point in $\mathbb R_{>0}$, or
+    \item if an open neighbourhood of $\plC_0$ is contracted and $t_1,\ldots,t_k$ are the flags whose vertex is mapped to $F(\plC_0)$, but along which $F$ has nonzero slope; then, the minimum of the distances from $\plC_0$ to $t_i$ occurs for at least two indices $i$.
 \end{enumerate}
@@
 Let $p$ be the point to which the genus one subcurve is contracted.
-Passing to an open neighborhood of $p$, the map to the bundle is given by a rational function $f$ on an open curve $C^\circ$, determined by the the subgraph formed by $\plC_0$ and the flags $t_i$ described in the definition above.
+Passing to an open neighbourhood of $p$, the map to the bundle is given by a rational function $f$ on an open curve $C^\circ$, determined by the the subgraph formed by $\plC_0$ and the flags $t_i$ described in the definition above.
 To describe the tropical map to $\mathbb R_{>0}$, we observe that $\plC_0$ is contracted to a fixed point $q\in\mathbb R_{>0}$.
@@
 \noindent
-\textbf{Step 3.} Given a tropical map $F: \plC\to \mathbb R_{\geq 0}$ parameterized by $\Sigma^{\mathrm{Kim}}$, there is a largest radius $\delta$ (possibly equal to $0$) such that every vertex strictly contained in the circle of radius $\delta$ around the core has degree-marking $d=0$.
+\textbf{Step 3.} Given a tropical map $F: \plC\to \mathbb R_{\geq 0}$ parameterised by $\Sigma^{\mathrm{Kim}}$, there is a largest radius $\delta$ (possibly equal to $0$) such that every vertex strictly contained in the circle of radius $\delta$ around the core has degree-marking $d=0$.
 Let $
@@
 \VZ_{1,\alpha}(\mathbb P^N|H,d)$.
-Specifically, the fact that the cone complex $\Sigma^{\mathrm{cen}}$ is the cone complex attached to the logarithmic stack $\widetilde{\VZ}_{1,\alpha}(\mathbb P^N|H,d)$ of centrally aligned maps to expansions, follows immediately from its description as a subcategory of the fibreed category (over logarithmic schemes) of $\mathcal M^{\mathrm{log}}_{1,\alpha}(\mathbb P^N|H,d)$.
+Specifically, the fact that the cone complex $\Sigma^{\mathrm{cen}}$ is the cone complex attached to the logarithmic stack $\widetilde{\VZ}_{1,\alpha}(\mathbb P^N|H,d)$ of centrally aligned maps to expansions, follows immediately from its description as a subcategory of the fibred category (over logarithmic schemes) of $\mathcal M^{\mathrm{log}}_{1,\alpha}(\mathbb P^N|H,d)$.
 To complete the result, we note that $
@@
 \item fix a combinatorial type $\Delta$;
-\item perform the subdvidision of the resulting cone $\sigma \in \Sigma^{\operatorname{Kim}}$;
+\item perform the subdivision of the resulting cone $\sigma \in \Sigma^{\operatorname{Kim}}$;
 \item identify the dimension $k$ cones of that subdivision.
@@
 By definition $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ is contained in the  complement of this locus and can be expressed as a union of strata of positive codimension.
-Since $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ has codmension $1$, it must therefore be equal to a union of logarithmic divisors.\end{proof}
+Since $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ has codimension $1$, it must therefore be equal to a union of logarithmic divisors.\end{proof}
 
@@
 This process contains some redundancies: upon choosing a ray in the tropical moduli space, some of the edge lengths or vertex positions may get set to $0$.
-This induces a generization of the intial combinatorial type $\Delta$, given by contracting the corresponding edges of the dual graph and moving the corresponding vertices from $\RR_{>0}$ to $0$.
+This induces a generisation of the initial combinatorial type $\Delta$, given by contracting the corresponding edges of the dual graph and moving the corresponding vertices from $\RR_{>0}$ to $0$.
 When we speak of the combinatorial type of a stratum in $\VZ_{1,\alpha}(\PP^N|H,d)$, we will always mean this generisation.
-This is independent of the choice of $\Delta$, and in fact we can and will always choose $\Delta$ to coincide with the generization.
+This is independent of the choice of $\Delta$, and in fact we can and will always choose $\Delta$ to coincide with the generisation.
 
@@
 
-The map $\Dcal\to\Ecal$ is an isomorphism away from the exceptional centers, and the latter is contained in the locus where the core is contracted.
+The map $\Dcal\to\Ecal$ is an isomorphism away from the exceptional centres, and the latter is contained in the locus where the core is contracted.
 Given an element of $\Dcal$ we can split it along the nodes $q_1,\ldots,q_r$.
@@
 
-We summarize that the contribution of each term $\lambda_\Dcal [\Dcal]$ is given by integrating over the appropriate fibre product and then multiplying the result by $\lambda_\Dcal \cdot \deg\rho = \prod_{i=1}^r m_i$.
+We summarise that the contribution of each term $\lambda_\Dcal [\Dcal]$ is given by integrating over the appropriate fibre product and then multiplying the result by $\lambda_\Dcal \cdot \deg\rho = \prod_{i=1}^r m_i$.
 
@@
 This is implied by the fact that the cone $\tau$ corresponding to $\Dcal$ is a ray.
-If the vertex on the circle is strictly semistable -- so that in particular the collapsed map $f_B$ is constant along the corresponing component -- it can be seen that the factorisation condition is unaffected by $\Gm$-scaling the coordinate corresponding to that vertex in the moduli space of attaching data, so the map $\Dcal\to\Ecal$ has generic fibre of positive dimension and the contribution vanishes.
+If the vertex on the circle is strictly semistable -- so that in particular the collapsed map $f_B$ is constant along the corresponding component -- it can be seen that the factorisation condition is unaffected by $\Gm$-scaling the coordinate corresponding to that vertex in the moduli space of attaching data, so the map $\Dcal\to\Ecal$ has generic fibre of positive dimension and the contribution vanishes.
 
@@
 
-Finally, in case the maximal contact order is $m=1$, the image tangent vectors must be linearly dependent, in which case we can deduce as above that factorisation will be satisfied indepedently of the choice of alignment.
+Finally, in case the maximal contact order is $m=1$, the image tangent vectors must be linearly dependent, in which case we can deduce as above that factorisation will be satisfied independently of the choice of alignment.
 \end{proof}
@@
 The polyhedral criterion for equidimensionality is that every cone of the source maps surjectively onto a cone of the target.
-There is a universal logarithmic modification $\widetilde\Ecal \to \Ecal$ such that $\widetilde\Dcal \to \widetilde\Ecal$ is flat, constructed by taking the minimal subdivison of $\Ecal^{\operatorname{trop}}$ such that cones map surjectively to cones.
+There is a universal logarithmic modification $\widetilde\Ecal \to \Ecal$ such that $\widetilde\Dcal \to \widetilde\Ecal$ is flat, constructed by taking the minimal subdivision of $\Ecal^{\operatorname{trop}}$ such that cones map surjectively to cones.
 
@@
 Call these loci $\Xi_\Lambda$ for $\Lambda=(\Lambda_B,\Lambda_F)$ (compare with \cite[\S 3.2]{VZ} for an analogous phenomenon in the non-relative case); clearly, they may be in excess with respect to the expected codimension of $V(s)$, that is $N-1$.
-These loci are logarithmic substrata; therefore, there exists a logarithmic blow-up that principalizes them.
+These loci are logarithmic substrata; therefore, there exists a logarithmic blow-up that principalises them.
 We claim which $\widetilde\Dcal$ is (possibly a refinement of) such a blow-up.
@@
 First consider the type I loci.
-The genus one piece has strictly smaller degree (and hence is recursively known) exept in the following situation (with some stable distribution of the remaining markings):
+The genus one piece has strictly smaller degree (and hence is recursively known) except in the following situation (with some stable distribution of the remaining markings):
 \begin{center}
@@
 As in \S \ref{Section Gathmann line bundle}, we can give a logarithmic interpretation of this: it corresponds to the piecewise-linear function on the tropical moduli space which associates, to every rubber tropical map, the distance between $\varphi(\sqC_y)$ and the leftmost vertex of the tropical target, where $\sqC_y$ is the vertex of the source curve containing the flag corresponding to $y$.
-Using this tropical description, we may easily calculate the vanshing orders of $s_y^{\not\in\operatorname{bot}}$ along the various components of $\Dcal(y)$, and show that $\cchern_1(L_y^{\not\in\operatorname{bot}}) = \Psi_0 - \ev_y^\st Y$ (see also \cite{EKatzLB}, where similar results in the non-reduced setting are obtained, using different methods).
+Using this tropical description, we may easily calculate the vanishing orders of $s_y^{\not\in\operatorname{bot}}$ along the various components of $\Dcal(y)$, and show that $\cchern_1(L_y^{\not\in\operatorname{bot}}) = \Psi_0 - \ev_y^\st Y$ (see also \cite{EKatzLB}, where similar results in the non-reduced setting are obtained, using different methods).
 From this, we obtain a rubber recursion formula
@@
 But in this case the contribution is a rubber invariant where all of the insertions are pulled back via $\fgt_1^\st$, and hence we may apply the projection formula to identify this with an absolute invariant of $Y$ which is recursively known.
-We conclude that, up to recursively knwon terms, we may replace $\hat\psi_2$ by $\psi_2$ in the left-hand side of \eqref{step 4 recursion}.
+We conclude that, up to recursively known terms, we may replace $\hat\psi_2$ by $\psi_2$ in the left-hand side of \eqref{step 4 recursion}.
 If we now compare $\psi_2$ with $\fgt_1^\st \psi_2$ we see that the difference is given by the locus where $x_1$ and $x_2$ belong to a collapsed rational piece.

### 2019-06-28 EllipticSingularitiesSplitting.tex

@@
 This is substantially more delicate than the standard situation for two reasons.
-On the one hand, we need to study the interaction of the relative geometry with elliptic singularities, which involves a study of the factorization condition in terms of tautological vector bundles.
-On the other hand, the degenerate strata of moduli spaces are not simply fiber products of spaces with smaller numerical invariants, but compactified torus bundles over these strata, due to the introduction of logarithmic blowups.
+On the one hand, we need to study the interaction of the relative geometry with elliptic singularities, which involves a study of the factorisation condition in terms of tautological vector bundles.
+On the other hand, the degenerate strata of moduli spaces are not simply fibre products of spaces with smaller numerical invariants, but compactified torus bundles over these strata, due to the introduction of logarithmic blowups.
 This geometry is present throughout logarithmic enumerative geometry, particularly in the degeneration formula, and we provide a first systematic procedure that explains how to use tropical geometry to calculate with these torus bundles~\cite{R19}.

### 2019-06-28 EllipticSingularitiesSplitting.tex
minor changes

--- 2019-06-28 EllipticSingularitiesSplitting.tex
@@
 \usepackage[normalem]{ulem}
+
+%Maybe need this
+\usepackage[numbers]{natbib}
 
@@
 
-\title[Curve counting in genus one: elliptic singularities and relative geometry]{Curve counting in genus one: elliptic singularities {\it \&} relative geometry}
+\title[Curve counting in genus one: elliptic singularities {\it \&}  relative geometry]{Curve counting in genus one: elliptic singularities {\it \&} relative geometry}
 \author{Luca Battistella, Navid Nabijou and Dhruv Ranganathan}

### 2019-06-28 EllipticSingularitiesSplitting.tex
typos

@@
 While the higher genus situation is much more difficult, in the last several years, substantial theory has been developed towards a conceptual understanding of the genus one case.
-This began over a decade ago with the pioneering work of Li, Vakil, and Zinger~\cite{redgone,VZ,LZ,lz2,zingerstvsred,zingred}, and was recently reinvigorated involving ideas from singularity theory~\cite{BCM18,CM18,HL,SMY1,VISC} and logarithmic geometry~\cite{RSPW,RSPW2}.
+This began over a decade ago with the pioneering work of Li, Vakil, and Zinger~\cite{redgone,VZ,LZ,lz2,zingerstvsred,zingred}, and was recently reinvigorated using ideas from singularity theory~\cite{BCM18,CM18,HL,SMY1,VISC} and logarithmic geometry~\cite{RSPW,RSPW2}.
 The result is a \textbf{reduced} Gromov--Witten theory, which removes certain degenerate contributions from the ordinary theory.
-While the Atiyah--Bott localization for the reduced invariants was used to great effect by Zinger in his proof of the BCOV conjectures, two major components of the standard theory -- relative invariants and the degeneration formula -- have not been developed in this setting.
+While the Atiyah--Bott localisation for the reduced invariants was used to great effect by Zinger in his proof of the BCOV conjectures, two major components of the standard theory -- relative invariants and the degeneration formula -- have not been developed in this setting.
 Our results in this paper provide these as new {structural} tools in reduced genus one Gromov--Witten theory\footnote{Further motivation to consider the genus one case specifically comes simply from the fact that for Calabi--Yau geometries in dimension larger than $3$, Gromov--Witten theory vanishes in genera greater than one.}.
@@
 There exists a logarithmically smooth and proper Deligne--Mumford stack $\VZ_{1,\alpha}(\mathbb P^N|H,d)$ having expected dimension, and containing $\mathcal M_{1,\alpha}^\circ(\mathbb P^N|H,d)$  as a dense open subset.
-A point in this moduli space parameterizes maps
+A point in this moduli space parameterises maps
 \[
@@
 \item the reduced genus one relative Gromov--Witten invariants of $(X,Y)$; 
-\item the (restrirccted) reduced genus one rubber invariants of $\mathbb{P}=\PP_Y(\operatorname{N}_{Y|X} \oplus \OO_Y)$
+\item the (restricted) reduced genus one rubber invariants of $\mathbb{P}=\PP_Y(\operatorname{N}_{Y|X} \oplus \OO_Y)$
 \end{enumerate}
@@
 
-This reconstruction result is most directly a generalization of Gathmann's calculation~\cite{Ga}.
+This reconstruction result is most directly a generalisation of Gathmann's one~\cite{Ga}.
 A higher genus reconstruction result for the ordinary theory is proved in a paper of Maulik and Pandharipande~\cite{MaulikPandharipande}, but is of a fundamentally different approach than ours.
@@
 In the first, we describe the locus of degenerate maps as the zero locus of a logarithmic line bundle, arising from a piecewise linear function with a simple moduli theoretic description.
-The use of tropical techniques substantially simplifies Gathmann's calculations
+The use of tropical techniques substantially simplifies Gathmann's calculations.
 
@@
 This geometry is present throughout logarithmic enumerative geometry, particularly in the degeneration formula, and we provide a first systematic procedure that explains how to use tropical geometry to calculate with these torus bundles~\cite{R19}.
+
 In addition, the results of~\cite{RSPW} suggest the existence of a reduced higher genus Gromov--Witten theory formed by replacing contracted elliptic components with singularities\footnote{We have been informed by Jonathan Wise that his Ph.D.
@@
 Second, a key step in our recursion is a description of the locus of maps with higher than prescribed tangency, which was identified by Gathmann.
-We realize the locus as the vanishing locus of a section of a line bundle that comes from tropical geometry — from a piecewise linear function on the fan.
-The systematic understanding of logarithmic line bundles arising in this fashion is likely to play an important role in logarithmic enumerative geometry.
+We realise the locus as the vanishing locus of a section of a line bundle that comes from tropical geometry — from a piecewise linear function on the fan.
+The systematic understanding of logarithmic line bundles arising in this fashion is likely to play an important r\^ole in logarithmic enumerative geometry.
 
@@
 \begin{thm}[{\cite[Theorem B]{RSPW}}]
-The substack $\VZ_{1,n}(\mathbb P^N,d)$ of $\widetilde\VZ_{1,n}(\PP^N,d)$ parameterizing maps to $\mathbb P^N$ that satisfy the factorisation condition is smooth and proper of the expected dimension.
+The substack $\VZ_{1,n}(\mathbb P^N,d)$ of $\widetilde\VZ_{1,n}(\PP^N,d)$ parameterising maps to $\mathbb P^N$ that satisfy the factorisation condition is smooth and proper of the expected dimension.
 \end{thm}
@@
 
-We will first compactify the space described above, and then desingularize it.
+We will first compactify the space described above, and then desingularise it.
 For the compactification, we begin with Abramovich--Chen--Gross--Siebert's space of logarithmic stable maps, though we will typically work with various subcategories and variants~\cite{AbramovichChenLog,ChenLog,GrossSiebertLog,KimLog}.
@@
 The moduli space $\overline{\mathcal{M}}^{\operatorname{log}}_{1,\alpha}(\mathbb P^N|H,d)$ is a fibred category over logarithmic schemes, whose fibre over $(S,M_S)$ is the groupoid of logarithmically smooth curves of genus one over $(S,M_S)$ equipped with a logarithmic map to $\mathbb P^N$ of degree $d$ and contact order $\alpha$.
-It is a fundamental fact in the subject that this category is representable by a proper algebraic stack with logarithmic structure, parameterizing minimal objects~\cite{ChenLog}.
+It is a fundamental fact in the subject that this category is representable by a proper algebraic stack with logarithmic structure, parameterising minimal objects~\cite{ChenLog}.
 
@@
 \subsection{Relative geometry: alignment} As in the absolute setting, we consider the space of logarithmic morphisms from the universal curve $\mathcal{C} \to \mathfrak{M}_{1,n}^{\mathrm{cen}}$ to the logarithmic scheme $(\PP^N,H)$.
-Also as in the absolute case, we impose a compatibility condition, which says that the radius must pass through a vertex of positive degree in $\PP^N$ and contain only vertices of degree zero in its strict interior.
+As in the absolute case, we require the radius to pass through a vertex of positive degree in $\PP^N$ and contain only vertices of degree zero in its strict interior, but the alignment must also be compatible with the logarithmic map.
 In this way we obtain a logarithmic modification of the Abramovich--Chen--Gross--Siebert space.
@@
 which we refer to as the \textbf{moduli space of centrally aligned maps} to $(\PP^N,H)$.
-It parametrises transverse logarithmic maps to the expanded target with an alignment which is compatible with the collapsed map $C \to \PP^N$.
+This space parametrises transverse logarithmic maps to the expanded target with an alignment which is compatible with the map.
 Because of this compatibility condition, there is a morphism
@@
 \begin{equation*} \OO_{C_v} \left(\alpha_k x_k + \sum_e \mu_e x_e \right) \end{equation*}
-where the sum is over the edges $e$ adjacent to $v$ and distinct from $x_k$. Thus we see that:
+where the sum is over the edges $e$ adjacent to $v$ and distinct from $x_k$. Thus we have:
 \begin{equation*} \left( f^\st\OO(H) \otimes \pi^\st \Lcal_k^{-1} \right) \big|_{C_v} = \OO_{C_v} \left(\alpha_k x_k + \sum_e \mu_e x_e \right).\end{equation*}
@@
 \begin{equation*} \Sigma_{1,\alpha}(\PP^N|H,d) \to \Sigma^{\log} \to \RR_{\geq 0}.\end{equation*}
-Notice in particular that $\psi_k$ should be interpreted as a \textbf{collapsed psi class} on $\VZ_{1,\alpha}(\PP^N|H,d)$, i.e.
+In particular, $\psi_k$ should be interpreted as a \textbf{collapsed psi class} on $\VZ_{1,\alpha}(\PP^N|H,d)$, i.e.
 a psi class coming from the stabilised curve of the collapsed map.
@@
 \begin{equation}\label{equation recursion} (\alpha_k \psi_k + \ev_k^\st H) \cap [\VZ_{1,\alpha}(\PP^N|H,d)] = \sum_{\Dcal} \lambda_\Dcal [ \Dcal ].\end{equation}
-The sum is over irreducible components $\Dcal$ of the divisor $\Dcal_{1,\alpha,k}(\PP^N|H,d) \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$, and $\lambda_\Dcal$ is the vanishing order of $s_k$ along this component.
+The sum is over irreducible components of the divisor $\Dcal_{1,\alpha,k}(\PP^N|H,d) \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$, and $\lambda_\Dcal$ is the vanishing order of $s_k$ along this component.
 \end{thm}
@@
 
-In \S \ref{subsection indexing strata} we discussed a procedure for enumerating the logarithmic strata of $\VZ_{1,\alpha}(\PP^N|H,d)$, using the cones of the tropicalization $\Sigma_{1,\alpha}(\PP^N|H,d)$.
+In \S \ref{subsection indexing strata} we discussed how to enumerate the logarithmic strata of $\VZ_{1,\alpha}(\PP^N|H,d)$, using the cones of the tropicalization $\Sigma_{1,\alpha}(\PP^N|H,d)$.
 Every divisorial logarithmic stratum is obtained as follows:
@@
 
-We now investigate the three types I,II and III separately, giving a recursive description of the boundary divisor in each case.
+We now investigate the three types I, II and III separately, giving a recursive description of the boundary divisor in each case.
 For the remainder of this subsection, therefore, we fix a one-dimensional cone $\tau \in \Sigma_{1,\alpha}(\PP^N|H,d)$, let $\Dcal \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$ be the associated logarithmic divisor, and assume that $\Dcal$ is contained in $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ and is of type I, II or III.
@@
 \]
-The tropical curves on the left inherit a central alignment from the moduli space $\widetilde{\VZ}_{1,\alpha}(\PP^N|H,d)$, which orders a certain subset of the edge lengths.
+The tropical curves on the left inherit a central alignment from $\widetilde{\VZ}_{1,\alpha}(\PP^N|H,d)$, which orders a certain subset of the edge lengths.
 The polyhedral criterion for equidimensionality is that every cone of the source maps surjectively onto a cone of the target.
@@
 which gives a contribution of
-\begin{equation*} d\cdot \gamma \cap [\VZ_{1,(d,\underbrace{0,\ldots,0}_{n-1})}(X|Y,\beta)] \footnote{(Navid) Fix formatting}\end{equation*}
+\begin{equation*} d\cdot \gamma \cap [\VZ_{1,(d,\underbrace{0,\ldots,0}_{n-1})}(X|Y,\beta)]\end{equation*}
 to the right-hand side of \eqref{step 2 recursion}.
@@
 Recursing at $x_1$ we obtain:
-\begin{equation}\label{step 2 recursion 2} \left( (d-1)\psi_1 + \ev_1^\st Y \right)\cdot(-\tilde\gamma/d) \cap [\VZ_{1,(d-1,1,0,\ldots,0)}(X|Y,\beta)] = (-\tilde\gamma/d) \cap [\Dcal(1)].\end{equation}
+\begin{equation}\label{step 2 recursion 3} \left( (d-1)\psi_1 + \ev_1^\st Y \right)\cdot(-\tilde\gamma/d) \cap [\VZ_{1,(d-1,1,0,\ldots,0)}(X|Y,\beta)] = (-\tilde\gamma/d) \cap [\Dcal(1)].\end{equation}
 The difference between $\psi_1$ and $\fgt_y^\st \psi_1$ is given by the locus where $x_1$ and $y$ belong to a collapsed rational bubble:
@@
 \end{center}
-The contribution of this locus to the left-hand side of \eqref{step 2 recursion 2} is:
+The contribution of this locus to the left-hand side of \eqref{step 2 recursion 3} is:
 \begin{equation*} (d-1)\cdot(-\gamma/d) \cap [\VZ_{1,(d,\underbrace{0,\ldots,0}_{n-1})}(X|Y,\beta)].\end{equation*}

### 2019-06-28 EllipticSingularitiesSplitting.tex
arXiv v1

@@
 \author{Luca Battistella, Navid Nabijou and Dhruv Ranganathan}
-\date{\thismonthyear}
 
@@
 This reconstruction result is most directly a generalisation of Gathmann's one~\cite{Ga}.
-A higher genus reconstruction result for the ordinary theory is proved in a paper of Maulik and Pandharipande~\cite{MaulikPandharipande}, but is of a fundamentally different approach than ours.
+A higher genus reconstruction result for the ordinary theory is proved in a paper of Maulik and Pandharipande~\cite{MaulikPandharipande}, but follows a fundamentally different strategy to ours.
 In particular, localisation is never used in the analysis here, nor in the work of Gathmann.
@@
 \subsection*{Acknowledgements} We have benefited from fruitful conversations with friends and colleagues, including Pierrick Bousseau, Francesca Carocci, Cristina Manolache, Davesh Maulik, Keli Santos-Parker, and Jonathan Wise.
-Important aspects of this work were completed while L.B.
-and N.N.
-were visiting MIT in Spring 2018 and the University of Cambridge in Winter 2019, and we thank these institutions for their hospitality.
+The authors worked on this project during visits to MPIM-Bonn, MIT, University of Cambridge, and the University of Glasgow, and thank these institutions for ideal working conditions and support.
 L.B.
 and N.N.
-would like to thank Imperial College London, the LSGNT, the Royal Society, 3CinG and the University of Glasgow for support.
-L.B.
-would in addition like to thank the MSRI program ''Enumerative Geometry beyond Numbers'', and MPIM-Bonn.
+would in addition like to thank Imperial College London, the LSGNT, the Royal Society, 3CinG, and the MSRI program ''Enumerative Geometry beyond Numbers''.
 
@@
 \begin{lemma}\label{lem:generic_proj_bundle}
-Generically over $\Ecal$, $\widetilde \Dcal\to\widetilde\Ecal$ is the projectivisation of a tautological vector bundle.
+Generically over $\Ecal$, the morphism $\widetilde \Dcal\to\widetilde\Ecal$ is the projectivisation of a tautological vector bundle.
 \end{lemma}

### 2020-10-15 EllipticSingularitiesSplitting.tex
Dhruv's changes 14.10.2020

@@
 \usepackage[normalem]{ulem}
+%\usepackage{enumerate}
 
@@
 %This reverse-links the references in the paper. Useful for large papers.
-\usepackage[backref]{hyperref}
+\usepackage[backref=page]{hyperref}
 \hypersetup{
   colorlinks   = true,          %Colors links instead of ugly boxes
-  urlcolor     = violet,          %Color for external hyperlinks
-  linkcolor    = violet,          %Color of internal links
-  citecolor   = blue             %Color of citations
+  urlcolor     = red,          %Color for external hyperlinks
+  linkcolor    = blue,          %Color of internal links
+  citecolor   = violet             %Color of citations
 }
@@
 \DeclareMathAlphabet{\pazocal}{OMS}{zplm}{m}{n}
+
+  %Cool Dots in the TOC, courtesy Tyler Foster
+  \makeatletter
+\def\@tocline#1#2#3#4#5#6#7{\relax
+  \ifnum #1>\c@tocdepth % then omit
+  \else
+    \par \addpenalty\@secpenalty\addvspace{#2}%
+    \begingroup \hyphenpenalty\@M
+    \@ifempty{#4}{%
+      \@tempdima\csname r@tocindent\number#1\endcsname\relax
+    }{%
+      \@tempdima#4\relax
+    }%
+    \parindent\z@ \leftskip#3\relax \advance\leftskip\@tempdima\relax
+    \rightskip\@pnumwidth plus4em \parfillskip-\@pnumwidth
+    #5\leavevmode\hskip-\@tempdima
+      \ifcase #1
+       \or\or \hskip 1em \or \hskip 2em \else \hskip 3em \fi%
+      #6\nobreak\relax
+    \dotfill\hbox to\@pnumwidth{\@tocpagenum{#7}}\par
+    \nobreak
+    \endgroup
+  \fi}
+\makeatother
 
@@
 
+\DeclareMathOperator{\spec}{Spec}
+
 \theoremstyle{definition}
@@
 
-\title[Curve counting in genus one: elliptic singularities {\it \&}  relative geometry]{Curve counting in genus one: elliptic singularities {\it \&} relative geometry}
+\title[Curve counting in genus one: elliptic singularities {\it \&}  relative geometry]{Curve counting in genus one: \\ elliptic singularities {\it \&} relative geometry}
 \author{Luca Battistella, Navid Nabijou and Dhruv Ranganathan}
@@
 
-\setcounter{section}{-1}
-\section{Introduction}
+\setcounter{section}{0}
+
+\section*{Introduction}
 
@@
 
-While the higher genus situation is much more difficult, in the last several years, substantial theory has been developed towards a conceptual understanding of the genus one case.
-This began over a decade ago with the pioneering work of Li, Vakil, and Zinger~\cite{redgone,VZ,LZ,lz2,zingerstvsred,zingred}, and was recently reinvigorated using ideas from singularity theory~\cite{BCM18,CM18,HL,SMY1,VISC} and logarithmic geometry~\cite{RSPW,RSPW2}.
-The result is a \textbf{reduced} Gromov--Witten theory, which removes certain degenerate contributions from the ordinary theory.
-While the Atiyah--Bott localisation for the reduced invariants was used to great effect by Zinger in his proof of the BCOV conjectures, two major components of the standard theory -- relative invariants and the degeneration formula -- have not been developed in this setting.
-Our results in this paper provide these as new {structural} tools in reduced genus one Gromov--Witten theory\footnote{Further motivation to consider the genus one case specifically comes simply from the fact that for Calabi--Yau geometries in dimension larger than $3$, Gromov--Witten theory vanishes in genera greater than one.}.
-
-\subsection{Results} Our first contribution is a definition and construction of reduced Gromov--Witten theory of projective space relative to a hyperplane.
-The geometric content is the following, see \S \ref{section construction} for a precise formulation.
-
+The higher genus situation is much more delicate, and substantial theory has been developed in recent years to treat the genus one case, both for its intrinsic geometry, and for higher genus insights.
+This began over a decade ago with pioneering work of Li, Vakil, and Zinger~\cite{redgone,VZ,LZ,lz2,zingerstvsred,zingred}, and was recently reinvigorated using ideas from singularity theory~\cite{BCM18,HL,SMY1,VISC} and logarithmic geometry~\cite{RSPW,RSPW2}.
+The result is a \textbf{reduced} Gromov--Witten theory, which removes degenerate contributions from the ordinary theory.
+While the Atiyah--Bott localisation for the reduced invariants was used to great effect by Zinger in his proof of the BCOV conjectures, two major components of the subject -- relative invariants and the degeneration formula -- have not been developed in this setting.
+Our work provides these as new {structural} tools in reduced genus one Gromov--Witten theory\footnote{Further motivation to consider the genus one case specifically comes simply from the fact that for Calabi--Yau geometries in dimension larger than $3$, Gromov--Witten theory vanishes in genera greater than one.}.
+While the essential starting point is the early work on relative Gromov--Witten theory by Gathmann, modern tools are required in our setting.
+We establish both the conceptual framework and the formula by combining tropical geometry and logarithmic Gromov--Witten theory, as developed by Abramovich--Chen--Gross--Siebert, with the recent understanding of elliptic singularities and their interactions with logarithmic structures.
+
+\subsection{Results} Our first contribution is the construction of a \textbf{reduced relative} Gromov--Witten theory associated to elliptic curves in $\mathbb P^N$ with prescribed tangency along a hyperplane, and analogous invariants associated to smooth pairs $(X,Y)$ with $Y$ very ample.
+Our reduced relative theory differs from relative Gromov--Witten theory in a parallel fashion to how Li--Zinger's reduced Gromov--Witten theory differs from the standard theory.
+
+The geometric content is the following theorem, which provides a smooth and proper moduli space compactifying the space of elliptic curves in projective space with prescribed contact order data.
 Let $\mathcal M_{1,\alpha}^\circ(\mathbb P^N|H,d)$ be the moduli space of positive degree maps from smooth curves of genus one to $\mathbb P^N$ with dimensionally transverse contact order $\alpha\in\mathbb Z^n_{\geq 0}$ along $H$.
+A precise version of the following theorem requires a certain amount of tropical and logarithmic language, and is therefore stated precisely in \S \ref{section construction}.
 
@@
 There exists a logarithmically smooth and proper Deligne--Mumford stack $\VZ_{1,\alpha}(\mathbb P^N|H,d)$ having expected dimension, and containing $\mathcal M_{1,\alpha}^\circ(\mathbb P^N|H,d)$  as a dense open subset.
-A point in this moduli space parameterises maps
+A point in this moduli space determines commutative diagrams
 \[
-C\to \mathbb P^N[s]\to \mathbb P^N,
+\begin{tikzcd}
+C\arrow{r} & \overline C_1\arrow{d}\arrow{r} & \overline C_2\arrow{d} \\ 
+& \mathbb P^N[s]\arrow{r} & \mathbb P^N,
+\end{tikzcd}
 \]
-to an $s$-fold expansion of $\mathbb P^N$ along $H$ such that the map to the expansion and composite map $C\to \mathbb P^N$ each factor nontrivially through an elliptic singularity. 
+where $C$ is a nodal genus $1$ curve, $\overline C_1$ and $\overline C_2$ are Gorenstein curves of genus $1$, the map $C\to \PP^N[s]$ is a logarithmic map to an $s$-fold expansion of $\PP^N$ along $H$, and each of the vertical is \textbf{non-degenerate}.
 \end{customthm}
 
-The moduli space above is constructed by identifying two closed conditions that must be satisfied by the space of maps to the pair $(\mathbb P^N,H)$.
-Each condition requires the stable map to factor through an elliptic singularity.
-The behaviour mixes the geometry in~\cite{RSPW} and~\cite{RSPW2}.
-{Together with an analysis of the deformation theory of such maps, we are led to Theorem~\ref{thm: desingularization}}.
-
-Our second result explains how to do practical calculations on this space of stable maps.
+Intuitively, non-degeneracy is the condition that the maps in question are non-constant on some branch of the minimal genus $1$ subcurve, see  \S \ref{section construction} for details.
+
+%The moduli space above is constructed by identifying two closed conditions that must be satisfied by maps to the pair $(\mathbb P^N,H)$.
+Each condition requires the stable map to factor through an elliptic singularity, and the conditions together are required for the relative and absolute reduced theories to be related appropriately.
+{An analysis of the deformation theory of such maps leads to Theorem~\ref{thm: desingularization}}.
+
+The information involving singularities adds substantial complexity to the theory, and this motivates our next result, which shows that calculations are nonetheless possible.
 
@@
 \end{enumerate}
-from the full genus zero and reduced genus one invariants of the ambient variety $X$.
+from the absolute genus zero and absolute reduced genus one invariants of $X$.
 \end{customthm}
 
-This reconstruction result is most directly a generalisation of Gathmann's one~\cite{Ga}.
-A higher genus reconstruction result for the ordinary theory is proved in a paper of Maulik and Pandharipande~\cite{MaulikPandharipande}, but follows a fundamentally different strategy to ours.
+This reconstruction result generalies that of Gathmann~\cite{Ga}.
+A higher genus reconstruction result for the ordinary theory is proved by Maulik and Pandharipande~\cite{MaulikPandharipande}, but follows a fundamentally different strategy to ours.
 In particular, localisation is never used in the analysis here, nor in the work of Gathmann.
@@
 
-For the second step, we contend with the interaction of the relative splitting formula and the geometry of elliptic singularities, which is entirely new (\S \ref{subsection C0 splitting}).
+For the second step, we are forced to contend with the interaction of the relative splitting formula and the geometry of elliptic singularities, which is entirely new (\S \ref{subsection C0 splitting}).
 We express the factorisation condition -- central to the constructions in~\cite{RSPW,RSPW2} -- in terms of tautological classes, leading to Theorem~\ref{thm: recursion}.
 
-\subsection{Broader contributions} Beyond genus one, we pass through some useful general techniques.
-First, we explain how to describe degenerate moduli spaces as fibre products.
-This is substantially more delicate than the standard situation for two reasons.
-On the one hand, we need to study the interaction of the relative geometry with elliptic singularities, which involves a study of the factorisation condition in terms of tautological vector bundles.
-On the other hand, the degenerate strata of moduli spaces are not simply fibre products of spaces with smaller numerical invariants, but compactified torus bundles over these strata, due to the introduction of logarithmic blowups.
-This geometry is present throughout logarithmic enumerative geometry, particularly in the degeneration formula, and we provide a first systematic procedure that explains how to use tropical geometry to calculate with these torus bundles~\cite{R19}.
-
-In addition, the results of~\cite{RSPW} suggest the existence of a reduced higher genus Gromov--Witten theory formed by replacing contracted elliptic components with singularities\footnote{We have been informed by Jonathan Wise that his Ph.D.
+\subsection{Context and further discussion} This paper is a most directly related to recent work on aligned logarithmic structures, elliptic singularities, and stable maps, as developed in~\cite{RSPW,RSPW2}.
+The moduli spaces we construct lie in between the absolute and toric-boundary-relative geometries studied in the first and second of those papers, respectively.
+The degeneration algorithm presented here as a first practical implementation of the theory developed in that work.
+
+We pass through general techniques that we expect will be useful in logarithmic Gromov--Witten theory more broadly.
+We explain how to describe degenerate moduli spaces in terms of simpler spaces of maps.
+This is substantially more delicate than the standard situation, where the strata are simply fibre products.
+First, one must understand the interaction of the relative geometry with elliptic singularities, which involves a study of the factorisation condition in terms of tautological bundles.
+Second, the degenerate strata of moduli spaces are not simply fibre products of spaces with smaller numerical invariants, but compactified torus bundles over these strata, due to the introduction of logarithmic blowups.
+This geometry is at the heart of recent work on the degeneration formula~\cite{R19}.
+The main text provides a first systematic procedure that uses tropical geometry to calculate with these torus bundles.
+
+A key step in our recursion is a description of the locus of maps with higher than prescribed tangency, which was identified by Gathmann.
+We realise the locus as the vanishing locus of a section of a line bundle that comes from tropical geometry — from a piecewise linear function on the fan.
+The systematic understanding of logarithmic line bundles arising in this fashion is likely to play an important role in logarithmic enumerative geometry.
+
+Although the geometric ideas in Gathmann's recursion are clear, they are implemented within the space of ordinary stable maps, and do not formally fit within the formalism of logarithmic Gromov--Witten theory.
+On the way to our main results, we reinterpret Gathmann's idea of increasing tangency within logarithmic mapping spaces.
+%This is done by the introduction of \emph{fictitious markings}, and an identification of the space of maps with higher contact order with a boundary stratum inside that of lower contact order and more (fictitious) markings.
+
+%Our methods require us to work simultaneously with several variants of the space of relative/logarithmic stable maps, with fixed and expanded target.
+The conceptual features of one space are often computational bugs, and vice versa.
+Kato's perspective on logarithmic blowups as subfunctors lies at the heart of these ideas.
+We believe that the techniques developed in the genus one case here will be used repeatedly in logarithmic Gromov--Witten theory calculations.
+The necessity of working with multiple virtual birational models in logarithmic enumerative geometry is apparent in recent and ongoing work of a number of researchers, and we hope that the methods developed here will be useful more broadly.
+
+\subsection{Future directions} The results of~\cite{RSPW} also suggest the existence of a reduced higher genus Gromov--Witten theory formed by replacing contracted elliptic components with singularities.
+We have been informed by Jonathan Wise that his Ph.D.
 candidate Sebastian Bozlee has constructed these higher genus reduced Gromov--Witten invariants.
-A manuscript is in preparation.}.
-The discussion here is likely to carry over to this setting.
-
-Second, a key step in our recursion is a description of the locus of maps with higher than prescribed tangency, which was identified by Gathmann.
-We realise the locus as the vanishing locus of a section of a line bundle that comes from tropical geometry — from a piecewise linear function on the fan.
-The systematic understanding of logarithmic line bundles arising in this fashion is likely to play an important r\^ole in logarithmic enumerative geometry.
-
-We rephrase Gathmann's idea of increasing the tangency requirement within the framework of logarithmic stable maps (where maximal tangency is always assumed) by introducing \emph{fictitious markings}, and identifying the space of maps with higher contact order with a boundary stratum inside that of lower contact order and more (fictitious) markings.
-
-Our analysis leads naturally to the study of a ``main component’’ double ramification cycle for target manifolds in genus one.
+A manuscript is in preparation.
+The discussion here is expected to carry over to this setting.
+
+Our analysis leads naturally to the study of the main component of the double ramification cycle for target manifolds in genus one.
 The virtual geometry of this was studied in recent work of Janda, Pandharipande, Pixton, and Zvonkine~\cite{DRCBundle}.
-We do not know how to calculate a closed formula for this main component contribution (except in the case where the target manifold is a point), but we repurpose E.~Katz's topological recursion relations \cite{EKatz} to complete the algorithm.
-We note that even in genus one, an understanding of the main component contributions of the double ramification cycle for target manifolds would be interesting.
-
-Finally, we note that our methods require us to encounter several variants of the space of relative/logarithmic stable maps, with both fixed and expanded target.
-The conceptual features of one space are often computational bugs, and vice versa, and we believe that the techniques developed in the genus one case here will be used repeatedly in logarithmic Gromov--Witten theory calculations.
-In particular, we frequently use Kato's perspective on logarithmic blowups as subfunctors that was applied in~\cite{RSPW,RSPW2}.
+Even in genus one, an understanding of the main component contributions of the double ramification cycle for target manifolds seems to be lacking.
+Our main algorithm subverts the use of this class, but it would be more natural to use it.
+
+Finally, it would be natural to generalize the method of degenerating tangency conditions to targets with higher rank logarithmic structures.
+The extreme case when the target is a toric variety with its toric boundary, is intimately tied with the enumerative geometry of well-spaced tropical curves~\cite{LR18,RSPW2,Speyer}.
+%We will return to these questions in future work.
 
 \subsection*{Acknowledgements} We have benefited from fruitful conversations with friends and colleagues, including Pierrick Bousseau, Francesca Carocci, Cristina Manolache, Davesh Maulik, Keli Santos-Parker, and Jonathan Wise.
+The comments of an anonymous referee have proved very valuable.
 The authors worked on this project during visits to MPIM-Bonn, MIT, University of Cambridge, and the University of Glasgow, and thank these institutions for ideal working conditions and support.
@@
 would in addition like to thank Imperial College London, the LSGNT, the Royal Society, 3CinG, and the MSRI program ''Enumerative Geometry beyond Numbers''.
+N.N.
+was partially supported by EPSRC grant EP/R009325/1.
 
@@
 
-\subsection{The absolute case} Let $\mathfrak M_{1,n}$ be the logarithmic algebraic stack of $n$-pointed prestable curves of genus one.
+We briefly review some basic tropical structures in the theory of logarithmic curves and logarithmic stable maps.
+A detailed treatment is given by~\cite[Section~3]{CavalieriChanUlirschWise}.
+The following paragraphs are meant only as a reminder.
+
+\subsection*{Curves and tropical curves} A nodal curve $C$ over $\spec \mathbb C$ has an associated dual graph $\Gamma(C)$.
+Given a toric monoid $P$, there is a logarithmic point $\spec \CC_P$ which may be thought of as remembering the information of an embedding of a closed point into the toric variety $\spec \mathbb C[P]$.
+For a logarithmically smooth curve $C$ over $\spec \CC_P$, the dual graph $\Gamma(C)$ is enhanced: given an edge $e$ of $\Gamma(C)$, the logarithmic structure keeps track of a generalized ``edge length'' $\ell_e$, which is an element of $P$.
+These data can be repackaged into a cone complex $\plC$ together with a map to the dual cone $\sigma_P$
+\[
+\pi: \plC\to \sigma_P.
+\]
+A fiber of this map $\pi$ is a metric space enhancing the topological space $\Gamma(C)$, with edges given lengths in $\RR_{\geq 0}$.
+Over the interior of the cone $\sigma_P$ these edge lengths are nonzero, and the fibers are homoemorphic to $\Gamma(C)$.
+Over the faces of $\sigma_P$, the fibers can be identified with edge collapses.
+
+The discussion is globalized in~\cite{CavalieriChanUlirschWise}, and the construction can be carried out for the universal curve over the moduli space of logarithmic curves.
+Specifically, there is a stack over the category of cone complexes $\mathfrak M_{g,n}^{\mathrm{trop}}$ equipped with a universal curve
+\[
+\plC\to \mathfrak M_{g,n}^{\mathrm{trop}}.
+\]
+The reader is encourage to think of $\mathfrak M_{g,n}^{\mathrm{trop}}$ as playing the same role for $\mathfrak M_{g,n}$ as a fan plays for a toric variety.
+In particular, two constructions are relevant:
+\begin{enumerate}
+\item A subdivision of $\mathfrak M_{g,n}^{\mathrm{trop}}$ gives rise to a birational modification of $\mathfrak M_{g,n}$.
+\item A piecewise linear function on $\mathfrak M_{g,n}^{\mathrm{trop}}$ gives rise to a Cartier divisor on $\mathfrak M_{g,n}$.
+\end{enumerate}
+
+\subsection*{Maps and tropical maps}The discussion carries over to the setting of logarithmic maps.
+Specifically, given a logarithmic curve $C$ and a logarithmic map to a smooth pair $(X,Y)$ over a logarithmic scheme $S$.
+For simplicity, assume that $S$ is a $P$-logarithmic point, as above.
+There is an associated \textbf{tropicalization}, i.e.
+a family of tropical curves $\plC$ over $\sigma_P$, together with a map of cone complexes
+\[
+\plC\to \RR_{\geq 0}.
+\]
+Each fiber over $\sigma_P$ encodes a metric enhancement of the dual graph, together with a piecewise linear map to $\RR_{\geq 0}$.
+There is once again a cone stack representing the moduli problem of tropical maps; the technical details are only cosmetically different than those presented in~\cite{CavalieriChanUlirschWise}, and we leave these details to the reader.
+
+\subsection{Maps from curves and elliptic singularities} We provide a brief intuitive picture that underlies the work in~\cite{RSPW,RSPW2}.
+If $C$ is a Gorenstein curve and $f:C\to \mathbb P^N$ is a morphism, the ampleness of the the tangent bundle of $\mathbb P^N$ ensures that if no subcurve of arithmetic genus $1$ is contracted, the deformations of $f$ are unobstructed.
+In fact, the deformations \textit{over the stack of curves} are also unobstructed.
+The moduli space of Gorenstein genus $1$ is not smooth.
+However, a more sophisticated moduli problem, consisting of nodal curves together with a \textit{chosen contraction} to a Gorenstein curve, might be expected to resolve these singularities.
+The formation of such a moduli problem requires logarithmic geometry, and is achieved in~\cite[Section~3]{RSPW}.
+Once constructed, the corresponding moduli of stable maps out of a Gorenstein curve is also resolved.
+Note that maps from nodal genus $1$ curves may have stable limits that contract genus $1$ subcurves, but the allowance of Gorenstein singularities ensures that properness despite disallowing contracted genus $1$ components.
+
+When working with logarithmic geometries such as $(\mathbb P^N,H)$ as we do here, similar ideas may be expected to apply, but the deformation theory of maps becomes more delicate.
+Indeed, the logarithmic Euler sequence for this pair shows that the logarithmic tangent bundle is a quotient of $\mathcal O\oplus\mathcal O(1)^{\oplus 1}$, and additional obstructions appear.
+In simple terms, there exist logarithmic maps to the pair $(\mathbb P^N,H)$ with obstructed logarithmic deformations, whose underlying ordinary stable map is unobstructed.
+
+\subsection{Absolute geometry: reminders} Let $\mathfrak M_{1,n}$ be the logarithmic algebraic stack of $n$-pointed prestable curves of genus one.
 We begin by recalling the logarithmic moduli spaces of genus one curves constructed in~\cite[\S 2 \& \S 4]{RSPW}.
-Given a logarithmically smooth curve $C$ over a logarithmic geometric point $S$, let $\plC$ denote its tropicalization, and let $\lambda \in \overline{M}_{S}$ be the piecewise-linear function giving the distance from each vertex of $\sqC$ to the minimal genus one subcurve.
+
+Consider a logarithmically smooth curve $C$ over a logarithmic geometric point $S$ with monoid $P$ and let $\pi: \plC\to \sigma_P$ denote its tropicalization.
+Given a point $t$ in $\sigma_P$ we obtain a metric graph as explained above.
+Since the curve in question has genus $1$, there is a minimal genus $1$ subgraph -- either a vertex of genus $1$ or a cycle in the graph.
+We will refer to this as the \textbf{core}.
+Given a point $s$ with $\pi(s)$ equal to $t$, there is a well-defined distance in the metric graph $\pi^{-1}(t)$ from $s$ to the core.
+
+In particular, for each vertex $v$ of the dual graph $\Gamma(C)$, i.e.
+each component of $C$, there is a well-defined function $\lambda(v): \sigma_P\to \RR_{\geq 0}$, defined on the base of the tropical family.
+Given any other piecewise linear function $\delta$ on $\sigma_P$, say that $\delta$ is \textbf{comparable} to $\lambda(v)$ if there is a global order relation, either $\lambda(v)\leq \delta$ or $\lambda(v)\geq \delta$, that holds at all points of $\sigma_P$.
+
+Piecewise linear functions on $\sigma_P$ are naturally identified with global sections of the characteristic sheaf $\overline M_S$.
+Given an arbitrary logarithmically smooth curve $C/S$, conditions involving the comparability of piecewise linear functions can be imposed geometric point-by-point.
+This leads to the following definition.
+
 \begin{definition}
@@
 \end{definition}
-In essence, this says that the curve $\sqC$ is such that all vertices are either inside, outside, or on the circle of radius $\delta$, and that the collection of vertices inside the circle is totally ordered.
+In other words, for the tropical curve $\sqC$, all vertices are either inside, outside, or on the circle of radius $\delta$ regardless of the point on the base; the collection of vertices inside the circle is totally ordered by their distance to the core.
 
 The moduli stack $\mathfrak M_{1,n}^{\mathrm{cen}}$  of centrally aligned curves is a logarithmic algebraic stack in the smooth topology, and $\mathfrak M_{1,n}^{\mathrm{cen}}\to\mathfrak M_{1,n}$ is a logarithmic modification.
-The main construction of~\cite{RSPW} canonically associates to any centrally aligned family of curves $\mathcal C_S$ a partial destabilisation $\widetilde{\mathcal C}_S$ and a contraction
+The main construction of~\cite{RSPW} canonically associates to any centrally aligned family of curves $\mathcal C_S$ a partial destabilisation $\widetilde{\mathcal C}_S$, introducing $2$-pointed components, and a contraction
 \[
@@
 where $\overline{\mathcal C}_S$ may contain a Gorenstein elliptic singularity \cite{SMY1}.
-The number of branches is equal to the sum of the number of vertices of $\widetilde{\sqC}$ which lie on the circle of radius $\delta$.
-This data uniquely determines the singularity.
+Given a family of tropical curves, the function $\delta$ provides a non-negative real number for each point on the base.
+We may therefore consider the ``circle'' of points on each fiber whose distance from the minimal genus $1$ subgraph is equal to $\delta$.
+The partial destabilization, or ``bubbling'', introduces $2$-pointed rational curves into the curve by adding vertices to the dual graph at the points that lie on this circle.
+The number of branches is equal to the number of vertices of $\widetilde{\sqC}$ which lie on the circle of radius $\delta$.
+%This data uniquely determines the singularity.
 
@@
 A stable map in this space is said to satisfy the \textbf{factorisation condition} if the map $\mathcal C\to \mathbb P^N$ factors through the contraction $\widetilde{\mathcal C}\to \overline{\mathcal C}$.
+For ease of language, maps from nodal curves that are not constant on any subcurve of genus $1$ are taken to satisfy this condition.
 
@@
 
-The remainder of this section lifts this construction to the category of relative maps to the pair $(\mathbb P^N,H)$.
-The core of the result is identifying the necessary factorisation conditions that remove the obstructions.
+\begin{remark}[Constant maps]\label{rem: constant-maps}
+When the degree of the map is $1$, maps from smooth genus $1$ curves to $\PP^N$ are constant.
+The interior of the moduli space of stable maps in this case is empty, though the compactification by stable maps is non-empty.
+The space of maps satisfying the factorization condition is also empty.
+Only non-empty cases are considered.
+\end{remark}
+
+The remainder of this section lifts this construction to the category of relative maps to $(\mathbb P^N,H)$. The core result shows that two factorisation conditions remove the obstructions.
 
@@
 
-We will first compactify the space described above, and then desingularise it.
-For the compactification, we begin with Abramovich--Chen--Gross--Siebert's space of logarithmic stable maps, though we will typically work with various subcategories and variants~\cite{AbramovichChenLog,ChenLog,GrossSiebertLog,KimLog}.
+We compactify the space described above, and then desingularise it.
+For the compactification, we begin with Abramovich--Chen--Gross--Siebert's space of logarithmic stable maps, though we will work with variants~\cite{AbramovichChenLog,ChenLog,GrossSiebertLog,KimLog}.
 
@@
 \]
-Choose a subdivision of $\mathbb R_{\geq 0}$ whose vertices consist of the images of vertices of $\plC$.
-Pull this subdivision back to $\plC$ by marking all preimages of the vertices of $\mathbb R_{\geq 0}$.
+Choose a subdivision of $\mathbb R_{\geq 0}$ whose vertices are the images of vertices of $\plC$.
+Pull this subdivision back to $\plC$ by subdividing preimages of the vertices of $\mathbb R_{\geq 0}$.
 Denote the resulting map $\widetilde \plC \to \widetilde{\mathbb R}_{\geq 0}$.
-
 These subdivisions induce logarithmic modifications
@@
 The irreducible components of the target are in bijection with the vertices in $\widetilde{\mathbb R}_{\geq 0}$.
-The curve is modified by adding rational components corresponding to the newly introduced vertices.
+The curve is modified by adding rational components for the newly introduced vertices.
 
@@
 
-Globally, Kim constructs a moduli space of logarithmic stable maps to expanded degenerations, which on logarithmic points, reduces to the above construction~\cite{KimLog}.
-Indeed, by the above description, Kim's space is identified with a subcategory of the Abramovich--Chen--Gross--Siebert space, and its dual minimal monoids are cones in a subdivision of the dual minimal cones of the unexpanded space.
-This process is outlined in complete generality in~\cite[\S~2]{R19}.
-
-Since we will work mostly with expansions, we will use the notation
+Globally, Kim constructs a moduli space of logarithmic maps to expanded degenerations, which on logarithmic points, reduces to the above construction~\cite{KimLog}.
+Kim's space is identified with a subcategory of the Abramovich--Chen--Gross--Siebert space, and its dual minimal monoids are cones in a subdivision of the dual minimal cones of the unexpanded space, see~\cite[\S~2]{R19}.
+
+We typically work with expansions for convenience, and use the notation
 $\ol\Mcal_{1,\alpha}(\PP^N|H,d)$
-for Kim's space of logarithmic stable maps, with the understanding that this may just as easily be viewed as a logarithmic modification of the Abramovich--Chen--Gross--Siebert space.
-
-\subsection{Relative geometry: alignment} As in the absolute setting, we consider the space of logarithmic morphisms from the universal curve $\mathcal{C} \to \mathfrak{M}_{1,n}^{\mathrm{cen}}$ to the logarithmic scheme $(\PP^N,H)$.
-As in the absolute case, we require the radius to pass through a vertex of positive degree in $\PP^N$ and contain only vertices of degree zero in its strict interior, but the alignment must also be compatible with the logarithmic map.
+for Kim's space of logarithmic stable maps.
+
+\subsection{Relative geometry: alignment} We consider the space of logarithmic morphisms from the universal curve $\mathcal{C} \to \mathfrak{M}_{1,n}^{\mathrm{cen}}$ to the logarithmic scheme $(\PP^N,H)$.
+As in the absolute case, we require the radius to pass through a vertex of positive degree in $\PP^N$ and contain only vertices of degree zero in its strict interior.
 In this way we obtain a logarithmic modification of the Abramovich--Chen--Gross--Siebert space.
@@
 We refer to these latter components as \textbf{the higher levels}.
-Thus, we will say that a subcurve $D\subseteq C$ maps to \textbf{higher level} if the collapsed map
-\[
-C\to \mathbb P^N
-\]
-maps $D$ into $H\subset \mathbb P^N$.
+Thus, we will say that a subcurve $D\subseteq C$ maps to \textbf{higher level} if the composite $C\to \mathbb P^N$ maps $D$ into $H\subset \mathbb P^N$.
 
@@
 This coincides with the radius of the underlying map to $\mathbb P^N$.
-Of course, $\delta_F\leq \delta_B$, so $(C,\delta_F)$ is centrally aligned also.
+Of course, $\delta_F\leq \delta_B$, so $(C,\delta_F)$ is centrally aligned.
 
 The datum $(\delta_F,\delta_B)$ determines a destabilisation $\widetilde C$ of $C$ together with successive contractions $\widetilde C\to \overline C_F\to\overline C_B$.
-The contractions are constructed directly from~\cite[Section~3]{RSPW}.
-
+The contractions are constructed by~\cite[Section~3]{RSPW}.
+
+A Gorenstein elliptic singularity has a number of \textbf{branches}.
+Given a curve $\overline C$ of genus $1$ with such a singularity, define a branch of $\overline C$ to be an irreducible component containing a branch of the singularity.
+If the curve $C$ is nodal, then its branches will be understood to be the components of its minimal arithmetic genus $1$ subcurve, i.e.
+its core.
 The following condition identifies the locus of smoothable maps.
@@
 \begin{enumerate}
-\item the map $C\to \mathbb P^N[s]$ factors through $\overline C_F$ such that at least one branch of $\overline C_F$ has positive degree in the fibre direction; 
+\item the map $C\to \mathbb P^N[s]$ factors through $\overline C_F$ such that $F$ is non-constant on at least one branch of $\overline C_F$,
 \item the collapsed map to $\mathbb P^N$ factorises through $\overline C_B$ such that at least one branch of $\overline C_B$ has positive degree.
 \end{enumerate}
+The factorisation conditions are understood to be satisfied when $C\to \mathbb P^N[s]$ (resp. $C\to \mathbb P^N$) does not contract a genus $1$ subcurve. 
 \end{definition}
 
-In particular, if $[C\to \mathbb P^N[s]\to \mathbb P^N]$ is a family of centrally aligned maps over $S$ that factorises completely, there is a forgetful moduli map $S\to \VZ_{1,n}(\mathbb P^N,d)$, to the principal component of the space of absolute maps.
+If $[C\to \mathbb P^N[s]\to \mathbb P^N]$ is a family of centrally aligned maps over $S$ that factorises completely, there is a moduli map $S\to \VZ_{1,n}(\mathbb P^N,d)$, to the principal component of the space of absolute maps.
 Let
 \begin{equation*} \VZ_{1,\alpha}(\mathbb P^N|H,d) \subseteq \widetilde\VZ_{1,\alpha}(\PP^N|H,d) \end{equation*}
-be the stack of maps from centrally aligned curves to expansions of $\mathbb P^N$ that factorise completely.
+be the stack of maps from centrally aligned curves to expansions that factorise completely.
 
 \begin{thm}\label{thm: log-smoothness}
-The stack $\VZ_{1,\alpha}(\mathbb P^N|H,d)$ is proper and logarithmically smooth over $\mathrm{Spec} \ \mathbb C$. 
+The stack $\VZ_{1,\alpha}(\mathbb P^N|H,d)$ is logarithmically smooth and proper of the expected dimension.
 \end{thm}
 
+As noted in Remark~\ref{rem: constant-maps}, maps from elliptic curves to $\PP^N$ will always be taken to have degree at least $2$, ensuring that the main component is non-empty.
+
 \begin{proof}
-We prove the results via the forgetful morphism
+We examine the geometry of the space of maps to $(\PP^N|H)$ by utilising the forgetful morphism
 $$
@@
 which remembers only the stabilisation of the collapsed map.
-The map is certainly centrally aligned, and we have already argued above that it satisfies the factorisation property for $\mathbb P^N$ after composition.
+To see that the such a forgetful morphism exists, observe for a map $[C\to \mathbb P^N[s]\to \mathbb P^N]$, the stabilised composite map is certainly centrally aligned, and it satisfies the factorization property by construction.
 The moduli space $\VZ_{1,\alpha}(\mathbb P^N|H,d)$ is proper.
-Indeed, the verification of the valuative criterion follows exactly as in Vakil's Lemma~\cite[Lemma~5.9]{Vre}.
+Indeed, the verification of the valuative criterion follows from Vakil's Lemma~\cite[Lemma~5.9]{Vre}.
 A direct proof that the factorisation property is a closed condition may be found in~\cite[Theorem~4.3]{RSPW}.
 
-We come to logarithmic smoothness. If the elliptic curve does not map into higher level, then unobstructedness proceeds exactly as in~\cite[Section~4.5]{RSPW}.
+We come to logarithmic smoothness. If the elliptic curve does not map into higher level, then deformations of the map are unobstructed exactly as in~\cite[Section~4.5]{RSPW}.
 
@@
 \]
-where the former is the space of deformations of the curve and map to the base, as a factorised centrally aligned map.
-The latter is the space of obstructions to lifting a map to the base into the total space.
-The cokernel of this map are the absolute obstructions, which we will show vanishes, proving logarithmic smoothness.
-
-We note the manner in which the group $H^1(\overline{C}_F,\mathcal O_{\overline{C}_F})$ functions as the obstruction group for the lifting.
-It suffices to work near the minimal genus one subcurve $D_F$ of $C$, since the rest of the curve is rational.
-This lifting is given by a rational function with prescribed orders of poles given by the slopes of the tropicalization map.
-That is, if $\alpha$ be the piecewise linear function giving this tropical map, then the lifting is described by a section of the associated bundle $\mathcal O_{C}(-\alpha)$.
+where the former is the space of logarithmic deformations of the curve and map to the base, as a factorised centrally aligned map.
+More precisely, consider a strict square zero extension of $S$ and a deformation of the map $(C,f_B)$ satisfying the factorisation property.
+Since the deformation is strict, there is a canonically induced deformation of the expansion $\mathbb P^N[s]$.
+The corresponding element in $\mathrm{Obs}(f/(C,f_B))$ is the obstruction to lifting the deformation of $(C,f_B)$ to this canonical deformation of $\mathbb P^N[s]$ over $\mathbb P^N$.
+By comparing the cotangent complexes of the source, target, and fiber of the morphism $\nu$, we see that the cokernel of this map are the absolute logarithmic obstructions for the map.
+We will show these vanish, proving logarithmic smoothness.
+
+Consider the manner in which $H^1(\overline{C}_F,\mathcal O_{\overline{C}_F})$ functions as the obstruction group for the lifting.
+Near the minimal genus one subcurve $D_F$ of $C$, in order to lift the map from $\mathbb P^N$ to the expansion, we must provide a rational function on $D_F$ with poles bounded the divisor associated to the tropicalization, i.e.
+if $\alpha$ is the piecewise linear function giving this tropical map, the lifting is described by a section of the associated bundle $\mathcal O_{C}(-\alpha)$.
 
@@
 
-The line bundle $\mathcal O_{C}(-\alpha)$ is equivalent to the divisor $\sum a_i x_i$ where $x_i$ are the points connecting $D_F$ to the rest of the curve, and $a_i$ are the slopes of $\alpha$ along the edges corresponding to the $x_i$.
-Infinitesimally moving the point $x_i$ is a deformation of the curve that is unobstructed by the map $f_B$, since the map is constant on the interior of the circle of radius $\delta_B$.
-By deforming the $x_i$, at least one of which has nonzero $a_i$, we produce a one-dimensional space of obstructions.
-The absolute obstructions therefore vanish, so the result follows.
+On restricting to the minimal genus $1$ subcurve $D_F$, the line bundle $\mathcal O_{C}(-\alpha)$ is equivalent to the divisor $\sum a_i x_i$ where $x_i$ are the points connecting $D_F$ to the rest of the curve, and $a_i$ are the slopes of $\alpha$ along the edges corresponding to the $x_i$.
+Infinitesimally moving the point $x_i$ produces a nontrivial deformation of the line bundle $\mathcal O_{C}(-\alpha)$.
+The moduli space $\VZ_{1,n}(\mathbb P^N,d)$ is a logarithmically fibration over the universal Picard stack over the stack of $n$-pointed genus $1$ curves~\cite[Remark~4.5.3]{RSPW}.
+As a consequence, it is possible to find a logarithmic deformation of the map $(C,f_B)$ that induces the deformation of the line bundle that is given by infinitesimal motion.
+The obstruction group is $1$-dimensional, and we have produced a logarithmic deformation of the collapsed map that produces a nontrivial deformation of the line bundle $\mathcal O_{C}(-\alpha)$.
+Therefore, logarithmic deformations surject onto the obstruction space above.
+The absolute obstructions, which are the cokernel of this map therefore vanish, and the result follows.
 %Consider an $S$-family of expanded maps $[F: C\to \mathbb P^N[s]$.
@@
 
-The above theorem guarantees that the singularities of the space of totally factorised maps to expansions is logarithmically smooth. In fact, one can say more in this case.
+The theorem guarantees that the singularities of the space of totally factorised maps to expansions is logarithmically smooth. One can say more in this case.
 
@@
 We conclude from this that the blowup $\widetilde{\VZ}^{\mathrm{exp}}_{1,\alpha}(\mathbb P^N|H,d)$ obtained by centrally aligning Kim's spaces has simplicial cones.
-Finally, the morphism $\VZ_{1,\alpha}(\mathbb P^N|H,d)\to \widetilde{\VZ}^{\mathrm{exp}}_{1,\alpha}(\mathbb P^N|H,d)$ is strict, so the cones of $\VZ_{1,\alpha}(\mathbb P^N|H,d)$ are simplicial, as claimed.
+The morphism $\VZ_{1,\alpha}(\mathbb P^N|H,d)\to \widetilde{\VZ}^{\mathrm{exp}}_{1,\alpha}(\mathbb P^N|H,d)$ is strict, so the cones of $\VZ_{1,\alpha}(\mathbb P^N|H,d)$ are simplicial, as claimed.
 \end{proof}
 
-\subsection{Rubber variants}\label{subsection rubber} In our implementation of the relative theory, we will need the ``rubber'' variant of the space of maps $
-\VZ_{1,\alpha}(\mathbb P^N|H,d)$, where the entire curve is mapped into higher levels.
-
-Specifically, let $\mathbb P$ denote the projective bundle $\mathbb P(\mathcal O(1)\oplus\mathcal O)$ on $\mathbb P^{N-1}$.
+\subsection{Rubber variants}\label{subsection rubber} We require a ``rubber'' variant of the space of maps $
+\VZ_{1,\alpha}(\mathbb P^N|H,d)$, where the curve is contained in the higher levels.
+
+Let $\mathbb P$ denote the projective bundle $\mathbb P(\mathcal O(1)\oplus\mathcal O)$ on $\mathbb P^{N-1}$.
 Equip this space with the logarithmic structure coming from the $0$ and $\infty$ sections of the bundle.
@@
 \]
-which factorise completely, and where automorphisms are considered over the space of maps to $\mathbb P^{N-1}$.
-Specifically, two maps that differ by a $\mathbb G_{\operatorname{m}}$ translate in the fibre direction are considered equivalent.
-Total factorisation, similar to the previous case, means that the map to the bundle and the map to the base $\mathbb P^{N-1}$ both factorise through possibly different singularities.
+which factorise completely, and where automorphisms are taken to cover the identity on the map to $\mathbb P^{N-1}$; two maps that differ by a $\mathbb G_{\operatorname{m}}$ translate in the fibre direction are considered equivalent.
+As previously, the map to the bundle and the map to the base $\mathbb P^{N-1}$ both factorise through possibly different singularities.
 
 \begin{thm}\label{thm rubber log smooth}
-The stack $\VZ^{\leftrightarrow}_{1,\alpha}(\mathbb P|H_0+H_\infty,d)$ is logarithmically smooth.
+The stack $\VZ^{\leftrightarrow}_{1,\alpha}(\mathbb P|H_0+H_\infty,d)$ is logarithmically smooth and proper of the expected dimension.
 \end{thm}
 
-The main point in the proof of this statement is that on the space of non-degenerate maps with smooth domains, the map from $\VZ^\circ_{1,\alpha}(\mathbb P|H_0+H_\infty,d)\to \VZ^{\leftrightarrow,\circ}_{1,\alpha}(\mathbb P|H_0+H_\infty,d)$ is a $\mathbb G_{\operatorname{m}}$-torsor.
-Correspondingly, the map on compact moduli spaces is a nodal curve fibration.
+The main point in the proof is that on the space of non-degenerate maps with smooth domains, the map from $\VZ^\circ_{1,\alpha}(\mathbb P|H_0+H_\infty,d)\to \VZ^{\leftrightarrow,\circ}_{1,\alpha}(\mathbb P|H_0+H_\infty,d)$ is a $\mathbb G_{\operatorname{m}}$-torsor.
+One expects that the map on compact moduli spaces is a nodal curve fibration.
 To prove this, it is convenient to work with the logarithmic multiplicative group and its torsors.
 Recall that the \textbf{logarithmic multiplicative group} $\mathbb G_{\mathrm{log}}$ is the functor on logarithmic schemes whose value on a logarithmic scheme $S$ is the group of global sections $H^0(S,M_S^{\mathrm{gp}})$; it is a proper group functor, and it contains $\Gm$ as a subfunctor.
-This functor is representable only after a logarithmically \'etale cover.
-Background may be found in~\cite{MW17,RW19}.
+This functor is representable only after a logarithmically \'etale cover, see for instance~\cite{MW17,RW19}.
 
@@
 
-To conclude the main result, we compare the stacks $\VZ^{\leftrightarrow}_{1,\alpha}(\mathbb P_{\mathrm{log}},d)$ and  $\VZ^{\leftrightarrow}_{1,\alpha}(\mathbb P|H_0+H_\infty,d)$.
+To conclude the result, we compare $\VZ^{\leftrightarrow}_{1,\alpha}(\mathbb P_{\mathrm{log}},d)$ and  $\VZ^{\leftrightarrow}_{1,\alpha}(\mathbb P|H_0+H_\infty,d)$.
 Since a map to $(\mathbb P,H_0+H_\infty)$ gives rise immediately to a map to $\mathbb P_{\mathrm{log}}$, there is a morphism
@@
 \]
-An application of the infinitesimal lifting criterion shows that this map is logarithmically \'etale, so the result follows.
+The lifting criterion shows that this map is logarithmically \'etale, so the result follows.
 \end{proof}
 
-\subsection{Virtual construction for very ample pairs}\label{subsection virtual}
-Now let $(X,Y)$ be a smooth pair with $Y$ very ample.
-The definition given in \S \ref{subsection factorisation} applies in this setting, producing a moduli space $\VZ_{1,\alpha}(X|Y,\beta)$ together with a morphism
+\subsection{Hypersurface pairs}\label{subsection virtual}
+Let $(X,Y)$ be a smooth pair with $Y$ very ample. The definition in \S \ref{subsection factorisation} applies in this setting and yields a moduli space $\VZ_{1,\alpha}(X|Y,\beta)$ with a morphism
 \begin{equation*} \VZ_{1,\alpha}(X|Y,\beta) \to \ol\Mcal^{\operatorname{log}}_{1,\alpha}(X|Y,\beta)\end{equation*}
-obtained by performing a logarithmic modification and then passing to a closed substack.
-This moduli space will not in general be logarithmically smooth, but we may equip it with a virtual class as follows.
-The complete linear system $|\OO_X(Y)|$ defines an embedding $X \hookrightarrow \PP^N$ with $Y=X\cap H$ for $H$ some hyperplane.
-
-\begin{lemma} The following square is cartesian (in the category of ordinary stacks):
+obtained by performing a logarithmic modification and passing to a closed substack where the factorization property is satisfied.
+This moduli space will typically be non-equidimensional, but we equip it with a virtual class as follows.
+The divisor $Y$ defines an embedding $X \hookrightarrow \PP^N$ with $Y=X\cap H$ for $H$ a hyperplane.
+
+\begin{lemma} The following square is cartesian in the category of ordinary stacks:
 \bcd
@@
 \end{lemma}
-\begin{proof} It is clear from the modular description that this square is cartesian in the category of fs logarithmic stacks.
-But the morphism $i$ is strict, which implies that the square is also cartesian in the category of coherent logarithmic stacks.
-Since fibre products in the latter category are compatible with the functor forgetting logarithmic structures, the claim follows.\end{proof}
-
-Since $\VZ_{1,n}(\PP^N,d)$ is smooth and $\VZ_{1,n}(X,\beta)$ carries a natural virtual class \cite[Theorem 4.4.1]{RSPW} there is a diagonal pull-back morphism~\cite[Appendix C]{BattistellaNabijou}, which we use to define the virtual class on the space of maps to $(X,Y)$:
+\begin{proof} It is clear from the modular description that this square is cartesian in the category of fs logarithmic stacks, and since $i$ is strict, it is also cartesian in ordinary stacks.\end{proof}
+
+Since $\VZ_{1,n}(\PP^N,d)$ is smooth and $\VZ_{1,n}(X,\beta)$ carries a natural virtual class \cite[Theorem 4.4.1]{RSPW}, the diagonal of $\VZ_{1,n}(\PP^N,d)$ defines a pullback~\cite[Appendix C]{BattistellaNabijou}, and therefore the virtual class on the space of maps to $(X,Y)$:
 \begin{equation*} \virt{\VZ_{1,\alpha}(X|Y,\beta)} := i_\Delta^! [\VZ_{1,\alpha}(\PP^N|H,d)]. \end{equation*}
-Since $\VZ_{1,\alpha}(X|Y,\beta)$ comes equipped with evaluation maps and cotangent line classes, we immediately arrive at a definition of reduced Gromov--Witten invariants for the pair $(X,Y)$.
-This is the same manner in which Gathmann defines his virtual classes~\cite{Ga}.
+Note that this parallel to the virtual formalism in~\cite{Ga}.
+As $\VZ_{1,\alpha}(X|Y,\beta)$ is equipped with evaluation maps and cotangent lines on the universal curve, we arrive at a definition of reduced Gromov--Witten invariants for the pair $(X,Y)$ by the standard mechanics.
 
@@
 
-\noindent The logarithmic smoothness established in Theorem~\ref{thm: log-smoothness} implies that $\VZ_{1,\alpha}(\mathbb P^N|H,d)$ is an orbifold toroidal embedding.
-Consequently, the irreducible components of its boundary and their intersections form a stratification of the space.
-This stratification will be important in the sequel.
-
-The tropicalizations of logarithmic maps that factorise completely satisfy a natural combinatorial condition known as well-spacedness. The version we use here is essentially identical to~
+\noindent The logarithmic smoothnessof Theorem~\ref{thm: log-smoothness} implies that $\VZ_{1,\alpha}(\mathbb P^N|H,d)$ is an orbifold toroidal embedding.
+The irreducible components of its boundary stratify the space, as we now describe.
+
+The tropicalizations of logarithmic maps that factorise completely are combinatoriall constrained by a condition known as \textbf{well-spacedness}. The version we use here is essentially identical to~
 \cite{RSPW2}.
@@
 cit.
-guarantees the well-spacedness as required.
+guarantees the well-spacedness.
 \end{proof}
@@
 \VZ_{1,\alpha}(\mathbb P^N|H,d)$.
-Specifically, the fact that the cone complex $\Sigma^{\mathrm{cen}}$ is the cone complex attached to the logarithmic stack $\widetilde{\VZ}_{1,\alpha}(\mathbb P^N|H,d)$ of centrally aligned maps to expansions, follows immediately from its description as a subcategory of the fibred category (over logarithmic schemes) of $\mathcal M^{\mathrm{log}}_{1,\alpha}(\mathbb P^N|H,d)$.
-To complete the result, we note that $
+Specifically, the fact that $\Sigma^{\mathrm{cen}}$ is the cone complex attached to the logarithmic stack $\widetilde{\VZ}_{1,\alpha}(\mathbb P^N|H,d)$ of centrally aligned maps to expansions, follows from its description as a subcategory of the fibred category (over logarithmic schemes) of $\mathcal M^{\mathrm{log}}_{1,\alpha}(\mathbb P^N|H,d)$.
+To complete the result, note that $
 \VZ_{1,\alpha}(\mathbb P^N|H,d)$ has a strict map to $
 \VZ_{1,\alpha}(\mathbb P^N|H,d)$, so its cone complex is a subcomplex of $\Sigma^{\mathrm{cen}}$.
-The fact that it must be contained in the subcomplex of well-spaced curves is immediate from Proposition~\ref{prop: well-spaced}.
+The fact that it is contained in the subcomplex of well-spaced curves is immediate from Proposition~\ref{prop: well-spaced}.
 \end{proof}
@@
 Given $\sigma\in \Sigma^{\operatorname{Kim}}$ we then produce all the cones in $\Sigma_{1,\alpha}(\PP^N|H,d)$ mapping to $\sigma$ by performing Steps 3--4 outlined above.
-This amounts to taking a particular subdivision of $\sigma$.
-Note that in this process, new cones are created which map into larger-dimensional cones of $\Sigma^{\operatorname{Kim}}$.
+This amounts to a subdivision of $\sigma$.
+In this process, new cones are created which map into larger-dimensional cones of $\Sigma^{\operatorname{Kim}}$.
 The process for enumerating the codimension $k$ strata of $\VZ_{1,\alpha}(\PP^N|H,d)$ is therefore:
@@
 
-\section{Degeneration of contact order}\label{Section Gathmann line bundle} Consider a reduced relative space $\VZ_{1,\alpha}(\PP^N|H,d)$.
-For each marking $x_k$ we consider the locus $\Dcal_{1,\alpha,k}(\PP^N|H,d) \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$ where $x_k$ belongs to an internal component of the collapsed map.
-In this section, we use the logarithmic structure on $\VZ_{1,\alpha}(\PP^N|H,d)$ to construct a line bundle $\Lcal_k$ together with a section $s_k$ which vanishes precisely along $\Dcal_{1,\alpha,k}(\PP^N|H,d)$.
+\section{Degeneration of contact order}\label{Section Gathmann line bundle} Consider the moduli space $\VZ_{1,\alpha}(\PP^N|H,d)$ of relative maps that factorize completely.
+For each marking $x_k$, consider the locus $\Dcal_{1,\alpha,k}(\PP^N|H,d) \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$ where $x_k$ belongs to an \textbf{internal component} of the collapsed map, i.e.
+a component of the curve that is mapped into $H$.
+In this section, we use the logarithmic structure on $\VZ_{1,\alpha}(\PP^N|H,d)$ to construct a line bundle $\Lcal_k$ and section $s_k$ which vanishes precisely along $\Dcal_{1,\alpha,k}(\PP^N|H,d)$.
 We use the correspondence with tropical geometry to identify $\cchern_1(\Lcal_k)$ in terms of tautological classes on $\VZ_{1,\alpha}(\PP^N|H,d)$, and to compute the vanishing order of $s_k$ along the components of $\Dcal_{1,\alpha,k}(\PP^N|H,d)$.
-Combined with the relative splitting axioms established in the next section, we obtain a recursion relation inside $\VZ_{1,\alpha}(\PP^N|H,d)$
+Combined with the relative splitting formulas from in the next section, we obtain a recursion relation inside $\VZ_{1,\alpha}(\PP^N|H,d)$
 
@@
 and taking Chern classes gives
-\begin{equation*} \cchern_1(\Lcal_k) = \alpha_k \psi_k + \ev_k^\st H.\end{equation*}
+\begin{equation*} \cchern_1(\Lcal_k) = \alpha_k \psi_k + \ev_k^\st H,\end{equation*}
 as required.\end{proof}
-This gives the construction of $(\Lcal_k,s_k)$ and the calculation of $\cchern_1(\Lcal_k)$ on $\MLog_{1,\alpha}(\PP^N|H,d)$; the construction on $\VZ_{1,\alpha}(\PP^N|H,d)$ is given by pull-back.
+This produces $(\Lcal_k,s_k)$ and calculates $\cchern_1(\Lcal_k)$ on $\MLog_{1,\alpha}(\PP^N|H,d)$; this bundle is pulled back to $\VZ_{1,\alpha}(\PP^N|H,d)$.
 The relevant piecewise-linear function is the composition:
 \begin{equation*} \Sigma_{1,\alpha}(\PP^N|H,d) \to \Sigma^{\log} \to \RR_{\geq 0}.\end{equation*}
-In particular, $\psi_k$ should be interpreted as a \textbf{collapsed psi class} on $\VZ_{1,\alpha}(\PP^N|H,d)$, i.e.
-a psi class coming from the stabilised curve of the collapsed map.
-In this paper, all psi classes are collapsed unless stated otherwise.
-We immediately arrive at:
+Note that $\psi_k$ should be interpreted as a \textbf{collapsed class} on $\VZ_{1,\alpha}(\PP^N|H,d)$, i.e.
+the cotangent class from the source curve of the collapsed and stabilised map.
+We arrive at the the recursion.
 
@@
 A basic phenomenon is responsible for the nature of the forthcoming analysis.
-In contrast with nodal singularities, the functions on an elliptic singularity are not simply given as collections of functions on the normalisation subject to topological gluing conditions.
-As a consequence, in order to compute integrals, it is necessary to give a tautological description of this additional factorisation condition.
-
-In what follows, we provide an explicit description of the terms appearing in the right-hand side of \eqref{equation recursion}.
+In contrast with nodal singularities, the functions on an elliptic singularity are not simply collections of functions on the normalisation that agree at the gluing point.
+In order to compute integrals, it is necessary to give a tautological description of this additional condition that captures which functions (or maps) descend from the normalization to the singularity.
+
+We provide an explicit description of the terms appearing in the right-hand side of \eqref{equation recursion}.
 For each term, we provide a combinatorial formula for the vanishing order $\lambda_\Dcal$, and a recursive description of the stratum $\Dcal$.
@@
 The tautological description of the factorisation condition then leads to a recursive structure for calculating integrals.
-This last step is the heart of the analysis.
+This step is the heart of the analysis.
 
 \begin{remark}
-We remark that for the reduced relative theory of $(\mathbb P^N,H)$ with only primary fields, an analysis of the factorisation condition can be avoided by dimension considerations.
-This leads to the main results in~\cite{Vre}.
-In order to add descendant fields, study with more general pairs, or indeed work cycle theoretically, an analysis of these tautological classes is crucial.
+The reduced relative Gromov--Witten theory of $(\mathbb P^N,H)$ with only primary insertions, i.e.
+where all cohomological insertions in the invariants are pulled back along evaluation maps, computations can be carried out without an analysis of the factorisation condition; this follows from dimension considerations and leads to the main results in~\cite{Vre}.
+In order to add descendant insertions, study with more general pairs, or indeed work cycle theoretically, an analysis of these tautological classes is crucial.
 \end{remark}
 
-\subsection{Irreducible components of the degenerate locus} We explain the tropical geometric procedure to identify irreducible components of $\Dcal_{1,\alpha,k}(\PP^N|H,d)$.
+\subsection{Irreducible components of the degenerate locus} We explain the tropical procedure to identify irreducible components of $\Dcal_{1,\alpha,k}(\PP^N|H,d)$.
 
@@
 
-\begin{proof} The locus where the logarithmic structure is trivial coincides precisely with the  locus where the source curve is smooth, and consequently not mapped inside $H$.
+\begin{proof} The locus where the logarithmic structure is trivial is the  locus where the source curve is smooth, and thus not mapped inside $H$.
 Since $\VZ_{1,\alpha}(\PP^N|H,d)$ is toroidal this locus is open and dense.
 By definition $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ is contained in the  complement of this locus and can be expressed as a union of strata of positive codimension.
-Since $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ has codimension $1$, it must therefore be equal to a union of logarithmic divisors.\end{proof}
-
-In \S \ref{subsection indexing strata} we discussed how to enumerate the logarithmic strata of $\VZ_{1,\alpha}(\PP^N|H,d)$, using the cones of the tropicalization $\Sigma_{1,\alpha}(\PP^N|H,d)$.
+Since $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ has codimension $1$, it is a union of logarithmic divisors.\end{proof}
+
+In \S \ref{subsection indexing strata} we described the logarithmic strata of $\VZ_{1,\alpha}(\PP^N|H,d)$, using the cones of the tropicalization $\Sigma_{1,\alpha}(\PP^N|H,d)$.
 Every divisorial logarithmic stratum is obtained as follows:
@@
 \end{enumerate}
-This process contains some redundancies: upon choosing a ray in the tropical moduli space, some of the edge lengths or vertex positions may get set to $0$.
+This process contains redundancies: upon choosing a ray in the tropical moduli space, some of the edge lengths or vertex positions may get set to $0$.
 This induces a generisation of the initial combinatorial type $\Delta$, given by contracting the corresponding edges of the dual graph and moving the corresponding vertices from $\RR_{>0}$ to $0$.
@@
 
-The logarithmic divisors contained in $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ are precisely those whose  combinatorial types map the vertex of the dual graph containing $x_k$  into the interior $\RR_{>0} \subseteq \RR_{\geq 0}$.
-Thus via the above procedure, we enumerate the irreducible components of $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ in a combinatorial manner, and the combinatorial type $\Delta$ allows us to describe the general element of such a component.
-The remainder of this section gives a recursive description of the components, and a procedure to compute integrals over them in a recursive manner.
+The logarithmic divisors contained in $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ are those whose  combinatorial types map the vertex of the dual graph containing $x_k$  into the interior $\RR_{>0} \subseteq \RR_{\geq 0}$.
+Thus via the above procedure, we enumerate the components of $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ in a combinatorial manner; the combinatorial type $\Delta$ allows us to describe the general element of such a component.
+The remainder of this section gives a recursive description of the components and a recursive computation of integrals over them.
 
@@
 These two cases correspond, respectively, to when the core is assigned zero degree or nonzero degree by the combinatorial type.
-To begin with we will focus on the latter case.
+We begin with the latter.
 Suppose therefore that $\widetilde{\Dcal}$ is the proper transform of a logarithmic divisor:
@@
 \begin{lemma}\label{lem:combs} Let $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ be an irreducible component which contributes nontrivially to the Gromov--Witten invariant, and let $\Delta$ be the corresponding combinatorial type.
-Suppose that $\Delta$ assigns positive degree to the core.
-Then $\Delta$ takes one of the following forms:
+If $\Delta$ assigns positive degree to the core, then $\Delta$ takes one of the following forms:
 \begin{figure}[h]
@@
 
-\begin{remark} The difference in dimensions between $\Dcal$ and $\Fcal^{\text{\tiny{log}}}$ (or equivalently, the difference in virtual dimensions between $\Ecal$ and $\Ecal^{\text{\tiny{log}}}$) may be interpreted as the difference in dimensions between moduli spaces of \emph{disconnected} rubber and their images under the collapsing morphisms.
+\begin{remark} The difference in dimensions between $\Dcal$ and $\Fcal^{\text{\tiny{log}}}$ (or equivalently, between virtual dimensions of $\Ecal$ and $\Ecal^{\text{\tiny{log}}}$) may be interpreted as the difference in dimensions between moduli spaces of \emph{disconnected} rubber and their images under the collapsing morphisms.
 \end{remark}
@@
 
-\subsubsection{Type I}\label{subsubsection type A} Suppose $\Delta$ is of type I. Then $\Ecal$ admits a finite and surjective \textit{splitting morphism} onto the fibre product:
+\subsubsection{Type I}\label{subsubsection type A} Suppose $\Delta$ is of type I. Then $\Ecal$ admits a finite and surjective \textbf{splitting morphism} onto the fibre product:
 \begin{equation*} \Ecal \to \left( \ol\Mcal_{1,\alpha^{(1)}\cup(m_1)}(\PP^N|H,d_1) \times \prod_{i=2}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i) \right) \times_{H^r} \ol\Mcal^{\leftrightarrow}_{0,\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}(\mathbb{P}|H_0+H_\infty,d_0).\end{equation*}
@@
 Now suppose $\Delta$ is of type II.
-Note that in this case, it is impossible for the core to be contracted.
+In this case, it is impossible for the core to be contracted.
 Hence $\Ecal$ is disjoint from the blown-up locus, and the map $\Dcal \to \Ecal$ is an isomorphism.
-We thus obtain the following description, entirely in terms of genus zero data:
+We obtain the following description, entirely in terms of genus zero data:
 \begin{lemma} $\Dcal$ admits a finite and surjective splitting morphism:
@@
 such that $\Dcal \to \Ecal$ corresponds to the obvious map on fibre products.\end{lemma}
-Here the first factor in the fibre product is the logarithmic blow-up of the moduli space of rubber maps constructed in \S \ref{subsection rubber}.
-We will compute integrals over such spaces as part of the recursion (see \S \ref{section recursion algorithm}).
+The first factor in the fibre product is the logarithmic blowup of the moduli space of rubber maps constructed in \S \ref{subsection rubber}.
+We compute integrals over such spaces as part of the recursion (see \S \ref{section recursion algorithm}).
 
@@
 \begin{equation*} \label{degree of gluing} \dfrac{\prod_{i=1}^r m_i}{\lcm(m_1,\ldots,m_r)}. \end{equation*}\end{lemma}
-\begin{proof} The calculation is well known, and is recorded for instance in~\cite[Section~7.9]{ChenDegeneration}, \cite[Section~5.3]{ACGSDecomposition}.
+\begin{proof} The calculation is well known, see for instance~\cite[Section~7.9]{ChenDegeneration}, \cite[Section~5.3]{ACGSDecomposition}.
 \end{proof}
@@
 
-\subsubsection{Compactified bundles over strata: $\widetilde\Dcal$ from $\Ecal$}\label{subsection Dtilde from E} Recall that the map $\widetilde\Dcal \to \Ecal$ is obtained by restricting the logarithmic blow-up
+\subsubsection{Compactified bundles over strata: $\widetilde\Dcal$ from $\Ecal$}\label{subsection Dtilde from E} Recall that the map $\widetilde\Dcal \to \Ecal$ is obtained by restricting the logarithmic blowup
 \begin{equation*} \widetilde\VZ_{1,\alpha}(\PP^N|H,d) \to \ol\Mcal_{1,\alpha}(\PP^N|H,d)\end{equation*}
@@
 In order to describe this morphism more explicitly, we first subdivide the fan of $\Ecal$ by taking the images of cones in the fan of $\widetilde\Dcal$.
-This induces a toric blow-up of $\Ecal$ which we denote by $\widetilde\Ecal$.
+This induces a toric blowup of $\Ecal$ which we denote by $\widetilde\Ecal$.
 The morphism $\widetilde\Dcal \to \Ecal$ naturally factors through a morphism $\widetilde\Dcal \to \widetilde\Ecal$ which is now flat (in contrast to $\widetilde\Dcal \to \Ecal$), and  $\widetilde\Dcal$ may now be described as a compactification of a torus bundle over $\widetilde\Ecal$, with strata determined by the combinatorics of the fan.
@@
 {\bf Logarithmic structures on strata.} Let $W\subseteq X$ be an irreducible stratum in a toroidal embedding $X$.
-The stratum itself is toroidal, and hence logarithmically smooth.
-If $X$ and $W$ are merely logarithmic and not toroidal, there is nonetheless a strict map
+The stratum $W$ is itself toroidal, or equivalently, when equipped with the divisorial logarithmic structure coming from intersecting with the toroidal boundary divisors of $X$, the resulting structure makes $W$ logarithmically smooth.
+Note that this differs from the logarithmic structure pulled back from $X$ along the inclusion of $W$ into $X$.
+
+If $X$ and $W$ are merely logarithmic and not toroidal, there is an analogue of this. There exists a strict map
 \[
@@
 \]
-where $ \mathcal A_X$ is the Artin fan of $X$, which is a toroidal Artin stack.
-If $W\subseteq X$ maps to a stratum $\mathcal A_W$ under this map, the pullback of the logarithmic structure from $\mathcal A_W$ to $W$ endows the stratum with a logarithmic structure.
+where $ \mathcal A_X$ is the Artin fan of $X$, which is logarithmically \'etale over a point.
+The logarithmic structure of $\mathcal A_X$ is divisorial in the smooth topology.
+The Artin fan $\mathcal A_X$ possesses closed strata.
+Fix an irreducible stratum $\mathcal A_W$.
+In identical fashion to the paragraph above, this stack $\mathcal A_W$ possesses a logarithmic structure by restricting the divisors on $\mathcal A_X$ and taking the induced logarithmic structure.
+This equips a logarithmic stratum $W\hookrightarrow X$ with a logarithmic structure by pullback, mirroring the construction for toroidal embeddings above.
+
+\begin{remark}
 Note that the inclusion of a stratum $W\hookrightarrow X$ is \textit{not} a logarithmic morphism.
+The pullback logarithmic structure on a closed stratum includes residual information about the (virtual) normal bundle directions; the construction above effectively removes these directions.
+Using the equivalence of Artin fans with cone complexes~\cite{CavalieriChanUlirschWise}, the above construction can be combinatorialised.
+Given a cone $\sigma$ in a cone stack $\Sigma$, its \textbf{star} consists of all cones of $\Sigma$ that contain $\sigma$; these naturally form a new cone complex.
+The associated Artin fan gives rise to the logarithmic structure on $W$ above.
+\end{remark}
 
@@
 The moduli space of attaching data for the elliptic singularity is the complement of the coordinate hyperplanes in
-$$\PP\left(\bigoplus_{i=1}^rT_{q_i}C_i\right).$$
+$$\PP\left(\bigoplus_{i=1}^rT_{q_i}C_i\right),$$
+see~\cite[Section~2.2]{SMY2}.
+A point in this space parameterizes a particular map from the rational multiple point singularity to the elliptic multiple point singularity.
 On the boundary, the circle is allowed to miss some of the $\sqC_i$ -- but not all of them!
@@
 \subsubsection{$\Dcal$ from $\widetilde\Dcal$: first way}\label{subsection D from Dtilde} On $\widetilde\Dcal$ there is a tautological line bundle arising from the modular description of $\widetilde\VZ_{1,\alpha}(\PP^N|H,d)$, namely $\OO(\delta)$.
+Recall that the piecewise linear function $\delta$ may be viewed as a global section of the characteristic sheaf of the logarithmic structure on $\widetilde\VZ_{1,\alpha}(\PP^N|H,d)$.
+The toric geometry dictionary gives rise to an associated Cartier divisor.
+Alternatively, for any logarithmic stack $X$, the natural coboundary map induced by $$0\to \mathcal O_X^\star\to M_X\to \overline M_X\to 0$$ associates a $\mathcal O_X^\star$-torsor to a global section of the characteristic sheaf.
 
@@
 on $\Ecal$, where $q_i$ is the splitting node. Then $\OO(\delta)$ is isomorphic to the pull-back of $T_i$ to $\widetilde\Dcal$ twisted by all exceptional divisors.\end{lemma}
-We illustrate this lemma in the following example, which brings out the interplay between logarithmic moduli and blow-ups.
+We illustrate this lemma in the following example, which brings out the interplay between logarithmic moduli and blowups.
 \begin{example}
@@
 Call these loci $\Xi_\Lambda$ for $\Lambda=(\Lambda_B,\Lambda_F)$ (compare with \cite[\S 3.2]{VZ} for an analogous phenomenon in the non-relative case); clearly, they may be in excess with respect to the expected codimension of $V(s)$, that is $N-1$.
-These loci are logarithmic substrata; therefore, there exists a logarithmic blow-up that principalises them.
-We claim which $\widetilde\Dcal$ is (possibly a refinement of) such a blow-up.
+These loci are logarithmic substrata; therefore, there exists a logarithmic blowup that principalises them.
+We claim which $\widetilde\Dcal$ is (possibly a refinement of) such a blowup.
 \begin{lemma}
@@
 
-Finally, on $\widetilde\Dcal$ (or, in fact, on an intermediate blow-up $\widetilde{\mathcal P}\to\mathcal P$) there are exceptional divisors $\widetilde \Xi_\Lambda$ corresponding to $\Xi_\Lambda$ in $\mathcal P$.
+Finally, on $\widetilde\Dcal$ (or, in fact, on an intermediate blowup $\widetilde{\mathcal P}\to\mathcal P$) there are exceptional divisors $\widetilde \Xi_\Lambda$ corresponding to $\Xi_\Lambda$ in $\mathcal P$.
 Since the $\Xi_\Lambda$ exhaust all the excess-dimensional components of the vanishing locus of $s\in H^0(\mathcal P,W)$, the latter induces a section $\tilde s\in H^0(\widetilde\Dcal,W(-\Sigma_\Lambda \widetilde\Xi_\Lambda))$ by pullback and twisting, whose vanishing locus is dimensionally transverse to the boundary, and whose open part coincides with the generic point of $\Dcal$, therefore $V(\tilde s)=\Dcal$.
@@
 
-\subsection{Structure of the recursion} Given the genus-zero Gromov--Witten theory of $X$, the arguments of \cite{Ga} give an effective algorithm to reconstruct the genus-zero theories of $Y$ and $(X,Y)$; moreover, the genus-zero rubber theory of $\mathbb{P}$ is identical to the genus-zero theory of $Y$ \cite{GathmannThesis}.
+\subsection{Structure of the recursion} Given the genus-zero Gromov--Witten theory of $X$, the arguments of \cite{Ga} give an effective algorithm to reconstruct the genus-zero theories of $Y$ and $(X,Y)$; the genus-zero rubber theory of $\mathbb{P}$ is equal to the genus-zero theory of $Y$ \cite{GathmannThesis}.
 Thus we may assume that all genus-zero data is known.
@@
 which completes the recursion step as long as $d \neq 1$.
-But since $\VZ_{1,n}(H,1)=\emptyset$ it follows that $\VZ_{1,n}(Y,\beta)=\emptyset$ if $d=Y\cdot\beta=1$, so we may always assume $d \geq 2$ in the recursion.
+But since $\VZ_{1,n}(H,1)=\emptyset$ as noted in Remark~\ref{rem: constant-maps}, it follows that $\VZ_{1,n}(Y,\beta)=\emptyset$ if $d=Y\cdot\beta=1$, so we may always assume $d \geq 2$ in the recursion.
 
@@
 
-Let us denote the piece of the curve carrying all of the genus and degree by $C^\prime\subseteq C$.
+Denote the piece of the curve carrying all of the genus and degree by $C^\prime\subseteq C$.
 If $C^\prime$ is mapped to top level, then either it contains $x_1$, in which case we apply $\fgt_1$ to compute the contribution, or it does not contains $x_1$, in which case it has fewer than $n$ relative markings and is known recursively.

### 2020-10-16 EllipticSingularitiesSplitting.tex
minor changes to S1, in particular added a different formulation of pf(thm 1.4)

@@
 \usepackage{tikz,tikz-cd}
-\usetikzlibrary{decorations.pathmorphing,decorations.pathreplacing,patterns,arrows.meta}
+\usetikzlibrary{decorations.pathmorphing,decorations.pathreplacing,patterns,arrows.meta,shapes.misc}
 
@@
 The higher genus situation is much more delicate, and substantial theory has been developed in recent years to treat the genus one case, both for its intrinsic geometry, and for higher genus insights.
-This began over a decade ago with pioneering work of Li, Vakil, and Zinger~\cite{redgone,VZ,LZ,lz2,zingerstvsred,zingred}, and was recently reinvigorated using ideas from singularity theory~\cite{BCM18,HL,SMY1,VISC} and logarithmic geometry~\cite{RSPW,RSPW2}.
+This began over a decade ago with pioneering work of Li, Vakil, and Zinger~\cite{redgone,VZ,LZ,lz2,zingerstvsred,zingred}, and was recently reinvigorated using ideas from singularity theory~\cite{BCM18,HL,SMY1,VISC} and logarithmic geometry~\cite{RSPW,RSPW2,BC20}.
 The result is a \textbf{reduced} Gromov--Witten theory, which removes degenerate contributions from the ordinary theory.
@@
 \]
-where $C$ is a nodal genus $1$ curve, $\overline C_1$ and $\overline C_2$ are Gorenstein curves of genus $1$, the map $C\to \PP^N[s]$ is a logarithmic map to an $s$-fold expansion of $\PP^N$ along $H$, and each of the vertical is \textbf{non-degenerate}.
+where $C$ is a nodal genus $1$ curve, $\overline C_1$ and $\overline C_2$ are Gorenstein curves of genus $1$, the map $C\to \PP^N[s]$ is a logarithmic map to an $s$-fold expansion of $\PP^N$ along $H$, and each of the vertical maps does not contract the minimal subcurve of genus $1$.
 \end{customthm}
 
-Intuitively, non-degeneracy is the condition that the maps in question are non-constant on some branch of the minimal genus $1$ subcurve, see  \S \ref{section construction} for details.
+%Intuitively, non-degeneracy is the condition that the maps in question are non-constant on some branch of the minimal genus $1$ subcurve, see  \S \ref{section construction} for %details.
 
@@
 
-\subsection{Context and further discussion} This paper is a most directly related to recent work on aligned logarithmic structures, elliptic singularities, and stable maps, as developed in~\cite{RSPW,RSPW2}.
+\subsection{Context and further discussion} This paper is most directly related to recent work on aligned logarithmic structures, elliptic singularities, and stable maps, as developed in~\cite{RSPW,RSPW2}.
 The moduli spaces we construct lie in between the absolute and toric-boundary-relative geometries studied in the first and second of those papers, respectively.
@@
 was partially supported by EPSRC grant EP/R009325/1.
+L.B.
+is supported by the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) under Germany’s Excellence Strategy EXC-2181/1 - 390900948 (the Heidelberg STRUCTURES Cluster of Excellence).
 
@@
 \subsection*{Curves and tropical curves} A nodal curve $C$ over $\spec \mathbb C$ has an associated dual graph $\Gamma(C)$.
-Given a toric monoid $P$, there is a logarithmic point $\spec \CC_P$ which may be thought of as remembering the information of an embedding of a closed point into the toric variety $\spec \mathbb C[P]$.
+Given a toric monoid $P$, there is a logarithmic point $\spec \CC_P$ which may be thought of as remembering the information of the embedding of the torus-fixed closed point into the toric variety $\spec \mathbb C[P]$.
 For a logarithmically smooth curve $C$ over $\spec \CC_P$, the dual graph $\Gamma(C)$ is enhanced: given an edge $e$ of $\Gamma(C)$, the logarithmic structure keeps track of a generalized ``edge length'' $\ell_e$, which is an element of $P$.
@@
 Over the interior of the cone $\sigma_P$ these edge lengths are nonzero, and the fibers are homoemorphic to $\Gamma(C)$.
-Over the faces of $\sigma_P$, the fibers can be identified with edge collapses.
+Over the faces of $\sigma_P$, the fibers can be identified with edge contractions.
 
@@
 \]
-The reader is encourage to think of $\mathfrak M_{g,n}^{\mathrm{trop}}$ as playing the same role for $\mathfrak M_{g,n}$ as a fan plays for a toric variety.
+The reader is encouraged to think of $\mathfrak M_{g,n}^{\mathrm{trop}}$ as playing the same role for $\mathfrak M_{g,n}$ as a fan plays for a toric variety.
 In particular, two constructions are relevant:
@@
 There is once again a cone stack representing the moduli problem of tropical maps; the technical details are only cosmetically different than those presented in~\cite{CavalieriChanUlirschWise}, and we leave these details to the reader.
+See also \cite{GrossSiebertLog}.
 
@@
 In fact, the deformations \textit{over the stack of curves} are also unobstructed.
-The moduli space of Gorenstein genus $1$ is not smooth.
+The moduli space of Gorenstein genus $1$ curves is not smooth.
 However, a more sophisticated moduli problem, consisting of nodal curves together with a \textit{chosen contraction} to a Gorenstein curve, might be expected to resolve these singularities.
@@
 Once constructed, the corresponding moduli of stable maps out of a Gorenstein curve is also resolved.
-Note that maps from nodal genus $1$ curves may have stable limits that contract genus $1$ subcurves, but the allowance of Gorenstein singularities ensures that properness despite disallowing contracted genus $1$ components.
-
-When working with logarithmic geometries such as $(\mathbb P^N,H)$ as we do here, similar ideas may be expected to apply, but the deformation theory of maps becomes more delicate.
-Indeed, the logarithmic Euler sequence for this pair shows that the logarithmic tangent bundle is a quotient of $\mathcal O\oplus\mathcal O(1)^{\oplus 1}$, and additional obstructions appear.
+Note that maps from nodal genus $1$ curves may have stable limits that contract genus $1$ subcurves, but the allowance of Gorenstein singularities ensures properness despite disallowing contracted genus $1$ components.
+
+When working with logarithmic geometries such as $(\mathbb P^N,H)$, as we do here, similar ideas may be expected to apply, but the deformation theory of maps becomes more delicate.
+Indeed, the logarithmic Euler sequence for this pair shows that the logarithmic tangent bundle is a quotient of $\mathcal O\oplus\mathcal O(1)^{\oplus N}$, and additional obstructions appear.
 In simple terms, there exist logarithmic maps to the pair $(\mathbb P^N,H)$ with obstructed logarithmic deformations, whose underlying ordinary stable map is unobstructed.
@@
 
-Consider a logarithmically smooth curve $C$ over a logarithmic geometric point $S$ with monoid $P$ and let $\pi: \plC\to \sigma_P$ denote its tropicalization.
+Consider a logarithmically smooth curve $C$ over a logarithmic geometric point $S$ with monoid $P$ and let $\pi\colon \plC\to \sigma_P$ denote its tropicalization.
 Given a point $t$ in $\sigma_P$ we obtain a metric graph as explained above.
@@
 We will refer to this as the \textbf{core}.
+
 Given a point $s$ with $\pi(s)$ equal to $t$, there is a well-defined distance in the metric graph $\pi^{-1}(t)$ from $s$ to the core. 
-
 In particular, for each vertex $v$ of the dual graph $\Gamma(C)$, i.e.
 each component of $C$, there is a well-defined function $\lambda(v): \sigma_P\to \RR_{\geq 0}$, defined on the base of the tropical family.
-Given any other piecewise linear function $\delta$ on $\sigma_P$, say that $\delta$ is \textbf{comparable} to $\lambda(v)$ if there is a global order relation, either $\lambda(v)\leq \delta$ or $\lambda(v)\geq \delta$, that holds at all points of $\sigma_P$.
-
-Piecewise linear functions on $\sigma_P$ are naturally identified with global sections of the characteristic sheaf $\overline M_S$.
-Given an arbitrary logarithmically smooth curve $C/S$, conditions involving the comparability of piecewise linear functions can be imposed geometric point-by-point.
-This leads to the following definition.
+We may as well think of $\boldsymbol{\lambda}$ as a piecewise linear function $\lambda\colon\plC\to\RR_{\geq 0}\times\sigma_P$, see Figure \ref{fig:lambdaexample}.
+Given any other linear function $\delta$ on $\sigma_P$, say that $\delta$ is \textbf{comparable} to $\lambda(v)$ if there is a global order relation, either $\lambda(v)\leq \delta$ or $\lambda(v)\geq \delta$, that holds at all points of $\sigma_P$.
+
+Piecewise linear functions on $\plC$ are naturally identified with global sections of the characteristic sheaf $\overline M_C$; linear functions on $\sigma_P$ are naturally identified with global sections of the characteristic sheaf $\overline M_S$, and can be pulled back to $C$.
+Given an arbitrary logarithmically smooth curve $C/S$, conditions involving the comparability of piecewise linear functions can be imposed at the level of geometric points; they determine subdivisions of $\sigma_P$, and, in turn, logarithmic modifications of $S$.
+%This leads to the following definition.
 
@@
 
+\begin{figure}
+ \begin{tikzpicture} 
+  \tikzset{cross/.style={cross out, draw=black, fill=none, minimum size=2*(#1-\pgflinewidth), inner sep=0pt, outer sep=0pt}, cross/.default={3pt}}
+
+  \foreach \x in {(.5,2.5),(3.3,2.5),(3.65,2.5),(3.7,2.5),(4.4,2.5),(4.65,2.5),(-1.7,2.5)}
+  \draw \x node[cross,rotate=45] {};
+
+  \foreach \x in {(-1,1),(3.5,1.5),(3.2,2),(-2.5,2.5),(-.5,1.5),(1.5,3.5),(4.8,3),(5.8,3.5),(7,0),(-2,2.8),(4,3.2)}
+  \draw[fill=black] \x circle (2pt);
+
+  \draw[gray] (0,0) node[left]{$\plC_0$} -- (1,.2) -- (2,0) -- (1,-.2) -- (0,0); %core
+
+  \draw (0,0) -- (-2.5,2.5) -- (-2.7,4) (-2.5,2.5) -- (-2.3,4) (-1,1)--(1.5,3.5)--(1.3,4) (1.5,3.5)--(1.7,4) (-.5,1.5) -- (-1.7,2.5) -- (-2,2.8) --(-2.2,4) (-2,2.8) --(-1.8,4);
+  \draw (1,.2) -- (4,3.2) -- (3.9,4) (4,3.2) -- (4.1,4);
+  \draw (1,-.2) -- (3.2,2) -- (5,4) (3.2,2) -- (5.2,4);
+  \draw (2,0) -- (3.5,1.5) -- (4.8,3) -- (5.4,4) (4.8,3) -- (5.6,4) (3.5,1.5) -- (5.8,3.5) -- (5.8,4) (5.8,3.5) -- (6,4);
+
+  \draw[->] (7,0) -- (7,4); %real axis
+  \draw[dashed] (-2.7,1) -- (7.2,1) (-2.7,1.5) -- (7.2,1.5) (-2.7,2) -- (7.2,2); %heights
+  \draw[blue,dashed]  (-2.7,2.5) -- (7.2,2.5) node[right]{$\delta$};
+  \draw [->] (6,1.55) --node[above]{$\lambda$} (6.8,1.55); %arrow-lambda
+
+  \foreach \x in {(0,0),(1,.2),(1,-.2),(2,0)}
+  \draw[fill=gray] \x circle (2pt);
+ \end{tikzpicture}
+\caption{The function $\lambda$ (distance from the core) and its cutoff value $\delta$.}
+\label{fig:lambdaexample}
+\end{figure}
+
 The moduli stack $\mathfrak M_{1,n}^{\mathrm{cen}}$  of centrally aligned curves is a logarithmic algebraic stack in the smooth topology, and $\mathfrak M_{1,n}^{\mathrm{cen}}\to\mathfrak M_{1,n}$ is a logarithmic modification.
@@
 Given a family of tropical curves, the function $\delta$ provides a non-negative real number for each point on the base.
-We may therefore consider the ``circle'' of points on each fiber whose distance from the minimal genus $1$ subgraph is equal to $\delta$.
-The partial destabilization, or ``bubbling'', introduces $2$-pointed rational curves into the curve by adding vertices to the dual graph at the points that lie on this circle.
-The number of branches is equal to the number of vertices of $\widetilde{\sqC}$ which lie on the circle of radius $\delta$.
+We may therefore consider the ``\textbf{circle}'' of points on each fiber whose distance from the core is equal to $\delta$.
+A partial destabilization, or ``bubbling'', introduces $2$-pointed rational curves into the curve by adding vertices to the dual graph at the points that lie on this circle (the crosses at height $\delta$ in Figure \ref{fig:lambdaexample}); we denote this new tropical curve by $\widetilde{\plC}$.
+The open disc of radius $\delta$, i.e.
+the locus where $\lambda<\delta$, is then contracted to a Gorenstein singularity in $\overline{\mathcal C}_S$.
+The number of branches is equal to the number of vertices of $\widetilde{\sqC}$ which lie on the circle.
 %This data uniquely determines the singularity.
 
-The space of stable maps $\widetilde\VZ_{1,n}(\PP^N,d)$ from the universal nodal curve $\mathcal C$ over the stack $\mathfrak M_{1,n}^{\mathrm{cen}}$ is proper and algebraic, with projective coarse moduli space.
-A compatibility condition between the alignment and the map is required, namely that the circle of radius $\delta$ passes through at least one component of positive degree.
-A stable map in this space is said to satisfy the \textbf{factorisation condition} if the map $\mathcal C\to \mathbb P^N$ factors through the contraction $\widetilde{\mathcal C}\to \overline{\mathcal C}$.
-For ease of language, maps from nodal curves that are not constant on any subcurve of genus $1$ are taken to satisfy this condition.
+The space of stable maps $\widetilde\VZ_{1,n}(\PP^N,d)$ from the universal nodal curve $\mathcal C$ over the stack $\mathfrak M_{1,n}^{\mathrm{cen}}$ is Deligne-Mumford and proper, with projective coarse moduli space.
+A compatibility condition between the alignment and the map is required, namely that the circle of radius $\delta$ passes through \emph{at least one component of positive degree}.
+A stable map in this space is said to satisfy the \textbf{factorisation condition} if the map $\widetilde{\mathcal C}\to \mathcal C\to \mathbb P^N$ factors through the contraction $\widetilde{\mathcal C}\to \overline{\mathcal C}$.
+Maps that are not constant on any genus $1$ subcurve of $\mathcal C$ automatically satisfy this condition; indeed, the contraction is an isomorphism in this case.
 
@@
 The interior of the moduli space of stable maps in this case is empty, though the compactification by stable maps is non-empty.
-The space of maps satisfying the factorization condition is also empty.
-Only non-empty cases are considered.
+The space of maps satisfying the factorisation condition is also empty.
+We do not indulge on this any further.
 \end{remark}
@@
 Let $\alpha$ be a partition of the degree $d>0$.
-Consider the moduli space $\mathcal M_{1,\alpha}^\circ(\mathbb P^N|H,d)$ of maps from smooth elliptic curves $C\to \mathbb P^N$ that meet $H$ at finitely many marked points with vanishing orders given by the partition $\alpha$.
+Consider the moduli space $\mathcal M_{1,\alpha}^\circ(\mathbb P^N|H,d)$ of maps from smooth genus $1$ curves $C\to \mathbb P^N$ that meet $H$ at finitely many marked points with vanishing orders given by the partition $\alpha$.
 This is a smooth, but non-proper Deligne--Mumford stack.
@@
 
-In order make the obstruction theory more geometric, we expand the target.
+In order to make the obstruction theory more geometric, we expand the target.
 To elucidate the connection with the static target, consider a logarithmic stable map $[C\to (\mathbb P^N,H)]$ over $\mathrm{Spec} \ (\mathbb N\to \mathbb C)$.
-At the level of tropicalizations, there is a map of fans
+At the level of tropicalizations, there is a map of cone complexes:
 \[
@@
 Choose a subdivision of $\mathbb R_{\geq 0}$ whose vertices are the images of vertices of $\plC$.
-Pull this subdivision back to $\plC$ by subdividing preimages of the vertices of $\mathbb R_{\geq 0}$.
+Pull this subdivision back to $\plC$ by subdividing it along the preimage of the vertices of $\mathbb R_{\geq 0}$.
 Denote the resulting map $\widetilde \plC \to \widetilde{\mathbb R}_{\geq 0}$.
-These subdivisions induce logarithmic modifications
+These subdivisions induce logarithmic modifications:
 \[
@@
 Globally, Kim constructs a moduli space of logarithmic maps to expanded degenerations, which on logarithmic points, reduces to the above construction~\cite{KimLog}.
-Kim's space is identified with a subcategory of the Abramovich--Chen--Gross--Siebert space, and its dual minimal monoids are cones in a subdivision of the dual minimal cones of the unexpanded space, see~\cite[\S~2]{R19}.
+Kim's space is identified with a subcategory of the Abramovich--Chen--Gross--Siebert space (as stacks over logarithmic schemes), and its dual minimal monoids are cones in a subdivision of the dual minimal cones of the unexpanded space, see~\cite[\S~2]{R19}.
 
@@
 We refer to these latter components as \textbf{the higher levels}.
-Thus, we will say that a subcurve $D\subseteq C$ maps to \textbf{higher level} if the composite $C\to \mathbb P^N$ maps $D$ into $H\subset \mathbb P^N$.
-
-Let $D_F\subseteq C$ be the maximal genus one subcurve which is mapped to a higher level and contracted by the map $C\to \mathbb P^N[s]$.
+Thus, we will say that a subcurve $D\subseteq C$ \textbf{maps to higher level} if the composite $C\to \mathbb P^N$ maps $D$ into $H\subset \mathbb P^N$.
+
+Let $D_F\subseteq C$ be the maximal genus $1$ subcurve which is mapped to a higher level and contracted by the map $C\to \mathbb P^N[s]$.
 Let $\delta_F$ denote the distance from the core to the nearest component of $C \setminus D_F$.
-Similarly let $D_B\subseteq C$ be the maximal genus one subcurve that is contracted by the collapsed map to $\mathbb P^N$ and let $\delta_B$ be the associated radius.
+Similarly let $D_B\subseteq C$ be the maximal genus $1$ subcurve that is contracted by the collapsed map to $\mathbb P^N$, and let $\delta_B$ be the associated radius.
 This coincides with the radius of the underlying map to $\mathbb P^N$.
-Of course, $\delta_F\leq \delta_B$, so $(C,\delta_F)$ is centrally aligned.
+Of course, $\delta_F\leq \delta_B$, so $(C,\delta_F)$ is centrally aligned as well.
 
@@
 
-A Gorenstein elliptic singularity has a number of \textbf{branches}.
+%A Gorenstein elliptic singularity has a number of \textbf{branches}.
 Given a curve $\overline C$ of genus $1$ with such a singularity, define a branch of $\overline C$ to be an irreducible component containing a branch of the singularity.
@@
 its core.
+Recall that we name \emph{core} the minimal genus $1$ subcurve of a Gorenstein curve of arithmetic genus $1$, so the latter decomposes into the nodal union of the core and a (possibly empty) rational forest.
+If the curve contains an elliptic $m$-fold point, we say a map is non-constant on the core if at least one branch of the singularity is not contracted.
 The following condition identifies the locus of smoothable maps.
@@
 \begin{definition}
-The map $[C\to \mathbb P^N[s]\to \mathbb P^N]$ \textbf{factorises completely} if 
+The map $f\colon C\to \mathbb P^N[s]$ \textbf{factors completely} if 
 \begin{enumerate}
-\item the map $C\to \mathbb P^N[s]$ factors through $\overline C_F$ such that $F$ is non-constant on at least one branch of $\overline C_F$,
-\item the collapsed map to $\mathbb P^N$ factorises through $\overline C_B$ such that at least one branch of $\overline C_B$ has positive degree.
+\item $f$ factors through $\overline C_F$ and it is non-constant on its core,
+\item letting $f_B\colon C\to\PP^N$ denote the composite of $f$ with the collapsing map $\mathbb P^N[s]\to\mathbb P^N$, the map $f_B$ factors through $\overline C_B$ and it is non-constant on its core.
 \end{enumerate}
+\end{definition}
+
+\begin{rem}
  The factorisation conditions are understood to be satisfied when $C\to \mathbb P^N[s]$ (resp. $C\to \mathbb P^N$) does not contract a genus $1$ subcurve. 
-\end{definition}
-
-If $[C\to \mathbb P^N[s]\to \mathbb P^N]$ is a family of centrally aligned maps over $S$ that factorises completely, there is a moduli map $S\to \VZ_{1,n}(\mathbb P^N,d)$, to the principal component of the space of absolute maps.
+\end{rem}
+
 Let
 \begin{equation*} \VZ_{1,\alpha}(\mathbb P^N|H,d) \subseteq \widetilde\VZ_{1,\alpha}(\PP^N|H,d) \end{equation*}
-be the stack of maps from centrally aligned curves to expansions that factorise completely.
+be the stack of maps from centrally aligned curves to expansions that factor completely.
+
+If $[C\to \mathbb P^N[s]\to \mathbb P^N]$ is a family of centrally aligned maps over $S$ that factors completely, there is a moduli map $S\to \VZ_{1,n}(\mathbb P^N,d)$, to the principal component of the space of absolute maps.
 
@@
 We examine the geometry of the space of maps to $(\PP^N|H)$ by utilising the forgetful morphism
-$$
-\nu: \VZ_{1,\alpha}(\mathbb P^N|H,d)\to \VZ_{1,n}(\mathbb P^N,d),
-$$
+\[
+\nu\colon \VZ_{1,\alpha}(\mathbb P^N|H,d)\to \VZ_{1,n}(\mathbb P^N,d),
+\]
 which remembers only the stabilisation of the collapsed map.
-To see that the such a forgetful morphism exists, observe for a map $[C\to \mathbb P^N[s]\to \mathbb P^N]$, the stabilised composite map is certainly centrally aligned, and it satisfies the factorization property by construction.
+To see that such a forgetful morphism exists, we have already observed that, for a map $[C\to \mathbb P^N[s]\to \mathbb P^N]$, the stabilised composite map is certainly centrally aligned; moreover, it satisfies the factorisation condition by assumption.
+
 The moduli space $\VZ_{1,\alpha}(\mathbb P^N|H,d)$ is proper.
@@
 \ecd
-factorising completely. Let $f_B$ and $f$ be the maps from $C$ to the base and total space respectively. Examining the morphism $\nu$, we see that there is a map
+factoring completely. Let $f_B$ and $f$ be the maps from $C$ to the collapsed and expanded target respectively. Examining the morphism $\nu$, we see that there is a map
 \[
@@
 \]
-where the former is the space of logarithmic deformations of the curve and map to the base, as a factorised centrally aligned map.
-More precisely, consider a strict square zero extension of $S$ and a deformation of the map $(C,f_B)$ satisfying the factorisation property.
+where the former is the space of logarithmic deformations of the curve and map to the collapsed target, as a centrally aligned map satisfying simple factorisation.
+
+More precisely, consider a strict square-zero extension of $S$, and a deformation of the map $(C,f_B)$ satisfying the factorisation condition.
 Since the deformation is strict, there is a canonically induced deformation of the expansion $\mathbb P^N[s]$.
@@
 Consider the manner in which $H^1(\overline{C}_F,\mathcal O_{\overline{C}_F})$ functions as the obstruction group for the lifting.
-Near the minimal genus one subcurve $D_F$ of $C$, in order to lift the map from $\mathbb P^N$ to the expansion, we must provide a rational function on $D_F$ with poles bounded the divisor associated to the tropicalization, i.e.
+Near the minimal genus one subcurve $D_F$ of $C$, in order to lift the map from $\mathbb P^N$ to the expansion, we must provide a rational function on $D_F$ with poles bounded by the divisor associated to the tropicalization, i.e.
 if $\alpha$ is the piecewise linear function giving this tropical map, the lifting is described by a section of the associated bundle $\mathcal O_{C}(-\alpha)$.
@@
 Infinitesimally moving the point $x_i$ produces a nontrivial deformation of the line bundle $\mathcal O_{C}(-\alpha)$.
-The moduli space $\VZ_{1,n}(\mathbb P^N,d)$ is a logarithmically fibration over the universal Picard stack over the stack of $n$-pointed genus $1$ curves~\cite[Remark~4.5.3]{RSPW}.
+The moduli space $\VZ_{1,n}(\mathbb P^N,d)$ is a logarithmically smooth fibration over the universal Picard stack over the stack of centrally aligned $n$-pointed genus $1$ curves~\cite[Remark~4.5.3]{RSPW}.
 As a consequence, it is possible to find a logarithmic deformation of the map $(C,f_B)$ that induces the deformation of the line bundle that is given by infinitesimal motion.
@@
 Second, the target degeneration is now a toric degeneration, and the logarithmic tangent bundle is trivial.
+\textcolor{red}{luca's rewrite of log smoothness}
+
+The proof is analogous to that of \cite[Theorem 3.5.1]{RSPW2}. There is a forgetful morphism
+\[
+\nu\colon \VZ_{1,\alpha}(\mathbb P^N|H,d)\to \VZ_{1,n}(\mathbb P^N,d),
+\]
+remembering only the stabilisation of the composite $f_B\colon C\to\PP^N[s]\to\PP^N$.
+A priori, this is in $\overline{\pazocal M}_1(\PP^N,d)$, but in fact by assumption $(C,\delta_B)$ is centrally aligned, and $f_B$ factors through $\overline C_B$, as we have already remarked.
+
+The expanded target $\PP^N[s]$ is logarithmically \'etale over $\PP^N$ with the divisorial log structure associated to $H$, so it is equivalent to study the deformation theory of the unexpanded map to $(\PP^N,H)$.
+The logarithmic morphism $(\PP^N,H)\to \PP^N$ induces an exact sequence of log tangent bundles:
+\[0\to T_{\PP^N}(-\operatorname{log}H)\to T_{\PP^N}\to\OO_H(H)\to 0,\]
+relating the absolute and relative obstruction theories.
+This shows that $\nu$ can be obstructed only when a genus one subcurve is mapped to higher level in such a way that it is contracted by the collapsed map $f_B$.
+In this case, let $C_0$ denote the core, and let $E$ be the connected component of $f_B^{-1}(f_B(C_0))$ of arithmetic genus one.
+
+Let $f\colon C\to\PP^N[s]$ over the base $S$ be a possibly obstructed map to the expansion that factors completely, and let $S^\prime$ be a strict square-zero extension of the base.
+The deformation problem is local, so we may as well suppose that $\overline M_S^{\text{gp}}$ is a constant sheaf of monoids with stalk $\overline M_{S,s}^{\text{gp}}=:Q$, for a geometric point $s\in S$.
+Note that sections of $M_S$ such as $\delta_B$ and $\delta_F$ extend automatically due to strictness.
+Moreover, it is equivalent to deform $f$ or $f_F\colon\overline C_F\to\PP^N_S$, where $\overline C_F$ is given the trivial logarithmic structure around the elliptic singularity.
+
+The map $f_F\colon \overline C_F\to\PP^N[s]$ induces a tropical map $\alpha\colon\plC_F\to\RR_{\geq 0}\times\sigma_Q$, that we want to think of as a section $\alpha\in H^0(\overline C_F,\overline M_C^{\text{gp}})$.
+With notation as above, we obtain a trivialisation of the line bundle $\OO_{\overline C_F}(-\alpha)$ upon restriction to $E$.
+By \cite[Proposition 2.4.1]{RSPW}, the latter is isomorphic to $\OO_E(\sum\mu_i x_i)$, where $\mu_i$ is the slope/expansion factor of $\alpha$ along the edge $e_i$ of $\plC_F$, and $x_i$ the node corresponding to $e_i$ thought of as a smooth marking on $E$.
+
+The deformation problem for $f_F$ relative to $(C^\prime,\delta_B,f_B^\prime)$ reduces to the problem of extending $\alpha$ as a trivialisation of $\OO_E(\sum\mu_i x_i)$.
+This gives an interpretation of $\operatorname{Obs}(f/(C,\delta_B,f_B))$ as $H^1(\overline C_F,\OO)$.
+The latter is a vector space of dimension $1$.
+Associated to the forgetful morphism $\nu$ at the level of perfect obstruction theories, we find a map:
+\begin{equation}\label{eqn:def-obs}\operatorname{Def}(C,\delta_B,f_B)\to \operatorname{Obs}(f/(C,\delta_B,f_B)).\end{equation}
+The left-hand side contains in particular the space $\operatorname{Def}(E,\mathbf{x})=\operatorname{Ext}^1(\Omega_E(\mathbf x),\OO_E)$, since $E$ is contracted by $f_B$.
+Since by assumption at least one of the $\mu_i$ is non-zero, $\operatorname{Ext}^1(\Omega_E(\mathbf x),\OO_E)$ surjects onto $H^1(\overline C_F,\OO)$ by \cite[Corollary 3.5.3]{RSPW2}.
+Looking back at \eqref{eqn:def-obs}, we see that obstructions to deforming $f$ can be killed by an appropriate choice of lift $(C^\prime,\delta_B,f_B^\prime)$.
+
 \end{proof}
 
-The theorem guarantees that the singularities of the space of totally factorised maps to expansions is logarithmically smooth. One can say more in this case.
+The theorem guarantees that the singularities of the space of completely factoring maps to expansions is logarithmically smooth. One can say more in this case.
 
@@
 
-\subsection{Rubber variants}\label{subsection rubber} We require a ``rubber'' variant of the space of maps $
-\VZ_{1,\alpha}(\mathbb P^N|H,d)$, where the curve is contained in the higher levels.
-
-Let $\mathbb P$ denote the projective bundle $\mathbb P(\mathcal O(1)\oplus\mathcal O)$ on $\mathbb P^{N-1}$.
+\subsection{Rubber variants}\label{subsection rubber} We require a ``rubber'' variant of the space of maps $\VZ_{1,\alpha}(\mathbb P^N|H,d)$, where the curve is contained in the higher levels.
+
+Let $\mathbb P$ denote the projective bundle $\mathbb P(\mathcal O(1)\oplus\mathcal O)$ on $H\simeq\mathbb P^{N-1}$.
 Equip this space with the logarithmic structure coming from the $0$ and $\infty$ sections of the bundle.
@@
 \]
-which factorise completely, and where automorphisms are taken to cover the identity on the map to $\mathbb P^{N-1}$; two maps that differ by a $\mathbb G_{\operatorname{m}}$ translate in the fibre direction are considered equivalent.
-As previously, the map to the bundle and the map to the base $\mathbb P^{N-1}$ both factorise through possibly different singularities.
+which factor completely, and where automorphisms are taken to cover the identity on the map to $\mathbb P^{N-1}$; two maps that differ by a $\mathbb G_{\operatorname{m}}$ translate in the fibre direction are considered equivalent.
+As previously, the map to the bundle and the map to the base $\mathbb P^{N-1}$ both factor through possibly different singularities.
 
@@
 To prove this, it is convenient to work with the logarithmic multiplicative group and its torsors.
-Recall that the \textbf{logarithmic multiplicative group} $\mathbb G_{\mathrm{log}}$ is the functor on logarithmic schemes whose value on a logarithmic scheme $S$ is the group of global sections $H^0(S,M_S^{\mathrm{gp}})$; it is a proper group functor, and it contains $\Gm$ as a subfunctor.
+Recall that the \textbf{logarithmic multiplicative group} $\mathbb G_{\mathrm{log}}$ is the functor on logarithmic schemes whose value on a logarithmic scheme $S$ is the group of global sections $H^0(S,M_S^{\mathrm{gp}})$; it is a proper group functor, and it contains $\Gm$ as a subfunctor (from $\OO^\times_S\subseteq M_S^{\mathrm{gp}}$).
 This functor is representable only after a logarithmically \'etale cover, see for instance~\cite{MW17,RW19}.
@@
 \begin{proof}[Proof of Theorem \ref{thm rubber log smooth}]
-Consider the stack over logarithmic schemes $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}},d)$ of stable logarithmic maps that factorise completely.
+Consider the stack over logarithmic schemes $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}},d)$ of stable logarithmic maps that factor completely.
 Here, stability for the map coincides with stability for the projection to $\mathbb P^{N-1}$.
-The arguments in the previous section show that maps to $\mathbb P$ that factorise completely are unobstructed.
+The arguments in the previous section show that maps to $\mathbb P$ that factor completely are unobstructed.
 Since this space is a logarithmically \'etale cover of $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}},d)$, logarithmic smoothness of the latter follows.
@@
 It is representable after a logarithmically \'etale modification by a family of nodal curves.
-It follows that the space $\VZ^{\leftrightarrow}_{1,\alpha}(\mathbb P_{\mathrm{log}},d)$ of maps up to $\Glog$-translation that factorise completely is logarithmically smooth.
+It follows that the space $\VZ^{\leftrightarrow}_{1,\alpha}(\mathbb P_{\mathrm{log}},d)$ of maps up to $\Glog$-translation that factor completely is logarithmically smooth.
 
@@
 \begin{equation*} \VZ_{1,\alpha}(X|Y,\beta) \to \ol\Mcal^{\operatorname{log}}_{1,\alpha}(X|Y,\beta)\end{equation*}
-obtained by performing a logarithmic modification and passing to a closed substack where the factorization property is satisfied.
+obtained by performing a logarithmic modification and passing to a closed substack where the factorisation property is satisfied.
 This moduli space will typically be non-equidimensional, but we equip it with a virtual class as follows.
-The divisor $Y$ defines an embedding $X \hookrightarrow \PP^N$ with $Y=X\cap H$ for $H$ a hyperplane.
+The divisor $Y$ defines an embedding $X \hookrightarrow \PP^N$, with $Y=X\cap H$ for some hyperplane $H$.
 
@@
 
-Since $\VZ_{1,n}(\PP^N,d)$ is smooth and $\VZ_{1,n}(X,\beta)$ carries a natural virtual class \cite[Theorem 4.4.1]{RSPW}, the diagonal of $\VZ_{1,n}(\PP^N,d)$ defines a pullback~\cite[Appendix C]{BattistellaNabijou}, and therefore the virtual class on the space of maps to $(X,Y)$:
+Since $\VZ_{1,n}(\PP^N,d)$ is smooth and $\VZ_{1,n}(X,\beta)$ carries a natural virtual class \cite[Theorem 4.4.1]{RSPW}, the diagonal of $\VZ_{1,n}(\PP^N,d)$ defines a pullback~\cite[Appendix A]{BattistellaNabijou}, and therefore the virtual class on the space of maps to $(X,Y)$:
 \begin{equation*} \virt{\VZ_{1,\alpha}(X|Y,\beta)} := i_\Delta^! [\VZ_{1,\alpha}(\PP^N|H,d)]. \end{equation*}
-Note that this parallel to the virtual formalism in~\cite{Ga}.
+Note that this is parallel to the virtual formalism in~\cite{Ga}.
 As $\VZ_{1,\alpha}(X|Y,\beta)$ is equipped with evaluation maps and cotangent lines on the universal curve, we arrive at a definition of reduced Gromov--Witten invariants for the pair $(X,Y)$ by the standard mechanics.
@@
 
-The tropicalizations of logarithmic maps that factorise completely are combinatoriall constrained by a condition known as \textbf{well-spacedness}. The version we use here is essentially identical to~
+The tropicalizations of logarithmic maps that factor completely are combinatoriall constrained by a condition known as \textbf{well-spacedness}. The version we use here is essentially identical to~
 \cite{RSPW2}.
@@
 \begin{prop}\label{prop: well-spaced}
-Let $[C\to \mathbb P^N]$ be a logarithmic stable map from a centrally aligned curve to an expansion, that factorises completely. Then the tropicalization $\plC\to \mathbb R_{\geq 0}$ is well-spaced.
+Let $[C\to \mathbb P^N]$ be a logarithmic stable map from a centrally aligned curve to an expansion, that factors completely. Then the tropicalization $\plC\to \mathbb R_{\geq 0}$ is well-spaced.
 \end{prop}
@@
 \noindent Luca Battistella\\
-Max-Planck-Institut f\"ur Mathematik, Bonn \\
-\href{mailto:battistella@mpim-bonn.mpg.de}{battistella@mpim-bonn.mpg.de}\\
+Mathematisches Institut, Universit\"at Heidelberg \\
+\href{mailto:lbattistella@mathi.uni-heidelberg.de}{lbattistella@mathi.uni-heidelberg.de}\\
 
 \noindent Navid Nabijou \\
-School of Mathematics and Statistics, University of Glasgow \\
-\href{mailto:Navid.Nabijou@glasgow.ac.uk}{navid.nabijou@glasgow.ac.uk}\\
+Department of Pure Mathematics and Mathematical Statistics, University of Cambridge \\
+\href{mailto:nn333@cam.ac.uk}{nn333@cam.ac.uk}\\
 

### 2020-10-20 EllipticSingularitiesSplitting.tex
corrected figure off_we_go and added preliminary section on curve singularities

@@
 \usepackage{tikz,tikz-cd}
-\usetikzlibrary{decorations.pathmorphing,decorations.pathreplacing,patterns,arrows.meta,shapes.misc}
+\usetikzlibrary{ipe,decorations.pathmorphing,decorations.pathreplacing,patterns,arrows.meta,shapes.misc}
 
@@
 
+\DeclareRobustCommand{\plE}{\text{\reflectbox{$\exists$}}}
 \newcommand{\plC}{\scalebox{0.8}[1.3]{$\sqsubset$}}
@@
 
-\subsection*{Curves and tropical curves} A nodal curve $C$ over $\spec \mathbb C$ has an associated dual graph $\Gamma(C)$.
+\subsection{Curves and tropical curves} A nodal curve $C$ over $\spec \mathbb C$ has an associated dual graph $\Gamma(C)$.
 Given a toric monoid $P$, there is a logarithmic point $\spec \CC_P$ which may be thought of as remembering the information of the embedding of the torus-fixed closed point into the toric variety $\spec \mathbb C[P]$.
@@
 
-\subsection*{Maps and tropical maps}The discussion carries over to the setting of logarithmic maps.
+\subsection{Maps and tropical maps}The discussion carries over to the setting of logarithmic maps.
 Specifically, given a logarithmic curve $C$ and a logarithmic map to a smooth pair $(X,Y)$ over a logarithmic scheme $S$.
@@
 
+\subsection{Singularities and moduli of attachments} Isolated Gorenstein singularities of genus $1$ were classified by Smyth in \cite{SMY1}: for every fixed number of branches $m$, there is only one isomorphism type of curve germs with such characteristics.
+For $m=1,2$ we find the cusp ($A_2$) and tacnode ($A_3$) respectively; for $m\geq 3$ we find the union of $m$ general lines through the origin of $\Aaff^{m-1}$ - Smyth calls them \emph{elliptic $m$-fold points}.
+
+The problem of constructing an elliptic singularity from its pointed normalisation is more delicate; it was widely studied in van der Wyck's thesis \cite{vdW}.
+Recall that the seminormalisation $C^\text{sn}$ of a curve $C$ has the same underlying topological space, but its singularities consist of rational $m$-fold points only, i.e.
+they are locally isomorphic to the union of the axes in $\Aaff^m$.
+
+\begin{lemma}\label{lem:pushout}
+ The seminormalisation $\nu\colon C^\text{sn}\to C$ of an elliptic $m$-fold point is the collapse of a general tangent vector $v$ at the rational $m$-fold point.
+\end{lemma}
+
+This is equivalent to \cite[Lemma 2.2]{SMY1}, where he describes the seminormalisation of an elliptic singularity as the data of a hyperplane in the Zariski cotangent space, not containing the coordinate lines.
+We call \emph{moduli of attaching data} \cite[\S 2.2]{SMY2} (or \emph{crimping space}) the extra data needed to produce a singularity from its pointed normalisation.
+
+\begin{cor}
+ The moduli of attachments of an elliptic $m$-fold point is isomorphic to $\mathbb G_{\text{m}}^m$.
+\end{cor}
+One way to compactify it is by allowing \emph{sprouting} on the boundary, i.e.
+replacing a branch $R_i$ of the singularity with a strictly semistable component $\PP^1$ with the singularity at $0$ and the branch $R_i$ glued nodally at $\infty$.
+
+There are other ways to look at these data; we recall a construction from linear algebra.
+Let $V=\sum_{i=1}^mL_i$ be the presentation of a vector space as the direct sum of $m$ lines.
+It is equivalent to give compatible isomorphisms $\theta_{i,j}\colon L_i\simeq L_j$ and a general line $\ell$ in $V$ (or a hyperplane in the dual vector space $V^\vee$).
+Indeed, given a general line $\ell$, a vector $v\in\ell$ can be written as:
+\[v=a_1e_1+\ldots+a_me_m,\qquad a_i\neq 0\ \forall i=1,\ldots,m,\]
+for a fixed basis $\{e_i\in L_i\}$ of $V$. We can then define $\theta_{i,j}$ by:
+\[\theta_{i,j}(e_i)=\frac{a_j}{a_i}e_j;\]
+it is easy to see that it does not depend on any choice made. On the other hand, given the $\theta_{i,j}$, the line $\ell$ can be taken to be the graph of the morphism:
+\[(\theta_{1,2},\ldots,\theta_{1,m})\colon L_1\to L_2\oplus\ldots\oplus L_m.\]
+
+Lemma \ref{lem:pushout} provides a valuable characterisation of maps from an elliptic singularity $C$, that we are going to exploit in \S \ref{section reduced splitting}:
+\begin{cor}
+ A map $C\to X$ is the same as a map $C^\text{sn}\to X$ such that its differential sends $v$ to $0$.
+\end{cor}
+
+Line bundles on an elliptic $m$-fold point admit a similar description, see e.g. \cite[Lemma 7.5.12]{LiuQ}.
+\begin{lemma}\label{lem:PicE}
+ Let $C$ be a curve of arithmetic genus $1$ containing an elliptic $m$-fold point. Then $\operatorname{Pic}^0(C)\simeq\mathbb G_{\text{a}}$.
+\end{lemma}
+
 \subsection{Absolute geometry: reminders} Let $\mathfrak M_{1,n}$ be the logarithmic algebraic stack of $n$-pointed prestable curves of genus one.
@@
 Since the curve in question has genus $1$, there is a minimal genus $1$ subgraph -- either a vertex of genus $1$ or a cycle in the graph.
-We will refer to this as the \textbf{core}.
+We will refer to this as the \textbf{core}, denoted by $\plE$ below.
 
@@
 
-  \draw[gray] (0,0) node[left]{$\plC_0$} -- (1,.2) -- (2,0) -- (1,-.2) -- (0,0); %core
+  \draw[gray] (0,0) node[left]{$\plE$} -- (1,.2) -- (2,0) -- (1,-.2) -- (0,0); %core
 
@@
 
+\textcolor{red}{Up to a generalised root construction, $\VZ_{1,\alpha}(\mathbb P^N|H,d)$ is a smooth Deligne-Mumford stack.}
+
 \begin{proof}
@@
 
-\noindent The logarithmic smoothnessof Theorem~\ref{thm: log-smoothness} implies that $\VZ_{1,\alpha}(\mathbb P^N|H,d)$ is an orbifold toroidal embedding.
+\noindent The logarithmic smoothness of Theorem~\ref{thm: log-smoothness} implies that $\VZ_{1,\alpha}(\mathbb P^N|H,d)$ is an orbifold toroidal embedding.
 The irreducible components of its boundary stratify the space, as we now describe.
@@
 \begin{definition}
-Let $\plC$ be a tropical curve of genus one and let $\plC_0$ be its minimal subcurve of genus one.
+Let $\plC$ be a tropical curve of genus one and let $\plE$ be its minimal subcurve of genus one.
 A tropical map $F: \plC\to \mathbb R_{\geq 0}$ is said to be \textbf{well-spaced} if one of the following two conditions are satisfied:
 \begin{enumerate}
-    \item no open neighbourhood of $\plC_0$ is contracted to a point in $\mathbb R_{>0}$, or
-    \item if an open neighbourhood of $\plC_0$ is contracted and $t_1,\ldots,t_k$ are the flags whose vertex is mapped to $F(\plC_0)$, but along which $F$ has nonzero slope; then, the minimum of the distances from $\plC_0$ to $t_i$ occurs for at least two indices $i$.
+    \item no open neighbourhood of $\plE$ is contracted to a point in $\mathbb R_{>0}$, or
+    \item\label{pt:well-spaced2} if an open neighbourhood of $\plE$ is contracted and $t_1,\ldots,t_k$ are the flags whose vertex is mapped to $F(\plE)$, but along which $F$ has nonzero slope; then, the minimum of the distances from $\plE$ to a vertex supporting $t_i$ occurs for at least two indices $i$.
 \end{enumerate}
 \end{definition}
+
+\begin{figure}
+ \begin{tikzpicture}
+  %source curve
+  \draw[gray] (0,-1) to[out=150, in=210, edge node={node [left] {$\plE$}}] (0,1);
+  \draw[gray] (0,-1) to[out=30, in=-30] (0,1);
+  \draw (0,1) --node[right]{$\ell_1$} (0,2) --node[above]{$t_1$} (-4,2) (0,2) --node[above]{$t_2$} (4,2);
+  \draw[dotted] (-4.5,2) -- (-4,2) (4,2) -- (4.5,2);
+  \draw (0,-1) --node[right]{$\ell_2$} (0,-2) --node[above]{$t_3$} (-4,-2) (0,-2) --node[above]{$t_4$} (4,-2);
+  \draw[dotted] (-4.5,-2) -- (-4,-2) (4,-2) -- (4.5,-2);
+  \foreach \x in {(0,2), (0,-2)}
+  \draw[fill=black] \x circle (2pt);
+  \foreach \x in {(0,1), (0,-1)}
+  \draw[fill=gray] \x circle (2pt);
+  %arrow
+  \draw[->] (0,-2.5)--node[left]{$F$}(0,-3.5);
+  %target line
+  \draw (-4,-4)--(4,-4);
+  \draw[dotted] (-4.5,-4) -- (-4,-4) (4,-4) -- (4.5,-4);
+  \draw[fill=black] (0,-4) node[below]{$F(\plE)$} circle (2pt);
+
+ \end{tikzpicture}
+\caption{An example of well-spacedness: condition \eqref{pt:well-spaced2} becomes $\ell_1=\ell_2$.}
+\label{fig:exa_well-spaced}
+\end{figure}
+
+\begin{rem}
+Condition \eqref{pt:well-spaced2} is not relevant as far as rays of the tropical moduli space (i.e.
+divisors) are concerned, since there are always at least two parameters involved, namely $F(\plE)$ - or the distance from $F(\plE)$ to the origin of $\RR_{\geq 0}$ - and the distance from $\plE$ to the first flag of non-zero slope within $\plC$.
+As we mostly concentrate on divisors starting from \S \ref{Section Gathmann line bundle}, it will not play much of a role in the rest of the paper.
+\end{rem}
 
@@
 \begin{proof}
-The required result is essentially contained in~\cite[Section 4]{RSPW2}, so we explain how to deduce the requisite result from the one in loc.
+The required result is essentially contained in~\cite[Section 4]{RSPW2}, so we explain how to deduce it from the one in loc.
 cit.
@@
 Let $p$ be the point to which the genus one subcurve is contracted.
-Passing to an open neighbourhood of $p$, the map to the bundle is given by a rational function $f$ on an open curve $C^\circ$, determined by the the subgraph formed by $\plC_0$ and the flags $t_i$ described in the definition above.
-To describe the tropical map to $\mathbb R_{>0}$, we observe that $\plC_0$ is contracted to a fixed point $q\in\mathbb R_{>0}$.
+Passing to an open neighbourhood of $p$, the map to the bundle is given by a rational function $f$ on an open curve $C^\circ$, determined by the the subgraph formed by $\plE$ and the flags $t_i$ described in the definition above.
+To describe the tropical map to $\mathbb R_{>0}$, we observe that $\plE$ is contracted to a fixed point $q\in\mathbb R_{>0}$.
 The flags at $t_i$ correspond to nodes or markings of $C$.
@@
 
-\section{Degeneration of contact order}\label{Section Gathmann line bundle} Consider the moduli space $\VZ_{1,\alpha}(\PP^N|H,d)$ of relative maps that factorize completely.
+\section{Degeneration of contact order}\label{Section Gathmann line bundle} Consider the moduli space $\VZ_{1,\alpha}(\PP^N|H,d)$ of relative maps that factor completely.
+\begin{dfn}
  For each marking $x_k$, consider the locus $\Dcal_{1,\alpha,k}(\PP^N|H,d) \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$ where $x_k$ belongs to an \textbf{internal component} of the collapsed map, i.e.
 a component of the curve that is mapped into $H$.
+\end{dfn}
+\noindent Equivalently, for the expanded map, $x_k$ does not belong to a \emph{trivial bubble} component.
+
  In this section, we use the logarithmic structure on $\VZ_{1,\alpha}(\PP^N|H,d)$ to construct a line bundle $\Lcal_k$ and section $s_k$ which vanishes precisely along $\Dcal_{1,\alpha,k}(\PP^N|H,d)$.
 We use the correspondence with tropical geometry to identify $\cchern_1(\Lcal_k)$ in terms of tautological classes on $\VZ_{1,\alpha}(\PP^N|H,d)$, and to compute the vanishing order of $s_k$ along the components of $\Dcal_{1,\alpha,k}(\PP^N|H,d)$.
-Combined with the relative splitting formulas from in the next section, we obtain a recursion relation inside $\VZ_{1,\alpha}(\PP^N|H,d)$
+Combined with the relative splitting formulas from the next section, we obtain a recursion relation inside $\VZ_{1,\alpha}(\PP^N|H,d)$
 
@@
 In contrast with nodal singularities, the functions on an elliptic singularity are not simply collections of functions on the normalisation that agree at the gluing point.
-In order to compute integrals, it is necessary to give a tautological description of this additional condition that captures which functions (or maps) descend from the normalization to the singularity.
+Rather, the contraction map $C\to\overline C$ corresponds to a linear combination of tangent vectors at the pointed normalisation, whose kernel represents the functions descending to the elliptic singularity \cite[Lemma 2.2]{SMY1}.
+In order to compute integrals, it is necessary to give a tautological description of this additional condition.
+% that captures which functions (or maps) descend from the normalization to the singularity.
 
 We provide an explicit description of the terms appearing in the right-hand side of \eqref{equation recursion}.
-For each term, we provide a combinatorial formula for the vanishing order $\lambda_\Dcal$, and a recursive description of the stratum $\Dcal$.
+For each term, we provide a combinatorial formula for the vanishing order $\lambda_\Dcal$, and a recursive description of the stratum $\Dcal$
 in terms of fibre products of moduli spaces with smaller numerical data.
@@
     \end{minipage}
+
 \end{figure}
 
-\noindent The degrees of vertices, expansions factors, and remaining markings are distributed arbitrarily, subject to the following constraints:
+\noindent where black vertices represent rational components, white vertices represent genus one.
+The degrees of vertices, expansions factors, and remaining markings are distributed arbitrarily, subject to the following constraints:
 \begin{enumerate}
@@
 As a result, their combinatorial types exhibit very degenerate behaviour.
-Precisely, over the generic point of such a divisor, the target may expand multiple times, and the source tropical curve need not be bipartite with a single interior vertex.
+Precisely, over the generic point of such a divisor, the target may expand multiple times, and the source tropical curve need not be bipartite with a single interior vertex; see the left-hand side of Figure \ref{fig:off_we_go} for a concrete example.
 We stress once again that such degenerate contributions are at the heart of the reduced theory and cannot be removed.
-We begin with the following lemma:
+
+We begin with a series of lemmas describing the combinatorial types of rays associated to divisorial loci $\Dcal$ of type $\dag$ contributing nontrivially to the Gromov--Witten invariants.
 \begin{lemma} \label{lemma type C0 combinatorial types}
-Let $\Dcal$ be a locus of type $\dag$ with combinatorial type $\Delta$ which contributes nontrivially to the Gromov--Witten invariant.
  For every nonzero vertex $\diamond$ of the tropical target, the fibre of the tropical map over $\diamond$ contains exactly one stable vertex, which either is the core, or lies on the circle.
-Moreover, the maximal contact order at the core is $m>1$.
 \end{lemma}
 
-\begin{proof}
-Stability guarantees that at least one stable vertex lies over each vertex of the target.
-If there is more than one stable vertex, as in the proof of Lemma \ref{lem:combs}, the corresponding locus $\Fcal$ in the moduli space of unexpanded maps has high codimension.
+\begin{lemma}\label{lem:stable_vertices} All the vertices on the circle are stable (as opposed to semistable  vertices introduced by subdivision). \end{lemma}
+
+\begin{lemma}\label{lem:corecontact}
+ Among all the flags supported at the core, at least one must have expansion factor strictly greater than $1$.
+\end{lemma}
+
+\begin{proof}[Proof of Lemma \ref{lemma type C0 combinatorial types}]
+Stability of maps to an expansion guarantees that at least one stable vertex lies over each vertex of the target.
+If there is more than one stable vertex, then we can show as in the proof of Lemma \ref{lem:combs} that the corresponding locus $\Fcal$ in the moduli space of unexpanded maps has high codimension, i.e.
+the collapsing map has fibres of positive dimension.
 As both insertions and the factorisation property for the collapsed map to $\mathbb P^N$ are pulled back from the moduli space of maps without expansions, the contribution vanishes by the projection formula.
-
-For each vertex of the target there must always be at least one vertex in the preimage which lies on the circle.
-This is implied by the fact that the cone $\tau$ corresponding to $\Dcal$ is a ray.
-If the vertex on the circle is strictly semistable -- so that in particular the collapsed map $f_B$ is constant along the corresponding component -- it can be seen that the factorisation condition is unaffected by $\Gm$-scaling the coordinate corresponding to that vertex in the moduli space of attaching data, so the map $\Dcal\to\Ecal$ has generic fibre of positive dimension and the contribution vanishes.
-
-In particular, notice that vertices lying on the circle and tropically mapped to $0\in\mathbb R_{\geq0}$ all have the same contact order at the core, because by the previous paragraph we may assume that only strictly semistable vertices are encountered on the paths from these vertices to the core.
-For the same reason, this contact order $m$ is maximal among those of the edges adjacent to the core.
-
-Finally, in case the maximal contact order is $m=1$, the image tangent vectors must be linearly dependent, in which case we can deduce as above that factorisation will be satisfied independently of the choice of alignment.
 \end{proof}
+\begin{proof}[Proof of Lemma \ref{lem:stable_vertices}]
+Since we are looking at a one-parameter family of tropical maps, for every vertex of the target there must be at least one vertex above it which lies on the circle.
+If the vertex on the circle is strictly semistable -- so that in particular the collapsed map $f_B$ is constant along the corresponding component -- the factorisation condition for $f_B$ is unaffected by $\Gm$-scaling the coordinate corresponding to that vertex in the moduli space of attaching data \cite[\S 2.2]{SMY2}, so the map $\Dcal\to\Ecal$ has generic fibre of positive dimension and the contribution vanishes.
+\end{proof}
+\begin{proof}[Proof of Lemma \ref{lem:corecontact}]
+Consider the vertices that lie above $0\in\mathbb R_{\geq0}$ on the circle of radius $\delta$: the edges departing from them go directly (up to bubbling) to the core, since there cannot be stable vertices inside the open disc  when we have only one tropical parameter.
+In particular, all these edges have the same expansion factor $m$ (see again Figure \ref{fig:off_we_go}), which is maximal among those of the edges adjacent to the core.
+Indeed, all the edges from the core to the circle have the same length $\delta$, so the ones having maximal contact order are those that reach further from the core, and at least one must reach $0\in\mathbb R_{\geq0}$, for otherwise there would be an extra tropical parameter.
+
+Finally, in case the maximal contact order is $m=1$, in order for $f_B$ to factor, the image of the tangent vectors at the components lying on the circle must be linearly dependent in $T_{\PP^N,x}$, where $x$ denotes the image of the core under $f_B$.in which case we can deduce as above that factorisation will be satisfied independently of the choice of alignment.
+\end{proof}
+
 For the remainder of this section we use the following notation for the combinatorial type $\Delta$; we let $\sqC_0$ denotes the vertex of dual graph corresponding to the core, $\sqC_1,\ldots,\sqC_r$ the other stable vertices (genus zero and lying on the circle, by the previous lemma) and $q_1,\ldots,q_r$ the corresponding splitting nodes.
@@
 \begin{figure}
-\includegraphics[scale=.3]{off_we_go}
+%\includegraphics[scale=.3]{off_we_go}
+\begin{tikzpicture}[ipe import]
+  %\useasboundingbox (0, 0) rectangle (595, 842);
+  \draw
+    (64, 672)
+     -- (128, 688)
+     -- (64, 704)
+     -- (64, 704);
+  \draw
+    (128, 688)
+     -- (64, 736)
+     -- (64, 736);
+  \draw[red]
+    (128, 688) circle[radius=65.9697];
+  \draw
+    (128, 688)
+     -- (112, 752)
+     -- (64, 768)
+     -- (64, 768);
+  \draw
+    (112, 752)
+     -- (64, 784)
+     -- (64, 784);
+  \pic
+     at (64, 672) {ipe disk};
+  \pic
+     at (64, 704) {ipe disk};
+  \pic
+     at (64, 736) {ipe disk};
+  \pic
+     at (64, 768) {ipe disk};
+  \pic
+     at (64, 784) {ipe disk};
+  \pic
+     at (112, 752) {ipe disk};
+  \pic
+     at (75.2242, 727.582) {ipe cross};
+  \pic
+     at (112, 700) {ipe cross};
+  \pic
+     at (112, 692) {ipe cross};
+  \pic
+     at (112, 684) {ipe cross};
+  \pic
+     at (75.8121, 701.047) {ipe cross};
+  \pic
+     at (75.0704, 674.4388) {ipe cross};
+  \filldraw[fill=white]
+    (64, 608)
+     -- (208, 608)
+     -- (208, 608);
+  \pic
+     at (64, 608) {ipe disk};
+  \draw
+    (128, 688)
+     -- (208, 688)
+     -- (208, 688);
+  \pic
+     at (73.6978, 608) {ipe cross};
+  \pic
+     at (111.876, 608) {ipe cross};
+  \pic
+     at (127.674, 608) {ipe cross};
+  \pic[fill=white]
+     at (128, 688) {ipe fdisk};
+  \node[ipe node]
+     at (86.863, 690.301) {$m$};
+  \node[ipe node]
+     at (87.521, 671.212) {$m$};
+  \draw
+    (128, 688)
+     -- (91, 741.643);
+  \draw
+    (128, 688)
+     -- (160.586, 745.593)
+     -- (160.586, 745.593);
+  \pic
+     at (91, 741.643) {ipe disk};
+   \pic
+     at (91, 715.5) {ipe cross};
+     \pic
+     at (91, 697) {ipe cross};
+     \pic
+     at (91, 678.5) {ipe cross};
+     \pic
+     at (91, 608) {ipe cross};
+  \pic
+     at (160.486, 745.417) {ipe disk};
+     \pic
+     at (160.486, 688) {ipe cross};
+      \pic
+     at (160.486, 608) {ipe cross};
+
+  \draw[shift={(91.47, 741.051)}, xscale=0.95, yscale=0.6996]
+    (0, 0)
+     -- (-26.9879, 7.241)
+     -- (-26.9879, 7.241);
+  \draw
+    (160.486, 745.417)
+     -- (64.4824, 799.569);
+  \draw
+    (160.486, 745.417)
+     -- (208.637, 745.593);
+  \draw
+    (92.1286, 740.985)
+     -- (64.4824, 754.15);
+  \pic
+     at (64.4824, 746.909) {ipe disk};
+  \pic
+     at (64.4824, 798.91) {ipe disk};
+  \pic
+     at (64.4824, 753.492) {ipe disk};
+  \draw
+    (289.118, 672.0005)
+     -- (353.118, 688.0005)
+     -- (289.118, 704.0005)
+     -- (289.118, 704.0005);
+  \draw
+    (353.118, 688.0005)
+     -- (289.118, 736.0005)
+     -- (289.118, 736.0005);
+  \draw[red]
+    (353.118, 688.0005) circle[radius=65.9697];
+  \draw
+    (353.118, 688.0005)
+     -- (337.118, 752.0005)
+     -- (289.118, 768.0005)
+     -- (289.118, 768.0005);
+  \draw
+    (337.118, 752.0005)
+     -- (289.118, 784.0005)
+     -- (289.118, 784.0005);
+  \pic
+     at (289.118, 672.0005) {ipe disk};
+  \pic
+     at (289.118, 704.0005) {ipe disk};
+  \pic
+     at (289.118, 736.0005) {ipe disk};
+  \pic
+     at (289.118, 768.0005) {ipe disk};
+  \pic
+     at (289.118, 784.0005) {ipe disk};
+  \pic
+     at (337.118, 752.0005) {ipe disk};
+  \pic
+     at (300.3422, 727.5825) {ipe cross};
+  \pic
+     at (337.118, 700.0005) {ipe cross};
+  \pic
+     at (337.118, 692.0005) {ipe cross};
+  \pic
+     at (337.118, 684.0005) {ipe cross};
+  \pic
+     at (300.9301, 701.0475) {ipe cross};
+  \pic
+     at (300.1889, 674.4392) {ipe cross};
+  \filldraw[fill=white]
+    (289.118, 608.0005)
+     -- (433.118, 608.0005)
+     -- (433.118, 608.0005);
+  \pic
+     at (289.118, 608.0005) {ipe disk};
+  \draw
+    (353.118, 688.0005)
+     -- (433.118, 688.0005)
+     -- (433.118, 688.0005);
+  \pic
+     at (298.8158, 608.0205) {ipe cross};
+  \pic
+     at (336.994, 608.0207) {ipe cross};
+  \pic
+     at (352.792, 608.0209) {ipe cross};
+  \pic[fill=white]
+     at (353.118, 688.0005) {ipe fdisk};
+  \node[ipe node]
+     at (311.98, 690.301) {$m$};
+  \node[ipe node]
+     at (312.639, 671.212) {$m$};
+  \draw[shift={(353.118, 687.999)}, xscale=1.1287, yscale=1.1615]
+    (0, 0)
+     -- (-36.5297, 53.643);
+  \draw[shift={(353.119, 687.997)}, xscale=1.4269, yscale=1.3567]
+    (0, 0)
+     -- (32.586, 57.593)
+     -- (32.586, 57.593);
+  \pic
+     at (310, 751.5171) {ipe disk};
+  \pic
+     at (400.086, 767.1394) {ipe disk};
+
+           \pic
+     at (387, 688) {ipe cross};
+      \pic
+     at (387, 608) {ipe cross};
+
+  \draw[shift={(311.745, 750.197)}, xscale=0.8205, yscale=-0.5452]
+    (0, 0)
+     -- (-26.9879, 7.241)
+     -- (-26.9879, 7.241);
+  \draw[shift={(399.543, 767.54)}, xscale=1.1319, yscale=0.5704]
+    (0, 0)
+     -- (-96.0036, 54.152);
+  \draw[shift={(400.744, 767.146)}, xscale=0.6446, yscale=-1.3688]
+    (0, 0)
+     -- (48.151, 0.176);
+  \draw[shift={(311.717, 751.113)}, xscale=0.8, yscale=0.1453]
+    (0, 0)
+     -- (-27.6462, 13.165);
+  \pic
+     at (289.6004, 746.9095) {ipe disk};
+  \pic
+     at (289.6004, 798.9105) {ipe disk};
+  \pic
+     at (289.6004, 753.4925) {ipe disk};
+  \pic
+     at (387.02, 744.935) {ipe cross};
+  \pic
+     at (317.246, 742.961) {ipe cross};
+      \pic
+     at (317, 715.5) {ipe cross};
+     \pic
+     at (317, 697) {ipe cross};
+     \pic
+     at (317, 678.5) {ipe cross};
+     \pic
+     at (317, 608) {ipe cross};
+  \node[ipe node]
+     at (315.273, 748.884) {$\ell_{1}$};
+  \node[ipe node]
+     at (397.553, 752.175) {$\ell_{2}$};
+\end{tikzpicture}
 \caption{Moving vertices off the circle creates new tropical parameters.}\label{fig:off_we_go}

### 2020-10-20 EllipticSingularitiesSplitting.tex
split off a section about combs of multidegree (1,1,...,1)

@@
 
-\subsection{Singularities and moduli of attachments} Isolated Gorenstein singularities of genus $1$ were classified by Smyth in \cite{SMY1}: for every fixed number of branches $m$, there is only one isomorphism type of curve germs with such characteristics.
+\subsection{Singularities and moduli of attachments}\label{S:ellsing} Isolated Gorenstein singularities of genus $1$ were classified by Smyth in \cite{SMY1}: for every fixed number of branches $m$, there is only one isomorphism type of curve germs with such characteristics.
 For $m=1,2$ we find the cusp ($A_2$) and tacnode ($A_3$) respectively; for $m\geq 3$ we find the union of $m$ general lines through the origin of $\Aaff^{m-1}$ - Smyth calls them \emph{elliptic $m$-fold points}.
@@
 
-\textcolor{red}{Up to a generalised root construction, $\VZ_{1,\alpha}(\mathbb P^N|H,d)$ is a smooth Deligne-Mumford stack.}
+\textcolor{red}{Luca's rewrite of the Corollary: Up to a generalised root construction, $\VZ_{1,\alpha}(\mathbb P^N|H,d)$ is a smooth Deligne-Mumford stack.}
 
@@
 In contrast with nodal singularities, the functions on an elliptic singularity are not simply collections of functions on the normalisation that agree at the gluing point.
-Rather, the contraction map $C\to\overline C$ corresponds to a linear combination of tangent vectors at the pointed normalisation, whose kernel represents the functions descending to the elliptic singularity \cite[Lemma 2.2]{SMY1}.
+Rather, the contraction map $C\to\overline C$ corresponds to a linear combination of tangent vectors at the pointed normalisation, whose kernel represents the functions descending to the elliptic singularity - see \S \ref{S:ellsing}.
 In order to compute integrals, it is necessary to give a tautological description of this additional condition.
@@
 
-\begin{lemma}\label{lem:corecontact}
- Among all the flags supported at the core, at least one must have expansion factor strictly greater than $1$.
-\end{lemma}
+%\begin{lemma}\label{lem:corecontact}
+% Among all the flags supported at the core, at least one must have expansion factor strictly greater than $1$.
+%\end{lemma}
 
@@
 \end{proof}
+\begin{comment}
+
 \begin{proof}[Proof of Lemma \ref{lem:corecontact}]
@@
 For the remainder of this section we use the following notation for the combinatorial type $\Delta$; we let $\sqC_0$ denotes the vertex of dual graph corresponding to the core, $\sqC_1,\ldots,\sqC_r$ the other stable vertices (genus zero and lying on the circle, by the previous lemma) and $q_1,\ldots,q_r$ the corresponding splitting nodes.
+
+\end{comment}
+\subsubsection{Lines}
+We begin with a description of the boundary divisor corresponding to a comb whose teeth all have degree $1$.
+This is at the same time more concrete and peculiar, since the teeth are generically transverse (not just dimensionally) to the hyperplane $H$.
+For simplicity, we assume that the contact order is $(d)$, concentrated at a marking $x_1$ supported on the elliptic curve $E$ contracted to $H$.
+The combinatorial type looks as in Figure \ref{fig:comb111}.
+
+\begin{figure}
+ \begin{tikzpicture}
+ \tikzset{cross/.style={cross out, draw=black, fill=none, minimum size=2*(#1-\pgflinewidth), inner sep=0pt, outer sep=0pt}, cross/.default={3pt}}
+  \foreach \x in {(0,2),(0,1),(0,-1),(0,-2)}
+  \draw[fill=black] \x circle (2pt);
+  \foreach \x in {(0,2),(0,1),(0,-1)}
+  \draw \x --node[below]{\color{blue} $1$} (4,0);
+  \draw (0,0) node{$\ldots$};
+  \draw (4,0) --node[below]{\color{blue} $d$} (8,0);
+  \draw[->] (0,-2)--(8,-2);
+  \draw[fill=white] (4,0) circle (2pt);
+  \draw (4,-2) node[cross]{};
+  \draw [red] plot [smooth cycle] coordinates {(0,2) (0,1) (0,-1) (2,-1.5) (7,0) (2,2.5)};
+ \end{tikzpicture}
+ \caption{The combinatorial type of a comb with degree $1$ teeth.}
+ \label{fig:comb111}
+\end{figure}
+
+Start from the moduli space of logarithmic maps. There is a finite splitting morphism:
+\[\Ecal \to \left(\M{0}{(1)}{\PP^N}{1}^{\times N}\times_{H^N}H\right)\times \Mcal^{\leftrightarrow}_{1,(-1,\ldots,-1,d)},\]
+where the latter is the moduli space of genus one curves satisfying the \emph{double ramification} condition.
+As for $\widetilde{\Dcal}$, the latter should be replaced by $\VZ^{\leftrightarrow}_{1,(-1,\ldots,-1,d)}$, see \S \ref{subsection rubber}.
+
+The left-hand factor can be described very concretely as the choice of a point $p$ of $H$, and $d$ lines through it.
+A very important observation is that, at least generically, the vertices lying on the circle of radius $\delta$ over $0\in\mathbb R_{\geq 0}$ are automatically aligned.
+Indeed, if $R_i$ denotes the $i$-th tail of the curve, glued to $E$ at the node $q_i$, then the stable maps provide us with identifications:
+\[\operatorname{d}\! f_{i,q_i}\colon T_{R_i,q_i}\simeq N_{H/\PP^N,p}\]
+that can be combined into the $\theta_{i,j}$ of \S \ref{S:ellsing}. So, without further ado, we may produce a contraction $C\to\overline C$ to an elliptic $d$-fold point.
+
+Assume for example that $d\leq N$.
+Then, for the absolute factorisation to hold, the $d$ lines $f_i(R_i)$ have better to span a $(d-1)$-dimensional subspace of $T_{\PP^N,p}$.
+The dimension of the moduli space $\widetilde\Dcal$ is then $dN+d-2$.
+Without loss of generality, we may assume that $H$ is the hyperplane $\{z_0=0\}$, $p$ is the point $[0:\ldots:0:1]$, and that the $d$ lines span the subspace $\{z_{d-1}=\ldots=z_{N-1}=0\}$.
+The sections $z_i,\ i=d-1,\ldots,N,$ vanish identically near $E$, so they descend automatically to the singularity.
+The section $z_0$ does so by the construction of $\overline C$.
+Finally, the sections $z_i,\ i=1,\ldots,d-2,$ impose independent conditions to descend to $\overline C$.
+All in all, we find that $\Dcal$ has dimension $dN$, making it into a divisor in $\VZ_{1,(d)}(\PP^N|H,d)$.
+
+We can express the factorisation condition tautologically by combining the isomorphisms $\theta_{i,j}$ above, and the differential of $f$.
+It correponds to the vanishing of the following vector bundle map:
+\[T_{R_1,q_1}\xrightarrow{(1,\theta_{1,2}\ldots,\theta_{1,d})}\bigoplus_{i=1}^d T_{R_i,q_i}\xrightarrow{\sum\circ\operatorname{d}\!f=\operatorname{d}\!z_1+\ldots\operatorname{d}\!z_{d-2}}N_{H\cap\PP^{d-1}/\PP^{d-1},p}.\]
+
+In general, we shall see that the automatic alignment only involves the components corresponding to vertices on the circle that lie over $0$.
+The internal components on the circle must be aligned by hand.
+This means that $\widetilde\Dcal$ is a compactified torus bundle over $\Ecal$, see \ref{S:ellsing}.
+On the other hand, for higher contact order, the vector bundle map $\sum\circ\operatorname{d}\!f$ to $T_{\PP^N,p}$ factors naturally through $T_{H,p}$.
 
@@
 Let $\sigma \in \Sigma^{\Kim}$ be the minimal cone containing the image of $\tau$.
-The dimension of this cone could be large -- its dimension is equal to the the number of levels of the target expansion in the type $\Delta$.
+The dimension of this cone could be large (see again the left-hand side of Figure \ref{fig:off_we_go}) -- its dimension is equal to the the number of levels of the target expansion in the type $\Delta$.
 The cone $\sigma$ determines a stratum $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$, and the morphism above restricts to
@@
 The vertices over $0$ determine moduli spaces of ordinary relative stable maps, while the higher level vertices determine maps to rubber.
-Then $\Ecal$ admits a finite and surjective splitting morphism
+Then $\Ecal$ admits a finite splitting morphism
 \begin{equation}\label{IIIa fibre product} \Ecal \xrightarrow{\rho} \left( \prod_{v \in \Lambda_0} \ol\Mcal_{\Gamma_v}(\PP^N|H) \times \prod_{v \in \Lambda_{>0}} \ol\Mcal^{\leftrightarrow}_{\Gamma_v}(\mathbb{P}|H_0+H_\infty) \right) \times_{H^{2\epsilon}} H^{\epsilon} \end{equation}
@@
 \noindent
-{\bf Exportation to the ordinary geometry.}  Observe that we have a virtual divisor $\widetilde\Dcal \subseteq \widetilde\VZ_{1,\alpha}(\PP^N|H,d)$ such that 
+{\bf Exportation to the reduced geometry.}  Observe that we have a virtual divisor $\widetilde\Dcal \subseteq \widetilde\VZ_{1,\alpha}(\PP^N|H,d)$ such that 
 \[

### 2020-10-20 EllipticSingularitiesSplitting.tex
rewritten proof of lem:generic_proj_bundle

@@
 
-\subsubsection{Possible combinatorial types} A boundary divisor $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ is said to have \textbf{type $\dag$} if the core is assigned degree zero by the combinatorial type.
+\subsubsection{Possible combinatorial types}\label{S:combinatorialdescription} A boundary divisor $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ is said to have \textbf{type $\dag$} if the core is assigned degree zero by the combinatorial type.
 Divisors of this type occur as principal components in compactified torus bundles over strata in the space of relative maps.
@@
 Let $\sigma \in \Sigma^{\Kim}$ be the minimal cone containing the image of $\tau$.
-The dimension of this cone could be large (see again the left-hand side of Figure \ref{fig:off_we_go}) -- its dimension is equal to the the number of levels of the target expansion in the type $\Delta$.
+The dimension of this cone could be large (see again the left-hand side of Figure \ref{fig:off_we_go}) -- its dimension is equal to the number of levels of the target expansion in the type $\Delta$.
 The cone $\sigma$ determines a stratum $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$, and the morphism above restricts to
@@
 {\bf Splitting in the ordinary geometry.} The locus $\Ecal$ has the following description.
-Let $\Lambda_0$ for the collection of stable vertices of the combinatorial type which are mapped to $0\in \RR_{\geq 0}$, and $\Lambda_{>0}$ for the stable vertices which are mapped to $\RR_{>0}$.
-Each vertex $v$ has associated discrete data $\Gamma_v$.
+Let $\Lambda_0$ denote the collection of stable vertices of the combinatorial type which are mapped to $0\in \RR_{\geq 0}$, and use $\Lambda_{>0}$ for the stable vertices which are mapped to $\RR_{>0}$.
+Each vertex $v$ has associated discrete data $\Gamma_v$ (genus, degree, contact order).
 The vertices over $0$ determine moduli spaces of ordinary relative stable maps, while the higher level vertices determine maps to rubber.
@@
 {\bf Logarithmic structures on strata.} Let $W\subseteq X$ be an irreducible stratum in a toroidal embedding $X$.
-The stratum $W$ is itself toroidal, or equivalently, when equipped with the divisorial logarithmic structure coming from intersecting with the toroidal boundary divisors of $X$, the resulting structure makes $W$ logarithmically smooth.
+The stratum $W$ is itself toroidal, or, equivalently, when equipped with the divisorial logarithmic structure coming from intersecting with the toroidal boundary of $X$, the resulting structure makes $W$ logarithmically smooth.
 Note that this differs from the logarithmic structure pulled back from $X$ along the inclusion of $W$ into $X$.
@@
 In identical fashion to the paragraph above, this stack $\mathcal A_W$ possesses a logarithmic structure by restricting the divisors on $\mathcal A_X$ and taking the induced logarithmic structure.
-This equips a logarithmic stratum $W\hookrightarrow X$ with a logarithmic structure by pullback, mirroring the construction for toroidal embeddings above.
+This equips a logarithmic stratum $W\hookrightarrow X$ with a logarithmic structure by pullback from the Artin fan, mirroring the construction for toroidal embeddings above.
 
@@
 
+\begin{figure}
+ \begin{tikzpicture}
+ \tikzset{cross/.style={cross out, draw=black, fill=none, minimum size=2*(#1-\pgflinewidth), inner sep=0pt, outer sep=0pt}, cross/.default={3pt}}
+
+ %combinatorial type
+  \draw[fill=black] (1,1) circle (2 pt);
+  \draw[fill=black] (0,-1) circle (2 pt);
+  \draw (1,1)--node[below,blue]{$m_1$} (2,0) (0,-1)--node[below,blue]{$m_1$} (2,0) (2,0)--node[below,blue]{$m_1+m_2$} (4,0);
+  \draw (1,-.5) node[cross]{};
+  \draw[fill=white] (2,0) circle (2 pt);
+
+  \draw[->] (2,-1) -- (2,-1.8);
+
+  \draw[fill=black] (0,-2) circle (2 pt);
+  \draw[->] (0,-2)--node[below=.5cm]{$\Delta_\tau$} (4,-2);
+   \draw (1,-2) node[cross]{};
+   \draw (2,-2) node[cross]{};
+
+  \draw [red] plot [smooth cycle] coordinates {(1,1) (0,-1) (3.5,0)};
+
+ %subdivision 
+  \draw[->] (6,-2) --node[below=.5cm]{$\sigma$} (10,-2) node[right]{$\ell_1$};
+  \draw[->] (6,-2) -- (6,2) node[above]{$\ell_2$};
+  \draw[gray] (6,-2) -- (10,1) node[right]{$(m_2,m_1)=\operatorname{Im}(\tau)$};
+ \end{tikzpicture}
+\caption{From $\Ecal$ to $\widetilde{\Ecal}$. Typical subdivision of a two-dimensional cone $\sigma$ along the image of a ray $\tau$.}
+\label{fig:Etilde}
+\end{figure}
+
 The combinatorics of the flattening can be described explicitly. Consider the map on tropicalizations
@@
 The polyhedral criterion for equidimensionality is that every cone of the source maps surjectively onto a cone of the target.
-There is a universal logarithmic modification $\widetilde\Ecal \to \Ecal$ such that $\widetilde\Dcal \to \widetilde\Ecal$ is flat, constructed by taking the minimal subdivision of $\Ecal^{\operatorname{trop}}$ such that cones map surjectively to cones.
+There is a universal logarithmic modification $\widetilde\Ecal \to \Ecal$ such that $\widetilde\Dcal \to \widetilde\Ecal$ is flat, constructed by taking the minimal subdivision of $\Ecal^{\operatorname{trop}}$ such that cones map surjectively to cones (see Figure \ref{fig:Etilde}).
 
 This subdivision is best described using the formalism of extended tropicalizations \cite{Thuillier,ACP}.
-The subdividing cones are obtained from cones in the star of $\tau$ under the limit $e_1=\cdots=e_r=\infty$.
+The subdividing cones are obtained from cones in the star of $\tau$ under the limit $e_1=\cdots=e_r=\infty$\marginpar{Was $r$ called $\epsilon$ before?}.
 The cones in the star of $\tau$ are given by (in)equalities relating distances of pairs of vertices, and there are three cases to consider:
@@
 
-By construction, we have a map $\widetilde\Dcal \to \widetilde\Ecal$ which is a compactification of a torus bundle over $\widetilde\Ecal$.
+%By construction, we have a map $\widetilde\Dcal \to \widetilde\Ecal$ which is a compactification of a torus bundle over $\widetilde\Ecal$.
 The strata of $\widetilde\Dcal$ can be read off from its tropicalization, and in particular we have the information of how (polynomials in) the classes of boundary strata push forward to $\widetilde\Ecal$.
@@
 \begin{lemma}\label{lem:generic_proj_bundle}
-Generically over $\Ecal$, the morphism $\widetilde \Dcal\to\widetilde\Ecal$ is the projectivisation of a tautological vector bundle.
+Generically over $\Ecal$, the morphism $\widetilde \Dcal\to\Ecal$ is the projectivisation of a tautological vector bundle.
 \end{lemma}
@@
 Let us assume that the curve does not degenerate, so that the dual graph is as prescribed by $\Delta$.
-In particular there are components $\sqC_1,\ldots,\sqC_r$ generically lying on the circle of radius $\delta$.
+In particular there are vertices $\plC_1,\ldots,\plC_r$ generically lying on the circle of radius $\delta$.
 The moduli space of attaching data for the elliptic singularity is the complement of the coordinate hyperplanes in
-$$\PP\left(\bigoplus_{i=1}^rT_{q_i}C_i\right),$$
-see~\cite[Section~2.2]{SMY2}.
-A point in this space parameterizes a particular map from the rational multiple point singularity to the elliptic multiple point singularity.
-On the boundary, the circle is allowed to miss some of the $\sqC_i$ -- but not all of them!
---  cutting the edge between them and the core (correspondingly, there is a destabilisation of the curve, and an elliptic singularity containing strictly semistable branches).
-Tropically, pushing some of the vertices off the circle creates new finite-length edges with coordinates $\ell_i\in\RR_{\geq_0}$ (see Figure \ref{fig:off_we_go}).
-Since not all of them can be strictly positive, this represents the fan of a projective space.
-
-A slight modification of the argument above is required to account for the fact that all vertices that lie on the circle and are mapped to $0\in\mathbb R_{\geq0}$ by the tropical map are generically aligned on $\Ecal$: indeed, by Lemma \ref{lemma type C0 combinatorial types}, they all have the same contact order $m$, therefore their $T_{q_i}C_i^{\otimes m}$ can be identified via the target tangent line on the fibre product \eqref{IIIa fibre product}, and, after saturation, the $T_{q_i}C_i$ themselves are canonically isomorphic on $\Ecal$.
-Thus, only one summand should be taken to represent all of them in the projective bundle above.
+\begin{equation}\label{eqn:projectivebundle}
+ \PP\left(\bigoplus_{i=1}^rT_{q_i}C_i\right);
+\end{equation}
+
+this can also be thought of as parametrising compatible identifications $\theta_{i,j}\colon T_{C_i,q_i}\simeq T_{C_j,q_j}$, see \S \ref{S:ellsing}.
+A point in this space determines in particular a map from the rational $r$-fold singularity to the elliptic $r$-fold singularity.
+That this coincides with the fibre of the aligned moduli space of curves over the ordinary one is well explained in \cite[\S 3.4]{RSPW}.
+Along the boundary, some of the $\plC_i$ -- but not all of them!
+--  are allowed to move off from the circle, so that the latter cuts the edge between them and the core.
+Correspondingly, there is a destabilisation of the curve (semistable components are represented by crosses in our figures), and we obtain an elliptic singularity containing strictly semistable branches (\emph{sprouting}).
+This was already identified by Smyth as a compactification of the moduli space of attaching data carrying a Gorenstein universal curve \cite[\S 2.2]{SMY2}.
+
+Tropically, pushing some of the $\plC_i$ off the circle creates new finite-length edges with coordinates $\ell_i\in\RR_{\geq_0}$ (see the right-hand side of Figure \ref{fig:off_we_go}).
+Since not all of them can be strictly positive, the resulting fan is that of a projective space.
+This gives us a fibrewise description of $\widetilde\Dcal\to\Ecal$ over the generic point.
+
+A slight modification of the argument above is required to account for the fact that all vertices that lie on the circle and are mapped to $0\in\mathbb R_{\geq0}$ by the tropical map are generically aligned on $\Ecal$.
+Indeed, by the combinatorial description of rays in \S \ref{S:combinatorialdescription}, there are no stable vertices inside the circle, so all the edges going from a vertex of $\Lambda_0$ to the core have the same expansion factor $m$ (maximal among the contact orders at the core).
+Therefore, for all $i$ such that $\plC_i\in\Lambda_0$, the $T_{q_i}C_i^{\otimes m}$ can be identified to the target tangent line on the fibre product \eqref{IIIa fibre product}, and, after saturation, the $T_{q_i}C_i$ themselves are canonically isomorphic on $\Ecal$.
+Thus, only one summand should be taken to represent all of them in the projective bundle \eqref{eqn:projectivebundle}.
 \end{proof}
@@
      at (127.674, 608) {ipe cross};
-  \pic[fill=white]
-     at (128, 688) {ipe fdisk};
+
   \node[ipe node]
@@
      at (64.4824, 753.492) {ipe disk};
+     \pic[fill=white]
+     at (128, 688) {ipe fdisk};
   \draw
@@
      at (352.792, 608.0209) {ipe cross};
-  \pic[fill=white]
-     at (353.118, 688.0005) {ipe fdisk};
+
   \node[ipe node]
@@
     (0, 0)
-     -- (32.586, 57.593)
      -- (32.586, 57.593);
@@
 
-  \draw[shift={(311.745, 750.197)}, xscale=0.8205, yscale=-0.5452]
+  \draw[shift={(311.745, 750.197)}, xscale=0.8205, yscale=-0.5452,]
     (0, 0)
-     -- (-26.9879, 7.241)
      -- (-26.9879, 7.241);
@@
      at (397.553, 752.175) {$\ell_{2}$};
+     %thickenings of l1 and l2
+  \draw[line width=.5mm] (317,743.5)--(310,751.5);
+  \draw[line width=.5mm] (387,744)--(400,767);
+
+  \pic[fill=white]
+     at (353.118, 688.0005) {ipe fdisk};
 \end{tikzpicture}

### 2020-10-20 EllipticSingularitiesSplitting.tex
lemma fibre of O(delta)

@@
 Lemma \ref{lem:pushout} provides a valuable characterisation of maps from an elliptic singularity $C$, that we are going to exploit in \S \ref{section reduced splitting}:
-\begin{cor}
+\begin{cor}\label{cor:maps_from_elliptic_sing}
  A map $C\to X$ is the same as a map $C^\text{sn}\to X$ such that its differential sends $v$ to $0$.
@@
 \end{comment}
-\subsubsection{Lines}
+\subsubsection{Lines}\label{S:lines}
 We begin with a description of the boundary divisor corresponding to a comb whose teeth all have degree $1$.
@@
 The toric geometry dictionary gives rise to an associated Cartier divisor.
-Alternatively, for any logarithmic stack $X$, the natural coboundary map induced by $$0\to \mathcal O_X^\star\to M_X\to \overline M_X\to 0$$ associates a $\mathcal O_X^\star$-torsor to a global section of the characteristic sheaf.
+Alternatively\marginpar{worth moving to the preliminary section?}, for any logarithmic stack $X$, the natural coboundary map induced by $$0\to \mathcal O_X^\star\to M_X^\text{gp}\to \overline M_X^\text{gp}\to 0$$ associates a $\mathcal O_X^\star$-torsor to a global section of the characteristic sheaf.
 
@@
 The fibre of $\OO(\delta)$ over a moduli point is naturally isomorphic to
-\begin{equation*} T_{p}C^\prime \otimes T C_0\end{equation*}
-where $C^\prime$ is any component of $C$ which lies on the circle, $p$ is the adjacent node which points towards the core, and $T C_0$ is the universal tangent line bundle on the moduli space for $\sqC_0$.
+\begin{equation*} T_{p}C^\prime \otimes \mathbb T \end{equation*}
+where $C^\prime$ is any component of $C$ which lies on the circle of radius $\delta$, $p$ is the node separating it from the core, and $\mathbb T$ is the universal tangent line bundle on the moduli space for $\sqC_0$.
 \end{lemma}
+
+The moduli space of radially aligned curves of genus one $\VZ_{1,n}^\text{rad}$ coincides with the Vakil-Zinger blow-up of  $\overline \Mcal_{1,n}$ \cite[\S 2.3]{VZ}.
+In particular, up to twisting by exceptional divisors, the tangent line bundles at two marking $\widetilde{\mathbb T}_i$ and $\widetilde{\mathbb T}_j$ are identified (via the dual Hodge bundle $\mathbb E^\vee$), extending the identification on the smooth locus provided by regarding the elliptic curve as an algebraic group.
+The pullback of this to $\VZ^\leftrightarrow_{\Gamma_{\sqsubset_0}}$ is what we mean by  the universal tangent line bundle $\mathbb T$.
 
@@
 Then $\OO(\delta)$ is equal to the tensor product of tangent line bundles along the path of edges connecting $C^\prime$ to the core.
-However, this tensor product of line bundles is telescoping: any vertex which appears in the middle of the path will have an incoming and outgoing node, and since the vertex corresponds to a smooth rational curve these tangent spaces are naturally dual to each other~\cite[\S 2.2]{VZ}.
+However, this tensor product of line bundles is telescoping: any vertex which appears in the middle of the path will have an incoming and outgoing node (and possibly other nodes that are irrelevant for this product), and since the vertex corresponds to a smooth rational curve these tangent spaces are naturally dual to each other~\cite[\S 2.2]{VZ}.
 Thus these factors cancel, and the result follows.
@@
 \end{proof}
-The content of Lemma \ref{lemma fibres of Odelta} is that the choice of point in the fibre of $\widetilde\Dcal \to \widetilde\Ecal$ provides a natural identification between the inward-pointing tangent spaces on the circle.
-This identification amounts to a specific linear dependence relation between the tangent vectors, which gives a point in the moduli space of attaching data for the corresponding elliptic singularity \cite[\S 2.2]{SMY2}.
-We may therefore express the factorisation condition in terms of the following natural morphism of vector bundles on $\widetilde\Dcal$:
-\begin{equation*} \Sigma \operatorname{d}\!f \colon \OO(\delta)\otimes TC_0^\vee \to \ev_q^\st T H. \end{equation*}
-Here $\Sigma \operatorname{d}\!f$ is defined by summing the images of the tangent vectors at the inward-pointing nodes on the circle, using the natural identification of each of these tangent spaces with $\OO(\delta)\otimes TC_0^\vee$ established above.
-By Lemma \ref{lemma type C0 combinatorial types} we have that it takes values in $TH$, rather than $T\PP^N$.
+The content of Lemma \ref{lem:generic_proj_bundle} is that the choice of a point in the fibre of $\widetilde\Dcal \to \Ecal$ provides a natural identification between the inward-pointing tangent lines on the circle.
+According to Lemma \ref{lemma fibres of Odelta}, they can further be identified with the line bundle $\OO(\delta)\otimes \mathbb T^\vee$ on $\widetilde\Dcal$.
+%This identification amounts to a specific linear dependence relation between the tangent vectors, which gives a point in the moduli space of attaching data for the corresponding elliptic singularity \cite[\S 2.2]{SMY2}.
+After Corollary \ref{cor:maps_from_elliptic_sing}, we can therefore express the factorisation condition in terms of degeneracy of the following natural morphism of vector bundles on $\widetilde\Dcal$:
+\begin{equation*} \Sigma \operatorname{d}\!f \colon \OO(\delta)\otimes \mathbb T^\vee \to \ev_q^\st T H. \end{equation*}
+Here $\Sigma \operatorname{d}\!f$ is defined by summing the images of the tangent vectors at the inward-pointing nodes on the circle, using the natural identification of each of these tangent spaces with $\OO(\delta)\otimes \mathbb T^\vee$ established above.
+Apart from the case dealt with in \S \ref{S:lines}, the composite:
+\[\operatorname{pr}\circ\Sigma \operatorname{d}\!f \colon \OO(\delta)\otimes \mathbb T^\vee \to \ev_q^\st T \PP^N\to \ev_q^* N_{H/\PP^N}\]
+ vanishes, because the contact order of the exterior components with $H$ is strictly higher than $1$. So, $\Sigma \operatorname{d}\!f$ takes values in $TH$, rather than $T\PP^N$.
+
  This gives a section of the vector bundle
-\begin{equation*} V = (\ev_q^\st TH) \otimes (TC_0) \otimes \OO(-\delta) \end{equation*}
-which is transverse and whose vanishing locus coincides with $\Dcal$. Thus we obtain:
+\begin{equation*} V = (\ev_q^\st TH) \otimes \mathbb T \otimes \OO(-\delta) \end{equation*}
+which is transverse and whose vanishing locus coincides with $\Dcal$.
+Transversality follows from the construction, because any stratum of the boundary on which $\Sigma \operatorname{d}\!f$ may have vanished has been (blown up and) included into $\mathbb T \otimes \OO(-\delta)$ as a twist.
+In other words, the circle of radius $\delta$ always passes through at least one component which is not contracted by the map to the expansion.
+Now, if the vanishing locus of $\Sigma \operatorname{d}\!f$ does not contain any stratum of the boundary, then it is the closure of its intersection with the open stratum, which can be seen to be transverse.
+Thus we obtain:
 \begin{prop} \label{class of D} $[\Dcal] = \operatorname{e}(V) \cap [\widetilde\Dcal]$.\end{prop}
@@
 \begin{example}
-Consider the locus $\Ecal$ given by $\sigma$ below, and the exceptional divisor $\widetilde\Dcal_\rho \subseteq \widetilde\Dcal$ given by $\rho$:
+Consider the locus $\Ecal$ given by $\sigma$ below, and the codimension one locus $\widetilde\Dcal_\rho \subseteq \widetilde\Dcal_\sigma$ given by the two-dimensional (due to the alignment) cone $\rho$:
 \begin{figure}[!htbp]
@@
 \end{align*}
+
+In this example we have:
+\[\lambda(\plC^0_1)=\lambda(\plC^0_2)=e,\quad \lambda(\plC^1_1)=\lambda(\plC^2_1)=\lambda(\plC^2_2)=e+f=\delta,\quad \lambda(\plC^3_1)=\lambda(\plC^4_1)=e+2f.\]
 From now on we use the same symbol to denote an edge length and the corresponding node on $\widetilde\Dcal_\rho$. On this locus we have line bundles pulled back from $\Ecal$

### 2020-10-21 EllipticSingularitiesSplitting.tex
I've rewritten \S 4.3.5 - D from tilde D in the second way

@@
 This subdivision is best described using the formalism of extended tropicalizations \cite{Thuillier,ACP}.
-The subdividing cones are obtained from cones in the star of $\tau$ under the limit $e_1=\cdots=e_r=\infty$\marginpar{Was $r$ called $\epsilon$ before?}.
+The subdividing cones are obtained from cones in the star of $\tau$ under the limit $e_1=\cdots=e_r=\infty$\sidenote{Was $r$ called $\epsilon$ before?}.
 The cones in the star of $\tau$ are given by (in)equalities relating distances of pairs of vertices, and there are three cases to consider:
@@
 The toric geometry dictionary gives rise to an associated Cartier divisor.
-Alternatively\marginpar{worth moving to the preliminary section?}, for any logarithmic stack $X$, the natural coboundary map induced by $$0\to \mathcal O_X^\star\to M_X^\text{gp}\to \overline M_X^\text{gp}\to 0$$ associates a $\mathcal O_X^\star$-torsor to a global section of the characteristic sheaf.
+Alternatively\sidenote{worth moving to the preliminary section?}, for any logarithmic stack $X$, the natural coboundary map induced by $$0\to \mathcal O_X^\star\to M_X^\text{gp}\to \overline M_X^\text{gp}\to 0$$ associates a $\mathcal O_X^\star$-torsor to a global section of the characteristic sheaf.
 
@@
 
-\subsubsection{$\Dcal$ from $\widetilde\Dcal$: second way} To establish a more direct connection with the geometry of the fibre product \eqref{IIIa fibre product}, recall that $\widetilde\Ecal$ is built as an explicit modification of a finite cover of \eqref{IIIa fibre product}.
+\subsubsection{$\Dcal$ from $\widetilde\Dcal$: second way} %To establish a more direct connection with the geometry of the fibre product \eqref{IIIa fibre product}, recall that $\widetilde\Ecal$ is built as an explicit modification of a finite cover of \eqref{IIIa fibre product}.
 For $i \in\{1,\ldots,r\}$ (with the convention established at the end of Lemma \ref{lem:generic_proj_bundle}), it makes sense on $\widetilde\Ecal$ to consider the line bundle $\OO(\delta_i)$ associated to a shortest path from the core to the circle in the $\sqC_i$-direction.
+We analyse the degeneracy locus of $\Sigma\operatorname{d}\!f$, in order to have a more direct construction of $\Dcal$ from the fibre product \eqref{IIIa fibre product}.
+On $\Ecal$ consider the piecewise linear function $\delta_i$ ($i=1,\ldots,r$), defined as the minimal distance from a component of (i.e.
+generising to) the core $\plC_0$ to a non-contracted component of the $i$-th tail $\plC_i$, and the associated line bundle $\OO(\delta_i)$.
 Construct
-\begin{equation*}\mathcal P=\PP_{\widetilde\Ecal}\left(\bigoplus_{i=1}^r\OO(\delta_i)\right).\end{equation*}
-Since $\sqC_1,\ldots,\sqC_r$ are always ordered on $\widetilde \Dcal$ (they may lie on the circle, be the first component off the circle, or degenerate and lie in the strict interior), there is a morphism $\widetilde \Dcal\to\mathcal P$ lifting $\widetilde \Dcal\to\widetilde\Ecal$.
-Consider the map of vector bundles on $\mathcal P$:
+\begin{equation*}\mathcal P=\PP_{\Ecal}\left(\bigoplus_{i=1}^r\OO(\delta_i)\right)\xrightarrow{p}\Ecal.\end{equation*}
+When all fibre coordinates are non-zero, a point of $\mathcal P$ induces compatible isomorphisms $\OO(\delta_i)\simeq\OO(\delta_j)$ for all $i,j$.
+We think of this as saying that all the $\plC_i$ are at the same distance from the core.
+When some of the coordinates are $0$, the corresponding tail is further from the core.
+This corresponds to an alignment of $\plC_1,\ldots,\plC_r$ with respect to the radius $\delta$, that is the distance of the closest of them from the core.
+Therefore, by the universal property,
+%Since $\sqC_1,\ldots,\sqC_r$ are always ordered on $\widetilde \Dcal$ (they may lie on the circle, be the first component off the circle, or degenerate and lie in the strict interior),
+there is a morphism $\widetilde \Dcal\to\mathcal P$ lifting $\widetilde \Dcal\to \Ecal$.
+
+In order to express factorisation, consider the map of vector bundles on $\mathcal P$:
 \begin{equation*}  \OO_{\mathcal P}(-1)\to p^*\left(\bigoplus_{i=1}^r\OO(\delta_i)\right)\xrightarrow{\sum\operatorname{d}\!f}\ev_q^*TH.\end{equation*}
@@
 On the boundary, though, it may happen that a simultaneous degeneration in the base and the fibre makes this factorisation trivial, in the sense that the map $\bar f$ is constant on all the branches of the elliptic singularity.
-
+These loci may be identified explicitly: let $\Lambda=(\Lambda_B,\Lambda_F)$ with $\Lambda_B\subseteq \{\sqC_1,\ldots,\sqC_r\}$ and $\Lambda_F=\{\sqC_1,\ldots,\sqC_r\}\setminus \Lambda_B$, and let $\Xi_\Lambda$ be the locus in $\mathcal P$ where:
+\begin{itemize}
+ \item[(B)] $\forall i\in\Lambda_B$, the $i$-th component of the fibre product \eqref{IIIa fibre product}, namely the map $f_i\colon C_i\to(\PP^N|H)$, degenerates so that it is constant near the attaching point to the core.
+ \item[(F)] $\forall j\in\Lambda_F$, the $j$-th coordinate in the fibre of $p\colon\mathcal P\to\Ecal$ vanishes.
+\end{itemize}
+It should be noted that the degeneracy loci of (B) are themselves Gathmann's comb loci \cite{Ga}, similar to the loci $\pazocal D$ that we are considering, only this time in genus $0$, and therefore recursively computable.
 \begin{lemma} 
- For every $\Lambda_B\subseteq \{\sqC_1,\ldots,\sqC_r\}$ and $\Lambda_F=\{\sqC_1,\ldots,\sqC_r\}\setminus \Lambda_B$, $s$ vanishes along the loci where the factors corresponding to $\Lambda_B$ in $\widetilde \Ecal$ degenerate so that $f_i\colon C_i\to\PP^N$ is constant in a neighbourhood of $q_i$, and the fibre coordinates $(\lambda_j)_{j\in\Lambda_F}$ along $p\colon\mathcal P\to\widetilde \Ecal$ are set to be $0$.
+ The $\Xi_\Lambda$ are precisely the boundary loci on which $s$ vanishes.
 \end{lemma}
-Call these loci $\Xi_\Lambda$ for $\Lambda=(\Lambda_B,\Lambda_F)$ (compare with \cite[\S 3.2]{VZ} for an analogous phenomenon in the non-relative case); clearly, they may be in excess with respect to the expected codimension of $V(s)$, that is $N-1$.
+
+Compare with \cite[\S 3.2]{VZ} for an analogous phenomenon in the non-relative case.
+Clearly, these loci may be in excess with respect to the expected codimension of $V(s)$, that is $N-1$.
 These loci are logarithmic substrata; therefore, there exists a logarithmic blowup that principalises them.
-We claim which $\widetilde\Dcal$ is (possibly a refinement of) such a blowup.
+We claim that $\widetilde\Dcal$ is one.
 \begin{lemma}
@@
  \begin{enumerate}
-  \item equations on $\widetilde\Ecal$ cutting the locus where $C_i$ degenerates so that $f_i$ is constant on a neighbourhood of $q_i$ for $i\in \Lambda_B$: these correspond to the tropical functions $\delta_i-\lambda(q_i)$ where $\lambda$ is the distance function to the core;
+  \item equations on $\Ecal$ cutting the locus where $C_i$ degenerates so that $f_i$ is constant on a neighbourhood of $q_i$ for $i\in \Lambda_B$: these correspond to the tropical functions $\delta_i-\lambda(q_i)$ where $\lambda$ is the distance function to the core;
   \item equations on the fibre of $p$ for the linear subspace corresponding to $i\in \Lambda_F$: tropically, these correspond to the $\ell_i$ discussed in Lemma \ref{lem:generic_proj_bundle}.
  \end{enumerate}
-By construction, on $\widetilde \Dcal$ it is always possible to tell which of these tropical lengths is the shortest (the circle we have drawn on $\Xi_\Lambda$ is degenerate -- it passes through no vertex of positive horizontal degree -- therefore we need to decide for a strictly larger circle in order to lift to $\widetilde D$), which corresponds to principalising the ideal (see Figure \ref{fig:principalisation}).
+By construction, on $\widetilde \Dcal$ it is always possible to tell which of these tropical lengths is the shortest.
+Figure \ref{fig:principalisation} represents the situation: the circle we have drawn on $\Xi_\Lambda$ is degenerate - it passes through no non-contracted vertex - therefore we need to decide for a strictly larger circle in order to lift to $\widetilde D$.
+This shows that the ideal is principalised on $\widetilde \Dcal$.
 \end{proof}
 
-\begin{figure}
-\includegraphics[scale=.5]{principalisation}
+\begin{figure}[hbt]
+\begin{tikzpicture}[ipe import]
+  %\useasboundingbox (0, 0) rectangle (595, 842);
+
+ %%%%%%%%%%%%%%%% left
+  \draw
+    (64, 720)node[left]{$\plC_2$}
+     -- (112, 736)node[above]{$\plC_0$}
+     -- (96, 752)node[left]{$\plC_1$};
+  \draw[->]
+    (64, 704)
+     -- (128, 704);
+  \pic
+     at (64, 704) {ipe disk} ;
+  \pic
+     at (64, 720) {ipe disk};
+  \pic
+     at (96, 752) {ipe disk};
+  \draw[red, dotted]
+    (60.6969, 708.808)
+     arc[start angle=-161.5651, end angle=-71.5651, x radius=53.2078, y radius=-65.2105];
+
+   %%%%%%%%%%%%%%%%% right  
+ \draw[red]
+    (188.9249, 712.0225) node[right]{$\delta$}
+     arc[start angle=-156.5092, end angle=-115.3692, x radius=85.088, y radius=-96.462];
+
+  \draw
+    (192, 720) node[left]{$\plC_2$}
+     -- (240, 736)node[above]{$\plC_0$}
+     -- (224, 752)node[above]{$\plC_1^0$};
+  \draw[->]
+    (192, 704)
+     -- (256, 704);
+
+  \pic
+     at (192, 704) {ipe disk};
+  \pic
+     at (192, 720) {ipe disk};
+  \pic
+     at (224, 752) {ipe disk};
+
+  \draw
+    (112, 736)
+     -- (128, 736);
+  \draw
+    (240, 736)
+     -- (256, 736);
+  \draw
+    (208, 743) node[left]{$\plC_1^2$}
+     -- (224, 752);
+  \draw
+    (208, 759) node[left]{$\plC_1^1$}
+     -- (224, 752);
+  \pic
+     at (208, 743) {ipe disk};
+  \pic
+     at (208, 759) {ipe disk};
+  \pic
+     at (208, 704) {ipe cross};
+  \pic
+     at (224, 704) {ipe cross};
+  \pic
+     at (240, 704) {ipe cross};
+  \pic
+     at (96, 704) {ipe cross};
+  \pic
+     at (112, 704) {ipe cross};
+  \draw[red, dotted]
+    (231.0126, 755.9018)
+     { [rotate=-17.595] arc[start angle=135, end angle=225, x radius=21.7093, y radius=22.6274] };
+
+  \pic
+     at (220, 729) {ipe cross};
+
+    \pic[fill=white]
+     at (112, 736) {ipe fdisk};  
+     \pic[fill=white]
+     at (240, 736) {ipe fdisk};
+
+\end{tikzpicture}
+%\includegraphics[scale=.5]{principalisation}
 \caption{On the left, a generic point of $\mathcal P$.
@@
 The dotted circle is the one we draw on $\mathcal P$.
-The continuous circle represents one of the possible choices of $\delta$ enlarging the dotted one (a stratum of $\widetilde\Dcal$).}\label{fig:principalisation}
+The continuous circle represents $\delta$ enlarging the dotted one (a stratum of $\widetilde\Dcal$).}\label{fig:principalisation}
 \end{figure}
 
-Finally, on $\widetilde\Dcal$ (or, in fact, on an intermediate blowup $\widetilde{\mathcal P}\to\mathcal P$) there are exceptional divisors $\widetilde \Xi_\Lambda$ corresponding to $\Xi_\Lambda$ in $\mathcal P$.
+Finally, on $\widetilde\Dcal$ %(or, in fact, on an intermediate blowup $\widetilde{\mathcal P}\to\mathcal P$)
+there are exceptional divisors $\widetilde \Xi_\Lambda$ corresponding to $\Xi_\Lambda$ in $\mathcal P$.
 Since the $\Xi_\Lambda$ exhaust all the excess-dimensional components of the vanishing locus of $s\in H^0(\mathcal P,W)$, the latter induces a section $\tilde s\in H^0(\widetilde\Dcal,W(-\Sigma_\Lambda \widetilde\Xi_\Lambda))$ by pullback and twisting, whose vanishing locus is dimensionally transverse to the boundary, and whose open part coincides with the generic point of $\Dcal$, therefore $V(\tilde s)=\Dcal$.
 
-Expressing the pushforward of the Chern classes of $\OO_W(1)$ and $\OO(\widetilde\Xi_\Lambda)$ in terms of tautological classes on the fibre product underlying $\Ecal$, we get:
+\begin{prop}
+ \[ [\Dcal]=e(W(-\Sigma_\Lambda \widetilde\Xi_\Lambda))\cap[\widetilde{\mathcal P}]\]
+ where $\widetilde{\mathcal P}$ denotes the blow-up of $\mathcal P$ in the $\Xi_\Lambda$.
+\end{prop}
+
+Applying \cite[Corollary 4.2.2]{FUL}, we get:
+\begin{cor} In $A_*(\mathcal P)$ the following formula holds:
+ \[ [\Dcal]=\sum_{\Lambda}\sum_i s_i(\Xi_\Lambda,\mathcal P)c_{N-1-i}(\ev_q^*TH\otimes\OO_\mathcal P(1))\]
+\end{cor}
+
+It is possible to push the formula further down to $\Ecal$, and applying \cite[\S3.1]{FUL} we obtain an expression for $[\Dcal]$ in terms of:
+\begin{itemize}
+ \item evaluation classes, such as $\ev_q^*TH$;
+ \item Chern classes of the logarithmic line bundles $\OO(\delta_i)$;
+ \item Segre classes of Gathmann's comb loci indexed by $\Lambda_B$.
+\end{itemize}
+
 \begin{cor}

### 2020-10-26 EllipticSingularitiesSplitting.tex
Fixed ipe compatibility
Minor changes

@@
 %\linespread{1.25}
-\usepackage[margin=3.5cm]{geometry}
+\usepackage[margin=2.75cm]{geometry}
 
@@
 \usepackage{tikz,tikz-cd}
-\usetikzlibrary{ipe,decorations.pathmorphing,decorations.pathreplacing,patterns,arrows.meta,shapes.misc}
+\usetikzlibrary{decorations.pathmorphing,decorations.pathreplacing,patterns,arrows.meta,shapes.misc}
+\usetikzlibrary{ipe}
 
@@
 
-The Kontsevich moduli space of stable maps from genus zero curves to projective space exhibits remarkable geometry -- it is a smooth orbifold with a ``self-similar'' normal crossings boundary.
+\noindent The Kontsevich moduli space of stable maps from genus zero curves to projective space exhibits remarkable geometry -- it is a smooth orbifold with a ``self-similar'' normal crossings boundary.
 These facts have combined to produce a very {satisfactory} understanding of Gromov--Witten theory in genus zero.
@@
 \]
-where $C$ is a nodal genus $1$ curve, $\overline C_1$ and $\overline C_2$ are Gorenstein curves of genus $1$, the map $C\to \PP^N[s]$ is a logarithmic map to an $s$-fold expansion of $\PP^N$ along $H$, and each of the vertical maps does not contract the minimal subcurve of genus $1$.
+where $C$ is a nodal genus one curve, $\overline C_1$ and $\overline C_2$ are Gorenstein curves of genus one, the map $C\to \PP^N[s]$ is a logarithmic map to an $s$-fold expansion of $\PP^N$ along $H$, and each of the vertical maps does not contract the minimal subcurve of genus one.
 \end{customthm}
 
-%Intuitively, non-degeneracy is the condition that the maps in question are non-constant on some branch of the minimal genus $1$ subcurve, see  \S \ref{section construction} for %details.
+%Intuitively, non-degeneracy is the condition that the maps in question are non-constant on some branch of the minimal genus one subcurve, see  \S \ref{section construction} for %details.
 
@@
 The moduli spaces we construct lie in between the absolute and toric-boundary-relative geometries studied in the first and second of those papers, respectively.
-The degeneration algorithm presented here as a first practical implementation of the theory developed in that work.
+The degeneration algorithm presented here is a first practical implementation of the theory developed in that work.
 
@@
 
-Finally, it would be natural to generalize the method of degenerating tangency conditions to targets with higher rank logarithmic structures.
+Finally, it would be natural to generalise the method of degenerating tangency conditions to targets with higher rank logarithmic structures.
 The extreme case when the target is a toric variety with its toric boundary, is intimately tied with the enumerative geometry of well-spaced tropical curves~\cite{LR18,RSPW2,Speyer}.
@@
 and N.N.
-would in addition like to thank Imperial College London, the LSGNT, the Royal Society, 3CinG, and the MSRI program ''Enumerative Geometry beyond Numbers''.
+would in addition like to thank Imperial College London, the LSGNT, the Royal Society, 3CinG, and the MSRI program ``Enumerative Geometry beyond Numbers''.
 N.N.
@@
 \section{Constructions and logarithmic smoothness}\label{section construction}
-
-We briefly review some basic tropical structures in the theory of logarithmic curves and logarithmic stable maps.
-A detailed treatment is given by~\cite[Section~3]{CavalieriChanUlirschWise}.
-The following paragraphs are meant only as a reminder.
+\noindent We briefly review some basic tropical structures in the theory of logarithmic curves and logarithmic stable maps.
+A detailed treatment is given by~\cite[Section~3]{CavalieriChanUlirschWise}; the following paragraphs are meant only as a reminder.
 
 \subsection{Curves and tropical curves} A nodal curve $C$ over $\spec \mathbb C$ has an associated dual graph $\Gamma(C)$.
-Given a toric monoid $P$, there is a logarithmic point $\spec \CC_P$ which may be thought of as remembering the information of the embedding of the torus-fixed closed point into the toric variety $\spec \mathbb C[P]$.
-For a logarithmically smooth curve $C$ over $\spec \CC_P$, the dual graph $\Gamma(C)$ is enhanced: given an edge $e$ of $\Gamma(C)$, the logarithmic structure keeps track of a generalized ``edge length'' $\ell_e$, which is an element of $P$.
+Given a toric monoid $P$, there is a logarithmic point $\spec (P \to \CC)$ which may be thought of as remembering the information of the embedding of the torus-fixed closed point into the affine toric variety $\spec \mathbb C[P]$.
+For a logarithmically smooth curve $C$ over $\spec (P \to \CC)$, the dual graph $\Gamma(C)$ is enhanced: given an edge $e$ of $\Gamma(C)$, the logarithmic structure keeps track of a generalised ``edge length'' $\ell_e$, which is an element of $P$.
 These data can be repackaged into a cone complex $\plC$ together with a map to the dual cone $\sigma_P$
@@
 \]
-A fiber of this map $\pi$ is a metric space enhancing the topological space $\Gamma(C)$, with edges given lengths in $\RR_{\geq 0}$.
-Over the interior of the cone $\sigma_P$ these edge lengths are nonzero, and the fibers are homoemorphic to $\Gamma(C)$.
-Over the faces of $\sigma_P$, the fibers can be identified with edge contractions.
+A fibre of this map $\pi$ is a metric space enhancing the topological space $\Gamma(C)$, with edges given lengths in $\RR_{\geq 0}$.
+Over the interior of the cone $\sigma_P$ these edge lengths are nonzero, and the fibres are homoemorphic to $\Gamma(C)$.
+Over the faces of $\sigma_P$, the fibres can be identified with edge contractions.
 
 The discussion is globalized in~\cite{CavalieriChanUlirschWise}, and the construction can be carried out for the universal curve over the moduli space of logarithmic curves.
-Specifically, there is a stack over the category of cone complexes $\mathfrak M_{g,n}^{\mathrm{trop}}$ equipped with a universal curve
+Specifically, there is a stack $\mathfrak M_{g,n}^{\mathrm{trop}}$ over the category of cone complexes equipped with a universal curve
 \[
@@
 \subsection{Maps and tropical maps}The discussion carries over to the setting of logarithmic maps.
-Specifically, given a logarithmic curve $C$ and a logarithmic map to a smooth pair $(X,Y)$ over a logarithmic scheme $S$.
+Specifically, suppose we are given a logarithmic curve $C$ and a logarithmic map to a smooth pair $(X,Y)$ over a logarithmic scheme $S$.
 For simplicity, assume that $S$ is a $P$-logarithmic point, as above.
 There is an associated \textbf{tropicalization}, i.e.
-a family of tropical curves $\plC$ over $\sigma_P$, together with a map of cone complexes
+a family of tropical curves $\plC \to \sigma_P$, together with a map of cone complexes
 \[
@@
 \]
-Each fiber over $\sigma_P$ encodes a metric enhancement of the dual graph, together with a piecewise linear map to $\RR_{\geq 0}$.
-There is once again a cone stack representing the moduli problem of tropical maps; the technical details are only cosmetically different than those presented in~\cite{CavalieriChanUlirschWise}, and we leave these details to the reader.
-See also \cite{GrossSiebertLog}.
+Here $\RR_{\geq 0}$ is the tropicalization (or ``fan'') of the smooth pair $(X,Y)$.
+Each fibre over $\sigma_P$ encodes a metric enhancement of the dual graph, together with a piecewise linear map to $\RR_{\geq 0}$.
+There is once again a cone stack representing the moduli problem of tropical maps; the technical details are only cosmetically different than those presented in~\cite{CavalieriChanUlirschWise}, and we leave these details to the reader (see also \cite{GrossSiebertLog}).
 
 \subsection{Maps from curves and elliptic singularities} We provide a brief intuitive picture that underlies the work in~\cite{RSPW,RSPW2}.
-If $C$ is a Gorenstein curve and $f:C\to \mathbb P^N$ is a morphism, the ampleness of the the tangent bundle of $\mathbb P^N$ ensures that if no subcurve of arithmetic genus $1$ is contracted, the deformations of $f$ are unobstructed.
-In fact, the deformations \textit{over the stack of curves} are also unobstructed.
-The moduli space of Gorenstein genus $1$ curves is not smooth.
-However, a more sophisticated moduli problem, consisting of nodal curves together with a \textit{chosen contraction} to a Gorenstein curve, might be expected to resolve these singularities.
+If $C$ is a Gorenstein curve and $f:C\to \mathbb P^m$ is a morphism, the ampleness of the the tangent bundle of $\mathbb P^m$ ensures that if $f$ is non-constant on the minimal subcurve of $C$ of arithmetic genus one, then the deformations of $f$ are unobstructed; in fact, the deformations \textit{over the stack of curves} are also unobstructed.
+It is  natural to attempt to resolve the moduli space of stable maps, by replacing it with a moduli space parametrising Gorenstein curves obtained from nodal curves by contracting a genus one subcurve.
+The moduli space of Gorenstein genus one curves is not smooth.
+However, a more sophisticated moduli problem, consisting of nodal curves $C$ together with a \textit{chosen contraction} to a Gorenstein curve $\bar{C}$, might be expected to resolve these singularities.
 The formation of such a moduli problem requires logarithmic geometry, and is achieved in~\cite[Section~3]{RSPW}.
 Once constructed, the corresponding moduli of stable maps out of a Gorenstein curve is also resolved.
-Note that maps from nodal genus $1$ curves may have stable limits that contract genus $1$ subcurves, but the allowance of Gorenstein singularities ensures properness despite disallowing contracted genus $1$ components.
+Note that maps from nodal genus one curves may have stable limits that contract genus one subcurves, but the introduction of Gorenstein singularities ensures properness while disallowing contracted genus one components.
 
@@
 
-\subsection{Singularities and moduli of attachments}\label{S:ellsing} Isolated Gorenstein singularities of genus $1$ were classified by Smyth in \cite{SMY1}: for every fixed number of branches $m$, there is only one isomorphism type of curve germs with such characteristics.
-For $m=1,2$ we find the cusp ($A_2$) and tacnode ($A_3$) respectively; for $m\geq 3$ we find the union of $m$ general lines through the origin of $\Aaff^{m-1}$ - Smyth calls them \emph{elliptic $m$-fold points}.
+\subsection{Singularities and moduli of attachments}\label{S:ellsing} Isolated Gorenstein singularities of genus one were classified by Smyth in \cite{SMY1}: for every fixed number of branches $m$, there is precisely one isomorphism type of curve germ.
+For $m=1$ and $2$ these are the cusp ($A_2$) and tacnode ($A_3$) respectively; for $m\geq 3$ they are the union of $m$ general lines through the origin of $\Aaff^{m-1}$ -- following Smyth, we refer to these as \emph{elliptic $m$-fold points}.
 
@@
 \begin{lemma}\label{lem:PicE}
- Let $C$ be a curve of arithmetic genus $1$ containing an elliptic $m$-fold point. Then $\operatorname{Pic}^0(C)\simeq\mathbb G_{\text{a}}$.
+ Let $C$ be a curve of arithmetic genus one containing an elliptic $m$-fold point. Then $\operatorname{Pic}^0(C)\simeq\mathbb G_{\text{a}}$.
 \end{lemma}
@@
 Given a point $t$ in $\sigma_P$ we obtain a metric graph as explained above.
-Since the curve in question has genus $1$, there is a minimal genus $1$ subgraph -- either a vertex of genus $1$ or a cycle in the graph.
+Since the curve in question has genus one, there is a minimal genus one subgraph -- either a vertex of genus one or a cycle in the graph.
 We will refer to this as the \textbf{core}, denoted by $\plE$ below.
@@
 Given a family of tropical curves, the function $\delta$ provides a non-negative real number for each point on the base.
-We may therefore consider the ``\textbf{circle}'' of points on each fiber whose distance from the core is equal to $\delta$.
+We may therefore consider the ``\textbf{circle}'' of points on each fibre whose distance from the core is equal to $\delta$.
 A partial destabilization, or ``bubbling'', introduces $2$-pointed rational curves into the curve by adding vertices to the dual graph at the points that lie on this circle (the crosses at height $\delta$ in Figure \ref{fig:lambdaexample}); we denote this new tropical curve by $\widetilde{\plC}$.
@@
 A stable map in this space is said to satisfy the \textbf{factorisation condition} if the map $\widetilde{\mathcal C}\to \mathcal C\to \mathbb P^N$ factors through the contraction $\widetilde{\mathcal C}\to \overline{\mathcal C}$.
-Maps that are not constant on any genus $1$ subcurve of $\mathcal C$ automatically satisfy this condition; indeed, the contraction is an isomorphism in this case.
+Maps that are not constant on any genus one subcurve of $\mathcal C$ automatically satisfy this condition; indeed, the contraction is an isomorphism in this case.
 
@@
 \begin{remark}[Constant maps]\label{rem: constant-maps}
-When the degree of the map is $1$, maps from smooth genus $1$ curves to $\PP^N$ are constant.
+When the degree of the map is $1$, maps from smooth genus one curves to $\PP^N$ are constant.
 The interior of the moduli space of stable maps in this case is empty, though the compactification by stable maps is non-empty.
@@
 Let $\alpha$ be a partition of the degree $d>0$.
-Consider the moduli space $\mathcal M_{1,\alpha}^\circ(\mathbb P^N|H,d)$ of maps from smooth genus $1$ curves $C\to \mathbb P^N$ that meet $H$ at finitely many marked points with vanishing orders given by the partition $\alpha$.
+Consider the moduli space $\mathcal M_{1,\alpha}^\circ(\mathbb P^N|H,d)$ of maps from smooth genus one curves $C\to \mathbb P^N$ that meet $H$ at finitely many marked points with vanishing orders given by the partition $\alpha$.
 This is a smooth, but non-proper Deligne--Mumford stack.
@@
 
-Let $D_F\subseteq C$ be the maximal genus $1$ subcurve which is mapped to a higher level and contracted by the map $C\to \mathbb P^N[s]$.
+Let $D_F\subseteq C$ be the maximal genus one subcurve which is mapped to a higher level and contracted by the map $C\to \mathbb P^N[s]$.
 Let $\delta_F$ denote the distance from the core to the nearest component of $C \setminus D_F$.
-Similarly let $D_B\subseteq C$ be the maximal genus $1$ subcurve that is contracted by the collapsed map to $\mathbb P^N$, and let $\delta_B$ be the associated radius.
+Similarly let $D_B\subseteq C$ be the maximal genus one subcurve that is contracted by the collapsed map to $\mathbb P^N$, and let $\delta_B$ be the associated radius.
 This coincides with the radius of the underlying map to $\mathbb P^N$.
@@
 %A Gorenstein elliptic singularity has a number of \textbf{branches}.
-Given a curve $\overline C$ of genus $1$ with such a singularity, define a branch of $\overline C$ to be an irreducible component containing a branch of the singularity.
-If the curve $C$ is nodal, then its branches will be understood to be the components of its minimal arithmetic genus $1$ subcurve, i.e.
+Given a curve $\overline C$ of genus one with such a singularity, define a branch of $\overline C$ to be an irreducible component containing a branch of the singularity.
+If the curve $C$ is nodal, then its branches will be understood to be the components of its minimal arithmetic genus one subcurve, i.e.
 its core.
-Recall that we name \emph{core} the minimal genus $1$ subcurve of a Gorenstein curve of arithmetic genus $1$, so the latter decomposes into the nodal union of the core and a (possibly empty) rational forest.
+Recall that we name \emph{core} the minimal genus one subcurve of a Gorenstein curve of arithmetic genus one, so the latter decomposes into the nodal union of the core and a (possibly empty) rational forest.
 If the curve contains an elliptic $m$-fold point, we say a map is non-constant on the core if at least one branch of the singularity is not contracted.
@@
 \begin{rem}
- The factorisation conditions are understood to be satisfied when $C\to \mathbb P^N[s]$ (resp. $C\to \mathbb P^N$) does not contract a genus $1$ subcurve. 
+ The factorisation conditions are understood to be satisfied when $C\to \mathbb P^N[s]$ (resp. $C\to \mathbb P^N$) does not contract a genus one subcurve. 
 \end{rem}
@@
 The corresponding element in $\mathrm{Obs}(f/(C,f_B))$ is the obstruction to lifting the deformation of $(C,f_B)$ to this canonical deformation of $\mathbb P^N[s]$ over $\mathbb P^N$.
-By comparing the cotangent complexes of the source, target, and fiber of the morphism $\nu$, we see that the cokernel of this map are the absolute logarithmic obstructions for the map.
+By comparing the cotangent complexes of the source, target, and fibre of the morphism $\nu$, we see that the cokernel of this map are the absolute logarithmic obstructions for the map.
 We will show these vanish, proving logarithmic smoothness.
@@
 
-On restricting to the minimal genus $1$ subcurve $D_F$, the line bundle $\mathcal O_{C}(-\alpha)$ is equivalent to the divisor $\sum a_i x_i$ where $x_i$ are the points connecting $D_F$ to the rest of the curve, and $a_i$ are the slopes of $\alpha$ along the edges corresponding to the $x_i$.
+On restricting to the minimal genus one subcurve $D_F$, the line bundle $\mathcal O_{C}(-\alpha)$ is equivalent to the divisor $\sum a_i x_i$ where $x_i$ are the points connecting $D_F$ to the rest of the curve, and $a_i$ are the slopes of $\alpha$ along the edges corresponding to the $x_i$.
 Infinitesimally moving the point $x_i$ produces a nontrivial deformation of the line bundle $\mathcal O_{C}(-\alpha)$.
-The moduli space $\VZ_{1,n}(\mathbb P^N,d)$ is a logarithmically smooth fibration over the universal Picard stack over the stack of centrally aligned $n$-pointed genus $1$ curves~\cite[Remark~4.5.3]{RSPW}.
+The moduli space $\VZ_{1,n}(\mathbb P^N,d)$ is a logarithmically smooth fibration over the universal Picard stack over the stack of centrally aligned $n$-pointed genus one curves~\cite[Remark~4.5.3]{RSPW}.
 As a consequence, it is possible to find a logarithmic deformation of the map $(C,f_B)$ that induces the deformation of the line bundle that is given by infinitesimal motion.
@@
 
+\footnotesize
+
 \bibliographystyle{alpha}
@@
 
-\end{document}
+\end{document}w

### 2020-10-26 EllipticSingularitiesSplitting.tex
minor tweaks

@@
 \end{dfn}
-\noindent Equivalently, for the expanded map, $x_k$ does not belong to a \emph{trivial bubble} component.
-
- In this section, we use the logarithmic structure on $\VZ_{1,\alpha}(\PP^N|H,d)$ to construct a line bundle $\Lcal_k$ and section $s_k$ which vanishes precisely along $\Dcal_{1,\alpha,k}(\PP^N|H,d)$.
+%\noindent Equivalently, for the expanded map, $x_k$ is mapped to a higher level and does not belong to a \emph{trivial bubble} component.
+\noindent In this section, we use the logarithmic structure on $\VZ_{1,\alpha}(\PP^N|H,d)$ to construct a line bundle $\Lcal_k$ and section $s_k$ which vanishes precisely along $\Dcal_{1,\alpha,k}(\PP^N|H,d)$.
 We use the correspondence with tropical geometry to identify $\cchern_1(\Lcal_k)$ in terms of tautological classes on $\VZ_{1,\alpha}(\PP^N|H,d)$, and to compute the vanishing order of $s_k$ along the components of $\Dcal_{1,\alpha,k}(\PP^N|H,d)$.
-Combined with the relative splitting formulas from the next section, we obtain a recursion relation inside $\VZ_{1,\alpha}(\PP^N|H,d)$
+Combined with the relative splitting formulas from the next section, this produces a recursion relation inside $\VZ_{1,\alpha}(\PP^N|H,d)$
 
@@
 \ecd
-where $x_k$ is the section which for every point $\lambda \in \Sigma^{\log}$ picks out the vertex of $\sqC_\lambda$ containing the leg $x_k$.
+where $x_k$ is the section which for every point $\lambda \in \Sigma^{\log}$ picks out the vertex of $\sqC_\lambda$ supporting the leg $x_k$.
 The composition $f \circ x_k \colon \Sigma^{\log} \to \RR_{\geq 0}$ defines a piecewise-linear function on $\Sigma^{\log}$ whose preimage over the open cone $\RR_{>0}$ consists of those tropical maps where $x_k$ belongs to an internal component.
@@
 \begin{equation*} \Sigma_{1,\alpha}(\PP^N|H,d) \to \Sigma^{\log} \to \RR_{\geq 0}.\end{equation*}
-Note that $\psi_k$ should be interpreted as a \textbf{collapsed class} on $\VZ_{1,\alpha}(\PP^N|H,d)$, i.e.
+Note in particular that $\psi_k$ should be interpreted as a \textbf{collapsed class} on $\VZ_{1,\alpha}(\PP^N|H,d)$, i.e.
 the cotangent class from the source curve of the collapsed and stabilised map.
@@
 
-A basic phenomenon is responsible for the nature of the forthcoming analysis.
+\noindent A basic phenomenon is responsible for the nature of the forthcoming analysis.
 In contrast with nodal singularities, the functions on an elliptic singularity are not simply collections of functions on the normalisation that agree at the gluing point.
-Rather, the contraction map $C\to\overline C$ corresponds to a linear combination of tangent vectors at the pointed normalisation, whose kernel represents the functions descending to the elliptic singularity - see \S \ref{S:ellsing}.
+Rather, the contraction map $C\to\overline C$ corresponds to a particular linear combination of tangent vectors at the pointed normalisation, whose kernel consists of those functions descending to the elliptic singularity (see \S \ref{S:ellsing}).
 In order to compute integrals, it is necessary to give a tautological description of this additional condition.
@@
 
-\begin{remark}
-The reduced relative Gromov--Witten theory of $(\mathbb P^N,H)$ with only primary insertions, i.e.
+\begin{remark} For the reduced relative Gromov--Witten theory of $(\mathbb P^N,H)$ with only primary insertions, i.e.
 where all cohomological insertions in the invariants are pulled back along evaluation maps, computations can be carried out without an analysis of the factorisation condition; this follows from dimension considerations and leads to the main results in~\cite{Vre}.
-In order to add descendant insertions, study with more general pairs, or indeed work cycle theoretically, an analysis of these tautological classes is crucial.
+However if we wish to include descendant insertions, work with more general pairs, or produce cycle-level statements, an analysis of the tautological classes arising from the factorisation condition is crucial.
 \end{remark}
@@
 
-\begin{proof} The locus where the logarithmic structure is trivial is the  locus where the source curve is smooth, and thus not mapped inside $H$.
+\begin{proof} The locus where the logarithmic structure is trivial is the locus where the source curve is smooth and not mapped inside $H$.
 Since $\VZ_{1,\alpha}(\PP^N|H,d)$ is toroidal this locus is open and dense.
 By definition $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ is contained in the  complement of this locus and can be expressed as a union of strata of positive codimension.
-Since $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ has codimension $1$, it is a union of logarithmic divisors.\end{proof}
-
-In \S \ref{subsection indexing strata} we described the logarithmic strata of $\VZ_{1,\alpha}(\PP^N|H,d)$, using the cones of the tropicalization $\Sigma_{1,\alpha}(\PP^N|H,d)$.
+Since $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ is pure codimension $1$, it is a union of logarithmic divisors.\end{proof}
+
+\noindent In \S \ref{subsection indexing strata} we described the logarithmic strata of $\VZ_{1,\alpha}(\PP^N|H,d)$, using the cones of the tropicalization $\Sigma_{1,\alpha}(\PP^N|H,d)$.
 Every divisorial logarithmic stratum is obtained as follows:
@@
 
-\subsection{Recursive description of the divisors: types I,II and III} Choose an irreducible component $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$.
+\subsection{Recursive description of the divisors: types I, II and III} Choose an irreducible component $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$.
 By Lemma \ref{Lemma components are logarithmic divisors} this is a logarithmic divisor, and hence may be written as:
@@
 is a logarithmic modification, the divisor $\widetilde{\Dcal}$ is either exceptional or the strict transform of a logarithmic divisor.
-These two cases correspond, respectively, to when the core is assigned zero degree or nonzero degree by the combinatorial type.
-We begin with the latter.
-Suppose therefore that $\widetilde{\Dcal}$ is the proper transform of a logarithmic divisor:
+By the nature of the subdivision procedure these two cases correspond, respectively, to when the core is assigned zero degree or nonzero degree by the combinatorial type.
+
+We begin with the latter. Suppose therefore that $\widetilde{\Dcal}$ is the strict transform of a logarithmic divisor:
 \begin{equation*} \Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d). \end{equation*}
@@
 
-\noindent where black vertices represent rational components, white vertices represent genus one.
+\noindent where black vertices represent rational components, white vertices components of genus one.
 The degrees of vertices, expansions factors, and remaining markings are distributed arbitrarily, subject to the following constraints:
@@
 \end{enumerate}\end{lemma}
-In \cite{Vre} these cases are referred to, respectively, as types $A,B$ and $C^+$.
-
-\begin{proof} Let $\sigma \in \Sigma_{1,\alpha}(\PP^N|H,d)$ be the cone corresponding to the $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$.
-By the discussion above $\Dcal$ corresponds to a ray in the subdivision of $\sigma$ given by imposing the central alignment condition.
+\noindent In \cite{Vre} these cases are referred to, respectively, as types $A,B$ and $C^+$.
+
+\begin{proof} Let $\sigma \in \Sigma_{1,\alpha}(\PP^N|H,d)$ be the cone corresponding to $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$.
+By the discussion above $\Dcal$ corresponds to a ray in the subdivision of $\sigma$ obtained by imposing the central alignment condition.
 Since the elliptic core is assigned positive degree, both radii are equal to $0$ and the subdivision is trivial.
@@
 In order for the cone $\sigma$ to be $1$-dimensional, the dual graph $\Gamma$ must be bipartite, with vertices over $0$ and $\diamond$.
-The cases I,II and III enumerated above cover situations where there is a single vertex mapped to $\diamond$.
+The cases I, II and III enumerated above cover situations where there is a single vertex mapped to $\diamond$.
 If there is more than one such vertex, then the contribution to the Gromov--Witten invariant vanishes.
@@
 For the remainder of this subsection, therefore, we fix a one-dimensional cone $\tau \in \Sigma_{1,\alpha}(\PP^N|H,d)$, let $\Dcal \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$ be the associated logarithmic divisor, and assume that $\Dcal$ is contained in $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ and is of type I, II or III.
-We let $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$ be the logarithmic stratum into which $\Dcal$ is mapped; this is indexed by a cone $\epsilon \in \Sigma^{\Kim}$ corresponding to a combinatorial type $\Delta$, and $\epsilon$ is one-dimensional since we are restricting to the type I,II,III cases.
+We let $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$ be the logarithmic stratum into which $\Dcal$ is mapped; this is indexed by a cone $\epsilon \in \Sigma^{\Kim}$ corresponding to a combinatorial type $\Delta$, and $\epsilon$ is one-dimensional since we are restricting to the type I, II, III cases.
 
@@
 \begin{equation*}\Dcal \xrightarrow{\rho} \left(\VZ_{1,\alpha^{(1)}\cup(m_1)}(\PP^N|H,d_1)\times\prod_{i=2}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i)\right) \times_{H^r} \ol\Mcal^{\leftrightarrow}_{0,\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}(\mathbb{P}|H_0+H_\infty,d_0)\end{equation*}
-such that the map $\Dcal \to \Ecal$ covers the map on fibre products obtained by desingularising the main component of the factor corresponding to $\sqC_1$.\end{lemma}
+such that the map $\Dcal \to \Ecal$ lifts the map on fibre products obtained by desingularising the main component of the first factor.\end{lemma}
 
@@
 In particular, if $\sqC_1$ is degenerate and if $\delta$ denotes the minimal distance from the core to a non-contracted vertex of $\sqC_1$ (which certainly exists since $\sqC_1$ has positive degree) then $\delta < e_1 \leq \lambda(\sqC^\prime)$, as claimed.\end{proof}
-
-Lemma \ref{Lemma type A gluing} provides a means to calculate integrals over the class $\lambda_\Dcal[\Dcal]$ appearing on the right-hand side of Theorem \ref{theorem recursion}, provided that we can calculate $\lambda_\Dcal$ and the degree of the splitting morphism.
+\noindent Lemma \ref{Lemma type A gluing} provides a means to calculate integrals over the class $\lambda_\Dcal[\Dcal]$ appearing on the right-hand side of Theorem \ref{theorem recursion}, provided that we can calculate $\lambda_\Dcal$ and the degree of the splitting morphism.
 Simple closed formulae for these are given in \S \ref{subsubsection splitting degree} below.
@@
 such that $\Dcal \to \Ecal$ corresponds to the obvious map on fibre products.\end{lemma}
-The first factor in the fibre product is the logarithmic blowup of the moduli space of rubber maps constructed in \S \ref{subsection rubber}.
-We compute integrals over such spaces as part of the recursion (see \S \ref{section recursion algorithm}).
+\noindent The final factor in the fibre product is the logarithmic blowup of the moduli space of rubber maps constructed in \S \ref{subsection rubber}.
+We will compute integrals over such spaces as part of the recursion (see \S \ref{section recursion algorithm}).
 
@@
 Here we describe the degree of $\rho$ and calculate the vanishing order $\lambda_\Dcal$ of the section $s_k$ constructed in \S \ref{Section Gathmann line bundle}.
-This gives a complete recursive description of the terms appearing on the right-hand side of Theorem \ref{theorem recursion} which are of type I,II or III.
+This gives a complete recursive description of the terms appearing on the right-hand side of Theorem \ref{theorem recursion} which are of type I, II or III.
 
@@
 \begin{equation*} \label{degree of gluing} \dfrac{\prod_{i=1}^r m_i}{\lcm(m_1,\ldots,m_r)}. \end{equation*}\end{lemma}
-\begin{proof} The calculation is well known, see for instance~\cite[Section~7.9]{ChenDegeneration}, \cite[Section~5.3]{ACGSDecomposition}.
+\begin{proof} This calculation is well known, see for instance~\cite[Section~7.9]{ChenDegeneration}, \cite[Section~5.3]{ACGSDecomposition}.
 \end{proof}
@@
 
-We summarise that the contribution of each term $\lambda_\Dcal [\Dcal]$ is given by integrating over the appropriate fibre product and then multiplying the result by $\lambda_\Dcal \cdot \deg\rho = \prod_{i=1}^r m_i$.
+In summary, the contribution of each term $\lambda_\Dcal [\Dcal]$ is given by integrating over the appropriate fibre product and then multiplying the result by $\lambda_\Dcal \cdot \deg\rho = \prod_{i=1}^r m_i$.
 
@@
 \begin{proof}[Proof of Lemma \ref{lem:stable_vertices}]
-Since we are looking at a one-parameter family of tropical maps, for every vertex of the target there must be at least one vertex above it which lies on the circle.
+Since the corresponding family of tropical maps is one-dimensional, for every vertex of the target there must be at least one vertex above it which lies on the circle.
 If the vertex on the circle is strictly semistable -- so that in particular the collapsed map $f_B$ is constant along the corresponding component -- the factorisation condition for $f_B$ is unaffected by $\Gm$-scaling the coordinate corresponding to that vertex in the moduli space of attaching data \cite[\S 2.2]{SMY2}, so the map $\Dcal\to\Ecal$ has generic fibre of positive dimension and the contribution vanishes.
@@
 We begin with a description of the boundary divisor corresponding to a comb whose teeth all have degree $1$.
-This is at the same time more concrete and peculiar, since the teeth are generically transverse (not just dimensionally) to the hyperplane $H$.
+This is a concrete but atypical case, since the teeth are generically transverse (not just dimensionally) to the hyperplane $H$.
 For simplicity, we assume that the contact order is $(d)$, concentrated at a marking $x_1$ supported on the elliptic curve $E$ contracted to $H$.
@@
  \tikzset{cross/.style={cross out, draw=black, fill=none, minimum size=2*(#1-\pgflinewidth), inner sep=0pt, outer sep=0pt}, cross/.default={3pt}}
-  \foreach \x in {(0,2),(0,1),(0,-1),(0,-2)}
+  \foreach \x in {(0,2),(0,1),(0,-1)}
   \draw[fill=black] \x circle (2pt);
+  \draw[fill=blue] (0,-2) circle (2pt);
   \foreach \x in {(0,2),(0,1),(0,-1)}
   \draw \x --node[below]{\color{blue} $1$} (4,0);
-  \draw (0,0) node{$\ldots$};
-  \draw (4,0) --node[below]{\color{blue} $d$} (8,0);
-  \draw[->] (0,-2)--(8,-2);
+  \draw (0,0) node{$\vdots$};
+  \draw[->] (4,0) --node[above]{\color{blue} $d$} (6,0);
+  \draw[blue,->] (0,-2)--(6,-2);
   \draw[fill=white] (4,0) circle (2pt);
-  \draw (4,-2) node[cross]{};
+  \draw[fill=blue,blue] (4,-2) node[cross]{};
   \draw [red] plot [smooth cycle] coordinates {(0,2) (0,1) (0,-1) (2,-1.5) (7,0) (2,2.5)};

### 2020-11-03 EllipticSingularitiesSplitting.tex
Fixed up recursion up to start of Step 3

@@
 
-\subsection{Results} Our first contribution is the construction of a \textbf{reduced relative} Gromov--Witten theory associated to elliptic curves in $\mathbb P^N$ with prescribed tangency along a hyperplane, and analogous invariants associated to smooth pairs $(X,Y)$ with $Y$ very ample.
+\subsection{Results} Our first contribution is the construction of a \textbf{reduced relative} Gromov--Witten theory associated to elliptic curves in $\mathbb P^m$ with prescribed tangency along a hyperplane, and analogous invariants associated to smooth pairs $(X,Y)$ with $Y$ very ample.
 Our reduced relative theory differs from relative Gromov--Witten theory in a parallel fashion to how Li--Zinger's reduced Gromov--Witten theory differs from the standard theory.
@@
 The geometric content is the following theorem, which provides a smooth and proper moduli space compactifying the space of elliptic curves in projective space with prescribed contact order data.
-Let $\mathcal M_{1,\alpha}^\circ(\mathbb P^N|H,d)$ be the moduli space of positive degree maps from smooth curves of genus one to $\mathbb P^N$ with dimensionally transverse contact order $\alpha\in\mathbb Z^n_{\geq 0}$ along $H$.
+Let $\mathcal M_{1,\alpha}^\circ(\mathbb P^m|H,d)$ be the moduli space of positive degree maps from smooth curves of genus one to $\mathbb P^m$ with dimensionally transverse contact order $\alpha\in\mathbb Z^n_{\geq 0}$ along $H$.
 A precise version of the following theorem requires a certain amount of tropical and logarithmic language, and is therefore stated precisely in \S \ref{section construction}.
@@
 \begin{customthm}{A}\label{thm: desingularization}
-There exists a logarithmically smooth and proper Deligne--Mumford stack $\VZ_{1,\alpha}(\mathbb P^N|H,d)$ having expected dimension, and containing $\mathcal M_{1,\alpha}^\circ(\mathbb P^N|H,d)$  as a dense open subset.
+There exists a logarithmically smooth and proper Deligne--Mumford stack $\VZ_{1,\alpha}(\mathbb P^m|H,d)$ having expected dimension, and containing $\mathcal M_{1,\alpha}^\circ(\mathbb P^m|H,d)$  as a dense open subset.
 A point in this moduli space determines commutative diagrams
@@
 C\arrow{r} & \overline C_1\arrow{d}\arrow{r} & \overline C_2\arrow{d} \\ 
-& \mathbb P^N[s]\arrow{r} & \mathbb P^N,
+& \mathbb P^m[s]\arrow{r} & \mathbb P^m,
 \end{tikzcd}
 \]
-where $C$ is a nodal genus one curve, $\overline C_1$ and $\overline C_2$ are Gorenstein curves of genus one, the map $C\to \PP^N[s]$ is a logarithmic map to an $s$-fold expansion of $\PP^N$ along $H$, and each of the vertical maps does not contract the minimal subcurve of genus one.
+where $C$ is a nodal genus one curve, $\overline C_1$ and $\overline C_2$ are Gorenstein curves of genus one, the map $C\to \PP^m[s]$ is a logarithmic map to an $s$-fold expansion of $\PP^m$ along $H$, and each of the vertical maps does not contract the minimal subcurve of genus one.
 \end{customthm}
@@
 
-%The moduli space above is constructed by identifying two closed conditions that must be satisfied by maps to the pair $(\mathbb P^N,H)$.
+%The moduli space above is constructed by identifying two closed conditions that must be satisfied by maps to the pair $(\mathbb P^m,H)$.
 Each condition requires the stable map to factor through an elliptic singularity, and the conditions together are required for the relative and absolute reduced theories to be related appropriately.
@@
 \subsection{Maps from curves and elliptic singularities} We provide a brief intuitive picture that underlies the work in~\cite{RSPW,RSPW2}.
-If $C$ is a Gorenstein curve and $f:C\to \mathbb P^m$ is a morphism, the ampleness of the the tangent bundle of $\mathbb P^m$ ensures that if $f$ is non-constant on the minimal subcurve of $C$ of arithmetic genus one, then the deformations of $f$ are unobstructed; in fact, the deformations \textit{over the stack of curves} are also unobstructed.
-It is  natural to attempt to resolve the moduli space of stable maps, by replacing it with a moduli space parametrising Gorenstein curves obtained from nodal curves by contracting a genus one subcurve.
-The moduli space of Gorenstein genus one curves is not smooth.
-However, a more sophisticated moduli problem, consisting of nodal curves $C$ together with a \textit{chosen contraction} to a Gorenstein curve $\bar{C}$, might be expected to resolve these singularities.
+If $C$ is a Gorenstein curve of genus one and $f:C\to \mathbb P^m$ is a morphism, the ampleness of the the tangent bundle of $\mathbb P^m$ ensures that if $f$ is non-constant on the minimal subcurve of $C$ of arithmetic genus one, then the deformations of $f$ are unobstructed; in fact, the deformations \textit{over the stack of curves} are also unobstructed.
+It is natural to attempt to resolve the moduli space of stable maps, by contracting the genus one subcurve on which the map is constant.
+Whilst the moduli space of Gorenstein genus one curves is not smooth, a more sophisticated moduli problem, consisting of nodal curves $C$ together with a \textit{chosen contraction} to a Gorenstein curve $\bar{C}$, might be expected to resolve these singularities.
 The formation of such a moduli problem requires logarithmic geometry, and is achieved in~\cite[Section~3]{RSPW}.
@@
 
-When working with logarithmic geometries such as $(\mathbb P^N,H)$, as we do here, similar ideas may be expected to apply, but the deformation theory of maps becomes more delicate.
-Indeed, the logarithmic Euler sequence for this pair shows that the logarithmic tangent bundle is a quotient of $\mathcal O\oplus\mathcal O(1)^{\oplus N}$, and additional obstructions appear.
-In simple terms, there exist logarithmic maps to the pair $(\mathbb P^N,H)$ with obstructed logarithmic deformations, whose underlying ordinary stable map is unobstructed.
+When working with logarithmic targets such as $(\mathbb P^m,H)$, as we do here, similar ideas may be expected to apply, but the deformation theory of maps becomes more delicate.
+Indeed, the logarithmic Euler sequence for this pair shows that the logarithmic tangent bundle is a quotient of $\mathcal O\oplus\mathcal O(1)^{\oplus m}$, and additional obstructions appear.
+In simple terms: there exist logarithmic stable maps to the pair $(\mathbb P^m,H)$ with obstructed logarithmic deformations, whose underlying stable map to $\PP^m$ is unobstructed.
 
@@
 
-This is equivalent to \cite[Lemma 2.2]{SMY1}, where he describes the seminormalisation of an elliptic singularity as the data of a hyperplane in the Zariski cotangent space, not containing the coordinate lines.
+\noindent This is equivalent to \cite[Lemma 2.2]{SMY1}, where he describes the seminormalisation of an elliptic singularity as the data of a hyperplane in the Zariski cotangent space not containing the coordinate lines.
 We call \emph{moduli of attaching data} \cite[\S 2.2]{SMY2} (or \emph{crimping space}) the extra data needed to produce a singularity from its pointed normalisation.
@@
 \end{cor}
-One way to compactify it is by allowing \emph{sprouting} on the boundary, i.e.
+\noindent One way to compactify it is to allow \emph{sprouting} on the boundary, i.e.
 replacing a branch $R_i$ of the singularity with a strictly semistable component $\PP^1$ with the singularity at $0$ and the branch $R_i$ glued nodally at $\infty$.
@@
 There are other ways to look at these data; we recall a construction from linear algebra.
-Let $V=\sum_{i=1}^mL_i$ be the presentation of a vector space as the direct sum of $m$ lines.
-It is equivalent to give compatible isomorphisms $\theta_{i,j}\colon L_i\simeq L_j$ and a general line $\ell$ in $V$ (or a hyperplane in the dual vector space $V^\vee$).
+Let $V=\sum_{i=1}^mL_i$ be a presentation of a vector space as the direct sum of $m$ lines.
+Then the data of a general line $\ell$ in $V$ (or a general hyperplane in $V^\vee$) is equivalent to the data of compatible isomorphisms $\theta_{ij} \colon L_i \cong L_j$.
 Indeed, given a general line $\ell$, a vector $v\in\ell$ can be written as:
-\[v=a_1e_1+\ldots+a_me_m,\qquad a_i\neq 0\ \forall i=1,\ldots,m,\]
-for a fixed basis $\{e_i\in L_i\}$ of $V$. We can then define $\theta_{i,j}$ by:
-\[\theta_{i,j}(e_i)=\frac{a_j}{a_i}e_j;\]
-it is easy to see that it does not depend on any choice made. On the other hand, given the $\theta_{i,j}$, the line $\ell$ can be taken to be the graph of the morphism:
-\[(\theta_{1,2},\ldots,\theta_{1,m})\colon L_1\to L_2\oplus\ldots\oplus L_m.\]
-
-Lemma \ref{lem:pushout} provides a valuable characterisation of maps from an elliptic singularity $C$, that we are going to exploit in \S \ref{section reduced splitting}:
+\[v=a_1e_1+\ldots+a_me_m,\qquad \text{with $a_i\neq 0$ for all $i$}\]
+for a fixed basis $\{e_i\in L_i\}$ of $V$. We can then define $\theta_{ij}$ by
+\[\theta_{i,j}(e_i)=(a_j/a_i)\cdot e_j\]
+and it is easy to see that it does not depend on any of the choices. On the other hand, given the $\theta_{ij}$, the line $\ell$ can be taken to be the graph of the morphism:
+\[(\theta_{12},\ldots,\theta_{1m})\colon L_1\to L_2\oplus\ldots\oplus L_m.\]
+Thus the attaching data can be viewed as specifying an identification of tangent spaces of the pointed normalisation at the singularity.
+
+Lemma \ref{lem:pushout} provides a valuable characterisation of maps from an elliptic singularity $C$, which we will exploit in \S \ref{section reduced splitting}:
 \begin{cor}\label{cor:maps_from_elliptic_sing}
- A map $C\to X$ is the same as a map $C^\text{sn}\to X$ such that its differential sends $v$ to $0$.
+ A map $C\to X$ is the same as a map $C^\text{sn}\to X$ such that its differential sends $v \mapsto 0$.
 \end{cor}
-
-Line bundles on an elliptic $m$-fold point admit a similar description, see e.g. \cite[Lemma 7.5.12]{LiuQ}.
+\noindent Line bundles on an elliptic $m$-fold point admit a similar description, see e.g. \cite[Lemma 7.5.12]{LiuQ}.
 \begin{lemma}\label{lem:PicE}
- Let $C$ be a curve of arithmetic genus one containing an elliptic $m$-fold point. Then $\operatorname{Pic}^0(C)\simeq\mathbb G_{\text{a}}$.
+ Let $C$ be a curve of arithmetic genus one containing an elliptic $m$-fold point. Then $\operatorname{Pic}^0(C)\cong\mathbb G_{\text{a}}$.
 \end{lemma}
 
-\subsection{Absolute geometry: reminders} Let $\mathfrak M_{1,n}$ be the logarithmic algebraic stack of $n$-pointed prestable curves of genus one.
+\subsection{Absolute geometry: background} Let $\mathfrak M_{1,n}$ be the logarithmic algebraic stack of $n$-pointed prestable curves of genus one.
 We begin by recalling the logarithmic moduli spaces of genus one curves constructed in~\cite[\S 2 \& \S 4]{RSPW}.
@@
 
-The space of stable maps $\widetilde\VZ_{1,n}(\PP^N,d)$ from the universal nodal curve $\mathcal C$ over the stack $\mathfrak M_{1,n}^{\mathrm{cen}}$ is Deligne-Mumford and proper, with projective coarse moduli space.
+The space of stable maps $\widetilde\VZ_{1,n}(\PP^m,d)$ from the universal nodal curve $\mathcal C$ over the stack $\mathfrak M_{1,n}^{\mathrm{cen}}$ is Deligne-Mumford and proper, with projective coarse moduli space.
 A compatibility condition between the alignment and the map is required, namely that the circle of radius $\delta$ passes through \emph{at least one component of positive degree}.
-A stable map in this space is said to satisfy the \textbf{factorisation condition} if the map $\widetilde{\mathcal C}\to \mathcal C\to \mathbb P^N$ factors through the contraction $\widetilde{\mathcal C}\to \overline{\mathcal C}$.
+A stable map in this space is said to satisfy the \textbf{factorisation condition} if the map $\widetilde{\mathcal C}\to \mathcal C\to \mathbb P^m$ factors through the contraction $\widetilde{\mathcal C}\to \overline{\mathcal C}$.
 Maps that are not constant on any genus one subcurve of $\mathcal C$ automatically satisfy this condition; indeed, the contraction is an isomorphism in this case.
@@
 \begin{thm}[{\cite[Theorem B]{RSPW}}]
-The substack $\VZ_{1,n}(\mathbb P^N,d)$ of $\widetilde\VZ_{1,n}(\PP^N,d)$ parameterising maps to $\mathbb P^N$ that satisfy the factorisation condition is smooth and proper of the expected dimension.
+The substack $\VZ_{1,n}(\mathbb P^m,d)$ of $\widetilde\VZ_{1,n}(\PP^m,d)$ parameterising maps to $\mathbb P^m$ that satisfy the factorisation condition is smooth and proper of the expected dimension.
 \end{thm}
@@
 \begin{remark}[Constant maps]\label{rem: constant-maps}
-When the degree of the map is $1$, maps from smooth genus one curves to $\PP^N$ are constant.
+When the degree of the map is $1$, maps from smooth genus one curves to $\PP^m$ are constant.
 The interior of the moduli space of stable maps in this case is empty, though the compactification by stable maps is non-empty.
@@
 
-The remainder of this section lifts this construction to the category of relative maps to $(\mathbb P^N,H)$. The core result shows that two factorisation conditions remove the obstructions.
-
-\subsection{Relative geometry: compactification} Fix a hyperplane $H\subseteq \mathbb P^N$.
+The remainder of this section lifts this construction to the category of relative maps to $(\mathbb P^m,H)$. The core result shows that two factorisation conditions remove the obstructions.
+
+\subsection{Relative geometry: compactification} Fix a hyperplane $H\subseteq \mathbb P^m$.
 Let $\alpha$ be a partition of the degree $d>0$.
-Consider the moduli space $\mathcal M_{1,\alpha}^\circ(\mathbb P^N|H,d)$ of maps from smooth genus one curves $C\to \mathbb P^N$ that meet $H$ at finitely many marked points with vanishing orders given by the partition $\alpha$.
+Consider the moduli space $\mathcal M_{1,\alpha}^\circ(\mathbb P^m|H,d)$ of maps from smooth genus one curves $C\to \mathbb P^m$ that meet $H$ at finitely many marked points with vanishing orders given by the partition $\alpha$.
 This is a smooth, but non-proper Deligne--Mumford stack.
@@
 
-Let $\PP^N$ be endowed with the divisorial logarithmic structure induced by $H$.
-The moduli space $\overline{\mathcal{M}}^{\operatorname{log}}_{1,\alpha}(\mathbb P^N|H,d)$ is a fibred category over logarithmic schemes, whose fibre over $(S,M_S)$ is the groupoid of logarithmically smooth curves of genus one over $(S,M_S)$ equipped with a logarithmic map to $\mathbb P^N$ of degree $d$ and contact order $\alpha$.
+Let $\PP^m$ be endowed with the divisorial logarithmic structure induced by $H$.
+The moduli space $\overline{\mathcal{M}}^{\operatorname{log}}_{1,\alpha}(\mathbb P^m|H,d)$ is a fibred category over logarithmic schemes, whose fibre over $(S,M_S)$ is the groupoid of logarithmically smooth curves of genus one over $(S,M_S)$ equipped with a logarithmic map to $\mathbb P^m$ of degree $d$ and contact order $\alpha$.
 It is a fundamental fact in the subject that this category is representable by a proper algebraic stack with logarithmic structure, parameterising minimal objects~\cite{ChenLog}.
@@
 $$
-\overline{\mathcal M}^{\mathrm{log}}_{1,\alpha}(\mathbb P^N|H,d) \to \overline{\mathcal M}_{1,n}(\mathbb P^N,d).
+\overline{\mathcal M}^{\mathrm{log}}_{1,\alpha}(\mathbb P^m|H,d) \to \overline{\mathcal M}_{1,n}(\mathbb P^m,d).
 $$
@@
 \begin{comment}
-As in the absolute setting, we consider the space of logarithmic morphisms from the universal curve $\mathcal{C} \to \mathfrak{M}_{1,n}^{\mathrm{cen}}$ to the logarithmic scheme $(\PP^N,H)$.
-We impose a compatibility condition, which says that the radius must pass through a vertex of positive degree in $\PP^N$ and contain only vertices of degree zero in its strict interior.
+As in the absolute setting, we consider the space of logarithmic morphisms from the universal curve $\mathcal{C} \to \mathfrak{M}_{1,n}^{\mathrm{cen}}$ to the logarithmic scheme $(\PP^m,H)$.
+We impose a compatibility condition, which says that the radius must pass through a vertex of positive degree in $\PP^m$ and contain only vertices of degree zero in its strict interior.
 In this way we obtain a logarithmic modification
-\begin{equation*} \widetilde\VZ_{1,\alpha}(\PP^N|H,d) \to \ol\Mcal^{\mathrm{log}}_{1,\alpha}(\PP^N|H,d)\end{equation*}
-which we refer to as the \textbf{moduli space of centrally aligned maps to $(\PP^N,H)$}.
-It is a logarithmic modification of $\overline{\mathcal M}^{\mathrm{log}}_{1,\alpha}(\mathbb P^N|H,d)$.
-We note that by definition this space maps down to $\widetilde\VZ_{1,n}(\PP^N,d)$, by forgetting the logarithmic structure of the target.
+\begin{equation*} \widetilde\VZ_{1,\alpha}(\PP^m|H,d) \to \ol\Mcal^{\mathrm{log}}_{1,\alpha}(\PP^m|H,d)\end{equation*}
+which we refer to as the \textbf{moduli space of centrally aligned maps to $(\PP^m,H)$}.
+It is a logarithmic modification of $\overline{\mathcal M}^{\mathrm{log}}_{1,\alpha}(\mathbb P^m|H,d)$.
+We note that by definition this space maps down to $\widetilde\VZ_{1,n}(\PP^m,d)$, by forgetting the logarithmic structure of the target.
 \end{comment}
@@
 
-\begin{comment}Our next task is to pick out a non-singular principal component in $\widetilde{\VZ}_{1,\alpha}(\mathbb P^N|H,d)$.
-The principal component of this space, consisting of the closure of the space of maps from nonsingular curves, maps into the principal component of $\widetilde\VZ_{1,n}(\PP^N,d)$.
+\begin{comment}Our next task is to pick out a non-singular principal component in $\widetilde{\VZ}_{1,\alpha}(\mathbb P^m|H,d)$.
+The principal component of this space, consisting of the closure of the space of maps from nonsingular curves, maps into the principal component of $\widetilde\VZ_{1,n}(\PP^m,d)$.
 Indeed, smoothable logarithmic maps are, in particular, smoothable as ordinary maps.
@@
 In order to make the obstruction theory more geometric, we expand the target.
-To elucidate the connection with the static target, consider a logarithmic stable map $[C\to (\mathbb P^N,H)]$ over $\mathrm{Spec} \ (\mathbb N\to \mathbb C)$.
+To elucidate the connection with the static target, consider a logarithmic stable map $[C\to (\mathbb P^m,H)]$ over $\mathrm{Spec} \ (\mathbb N\to \mathbb C)$.
 At the level of tropicalizations, there is a map of cone complexes:
@@
 \[
-\widetilde C\to \mathbb P^N[s],
+\widetilde C\to \mathbb P^m[s],
 \]
 see~\cite{AW}.
-Here the latter is the $s$-times iterated deformation to the normal cone of $H$ in $\mathbb P^N$.
+Here the latter is the $s$-times iterated deformation to the normal cone of $H$ in $\mathbb P^m$.
 The irreducible components of the target are in bijection with the vertices in $\widetilde{\mathbb R}_{\geq 0}$.
@@
 
-The result is a logarithmic stable map to an expanded target $\mathbb P^N[s]$, together with a contraction to the main target component $\mathbb P^N[s]\to\mathbb P^N$.
+The result is a logarithmic stable map to an expanded target $\mathbb P^m[s]$, together with a contraction to the main target component $\mathbb P^m[s]\to\mathbb P^m$.
 Two maps are considered equivalent if they differ by $\Gm$-scaling the target at higher level.
@@
 We typically work with expansions for convenience, and use the notation
-$\ol\Mcal_{1,\alpha}(\PP^N|H,d)$
+$\ol\Mcal_{1,\alpha}(\PP^m|H,d)$
 for Kim's space of logarithmic stable maps.
 
-\subsection{Relative geometry: alignment} We consider the space of logarithmic morphisms from the universal curve $\mathcal{C} \to \mathfrak{M}_{1,n}^{\mathrm{cen}}$ to the logarithmic scheme $(\PP^N,H)$.
-As in the absolute case, we require the radius to pass through a vertex of positive degree in $\PP^N$ and contain only vertices of degree zero in its strict interior.
+\subsection{Relative geometry: alignment} We consider the space of logarithmic morphisms from the universal curve $\mathcal{C} \to \mathfrak{M}_{1,n}^{\mathrm{cen}}$ to the logarithmic scheme $(\PP^m,H)$.
+As in the absolute case, we require the radius to pass through a vertex of positive degree in $\PP^m$ and contain only vertices of degree zero in its strict interior.
 In this way we obtain a logarithmic modification of the Abramovich--Chen--Gross--Siebert space.
 If we further perform the subdivisions of target and source outlined in the previous section, we obtain a logarithmic modification of Kim's space:
-\begin{equation*} \widetilde\VZ_{1,\alpha}(\PP^N|H,d) \to \ol\Mcal_{1,\alpha}(\PP^N|H,d)\end{equation*}
-which we refer to as the \textbf{moduli space of centrally aligned maps} to $(\PP^N,H)$.
+\begin{equation*} \widetilde\VZ_{1,\alpha}(\PP^m|H,d) \to \ol\Mcal_{1,\alpha}(\PP^m|H,d)\end{equation*}
+which we refer to as the \textbf{moduli space of centrally aligned maps} to $(\PP^m,H)$.
 This space parametrises transverse logarithmic maps to the expanded target with an alignment which is compatible with the map.
 Because of this compatibility condition, there is a morphism
-\begin{equation*} \widetilde\VZ_{1,\alpha}(\PP^N|H,d) \to \widetilde\VZ_{1,n}(\PP^N,d)\end{equation*}
+\begin{equation*} \widetilde\VZ_{1,\alpha}(\PP^m|H,d) \to \widetilde\VZ_{1,n}(\PP^m,d)\end{equation*}
 obtained by forgetting the logarithmic structure on the target and collapsing the map.
 
-\subsection{Relative geometry: factorisation}\label{subsection factorisation} Let $[C\to \mathbb P^N[s]\to \mathbb P^N]$ be a centrally aligned logarithmic map.
-Recall that $\mathbb P^N[s]$ consists of a union of $\mathbb P^N$ with $s$ copies of the projective bundle $\mathbb{P} = \mathbb P(\mathcal O_H\oplus \mathcal O_H(1))$.
+\subsection{Relative geometry: factorisation}\label{subsection factorisation} Let $[C\to \mathbb P^m[s]\to \mathbb P^m]$ be a centrally aligned logarithmic map.
+Recall that $\mathbb P^m[s]$ consists of a union of $\mathbb P^m$ with $s$ copies of the projective bundle $\mathbb{P} = \mathbb P(\mathcal O_H\oplus \mathcal O_H(1))$.
 We refer to these latter components as \textbf{the higher levels}.
-Thus, we will say that a subcurve $D\subseteq C$ \textbf{maps to higher level} if the composite $C\to \mathbb P^N$ maps $D$ into $H\subset \mathbb P^N$.
-
-Let $D_F\subseteq C$ be the maximal genus one subcurve which is mapped to a higher level and contracted by the map $C\to \mathbb P^N[s]$.
+Thus, we will say that a subcurve $D\subseteq C$ \textbf{maps to higher level} if the composite $C\to \mathbb P^m$ maps $D$ into $H\subset \mathbb P^m$.
+
+Let $D_F\subseteq C$ be the maximal genus one subcurve which is mapped to a higher level and contracted by the map $C\to \mathbb P^m[s]$.
 Let $\delta_F$ denote the distance from the core to the nearest component of $C \setminus D_F$.
-Similarly let $D_B\subseteq C$ be the maximal genus one subcurve that is contracted by the collapsed map to $\mathbb P^N$, and let $\delta_B$ be the associated radius.
-This coincides with the radius of the underlying map to $\mathbb P^N$.
+Similarly let $D_B\subseteq C$ be the maximal genus one subcurve that is contracted by the collapsed map to $\mathbb P^m$, and let $\delta_B$ be the associated radius.
+This coincides with the radius of the underlying map to $\mathbb P^m$.
 Of course, $\delta_F\leq \delta_B$, so $(C,\delta_F)$ is centrally aligned as well.
@@
 \begin{definition}
-The map $f\colon C\to \mathbb P^N[s]$ \textbf{factors completely} if 
+The map $f\colon C\to \mathbb P^m[s]$ \textbf{factors completely} if 
 \begin{enumerate}
 \item $f$ factors through $\overline C_F$ and it is non-constant on its core,
-\item letting $f_B\colon C\to\PP^N$ denote the composite of $f$ with the collapsing map $\mathbb P^N[s]\to\mathbb P^N$, the map $f_B$ factors through $\overline C_B$ and it is non-constant on its core.
+\item letting $f_B\colon C\to\PP^m$ denote the composite of $f$ with the collapsing map $\mathbb P^m[s]\to\mathbb P^m$, the map $f_B$ factors through $\overline C_B$ and it is non-constant on its core.
 \end{enumerate}
@@
 \begin{rem}
- The factorisation conditions are understood to be satisfied when $C\to \mathbb P^N[s]$ (resp. $C\to \mathbb P^N$) does not contract a genus one subcurve. 
+ The factorisation conditions are understood to be satisfied when $C\to \mathbb P^m[s]$ (resp. $C\to \mathbb P^m$) does not contract a genus one subcurve. 
 \end{rem}
@@
 Let
-\begin{equation*} \VZ_{1,\alpha}(\mathbb P^N|H,d) \subseteq \widetilde\VZ_{1,\alpha}(\PP^N|H,d) \end{equation*}
+\begin{equation*} \VZ_{1,\alpha}(\mathbb P^m|H,d) \subseteq \widetilde\VZ_{1,\alpha}(\PP^m|H,d) \end{equation*}
 be the stack of maps from centrally aligned curves to expansions that factor completely.
 
-If $[C\to \mathbb P^N[s]\to \mathbb P^N]$ is a family of centrally aligned maps over $S$ that factors completely, there is a moduli map $S\to \VZ_{1,n}(\mathbb P^N,d)$, to the principal component of the space of absolute maps.
+If $[C\to \mathbb P^m[s]\to \mathbb P^m]$ is a family of centrally aligned maps over $S$ that factors completely, there is a moduli map $S\to \VZ_{1,n}(\mathbb P^m,d)$, to the principal component of the space of absolute maps.
 
 \begin{thm}\label{thm: log-smoothness}
-The stack $\VZ_{1,\alpha}(\mathbb P^N|H,d)$ is logarithmically smooth and proper of the expected dimension.
+The stack $\VZ_{1,\alpha}(\mathbb P^m|H,d)$ is logarithmically smooth and proper of the expected dimension.
 \end{thm}
 
-As noted in Remark~\ref{rem: constant-maps}, maps from elliptic curves to $\PP^N$ will always be taken to have degree at least $2$, ensuring that the main component is non-empty.
+As noted in Remark~\ref{rem: constant-maps}, maps from elliptic curves to $\PP^m$ will always be taken to have degree at least $2$, ensuring that the main component is non-empty.
 
 \begin{proof}
-We examine the geometry of the space of maps to $(\PP^N|H)$ by utilising the forgetful morphism
+We examine the geometry of the space of maps to $(\PP^m|H)$ by utilising the forgetful morphism
 \[
-\nu\colon \VZ_{1,\alpha}(\mathbb P^N|H,d)\to \VZ_{1,n}(\mathbb P^N,d),
+\nu\colon \VZ_{1,\alpha}(\mathbb P^m|H,d)\to \VZ_{1,n}(\mathbb P^m,d),
 \]
 which remembers only the stabilisation of the collapsed map.
-To see that such a forgetful morphism exists, we have already observed that, for a map $[C\to \mathbb P^N[s]\to \mathbb P^N]$, the stabilised composite map is certainly centrally aligned; moreover, it satisfies the factorisation condition by assumption.
-
-The moduli space $\VZ_{1,\alpha}(\mathbb P^N|H,d)$ is proper.
+To see that such a forgetful morphism exists, we have already observed that, for a map $[C\to \mathbb P^m[s]\to \mathbb P^m]$, the stabilised composite map is certainly centrally aligned; moreover, it satisfies the factorisation condition by assumption.
+
+The moduli space $\VZ_{1,\alpha}(\mathbb P^m|H,d)$ is proper.
 Indeed, the verification of the valuative criterion follows from Vakil's Lemma~\cite[Lemma~5.9]{Vre}.
@@
 Assume now that the elliptic curve maps into higher level.
-Note that the relative logarithmic tangent bundle of the expansion, over the base $\mathbb P^N$ is a trivial line bundle of rank $1$, as the fibres are toric.
+Note that the relative logarithmic tangent bundle of the expansion, over the base $\mathbb P^m$ is a trivial line bundle of rank $1$, as the fibres are toric.
 Consider an $S$-family of maps.
@@
 C \ar[r] & \overline{C}_F \ar[r] \ar[d] & \overline{C}_B \ar[d] \\
-& \mathbb P^N[s] \ar[r] & \mathbb P^N
+& \mathbb P^m[s] \ar[r] & \mathbb P^m
 \ecd
@@
 More precisely, consider a strict square-zero extension of $S$, and a deformation of the map $(C,f_B)$ satisfying the factorisation condition.
-Since the deformation is strict, there is a canonically induced deformation of the expansion $\mathbb P^N[s]$.
-The corresponding element in $\mathrm{Obs}(f/(C,f_B))$ is the obstruction to lifting the deformation of $(C,f_B)$ to this canonical deformation of $\mathbb P^N[s]$ over $\mathbb P^N$.
+Since the deformation is strict, there is a canonically induced deformation of the expansion $\mathbb P^m[s]$.
+The corresponding element in $\mathrm{Obs}(f/(C,f_B))$ is the obstruction to lifting the deformation of $(C,f_B)$ to this canonical deformation of $\mathbb P^m[s]$ over $\mathbb P^m$.
 By comparing the cotangent complexes of the source, target, and fibre of the morphism $\nu$, we see that the cokernel of this map are the absolute logarithmic obstructions for the map.
@@
 Consider the manner in which $H^1(\overline{C}_F,\mathcal O_{\overline{C}_F})$ functions as the obstruction group for the lifting.
-Near the minimal genus one subcurve $D_F$ of $C$, in order to lift the map from $\mathbb P^N$ to the expansion, we must provide a rational function on $D_F$ with poles bounded by the divisor associated to the tropicalization, i.e.
+Near the minimal genus one subcurve $D_F$ of $C$, in order to lift the map from $\mathbb P^m$ to the expansion, we must provide a rational function on $D_F$ with poles bounded by the divisor associated to the tropicalization, i.e.
 if $\alpha$ is the piecewise linear function giving this tropical map, the lifting is described by a section of the associated bundle $\mathcal O_{C}(-\alpha)$.
@@
 Infinitesimally moving the point $x_i$ produces a nontrivial deformation of the line bundle $\mathcal O_{C}(-\alpha)$.
-The moduli space $\VZ_{1,n}(\mathbb P^N,d)$ is a logarithmically smooth fibration over the universal Picard stack over the stack of centrally aligned $n$-pointed genus one curves~\cite[Remark~4.5.3]{RSPW}.
+The moduli space $\VZ_{1,n}(\mathbb P^m,d)$ is a logarithmically smooth fibration over the universal Picard stack over the stack of centrally aligned $n$-pointed genus one curves~\cite[Remark~4.5.3]{RSPW}.
 As a consequence, it is possible to find a logarithmic deformation of the map $(C,f_B)$ that induces the deformation of the line bundle that is given by infinitesimal motion.
@@
 The absolute obstructions, which are the cokernel of this map therefore vanish, and the result follows.
-%Consider an $S$-family of expanded maps $[F: C\to \mathbb P^N[s]$.
+%Consider an $S$-family of expanded maps $[F: C\to \mathbb P^m[s]$.
 Choose $N$ generic hyperplanes in and let $\Delta = \{H\}\cup\{H_1,\ldots,H_N}$ be this set of hyperplanes.
-There is a morphism of logarithmic schemes $(\mathbb P^N,\Delta)\to (\mathbb P^N,H)$.
-This induces a new expansion $\mathbb P^N[\Delta,s]$.
+There is a morphism of logarithmic schemes $(\mathbb P^m,\Delta)\to (\mathbb P^m,H)$.
+This induces a new expansion $\mathbb P^m[\Delta,s]$.
 Moreover, by the genericity of the $H_i$, they each intersect the image of $C$ in finitely many reduced points.
@@
 %\[
-%F': C'\to \mathbb P^N[\Delta,s].
+%F': C'\to \mathbb P^m[\Delta,s].
 %\]
@@
 \[
-\nu\colon \VZ_{1,\alpha}(\mathbb P^N|H,d)\to \VZ_{1,n}(\mathbb P^N,d),
+\nu\colon \VZ_{1,\alpha}(\mathbb P^m|H,d)\to \VZ_{1,n}(\mathbb P^m,d),
 \]
-remembering only the stabilisation of the composite $f_B\colon C\to\PP^N[s]\to\PP^N$.
-A priori, this is in $\overline{\pazocal M}_1(\PP^N,d)$, but in fact by assumption $(C,\delta_B)$ is centrally aligned, and $f_B$ factors through $\overline C_B$, as we have already remarked.
-
-The expanded target $\PP^N[s]$ is logarithmically \'etale over $\PP^N$ with the divisorial log structure associated to $H$, so it is equivalent to study the deformation theory of the unexpanded map to $(\PP^N,H)$.
-The logarithmic morphism $(\PP^N,H)\to \PP^N$ induces an exact sequence of log tangent bundles:
-\[0\to T_{\PP^N}(-\operatorname{log}H)\to T_{\PP^N}\to\OO_H(H)\to 0,\]
+remembering only the stabilisation of the composite $f_B\colon C\to\PP^m[s]\to\PP^m$.
+A priori, this is in $\overline{\pazocal M}_1(\PP^m,d)$, but in fact by assumption $(C,\delta_B)$ is centrally aligned, and $f_B$ factors through $\overline C_B$, as we have already remarked.
+
+The expanded target $\PP^m[s]$ is logarithmically \'etale over $\PP^m$ with the divisorial log structure associated to $H$, so it is equivalent to study the deformation theory of the unexpanded map to $(\PP^m,H)$.
+The logarithmic morphism $(\PP^m,H)\to \PP^m$ induces an exact sequence of log tangent bundles:
+\[0\to T_{\PP^m}(-\operatorname{log}H)\to T_{\PP^m}\to\OO_H(H)\to 0,\]
 relating the absolute and relative obstruction theories.
@@
 
-Let $f\colon C\to\PP^N[s]$ over the base $S$ be a possibly obstructed map to the expansion that factors completely, and let $S^\prime$ be a strict square-zero extension of the base.
+Let $f\colon C\to\PP^m[s]$ over the base $S$ be a possibly obstructed map to the expansion that factors completely, and let $S^\prime$ be a strict square-zero extension of the base.
 The deformation problem is local, so we may as well suppose that $\overline M_S^{\text{gp}}$ is a constant sheaf of monoids with stalk $\overline M_{S,s}^{\text{gp}}=:Q$, for a geometric point $s\in S$.
 Note that sections of $M_S$ such as $\delta_B$ and $\delta_F$ extend automatically due to strictness.
-Moreover, it is equivalent to deform $f$ or $f_F\colon\overline C_F\to\PP^N_S$, where $\overline C_F$ is given the trivial logarithmic structure around the elliptic singularity.
-
-The map $f_F\colon \overline C_F\to\PP^N[s]$ induces a tropical map $\alpha\colon\plC_F\to\RR_{\geq 0}\times\sigma_Q$, that we want to think of as a section $\alpha\in H^0(\overline C_F,\overline M_C^{\text{gp}})$.
+Moreover, it is equivalent to deform $f$ or $f_F\colon\overline C_F\to\PP^m_S$, where $\overline C_F$ is given the trivial logarithmic structure around the elliptic singularity.
+
+The map $f_F\colon \overline C_F\to\PP^m[s]$ induces a tropical map $\alpha\colon\plC_F\to\RR_{\geq 0}\times\sigma_Q$, that we want to think of as a section $\alpha\in H^0(\overline C_F,\overline M_C^{\text{gp}})$.
 With notation as above, we obtain a trivialisation of the line bundle $\OO_{\overline C_F}(-\alpha)$ upon restriction to $E$.
@@
 \begin{cor}
-The logarithmically smooth stack $\VZ_{1,\alpha}(\mathbb P^N|H,d)$ has at worst orbifold singularities, i.e. admits a non-representable cover by a smooth Deligne--Mumford stack.
+The logarithmically smooth stack $\VZ_{1,\alpha}(\mathbb P^m|H,d)$ has at worst orbifold singularities, i.e. admits a non-representable cover by a smooth Deligne--Mumford stack.
 \end{cor}
 
-\textcolor{red}{Luca's rewrite of the Corollary: Up to a generalised root construction, $\VZ_{1,\alpha}(\mathbb P^N|H,d)$ is a smooth Deligne-Mumford stack.}
+\textcolor{red}{Luca's rewrite of the Corollary: Up to a generalised root construction, $\VZ_{1,\alpha}(\mathbb P^m|H,d)$ is a smooth Deligne-Mumford stack.}
 
 \begin{proof}
-Since $\VZ_{1,\alpha}(\mathbb P^N|H,d)$ is logarithmically smooth, it will suffice to show that the cones of its tropicalization are simplicial.
-To see this, consider a logarithmic stable map to an expansion $C\to \mathbb P^N[s]$ without a central alignment.
+Since $\VZ_{1,\alpha}(\mathbb P^m|H,d)$ is logarithmically smooth, it will suffice to show that the cones of its tropicalization are simplicial.
+To see this, consider a logarithmic stable map to an expansion $C\to \mathbb P^m[s]$ without a central alignment.
 The tropical moduli cone obtained as the dual of the minimal base monoid can be identified with $\mathbb R_{\geq 0}^{s}$, see for instance~\cite[Section~2.2]{ChenDegeneration}.
 The alignment procedure is an iterated barycentric subdivision at the level of tropical moduli spaces, as explained in~\cite[Section 4.6]{RSPW}, and such subdivisions preserve the property of being simplicial.
-We conclude from this that the blowup $\widetilde{\VZ}^{\mathrm{exp}}_{1,\alpha}(\mathbb P^N|H,d)$ obtained by centrally aligning Kim's spaces has simplicial cones.
-The morphism $\VZ_{1,\alpha}(\mathbb P^N|H,d)\to \widetilde{\VZ}^{\mathrm{exp}}_{1,\alpha}(\mathbb P^N|H,d)$ is strict, so the cones of $\VZ_{1,\alpha}(\mathbb P^N|H,d)$ are simplicial, as claimed.
+We conclude from this that the blowup $\widetilde{\VZ}^{\mathrm{exp}}_{1,\alpha}(\mathbb P^m|H,d)$ obtained by centrally aligning Kim's spaces has simplicial cones.
+The morphism $\VZ_{1,\alpha}(\mathbb P^m|H,d)\to \widetilde{\VZ}^{\mathrm{exp}}_{1,\alpha}(\mathbb P^m|H,d)$ is strict, so the cones of $\VZ_{1,\alpha}(\mathbb P^m|H,d)$ are simplicial, as claimed.
 \end{proof}
 
-\subsection{Rubber variants}\label{subsection rubber} We require a ``rubber'' variant of the space of maps $\VZ_{1,\alpha}(\mathbb P^N|H,d)$, where the curve is contained in the higher levels.
-
-Let $\mathbb P$ denote the projective bundle $\mathbb P(\mathcal O(1)\oplus\mathcal O)$ on $H\simeq\mathbb P^{N-1}$.
+\subsection{Rubber variants}\label{subsection rubber} We require a ``rubber'' variant of the space of maps $\VZ_{1,\alpha}(\mathbb P^m|H,d)$, where the curve is contained in the higher levels.
+
+Let $\mathbb P$ denote the projective bundle $\mathbb P(\mathcal O(1)\oplus\mathcal O)$ on $H\cong\mathbb P^{N-1}$.
 Equip this space with the logarithmic structure coming from the $0$ and $\infty$ sections of the bundle.
@@
 This moduli space will typically be non-equidimensional, but we equip it with a virtual class as follows.
-The divisor $Y$ defines an embedding $X \hookrightarrow \PP^N$, with $Y=X\cap H$ for some hyperplane $H$.
+The divisor $Y$ defines an embedding $X \hookrightarrow \PP^m$, with $Y=X\cap H$ for some hyperplane $H$.
 
@@
 \bcd
-\VZ_{1,\alpha}(X|Y,\beta) \ar[r] \ar[d] \ar[rd,phantom,"\square"] & \VZ_{1,\alpha}(\PP^N|H,d) \ar[d] \\
-\VZ_{1,n}(X,\beta) \ar[r,"i"] & \VZ_{1,n}(\PP^N,d).
+\VZ_{1,\alpha}(X|Y,\beta) \ar[r] \ar[d] \ar[rd,phantom,"\square"] & \VZ_{1,\alpha}(\PP^m|H,d) \ar[d] \\
+\VZ_{1,n}(X,\beta) \ar[r,"i"] & \VZ_{1,n}(\PP^m,d).
 \ecd
@@
 
-Since $\VZ_{1,n}(\PP^N,d)$ is smooth and $\VZ_{1,n}(X,\beta)$ carries a natural virtual class \cite[Theorem 4.4.1]{RSPW}, the diagonal of $\VZ_{1,n}(\PP^N,d)$ defines a pullback~\cite[Appendix A]{BattistellaNabijou}, and therefore the virtual class on the space of maps to $(X,Y)$:
-\begin{equation*} \virt{\VZ_{1,\alpha}(X|Y,\beta)} := i_\Delta^! [\VZ_{1,\alpha}(\PP^N|H,d)]. \end{equation*}
+Since $\VZ_{1,n}(\PP^m,d)$ is smooth and $\VZ_{1,n}(X,\beta)$ carries a natural virtual class \cite[Theorem 4.4.1]{RSPW}, the diagonal of $\VZ_{1,n}(\PP^m,d)$ defines a pullback~\cite[Appendix A]{BattistellaNabijou}, and therefore the virtual class on the space of maps to $(X,Y)$:
+\begin{equation*} \virt{\VZ_{1,\alpha}(X|Y,\beta)} := i_\Delta^! [\VZ_{1,\alpha}(\PP^m|H,d)]. \end{equation*}
 Note that this is parallel to the virtual formalism in~\cite{Ga}.
@@
 
-\noindent The logarithmic smoothness of Theorem~\ref{thm: log-smoothness} implies that $\VZ_{1,\alpha}(\mathbb P^N|H,d)$ is an orbifold toroidal embedding.
+\noindent The logarithmic smoothness of Theorem~\ref{thm: log-smoothness} implies that $\VZ_{1,\alpha}(\mathbb P^m|H,d)$ is an orbifold toroidal embedding.
 The irreducible components of its boundary stratify the space, as we now describe.
@@
 \begin{prop}\label{prop: well-spaced}
-Let $[C\to \mathbb P^N]$ be a logarithmic stable map from a centrally aligned curve to an expansion, that factors completely. Then the tropicalization $\plC\to \mathbb R_{\geq 0}$ is well-spaced.
+Let $[C\to \mathbb P^m]$ be a logarithmic stable map from a centrally aligned curve to an expansion, that factors completely. Then the tropicalization $\plC\to \mathbb R_{\geq 0}$ is well-spaced.
 \end{prop}
@@
 cit.
-We may focus on a single component of the expansion $\mathbb P^N[s]$ that contains the image of a contracted genus one subcurve, as this is the only relevant case.
+We may focus on a single component of the expansion $\mathbb P^m[s]$ that contains the image of a contracted genus one subcurve, as this is the only relevant case.
 We may thus replace the target with the projective bundle $\mathbb P(\mathcal O(1)\oplus \mathcal O)$ over $\mathbb P^{N-1}$ equipped with the divisorial logarithmic structure from the $0$ and $\infty$ sections.
@@
 Let $\Sigma^{\mathrm{log}}$ be the tropical moduli space of genus one tropical stable maps to $\mathbb R_{\geq 0}$.
-This is naturally identified with the tropicalization (in the logarithmic sense) of the Abramovich--Chen--Gross--Siebert space of logarithmic stable maps to the pair $(\mathbb P^N,H)$.
+This is naturally identified with the tropicalization (in the logarithmic sense) of the Abramovich--Chen--Gross--Siebert space of logarithmic stable maps to the pair $(\mathbb P^m,H)$.
 \\
@@
 The combinatorial types of such \textbf{image-ordered} maps produce the cones of a subdivision of $\Sigma^{\mathrm{log}}$ which we denote $\Sigma^{\mathrm{Kim}}$.
-As the notation suggests, $\Sigma^{\Kim}$ is the tropicalization of Kim's moduli space of logarithmic maps to $(\PP^N,H)$.\\
+As the notation suggests, $\Sigma^{\Kim}$ is the tropicalization of Kim's moduli space of logarithmic maps to $(\PP^m,H)$.\\
 
@@
 \noindent
-\textbf{Step 4}. Let $\Sigma_{1,\alpha}(\mathbb P^N|H,d)$ be the subcomplex of $\Sigma^{\mathrm{cen}}$ consisting of well-spaced tropical maps.
+\textbf{Step 4}. Let $\Sigma_{1,\alpha}(\mathbb P^m|H,d)$ be the subcomplex of $\Sigma^{\mathrm{cen}}$ consisting of well-spaced tropical maps.
 
@@
 The cone complex $
-\Sigma_{1,\alpha}(\mathbb P^N|H,d)$ is the fan of the toroidal embedding $
-\VZ_{1,\alpha}(\mathbb P^N|H,d)$. In particular, the codimension $k$ strata of $
-\VZ_{1,\alpha}(\mathbb P^N|H,d)$ are in inclusion reversing bijection with the dimension $k$ cones in $
-\Sigma_{1,\alpha}(\mathbb P^N|H,d)$.
+\Sigma_{1,\alpha}(\mathbb P^m|H,d)$ is the fan of the toroidal embedding $
+\VZ_{1,\alpha}(\mathbb P^m|H,d)$. In particular, the codimension $k$ strata of $
+\VZ_{1,\alpha}(\mathbb P^m|H,d)$ are in inclusion reversing bijection with the dimension $k$ cones in $
+\Sigma_{1,\alpha}(\mathbb P^m|H,d)$.
 \end{prop}
@@
 The construction above has been given to mimic the construction of the space $
-\VZ_{1,\alpha}(\mathbb P^N|H,d)$.
-Specifically, the fact that $\Sigma^{\mathrm{cen}}$ is the cone complex attached to the logarithmic stack $\widetilde{\VZ}_{1,\alpha}(\mathbb P^N|H,d)$ of centrally aligned maps to expansions, follows from its description as a subcategory of the fibred category (over logarithmic schemes) of $\mathcal M^{\mathrm{log}}_{1,\alpha}(\mathbb P^N|H,d)$.
+\VZ_{1,\alpha}(\mathbb P^m|H,d)$.
+Specifically, the fact that $\Sigma^{\mathrm{cen}}$ is the cone complex attached to the logarithmic stack $\widetilde{\VZ}_{1,\alpha}(\mathbb P^m|H,d)$ of centrally aligned maps to expansions, follows from its description as a subcategory of the fibred category (over logarithmic schemes) of $\mathcal M^{\mathrm{log}}_{1,\alpha}(\mathbb P^m|H,d)$.
 To complete the result, note that $
-\VZ_{1,\alpha}(\mathbb P^N|H,d)$ has a strict map to $
-\VZ_{1,\alpha}(\mathbb P^N|H,d)$, so its cone complex is a subcomplex of $\Sigma^{\mathrm{cen}}$.
+\VZ_{1,\alpha}(\mathbb P^m|H,d)$ has a strict map to $
+\VZ_{1,\alpha}(\mathbb P^m|H,d)$, so its cone complex is a subcomplex of $\Sigma^{\mathrm{cen}}$.
 The fact that it is contained in the subcomplex of well-spaced curves is immediate from Proposition~\ref{prop: well-spaced}.
@@
 
-\subsection{Indexing the strata} \label{subsection indexing strata} The dimension-$k$ cones in $\Sigma_{1,\alpha}(\PP^N|H,d)$ can be enumerated as follows.
+\subsection{Indexing the strata} \label{subsection indexing strata} The dimension-$k$ cones in $\Sigma_{1,\alpha}(\PP^m|H,d)$ can be enumerated as follows.
 First, the cones in $\Sigma=\Sigma^{\Kim}$ are indexed by \textbf{combinatorial types} of tropical maps to $\RR_{\geq 0}$.
@@
 The corresponding cone $\sigma \in \Sigma^{\operatorname{Kim}}$ is then given by the resulting moduli space of tropical maps, given by choices of edge lengths on source and target which produce a continuous tropical map.
-Given $\sigma\in \Sigma^{\operatorname{Kim}}$ we then produce all the cones in $\Sigma_{1,\alpha}(\PP^N|H,d)$ mapping to $\sigma$ by performing Steps 3--4 outlined above.
+Given $\sigma\in \Sigma^{\operatorname{Kim}}$ we then produce all the cones in $\Sigma_{1,\alpha}(\PP^m|H,d)$ mapping to $\sigma$ by performing Steps 3--4 outlined above.
 This amounts to a subdivision of $\sigma$.
 In this process, new cones are created which map into larger-dimensional cones of $\Sigma^{\operatorname{Kim}}$.
-The process for enumerating the codimension $k$ strata of $\VZ_{1,\alpha}(\PP^N|H,d)$ is therefore:
+The process for enumerating the codimension $k$ strata of $\VZ_{1,\alpha}(\PP^m|H,d)$ is therefore:
 \begin{enumerate}
@@
 
-\section{Degeneration of contact order}\label{Section Gathmann line bundle} Consider the moduli space $\VZ_{1,\alpha}(\PP^N|H,d)$ of relative maps that factor completely.
+\section{Degeneration of contact order}\label{Section Gathmann line bundle} Consider the moduli space $\VZ_{1,\alpha}(\PP^m|H,d)$ of relative maps that factor completely.
 \begin{dfn}
- For each marking $x_k$, consider the locus $\Dcal_{1,\alpha,k}(\PP^N|H,d) \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$ where $x_k$ belongs to an \textbf{internal component} of the collapsed map, i.e.
+ For each marking $x_k$, consider the locus $\Dcal_{1,\alpha,k}(\PP^m|H,d) \subseteq \VZ_{1,\alpha}(\PP^m|H,d)$ where $x_k$ belongs to an \textbf{internal component} of the collapsed map, i.e.
 a component of the curve that is mapped into $H$.
@@
 %\noindent Equivalently, for the expanded map, $x_k$ is mapped to a higher level and does not belong to a \emph{trivial bubble} component.
-\noindent In this section, we use the logarithmic structure on $\VZ_{1,\alpha}(\PP^N|H,d)$ to construct a line bundle $\Lcal_k$ and section $s_k$ which vanishes precisely along $\Dcal_{1,\alpha,k}(\PP^N|H,d)$.
-We use the correspondence with tropical geometry to identify $\cchern_1(\Lcal_k)$ in terms of tautological classes on $\VZ_{1,\alpha}(\PP^N|H,d)$, and to compute the vanishing order of $s_k$ along the components of $\Dcal_{1,\alpha,k}(\PP^N|H,d)$.
-Combined with the relative splitting formulas from the next section, this produces a recursion relation inside $\VZ_{1,\alpha}(\PP^N|H,d)$
-
-The pair $(\Lcal_k,s_k)$ is most naturally constructed on the moduli space $\MLog_{1,\alpha}(\PP^N|H,d)$ of non-expanded logarithmic maps; the corresponding pair on $\VZ_{1,\alpha}(\PP^N|H,d)$ will be obtained via pull-back.
-Consider therefore the tropicalization $\Sigma^{\log}$ of $\MLog_{1,\alpha}(\PP^N|H,d)$, identified as usual with the moduli space of tropical maps to $\RR_{\geq 0}$.
+\noindent In this section, we use the logarithmic structure on $\VZ_{1,\alpha}(\PP^m|H,d)$ to construct a line bundle $\Lcal_k$ and section $s_k$ which vanishes precisely along $\Dcal_{1,\alpha,k}(\PP^m|H,d)$.
+We use the correspondence with tropical geometry to identify $\cchern_1(\Lcal_k)$ in terms of tautological classes on $\VZ_{1,\alpha}(\PP^m|H,d)$, and to compute the vanishing order of $s_k$ along the components of $\Dcal_{1,\alpha,k}(\PP^m|H,d)$.
+Combined with the relative splitting formulas from the next section, this produces a recursion relation inside $\VZ_{1,\alpha}(\PP^m|H,d)$
+
+The pair $(\Lcal_k,s_k)$ is most naturally constructed on the moduli space $\MLog_{1,\alpha}(\PP^m|H,d)$ of non-expanded logarithmic maps; the corresponding pair on $\VZ_{1,\alpha}(\PP^m|H,d)$ will be obtained via pull-back.
+Consider therefore the tropicalization $\Sigma^{\log}$ of $\MLog_{1,\alpha}(\PP^m|H,d)$, identified as usual with the moduli space of tropical maps to $\RR_{\geq 0}$.
 We have a universal family
@@
 The composition $f \circ x_k \colon \Sigma^{\log} \to \RR_{\geq 0}$ defines a piecewise-linear function on $\Sigma^{\log}$ whose preimage over the open cone $\RR_{>0}$ consists of those tropical maps where $x_k$ belongs to an internal component.
-This produces a section of the ghost sheaf on $\MLog_{1,\alpha}(\PP^N|H,d)$, which in the usual way induces a line bundle and section $(\Lcal_k,s_k)$ on the moduli space, and the tropical description above shows that the zero locus of $s_k$ is (set-theoretically) the locus where $x_k$ belongs to an internal component.\medskip
+This produces a section of the ghost sheaf on $\MLog_{1,\alpha}(\PP^m|H,d)$, which in the usual way induces a line bundle and section $(\Lcal_k,s_k)$ on the moduli space, and the tropical description above shows that the zero locus of $s_k$ is (set-theoretically) the locus where $x_k$ belongs to an internal component.\medskip
 
@@
 By construction, the line bundle associated to this section is $\pi^\st \Lcal_k$.
-Consider on the other hand the generator $1 \in \N = \Gamma(\PP^N,\ol{M}_{\PP^N})$ with associated line bundle $\OO(H)$.
+Consider on the other hand the generator $1 \in \N = \Gamma(\PP^m,\ol{M}_{\PP^m})$ with associated line bundle $\OO(H)$.
 The section $f^\flat(1) \in \Gamma(C,\ol{M}_C)$ has associated line bundle $f^\st\OO(H)$.
@@
 as required.\end{proof}
-This produces $(\Lcal_k,s_k)$ and calculates $\cchern_1(\Lcal_k)$ on $\MLog_{1,\alpha}(\PP^N|H,d)$; this bundle is pulled back to $\VZ_{1,\alpha}(\PP^N|H,d)$.
+This produces $(\Lcal_k,s_k)$ and calculates $\cchern_1(\Lcal_k)$ on $\MLog_{1,\alpha}(\PP^m|H,d)$; this bundle is pulled back to $\VZ_{1,\alpha}(\PP^m|H,d)$.
 The relevant piecewise-linear function is the composition:
-\begin{equation*} \Sigma_{1,\alpha}(\PP^N|H,d) \to \Sigma^{\log} \to \RR_{\geq 0}.\end{equation*}
-Note in particular that $\psi_k$ should be interpreted as a \textbf{collapsed class} on $\VZ_{1,\alpha}(\PP^N|H,d)$, i.e.
+\begin{equation*} \Sigma_{1,\alpha}(\PP^m|H,d) \to \Sigma^{\log} \to \RR_{\geq 0}.\end{equation*}
+Note in particular that $\psi_k$ should be interpreted as a \textbf{collapsed class} on $\VZ_{1,\alpha}(\PP^m|H,d)$, i.e.
 the cotangent class from the source curve of the collapsed and stabilised map.
@@
 
-\begin{thm} \label{theorem recursion} We have the following relation in the Chow ring of $\VZ_{1,\alpha}(\PP^N|H,d)$:
-\begin{equation}\label{equation recursion} (\alpha_k \psi_k + \ev_k^\st H) \cap [\VZ_{1,\alpha}(\PP^N|H,d)] = \sum_{\Dcal} \lambda_\Dcal [ \Dcal ].\end{equation}
-The sum is over irreducible components of the divisor $\Dcal_{1,\alpha,k}(\PP^N|H,d) \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$, and $\lambda_\Dcal$ is the vanishing order of $s_k$ along this component.
+\begin{thm} \label{theorem recursion} We have the following relation in the Chow ring of $\VZ_{1,\alpha}(\PP^m|H,d)$:
+\begin{equation}\label{equation recursion} (\alpha_k \psi_k + \ev_k^\st H) \cap [\VZ_{1,\alpha}(\PP^m|H,d)] = \sum_{\Dcal} \lambda_\Dcal [ \Dcal ].\end{equation}
+The sum is over irreducible components of the divisor $\Dcal_{1,\alpha,k}(\PP^m|H,d) \subseteq \VZ_{1,\alpha}(\PP^m|H,d)$, and $\lambda_\Dcal$ is the vanishing order of $s_k$ along this component.
 \end{thm}
@@
 
-\begin{remark} For the reduced relative Gromov--Witten theory of $(\mathbb P^N,H)$ with only primary insertions, i.e.
+\begin{remark} For the reduced relative Gromov--Witten theory of $(\mathbb P^m,H)$ with only primary insertions, i.e.
 where all cohomological insertions in the invariants are pulled back along evaluation maps, computations can be carried out without an analysis of the factorisation condition; this follows from dimension considerations and leads to the main results in~\cite{Vre}.
@@
 
-\subsection{Irreducible components of the degenerate locus} We explain the tropical procedure to identify irreducible components of $\Dcal_{1,\alpha,k}(\PP^N|H,d)$.
-
-\begin{lemma} \label{Lemma components are logarithmic divisors} Every irreducible component of $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ is a codimension $1$ logarithmic stratum.\end{lemma}
+\subsection{Irreducible components of the degenerate locus} We explain the tropical procedure to identify irreducible components of $\Dcal_{1,\alpha,k}(\PP^m|H,d)$.
+
+\begin{lemma} \label{Lemma components are logarithmic divisors} Every irreducible component of $\Dcal_{1,\alpha,k}(\PP^m|H,d)$ is a codimension $1$ logarithmic stratum.\end{lemma}
 
 \begin{proof} The locus where the logarithmic structure is trivial is the locus where the source curve is smooth and not mapped inside $H$.
-Since $\VZ_{1,\alpha}(\PP^N|H,d)$ is toroidal this locus is open and dense.
-By definition $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ is contained in the  complement of this locus and can be expressed as a union of strata of positive codimension.
-Since $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ is pure codimension $1$, it is a union of logarithmic divisors.\end{proof}
-
-\noindent In \S \ref{subsection indexing strata} we described the logarithmic strata of $\VZ_{1,\alpha}(\PP^N|H,d)$, using the cones of the tropicalization $\Sigma_{1,\alpha}(\PP^N|H,d)$.
+Since $\VZ_{1,\alpha}(\PP^m|H,d)$ is toroidal this locus is open and dense.
+By definition $\Dcal_{1,\alpha,k}(\PP^m|H,d)$ is contained in the  complement of this locus and can be expressed as a union of strata of positive codimension.
+Since $\Dcal_{1,\alpha,k}(\PP^m|H,d)$ is pure codimension $1$, it is a union of logarithmic divisors.\end{proof}
+
+\noindent In \S \ref{subsection indexing strata} we described the logarithmic strata of $\VZ_{1,\alpha}(\PP^m|H,d)$, using the cones of the tropicalization $\Sigma_{1,\alpha}(\PP^m|H,d)$.
 Every divisorial logarithmic stratum is obtained as follows:
@@
 This induces a generisation of the initial combinatorial type $\Delta$, given by contracting the corresponding edges of the dual graph and moving the corresponding vertices from $\RR_{>0}$ to $0$.
-When we speak of the combinatorial type of a stratum in $\VZ_{1,\alpha}(\PP^N|H,d)$, we will always mean this generisation.
+When we speak of the combinatorial type of a stratum in $\VZ_{1,\alpha}(\PP^m|H,d)$, we will always mean this generisation.
 This is independent of the choice of $\Delta$, and in fact we can and will always choose $\Delta$ to coincide with the generisation.
 
-The logarithmic divisors contained in $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ are those whose  combinatorial types map the vertex of the dual graph containing $x_k$  into the interior $\RR_{>0} \subseteq \RR_{\geq 0}$.
-Thus via the above procedure, we enumerate the components of $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ in a combinatorial manner; the combinatorial type $\Delta$ allows us to describe the general element of such a component.
+The logarithmic divisors contained in $\Dcal_{1,\alpha,k}(\PP^m|H,d)$ are those whose  combinatorial types map the vertex of the dual graph containing $x_k$  into the interior $\RR_{>0} \subseteq \RR_{\geq 0}$.
+Thus via the above procedure, we enumerate the components of $\Dcal_{1,\alpha,k}(\PP^m|H,d)$ in a combinatorial manner; the combinatorial type $\Delta$ allows us to describe the general element of such a component.
 The remainder of this section gives a recursive description of the components and a recursive computation of integrals over them.
 
-\subsection{Recursive description of the divisors: types I, II and III} Choose an irreducible component $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$.
+\subsection{Recursive description of the divisors: types I, II and III} Choose an irreducible component $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^m|H,d)$.
 By Lemma \ref{Lemma components are logarithmic divisors} this is a logarithmic divisor, and hence may be written as:
-\begin{equation*} \Dcal = \widetilde\Dcal \cap \VZ_{1,\alpha}(\PP^N|H,d) \end{equation*}
-for a unique logarithmic stratum $\widetilde\Dcal \subseteq \widetilde{\VZ}_{1,\alpha}(\PP^N|H,d)$. Since
-\begin{equation*}\widetilde{\VZ}_{1,\alpha}(\PP^N|H,d) \to \ol\Mcal_{1,\alpha}(\PP^N|H,d)\end{equation*}
+\begin{equation*} \Dcal = \widetilde\Dcal \cap \VZ_{1,\alpha}(\PP^m|H,d) \end{equation*}
+for a unique logarithmic stratum $\widetilde\Dcal \subseteq \widetilde{\VZ}_{1,\alpha}(\PP^m|H,d)$. Since
+\begin{equation*}\widetilde{\VZ}_{1,\alpha}(\PP^m|H,d) \to \ol\Mcal_{1,\alpha}(\PP^m|H,d)\end{equation*}
 is a logarithmic modification, the divisor $\widetilde{\Dcal}$ is either exceptional or the strict transform of a logarithmic divisor.
@@
 We begin with the latter. Suppose therefore that $\widetilde{\Dcal}$ is the strict transform of a logarithmic divisor:
-\begin{equation*} \Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d). \end{equation*}
+\begin{equation*} \Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^m|H,d). \end{equation*}
 The birational map $\widetilde{\Dcal} \to \Ecal$ induces a morphism $\Dcal \to \Ecal$.
@@
 
-\begin{lemma}\label{lem:combs} Let $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ be an irreducible component which contributes nontrivially to the Gromov--Witten invariant, and let $\Delta$ be the corresponding combinatorial type.
+\begin{lemma}\label{lem:combs} Let $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^m|H,d)$ be an irreducible component which contributes nontrivially to the Gromov--Witten invariant, and let $\Delta$ be the corresponding combinatorial type.
 If $\Delta$ assigns positive degree to the core, then $\Delta$ takes one of the following forms:
@@
 
-\begin{proof} Let $\sigma \in \Sigma_{1,\alpha}(\PP^N|H,d)$ be the cone corresponding to $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$.
+\begin{proof} Let $\sigma \in \Sigma_{1,\alpha}(\PP^m|H,d)$ be the cone corresponding to $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^m|H,d)$.
 By the discussion above $\Dcal$ corresponds to a ray in the subdivision of $\sigma$ obtained by imposing the central alignment condition.
@@
 To see this, we consider the stratum
-\begin{equation*} \Ecal^{\text{\tiny{log}}} \subseteq \ol\Mcal^{\text{\tiny{log}}}_{1,\alpha}(\PP^N|H,d) \end{equation*}
+\begin{equation*} \Ecal^{\text{\tiny{log}}} \subseteq \ol\Mcal^{\text{\tiny{log}}}_{1,\alpha}(\PP^m|H,d) \end{equation*}
 to which $\Ecal$ maps under the collapsing morphism, and examine the composition $\Dcal \to \Ecal \to \Ecal^{\text{\tiny{log}}}$.
@@
 We now investigate the three types I, II and III separately, giving a recursive description of the boundary divisor in each case.
-For the remainder of this subsection, therefore, we fix a one-dimensional cone $\tau \in \Sigma_{1,\alpha}(\PP^N|H,d)$, let $\Dcal \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$ be the associated logarithmic divisor, and assume that $\Dcal$ is contained in $\Dcal_{1,\alpha,k}(\PP^N|H,d)$ and is of type I, II or III.
-We let $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$ be the logarithmic stratum into which $\Dcal$ is mapped; this is indexed by a cone $\epsilon \in \Sigma^{\Kim}$ corresponding to a combinatorial type $\Delta$, and $\epsilon$ is one-dimensional since we are restricting to the type I, II, III cases.
+For the remainder of this subsection, therefore, we fix a one-dimensional cone $\tau \in \Sigma_{1,\alpha}(\PP^m|H,d)$, let $\Dcal \subseteq \VZ_{1,\alpha}(\PP^m|H,d)$ be the associated logarithmic divisor, and assume that $\Dcal$ is contained in $\Dcal_{1,\alpha,k}(\PP^m|H,d)$ and is of type I, II or III.
+We let $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^m|H,d)$ be the logarithmic stratum into which $\Dcal$ is mapped; this is indexed by a cone $\epsilon \in \Sigma^{\Kim}$ corresponding to a combinatorial type $\Delta$, and $\epsilon$ is one-dimensional since we are restricting to the type I, II, III cases.
 
 \subsubsection{Type I}\label{subsubsection type A} Suppose $\Delta$ is of type I. Then $\Ecal$ admits a finite and surjective \textbf{splitting morphism} onto the fibre product:
-\begin{equation*} \Ecal \to \left( \ol\Mcal_{1,\alpha^{(1)}\cup(m_1)}(\PP^N|H,d_1) \times \prod_{i=2}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i) \right) \times_{H^r} \ol\Mcal^{\leftrightarrow}_{0,\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}(\mathbb{P}|H_0+H_\infty,d_0).\end{equation*}
+\begin{equation*} \Ecal \to \left( \ol\Mcal_{1,\alpha^{(1)}\cup(m_1)}(\PP^m|H,d_1) \times \prod_{i=2}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^m|H,d_i) \right) \times_{H^r} \ol\Mcal^{\leftrightarrow}_{0,\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}(\mathbb{P}|H_0+H_\infty,d_0).\end{equation*}
 
 \begin{lemma} \label{Lemma type A gluing} The divisor $\Dcal$ admits a natural splitting morphism
-\begin{equation*}\Dcal \xrightarrow{\rho} \left(\VZ_{1,\alpha^{(1)}\cup(m_1)}(\PP^N|H,d_1)\times\prod_{i=2}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i)\right) \times_{H^r} \ol\Mcal^{\leftrightarrow}_{0,\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}(\mathbb{P}|H_0+H_\infty,d_0)\end{equation*}
+\begin{equation*}\Dcal \xrightarrow{\rho} \left(\VZ_{1,\alpha^{(1)}\cup(m_1)}(\PP^m|H,d_1)\times\prod_{i=2}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^m|H,d_i)\right) \times_{H^r} \ol\Mcal^{\leftrightarrow}_{0,\alpha^{(0)}\cup (-m_1,\ldots,-m_r)}(\mathbb{P}|H_0+H_\infty,d_0)\end{equation*}
 such that the map $\Dcal \to \Ecal$ lifts the map on fibre products obtained by desingularising the main component of the first factor.\end{lemma}
@@
 %\begin{proof} Observe first that $\Dcal$ is obtained as the disjoint union of the locally closed logarithmic strata contained in the closure of the stratum where all of the $\sqC_i$ are irreducible.
-We choose and examine one of these boundary strataIf we look at one of these boundary strata, then by definition the associated cone $\sigma \in \Sigma_{1,\alpha}(\PP^N|H,d)$ contains a ray $\tau$ corresponding to the stratum where all the $\sqC_i$ are irreducible; this amounts to setting all edge lengths other than $e_1,\ldots,e_r$ to zero.
+We choose and examine one of these boundary strataIf we look at one of these boundary strata, then by definition the associated cone $\sigma \in \Sigma_{1,\alpha}(\PP^m|H,d)$ contains a ray $\tau$ corresponding to the stratum where all the $\sqC_i$ are irreducible; this amounts to setting all edge lengths other than $e_1,\ldots,e_r$ to zero.
 If $f_1,\ldots,f_l$ are some collection of additional edge lengths in $\sigma$ (corresponding to internal nodes in degenerations of the $\sqC_i$) then since $\sigma$ is adjacent to $\tau$ we must have (by construction of the subdivision) $f_1+\ldots+f_l < e_j$ for all $j\in\{1,\ldots,r\}$, since $f_1=\ldots=f_l=0$ and $e_j \neq 0$ on $\tau$.
@@
 \begin{lemma} $\Dcal$ admits a finite and surjective splitting morphism:
-\begin{equation*} \Dcal \xrightarrow{\rho} \left(\ol\Mcal_{0,\alpha^{(1)}\cup(m_1,m_2)}(\PP^N|H,d_1)\times\prod_{i=3}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i)\right) \times_{H^r} \ol\Mcal^{\leftrightarrow}_{0,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(\mathbb P|H_0+H_\infty,d_0).\end{equation*}\end{lemma}
+\begin{equation*} \Dcal \xrightarrow{\rho} \left(\ol\Mcal_{0,\alpha^{(1)}\cup(m_1,m_2)}(\PP^m|H,d_1)\times\prod_{i=3}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^m|H,d_i)\right) \times_{H^r} \ol\Mcal^{\leftrightarrow}_{0,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(\mathbb P|H_0+H_\infty,d_0).\end{equation*}\end{lemma}
 
 \subsubsection{Type III} \label{subsubsection type C+} Finally suppose that $\Delta$ is of type III. As before we have a finite and surjective morphism:
-\begin{equation*} \Ecal \to  \left( \prod_{i=1}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i) \right) \times_{H^r} \ol\Mcal^{\leftrightarrow}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(\mathbb{P}|H_0+H_\infty,d_0).
+\begin{equation*} \Ecal \to  \left( \prod_{i=1}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^m|H,d_i) \right) \times_{H^r} \ol\Mcal^{\leftrightarrow}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(\mathbb{P}|H_0+H_\infty,d_0).
 \end{equation*}
@@
 \begin{lemma} $\Dcal$ admits a finite splitting morphism
-\begin{equation*}\Dcal \xrightarrow{\rho} \left( \prod_{i=1}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^N|H,d_i) \right) \times_{H^r} \VZ^{\leftrightarrow}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(\mathbb{P}|H_0+H_\infty,d_0)\end{equation*}
+\begin{equation*}\Dcal \xrightarrow{\rho} \left( \prod_{i=1}^r \ol\Mcal_{0,\alpha^{(i)}\cup(m_i)}(\PP^m|H,d_i) \right) \times_{H^r} \VZ^{\leftrightarrow}_{1,\alpha^{(0)}\cup(-m_1,\ldots,-m_r)}(\mathbb{P}|H_0+H_\infty,d_0)\end{equation*}
 such that $\Dcal \to \Ecal$ corresponds to the obvious map on fibre products.\end{lemma}
@@
 \end{lemma}
-\begin{proof} Let $\tau \in \Sigma_{1,\alpha}(\PP^N|H,d)$ be the cone corresponding to $\Dcal$ and let
-\begin{equation*} \varphi \colon \Sigma_{1,\alpha}(\PP^N|H,d) \to \Sigma^{\log} \to \RR_{\geq 0} \end{equation*}
+\begin{proof} Let $\tau \in \Sigma_{1,\alpha}(\PP^m|H,d)$ be the cone corresponding to $\Dcal$ and let
+\begin{equation*} \varphi \colon \Sigma_{1,\alpha}(\PP^m|H,d) \to \Sigma^{\log} \to \RR_{\geq 0} \end{equation*}
 be the piecewise-linear function constructed in \S \ref{Section Gathmann line bundle}.
@@
 
-\subsubsection{Possible combinatorial types}\label{S:combinatorialdescription} A boundary divisor $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^N|H,d)$ is said to have \textbf{type $\dag$} if the core is assigned degree zero by the combinatorial type.
+\subsubsection{Possible combinatorial types}\label{S:combinatorialdescription} A boundary divisor $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^m|H,d)$ is said to have \textbf{type $\dag$} if the core is assigned degree zero by the combinatorial type.
 Divisors of this type occur as principal components in compactified torus bundles over strata in the space of relative maps.
@@
 the collapsing map has fibres of positive dimension.
-As both insertions and the factorisation property for the collapsed map to $\mathbb P^N$ are pulled back from the moduli space of maps without expansions, the contribution vanishes by the projection formula.
+As both insertions and the factorisation property for the collapsed map to $\mathbb P^m$ are pulled back from the moduli space of maps without expansions, the contribution vanishes by the projection formula.
 \end{proof}
@@
 
-Finally, in case the maximal contact order is $m=1$, in order for $f_B$ to factor, the image of the tangent vectors at the components lying on the circle must be linearly dependent in $T_{\PP^N,x}$, where $x$ denotes the image of the core under $f_B$.in which case we can deduce as above that factorisation will be satisfied independently of the choice of alignment.
+Finally, in case the maximal contact order is $m=1$, in order for $f_B$ to factor, the image of the tangent vectors at the components lying on the circle must be linearly dependent in $T_{\PP^m,x}$, where $x$ denotes the image of the core under $f_B$.in which case we can deduce as above that factorisation will be satisfied independently of the choice of alignment.
 \end{proof}
@@
 Start from the moduli space of logarithmic maps. There is a finite splitting morphism:
-\[\Ecal \to \left(\M{0}{(1)}{\PP^N}{1}^{\times N}\times_{H^N}H\right)\times \Mcal^{\leftrightarrow}_{1,(-1,\ldots,-1,d)},\]
+\[\Ecal \to \left(\M{0}{(1)}{\PP^m}{1}^{\times N}\times_{H^N}H\right)\times \Mcal^{\leftrightarrow}_{1,(-1,\ldots,-1,d)},\]
 where the latter is the moduli space of genus one curves satisfying the \emph{double ramification} condition.
@@
 Indeed, if $R_i$ denotes the $i$-th tail of the curve, glued to $E$ at the node $q_i$, then the stable maps provide us with identifications:
-\[\operatorname{d}\! f_{i,q_i}\colon T_{R_i,q_i}\simeq N_{H/\PP^N,p}\]
+\[\operatorname{d}\! f_{i,q_i}\colon T_{R_i,q_i}\cong N_{H/\PP^m,p}\]
 that can be combined into the $\theta_{i,j}$ of \S \ref{S:ellsing}. So, without further ado, we may produce a contraction $C\to\overline C$ to an elliptic $d$-fold point.
@@
 Assume for example that $d\leq N$.
-Then, for the absolute factorisation to hold, the $d$ lines $f_i(R_i)$ have better to span a $(d-1)$-dimensional subspace of $T_{\PP^N,p}$.
+Then, for the absolute factorisation to hold, the $d$ lines $f_i(R_i)$ have better to span a $(d-1)$-dimensional subspace of $T_{\PP^m,p}$.
 The dimension of the moduli space $\widetilde\Dcal$ is then $dN+d-2$.
@@
 Finally, the sections $z_i,\ i=1,\ldots,d-2,$ impose independent conditions to descend to $\overline C$.
-All in all, we find that $\Dcal$ has dimension $dN$, making it into a divisor in $\VZ_{1,(d)}(\PP^N|H,d)$.
+All in all, we find that $\Dcal$ has dimension $dN$, making it into a divisor in $\VZ_{1,(d)}(\PP^m|H,d)$.
 
@@
 This means that $\widetilde\Dcal$ is a compactified torus bundle over $\Ecal$, see \ref{S:ellsing}.
-On the other hand, for higher contact order, the vector bundle map $\sum\circ\operatorname{d}\!f$ to $T_{\PP^N,p}$ factors naturally through $T_{H,p}$.
+On the other hand, for higher contact order, the vector bundle map $\sum\circ\operatorname{d}\!f$ to $T_{\PP^m,p}$ factors naturally through $T_{H,p}$.
 
@@
 \[
-\VZ_{1,\alpha}(\PP^N|H,d)\hookrightarrow \widetilde{\VZ}_{1,\alpha}(\PP^N|H,d)\to \overline\Mcal_{1,\alpha}(\PP^N|H,d).
+\VZ_{1,\alpha}(\PP^m|H,d)\hookrightarrow \widetilde{\VZ}_{1,\alpha}(\PP^m|H,d)\to \overline\Mcal_{1,\alpha}(\PP^m|H,d).
 \]
@@
 The second morphism is a logarithmic modification.
-Let $\tau \in \Sigma_{1,\alpha}(\PP^N|H,d)$ be the ray corresponding to $\Dcal \subseteq \VZ_{1,\alpha}(\PP^N|H,d)$, and to the virtual divisor $\widetilde \Dcal \subseteq \widetilde{\VZ}_{1,\alpha}(\PP^N|H,d)$.
+Let $\tau \in \Sigma_{1,\alpha}(\PP^m|H,d)$ be the ray corresponding to $\Dcal \subseteq \VZ_{1,\alpha}(\PP^m|H,d)$, and to the virtual divisor $\widetilde \Dcal \subseteq \widetilde{\VZ}_{1,\alpha}(\PP^m|H,d)$.
 
@@
 The dimension of this cone could be large (see again the left-hand side of Figure \ref{fig:off_we_go}) -- its dimension is equal to the number of levels of the target expansion in the type $\Delta$.
-The cone $\sigma$ determines a stratum $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^N|H,d)$, and the morphism above restricts to
+The cone $\sigma$ determines a stratum $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^m|H,d)$, and the morphism above restricts to
 \[
@@
 Then $\Ecal$ admits a finite splitting morphism
-\begin{equation}\label{IIIa fibre product} \Ecal \xrightarrow{\rho} \left( \prod_{v \in \Lambda_0} \ol\Mcal_{\Gamma_v}(\PP^N|H) \times \prod_{v \in \Lambda_{>0}} \ol\Mcal^{\leftrightarrow}_{\Gamma_v}(\mathbb{P}|H_0+H_\infty) \right) \times_{H^{2\epsilon}} H^{\epsilon} \end{equation}
+\begin{equation}\label{IIIa fibre product} \Ecal \xrightarrow{\rho} \left( \prod_{v \in \Lambda_0} \ol\Mcal_{\Gamma_v}(\PP^m|H) \times \prod_{v \in \Lambda_{>0}} \ol\Mcal^{\leftrightarrow}_{\Gamma_v}(\mathbb{P}|H_0+H_\infty) \right) \times_{H^{2\epsilon}} H^{\epsilon} \end{equation}
 where $\epsilon$ is the number of edges of the stabilised dual graph, and the fibre product is taken over the appropriate evaluation maps.
@@
 \noindent
-{\bf Exportation to the reduced geometry.}  Observe that we have a virtual divisor $\widetilde\Dcal \subseteq \widetilde\VZ_{1,\alpha}(\PP^N|H,d)$ such that 
+{\bf Exportation to the reduced geometry.}  There is a virtual divisor $\widetilde\Dcal \subseteq \widetilde\VZ_{1,\alpha}(\PP^m|H,d)$ such that 
 \[
-\Dcal = \widetilde\Dcal \cap \VZ_{1,\alpha}(\PP^N|H,d).
+\Dcal = \widetilde\Dcal \cap \VZ_{1,\alpha}(\PP^m|H,d).
 \]
-We wish to use the splitting of $\Ecal$ in the ordinary geometry to recursively compute integrals in the reduced geometry.
-Noting that $\Dcal$ is cut out of the excess dimensional space $\widetilde \Dcal$ by the factorisation properties, we make the reduction in two steps:
+We wish to use the splitting of $\Ecal$ to recursively compute integrals on $\Dcal$.
+Noting that $\Dcal$ is cut out of the excess-dimensional space $\widetilde \Dcal$ by the factorisation properties, we make the reduction in two steps:
 \begin{enumerate}
@@
 The degree of $\rho$ is given exactly as in Lemma \ref{lem:saturation}, where now we obtain one such factor for each bounded edge of the tropical target.
-The vanishing order $\lambda_{\Dcal}$ is slightly more delicate, but may be computed as the index of an explicit morphism of one-dimensional lattices, as explained in the proof of Lemma \ref{lemma vanishing order}.
+The vanishing order $\lambda_{\Dcal}$ is slightly more combinatorially delicate, but may be computed as the index of an explicit morphism of one-dimensional lattices, as explained in the proof of Lemma \ref{lemma vanishing order}.
 \end{remark}
@@
 \subsubsection{Compactified bundles over strata: $\widetilde\Dcal$ from $\Ecal$}\label{subsection Dtilde from E} Recall that the map $\widetilde\Dcal \to \Ecal$ is obtained by restricting the logarithmic blowup
-\begin{equation*} \widetilde\VZ_{1,\alpha}(\PP^N|H,d) \to \ol\Mcal_{1,\alpha}(\PP^N|H,d)\end{equation*}
+\begin{equation*} \widetilde\VZ_{1,\alpha}(\PP^m|H,d) \to \ol\Mcal_{1,\alpha}(\PP^m|H,d)\end{equation*}
 to the locus $\widetilde\Dcal$.
-Toroidal geometry gives a construction of $\widetilde \Dcal$ as a compactification of a torus bundle over a locally closed stratum in $\overline\Mcal_{1,\alpha}(\PP^N|H,d)$.
+Toroidal geometry gives a construction of $\widetilde \Dcal$ as a compactification of a torus bundle over a locally closed stratum in $\overline\Mcal_{1,\alpha}(\PP^m|H,d)$.
 \medskip
@@
   \draw[fill=black] (0,-1) circle (2 pt);
-  \draw (1,1)--node[below,blue]{$m_1$} (2,0) (0,-1)--node[below,blue]{$m_1$} (2,0) (2,0)--node[below,blue]{$m_1+m_2$} (4,0);
+  \draw[->] (1,1)--node[below,blue]{$m_1$} (2,0) (0,-1)--node[below,blue]{$m_1$} (2,0) (2,0)--node[below,blue]{$m_1+m_2$} (4,0);
   \draw (1,-.5) node[cross]{};
@@
 \]
-The tropical curves on the left inherit a central alignment from $\widetilde{\VZ}_{1,\alpha}(\PP^N|H,d)$, which orders a certain subset of the edge lengths.
+The tropical curves on the left inherit a central alignment from $\widetilde{\VZ}_{1,\alpha}(\PP^m|H,d)$, which orders a certain subset of the edge lengths.
 The polyhedral criterion for equidimensionality is that every cone of the source maps surjectively onto a cone of the target.
@@
 
-This subdivision is best described using the formalism of extended tropicalizations \cite{Thuillier,ACP}.
+This subdivision may be described explicitly.
+For this, it is convenient to employ the formalism of extended tropicalizations \cite{Thuillier,ACP}.
 The subdividing cones are obtained from cones in the star of $\tau$ under the limit $e_1=\cdots=e_r=\infty$\sidenote{Was $r$ called $\epsilon$ before?}.
@@
 In particular there are vertices $\plC_1,\ldots,\plC_r$ generically lying on the circle of radius $\delta$.
-The moduli space of attaching data for the elliptic singularity is the complement of the coordinate hyperplanes in
+The moduli space of attaching data for the elliptic singularity is the complement of the coordinate hyperplanes in:
 \begin{equation}\label{eqn:projectivebundle}
- \PP\left(\bigoplus_{i=1}^rT_{q_i}C_i\right);
+ \PP\left(\bigoplus_{i=1}^rT_{q_i}C_i\right).
 \end{equation}
-
-this can also be thought of as parametrising compatible identifications $\theta_{i,j}\colon T_{C_i,q_i}\simeq T_{C_j,q_j}$, see \S \ref{S:ellsing}.
-A point in this space determines in particular a map from the rational $r$-fold singularity to the elliptic $r$-fold singularity.
-That this coincides with the fibre of the aligned moduli space of curves over the ordinary one is well explained in \cite[\S 3.4]{RSPW}.
-Along the boundary, some of the $\plC_i$ -- but not all of them!
---  are allowed to move off from the circle, so that the latter cuts the edge between them and the core.
+This can also be thought of as parametrising compatible identifications $\theta_{ij}\colon T_{C_i,q_i}\cong T_{C_j,q_j}$ (see \S \ref{S:ellsing}).
+A point in this space determines a map from the rational $r$-fold singularity to the elliptic $r$-fold singularity (this coincides with the fibre of the space of aligned curves over the space of nodal curves; see \cite[\S 3.4]{RSPW}).
+Along the boundary, some of the $\plC_i$ (though not all of them) may move off from the circle, so that the latter subdivides the edge between them and the core.
 Correspondingly, there is a destabilisation of the curve (semistable components are represented by crosses in our figures), and we obtain an elliptic singularity containing strictly semistable branches (\emph{sprouting}).
@@
 
-\subsubsection{$\Dcal$ from $\widetilde\Dcal$: first way}\label{subsection D from Dtilde} On $\widetilde\Dcal$ there is a tautological line bundle arising from the modular description of $\widetilde\VZ_{1,\alpha}(\PP^N|H,d)$, namely $\OO(\delta)$.
-Recall that the piecewise linear function $\delta$ may be viewed as a global section of the characteristic sheaf of the logarithmic structure on $\widetilde\VZ_{1,\alpha}(\PP^N|H,d)$.
+\subsubsection{$\Dcal$ from $\widetilde\Dcal$: first way}\label{subsection D from Dtilde} On $\widetilde\Dcal$ there is a tautological line bundle arising from the modular description of $\widetilde\VZ_{1,\alpha}(\PP^m|H,d)$, namely $\OO(\delta)$.
+Recall that the piecewise linear function $\delta$ may be viewed as a global section of the characteristic sheaf of the logarithmic structure on $\widetilde\VZ_{1,\alpha}(\PP^m|H,d)$.
 The toric geometry dictionary gives rise to an associated Cartier divisor.
@@
 Apart from the case dealt with in \S \ref{S:lines}, the composite:
-\[\operatorname{pr}\circ\Sigma \operatorname{d}\!f \colon \OO(\delta)\otimes \mathbb T^\vee \to \ev_q^\st T \PP^N\to \ev_q^* N_{H/\PP^N}\]
- vanishes, because the contact order of the exterior components with $H$ is strictly higher than $1$. So, $\Sigma \operatorname{d}\!f$ takes values in $TH$, rather than $T\PP^N$.
+\[\operatorname{pr}\circ\Sigma \operatorname{d}\!f \colon \OO(\delta)\otimes \mathbb T^\vee \to \ev_q^\st T \PP^m\to \ev_q^* N_{H/\PP^m}\]
+ vanishes, because the contact order of the exterior components with $H$ is strictly higher than $1$. So, $\Sigma \operatorname{d}\!f$ takes values in $TH$, rather than $T\PP^m$.
 
@@
 \begin{equation*}\mathcal P=\PP_{\Ecal}\left(\bigoplus_{i=1}^r\OO(\delta_i)\right)\xrightarrow{p}\Ecal.\end{equation*}
-When all fibre coordinates are non-zero, a point of $\mathcal P$ induces compatible isomorphisms $\OO(\delta_i)\simeq\OO(\delta_j)$ for all $i,j$.
+When all fibre coordinates are non-zero, a point of $\mathcal P$ induces compatible isomorphisms $\OO(\delta_i)\cong\OO(\delta_j)$ for all $i,j$.
 We think of this as saying that all the $\plC_i$ are at the same distance from the core.
@@
 \begin{itemize}
- \item[(B)] $\forall i\in\Lambda_B$, the $i$-th component of the fibre product \eqref{IIIa fibre product}, namely the map $f_i\colon C_i\to(\PP^N|H)$, degenerates so that it is constant near the attaching point to the core.
+ \item[(B)] $\forall i\in\Lambda_B$, the $i$-th component of the fibre product \eqref{IIIa fibre product}, namely the map $f_i\colon C_i\to(\PP^m|H)$, degenerates so that it is constant near the attaching point to the core.
  \item[(F)] $\forall j\in\Lambda_F$, the $j$-th coordinate in the fibre of $p\colon\mathcal P\to\Ecal$ vanishes.
@@
 \subsection{Recursion for general $(X,Y)$}\label{section recursion for general pair} Now let $(X,Y)$ be a general smooth very ample pair.
-In \S \ref{subsection virtual} we studied the moduli space $\VZ_{1,\alpha}(X|Y,\beta)$ of centrally aligned maps to $(X,Y)$ and equipped it with a virtual fundamental class by diagonal pull-back from $\VZ_{1,\alpha}(\PP^N|H,d)$.
-
-This construction of the virtual fundamental class means that once we have established a recursion formula for $(\PP^N,H)$, it immediately pulls back to give a recursion formula for $(X,Y)$.
+In \S \ref{subsection virtual} we studied the moduli space $\VZ_{1,\alpha}(X|Y,\beta)$ of centrally aligned maps to $(X,Y)$ and equipped it with a virtual fundamental class by diagonal pull-back from $\VZ_{1,\alpha}(\PP^m|H,d)$.
+
+This construction of the virtual fundamental class means that once we have established a recursion formula for $(\PP^m,H)$, it immediately pulls back to give a recursion formula for $(X,Y)$.
 To be more precise, Theorem \ref{theorem recursion} holds \emph{mutatis mutandis}, with the same values of $\lambda_\Dcal$.
@@
 \begin{equation*} \fgt_S \colon \VZ_{1,\alpha}(X|Y,\beta) \to \VZ_{1,m-\#S}(X,\beta).\end{equation*}
+Note that even the case $S=\emptyset$ entails a nontrivial forgetful morphism.
 In particular, all the psi classes which we consider are \textbf{collapsed psi classes}, meaning that they are relative cotangent line classes for the corresponding collapsed stable map.
-Note that, unlike in the absolute case, in the relative case it may well be the case that the entire insertion is pulled back along a single forgetful map $\fgt_S$.
+Note that, unlike in the absolute case, in the relative case it may well be that the entire insertion is pulled back along a single forgetful map $\fgt_S$.
 The reduced rubber invariants of $\mathbb{P}$ are defined similarly (again using collapsed psi classes).
@@
 
-\subsection{Fictitious and true markings} The recursion procedure is rather delicate.
+\subsection{Fictitious and true markings} The recursion procedure we outline is rather delicate.
 Roughly speaking, we will induct on the degree (meaning $Y\cdot\beta$), number of marked points and total tangency.
-To get the correct notion of number of markings and total tangency in  the relative setting, we introduce the concept of \textbf{fictitious markings}.
+We adopt Gathmann's point of view on relative Gromov--Witten theory \cite{Ga}, whereby only a subset of the contact points with the divisor are required to be marked; this allows for ``total tangency'' strictly smaller than $Y\cdot\beta$.
+
+In order to make sense of this in the logarithmic setting (in which all contact points must be marked), we introduce the concept of \textbf{fictitious markings}.
 Consider a moduli space $\VZ_{1,\alpha}(X|Y,\beta)$ of reduced relative stable maps and a corresponding integrand $\gamma$.
-We let $F \subseteq \{1,\ldots,m\}$ be the maximal subset of marked points such that:
+We let $F \subseteq \{1,\ldots,m\}$ be the maximal subset of marked points such that the following two conditions are satisfied:
 \begin{enumerate}
@@
 This subset is uniquely determined, and its elements are referred to as \textbf{fictitious markings}.
-Markings which are not fictitious are referred to as \textbf{true}.
-When inducting on relative invariants we will always be interested in the number of true markings (as opposed to the total number of markings) and the true tangency
+We note that $\alpha_i=1$ is not sufficient for $x_i$ to be fictitious; it must also be the case that all the insertions are pulled back along forgetting $x_i$.
+Markings which are not fictitious are referred to as \textbf{true markings}.
+When inducting on relative invariants we will always be interested in the number of true markings (as opposed to the total number of markings) and the \textbf{true tangency}
 \begin{equation*} \sum_{i \not\in F} \alpha_i \leq d=Y\cdot \beta \end{equation*}
@@
 \subsection{Structure of the recursion} Given the genus-zero Gromov--Witten theory of $X$, the arguments of \cite{Ga} give an effective algorithm to reconstruct the genus-zero theories of $Y$ and $(X,Y)$; the genus-zero rubber theory of $\mathbb{P}$ is equal to the genus-zero theory of $Y$ \cite{GathmannThesis}.
-Thus we may assume that all genus-zero data is known.
+Thus we may assume that all genus-zero invariants are known.
 We assume in addition that we know the genus one reduced theory of $X$.
-The structure of the recursion is then as follows:
-
-\begin{algorithm}
+The structure of the recursion is then as follows:\bigskip
+
+\begin{algorithm}[H]
 \DontPrintSemicolon
@@
 }
-\end{algorithm}
-\noindent Although the loops involving $d, n$ and $m$ have infinite length, in order to compute any single invariant it is only necessarily to iterate the preceding loops for a finite amount of time.
-A \textbf{forgetful relative invariant} of $(X,Y)$ is by definition a reduced relative invariant with a marked point $x_0$ such that all of the insertions are pulled back along $\fgt_{x_0}$.
-In our recursion, we first deal with this special class of relative invariants (with $n+1$ true markings), before computing the absolute invariants (with $n$ markings) and then returning to compute all of the relative invariants (with $n$ true markings).
-This need to treat separately a particular subclass of the relative invariants is an inescapable feature of the genus one recursion.
-
-The base terms of the recursion all have $d=0$ and as such are easy to compute: the relative invariants of $(X,Y)$ are nothing but absolute invariants of $X$ and the absolute invariants of $Y$ are given by obstruction bundle integrals over Deligne--Mumford spaces.
-The rubber invariants of $\mathbb{P}$ in degree zero are given by integrals over the main component of the double ramification cycle; this can likewise be computed as an integral over Deligne--Mumford space, by correcting the formula for the ordinary double ramification cycle \cite{Hain,JPPZ} by the obvious contribution from the boundary irreducible component (the observation which makes this easy to do in genus one is that the rubber moduli space is pure-dimensional, so that the virtual class is simply the sum of the fundamental classes of the irreducible components).
+\end{algorithm}\bigskip
+
+\noindent Here each loop begins at $0$ and proceeds through successively larger values, with the invariants at each step expressed recursively in terms of invariants computed in the preceding steps.
+Although the loops involving $d, n$ and $m$ have infinite length, in order to compute any single invariant it is only necessarily to iterate the preceding loops for a finite amount of time.
+
+In Step 1 above, a \textbf{forgetful relative invariant} of $(X,Y)$ is by definition a reduced relative invariant for which there exists a marking $x_0$ such that all of the insertions are pulled back along $\fgt_{x_0}$.
+In our recursion, we first deal with the special class of forgetful relative invariants (with $n+1$ true markings), before computing the absolute invariants (with $n$ markings) and then returning to compute all of the relative invariants (with $n$ true markings).
+The need to separately treat a particular subclass of the relative invariants is an inescapable feature of the genus one recursion.
+
+The base terms of the recursion all have $d=0$ and as such are easy to compute: the relative invariants of $(X,Y)$ are nothing but absolute invariants of $X$ (i.e.
+there are no tangency conditions), and the absolute invariants of $Y$ are given by obstruction bundle integrals over Deligne--Mumford spaces.
+The rubber invariants of $\mathbb{P}$ in degree zero are given by integrals over the main component of the double ramification cycle (in the rubber case there may be markings with tangency even for $d=0$, since $d$ only records the degree covering the base); this can likewise be computed as an integral over Deligne--Mumford space, by correcting the formula for the ordinary double ramification cycle \cite{Hain,JPPZ} by the obvious contribution from the boundary irreducible component (the observation which makes this easy to do in genus one is that the rubber moduli space is pure-dimensional, so that the virtual class is simply the sum of the fundamental classes of the irreducible components).
 We will now explain how to perform each of the four inductive steps outlined above.
@@
 \subsection*{Step 1} Suppose we are given a forgetful relative invariant to compute.
-That is, we have a relative space $\VZ_{1,\alpha}(X|Y,\beta)$ of degree $d$, with $n+1$ true markings and true tangency $t$, and a marking $x_0$ such that the insertion $\gamma$ is pulled back along $\fgt_{x_0}$.
-We assume inductively that every absolute, relative and rubber invariant with $(d^\prime,n^\prime) < (d,n)$ is known, and also that every forgetful relative invariant with $(d^\prime,n^\prime,t^\prime) < (d,n+1,t)$ is known.
-Choose a true marking $x_1$ with $\alpha_1 \geq 1$ and consider the space:
+That is, we have a relative space $\VZ_{1,\alpha}(X|Y,\beta)$ of degree $d$, with $n+1$ true markings and true tangency $t$, and a marking $x_0$ such that the insertion $\gamma=\fgt_{x_0}^\star \delta$ for some class $\delta$.
+We assume inductively that every absolute, relative and rubber invariant with $(d^\prime,n^\prime) < (d,n)$ has been computed, as well as every forgetful relative invariant with $(d^\prime,n^\prime,t^\prime) < (d,n+1,t)$.
+As noted above, we may assume that $d \geq 1$ which means that there exists a true marking $x_1$ with $\alpha_1 \geq 1$.
+We will decrease the tangency at $x_1$.
+Consider the vector of tangency orders
+\begin{equation*} \alpha - e_1 \end{equation*}
+obtained from $\alpha$ by replacing the entry $\alpha_1$ by $\alpha_1-1$. Consider then the moduli space:
 \begin{equation*} \VZ_{1,(\alpha-e_1) \cup (1)}(X|Y,\beta). \end{equation*}
-Denote the newly-introduced marking by $y$ and consider the integrand $\tilde\gamma$ obtained from $\gamma$ by introducing $\fgt_y^\st$ everywhere. Applying our recursion formula to $x_1$, we obtain:
+Denote the newly-introduced marking by $y$ and take the integrand $\tilde\gamma=\fgt_y^\st \gamma$. Applying our recursion formula to $x_1$, we obtain:
 \begin{equation}\label{step 1 recursion}\left( (\alpha_1-1)\psi_1 + \ev_1^\st Y\right) \tilde\gamma \cap [\VZ_{1,(\alpha-e_1) \cup (1)}(X|Y,\beta)] = \tilde\gamma \cap [\Dcal(1)].\end{equation}
-Let us first examine the left-hand side.
+We first examine the left-hand side.
 The class $\psi_1$ differs from $\fgt_y^\st \psi_1$ by the locus where $x_1$ and $y$ are contained on a contracted rational bubble.
-This locus consists of reduced relative stable maps of the form \medskip
+This locus consists of stable maps of the form \medskip
 
@@
 This is isomorphic to $\VZ_{1,\alpha}(X|Y,\beta)$ and when we restrict $\tilde\gamma$ to this locus we obtain precisely the class $\gamma$ which we started with.
-Thus the left-hand side of \eqref{step 1 recursion} may be written as
-\begin{equation*} (\alpha_1-1) I + \fgt_y^\st \left( (\alpha_1-1)\psi_1 + \ev_1^\st Y\right)  \tilde\gamma \cap [\VZ_{1,(\alpha-e_1)\cup(1)}(X|Y,\beta)]\end{equation*}
-where $I$ is the invariant we are trying to compute.
-The second term is a forgetful relative invariant with the same degree and number of true markings (since $y$ is fictitious), and strictly smaller true tangency; hence it is recursively known.
-We now examine the right-hand side of \eqref{step 1 recursion}.
+Thus \eqref{step 1 recursion} may be written as
+\begin{equation} \label{step 1 recursion 2} (\alpha_1-1) I + \fgt_y^\st \left( (\alpha_1-1)\psi_1 + \ev_1^\st Y\right)  \tilde\gamma \cap [\VZ_{1,(\alpha-e_1)\cup(1)}(X|Y,\beta)] = \tilde\gamma \cap [\Dcal(1)].
+\end{equation}
+where $I$ is the invariant we are trying to compute. We will now show that the other terms have already been computed earlier in the recursion.
+
+The second term on the left-hand side is a forgetful relative invariant with the same degree and number of true markings (since $y$ is fictitious), and strictly smaller true tangency; hence it has been computed at an earlier step in the recursion.
+We now examine the right-hand side of \eqref{step 1 recursion 2}.
 Recall that all of the genus zero data has already been computed, so we only need to focus on the genus one pieces.
 First consider the type I loci.
-The genus one piece has strictly smaller degree (and hence is recursively known) except in the following situation (with some stable distribution of the remaining markings):
+The genus one piece has strictly smaller degree (and so has already been computed) except in the following situation (with some stable distribution of the remaining markings):
 \begin{center}
@@
 \end{center}
-In this situation, $C_1$ contains at most $n+1$ true markings.
-If it has $n-1$ or fewer, than it is known recursively.
-If it has exactly $n$ this means that $C_0$ contains exactly one true marking (besides $x_1$, which may be true or fictitious).
-We claim that in this situation we must have $y \in C_1$, since otherwise we would have a moduli space for $C_0$ given by $\ol\Mcal_{0,k}$ with $k \geq 4$, and  applying the projection formula with $\fgt_y$ we would conclude that the contribution is zero.
-Thus we have $y \in C_1$, and so the genus one contribution is a forgetful relative invariant with $n$ true markings, and hence is recursively known.
-
-Finally, if $C_1$ contains exactly $n+1$ true markings, then the only additional markings on $C_0$ are fictitious, and by the same argument as in the previous paragraph there can only be one.
+In this situation, $C_1$ contains at most $n+1$ true markings. We consider three possible cases:
+\begin{enumerate}
+\item If $C_1$ has $n-1$ or fewer true markings, then it has already been computed earlier in the recursion.
+\item If $C_1$ has exactly $n$ true markings, then $C_0$ contains exactly one true marking besides $x_1$ (which itself may be true or fictitious).
+In this situation we must have $y \in C_1$, since otherwise we would have a moduli space for $C_0$ given by $\ol\Mcal_{0,k}$ with $k \geq 4$, and applying the projection formula with $\fgt_y$ we would conclude that the contribution is zero.
+Thus we have $y \in C_1$, and so the genus one contribution is a forgetful relative invariant with $n$ true markings, and so has already been computed.
+\item Finally, if $C_1$ contains exactly $n+1$ true markings, then the only additional markings on $C_0$ are fictitious, and by the same argument as in the previous paragraph there can only be one.
 Thus for each fictitious marked point we obtain a locus isomorphic to $\VZ_{1,\alpha}(X|Y,\beta)$ and $\tilde\gamma$ restricts to $\gamma$ here (from the point of view of computing invariants, the fictitious marked points are indistinguishable, meaning that the contributions are all the same).
-Thus for each fictitious marked point (of which there is at least one, namely $y$) we get a contribution of $\alpha_1 I$ to the right-hand side of \eqref{step 1 recursion}.
-
-The contributions of the type II loci only involve genus zero data and hence are known.
-The contributions of the type $\dag$ loci are determined by genus zero data and tautological integrals on Deligne--Mumford space, hence are also known.
+Thus for each fictitious marked point (of which there is at least one, namely $y$) we get a contribution of $\alpha_1 I$ to the right-hand side of \eqref{step 1 recursion 2}, where as before $I$ is the invariant we are trying to compute.
+\end{enumerate}\medskip
+The contributions of the type II loci only involve genus zero data and so can be computed algorithmically following \cite{Ga}.
+
+The contributions of the type $\dag$ loci are determined by genus zero data and tautological integrals on Deligne--Mumford space, and so can also be computed algorithmically.
+
 It remains to consider type III loci.
@@
 But by assumption there is another marked point $x_0$ with all of the insertions pulled back along $\fgt_{x_0}$, so a further application of the projection formula shows that this contribution vanishes.
-To conclude, we may rearrange \eqref{step 1 recursion} to obtain an expression of the form
-\begin{equation*} \lambda I = \text{recursively known terms} \end{equation*}
+To conclude, we may rearrange \eqref{step 1 recursion 2} to obtain an expression of the form
+\begin{equation*} \lambda I = \text{previously computed terms} \end{equation*}
 where $\lambda$ is an explicit scalar which is always nonzero; we have thus determined $I$, which completes Step 1.
 
-\subsection*{Step 2} Consider now the absolute space $\VZ_{1,n}(Y,\beta)$ with an insertion $\gamma$, and suppose inductively that we have computed all forgetful relative invariants with $(d^\prime,n^\prime) \leq (d,n+1)$, all relative invariants and absolute invariants with $(d^\prime,n^\prime) < (d,n)$, and all special rubber invariants with $d^\prime < d$.
-Consider the following moduli space with $n+1$ markings:
+\subsection*{Step 2} Consider now the absolute space $\VZ_{1,n}(Y,\beta)$ with an insertion $\gamma$, and suppose inductively that we have computed all forgetful relative invariants with $(d^\prime,n^\prime) \leq (d,n+1)$, all relative invariants and absolute invariants with $(d^\prime,n^\prime) < (d,n)$, and all rubber invariants with $d^\prime < d$.
+\medskip
+
+\noindent \emph{Step 2a.} Consider the following moduli space with $n+1$ markings:
 \begin{equation*} \VZ_{1,(d,0,\ldots,0)}(X|Y,\beta). \end{equation*}
-Let $x_0$ denote the relative marking and consider the integrand $\tilde\gamma$ obtained from $\gamma$ by introducing $\fgt^\st_{x_0}$ everywhere. Now recurse at $x_1$ to obtain:
+Let $x_0$ denote the relative marking and consider the integrand $\tilde\gamma= \fgt_{x_0}^\st \gamma$. Now recurse at $x_1$ to obtain:
 \begin{equation}\label{step 2 recursion} \ev_1^\st Y \cdot \tilde\gamma \cap [\VZ_{1,(d,0,\ldots,0)}(X|Y,\beta)] = \tilde\gamma\cap[\Dcal(1)].\end{equation}
 The left-hand side is a forgetful relative invariant of degree $d$ and $\leq n+1$ true markings, and so has already been computed.
-For the right-hand side, let us begin with loci of type I.
-The genus one contributions from each loci have $(d^\prime,n^\prime) < (d,n)$ except in the following case
+
+On the right-hand side, similar arguments to those in Step~1 show that the contributions of type~II and type~$\dag$ loci have already been computed.
+Similarly, the contributions of type III loci have already been computed, except for the locus where the entire curve is mapped into the divisor.
+On this locus we apply the projection formula to $\fgt_{x_0}$ to identify the contribution with
+\begin{equation*} d^2 \cdot \gamma \cap [\VZ_{1,n}(Y,\beta)] = d^2 \cdot I \end{equation*}
+where $I$ is the invariant we are trying to compute.
+
+Finally, consider loci of type I. The genus one contributions from each locus have $(d^\prime,n^\prime) < (d,n)$ (and hence have already been computed) except in the following case
 \begin{center}
@@
 Here $\gamma$ is the insertion we started with; the difference is that we are now considering relative maps to $(X,Y)$ with maximal tangency at $x_1$, rather than absolute maps to $Y$.
-The type II and $\dag$ loci are recursively determined as in Step~1, and similarly the type III loci are recursively determined except for the locus where the entire curve is mapped into the divisor.
-On this locus we may apply $\fgt_{x_0}$ and identify the contribution with
-\begin{equation*} d^2 \cdot \gamma \cap [\VZ_{1,n}(Y,\beta)] = d^2 \cdot I \end{equation*}
-where $I$ is the invariant we are trying to compute. Putting this all together, we obtain
-\begin{equation}\label{step 2 recursion 2} I = (-\gamma/d) \cap [\VZ_{1,(d,\underbrace{0,\ldots,0}_{n-1})}(X|Y,\beta)] + \text{recursively known terms} \end{equation}
-where on the right-hand side there are $n-1$ non-relative markings $x_2,\ldots,x_n$, and a relative marking $x_1$. We now apply the recursion again to the right-hand side, by considering the space
+Putting this all together, we obtain from \eqref{step 2 recursion}
+\begin{equation}\label{step 2 recursion 2} I = (-\gamma/d) \cap [\VZ_{1,(d,\underbrace{0,\ldots,0}_{n-1})}(X|Y,\beta)] + \text{previously computed terms} \end{equation}
+where on the right-hand side there are $n-1$ non-relative markings $x_2,\ldots,x_n$, and a relative marking $x_1$.\medskip
+
+\noindent \emph{Step 2b.} We now apply the recursion to the right-hand side of \eqref{step 2 recursion 2}. Consider the space
 \begin{equation*} \VZ_{1,(d-1,1,0,\ldots,0)}(X|Y,\beta) \end{equation*}
-where $x_1$ now has tangency $d-1$ and we have introduced a new marking $y$ with tangency $1$.
-We consider a new insertion, denoted $\tilde\gamma$ as usual, by introducing $\fgt_y^\st$ everywhere.
-Recursing at $x_1$ we obtain:
+where $x_1$ now has tangency $d-1$ and we have introduced a new marking $y$ with tangency $1$. As usual we take the insertion $\tilde\gamma=\fgt_y^\st \gamma$. Recursing at $x_1$ we obtain:
 \begin{equation}\label{step 2 recursion 3} \left( (d-1)\psi_1 + \ev_1^\st Y \right)\cdot(-\tilde\gamma/d) \cap [\VZ_{1,(d-1,1,0,\ldots,0)}(X|Y,\beta)] = (-\tilde\gamma/d) \cap [\Dcal(1)].\end{equation}
@@
 \begin{equation*} (d-1)\cdot(-\gamma/d) \cap [\VZ_{1,(d,\underbrace{0,\ldots,0}_{n-1})}(X|Y,\beta)].\end{equation*}
-What remains on the left-hand side is a forgetful relative invariant of degree $d$ and $\leq n+1$ true markings ($y$ being the ``forgetful'' marking), hence is recursively known.
+What remains on the left-hand side  of \eqref{step 2 recursion 3} is a forgetful relative invariant with degree $d$ and $\leq n+1$ true markings (here $y$ is the ``forgetful marking''); this has been computed earlier in the recursion.
+
 On the right-hand side, the type I loci are recursively known except possibly in the following special cases (with some stable distribution of the remaining non-relative markings):
@@
 \end{center}
-In Case 1 the contribution from $C_1$ is a forgetful relative invariant with $\leq n$ true markings, hence is recursively known.
-In Case 2, we first note that there cannot be any more markings on $C_0$ (since otherwise we could apply $\fgt_y$ and conclude that the contribution vanishes).
-Thus we obtain a single locus, which contributes precisely
-\begin{equation*} d\cdot(-\gamma/d) \cap [\VZ_{1,(d,\underbrace{0,\ldots,0}_{n-1})}(X|Y,\beta)] = -\gamma\cap[\VZ_{1,(d,\underbrace{0,\ldots,0}_{n-1})}(X|Y,\beta)]\end{equation*}
-which gives us the first term on the right-hand side of \eqref{step 2 recursion 2}.
-As usual the type II and $\dag$ contributions are known recursively, and the only type III contribution not known recursively occurs when the entire curve is mapped into the divisor, in which case we apply $\fgt_y$ to calculate the contribution as:
+We deal with these cases individually:
+\begin{itemize}
+\item In Case 1, the contribution from $C_1$ is a forgetful relative invariant with $\leq n$ true markings, and hence has previously been computed. 
+\item In Case 2, we first note that there cannot be any more markings on $C_0$ (since otherwise applying the projection formula with $\fgt_y$ shows that the contribution vanishes).
+We thus obtain a single locus, which contributes precisely:
+\begin{equation*} d\cdot(-\gamma/d) \cap [\VZ_{1,(d,\underbrace{0,\ldots,0}_{n-1})}(X|Y,\beta)] = -\gamma\cap[\VZ_{1,(d,\underbrace{0,\ldots,0}_{n-1})}(X|Y,\beta)].\end{equation*}
+\end{itemize}
+As in Step~1 we see that the type II and type $\dag$ contributions have already been computed.
+Finally, the only type III contribution which has not been computed occurs when the entire curve is mapped into the divisor.
+In this case we apply the projection formula with $\fgt_y$ to calculate the contribution as:
 \begin{equation*} (-\gamma/d) \cap [\VZ_{1,n}(Y,\beta)] = -I/d.\end{equation*}
-Substituting into \eqref{step 2 recursion 2} we end up with
-\begin{equation*} I(1-d^{-1}) = \text{recursively known terms} \end{equation*}
+Thus \eqref{step 2 recursion 3} gives:
+\begin{equation*} -(\gamma/d) \cap [\VZ_{1,(d,\underbrace{0,\ldots,0}_{n-1})}(X|Y,\beta)] = I/d + \text{previously computed terms}.\end{equation*}
+Substituting into \eqref{step 2 recursion 2}, we obtain
+\begin{equation*} I\cdot(1-d^{-1}) = \text{previously computed terms} \end{equation*}
 which completes the recursion step as long as $d \neq 1$.
-But since $\VZ_{1,n}(H,1)=\emptyset$ as noted in Remark~\ref{rem: constant-maps}, it follows that $\VZ_{1,n}(Y,\beta)=\emptyset$ if $d=Y\cdot\beta=1$, so we may always assume $d \geq 2$ in the recursion.
+But since $\VZ_{1,n}(H,1)=\emptyset$ as noted in Remark~\ref{rem: constant-maps}, it follows that $\VZ_{1,n}(Y,\beta)=\emptyset$ if $d=Y\cdot\beta=1$, so we may assume $d \geq 2$ in this step.
 
@@
 As usual the type II and $\dag$ contributions are recursively known.
-The type $III$ contributions are determined by lower-degree rubber invariants, except for when the whole curve is mapped into $Y$; however in this case we may apply $\fgt_y$ to identify the contribution with an absolute invariant of $Y$ with degree $d$ and $n$ markings, which is also recursively known.
+The type III contributions are determined by lower-degree rubber invariants, except for when the whole curve is mapped into $Y$; however in this case we may apply $\fgt_y$ to identify the contribution with an absolute invariant of $Y$ with degree $d$ and $n$ markings, which is also recursively known.
 Thus we have determined the invariant $I$.

### 2020-11-03 EllipticSingularitiesSplitting.tex
Finished changes to recursion section

@@
 \end{equation}
-where $I$ is the invariant we are trying to compute. We will now show that the other terms have already been computed earlier in the recursion.
+where $I$ is the invariant we are trying to compute. We will now show that the other terms may be expressed in terms of invariants computed earlier in the recursion.
 
@@
 \begin{enumerate}
-\item If $C_1$ has $n-1$ or fewer true markings, then it has already been computed earlier in the recursion.
+\item If $C_1$ has $n-1$ or fewer true markings, then its contribution has already been computed earlier in the recursion.
 \item If $C_1$ has exactly $n$ true markings, then $C_0$ contains exactly one true marking besides $x_1$ (which itself may be true or fictitious).
@@
 The contributions of the type II loci only involve genus zero data and so can be computed algorithmically following \cite{Ga}.
-
-The contributions of the type $\dag$ loci are determined by genus zero data and tautological integrals on Deligne--Mumford space, and so can also be computed algorithmically.
+The contributions of the type $\dag$ loci are determined by genus zero data and tautological integrals on genus one Deligne--Mumford spaces, which can also be computed algorithmically using the string and dilaton equations.
 
@@
 To conclude, we may rearrange \eqref{step 1 recursion 2} to obtain an expression of the form
-\begin{equation*} \lambda I = \text{previously computed terms} \end{equation*}
-where $\lambda$ is an explicit scalar which is always nonzero; we have thus determined $I$, which completes Step 1.
+\begin{equation*} \lambda I = \text{polynomial in previously computed invariants} \end{equation*}
+where $\lambda$ is an explicit scalar which is always nonzero; we have thus determined the forgetful relative invariant $I$, which completes Step 1.
 
@@
 
-On the right-hand side, similar arguments to those in Step~1 show that the contributions of type~II and type~$\dag$ loci have already been computed.
+On the right-hand side, similar arguments to those in Step~1 show that the contributions of type~II and type~$\dag$ loci can be expressed in terms of invariants computed earlier in the recursion.
 Similarly, the contributions of type III loci have already been computed, except for the locus where the entire curve is mapped into the divisor.
@@
 Putting this all together, we obtain from \eqref{step 2 recursion}
-\begin{equation}\label{step 2 recursion 2} I = (-\gamma/d) \cap [\VZ_{1,(d,\underbrace{0,\ldots,0}_{n-1})}(X|Y,\beta)] + \text{previously computed terms} \end{equation}
+\begin{equation}\label{step 2 recursion 2} I = (-\gamma/d) \cap [\VZ_{1,(d,\underbrace{0,\ldots,0}_{n-1})}(X|Y,\beta)] + \text{polynomial in previously computed invariants} \end{equation}
 where on the right-hand side there are $n-1$ non-relative markings $x_2,\ldots,x_n$, and a relative marking $x_1$.\medskip
@@
 \end{itemize}
-As in Step~1 we see that the type II and type $\dag$ contributions have already been computed.
-Finally, the only type III contribution which has not been computed occurs when the entire curve is mapped into the divisor.
-In this case we apply the projection formula with $\fgt_y$ to calculate the contribution as:
+As in Step~1, we see that the type II and type $\dag$ contributions have already been computed earlier in the algorithm.
+The only type III locus whose contribution has not previously been computed is when the entire curve is mapped into the divisor.
+In this case we apply the projection formula with $\fgt_y$ to calculate its contribution as:
 \begin{equation*} (-\gamma/d) \cap [\VZ_{1,n}(Y,\beta)] = -I/d.\end{equation*}
 Thus \eqref{step 2 recursion 3} gives:
-\begin{equation*} -(\gamma/d) \cap [\VZ_{1,(d,\underbrace{0,\ldots,0}_{n-1})}(X|Y,\beta)] = I/d + \text{previously computed terms}.\end{equation*}
+\begin{equation*} -(\gamma/d) \cap [\VZ_{1,(d,\underbrace{0,\ldots,0}_{n-1})}(X|Y,\beta)] = I/d + \text{polynomial in previously computed invariants}.\end{equation*}
 Substituting into \eqref{step 2 recursion 2}, we obtain
-\begin{equation*} I\cdot(1-d^{-1}) = \text{previously computed terms} \end{equation*}
+\begin{equation*} I\cdot(1-d^{-1}) = \text{polynomial in previously computed invariants} \end{equation*}
 which completes the recursion step as long as $d \neq 1$.
@@
 
+We have thus computed the reduced absolute invariant of $Y$ of degree $d$ and $n$ markings, which completes Step 2.
+
 \subsection*{Step 3} Now suppose we are given a relative space $\VZ_{1,\alpha}(X|Y,\beta)$ with an insertion $\gamma$, and suppose inductively that we have computed all forgetful relative invariants with $(d^\prime,n^\prime) \leq (d,n+1)$, all absolute invariants with $(d^\prime,n^\prime) \leq (d,n)$, all relative invariants with $(d^\prime,n^\prime,t^\prime)<(d,n,t)$ and all rubber invariants with $d^\prime < d$.
+
 Choose a true marking $x_1$ with $\alpha_1 \geq 1$ and consider the moduli space
 \begin{equation*} \VZ_{1,(\alpha-e_1)\cup(1)}(X|Y,\beta) \end{equation*}
-where $y$ is the newly-introduced marking. As usual consider the insertion $\tilde\gamma$ obtained from $\gamma$ by introducing $\fgt_y$ everywhere. Recursing at $x_1$ we obtain:
-\begin{equation*} \left( (\alpha_1-1)\psi_1 + \ev_1^\st H\right) \tilde\gamma \cap [\VZ_{1,(\alpha-e_1)\cup(1)}(X|Y,\beta)] = \tilde\gamma \cap [\Dcal(1)].\end{equation*}
-The left-hand side is a relative invariant with the same degree and number of true markings, but smaller true tangency: hence it is recursively known.
-On the right-hand side, the type I contributions are recursively known except for those of the following form
-
+where $y$ is the newly-introduced marking. As usual consider the insertion $\tilde\gamma=\fgt_y^\star \gamma$. Recursing at $x_1$ we obtain:
+\begin{equation}\label{step 3} \left( (\alpha_1-1)\psi_1 + \ev_1^\st H\right) \tilde\gamma \cap [\VZ_{1,(\alpha-e_1)\cup(1)}(X|Y,\beta)] = \tilde\gamma \cap [\Dcal(1)].\end{equation}
+The left-hand side is a relative invariant with the same degree and number of true markings, but smaller true tangency; hence it has already been computed in the recursion.
+
+On the right-hand side, the type I contributions have already been computed except for those of the following form
 \begin{center}
@@
 where $C_0$ contains a single fictitious marking (if it had multiple fictitious markings then the contribution would vanish by projection formula) and all the other markings are on $C_1$.
-Thus for each fictitious marking we get a contribution of $\alpha_1 I$ where $I$ is the invariant we are trying to compute.
-Note that $\alpha_1 \neq 0$, and that this term appears at least once since $y$ is a fictitious marking; so we get a nonzero multiple of $I$.
-
-As usual the type II and $\dag$ contributions are recursively known.
-The type III contributions are determined by lower-degree rubber invariants, except for when the whole curve is mapped into $Y$; however in this case we may apply $\fgt_y$ to identify the contribution with an absolute invariant of $Y$ with degree $d$ and $n$ markings, which is also recursively known.
-Thus we have determined the invariant $I$.
-
-\subsection*{Step 4} Finally, consider a rubber space $\VZ^{\leftrightarrow}_{1,\alpha}(\mathbb P|Y_0+Y_\infty,\beta)$ with insertion $\gamma$.
+There is one such locus for each fictitious marking, and each contributes $\alpha_1 I$ where $I$ is the invariant we are trying to compute.
+Note that $\alpha_1 \neq 0$, and that this term appears at least once since $y$ is a fictitious marking; so we obtain a nonzero multiple of $I$.
+
+Using the same arguments as in Step~1, we see that the type II and $\dag$ contributions have already been computed.
+The type III contributions are determined by lower-degree rubber invariants, except for when the whole curve is mapped into $Y$; however in this case we may apply the projection formula with $\fgt_y$ to identify the contribution with an absolute invariant of $Y$ with degree $d$ and $n$ markings, which has also been computed earlier (in Step 2).
+We therefore see that \eqref{step 3} may be rearranged to give:
+\begin{equation*} I = \text{polynomial in previously computed invariants}.\end{equation*}
+We have thus computed the reduced relative invariant of $(X,Y)$ with degree $d$, $n$ true markings and true tangency $t$, which completes Step 3.
+
+\subsection*{Step 4} For the final step, consider a rubber space $\VZ^{\leftrightarrow}_{1,\alpha}(\mathbb P|Y_0+Y_\infty,\beta)$ with insertion $\gamma$.
 Suppose inductively that we have computed all absolute and relative invariants with $d^\prime \leq d$ and all rubber invariants with $(d^\prime,n^\prime,m^\prime) < (d,n,m)$.
 
-We first note the following important reduction: if there exists a relative marking $x_k$ such that all insertions are pulled back along $\fgt_{k}$, then we may apply the projection formula, together with the fact that
+We first note the following important reduction: if there exists a relative marking $x_k$ such that all insertions are pulled back along $\fgt_{k}$, then we may apply the projection formula, together with the following identity (arising from the torsion in the Jacobian of an elliptic curve)
 \begin{equation*} (\fgt_{k})_\st [\VZ^{\leftrightarrow}_{1,\alpha}(\mathbb P|Y_0+Y_\infty,\beta)] = \alpha_k^2 \cdot [\VZ_{1,n+m-1}(Y,\beta)] \end{equation*}
-to identify the rubber invariant with a multiple of a reduced invariant of $Y$, which has the same degree and hence is known recursively.
+to identify the rubber invariant with a multiple of a reduced invariant of $Y$, which has the same degree and hence has been computed earlier.
 
@@
 obtained by introducing a marked point $y$ with no tangency.
-Let $x_1$ be a positive-tangency marking (such a marking always exists since $d \geq 2$) and let $\tilde\gamma$ be the insertion obtained from $\gamma$ by replacing $\ev_1$ and $\psi_1$ by $\ev_y$ and $\psi_y$, and then introducing $\fgt_{1}^\st$ everywhere.
-
-We will make use of a recursion formula for rubber spaces analogous to the recursion formula for relative spaces used in Steps 1--3.
-Following \cite{EKatz}, there is a line bundle $L_y^{\not\in \operatorname{bot}}$ on $\VZ^{\leftrightarrow}_{1,\alpha\cup (0)}(\mathbb P|Y_0+Y_\infty,\beta)$, together with a section $s_y^{\not\in\operatorname{bot}}$ whose vanishing locus consists of the locus $\Dcal(y)$ of rubber maps where $y$ is not mapped into the bottom level of the expanded target.
+Let $x_1$ be a positive-tangency marking (such a marking always exists since $d \geq 2$) and let $\tilde\gamma$ be the insertion obtained from $\gamma$ by replacing $\ev_1$ and $\psi_1$ by $\ev_y$ and $\psi_y$, and then pulling back along $\fgt_1$.
+
+We will make use of a recursion formula for rubber spaces analogous to the recursion formula for relative spaces used in Steps 1--3. Following \cite{EKatz}, there is a line bundle
+\begin{equation*} L_y^{\not\in \operatorname{bot}} \text{ on } \VZ^{\leftrightarrow}_{1,\alpha\cup (0)}(\mathbb P|Y_0+Y_\infty,\beta)\end{equation*}
+together with a section $s_y^{\not\in\operatorname{bot}}$ whose vanishing locus consists of the locus $\Dcal(y)$ of rubber maps where $y$ is not mapped into the bottom level of the expanded target.
 As in \S \ref{Section Gathmann line bundle}, we can give a logarithmic interpretation of this: it corresponds to the piecewise-linear function on the tropical moduli space which associates, to every rubber tropical map, the distance between $\varphi(\sqC_y)$ and the leftmost vertex of the tropical target, where $\sqC_y$ is the vertex of the source curve containing the flag corresponding to $y$.
-Using this tropical description, we may easily calculate the vanishing orders of $s_y^{\not\in\operatorname{bot}}$ along the various components of $\Dcal(y)$, and show that $\cchern_1(L_y^{\not\in\operatorname{bot}}) = \Psi_0 - \ev_y^\st Y$ (see also \cite{EKatzLB}, where similar results in the non-reduced setting are obtained, using different methods).
-From this, we obtain a rubber recursion formula
-\begin{equation}\label{step 4 recursion} (\Psi_0 - \ev_y^\st Y) \tilde\gamma \cap [\VZ^{\leftrightarrow}_{1,\alpha\cup(0)}(\mathbb P|Y_0+Y_\infty,\beta)] = \tilde\gamma \cap [\Dcal(y)]\end{equation}
-where the fundamental class $[\Dcal(y)]$ is weighted by vanishing orders on the components.
-We will first show that the left-hand side is recursively known.
-By construction the class $\tilde\gamma$ is pulled back via $\fgt_{1}^\st$, and the same is true for $\ev_y^\st Y$.
+Using this tropical description, we may easily calculate the vanishing orders of $s_y^{\not\in\operatorname{bot}}$ along the various components of $\Dcal(y)$, and show that
+\begin{equation*}\cchern_1(L_y^{\not\in\operatorname{bot}}) = \Psi_0 - \ev_y^\st Y\end{equation*}
+where $\Psi_0$ is a target psi class (see also \cite{EKatzLB}, where similar results in the non-reduced setting are obtained, using different methods). From this, we obtain a rubber recursion formula
+\begin{equation}\label{step 4 recursion} (\Psi_0 - \ev_y^\st Y)\cdot \tilde\gamma \cap [\VZ^{\leftrightarrow}_{1,\alpha\cup(0)}(\mathbb P|Y_0+Y_\infty,\beta)] = \tilde\gamma \cap [\Dcal(y)]\end{equation}
+where the fundamental class $[\Dcal(y)]$ is weighted by vanishing orders on the components.\medskip
+
+\noindent \emph{Step 4a.} We will first show that the left-hand side can be expressed in terms of previously computed invariants.
+By construction the classes $\tilde\gamma$ and $\ev_y^\star Y$ are both pulled back along $\fgt_{1}$.
 It remains to examine $\Psi_0$.
@@
 \begin{equation*}\label{Psi0 formula} \Psi_0 = -\alpha_2 \hat\psi_2 - \ev_2^\st Y \end{equation*}
-where $\hat\psi_2$ is a \textbf{non-collapsed} psi class.
-(If there are no negative-tangency markings, then the construction given in \cite[\S 1.5.2]{MaulikPandharipande} shows that $\Psi_0=0$.) Now, $\hat\psi_2 - \psi_2$ is given by the loci where $x_2$ belongs to a trivial bubble.
+where $\hat\psi_2$ is a \textbf{non-collapsed} psi class. (If there are no negative-tangency markings, then the construction given in \cite[\S 1.5.2]{MaulikPandharipande} shows that $\Psi_0=0$.)
+
+Now, $\hat\psi_2 - \psi_2$ is given by the locus where $x_2$ belongs to a trivial bubble.
 This entails a splitting of the curve into pieces, each of which contributes a rubber integral.
-Typically each of these pieces will have $(g^\prime,d^\prime,n^\prime,m^\prime) < (1,d,n,m)$ and hence be recursively known.
+Typically each such piece will have $(g^\prime,d^\prime,n^\prime,m^\prime) < (1,d,n,m)$ and hence has previously been computed.
 The one exception is when all of the genus and degree is concentrated on the top level of the expansion, with the bottom level containing only a single non-relative marking in addition to all the negative-tangency markings.
-But in this case the contribution is a rubber invariant where all of the insertions are pulled back via $\fgt_1^\st$, and hence we may apply the projection formula to identify this with an absolute invariant of $Y$ which is recursively known.
-We conclude that, up to recursively known terms, we may replace $\hat\psi_2$ by $\psi_2$ in the left-hand side of \eqref{step 4 recursion}.
+But in this case the contribution is a rubber invariant where all of the insertions are pulled back along $\fgt_1$, and hence we may apply our fundamental reduction, using the projection formula to identify the rubber invariant with (a multiple of) an absolute invariant of $Y$, which has previously been computed.
+We conclude that, up to previously computed terms, we may replace $\hat\psi_2$ by $\psi_2$ in the left-hand side of \eqref{step 4 recursion}.
+
 If we now compare $\psi_2$ with $\fgt_1^\st \psi_2$ we see that the difference is given by the locus where $x_1$ and $x_2$ belong to a collapsed rational piece.
-The contribution of this locus consists of rubber invariant with strictly fewer relative markings, and hence is recursively known.
-So up to recursively-known terms \eqref{step 4 recursion} becomes
-\begin{equation*} \fgt_1^\st (-\alpha_2\psi_2 - \ev_y^\st Y)\tilde\gamma \cap [\VZ^{\leftrightarrow}_{1,\alpha\cup(0)}(\mathbb P|Y_0+Y_\infty,\beta)] = \tilde\gamma\cap[\Dcal(y)]\end{equation*}
-and now the left-hand side is also recursively known, by the projection formula.
-Let us now examine the right-hand side.
-The components of $\Dcal(y)$ are indexed by splittings of the curve, and certainly the contributions are recursively known unless there is a piece of the curve carrying all of the genus and degree, so we may restrict to examining these contributions.
-
+The contribution of this locus consists of rubber invariants with strictly fewer relative markings, and hence is recursively known.
+So up to previously computed invariants, \eqref{step 4 recursion} becomes
+\begin{equation}\label{step 4 recursion 2} \fgt_1^\st (-\alpha_2\psi_2 - \ev_y^\st Y)\tilde\gamma \cap [\VZ^{\leftrightarrow}_{1,\alpha\cup(0)}(\mathbb P|Y_0+Y_\infty,\beta)] = \tilde\gamma\cap[\Dcal(y)]\end{equation}
+and now the left-hand side can also be expressed in terms of previously computed invariants, via the projection formula. \medskip
+
+\noindent \emph{Step 4b.} Let us now examine the right-hand side of \eqref{step 4 recursion 2}.
+The components of $\Dcal(y)$ are indexed by splittings of the curve, and the contributions can be expressed in terms of previously computed invariants unless there is a piece of the curve carrying all of the genus and degree.
+We therefore restrict to considering these cases.
 Denote the piece of the curve carrying all of the genus and degree by $C^\prime\subseteq C$.
-If $C^\prime$ is mapped to top level, then either it contains $x_1$, in which case we apply $\fgt_1$ to compute the contribution, or it does not contains $x_1$, in which case it has fewer than $n$ relative markings and is known recursively.
-If on the other hand $C^\prime$ is not mapped to top level, then generically it is mapped to the bottom level (since generically the core is not contracted on this locus, so the desingularisation process does nothing).
+\begin{enumerate}
+\item If $C^\prime$ is mapped to top level, then either it contains $x_1$, in which case we apply $\fgt_1$ to compute the contribution, or it does not contains $x_1$, in which case it has fewer than $n$ relative markings and is known recursively.
+\item  If on the other hand $C^\prime$ is not mapped to top level, then generically it is mapped to the bottom level (since generically the core is not contracted on this locus, so the desingularisation process does nothing).
 One possible contribution is given by the following locus
@@
 \end{center}
-which contributes a nonzero multiple of the invariant $I$ we are trying to compute.
+with all other markings located on the genus one vertex. This contributes a nonzero multiple of the invariant $I$ we are trying to compute.
+
 For the other possibilities, first note that, unless every component at the top level contains a single positive-tangency marking and a single node (together with possibly some tangency-zero markings), then $C^\prime$ has fewer than $n$ relative markings and hence the contribution is known recursively.
 On the other hand, if any non-relative marking other than $y$ is mapped to the top level, $C^\prime$ has $\leq n$ relative markings and less than $m$ non-relative markings, and hence again the contribution is known recursively.
-The only remaining possibilities are when $x_1$ is replaced by another positive-tangency marking $x_k$ in the above picture; but then the contribution can be calculated by applying the projection formula to $\fgt_{1}$.
-We therefore conclude that the only contribution to the right-hand side of \eqref{step 4 recursion} which is not known recursively is a nonzero multiple of the invariant we were trying to compute.
-This completes the recursion step.
+The only remaining possibilities are when $x_1$ is replaced by another positive-tangency marking $x_k$ in the above picture; but then the contribution can be calculated by applying the projection formula with $\fgt_{1}$.
+\end{enumerate}
+We therefore conclude that the only contribution to the right-hand side of \eqref{step 4 recursion 2} which cannot be expressed in terms of previously computed invariants is a nonzero multiple of the invariant we were trying to compute.
+We thus compute the reduced rubber invariant of $\PP$ with degree $d$, $n$ relative markings and $m$ non-relative markings, which completes Step 4 and the recursion.
 

### 2020-11-04 EllipticSingularitiesSplitting.tex
Finished changes to Section 5

@@
 
-\section{Degeneration of contact order}\label{Section Gathmann line bundle} Consider the moduli space $\VZ_{1,\alpha}(\PP^m|H,d)$ of relative maps that factor completely.
+\section{Degeneration of contact order}\label{Section Gathmann line bundle}
+\noindent Consider the moduli space $\VZ_{1,\alpha}(\PP^m|H,d)$ of relative maps that factor completely.
 \begin{dfn}
@@
 \section{Quantum Lefschetz algorithm}\label{section recursion algorithm}
-Consider a smooth pair $(X,Y)$ with $Y$ very ample, and let $\mathbb{P}$ be the projective bundle $\mathbb{P}=\PP_Y(\operatorname{N}_{Y|X} \oplus\OO_Y)$.
-We assume that the genus zero and reduced genus one Gromov--Witten theories of $X$ are known.
+\noindent Consider a smooth pair $(X,Y)$ with $Y$ very ample, and let $\mathbb{P}$ be the projective bundle $\mathbb{P}=\PP_Y(\operatorname{N}_{Y|X} \oplus\OO_Y)$.
+We assume that all genus zero and reduced genus one Gromov--Witten invariants of $X$ are known.
 From this starting data, we will apply our recursion formula to compute:
@@
 
-\subsection{Reduced absolute, relative and rubber invariants} To be precise: by a reduced invariant of $Y$ we mean an integral over $\VZ_{1,n}(Y,\beta)$ of products of pullbacks of evaluation and psi classes along morphisms which forget a subset $S$ of the marked points (taking $S=\emptyset$ gives the ordinary evaluation and psi classes).
-Here the evaluation maps are viewed as mapping into $X$ (hence the adjective ``restricted'').
-Reduced relative invariants of $(X,Y)$ are defined in the same way, except now the forgetful morphism maps into a space of absolute maps:
-\begin{equation*} \fgt_S \colon \VZ_{1,\alpha}(X|Y,\beta) \to \VZ_{1,m-\#S}(X,\beta).\end{equation*}
+\subsection{Reduced absolute, relative and rubber invariants} To be precise: by a reduced invariant of $Y$ we mean an integral over $\VZ_{1,n}(Y,\beta)$ of a product of evaluation classes and pullbacks of psi classes along morphisms forgetting subsets of the marked points:
+\begin{equation*} \int_{[\VZ_{1,n}(Y,\, \beta)]} \prod_{i=1}^n \fgt_{S_i}^\star \psi_i^{k_i} \cdot \ev_i^\star \gamma_i.\end{equation*}
+(Here $S_i \subseteq \{1,\ldots,n\}$ with $i \not\in S_i$ for all $i$; taking $S=\emptyset$ gives the ordinary  psi classes.).
+The evaluation maps are viewed as mapping into $X$ (hence the adjective ``restricted'').
+Reduced relative invariants of $(X,Y)$ are defined in the same way
+\begin{equation*} \int_{[\VZ_{1,\alpha}(X|Y,\, \beta)]} \prod_{i=1}^n \fgt_{S_i}^\star \psi_i^{k_i} \cdot \ev_i^\star \gamma_i\end{equation*}
+except now the forgetful morphism maps into a space of absolute stable maps:
+\begin{equation*} \fgt_S \colon \VZ_{1,\alpha}(X|Y,\beta) \to \VZ_{1,n-\#S}(X,\beta).\end{equation*}
 Note that even the case $S=\emptyset$ entails a nontrivial forgetful morphism.
@@
 
-The systems of invariants defined above are equivalent to the classical systems of invariants (which do not use forgetful morphisms) by well-known topological recursion relations.
+\begin{remark}The systems of invariants defined above are equivalent to the classical systems of invariants (which do not use forgetful morphisms) by well-known topological recursion relations.\end{remark}
+
+\begin{remark} In the following discussion we will sometimes omit the adjective ``reduced'' when discussing genus one invariants, but it is always implicit; all genus one invariants we consider will be reduced.\end{remark}
 
@@
 Consider a moduli space $\VZ_{1,\alpha}(X|Y,\beta)$ of reduced relative stable maps and a corresponding integrand $\gamma$.
-We let $F \subseteq \{1,\ldots,m\}$ be the maximal subset of marked points such that the following two conditions are satisfied:
+We let $F \subseteq \{1,\ldots,n\}$ be the maximal subset of marked points such that the following two conditions are satisfied:
 \begin{enumerate}
@@
 When inducting on relative invariants we will always be interested in the number of true markings (as opposed to the total number of markings) and the \textbf{true tangency}
-\begin{equation*} \sum_{i \not\in F} \alpha_i \leq d=Y\cdot \beta \end{equation*}
+\begin{equation*} t:= \sum_{i \not\in F} \alpha_i \leq Y\cdot \beta =d\end{equation*}
 as opposed to the total tangency, which is always $d$.
@@
 
-\subsection{Structure of the recursion} Given the genus-zero Gromov--Witten theory of $X$, the arguments of \cite{Ga} give an effective algorithm to reconstruct the genus-zero theories of $Y$ and $(X,Y)$; the genus-zero rubber theory of $\mathbb{P}$ is equal to the genus-zero theory of $Y$ \cite{GathmannThesis}.
-Thus we may assume that all genus-zero invariants are known.
+\subsection{Structure of the recursion} Given the genus zero Gromov--Witten theory of $X$, the results of \cite{Ga} give an effective algorithm to reconstruct the genus zero theories of $Y$ and $(X,Y)$; the genus zero rubber theory of $\mathbb{P}$ is equal to the genus zero theory of $Y$ \cite{GathmannThesis}.
+Thus we may assume that all genus zero invariants are known.
 We assume in addition that we know the genus one reduced theory of $X$.
@@
 
-\noindent Here each loop begins at $0$ and proceeds through successively larger values, with the invariants at each step expressed recursively in terms of invariants computed in the preceding steps.
+\noindent Here each loop begins at $0$ and proceeds through successively larger values, with the invariants at each step expressed recursively in terms of invariants computed in the preceding steps and genus zero invariants.
 Although the loops involving $d, n$ and $m$ have infinite length, in order to compute any single invariant it is only necessarily to iterate the preceding loops for a finite amount of time.
 
-In Step 1 above, a \textbf{forgetful relative invariant} of $(X,Y)$ is by definition a reduced relative invariant for which there exists a marking $x_0$ such that all of the insertions are pulled back along $\fgt_{x_0}$.
+\begin{remark}[Forgetful relative invariants] In Step 1 above, a \textbf{forgetful relative invariant} of $(X,Y)$ is by definition a reduced relative invariant for which there exists a marking $x_0$ such that all of the insertions are pulled back along $\fgt_{x_0}$.
 In our recursion, we first deal with the special class of forgetful relative invariants (with $n+1$ true markings), before computing the absolute invariants (with $n$ markings) and then returning to compute all of the relative invariants (with $n$ true markings).
-The need to separately treat a particular subclass of the relative invariants is an inescapable feature of the genus one recursion.
-
+The need to separately treat a particular subclass of the relative invariants is an inescapable feature of the genus one recursion.\end{remark}
+
+\begin{remark}[The base case]
 The base terms of the recursion all have $d=0$ and as such are easy to compute: the relative invariants of $(X,Y)$ are nothing but absolute invariants of $X$ (i.e.
@@
 The rubber invariants of $\mathbb{P}$ in degree zero are given by integrals over the main component of the double ramification cycle (in the rubber case there may be markings with tangency even for $d=0$, since $d$ only records the degree covering the base); this can likewise be computed as an integral over Deligne--Mumford space, by correcting the formula for the ordinary double ramification cycle \cite{Hain,JPPZ} by the obvious contribution from the boundary irreducible component (the observation which makes this easy to do in genus one is that the rubber moduli space is pure-dimensional, so that the virtual class is simply the sum of the fundamental classes of the irreducible components).
-We will now explain how to perform each of the four inductive steps outlined above.
-
-\begin{notation}Given tuples $\mathbf{a}=(a_1,\ldots,a_n)$ and $\mathbf{b}=(b_1,\ldots,b_n)$, we say that $\mathbf{a}<\mathbf{b}$ if there exists an $i \in \{1,\ldots,n\}$ such that $a_j = b_j$ for $j < i$ and $a_i < b_i$.\end{notation}
+We will now explain how to perform each of the four inductive steps outlined above.\end{remark}
+
+\begin{notation}Given tuples $\mathbf{a}=(a_1,\ldots,a_k)$ and $\mathbf{b}=(b_1,\ldots,b_k)$, we say that $\mathbf{a}<\mathbf{b}$ if there exists an $i \in \{1,\ldots,k\}$ such that $a_j = b_j$ for $j < i$ and $a_i < b_i$.\end{notation}
 
@@
 %target
-\draw [color=blue,->] (0,-1) to (2,-1);
+\draw [color=blue,->] (0,-1) to (4,-1);
 \draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
-\draw [color=blue] (2,-1) node[right]{\small$\Sigma(X|Y)$};
+%\draw [color=blue] (2,-1) node[right]{\small$\Sigma(X|Y)$};
+\draw[color=blue] (2,-1) node{$\times$};
 \end{tikzpicture}
@@
 \draw (2,0) node[above]{\small$\sqC_0$};
-\draw [->] (2,0) -- (3,0);
-\draw (2.9,0) node[right]{$x_1$};
+\draw [->] (2,0) -- (4,0);
+\draw (3.9,0) node[right]{$x_1$};
 
@@
 
-\draw [color=blue,->] (0,-1) to (2,-1);
+\draw [color=blue,->] (0,-1) to (4,-1);
 \draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
-\draw [color=blue] (2,-1) node[right]{\small$\Sigma(X|Y)$};
+%\draw [color=blue] (2,-1) node[right]{\small$\Sigma(X|Y)$};
+\draw[color=blue] (2,-1) node{$\times$};
 \end{tikzpicture}
@@
 where $I$ is the invariant we are trying to compute.
-
-Finally, consider loci of type I. The genus one contributions from each locus have $(d^\prime,n^\prime) < (d,n)$ (and hence have already been computed) except in the following case
+Finally, consider loci of type I.
+The genus one contributions from each locus have $(d^\prime,n^\prime) < (d,n)$ (and hence have already been computed) except in the following case
 \begin{center}
@@
 %target
-\draw [color=blue,->] (0,-1) to (2,-1);
+\draw [color=blue,->] (0,-1) to (4,-1);
 \draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
-\draw [color=blue] (2,-1) node[right]{\small$\Sigma(X|Y)$};
+\draw[color=blue] (2,-1) node{$\times$};
+%\draw [color=blue] (2,-1) node[right]{\small$\Sigma(X|Y)$};
 \end{tikzpicture}
@@
 What remains on the left-hand side  of \eqref{step 2 recursion 3} is a forgetful relative invariant with degree $d$ and $\leq n+1$ true markings (here $y$ is the ``forgetful marking''); this has been computed earlier in the recursion.
-
 On the right-hand side, the type I loci are recursively known except possibly in the following special cases (with some stable distribution of the remaining non-relative markings):
@@
 %target
-\draw [color=blue,->] (0,-1) to (2,-1);
+\draw [color=blue,->] (0,-1) to (4,-1);
 \draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
-\draw [color=blue] (2,-1) node[right]{\small$\Sigma(X|Y)$};
-
+\draw[color=blue] (2,-1) node{$\times$};
+
+%\draw [color=blue] (2,-1) node[right]{\small$\Sigma(X|Y)$};
 \draw (2,-1.3) node[below]{\small{Case 1}};
@@
 %target
-\draw [color=blue,->] (0,-1) to (2,-1);
+\draw [color=blue,->] (0,-1) to (4,-1);
 \draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
-\draw [color=blue] (2,-1) node[right]{\small$\Sigma(X|Y)$};
+\draw[color=blue] (2,-1) node{$\times$};
+
+%\draw [color=blue] (2,-1) node[right]{\small$\Sigma(X|Y)$};
 
@@
 The left-hand side is a relative invariant with the same degree and number of true markings, but smaller true tangency; hence it has already been computed in the recursion.
-
 On the right-hand side, the type I contributions have already been computed except for those of the following form
@@
 
-\draw [color=blue,->] (0,-1) to (2,-1);
+\draw [color=blue,->] (0,-1) to (4,-1);
 \draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
-\draw [color=blue] (2,-1) node[right]{\small$\Sigma(X|Y)$};
+\draw[color=blue] (2,-1) node{$\times$};
+%\draw [color=blue] (2,-1) node[right]{\small$\Sigma(X|Y)$};
 \end{tikzpicture}

### 2020-11-04 Response to referee/AG Genus One Response to Referee.tex
Added Section 5 response to referee comments

 \documentclass[11pt]{amsart}

\usepackage{accents}
\usepackage[all]{xy}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{cite}
\usepackage{color}
\usepackage{epstopdf}
\usepackage{fancyhdr}
\usepackage{float}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{latexsym}
\usepackage{mathrsfs}
\usepackage{natbib}
\usepackage{sseq}
\usepackage{tikz-cd}
\usepackage{url}
\usepackage{verbatim}

%\usepackage{makeidx}
%\makeindex

\usepackage[full]{textcomp}
\usepackage[sups]{Baskervaldx}
\usepackage{cabin}
\usepackage[varqu,varl]{inconsolata}
\usepackage[baskervaldx,bigdelims,vvarbb]{newtxmath}
\usepackage[cal=cm]{mathalfa}

\usepackage[margin=0.8in]{geometry}

%\usepackage{moreverb}
%\usepackage{mathtools}
%\usepackage{marginnote}
%\usepackage{pifont}
%\usepackage{pictexwd,dcpic}
%\usepackage{setspace}
%\usepackage{lastpage}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]

\newtheorem{claim}[theorem]{Claim}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
%\newtheorem{question}[theorem]{Question}

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\theoremstyle{definition}
\newtheorem{aside}[theorem]{Aside}
\newtheorem*{aside*}{Aside}
\newtheorem*{question*}{Question}
\newtheorem{condition}[theorem]{Condition}
\newtheorem{construction}[theorem]{Construction}
\newtheorem{convention}[theorem]{Convention}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{exercise}{Exercise}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{proposition-definition}[theorem]{Proposition-Definition}
\newtheorem{question}[theorem]{Question}
\newtheorem{setting}[theorem]{Setting}

%\numberwithin{equation}{section}

\DeclareMathOperator{\ev}{ev}
\DeclareMathOperator{\vdim}{vdim}
\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\mult}{mult}
\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\Bl}{Bl}
\DeclareMathOperator{\Pic}{Pic}
\DeclareMathOperator{\frPic}{\mathfrak{Pic}}
\DeclareMathOperator{\GW}{GW}
\DeclareMathOperator{\Achow}{A}
\DeclareMathOperator{\pt}{pt}

\newcommand{\virt}[1]{[#1]^{\operatorname{virt}}}
\newcommand{\M}[4]{\overline{\mathcal{M}}_{#1,#2}(#3,#4)}
\newcommand{\Q}[4]{\overline{\mathcal{Q}}_{#1,#2}(#3,#4)}
\newcommand{\C}{\mathbb{C}}
\newcommand{\T}{\mathbb{T}}
\newcommand{\G}{\mathbb{G}}
\newcommand{\PP}{\mathbb{P}}
\newcommand{\OO}{\mathcal{O}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\QQ}{\mathbb{Q}}
\newcommand{\A}{\mathbb{A}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\CP}{\mathbb{CP}}
\newcommand{\PD}{\mathrm{PD}}
\newcommand{\HH}{\operatorname{H}}

\newcommand{\mg}{\mathcal{M}_g}
\newcommand{\mgbar}{\bar{\mathcal{M}}_g}
\newcommand{\mgnbar}{\bar{\mathcal{M}}_{g,n}}
\newcommand{\monbar}{\bar{\mathcal{M}}_{0,n}}

\newcommand{\FF}{\mathcal{F}}
\newcommand{\calChat}{\hat{\cC}}
\newcommand{\calC}{\mathcal{C}}
\newcommand{\calO}{\mathcal{O}}
\newcommand{\calQ}{\mathcal{Q}}
\newcommand{\calL}{\mathcal{L}}
\newcommand{\calLbar}{\underline{\mathcal{L}}}
\newcommand{\frC}{\mathfrak{C}}
\newcommand{\frCbar}{\underline{\mathfrak{C}}}
\newcommand{\frD}{\mathfrak{D}}
\newcommand{\calM}{\mathcal{M}}
\newcommand{\calI}{\mathcal{I}}
\newcommand{\calE}{\mathcal{E}}
\newcommand{\frM}{\mathfrak{M}}
\newcommand{\frN}{\mathfrak{N}}
\newcommand{\frNbar}{\underline{\mathfrak{N}}}
\newcommand{\frX}{\mathfrak{X}}
\newcommand{\frXbar}{\underline{\mathfrak{X}}}
\newcommand{\Cstar}{\C^\times}
\newcommand{\pibar}{\underline{\pi}}
\newcommand{\ubar}{\underline{u}}
\newcommand{\frA}{\mathfrak{A}}
\newcommand{\frAbar}{\underline{\mathfrak{A}}}
\newcommand{\frd}{\mathfrak{d}}
\newcommand{\frF}{\mathfrak{F}}
\newcommand{\frFbar}{\underline{\mathfrak{F}}}
\newcommand{\sbar}{\underline{s}}
\newcommand{\frG}{\mathfrak{G}}
\newcommand{\frL}{\mathfrak{L}}
\newcommand{\frP}{\mathfrak{P}}
\newcommand{\frLbar}{\underline{\mathfrak{L}}}
\newcommand{\vhat}{\overline{v}}
\newcommand{\frE}{\mathfrak{E}}
\newcommand{\Cbar}{\underline{C}}
\newcommand{\Lbar}{\underline{L}}
\newcommand{\vbar}{\overline{v}}

\newcommand{\red}{\text{red}}

\newcommand{\im}{\text{im }}
\newcommand{\tick}{\ding{52}}
\newcommand{\quo}[1]{#1/\mathord{\sim}}
\newcommand{\sltwo}{\operatorname{SL_2}(\mathbb{Z})}
\newcommand{\sltwor}{\operatorname{SL_2}(\mathbb{R})}
\newcommand{\dd}{\text{d}}
\newcommand{\grad}{\text{grad}}
\newcommand{\ind}[1]{\text{Ind}(#1)}

\newcommand{\Newt}[1]{\text{Newt}(#1)}
\newcommand{\conv}{\text{conv}}
\newcommand{\val}{\text{val}}
\newcommand{\rank}[1]{\text{rank} \ #1}

\newcommand{\MnX}{\overline{\mathcal{M}}_{g,n}(X,\beta)}
\newcommand{\MnXD}{\overline{\mathcal{M}}_{g,n}(X/D,\beta,\underline{\alpha})}
\newcommand{\Spec}{\text{Spec}}
\newcommand{\acts}{\curvearrowright}

\def\bibfont{\footnotesize}

\begin{document}

\title{Response to referee report: AG 608 (Version 1)}
%\author{}
\maketitle

We thank the referee for their careful examination of our paper, and for their many valuable suggestions which have helped greatly in improving the quality of the exposition. [TODO]

We have made many improvements to the paper which directly address the referee's comments. Following their suggestion, we have also gone through and made additional changes, in order to improve the readability and appeal to a wider audience. These are detailed below.

\subsection*{Response to specific comments}
\begin{enumerate}
\item[(25)] At the start of Section 5.1 we have added formulae to clarify the definition of the invariants.
\item[(26)] In Section 5.2 we define ``true tangency'' and ``true markings''; we have including more motivation for considering true and fictitious markings. In Section 5.3 we have added (following the table) a more detailed explanation of the recursion algorithm, which clarifies why all the base cases have degree zero. We have moreover discussed these cases in more depth (see Remark 5.4), clarifying the role played by ``tangency'' in this degenerate setting.
\item[(27)] We have clarified the meaning of $\alpha-e_1$. Here true markings can have $\alpha_1=1$, as long as all insertions are not pulled back along forgetting $x_1$; we have added a remark to this effect in Section 5.2. The term ``reduced relative'' is potentially confusing and has been removed.
\item[(28)] Throughout Section 5 we have replaced the ambiguous phrase ``is recursively known'' by the more precise ``has been computed earlier in the recursion'' or ``can be expressed as a polynomial in previously computed invariants''.
\item[(29)] Throughout Section 5 we have replaced this phrase with an explicit formula.
\item[(30)]
\item[(31)] We point out that this uses the same arguments as in Step~1. In the Step~1 arguments, we add explicit references to Gathmann's genus zero results and the necessary recursions on genus one Deligne--Mumford space.
\item[(32)] We have broken up Step 2 and Step 4 into smaller pieces. At several points we have made use of numbered lists for case analysis, which clarifies the logical structure. We have also provided summaries within steps as well as at the end of each step, to help the reader follow which parts of the formula the present arguments pertain to.
\end{enumerate}

\subsection*{Additional changes}
\begin{enumerate}
\item	
\end{enumerate}

\end{document}

### 2020-11-05 EllipticSingularitiesSplitting.tex
Some changes to Section 4

@@
 for a fixed basis $\{e_i\in L_i\}$ of $V$. We can then define $\theta_{ij}$ by
-\[\theta_{i,j}(e_i)=(a_j/a_i)\cdot e_j\]
+\[\theta_{ij}(e_i)=(a_j/a_i)\cdot e_j\]
 and it is easy to see that it does not depend on any of the choices. On the other hand, given the $\theta_{ij}$, the line $\ell$ can be taken to be the graph of the morphism:
@@
 For simplicity, we assume that the contact order is $(d)$, concentrated at a marking $x_1$ supported on the elliptic curve $E$ contracted to $H$.
-The combinatorial type looks as in Figure \ref{fig:comb111}.
+The combinatorial type is as in Figure \ref{fig:comb111}.
 
@@
   \foreach \x in {(0,2),(0,1),(0,-1)}
-  \draw \x --node[below]{\color{blue} $1$} (4,0);
-  \draw (0,0) node{$\vdots$};
-  \draw[->] (4,0) --node[above]{\color{blue} $d$} (6,0);
+  \draw \x --node[below,blue]{\SMALL$1$} (4,0);
+  \draw (1,0) node{$\vdots$};
+  \draw[->] (4,0) --node[below]{\color{blue} $d$} (6,0);
   \draw[blue,->] (0,-2)--(6,-2);
   \draw[fill=white] (4,0) circle (2pt);
-  \draw[fill=blue,blue] (4,-2) node[cross]{};
+  \draw[fill=blue,blue] (4,-2) node[blue]{$\times$};
   \draw [red] plot [smooth cycle] coordinates {(0,2) (0,1) (0,-1) (2,-1.5) (7,0) (2,2.5)};
@@
 \end{figure}
-
-Start from the moduli space of logarithmic maps. There is a finite splitting morphism:
-\[\Ecal \to \left(\M{0}{(1)}{\PP^m}{1}^{\times N}\times_{H^N}H\right)\times \Mcal^{\leftrightarrow}_{1,(-1,\ldots,-1,d)},\]
-where the latter is the moduli space of genus one curves satisfying the \emph{double ramification} condition.
-As for $\widetilde{\Dcal}$, the latter should be replaced by $\VZ^{\leftrightarrow}_{1,(-1,\ldots,-1,d)}$, see \S \ref{subsection rubber}.
-
-The left-hand factor can be described very concretely as the choice of a point $p$ of $H$, and $d$ lines through it.
-A very important observation is that, at least generically, the vertices lying on the circle of radius $\delta$ over $0\in\mathbb R_{\geq 0}$ are automatically aligned.
-Indeed, if $R_i$ denotes the $i$-th tail of the curve, glued to $E$ at the node $q_i$, then the stable maps provide us with identifications:
+Start with the moduli space of logarithmic stable maps. There is a finite splitting morphism:
+\[\Ecal \to \left(\M{0}{(1)}{\PP^m|H}{1}^{\times m}\times_{H^m}H\right)\times \overline{\Mcal}^{\leftrightarrow}_{1,(-1,\ldots,-1,d)}(\PP^1|0+\infty,d),\]
+where the latter is the moduli space of genus one rubber maps.
+To obtain $\widetilde{\Dcal}$ from $\Ecal$ we replace the final factor by $\VZ^{\leftrightarrow}_{1,(-1,\ldots,-1,d)}(\PP^1|0+\infty,d)$ (see \S \ref{subsection rubber}).
+
+The first  factor can be described very concretely as the choice of a point $p$ of $H$, and $d$ lines through it.
+A very important observation is that, at least generically, the vertices which lie on the circle of radius $\delta$ and map to $0\in\mathbb R_{\geq 0}$ are automatically aligned.
+Indeed, if $R_i$ denotes the $i$-th tail of the curve, glued to $E$ at the node $q_i$, then the stable map provides us with identifications:
 \[\operatorname{d}\! f_{i,q_i}\colon T_{R_i,q_i}\cong N_{H/\PP^m,p}\]
-that can be combined into the $\theta_{i,j}$ of \S \ref{S:ellsing}. So, without further ado, we may produce a contraction $C\to\overline C$ to an elliptic $d$-fold point.
-
-Assume for example that $d\leq N$.
-Then, for the absolute factorisation to hold, the $d$ lines $f_i(R_i)$ have better to span a $(d-1)$-dimensional subspace of $T_{\PP^m,p}$.
-The dimension of the moduli space $\widetilde\Dcal$ is then $dN+d-2$.
-Without loss of generality, we may assume that $H$ is the hyperplane $\{z_0=0\}$, $p$ is the point $[0:\ldots:0:1]$, and that the $d$ lines span the subspace $\{z_{d-1}=\ldots=z_{N-1}=0\}$.
-The sections $z_i,\ i=d-1,\ldots,N,$ vanish identically near $E$, so they descend automatically to the singularity.
-The section $z_0$ does so by the construction of $\overline C$.
-Finally, the sections $z_i,\ i=1,\ldots,d-2,$ impose independent conditions to descend to $\overline C$.
-All in all, we find that $\Dcal$ has dimension $dN$, making it into a divisor in $\VZ_{1,(d)}(\PP^m|H,d)$.
-
-We can express the factorisation condition tautologically by combining the isomorphisms $\theta_{i,j}$ above, and the differential of $f$.
-It correponds to the vanishing of the following vector bundle map:
-\[T_{R_1,q_1}\xrightarrow{(1,\theta_{1,2}\ldots,\theta_{1,d})}\bigoplus_{i=1}^d T_{R_i,q_i}\xrightarrow{\sum\circ\operatorname{d}\!f=\operatorname{d}\!z_1+\ldots\operatorname{d}\!z_{d-2}}N_{H\cap\PP^{d-1}/\PP^{d-1},p}.\]
-
-In general, we shall see that the automatic alignment only involves the components corresponding to vertices on the circle that lie over $0$.
-The internal components on the circle must be aligned by hand.
-This means that $\widetilde\Dcal$ is a compactified torus bundle over $\Ecal$, see \ref{S:ellsing}.
-On the other hand, for higher contact order, the vector bundle map $\sum\circ\operatorname{d}\!f$ to $T_{\PP^m,p}$ factors naturally through $T_{H,p}$.
+which we may compose to obtain attaching data $\theta_{ij}$  (see \S \ref{S:ellsing}).
+This produces a contraction $C\to\overline C$ to an elliptic $d$-fold point.
+The dimension of $\widetilde\Dcal$ coincides with the dimension of $\Ecal$, which is $dm + m - 1$.
+
+Assume for simplicity that $d\leq m$.
+For the absolute factorisation to hold, the $d$ lines $f_i(R_i)$ must span a subspace of $T_{\PP^m,p}$ of dimension at most $d-1$.
+The locus of maps satisfying this condition has dimension:
+\begin{equation*} (dm+m-1) - (m-d+1) = dm + d -2.\end{equation*}
+Without loss of generality, we may assume that $H=\{z_0=0\}$, $p=[0,\ldots,0,1]$, and that the $d$ lines span the subspace $\{z_{d-1}=\ldots=z_{m-1}=0\}$.
+The sections $z_i$ for $i=d-1,\ldots,m$ vanish identically near $E$, so descend automatically to the singularity.
+On the other hand the section $z_0$ descends to the singularity by the construction of $\overline C$.
+Finally, the sections $z_i$ for $i=1,\ldots,d-2$ impose independent conditions to descend to $\overline C$.
+Imposing these conditions, we find that $\Dcal$ has dimension
+\begin{equation*} (dm+d-2)-(d-2) = dm \end{equation*}
+making it into a divisor in $\VZ_{1,(d)}(\PP^m|H,d)$.\sidenote{What about d>m?}
+
+We can express the factorisation condition tautologically by combining the isomorphisms $\theta_{ij}$ above with the differential of $f$.
+We see that factorisation amounts to the vanishing of the following vector bundle map:
+\[T_{R_1,q_1}\xrightarrow{(1,\theta_{12}\ldots,\theta_{1d})}\bigoplus_{i=1}^d T_{R_i,q_i}\xrightarrow{\sum\circ\operatorname{d}\!f=\operatorname{d}\!z_1+\ldots\operatorname{d}\!z_{d-2}} {N_{H\cap\PP^{d-1}|\PP^{d-1}}}|_p.\]
+For strata with higher tangency, we will see that the automatic alignment only occurs for vertices on the circle which map to $0\in\RR_{\geq 0}$.
+For internal components which lie on the circle, the alignment must be imposed separately.
+This means that $\widetilde\Dcal$ is a compactified torus bundle over $\Ecal$ (see \S\ref{S:ellsing}).
+On the other hand, for higher contact order,s the vector bundle map $\Sigma\circ\operatorname{d}\!f$ to $T_{\PP^m,p}$ factors naturally through $T_{H,p}$.
+This is discussed in detail in \S\S \ref{subsection D from Dtilde} and \ref{section D from Dtilde second}.
 
@@
 The dimension of this cone could be large (see again the left-hand side of Figure \ref{fig:off_we_go}) -- its dimension is equal to the number of levels of the target expansion in the type $\Delta$.
-The cone $\sigma$ determines a stratum $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^m|H,d)$, and the morphism above restricts to
+The cone $\sigma$ determines a stratum $\Ecal \subseteq \ol\Mcal_{1,\alpha}(\PP^m|H,d)$, and the morphism above restricts to a morphism
 \[
@@
 Each vertex $v$ has associated discrete data $\Gamma_v$ (genus, degree, contact order).
-The vertices over $0$ determine moduli spaces of ordinary relative stable maps, while the higher level vertices determine maps to rubber.
-Then $\Ecal$ admits a finite splitting morphism
+The vertices over $0$ determine moduli spaces of relative stable maps, while the higher level vertices determine maps to rubber.
+The stratum $\Ecal$ admits a finite splitting morphism
 \begin{equation}\label{IIIa fibre product} \Ecal \xrightarrow{\rho} \left( \prod_{v \in \Lambda_0} \ol\Mcal_{\Gamma_v}(\PP^m|H) \times \prod_{v \in \Lambda_{>0}} \ol\Mcal^{\leftrightarrow}_{\Gamma_v}(\mathbb{P}|H_0+H_\infty) \right) \times_{H^{2\epsilon}} H^{\epsilon} \end{equation}
@@
 
-Equipped with the strata logarithmic structures, the morphism
+Equipped with the strata logarithmic structures, there is a logarithmic morphism
 \[
@@
 \]
-is a logarithmic morphism. The generic fibre of this morphism is a toric variety.  \medskip
+whose generic fibre is a toric variety.  \medskip
 
@@
   \draw[fill=black] (0,-1) circle (2 pt);
-  \draw[->] (1,1)--node[below,blue]{$m_1$} (2,0) (0,-1)--node[below,blue]{$m_1$} (2,0) (2,0)--node[below,blue]{$m_1+m_2$} (4,0);
+  \draw[->] (1,1)--node[below,blue]{$m_1$} (2,0) (0,-1)--node[below,blue]{$m_2$} (2,0) (2,0)--node[below,blue]{$m_1+m_2$} (4,0);
   \draw (1,-.5) node[cross]{};
@@
 
-  \draw[fill=black] (0,-2) circle (2 pt);
-  \draw[->] (0,-2)--node[below=.5cm]{$\Delta_\tau$} (4,-2);
-   \draw (1,-2) node[cross]{};
-   \draw (2,-2) node[cross]{};
+  \draw[fill=blue] (0,-2) circle (2 pt);
+  \draw[blue,->] (0,-2)--node[below=.5cm]{$\Delta_\tau$} (4,-2);
+   \draw[blue] (1,-2) node[blue]{$\times$};
+   \draw[blue] (2,-2) node[blue]{$\times$};
 
@@
  %subdivision 
-  \draw[->] (6,-2) --node[below=.5cm]{$\sigma$} (10,-2) node[right]{$\ell_1$};
-  \draw[->] (6,-2) -- (6,2) node[above]{$\ell_2$};
+  \draw[->] (6,-2) --node[below=.5cm]{$\sigma$} (10,-2) node[right]{$e_1$};
+  \draw[->] (6,-2) -- (6,2) node[above]{$e_2$};
   \draw[gray] (6,-2) -- (10,1) node[right]{$(m_2,m_1)=\operatorname{Im}(\tau)$};
@@
 \[
-\widetilde{\Dcal}^{\operatorname{trop}} \to \Ecal^{\operatorname{trop}}.
+\tau=\widetilde{\Dcal}^{\operatorname{trop}} \to \Ecal^{\operatorname{trop}}=\sigma.
 \]
-The tropical curves on the left inherit a central alignment from $\widetilde{\VZ}_{1,\alpha}(\PP^m|H,d)$, which orders a certain subset of the edge lengths.
+The tropical curves parametrised on the left inherit a central alignment from $\widetilde{\VZ}_{1,\alpha}(\PP^m|H,d)$, which orders a certain subset of the edge lengths.
 The polyhedral criterion for equidimensionality is that every cone of the source maps surjectively onto a cone of the target.
@@
 
-The moduli space of radially aligned curves of genus one $\VZ_{1,n}^\text{rad}$ coincides with the Vakil-Zinger blow-up of  $\overline \Mcal_{1,n}$ \cite[\S 2.3]{VZ}.
-In particular, up to twisting by exceptional divisors, the tangent line bundles at two marking $\widetilde{\mathbb T}_i$ and $\widetilde{\mathbb T}_j$ are identified (via the dual Hodge bundle $\mathbb E^\vee$), extending the identification on the smooth locus provided by regarding the elliptic curve as an algebraic group.
-The pullback of this to $\VZ^\leftrightarrow_{\Gamma_{\sqsubset_0}}$ is what we mean by  the universal tangent line bundle $\mathbb T$.
-
+Here we explain the meaning of $\mathbb{T}$. Isolating the subcurve $C_0 \subseteq C$ gives rise to a morphism from $\widetilde\Dcal$ to the moduli space of radially aligned curves of genus one:
+\begin{equation*} \widetilde\Dcal \to \VZ^{\text{rad}}_{1,n}.\end{equation*}
+The latter space coincides with the Vakil--Zinger blow-up of $\overline \Mcal_{1,n}$ \cite[\S 2.3]{VZ}.
+In particular, after twisting by exceptional divisors, the tangent line bundles at two marking $\widetilde{\mathbb T}_i$ and $\widetilde{\mathbb T}_j$ are identified (via the dual Hodge bundle $\mathbb E^\vee$), extending the identification on the smooth locus provided by regarding the elliptic curve as an algebraic group.
+This gives rise to a single line bundle -- the ``universal tangent line bundle'' -- on $\VZ^{\text{rad}}_{1,n}$; we let $\mathbb{T}$ denote its pullback to $\widetilde\Dcal$.
 \begin{proof}
@@
 %This identification amounts to a specific linear dependence relation between the tangent vectors, which gives a point in the moduli space of attaching data for the corresponding elliptic singularity \cite[\S 2.2]{SMY2}.
-After Corollary \ref{cor:maps_from_elliptic_sing}, we can therefore express the factorisation condition in terms of degeneracy of the following natural morphism of vector bundles on $\widetilde\Dcal$:
+After Corollary \ref{cor:maps_from_elliptic_sing}, we can therefore express the factorisation condition as the degeneracy of the following natural morphism of vector bundles on $\widetilde\Dcal$:
 \begin{equation*} \Sigma \operatorname{d}\!f \colon \OO(\delta)\otimes \mathbb T^\vee \to \ev_q^\st T H. \end{equation*}
 Here $\Sigma \operatorname{d}\!f$ is defined by summing the images of the tangent vectors at the inward-pointing nodes on the circle, using the natural identification of each of these tangent spaces with $\OO(\delta)\otimes \mathbb T^\vee$ established above.
-Apart from the case dealt with in \S \ref{S:lines}, the composite:
-\[\operatorname{pr}\circ\Sigma \operatorname{d}\!f \colon \OO(\delta)\otimes \mathbb T^\vee \to \ev_q^\st T \PP^m\to \ev_q^* N_{H/\PP^m}\]
- vanishes, because the contact order of the exterior components with $H$ is strictly higher than $1$. So, $\Sigma \operatorname{d}\!f$ takes values in $TH$, rather than $T\PP^m$.
-
+This morphism takes values in $\ev_q^\star TH$ rather than $\ev_q^\star T\PP^m$ because the contact order of the exterior components with $H$ is strictly larger than $1$ (except for the case of lines, dealt with separately in \S \ref{S:lines}).
 This gives a section of the vector bundle
@@
 which is transverse and whose vanishing locus coincides with $\Dcal$.
-Transversality follows from the construction, because any stratum of the boundary on which $\Sigma \operatorname{d}\!f$ may have vanished has been (blown up and) included into $\mathbb T \otimes \OO(-\delta)$ as a twist.
-In other words, the circle of radius $\delta$ always passes through at least one component which is not contracted by the map to the expansion.
+Transversality follows by construction, because any stratum of the boundary on which $\Sigma \operatorname{d}\!f$ vanishes has been (blown up and) included into $\mathbb T \otimes \OO(-\delta)$ as a twist; in other words, the circle of radius $\delta$ always passes through at least one component which is not contracted by the map to the expansion.
 Now, if the vanishing locus of $\Sigma \operatorname{d}\!f$ does not contain any stratum of the boundary, then it is the closure of its intersection with the open stratum, which can be seen to be transverse.
@@
 
-\subsubsection{$\Dcal$ from $\widetilde\Dcal$: second way} %To establish a more direct connection with the geometry of the fibre product \eqref{IIIa fibre product}, recall that $\widetilde\Ecal$ is built as an explicit modification of a finite cover of \eqref{IIIa fibre product}.
+\subsubsection{$\Dcal$ from $\widetilde\Dcal$: second way} \label{section D from Dtilde second} %To establish a more direct connection with the geometry of the fibre product \eqref{IIIa fibre product}, recall that $\widetilde\Ecal$ is built as an explicit modification of a finite cover of \eqref{IIIa fibre product}.
 For $i \in\{1,\ldots,r\}$ (with the convention established at the end of Lemma \ref{lem:generic_proj_bundle}), it makes sense on $\widetilde\Ecal$ to consider the line bundle $\OO(\delta_i)$ associated to a shortest path from the core to the circle in the $\sqC_i$-direction.
@@
 \subsection{Reduced absolute, relative and rubber invariants} To be precise: by a reduced invariant of $Y$ we mean an integral over $\VZ_{1,n}(Y,\beta)$ of a product of evaluation classes and pullbacks of psi classes along morphisms forgetting subsets of the marked points:
-\begin{equation*} \int_{[\VZ_{1,n}(Y,\, \beta)]} \prod_{i=1}^n \fgt_{S_i}^\star \psi_i^{k_i} \cdot \ev_i^\star \gamma_i.\end{equation*}
+\begin{equation*} \int_{\virt{[\VZ_{1,n}(Y,\, \beta)]}} \prod_{i=1}^n \fgt_{S_i}^\star \psi_i^{k_i} \cdot \ev_i^\star \gamma_i.\end{equation*}
 (Here $S_i \subseteq \{1,\ldots,n\}$ with $i \not\in S_i$ for all $i$; taking $S=\emptyset$ gives the ordinary  psi classes.).
@@
 Reduced relative invariants of $(X,Y)$ are defined in the same way
-\begin{equation*} \int_{[\VZ_{1,\alpha}(X|Y,\, \beta)]} \prod_{i=1}^n \fgt_{S_i}^\star \psi_i^{k_i} \cdot \ev_i^\star \gamma_i\end{equation*}
+\begin{equation*} \int_{\virt{[\VZ_{1,\alpha}(X|Y,\, \beta)]}} \prod_{i=1}^n \fgt_{S_i}^\star \psi_i^{k_i} \cdot \ev_i^\star \gamma_i\end{equation*}
 except now the forgetful morphism maps into a space of absolute stable maps:

### 2020-11-09 Response to referee/AG Genus One Response to Referee.tex
Some changes to Section 4
Finished Navid changes

@@
 
-We thank the referee for their careful examination of our paper, and for their many valuable suggestions which have helped greatly in improving the quality of the exposition. [TODO]
+\noindent We thank the referee for their careful reading of our paper, and their many valuable suggestions which have greatly helped in improving the quality of the exposition.
 
@@
 Following their suggestion, we have also gone through and made additional changes, in order to improve the readability and appeal to a wider audience.
-These are detailed below.
+Major such changes include:
+\begin{enumerate}
+	\item An improved introduction (see \S\S 1.1--1.5), explicating the connection between logarithmic structures and moduli of Gorenstein singularities which is a key geometric ingredient in the paper.
+	\item More details in the proof of Theorem 1.9 (logarithmic smoothness of the moduli space), including a careful analysis of the various relative deformation/obstruction theories. 
+\end{enumerate}
 
@@
 
-\subsection*{Additional changes}
+\subsection*{Additional minor changes}
 \begin{enumerate}
-\item	
+\item The term ``special rubber'' used at the start of Step 2 is an anachronism from a draft version of the paper, and has been removed.
 \end{enumerate}

### 2020-11-09 EllipticSingularitiesSplitting.tex
Finished Navid changes

@@
 A key step in our recursion is a description of the locus of maps with higher than prescribed tangency, which was identified by Gathmann.
-We realise the locus as the vanishing locus of a section of a line bundle that comes from tropical geometry — from a piecewise linear function on the fan.
-The systematic understanding of logarithmic line bundles arising in this fashion is likely to play an important role in logarithmic enumerative geometry.
+We realise the locus as the vanishing locus of a section of a line bundle that comes from tropical geometry — from a piecewise linear function on the fan/tropicalization.
+The systematic understanding of logarithmic line bundles arising in this fashion is expected to play an important role in logarithmic enumerative geometry.
 
@@
 Even in genus one, an understanding of the main component contributions of the double ramification cycle for target manifolds seems to be lacking.
-Our main algorithm subverts the use of this class, but it would be more natural to use it.
+Our main algorithm provides a method for calculating integrals over this class, but it would be more natural to have a formula for it.
 
@@
 where $\overline{\mathcal C}_S$ may contain a Gorenstein elliptic singularity \cite{SMY1}.
-Given a family of tropical curves, the function $\delta$ provides a non-negative real number for each point on the base.
+Intuitively, this is achieved by interpreting the exceptional directions of $\mathfrak M_{1,n}^{\mathrm{cen}}\to\mathfrak M_{1,n}$ as moduli of attaching data.
+
+Formally, given a family of tropical curves, the function $\delta$ provides a non-negative real number for each point on the base.
 We may therefore consider the ``\textbf{circle}'' of points on each fibre whose distance from the core is equal to $\delta$.
@@
 A very important observation is that, at least generically, the vertices which lie on the circle of radius $\delta$ and map to $0\in\mathbb R_{\geq 0}$ are automatically aligned.
-Indeed, if $R_i$ denotes the $i$-th tail of the curve, glued to $E$ at the node $q_i$, then the stable map provides us with identifications:
+Indeed, if $R_i$ denotes the $i$th tail of the curve, glued to $E$ at the node $q_i$, then the stable map provides us with identifications:
 \[\operatorname{d}\! f_{i,q_i}\colon T_{R_i,q_i}\cong N_{H/\PP^m,p}\]
@@
 
-Assume for simplicity that $d\leq m$.
-For the absolute factorisation to hold, the $d$ lines $f_i(R_i)$ must span a subspace of $T_{\PP^m,p}$ of dimension at most $d-1$.
+Assume first that $d\leq m$.
+For the absolute factorisation to hold, it is necessary (but not sufficient) for the $d$ lines $f_i(R_i)$ to span a subspace of $T_{\PP^m,p}$ of dimension at most $d-1$.
 The locus of maps satisfying this condition has dimension:
@@
 \begin{equation*} (dm+d-2)-(d-2) = dm \end{equation*}
-making it into a divisor in $\VZ_{1,(d)}(\PP^m|H,d)$.\sidenote{What about d>m?}
+making it into a divisor in $\VZ_{1,(d)}(\PP^m|H,d)$.
+The case $d>m$ is similar, except that the lines $f_i(R_i)$ are automatically linearly dependent and so this condition does not need to be imposed.
 
@@
 \begin{lemma}\label{lem:generic_proj_bundle}
-Generically over $\Ecal$, the morphism $\widetilde \Dcal\to\Ecal$ is the projectivisation of a tautological vector bundle.
+Generically over $\widetilde\Ecal$, the morphism $\widetilde \Dcal\to\widetilde\Ecal$ is the projectivisation of a tautological vector bundle.
 \end{lemma}
@@
 Since not all of them can be strictly positive, the resulting fan is that of a projective space.
-This gives us a fibrewise description of $\widetilde\Dcal\to\Ecal$ over the generic point.
-
-A slight modification of the argument above is required to account for the fact that all vertices that lie on the circle and are mapped to $0\in\mathbb R_{\geq0}$ by the tropical map are generically aligned on $\Ecal$.
+This gives us a fibrewise description of $\widetilde\Dcal\to\widetilde\Ecal$ over the generic point.
+
+A slight modification of the argument above is required to account for the fact that all vertices that lie on the circle and are mapped to $0\in\mathbb R_{\geq0}$ by the tropical map are already generically aligned on $\widetilde\Ecal$.
 Indeed, by the combinatorial description of rays in \S \ref{S:combinatorialdescription}, there are no stable vertices inside the circle, so all the edges going from a vertex of $\Lambda_0$ to the core have the same expansion factor $m$ (maximal among the contact orders at the core).
-Therefore, for all $i$ such that $\plC_i\in\Lambda_0$, the $T_{q_i}C_i^{\otimes m}$ can be identified to the target tangent line on the fibre product \eqref{IIIa fibre product}, and, after saturation, the $T_{q_i}C_i$ themselves are canonically isomorphic on $\Ecal$.
+Therefore, for all $i$ such that $\plC_i\in\Lambda_0$, the $T_{q_i}C_i^{\otimes m}$ can be identified to the target tangent line on the fibre product \eqref{IIIa fibre product}, and, after saturation, the $T_{q_i}C_i$ themselves are canonically isomorphic on $\widetilde\Ecal$.
 Thus, only one summand should be taken to represent all of them in the projective bundle \eqref{eqn:projectivebundle}.
@@
 \begin{example}
-Consider the locus $\Ecal$ given by $\sigma$ below, and the codimension one locus $\widetilde\Dcal_\rho \subseteq \widetilde\Dcal_\sigma$ given by the two-dimensional (due to the alignment) cone $\rho$:
+Consider the locus $\Ecal$ given by $\sigma$ below, and the codimension-one locus $\widetilde\Dcal_\rho \subseteq \widetilde\Dcal_\sigma$ given by the two-dimensional (due to the alignment) cone $\rho$:
 \begin{figure}[!htbp]
@@
 \begin{figure}[hbt]
-\begin{tikzpicture}[ipe import]
+\begin{tikzpicture}[ipe import,scale=1.5]
   %\useasboundingbox (0, 0) rectangle (595, 842);
@@
 The dotted circle is the one we draw on $\mathcal P$.
-The continuous circle represents $\delta$ enlarging the dotted one (a stratum of $\widetilde\Dcal$).}\label{fig:principalisation}
+The solid circle represents a radius $\delta$ enlarging the dotted one (a stratum of $\widetilde\Dcal$).}\label{fig:principalisation}
 \end{figure}

### 2020-11-10 Response to referee/AG Genus One Response to Referee.tex
completed response to referee

@@
 \DeclareMathOperator{\pt}{pt}
+
+\DeclareRobustCommand{\plE}{\text{\reflectbox{$\exists$}}}
+\newcommand{\plC}{\scalebox{0.8}[1.3]{$\sqsubset$}}
+\newcommand{\sidenote}[1]{\marginpar{\textbf{\color{red}#1}}}
+\newcommand{\lcm}{\operatorname{lcm}}
 
@@
 	\item More details in the proof of Theorem 1.9 (logarithmic smoothness of the moduli space), including a careful analysis of the various relative deformation/obstruction theories.
+	\item The arguments of \S 4.3 have been expanded and streamlined.
 \end{enumerate}
@@
 \begin{enumerate}
+\item[(1)] The statement of Theorem A now refers explicitly to logarithmic maps not contracting the minimal genus one subcurve.
+\item[(2)] Theorem B: We have clarified that the relative genus one invariants are not required as an input.
+\item[(3)] \S 1.5 now contains the relevant definitions. We hope that Figure 1 will help the reader as well.
+\item[(4)] When the minimal genus one subcurve of $C$ is not contracted, the map is automatically included in the stack $\mathcal{V\!Z}$, with no need for any Gorenstein contraction $\overline{C}$.
+\item[(5)] We have phrased the definition (now 1.8) more carefully: there are two maps from curves with Gorenstein singularities, $\overline C_F\to\PP^m[s]$ to the expansion, and $\overline C_B\to\PP^m$ to the collapsed target, and both are required not to contract the minimal genus one subcurve.
+\item[(6)] The case of degree $1$ is discussed in Remark 1.7. The proof of the theorem has been rewritten.
+\item[(7)] The minimal genus one subcurve is now denoted by $\plE$.
+Since an open neighbourhood of $\plE$ is contracted, but the flags $t_1,\ldots,t_k$ are not, they cannot be supported on $\plE$.
+Instead, they are supported on $F^{-1}F(\plE)$; they are, so to say, the first bits of the curve that move off from $F^{-1}F(\plE)$.
+Hopefully Figure 2 will clarify the mysterious condition.
+\item[(8)] The core is now defined at the beginning of \S 1.5 (it is the minimal subcurve of genus one). The core is the centre of the circle of radius $\delta$.
+\item[(9)] An internal component is one that is entirely mapped into $H$. See Definition 3.1.
+\item[(10)] Primary insertions.
+\item[(11)] White circles represent components of genus one, black circles rational components. We now say it in the statement of Lemma 4.3.
+\item[(12)] Lemma 4.10 has been split into two.
+Moreover, a section called ``Lines'' (including Fig.
+6) has been added, addressing the combinatorial type of a comb with degree $1$ teeth.
+This case is both peculiar (because it is not true that the tangent lines of the tails at the nodes are mapped to $0$ in $N_{H/\PP^m}$ by $\operatorname{d}\!f$) and simpler (because, generically, the tails are automatically aligned), so we thought it worth of mention in order to familiarise the reader with the line of argument of the rest of section \S 4.
+\item[(13)] We point to Figure 8 for such an example.
+\item[(14)] We clarified the distinction between the substratum log structure and the intrinsic one.
+\item[(15)] Figure 7 exhibits the simplest modular example.
+\item[(16)] Moduli of attachments are described in \S 1.4, which is a reinterpretation of work of D.
+Smyth.
+He already described a compactification of them, which is isomorphic to projective space, and whose boundary strata parametrise ``sprouted'' curves: in our language this corresponds to the partial destabilisation $\widetilde C$.
+Figure 8 explains tropically how to see the fan of projective space (fibrewise).
+\item[(17)] At the beginning of Section 4.3.5 we remind the reader of the correspondence between piecewise-linear functions on the tropicalization and line bundles on the space.
+\item[(18)] We point out how other nodes are irrelevant.
+\item[(19)] By construction, the vanishing locus is the closure of its open part (since all the intersections with boundary strata have been blown up and put in the vector bundle as a twist).
+Transversality follows.
+\item[(20)] We do not make an indexing set explicit; on the other hand, it can be deduced from the combinatorics of the tropicalization.
+\item[(21)] We have made the various identifications more explicit.
+\item[(22)] $\mathcal P$ can be thought of as a moduli space of partial alignments (among the tails specified along the circle, notwithstanding their possible degenerations), or a stratum of a logarithmic blowup of the moduli space.
+$\widetilde D$ is nothing but a further blowup of this.
+\item[(23)] We meant the factors in the product (3), which are themselves moduli spaces of maps (relative, genus zero; or rubber, genus one).
+\item[(24)] We left the final statement as vague as it was, but we put some effort in clarifying it through the discussion of Proposition 4.21 and Corollary 4.22.
 \item[(25)] At the start of Section 5.1 we have added formulae to clarify the definition of the invariants.

### 2020-11-10 EllipticSingularitiesSplitting.tex
completed response to referee

@@
 \begin{proof}
+\begin{comment}
 We examine the geometry of the space of maps to $(\PP^m|H)$ by utilising the forgetful morphism
@@
 The absolute obstructions, which are the cokernel of this map therefore vanish, and the result follows.
+\end{comment}
 %Consider an $S$-family of expanded maps $[F: C\to \mathbb P^m[s]$.
@@
 Second, the target degeneration is now a toric degeneration, and the logarithmic tangent bundle is trivial.
-\textcolor{red}{luca's rewrite of log smoothness}
+%\textcolor{red}{luca's rewrite of log smoothness}
 
@@
 This means that $\widetilde\Dcal$ is a compactified torus bundle over $\Ecal$ (see \S\ref{S:ellsing}).
-On the other hand, for higher contact order,s the vector bundle map $\Sigma\circ\operatorname{d}\!f$ to $T_{\PP^m,p}$ factors naturally through $T_{H,p}$.
+On the other hand, for higher contact orders, the vector bundle map $\Sigma\circ\operatorname{d}\!f$ to $T_{\PP^m,p}$ factors naturally through $T_{H,p}$.
 This is discussed in detail in \S\S \ref{subsection D from Dtilde} and \ref{section D from Dtilde second}.

### 2020-11-20 Response to referee/AG Genus One Response to Referee.tex
Added Dhruv changes

@@
 
-We have made many improvements to the paper which directly address the referee's comments.
+We have made many improvements to the paper which directly address the referee's comments, without exceptions.
 Following their suggestion, we have also gone through and made additional changes, in order to improve the readability and appeal to a wider audience.
+While adding more exposition, we have strived to cut down on unnecessary words and phrases and streamline the language, so the length of the paper has not changed substantially.
 Major such changes include:
@@
 	\item An improved introduction (see \S\S 1.1--1.5), explicating the connection between logarithmic structures and moduli of Gorenstein singularities which is a key geometric ingredient in the paper.
-	\item More details in the proof of Theorem 1.9 (logarithmic smoothness of the moduli space), including a careful analysis of the various relative deformation/obstruction theories.
+In particular, this includes working definitions of the background material.
+	\item The introduction has also been streamlined to better reflect the growing body of work on the connections between curve singularities, logarithmic structures and stable maps.
+	\item The argument proving Theorem 1.9 has been reworked to have a clearer logical structure, with additional details. 
 	\item The arguments of \S 4.3 have been expanded and streamlined.
@@
 This case is both peculiar (because it is not true that the tangent lines of the tails at the nodes are mapped to $0$ in $N_{H/\PP^m}$ by $\operatorname{d}\!f$) and simpler (because, generically, the tails are automatically aligned), so we thought it worth of mention in order to familiarise the reader with the line of argument of the rest of section \S 4.
-\item[(13)] We point to Figure 8 for such an example.
+\item[(13)] We point to Figure 8 and explain why it records an example of this behaviour.
 \item[(14)] We clarified the distinction between the substratum log structure and the intrinsic one.
@@
 \item[(29)] Throughout Section 5 we have replaced this phrase with an explicit formula.
-\item[(30)]
+\item[(30)] A remark has been added with reminders elsewhere in the text.
 \item[(31)] We point out that this uses the same arguments as in Step~1.

### 2020-11-20 EllipticSingularitiesSplitting.tex
Added Dhruv changes

@@
 
-\noindent The Kontsevich moduli space of stable maps from genus zero curves to projective space exhibits remarkable geometry -- it is a smooth orbifold with a ``self-similar'' normal crossings boundary.
-These facts have combined to produce a very {satisfactory} understanding of Gromov--Witten theory in genus zero.
-
-The higher genus situation is much more delicate, and substantial theory has been developed in recent years to treat the genus one case, both for its intrinsic geometry, and for higher genus insights.
+\noindent The Kontsevich space of stable maps from genus zero curves to projective space exhibits remarkable geometry -- it is a smooth orbifold with a ``self-similar'' normal crossings boundary.
+A combination of these facts yields a very satisfactory understanding of Gromov--Witten theory in genus zero.
+
+The higher genus situation is more delicate, and substantial theory has been developed in recent years to treat the genus one case, both for its intrinsic geometry, and for higher genus insights.
 This began over a decade ago with pioneering work of Li, Vakil, and Zinger~\cite{redgone,VZ,LZ,lz2,zingerstvsred,zingred}, and was recently reinvigorated using ideas from singularity theory~\cite{BCM18,HL,SMY1,VISC} and logarithmic geometry~\cite{RSPW,RSPW2,BC20}.
 The result is a \textbf{reduced} Gromov--Witten theory, which removes degenerate contributions from the ordinary theory.
-While the Atiyah--Bott localisation for the reduced invariants was used to great effect by Zinger in his proof of the BCOV conjectures, two major components of the subject -- relative invariants and the degeneration formula -- have not been developed in this setting.
+Fundamental ingredients in Gromov--Witten theory are torus localisation, relative stable maps, and degeneration formulas.
+While the Atiyah--Bott localisation for the reduced invariants was used to great effect by Zinger in his proof of the BCOV conjectures, the remaining components -- relative invariants and the degeneration formula -- have not been developed in this setting.
 Our work provides these as new {structural} tools in reduced genus one Gromov--Witten theory\footnote{Further motivation to consider the genus one case specifically comes simply from the fact that for Calabi--Yau geometries in dimension larger than $3$, Gromov--Witten theory vanishes in genera greater than one.}.
-While the essential starting point is the early work on relative Gromov--Witten theory by Gathmann, modern tools are required in our setting.
-We establish both the conceptual framework and the formula by combining tropical geometry and logarithmic Gromov--Witten theory, as developed by Abramovich--Chen--Gross--Siebert, with the recent understanding of elliptic singularities and their interactions with logarithmic structures.
-
-\subsection{Results} Our first contribution is the construction of a \textbf{reduced relative} Gromov--Witten theory associated to elliptic curves in $\mathbb P^m$ with prescribed tangency along a hyperplane, and analogous invariants associated to smooth pairs $(X,Y)$ with $Y$ very ample.
-Our reduced relative theory differs from relative Gromov--Witten theory in a parallel fashion to how Li--Zinger's reduced Gromov--Witten theory differs from the standard theory.
-
-The geometric content is the following theorem, which provides a smooth and proper moduli space compactifying the space of elliptic curves in projective space with prescribed contact order data.
+
+The essential starting point for our relative theory is the early work on relative Gromov--Witten theory by Gathmann.
+However, modern tools are required in our setting.
+The conceptual framework and the degeneration formalism itself are obtained by combining tropical geometry and logarithmic Gromov--Witten theory, as developed by Abramovich--Chen--Gross--Siebert, with the recent understanding of elliptic singularities and their interactions with logarithmic structures.
+The latter sections of this paper are devoted to demonstrating that the new ingredients can be combined in a concrete fashion, using tautological vector bundles and their Chern classes.
+
+\subsection{Results} Our main construction yields a \textbf{reduced relative} Gromov--Witten theory for elliptic curves in $\mathbb P^m$ with prescribed tangency along a hyperplane, and analogous invariants for smooth hyperplane section pairs $(X,Y)$.
+The reduced relative theory differs from the relative theory in a parallel fashion to how Li--Zinger's reduced Gromov--Witten theory differs from the standard one.
+
+The geometric content is the following theorem, which provides a smooth and proper moduli space compactifying the space of elliptic curves in $\mathbb P^m$ with prescribed contact order data.
 Let $\mathcal M_{1,\alpha}^\circ(\mathbb P^m|H,d)$ be the moduli space of positive degree maps from smooth curves of genus one to $\mathbb P^m$ with dimensionally transverse contact order $\alpha\in\mathbb Z^n_{\geq 0}$ along $H$.
-A precise version of the following theorem requires a certain amount of tropical and logarithmic language, and is therefore stated precisely in \S \ref{section construction}.
+A precise version of the following theorem requires tropical and logarithmic language, and is therefore stated precisely in \S \ref{section construction}.
 
 \begin{customthm}{A}\label{thm: desingularization}
-There exists a logarithmically smooth and proper Deligne--Mumford stack $\VZ_{1,\alpha}(\mathbb P^m|H,d)$ having expected dimension, and containing $\mathcal M_{1,\alpha}^\circ(\mathbb P^m|H,d)$  as a dense open subset.
-A point in this moduli space determines commutative diagrams
+There exists a proper Deligne--Mumford stack $\VZ_{1,\alpha}(\mathbb P^m|H,d)$ that is logarithmically smooth of expected dimension, and contains $\mathcal M_{1,\alpha}^\circ(\mathbb P^m|H,d)$  as a dense open subset.
+A point in this moduli space determines commutative diagrams of maps out of genus one curves:
 \[
@@
 \]
-where $C$ is a nodal genus one curve, $\overline C_1$ and $\overline C_2$ are Gorenstein curves of genus one, the map $C\to \PP^m[s]$ is a logarithmic map to an $s$-fold expansion of $\PP^m$ along $H$, and each of the vertical maps does not contract the minimal subcurve of genus one.
+where $C$ is nodal, $\overline C_1$ and $\overline C_2$ are Gorenstein, $C\to \PP^m[s]$ is a logarithmic map to an $s$-fold expansion of $\PP^m$ along $H$, and the vertical maps do not contract any subcurve of genus one.
 \end{customthm}
@@
 
-This reconstruction result generalies that of Gathmann~\cite{Ga}.
-A higher genus reconstruction result for the ordinary theory is proved by Maulik and Pandharipande~\cite{MaulikPandharipande}, but follows a fundamentally different strategy to ours.
-In particular, localisation is never used in the analysis here, nor in the work of Gathmann.
-
-We pursue a strategy laid out by Vakil, building on work of Caporaso and Harris~\cite{CH98,Vre}.
-The first step is to express the locus of maps where the contact order degenerates in terms of Chern classes of tautological vector bundles.
-The second step is to describe that locus in terms of fibre products of moduli spaces with smaller invariants.
-
+A conceptual consequence is that the absolute and relative reduced genus one theories, together with the genus zero theory, form a \textit{self-contained} system of invariants, i.e.
+the non-reduced relative theory is not required to perform a degeneration computation in the reduced theory.
+%The second is that the theorems together give a Gromov--Witten theoretic perspective on the ``main component'' calculations performed in the PhD thesis of Vakil~\cite{Vre}.
+The first theorem generalises the definition of the invariants in loc.
+cit.
+while the second generalises the calculation scheme itself.
+
+The reconstruction algorithm generalises that of Gathmann~\cite{Ga}.
+A higher genus reconstruction for the ordinary theory is given by Maulik and Pandharipande~\cite{MaulikPandharipande}, but follows a different strategy; localisation is never used in the analysis here, nor in that of Gathmann.
+
+We pursue a strategy laid out by Vakil and Caporaso--Harris~\cite{CH98,Vre}.
+We express the locus of maps with degenerate tangency orders in terms of Chern classes of tautological bundles, and then describe that locus in terms of moduli spaces with smaller invariants.
 Novelties are introduced in both steps.
-In the first, we describe the locus of degenerate maps as the zero locus of a logarithmic line bundle, arising from a piecewise linear function with a simple moduli theoretic description.
-The use of tropical techniques substantially simplifies Gathmann's calculations.
-
-For the second step, we are forced to contend with the interaction of the relative splitting formula and the geometry of elliptic singularities, which is entirely new (\S \ref{subsection C0 splitting}).
-We express the factorisation condition -- central to the constructions in~\cite{RSPW,RSPW2} -- in terms of tautological classes, leading to Theorem~\ref{thm: recursion}.
-
-\subsection{Context and further discussion} This paper is most directly related to recent work on aligned logarithmic structures, elliptic singularities, and stable maps, as developed in~\cite{RSPW,RSPW2}.
-The moduli spaces we construct lie in between the absolute and toric-boundary-relative geometries studied in the first and second of those papers, respectively.
-The degeneration algorithm presented here is a first practical implementation of the theory developed in that work.
-
-We pass through general techniques that we expect will be useful in logarithmic Gromov--Witten theory more broadly.
-We explain how to describe degenerate moduli spaces in terms of simpler spaces of maps.
-This is substantially more delicate than the standard situation, where the strata are simply fibre products.
-First, one must understand the interaction of the relative geometry with elliptic singularities, which involves a study of the factorisation condition in terms of tautological bundles.
-Second, the degenerate strata of moduli spaces are not simply fibre products of spaces with smaller numerical invariants, but compactified torus bundles over these strata, due to the introduction of logarithmic blowups.
-This geometry is at the heart of recent work on the degeneration formula~\cite{R19}.
-The main text provides a first systematic procedure that uses tropical geometry to calculate with these torus bundles.
+In the first, we describe the locus of degenerate maps as the zero locus of a logarithmic line bundle, arising from a piecewise linear function with a tropical moduli theoretic description.
+The use of tropical techniques simplifies Gathmann's calculations.
+
+For the second step, we contend with the interaction of the relative splitting formula with the structure of elliptic singularities, which is new (\S \ref{subsection C0 splitting}).
+The factorisation condition -- central to the constructions in~\cite{RSPW,RSPW2} -- is expressed as a tautological class, leading to Theorem~\ref{thm: recursion}.
+
+\subsection{Context and techniques} The present work is part of a larger ongoing program relating to the role of curve singularities in Gromov--Witten theory that go beyond the well-studied nodal case~\cite{BC20,BCM18,Boz19,RSPW,RSPW2}.
+The basic motivation for this direction is that such alternative curve counting theories can often be more {enumerative} in nature and satisfy Lefschetz section theorems.
+Degeneration methods are a crucial tool in Gromov--Witten theory, and our results point to a fruitful use of these methods in this direction.
+
+The computations performed in this paper may be of use more broadly in logarithmic Gromov--Witten theory.
+Degenerate moduli spaces are constructed from simpler spaces of maps, but the geometry is substantially more delicate than the standard situation, where the strata are simply fibre products.
+First, one must describe the moduli space of maps out of elliptic singular curves in terms of maps out of the branches of this curves.
+We describe this in terms of natural tautological classes.
+Second, the degenerate strata of moduli spaces are not simply fibre products of spaces with smaller numerical invariants, but compactified torus bundles over these strata.
+The latter phenomenon is a constant presence in logarithmic Gromov--Witten theory~\cite{AW,R19}.
+The text provides a model procedure that uses tropical geometry to calculate with these torus bundles.
 
@@
 
-Although the geometric ideas in Gathmann's recursion are clear, they are implemented within the space of ordinary stable maps, and do not formally fit within the formalism of logarithmic Gromov--Witten theory.
-On the way to our main results, we reinterpret Gathmann's idea of increasing tangency within logarithmic mapping spaces.
+The geometric ideas in Gathmann's recursion are clear, but are implemented in the space of stable maps, and do not formally fit within the logarithmic context On the way to our main results, we reinterpret Gathmann's idea of increasing tangency in logarithmic Gromov--Witten theory.
 %This is done by the introduction of \emph{fictitious markings}, and an identification of the space of maps with higher contact order with a boundary stratum inside that of lower contact order and more (fictitious) markings.
@@
 
-\subsection{Future directions} The results of~\cite{RSPW} also suggest the existence of a reduced higher genus Gromov--Witten theory formed by replacing contracted elliptic components with singularities.
-We have been informed by Jonathan Wise that his Ph.D.
-candidate Sebastian Bozlee has constructed these higher genus reduced Gromov--Witten invariants.
-A manuscript is in preparation.
-The discussion here is expected to carry over to this setting.
-
-Our analysis leads naturally to the study of the main component of the double ramification cycle for target manifolds in genus one.
+\subsection{Future directions} There are two natural directions moving forward -- generalisations on the curve side and on the target side.
+The results of~\cite{RSPW} suggest the existence of a reduced higher genus Gromov--Witten theory formed by replacing contracted elliptic components with singularities, and this is reaffirmed by recent work of Bozlee~\cite{Boz19}.
+More general singularities are introduced and studied in work of Battistella--Carocci~\cite{BC20}.
+We expect the relative geometry and splitting techniques studied here to be useful in controlling these more exotic invariants.%, where few computations have been done.
+
+%Our analysis leads naturally to the study of the main component of the double ramification cycle for target manifolds in genus one.
 The virtual geometry of this was studied in recent work of Janda, Pandharipande, Pixton, and Zvonkine~\cite{DRCBundle}.
@@
 
-Finally, it would be natural to generalise the method of degenerating tangency conditions to targets with higher rank logarithmic structures.
-The extreme case when the target is a toric variety with its toric boundary, is intimately tied with the enumerative geometry of well-spaced tropical curves~\cite{LR18,RSPW2,Speyer}.
+On the target side, it would be natural to generalise the method of degenerating tangency conditions to higher rank logarithmic structures.
+When the target is a toric pair the problem is tied in with the enumerative geometry of well-spaced tropical curves~\cite{LR18,RSPW2,Speyer}.
 %We will return to these questions in future work.
@@
 \subsection*{Acknowledgements} We have benefited from fruitful conversations with friends and colleagues, including Pierrick Bousseau, Francesca Carocci, Cristina Manolache, Davesh Maulik, Keli Santos-Parker, and Jonathan Wise.
-The comments of an anonymous referee have proved very valuable.
 The authors worked on this project during visits to MPIM-Bonn, MIT, University of Cambridge, and the University of Glasgow, and thank these institutions for ideal working conditions and support.
-L.B.
+The text has been improved substantially by the careful reading and comments of a referee, to whom we are very grateful.
+
+\subsection*{Funding} L.B.
 and N.N.
@@
 \section{Constructions and logarithmic smoothness}\label{section construction}
-\noindent We briefly review some basic tropical structures in the theory of logarithmic curves and logarithmic stable maps.
-A detailed treatment is given by~\cite[Section~3]{CavalieriChanUlirschWise}; the following paragraphs are meant only as a reminder.
+\noindent We review the basic tropical structures in the theory of logarithmic curves and maps.
+A detailed treatment is given by~\cite[Section~3]{CavalieriChanUlirschWise}; the following paragraphs are meant as a reminder.
 
 \subsection{Curves and tropical curves} A nodal curve $C$ over $\spec \mathbb C$ has an associated dual graph $\Gamma(C)$.
-Given a toric monoid $P$, there is a logarithmic point $\spec (P \to \CC)$ which may be thought of as remembering the information of the embedding of the torus-fixed closed point into the affine toric variety $\spec \mathbb C[P]$.
+Given a toric monoid $P$, there is a logarithmic point $\spec (P \to \CC)$ which may be thought of as remembering the information of the embedding of the torus-fixed closed point into the toric variety $\spec \mathbb C[P]$.
 For a logarithmically smooth curve $C$ over $\spec (P \to \CC)$, the dual graph $\Gamma(C)$ is enhanced: given an edge $e$ of $\Gamma(C)$, the logarithmic structure keeps track of a generalised ``edge length'' $\ell_e$, which is an element of $P$.
@@
 \]
-A fibre of this map $\pi$ is a metric space enhancing the topological space $\Gamma(C)$, with edges given lengths in $\RR_{\geq 0}$.
+A fibre of $\pi$ is a metric space enhancing the topological space $\Gamma(C)$, with edges given lengths in $\RR_{\geq 0}$.
 Over the interior of the cone $\sigma_P$ these edge lengths are nonzero, and the fibres are homoemorphic to $\Gamma(C)$.
-Over the faces of $\sigma_P$, the fibres can be identified with edge contractions.
+Over the faces of $\sigma_P$, the fibres are viewed as edge contractions of $\Gamma(C)$.
 
 The discussion is globalized in~\cite{CavalieriChanUlirschWise}, and the construction can be carried out for the universal curve over the moduli space of logarithmic curves.
-Specifically, there is a stack $\mathfrak M_{g,n}^{\mathrm{trop}}$ over the category of cone complexes equipped with a universal curve
+There is a stack $\mathfrak M_{g,n}^{\mathrm{trop}}$ over the category of cone complexes equipped with a universal curve
 \[
@@
 \]
-The reader is encouraged to think of $\mathfrak M_{g,n}^{\mathrm{trop}}$ as playing the same role for $\mathfrak M_{g,n}$ as a fan plays for a toric variety.
-In particular, two constructions are relevant:
+It is common to view $\mathfrak M_{g,n}^{\mathrm{trop}}$ as playing the same role for $\mathfrak M_{g,n}$ as a fan plays for a toric variety. Two specific such roles are relevant:
 \begin{enumerate}
 \item A subdivision of $\mathfrak M_{g,n}^{\mathrm{trop}}$ gives rise to a birational modification of $\mathfrak M_{g,n}$.
-\item A piecewise linear function on $\mathfrak M_{g,n}^{\mathrm{trop}}$ gives rise to a Cartier divisor on $\mathfrak M_{g,n}$.
+\item A piecewise linear function on $\mathfrak M_{g,n}^{\mathrm{trop}}$ furnishes a Cartier divisor on $\mathfrak M_{g,n}$ with a section.
 \end{enumerate}
@@
 \subsection{Maps and tropical maps}The discussion carries over to the setting of logarithmic maps.
-Specifically, suppose we are given a logarithmic curve $C$ and a logarithmic map to a smooth pair $(X,Y)$ over a logarithmic scheme $S$.
+Consider a logarithmic curve $C$ and a logarithmic map to a smooth pair $(X,Y)$ over a logarithmic scheme $S$, with $Y$ connected.
 For simplicity, assume that $S$ is a $P$-logarithmic point, as above.
@@
 Here $\RR_{\geq 0}$ is the tropicalization (or ``fan'') of the smooth pair $(X,Y)$.
-Each fibre over $\sigma_P$ encodes a metric enhancement of the dual graph, together with a piecewise linear map to $\RR_{\geq 0}$.
-There is once again a cone stack representing the moduli problem of tropical maps; the technical details are only cosmetically different than those presented in~\cite{CavalieriChanUlirschWise}, and we leave these details to the reader (see also \cite{GrossSiebertLog}).
-
-\subsection{Maps from curves and elliptic singularities} We provide a brief intuitive picture that underlies the work in~\cite{RSPW,RSPW2}.
-If $C$ is a Gorenstein curve of genus one and $f:C\to \mathbb P^m$ is a morphism, the ampleness of the the tangent bundle of $\mathbb P^m$ ensures that if $f$ is non-constant on the minimal subcurve of $C$ of arithmetic genus one, then the deformations of $f$ are unobstructed; in fact, the deformations \textit{over the stack of curves} are also unobstructed.
-It is natural to attempt to resolve the moduli space of stable maps, by contracting the genus one subcurve on which the map is constant.
+A fibre over $\sigma_P$ encodes a metric enhancement of the dual graph, together with a piecewise linear map to $\RR_{\geq 0}$.
+There is again a cone stack representing the moduli problem of tropical maps; the construction differs cosmetically from the one presented in~\cite{CavalieriChanUlirschWise}, and we leave the details to the reader; see also~\cite{GrossSiebertLog}.
+
+\subsection{Stable maps and elliptic singularities} We provide a summary of the approach of~\cite{RSPW}.
+If $C$ is a Gorenstein curve of genus one and $f:C\to \mathbb P^m$ is a morphism, the ampleness of the tangent bundle of $\mathbb P^m$ ensures that if $f$ is non-constant on the minimal subcurve of $C$ of arithmetic genus one, then the deformations of $f$ are unobstructed; in fact, the deformations \textit{over the stack of curves} are also unobstructed.
+
+It is natural to attempt to resolve the moduli space of stable maps by contracting the genus one subcurve on which the map is constant.
 Whilst the moduli space of Gorenstein genus one curves is not smooth, a more sophisticated moduli problem, consisting of nodal curves $C$ together with a \textit{chosen contraction} to a Gorenstein curve $\bar{C}$, might be expected to resolve these singularities.
-The formation of such a moduli problem requires logarithmic geometry, and is achieved in~\cite[Section~3]{RSPW}.
+The formation of this moduli problem requires logarithmic geometry, and furnishes a moduli space with a universal \textit{nodal curve}, universal \textit{elliptically singular} curves, and contractions from the former to the latter~\cite[Section~3]{RSPW}.
 Once constructed, the corresponding moduli of stable maps out of a Gorenstein curve is also resolved.
-Note that maps from nodal genus one curves may have stable limits that contract genus one subcurves, but the introduction of Gorenstein singularities ensures properness while disallowing contracted genus one components.
-
-When working with logarithmic targets such as $(\mathbb P^m,H)$, as we do here, similar ideas may be expected to apply, but the deformation theory of maps becomes more delicate.
-Indeed, the logarithmic Euler sequence for this pair shows that the logarithmic tangent bundle is a quotient of $\mathcal O\oplus\mathcal O(1)^{\oplus m}$, and additional obstructions appear.
-In simple terms: there exist logarithmic stable maps to the pair $(\mathbb P^m,H)$ with obstructed logarithmic deformations, whose underlying stable map to $\PP^m$ is unobstructed.
-
-\subsection{Singularities and moduli of attachments}\label{S:ellsing} Isolated Gorenstein singularities of genus one were classified by Smyth in \cite{SMY1}: for every fixed number of branches $m$, there is precisely one isomorphism type of curve germ.
-For $m=1$ and $2$ these are the cusp ($A_2$) and tacnode ($A_3$) respectively; for $m\geq 3$ they are the union of $m$ general lines through the origin of $\Aaff^{m-1}$ -- following Smyth, we refer to these as \emph{elliptic $m$-fold points}.
-
-The problem of constructing an elliptic singularity from its pointed normalisation is more delicate; it was widely studied in van der Wyck's thesis \cite{vdW}.
+Maps from nodal genus one curves may have stable limits that contract genus one subcurves, but the introduction of Gorenstein singularities -- with an appropriate stability condition -- ensures properness without allowing contracted genus one components.
+
+The main target space in the present work is $(\mathbb P^m,H)$, and ideas parallel to those above can be expected to apply.
+However, the deformation theory of logarithmic maps is more delicate: the Euler sequence for this pair shows that the logarithmic tangent bundle is a quotient of $\mathcal O\oplus\mathcal O(1)^{\oplus m}$, and additional obstructions appear due to the trivial factor.
+%In simple terms: there exist logarithmic stable maps to the pair $(\mathbb P^m,H)$ with obstructed logarithmic deformations, whose underlying stable map to $\PP^m$ is unobstructed.
+
+\subsection{Singularities and moduli of attachments}\label{S:ellsing} Isolated Gorenstein singularities of genus one were classified by Smyth~\cite{SMY1}: for every fixed number of branches $m$, there is a unique isomorphism type of curve germ.
+For $m=1$ and $2$ these are the cusp ($A_2$) and tacnode ($A_3$) respectively; for $m\geq 3$ they are the union of $m$ general lines through the origin of $\Aaff^{m-1}$ -- the \emph{elliptic $m$-fold points}.
+
+The problem of constructing an elliptic singularity from its pointed normalisation is delicate; it was studied in van der Wyck's thesis \cite{vdW}.
 Recall that the seminormalisation $C^\text{sn}$ of a curve $C$ has the same underlying topological space, but its singularities consist of rational $m$-fold points only, i.e.
@@
 \noindent This is equivalent to \cite[Lemma 2.2]{SMY1}, where he describes the seminormalisation of an elliptic singularity as the data of a hyperplane in the Zariski cotangent space not containing the coordinate lines.
-We call \emph{moduli of attaching data} \cite[\S 2.2]{SMY2} (or \emph{crimping space}) the extra data needed to produce a singularity from its pointed normalisation.
+We use the term \emph{moduli of attaching data} \cite[\S 2.2]{SMY2} for the extra data needed to produce a singularity from its pointed normalisation.
 
 \begin{cor}
- The moduli of attachments of an elliptic $m$-fold point is isomorphic to $\mathbb G_{\text{m}}^m$.
+ The moduli of attaching data of an elliptic $m$-fold point is isomorphic to $\mathbb G_{\text{m}}^m$.
 \end{cor}
-\noindent One way to compactify it is to allow \emph{sprouting} on the boundary, i.e.
-replacing a branch $R_i$ of the singularity with a strictly semistable component $\PP^1$ with the singularity at $0$ and the branch $R_i$ glued nodally at $\infty$.
+\noindent This torus may be compactified by allowing \emph{sprouting} on the boundary: a branch $R_i$ of the singularity is replaced with a strictly semistable $\PP^1$ with the singularity at $0$ and $R_i$ glued nodally at $\infty$.
 
@@
 Let $V=\sum_{i=1}^mL_i$ be a presentation of a vector space as the direct sum of $m$ lines.
-Then the data of a general line $\ell$ in $V$ (or a general hyperplane in $V^\vee$) is equivalent to the data of compatible isomorphisms $\theta_{ij} \colon L_i \cong L_j$.
-Indeed, given a general line $\ell$, a vector $v\in\ell$ can be written as:
+The datum of a general line $\ell$ in $V$ (or a general hyperplane in $V^\vee$) is equivalent to the data of compatible isomorphisms $\theta_{ij} \colon L_i \cong L_j$.
+Given a general line $\ell$, a vector $v\in\ell$ can be written as:
 \[v=a_1e_1+\ldots+a_me_m,\qquad \text{with $a_i\neq 0$ for all $i$}\]
@@
 
-Lemma \ref{lem:pushout} provides a valuable characterisation of maps from an elliptic singularity $C$, which we will exploit in \S \ref{section reduced splitting}:
+Lemma \ref{lem:pushout} yields a characterisation of maps from an elliptic singularity $C$, which is used in \S \ref{section reduced splitting}:
 \begin{cor}\label{cor:maps_from_elliptic_sing}
@@
 \begin{lemma}\label{lem:PicE}
- Let $C$ be a curve of arithmetic genus one containing an elliptic $m$-fold point. Then $\operatorname{Pic}^0(C)\cong\mathbb G_{\text{a}}$.
+ If $C$ is a curve of arithmetic genus one with an elliptic $m$-fold point then $\operatorname{Pic}^0(C)\cong\mathbb G_{\text{a}}$.
 \end{lemma}
@@
 \subsection{Absolute geometry: background} Let $\mathfrak M_{1,n}$ be the logarithmic algebraic stack of $n$-pointed prestable curves of genus one.
-We begin by recalling the logarithmic moduli spaces of genus one curves constructed in~\cite[\S 2 \& \S 4]{RSPW}.
+We recall the logarithmic moduli spaces of genus one curves constructed in~\cite[\S 2 \& \S 4]{RSPW}.
 
@@
 Since the curve in question has genus one, there is a minimal genus one subgraph -- either a vertex of genus one or a cycle in the graph.
-We will refer to this as the \textbf{core}, denoted by $\plE$ below.
+We refer to this as the \textbf{core}, and denote it $\plE$.
 
 Given a point $s$ with $\pi(s)$ equal to $t$, there is a well-defined distance in the metric graph $\pi^{-1}(t)$ from $s$ to the core. 
-In particular, for each vertex $v$ of the dual graph $\Gamma(C)$, i.e.
-each component of $C$, there is a well-defined function $\lambda(v): \sigma_P\to \RR_{\geq 0}$, defined on the base of the tropical family.
-We may as well think of $\boldsymbol{\lambda}$ as a piecewise linear function $\lambda\colon\plC\to\RR_{\geq 0}\times\sigma_P$, see Figure \ref{fig:lambdaexample}.
-Given any other linear function $\delta$ on $\sigma_P$, say that $\delta$ is \textbf{comparable} to $\lambda(v)$ if there is a global order relation, either $\lambda(v)\leq \delta$ or $\lambda(v)\geq \delta$, that holds at all points of $\sigma_P$.
+For each vertex $v$ of the dual graph $\Gamma(C)$, there is a well-defined function $\lambda(v): \sigma_P\to \RR_{\geq 0}$, defined on the base of the tropical family.
+We view $\boldsymbol{\lambda}$ as a piecewise linear function $\lambda\colon\plC\to\RR_{\geq 0}\times\sigma_P$, see Figure \ref{fig:lambdaexample}.
+Given any linear function $\delta$ on $\sigma_P$, say that $\delta$ is \textbf{comparable} to $\lambda(v)$ if a global order relation, either $\lambda(v)\leq \delta$ or $\lambda(v)\geq \delta$, that holds at all points of $\sigma_P$.
 
 Piecewise linear functions on $\plC$ are naturally identified with global sections of the characteristic sheaf $\overline M_C$; linear functions on $\sigma_P$ are naturally identified with global sections of the characteristic sheaf $\overline M_S$, and can be pulled back to $C$.
-Given an arbitrary logarithmically smooth curve $C/S$, conditions involving the comparability of piecewise linear functions can be imposed at the level of geometric points; they determine subdivisions of $\sigma_P$, and, in turn, logarithmic modifications of $S$.
+Given a logarithmically smooth curve $C/S$, conditions involving the comparability of piecewise linear functions can be imposed at the level of geometric points; they determine subdivisions of $\sigma_P$, and, in turn, logarithmic modifications of $S$.
 %This leads to the following definition.
 
-\begin{definition}
+\begin{definition}\label{def: alignment}
 A \textbf{centrally aligned curve} is a pair $(C/S,\delta)$, where $\delta\in\overline{M}_S$, such that:
@@
     \item the section $\delta$ is comparable to $\lambda(v)$ for all vertices $v$ of $\plC$;
-    \item for any pair of vertices $v$ and $w$ of distance less than $\delta$, the sections $\lambda(v)$ and $\lambda(w)$ are comparable.
+    \item for any pair of vertices $v$ and $w$ of distance less than $\delta$ from the core, the sections $\lambda(v)$ and $\lambda(w)$ are comparable.
 \end{enumerate}
+The order relations among the vertex position functions is referred to as an \textbf{alignment}. 
 \end{definition}
-In other words, for the tropical curve $\sqC$, all vertices are either inside, outside, or on the circle of radius $\delta$ regardless of the point on the base; the collection of vertices inside the circle is totally ordered by their distance to the core.
+For a tropical curve  family $\sqC$, each vertex is either inside, outside, or on the circle of radius $\delta$ regardless of the point on the base; the vertices inside the circle are ordered by distance to the core.
 
@@
 
-Formally, given a family of tropical curves, the function $\delta$ provides a non-negative real number for each point on the base.
-We may therefore consider the ``\textbf{circle}'' of points on each fibre whose distance from the core is equal to $\delta$.
+Given a family of tropical curves, the function $\delta$ provides a non-negative real number for each point on the base.
+We consider the \textbf{circle} of points on each fibre whose distance from the core is equal to $\delta$.
 A partial destabilization, or ``bubbling'', introduces $2$-pointed rational curves into the curve by adding vertices to the dual graph at the points that lie on this circle (the crosses at height $\delta$ in Figure \ref{fig:lambdaexample}); we denote this new tropical curve by $\widetilde{\plC}$.
@@
 \begin{thm}[{\cite[Theorem B]{RSPW}}]
-The substack $\VZ_{1,n}(\mathbb P^m,d)$ of $\widetilde\VZ_{1,n}(\PP^m,d)$ parameterising maps to $\mathbb P^m$ that satisfy the factorisation condition is smooth and proper of the expected dimension.
+The substack $\VZ_{1,n}(\mathbb P^m,d)$ of $\widetilde\VZ_{1,n}(\PP^m,d)$ of maps to $\mathbb P^m$ that satisfy the factorisation condition is smooth, proper, and has the expected dimension.
 \end{thm}
@@
 \begin{remark}[Constant maps]\label{rem: constant-maps}
-When the degree of the map is $1$, maps from smooth genus one curves to $\PP^m$ are constant.
-The interior of the moduli space of stable maps in this case is empty, though the compactification by stable maps is non-empty.
+If the degree of the map is at most $1$, maps from smooth genus one curves to $\PP^m$ are constant and the interior of the space of stable maps is empty; the compactification by stable maps is non-empty.
 The space of maps satisfying the factorisation condition is also empty.
-We do not indulge on this any further.
+%We do not indulge on this any further.
 \end{remark}
@@
 
-We compactify the space described above, and then desingularise it.
-For the compactification, we begin with Abramovich--Chen--Gross--Siebert's space of logarithmic stable maps, though we will work with variants~\cite{AbramovichChenLog,ChenLog,GrossSiebertLog,KimLog}.
+We compactify the space described and then desingularise it.
+For compactification, we begin with Abramovich--Chen--Gross--Siebert's logarithmic stable maps, and then work with expanded variants~\cite{AbramovichChenLog,ChenLog,GrossSiebertLog,KimLog}.
 
@@
 The moduli space $\overline{\mathcal{M}}^{\operatorname{log}}_{1,\alpha}(\mathbb P^m|H,d)$ is a fibred category over logarithmic schemes, whose fibre over $(S,M_S)$ is the groupoid of logarithmically smooth curves of genus one over $(S,M_S)$ equipped with a logarithmic map to $\mathbb P^m$ of degree $d$ and contact order $\alpha$.
-It is a fundamental fact in the subject that this category is representable by a proper algebraic stack with logarithmic structure, parameterising minimal objects~\cite{ChenLog}.
+This category is representable by a proper algebraic stack with logarithmic structure, parameterising minimal objects~\cite{ChenLog}.
 
@@
 To elucidate the connection with the static target, consider a logarithmic stable map $[C\to (\mathbb P^m,H)]$ over $\mathrm{Spec} \ (\mathbb N\to \mathbb C)$.
-At the level of tropicalizations, there is a map of cone complexes:
+There is a map of tropicalizations:
 \[
@@
 Choose a subdivision of $\mathbb R_{\geq 0}$ whose vertices are the images of vertices of $\plC$.
-Pull this subdivision back to $\plC$ by subdividing it along the preimage of the vertices of $\mathbb R_{\geq 0}$.
+Pull this subdivision back to $\plC$ by subdividing it along the preimage of the new vertices of $\mathbb R_{\geq 0}$.
 Denote the resulting map $\widetilde \plC \to \widetilde{\mathbb R}_{\geq 0}$.
@@
 see~\cite{AW}.
-Here the latter is the $s$-times iterated deformation to the normal cone of $H$ in $\mathbb P^m$.
-The irreducible components of the target are in bijection with the vertices in $\widetilde{\mathbb R}_{\geq 0}$.
+The latter is the $s$-times iterated deformation to the normal cone of $H$ in $\mathbb P^m$.
+Components of the target are in bijection with the vertices in $\widetilde{\mathbb R}_{\geq 0}$.
 The curve is modified by adding rational components for the newly introduced vertices.
 
-The result is a logarithmic stable map to an expanded target $\mathbb P^m[s]$, together with a contraction to the main target component $\mathbb P^m[s]\to\mathbb P^m$.
-Two maps are considered equivalent if they differ by $\Gm$-scaling the target at higher level.
-This is the logarithmic enhancement of the classical theory of relative stable maps, due to Li \cite{Li1,Li2}.
-
-Globally, Kim constructs a moduli space of logarithmic maps to expanded degenerations, which on logarithmic points, reduces to the above construction~\cite{KimLog}.
+The result is a logarithmic stable map to an expansion $\mathbb P^m[s]$, with a collapse to the main component $\mathbb P^m[s]\to\mathbb P^m$.
+Maps are considered equivalent if they differ by $\Gm$-scaling the target at higher level.
+This is a logarithmic enhancement of the theory of relative maps, due to Li \cite{Li1}.
+
+Kim constructs a moduli space of logarithmic maps to expanded degenerations, which on logarithmic points, gives the above construction~\cite{KimLog}.
 Kim's space is identified with a subcategory of the Abramovich--Chen--Gross--Siebert space (as stacks over logarithmic schemes), and its dual minimal monoids are cones in a subdivision of the dual minimal cones of the unexpanded space, see~\cite[\S~2]{R19}.
-
-We typically work with expansions for convenience, and use the notation
+The map from this space to the logarithmic space is akin to a blowup: it is a logarithmic modification induced by a subdivision of tropical moduli spaces.
+We typically work with expansions, and use the notation
 $\ol\Mcal_{1,\alpha}(\PP^m|H,d)$
@@
 
-\subsection{Relative geometry: alignment} We consider the space of logarithmic morphisms from the universal curve $\mathcal{C} \to \mathfrak{M}_{1,n}^{\mathrm{cen}}$ to the logarithmic scheme $(\PP^m,H)$.
-As in the absolute case, we require the radius to pass through a vertex of positive degree in $\PP^m$ and contain only vertices of degree zero in its strict interior.
-In this way we obtain a logarithmic modification of the Abramovich--Chen--Gross--Siebert space.
-If we further perform the subdivisions of target and source outlined in the previous section, we obtain a logarithmic modification of Kim's space:
+\subsection{Relative geometry: alignment} Consider the space of logarithmic morphisms from the universal curve $\mathcal{C} \to \mathfrak{M}_{1,n}^{\mathrm{cen}}$ to the logarithmic scheme $(\PP^m,H)$.
+As in the absolute case, an alignment can be introduced on the source curve as in Definition~\ref{def: alignment}.
+The circle associated to the alignment must pass through a vertex of positive degree in $\PP^m$ and contain only vertices of degree zero in its strict interior.
+We obtain a logarithmic modification of the Abramovich--Chen--Gross--Siebert space.
+By means of additional subdivisions of the tropical target and source, as outlined in the previous section, we obtain a logarithmic modification of Kim's space with expansions:
 \begin{equation*} \widetilde\VZ_{1,\alpha}(\PP^m|H,d) \to \ol\Mcal_{1,\alpha}(\PP^m|H,d)\end{equation*}
 which we refer to as the \textbf{moduli space of centrally aligned maps} to $(\PP^m,H)$.
-This space parametrises transverse logarithmic maps to the expanded target with an alignment which is compatible with the map.
-Because of this compatibility condition, there is a morphism
+This space parametrises logarithmic maps to the expanded target with an alignment which is compatible with the map.
+There is a morphism
 \begin{equation*} \widetilde\VZ_{1,\alpha}(\PP^m|H,d) \to \widetilde\VZ_{1,n}(\PP^m,d)\end{equation*}
@@
 Recall that $\mathbb P^m[s]$ consists of a union of $\mathbb P^m$ with $s$ copies of the projective bundle $\mathbb{P} = \mathbb P(\mathcal O_H\oplus \mathcal O_H(1))$.
-We refer to these latter components as \textbf{the higher levels}.
-Thus, we will say that a subcurve $D\subseteq C$ \textbf{maps to higher level} if the composite $C\to \mathbb P^m$ maps $D$ into $H\subset \mathbb P^m$.
+The latter components are \textbf{the higher levels}.
+We will say that a subcurve $D\subseteq C$ \textbf{maps to higher level} if the composite $C\to \mathbb P^m$ maps $D$ into $H\subset \mathbb P^m$.
 
@@
 its core.
-Recall that we name \emph{core} the minimal genus one subcurve of a Gorenstein curve of arithmetic genus one, so the latter decomposes into the nodal union of the core and a (possibly empty) rational forest.
+The \emph{core} of a Gorenstein curve of genus one is the minimal genus one subcurve.
+Any such curve decomposes as the nodal union of the core and a (possibly empty) rational forest.
 If the curve contains an elliptic $m$-fold point, we say a map is non-constant on the core if at least one branch of the singularity is not contracted.
-The following condition identifies the locus of smoothable maps.
+The following condition identifies smoothable maps.
 
@@
 \begin{rem}
- The factorisation conditions are understood to be satisfied when $C\to \mathbb P^m[s]$ (resp. $C\to \mathbb P^m$) does not contract a genus one subcurve. 
+ The factorisation conditions are understood to be satisfied if $C\to \mathbb P^m[s]$ (resp. $C\to \mathbb P^m$) does not contract a genus one subcurve. 
 \end{rem}
@@
 be the stack of maps from centrally aligned curves to expansions that factor completely.
-
 If $[C\to \mathbb P^m[s]\to \mathbb P^m]$ is a family of centrally aligned maps over $S$ that factors completely, there is a moduli map $S\to \VZ_{1,n}(\mathbb P^m,d)$, to the principal component of the space of absolute maps.
@@
 \begin{thm}\label{thm: log-smoothness}
-The stack $\VZ_{1,\alpha}(\mathbb P^m|H,d)$ is logarithmically smooth and proper of the expected dimension.
+The stack $\VZ_{1,\alpha}(\mathbb P^m|H,d)$ is logarithmically smooth, proper, and has the expected dimension.
 \end{thm}
 
-As noted in Remark~\ref{rem: constant-maps}, maps from elliptic curves to $\PP^m$ will always be taken to have degree at least $2$, ensuring that the main component is non-empty.
+Maps out of elliptic curves will be assumed to have degree at least $2$, ensuring that the main component is non-empty, c.f. Remark~\ref{rem: constant-maps}.
 
@@
 
-The proof is analogous to that of \cite[Theorem 3.5.1]{RSPW2}. There is a forgetful morphism
+There is a forgetful morphism
 \[
@@
 \]
-remembering only the stabilisation of the composite $f_B\colon C\to\PP^m[s]\to\PP^m$.
-A priori, this is in $\overline{\pazocal M}_1(\PP^m,d)$, but in fact by assumption $(C,\delta_B)$ is centrally aligned, and $f_B$ factors through $\overline C_B$, as we have already remarked.
-
-The expanded target $\PP^m[s]$ is logarithmically \'etale over $\PP^m$ with the divisorial log structure associated to $H$, so it is equivalent to study the deformation theory of the unexpanded map to $(\PP^m,H)$.
-The logarithmic morphism $(\PP^m,H)\to \PP^m$ induces an exact sequence of log tangent bundles:
+remembering the stabilisation of the composite $f_B\colon C\to\PP^m[s]\to\PP^m$.
+A priori, this is in $\overline{\pazocal M}_1(\PP^m,d)$, but by assumption $(C,\delta_B)$ is centrally aligned, and $f_B$ factors through $\overline C_B$.
+
+Before embarking, we record that the proof will utilise $\nu$ in the following way: the deformation spaces of objects in the domain of $\nu$ will be cut out from the deformation spaces of their images in the target of $\nu$, by the vanishing of an obstruction class.
+It will then be shown that this subspace of deformations has everywhere the expected dimension.
+
+The expanded target $\PP^m[s]$ is logarithmically \'etale over $\PP^m$ with the divisorial structure associated to $H$, so it is equivalent to study the deformation theory of the unexpanded map to $(\PP^m,H)$.
+The logarithmic morphism $(\PP^m,H)\to \PP^m$ induces an exact sequence:
 \[0\to T_{\PP^m}(-\operatorname{log}H)\to T_{\PP^m}\to\OO_H(H)\to 0,\]
-relating the absolute and relative obstruction theories.
-This shows that $\nu$ can be obstructed only when a genus one subcurve is mapped to higher level in such a way that it is contracted by the collapsed map $f_B$.
-In this case, let $C_0$ denote the core, and let $E$ be the connected component of $f_B^{-1}(f_B(C_0))$ of arithmetic genus one.
+relating the absolute logarithmic deformation/obstruction theory of the map with the those relative to the target of $\nu$.
+By examining the associated long exact sequence, we find that a stable map can be obstructed only when a genus one subcurve is mapped to higher level in such a way that it is contracted by the collapsed map $f_B$.
+In this case, let $C_0$ denote the core, and $E$ the connected component of $f_B^{-1}(f_B(C_0))$ of arithmetic genus one.
 
@@
 The deformation problem is local, so we may as well suppose that $\overline M_S^{\text{gp}}$ is a constant sheaf of monoids with stalk $\overline M_{S,s}^{\text{gp}}=:Q$, for a geometric point $s\in S$.
-Note that sections of $M_S$ such as $\delta_B$ and $\delta_F$ extend automatically due to strictness.
+Note that sections of $\overline M_S$ such as $\delta_B$ and $\delta_F$ extend automatically due to strictness.
 Moreover, it is equivalent to deform $f$ or $f_F\colon\overline C_F\to\PP^m_S$, where $\overline C_F$ is given the trivial logarithmic structure around the elliptic singularity.
 
-The map $f_F\colon \overline C_F\to\PP^m[s]$ induces a tropical map $\alpha\colon\plC_F\to\RR_{\geq 0}\times\sigma_Q$, that we want to think of as a section $\alpha\in H^0(\overline C_F,\overline M_C^{\text{gp}})$.
-With notation as above, we obtain a trivialisation of the line bundle $\OO_{\overline C_F}(-\alpha)$ upon restriction to $E$.
-By \cite[Proposition 2.4.1]{RSPW}, the latter is isomorphic to $\OO_E(\sum\mu_i x_i)$, where $\mu_i$ is the slope/expansion factor of $\alpha$ along the edge $e_i$ of $\plC_F$, and $x_i$ the node corresponding to $e_i$ thought of as a smooth marking on $E$.
-
+The map $f_F\colon \overline C_F\to\PP^m[s]$ induces a tropical map $\alpha\colon\plC_F\to\RR_{\geq 0}\times\sigma_Q$; we view this piecewise linear function as a section $\alpha\in H^0(\overline C_F,\overline M_C^{\text{gp}})$.
+With notation as above, we obtain a trivialisation of the line bundle $\OO_{\overline C_F}(-\alpha)$ associated to $\alpha$, after restriction to $E$.
+By \cite[Proposition 2.4.1]{RSPW}, the latter is isomorphic to $\OO_E(\sum\mu_i x_i)$, where $\mu_i$ is the slope of $\alpha$ along the edge $e_i$ of $\plC_F$, and $x_i$ the node corresponding to $e_i$ thought of as a smooth marking on $E$.
+
+For a \textit{strict} deformation of the curve, the piecewise linear function $\alpha$ extends canonically.
 The deformation problem for $f_F$ relative to $(C^\prime,\delta_B,f_B^\prime)$ reduces to the problem of extending $\alpha$ as a trivialisation of $\OO_E(\sum\mu_i x_i)$.
-This gives an interpretation of $\operatorname{Obs}(f/(C,\delta_B,f_B))$ as $H^1(\overline C_F,\OO)$.
+This identifies $\operatorname{Obs}(f/(C,\delta_B,f_B))$ as $H^1(\overline C_F,\OO)$.
 The latter is a vector space of dimension $1$.
@@
 \begin{equation}\label{eqn:def-obs}\operatorname{Def}(C,\delta_B,f_B)\to \operatorname{Obs}(f/(C,\delta_B,f_B)).\end{equation}
-The left-hand side contains in particular the space $\operatorname{Def}(E,\mathbf{x})=\operatorname{Ext}^1(\Omega_E(\mathbf x),\OO_E)$, since $E$ is contracted by $f_B$.
-Since by assumption at least one of the $\mu_i$ is non-zero, $\operatorname{Ext}^1(\Omega_E(\mathbf x),\OO_E)$ surjects onto $H^1(\overline C_F,\OO)$ by \cite[Corollary 3.5.3]{RSPW2}.
-Looking back at \eqref{eqn:def-obs}, we see that obstructions to deforming $f$ can be killed by an appropriate choice of lift $(C^\prime,\delta_B,f_B^\prime)$.
-
+The left-hand side contains  $\operatorname{Def}(E,\mathbf{x})=\operatorname{Ext}^1(\Omega_E(\mathbf x),\OO_E)$, since $E$ is contracted by $f_B$.
+Since at least one of the $\mu_i$ is non-zero, $\operatorname{Ext}^1(\Omega_E(\mathbf x),\OO_E)$ surjects onto $H^1(\overline C_F,\OO)$ c.f.
+\cite[Corollary 3.5.3]{RSPW2}.
+Looking back at \eqref{eqn:def-obs}, given an infinitesimal deformation of $(C^\prime,\delta_B,f_B^\prime)$, it is possible to adjust the curve by a deformation of the points $\mathbf x$ to ensure that the obstruction vanishes.
+
+We put the pieces together.
+The space $ \operatorname{Obs}(f/(C,\delta_B,f_B))$ always has rank $1$.
+Next, note that once the collapsed stable map is fixed, there are no nontrivial \textit{logarithmic} deformations of the map to $\mathbb P^m[s]$: the morphism from logarithmic maps to ordinary maps is finite~\cite[\S~3.7]{ChenLog}.
+Therefore, we may view the logarithmic deformation spaces of $f$ as a subspace of the logarithmic deformation spaces of $(C^\prime,\delta_B,f_B^\prime)$, consisting of those deformations with vanishing class in $\operatorname{Obs}(f/(C,\delta_B,f_B))$.
+The data $(C^\prime,\delta_B,f_B^\prime)$ have unobstructed deformations, so this subspace is everywhere of the expected dimension.
+The obstructions to logarithmic deformations of $f$ vanish, and we conclude.
 \end{proof}
 
-The theorem guarantees that the singularities of the space of completely factoring maps to expansions is logarithmically smooth. One can say more in this case.
+The theorem guarantees that the space of completely factoring maps to expansions has toric singularities, but one can say more.
 
@@
 
-\textcolor{red}{Luca's rewrite of the Corollary: Up to a generalised root construction, $\VZ_{1,\alpha}(\mathbb P^m|H,d)$ is a smooth Deligne-Mumford stack.}
+%\textcolor{red}{Luca's rewrite of the Corollary: Up to a generalised root construction, $\VZ_{1,\alpha}(\mathbb P^m|H,d)$ is a smooth Deligne-Mumford stack.}
 
@@
 Since $\VZ_{1,\alpha}(\mathbb P^m|H,d)$ is logarithmically smooth, it will suffice to show that the cones of its tropicalization are simplicial.
-To see this, consider a logarithmic stable map to an expansion $C\to \mathbb P^m[s]$ without a central alignment.
+Consider a logarithmic stable map to an expansion $C\to \mathbb P^m[s]$ without a central alignment.
 The tropical moduli cone obtained as the dual of the minimal base monoid can be identified with $\mathbb R_{\geq 0}^{s}$, see for instance~\cite[Section~2.2]{ChenDegeneration}.
-The alignment procedure is an iterated barycentric subdivision at the level of tropical moduli spaces, as explained in~\cite[Section 4.6]{RSPW}, and such subdivisions preserve the property of being simplicial.
-We conclude from this that the blowup $\widetilde{\VZ}^{\mathrm{exp}}_{1,\alpha}(\mathbb P^m|H,d)$ obtained by centrally aligning Kim's spaces has simplicial cones.
+The alignment is an iterated stellar subdivision on tropical moduli spaces, see~\cite[Section 4.6]{RSPW}, and such subdivisions preserve the property of being simplicial.
+We conclude that the blowup $\widetilde{\VZ}^{\mathrm{exp}}_{1,\alpha}(\mathbb P^m|H,d)$ obtained by centrally aligning Kim's spaces has simplicial cones.
 The morphism $\VZ_{1,\alpha}(\mathbb P^m|H,d)\to \widetilde{\VZ}^{\mathrm{exp}}_{1,\alpha}(\mathbb P^m|H,d)$ is strict, so the cones of $\VZ_{1,\alpha}(\mathbb P^m|H,d)$ are simplicial, as claimed.
@@
 
-\subsection{Rubber variants}\label{subsection rubber} We require a ``rubber'' variant of the space of maps $\VZ_{1,\alpha}(\mathbb P^m|H,d)$, where the curve is contained in the higher levels.
-
+\subsection{Rubber variants}\label{subsection rubber} There exists a rubber variant of $\VZ_{1,\alpha}(\mathbb P^m|H,d)$, where the curve is contained in the higher levels, whose construction is analogous.
 Let $\mathbb P$ denote the projective bundle $\mathbb P(\mathcal O(1)\oplus\mathcal O)$ on $H\cong\mathbb P^{N-1}$.
@@
 \begin{thm}\label{thm rubber log smooth}
-The stack $\VZ^{\leftrightarrow}_{1,\alpha}(\mathbb P|H_0+H_\infty,d)$ is logarithmically smooth and proper of the expected dimension.
+The stack $\VZ^{\leftrightarrow}_{1,\alpha}(\mathbb P|H_0+H_\infty,d)$ is logarithmically smooth, proper, and has the expected dimension.
 \end{thm}
 
-The main point in the proof is that on the space of non-degenerate maps with smooth domains, the map from $\VZ^\circ_{1,\alpha}(\mathbb P|H_0+H_\infty,d)\to \VZ^{\leftrightarrow,\circ}_{1,\alpha}(\mathbb P|H_0+H_\infty,d)$ is a $\mathbb G_{\operatorname{m}}$-torsor.
+On the locus of maps from smooth domains, the map from $\VZ^\circ_{1,\alpha}(\mathbb P|H_0+H_\infty,d)\to \VZ^{\leftrightarrow,\circ}_{1,\alpha}(\mathbb P|H_0+H_\infty,d)$ is a $\mathbb G_{\operatorname{m}}$-torsor.
 One expects that the map on compact moduli spaces is a nodal curve fibration.
 To prove this, it is convenient to work with the logarithmic multiplicative group and its torsors.
-Recall that the \textbf{logarithmic multiplicative group} $\mathbb G_{\mathrm{log}}$ is the functor on logarithmic schemes whose value on a logarithmic scheme $S$ is the group of global sections $H^0(S,M_S^{\mathrm{gp}})$; it is a proper group functor, and it contains $\Gm$ as a subfunctor (from $\OO^\times_S\subseteq M_S^{\mathrm{gp}}$).
-This functor is representable only after a logarithmically \'etale cover, see for instance~\cite{MW17,RW19}.
-
-Each fibre of the bundle $\mathbb P \to \mathbb P^{N-1}$ admits a natural log \'etale morphism to $\mathbb G_{\mathrm{log}}$.
-Replacing these fibres by $\mathbb G_{\mathrm{log}}$, we obtain a non-representable functor on logarithmic schemes $\mathbb P_{\mathrm{log}}$ and a logarithmically \'etale modification
-\[
-\mathbb P\to \mathbb P_{\mathrm{log}}.
-\]
+The \textbf{logarithmic multiplicative group} $\mathbb G_{\mathrm{log}}$ is the functor on logarithmic schemes whose value on a logarithmic scheme $S$ is the group of global sections $H^0(S,M_S^{\mathrm{gp}})$; it is a proper group functor, and contains $\Gm$ as a subfunctor (from $\OO^\times_S\subseteq M_S^{\mathrm{gp}}$).
+This functor is representable after a logarithmically \'etale~\cite[Proposition~1]{RW19}.
+
+The morphism $\mathbb P \to \mathbb P^{N-1}$ determines a $\mathbb G_m$-torsor; the inclusion $\mathbb G_m\hookrightarrow \mathbb G_{\mathrm{log}}$, determines a $\mathbb G_{\mathrm{log}}$-torsor denoted $\mathbb P_{\mathrm{log}}$ which is a functor on logarithmic schemes with a logarithmically \'etale cover by a scheme equipped with a logarithmic structure.
 
@@
 \begin{proof}[Proof of Theorem \ref{thm rubber log smooth}]
-Consider the stack over logarithmic schemes $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}},d)$ of stable logarithmic maps that factor completely.
-Here, stability for the map coincides with stability for the projection to $\mathbb P^{N-1}$.
-The arguments in the previous section show that maps to $\mathbb P$ that factor completely are unobstructed.
-Since this space is a logarithmically \'etale cover of $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}},d)$, logarithmic smoothness of the latter follows.
-
-The logarithmic multiplicative group $\mathbb G_{\mathrm{log}}$ acts on $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}},d)$ by translation.
-Tautologically, $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}},d)$ is a $\mathbb G_{\mathrm{log}}$-torsor over the moduli problem of maps up to this $\mathbb G_{\mathrm{log}}$ translation.
-It is representable after a logarithmically \'etale modification by a family of nodal curves.
-It follows that the space $\VZ^{\leftrightarrow}_{1,\alpha}(\mathbb P_{\mathrm{log}},d)$ of maps up to $\Glog$-translation that factor completely is logarithmically smooth.
-
-To conclude the result, we compare $\VZ^{\leftrightarrow}_{1,\alpha}(\mathbb P_{\mathrm{log}},d)$ and  $\VZ^{\leftrightarrow}_{1,\alpha}(\mathbb P|H_0+H_\infty,d)$.
-Since a map to $(\mathbb P,H_0+H_\infty)$ gives rise immediately to a map to $\mathbb P_{\mathrm{log}}$, there is a morphism
+Consider the stack over logarithmic schemes $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}},d)$ of stable logarithmic maps that factor completely, noting the factorisation for the map to $\mathbb P_{\mathrm{log}}$ may be imposed after passing to an expansion c.f.~\cite[Section~3.3]{RSPW2}.
+Stability here coincides with stability for the projection to $\mathbb P^{N-1}$.
+The proof of Theorem~\ref{thm: log-smoothness} applies here to show that maps to $\mathbb P$ factorising completely are unobstructed.
+This space is a logarithmically \'etale cover of $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}},d)$, and logarithmic smoothness of the latter also follows.
+
+The logarithmic multiplicative group $\mathbb G_{\mathrm{log}}$ acts on $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}},d)$ by translation without fixed points.
+Tautologically, $\VZ_{1,\alpha}(\mathbb P_{\mathrm{log}},d)$ is a $\mathbb G_{\mathrm{log}}$-torsor over the moduli problem of maps up to this $\mathbb G_{\mathrm{log}}$-translation.
+As $\mathbb G_{\mathrm{log}}$ is logarithmically smooth, the space $\VZ^{\leftrightarrow}_{1,\alpha}(\mathbb P_{\mathrm{log}},d)$ of maps up to $\Glog$-translation that factor completely is also logarithmically smooth.
+
+We compare $\VZ^{\leftrightarrow}_{1,\alpha}(\mathbb P_{\mathrm{log}},d)$ and  $\VZ^{\leftrightarrow}_{1,\alpha}(\mathbb P|H_0+H_\infty,d)$.
+A map to $(\mathbb P,H_0+H_\infty)$ gives rise to a map to $\mathbb P_{\mathrm{log}}$.
+The morphism
 \[
@@
 \]
-The lifting criterion shows that this map is logarithmically \'etale, so the result follows.
+is log \'etale by the lifting cirterion, as in~\cite[Theorem~5.3.4]{MW17}. The result is a consequence. 
 \end{proof}
@@
 \subsection{Hypersurface pairs}\label{subsection virtual}
-Let $(X,Y)$ be a smooth pair with $Y$ very ample. The definition in \S \ref{subsection factorisation} applies in this setting and yields a moduli space $\VZ_{1,\alpha}(X|Y,\beta)$ with a morphism
+Let $(X,Y)$ be a smooth pair with $Y$ very ample. The definition in \S \ref{subsection factorisation} applies and yields a moduli space $\VZ_{1,\alpha}(X|Y,\beta)$ with a morphism
 \begin{equation*} \VZ_{1,\alpha}(X|Y,\beta) \to \ol\Mcal^{\operatorname{log}}_{1,\alpha}(X|Y,\beta)\end{equation*}
-obtained by performing a logarithmic modification and passing to a closed substack where the factorisation property is satisfied.
+obtained a logarithmic modification and the application of the factorisation property.
 This moduli space will typically be non-equidimensional, but we equip it with a virtual class as follows.
@@
 
-Since $\VZ_{1,n}(\PP^m,d)$ is smooth and $\VZ_{1,n}(X,\beta)$ carries a natural virtual class \cite[Theorem 4.4.1]{RSPW}, the diagonal of $\VZ_{1,n}(\PP^m,d)$ defines a pullback~\cite[Appendix A]{BattistellaNabijou}, and therefore the virtual class on the space of maps to $(X,Y)$:
+Since $\VZ_{1,n}(\PP^m,d)$ is smooth and $\VZ_{1,n}(X,\beta)$ carries a virtual class \cite[Theorem 4.4.1]{RSPW}, the diagonal of $\VZ_{1,n}(\PP^m,d)$ defines a pullback~\cite[Appendix A]{BattistellaNabijou}, and therefore the virtual class on the space of maps to $(X,Y)$:
 \begin{equation*} \virt{\VZ_{1,\alpha}(X|Y,\beta)} := i_\Delta^! [\VZ_{1,\alpha}(\PP^m|H,d)]. \end{equation*}
-Note that this is parallel to the virtual formalism in~\cite{Ga}.
+The virtual formalism is parallel to the one in~\cite{Ga}.
 As $\VZ_{1,\alpha}(X|Y,\beta)$ is equipped with evaluation maps and cotangent lines on the universal curve, we arrive at a definition of reduced Gromov--Witten invariants for the pair $(X,Y)$ by the standard mechanics.
@@
 
-\noindent The logarithmic smoothness of Theorem~\ref{thm: log-smoothness} implies that $\VZ_{1,\alpha}(\mathbb P^m|H,d)$ is an orbifold toroidal embedding.
-The irreducible components of its boundary stratify the space, as we now describe.
-
-The tropicalizations of logarithmic maps that factor completely are combinatoriall constrained by a condition known as \textbf{well-spacedness}. The version we use here is essentially identical to~
-\cite{RSPW2}.
+\noindent It is know by Theorem~\ref{thm: log-smoothness} that $\VZ_{1,\alpha}(\mathbb P^m|H,d)$ is a toroidal orbifold.
+The irreducible components of its boundary stratify the space.
+The tropicalizations of logarithmic maps that factor completely are constrained by a condition called \textbf{well-spacedness}, c.f.~\cite[Section~4]{RSPW2}.
 
@@
 \begin{rem}
-Condition \eqref{pt:well-spaced2} is not relevant as far as rays of the tropical moduli space (i.e.
-divisors) are concerned, since there are always at least two parameters involved, namely $F(\plE)$ - or the distance from $F(\plE)$ to the origin of $\RR_{\geq 0}$ - and the distance from $\plE$ to the first flag of non-zero slope within $\plC$.
+Condition \eqref{pt:well-spaced2} is not relevant to the rays of the tropical moduli space (i.e.
+divisors), since there are always at least two parameters involved, namely $F(\plE)$ - or the distance from $F(\plE)$ to the origin of $\RR_{\geq 0}$ - and the distance from $\plE$ to the first flag of non-zero slope within $\plC$.
 As we mostly concentrate on divisors starting from \S \ref{Section Gathmann line bundle}, it will not play much of a role in the rest of the paper.
@@
 \begin{proof}
-The required result is essentially contained in~\cite[Section 4]{RSPW2}, so we explain how to deduce it from the one in loc.
-cit.
+The required result is a consequence of~\cite[Section 4]{RSPW2}, and we explain how to deduce it.
 We may focus on a single component of the expansion $\mathbb P^m[s]$ that contains the image of a contracted genus one subcurve, as this is the only relevant case.
-We may thus replace the target with the projective bundle $\mathbb P(\mathcal O(1)\oplus \mathcal O)$ over $\mathbb P^{N-1}$ equipped with the divisorial logarithmic structure from the $0$ and $\infty$ sections.
+We replace the target with the projective bundle $\mathbb P(\mathcal O(1)\oplus \mathcal O)$ over $\mathbb P^{N-1}$ equipped with the divisorial logarithmic structure from the $0$ and $\infty$ sections.
 Let $p$ be the point to which the genus one subcurve is contracted.
-Passing to an open neighbourhood of $p$, the map to the bundle is given by a rational function $f$ on an open curve $C^\circ$, determined by the the subgraph formed by $\plE$ and the flags $t_i$ described in the definition above.
+Passing to an open neighbourhood of $p$, the map to the bundle is given by a rational function $f$ on an open curve $C^\circ$, determined by the subgraph formed by $\plE$ and the flags $t_i$ described above.
 To describe the tropical map to $\mathbb R_{>0}$, we observe that $\plE$ is contracted to a fixed point $q\in\mathbb R_{>0}$.
@@
 The pole orders of $f$ at these distinguished points determine the slopes of the tropical map.
-We are now exactly in the situation considered in~\cite[Second Paragraph of \S~4.6]{RSPW2}, and Lemma~4.6.1 of loc.
+We are now in the situation considered in~\cite[Second Paragraph of \S~4.6]{RSPW2}, and Lemma~4.6.1 of loc.
 cit.
@@
 
-\subsection{The cone complex} To understand the stratification via combinatorial data, we will build the stratification from known objects. \\
+\subsection{The cone complex} To understand the stratification via combinatorial data, we will build the stratification from known objects. \smallskip
 
@@
 This is naturally identified with the tropicalization (in the logarithmic sense) of the Abramovich--Chen--Gross--Siebert space of logarithmic stable maps to the pair $(\mathbb P^m,H)$.
-\\
+\smallskip
 
@@
 The combinatorial types of such \textbf{image-ordered} maps produce the cones of a subdivision of $\Sigma^{\mathrm{log}}$ which we denote $\Sigma^{\mathrm{Kim}}$.
-As the notation suggests, $\Sigma^{\Kim}$ is the tropicalization of Kim's moduli space of logarithmic maps to $(\PP^m,H)$.\\
+As the notation suggests, $\Sigma^{\Kim}$ is the tropicalization of Kim's space of logarithmic maps to $(\PP^m,H)$.\smallskip
 
@@
 \Sigma^{\mathrm{cen}}$ be the subdivision obtained by requiring that the vertices contained within the circle of radius $\delta$ around the core of $\plC$ are totally ordered.
-This involves introducing cones along which certain $\Z$-linear combinations of edge lengths are identified.\\
+This involves introducing cones along which certain $\Z$-linear combinations of edge lengths are identified.\smallskip
 
@@
 The cone complex $
-\Sigma_{1,\alpha}(\mathbb P^m|H,d)$ is the fan of the toroidal embedding $
-\VZ_{1,\alpha}(\mathbb P^m|H,d)$. In particular, the codimension $k$ strata of $
+\Sigma_{1,\alpha}(\mathbb P^m|H,d)$ is the fan of $
+\VZ_{1,\alpha}(\mathbb P^m|H,d)$ viewed as a toroidal embedding. In particular, the codimension $k$ strata of $
 \VZ_{1,\alpha}(\mathbb P^m|H,d)$ are in inclusion reversing bijection with the dimension $k$ cones in $
@@
 \VZ_{1,\alpha}(\mathbb P^m|H,d)$ has a strict map to $
-\VZ_{1,\alpha}(\mathbb P^m|H,d)$, so its cone complex is a subcomplex of $\Sigma^{\mathrm{cen}}$.
-The fact that it is contained in the subcomplex of well-spaced curves is immediate from Proposition~\ref{prop: well-spaced}.
+\VZ_{1,\alpha}(\mathbb P^m|H,d)$, so its cone complex is a subcomplex of $\Sigma^{\mathrm{cen}}$. It is contained in the subcomplex of well-spaced curves is by Proposition~\ref{prop: well-spaced}.
 \end{proof}
@@
 \end{enumerate}
-In \S \ref{section reduced splitting} we will perform this analysis in the case $k=1$.
+In \S \ref{section reduced splitting} we perform this analysis in the case $k=1$.
 
@@
 \begin{dfn}
- For each marking $x_k$, consider the locus $\Dcal_{1,\alpha,k}(\PP^m|H,d) \subseteq \VZ_{1,\alpha}(\PP^m|H,d)$ where $x_k$ belongs to an \textbf{internal component} of the collapsed map, i.e.
+ For a marking $x_k$, consider the locus $\Dcal_{1,\alpha,k}(\PP^m|H,d) \subseteq \VZ_{1,\alpha}(\PP^m|H,d)$ where $x_k$ belongs to an \textbf{internal component} of the collapsed map, i.e.
 a component of the curve that is mapped into $H$.
@@
 
-The pair $(\Lcal_k,s_k)$ is most naturally constructed on the moduli space $\MLog_{1,\alpha}(\PP^m|H,d)$ of non-expanded logarithmic maps; the corresponding pair on $\VZ_{1,\alpha}(\PP^m|H,d)$ will be obtained via pull-back.
+The pair $(\Lcal_k,s_k)$ is natural on the moduli space $\MLog_{1,\alpha}(\PP^m|H,d)$ of non-expanded logarithmic maps; the corresponding pair on $\VZ_{1,\alpha}(\PP^m|H,d)$ will be obtained via pull-back.
 Consider therefore the tropicalization $\Sigma^{\log}$ of $\MLog_{1,\alpha}(\PP^m|H,d)$, identified as usual with the moduli space of tropical maps to $\RR_{\geq 0}$.
@@
 the cotangent class from the source curve of the collapsed and stabilised map.
-We arrive at the the recursion.
+We arrive at the recursion.
 
@@
 
-\begin{remark} This construction gives the natural logarithmic analogue of Gathmann's line bundle and section \cite[Construction 2.1]{Ga}.
-A benefit of the logarithmic approach is to make the computation of vanishing orders entirely combinatorial (see \S \ref{subsubsection splitting degree} below), circumventing the difficult technical calculation given by Gathmann.
+\begin{remark} This construction gives the logarithmic analogue of Gathmann's line bundle and section \cite[Construction 2.1]{Ga}.
+The logarithmic approach makes the computation of vanishing orders combinatorial (see \S \ref{subsubsection splitting degree} below), circumventing a difficult calculation given by Gathmann.
 \end{remark}
@@
 \begin{remark} For the reduced relative Gromov--Witten theory of $(\mathbb P^m,H)$ with only primary insertions, i.e.
-where all cohomological insertions in the invariants are pulled back along evaluation maps, computations can be carried out without an analysis of the factorisation condition; this follows from dimension considerations and leads to the main results in~\cite{Vre}.
-However if we wish to include descendant insertions, work with more general pairs, or produce cycle-level statements, an analysis of the tautological classes arising from the factorisation condition is crucial.
+where all cohomological insertions are pulled back along evaluation maps, computations can be carried out without an analysis of the factorisation condition; this follows from dimension considerations and leads to the main results in~\cite{Vre}.
+However, to include descendant insertions, work with more general pairs, or produce cycle-level statements, an analysis of the tautological classes arising from the factorisation condition is crucial.
 \end{remark}
@@
 
-\begin{lemma} \label{Lemma components are logarithmic divisors} Every irreducible component of $\Dcal_{1,\alpha,k}(\PP^m|H,d)$ is a codimension $1$ logarithmic stratum.\end{lemma}
+\begin{lemma} \label{Lemma components are logarithmic divisors} Every irreducible component of $\Dcal_{1,\alpha,k}(\PP^m|H,d)$ is a codimension $1$ stratum.\end{lemma}
 
@@
 Thus via the above procedure, we enumerate the components of $\Dcal_{1,\alpha,k}(\PP^m|H,d)$ in a combinatorial manner; the combinatorial type $\Delta$ allows us to describe the general element of such a component.
-The remainder of this section gives a recursive description of the components and a recursive computation of integrals over them.
+The remainder of this section describes the components and a recursive computation of integrals over them.
 
@@
 
-We now investigate the three types I, II and III separately, giving a recursive description of the boundary divisor in each case.
+We investigate the three types I, II and III separately, giving a recursive description of the boundary divisor in each case.
 For the remainder of this subsection, therefore, we fix a one-dimensional cone $\tau \in \Sigma_{1,\alpha}(\PP^m|H,d)$, let $\Dcal \subseteq \VZ_{1,\alpha}(\PP^m|H,d)$ be the associated logarithmic divisor, and assume that $\Dcal$ is contained in $\Dcal_{1,\alpha,k}(\PP^m|H,d)$ and is of type I, II or III.
@@
 We claim that $\sqC$ satisfies the factorisation property if and only if $\sqC_1$ does.
-This immediately implies the lemma.
+This implies the lemma.
 
@@
 Here we describe the degree of $\rho$ and calculate the vanishing order $\lambda_\Dcal$ of the section $s_k$ constructed in \S \ref{Section Gathmann line bundle}.
-This gives a complete recursive description of the terms appearing on the right-hand side of Theorem \ref{theorem recursion} which are of type I, II or III.
+This completely describes the terms appearing on the right-hand side of Theorem \ref{theorem recursion} which are of type I, II or III.
 
@@
 
-In summary, the contribution of each term $\lambda_\Dcal [\Dcal]$ is given by integrating over the appropriate fibre product and then multiplying the result by $\lambda_\Dcal \cdot \deg\rho = \prod_{i=1}^r m_i$.
-
-\subsection{Recursive description of the divisors: type $\dag$}\label{subsection C0 splitting} The treatment of the type I, II and III cases above is a fairly straightforward extension of the ideas of Vakil and Gathmann (albeit updated with logarithmic and tropical technology, which streamlines the presentation and simplifies the proofs).
-The remaining type $\dag$ case, however, is entirely new.
-In this section we provide a recursive description of these boundary divisors.
-This constitutes the technical heart of the paper.
-
-\subsubsection{Possible combinatorial types}\label{S:combinatorialdescription} A boundary divisor $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^m|H,d)$ is said to have \textbf{type $\dag$} if the core is assigned degree zero by the combinatorial type.
+In summary, the contribution of each term $\lambda_\Dcal [\Dcal]$ is given by integrating over the appropriate fibre product and multiplying the result by $\lambda_\Dcal \cdot \deg\rho = \prod_{i=1}^r m_i$.
+
+\subsection{Recursive description of the divisors: type $\dag$}\label{subsection C0 splitting} The treatment of the type I, II and III strata are direct extensions of ideas of  Gathmann--Vakil.
+The type $\dag$ case is entirely new.
+We provide a recursive description of such boundary divisors; this forms the technical heart of the paper.
+
+\subsubsection{Possible combinatorial types}\label{S:combinatorialdescription} A boundary divisor $\Dcal \subseteq \Dcal_{1,\alpha,k}(\PP^m|H,d)$ is said to have \textbf{type $\dag$} if the core is assigned degree zero.
 Divisors of this type occur as principal components in compactified torus bundles over strata in the space of relative maps.
-As a result, their combinatorial types exhibit very degenerate behaviour.
-Precisely, over the generic point of such a divisor, the target may expand multiple times, and the source tropical curve need not be bipartite with a single interior vertex; see the left-hand side of Figure \ref{fig:off_we_go} for a concrete example.
-We stress once again that such degenerate contributions are at the heart of the reduced theory and cannot be removed.
-
-We begin with a series of lemmas describing the combinatorial types of rays associated to divisorial loci $\Dcal$ of type $\dag$ contributing nontrivially to the Gromov--Witten invariants.
+As a result, their combinatorial types exhibit degenerate behaviour.
+Precisely, over the generic point of such a divisor, the target may expand multiple times, and the source tropical curve need not be bipartite with a single interior vertex.
+An instance of this can be seen the left hand side of Figure \ref{fig:off_we_go}: at first sight, the multiple expansions seen in the target appear to depict a high codimension stratum, but due to the alignment condition, which is required to pick out the main component, these lengths cannot be varied independently.
+The degenerate contributions are at the heart of the reduced theory and cannot be removed.
+
+The next two lemmas describe the combinatorial types associated to rays whose divisors $\Dcal$ have type $\dag$ and contribute nontrivially to the Gromov--Witten invariants.
 \begin{lemma} \label{lemma type C0 combinatorial types}
@@
 
-\begin{lemma}\label{lem:stable_vertices} All the vertices on the circle are stable (as opposed to semistable  vertices introduced by subdivision). \end{lemma}
+\begin{lemma}\label{lem:stable_vertices} All the vertices on the circle are stable i.e. they are not Galois covers of fibers of a component of an expansion.
+\end{lemma}
 
@@
 \begin{proof}[Proof of Lemma \ref{lemma type C0 combinatorial types}]
-Stability of maps to an expansion guarantees that at least one stable vertex lies over each vertex of the target.
-If there is more than one stable vertex, then we can show as in the proof of Lemma \ref{lem:combs} that the corresponding locus $\Fcal$ in the moduli space of unexpanded maps has high codimension, i.e.
+Stability of maps to an expansion requires that at least one stable vertex lies over each vertex of the target.
+If there is more than one stable vertex, then we show as in the proof of Lemma \ref{lem:combs} that the corresponding locus $\Fcal$ in the moduli space of unexpanded maps has high codimension, i.e.
 the collapsing map has fibres of positive dimension.
@@
 The first  factor can be described very concretely as the choice of a point $p$ of $H$, and $d$ lines through it.
-A very important observation is that, at least generically, the vertices which lie on the circle of radius $\delta$ and map to $0\in\mathbb R_{\geq 0}$ are automatically aligned.
+An important observation is that, generically, the vertices which lie on the circle of radius $\delta$ and map to $0\in\mathbb R_{\geq 0}$ are automatically aligned.
 Indeed, if $R_i$ denotes the $i$th tail of the curve, glued to $E$ at the node $q_i$, then the stable map provides us with identifications:
@@
 
-We can express the factorisation condition tautologically by combining the isomorphisms $\theta_{ij}$ above with the differential of $f$.
-We see that factorisation amounts to the vanishing of the following vector bundle map:
+We express the factorisation condition tautologically by combining the isomorphisms $\theta_{ij}$ above with the differential of $f$.
+Factorisation amounts to the vanishing of the following vector bundle map:
 \[T_{R_1,q_1}\xrightarrow{(1,\theta_{12}\ldots,\theta_{1d})}\bigoplus_{i=1}^d T_{R_i,q_i}\xrightarrow{\sum\circ\operatorname{d}\!f=\operatorname{d}\!z_1+\ldots\operatorname{d}\!z_{d-2}} {N_{H\cap\PP^{d-1}|\PP^{d-1}}}|_p.\]
@@
 to the locus $\widetilde\Dcal$.
-Toroidal geometry gives a construction of $\widetilde \Dcal$ as a compactification of a torus bundle over a locally closed stratum in $\overline\Mcal_{1,\alpha}(\PP^m|H,d)$.
+Toroidal geometry constructs $\widetilde \Dcal$ as a compactification of a torus bundle over a locally closed stratum in $\overline\Mcal_{1,\alpha}(\PP^m|H,d)$.
 \medskip
@@
 
-If $X$ and $W$ are merely logarithmic and not toroidal, there is an analogue of this. There exists a strict map
+If $X$ and $W$ are logarithmic but not toroidal, there is an analogue. There exists a strict map
 \[
@@
 Fix an irreducible stratum $\mathcal A_W$.
-In identical fashion to the paragraph above, this stack $\mathcal A_W$ possesses a logarithmic structure by restricting the divisors on $\mathcal A_X$ and taking the induced logarithmic structure.
+In identical fashion to the paragraph above, this stack $\mathcal A_W$ possesses a logarithmic structure by restricting the divisors on $\mathcal A_X$ to $\mathcal A_W$ and taking the induced logarithmic structure.
 This equips a logarithmic stratum $W\hookrightarrow X$ with a logarithmic structure by pullback from the Artin fan, mirroring the construction for toroidal embeddings above.
@@
 \begin{remark}
-Note that the inclusion of a stratum $W\hookrightarrow X$ is \textit{not} a logarithmic morphism.
-The pullback logarithmic structure on a closed stratum includes residual information about the (virtual) normal bundle directions; the construction above effectively removes these directions.
-Using the equivalence of Artin fans with cone complexes~\cite{CavalieriChanUlirschWise}, the above construction can be combinatorialised.
-Given a cone $\sigma$ in a cone stack $\Sigma$, its \textbf{star} consists of all cones of $\Sigma$ that contain $\sigma$; these naturally form a new cone complex.
-The associated Artin fan gives rise to the logarithmic structure on $W$ above.
+The inclusion of a stratum $W\hookrightarrow X$ is \textit{not} logarithmic.
+The pullback logarithmic structure on a closed stratum includes residual information about the normal bundle of the stratum; the construction above removes these directions.
+By the equivalence of Artin fans with cone stacks~\cite{CavalieriChanUlirschWise}, the above construction can be combinatorialised.
+Given a cone $\sigma$ in a cone stack $\Sigma$, its \textbf{star} consists of all cones of $\Sigma$ that contain $\sigma$; these naturally form a new cone complex whose Artin fan gives the logarithmic structure on $W$ above.
 \end{remark}
@@
 \noindent
-{\bf Flattening the map to $\Ecal$.} The morphism $\widetilde \Dcal\to \Ecal$ is not flat.
+{\bf Flattening the map.} The morphism $\widetilde \Dcal\to \Ecal$ is not flat.
 In order to push integrals forward, it will be convenient to flatten the map by blowing up $\Ecal$.
-This can be done in a universal manner, following~\cite{AK,Mol16}.
+This can be done universally~\cite{AK,Mol16}.
 
@@
 
-The combinatorics of the flattening can be described explicitly. Consider the map on tropicalizations
+The combinatorics of the flattening can made explicit. Consider the map on tropicalizations
 \[
@@
 
-This subdivision may be described explicitly.
-For this, it is convenient to employ the formalism of extended tropicalizations \cite{Thuillier,ACP}.
-The subdividing cones are obtained from cones in the star of $\tau$ under the limit $e_1=\cdots=e_r=\infty$\sidenote{Was $r$ called $\epsilon$ before?}.
-The cones in the star of $\tau$ are given by (in)equalities relating distances of pairs of vertices, and there are three cases to consider:
+This subdivision may be described explicitly by employing the formalism of extended tropicalizations, see for instance~\cite[Section~2]{ACP}.
+The subdividing cones are obtained from cones in the star of $\tau$ under the limit $e_1=\cdots=e_r=\infty$.
+Cones in the star of $\tau$ are given by (in)equalities relating distances of pairs of vertices, and there are three cases to consider:
 \begin{enumerate}
@@
 \begin{lemma}\label{lem:generic_proj_bundle}
-Generically over $\widetilde\Ecal$, the morphism $\widetilde \Dcal\to\widetilde\Ecal$ is the projectivisation of a tautological vector bundle.
+Generically over $\widetilde\Ecal$, the map $\widetilde \Dcal\to\widetilde\Ecal$ is a projectivised tautological vector bundle.
 \end{lemma}
@@
 In particular there are vertices $\plC_1,\ldots,\plC_r$ generically lying on the circle of radius $\delta$.
-The moduli space of attaching data for the elliptic singularity is the complement of the coordinate hyperplanes in:
+The moduli of attaching data for the elliptic singularity is the complement of the coordinate hyperplanes in:
 \begin{equation}\label{eqn:projectivebundle}
@@
 Since not all of them can be strictly positive, the resulting fan is that of a projective space.
-This gives us a fibrewise description of $\widetilde\Dcal\to\widetilde\Ecal$ over the generic point.
+This describes $\widetilde\Dcal\to\widetilde\Ecal$ fiberwise over the interior.
 
@@
 The toric geometry dictionary gives rise to an associated Cartier divisor.
-Alternatively\sidenote{worth moving to the preliminary section?}, for any logarithmic stack $X$, the natural coboundary map induced by $$0\to \mathcal O_X^\star\to M_X^\text{gp}\to \overline M_X^\text{gp}\to 0$$ associates a $\mathcal O_X^\star$-torsor to a global section of the characteristic sheaf.
+Alternatively, for any logarithmic stack $X$, the natural coboundary map induced by $$0\to \mathcal O_X^\star\to M_X^\text{gp}\to \overline M_X^\text{gp}\to 0$$ associates a $\mathcal O_X^\star$-torsor to a global section of the characteristic sheaf.
 
@@
 
-Here we explain the meaning of $\mathbb{T}$. Isolating the subcurve $C_0 \subseteq C$ gives rise to a morphism from $\widetilde\Dcal$ to the moduli space of radially aligned curves of genus one:
+We explain the meaning of $\mathbb{T}$. Isolating the subcurve $C_0 \subseteq C$ gives rise to a morphism from $\widetilde\Dcal$ to the moduli space of radially aligned curves of genus one:
 \begin{equation*} \widetilde\Dcal \to \VZ^{\text{rad}}_{1,n}.\end{equation*}
@@
 \end{proof}
-The content of Lemma \ref{lem:generic_proj_bundle} is that the choice of a point in the fibre of $\widetilde\Dcal \to \Ecal$ provides a natural identification between the inward-pointing tangent lines on the circle.
-According to Lemma \ref{lemma fibres of Odelta}, they can further be identified with the line bundle $\OO(\delta)\otimes \mathbb T^\vee$ on $\widetilde\Dcal$.
+The content of Lemma \ref{lem:generic_proj_bundle} is that the choice of a point in the fibre of $\widetilde\Dcal \to \Ecal$ provides an identification between the inward-pointing tangent lines on the circle.
+By Lemma \ref{lemma fibres of Odelta}, they can further be identified with the line bundle $\OO(\delta)\otimes \mathbb T^\vee$ on $\widetilde\Dcal$.
 %This identification amounts to a specific linear dependence relation between the tangent vectors, which gives a point in the moduli space of attaching data for the corresponding elliptic singularity \cite[\S 2.2]{SMY2}.
-After Corollary \ref{cor:maps_from_elliptic_sing}, we can therefore express the factorisation condition as the degeneracy of the following natural morphism of vector bundles on $\widetilde\Dcal$:
+Corollary \ref{cor:maps_from_elliptic_sing} therefore expresses the factorisation condition as the degeneracy of the following morphism of vector bundles on $\widetilde\Dcal$:
 \begin{equation*} \Sigma \operatorname{d}\!f \colon \OO(\delta)\otimes \mathbb T^\vee \to \ev_q^\st T H. \end{equation*}
@@
 Transversality follows by construction, because any stratum of the boundary on which $\Sigma \operatorname{d}\!f$ vanishes has been (blown up and) included into $\mathbb T \otimes \OO(-\delta)$ as a twist; in other words, the circle of radius $\delta$ always passes through at least one component which is not contracted by the map to the expansion.
-Now, if the vanishing locus of $\Sigma \operatorname{d}\!f$ does not contain any stratum of the boundary, then it is the closure of its intersection with the open stratum, which can be seen to be transverse.
+If the vanishing locus of $\Sigma \operatorname{d}\!f$ does not contain any stratum of the boundary, it is the closure of its intersection with the open stratum.
 Thus we obtain:
@@
 Thus we have proven \eqref{Odelta eqn}.
-This observation generalises, giving a precise relation between the intrinsically-defined line bundle $\OO(\delta)$ on $\widetilde\Dcal$ (which we use to impose the factorisation condition) and the the line bundles $T_i$ pulled back from $\Ecal$.
+This observation generalises, giving a precise relation between the intrinsically-defined line bundle $\OO(\delta)$ on $\widetilde\Dcal$ (which we use to impose the factorisation condition) and the line bundles $T_i$ pulled back from $\Ecal$.
 This allows us to express the Chern classes of $\OO(\delta)$ (and hence $V$) in terms of pull-backs of tautological classes from $\Ecal$ and boundary strata on $\widetilde\Dcal$, which is sufficient in order to compute integrals.
@@
 \end{itemize}
-It should be noted that the degeneracy loci of (B) are themselves Gathmann's comb loci \cite{Ga}, similar to the loci $\pazocal D$ that we are considering, only this time in genus $0$, and therefore recursively computable.
+It should be noted that the degeneracy loci of (B) are among Gathmann's comb loci \cite{Ga}, similar to the loci $\pazocal D$ that we are considering, but in genus $0$, and therefore recursively computable.
 \begin{lemma} 
@@
 
-Compare with \cite[\S 3.2]{VZ} for an analogous phenomenon in the non-relative case.
+See \cite[\S 3.2]{VZ} for an analogous phenomenon in the non-relative case.
 Clearly, these loci may be in excess with respect to the expected codimension of $V(s)$, that is $N-1$.
-These loci are logarithmic substrata; therefore, there exists a logarithmic blowup that principalises them.
+These loci are logarithmic strata, so there exists a logarithmic blowup that principalises them.
 We claim that $\widetilde\Dcal$ is one.
@@
 there are exceptional divisors $\widetilde \Xi_\Lambda$ corresponding to $\Xi_\Lambda$ in $\mathcal P$.
-Since the $\Xi_\Lambda$ exhaust all the excess-dimensional components of the vanishing locus of $s\in H^0(\mathcal P,W)$, the latter induces a section $\tilde s\in H^0(\widetilde\Dcal,W(-\Sigma_\Lambda \widetilde\Xi_\Lambda))$ by pullback and twisting, whose vanishing locus is dimensionally transverse to the boundary, and whose open part coincides with the generic point of $\Dcal$, therefore $V(\tilde s)=\Dcal$.
+The $\Xi_\Lambda$ exhaust the excess-dimensional components of the vanishing of $s\in H^0(\mathcal P,W)$, so the latter induces a section $\tilde s\in H^0(\widetilde\Dcal,W(-\Sigma_\Lambda \widetilde\Xi_\Lambda))$ by pullback and twisting; the vanishing locus is dimensionally transverse to the boundary, and on a dense open coincides with the generic point of $\Dcal$, therefore $V(\tilde s)=\Dcal$.
 
@@
 
-It is possible to push the formula further down to $\Ecal$, and applying \cite[\S3.1]{FUL} we obtain an expression for $[\Dcal]$ in terms of:
+It is possible to push the formula to $\Ecal$ and apply \cite[\S3.1]{FUL} to calculate $[\Dcal]$ in terms of:
 \begin{itemize}
@@
 
-This construction of the virtual fundamental class means that once we have established a recursion formula for $(\PP^m,H)$, it immediately pulls back to give a recursion formula for $(X,Y)$.
+This construction of the virtual fundamental class means that once we have established a recursion formula for $(\PP^m,H)$, it pulls back to give a recursion formula for $(X,Y)$.
 To be more precise, Theorem \ref{theorem recursion} holds \emph{mutatis mutandis}, with the same values of $\lambda_\Dcal$.
@@
 We assume that all genus zero and reduced genus one Gromov--Witten invariants of $X$ are known.
-From this starting data, we will apply our recursion formula to compute:
+From these starting data, we will apply our recursion formula to compute:
 \begin{enumerate}
@@
 Note that, unlike in the absolute case, in the relative case it may well be that the entire insertion is pulled back along a single forgetful map $\fgt_S$.
-The reduced rubber invariants of $\mathbb{P}$ are defined similarly (again using collapsed psi classes).
+The reduced rubber invariants of $\mathbb{P}$ are defined similarly, using collapsed psi classes.
 
@@
 
-\begin{remark} In the following discussion we will sometimes omit the adjective ``reduced'' when discussing genus one invariants, but it is always implicit; all genus one invariants we consider will be reduced.\end{remark}
-
-\subsection{Fictitious and true markings} The recursion procedure we outline is rather delicate.
-Roughly speaking, we will induct on the degree (meaning $Y\cdot\beta$), number of marked points and total tangency.
-We adopt Gathmann's point of view on relative Gromov--Witten theory \cite{Ga}, whereby only a subset of the contact points with the divisor are required to be marked; this allows for ``total tangency'' strictly smaller than $Y\cdot\beta$.
-
-In order to make sense of this in the logarithmic setting (in which all contact points must be marked), we introduce the concept of \textbf{fictitious markings}.
+\begin{remark} In the following discussion we may omit the adjective ``reduced'' when discussing genus one invariants, but it is always implicit; all genus one invariants we consider will be reduced.\end{remark}
+
+\subsection{Fictitious and true markings} Roughly speaking, we induct on the degree (meaning $Y\cdot\beta$), number of marked points and total tangency.
+We adopt Gathmann's point of view on the relative theory \cite{Ga}, where only a subset of the contact points with the divisor are required to be marked; this allows for ``total tangency'' strictly smaller than $Y\cdot\beta$.
+
+In order to make sense of this in the logarithmic setting (where all contact points must be marked), we introduce the concept of \textbf{fictitious markings}.
 Consider a moduli space $\VZ_{1,\alpha}(X|Y,\beta)$ of reduced relative stable maps and a corresponding integrand $\gamma$.
@@
 \begin{remark}[The base case]
-The base terms of the recursion all have $d=0$ and as such are easy to compute: the relative invariants of $(X,Y)$ are nothing but absolute invariants of $X$ (i.e.
-there are no tangency conditions), and the absolute invariants of $Y$ are given by obstruction bundle integrals over Deligne--Mumford spaces.
-The rubber invariants of $\mathbb{P}$ in degree zero are given by integrals over the main component of the double ramification cycle (in the rubber case there may be markings with tangency even for $d=0$, since $d$ only records the degree covering the base); this can likewise be computed as an integral over Deligne--Mumford space, by correcting the formula for the ordinary double ramification cycle \cite{Hain,JPPZ} by the obvious contribution from the boundary irreducible component (the observation which makes this easy to do in genus one is that the rubber moduli space is pure-dimensional, so that the virtual class is simply the sum of the fundamental classes of the irreducible components).
+The base terms of the recursion all have $d=0$ and are easily computed: the relative invariants of $(X,Y)$ are absolute invariants of $X$ (i.e.
+without specified tangency conditions), and the absolute invariants of $Y$ are given by obstruction bundle integrals over Deligne--Mumford spaces.
+The rubber invariants of $\mathbb{P}$ in degree zero are given by integrals over the main component of the double ramification cycle (in the rubber case there may be markings with tangency even for $d=0$, since $d$ only records the degree covering the base); this can likewise be computed as an integral over Deligne--Mumford space, by correcting the formula for the ordinary double ramification cycle \cite{Hain,JPPZ} by the obvious contribution from the boundary irreducible component (the observation that enables this in genus one is that the rubber moduli space is pure-dimensional, and the virtual class is simply the sum of the fundamental classes of the components).
 We will now explain how to perform each of the four inductive steps outlined above.\end{remark}
@@
 As noted above, we may assume that $d \geq 1$ which means that there exists a true marking $x_1$ with $\alpha_1 \geq 1$.
-We will decrease the tangency at $x_1$.
+We decrease the tangency at $x_1$.
 Consider the vector of tangency orders
@@
 \begin{equation}\label{step 1 recursion}\left( (\alpha_1-1)\psi_1 + \ev_1^\st Y\right) \tilde\gamma \cap [\VZ_{1,(\alpha-e_1) \cup (1)}(X|Y,\beta)] = \tilde\gamma \cap [\Dcal(1)].\end{equation}
-We first examine the left-hand side.
+We examine the left-hand side.
 The class $\psi_1$ differs from $\fgt_y^\st \psi_1$ by the locus where $x_1$ and $y$ are contained on a contracted rational bubble.
@@
 \end{equation}
-where $I$ is the invariant we are trying to compute. We will now show that the other terms may be expressed in terms of invariants computed earlier in the recursion.
+where $I$ is the invariant we are trying to compute. We now show that the other terms may be expressed in terms of invariants computed earlier in the recursion.
 
@@
 Thus for each fictitious marked point we obtain a locus isomorphic to $\VZ_{1,\alpha}(X|Y,\beta)$ and $\tilde\gamma$ restricts to $\gamma$ here (from the point of view of computing invariants, the fictitious marked points are indistinguishable, meaning that the contributions are all the same).
-Thus for each fictitious marked point (of which there is at least one, namely $y$) we get a contribution of $\alpha_1 I$ to the right-hand side of \eqref{step 1 recursion 2}, where as before $I$ is the invariant we are trying to compute.
+Thus for each fictitious marked point (of which there is at least one, namely $y$) we get a contribution of $\alpha_1 I$ to the right-hand side of \eqref{step 1 recursion 2}, where $I$ is the invariant we are trying to compute.
 \end{enumerate}\medskip
-The contributions of the type II loci only involve genus zero data and so can be computed algorithmically following \cite{Ga}.
-The contributions of the type $\dag$ loci are determined by genus zero data and tautological integrals on genus one Deligne--Mumford spaces, which can also be computed algorithmically using the string and dilaton equations.
+The contributions of the type II loci only involve genus zero data and can be computed algorithmically following \cite{Ga}.
+The contributions of the type $\dag$ loci are determined by genus zero data and tautological integrals on genus one Deligne--Mumford spaces, which can be computed algorithmically using the string and dilaton equations.
 
@@
 If the degree of the genus one piece is less than $d$ then we have a rubber invariant of strictly smaller degree.
-The only other possibility is that the entire curve is mapped into the divisor.
-In this case we may apply the projection formula with $\fgt_y$ to identify this with an integral over $\VZ_{1,m}(Y,\beta)$ for some (possibly large) number $m$ of marked points.
+The other possibility is that the entire curve is mapped into the divisor.
+In this case we apply the projection formula with $\fgt_y$ to identify this with an integral over $\VZ_{1,m}(Y,\beta)$ for some (possibly large) number $m$ of marked points.
 But by assumption there is another marked point $x_0$ with all of the insertions pulled back along $\fgt_{x_0}$, so a further application of the projection formula shows that this contribution vanishes.
-To conclude, we may rearrange \eqref{step 1 recursion 2} to obtain an expression of the form
+To conclude, we rearrange \eqref{step 1 recursion 2} to obtain an expression of the form
 \begin{equation*} \lambda I = \text{polynomial in previously computed invariants} \end{equation*}
-where $\lambda$ is an explicit scalar which is always nonzero; we have thus determined the forgetful relative invariant $I$, which completes Step 1.
+with $\lambda$ an explicit nonzero scalar; we have determined the forgetful relative invariant $I$, completing Step 1.
 
@@
 \end{center}
-which gives a contribution of
+which contributes
 \begin{equation*} d\cdot \gamma \cap [\VZ_{1,(d,\underbrace{0,\ldots,0}_{n-1})}(X|Y,\beta)]\end{equation*}
@@
 
-We have thus computed the reduced absolute invariant of $Y$ of degree $d$ and $n$ markings, which completes Step 2.
+Step 2, computing the reduced absolute invariant of $Y$ of degree $d$ and $n$ markings, is complete.
 
@@
 
-We first note the following important reduction: if there exists a relative marking $x_k$ such that all insertions are pulled back along $\fgt_{k}$, then we may apply the projection formula, together with the following identity (arising from the torsion in the Jacobian of an elliptic curve)
+We note the following important reduction: if there exists a relative marking $x_k$ such that all insertions are pulled back along $\fgt_{k}$, then we may apply the projection formula, together with the following identity (arising from the torsion in the Jacobian of an elliptic curve)
 \begin{equation*} (\fgt_{k})_\st [\VZ^{\leftrightarrow}_{1,\alpha}(\mathbb P|Y_0+Y_\infty,\beta)] = \alpha_k^2 \cdot [\VZ_{1,n+m-1}(Y,\beta)] \end{equation*}
@@
 
-We will make use of a recursion formula for rubber spaces analogous to the recursion formula for relative spaces used in Steps 1--3. Following \cite{EKatz}, there is a line bundle
+We make use of a recursion formula for rubber spaces analogous to the recursion formula for relative spaces used in Steps 1--3. Following \cite{EKatz}, there is a line bundle
 \begin{equation*} L_y^{\not\in \operatorname{bot}} \text{ on } \VZ^{\leftrightarrow}_{1,\alpha\cup (0)}(\mathbb P|Y_0+Y_\infty,\beta)\end{equation*}
@@
 As in \S \ref{Section Gathmann line bundle}, we can give a logarithmic interpretation of this: it corresponds to the piecewise-linear function on the tropical moduli space which associates, to every rubber tropical map, the distance between $\varphi(\sqC_y)$ and the leftmost vertex of the tropical target, where $\sqC_y$ is the vertex of the source curve containing the flag corresponding to $y$.
-Using this tropical description, we may easily calculate the vanishing orders of $s_y^{\not\in\operatorname{bot}}$ along the various components of $\Dcal(y)$, and show that
+Using this tropical description, we calculate the vanishing orders of $s_y^{\not\in\operatorname{bot}}$ along the various components of $\Dcal(y)$, and show that
 \begin{equation*}\cchern_1(L_y^{\not\in\operatorname{bot}}) = \Psi_0 - \ev_y^\st Y\end{equation*}
-where $\Psi_0$ is a target psi class (see also \cite{EKatzLB}, where similar results in the non-reduced setting are obtained, using different methods). From this, we obtain a rubber recursion formula
+where $\Psi_0$ is a target psi class (see \cite{EKatzLB} for an analogue in the standard theory). From this, we obtain a rubber recursion formula
 \begin{equation}\label{step 4 recursion} (\Psi_0 - \ev_y^\st Y)\cdot \tilde\gamma \cap [\VZ^{\leftrightarrow}_{1,\alpha\cup(0)}(\mathbb P|Y_0+Y_\infty,\beta)] = \tilde\gamma \cap [\Dcal(y)]\end{equation}
@@
 
-If we now compare $\psi_2$ with $\fgt_1^\st \psi_2$ we see that the difference is given by the locus where $x_1$ and $x_2$ belong to a collapsed rational piece.
+The difference between $\psi_2$ with $\fgt_1^\st \psi_2$ is given by the locus where $x_1$ and $x_2$ belong to a collapsed rational piece.
 The contribution of this locus consists of rubber invariants with strictly fewer relative markings, and hence is recursively known.
-So up to previously computed invariants, \eqref{step 4 recursion} becomes
+Up to previously computed invariants, \eqref{step 4 recursion} becomes
 \begin{equation}\label{step 4 recursion 2} \fgt_1^\st (-\alpha_2\psi_2 - \ev_y^\st Y)\tilde\gamma \cap [\VZ^{\leftrightarrow}_{1,\alpha\cup(0)}(\mathbb P|Y_0+Y_\infty,\beta)] = \tilde\gamma\cap[\Dcal(y)]\end{equation}
-and now the left-hand side can also be expressed in terms of previously computed invariants, via the projection formula. \medskip
+and the left side can be expressed via previously computed invariants, by the projection formula. \medskip
 
@@
 We therefore restrict to considering these cases.
-Denote the piece of the curve carrying all of the genus and degree by $C^\prime\subseteq C$.
+Denote subcurve carrying all of the genus and degree by $C^\prime\subseteq C$.
 \begin{enumerate}
@@
 \end{enumerate}
-We therefore conclude that the only contribution to the right-hand side of \eqref{step 4 recursion 2} which cannot be expressed in terms of previously computed invariants is a nonzero multiple of the invariant we were trying to compute.
+We conclude that the only contribution to the right-hand side of \eqref{step 4 recursion 2} which cannot be expressed in terms of previously computed invariants is a nonzero multiple of the invariant we were trying to compute.
 We thus compute the reduced rubber invariant of $\PP$ with degree $d$, $n$ relative markings and $m$ non-relative markings, which completes Step 4 and the recursion.

### 2020-11-20 EllipticSingularitiesSplitting.tex
Minor changes

@@
 The higher genus situation is more delicate, and substantial theory has been developed in recent years to treat the genus one case, both for its intrinsic geometry, and for higher genus insights.
-This began over a decade ago with pioneering work of Li, Vakil, and Zinger~\cite{redgone,VZ,LZ,lz2,zingerstvsred,zingred}, and was recently reinvigorated using ideas from singularity theory~\cite{BCM18,HL,SMY1,VISC} and logarithmic geometry~\cite{RSPW,RSPW2,BC20}.
+This began over a decade ago with pioneering work of Li, Vakil, and Zinger~\cite{redgone,VZ,LZ,lz2,zingerstvsred,zingred,HLN}, and was recently reinvigorated using ideas from singularity theory~\cite{BCM18,HL,SMY1,VISC} and logarithmic geometry~\cite{RSPW,RSPW2,BC20}.
 The result is a \textbf{reduced} Gromov--Witten theory, which removes degenerate contributions from the ordinary theory.
@@
 On the target side, it would be natural to generalise the method of degenerating tangency conditions to higher rank logarithmic structures.
+The techniques developed in \cite{MaximalContacts} are expected to play a role.
 When the target is a toric pair the problem is tied in with the enumerative geometry of well-spaced tropical curves~\cite{LR18,RSPW2,Speyer}.
@@
   \draw (1,0) node{$\vdots$};
-  \draw[->] (4,0) --node[below]{\color{blue} $d$} (6,0);
+  \draw[->] (4,0) --node[above]{\color{blue} \SMALL$d$} (6,0);
   \draw[blue,->] (0,-2)--(6,-2);
@@
 \subsection{Reduced absolute, relative and rubber invariants} To be precise: by a reduced invariant of $Y$ we mean an integral over $\VZ_{1,n}(Y,\beta)$ of a product of evaluation classes and pullbacks of psi classes along morphisms forgetting subsets of the marked points:
-\begin{equation*} \int_{\virt{[\VZ_{1,n}(Y,\, \beta)]}} \prod_{i=1}^n \fgt_{S_i}^\star \psi_i^{k_i} \cdot \ev_i^\star \gamma_i.\end{equation*}
-(Here $S_i \subseteq \{1,\ldots,n\}$ with $i \not\in S_i$ for all $i$; taking $S=\emptyset$ gives the ordinary  psi classes.).
+\begin{equation*} \int_{\virt{\VZ_{1,n}(Y,\, \beta)}} \prod_{i=1}^n \fgt_{S_i}^\star \psi_i^{k_i} \cdot \ev_i^\star \gamma_i.\end{equation*}
+Here $S_i \subseteq \{1,\ldots,n\}$ with $i \not\in S_i$ for all $i$; taking $S=\emptyset$ gives the ordinary  psi classes.
 The evaluation maps are viewed as mapping into $X$ (hence the adjective ``restricted'').
 Reduced relative invariants of $(X,Y)$ are defined in the same way
-\begin{equation*} \int_{\virt{[\VZ_{1,\alpha}(X|Y,\, \beta)]}} \prod_{i=1}^n \fgt_{S_i}^\star \psi_i^{k_i} \cdot \ev_i^\star \gamma_i\end{equation*}
+\begin{equation*} \int_{\virt{\VZ_{1,\alpha}(X|Y,\, \beta)}} \prod_{i=1}^n \fgt_{S_i}^\star \psi_i^{k_i} \cdot \ev_i^\star \gamma_i\end{equation*}
 except now the forgetful morphism maps into a space of absolute stable maps:
@@
 But since $\VZ_{1,n}(H,1)=\emptyset$ as noted in Remark~\ref{rem: constant-maps}, it follows that $\VZ_{1,n}(Y,\beta)=\emptyset$ if $d=Y\cdot\beta=1$, so we may assume $d \geq 2$ in this step.
-
 Step 2, computing the reduced absolute invariant of $Y$ of degree $d$ and $n$ markings, is complete.

### 2020-11-20 EllipticSingularitiesSplitting.tex
typos

@@
 \]
-is log \'etale by the lifting cirterion, as in~\cite[Theorem~5.3.4]{MW17}. The result is a consequence. 
+is log \'etale by the lifting criterion, as in~\cite[Theorem~5.3.4]{MW17}. The result is a consequence. 
 \end{proof}
@@
 Since not all of them can be strictly positive, the resulting fan is that of a projective space.
-This describes $\widetilde\Dcal\to\widetilde\Ecal$ fiberwise over the interior.
+This describes $\widetilde\Dcal\to\widetilde\Ecal$ fibrewise over the interior.
 

### 2021-03-28 Response to referee/AG Genus One Response to Referee.tex
Imported Dhruv v2 submmited to AG

@@
 
-\noindent We thank the referee for their careful reading of our paper, and their many valuable suggestions which have greatly helped in improving the quality of the exposition.
+\noindent We thank the referee for their careful reading of our paper, and the many valuable suggestions which have greatly helped in improving the quality of the exposition.
 
-We have made many improvements to the paper which directly address the referee's comments, without exceptions.
+We have made many improvements to the paper in order to directly address the referee's comments, without exceptions.
 Following their suggestion, we have also gone through and made additional changes, in order to improve the readability and appeal to a wider audience.
@@
 \begin{enumerate}
-	\item An improved introduction (see \S\S 1.1--1.5), explicating the connection between logarithmic structures and moduli of Gorenstein singularities which is a key geometric ingredient in the paper.
-In particular, this includes working definitions of the background material.
-	\item The introduction has also been streamlined to better reflect the growing body of work on the connections between curve singularities, logarithmic structures and stable maps.
+	\item The introduction has been streamlined to better reflect the growing body of work on the connections between curve singularities, logarithmic structures and stable maps.
+	\item An improved background section (see \S\S 1.1--1.5), explicating the connection between logarithmic structures and moduli of Gorenstein singularities, which is a key geometric ingredient in the paper.
+In particular, we have included working definitions of the background material.
 	\item The argument proving Theorem 1.9 has been reworked to have a clearer logical structure, with additional details. 
@@
 
-\subsection*{Additional minor changes}
-\begin{enumerate}
-\item The term ``special rubber'' used at the start of Step 2 is an anachronism from a draft version of the paper, and has been removed.
-\end{enumerate}
+%\subsection*{Additional minor changes}
+%\begin{enumerate}
+%\item The term ``special rubber'' used at the start of Step 2 is an anachronism from a draft version of the paper, and has been removed.
+%\end{enumerate}
 

### 2021-03-28 EllipticSingularitiesSplitting.tex
Imported Dhruv v2 submmited to AG

@@
 The higher genus situation is more delicate, and substantial theory has been developed in recent years to treat the genus one case, both for its intrinsic geometry, and for higher genus insights.
-This began over a decade ago with pioneering work of Li, Vakil, and Zinger~\cite{redgone,VZ,LZ,lz2,zingerstvsred,zingred,HLN}, and was recently reinvigorated using ideas from singularity theory~\cite{BCM18,HL,SMY1,VISC} and logarithmic geometry~\cite{RSPW,RSPW2,BC20}.
+This began over a decade ago with pioneering work of Li, Vakil, and Zinger~\cite{redgone,VZ,LZ,lz2,zingerstvsred,zingred}, and was recently reinvigorated using ideas from singularity theory~\cite{BCM18,HL,SMY1,VISC} and logarithmic geometry~\cite{RSPW,RSPW2,BC20}.
 The result is a \textbf{reduced} Gromov--Witten theory, which removes degenerate contributions from the ordinary theory.
@@
 
-\subsection{Context and techniques} The present work is part of a larger ongoing program relating to the role of curve singularities in Gromov--Witten theory that go beyond the well-studied nodal case~\cite{BC20,BCM18,Boz19,RSPW,RSPW2}.
-The basic motivation for this direction is that such alternative curve counting theories can often be more {enumerative} in nature and satisfy Lefschetz section theorems.
+\subsection{Context and techniques} The present work is part of a larger ongoing program relating to the role of curve singularities and alternate compactifications in Gromov--Witten theory that go beyond the well-studied geometry of stable maps from nodal curves~\cite{BC20,BCM18,Boz19,HLN,RSPW,RSPW2}.
+The motivation for this direction is that such alternative curve counting theories can often be more {enumerative} in nature and satisfy Lefschetz section theorems.
 Degeneration methods are a crucial tool in Gromov--Witten theory, and our results point to a fruitful use of these methods in this direction.
@@
 The space $ \operatorname{Obs}(f/(C,\delta_B,f_B))$ always has rank $1$.
-Next, note that once the collapsed stable map is fixed, there are no nontrivial \textit{logarithmic} deformations of the map to $\mathbb P^m[s]$: the morphism from logarithmic maps to ordinary maps is finite~\cite[\S~3.7]{ChenLog}.
-Therefore, we may view the logarithmic deformation spaces of $f$ as a subspace of the logarithmic deformation spaces of $(C^\prime,\delta_B,f_B^\prime)$, consisting of those deformations with vanishing class in $\operatorname{Obs}(f/(C,\delta_B,f_B))$.
-The data $(C^\prime,\delta_B,f_B^\prime)$ have unobstructed deformations, so this subspace is everywhere of the expected dimension.
-The obstructions to logarithmic deformations of $f$ vanish, and we conclude.
+Next, note that once the collapsed stable map is fixed, there are no \textit{logarithmic} deformations of the map to $\mathbb P^m[s]$: the morphism from logarithmic maps to ordinary maps is finite~\cite[\S~3.7]{ChenLog}.
+View the logarithmic deformation spaces of $f$ as subspace of the logarithmic deformation spaces of $(C^\prime,\delta_B,f_B^\prime)$, consisting of those deformations with vanishing class in $\operatorname{Obs}(f/(C,\delta_B,f_B))$.
+The map to this obstruction group is everywhere surjective, and since the data $(C^\prime,\delta_B,f_B^\prime)$ have unobstructed deformations, this subspace is everywhere of the expected dimension.
+Obstructions to logarithmic deformations of $f$ vanish, and we conclude.
 \end{proof}
@@
 \begin{proof}
-Since $\VZ_{1,\alpha}(\mathbb P^m|H,d)$ is logarithmically smooth, it will suffice to show that the cones of its tropicalization are simplicial.
+Since $\VZ_{1,\alpha}(\mathbb P^m|H,d)$ is logarithmically smooth, we must show that the cones of its tropicalization are simplicial.
 Consider a logarithmic stable map to an expansion $C\to \mathbb P^m[s]$ without a central alignment.
@@
 We conclude that the blowup $\widetilde{\VZ}^{\mathrm{exp}}_{1,\alpha}(\mathbb P^m|H,d)$ obtained by centrally aligning Kim's spaces has simplicial cones.
-The morphism $\VZ_{1,\alpha}(\mathbb P^m|H,d)\to \widetilde{\VZ}^{\mathrm{exp}}_{1,\alpha}(\mathbb P^m|H,d)$ is strict, so the cones of $\VZ_{1,\alpha}(\mathbb P^m|H,d)$ are simplicial, as claimed.
+The morphism $\VZ_{1,\alpha}(\mathbb P^m|H,d)\to \widetilde{\VZ}^{\mathrm{exp}}_{1,\alpha}(\mathbb P^m|H,d)$ is strict, so the cones of $\VZ_{1,\alpha}(\mathbb P^m|H,d)$ are simplicial.
 \end{proof}
@@
 \begin{proof}
-We first consider the statement of the lemma in the category of fine but not necessarily saturated logarithmic schemes, so that a relative stable map to an expansion admits a unique logarithmic lifting.
+We consider the statement of the lemma in logarithmic schemes, so that a relative stable map to an expansion admits a unique logarithmic lifting, and later saturate the structures.
 The fibre product description preceding the lemma is an isomorphism in this category~\cite[Lemma~4.2.2]{AbramovichMarcusWiseComparison}.
@@
 \begin{remark}[Splitting degree and vanishing order, revisited] Similarly to \S \ref{subsubsection splitting degree} above, we can calculate the degree of $\rho$ and the vanishing order $\lambda_{\Dcal}$ of the section $s_k$ along $\Dcal$.
-The degree of $\rho$ is given exactly as in Lemma \ref{lem:saturation}, where now we obtain one such factor for each bounded edge of the tropical target.
-The vanishing order $\lambda_{\Dcal}$ is slightly more combinatorially delicate, but may be computed as the index of an explicit morphism of one-dimensional lattices, as explained in the proof of Lemma \ref{lemma vanishing order}.
+The degree of $\rho$ is given exactly as in Lemma \ref{lem:saturation}, where we obtain one such factor for each bounded edge of the tropical target.
+The vanishing order $\lambda_{\Dcal}$ is more delicate, but may be computed as the index of an explicit morphism of one-dimensional lattices, explained in the proof of Lemma \ref{lemma vanishing order}.
 \end{remark}

### 2021-03-28 EllipticSingularitiesSplitting.tex
Added keywords etc.

@@
 
+\footnotetext{\emph{2020 Mathematics Subject Classification.} Primary: 14N35.
+Secondary: 14H10.\\ \emph{Keywords:} enumerative geometry, logarithmic Gromov--Witten theory, elliptic singularities, quantum Lefschetz.}
+
 \noindent The Kontsevich space of stable maps from genus zero curves to projective space exhibits remarkable geometry -- it is a smooth orbifold with a ``self-similar'' normal crossings boundary.
@@
 \noindent Luca Battistella\\
-Mathematisches Institut, Universit\"at Heidelberg \\
+Mathematisches Institut, Ruprecht-Karls-Universit\"at Heidelberg, Im Neuenheimer Feld 205, 69120 Heidelberg, Germany \\
 \href{mailto:lbattistella@mathi.uni-heidelberg.de}{lbattistella@mathi.uni-heidelberg.de}\\
@@
 \noindent Navid Nabijou \\
-Department of Pure Mathematics and Mathematical Statistics, University of Cambridge \\
+Department of Pure Mathematics and Mathematical Statistics, University of Cambridge, Centre for Mathematical Sciences, Wilberforce Road, Cambridge CB3 0WB, United Kingdom \\
 \href{mailto:nn333@cam.ac.uk}{nn333@cam.ac.uk}\\
@@
 \noindent Dhruv Ranganathan \\
-Department of Pure Mathematics and Mathematical Statistics, University of Cambridge \\
+Department of Pure Mathematics and Mathematical Statistics, University of Cambridge, Centre for Mathematical Sciences, Wilberforce Road, Cambridge CB3 0WB, United Kingdom \\
 \href{mailto:dr508@cam.ac.uk}{dr508@cam.ac.uk}
